### 2014-02-24 qfenv_paper/qf_environment.tex
QF environment paper added

\documentclass{emulateapj}
\bibliographystyle{apj}

%define general packages
\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{footnote}
\usepackage{courier}

%internal short cuts
\def \HgA {H$\gamma_A$}
\def \gon {Gonz\'{a}lez}
\def \Hbp {H$\beta ^\prime$}

\begin{document}

\title{PRIMUS: Quiescent Fraction as a Function of Environment and Redshift}
\author{ChangHoon Hahn, Michael Blanton, John Moustakas}

\begin{abstract}
We examine the evolution of the quiescent fraction, for galaxies in 
different density environments from $z=0.2-0.8$, using spectroscopic 
redshift and multi-wavelength imaging data from PRism MUlti-object 
Survey (PRIMUS) and the Sloan Digitial Sky Survey (SDSS). Using this 
data we construct a stellar mass limited target galaxy population of 
$40430$ galaxies from PRIMUS within redshift range $0.2-1.0$ and $106732$
galaxies from SDSS within redshift range $0.06-0.145$. This population 
is then classified as quiescent or star-forming using an evolving cut 
based on specific star-formation rate. The environment of the target 
population is then measured using a fixed cylindrical aperture method 
on a volume-limited {\em Environment Defining Population} constructed
from PRIMUS and SDSS.

Thresholds for the environment are imposed to classify the target galaxies as
high, mid, or low environments. For the quiescent and star-forming 
target galaxies we calculate the stellar mass functions in different environments and redshift.
Afterwards, we compute the quiescent fraction (QF) using the SMFs for the different environment 
and redshift ranges.  Comparing the QFs in these environment and redshift bins, we find the 
QF increases over time (decrease in redshift); however, the change of 
the QFs for the different environments are independent of the 
environment of galaxies. 
\end{abstract}

%Section heading
\section{Introduction}
Galaxies, in their detailed properties, carry the imprints of their
surroundings, with a strong dependence of the quiescent fraction of
galaxies on their local environment (e.g. \citealt{hubble36a,
oemler74a, dressler80a, hermit96a, guzzo97a}; for a recent review see
\citealt{blanton09a}).  The strength of this dependence is itself a
strongly decreasing function of galaxy stellar mass; at the extreme,
the lowest masses ($<10^{9}$ $M_\odot$) galaxies are quenched only in
dense regions, and never in isolation (\citealt{geha12a}).  These
effects vary with redshift at least in the densest clusters, as
observed in the changing fraction of late-type spirals relative to the
field found in studies of the morphology-density relation
(\citealt{dressler84a, desai07a}).  Clearly understanding the
properties of galaxies in the present-day universe requires a careful
investigation of the role of environment, and how that role changes
over time.

Nevertheless, the evolution of the role of environment is a relatively
subtle effect and difficult to study.  Although history of galaxies
prior to $z\sim 1$ appears to have been one of rapid assembly, since
that time the galaxy population has continued to evolve, but less
dramatically. Although there are detectable changes in the population,
the major classes of galaxies existed at $z\sim 1$, in roughly the
same relative numbers as today (\citealt{bundy06a, borch06a,
taylor09a, moustakas13a}. Furthermore, at those redshifts we can also
detect the dependence of galaxy properties on environment, with lower
star-formation rate early-type galaxies populating the denser regions
(\citealt{cooper08a, patel09a, kovac10a}).

The most dramatic change in galaxy properties during the past eight
billion years has been a remarkable decline in the star-formation rate
of galaxies in the Universe (\citealt{hopkins06a}).  This decline
appears dominated by decreases in the rates of star-formation of
individual galaxies (\citealt{noeske07a}). There is evidence that a
large fraction of the decline associated with strongly
infrared-emitting starbursts (\citealt{bell05a, magnelli09a}).  The
decline does not appear to be due to the quenching of a large
fractions of the star-forming population, as reflected in observations
of the stellar mass function of quiescent and star-forming galaxies
(\citealt{blanton06a, bundy06a, borch06a, moustakas13a}).  These
findings leave little room for the participation of
environmentally-driven quenching in the global census of
star-formation.  As \citet{cooper08a} and others have pointed out,
because the environmental dependence of total star-formation rates at
fixed redshift is relatively small, environmentally effects are
unlikely to cause the overall star-formation rate decline.

Thus, the impact of environment on galaxy formation has to be
interpreted on top of the background of this overall decline affecting
galaxies in all environments.  The most straightforward investigation
of would directly determine the star-forming properties of galaxies as
a function of environment, stellar mass and redshift in a single,
consistently analyzed data set. This analysis can reveal how galaxies
are quenched in the universe over time, quantitatively establish the
contribution of environmental effects to the overall trends, and
reveal whether those trends happen equally in all environments.
However, such an analysis has not been done previously due to the lack
of sufficiently large samples. In this paper, we apply this approach
using the Prism Multi-object Survey (PRIMUS; \citealt{coil11a,
cool13a}), the largest available redshift survey covering the epochs
between $0<z<1$.

\section{Sample Selection}
In this paper we are interested in measuring the quiescent fraction over a wide range of redshifts and for galaxies in different environments. 
To do so, we use galaxies at intermediate redshifts from PRIMUS and galaxies at low redshift from SDSS.

We begin with a brief summary of the PRIMUS data in Section~\ref{sec:primus} followed by a summary of the SDSS data in Section~\ref{sec:sdss}.
Then in Section~\ref{sec:target} we use this data to define the stellar mass complete target galaxy population.
Afterwards, in Section~\ref{sec:sfq}, we classify these target galaxies as quiescent or active star-forming galaxies. 
Then for each of the classified target galaxies, in Section \ref{sec:environment}, we obtain the environment using a volume-limited {\em Environment Defining Population}.
Finally in Section \ref{sec:edgeeffect}, we correct the target galaxy environment for the survey edge effects.

\subsection{PRIMUS} \label{sec:primus}
For galaxies at intermediate redshifts we use multiwavelength imaging and spectroscopic redshifts data of PRIMUS, which is a faint galaxy survey with precise spectroscopic redshifts ($\sigma_z/(1+z) \approx 0.5 \%$) for $\sim 120,000$ galaxies within redshifts $z \approx 0-1.2$.
The survey was conducted using a IMACS spectrograph on a Magellan I Baade $6.5$ m telescope with a slitmask and low dispersion prism.
For further details on the PRIMUS observation methods, including survey design, targeting, and data summary, we refer readers to the survey papers: \cite{Coil:2011aa} and \cite{Cool:2013aa}.

As done in \cite{Moustakas:2013aa}, we only use fields targeted by PRIMUS with $GALEX$ and {\em Spitzer}/IRAC imaging.
This restricts us to five fields.
Four of these fields are a part of the {\em Spitzer} Wide-area Infrared Extragalactic Survey (SWIRE\footnote{http://swire.ipac.caltech.edu/swire/swire.html} ): 
the European Large Area ISO Survey - South $1$ field (ELAIS-S1\footnote{http://dipastro.pd.astro.it/esis}), the Chanddra Deep Field South SWIRE field (CDFS), 
and the XMM Large Scale Structure Survey field (XMM-LSS).
The XMM-LSS consists of two separate but spatially adjacent fields: the Subaru/XMM-Newton DEEP Survey fied (XMM-SXDSS\footnote{http://www.naoj.org/cience/SubaruProject/SDS})
and the Canadian-France-Hawaii Telescope Legacy Survey field (XMM-CFHTLS\footnote{http://www.cfht.hawaii.edu/Science/CFHLS}).
In addition to the SWIRE fields we also include the COSMOS\footnote{http://cosmos.astro.caltech.edu} field for a total of five fields.

In all of the PRIMUS target fields we have near-UV (NUV) and far-UV (FUV) measurements from the {\em GALEX} Deep Imaging Survey (DIS; CITECITE ). 
To minimize contamination from neighboring sources, we use a Bayesian photometric code EM$_{\rm{PHOT}}$ (based on expectation maximization algorithm of CITECITE ). 
Furthermore, we use ground-based optical and {\em Spitzer}/IRAC mid-infrared photometric catalogs in each of the fields to obtain integrated fluxes in all 
photometric bands.
To summarize, the general strategy employed is to use a circular aperture photometry to constrain the shape of the SED and then fixing the overall normalization to 
a estimate of the total magnitude in the detection band. 
\cite{Moustakas:2013aa} provides a detailed description of the calculation for each of our target fields.

From the spectroscopic redshift and photometry described above, we use \texttt{iSEDfit} to determine stellar masses, star formation rates (SFRs) and other physical properties
in a simplified Bayesian framework.
\texttt{iSEDfit}, which we will only briefly mention in this paper is discussed in detail in Appendix A of \cite{Moustakas:2013aa}.
The code uses the redshift and the observed photometry of the galaxies to determine the statistical likelihood of a large ensemble of generated model SEDs. 
These generated model SEDs depend on population synthesis models and prior parameters.
In order to derive our fiducial stellar masses and star formation rates, we use the Flexible Stellar Population Synthesis (FSPS) models (CITECITE) based on the Chabrier (2003) IMF. 
Other prior parameters are listed in Section 4.1 of \cite{Moustakas}. 
The photometric bands we use for the fitting in our PRIMUS data are the {\em GALEX} FUV and NUV, the two shortest IRAC bands at $3.6$ and $4.5 \mu \rm{m}$, and the five optical bands
(in the COSMOS field, we fit seven optical bands and near-infrared bands, see Section 2.3 of \cite{Moustakas:2013aa}).
For a more detailed description of the data used in this paper, we refer readers to \cite{Moustakas:2013aa} Section 2 and Section 4.1.

\subsection{SDSS-GALEX} \label{sec:sdss}
For galaxies at low redshifts we use the SDSS Data Release 7 (DR7; CITECITE). 
From the SDSS DR7 data, which provides high fidelity $ugriz$ photometry and spectroscopic redshift, we specifically use galaxies from the New York University 
Value-Added Galaxy Catalog that satisfy the main sample criterion (CITECITE) and have galaxy extinction corrected (CITECITE) Petrosian magnitudes $14.5 < r < 17.6$ 
and spectroscopic redshits $0.01<z<0.2$. 
Within this sample, we select galaxies with medium depth observations from GALEX. 
This is done by first retrieving the positions of all {\em GALEX} tiles from GALEX Release 6 with total exposure time greater than $1$ ks and then constructing 
a joint angular selection function of the SDSS-{\em GALEX} Sample. 
This results in a final sample of $167,727$ SDSS galaxies with {\em GALEX} imaging.

For this final sample, we use the MAST/CasJobs\footnote{http://galex.stsci.edu/casjobs} interface and a $4''$ diamater search radius to obtain the NUV and FUV photometry. 
For the optical photometry we use $ugriz$ bands (from the SDSS \texttt{model} magnitudes) scaled to the $r$-band \texttt{cmodel} magnitude. 
We supplement the above UV and optical photometry with integrated $JHK_s$ magnitudes from the 2MASS Extended Source Catalog (XSC; CITECITE) and with photometry at $3.4$ 
and $4.6 \mu \rm{m}$ from the WISE All-Sky Data Release\footnote{http://wise2.ipac.caltech.edu/docs/release/allsky}. 
Further details on the photometry of the SDSS data used in this paper is provided in \cite{Moustakas:2013aa} Section 2.4.

To obtain the stellar masses and SFRs for the SDSS data, we use \texttt{iSEDfit} as done in Section \ref{sec:primus}. 
Except we use twelve photometric bands: {\em GALEX} FUV and NUV, SDSS $ugriz$, 2MASS $JHK_{s}$, and WISE $3.4$ and $4.6 \mu \rm{m}$.

\subsection{Galaxy Sample} \label{sec:target} 
In this seciton we will define the galaxy sample we use for our SMFs and QFs.
The population at intermediate redshift is derived from the PRIMUS data and the population at low redshift is derived from the SDSS data, both described above.
For the intermediate redshift target galaxy population, we begin with the selection criteria imposed in \cite{Moustakas:2013aa} for its parent sample.
We take the statistically complete {\em primary} sample from the PRIMUS data, \cite{Coil:2011aa}, and then we impose magnitude limits on optical selection bands as specified in 
\cite{Moustakas:2013aa} (listed in its Table 1).
These limits are in different optical selection bands and have different values for our five PRIMUS target fields.
Next, we join the PRIMUS, {\em GALEX}, and IRAC window functions to construct the angular selection function.
We then exclude stars and broad-line AGN to only select objects spectroscopically classified as galaxies, with high-quality spectroscopic redshifts ($Q \geq 3$) within the 
redshift range $0.2 - 1.0$.
Afterwards we assign statistical weights (described in \cite{Coil:2011aa} and \cite{Cool:2013aa}) to the objects in order to correct for targeting incompleteness and redshift 
failures.
The statistical weight, $w_i$, for each galaxy is given by
\begin{equation}
w_{i} = (f_{\rm{target}} \times f_{\rm{collision}} \times f_{\rm{success}})^{-1},
\end{equation}
Equation 1 in \cite{Moustakas:2013aa}.
In addition to the selection criteria above, we impose stellar mass limits to have a stellar mass complete sample.  
Stellar mass completeness limits for a magnitude-limited survey such as PRIMUS is a function of redshift, apparent magnitude limit of the survey, and the typical stellar 
mass-to-light ratio of galaxies near the flux limit.

As done in \cite{Moustakas:2013aa}, we follow \cite{Pozzetti:2010aa} to empirically determine the stellar mass completeness limits.
Briefly, for each of the target galaxies we compute $\mathcal{M}_{\rm{lim}}$ using $log \mathcal{M}_{\rm{lim}} = log \mathcal{M} + 0.4 ( m - m_{\rm{lim}})$.
$\mathcal{M}$ is the stellar mass of the galaxy in units of $\mathcal{M_{\odot}}$, $\mathcal{M}_{\rm{lim}}$ is the stellar mass of each galaxy if its magnitude was 
equal to the survey magnitude limit, $m$ is observed apparent magnitude in the selection band, and $m_{\rm{lim}}$ is the magnitude limit for our five fields mentioned above.
We construct a cumulative distribution of $\mathcal{M}_{\rm{lim}}$ for the $15\%$ faintested galaxies in $\Delta z=0.04$ redshift bins.
In each of these redshift bins, we calculate the minimum stellar mass that includes $95 \%$ of the galaxies.
Separately for quiescent and star-forming galaxies, we fit quadratic polynomials to the minimum stellar masses versus redshift (classificiation scheme for quiescent 
and star-forming galaxies is included in the following section).
Finally, we use these polynomials to obtain the minimum stellar masses at the center of the redshift bins, $0.2-0.4$, $0.4-0.6$, $0.6-0.8$, and $0.8-1.0$.
Note that these redshift bins will later be used to divide the target population during SMF and QF calculations.

For our target galaxy population at low redshift we use our SDSS-{\em GALEX} data. 
We limit our target population within the redshift range $0.06-0.145$ due to redshift limits later imposed for the volume-limited Environment Defining Population (\ref{sec:environment}).
The NYU-VAGC provides statistical weight estimates for targeting completeness.
In order to have a stellar mass complete low redshift target population, we use a uniform stellar mass limit of $10^9 \mathcal{M}_{odot}$, which is above the surface 
brightness and stellar mass-to-light ratio completness limits (CITECITE).
The absolute magnitude ($M_g$) versus redshift for the target galaxy population at both low redshift and intermediate redshift is plotted in Figure \ref{fig:targetEDP}.
We again refer readers to \cite{Moustakas:2013aa} for details; more specifically, Figure 2., Sections 3.1, and 4.3.

\subsection{Classifying Quiescent and Star-Forming Galaxies} \label{sec:sfq}
We classify the galaxies from the target sample, defined in the last section, using an evolving cut based on specific star-formation rate utilized in \cite{Moustakas:2013aa}.
For a detailed description of the classification scheme, we refer readers to Section 3.2 in \cite{Moustakas:2013aa}.

To summarize, this classification method utilizes the star-forming (SF) sequence, which is the correlation between star-formation rate (SFR) and stellar mass in star-forming 
galaxies observed at least until $z \sim 2$.
As stated in \cite{Moustakas:2013aa}, the PRIMUS sample displays a well-defined SF sequence within the redshift range of our target population.
Using the power-law slope for the SF sequence derived by \cite{Salim:2007aa} (SFR $\propto \mathcal{M}^{0.65}$) and the minimum of the quiescent/star-forming bimodality, 
determined by eye, we obtain the following equation to classify the target galaxies (Equation 2 in \cite{Moustakas:2013aa}):
\begin{equation}
\label{eq:qsfclass} 
\rm{log}(\rm{SFR}_{\rm{min}}) = -0.49 + 0.64 \rm{log}(\mathcal{M} - 10) +1.07(z-0.1), 
\end{equation}
where $\mathcal{M}$ is the stellar mass of the galaxy.
If the target galaxy SFR and stellar mass place the galaxy above Equation \ref{eq:qsfclass} we classify it as star-forming; if below, as quiescent (\cite{Moustakas:2013aa} Figure 1.).

\begin{table*} %Will contain much more information on environments. 
  \caption{Subsample}
  \label{tab:subsample}
  \begin{center}
    \leavevmode
    \begin{tabular}{lllll} \hline \hline              
  Survey    &Redshift ($z$) &Environment    &Quiescent $N_{\rm{g}}$ &Star-forming $N_{\rm{g}}$  \\ \hline 
  SDSS      &$0.0375-0.145$ &High           &5470                       &4501                           \\
            &               &Mid            &3614                       &4438                           \\
            &               &Low            &5419                       &8927                           \\
            &               &               &                       &                           \\ \hline
  PRIMUS    &$0.2-0.4$      &High           &322                    &583                           \\
            &               &Mid            &177                    &403                          \\
            &               &Low            &768                    &2516                           \\
            &               &               &                       &                           \\ \hline
  PRIMUS    &$0.4-0.6$      &High           &350                       &675                           \\
            &               &Mid            &195                       &405                           \\
            &               &Low            &871                       &2385                           \\
            &               &               &                       &                           \\ \hline
  PRIMUS    &$0.6-0.8$      &High           &347                       &430                           \\
            &               &Mid            &186                       &327                           \\
            &               &Low            &833                       &1847                           \\
            &               &               &                       &                           \\ \hline
  PRIMUS    &$0.8-1.0$      &High           &136                       &232                           \\
            &               &Mid            &94                       &163                           \\
            &               &Low            &373                       &810                           \\
            &               &               &                       &                           \\ \hline
  \multicolumn{5}{l}{}                                             \\       
    \end{tabular}
  \end{center}
\end{table*}

\subsection{Galaxy Environment} \label{sec:environment}
We define the environment of a galaxy as the number of neighboring galaxies contained within a fixed aperture centered around it.
We use fixed cylindrical apertures with dimensions specified in Table \ref{tab:aperture} to probe the environment of the target sample galaxies. 
A fixed cylindrical apertures was chosen over a spherical one, often used in literature (e.g. \cite{Croton:2005aa}), due to redshift errors in the PRIMUS data 
and considerations of redshift space distortions within our PRIMUS data redshift range, $[0.2,1.0]$.
Furthermore, we use aperture dimensions listed in Table \ref{tab:aperture} based on the analysis of scale dependence for clustering in \cite{Blanton:2006aa}.
As \cite{Blanton:2006aa} suggests, galactic properties such as their star-formation histories are dependent on properties such as the masses of their host dark matter halos.
Hence, by employing fixed cylindrical apertures with $r_{\rm{ap}} = 1, 2 \rm{Mpc}$ we are able to probe the local small scale environment within the scales of the host dark matter halos.
As a comparison, we also include fixed cylindrical apertures with $r_{\rm{ap}} \ge 5 \rm{Mpc}$ to probe large scale environment, which \cite{Blanton:2006aa} finds to be unrelated to the 
recent star formation history of galaxies.

In order to obtain the fixed aperture based environment for the galaxies in the target population, 
we first establish a volume limited {\it Environment Defining Population} (EDP) by imposing a fixed 
cumulative number density absolute magnitude cut off. 
\begin{table*} %Will contain much more information on environments. 
  \caption{Fixed Cylindrical Aperture Dimensions}
  \label{tab:aperture}
  \begin{center}
    \leavevmode
    \begin{tabular}{llllll} \hline \hline              
  Radius (Mpc)          &Height (Mpc)      &$n_{bin}$   &Edgecut &High Env Threshold (galaxies) &Low Env Threshold (galaxies) \\ \hline 
  1.0 &50 &6 & 80\% & 1.5 & 0.0          \\
  2.0 &50 &6 & 75\% & 4.0 & 0.0          \\ \hline
  \multicolumn{6}{l}{}                                             \\       
    \end{tabular}
  \end{center}
\end{table*}
The EDP for the PRIMUS sample is derived from the same parent sample as the target galaxies. 
We restrict the PRIMUS EDP galaxies within the redshift range $0.2-1.0$ and divide them into redshift bins of width $\Delta z = 0.2$. 
For each of these redshift bins, we impose separate absolute magnitude ($M_{g,\rm{lim}}$) limits such 
that the cumulative number density of the sample ordered by $M_{g}$ is equal to the cumulative 
number density of the highest redshift bin with an empirically determined limit. 
First, to determine the highest redshift bin ($0.8-1.0$) limit we look at the $M_{g}$ distribution with bin size
$\Delta M_{g} = 0.25$ and select $M_{g,\rm{lim}}$ to be the $M_{g}$ value near the peak of the 
distribution where number density of the bins with fainter objects (greater $M_{g}$ value) are smaller
than the number density of the bin at $M_{g, \rm{lim}}$. 
We find this $M_{g, \rm{lim}}( 0.8 < z < 1.0)$ to be, conservatively, $M_{g} = -20.75$. 
With this value we then calculate the rest of the $M_{g, \rm{lim}}$s by finding the
$M_{g}$ value where the cumulative number density ordered by absolute magnitude of the redshift bins 
equals that of the the highest redshift bin at $M_{g, \rm{lim}}( 0.8 < z < 1.0)$. 
Note that when calculating the number densities, the number of galaxies takes into account the 
statistical weights (described in Section \ref{sec:primus} and \ref{sec:sdss}).

For the EDP of the SDSS-{\em GALEX} sample (hereafter simply referred to as the SDSS EDP), 
we do not use the parent sample of the data due to 
the geometry of the combined angular selection function of the SDSS VAGC and {\em GALEX}. 
Instead, since we are not interested in the $FUV, NUV$ values for the EDP, we just use the
SDSS VAGC where the SDSS-{\em GALEX} catalog is derived from. 
Furthermore, we impose a redshift limit $0.0375-0.145$ on the SDSS EDP sample as opposed 
to the redshift range of $0.01-0.2$ in \cite{Moustakas:20133aa}.
This is due to the lack of faint galaxies at $z \sim 0.2$ and the lack of bright 
galaxies at $z \sim 0.01$. 
In other words, the lower bound for the redshif range was empirically determined by the bright limit of 
the $M_{g}$ versus redshift distribution and the upper bound by the faint limit of the 
$M_{g}$ versus redshift distribution. 
The same fixed cumulative number density method is used on this SDSS EDP. 
By using a fixed cumulative number density method of 
Ultimately we use $M_{g,\rm{lim}} = -20.57$, $-20.73$, $-20.80$ and $-20.95$ for the redshift bins 
$0.06-0.145$, $0.2-0.4$, $0.4-0.6$, $0.6-0.8$, respectively. 
These absolute magnitude limits are illustrated in Figure \ref{fig:targetEDP}, which plots the absolute magnitude versus the redshift for the EDP galaxies and the target galaxies. 
\begin{figure*}
    \begin{center}
        \leavevmode
        \label{fig:targetEDP}
        \epsscale{1.0}
        \plotone{absmag_redshift_target_EDP_sdss00375-0145_primus02-10.png}
        \caption{Absolute magnitude $M_{g}$ vs. redshift for the target galaxy population (black) with the Environment Defining Population (red) plotted on top. Both samples are divided into redshift bins:$0.06-0.145$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$. The target galaxy population is stellar mass complete (Section \ref{sec:target} while the EDP is volume limited through $M_{g}$ limits (Section \ref{sec:environment}).}
    \end{center}
\end{figure*}

Using the above definition of environment and the EDP galaxies, we obtain the environment for each of the target population galaxies by counting the number of EDP galaxies, 
$n_{env}$, within the fixed cylinder aperture surrounding it. 
Since we use apertures of different dimensions, we are interested in the relative densitites rather than the actual $n_{env}$ values.
Hence, we use the percentage rank of the galaxy environment to quantify overdense environments and underdense environments.
More specifically, for each of the redshift bins ($0.2-0.4$, $0.4-0.6$, $0.6-0.8$, and $0.8-1.0$) the $n_{env}$ values for all target galaxies in that bin are listed and assigned a percentage rank based on their position in the list: $n_{env} = 0$ corresponding to $0\%$ and the maximum $n_{env}$ for a target galaxy in the $z$-bin corresponding to $100\%$. 
Using these percentage ranks, each target galaxy is classified as high-, mid-, or low-environment based on the cut-offs specified in Table \ref{tab:aperture}. 
Target sample galaxies are classified as high-environment if its percentage rank lies within the top $20\%$ and as low-environment if its percentage rank lies within the bottom $20\%$. 
In Table \ref{tab:aperture}, apertures with radius $1 h^{-1} \rm{Mpc}$ have a low-eneivonrment cut-off of higher than $20\%$.
This is because over $20\%$ of target sample galaxies have $n_{env}=0$ such a smaller aperture size.
Hence we defined the low-environment percentage rank cut-off to contain all galaxies with $n_{env}=0$. 
In order to have a fair comparison for the different $z$-bins when using this aperture, the low-environment cut-off was selected as the lowest cut-off that includes all galaxies with $n_{env}=0$ for all $z$-bin.
More specific details for the high- and low-environment cut-offs are provided in Table \ref{tab:aperture}.

Similar fixed aperture methods have also been used in \cite{Croton:2005aa} for galaxies in the 2dF Galaxy Redshift Survey (\cite{Colless:2003aa}) and in \cite{Muldrew:2012aa} 
for a mock galaxy catalogue generated from embedding galaxies onto the Millenium Dark Matter Simulation (\cite{Springel:2005aa}). 
%Perhaps include a sentence that sums up everything in Croton and Muldrew?

\subsection{Edge Effects} \label{sec:edgeeffect}
One of the challenges in obtaining the galaxy environment using a fixed aperture method is accounting for the edge effects of the survey.
For the target galaxies located near the edge of the survey, part of the fixed aperture encompassing it will lie outside the survey regions. 
In this case, the $n_{env}$ will only reflect the galaxies which lie in the fraction of the aperture contained within the survey geometry.

In order to account for these edge effects, we use a Monte Carlo method to impose edge cuts on the target galaxy population. 
We first divide the target sample galaxies into $n_{bin}$ redshift bins, specified in Table \ref{tab:aperture}. 
For each of the bins we compute the angular separation, $\theta_{\rm{ap}}$ that corresponds to the radius of the aperture at the central redshift of the bin.
Then the target galaxies in each bin are matched up to a sample of $N_{ransack}=1,000,000$ points with arbitrary $RA$ and $Dec$ values within the target sample fields, 
hereafter referred to as the ransack sample (named based on the procedure used to construct them). 
We count the number of ransack points, $n_{\rm{ransack}}$, within $\theta_{\rm{ap}}$ for the target galaxies in each of the redshift bins.
$n_{\rm{ransack}}$ values for the target galaxies are then compared to the expected value:
\begin{equation} \label{eq:ransack}
E[n_{\rm{ransack}}] = \frac{N_{\rm{ransack}}}{A_{\rm{fields}}}\times {\pi \theta_{\rm{ap}}^2} \times f_{\rm{thresh}} 
\end{equation} 
where $A_{\rm{fields}}$ is the total angular area of the target fields and $f_{\rm{thresh}}$ is the fractional threshold for the edge effect cut-off, specified in Table 
\ref{tab:aperture}.
If $n_{\rm{ransack}}$ for a target galaxy is greater than $E[n_{\rm{ransack}}]$ then the target galaxy remains in the sample; otherwise, it is discarded.

\section{Results}
In this section, we describe our calculation to obtain the stellar mass functions (SMF) and quiescent fraction (QF) using the stellar mass complete target population.
In Section \ref{sec:smf_const} we construct the non-parametric estimate of SMFs for star-forming and quiescent galaxies in redshift bins: $0.06-0.145$, $0.2-0.4$, 
$0.4-0.6$, $0.6-0.8$, and $0.8-1.0$.
Form these SMFs, we calculate the QFs in section \ref{sec:qf_const}.

\subsection{Stellar Mass Function} \label{sec:smf_const}
\begin{figure*}
    \begin{center}
        \leavevmode
        \label{fig:smf}
        \epsscale{1.0}
        \plotone{smf_cylr1h50_thresh80_PRIMUS_nbin6_SDSS_nbin2_smf_massbin03_jackknife.png}
        \caption{Stellar mass functions and quiescent fraction for galaxies in the $30$ subsamples divided into redshift bins, $0.06-0.145$ (green), $0.2-0.4$ (red), $0.4-0.6$ 
(magenta), $0.6-0.8$ (blue), and $0.8-1.0$ (black) with low, mid, and high environments. The environments were classified using cylindrical aperture of $R=1\rm{Mpc}$ and $H=50\rm{Mpc}$ 
with environment classification thresholds specified in Table \ref{tab:aperture}. The mass bins for the SMFs and QFs have widths $\Delta \rm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.3$. 
SMFs for subsamples with the same environment density classification are plotted on panels along the same column: low (left), mid (middle), and high (right) environments. The top
panels plot SMFs for subsamples with star forming galaxies. The middle panels plot the SMFs for subsamples with quiescent galaxies. The bottom panels plot the QFs for the 
corresponding star-forming SMFs and quiescent SMFs in the same environment classification and redshift bin.}
    \end{center}
\end{figure*}
Our primary interest in the SMFs is to investigate the evolution of the quiescent fraction in different density environments over our redshift range. 
Hence, we first divide the target galaxy sample into quiescent and star-forming target samples using the classification scheme from Section \ref{sec:sfq}.
Both the quiescent and star-forming target samples are then divided into "high-environment","mid-environment", and "low-environment" based on their environment classification described in 
Section \ref{sec:environment}.
We use the five redshift bins described in \ref{target} to get a total of $30$ subsamples that are classified based on star-forming/quiescent, environment, and redshift.
For each of these subsamples, we calculate the SMFs and their errors.

To calculate the SMFs we employ a non-parametric $1/{V_{\rm{max}}}$ estimator commonly used for galaxy luminosity functions, as done in \cite{Moustakas:2013aa} and discussed 
in the review \cite{Johnston:2011aa}. 
The differential SMF is given by the following equation:
\begin{equation} \label{eq:phi}
\Phi(\rm{log}\: \mathcal{M}) \Delta(\rm{log} \:\mathcal{M}) = \sum\limits_{i=1}^{N} \frac{w_i}{V_{\rm{max,avail},i}}. 
\end{equation}
The equation above is the same as Equation 3. in \cite{Moustakas:2013aa} other than the use of $V_{\rm{max,avail}}$ instead than $V_{\rm{max}}$, which is used because of edge effect 
considerations along the edges of the survey. 
$w_i$ represnts the statistical weight of each galaxy $i$ and $\Phi(\rm{log}\: \mathcal{M}) \Delta(\rm{log}\: \mathcal{M})$ is the number of galaxies ($N$) per unit volume within the 
stellar mass range $[\rm{log} \:\mathcal{M}, \rm{log} \:\mathcal{M}+\Delta(\rm{log} \:\mathcal{M})]$.

$V_{\rm{max},i}$ is the maximum cosmological volume where it is possible to observe each galaxy $i$ given the apparent magnitude limits of the survey.
However in Section \ref{sec:edgeffect} we remove the galaxies that lie on the edge of from the target sample. 
In doing so we reduce the maximum cosmological volume where a galaxy can be observed, thereby reducing $V_{\rm{max},i}$ to a what we will refer to as $V_{\rm{max,avail},i}$.

To calculate $V_{\rm{max,avail},i}$, we generate a sample of points with random $RA$, $Dec$, and $z$ (not to be confused with the ransack sample in Section \ref{sec:edgeeffect}) 
within the target fields and the redshift limits of the surveys.
We then impose the same edge effect cut-off used on the target galaxy population, described in Section \ref{sec:edgeeffect}, onto this random sample. 
For each redshift bin $j$ out of the $n_{\rm{bin}}$ redshift bins, we compute the fraction of the random points that remain in the bin after the points near the edges are removed: 
$f_{\rm{edge},j}$.
Finally we calculate: $V_{\rm{max,avail},i} = V_{\rm{max},i} \times f_{\rm{edge},j}$. 
The $V_{\rm{max},i}$ values in the equation above are computed following the method described in \cite{Moustakas:2013aa} with the same redshift-dependent $K$-correction 
from observed SED and luminosity evolution model.
For more details on computing $V_{\rm{max}}$ we refer readers to Section 4.2 in \cite{Moustakas:2013aa}.

In order to calculate the uncertainty of the SMFs from the sample variance, we use a standard jackknife technique as done in \cite{Moustakas:2013aa}.
For the PRIMUS target galaxies, we calculate SMFs after excluding one of the target fields each time.
Note in these SMF calculations, the $1/V_{\rm{max},\rm{avail}}$ is corrected for the fact that excluding a field changes the total area of the survey.
Then using the calculated SMFs we calculate the uncertainty: 
\begin{equation}
\sigma^j = \sqrt{\frac{M-1}{M} \sum\limits_{k=1}^{M} (\Phi^j_k - \langle \Phi^j \rangle)^2}
\end{equation} 
$M$ in this equation is the number of jack knife SMFs in the mass bin; this value is different for each of the stellar mass bins since not all mass bins have galaxies from all five target fields.
$\langle \Phi^j \rangle$ is the mean number density of galaxies in each stellar mass bin for all of the jack knife $\Phi^j$s.

Since the SDSS-{\em GALEX} data are contained in one field, we first divide the field into a $30 \times 20$ rectangular grid and then only keep the sectors with at least $100$ galaxies in them. 
Then we use the same method as above to compute the uncertainties through the jack knife technique. 
The panels in the top two rows of Figure \ref{fig:smf} show the SMFs with uncertainties for all $30$ subsamples using aperture with dimensions $R_{\rm{ap}} = 1 \rm{Mpc}$ and $h_{\rm{ap}} = 50 \rm{Mpc}$.

%Multiple apertures Additionally, we employ multiple apertures, as listed in Table \ref{tab:aperture}, since we are interested in probing the density environment at various scales. 
%Each aperture size will result in a different environment classification; so, $18$ SMFs are generated separately for every aperture we employ.

\subsection{Quiescent Fraction} \label{sec:qf_const}
In the last section, we calculated the SMFs for all subsamples of the target galaxies classified by star-forming/quiescent, environment, and redshift. 
In this section, we use the $\Phi$ calculated for each subsample above to compute their respective $\rm{QF}$s: 
\begin{equation}
\rm{QF} = \frac{\Phi_{Q}}{\Phi_{SF}+\Phi_{Q}}.
\end{equation}
$\Phi_{Q}$ and $\Phi_{SF}$ are the total number of galaxies per unit volume in stellar mass bin $\Delta(\rm{log} \: \mathcal{M})$ (Equation \ref{eq:phi}) for the quiescent and star-forming subsamples, respectively.
A value for the $\rm{QF}$ is not assigned in stellar mass bins where either the star-formation subsample or the quiescent subsample do not have any galaxies. 
The bottom panels of Figure \ref{fig:smf} shows the $\rm{QF}$s for the different redshift bins and environment density classifications.

In order to compare the $\rm{QF}$s at different redshift for each of the environment classifications, we perform a linear least squares fit on the $\rm{QF}$ for all the $\rm{QF}$s. 
Then we use the value of the linear fit at an empirically selected fiducial mass $\rm{log} \: \mathcal{M}/\mathcal{M}_{\odot} = 10.5$ (using fiducial mass of $\rm{log} \: \mathcal{M}/
\mathcal{M}_\odot = 11.0$ does not noteably change the outcome).
These values are used to highlight and attempt to quantify the differences of the $\rm{QFs}$ at the different redshifts, Figure \ref{fig:qf}
%of the low redshift and low environemnt subsample.
%The slope obtained from this fit is then used to perform a lienar fit for the rest of the $\rm{QF}$s.

The figures and analysis described in this paper are done using galaxy environment determined from a fixed aperture with $r_{\rm{ap}} = 1 \rm{Mpc}$ and $h_{\rm{ap}} = 50 \rm{Mpc}$.
The same analysis was repeated for various aperture dimensions: $r_{\rm{ap}} = 0.5, 1, 2, 3 \rm{Mpc}$ and $h_{\rm{ap}} = 25, 50 \rm{Mpc}$. 
Minor adjustments to the environment classification thresholds were adopted in these analyses for the smaller apertures ($r_{\rm{ap}} = 0.5, 1 \rm{Mpc}$ and $r_{\rm{ap}} = 25 \rm{Mpc}$).
The results obtained from using these different are consistent with the results displayed in this paper. 
\begin{figure}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \plotone{QFfit_cylr1h50_PRIMUS_nbin6_SDSS_nbin2_z00-10_slope-yint-err-fit_mass_100-115_105fidmass_01massbin.png}
        \label{fig:qf}
        \caption{Quiescent fraction at fiducial mass $\rm{log} (\mathcal{M}/\mathcal{M}_{\odot}) = 10.5$ for low (triangle), mid (square) and high (circle) environments in redshift bins: $0.06-0.145$, $0.2-0.4$, $0.4-0.6$, $0.6-0.8$, and $0.8-1.0$. Comparing these linear fit values in the redshift range for the different environment densities suggest that the change in QFs is indepdent of environment density.}
    \end{center}
\end{figure}

\section{Discussion and Conclusions}
We have measured the SMFs and QFs using low redshift SDSS-{\em GALEX} galaxies and intermeidate redshift PRIMUS galaxies. 
Specifically we anlayzed the evolution of the QFs over the redshift range $0.0-1.0$ for galaxies in environment densities (Figure \ref{fig:qf}). 
We find that there is an expected increase in QF with decrease in the redshift for subsamples in all environment densities.
More importantly we find that the change in QF over redshift is independent of the environment and remains relatively equal for all environments.

\begin{itemize}
    \item Comparison to other works. 
    \begin{itemize}
        \item Alberts et al. 2013 
    \end{itemize}
\end{itemize}

%
% References
%
\bibliography{PRIMUS}

\section{Appendix}
\subsection{Stellar Mass Function} \label{sec:smf_const}
\begin{figure*}
    \begin{center}
        \leavevmode
        \label{fig:smf}
        \epsscale{1.0}
        \plotone{smf_cylr2h50_thresh75_PRIMUS_nbin20_SDSS_nbin5_006_0145_smf_massbin03_jackknife.png}
        \caption{SMF and QF for $r_{\rm{ap}}=2 \rm{Mpc}$ and $h_{\rm{ap}}=50 \rm{Mpc}$}
    \end{center}
\end{figure*}

\begin{figure*}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \plotone{QFfit_cylr2h50_PRIMUS_nbin20_SDSS_nbin5_z00-10_slope-yint-err-fit_mass_100-110_105fidmass_01massbin.png}
        \label{fig:qf}
        \caption{QF at fiducial mass for $r_{\rm{ap}}=2 \rm{Mpc}$ and $h_{\rm{ap}}=50 \rm{Mpc}$}
    \end{center}
\end{figure*}

\subsection{Stellar Mass Function} \label{sec:smf_const}
\begin{figure*}
    \begin{center}
        \leavevmode
        \label{fig:smf}
        \epsscale{1.0}
        \plotone{smf_cylr1h25_thresh80_PRIMUS_nbin20_02_08_smf_massbin03_jackknife.png}
        \caption{SMF and QF for $r_{\rm{ap}}=1 \rm{Mpc}$ and $h_{\rm{ap}}=25 \rm{Mpc}$}
    \end{center}
\end{figure*}

\begin{figure*}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \plotone{QFfit_cylr1h25_PRIMUS_z02-08_slope-yint-err-fit_mass_100-115_105fidmass_03massbin}
        \label{fig:qf}
        \caption{QF at fiducial mass for $r_{\rm{ap}}=1 \rm{Mpc}$ and $h_{\rm{ap}}=25 \rm{Mpc}$}
    \end{center}
\end{figure*}
\end{document}

\end{document}

### 2014-02-24 qfenv_paper/qf_environment.tex
updated figures

@@
 \subsection{Galaxy Sample} \label{sec:target} 
+\begin{table*} %Will contain much more information on environments. 
+  \caption{Subsample}
+  \label{tab:subsample}
+  \begin{center}
+    \leavevmode
+    \begin{tabular}{lllll} \hline \hline              
+  Survey    &Redshift ($z$) &Environment    &Quiescent $N_{\rm{g}}$ &Star-forming $N_{\rm{g}}$  \\ \hline 
+  SDSS      &$0.0375-0.145$ &High           &5470                       &4501                           \\
+            &               &Mid            &3614                       &4438                           \\
+            &               &Low            &5419                       &8927                           \\
+            &               &               &                       &                           \\ \hline
+  PRIMUS    &$0.2-0.4$      &High           &322                    &583                           \\
+            &               &Mid            &177                    &403                          \\
+            &               &Low            &768                    &2516                           \\
+            &               &               &                       &                           \\ \hline
+  PRIMUS    &$0.4-0.6$      &High           &350                       &675                           \\
+            &               &Mid            &195                       &405                           \\
+            &               &Low            &871                       &2385                           \\
+            &               &               &                       &                           \\ \hline
+  PRIMUS    &$0.6-0.8$      &High           &347                       &430                           \\
+            &               &Mid            &186                       &327                           \\
+            &               &Low            &833                       &1847                           \\
+            &               &               &                       &                           \\ \hline
+  PRIMUS    &$0.8-1.0$      &High           &136                       &232                           \\
+            &               &Mid            &94                       &163                           \\
+            &               &Low            &373                       &810                           \\
+            &               &               &                       &                           \\ \hline
+  \multicolumn{5}{l}{}                                             \\       
+    \end{tabular}
+  \end{center}
+\end{table*}
 In this seciton we will define the galaxy sample we use for our SMFs and QFs.
@@
 
+\begin{figure*}
+    \begin{center}
+        \leavevmode
+        \label{fig:targetEDP}
+        \epsscale{1.0}
+        \plotone{fig_EDP_absmag_redshift.png}
+        \caption{Absolute magnitude $M_{r}$ vs.
+redshift for the target galaxy population (black) with the Environment Defining Population (red) plotted on top.
+Both samples are divided into redshift bins:$0.06-0.145$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$.
+The target galaxy population is stellar mass complete (Section \ref{sec:target} while the EDP is volume limited through $M_{g}$ limits (Section \ref{sec:environment}).}
+    \end{center}
+\end{figure*}
 \subsection{Classifying Quiescent and Star-Forming Galaxies} \label{sec:sfq}
@@
 
-\begin{table*} %Will contain much more information on environments. 
-  \caption{Subsample}
-  \label{tab:subsample}
-  \begin{center}
-    \leavevmode
-    \begin{tabular}{lllll} \hline \hline              
-  Survey    &Redshift ($z$) &Environment    &Quiescent $N_{\rm{g}}$ &Star-forming $N_{\rm{g}}$  \\ \hline 
-  SDSS      &$0.0375-0.145$ &High           &5470                       &4501                           \\
-            &               &Mid            &3614                       &4438                           \\
-            &               &Low            &5419                       &8927                           \\
-            &               &               &                       &                           \\ \hline
-  PRIMUS    &$0.2-0.4$      &High           &322                    &583                           \\
-            &               &Mid            &177                    &403                          \\
-            &               &Low            &768                    &2516                           \\
-            &               &               &                       &                           \\ \hline
-  PRIMUS    &$0.4-0.6$      &High           &350                       &675                           \\
-            &               &Mid            &195                       &405                           \\
-            &               &Low            &871                       &2385                           \\
-            &               &               &                       &                           \\ \hline
-  PRIMUS    &$0.6-0.8$      &High           &347                       &430                           \\
-            &               &Mid            &186                       &327                           \\
-            &               &Low            &833                       &1847                           \\
-            &               &               &                       &                           \\ \hline
-  PRIMUS    &$0.8-1.0$      &High           &136                       &232                           \\
-            &               &Mid            &94                       &163                           \\
-            &               &Low            &373                       &810                           \\
-            &               &               &                       &                           \\ \hline
-  \multicolumn{5}{l}{}                                             \\       
-    \end{tabular}
-  \end{center}
-\end{table*}
-
 \subsection{Galaxy Environment} \label{sec:environment}
@@
 cumulative number density absolute magnitude cut off.
-\begin{table*} %Will contain much more information on environments. 
-  \caption{Fixed Cylindrical Aperture Dimensions}
-  \label{tab:aperture}
-  \begin{center}
-    \leavevmode
-    \begin{tabular}{llllll} \hline \hline              
-  Radius (Mpc)          &Height (Mpc)      &$n_{bin}$   &Edgecut &High Env Threshold (galaxies) &Low Env Threshold (galaxies) \\ \hline 
-  1.0 &50 &6 & 80\% & 1.5 & 0.0          \\
-  2.0 &50 &6 & 75\% & 4.0 & 0.0          \\ \hline
-  \multicolumn{6}{l}{}                                             \\       
-    \end{tabular}
-  \end{center}
-\end{table*}
+
 The EDP for the PRIMUS sample is derived from the same parent sample as the target galaxies. 
@@
 These absolute magnitude limits are illustrated in Figure \ref{fig:targetEDP}, which plots the absolute magnitude versus the redshift for the EDP galaxies and the target galaxies.
-\begin{figure*}
-    \begin{center}
-        \leavevmode
-        \label{fig:targetEDP}
-        \epsscale{1.0}
-        \plotone{absmag_redshift_target_EDP_sdss00375-0145_primus02-10.png}
-        \caption{Absolute magnitude $M_{g}$ vs.
-redshift for the target galaxy population (black) with the Environment Defining Population (red) plotted on top.
-Both samples are divided into redshift bins:$0.06-0.145$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$.
-The target galaxy population is stellar mass complete (Section \ref{sec:target} while the EDP is volume limited through $M_{g}$ limits (Section \ref{sec:environment}).}
-    \end{center}
-\end{figure*}
 
@@
 
+\begin{figure*}
+    \begin{center}
+        \leavevmode
+        \label{fig:smf}
+        \epsscale{1.0}
+        \plotone{fig_smf_cylr2h25_thresh75_bin0_25.png}
+        \caption{Stellar mass functions for galaxies in the $30$ subsamples divided into redshift bins, $0.06-0.145$ (green), $0.2-0.4$ (red), $0.4-0.6$ 
+(magenta), $0.6-0.8$ (blue), and $0.8-1.0$ (black) with low, mid, and high environments. The environments were classified using cylindrical aperture of $R=1\rm{Mpc}$ and $H=50\rm{Mpc}$ 
+with environment classification thresholds specified in Table \ref{tab:aperture}. The mass bins for the SMFs and QFs have widths $\Delta \rm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.3$. 
+SMFs for subsamples with the same environment density classification are plotted on panels along the same column: low (left), mid (middle), and high (right) environments. The top
+panels plot SMFs for subsamples with star forming galaxies. The middle panels plot the SMFs for subsamples with quiescent galaxies. The bottom panels plot the QFs for the 
+corresponding star-forming SMFs and quiescent SMFs in the same environment classification and redshift bin.}
+    \end{center}
+\end{figure*}
 \subsection{Edge Effects} \label{sec:edgeeffect}
@@
 \subsection{Stellar Mass Function} \label{sec:smf_const}
-\begin{figure*}
-    \begin{center}
-        \leavevmode
-        \label{fig:smf}
-        \epsscale{1.0}
-        \plotone{smf_cylr1h50_thresh80_PRIMUS_nbin6_SDSS_nbin2_smf_massbin03_jackknife.png}
-        \caption{Stellar mass functions and quiescent fraction for galaxies in the $30$ subsamples divided into redshift bins, $0.06-0.145$ (green), $0.2-0.4$ (red), $0.4-0.6$ 
-(magenta), $0.6-0.8$ (blue), and $0.8-1.0$ (black) with low, mid, and high environments. The environments were classified using cylindrical aperture of $R=1\rm{Mpc}$ and $H=50\rm{Mpc}$ 
-with environment classification thresholds specified in Table \ref{tab:aperture}. The mass bins for the SMFs and QFs have widths $\Delta \rm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.3$. 
-SMFs for subsamples with the same environment density classification are plotted on panels along the same column: low (left), mid (middle), and high (right) environments. The top
-panels plot SMFs for subsamples with star forming galaxies. The middle panels plot the SMFs for subsamples with quiescent galaxies. The bottom panels plot the QFs for the 
-corresponding star-forming SMFs and quiescent SMFs in the same environment classification and redshift bin.}
-    \end{center}
-\end{figure*}
 Our primary interest in the SMFs is to investigate the evolution of the quiescent fraction in different density environments over our redshift range. 
@@
 The panels in the top two rows of Figure \ref{fig:smf} show the SMFs with uncertainties for all $30$ subsamples using aperture with dimensions $R_{\rm{ap}} = 1 \rm{Mpc}$ and $h_{\rm{ap}} = 50 \rm{Mpc}$.
-
 %Multiple apertures Additionally, we employ multiple apertures, as listed in Table \ref{tab:aperture}, since we are interested in probing the density environment at various scales. 
 %Each aperture size will result in a different environment classification; so, $18$ SMFs are generated separately for every aperture we employ. 
+\begin{figure*}
+    \begin{center}
+        \leavevmode
+        \label{fig:smf}
+        \epsscale{1.0}
+        \plotone{fig_qf_cylr2h25_thresh75_bin0_25.png}
+        \caption{Quiescent fraction for galaxies in the $30$ subsamples divided into redshift bins, $0.06-0.145$ (green), $0.2-0.4$ (red), $0.4-0.6$ 
+(magenta), $0.6-0.8$ (blue), and $0.8-1.0$ (black) with low, mid, and high environments. The environments were classified using cylindrical aperture of $R=1\rm{Mpc}$ and $H=50\rm{Mpc}$ 
+with environment classification thresholds specified in Table \ref{tab:aperture}. The mass bins for the SMFs and QFs have widths $\Delta \rm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.3$. 
+SMFs for subsamples with the same environment density classification are plotted on panels along the same column: low (left), mid (middle), and high (right) environments. The top
+panels plot SMFs for subsamples with star forming galaxies. The middle panels plot the SMFs for subsamples with quiescent galaxies. The bottom panels plot the QFs for the 
+corresponding star-forming SMFs and quiescent SMFs in the same environment classification and redshift bin.}
+    \end{center}
+\end{figure*}
 
@@
         \epsscale{1.0}
-        \plotone{QFfit_cylr1h50_PRIMUS_nbin6_SDSS_nbin2_z00-10_slope-yint-err-fit_mass_100-115_105fidmass_01massbin.png}
+        \plotone{fig_qffit_cylr2h25_thresh75_bin0_25.eps}
         \label{fig:qf}
@@
 \section{Appendix}
+\begin{table*} %Will contain much more information on environments. 
+  \caption{Fixed Cylindrical Aperture Dimensions}
+  \label{tab:aperture}
+  \begin{center}
+    \leavevmode
+    \begin{tabular}{llllll} \hline \hline              
+  Radius (Mpc)          &Height (Mpc)      &$n_{bin}$   &Edgecut &High Env Threshold (galaxies) &Low Env Threshold (galaxies) \\ \hline 
+  1.0 &50 &6 & 80\% & 1.5 & 0.0          \\
+  2.0 &50 &6 & 75\% & 4.0 & 0.0          \\ \hline
+  \multicolumn{6}{l}{}                                             \\       
+    \end{tabular}
+  \end{center}
+\end{table*}
 \subsection{Stellar Mass Function} \label{sec:smf_const}
@@
         \epsscale{1.0}
-        \plotone{smf_cylr2h50_thresh75_PRIMUS_nbin20_SDSS_nbin5_006_0145_smf_massbin03_jackknife.png}
-        \caption{SMF and QF for $r_{\rm{ap}}=2 \rm{Mpc}$ and $h_{\rm{ap}}=50 \rm{Mpc}$}
-    \end{center}
-\end{figure*}
-
-\begin{figure*}
-    \begin{center}
-        \leavevmode
-        \epsscale{1.0}
-        \plotone{QFfit_cylr2h50_PRIMUS_nbin20_SDSS_nbin5_z00-10_slope-yint-err-fit_mass_100-110_105fidmass_01massbin.png}
-        \label{fig:qf}
-        \caption{QF at fiducial mass for $r_{\rm{ap}}=2 \rm{Mpc}$ and $h_{\rm{ap}}=50 \rm{Mpc}$}
-    \end{center}
-\end{figure*}
-
-\subsection{Stellar Mass Function} \label{sec:smf_const}
-\begin{figure*}
-    \begin{center}
-        \leavevmode
-        \label{fig:smf}
-        \epsscale{1.0}
-        \plotone{smf_cylr1h25_thresh80_PRIMUS_nbin20_02_08_smf_massbin03_jackknife.png}
+        \plotone{fig_smf_cylr1h25_thresh80_bin0_25.png}
         \caption{SMF and QF for $r_{\rm{ap}}=1 \rm{Mpc}$ and $h_{\rm{ap}}=25 \rm{Mpc}$}
@@
         \epsscale{1.0}
-        \plotone{QFfit_cylr1h25_PRIMUS_z02-08_slope-yint-err-fit_mass_100-115_105fidmass_03massbin}
+        \plotone{fig_qffit_cylr1h25_thresh80_bin0_25.eps}
         \label{fig:qf}
@@
 \end{document}
-
-\end{document}

### 2014-02-25 qfenv_paper/qf_environment.tex
Properly merged with home laptop

--- 2014-02-24 qfenv_paper/qf_environment.tex
@@
 \title{PRIMUS: Quiescent Fraction as a Function of Environment and Redshift}
-\author{ChangHoon Hahn, Michael Blanton, John Moustakas}
+\author{ChangHoon Hahn, Michael Blanton, Alison Coil, Richard Cool, Daniel Eisenstein, John Moustakas, Ken Wong, Guangtun Zhu}
 
 \begin{abstract}
-We examine the evolution of the quiescent fraction, for galaxies in 
-different density environments from $z=0.2-0.8$, using spectroscopic 
+We examine the evolution of the quiescent fraction (QF) for galaxies in 
+different density environments from $z=0.2-0.8$ using spectroscopic 
 redshift and multi-wavelength imaging data from PRism MUlti-object 
@@
 target galaxies we calculate the stellar mass functions in different environments and redshift.
-Afterwards, we compute the quiescent fraction (QF) using the SMFs for the different environment 
+Afterwards, we compute the QFs using the SMFs for the different environment 
 and redshift ranges.  Comparing the QFs in these environment and redshift bins, we find the 
-QF increases over time (decrease in redshift); however, the change of 
+QF increases over cosmic time (decrease in redshift); however, the change of 
 the QFs for the different environments are independent of the 
@@
 
+\begin{table*} %Subject to significant change based on the classification of environment
+  \caption{Summary of Galaxy Subsample}
+  \label{tab:subsample}
+  \begin{center}
+    \leavevmode
+    \begin{tabular}{lllll} \hline \hline              
+  Survey    &Redshift ($z$) &Density        &Quiescent $N_{\rm{g}}$ &Star-forming $N_{\rm{g}}$  \\ \hline 
+  SDSS      &$0.0375-0.145$ &High           &5470                       &4501                           \\
+            &               &Mid            &3614                       &4438                           \\
+            &               &Low            &5419                       &8927                           \\
+            &               &               &                       &                           \\ \hline
+  PRIMUS    &$0.2-0.4$      &High           &322                    &583                           \\
+            &               &Mid            &177                    &403                          \\
+            &               &Low            &768                    &2516                           \\
+            &               &               &                       &                           \\ \hline
+  PRIMUS    &$0.4-0.6$      &High           &350                       &675                           \\
+            &               &Mid            &195                       &405                           \\
+            &               &Low            &871                       &2385                           \\
+            &               &               &                       &                           \\ \hline
+  PRIMUS    &$0.6-0.8$      &High           &347                       &430                           \\
+            &               &Mid            &186                       &327                           \\
+            &               &Low            &833                       &1847                           \\
+            &               &               &                       &                           \\ \hline
+  PRIMUS    &$0.8-1.0$      &High           &136                       &232                           \\
+            &               &Mid            &94                       &163                           \\
+            &               &Low            &373                       &810                           \\
+            &               &               &                       &                           \\ \hline
+  \multicolumn{5}{l}{}                                             \\       
+    \end{tabular} 
+  \end{center}
+\end{table*}
+
 \section{Sample Selection}
@@
 
-In all of the PRIMUS target fields we have near-UV (NUV) and far-UV (FUV) measurements from the {\em GALEX} Deep Imaging Survey (DIS; CITECITE ). 
-To minimize contamination from neighboring sources, we use a Bayesian photometric code EM$_{\rm{PHOT}}$ (based on expectation maximization algorithm of CITECITE ). 
+In all of the PRIMUS target fields we have near-UV (NUV) and far-UV (FUV) measurements from the {\em GALEX} Deep Imaging Survey (DIS; \cite{Martin:2005aa}; \cite{Morrissey:2005aa}). 
+To minimize contamination from neighboring sources, we use a Bayesian photometric code EM$_{\rm{PHOT}}$ (based on expectation maximization algorithm of \cite{Guillaume:2006aa}). 
 Furthermore, we use ground-based optical and {\em Spitzer}/IRAC mid-infrared photometric catalogs in each of the fields to obtain integrated fluxes in all 
@@
 These generated model SEDs depend on population synthesis models and prior parameters.
-In order to derive our fiducial stellar masses and star formation rates, we use the Flexible Stellar Population Synthesis (FSPS) models (CITECITE) based on the Chabrier (2003) IMF. 
-Other prior parameters are listed in Section 4.1 of \cite{Moustakas}. 
+In order to derive our fiducial stellar masses and star formation rates, we use the Flexible Stellar Population Synthesis (FSPS) models (\cite{Conroy:2010aa}) based on the \cite{Chabrier:2003aa} IMF. 
+Other prior parameters are listed in Section 4.1 of \cite{Moustakas:2013aa}. 
 The photometric bands we use for the fitting in our PRIMUS data are the {\em GALEX} FUV and NUV, the two shortest IRAC bands at $3.6$ and $4.5 \mu \rm{m}$, and the five optical bands
@@
 
+\begin{figure*}
+    \begin{center}
+        \leavevmode
+        \label{fig:targetEDP}
+        \epsscale{1.0}
+	\plotone{fig_EDP_absmag_redshift.png}
+        \caption{Absolute magnitude $M_{r}$ vs.
+redshift for the target galaxy population (black) with the Environment Defining Population (red) plotted on top.
+Both samples are divided into redshift bins:$0.06-0.145$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$.
+The target galaxy population is stellar mass complete (Section \ref{sec:target} while the EDP is volume limited through $M_{g}$ limits (Section \ref{sec:environment}).}
+    \end{center}
+\end{figure*}
+
 \subsection{SDSS-GALEX} \label{sec:sdss}
-For galaxies at low redshifts we use the SDSS Data Release 7 (DR7; CITECITE). 
+For galaxies at low redshifts we use the SDSS Data Release 7 (DR7; \cite{Abazajian:2009aa}). 
 From the SDSS DR7 data, which provides high fidelity $ugriz$ photometry and spectroscopic redshift, we specifically use galaxies from the New York University 
-Value-Added Galaxy Catalog that satisfy the main sample criterion (CITECITE) and have galaxy extinction corrected (CITECITE) Petrosian magnitudes $14.5 < r < 17.6$ 
-and spectroscopic redshits $0.01<z<0.2$. 
+Value-Added Galaxy Catalog that satisfy the main sample criterion and have galaxy extinction corrected Petrosian magnitudes $14.5 < r < 17.6$ 
+and spectroscopic redshits $0.01<z<0.2$ (\cite{Blanton:2005aa}). 
 Within this sample, we select galaxies with medium depth observations from GALEX. 
@@
 For the optical photometry we use $ugriz$ bands (from the SDSS \texttt{model} magnitudes) scaled to the $r$-band \texttt{cmodel} magnitude. 
-We supplement the above UV and optical photometry with integrated $JHK_s$ magnitudes from the 2MASS Extended Source Catalog (XSC; CITECITE) and with photometry at $3.4$ 
+We supplement the above UV and optical photometry with integrated $JHK_s$ magnitudes from the 2MASS Extended Source Catalog (XSC; \cite{Jarrett:2000aa}) and with photometry at $3.4$ 
 and $4.6 \mu \rm{m}$ from the WISE All-Sky Data Release\footnote{http://wise2.ipac.caltech.edu/docs/release/allsky}. 
@@
 Except we use twelve photometric bands: {\em GALEX} FUV and NUV, SDSS $ugriz$, 2MASS $JHK_{s}$, and WISE $3.4$ and $4.6 \mu \rm{m}$.
-
-\subsection{Galaxy Sample} \label{sec:target} 
+\subsection{Galaxy Samples} \label{sec:target} 
 In this seciton we will define the galaxy sample we use for our SMFs and QFs.
@@
 We take the statistically complete {\em primary} sample from the PRIMUS data, \cite{Coil:2011aa}, and then we impose magnitude limits on optical selection bands as specified in 
-\cite{Moustakas:2013aa} (listed in its Table 1).
+\cite{Moustakas:2013aa} Table 1.
 These limits are in different optical selection bands and have different values for our five PRIMUS target fields.
@@
 The NYU-VAGC provides statistical weight estimates for targeting completeness.
-In order to have a stellar mass complete low redshift target population, we use a uniform stellar mass limit of $10^9 \mathcal{M}_{odot}$, which is above the surface 
-brightness and stellar mass-to-light ratio completness limits (CITECITE).
+In order to have a stellar mass complete low redshift target population, we use a uniform stellar mass limit of $10^9 \mathcal{M}_{\odot}$, which is above the surface 
+brightness and stellar mass-to-light ratio completness limits (\cite{Blanton:2005ab}; \cite{Baldry:2008aa}).
 The absolute magnitude ($M_g$) versus redshift for the target galaxy population at both low redshift and intermediate redshift is plotted in Figure \ref{fig:targetEDP}.
@@
 cumulative number density absolute magnitude cut off. 
-\begin{table*} %Will contain much more information on environments. 
-  \caption{Fixed Cylindrical Aperture Dimensions}
-  \label{tab:aperture}
+By using a fixed cumulative number density for this sample we seek to build an EDP with galaxies that 
+have similar populations in all of the redshift bins i.e. accounting for the progenitor bias. 
+As \cite{Behroozi:2013aa} and \cite{Leja:2013aa} find in their analysis of the cumulative number density 
+method using a dark matter simulation with abundance matching and a semi-analytic model, respectively, 
+cumulative number density method, while it does not precisely account for the scatter in mass accretion or 
+galaxy-galaxy mergers, provides a promising tool to compare galaxy populations over a wide range of cosmic time.
+In addition we use the highest redshift bin cumulative number density as the fixed number density 
+%%%FINISH THIS SENTENCE
+Furthermore \cite{Behroozi:2013aa}
+
+\begin{figure*}
     \begin{center}
         \leavevmode
-    \begin{tabular}{llllll} \hline \hline              
-  Radius (Mpc)          &Height (Mpc)      &$n_{bin}$   &Edgecut &High Env Threshold (galaxies) &Low Env Threshold (galaxies) \\ \hline 
-  1.0 &50 &6 & 80\% & 1.5 & 0.0          \\
-  2.0 &50 &6 & 75\% & 4.0 & 0.0          \\ \hline
-  \multicolumn{6}{l}{}                                             \\       
-    \end{tabular}
+        \label{fig:smf}
+        \epsscale{1.0}
+        \plotone{fig_smf_cylr2h25_thresh75_bin0_25.png}
+        \caption{Stellar mass functions and quiescent fraction for galaxies in the $30$ subsamples divided into redshift bins, $0.06-0.145$ (green), $0.2-0.4$ (red), $0.4-0.6$ 
+(magenta), $0.6-0.8$ (blue), and $0.8-1.0$ (black) with low, mid, and high environments. The environments were classified using cylindrical aperture of $R=1\rm{Mpc}$ and $H=50\rm{Mpc}$ 
+with environment classification thresholds specified in Table \ref{tab:aperture}. The mass bins for the SMFs and QFs have widths $\Delta \rm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.3$. 
+SMFs for subsamples with the same environment density classification are plotted on panels along the same column: low (left), mid (middle), and high (right) environments. The top
+panels plot SMFs for subsamples with star forming galaxies. The middle panels plot the SMFs for subsamples with quiescent galaxies. The bottom panels plot the QFs for the 
+corresponding star-forming SMFs and quiescent SMFs in the same environment classification and redshift bin.}
     \end{center}
-\end{table*}
+\end{figure*}
+
 The EDP for the PRIMUS sample is derived from the same parent sample as the target galaxies. 
@@
 The same fixed cumulative number density method is used on this SDSS EDP. 
-By using a fixed cumulative number density method of 
 Ultimately we use $M_{g,\rm{lim}} = -20.57$, $-20.73$, $-20.80$ and $-20.95$ for the redshift bins 
@@
 \subsection{Edge Effects} \label{sec:edgeeffect}
+\begin{figure*}
+    \begin{center}
+        \leavevmode
+        \label{fig:smf}
+        \epsscale{1.0}
+        \plotone{fig_qf_cylr2h25_thresh75_bin0_25.png}
+        \caption{Quiescent fraction for galaxies in the $30$ subsamples divided into redshift bins, $0.06-0.145$ (green), $0.2-0.4$ (red), $0.4-0.6$ 
+(magenta), $0.6-0.8$ (blue), and $0.8-1.0$ (black) with low, mid, and high environments. The environments were classified using cylindrical aperture of $R=1\rm{Mpc}$ and $H=50\rm{Mpc}$ 
+with environment classification thresholds specified in Table \ref{tab:aperture}. The mass bins for the SMFs and QFs have widths $\Delta \rm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.3$. 
+SMFs for subsamples with the same environment density classification are plotted on panels along the same column: low (left), mid (middle), and high (right) environments. The top
+panels plot SMFs for subsamples with star forming galaxies. The middle panels plot the SMFs for subsamples with quiescent galaxies. The bottom panels plot the QFs for the 
+corresponding star-forming SMFs and quiescent SMFs in the same environment classification and redshift bin.}
+    \end{center}
+\end{figure*}
+
 One of the challenges in obtaining the galaxy environment using a fixed aperture method is accounting for the edge effects of the survey.
@@
 $V_{\rm{max},i}$ is the maximum cosmological volume where it is possible to observe each galaxy $i$ given the apparent magnitude limits of the survey.
-However in Section \ref{sec:edgeffect} we remove the galaxies that lie on the edge of from the target sample. 
+However in Section \ref{sec:edgeeffect} we remove the galaxies that lie on the edge of from the target sample. 
 In doing so we reduce the maximum cosmological volume where a galaxy can be observed, thereby reducing $V_{\rm{max},i}$ to a what we will refer to as $V_{\rm{max,avail},i}$.
@@
         \epsscale{1.0}
-        \plotone{QFfit_cylr1h50_PRIMUS_nbin6_SDSS_nbin2_z00-10_slope-yint-err-fit_mass_100-115_105fidmass_01massbin.png}
+        \plotone{fig_qffit_cylr2h25_thresh75_bin0_25.png}
         \label{fig:qf}
@@
 
-\section{Appendix}
+\appendix
+\begin{table*} %Will contain much more information on environments. 
+  \caption{Fixed Cylindrical Aperture Dimensions}
+  \label{tab:aperture}
+  \begin{center}
+    \leavevmode
+    \begin{tabular}{llllll} \hline \hline              
+  Radius (Mpc)          &Height (Mpc)      &$n_{bin}$   &Edgecut &High Env Threshold (galaxies) &Low Env Threshold (galaxies) \\ \hline 
+  1.0 &50 &6 & 80\% & 1.5 & 0.0          \\
+  2.0 &50 &6 & 75\% & 4.0 & 0.0          \\ \hline
+  \multicolumn{6}{l}{}                                             \\       
+    \end{tabular}
+  \end{center}
+\end{table*}
+
 \subsection{Stellar Mass Function} \label{sec:smf_const}
@@
         \epsscale{1.0}
-        \plotone{smf_cylr2h50_thresh75_PRIMUS_nbin20_SDSS_nbin5_006_0145_smf_massbin03_jackknife.png}
-        \caption{SMF and QF for $r_{\rm{ap}}=2 \rm{Mpc}$ and $h_{\rm{ap}}=50 \rm{Mpc}$}
+        \plotone{fig_smf_cylr1h25_thresh80_bin0_25.png}
+        \caption{SMF for $r_{\rm{ap}}=1 \rm{Mpc}$ and $h_{\rm{ap}}=25 \rm{Mpc}$}
+    \end{center}
+\end{figure*}
+
+\begin{figure*}
+    \begin{center}
+        \leavevmode
+        \label{fig:smf}
+        \epsscale{1.0}
+        \plotone{fig_qf_cylr1h25_thresh80_bin0_25.png}
+        \caption{QF for $r_{\rm{ap}}=1 \rm{Mpc}$ and $h_{\rm{ap}}=25 \rm{Mpc}$}
     \end{center}
@@
         \epsscale{1.0}
-        \plotone{QFfit_cylr2h50_PRIMUS_nbin20_SDSS_nbin5_z00-10_slope-yint-err-fit_mass_100-110_105fidmass_01massbin.png}
+        \plotone{fig_qffit_cylr1h25_thresh80_bin0_25.png}
         \label{fig:qf}
@@
 
-\subsection{Stellar Mass Function} \label{sec:smf_const}
-\begin{figure*}
-    \begin{center}
-        \leavevmode
-        \label{fig:smf}
-        \epsscale{1.0}
-        \plotone{smf_cylr1h25_thresh80_PRIMUS_nbin20_02_08_smf_massbin03_jackknife.png}
-        \caption{SMF and QF for $r_{\rm{ap}}=1 \rm{Mpc}$ and $h_{\rm{ap}}=25 \rm{Mpc}$}
-    \end{center}
-\end{figure*}
-
-\begin{figure*}
-    \begin{center}
-        \leavevmode
-        \epsscale{1.0}
-        \plotone{QFfit_cylr1h25_PRIMUS_z02-08_slope-yint-err-fit_mass_100-115_105fidmass_03massbin}
-        \label{fig:qf}
-        \caption{QF at fiducial mass for $r_{\rm{ap}}=1 \rm{Mpc}$ and $h_{\rm{ap}}=25 \rm{Mpc}$}
-    \end{center}
-\end{figure*}
 \end{document}
-
-\end{document}

### 2014-02-25 qfenv_paper/qf_environment.tex
Updated paper

@@
 \usepackage{epsfig}
+\usepackage{rotating}
 \usepackage{amsmath}
@@
 appears dominated by decreases in the rates of star-formation of
-individual galaxies (\citealt{noeske07a}). There is evidence that a
+individual galaxies (\cite{Noeske:2007aa}). There is evidence that a
 large fraction of the decline associated with strongly
@@
 of the stellar mass function of quiescent and star-forming galaxies
-(\citealt{blanton06a, bundy06a, borch06a, moustakas13a}).  These
+(\cite{Blanton:2006aa},\citealt{bundy06a, borch06a, moustakas13a}).  These
 findings leave little room for the participation of
@@
 of sufficiently large samples. In this paper, we apply this approach
-using the Prism Multi-object Survey (PRIMUS; \citealt{coil11a,
-cool13a}), the largest available redshift survey covering the epochs
+using the Prism Multi-object Survey (PRIMUS; \cite{Coil:2011aa}, 
+\cite{Cool:2013aa}), the largest available redshift survey covering the epochs
 between $0<z<1$.
@@
 Furthermore \cite{Behroozi:2013aa}
-
 \begin{figure*}
@@
      \label{fig:smf}
-        \epsscale{1.0}
-        \plotone{fig_smf_cylr2h25_thresh75_bin0_25.png}
-        \caption{Stellar mass functions and quiescent fraction for galaxies in the $30$ subsamples divided into redshift bins, $0.06-0.145$ (green), $0.2-0.4$ (red), $0.4-0.6$ 
-(magenta), $0.6-0.8$ (blue), and $0.8-1.0$ (black) with low, mid, and high environments. The environments were classified using cylindrical aperture of $R=1\rm{Mpc}$ and $H=50\rm{Mpc}$ 
-with environment classification thresholds specified in Table \ref{tab:aperture}. The mass bins for the SMFs and QFs have widths $\Delta \rm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.3$. 
-SMFs for subsamples with the same environment density classification are plotted on panels along the same column: low (left), mid (middle), and high (right) environments. The top
-panels plot SMFs for subsamples with star forming galaxies. The middle panels plot the SMFs for subsamples with quiescent galaxies. The bottom panels plot the QFs for the 
-corresponding star-forming SMFs and quiescent SMFs in the same environment classification and redshift bin.}
+     \epsfig{file=fig_smf_cylr2h25_thresh75_bin0_25.eps,height=0.75\textwidth,angle=90}
+     \caption{Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) target galaxies in 
+low (left) and high (right) environments from redshift range $z=0-0.8$. The environment of each galaxy  
+was calculated using a cylindrical aperture size of $R=2\rm{Mpc}$ and $H=25\rm{Mpc}$ and  
+classification based on the cut-offs specified in Table \ref{tab:aperture}. The SMFs use mass bins of 
+width $\Delta \rm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.25$. In each panel we use shades of blue 
+(star-forming) and orange (quiescent) to represent the SMF at different redshift, higher redshifts being
+progressively lighter.}
     \end{center}
@@
 Furthermore, we impose a redshift limit $0.0375-0.145$ on the SDSS EDP sample as opposed 
-to the redshift range of $0.01-0.2$ in \cite{Moustakas:20133aa}.
+to the redshift range of $0.01-0.2$ in \cite{Moustakas:2013aa}.
 This is due to the lack of faint galaxies at $z \sim 0.2$ and the lack of bright 
@@
         \label{fig:smf}
-        \epsscale{1.0}
-        \plotone{fig_qf_cylr2h25_thresh75_bin0_25.png}
-        \caption{Quiescent fraction for galaxies in the $30$ subsamples divided into redshift bins, $0.06-0.145$ (green), $0.2-0.4$ (red), $0.4-0.6$ 
-(magenta), $0.6-0.8$ (blue), and $0.8-1.0$ (black) with low, mid, and high environments. The environments were classified using cylindrical aperture of $R=1\rm{Mpc}$ and $H=50\rm{Mpc}$ 
-with environment classification thresholds specified in Table \ref{tab:aperture}. The mass bins for the SMFs and QFs have widths $\Delta \rm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.3$. 
-SMFs for subsamples with the same environment density classification are plotted on panels along the same column: low (left), mid (middle), and high (right) environments. The top
-panels plot SMFs for subsamples with star forming galaxies. The middle panels plot the SMFs for subsamples with quiescent galaxies. The bottom panels plot the QFs for the 
-corresponding star-forming SMFs and quiescent SMFs in the same environment classification and redshift bin.}
+        \epsfig{file=fig_qf_cylr2h25_thresh75_bin0_25.eps,height=0.75\textwidth,angle=90}
+        \caption{Evolution of the quiescent fraction for target galaxies in low (left) and (high) environments
+from redshift range $z=0-0.8$. The QFs were calculated using the SMFs specificed in Figure \ref{fig:smf}. We use
+lighter shades of orange for the QFs at higher redshifts.}
     \end{center}
@@
         \label{fig:qf}
-        \caption{Quiescent fraction at fiducial mass $\rm{log} (\mathcal{M}/\mathcal{M}_{\odot}) = 10.5$ for low (triangle), mid (square) and high (circle) environments in redshift bins: $0.06-0.145$, $0.2-0.4$, $0.4-0.6$, $0.6-0.8$, and $0.8-1.0$.
-Comparing these linear fit values in the redshift range for the different environment densities suggest that the change in QFs is indepdent of environment density.}
+        \caption{Quiescent fraction at fiducial mass $\rm{log} (\mathcal{M}/\mathcal{M}_{\odot}) = 10.5$ for 
+low (square) and high (circle) environments in the redshift range $z = 0 - 0.8$. The evolution of 
+$f_{Q}(\mathcal{M}_{\rm{fid}})$ for galaxies in different environments shows an evolution over the redshift
+range that is independent of environment density. Futhermore throughout the redshift range the difference in 
+$f_{Q}(\mathcal{M}_{\rm{fid}})$ remains relatively constant and $ < 0.15$.}
     \end{center}

### 2014-02-25 qfenv_paper/qf_environment.tex
Abstract editted

@@
 \begin{abstract}
-We examine the evolution of the quiescent fraction (QF) for galaxies in 
-different density environments from $z=0.2-0.8$ using spectroscopic 
+We examine the evolution of the quiescent fraction ($f_{\rm{Q}}$) for galaxies in 
+different density environments from $z=0.0-0.8$ using spectroscopic 
 redshift and multi-wavelength imaging data from PRism MUlti-object 
-Survey (PRIMUS) and the Sloan Digitial Sky Survey (SDSS). Using this 
-data we construct a stellar mass limited target galaxy population of 
-$40430$ galaxies from PRIMUS within redshift range $0.2-1.0$ and $106732$
-galaxies from SDSS within redshift range $0.06-0.145$. This population 
-is then classified as quiescent or star-forming using an evolving cut 
-based on specific star-formation rate. The environment of the target 
-population is then measured using a fixed cylindrical aperture method 
+Survey (PRIMUS) and the Sloan Digitial Sky Survey (SDSS). We construct 
+a stellar mass limited target galaxy population of 
+$40430$ galaxies from PRIMUS within the redshift range $0.2-0.8$ and $106732$
+galaxies from SDSS within redshift range $0.0375-0.145$. We classify  
+these target galaxies as quiescent or star-forming using an evolving cut 
+based on specific star formation rate (SSFR). For each of these galaxies 
+we also measure its environment using a fixed cylindrical aperture method 
 on a volume-limited {\em Environment Defining Population} constructed
-from PRIMUS and SDSS.
+from PRIMUS and SDSS. Based on its environment measurements we classify our target
+population into high or low density environments.
 
-Thresholds for the environment are imposed to classify the target galaxies as
-high, mid, or low environments. For the quiescent and star-forming 
-target galaxies we calculate the stellar mass functions in different environments and redshift.
-Afterwards, we compute the QFs using the SMFs for the different environment 
-and redshift ranges.  Comparing the QFs in these environment and redshift bins, we find the 
-QF increases over cosmic time (decrease in redshift); however, the change of 
-the QFs for the different environments are independent of the 
-environment of galaxies. 
+With the target galaxy population divided into quiescent and star-forming galaxies 
+in high and low density environments, we calculate the stellar mass functions 
+(SMFs) for each of these subsamples. Over the redshift range $z=0.8$ to $0.0$, 
+in high density environments we find that the SMFs of the quiescent galaxies 
+increase by a factor of $over9000$ for $\mathcal{M}_{*} < 11.0$ while the SMF 
+of the star-forming galaxies evolves little for all masses. Meanwhile in low 
+density environments from $z=0.8$ to $0.0$, we find that the SMF of quiescent 
+galaxies evolves little for all stellar masses and the SMF of star-forming 
+galaxies decreases by a factor of $over9000$ for $\mathcal{M}_{*} > 10.5$.  
+Furthermore, we compute the $f_{\rm{Q}}$s using the SMFs in the subsamples to 
+examine the evolution of the $f_{\rm{Q}}$ in high and low density environments
+over the redshift range. We find that at $\mathcal{M}_{*} \sim 10.5$, $f_{\rm{Q}}$ 
+increases by $\sim 0.15$ from $z=0.8$ to $0.0$ for both high and low environments. 
+In addition, throughout the entire redshift range the difference between the
+$f_{\rm{Q}}$ at high and low environment remains constant at $\sim 0.1$. 
+These results suggest that the evolution of $f_{\rm{Q}}$ is independent of environment. 
 \end{abstract}
@@
 \section{Introduction}
+\begin{table*} %Subject to significant change based on the classification of environment
+  \caption{Summary of Galaxy Subsample}
+  \label{tab:subsample}
+  \begin{center}
+    \leavevmode
+    \begin{tabular}{lllll} \hline \hline              
+  Survey    &Redshift ($z$) &Density        &Quiescent $N_{\rm{g}}$ &Star-forming $N_{\rm{g}}$  \\ \hline 
+  SDSS      &$0.0375-0.145$ &High           &5470                       &4501                           \\
+            &               &Mid            &3614                       &4438                           \\
+            &               &Low            &5419                       &8927                           \\
+            &               &               &                       &                           \\ \hline
+  PRIMUS    &$0.2-0.4$      &High           &322                    &583                           \\
+            &               &Mid            &177                    &403                          \\
+            &               &Low            &768                    &2516                           \\
+            &               &               &                       &                           \\ \hline
+  PRIMUS    &$0.4-0.6$      &High           &350                       &675                           \\
+            &               &Mid            &195                       &405                           \\
+            &               &Low            &871                       &2385                           \\
+            &               &               &                       &                           \\ \hline
+  PRIMUS    &$0.6-0.8$      &High           &347                       &430                           \\
+            &               &Mid            &186                       &327                           \\
+            &               &Low            &833                       &1847                           \\
+            &               &               &                       &                           \\ \hline
+  PRIMUS    &$0.8-1.0$      &High           &136                       &232                           \\
+            &               &Mid            &94                       &163                           \\
+            &               &Low            &373                       &810                           \\
+            &               &               &                       &                           \\ \hline
+  \multicolumn{5}{l}{}                                             \\       
+    \end{tabular} 
+  \end{center}
+\end{table*}
 Galaxies, in their detailed properties, carry the imprints of their
@@
 
-\begin{table*} %Subject to significant change based on the classification of environment
-  \caption{Summary of Galaxy Subsample}
-  \label{tab:subsample}
-  \begin{center}
-    \leavevmode
-    \begin{tabular}{lllll} \hline \hline              
-  Survey    &Redshift ($z$) &Density        &Quiescent $N_{\rm{g}}$ &Star-forming $N_{\rm{g}}$  \\ \hline 
-  SDSS      &$0.0375-0.145$ &High           &5470                       &4501                           \\
-            &               &Mid            &3614                       &4438                           \\
-            &               &Low            &5419                       &8927                           \\
-            &               &               &                       &                           \\ \hline
-  PRIMUS    &$0.2-0.4$      &High           &322                    &583                           \\
-            &               &Mid            &177                    &403                          \\
-            &               &Low            &768                    &2516                           \\
-            &               &               &                       &                           \\ \hline
-  PRIMUS    &$0.4-0.6$      &High           &350                       &675                           \\
-            &               &Mid            &195                       &405                           \\
-            &               &Low            &871                       &2385                           \\
-            &               &               &                       &                           \\ \hline
-  PRIMUS    &$0.6-0.8$      &High           &347                       &430                           \\
-            &               &Mid            &186                       &327                           \\
-            &               &Low            &833                       &1847                           \\
-            &               &               &                       &                           \\ \hline
-  PRIMUS    &$0.8-1.0$      &High           &136                       &232                           \\
-            &               &Mid            &94                       &163                           \\
-            &               &Low            &373                       &810                           \\
-            &               &               &                       &                           \\ \hline
-  \multicolumn{5}{l}{}                                             \\       
-    \end{tabular} 
-  \end{center}
-\end{table*}
+\section{Sample Selection}
+In this paper we are interested in measuring the evolution of the quiescent 
+fraction over a wide range of redshifts and in different galaxy density environments. 
+In order construct a sample with redshift depth and robust enough redshift values 
+to measure galaxy environment, we use galaxies at intermediate redshifts from PRIMUS. 
+Additionally we supplement our sample with galaxies at low redshift ($z \sim 0.1$) from SDSS.
 
-\section{Sample Selection}
-In this paper we are interested in measuring the quiescent fraction over a wide range of redshifts and for galaxies in different environments. 
-To do so, we use galaxies at intermediate redshifts from PRIMUS and galaxies at low redshift from SDSS.
-
-We begin with a brief summary of the PRIMUS data in Section~\ref{sec:primus} followed by a summary of the SDSS data in Section~\ref{sec:sdss}.
-Then in Section~\ref{sec:target} we use this data to define the stellar mass complete target galaxy population.
+We begin with a brief summary of the PRIMUS data in Section \ref{sec:primus} followed by a summary of the SDSS data in Section \ref{sec:sdss}.
+Then in Section \ref{sec:target} we use this data to define the stellar mass complete target galaxy population.
 Afterwards, in Section~\ref{sec:sfq}, we classify these target galaxies as quiescent or active star-forming galaxies. 
-Then for each of the classified target galaxies, in Section \ref{sec:environment}, we obtain the environment using a volume-limited {\em Environment Defining Population}.
-Finally in Section \ref{sec:edgeeffect}, we correct the target galaxy environment for the survey edge effects.
+We then obtain the environment for the target galaxy population using a volume-limited {\em Environment Defining Population} in Section \ref{sec:environment}. 
+Finally in Section \ref{sec:edgeeffect}, we impose cuts on the target galaxy environment based on the edges of the survey.
 
@@
 in a simplified Bayesian framework.
-\texttt{iSEDfit}, which we will only briefly mention in this paper is discussed in detail in Appendix A of \cite{Moustakas:2013aa}.
+\texttt{iSEDfit}, which we will only briefly mention in this paper is discussed in detail in Appendix A. of \cite{Moustakas:2013aa}.
 The code uses the redshift and the observed photometry of the galaxies to determine the statistical likelihood of a large ensemble of generated model SEDs. 
@@
 	\plotone{fig_EDP_absmag_redshift.png}
-        \caption{Absolute magnitude $M_{r}$ vs.
-redshift for the target galaxy population (black) with the Environment Defining Population (red) plotted on top.
-Both samples are divided into redshift bins:$0.06-0.145$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$.
-The target galaxy population is stellar mass complete (Section \ref{sec:target} while the EDP is volume limited through $M_{g}$ limits (Section \ref{sec:environment}).}
+        \caption{Absolute magnitude $M_{r}$ versus redshift for the target galaxy population (black) with the 
+Environment Defining Population (red) plotted on top. Both samples are divided into redshift bins:$0.0375-0.145$, 
+$0.2-0.4$, $0.4-0.6$, and $0.6-0.8$. Stellar mass completeness limits are imposed on the target galaxy population (Section \ref{sec:target}) 
+while the $M_{r}$ limits are imposed on the EDP (Section \ref{sec:environment}).}
     \end{center}
@@
 Value-Added Galaxy Catalog that satisfy the main sample criterion and have galaxy extinction corrected Petrosian magnitudes $14.5 < r < 17.6$ 
-and spectroscopic redshits $0.01<z<0.2$ (\cite{Blanton:2005aa}). 
+and spectroscopic redshits within $0.01<z<0.2$ (\cite{Blanton:2005aa}). 
 Within this sample, we select galaxies with medium depth observations from GALEX. 
@@
 
-To obtain the stellar masses and SFRs for the SDSS data, we use \texttt{iSEDfit} as done in Section \ref{sec:primus}. 
-Except we use twelve photometric bands: {\em GALEX} FUV and NUV, SDSS $ugriz$, 2MASS $JHK_{s}$, and WISE $3.4$ and $4.6 \mu \rm{m}$.
-\subsection{Galaxy Samples} \label{sec:target} 
-In this seciton we will define the galaxy sample we use for our SMFs and QFs.
+To obtain the stellar masses and SFRs for the SDSS data we use \texttt{iSEDfit}, as we did for the PRIMUS data in Section \ref{sec:primus}.  
+However, we use twelve photometric bands: {\em GALEX} FUV and NUV, SDSS $ugriz$, 2MASS $JHK_{s}$, and WISE $3.4$ and $4.6 \mu \rm{m}$.
+
+\subsection{Target Galaxy Samples} \label{sec:target} 
+In this seciton we will define the target galaxy sample we use for our SMFs and QFs.
 The population at intermediate redshift is derived from the PRIMUS data and the population at low redshift is derived from the SDSS data, both described above.
@@
 We then exclude stars and broad-line AGN to only select objects spectroscopically classified as galaxies, with high-quality spectroscopic redshifts ($Q \geq 3$) within the 
-redshift range $0.2 - 1.0$.
-Afterwards we assign statistical weights (described in \cite{Coil:2011aa} and \cite{Cool:2013aa}) to the objects in order to correct for targeting incompleteness and redshift 
-failures.
+redshift range $0.2 - 0.8$.
+Afterwards we assign statistical weights (described in \cite{Coil:2011aa} and \cite{Cool:2013aa}) to the objects in order to correct for targeting incompleteness and redshift failures.
 The statistical weight, $w_i$, for each galaxy is given by
@@
 \end{equation}
-Equation 1 in \cite{Moustakas:2013aa}.
+Equation (1) in \cite{Moustakas:2013aa}.
 In addition to the selection criteria above, we impose stellar mass limits to have a stellar mass complete sample.  
@@
 In order to obtain the fixed aperture based environment for the galaxies in the target population, 
-we first establish a volume limited {\it Environment Defining Population} (EDP) by imposing a fixed 
-cumulative number density absolute magnitude cut off. 
-By using a fixed cumulative number density for this sample we seek to build an EDP with galaxies that 
-have similar populations in all of the redshift bins i.e. accounting for the progenitor bias. 
+we first construct a volume limited {\it Environment Defining Population} (EDP) with absolute 
+magnitude cut-offs ($M_{r}$) at each redshift bin. The $M_{r}$ cut-offs are selected so that  
+the cumulative number density of all redshift bin are equal to one another. 
+We use this fixed cumulative number density at each redshift bin in order to build an EDP with galaxies that 
+have similar populations in all of the redshift bins i.e. accounts for the progenitor bias. 
 As \cite{Behroozi:2013aa} and \cite{Leja:2013aa} find in their analysis of the cumulative number density 
 method using a dark matter simulation with abundance matching and a semi-analytic model, respectively, 
-cumulative number density method, while it does not precisely account for the scatter in mass accretion or 
-galaxy-galaxy mergers, provides a promising tool to compare galaxy populations over a wide range of cosmic time.
+the cumulative number density method, while it does not precisely account for the scatter in mass accretion or 
+galaxy-galaxy mergers, provides a reasonable means to compare galaxy populations over a wide range of cosmic time. 
 In addition we use the highest redshift bin cumulative number density as the fixed number density 
@@
 The EDP for the PRIMUS sample is derived from the same parent sample as the target galaxies. 
-We restrict the PRIMUS EDP galaxies within the redshift range $0.2-1.0$ and divide them into redshift bins of width $\Delta z = 0.2$. 
-For each of these redshift bins, we impose separate absolute magnitude ($M_{g,\rm{lim}}$) limits such 
+We restrict the PRIMUS EDP galaxies within the redshift range $0.2-0.8$ and divide them into redshift bins of width $\Delta z = 0.2$. 
+For each of these redshift bins, we impose separate absolute magnitude limits ($M_{r,\rm{lim}}$) such 
 that the cumulative number density of the sample ordered by $M_{g}$ is equal to the cumulative 
@@
 
-For the EDP of the SDSS-{\em GALEX} sample (hereafter simply referred to as the SDSS EDP), 
-we do not use the parent sample of the data due to 
+For the EDP of the SDSS-{\em GALEX} sample (hereafter referred to as the SDSS EDP), we do not use the parent sample of the data due to 
 the geometry of the combined angular selection function of the SDSS VAGC and {\em GALEX}. 

### 2014-02-27 qfenv_paper/qf_environment.tex
Section 2 edited

@@
 \begin{abstract}
-We examine the evolution of the quiescent fraction ($f_{\rm{Q}}$) for galaxies in 
-different density environments from $z=0.0-0.8$ using spectroscopic 
+We present the evolution of the quiescent fraction ($f_{\rm{Q}}$) for galaxies in 
+different density environments from $z=0.0$ to $0.8$ using spectroscopic 
 redshift and multi-wavelength imaging data from PRism MUlti-object 
 Survey (PRIMUS) and the Sloan Digitial Sky Survey (SDSS). We construct 
-a stellar mass limited target galaxy population of 
-$40430$ galaxies from PRIMUS within the redshift range $0.2-0.8$ and $106732$
-galaxies from SDSS within redshift range $0.0375-0.145$. We classify  
-these target galaxies as quiescent or star-forming using an evolving cut 
-based on specific star formation rate (SSFR). For each of these galaxies 
-we also measure its environment using a fixed cylindrical aperture method 
-on a volume-limited {\em Environment Defining Population} constructed
-from PRIMUS and SDSS. Based on its environment measurements we classify our target
-population into high or low density environments.
+a stellar mass limited galaxy population of 
+$\sim 40000$ galaxies from PRIMUS within the redshift range $0.2-0.8$ and $\sim 100000$
+galaxies from SDSS within redshift range $0.0375-0.145$. Using an evolving cut based on
+specific star formation, we classify the galaxies as quiescent or star-forming and
+measure its environment using a fixed cylindrical aperture method 
+on a volume-limited {\em Environment Defining Population} we construct 
+from PRIMUS and SDSS. Based on its environment we classify our target
+population into dense or sparse environments.
 
 With the target galaxy population divided into quiescent and star-forming galaxies 
-in high and low density environments, we calculate the stellar mass functions 
-(SMFs) for each of these subsamples. Over the redshift range $z=0.8$ to $0.0$, 
-in high density environments we find that the SMFs of the quiescent galaxies 
-increase by a factor of $over9000$ for $\mathcal{M}_{*} < 11.0$ while the SMF 
-of the star-forming galaxies evolves little for all masses. Meanwhile in low 
-density environments from $z=0.8$ to $0.0$, we find that the SMF of quiescent 
-galaxies evolves little for all stellar masses and the SMF of star-forming 
-galaxies decreases by a factor of $over9000$ for $\mathcal{M}_{*} > 10.5$.  
-Furthermore, we compute the $f_{\rm{Q}}$s using the SMFs in the subsamples to 
-examine the evolution of the $f_{\rm{Q}}$ in high and low density environments
-over the redshift range. We find that at $\mathcal{M}_{*} \sim 10.5$, $f_{\rm{Q}}$ 
-increases by $\sim 0.15$ from $z=0.8$ to $0.0$ for both high and low environments. 
-In addition, throughout the entire redshift range the difference between the
-$f_{\rm{Q}}$ at high and low environment remains constant at $\sim 0.1$. 
-These results suggest that the evolution of $f_{\rm{Q}}$ is independent of environment. 
+in dense and sparse environments, we calculate the stellar mass functions 
+(SMFs) for each of these subsamples. % should I include any conclusions on SMF in the abstract? 
+With these SMFs, we compute the $f_{\rm{Q}}$s to find that at 
+$\mathcal{M}_{*} \sim 10.5$, $f_{\rm{Q}}$ increases by $\sim 0.15$ from 
+$z=0.8$ to $0.0$ for both high and low environments. 
+In addition, throughout the redshift range the difference between the
+$f_{\rm{Q}}$ at high and low environment remains constant at $< 0.1$. 
+These results suggest that while $f_{\rm{Q}}$ increases for galaxies in 
+both dense and sparse environments over redshift, the evolution of $f_{\rm{Q}}$ 
+is independent of environment. 
+%The SMF evolution suggests that in dense environments over the redshift range $z=0.8$ to $0.0$, the SMF of 
+%quiescent galaxies increase by a factor of $over9000$ for $\mathcal{M}_{*} < 11.0$ 
+%while the SMF of the star-forming galaxies evolves little for all masses. Meanwhile in low 
+%density environments from $z=0.8$ to $0.0$, we find that the SMF of quiescent 
+%galaxies evolves little for all stellar masses and the SMF of star-forming 
+%galaxies decreases by a factor of $over9000$ for $\mathcal{M}_{*} > 10.5$.  
 \end{abstract}
@@
 \section{Introduction}
-\begin{table*} %Subject to significant change based on the classification of environment
-  \caption{Summary of Galaxy Subsample}
-  \label{tab:subsample}
-  \begin{center}
-    \leavevmode
-    \begin{tabular}{lllll} \hline \hline              
-  Survey    &Redshift ($z$) &Density        &Quiescent $N_{\rm{g}}$ &Star-forming $N_{\rm{g}}$  \\ \hline 
-  SDSS      &$0.0375-0.145$ &High           &5470                       &4501                           \\
-            &               &Mid            &3614                       &4438                           \\
-            &               &Low            &5419                       &8927                           \\
-            &               &               &                       &                           \\ \hline
-  PRIMUS    &$0.2-0.4$      &High           &322                    &583                           \\
-            &               &Mid            &177                    &403                          \\
-            &               &Low            &768                    &2516                           \\
-            &               &               &                       &                           \\ \hline
-  PRIMUS    &$0.4-0.6$      &High           &350                       &675                           \\
-            &               &Mid            &195                       &405                           \\
-            &               &Low            &871                       &2385                           \\
-            &               &               &                       &                           \\ \hline
-  PRIMUS    &$0.6-0.8$      &High           &347                       &430                           \\
-            &               &Mid            &186                       &327                           \\
-            &               &Low            &833                       &1847                           \\
-            &               &               &                       &                           \\ \hline
-  PRIMUS    &$0.8-1.0$      &High           &136                       &232                           \\
-            &               &Mid            &94                       &163                           \\
-            &               &Low            &373                       &810                           \\
-            &               &               &                       &                           \\ \hline
-  \multicolumn{5}{l}{}                                             \\       
-    \end{tabular} 
-  \end{center}
-\end{table*}
 Galaxies, in their detailed properties, carry the imprints of their
@@
 In this paper we are interested in measuring the evolution of the quiescent 
-fraction over a wide range of redshifts and in different galaxy density environments. 
+fraction over a wide range of redshifts and in different galaxy environments. 
 In order construct a sample with redshift depth and robust enough redshift values 
@@
 Afterwards, in Section~\ref{sec:sfq}, we classify these target galaxies as quiescent or active star-forming galaxies. 
-We then obtain the environment for the target galaxy population using a volume-limited {\em Environment Defining Population} in Section \ref{sec:environment}. 
-Finally in Section \ref{sec:edgeeffect}, we impose cuts on the target galaxy environment based on the edges of the survey.
+For each galaxy we obtain the environment using a volume-limited {\em Environment Defining Population} in Section \ref{sec:environment}. 
+Finally in Section \ref{sec:edgeeffect}, we correct the galaxy sample and its environment measurements for the edge effects of the surveys.
 
@@
 For a more detailed description of the data used in this paper, we refer readers to \cite{Moustakas:2013aa} Section 2 and Section 4.1.
+\begin{table} %Subject to significant change based on the classification of environment
+  \caption{Galaxy Subsamples}
+  \label{tab:subsample}
+  \begin{center}
+    \leavevmode
+    \begin{tabular}{lllll} \hline \hline              
+  Survey    &Redshift ($z$) &Density        &Quiescent  &Star-forming  \\ \hline 
+  SDSS      &$0.0375-0.145$ &High           &5470                       &4501                           \\
+            &               &Mid            &3614                       &4438                           \\
+            &               &Low            &5419                       &8927                           \\
+            &               &               &                       &                           \\ \hline
+  PRIMUS    &$0.2-0.4$      &High           &322                    &583                           \\
+            &               &Mid            &177                    &403                          \\
+            &               &Low            &768                    &2516                           \\
+            &               &               &                       &                           \\ \hline
+  PRIMUS    &$0.4-0.6$      &High           &350                       &675                           \\
+            &               &Mid            &195                       &405                           \\
+            &               &Low            &871                       &2385                           \\
+            &               &               &                       &                           \\ \hline
+  PRIMUS    &$0.6-0.8$      &High           &347                       &430                           \\
+            &               &Mid            &186                       &327                           \\
+            &               &Low            &833                       &1847                           \\
+            &               &               &                       &                           \\ \hline
+  PRIMUS    &$0.8-1.0$      &High           &136                       &232                           \\
+            &               &Mid            &94                       &163                           \\
+            &               &Low            &373                       &810                           \\
+            &               &               &                       &                           \\ \hline
+  \multicolumn{5}{l}{}                                             \\       
+    \end{tabular} 
+  \end{center}
+\end{table}
 
@@
 \subsection{Target Galaxy Samples} \label{sec:target} 
-In this seciton we will define the target galaxy sample we use for our SMFs and QFs.
-The population at intermediate redshift is derived from the PRIMUS data and the population at low redshift is derived from the SDSS data, both described above.
+In this seciton we will define the target galaxy sample we use to compute the SMFs and QFs.
+The population at $z \sim 0.5$ is derived from the PRIMUS data and the population at $z \sim 0.1$ is derived from the SDSS data, both described above.
 For the intermediate redshift target galaxy population, we begin with the selection criteria imposed in \cite{Moustakas:2013aa} for its parent sample.
-We take the statistically complete {\em primary} sample from the PRIMUS data, \cite{Coil:2011aa}, and then we impose magnitude limits on optical selection bands as specified in 
+We take the statistically complete {\em primary} sample from the PRIMUS data (\cite{Coil:2011aa}) and then impose magnitude limits on optical selection bands as specified in 
 \cite{Moustakas:2013aa} Table 1.
@@
 As done in \cite{Moustakas:2013aa}, we follow \cite{Pozzetti:2010aa} to empirically determine the stellar mass completeness limits.
-Briefly, for each of the target galaxies we compute $\mathcal{M}_{\rm{lim}}$ using $log \mathcal{M}_{\rm{lim}} = log \mathcal{M} + 0.4 ( m - m_{\rm{lim}})$.
+Briefly, for each of the target galaxies we compute $\mathcal{M}_{\rm{lim}}$ using $\rm{log} \; \mathcal{M}_{\rm{lim}} = \rm{log} \; \mathcal{M} + 0.4 ( m - m_{\rm{lim}})$.
 $\mathcal{M}$ is the stellar mass of the galaxy in units of $\mathcal{M_{\odot}}$, $\mathcal{M}_{\rm{lim}}$ is the stellar mass of each galaxy if its magnitude was 
@@
 and star-forming galaxies is included in the following section).
-Finally, we use these polynomials to obtain the minimum stellar masses at the center of the redshift bins, $0.2-0.4$, $0.4-0.6$, $0.6-0.8$, and $0.8-1.0$.
-Note that these redshift bins will later be used to divide the target population during SMF and QF calculations.
+Finally, we use the polynomials to obtain the minimum stellar masses at the center of the redshift bins, $0.2-0.4$, $0.4-0.6$, $0.6-0.8$, and $0.8-1.0$.
+These redshift bins will later be used to divide the target sample in order to compute the SMFs and QFs.
 
 For our target galaxy population at low redshift we use our SDSS-{\em GALEX} data. 
-We limit our target population within the redshift range $0.06-0.145$ due to redshift limits later imposed for the volume-limited Environment Defining Population (\ref{sec:environment}).
+We limit our target population within the redshift range $0.0375-0.145$ due to redshift limits later imposed for the volume-limited Environment Defining Population (Section \ref{sec:environment}).
 The NYU-VAGC provides statistical weight estimates for targeting completeness.
@@
 brightness and stellar mass-to-light ratio completness limits (\cite{Blanton:2005ab}; \cite{Baldry:2008aa}).
-The absolute magnitude ($M_g$) versus redshift for the target galaxy population at both low redshift and intermediate redshift is plotted in Figure \ref{fig:targetEDP}.
-We again refer readers to \cite{Moustakas:2013aa} for details; more specifically, Figure 2., Sections 3.1, and 4.3.
+The absolute magnitude ($M_{r}$) versus redshift for the target galaxy population at both low redshift and intermediate redshift is plotted in Figure \ref{fig:targetEDP}.
+For further details we refer readers to \cite{Moustakas:2013aa} for details; more specifically, Figure 2., Sections 3.1, and 4.3.
 
 \subsection{Classifying Quiescent and Star-Forming Galaxies} \label{sec:sfq}
-We classify the galaxies from the target sample, defined in the last section, using an evolving cut based on specific star-formation rate utilized in \cite{Moustakas:2013aa}.
-For a detailed description of the classification scheme, we refer readers to Section 3.2 in \cite{Moustakas:2013aa}.
-
+With the galaxy sample defined in the previous section, we now classify the galaxies as quiescent or star-forming using an evolving cut based on specific star-formation rate utilized in \cite{Moustakas:2013aa} Section 3.2.
 To summarize, this classification method utilizes the star-forming (SF) sequence, which is the correlation between star-formation rate (SFR) and stellar mass in star-forming 
 galaxies observed at least until $z \sim 2$.
-As stated in \cite{Moustakas:2013aa}, the PRIMUS sample displays a well-defined SF sequence within the redshift range of our target population.
+The PRIMUS sample displays a well-defined SF sequence within the redshift range of our target population.
 Using the power-law slope for the SF sequence derived by \cite{Salim:2007aa} (SFR $\propto \mathcal{M}^{0.65}$) and the minimum of the quiescent/star-forming bimodality, 
-determined by eye, we obtain the following equation to classify the target galaxies (Equation 2 in \cite{Moustakas:2013aa}):
+determined empirically, we obtain the following equation to classify the target galaxies (Equation 2 in \cite{Moustakas:2013aa}):
 \begin{equation}
@@
 
-\subsection{Galaxy Environment} \label{sec:environment}
-We define the environment of a galaxy as the number of neighboring galaxies contained within a fixed aperture centered around it.
-We use fixed cylindrical apertures with dimensions specified in Table \ref{tab:aperture} to probe the environment of the target sample galaxies. 
-A fixed cylindrical apertures was chosen over a spherical one, often used in literature (e.g. \cite{Croton:2005aa}), due to redshift errors in the PRIMUS data 
-and considerations of redshift space distortions within our PRIMUS data redshift range, $[0.2,1.0]$.
-Furthermore, we use aperture dimensions listed in Table \ref{tab:aperture} based on the analysis of scale dependence for clustering in \cite{Blanton:2006aa}.
-As \cite{Blanton:2006aa} suggests, galactic properties such as their star-formation histories are dependent on properties such as the masses of their host dark matter halos.
-Hence, by employing fixed cylindrical apertures with $r_{\rm{ap}} = 1, 2 \rm{Mpc}$ we are able to probe the local small scale environment within the scales of the host dark matter halos.
-As a comparison, we also include fixed cylindrical apertures with $r_{\rm{ap}} \ge 5 \rm{Mpc}$ to probe large scale environment, which \cite{Blanton:2006aa} finds to be unrelated to the 
-recent star formation history of galaxies.
-
-In order to obtain the fixed aperture based environment for the galaxies in the target population, 
-we first construct a volume limited {\it Environment Defining Population} (EDP) with absolute 
-magnitude cut-offs ($M_{r}$) at each redshift bin. The $M_{r}$ cut-offs are selected so that  
-the cumulative number density of all redshift bin are equal to one another. 
-We use this fixed cumulative number density at each redshift bin in order to build an EDP with galaxies that 
-have similar populations in all of the redshift bins i.e. accounts for the progenitor bias. 
-As \cite{Behroozi:2013aa} and \cite{Leja:2013aa} find in their analysis of the cumulative number density 
-method using a dark matter simulation with abundance matching and a semi-analytic model, respectively, 
-the cumulative number density method, while it does not precisely account for the scatter in mass accretion or 
-galaxy-galaxy mergers, provides a reasonable means to compare galaxy populations over a wide range of cosmic time. 
-In addition we use the highest redshift bin cumulative number density as the fixed number density 
-%%%FINISH THIS SENTENCE
-Furthermore \cite{Behroozi:2013aa}
 \begin{figure*}
@@
 
-The EDP for the PRIMUS sample is derived from the same parent sample as the target galaxies. 
-We restrict the PRIMUS EDP galaxies within the redshift range $0.2-0.8$ and divide them into redshift bins of width $\Delta z = 0.2$. 
-For each of these redshift bins, we impose separate absolute magnitude limits ($M_{r,\rm{lim}}$) such 
-that the cumulative number density of the sample ordered by $M_{g}$ is equal to the cumulative 
-number density of the highest redshift bin with an empirically determined limit. 
-First, to determine the highest redshift bin ($0.8-1.0$) limit we look at the $M_{g}$ distribution with bin size
-$\Delta M_{g} = 0.25$ and select $M_{g,\rm{lim}}$ to be the $M_{g}$ value near the peak of the 
-distribution where number density of the bins with fainter objects (greater $M_{g}$ value) are smaller
-than the number density of the bin at $M_{g, \rm{lim}}$. 
-We find this $M_{g, \rm{lim}}( 0.8 < z < 1.0)$ to be, conservatively, $M_{g} = -20.75$. 
-With this value we then calculate the rest of the $M_{g, \rm{lim}}$s by finding the
-$M_{g}$ value where the cumulative number density ordered by absolute magnitude of the redshift bins 
-equals that of the the highest redshift bin at $M_{g, \rm{lim}}( 0.8 < z < 1.0)$. 
-Note that when calculating the number densities, the number of galaxies takes into account the 
-statistical weights (described in Section \ref{sec:primus} and \ref{sec:sdss}).
+\subsection{Galaxy Environment} \label{sec:environment}
+In addition to the quiescent/star-forming classification, we now measure the environment for the target galaxy sample. 
+First, we define the environment of a galaxy as the number of neighboring galaxies contained within a fixed aperture centered around it.
+As our aperture, we use a cylinder with dimensions with $R_{\rm{ap}} = 2 \; \rm{Mpc}/h$ and $H_{\rm{ap}} = 25 \; \rm{Mpc}/h$. 
+Though spherical apertures are often used in literature (e.g. \cite{Croton:2005aa}), we use a cylindrical aperture in order to 
+account for the PRIMUS redshift errors and redshift space distortions.  
+Furthermore, we use a cylinder with the specified dimensions based on scale dependence for clustering analysis done in 
+\cite{Blanton:2006aa}, which suggests that galactic properties such as star-formation histories are dependent on properties
+ such as the masses of their host dark matter halos.
+Hence, with cylindrical apertures of $R_{\rm{ap}} = 2 \; \rm{Mpc}/h$ we are able to probe the local small scale environment 
+within the scales of the host dark matter halos.
+We extend our analysis to cylindrical apertures with cylindrical apertures with $R_{\rm{ap}} = 1 \; \rm{Mpc}/h$; however 
+we find that the variation in $R_{\rm{ap}}$ does not change our results significantly (difference in $f_{Q} < 0.05$). 
+Similar fixed aperture methods have also been used in \cite{Croton:2005aa} for galaxies in the 2dF Galaxy Redshift 
+Survey (\cite{Colless:2003aa}) and in \cite{Muldrew:2012aa} for a mock galaxy catalogue generated from embedding 
+galaxies onto the Millenium Dark Matter Simulation (\cite{Springel:2005aa}). 
+%include a sentence that sums up everything in Croton and Muldrew?
 
-For the EDP of the SDSS-{\em GALEX} sample (hereafter referred to as the SDSS EDP), we do not use the parent sample of the data due to 
-the geometry of the combined angular selection function of the SDSS VAGC and {\em GALEX}. 
-Instead, since we are not interested in the $FUV, NUV$ values for the EDP, we just use the
-SDSS VAGC where the SDSS-{\em GALEX} catalog is derived from. 
-Furthermore, we impose a redshift limit $0.0375-0.145$ on the SDSS EDP sample as opposed 
-to the redshift range of $0.01-0.2$ in \cite{Moustakas:2013aa}.
-This is due to the lack of faint galaxies at $z \sim 0.2$ and the lack of bright 
-galaxies at $z \sim 0.01$. 
-In other words, the lower bound for the redshif range was empirically determined by the bright limit of 
-the $M_{g}$ versus redshift distribution and the upper bound by the faint limit of the 
-$M_{g}$ versus redshift distribution. 
-The same fixed cumulative number density method is used on this SDSS EDP. 
-Ultimately we use $M_{g,\rm{lim}} = -20.57$, $-20.73$, $-20.80$ and $-20.95$ for the redshift bins 
-$0.06-0.145$, $0.2-0.4$, $0.4-0.6$, $0.6-0.8$, respectively. 
-These absolute magnitude limits are illustrated in Figure \ref{fig:targetEDP}, which plots the absolute magnitude versus the redshift for the EDP galaxies and the target galaxies.
+In order to measure environment using an aperture defined above, we first construct a volume limited 
+{\em Environment Defining Population} (EDP) with absolute magnitude cut-offs ($M_{r}$) at each redshift bin. 
+The $M_{r}$ cut-offs are selected so that the cumulative number density over $M_{r}$ at all redshift bins are equal. 
+By equating the cumulative number densities at different redshifts not only can we reasonably compare the 
+environment values at different redshift bins but we also attempt to build an EDP that has a similar galaxy 
+population in all of the redshift bins i.e. accounts for the progenitor bias. 
+As \cite{Behroozi:2013aa} and \cite{Leja:2013aa} find in their analysis of the cumulative number density 
+method using a dark matter simulation with abundance matching and a semi-analytic model, respectively, 
+the cumulative number density method, while it does not precisely account for the scatter in mass accretion or 
+galaxy-galaxy mergers, provides a reasonable means to compare galaxy populations over a wide range of cosmic time. 
+Furthermore \cite{Behroozi:2013aa} %%%FINISH THIS SENTENCE
 
-Using the above definition of environment and the EDP galaxies, we obtain the environment for each of the target population galaxies by counting the number of EDP galaxies, 
-$n_{env}$, within the fixed cylinder aperture surrounding it. 
-Since we use apertures of different dimensions, we are interested in the relative densitites rather than the actual $n_{env}$ values.
-Hence, we use the percentage rank of the galaxy environment to quantify overdense environments and underdense environments.
-More specifically, for each of the redshift bins ($0.2-0.4$, $0.4-0.6$, $0.6-0.8$, and $0.8-1.0$) the $n_{env}$ values for all target galaxies in that bin are listed and assigned a percentage rank based on their position in the list: $n_{env} = 0$ corresponding to $0\%$ and the maximum $n_{env}$ for a target galaxy in the $z$-bin corresponding to $100\%$.
-Using these percentage ranks, each target galaxy is classified as high-, mid-, or low-environment based on the cut-offs specified in Table \ref{tab:aperture}. 
-Target sample galaxies are classified as high-environment if its percentage rank lies within the top $20\%$ and as low-environment if its percentage rank lies within the bottom $20\%$. 
-In Table \ref{tab:aperture}, apertures with radius $1 h^{-1} \rm{Mpc}$ have a low-eneivonrment cut-off of higher than $20\%$.
-This is because over $20\%$ of target sample galaxies have $n_{env}=0$ such a smaller aperture size.
-Hence we defined the low-environment percentage rank cut-off to contain all galaxies with $n_{env}=0$. 
-In order to have a fair comparison for the different $z$-bins when using this aperture, the low-environment cut-off was selected as the lowest cut-off that includes all galaxies with $n_{env}=0$ for all $z$-bin.
-More specific details for the high- and low-environment cut-offs are provided in Table \ref{tab:aperture}.
+To construct the EDP for the PRIMUS (hereafter PRIMUS EDP) we use the same PRIMUS data as the 
+target galaxies, described in Section \ref{sec:target}. 
+We restrict the PRIMUS galaxies to $0.2 < z < 0.8$ and divide them into bins of $\Delta z = 0.2$. 
+Before we consider the cumulative number densities in these bins, we first determine $M_r$ limit for the 
+highest redshift bin ($0.6-0.8$) by examining the $M_{r}$ distribution with bin size $\Delta M_{r} = 0.25$ 
+and select $M_{r,\rm{lim}}$ near the peak of the distribution where bins with $M_{r} > M_{r,\rm{lim}}$ 
+have fewer galaxies than the bin at $M_{r, \rm{lim}}$. 
+We choose $M_{r, \rm{lim}}(0.6 < z < 0.8)$ to be, conservatively, $M_{r} = -20.75$. 
+For the other redshift bins, we impose absolute magnitude limits ($M_{r,\rm{lim}}$) such 
+that the cumulative number density of the bin ordered by $M_{r}$ is equal to the cumulative 
+number density of the highest redshift bin. 
+The cumulative number density calculations accounts for the statistical weights of the galaxies (Section 
+\ref{sec:primus} and \ref{sec:sdss}).
 
-Similar fixed aperture methods have also been used in \cite{Croton:2005aa} for galaxies in the 2dF Galaxy Redshift Survey (\cite{Colless:2003aa}) and in \cite{Muldrew:2012aa} 
-for a mock galaxy catalogue generated from embedding galaxies onto the Millenium Dark Matter Simulation (\cite{Springel:2005aa}). 
-%Perhaps include a sentence that sums up everything in Croton and Muldrew?
+For the EDP of the SDSS-{\em GALEX} sample (hereafter SDSS EDP), we do not use the parent data of 
+the SDSS-{\em GALEX} target sample the geometry of the combined angular selection function of the 
+SDSS VAGC and {\em GALEX}. 
+Instead, since FUV, NUV values are not necessary for EDP, we extend the parent data of the SDSS EDP
+to the entire SDSS VAGC to include galaxies outside of the {\em GALEX} window function. 
+Furthermore, we impose a redshift range of $0.0375-0.145$ on the SDSS EDP. 
+This redshift range is due to the lack of faint galaxies at $z \sim 0.2$ and the lack of bright galaxies at 
+$z \sim 0.01$ in the SDSS VAGC data.  
+The lower bound for the redshift range was empirically determined by the bright limit and the upper bound 
+by the faint limit of the $M_{r}$ versus redshift distribution. 
+The same fixed cumulative number density method, described above, is used on this SDSS EDP to equate
+the cumulative number density of SDSS EDP to the highest redshift bin of the PRIMUS EDP. 
+Ultimately, we get $M_{r,\rm{lim}} = -20.57$, $-20.73$, $-20.80$ and $-20.95$ for the redshift bins $0.06-0.145$, 
+$0.2-0.4$, $0.4-0.6$, $0.6-0.8$, respectively.  %%%% PUT NEW VALUES
+These absolute magnitude limits are illustrated in Figure \ref{fig:targetEDP}, which plots $M_{r}$ distribution as 
+a function of redshift for the EDP (red) and the target galaxy sample (black).
 
-\subsection{Edge Effects} \label{sec:edgeeffect}
+Finally with the EDP we measure the environment for each of the target sample galaxies by counting the number
+of EDP galaxies, $n_{\rm{env}}$, with $RA$, $Dec$, and redshift within the aperture surrounding it. 
+$n_{\rm{env}}$ accounts for the statistical weights of the EDP galaxies. 
+%Since we use apertures of different dimensions, we are interested in the relative densitites rather than the actual $n_{env}$ values.
+%Hence, we use the percentage rank of the galaxy environment to quantify overdense environments and underdense environments.
+%More specifically, for each of the redshift bins ($0.2-0.4$, $0.4-0.6$, $0.6-0.8$, and $0.8-1.0$) the $n_{env}$ values for all target galaxies in that bin are listed and assigned a percentage rank based on their position in the list: $n_{env} = 0$ corresponding to $0\%$ and the maximum $n_{env}$ for a target galaxy in the $z$-bin corresponding to $100\%$.
+%Using these percentage ranks, each target galaxy is classified as high-, mid-, or low-environment based on the cut-offs specified in Table \ref{tab:aperture}. 
+%Target sample galaxies are classified as high-environment if its percentage rank lies within the top $20\%$ and as low-environment if its percentage rank lies within the bottom $20\%$. 
+%In Table \ref{tab:aperture}, apertures with radius $1 h^{-1} \rm{Mpc}$ have a low-eneivonrment cut-off of higher than $20\%$.
+%This is because over $20\%$ of target sample galaxies have $n_{env}=0$ such a smaller aperture size.
+%Hence we defined the low-environment percentage rank cut-off to contain all galaxies with $n_{env}=0$. 
+%In order to have a fair comparison for the different $z$-bins when using this aperture, the low-environment cut-off was selected as the lowest cut-off that includes all galaxies with $n_{env}=0$ for all $z$-bin.
+More specific details for the dense and sparse environment cut-offs the various apertures are provided in Table \ref{tab:aperture}.
+
 \begin{figure*}
@@
 
-One of the challenges in obtaining the galaxy environment using a fixed aperture method is accounting for the edge effects of the survey.
-For the target galaxies located near the edge of the survey, part of the fixed aperture encompassing it will lie outside the survey regions. 
-In this case, the $n_{env}$ will only reflect the galaxies which lie in the fraction of the aperture contained within the survey geometry.
+\subsection{Edge Effects} \label{sec:edgeeffect}
+One of the challenges in obtaining the galaxy environment using a fixed aperture method is accounting for the edges of the survey.
+For galaxies located near the edge of the survey, part of the fixed aperture encompassing it will lie outside the survey regions. 
+In this case, the $n_{env}$ will only reflect the fraction of the environment within the survey geometry.
 
-In order to account for these edge effects, we use a Monte Carlo method to impose edge cuts on the target galaxy population. 
-We first divide the target sample galaxies into $n_{bin}$ redshift bins, specified in Table \ref{tab:aperture}. 
-For each of the bins we compute the angular separation, $\theta_{\rm{ap}}$ that corresponds to the radius of the aperture at the central redshift of the bin.
-Then the target galaxies in each bin are matched up to a sample of $N_{ransack}=1,000,000$ points with arbitrary $RA$ and $Dec$ values within the target sample fields, 
-hereafter referred to as the ransack sample (named based on the procedure used to construct them). 
-We count the number of ransack points, $n_{\rm{ransack}}$, within $\theta_{\rm{ap}}$ for the target galaxies in each of the redshift bins.
-$n_{\rm{ransack}}$ values for the target galaxies are then compared to the expected value:
+In order to account for these edge effects, we use a Monte Carlo method to impose edge cuts on the target 
+galaxy population. 
+We begin by computing the angular separation, $\theta_{\rm{ap}}$ that corresponds to the radius of the 
+aperture at the redshifts of the target galaxies.
+Then the galaxies are matched to a sample of $N_{\rm{ransack}}=1,000,000$ points with $RA$ and $Dec$
+ randomly generated within the window function of the EDP.  
+We refer to this randomly generated redshift-less sample as the "ransack" sample, based on the procedure 
+used to construct them. 
+For each target galaxy, we count the number of ransack points, $n_{\rm{ransack}}$, within $\theta_{\rm{ap}}$
+of the galaxy's $RA$ and $Dec$ value.
+The $n_{\rm{ransack}}$ values are then compared to the expected value:
 \begin{equation} \label{eq:ransack}
-E[n_{\rm{ransack}}] = \frac{N_{\rm{ransack}}}{A_{\rm{fields}}}\times {\pi \theta_{\rm{ap}}^2} \times f_{\rm{thresh}} 
+E[n_{\rm{ransack}}] = \frac{N_{\rm{ransack}}}{A_{\rm{EDP}}}\times {\pi \theta_{\rm{ap}}^2} \times f_{\rm{thresh}} 
 \end{equation} 
-where $A_{\rm{fields}}$ is the total angular area of the target fields and $f_{\rm{thresh}}$ is the fractional threshold for the edge effect cut-off, specified in Table 
-\ref{tab:aperture}.
-If $n_{\rm{ransack}}$ for a target galaxy is greater than $E[n_{\rm{ransack}}]$ then the target galaxy remains in the sample; otherwise, it is discarded.
+where $A_{\rm{EDP}}$ is the total angular area of the target fields and $f_{\rm{thresh}}$ is the fractional 
+threshold for the edge effect cut-off, which we vary based on $R_{\rm{ap}}$ (listed in Table \ref{tab:aperture}).
+If $n_{\rm{ransack}}$ for a target galaxy is greater than $E[n_{\rm{ransack}}]$ then the target galaxy remains
+in the sample; otherwise, it is discarded from the sample.
 

### 2014-02-28 qfenv_paper/qf_environment.tex
Began changes in Section 3

@@
 is independent of environment. 
-%The SMF evolution suggests that in dense environments over the redshift range $z=0.8$ to $0.0$, the SMF of 
-%quiescent galaxies increase by a factor of $over9000$ for $\mathcal{M}_{*} < 11.0$ 
-%while the SMF of the star-forming galaxies evolves little for all masses. Meanwhile in low 
-%density environments from $z=0.8$ to $0.0$, we find that the SMF of quiescent 
-%galaxies evolves little for all stellar masses and the SMF of star-forming 
-%galaxies decreases by a factor of $over9000$ for $\mathcal{M}_{*} > 10.5$.  
 \end{abstract}
@@
 
-\section{Sample Selection}
+\section{Sample Selection} \label{sec:sample}
 In this paper we are interested in measuring the evolution of the quiescent 
@@
 %include a sentence that sums up everything in Croton and Muldrew? 
+%Also include remarks on Wilman et al.
 
@@
 \section{Results}
-In this section, we describe our calculation to obtain the stellar mass functions (SMF) and quiescent fraction (QF) using the stellar mass complete target population.
-In Section \ref{sec:smf_const} we construct the non-parametric estimate of SMFs for star-forming and quiescent galaxies in redshift bins: $0.06-0.145$, $0.2-0.4$, 
-$0.4-0.6$, $0.6-0.8$, and $0.8-1.0$.
-Form these SMFs, we calculate the QFs in section \ref{sec:qf_const}.
+In the section below, we calculate stellar mass functions (SMFs) for the target galaxy population divided into 
+quiescent/star-forming and dense/sparse environment, Section \ref{sec:smf_const}. We use a non-parametric 
+$1/V_{\rm{max}}$ estimate of SMFs for the subsamples further divided into redshift bins. Then using these 
+SMFs, we calculate the quiescent fractions (QFs), Section \ref{sec:qf_const}, 
+and examine it's evolution over our redshift range.
 
 \subsection{Stellar Mass Function} \label{sec:smf_const}
-Our primary interest in the SMFs is to investigate the evolution of the quiescent fraction in different density environments over our redshift range. 
-Hence, we first divide the target galaxy sample into quiescent and star-forming target samples using the classification scheme from Section \ref{sec:sfq}.
-Both the quiescent and star-forming target samples are then divided into "high-environment","mid-environment", and "low-environment" based on their environment classification described in 
-Section \ref{sec:environment}.
-We use the five redshift bins described in \ref{target} to get a total of $30$ subsamples that are classified based on star-forming/quiescent, environment, and redshift.
-For each of these subsamples, we calculate the SMFs and their errors.
+The target galaxy sample defined above has so far
+been classified into quiescent or star-forming and 
+dense or sparse. We further divide these subsamples 
+into bins of redshift:  in redshift bins of $0.06-0.145$, 
+$0.2-0.4$, $0.4-0.6$, and $0.6-0.8$. While the 
+PRIMUS data ranges from $0.2 < z < 1.2$, we only 
+consider galaxies with $ z<0.8$ due to insufficient
+statistics for robust environment measurements at 
+higher redshifts. With added redshift bins, we have a
+total of 16 subsamples. We calculate the SMF for 
+each of these 16 subsamples.
 
@@
 %Each aperture size will result in a different environment classification; so, $18$ SMFs are generated separately for every aperture we employ.
+
+%The SMF evolution suggests that in dense environments over the redshift range $z=0.8$ to $0.0$, the SMF of 
+%quiescent galaxies increase by a factor of $over9000$ for $\mathcal{M}_{*} < 11.0$ 
+%while the SMF of the star-forming galaxies evolves little for all masses. Meanwhile in low 
+%density environments from $z=0.8$ to $0.0$, we find that the SMF of quiescent 
+%galaxies evolves little for all stellar masses and the SMF of star-forming 
+%galaxies decreases by a factor of $over9000$ for $\mathcal{M}_{*} > 10.5$.
 

### 2014-03-03 qfenv_paper/qf_environment.tex
SMF section edits finished and started QF section edits

@@
 
-To calculate the SMFs we employ a non-parametric $1/{V_{\rm{max}}}$ estimator commonly used for galaxy luminosity functions, as done in \cite{Moustakas:2013aa} and discussed 
-in the review \cite{Johnston:2011aa}. 
-The differential SMF is given by the following equation:
+To calculate the SMFs we employ a non-parametric 
+$1/{V_{\rm{max}}}$ estimator commonly used for 
+galaxy luminosity functions and stellar mass functions
+, as done in \cite{Moustakas:2013aa} and discussed 
+in the review \cite{Johnston:2011aa}. The differential 
+SMF is given by the following equation:
 \begin{equation} \label{eq:phi}
@@
 \end{equation}
-The equation above is the same as Equation 3. in \cite{Moustakas:2013aa} other than the use of $V_{\rm{max,avail}}$ instead than $V_{\rm{max}}$, which is used because of edge effect 
-considerations along the edges of the survey. 
-$w_i$ represnts the statistical weight of each galaxy $i$ and $\Phi(\rm{log}\: \mathcal{M}) \Delta(\rm{log}\: \mathcal{M})$ is the number of galaxies ($N$) per unit volume within the 
-stellar mass range $[\rm{log} \:\mathcal{M}, \rm{log} \:\mathcal{M}+\Delta(\rm{log} \:\mathcal{M})]$.
+The equation above is same as Equation 3. in 
+\cite{Moustakas:2013aa} except for the distinction that 
+we use $V_{\rm{max,avail}}$ instead than $V_{\rm{max}}$, 
+to account for the edge effects of the survey for our
+environment measurements. $w_i$ here represents 
+the statistical weight of each galaxy $i$ and 
+$\Phi(\rm{log}\: \mathcal{M}) \Delta(\rm{log}\: \mathcal{M})$ 
+is the number of galaxies ($N$) per unit volume within the 
+stellar mass range 
+$[\rm{log} \:\mathcal{M}, \rm{log} \:\mathcal{M}+\Delta(\rm{log} \:\mathcal{M})]$.
 
-$V_{\rm{max},i}$ is the maximum cosmological volume where it is possible to observe each galaxy $i$ given the apparent magnitude limits of the survey.
-However in Section \ref{sec:edgeeffect} we remove the galaxies that lie on the edge of from the target sample. 
-In doing so we reduce the maximum cosmological volume where a galaxy can be observed, thereby reducing $V_{\rm{max},i}$ to a what we will refer to as $V_{\rm{max,avail},i}$.
+$V_{\rm{max},i}$ is the maximum cosmological volume 
+where it is possible to observe galaxy $i$ given the apparent 
+magnitude limits of the survey. However in Section \ref{sec:edgeeffect} 
+we remove the galaxies that lie on the edge from our sample. 
+In doing so we reduce the maximum cosmological volume 
+where a galaxy can be observed, thereby reducing $V_{\rm{max},i}$.
 
-To calculate $V_{\rm{max,avail},i}$, we generate a sample of points with random $RA$, $Dec$, and $z$ (not to be confused with the ransack sample in Section \ref{sec:edgeeffect}) 
-within the target fields and the redshift limits of the surveys.
-We then impose the same edge effect cut-off used on the target galaxy population, described in Section \ref{sec:edgeeffect}, onto this random sample. 
-For each redshift bin $j$ out of the $n_{\rm{bin}}$ redshift bins, we compute the fraction of the random points that remain in the bin after the points near the edges are removed: 
-$f_{\rm{edge},j}$.
-Finally we calculate: $V_{\rm{max,avail},i} = V_{\rm{max},i} \times f_{\rm{edge},j}$. 
-The $V_{\rm{max},i}$ values in the equation above are computed following the method described in \cite{Moustakas:2013aa} with the same redshift-dependent $K$-correction 
-from observed SED and luminosity evolution model.
-For more details on computing $V_{\rm{max}}$ we refer readers to Section 4.2 in \cite{Moustakas:2013aa}.
+To calculate $V_{\rm{max,avail},i}$, we generate a sample of 
+points with random $RA$, $Dec$ within the window function of 
+the target sample and $z$ in the redshift range. This is not to be 
+confused with the ransack sample in Section \ref{sec:edgeeffect}. 
+We then impose the same edge cuts we applied to the target 
+galaxy population. At redshift bins of $\Delta z \sim 0.01$, we 
+compute theraction of random points that remain in the bin after 
+the edge cuts: $f_{\rm{edge}}$. Afterwards we apply this factor to 
+compute $V_{\rm{max,avail}} = V_{\rm{max}} \times f_{\rm{edge}}$. 
+The $V_{\rm{max}}$ in the equation above are computed following 
+the method described in \cite{Moustakas:2013aa} Section 4.2 with 
+the same redshift-dependent $K$-correction from observed SED 
+and luminosity evolution model.
 
-In order to calculate the uncertainty of the SMFs from the sample variance, we use a standard jackknife technique as done in \cite{Moustakas:2013aa}.
-For the PRIMUS target galaxies, we calculate SMFs after excluding one of the target fields each time.
-Note in these SMF calculations, the $1/V_{\rm{max},\rm{avail}}$ is corrected for the fact that excluding a field changes the total area of the survey.
+In order to calculate the uncertainty of the SMFs from the sample 
+variance, we use a standard jackknife technique as done in \cite{Moustakas:2013aa}.
+For the PRIMUS target galaxies, we calculate SMFs after excluding 
+one of the five target fields each time. And for the SDSS target galaxies
+we divide the field into a 30 $\times$ 20 rectangular $RA$ and $Dec$ 
+grid and calculate the SMFs after excluding part of the field each time. 
 Then using the calculated SMFs we calculate the uncertainty: 
@@
 \end{equation} 
-$M$ in this equation is the number of jack knife SMFs in the mass bin; this value is different for each of the stellar mass bins since not all mass bins have galaxies from all five target fields.
-$\langle \Phi^j \rangle$ is the mean number density of galaxies in each stellar mass bin for all of the jack knife $\Phi^j$s.
+$M$ in this equation is the number of jack knife SMFs in the stellar mass
+bins. $\langle \Phi^j \rangle$ is the mean number density of galaxies 
+in each stellar mass bin for all of the jack knife $\Phi^j$s. The SMFs for 
+16 target galaxy subsamples classified into quiescent/star-forming (orange/blue)and 
+dense/spare environments are presented in Figure \ref{fig:smf}. The 
+redshift evolution of the SMFs are indicated by a darker shade for lower
+redshifts. The sample variance uncertainties are represented by the 
+width of the SMFs. The environment measurements and classifications
+for Figure \ref{fig:smf} is done using a cylindrical aperture with dimensions,
+$R_{\rm{ap}} = 2 \; \rm{Mpc}/h$ and $H_{\rm{ap}} = 25 \; \rm{Mpc}/h$.
 
-Since the SDSS-{\em GALEX} data are contained in one field, we first divide the field into a $30 \times 20$ rectangular grid and then only keep the sectors with at least $100$ galaxies in them. 
-Then we use the same method as above to compute the uncertainties through the jack knife technique. 
-The panels in the top two rows of Figure \ref{fig:smf} show the SMFs with uncertainties for all $30$ subsamples using aperture with dimensions $R_{\rm{ap}} = 1 \rm{Mpc}$ and $h_{\rm{ap}} = 50 \rm{Mpc}$.
-
-%Multiple apertures Additionally, we employ multiple apertures, as listed in Table \ref{tab:aperture}, since we are interested in probing the density environment at various scales. 
-%Each aperture size will result in a different environment classification; so, $18$ SMFs are generated separately for every aperture we employ.
-
-%The SMF evolution suggests that in dense environments over the redshift range $z=0.8$ to $0.0$, the SMF of 
-%quiescent galaxies increase by a factor of $over9000$ for $\mathcal{M}_{*} < 11.0$ 
-%while the SMF of the star-forming galaxies evolves little for all masses. Meanwhile in low 
-%density environments from $z=0.8$ to $0.0$, we find that the SMF of quiescent 
-%galaxies evolves little for all stellar masses and the SMF of star-forming 
-%galaxies decreases by a factor of $over9000$ for $\mathcal{M}_{*} > 10.5$.
+Examining the SMF evolution over $z \sim 0 - 0.8$, we find that in dense 
+environments, the quiescent SMFs increase by a factor of $over9000$ 
+for $\mathcal{M}_{*} < 11.0$ while the SMF of the star-forming 
+galaxies evolves little for all masses. Meanwhile in low density 
+environments from $z=0.8$ to $0.0$, we find that the SMF of 
+quiescent galaxies evolves little for all stellar masses and the 
+SMF of star-forming galaxies decreases by a factor of $over9000$ 
+for $\mathcal{M}_{*} > 10.5$.  
+%%% EXPAND ON ANALYSIS OF SMF
 
 \subsection{Quiescent Fraction} \label{sec:qf_const}
-In the last section, we calculated the SMFs for all subsamples of the target galaxies classified by star-forming/quiescent, environment, and redshift. 
-In this section, we use the $\Phi$ calculated for each subsample above to compute their respective $\rm{QF}$s: 
+Using the SMF number densities ($\Phi$) calculated above, 
+in this section, we compute the quiescent fraction, $f_{\rm{Q}}$ 
+for dense and sparse environments over the redshift range 
+$0.0 - 0.8$.  The quiescent fraction is simply given by the following 
+equation: 
 \begin{equation}
-\rm{QF} = \frac{\Phi_{Q}}{\Phi_{SF}+\Phi_{Q}}.
+f_{\rm{Q}} = \frac{\Phi_{Q}}{\Phi_{SF}+\Phi_{Q}}.
 \end{equation}
-$\Phi_{Q}$ and $\Phi_{SF}$ are the total number of galaxies per unit volume in stellar mass bin $\Delta(\rm{log} \: \mathcal{M})$ (Equation \ref{eq:phi}) for the quiescent and star-forming subsamples, respectively.
-A value for the $\rm{QF}$ is not assigned in stellar mass bins where either the star-formation subsample or the quiescent subsample do not have any galaxies. 
-The bottom panels of Figure \ref{fig:smf} shows the $\rm{QF}$s for the different redshift bins and environment density classifications.
+$\Phi_{Q}$ and $\Phi_{SF}$ are the total number of galaxies 
+per unit volume in stellar mass bin of $\Delta(\rm{log} \: \mathcal{M}) = 0.25$ 
+for the quiescent and star-forming subsamples, respectively 
+(Equation \ref{eq:phi}). The bottom panels of Figure \ref{fig:smf} 
+shows the evolution of $f_{\rm{Q}}$ for dense (right) and sparse (left)
+environments. As before, the darker shades of orange represent 
+lower redshift bins.
+
+%%% INCLUDE BRIEF QUALITATIVE ANALYSIS OF THE EVOLUTION OF THE QUIESCENT FRACTION
 

### 2014-03-24 qfenv_paper/qf_environment.tex
Wilman et al 2010
 to motivate choice in aperture radius and height

@@
 
-\subsection{Target Galaxy Samples} \label{sec:target} 
+\subsection{Target Galaxy Sample} \label{sec:target} 
 In this seciton we will define the target galaxy sample we use to compute the SMFs and QFs.
@@
 \subsection{Galaxy Environment} \label{sec:environment}
-In addition to the quiescent/star-forming classification, we now measure the environment for the target galaxy sample. 
-First, we define the environment of a galaxy as the number of neighboring galaxies contained within a fixed aperture centered around it.
-As our aperture, we use a cylinder with dimensions with $R_{\rm{ap}} = 2 \; \rm{Mpc}/h$ and $H_{\rm{ap}} = 25 \; \rm{Mpc}/h$. 
-Though spherical apertures are often used in literature (e.g. \cite{Croton:2005aa}), we use a cylindrical aperture in order to 
-account for the PRIMUS redshift errors and redshift space distortions.  
-Furthermore, we use a cylinder with the specified dimensions based on scale dependence for clustering analysis done in 
-\cite{Blanton:2006aa}, which suggests that galactic properties such as star-formation histories are dependent on properties
- such as the masses of their host dark matter halos.
-Hence, with cylindrical apertures of $R_{\rm{ap}} = 2 \; \rm{Mpc}/h$ we are able to probe the local small scale environment 
-within the scales of the host dark matter halos.
-We extend our analysis to cylindrical apertures with cylindrical apertures with $R_{\rm{ap}} = 1 \; \rm{Mpc}/h$; however 
-we find that the variation in $R_{\rm{ap}}$ does not change our results significantly (difference in $f_{Q} < 0.05$). 
-Similar fixed aperture methods have also been used in \cite{Croton:2005aa} for galaxies in the 2dF Galaxy Redshift 
-Survey (\cite{Colless:2003aa}) and in \cite{Muldrew:2012aa} for a mock galaxy catalogue generated from embedding 
-galaxies onto the Millenium Dark Matter Simulation (\cite{Springel:2005aa}). 
-%include a sentence that sums up everything in Croton and Muldrew? 
-%Also include remarks on Wilman et al.
+In addition to the quiescent/star-forming classification, in this section, 
+we measure the environment for our target galaxies. We define the 
+environment of a galaxy as the number of neighboring galaxies 
+contained within a fixed aperture centered around it. We use a fixed 
+aperture environment because, as \cite{Muldrew:2012aa} finds in 
+their comparison of different environment definition using simulations, 
+it provides a better probe of the entire halo in comparison to other 
+environment definitions such as nearest neighbor, which provides 
+a better tracer at inter-halo scales. For our aperture, 
+we use a cylinder of dimensions: $R_{\rm{ap}} = 2 \; \rm{Mpc}/h$ and 
+$H_{\rm{ap}} = 25 \; \rm{Mpc}/h$. Though spherical apertures are 
+often used in literature (e.g. \cite{Croton:2005aa}), we use a 
+cylindrical aperture in order to account for the PRIMUS redshift errors 
+and redshift space distortions (i.e. "Finger of God" effect). \cite{Cooper:2005aa} 
+finds that $\pm 1000 \; \rm{km} \rm{s^{-1}}$ optimally reduces the 
+effects of redshift space distortions and PRIMUS $\sigma_z \sim 
+0.0085$ at $z \sim 0.7$, so aperture height of $25 \; \rm{Mpc}/h$ 
+successfully accounts for both of these effects. Furthermore, our 
+choice of cylinder radius was motivated by scale dependence 
+analyses in literature (\cite{Blanton:2006aa}, \cite{Wilman:2010aa}, 
+and \cite{Muldrew:2012aa}), which suggest that galactic properties 
+such as color and quenched fractions are dependent on halo-scale 
+properties such as host dark matter halo mass. \cite{Wilman:2010aa}, 
+which uses environment defined by annuli of different radii, find 
+positive correlation for quenched fraction and color on scales 
+$< 1 \; \rm{Mpc}$ and anti-correlation on scales $> 3 \; \rm{Mpc}$. 
+Our choice of $2 \rm{Mpc}/h$ provides sufficient sample size of 
+galaxies in dense environments, for robust statistics, while 
+tracing galactic properties within the halo scale. When we extend our 
+analysis to cylindrical apertures with $R_{\rm{ap}} = 1 \; \rm{Mpc}/h$, 
+we find that the change in $R_{\rm{ap}}$ does not significantly change 
+our results (difference in $f_{Q} < 0.05$). 
+%Similar fixed aperture methods have also been used in \cite{Croton:2005aa} for galaxies in the 2dF Galaxy Redshift 
+%Survey (\cite{Colless:2003aa}) and in \cite{Muldrew:2012aa} for a mock galaxy catalogue generated from embedding 
+%galaxies onto the Millenium Dark Matter Simulation (\cite{Springel:2005aa}).
 
-In order to measure environment using an aperture defined above, we first construct a volume limited 
-{\em Environment Defining Population} (EDP) with absolute magnitude cut-offs ($M_{r}$) at each redshift bin. 
-The $M_{r}$ cut-offs are selected so that the cumulative number density over $M_{r}$ at all redshift bins are equal. 
-By equating the cumulative number densities at different redshifts not only can we reasonably compare the 
-environment values at different redshift bins but we also attempt to build an EDP that has a similar galaxy 
-population in all of the redshift bins i.e. accounts for the progenitor bias. 
-As \cite{Behroozi:2013aa} and \cite{Leja:2013aa} find in their analysis of the cumulative number density 
-method using a dark matter simulation with abundance matching and a semi-analytic model, respectively, 
-the cumulative number density method, while it does not precisely account for the scatter in mass accretion or 
-galaxy-galaxy mergers, provides a reasonable means to compare galaxy populations over a wide range of cosmic time. 
-Furthermore \cite{Behroozi:2013aa} %%%FINISH THIS SENTENCE
+With proper motivation for the fixed aperture environment definition, 
+we now proceed to measuring the environment for our target galaxies. 
+First, we construct a volume limited {\em Environment Defining 
+Population} (EDP) with absolute magnitude cut-offs ($M_{r}$) at 
+each redshift bin. EDP galaxies within the aperture surrounding each 
+target galaxy are the neighboring galaxies in our definition of 
+environment. The $M_{r}$ cut-offs for the EDP are selected so that 
+the cumulative number density over $M_{r}$ at all redshift bins are 
+equal. Not only does this provide a reasonably comparison of the 
+environment measurements at different redshifts but it also seeks 
+to construct an EDP that contains similar galaxy populations 
+throughout our redshift range (i.e. to account for the progenitor bias 
+in our EDP). As \cite{Behroozi:2013aa} and \cite{Leja:2013aa} find 
+in their analysis of the cumulative number density method, the 
+cumulative number density method, though it does not precisely 
+account for the scatter in mass accretion or galaxy-galaxy mergers, 
+provides a reasonable means to compare galaxy populations over 
+a wide range of cosmic time.
 
-To construct the EDP for the PRIMUS (hereafter PRIMUS EDP) we use the same PRIMUS data as the 
+In constructing the EDP for the PRIMUS (hereafter PRIMUS EDP) we use the same PRIMUS data as the 
 target galaxies, described in Section \ref{sec:target}. 
@@
 
-For the EDP of the SDSS-{\em GALEX} sample (hereafter SDSS EDP), we do not use the parent data of 
-the SDSS-{\em GALEX} target sample the geometry of the combined angular selection function of the 
+For the SDSS-{\em GALEX} EDP (hereafter SDSS EDP), we do not use the parent data of 
+the SDSS-{\em GALEX} target sample which uses the geometry of the combined angular selection function of the 
 SDSS VAGC and {\em GALEX}. 
 Instead, since FUV, NUV values are not necessary for EDP, we extend the parent data of the SDSS EDP
-to the entire SDSS VAGC to include galaxies outside of the {\em GALEX} window function. 
+to the entire SDSS VAGC, including galaxies outside of the {\em GALEX} window function. 
 Furthermore, we impose a redshift range of $0.0375-0.145$ on the SDSS EDP. 

### 2014-04-16 qfenv_paper/qf_environment.tex
Edits and additions

@@
 \subsection{Target Galaxy Sample} \label{sec:target} 
-In this seciton we will define the target galaxy sample we use to compute the SMFs and QFs.
-The population at $z \sim 0.5$ is derived from the PRIMUS data and the population at $z \sim 0.1$ is derived from the SDSS data, both described above.
-For the intermediate redshift target galaxy population, we begin with the selection criteria imposed in \cite{Moustakas:2013aa} for its parent sample.
-We take the statistically complete {\em primary} sample from the PRIMUS data (\cite{Coil:2011aa}) and then impose magnitude limits on optical selection bands as specified in 
-\cite{Moustakas:2013aa} Table 1.
-These limits are in different optical selection bands and have different values for our five PRIMUS target fields.
-Next, we join the PRIMUS, {\em GALEX}, and IRAC window functions to construct the angular selection function.
-We then exclude stars and broad-line AGN to only select objects spectroscopically classified as galaxies, with high-quality spectroscopic redshifts ($Q \geq 3$) within the 
-redshift range $0.2 - 0.8$.
-Afterwards we assign statistical weights (described in \cite{Coil:2011aa} and \cite{Cool:2013aa}) to the objects in order to correct for targeting incompleteness and redshift failures.
-The statistical weight, $w_i$, for each galaxy is given by
+In this section we will define the target galaxy sample 
+used to compute the SMFs and QFs. The population 
+at $z \sim 0.5$ is derived from PRIMUS data and the 
+population at $z \sim 0.1$ is derived from SDSS-{\em GALEX} 
+data, both described above. For the intermediate redshift 
+population, we begin with the selection criteria imposed 
+in \cite{Moustakas:2013aa} for their parent sample. We 
+take the statistically complete {\em primary} sample from 
+the PRIMUS data (\cite{Coil:2011aa}) and impose magnitude 
+limits on optical selection bands as specified in 
+\cite{Moustakas:2013aa} Table 1. These limits are in different 
+optical selection bands and have distinct values for the 
+five PRIMUS target fields. We then exclude stars and 
+broad-line AGN to only select objects spectroscopically 
+classified as galaxies, with high-quality spectroscopic redshifts 
+($Q \geq 3$) within the redshift range $0.2 - 0.8$. For 
+each of these objects we assign statistical weights (described 
+in \cite{Coil:2011aa} and \cite{Cool:2013aa}) in order to correct 
+for targeting incompleteness and redshift failures. The 
+statistical weight, $w_i$, for each galaxy is given by
 \begin{equation}
@@
 \end{equation}
-Equation (1) in \cite{Moustakas:2013aa}.
-In addition to the selection criteria above, we impose stellar mass limits to have a stellar mass complete sample.  
-Stellar mass completeness limits for a magnitude-limited survey such as PRIMUS is a function of redshift, apparent magnitude limit of the survey, and the typical stellar 
-mass-to-light ratio of galaxies near the flux limit.
+Equation (1) in \cite{Moustakas:2013aa}. Then to account 
+for stellar mass incompleteness, we impose derived stellar 
+mass limits to the sample.
 
-As done in \cite{Moustakas:2013aa}, we follow \cite{Pozzetti:2010aa} to empirically determine the stellar mass completeness limits.
-Briefly, for each of the target galaxies we compute $\mathcal{M}_{\rm{lim}}$ using $\rm{log} \; \mathcal{M}_{\rm{lim}} = \rm{log} \; \mathcal{M} + 0.4 ( m - m_{\rm{lim}})$.
-$\mathcal{M}$ is the stellar mass of the galaxy in units of $\mathcal{M_{\odot}}$, $\mathcal{M}_{\rm{lim}}$ is the stellar mass of each galaxy if its magnitude was 
-equal to the survey magnitude limit, $m$ is observed apparent magnitude in the selection band, and $m_{\rm{lim}}$ is the magnitude limit for our five fields mentioned above.
-We construct a cumulative distribution of $\mathcal{M}_{\rm{lim}}$ for the $15\%$ faintested galaxies in $\Delta z=0.04$ redshift bins.
-In each of these redshift bins, we calculate the minimum stellar mass that includes $95 \%$ of the galaxies.
-Separately for quiescent and star-forming galaxies, we fit quadratic polynomials to the minimum stellar masses versus redshift (classificiation scheme for quiescent 
-and star-forming galaxies is included in the following section).
-Finally, we use the polynomials to obtain the minimum stellar masses at the center of the redshift bins, $0.2-0.4$, $0.4-0.6$, $0.6-0.8$, and $0.8-1.0$.
-These redshift bins will later be used to divide the target sample in order to compute the SMFs and QFs.
+Stellar mass completeness limits for a magnitude-limited 
+survey such as PRIMUS is a function of redshift, apparent 
+magnitude limit of the survey, and the typical stellar 
+mass-to-light ratio of galaxies near the flux limit. As done 
+in \cite{Moustakas:2013aa}, we follow \cite{Pozzetti:2010aa} 
+to empirically determine the stellar mass completeness limits.
+Briefly, for each of the target galaxies we compute 
+$\mathcal{M}_{\rm{lim}}$ using $\rm{log} \; \mathcal{M}_{\rm{lim}} = \rm{log} \; \mathcal{M} + 0.4 ( m - m_{\rm{lim}})$.
+$\mathcal{M}$ is the stellar mass of the galaxy in $\mathcal{M_{\odot}}$, 
+$\mathcal{M}_{\rm{lim}}$ is the stellar mass of each galaxy 
+if its magnitude was equal to the survey magnitude limit, 
+$m$ is observed apparent magnitude in the selection band, 
+and $m_{\rm{lim}}$ is the magnitude limit for our five 
+fields mentioned above. We construct a cumulative 
+distribution of $\mathcal{M}_{\rm{lim}}$ for the $15\%$ 
+faintest galaxies in $\Delta z=0.04$ bins. In each of these 
+redshift bins, we calculate the minimum stellar mass that 
+includes $95 \%$ of the galaxies. Separately for quiescent 
+and star-forming galaxies, we fit quadratic polynomials to 
+the minimum stellar masses versus redshift (galaxies are 
+classified into star-forming or quiescent in the following section).
+Finally, we use the polynomials to obtain the minimum stellar 
+masses at the center of redshift bins, $0.2-0.4$, $0.4-0.6$, 
+and $0.6-0.8$, which are then used as PRIMUS stellar mass
+completeness limits.
 
-For our target galaxy population at low redshift we use our SDSS-{\em GALEX} data. 
-We limit our target population within the redshift range $0.0375-0.145$ due to redshift limits later imposed for the volume-limited Environment Defining Population (Section \ref{sec:environment}).
-The NYU-VAGC provides statistical weight estimates for targeting completeness.
-In order to have a stellar mass complete low redshift target population, we use a uniform stellar mass limit of $10^9 \mathcal{M}_{\odot}$, which is above the surface 
-brightness and stellar mass-to-light ratio completness limits (\cite{Blanton:2005ab}; \cite{Baldry:2008aa}).
-The absolute magnitude ($M_{r}$) versus redshift for the target galaxy population at both low redshift and intermediate redshift is plotted in Figure \ref{fig:targetEDP}.
-For further details we refer readers to \cite{Moustakas:2013aa} for details; more specifically, Figure 2., Sections 3.1, and 4.3.
+For our target galaxy population at low redshift we start with 
+the SDSS-{\em GALEX} data. We limit our population within 
+the redshift range $0.0375-0.145$ due to redshift limits later 
+imposed on the volume-limited Environment Defining Population 
+(Section \ref{sec:environment}). To account for targeting 
+completeness of this sample, we use the statistical weight 
+estimates provided by the NYU-VAGC. Then to account for 
+stellar mass incompleteness, we impose a uniform stellar mass 
+limit of $10^9.8 \mathcal{M}_{\odot}$, a limit determined by the 
+stellar mass-to-light ratio completeness of the NYU-VAGC 
+sample given the redshift limits.
+
+The absolute magnitude ($M_{r}$) versus redshift for the 
+target galaxy population (black squares) is plotted in Figure 
+\ref{fig:targetEDP}. The left-most panel corresponds to the
+target sample derived from the SDSS-{\em GALEX} data and
+the rest correspond to the target sample derived from the 
+PRIMUS data divided in bins with $\Delta z \sim 0.2$.
 
@@
     \leavevmode
-     \label{fig:smf}
-     \epsfig{file=fig_smf_cylr2h25_thresh75_bin0_25.eps,height=0.75\textwidth,angle=90}
+     \epsfig{file=fig_smf_cylr2h25_thresh75_bin0_25_2envbin_primuszerr.eps,height=0.75\textwidth,angle=90}
      \caption{Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) target galaxies in 
 low (left) and high (right) environments from redshift range $z=0-0.8$. The environment of each galaxy  
-was calculated using a cylindrical aperture size of $R=2\rm{Mpc}$ and $H=25\rm{Mpc}$ and  
+was calculated using a cylindrical aperture size of $R=2 \: \rm{Mpc}$ and $H=25 \: \rm{Mpc}$ and  
 classification based on the cut-offs specified in Table \ref{tab:aperture}. The SMFs use mass bins of 
@@
 (star-forming) and orange (quiescent) to represent the SMF at different redshift, higher redshifts being
-progressively lighter.}
+progressively lighter.}      \label{fig:smf}
     \end{center}
@@
 the cumulative number density of SDSS EDP to the highest redshift bin of the PRIMUS EDP. 
-Ultimately, we get $M_{r,\rm{lim}} = -20.57$, $-20.73$, $-20.80$ and $-20.95$ for the redshift bins $0.06-0.145$, 
+Ultimately, we get $M_{r,\rm{lim}} = -20.57$, $-20.73$, $-20.80$ and $-20.95$ for the redshift bins $0.0375-0.145$, 
 $0.2-0.4$, $0.4-0.6$, $0.6-0.8$, respectively.  %%%% PUT NEW VALUES
@@
         \leavevmode
-        \label{fig:smf}
-        \epsfig{file=fig_qf_cylr2h25_thresh75_bin0_25.eps,height=0.75\textwidth,angle=90}
-        \caption{Evolution of the quiescent fraction for target galaxies in low (left) and (high) environments
-from redshift range $z=0-0.8$. The QFs were calculated using the SMFs specificed in Figure \ref{fig:smf}. We use
-lighter shades of orange for the QFs at higher redshifts.}
+        \epsfig{file=fig_qf_cylr2h25_thresh75_bin0_25_primuszerr.eps,height=0.75\textwidth,angle=90}
+        \caption{Evolution of the quiescent fraction $f_{\rm{Q}}$ for target galaxies in spare (left) and dense (rights) environments
+from $z \sim 0.7$ to $z \sim 0.1$.
+$f_{\rm{Q}}$s were calculated using the SMFs computed in Section \ref{sec:smf} and shown in Figure\ref{fig:smf}, as described in text.
+Darker shading indicates lower redshift.}         \label{fig:qf}
     \end{center}
@@
 
-\section{Results}
-In the section below, we calculate stellar mass functions (SMFs) for the target galaxy population divided into 
-quiescent/star-forming and dense/sparse environment, Section \ref{sec:smf_const}. We use a non-parametric 
-$1/V_{\rm{max}}$ estimate of SMFs for the subsamples further divided into redshift bins. Then using these 
-SMFs, we calculate the quiescent fractions (QFs), Section \ref{sec:qf_const}, 
-and examine it's evolution over our redshift range.
+%\section{Results}
+%In the section below, we calculate stellar mass functions (SMFs) for the target galaxy population divided into 
+%quiescent/star-forming and dense/sparse environment, Section \ref{sec:smf_const}. We use a non-parametric 
+%$1/V_{\rm{max}}$ estimate of SMFs for the subsamples further divided into redshift bins. Then using these 
+%SMFs, we calculate the quiescent fractions (QFs), Section \ref{sec:qf_const}, 
+%and examine it's evolution over our redshift range.
 
-\subsection{Stellar Mass Function} \label{sec:smf_const}
+\section{Stellar Mass Function} \label{sec:smf}
 The target galaxy sample defined above has so far
@@
 dense or sparse. We further divide these subsamples 
-into bins of redshift:  in redshift bins of $0.06-0.145$, 
+into bins of redshift:  in redshift bins of $0.0375-0.145$, 
 $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$. While the 
@@
 bins. $\langle \Phi^j \rangle$ is the mean number density of galaxies 
-in each stellar mass bin for all of the jack knife $\Phi^j$s. The SMFs for 
-16 target galaxy subsamples classified into quiescent/star-forming (orange/blue)and 
+in each stellar mass bin for all of the jack knife $\Phi^j$s.
+
+SMFs for 16 target galaxy subsamples classified into quiescent/star-forming (orange/blue)and 
 dense/spare environments are presented in Figure \ref{fig:smf}. The 
@@
 width of the SMFs. The environment measurements and classifications
-for Figure \ref{fig:smf} is done using a cylindrical aperture with dimensions,
+for Figure \ref{fig:smf} are done using a cylindrical aperture with dimensions,
 $R_{\rm{ap}} = 2 \; \rm{Mpc}/h$ and $H_{\rm{ap}} = 25 \; \rm{Mpc}/h$.
 
-Examining the SMF evolution over $z \sim 0 - 0.8$, we find that in dense 
-environments, the quiescent SMFs increase by a factor of $over9000$ 
-for $\mathcal{M}_{*} < 11.0$ while the SMF of the star-forming 
-galaxies evolves little for all masses. Meanwhile in low density 
-environments from $z=0.8$ to $0.0$, we find that the SMF of 
-quiescent galaxies evolves little for all stellar masses and the 
-SMF of star-forming galaxies decreases by a factor of $over9000$ 
-for $\mathcal{M}_{*} > 10.5$.  
-%%% EXPAND ON ANALYSIS OF SMF
+Examining the SMF evolution from $z \sim 0.7$ to $z \sim 0.1$, 
+we find that in dense environments both the star-forming and quiescent
+SMFs increase at $\mathcal{M}_{*}$ below the knee of mass function 
+($\rm{log}\: \mathcal{M}_{*}/\mathcal{M}_{\odot} < 10.75$ for star-forming; 
+$\rm{log}\: \mathcal{M}_{*}/\mathcal{M}_{\odot} < 11.0$ for quiescent). 
+Meanwhile, at masses above the knee the SMFs for dense environments 
+exhibit little change throughout the redshift range.
 
-\subsection{Quiescent Fraction} \label{sec:qf_const}
-Using the SMF number densities ($\Phi$) calculated above, 
-in this section, we compute the quiescent fraction, $f_{\rm{Q}}$ 
-for dense and sparse environments over the redshift range 
-$0.0 - 0.8$.  The quiescent fraction is simply given by the following 
-equation: 
+At sparse environments, the quiescent SMF remains relatively constant 
+for galaxies with $\rm{log}\: \mathcal{M}_{*}/\mathcal{M}_{\odot} < 10.75$.
+At higher stellar masses, however, the SMF decreases notably. Finally 
+the sparse environment star-forming SMF shows a decrease at all 
+stellar mass ranges over the redshift range.
+
+%%% COMPARISON TO OTHER LITERATURE?
+
+\section{Quiescent Fraction} \label{sec:qf_const}
+From the SMF number densities ($\Phi$) calculated
+in the previous section, the quiescent fraction is computed 
+as follows, 
 \begin{equation}
@@
 for the quiescent and star-forming subsamples, respectively 
-(Equation \ref{eq:phi}). The bottom panels of Figure \ref{fig:smf} 
-shows the evolution of $f_{\rm{Q}}$ for dense (right) and sparse (left)
-environments. As before, the darker shades of orange represent 
-lower redshift bins.
+(Equation \ref{eq:phi}). We compute $f_{\rm{Q}}$ for dense 
+and spare environments over our redshift range as plotted in
+ Figure \ref{fig:qf}, which shows the evolution of $f_{\rm{Q}}$ 
+ for dense (right) and sparse (left) environments. As in 
+ Figure \ref{fig:smf}, the darker shading represent lower redshifts.
 
+For both the spare and dense environments there is a notable 
+increase in $f_{\rm{Q}}$ at all stellar masses as redshift decreases.
 %%% INCLUDE BRIEF QUALITATIVE ANALYSIS OF THE EVOLUTION OF THE QUIESCENT FRACTION
@@
         \plotone{fig_qffit_cylr2h25_thresh75_bin0_25.png}
-        \label{fig:qf}
+        \label{fig:qffit}
         \caption{Quiescent fraction at fiducial mass $\rm{log} (\mathcal{M}/\mathcal{M}_{\odot}) = 10.5$ for 
@@
 
-\section{Discussion and Conclusions}
+\section{Summary}
 We have measured the SMFs and QFs using low redshift SDSS-{\em GALEX} galaxies and intermeidate redshift PRIMUS galaxies. 
@@
         \leavevmode
-        \label{fig:smf}
         \epsscale{1.0}
@@
         \plotone{fig_qffit_cylr1h25_thresh80_bin0_25.png}
-        \label{fig:qf}
         \caption{QF at fiducial mass for $r_{\rm{ap}}=2 \rm{Mpc}$ and $h_{\rm{ap}}=50 \rm{Mpc}$}

### 2014-04-17 qfenv_paper/qf_environment.tex
Significant additions to SMF and QF sections

@@
 dense or sparse. We further divide these subsamples 
-into bins of redshift:  in redshift bins of $0.0375-0.145$, 
+into bins of redshift: $0.0375-0.145$, 
 $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$. While the 
@@
 statistics for robust environment measurements at 
-higher redshifts. With added redshift bins, we have a
+$z > 0.8$. With added redshift bins, we have a
 total of 16 subsamples. We calculate the SMF for 
 each of these 16 subsamples. 
+%% EMPHASIZE THE FACT THAT WE HAVE ENVIRONMENT MEASURES AND A ROBUST ENOUGH DATA TO PROBE 
+%% UP TO REDSHIFT 0.7! THAT WAY WE CAN SEE THE MASS DISTRIBUTION OF VERY SPECIFIC POPULATIONS OF
+%% GALAXIES UP TO A PRETTY HIGH REDSHIFT!
 
@@
 \section{Quiescent Fraction} \label{sec:qf_const}
-From the SMF number densities ($\Phi$) calculated
+The SMFs calculated in the previous section describe
+the distribution of our galaxy population in stellar mass 
+and reveal the evolution of this distribution
+over comic time. From the SMFs, we 
+compute the quiescent fractions in order to compare the 
+quiescent and the star-forming populations 
+and to quantify the fraction of galaxies that have
+depleted their star-formation. Furthermore, by dividing our 
+galaxy sample using environment measurements into dense
+and sparse samples, we investigate the environment 
+dependence on the quiescent fraction and consequently 
+on environment dependent quenching mechanisms.
+
+From the SMF number densities ($\Phi$)
 in the previous section, the quiescent fraction is computed 
@@
 
-For both the spare and dense environments there is a notable 
-increase in $f_{\rm{Q}}$ at all stellar masses as redshift decreases.
-%%% INCLUDE BRIEF QUALITATIVE ANALYSIS OF THE EVOLUTION OF THE QUIESCENT FRACTION
+In both sparse and dense environments, Figure \ref{fig:qf}
+clearly shows an increase in $f_{\rm{Q}}$ with decrease in redshift at all 
+stellar masses. Qualitatively, this $f_{\rm{Q}}$ evolution 
+exhibits a notable mass dependence. More specifically, 
+the $f_{\rm{Q}}$ in sparse environments shows a greater 
+evolution between redshift bins at high masses than at low 
+masses. On the other hand, the $f_{\rm{Q}}$ in dense 
+environments shows a greater evolution between redshift 
+bins at low masses than at high masses.
 
-In order to compare the $\rm{QF}$s at different redshift for each of the environment classifications, we perform a linear least squares fit on the $\rm{QF}$ for all the $\rm{QF}$s. 
-Then we use the value of the linear fit at an empirically selected fiducial mass $\rm{log} \: \mathcal{M}/\mathcal{M}_{\odot} = 10.5$ (using fiducial mass of $\rm{log} \: \mathcal{M}/
-\mathcal{M}_\odot = 11.0$ does not noteably change the outcome).
-These values are used to highlight and attempt to quantify the differences of the $\rm{QFs}$ at the different redshifts, Figure \ref{fig:qf}
-%of the low redshift and low environemnt subsample.
-%The slope obtained from this fit is then used to perform a lienar fit for the rest of the $\rm{QF}$s.
-
-The figures and analysis described in this paper are done using galaxy environment determined from a fixed aperture with $r_{\rm{ap}} = 1 \rm{Mpc}$ and $h_{\rm{ap}} = 50 \rm{Mpc}$.
-The same analysis was repeated for various aperture dimensions: $r_{\rm{ap}} = 0.5, 1, 2, 3 \rm{Mpc}$ and $h_{\rm{ap}} = 25, 50 \rm{Mpc}$. 
-Minor adjustments to the environment classification thresholds were adopted in these analyses for the smaller apertures ($r_{\rm{ap}} = 0.5, 1 \rm{Mpc}$ and $r_{\rm{ap}} = 25 \rm{Mpc}$).
-The results obtained from using these different are consistent with the results displayed in this paper. 
 \begin{figure}
@@
         \epsscale{1.0}
-        \plotone{fig_qffit_cylr2h25_thresh75_bin0_25.png}
-        \label{fig:qffit}
-        \caption{Quiescent fraction at fiducial mass $\rm{log} (\mathcal{M}/\mathcal{M}_{\odot}) = 10.5$ for 
-low (square) and high (circle) environments in the redshift range $z = 0 - 0.8$. The evolution of 
-$f_{Q}(\mathcal{M}_{\rm{fid}})$ for galaxies in different environments shows an evolution over the redshift
-range that is independent of environment density. Futhermore throughout the redshift range the difference in 
-$f_{Q}(\mathcal{M}_{\rm{fid}})$ remains relatively constant and $ < 0.15$.}
+        \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_25_fidmass10_5_primuszerr.eps,height=0.45\textwidth}
+        \caption{The evolution of the quiescent fraction at fiducial mass, $f_{Q}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$, for sparse (square) and dense (circle) environments within the redshift range $z = 0.0 - 0.8$.
+There is a significant increase in $f_{Q}(\mathcal{M}_{\rm{fid}})$ with decrease in redshift for both environments.
+In addition, over the entire redshift range, $f_{Q}(\mathcal{M}_{\rm{fid}})$ for dense environment is greater than $f_{Q}(\mathcal{M}_{\rm{fid}})$ for lower environment.
+However the difference in $f_{Q}(\mathcal{M}_{\rm{fid}})$ for the two environments remains constant throughout suggesting that while the quiescent fraction is higher in dense environments, the evolution of the quiescent fraction is independent of environment.}         \label{fig:qffit}
     \end{center}
 \end{figure}
+%fiducial mass may be 11.0 depending on what we want.
+% fixed slope? Can't do fixed slope if we say there is mass dependence in f_q evolution
+
+While trends are apparent from Figure \ref{fig:qf}, quantitative comparisons of the 
+$f_{\rm{Q}}$ for different environment over redshift is made challenging by the distinct stellar mass 
+completeness limits for each redshift bin.
+In order to quantify the quiescent fraction over the stellar mass complete rate, we fit each $f_{\rm{Q}}$ to a power-law parameterization as a function of stellar mass,
+\begin{equation} 
+f_{\rm{Q}}(\mathcal{M}_{*}) = a \: \rm{log} \; \left(\frac{ \mathcal{M}_{*}}{10^{10.5} \: \mathcal{M}_{\odot}} \right)+b,
+\end{equation}
+where $a$ are $b$ are best-fit parameters using {\em MPFIT} (\cite{Markwardt:2009aa}).
+The value $10^{10.5} \: \mathcal{M}_{\odot}$ in the equation represents an empirically selected
+fiducial mass $\mathcal{M}_{\rm{fid}}$ within the stellar mass completeness limits. This fiducial mass 
+serves to highlight and quantify the $f_{\rm{Q}}$ evolution for different redshifts and using $\mathcal{M}_{\rm{fid}} = 10^{11} \mathcal{M}_\odot$ 
+does not notably alter the results. Figure \ref{fig:qffit} shows the evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ 
+for sparse (diamond) and dense (circle) environments.
+For both dense and spare environments, $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ increases as redshift decreases.
+In addition, through the redshift range explored in our analysis, dense environment $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ is significantly greater than the sparse environment $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$.
+However when we compute $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})_{\rm{dense}} - f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})_{\rm{sparse}}$, we find the difference remains constant throughout the redshift range ($ < 0.15$ throughout redshift range).
+Furthermore, the total evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ show no strong environment dependence.
+
+The analysis described in this paper use a fixed cylindrical aperture with dimensions $R_{\rm{ap}} = 2 \: \rm{Mpc}$ and $H_{\rm{ap}} = 25 \: \rm{Mpc}$ to measure environment, the same analysis was extended for varying aperture dimensions $R_{\rm{ap}} = 1, 2, 3 \: \rm{Mpc}$ and $H_{\rm{ap}} = 25, 50 \: \rm{Mpc}$.
+Minor adjustments to the environment classification thresholds were adopted in these analyses for the smaller apertures ($r_{\rm{ap}} = 0.5, 1 \rm{Mpc}$ and $r_{\rm{ap}} = 25 \rm{Mpc}$).
+The results obtained from using these different are consistent with the results displayed in this paper.
 

### 2014-05-23 qfenv_paper/qf_environment.tex
edits on the paper

@@
 \def \HgA {H$\gamma_A$}
-\def \gon {Gonz\'{a}lez}
 \def \Hbp {H$\beta ^\prime$}
@@
 
-\title{PRIMUS: Quiescent Fraction as a Function of Environment and Redshift}
+\title{PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 1$}
 \author{ChangHoon Hahn, Michael Blanton, Alison Coil, Richard Cool, Daniel Eisenstein, John Moustakas, Ken Wong, Guangtun Zhu}
@@
 \begin{abstract}
-We present the evolution of the quiescent fraction ($f_{\rm{Q}}$) for galaxies in 
-different density environments from $z=0.0$ to $0.8$ using spectroscopic 
-redshift and multi-wavelength imaging data from PRism MUlti-object 
-Survey (PRIMUS) and the Sloan Digitial Sky Survey (SDSS). We construct 
-a stellar mass limited galaxy population of 
-$\sim 40000$ galaxies from PRIMUS within the redshift range $0.2-0.8$ and $\sim 100000$
-galaxies from SDSS within redshift range $0.0375-0.145$. Using an evolving cut based on
-specific star formation, we classify the galaxies as quiescent or star-forming and
-measure its environment using a fixed cylindrical aperture method 
-on a volume-limited {\em Environment Defining Population} we construct 
-from PRIMUS and SDSS. Based on its environment we classify our target
-population into dense or sparse environments.
-
-With the target galaxy population divided into quiescent and star-forming galaxies 
-in dense and sparse environments, we calculate the stellar mass functions 
-(SMFs) for each of these subsamples. % should I include any conclusions on SMF in the abstract? 
-With these SMFs, we compute the $f_{\rm{Q}}$s to find that at 
-$\mathcal{M}_{*} \sim 10.5$, $f_{\rm{Q}}$ increases by $\sim 0.15$ from 
-$z=0.8$ to $0.0$ for both high and low environments. 
-In addition, throughout the redshift range the difference between the
-$f_{\rm{Q}}$ at high and low environment remains constant at $< 0.1$. 
-These results suggest that while $f_{\rm{Q}}$ increases for galaxies in 
-both dense and sparse environments over redshift, the evolution of $f_{\rm{Q}}$ 
-is independent of environment. 
+We investigate the effects of galaxy environment on the evolution of the quiescent fraction ($f_{\rm{Q}}$) from $z =0.8 $ to $ 0.0$ using spectroscopic redshifts and multi-wavelength imaging data from PRism MUlti-object Survey (PRIMUS) and the Sloan Digitial Sky Survey (SDSS).
+Our stellar mass limited galaxy sample consists of $\sim 40000$ PRIMUS galaxies within $z = 0.2-0.8$ and $\sim 130000$ SDSS galaxies within $z = 0.0375-0.145$.
+We classify the galaxies as quiescent or star-forming, based on an evolving specific star formation cut, and as low or high density environments, based on fixed cylindrical aperture environment measurements on a volume-limited {\em Environment Definition Population} (from PRIMUS and SDSS).
+We examine the stellar mass function (SMF) evolution for each of our subsamples of quiescent and star-forming galaxies in low and high density environments.
+We find, from the $f_{\rm{Q}}(\mathcal{M}_{*})$ computed from these SMFs, that in both low and high density environments the quiescent fraction increases with cosmic time over the probed redshift range.
+Moreover, the difference between the quiescent fraction in low and high density environments remains constant throughout the redshift range.
+These results suggest that the evolution of the quiescent fraction is independent of environment and provide constraints on quenching mechanisms in high density environments such as groups and clusters.
 \end{abstract}

### 2014-05-24 qfenv_paper/qf_environment.tex
clashing?

--- 2014-04-16 qfenv_paper/qf_environment.tex
@@
 \subsection{Target Galaxy Sample} \label{sec:target} 
-In this section we will define the target galaxy sample 
-used to compute the SMFs and QFs. The population 
-at $z \sim 0.5$ is derived from PRIMUS data and the 
-population at $z \sim 0.1$ is derived from SDSS-{\em GALEX} 
-data, both described above. For the intermediate redshift 
-population, we begin with the selection criteria imposed 
-in \cite{Moustakas:2013aa} for their parent sample. We 
-take the statistically complete {\em primary} sample from 
-the PRIMUS data (\cite{Coil:2011aa}) and impose magnitude 
-limits on optical selection bands as specified in 
-\cite{Moustakas:2013aa} Table 1. These limits are in different 
-optical selection bands and have distinct values for the 
-five PRIMUS target fields. We then exclude stars and 
-broad-line AGN to only select objects spectroscopically 
-classified as galaxies, with high-quality spectroscopic redshifts 
-($Q \geq 3$) within the redshift range $0.2 - 0.8$. For 
-each of these objects we assign statistical weights (described 
-in \cite{Coil:2011aa} and \cite{Cool:2013aa}) in order to correct 
-for targeting incompleteness and redshift failures. The 
-statistical weight, $w_i$, for each galaxy is given by
+In this seciton we will define the target galaxy sample we use to compute the SMFs and QFs.
+The population at $z \sim 0.5$ is derived from the PRIMUS data and the population at $z \sim 0.1$ is derived from the SDSS data, both described above.
+For the intermediate redshift target galaxy population, we begin with the selection criteria imposed in \cite{Moustakas:2013aa} for its parent sample.
+We take the statistically complete {\em primary} sample from the PRIMUS data (\cite{Coil:2011aa}) and then impose magnitude limits on optical selection bands as specified in 
+\cite{Moustakas:2013aa} Table 1.
+These limits are in different optical selection bands and have different values for our five PRIMUS target fields.
+Next, we join the PRIMUS, {\em GALEX}, and IRAC window functions to construct the angular selection function.
+We then exclude stars and broad-line AGN to only select objects spectroscopically classified as galaxies, with high-quality spectroscopic redshifts ($Q \geq 3$) within the 
+redshift range $0.2 - 0.8$.
+Afterwards we assign statistical weights (described in \cite{Coil:2011aa} and \cite{Cool:2013aa}) to the objects in order to correct for targeting incompleteness and redshift failures.
+The statistical weight, $w_i$, for each galaxy is given by
 \begin{equation}
@@
 \end{equation}
-Equation (1) in \cite{Moustakas:2013aa}. Then to account 
-for stellar mass incompleteness, we impose derived stellar 
-mass limits to the sample.
+Equation (1) in \cite{Moustakas:2013aa}.
+In addition to the selection criteria above, we impose stellar mass limits to have a stellar mass complete sample.  
+Stellar mass completeness limits for a magnitude-limited survey such as PRIMUS is a function of redshift, apparent magnitude limit of the survey, and the typical stellar 
+mass-to-light ratio of galaxies near the flux limit.
 
-Stellar mass completeness limits for a magnitude-limited 
-survey such as PRIMUS is a function of redshift, apparent 
-magnitude limit of the survey, and the typical stellar 
-mass-to-light ratio of galaxies near the flux limit. As done 
-in \cite{Moustakas:2013aa}, we follow \cite{Pozzetti:2010aa} 
-to empirically determine the stellar mass completeness limits.
-Briefly, for each of the target galaxies we compute 
-$\mathcal{M}_{\rm{lim}}$ using $\rm{log} \; \mathcal{M}_{\rm{lim}} = \rm{log} \; \mathcal{M} + 0.4 ( m - m_{\rm{lim}})$.
-$\mathcal{M}$ is the stellar mass of the galaxy in $\mathcal{M_{\odot}}$, 
-$\mathcal{M}_{\rm{lim}}$ is the stellar mass of each galaxy 
-if its magnitude was equal to the survey magnitude limit, 
-$m$ is observed apparent magnitude in the selection band, 
-and $m_{\rm{lim}}$ is the magnitude limit for our five 
-fields mentioned above. We construct a cumulative 
-distribution of $\mathcal{M}_{\rm{lim}}$ for the $15\%$ 
-faintest galaxies in $\Delta z=0.04$ bins. In each of these 
-redshift bins, we calculate the minimum stellar mass that 
-includes $95 \%$ of the galaxies. Separately for quiescent 
-and star-forming galaxies, we fit quadratic polynomials to 
-the minimum stellar masses versus redshift (galaxies are 
-classified into star-forming or quiescent in the following section).
-Finally, we use the polynomials to obtain the minimum stellar 
-masses at the center of redshift bins, $0.2-0.4$, $0.4-0.6$, 
-and $0.6-0.8$, which are then used as PRIMUS stellar mass
-completeness limits.
+As done in \cite{Moustakas:2013aa}, we follow \cite{Pozzetti:2010aa} to empirically determine the stellar mass completeness limits.
+Briefly, for each of the target galaxies we compute $\mathcal{M}_{\rm{lim}}$ using $\rm{log} \; \mathcal{M}_{\rm{lim}} = \rm{log} \; \mathcal{M} + 0.4 ( m - m_{\rm{lim}})$.
+$\mathcal{M}$ is the stellar mass of the galaxy in units of $\mathcal{M_{\odot}}$, $\mathcal{M}_{\rm{lim}}$ is the stellar mass of each galaxy if its magnitude was 
+equal to the survey magnitude limit, $m$ is observed apparent magnitude in the selection band, and $m_{\rm{lim}}$ is the magnitude limit for our five fields mentioned above.
+We construct a cumulative distribution of $\mathcal{M}_{\rm{lim}}$ for the $15\%$ faintested galaxies in $\Delta z=0.04$ redshift bins.
+In each of these redshift bins, we calculate the minimum stellar mass that includes $95 \%$ of the galaxies.
+Separately for quiescent and star-forming galaxies, we fit quadratic polynomials to the minimum stellar masses versus redshift (classificiation scheme for quiescent 
+and star-forming galaxies is included in the following section).
+Finally, we use the polynomials to obtain the minimum stellar masses at the center of the redshift bins, $0.2-0.4$, $0.4-0.6$, $0.6-0.8$, and $0.8-1.0$.
+These redshift bins will later be used to divide the target sample in order to compute the SMFs and QFs.
 
-For our target galaxy population at low redshift we start with 
-the SDSS-{\em GALEX} data. We limit our population within 
-the redshift range $0.0375-0.145$ due to redshift limits later 
-imposed on the volume-limited Environment Defining Population 
-(Section \ref{sec:environment}). To account for targeting 
-completeness of this sample, we use the statistical weight 
-estimates provided by the NYU-VAGC. Then to account for 
-stellar mass incompleteness, we impose a uniform stellar mass 
-limit of $10^9.8 \mathcal{M}_{\odot}$, a limit determined by the 
-stellar mass-to-light ratio completeness of the NYU-VAGC 
-sample given the redshift limits.
-
-The absolute magnitude ($M_{r}$) versus redshift for the 
-target galaxy population (black squares) is plotted in Figure 
-\ref{fig:targetEDP}. The left-most panel corresponds to the
-target sample derived from the SDSS-{\em GALEX} data and
-the rest correspond to the target sample derived from the 
-PRIMUS data divided in bins with $\Delta z \sim 0.2$.
+For our target galaxy population at low redshift we use our SDSS-{\em GALEX} data. 
+We limit our target population within the redshift range $0.0375-0.145$ due to redshift limits later imposed for the volume-limited Environment Defining Population (Section \ref{sec:environment}).
+The NYU-VAGC provides statistical weight estimates for targeting completeness.
+In order to have a stellar mass complete low redshift target population, we use a uniform stellar mass limit of $10^9 \mathcal{M}_{\odot}$, which is above the surface 
+brightness and stellar mass-to-light ratio completness limits (\cite{Blanton:2005ab}; \cite{Baldry:2008aa}).
+The absolute magnitude ($M_{r}$) versus redshift for the target galaxy population at both low redshift and intermediate redshift is plotted in Figure \ref{fig:targetEDP}.
+For further details we refer readers to \cite{Moustakas:2013aa} for details; more specifically, Figure 2., Sections 3.1, and 4.3.
 
@@
     \leavevmode
-     \epsfig{file=fig_smf_cylr2h25_thresh75_bin0_25_2envbin_primuszerr.eps,height=0.75\textwidth,angle=90}
-     \caption{Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) target galaxies in 
+     \label{fig:smf}
+     \epsfig{file=fig_smf_cylr2h25_thresh75_bin0_25.eps,height=0.75\textwidth,angle=90}
+     \caption{NEED TO UPDATE WITH CORRECT SDSS MASS LIMIT. Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) galaxies in 
 low (left) and high (right) environments from redshift range $z=0-0.8$. The environment of each galaxy  
-was calculated using a cylindrical aperture size of $R=2 \: \rm{Mpc}$ and $H=25 \: \rm{Mpc}$ and  
+was calculated using a cylindrical aperture size of $R=2\rm{Mpc}$ and $H=25\rm{Mpc}$ and  
 classification based on the cut-offs specified in Table \ref{tab:aperture}. The SMFs use mass bins of 
@@
 (star-forming) and orange (quiescent) to represent the SMF at different redshift, higher redshifts being
-progressively lighter.}      \label{fig:smf}
+progressively lighter.}
     \end{center}
@@
 the cumulative number density of SDSS EDP to the highest redshift bin of the PRIMUS EDP. 
-Ultimately, we get $M_{r,\rm{lim}} = -20.57$, $-20.73$, $-20.80$ and $-20.95$ for the redshift bins $0.0375-0.145$, 
+Ultimately, we get $M_{r,\rm{lim}} = -20.57$, $-20.73$, $-20.80$ and $-20.95$ for the redshift bins $0.06-0.145$, 
 $0.2-0.4$, $0.4-0.6$, $0.6-0.8$, respectively.  %%%% PUT NEW VALUES
@@
         \leavevmode
+        \label{fig:smf}
         \epsfig{file=fig_qf_cylr2h25_thresh75_bin0_25_primuszerr.eps,height=0.75\textwidth,angle=90}
-        \caption{Evolution of the quiescent fraction $f_{\rm{Q}}$ for target galaxies in spare (left) and dense (rights) environments
-from $z \sim 0.7$ to $z \sim 0.1$.
-$f_{\rm{Q}}$s were calculated using the SMFs computed in Section \ref{sec:smf} and shown in Figure\ref{fig:smf}, as described in text.
-Darker shading indicates lower redshift.}         \label{fig:qf}
+        \caption{Evolution of the quiescent fraction for target galaxies in low (left) and (high) environments
+from redshift range $z=0-0.8$. The QFs were calculated using the SMFs specificed in Figure \ref{fig:smf}. We use
+lighter shades of orange for the QFs at higher redshifts.}
     \end{center}
@@
 
-%\section{Results}
-%In the section below, we calculate stellar mass functions (SMFs) for the target galaxy population divided into 
-%quiescent/star-forming and dense/sparse environment, Section \ref{sec:smf_const}. We use a non-parametric 
-%$1/V_{\rm{max}}$ estimate of SMFs for the subsamples further divided into redshift bins. Then using these 
-%SMFs, we calculate the quiescent fractions (QFs), Section \ref{sec:qf_const}, 
-%and examine it's evolution over our redshift range.
+\section{Results}
+In the section below, we calculate stellar mass functions (SMFs) for the target galaxy population divided into 
+quiescent/star-forming and dense/sparse environment, Section \ref{sec:smf_const}. We use a non-parametric 
+$1/V_{\rm{max}}$ estimate of SMFs for the subsamples further divided into redshift bins. Then using these 
+SMFs, we calculate the quiescent fractions (QFs), Section \ref{sec:qf_const}, 
+and examine it's evolution over our redshift range.
 
-\section{Stellar Mass Function} \label{sec:smf}
+\subsection{Stellar Mass Function} \label{sec:smf_const}
 The target galaxy sample defined above has so far
@@
 dense or sparse. We further divide these subsamples 
-into bins of redshift:  in redshift bins of $0.0375-0.145$, 
+into bins of redshift:  in redshift bins of $0.06-0.145$, 
 $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$. While the 
@@
 bins. $\langle \Phi^j \rangle$ is the mean number density of galaxies 
-in each stellar mass bin for all of the jack knife $\Phi^j$s.
-
-SMFs for 16 target galaxy subsamples classified into quiescent/star-forming (orange/blue)and 
+in each stellar mass bin for all of the jack knife $\Phi^j$s. The SMFs for 
+16 target galaxy subsamples classified into quiescent/star-forming (orange/blue)and 
 dense/spare environments are presented in Figure \ref{fig:smf}. The 
@@
 width of the SMFs. The environment measurements and classifications
-for Figure \ref{fig:smf} are done using a cylindrical aperture with dimensions,
+for Figure \ref{fig:smf} is done using a cylindrical aperture with dimensions,
 $R_{\rm{ap}} = 2 \; \rm{Mpc}/h$ and $H_{\rm{ap}} = 25 \; \rm{Mpc}/h$.
 
-Examining the SMF evolution from $z \sim 0.7$ to $z \sim 0.1$, 
-we find that in dense environments both the star-forming and quiescent
-SMFs increase at $\mathcal{M}_{*}$ below the knee of mass function 
-($\rm{log}\: \mathcal{M}_{*}/\mathcal{M}_{\odot} < 10.75$ for star-forming; 
-$\rm{log}\: \mathcal{M}_{*}/\mathcal{M}_{\odot} < 11.0$ for quiescent). 
-Meanwhile, at masses above the knee the SMFs for dense environments 
-exhibit little change throughout the redshift range.
+Examining the SMF evolution over $z \sim 0 - 0.8$, we find that in dense 
+environments, the quiescent SMFs increase by a factor of $over9000$ 
+for $\mathcal{M}_{*} < 11.0$ while the SMF of the star-forming 
+galaxies evolves little for all masses. Meanwhile in low density 
+environments from $z=0.8$ to $0.0$, we find that the SMF of 
+quiescent galaxies evolves little for all stellar masses and the 
+SMF of star-forming galaxies decreases by a factor of $over9000$ 
+for $\mathcal{M}_{*} > 10.5$.  
+%%% EXPAND ON ANALYSIS OF SMF
 
-At sparse environments, the quiescent SMF remains relatively constant 
-for galaxies with $\rm{log}\: \mathcal{M}_{*}/\mathcal{M}_{\odot} < 10.75$.
-At higher stellar masses, however, the SMF decreases notably. Finally 
-the sparse environment star-forming SMF shows a decrease at all 
-stellar mass ranges over the redshift range.
-
-%%% COMPARISON TO OTHER LITERATURE?
-
-\section{Quiescent Fraction} \label{sec:qf_const}
-From the SMF number densities ($\Phi$) calculated
-in the previous section, the quiescent fraction is computed 
-as follows, 
+\subsection{Quiescent Fraction} \label{sec:qf_const}
+Using the SMF number densities ($\Phi$) calculated above, 
+in this section, we compute the quiescent fraction, $f_{\rm{Q}}$ 
+for dense and sparse environments over the redshift range 
+$0.0 - 0.8$.  The quiescent fraction is simply given by the following 
+equation: 
 \begin{equation}
@@
 for the quiescent and star-forming subsamples, respectively 
-(Equation \ref{eq:phi}). We compute $f_{\rm{Q}}$ for dense 
-and spare environments over our redshift range as plotted in
- Figure \ref{fig:qf}, which shows the evolution of $f_{\rm{Q}}$ 
- for dense (right) and sparse (left) environments. As in 
- Figure \ref{fig:smf}, the darker shading represent lower redshifts.
+(Equation \ref{eq:phi}). The bottom panels of Figure \ref{fig:smf} 
+shows the evolution of $f_{\rm{Q}}$ for dense (right) and sparse (left)
+environments. As before, the darker shades of orange represent 
+lower redshift bins.
 
-For both the spare and dense environments there is a notable 
-increase in $f_{\rm{Q}}$ at all stellar masses as redshift decreases.
 %%% INCLUDE BRIEF QUALITATIVE ANALYSIS OF THE EVOLUTION OF THE QUIESCENT FRACTION
@@
         \epsscale{1.0}
-        \plotone{fig_qffit_cylr2h25_thresh75_bin0_25.png}
-        \label{fig:qffit}
+        \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_25_fidmass10_5_fixedslope_primuszerr.eps,height=0.5\textwidth}
+        \label{fig:qf}
         \caption{Quiescent fraction at fiducial mass $\rm{log} (\mathcal{M}/\mathcal{M}_{\odot}) = 10.5$ for 
@@
 
-\section{Summary}
+\section{Discussion and Conclusions}
 We have measured the SMFs and QFs using low redshift SDSS-{\em GALEX} galaxies and intermeidate redshift PRIMUS galaxies. 
@@
         \leavevmode
+        \label{fig:smf}
         \epsscale{1.0}
@@
         \plotone{fig_qffit_cylr1h25_thresh80_bin0_25.png}
+        \label{fig:qf}
         \caption{QF at fiducial mass for $r_{\rm{ap}}=2 \rm{Mpc}$ and $h_{\rm{ap}}=50 \rm{Mpc}$}

### 2014-05-29 qfenv_paper/qf_environment.tex
Abstract Editted

--- 2014-05-23 qfenv_paper/qf_environment.tex
@@
 We classify the galaxies as quiescent or star-forming, based on an evolving specific star formation cut, and as low or high density environments, based on fixed cylindrical aperture environment measurements on a volume-limited {\em Environment Definition Population} (from PRIMUS and SDSS).
-We examine the stellar mass function (SMF) evolution for each of our subsamples of quiescent and star-forming galaxies in low and high density environments.
-We find, from the $f_{\rm{Q}}(\mathcal{M}_{*})$ computed from these SMFs, that in both low and high density environments the quiescent fraction increases with cosmic time over the probed redshift range.
+For each of these subsamples, we examine the stellar mass function (SMF) evolution and compute the $f_{\rm{Q}}(\mathcal{M}_{*})$.
+We find that in both low and high density environments the quiescent fraction increases with cosmic time over the probed redshift range.
 Moreover, the difference between the quiescent fraction in low and high density environments remains constant throughout the redshift range.

### 2014-05-29 qfenv_paper/qf_environment.tex
Edited Section 2.1-2.4

@@
 
+In Section \ref{sec:sample}, we present 
+%%% INCLUDE OUTLINE OF PAPER
+
 \section{Sample Selection} \label{sec:sample}
-In this paper we are interested in measuring the evolution of the quiescent 
-fraction over a wide range of redshifts and in different galaxy environments. 
-In order construct a sample with redshift depth and robust enough redshift values 
-to measure galaxy environment, we use galaxies at intermediate redshifts from PRIMUS. 
-Additionally we supplement our sample with galaxies at low redshift ($z \sim 0.1$) from SDSS.
+We are interested in quantifying the effects of galaxy environment on the evolution of the quiescent fraction over the redshift range $ z < 1.0$.
+For our analysis, we require a sample with sufficient depth to probe the redshift range and robust redshifts to measure galaxy environment.
+PRIMUS, with its $\sim 120,000$ spectroscopic redshifts provides ideal data at intermediate redshifts for our analysis.
+In addition, we anchor our analysis of the intermediate redshift sample with a low redshift sample derived from SDSS.
 
-We begin with a brief summary of the PRIMUS data in Section \ref{sec:primus} followed by a summary of the SDSS data in Section \ref{sec:sdss}.
-Then in Section \ref{sec:target} we use this data to define the stellar mass complete target galaxy population.
-Afterwards, in Section~\ref{sec:sfq}, we classify these target galaxies as quiescent or active star-forming galaxies. 
-For each galaxy we obtain the environment using a volume-limited {\em Environment Defining Population} in Section \ref{sec:environment}. 
-Finally in Section \ref{sec:edgeeffect}, we correct the galaxy sample and its environment measurements for the edge effects of the surveys.
+In Section \ref{sec:primus} and Section \ref{sec:sdss} we provide a brief summary of the PRIMUS data and the SDSS data used for our sample selection.
+Then in Section \ref{sec:target} we define our stellar mass complete target galaxy population.
+Afterwards, in Section \ref{sec:sfq}, we classify our sample galaxies as quiescent or star-forming then calculate the environment using a volume-limited {\em Environment Defining Population} in Section \ref{sec:environment}.
+Finally in Section \ref{sec:edgeeffect}, we correct our galaxy sample and environment measurements for edge effects of the surveys.
 
 \subsection{PRIMUS} \label{sec:primus}
-For galaxies at intermediate redshifts we use multiwavelength imaging and spectroscopic redshifts data of PRIMUS, which is a faint galaxy survey with precise spectroscopic redshifts ($\sigma_z/(1+z) \approx 0.5 \%$) for $\sim 120,000$ galaxies within redshifts $z \approx 0-1.2$.
+For our sample at intermediate redshifts we use multiwavelength imaging and spectroscopic redshifts from PRIMUS, a faint galaxy survey with $\sim 120,000$ precise spectroscopic redshifts ($\sigma_z/(1+z) \approx 0.5 \%$) within the range $z \approx 0-1.2$.
 The survey was conducted using a IMACS spectrograph on a Magellan I Baade $6.5$ m telescope with a slitmask and low dispersion prism.
-For further details on the PRIMUS observation methods, including survey design, targeting, and data summary, we refer readers to the survey papers: \cite{Coil:2011aa} and \cite{Cool:2013aa}.
+For details on the PRIMUS observation methods such as survey design, targeting, and data summary, we refer readers to the survey papers: \cite{Coil:2011aa} and \cite{Cool:2013aa}.
 
-As done in \cite{Moustakas:2013aa}, we only use fields targeted by PRIMUS with $GALEX$ and {\em Spitzer}/IRAC imaging.
-This restricts us to five fields.
-Four of these fields are a part of the {\em Spitzer} Wide-area Infrared Extragalactic Survey (SWIRE\footnote{http://swire.ipac.caltech.edu/swire/swire.html} ): 
-the European Large Area ISO Survey - South $1$ field (ELAIS-S1\footnote{http://dipastro.pd.astro.it/esis}), the Chanddra Deep Field South SWIRE field (CDFS), 
-and the XMM Large Scale Structure Survey field (XMM-LSS).
-The XMM-LSS consists of two separate but spatially adjacent fields: the Subaru/XMM-Newton DEEP Survey fied (XMM-SXDSS\footnote{http://www.naoj.org/cience/SubaruProject/SDS})
-and the Canadian-France-Hawaii Telescope Legacy Survey field (XMM-CFHTLS\footnote{http://www.cfht.hawaii.edu/Science/CFHLS}).
-In addition to the SWIRE fields we also include the COSMOS\footnote{http://cosmos.astro.caltech.edu} field for a total of five fields.
+While the PRIMUS survey targeted seven distinct extragalactic deep fields for a total of $\sim 9 \; \rm{deg}^2$, we restrict our sample to five fields that have $GALEX$ and {\em Spitzer}/IRAC imaging (similar to the sample selection in \cite{Moustakas:2013aa}).
+Four of these fields are a part of the {\em Spitzer} Wide-area Infrared Extragalactic Survey (SWIRE\footnote{http://swire.ipac.caltech.edu/swire/swire.html} ): the European Large Area ISO Survey - South $1$ field (ELAIS-S1\footnote{http://dipastro.pd.astro.it/esis}), the Chanddra Deep Field South SWIRE field (CDFS), and the XMM Large Scale Structure Survey field (XMM-LSS).
+The XMM-LSS consists of two separate but spatially adjacent fields: the Subaru/XMM-Newton DEEP Survey fied (XMM-SXDSS\footnote{http://www.naoj.org/cience/SubaruProject/SDS}) and the Canadian-France-Hawaii Telescope Legacy Survey field (XMM-CFHTLS\footnote{http://www.cfht.hawaii.edu/Science/CFHLS}).
+Our fifth and final field is the Cosmic Evolution Survey (COSMOS\footnote{http://cosmos.astro.caltech.edu}) field.
+For all of our fields we have near-UV (NUV) and far-UV (FUV) photometry from the {\em GALEX} Deep Imaging Survey (DIS; \cite{Martin:2005aa}; \cite{Morrissey:2005aa}) as well as ground-based optical and {\em Spitzer}/IRAC mid-infrared photometric catalogs.
+\cite{Moustakas:2013aa} provides detailed descriptions of integrated flux calculations in the photometric bands for each of our fields.
 
-In all of the PRIMUS target fields we have near-UV (NUV) and far-UV (FUV) measurements from the {\em GALEX} Deep Imaging Survey (DIS; \cite{Martin:2005aa}; \cite{Morrissey:2005aa}). 
-To minimize contamination from neighboring sources, we use a Bayesian photometric code EM$_{\rm{PHOT}}$ (based on expectation maximization algorithm of \cite{Guillaume:2006aa}). 
-Furthermore, we use ground-based optical and {\em Spitzer}/IRAC mid-infrared photometric catalogs in each of the fields to obtain integrated fluxes in all 
-photometric bands.
-To summarize, the general strategy employed is to use a circular aperture photometry to constrain the shape of the SED and then fixing the overall normalization to 
-a estimate of the total magnitude in the detection band. 
-\cite{Moustakas:2013aa} provides a detailed description of the calculation for each of our target fields.
+Finally, from the spectroscopic redshift and broad wavelength photometry we use \texttt{iSEDfit}, a Bayesian SED modeling code, to calculate stellar masses and star formation rates (SFRs) for our sample galaxies.
+\texttt{iSEDfit}, uses the redshift and the observed photometry of the galaxies to determine the statistical likelihood of a large ensemble of generated model SEDs.
+The model SEDs are generated using Flexible Stellar Population Synthesis (FSPS) models (\cite{Conroy:2010aa}) based on \cite{Chabrier:2003aa} IMF, along with other prior parameters beyond the scope of this paper.
+For details we refer readers to Section 4.1 and Appendix A.
+of \cite{Moustakas:2013aa}.
+For the observed photometry, we use the {\em GALEX} FUV and NUV, the two shortest IRAC bands at $3.6$ and $4.5 \mu \rm{m}$ (the two longer-wavelength IRAC channels are excluded because \texttt{iSEDfit} does not model hot dust or polycyclic aromatic hydrocarbons emission lines), and the optical bands.
 
-From the spectroscopic redshift and photometry described above, we use \texttt{iSEDfit} to determine stellar masses, star formation rates (SFRs) and other physical properties
-in a simplified Bayesian framework.
-\texttt{iSEDfit}, which we will only briefly mention in this paper is discussed in detail in Appendix A. of \cite{Moustakas:2013aa}.
-The code uses the redshift and the observed photometry of the galaxies to determine the statistical likelihood of a large ensemble of generated model SEDs. 
-These generated model SEDs depend on population synthesis models and prior parameters.
-In order to derive our fiducial stellar masses and star formation rates, we use the Flexible Stellar Population Synthesis (FSPS) models (\cite{Conroy:2010aa}) based on the \cite{Chabrier:2003aa} IMF. 
-Other prior parameters are listed in Section 4.1 of \cite{Moustakas:2013aa}. 
-The photometric bands we use for the fitting in our PRIMUS data are the {\em GALEX} FUV and NUV, the two shortest IRAC bands at $3.6$ and $4.5 \mu \rm{m}$, and the five optical bands
-(in the COSMOS field, we fit seven optical bands and near-infrared bands, see Section 2.3 of \cite{Moustakas:2013aa}).
-For a more detailed description of the data used in this paper, we refer readers to \cite{Moustakas:2013aa} Section 2 and Section 4.1.
 \begin{table} %Subject to significant change based on the classification of environment
@@
     \begin{tabular}{lllll} \hline \hline              
-  Survey    &Redshift ($z$) &Density        &Quiescent  &Star-forming  \\ \hline 
+      &$z$ &Environment        &Quiescent  &Star-forming  \\ \hline 
   SDSS      &$0.0375-0.145$ &High           &5470                       &4501                           \\
-            &               &Mid            &3614                       &4438                           \\
             &               &Low            &5419                       &8927                           \\
@@
   PRIMUS    &$0.2-0.4$      &High           &322                    &583                           \\
-            &               &Mid            &177                    &403                          \\
             &               &Low            &768                    &2516                           \\
@@
   PRIMUS    &$0.4-0.6$      &High           &350                       &675                           \\
-            &               &Mid            &195                       &405                           \\
             &               &Low            &871                       &2385                           \\
@@
   PRIMUS    &$0.6-0.8$      &High           &347                       &430                           \\
-            &               &Mid            &186                       &327                           \\
             &               &Low            &833                       &1847                           \\
@@
   PRIMUS    &$0.8-1.0$      &High           &136                       &232                           \\
-            &               &Mid            &94                       &163                           \\
             &               &Low            &373                       &810                           \\
@@
         \leavevmode
-        \label{fig:targetEDP}
         \epsscale{1.0}
 	\plotone{fig_EDP_absmag_redshift.png}
-        \caption{Absolute magnitude $M_{r}$ versus redshift for the target galaxy population (black) with the 
-Environment Defining Population (red) plotted on top. Both samples are divided into redshift bins:$0.0375-0.145$, 
-$0.2-0.4$, $0.4-0.6$, and $0.6-0.8$. Stellar mass completeness limits are imposed on the target galaxy population (Section \ref{sec:target}) 
-while the $M_{r}$ limits are imposed on the EDP (Section \ref{sec:environment}).}
+        \caption{Absolute magnitude $M_{r}$ versus redshift for the target galaxy population (black squares) with the Environment Defining Population (red circles) plotted on top.
+Both samples are divided into redshift bins:$z \approx 0.0375-0.145$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ (panels left to right).
+Stellar mass completeness limits are imposed on the target galaxy population (Section \ref{sec:target}) while the $M_{r}$ limits are imposed on the EDP (Section \ref{sec:environment}).
+The lowest redshift bin ($z \approx 0.0375-0.145$; leftmost panel) contain our galaxy sample and EDP selected from SDSS.
+The rest contain galaxies and EDP selected from PRIMUS.} \label{fig:targetEDP}
     \end{center}
@@
 \subsection{SDSS-GALEX} \label{sec:sdss}
-For galaxies at low redshifts we use the SDSS Data Release 7 (DR7; \cite{Abazajian:2009aa}). 
-From the SDSS DR7 data, which provides high fidelity $ugriz$ photometry and spectroscopic redshift, we specifically use galaxies from the New York University 
-Value-Added Galaxy Catalog that satisfy the main sample criterion and have galaxy extinction corrected Petrosian magnitudes $14.5 < r < 17.6$ 
-and spectroscopic redshits within $0.01<z<0.2$ (\cite{Blanton:2005aa}). 
-Within this sample, we select galaxies with medium depth observations from GALEX. 
-This is done by first retrieving the positions of all {\em GALEX} tiles from GALEX Release 6 with total exposure time greater than $1$ ks and then constructing 
-a joint angular selection function of the SDSS-{\em GALEX} Sample. 
-This results in a final sample of $167,727$ SDSS galaxies with {\em GALEX} imaging.
+For our low redshift sample, we use spectroscopic redshifts and high fidelity $ugriz$ photometry from the SDSS Data Release 7 (DR7; \cite{Abazajian:2009aa}).
+More specifically we select galaxies from the New York University Value-Added Galaxy Catalog (SDSS VAGC) that satisfy the main sample criterion and have galaxy extinction corrected Petrosian magnitudes $14.5 < r < 17.6$ and spectroscopic redshifts within $0.01 < z < 0.2$ (\cite{Blanton:2005aa}).
+We further narrow down the SDSS VAGC sample to only galaxies with medium depth observations with total exposure time greater than $1 \; \rm{ks}$ from {\em GALEX} Release 6.
+This SDSS-{\em GALEX} sample contains $167,727$ galaxies.
 
-For this final sample, we use the MAST/CasJobs\footnote{http://galex.stsci.edu/casjobs} interface and a $4''$ diamater search radius to obtain the NUV and FUV photometry. 
-For the optical photometry we use $ugriz$ bands (from the SDSS \texttt{model} magnitudes) scaled to the $r$-band \texttt{cmodel} magnitude. 
-We supplement the above UV and optical photometry with integrated $JHK_s$ magnitudes from the 2MASS Extended Source Catalog (XSC; \cite{Jarrett:2000aa}) and with photometry at $3.4$ 
-and $4.6 \mu \rm{m}$ from the WISE All-Sky Data Release\footnote{http://wise2.ipac.caltech.edu/docs/release/allsky}. 
-Further details on the photometry of the SDSS data used in this paper is provided in \cite{Moustakas:2013aa} Section 2.4.
+Using the MAST/CasJobs\footnote{http://galex.stsci.edu/casjobs} interface and a $4''$ diameter search radius, we obtain the NUV and FNU photometry for the SDSS-{\em GALEX} galaxies.
+For optical photometry, we use the $ugriz$ bands from the SDSS \texttt{model} magnitudes scaled to the $r$-band \texttt{cmodel} magnitude.
+These photometric bands are then supplemented with integrated $JHK_s$ magnitudes from the 2MASS Extended Source Catalog (XSC; \cite{Jarrett:2000aa}) and with photometry at $3.4$ and $4.6 \mu \rm{m}$ from the WISE All-Sky Data Release\footnote{http://wise2.ipac.caltech.edu/docs/release/allsky}.
+Further details regarding the SDSS-{\em GALEX} sample photometry can be found in Section 2.4 of \cite{Moustakas:2013aa}.
+As we did with the PRIMUS data above, we use \texttt{iSEDfit} with the above observed photometry to obtain the stellar masses and star formation rates for the SDSS-{\em GALEX} sample.
 
-To obtain the stellar masses and SFRs for the SDSS data we use \texttt{iSEDfit}, as we did for the PRIMUS data in Section \ref{sec:primus}.  
-However, we use twelve photometric bands: {\em GALEX} FUV and NUV, SDSS $ugriz$, 2MASS $JHK_{s}$, and WISE $3.4$ and $4.6 \mu \rm{m}$.
+\subsection{Galaxy Sample} \label{sec:target} 
+Using the low redshift SDSS-{\em GALEX} and intermediate redshift PRIMUS data described above, in this section, we define our galaxy sample which will be used to compute the SMFs and QFs.
+For PRIMUS, we begin with the selection criteria imposed in \cite{Moustakas:2013aa} for their parent sample.
+We take the statistically complete {\em primary} sample from the PRIMUS data (\cite{Coil:2011aa}) and impose magnitude limits on optical selection bands as specified in \cite{Moustakas:2013aa} Table 1.
+These limits are in different optical selection bands and have distinct values for the five PRIMUS target fields.
+We then exclude stars and broad-line AGN to only select objects spectroscopically classified as galaxies, with high-quality spectroscopic redshifts ($Q \geq 3$).
+In addition we impose a redshift range of $ 0.2 < z < 0.8$ for the PRIMUS galaxy sample, where $ z > 0.2$ is selected due to limitations from sample variance and $ z < 0.8$ is selected due to the lack of sufficient statistics in subsamples defined below.
 
-\subsection{Target Galaxy Sample} \label{sec:target} 
-In this section we will define the target galaxy sample 
-used to compute the SMFs and QFs. The population 
-at $z \sim 0.5$ is derived from PRIMUS data and the 
-population at $z \sim 0.1$ is derived from SDSS-{\em GALEX} 
-data, both described above. For the intermediate redshift 
-population, we begin with the selection criteria imposed 
-in \cite{Moustakas:2013aa} for their parent sample. We 
-take the statistically complete {\em primary} sample from 
-the PRIMUS data (\cite{Coil:2011aa}) and impose magnitude 
-limits on optical selection bands as specified in 
-\cite{Moustakas:2013aa} Table 1. These limits are in different 
-optical selection bands and have distinct values for the 
-five PRIMUS target fields. We then exclude stars and 
-broad-line AGN to only select objects spectroscopically 
-classified as galaxies, with high-quality spectroscopic redshifts 
-($Q \geq 3$) within the redshift range $0.2 - 0.8$. For 
-each of these objects we assign statistical weights (described 
-in \cite{Coil:2011aa} and \cite{Cool:2013aa}) in order to correct 
-for targeting incompleteness and redshift failures. The 
-statistical weight, $w_i$, for each galaxy is given by
+For the PRIMUS objects that meet the above criteria, we assign statistical weights (described in \cite{Coil:2011aa} and \cite{Cool:2013aa}) in order to correct for targeting incompleteness and redshift failures.
+The statistical weight, $w_i$, for each galaxy is given by
 \begin{equation}
@@
 \end{equation}
-Equation (1) in \cite{Moustakas:2013aa}. Then to account 
-for stellar mass incompleteness, we impose derived stellar 
-mass limits to the sample.
+Equation (1) in \cite{Moustakas:2013aa}.
+Given that our ultimate interest is in deriving the SMFs and QFs from our sample, we impose stellar mass limits in order to derive a stellar mass complete galaxy sample.
 
-Stellar mass completeness limits for a magnitude-limited 
-survey such as PRIMUS is a function of redshift, apparent 
-magnitude limit of the survey, and the typical stellar 
-mass-to-light ratio of galaxies near the flux limit. As done 
-in \cite{Moustakas:2013aa}, we follow \cite{Pozzetti:2010aa} 
-to empirically determine the stellar mass completeness limits.
-Briefly, for each of the target galaxies we compute 
-$\mathcal{M}_{\rm{lim}}$ using $\rm{log} \; \mathcal{M}_{\rm{lim}} = \rm{log} \; \mathcal{M} + 0.4 ( m - m_{\rm{lim}})$.
-$\mathcal{M}$ is the stellar mass of the galaxy in $\mathcal{M_{\odot}}$, 
-$\mathcal{M}_{\rm{lim}}$ is the stellar mass of each galaxy 
-if its magnitude was equal to the survey magnitude limit, 
-$m$ is observed apparent magnitude in the selection band, 
-and $m_{\rm{lim}}$ is the magnitude limit for our five 
-fields mentioned above. We construct a cumulative 
-distribution of $\mathcal{M}_{\rm{lim}}$ for the $15\%$ 
-faintest galaxies in $\Delta z=0.04$ bins. In each of these 
-redshift bins, we calculate the minimum stellar mass that 
-includes $95 \%$ of the galaxies. Separately for quiescent 
-and star-forming galaxies, we fit quadratic polynomials to 
-the minimum stellar masses versus redshift (galaxies are 
-classified into star-forming or quiescent in the following section).
-Finally, we use the polynomials to obtain the minimum stellar 
-masses at the center of redshift bins, $0.2-0.4$, $0.4-0.6$, 
-and $0.6-0.8$, which are then used as PRIMUS stellar mass
-completeness limits.
+Stellar mass completeness limits for a magnitude-limited survey such as PRIMUS is a function of redshift, the apparent magnitude limit of the survey, and the typical stellar mass-to-light ratio of galaxies near the flux limit.
+As done in \cite{Moustakas:2013aa}, we follow \cite{Pozzetti:2010aa} to empirically determine the stellar mass completeness limits.
+For each of the target galaxies we compute $\mathcal{M}_{\rm{lim}}$ using $\rm{log} \; \mathcal{M}_{\rm{lim}} = \rm{log} \; \mathcal{M} + 0.4 ( m - m_{\rm{lim}})$, where $\mathcal{M}$ is the stellar mass of the galaxy in $\mathcal{M_{\odot}}$, $\mathcal{M}_{\rm{lim}}$ is the stellar mass of each galaxy if its magnitude was equal to the survey magnitude limit, $m$ is observed apparent magnitude in the selection band, and $m_{\rm{lim}}$ is the magnitude limit for our five fields mentioned above.
+We construct a cumulative distribution of $\mathcal{M}_{\rm{lim}}$ for the $15\%$ faintest galaxies in $\Delta z=0.04$ bins.
+In each of these redshift bins, we calculate the minimum stellar mass that includes $95 \%$ of the galaxies.
+Separately for quiescent and star-forming galaxies, we fit quadratic polynomials to the minimum stellar masses versus redshift (galaxies are classified into star-forming or quiescent in the following section).
+Finally, we use the polynomials to obtain the minimum stellar masses at the center of redshift bins, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$, which are then used as PRIMUS stellar mass completeness limits.
 
-For our target galaxy population at low redshift we start with 
-the SDSS-{\em GALEX} data. We limit our population within 
-the redshift range $0.0375-0.145$ due to redshift limits later 
-imposed on the volume-limited Environment Defining Population 
-(Section \ref{sec:environment}). To account for targeting 
-completeness of this sample, we use the statistical weight 
-estimates provided by the NYU-VAGC. Then to account for 
-stellar mass incompleteness, we impose a uniform stellar mass 
-limit of $10^9.8 \mathcal{M}_{\odot}$, a limit determined by the 
-stellar mass-to-light ratio completeness of the NYU-VAGC 
-sample given the redshift limits.
+To derive the low redshift portion of our galaxy sample, we start by limiting the SDSS-{\em GALEX} data to objects within $0.0375 < z < 0.145$, a redshift range later imposed on the volume-limited Environment Defining Population (Section \ref{sec:environment}).
+To account for the targeting incompleteness of the SDSS-{\em GALEX} sample, we use the statistical weight estimates provided by the NYU-VAGC catalog.
+Furthermore, to derive a stellar mass complete sample, we impose a uniform stellar mass limit of $10^9.8 \; \mathcal{M}_{\odot}$, which is determined from the mass-to-light ratio completeness limit of the SDSS-{\em GALEX} sample within the imposed redshift limit.
 
-The absolute magnitude ($M_{r}$) versus redshift for the 
-target galaxy population (black squares) is plotted in Figure 
-\ref{fig:targetEDP}. The left-most panel corresponds to the
-target sample derived from the SDSS-{\em GALEX} data and
-the rest correspond to the target sample derived from the 
-PRIMUS data divided in bins with $\Delta z \sim 0.2$.
+The absolute magnitude ($M_{r}$) versus redshift for the galaxy sample (black squares) is plotted in Figure \ref{fig:targetEDP}.
+The left-most panel corresponds to the target sample derived from the SDSS-{\em GALEX} data and the rest correspond to the target sample derived from the PRIMUS data divided in bins with $\Delta z \sim 0.2$.
 
@@
 With the galaxy sample defined in the previous section, we now classify the galaxies as quiescent or star-forming using an evolving cut based on specific star-formation rate utilized in \cite{Moustakas:2013aa} Section 3.2.
-To summarize, this classification method utilizes the star-forming (SF) sequence, which is the correlation between star-formation rate (SFR) and stellar mass in star-forming 
-galaxies observed at least until $z \sim 2$.
-The PRIMUS sample displays a well-defined SF sequence within the redshift range of our target population.
-Using the power-law slope for the SF sequence derived by \cite{Salim:2007aa} (SFR $\propto \mathcal{M}^{0.65}$) and the minimum of the quiescent/star-forming bimodality, 
-determined empirically, we obtain the following equation to classify the target galaxies (Equation 2 in \cite{Moustakas:2013aa}):
+This classification method utilizes the star-forming (SF) sequence, which is the correlation between star-formation rate (SFR) and stellar mass in star-forming galaxies observed at least until $z \sim 2$ (\cite{Noeske:2007aa}).
+The PRIMUS sample displays a well-defined SF sequence within the redshift range of our galaxy sample.
+Then using the power-law slope for the SF sequence derived by \cite{Salim:2007aa} (SFR $\propto \mathcal{M}^{0.65}$) and the minimum of the quiescent/star-forming bimodality, determined empirically, we obtain the following equation to classify the target galaxies (Equation 2 in \cite{Moustakas:2013aa}):
 \begin{equation}
-\label{eq:qsfclass} 
 \rm{log}(\rm{SFR}_{\rm{min}}) = -0.49 + 0.64 \rm{log}(\mathcal{M} - 10) +1.07(z-0.1), 
-\end{equation}
+\end{equation} \label{eq:qsfclass} 
 where $\mathcal{M}$ is the stellar mass of the galaxy.
-If the target galaxy SFR and stellar mass place the galaxy above Equation \ref{eq:qsfclass} we classify it as star-forming; if below, as quiescent (\cite{Moustakas:2013aa} Figure 1.).
+If the target galaxy SFR and stellar mass lies above Equation \ref{eq:qsfclass} we classify it as star-forming; if below, as quiescent (\cite{Moustakas:2013aa} Figure 1.).
 
@@
 \subsection{Galaxy Environment} \label{sec:environment}
-In addition to the quiescent/star-forming classification, in this section, 
-we measure the environment for our target galaxies. We define the 
-environment of a galaxy as the number of neighboring galaxies 
-contained within a fixed aperture centered around it. We use a fixed 
-aperture environment because, as \cite{Muldrew:2012aa} finds in 
-their comparison of different environment definition using simulations, 
-it provides a better probe of the entire halo in comparison to other 
-environment definitions such as nearest neighbor, which provides 
-a better tracer at inter-halo scales. For our aperture, 
-we use a cylinder of dimensions: $R_{\rm{ap}} = 2 \; \rm{Mpc}/h$ and 
-$H_{\rm{ap}} = 25 \; \rm{Mpc}/h$. Though spherical apertures are 
-often used in literature (e.g. \cite{Croton:2005aa}), we use a 
-cylindrical aperture in order to account for the PRIMUS redshift errors 
-and redshift space distortions (i.e. "Finger of God" effect). \cite{Cooper:2005aa} 
-finds that $\pm 1000 \; \rm{km} \rm{s^{-1}}$ optimally reduces the 
-effects of redshift space distortions and PRIMUS $\sigma_z \sim 
-0.0085$ at $z \sim 0.7$, so aperture height of $25 \; \rm{Mpc}/h$ 
-successfully accounts for both of these effects. Furthermore, our 
-choice of cylinder radius was motivated by scale dependence 
-analyses in literature (\cite{Blanton:2006aa}, \cite{Wilman:2010aa}, 
-and \cite{Muldrew:2012aa}), which suggest that galactic properties 
-such as color and quenched fractions are dependent on halo-scale 
-properties such as host dark matter halo mass. \cite{Wilman:2010aa}, 
-which uses environment defined by annuli of different radii, find 
-positive correlation for quenched fraction and color on scales 
-$< 1 \; \rm{Mpc}$ and anti-correlation on scales $> 3 \; \rm{Mpc}$. 
-Our choice of $2 \rm{Mpc}/h$ provides sufficient sample size of 
-galaxies in dense environments, for robust statistics, while 
-tracing galactic properties within the halo scale. When we extend our 
-analysis to cylindrical apertures with $R_{\rm{ap}} = 1 \; \rm{Mpc}/h$, 
-we find that the change in $R_{\rm{ap}}$ does not significantly change 
-our results (difference in $f_{Q} < 0.05$). 
+In addition to dividing the galaxy sample into quiescent and star-forming galaxies, we also classify the galaxies into high and low density environments.In this section, we measure the environment for our galaxy sample.
+We define the environment of a galaxy as the number of neighboring galaxies within a fixed aperture centered around it.
+We use a fixed aperture measurement of environment because, as \cite{Muldrew:2012aa} finds in their comparison of different environment definition using simulations, it provides a better probe of the entire halo in comparison to other environment definitions such as nearest neighbor, which provides a better tracer at inter-halo scales.
+For our aperture, we use a cylinder of dimensions: $R_{\rm{ap}} = 2 \; \rm{Mpc}/h$ and $H_{\rm{ap}} = 25 \; \rm{Mpc}/h$.
+Though spherical apertures are often used in literature (e.g.
+\cite{Croton:2005aa}), we use a cylindrical aperture in order to account for the PRIMUS redshift errors and redshift space distortions (i.e.
+"Finger of God" effect).
+\cite{Cooper:2005aa} finds that $\pm 1000 \; \rm{km} \rm{s^{-1}}$ optimally reduces the effects of redshift space distortions and PRIMUS $\sigma_z \sim 0.0085$ at $z \sim 0.7$, so aperture height of $25 \; \rm{Mpc}/h$ successfully accounts for both of these effects.
+Furthermore, our choice of cylinder radius was motivated by scale dependence analyses in literature (\cite{Blanton:2006aa}, \cite{Wilman:2010aa}, and \cite{Muldrew:2012aa}), which suggest that galactic properties such as color and quenched fractions are dependent on halo-scale properties such as host dark matter halo mass.
+\cite{Wilman:2010aa}, which uses environment defined by annuli of different radii, find positive correlation for quenched fraction and color on scales $< 1 \; \rm{Mpc}$ and anti-correlation on scales $> 3 \; \rm{Mpc}$.
+Our choice of $2 \rm{Mpc}/h$ provides sufficient sample size of galaxies in dense environments, for robust statistics, while tracing galactic properties within the halo scale.
+When we extend our analysis to cylindrical apertures with $R_{\rm{ap}} = 1 \; \rm{Mpc}/h$, we find that the change does not qualitatively change our results (difference in $f_{Q} < 0.05$).
 %Similar fixed aperture methods have also been used in \cite{Croton:2005aa} for galaxies in the 2dF Galaxy Redshift 

### 2014-05-30 qfenv_paper/qf_environment.tex
Major edits on all sections and figure updates

@@
 
-In Section \ref{sec:sample}, we present 
+In Section \ref{sec:sample} we present a brief description of the PRIMUS and SDSS data, our sample construction, and galaxy environment measurements.
+In Section \ref{sec:smf} we examine the stellar mass function evolution for star-forming/quiescent and high/low density environment subsamples.
+In Section \ref{sec:qf_const} compare the quiescent fraction evolution in high and low density environments.
+In Section \ref{sec:summary} we summarize our results and discuss implications of the results on quenching mechanisms.
+
+Throughout the paper we assume cosmology with $\Omega_{m} = 0.3, \Omega_{\Lambda} = 0.7$, and $H_0 = 70 \rm{km} \; \rm{s}^{-1} \rm{Mpc}^{-1}$.
 %%% INCLUDE OUTLINE OF PAPER
@@
 In Section \ref{sec:primus} and Section \ref{sec:sdss} we provide a brief summary of the PRIMUS data and the SDSS data used for our sample selection.
-Then in Section \ref{sec:target} we define our stellar mass complete target galaxy population.
+Then in Section \ref{sec:target} we define our stellar mass complete galaxy sample.
 Afterwards, in Section \ref{sec:sfq}, we classify our sample galaxies as quiescent or star-forming then calculate the environment using a volume-limited {\em Environment Defining Population} in Section \ref{sec:environment}.
@@
 
+While the SDSS-{\em GALEX} data discussed above is derived from SDSS VAGC Data Release 7, since the release of the catalog, there have been significant improvements in the photometry.
+Notably, \cite{Blanton:2011aa} find that the background subtractions in SDSS Data Release 7 has a size dependent bias in the galaxy fluxes, where galaxy fluxes are underestimated by $\sim 1.5$ mag for galaxies with $r_{50} \sim 100 $ arcsec.
+In addition \cite{Bernardi:2013aa} find that the luminosity, and ultimately stellar mass, is underestimated when they are derived from the SDSS \texttt{cmodel} magnitudes in comparison to \texttt{PyMorph} single-Sersic and Sersic-Exponential fits to the surface brightness profiles.
+
+In order to quantify the effects of these photometric underestimations in our analysis, we replace our SDSS fluxes in the $ugriz$ band with $ugriz$ fluxes from the NASA-Sloan Atlas (NSA) catalog, which incorporate the background subtraction improvements presented in \cite{Blanton:2011aa} and are single-Seric fit fluxes rather than the standard SDSS \texttt{cmodel} fluxes.
+Using the ratio of the luminosity derived from the improved photometry over the luminosity derived from the standard SDSS VAGC photometry, we impose a correction on the stellar mass values obtained from \texttt{iSEDfit} assuming a constant mass-to-light ratio.
+This mass correction leads to a significant increase in the stellar mass function for $\mathcal{M} > 10^{11} \mathcal{M}_{\odot}$ that matches the results from \cite{Bernardi:2013aa}.
+However, the effect of the mass correction was negligible for the quiescent fraction evolution results.
+As a result, we do not discuss the issues with photometric measurements any further in this paper.
+The effects of the discussed photometry methods on the luminosity function and stellar mass function will be examined in detail in future work.
+
 \subsection{Galaxy Sample} \label{sec:target} 
@@
 
+With the stellar mass completeness limits above, we have a stellar mass complete sample derived from SDSS-{\em GALEX} and PRIMUS.
+However since our sample is derived from two different surveys, we must account for the disparity in the redshift uncertainty.
+While PRIMUS provides precise spectroscopic redshifts with $\sigma_{z}/(1+z) \approx 0.5 \%$, due to the higher redshift ranges it probes the uncertainties are significantly greater than that of the SDSS-{\em GALEX} redshifts.
+The differences in redshift uncertainties becomes especially important in environment classifications (environment measurements and classification is later discussed in Section \ref{sec:environment}).
+In order to have comparable contamination in environment classifications, we apply PRIMUS redshift uncertainties to our galaxy sample selected from SDSS-{\em GALEX}.
+For each SDSS-{\em GALEX} galaxy in our sample, we compute its $\sigma_z$ by randomly sampling within three standard deviations of a normal distribution where the standard deviation is derived from the $z_{\rm{SDSS}-GALEX}$ of the galaxy, $\sigma = 0.005 (1+z_{\rm{SDSS}- GALEX})$
+
 The absolute magnitude ($M_{r}$) versus redshift for the galaxy sample (black squares) is plotted in Figure \ref{fig:targetEDP}.
-The left-most panel corresponds to the target sample derived from the SDSS-{\em GALEX} data and the rest correspond to the target sample derived from the PRIMUS data divided in bins with $\Delta z \sim 0.2$.
+The left-most panel corresponds to the portion of the sample derived from the SDSS-{\em GALEX} data and the rest correspond to the target sample derived from the PRIMUS data divided in bins with $\Delta z \sim 0.2$.
 
@@
     \leavevmode
-     \epsfig{file=fig_smf_cylr2h25_thresh75_bin0_25_2envbin_primuszerr.eps,height=0.75\textwidth,angle=90}
+     \epsfig{file=fig_smf_cylr2h25_thresh75_bin0_25_lit_2envbin_primuszerr.eps,height=0.75\textwidth,angle=90}
      \caption{Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) target galaxies in 
@@
 \subsection{Galaxy Environment} \label{sec:environment}
-In addition to dividing the galaxy sample into quiescent and star-forming galaxies, we also classify the galaxies into high and low density environments.In this section, we measure the environment for our galaxy sample.
-We define the environment of a galaxy as the number of neighboring galaxies within a fixed aperture centered around it.
-We use a fixed aperture measurement of environment because, as \cite{Muldrew:2012aa} finds in their comparison of different environment definition using simulations, it provides a better probe of the entire halo in comparison to other environment definitions such as nearest neighbor, which provides a better tracer at inter-halo scales.
+With the galaxy sample divided into quiescent and star-forming galaxies above, we now classify the galaxies into high and low density environments.
+In this section, we describe our method for measuring the environment for our galaxy sample.
+First, we define the environment of a galaxy as the number of neighboring {\em Environment Defining Population} galaxies (defined below) within a fixed aperture centered around it.
+We use a fixed aperture measurement of environment because, as \cite{Muldrew:2012aa} finds in their comparison of different environment definition using simulations, it provides a better probe of the entire halo in comparison to other definitions of environment such as nearest neighbor, which provides a better tracer at inter-halo scales.
 For our aperture, we use a cylinder of dimensions: $R_{\rm{ap}} = 2 \; \rm{Mpc}/h$ and $H_{\rm{ap}} = 25 \; \rm{Mpc}/h$.
@@
 "Finger of God" effect).
-\cite{Cooper:2005aa} finds that $\pm 1000 \; \rm{km} \rm{s^{-1}}$ optimally reduces the effects of redshift space distortions and PRIMUS $\sigma_z \sim 0.0085$ at $z \sim 0.7$, so aperture height of $25 \; \rm{Mpc}/h$ successfully accounts for both of these effects.
-Furthermore, our choice of cylinder radius was motivated by scale dependence analyses in literature (\cite{Blanton:2006aa}, \cite{Wilman:2010aa}, and \cite{Muldrew:2012aa}), which suggest that galactic properties such as color and quenched fractions are dependent on halo-scale properties such as host dark matter halo mass.
+\cite{Cooper:2005aa} finds that $\pm 1000 \; \rm{km} \; \rm{s^{-1}}$ optimally reduces the effects of redshift space distortions and the PRIMUS redshift uncertainty at $z \sim 0.7$ corresponds to $\sigma_z < 0.01$, so aperture height of $25 \; \rm{Mpc}/h$ accounts for both of these effects.
+Our choice of cylinder radius was motivated by scale dependence analyses in literature (\cite{Blanton:2006aa}, \cite{Wilman:2010aa}, and \cite{Muldrew:2012aa}), which suggest that galactic properties such as color and quenched fractions are dependent on halo-scale properties such as host dark matter halo mass.
 \cite{Wilman:2010aa}, which uses environment defined by annuli of different radii, find positive correlation for quenched fraction and color on scales $< 1 \; \rm{Mpc}$ and anti-correlation on scales $> 3 \; \rm{Mpc}$.
@@
 
-With proper motivation for the fixed aperture environment definition, 
-we now proceed to measuring the environment for our target galaxies. 
-First, we construct a volume limited {\em Environment Defining 
-Population} (EDP) with absolute magnitude cut-offs ($M_{r}$) at 
-each redshift bin. EDP galaxies within the aperture surrounding each 
-target galaxy are the neighboring galaxies in our definition of 
-environment. The $M_{r}$ cut-offs for the EDP are selected so that 
-the cumulative number density over $M_{r}$ at all redshift bins are 
-equal. Not only does this provide a reasonably comparison of the 
-environment measurements at different redshifts but it also seeks 
-to construct an EDP that contains similar galaxy populations 
-throughout our redshift range (i.e. to account for the progenitor bias 
-in our EDP). As \cite{Behroozi:2013aa} and \cite{Leja:2013aa} find 
-in their analysis of the cumulative number density method, the 
-cumulative number density method, though it does not precisely 
-account for the scatter in mass accretion or galaxy-galaxy mergers, 
-provides a reasonable means to compare galaxy populations over 
-a wide range of cosmic time.
+Using the fixed aperture environment definition, we now measure the environment for our galaxy sample.
+First, we construct a volume limited {\em Environment Defining Population} (EDP) with absolute magnitude cut-offs ($M_{r}$) at redshift bin of $\Delta z \sim 0.2$.
+The $M_{r}$ cut-offs for the EDP are selected such that the cumulative number density over $M_{r}$ for all redshift bins are equal.
+In addition to providing a reasonable comparison of environment measurements for wide redshift range, it also seeks to construct an EDP that contains similar galaxy populations through the redshift range (i.e.
+accounts for the progenitor bias).
+As \cite{Behroozi:2013aa} and \cite{Leja:2013aa} find in their analysis of the cumulative number density method, though it does not precisely account for the scatter in mass accretion or galaxy-galaxy mergers, it provides a reasonable means to compare galaxy populations over a wide range of cosmic time.
 
-In constructing the EDP for the PRIMUS (hereafter PRIMUS EDP) we use the same PRIMUS data as the 
-target galaxies, described in Section \ref{sec:target}. 
+In constructing the EDP for the PRIMUS (hereafter PRIMUS EDP) we use the same PRIMUS data used to select our galaxy sample (described in Section \ref{sec:target}).
 We restrict the PRIMUS galaxies to $0.2 < z < 0.8$ and divide them into bins of $\Delta z = 0.2$.
-Before we consider the cumulative number densities in these bins, we first determine $M_r$ limit for the 
-highest redshift bin ($0.6-0.8$) by examining the $M_{r}$ distribution with bin size $\Delta M_{r} = 0.25$ 
-and select $M_{r,\rm{lim}}$ near the peak of the distribution where bins with $M_{r} > M_{r,\rm{lim}}$ 
-have fewer galaxies than the bin at $M_{r, \rm{lim}}$. 
-We choose $M_{r, \rm{lim}}(0.6 < z < 0.8)$ to be, conservatively, $M_{r} = -20.75$. 
-For the other redshift bins, we impose absolute magnitude limits ($M_{r,\rm{lim}}$) such 
-that the cumulative number density of the bin ordered by $M_{r}$ is equal to the cumulative 
-number density of the highest redshift bin. 
-The cumulative number density calculations accounts for the statistical weights of the galaxies (Section 
-\ref{sec:primus} and \ref{sec:sdss}).
+Before we consider the cumulative number densities in these bins, we first determine the $M_r$ limit for the highest redshift bin ($0.6-0.8$) by examining the $M_{r}$ distribution with bin size $\Delta M_{r} = 0.25$ and select $M_{r,\rm{lim}}$ near the peak of the distribution where bins with $M_{r} > M_{r,\rm{lim}}$ have fewer galaxies than the bin at $M_{r, \rm{lim}}$.
+We conservatively choose $M_{r, \rm{lim}}(0.6 < z < 0.8)$ to be $M_{r} = -20.75$.
+Then for the lower redshift bins, we impose absolute magnitude limits ($M_{r,\rm{lim}}$) such that the cumulative number density of the bin ordered by $M_{r}$ is equal to the cumulative number density of the highest redshift bin at $M_{r, \rm{lim}}(0.6 < z < 0.8) = -20.75$.
+In these cumulative number density calculations, we account for the statistical weights of the galaxies (Section \ref{sec:primus} and \ref{sec:sdss}).
 
-For the SDSS-{\em GALEX} EDP (hereafter SDSS EDP), we do not use the parent data of 
-the SDSS-{\em GALEX} target sample which uses the geometry of the combined angular selection function of the 
-SDSS VAGC and {\em GALEX}. 
-Instead, since FUV, NUV values are not necessary for EDP, we extend the parent data of the SDSS EDP
-to the entire SDSS VAGC, including galaxies outside of the {\em GALEX} window function. 
+For the EDP of the SDSS-{\em GALEX} galaxy sample (hereafter SDSS EDP), we do not use the SDSS-{\em GALEX} parent data which uses the geometry of the combined angular selection function of the SDSS VAGC and {\em GALEX} (Section \ref{sec:sdss}).
+Instead, since FUV, NUV values are not necessary for EDP, we extend the parent data of the SDSS EDP to the entire SDSS VAGC, including galaxies outside of the {\em GALEX} window function.
 Furthermore, we impose a redshift range of $0.0375-0.145$ on the SDSS EDP.
-This redshift range is due to the lack of faint galaxies at $z \sim 0.2$ and the lack of bright galaxies at 
-$z \sim 0.01$ in the SDSS VAGC data.  
-The lower bound for the redshift range was empirically determined by the bright limit and the upper bound 
-by the faint limit of the $M_{r}$ versus redshift distribution. 
-The same fixed cumulative number density method, described above, is used on this SDSS EDP to equate
-the cumulative number density of SDSS EDP to the highest redshift bin of the PRIMUS EDP. 
-Ultimately, we get $M_{r,\rm{lim}} = -20.57$, $-20.73$, $-20.80$ and $-20.95$ for the redshift bins $0.0375-0.145$, 
-$0.2-0.4$, $0.4-0.6$, $0.6-0.8$, respectively.  %%%% PUT NEW VALUES
-These absolute magnitude limits are illustrated in Figure \ref{fig:targetEDP}, which plots $M_{r}$ distribution as 
-a function of redshift for the EDP (red) and the target galaxy sample (black).
+This redshift range was empirically determined to account for the lack of faint galaxies at $z \sim 0.2$ and the lack of bright galaxies at $z \sim 0.01$ in the SDSS VAGC.
+The lower bound was determined by the bright limit and the upper bound by the faint limit of the $M_r$ versus redshift distribution.
+As with the PRIMUS redshift bins, we determine the SDSS EDP $M_{r; \rm{lim}}$ by matching the cumulative number density of the highest redshift bin.
+We get $M_{r,\rm{lim}} = -20.57$, $-20.73$, $-20.80$ and $-20.95$ for the redshift bins $0.0375-0.145$, $0.2-0.4$, $0.4-0.6$, $0.6-0.8$, respectively.
+These absolute magnitude limits are illustrated in Figure \ref{fig:targetEDP}, which show clear $M_r$ cutoffs in the $M_{r}$ distribution versus redshift for the EDP (red circles) on top of the target galaxy sample (black).
 
-Finally with the EDP we measure the environment for each of the target sample galaxies by counting the number
-of EDP galaxies, $n_{\rm{env}}$, with $RA$, $Dec$, and redshift within the aperture surrounding it. 
-$n_{\rm{env}}$ accounts for the statistical weights of the EDP galaxies. 
-%Since we use apertures of different dimensions, we are interested in the relative densitites rather than the actual $n_{env}$ values.
-%Hence, we use the percentage rank of the galaxy environment to quantify overdense environments and underdense environments.
-%More specifically, for each of the redshift bins ($0.2-0.4$, $0.4-0.6$, $0.6-0.8$, and $0.8-1.0$) the $n_{env}$ values for all target galaxies in that bin are listed and assigned a percentage rank based on their position in the list: $n_{env} = 0$ corresponding to $0\%$ and the maximum $n_{env}$ for a target galaxy in the $z$-bin corresponding to $100\%$.
-%Using these percentage ranks, each target galaxy is classified as high-, mid-, or low-environment based on the cut-offs specified in Table \ref{tab:aperture}. 
-%Target sample galaxies are classified as high-environment if its percentage rank lies within the top $20\%$ and as low-environment if its percentage rank lies within the bottom $20\%$. 
-%In Table \ref{tab:aperture}, apertures with radius $1 h^{-1} \rm{Mpc}$ have a low-eneivonrment cut-off of higher than $20\%$.
-%This is because over $20\%$ of target sample galaxies have $n_{env}=0$ such a smaller aperture size.
-%Hence we defined the low-environment percentage rank cut-off to contain all galaxies with $n_{env}=0$. 
-%In order to have a fair comparison for the different $z$-bins when using this aperture, the low-environment cut-off was selected as the lowest cut-off that includes all galaxies with $n_{env}=0$ for all $z$-bin.
-More specific details for the dense and sparse environment cut-offs the various apertures are provided in Table \ref{tab:aperture}.
+Finally we measure the environment for each galaxy in our sampling by counting the number of EDP galaxies, $n_{\rm{env}}$ with $RA$, $Dec$, and $z$ within our cylindrical aperture centered around it.
+Note that $n_{\rm{env}}$ accounts for the statistical weights of the EDP galaxies.
+Once we obtain environment measurements for all the galaxies in our galaxy sample, we classify galaxies with $n_{\rm{env}} < 1$ to be "low" environment density and galaxies with $n_{\rm{env}} > 3$ to be "high" environment densities.
+The high environment cutoff was selected in order to reduce contamination from galaxies in low environment densities while maintaining sufficient
 
@@
         \leavevmode
-        \epsfig{file=fig_qf_cylr2h25_thresh75_bin0_25_primuszerr.eps,height=0.75\textwidth,angle=90}
-        \caption{Evolution of the quiescent fraction $f_{\rm{Q}}$ for target galaxies in spare (left) and dense (rights) environments
-from $z \sim 0.7$ to $z \sim 0.1$.
-$f_{\rm{Q}}$s were calculated using the SMFs computed in Section \ref{sec:smf} and shown in Figure\ref{fig:smf}, as described in text.
+        \epsfig{file=fig_qf_cylr2h25_thresh75_bin0_25_lit_primuszerr.eps,height=0.75\textwidth,angle=90}
+        \caption{Evolution of the quiescent fraction $f_{\rm{Q}}$ for galaxies in low (left) and high (rights) density environments for $z < 0.8$.
+$f_{\rm{Q}}$s were calculated using the SMFs in Figure\ref{fig:smf}, as described in text.
 Darker shading indicates lower redshift.}         \label{fig:qf}
@@
 \subsection{Edge Effects} \label{sec:edgeeffect}
-One of the challenges in obtaining the galaxy environment using a fixed aperture method is accounting for the edges of the survey.
+One of the challenges in obtaining accurate galaxy environments using a fixed aperture method is accounting for the edges of the survey.
 For galaxies located near the edge of the survey, part of the fixed aperture encompassing it will lie outside the survey regions.
-In this case, the $n_{env}$ will only reflect the fraction of the environment within the survey geometry.
+In this case, $n_{env}$ only reflects the fraction of the environment within the survey geometry.
 
-In order to account for these edge effects, we use a Monte Carlo method to impose edge cuts on the target 
-galaxy population. 
-We begin by computing the angular separation, $\theta_{\rm{ap}}$ that corresponds to the radius of the 
-aperture at the redshifts of the target galaxies.
-Then the galaxies are matched to a sample of $N_{\rm{ransack}}=1,000,000$ points with $RA$ and $Dec$
- randomly generated within the window function of the EDP.  
-We refer to this randomly generated redshift-less sample as the "ransack" sample, based on the procedure 
-used to construct them. 
-For each target galaxy, we count the number of ransack points, $n_{\rm{ransack}}$, within $\theta_{\rm{ap}}$
-of the galaxy's $RA$ and $Dec$ value.
-The $n_{\rm{ransack}}$ values are then compared to the expected value:
+To account for these edge effects, we use a Monte Carlo method to impose edge cutoffs on our galaxy sample.
+We begin by computing the angular separation, $\theta_{\rm{ap}}$ that corresponds to the radius of the fixed aperture (used to measure environment) at the redshifts of the galaxies.
+Then we compute the environment, $n_{\rm{ransack}}$, of our galaxy sample with the EDP replaced by a \texttt{ransack} sample of $N_{\rm{ransack}} = 1,000,000$ points with $RA$ and $Dec$ randomly selected within the window function of the EDP.
+We compare the $n_{\rm{ransack}}$ values to the expected value computed based on the angular area of the environment defining aperture and the EDP window function:
 \begin{equation} \label{eq:ransack}
-E[n_{\rm{ransack}}] = \frac{N_{\rm{ransack}}}{A_{\rm{EDP}}}\times {\pi \theta_{\rm{ap}}^2} \times f_{\rm{thresh}} 
+E[n_{\rm{ransack}}] = \frac{N_{\rm{ransack}}}{A_{\rm{EDP}}}\times {\pi \theta_{\rm{ap}}^2} \times f_{\rm{thresh}}. 
 \end{equation} 
-where $A_{\rm{EDP}}$ is the total angular area of the target fields and $f_{\rm{thresh}}$ is the fractional 
-threshold for the edge effect cut-off, which we vary based on $R_{\rm{ap}}$ (listed in Table \ref{tab:aperture}).
-If $n_{\rm{ransack}}$ for a target galaxy is greater than $E[n_{\rm{ransack}}]$ then the target galaxy remains
-in the sample; otherwise, it is discarded from the sample.
-
-%\section{Results}
-%In the section below, we calculate stellar mass functions (SMFs) for the target galaxy population divided into 
-%quiescent/star-forming and dense/sparse environment, Section \ref{sec:smf_const}. We use a non-parametric 
-%$1/V_{\rm{max}}$ estimate of SMFs for the subsamples further divided into redshift bins. Then using these 
-%SMFs, we calculate the quiescent fractions (QFs), Section \ref{sec:qf_const}, 
-%and examine it's evolution over our redshift range.
+$A_{\rm{EDP}}$ is the total angular area of the EDP window function and $f_{\rm{thresh}}$ is the fractional threshold for the edge effect cut-off, which we vary based on $R_{\rm{ap}}$ (listed in Table \ref{tab:aperture}).
+If $n_{\rm{ransack}}$ for a target galaxy is greater than $E[n_{\rm{ransack}}]$ then the galaxy remains in our sample; otherwise, it is discarded.
 
 \section{Stellar Mass Function} \label{sec:smf}
-The target galaxy sample defined above has so far
-been classified into quiescent or star-forming and 
-dense or sparse. We further divide these subsamples 
-into bins of redshift: $0.0375-0.145$, 
-$0.2-0.4$, $0.4-0.6$, and $0.6-0.8$. While the 
-PRIMUS data ranges from $0.2 < z < 1.2$, we only 
-consider galaxies with $ z<0.8$ due to insufficient
-statistics for robust environment measurements at 
-$z > 0.8$. With added redshift bins, we have a
-total of 16 subsamples. We calculate the SMF for 
-each of these 16 subsamples. 
-%% EMPHASIZE THE FACT THAT WE HAVE ENVIRONMENT MEASURES AND A ROBUST ENOUGH DATA TO PROBE 
-%% UP TO REDSHIFT 0.7! THAT WAY WE CAN SEE THE MASS DISTRIBUTION OF VERY SPECIFIC POPULATIONS OF
-%% GALAXIES UP TO A PRETTY HIGH REDSHIFT!
+The target galaxy sample defined above has so far been classified into quiescent or star-forming and low or high density environments.
+We further divide these subsamples into bins of redshift: $0.0375-0.145$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ for a total 16 subsamples.
+In this section, we calculate the SMF for each of these 16 subsamples.
 
-To calculate the SMFs we employ a non-parametric 
-$1/{V_{\rm{max}}}$ estimator commonly used for 
-galaxy luminosity functions and stellar mass functions
-, as done in \cite{Moustakas:2013aa} and discussed 
-in the review \cite{Johnston:2011aa}. The differential 
-SMF is given by the following equation:
+To calculate the SMFs we employ a non-parametric $1/{V_{\rm{max}}}$ estimator commonly used for galaxy luminosity functions and stellar mass functions, as done in \cite{Moustakas:2013aa} and discussed in the review \cite{Johnston:2011aa}.
+The differential SMF is given by the following equation:
 \begin{equation} \label{eq:phi}
@@
 \end{equation}
-The equation above is same as Equation 3. in 
-\cite{Moustakas:2013aa} except for the distinction that 
-we use $V_{\rm{max,avail}}$ instead than $V_{\rm{max}}$, 
-to account for the edge effects of the survey for our
-environment measurements. $w_i$ here represents 
-the statistical weight of each galaxy $i$ and 
-$\Phi(\rm{log}\: \mathcal{M}) \Delta(\rm{log}\: \mathcal{M})$ 
-is the number of galaxies ($N$) per unit volume within the 
-stellar mass range 
-$[\rm{log} \:\mathcal{M}, \rm{log} \:\mathcal{M}+\Delta(\rm{log} \:\mathcal{M})]$.
+The equation above is same as Equation 3.
+in \cite{Moustakas:2013aa} except for $V_{\rm{max,avail}}$ instead than $V_{\rm{max}}$, to account for the edge effects of the survey discussed in Section \ref{sec:edgeeffect}.
+$w_i$ is the statistical weight of galaxy $i$ and $\Phi(\rm{log}\: \mathcal{M}) \Delta(\rm{log}\: \mathcal{M})$ is the number of galaxies ($N$) per unit volume within the stellar mass range $[\rm{log} \:\mathcal{M}, \rm{log} \:\mathcal{M}+\Delta(\rm{log} \:\mathcal{M})]$.
 
-$V_{\rm{max},i}$ is the maximum cosmological volume 
-where it is possible to observe galaxy $i$ given the apparent 
-magnitude limits of the survey. However in Section \ref{sec:edgeeffect} 
-we remove the galaxies that lie on the edge from our sample. 
-In doing so we reduce the maximum cosmological volume 
-where a galaxy can be observed, thereby reducing $V_{\rm{max},i}$.
+$V_{\rm{max},i}$ is the maximum cosmological volume where it is possible to observe galaxy $i$ given the apparent magnitude limits of the survey.
+However in Section \ref{sec:edgeeffect} we remove galaxies that lie on the edge from our sample.
+In doing so we reduce the maximum cosmological volume where a galaxy can be observed, thereby reducing $V_{\rm{max},i}$.
+We introduce the term $V_{\rm{max,avail},i}$ for the $V_{\rm{max},i}$ value that accounts for the survey edge effects.
 
-To calculate $V_{\rm{max,avail},i}$, we generate a sample of 
-points with random $RA$, $Dec$ within the window function of 
-the target sample and $z$ in the redshift range. This is not to be 
-confused with the ransack sample in Section \ref{sec:edgeeffect}. 
-We then impose the same edge cuts we applied to the target 
-galaxy population. At redshift bins of $\Delta z \sim 0.01$, we 
-compute theraction of random points that remain in the bin after 
-the edge cuts: $f_{\rm{edge}}$. Afterwards we apply this factor to 
-compute $V_{\rm{max,avail}} = V_{\rm{max}} \times f_{\rm{edge}}$. 
-The $V_{\rm{max}}$ in the equation above are computed following 
-the method described in \cite{Moustakas:2013aa} Section 4.2 with 
-the same redshift-dependent $K$-correction from observed SED 
-and luminosity evolution model.
+To calculate $V_{\rm{max,avail},i}$, we generate a sample of points with random $RA$, $Dec$ within the window function of our galaxy sample (SDSS-{\em GALEX} window function and the five PRIMUS fields) and random $z$ within the redshift range.
+This is not to be confused with the \texttt{ransack} sample in Section \ref{sec:edgeeffect}.
+We then impose the same edge effect cutoffs we applied to our galaxy sample, using the same \texttt{ransack} environment calculation method from above.
+At redshift bins of $\Delta z \sim 0.01$, we compute the fraction of random points that remain in the bin after the edge effect cutoffs: $f_{\rm{edge}}$.
+We then apply this factor to compute $V_{\rm{max,avail}} = V_{\rm{max}} \times f_{\rm{edge}}$.
+The $V_{\rm{max}}$ in the equation above are computed following the method described in \cite{Moustakas:2013aa} Section 4.2 with the same redshift-dependent $K$-correction from observed SED and luminosity evolution model.
 
-In order to calculate the uncertainty of the SMFs from the sample 
-variance, we use a standard jackknife technique as done in \cite{Moustakas:2013aa}.
-For the PRIMUS target galaxies, we calculate SMFs after excluding 
-one of the five target fields each time. And for the SDSS target galaxies
-we divide the field into a 30 $\times$ 20 rectangular $RA$ and $Dec$ 
-grid and calculate the SMFs after excluding part of the field each time. 
+In order to calculate the uncertainty of the SMFs from the sample variance, we use a standard jackknife technique (as done in \cite{Moustakas:2013aa}).
+For the PRIMUS galaxies, we calculate SMFs after excluding one of the five target fields at a time.
+For the SDSS target galaxies we divide the field into a 12 $\times$ 9 rectangular $RA$ and $Dec$ grid and calculate the SMFs after excluding one grid each time.
 Then using the calculated SMFs we calculate the uncertainty:
@@
 \end{equation} 
-$M$ in this equation is the number of jack knife SMFs in the stellar mass
-bins. $\langle \Phi^j \rangle$ is the mean number density of galaxies 
+$M$ in this equation is the number of jack knife SMFs in the stellar mass bin. $\langle \Phi^j \rangle$ is the mean number density of galaxies 
 in each stellar mass bin for all of the jack knife $\Phi^j$s.
 
-SMFs for 16 target galaxy subsamples classified into quiescent/star-forming (orange/blue)and 
-dense/spare environments are presented in Figure \ref{fig:smf}. The 
-redshift evolution of the SMFs are indicated by a darker shade for lower
-redshifts. The sample variance uncertainties are represented by the 
-width of the SMFs. The environment measurements and classifications
-for Figure \ref{fig:smf} are done using a cylindrical aperture with dimensions,
-$R_{\rm{ap}} = 2 \; \rm{Mpc}/h$ and $H_{\rm{ap}} = 25 \; \rm{Mpc}/h$.
+We present the SMFs for 16 target galaxy subsamples classified into quiescent/star-forming (orange/blue, bottom/top panels) and high/low environment density (left/right panels) in Figure \ref{fig:smf}.
+The redshift evolution of the SMFs in each of these panels are indicated by a darker shade for lower redshift bins.
+The sample variance uncertainties are incorporated in the width of the SMFs.
 
-Examining the SMF evolution from $z \sim 0.7$ to $z \sim 0.1$, 
-we find that in dense environments both the star-forming and quiescent
-SMFs increase at $\mathcal{M}_{*}$ below the knee of mass function 
-($\rm{log}\: \mathcal{M}_{*}/\mathcal{M}_{\odot} < 10.75$ for star-forming; 
-$\rm{log}\: \mathcal{M}_{*}/\mathcal{M}_{\odot} < 11.0$ for quiescent). 
-Meanwhile, at masses above the knee the SMFs for dense environments 
-exhibit little change throughout the redshift range.
+Examining the SMF evolution from $z \sim 0.7$ to $z \sim 0.1$, we find that in high density environments both the star-forming and quiescent SMFs increase at $\mathcal{M}_{*}$ below the knee of mass function ($\rm{log}\: \mathcal{M}_{*}/\mathcal{M}_{\odot} < 10.75$ for star-forming; $\rm{log}\: \mathcal{M}_{*}/\mathcal{M}_{\odot} < 11.0$ for quiescent).
+Meanwhile, at masses above the knee the SMFs for high density environments exhibit little change over the entire cosmic time range.
 
-At sparse environments, the quiescent SMF remains relatively constant 
-for galaxies with $\rm{log}\: \mathcal{M}_{*}/\mathcal{M}_{\odot} < 10.75$.
-At higher stellar masses, however, the SMF decreases notably. Finally 
-the sparse environment star-forming SMF shows a decrease at all 
-stellar mass ranges over the redshift range.
-
-%%% COMPARISON TO OTHER LITERATURE?
+At low density environments, the quiescent SMF remains relatively constant for galaxies with $\rm{log}\: \mathcal{M}_{*}/\mathcal{M}_{\odot} < 10.75$.
+At higher stellar masses, however, the quiescent low density environment SMF decreases notably.
+Finally, the low density environment star-forming SMF shows a decrease at all stellar mass ranges over the redshift range.
+We caution readers and reserve any detailed analysis of the SMF evolution to future work due to the improvements in photometry that significantly alter the lowest redshift bin SMFs mentioned in Section \ref{sec:sdss}.
 
 \section{Quiescent Fraction} \label{sec:qf_const}
-The SMFs calculated in the previous section describe
-the distribution of our galaxy population in stellar mass 
-and reveal the evolution of this distribution
-over comic time. From the SMFs, we 
-compute the quiescent fractions in order to compare the 
-quiescent and the star-forming populations 
-and to quantify the fraction of galaxies that have
-depleted their star-formation. Furthermore, by dividing our 
-galaxy sample using environment measurements into dense
-and sparse samples, we investigate the environment 
-dependence on the quiescent fraction and consequently 
-on environment dependent quenching mechanisms.
+The SMFs calculated in the previous section describe the stellar mass distribution of our galaxy population and reveal the evolution of this distribution over comic time.
+When we compute the quiescent fractions we compare the quiescent and the star-forming populations and quantify the fraction of galaxies that have depleted their star-formation.
+By adding environment classifications to our analysis, we investigate the effects of the environment on the quiescent fraction and its evolution.
+Moreover, by analyzing the quiescent fraction, we are able to reveal the environment dependence of quenching mechanisms.
 
-From the SMF number densities ($\Phi$)
-in the previous section, the quiescent fraction is computed 
-as follows, 
+From the SMF number densities ($\Phi$) the quiescent fraction is computed as follows, 
 \begin{equation}
@@
 \end{equation}
-$\Phi_{Q}$ and $\Phi_{SF}$ are the total number of galaxies 
-per unit volume in stellar mass bin of $\Delta(\rm{log} \: \mathcal{M}) = 0.25$ 
-for the quiescent and star-forming subsamples, respectively 
-(Equation \ref{eq:phi}). We compute $f_{\rm{Q}}$ for dense 
-and spare environments over our redshift range as plotted in
- Figure \ref{fig:qf}, which shows the evolution of $f_{\rm{Q}}$ 
- for dense (right) and sparse (left) environments. As in 
- Figure \ref{fig:smf}, the darker shading represent lower redshifts.
+$\Phi_{Q}$ and $\Phi_{SF}$ are the total number of galaxies per unit volume in stellar mass bin of $\Delta(\rm{log} \: \mathcal{M}) = 0.25$ for the quiescent and star-forming subsamples, respectively (Equation \ref{eq:phi}).
+We compute $f_{\rm{Q}}$ for high and low density environments for all redshift bins as plotted in Figure \ref{fig:qf}, which shows the evolution of $f_{\rm{Q}}$ for high (right) and low (left) density environments.
+As in Figure \ref{fig:smf}, the darker shading represent lower redshift bins.
 
-In both sparse and dense environments, Figure \ref{fig:qf}
-clearly shows an increase in $f_{\rm{Q}}$ with decrease in redshift at all 
-stellar masses. Qualitatively, this $f_{\rm{Q}}$ evolution 
-exhibits a notable mass dependence. More specifically, 
-the $f_{\rm{Q}}$ in sparse environments shows a greater 
-evolution between redshift bins at high masses than at low 
-masses. On the other hand, the $f_{\rm{Q}}$ in dense 
-environments shows a greater evolution between redshift 
-bins at low masses than at high masses.
+In both high and low density environments, Figure \ref{fig:qf} shows a clear increase in $f_{\rm{Q}}$ with decrease in redshift at all stellar masses.
+Qualitatively, this $f_{\rm{Q}}$ evolution exhibits a noticeable mass dependence.
+More specifically, the $f_{\rm{Q}}$ in low density environments shows a greater evolution between redshift bins at high masses than at low masses.
+On the other hand, the $f_{\rm{Q}}$ in high density environments shows a greater evolution between redshift bins at low masses than at high masses.
 
@@
         \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_25_fidmass10_5_primuszerr.eps,height=0.45\textwidth}
-        \caption{The evolution of the quiescent fraction at fiducial mass, $f_{Q}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$, for sparse (square) and dense (circle) environments within the redshift range $z = 0.0 - 0.8$.
+        \caption{The evolution of the quiescent fraction at fiducial mass, $f_{Q}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$, for low (square) and high (circle) density environments within the redshift range $z = 0.0 - 0.8$.
 There is a significant increase in $f_{Q}(\mathcal{M}_{\rm{fid}})$ with decrease in redshift for both environments.
-In addition, over the entire redshift range, $f_{Q}(\mathcal{M}_{\rm{fid}})$ for dense environment is greater than $f_{Q}(\mathcal{M}_{\rm{fid}})$ for lower environment.
+In addition, over the entire redshift range, high density environment $f_{Q}(\mathcal{M}_{\rm{fid}})$ is greater than low density environment $f_{Q}(\mathcal{M}_{\rm{fid}})$.
 However the difference in $f_{Q}(\mathcal{M}_{\rm{fid}})$ for the two environments remains constant throughout suggesting that while the quiescent fraction is higher in dense environments, the evolution of the quiescent fraction is independent of environment.}         \label{fig:qffit}
@@
 %fiducial mass may be 11.0 depending on what we want.
-% fixed slope? Can't do fixed slope if we say there is mass dependence in f_q evolution
 
-While trends are apparent from Figure \ref{fig:qf}, quantitative comparisons of the 
-$f_{\rm{Q}}$ for different environment over redshift is made challenging by the distinct stellar mass 
-completeness limits for each redshift bin.
+While Figure \ref{fig:qf} show the apparent trends, quantitative comparisons of $f_{\rm{Q}}$ for different density environment over redshift is made challenging by the distinct stellar mass limits at each redshift bin.
 In order to quantify the quiescent fraction over the stellar mass complete rate, we fit each $f_{\rm{Q}}$ to a power-law parameterization as a function of stellar mass,
@@
 where $a$ are $b$ are best-fit parameters using {\em MPFIT} (\cite{Markwardt:2009aa}).
-The value $10^{10.5} \: \mathcal{M}_{\odot}$ in the equation represents an empirically selected
-fiducial mass $\mathcal{M}_{\rm{fid}}$ within the stellar mass completeness limits. This fiducial mass 
-serves to highlight and quantify the $f_{\rm{Q}}$ evolution for different redshifts and using $\mathcal{M}_{\rm{fid}} = 10^{11} \mathcal{M}_\odot$ 
-does not notably alter the results. Figure \ref{fig:qffit} shows the evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ 
-for sparse (diamond) and dense (circle) environments.
-For both dense and spare environments, $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ increases as redshift decreases.
-In addition, through the redshift range explored in our analysis, dense environment $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ is significantly greater than the sparse environment $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$.
-However when we compute $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})_{\rm{dense}} - f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})_{\rm{sparse}}$, we find the difference remains constant throughout the redshift range ($ < 0.15$ throughout redshift range).
+The value $10^{10.5} \: \mathcal{M}_{\odot}$ in the equation represents an empirically selected fiducial mass $\mathcal{M}_{\rm{fid}}$ within the stellar mass limits where there is a sufficiently large number of galaxies.
+This fiducial mass serves to highlight and quantify the $f_{\rm{Q}}$ evolution for different redshifts and using $\mathcal{M}_{\rm{fid}} = 10^{11} \mathcal{M}_\odot$ does not notably alter the results.
+Figure \ref{fig:qffit} shows the evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ for low (diamond) and high (circle) density environments.
+For both density environments, $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ increases as redshift decreases similar to the trend we noted qualitatively.
+In addition, throughout the redshift range, high density environment $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ is significantly greater than the low density environment $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$.
+However when we compute $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})_{\rm{high}} - f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})_{\rm{low}}$, we find the difference remains constant throughout the redshift range ($ < 0.15$ throughout redshift range).
 Furthermore, the total evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ show no strong environment dependence.
@@
 
-\section{Summary}
-We have measured the SMFs and QFs using low redshift SDSS-{\em GALEX} galaxies and intermeidate redshift PRIMUS galaxies. 
-Specifically we anlayzed the evolution of the QFs over the redshift range $0.0-1.0$ for galaxies in environment densities (Figure \ref{fig:qf}). 
-We find that there is an expected increase in QF with decrease in the redshift for subsamples in all environment densities.
-More importantly we find that the change in QF over redshift is independent of the environment and remains relatively equal for all environments.
+\section{Summary} \label{sec:summary}
+Using a stellar mass complete galaxy sample, we demonstrate that the quiescent fraction increases over cosmic time for $ z < 0.8$.
+Furthermore with a consistently measured galaxy environment from robust spectroscopic redshift, we demonstrate that the quiescent fraction in high density environments is always greater than the quiescent fraction in low density environments.
+While the difference in quiescent fraction between the two environments is significant, it remains constant throughout the redshift range suggesting that the evolution of the quiescent fraction is independent of environment.
 
@@
 \begin{table*} %Will contain much more information on environments. 
-  \caption{Fixed Cylindrical Aperture Dimensions}
+  \caption{Environment Defining Aperture Dimensions}
   \label{tab:aperture}
@@
     \begin{tabular}{llllll} \hline \hline              
-  Radius (Mpc)          &Height (Mpc)      &$n_{bin}$   &Edgecut &High Env Threshold (galaxies) &Low Env Threshold (galaxies) \\ \hline 
-  1.0 &50 &6 & 80\% & 1.5 & 0.0          \\
-  2.0 &50 &6 & 75\% & 4.0 & 0.0          \\ \hline
-  \multicolumn{6}{l}{}                                             \\       
+  Radius (Mpc)          &Height (Mpc)      & Edge Effect Cutoff &High Env (galaxies) &Low Env (galaxies) \\ \hline 
+  1.0 &50 & 80\% & 1.5 & 0.0          \\
+  2.0 &50 & 75\% & 4.0 & 0.0          \\ \hline
+  \multicolumn{5}{l}{}                                             \\       
     \end{tabular}
@@
 \end{table*}
-
-\subsection{Stellar Mass Function} \label{sec:smf_const}
-\begin{figure*}
-    \begin{center}
-        \leavevmode
-        \epsscale{1.0}
-        \plotone{fig_smf_cylr1h25_thresh80_bin0_25.png}
-        \caption{SMF for $r_{\rm{ap}}=1 \rm{Mpc}$ and $h_{\rm{ap}}=25 \rm{Mpc}$}
-    \end{center}
-\end{figure*}
-
-\begin{figure*}
-    \begin{center}
-        \leavevmode
-        \epsscale{1.0}
-        \plotone{fig_qf_cylr1h25_thresh80_bin0_25.png}
-        \caption{QF for $r_{\rm{ap}}=1 \rm{Mpc}$ and $h_{\rm{ap}}=25 \rm{Mpc}$}
-    \end{center}
-\end{figure*}
-
-\begin{figure*}
-    \begin{center}
-        \leavevmode
-        \epsscale{1.0}
-        \plotone{fig_qffit_cylr1h25_thresh80_bin0_25.png}
-        \caption{QF at fiducial mass for $r_{\rm{ap}}=2 \rm{Mpc}$ and $h_{\rm{ap}}=50 \rm{Mpc}$}
-    \end{center}
-\end{figure*}
-
 \end{document}

### 2014-05-30 qfenv_paper/qf_environment.tex
Minor changes

@@
 Using a stellar mass complete galaxy sample, we demonstrate that the quiescent fraction increases over cosmic time for $ z < 0.8$.
-Furthermore with a consistently measured galaxy environment from robust spectroscopic redshift, we demonstrate that the quiescent fraction in high density environments is always greater than the quiescent fraction in low density environments.
+Furthermore with a consistently measured galaxy environment from robust spectroscopic redshift, we demonstrate that the quiescent fraction in high density environments is always greater than the fraction in low density environments.
 While the difference in quiescent fraction between the two environments is significant, it remains constant throughout the redshift range suggesting that the evolution of the quiescent fraction is independent of environment.

### 2014-06-09 qfenv_paper/qf_environment.tex
Edits

--- 2014-05-29 qfenv_paper/qf_environment.tex
@@
 We classify the galaxies as quiescent or star-forming, based on an evolving specific star formation cut, and as low or high density environments, based on fixed cylindrical aperture environment measurements on a volume-limited {\em Environment Definition Population} (from PRIMUS and SDSS).
-For each of these subsamples, we examine the stellar mass function (SMF) evolution and compute the $f_{\rm{Q}}(\mathcal{M}_{*})$.
-We find that in both low and high density environments the quiescent fraction increases with cosmic time over the probed redshift range.
+We examine the stellar mass function (SMF) evolution for each of our subsamples of quiescent and star-forming galaxies in low and high density environments.
+We find, from the $f_{\rm{Q}}(\mathcal{M}_{*})$ computed from these SMFs, that in both low and high density environments the quiescent fraction increases with cosmic time over the probed redshift range.
 Moreover, the difference between the quiescent fraction in low and high density environments remains constant throughout the redshift range.
@@
 
-In Section \ref{sec:sample}, we present 
-%%% INCLUDE OUTLINE OF PAPER
+\section{Sample Selection} \label{sec:sample}
+In this paper we are interested in quantifying the effects of galaxy environment on the evolution of the quiescent fraction over the redshift range $z \sim 0.8$ to $0.1$.
+In order to do so, we construct a sample with the necessary redshift depth to probe the evolution and robustness to measure galaxy environment.
+For the intermediate redshift range, $0.2 < z < 0.8$ we use galaxies from PRIMUS
 
-\section{Sample Selection} \label{sec:sample}
-We are interested in quantifying the effects of galaxy environment on the evolution of the quiescent fraction over the redshift range $ z < 1.0$.
-For our analysis, we require a sample with sufficient depth to probe the redshift range and robust redshifts to measure galaxy environment.
-PRIMUS, with its $\sim 120,000$ spectroscopic redshifts provides ideal data at intermediate redshifts for our analysis.
-In addition, we anchor our analysis of the intermediate redshift sample with a low redshift sample derived from SDSS.
+In this paper we measure the quiescent fraction evolution over the redshift range $z ~ 0.8$ to $0.1$ for galaxies in different environment densities.
+In order to construct a sample with the necessary redshift depth and robustness to measure galaxy environment, we use galaxies from PRIMUS for intermediate redshifts and galaxies from SDSS for low redshifts.
 
-In Section \ref{sec:primus} and Section \ref{sec:sdss} we provide a brief summary of the PRIMUS data and the SDSS data used for our sample selection.
-Then in Section \ref{sec:target} we define our stellar mass complete target galaxy population.
-Afterwards, in Section \ref{sec:sfq}, we classify our sample galaxies as quiescent or star-forming then calculate the environment using a volume-limited {\em Environment Defining Population} in Section \ref{sec:environment}.
-Finally in Section \ref{sec:edgeeffect}, we correct our galaxy sample and environment measurements for edge effects of the surveys.
+We begin with a brief summary of the PRIMUS data in Section \ref{sec:primus} followed by a summary of the SDSS data in Section \ref{sec:sdss}.
+Then in Section \ref{sec:target} we use this data to define the stellar mass complete target galaxy population.
+Afterwards, in Section~\ref{sec:sfq}, we classify these target galaxies as quiescent or active star-forming galaxies. 
+For each galaxy we obtain the environment using a volume-limited {\em Environment Defining Population} in Section \ref{sec:environment}. 
+Finally in Section \ref{sec:edgeeffect}, we correct the galaxy sample and its environment measurements for the edge effects of the surveys.
 
 \subsection{PRIMUS} \label{sec:primus}
-For our sample at intermediate redshifts we use multiwavelength imaging and spectroscopic redshifts from PRIMUS, a faint galaxy survey with $\sim 120,000$ precise spectroscopic redshifts ($\sigma_z/(1+z) \approx 0.5 \%$) within the range $z \approx 0-1.2$.
+For galaxies at intermediate redshifts we use multiwavelength imaging and spectroscopic redshifts data of PRIMUS, which is a faint galaxy survey with precise spectroscopic redshifts ($\sigma_z/(1+z) \approx 0.5 \%$) for $\sim 120,000$ galaxies within redshifts $z \approx 0-1.2$.
 The survey was conducted using a IMACS spectrograph on a Magellan I Baade $6.5$ m telescope with a slitmask and low dispersion prism.
-For details on the PRIMUS observation methods such as survey design, targeting, and data summary, we refer readers to the survey papers: \cite{Coil:2011aa} and \cite{Cool:2013aa}.
+For further details on the PRIMUS observation methods, including survey design, targeting, and data summary, we refer readers to the survey papers: \cite{Coil:2011aa} and \cite{Cool:2013aa}.
 
-While the PRIMUS survey targeted seven distinct extragalactic deep fields for a total of $\sim 9 \; \rm{deg}^2$, we restrict our sample to five fields that have $GALEX$ and {\em Spitzer}/IRAC imaging (similar to the sample selection in \cite{Moustakas:2013aa}).
-Four of these fields are a part of the {\em Spitzer} Wide-area Infrared Extragalactic Survey (SWIRE\footnote{http://swire.ipac.caltech.edu/swire/swire.html} ): the European Large Area ISO Survey - South $1$ field (ELAIS-S1\footnote{http://dipastro.pd.astro.it/esis}), the Chanddra Deep Field South SWIRE field (CDFS), and the XMM Large Scale Structure Survey field (XMM-LSS).
-The XMM-LSS consists of two separate but spatially adjacent fields: the Subaru/XMM-Newton DEEP Survey fied (XMM-SXDSS\footnote{http://www.naoj.org/cience/SubaruProject/SDS}) and the Canadian-France-Hawaii Telescope Legacy Survey field (XMM-CFHTLS\footnote{http://www.cfht.hawaii.edu/Science/CFHLS}).
-Our fifth and final field is the Cosmic Evolution Survey (COSMOS\footnote{http://cosmos.astro.caltech.edu}) field.
-For all of our fields we have near-UV (NUV) and far-UV (FUV) photometry from the {\em GALEX} Deep Imaging Survey (DIS; \cite{Martin:2005aa}; \cite{Morrissey:2005aa}) as well as ground-based optical and {\em Spitzer}/IRAC mid-infrared photometric catalogs.
-\cite{Moustakas:2013aa} provides detailed descriptions of integrated flux calculations in the photometric bands for each of our fields.
+As done in \cite{Moustakas:2013aa}, we only use fields targeted by PRIMUS with $GALEX$ and {\em Spitzer}/IRAC imaging.
+This restricts us to five fields.
+Four of these fields are a part of the {\em Spitzer} Wide-area Infrared Extragalactic Survey (SWIRE\footnote{http://swire.ipac.caltech.edu/swire/swire.html} ): 
+the European Large Area ISO Survey - South $1$ field (ELAIS-S1\footnote{http://dipastro.pd.astro.it/esis}), the Chanddra Deep Field South SWIRE field (CDFS), 
+and the XMM Large Scale Structure Survey field (XMM-LSS).
+The XMM-LSS consists of two separate but spatially adjacent fields: the Subaru/XMM-Newton DEEP Survey fied (XMM-SXDSS\footnote{http://www.naoj.org/cience/SubaruProject/SDS})
+and the Canadian-France-Hawaii Telescope Legacy Survey field (XMM-CFHTLS\footnote{http://www.cfht.hawaii.edu/Science/CFHLS}).
+In addition to the SWIRE fields we also include the COSMOS\footnote{http://cosmos.astro.caltech.edu} field for a total of five fields.
 
-Finally, from the spectroscopic redshift and broad wavelength photometry we use \texttt{iSEDfit}, a Bayesian SED modeling code, to calculate stellar masses and star formation rates (SFRs) for our sample galaxies.
-\texttt{iSEDfit}, uses the redshift and the observed photometry of the galaxies to determine the statistical likelihood of a large ensemble of generated model SEDs.
-The model SEDs are generated using Flexible Stellar Population Synthesis (FSPS) models (\cite{Conroy:2010aa}) based on \cite{Chabrier:2003aa} IMF, along with other prior parameters beyond the scope of this paper.
-For details we refer readers to Section 4.1 and Appendix A.
-of \cite{Moustakas:2013aa}.
-For the observed photometry, we use the {\em GALEX} FUV and NUV, the two shortest IRAC bands at $3.6$ and $4.5 \mu \rm{m}$ (the two longer-wavelength IRAC channels are excluded because \texttt{iSEDfit} does not model hot dust or polycyclic aromatic hydrocarbons emission lines), and the optical bands.
+In all of the PRIMUS target fields we have near-UV (NUV) and far-UV (FUV) measurements from the {\em GALEX} Deep Imaging Survey (DIS; \cite{Martin:2005aa}; \cite{Morrissey:2005aa}). 
+To minimize contamination from neighboring sources, we use a Bayesian photometric code EM$_{\rm{PHOT}}$ (based on expectation maximization algorithm of \cite{Guillaume:2006aa}). 
+Furthermore, we use ground-based optical and {\em Spitzer}/IRAC mid-infrared photometric catalogs in each of the fields to obtain integrated fluxes in all 
+photometric bands.
+To summarize, the general strategy employed is to use a circular aperture photometry to constrain the shape of the SED and then fixing the overall normalization to 
+a estimate of the total magnitude in the detection band. 
+\cite{Moustakas:2013aa} provides a detailed description of the calculation for each of our target fields.
 
+From the spectroscopic redshift and photometry described above, we use \texttt{iSEDfit} to determine stellar masses, star formation rates (SFRs) and other physical properties
+in a simplified Bayesian framework.
+\texttt{iSEDfit}, which we will only briefly mention in this paper is discussed in detail in Appendix A. of \cite{Moustakas:2013aa}.
+The code uses the redshift and the observed photometry of the galaxies to determine the statistical likelihood of a large ensemble of generated model SEDs. 
+These generated model SEDs depend on population synthesis models and prior parameters.
+In order to derive our fiducial stellar masses and star formation rates, we use the Flexible Stellar Population Synthesis (FSPS) models (\cite{Conroy:2010aa}) based on the \cite{Chabrier:2003aa} IMF. 
+Other prior parameters are listed in Section 4.1 of \cite{Moustakas:2013aa}. 
+The photometric bands we use for the fitting in our PRIMUS data are the {\em GALEX} FUV and NUV, the two shortest IRAC bands at $3.6$ and $4.5 \mu \rm{m}$, and the five optical bands
+(in the COSMOS field, we fit seven optical bands and near-infrared bands, see Section 2.3 of \cite{Moustakas:2013aa}).
+For a more detailed description of the data used in this paper, we refer readers to \cite{Moustakas:2013aa} Section 2 and Section 4.1.
 \begin{table} %Subject to significant change based on the classification of environment
@@
     \begin{tabular}{lllll} \hline \hline              
-      &$z$ &Environment        &Quiescent  &Star-forming  \\ \hline 
+  Survey    &Redshift ($z$) &Density        &Quiescent  &Star-forming  \\ \hline 
   SDSS      &$0.0375-0.145$ &High           &5470                       &4501                           \\
+            &               &Mid            &3614                       &4438                           \\
             &               &Low            &5419                       &8927                           \\
@@
   PRIMUS    &$0.2-0.4$      &High           &322                    &583                           \\
+            &               &Mid            &177                    &403                          \\
             &               &Low            &768                    &2516                           \\
@@
   PRIMUS    &$0.4-0.6$      &High           &350                       &675                           \\
+            &               &Mid            &195                       &405                           \\
             &               &Low            &871                       &2385                           \\
@@
   PRIMUS    &$0.6-0.8$      &High           &347                       &430                           \\
+            &               &Mid            &186                       &327                           \\
             &               &Low            &833                       &1847                           \\
@@
   PRIMUS    &$0.8-1.0$      &High           &136                       &232                           \\
+            &               &Mid            &94                       &163                           \\
             &               &Low            &373                       &810                           \\
@@
         \leavevmode
+        \label{fig:targetEDP}
         \epsscale{1.0}
 	\plotone{fig_EDP_absmag_redshift.png}
-        \caption{Absolute magnitude $M_{r}$ versus redshift for the target galaxy population (black squares) with the Environment Defining Population (red circles) plotted on top.
-Both samples are divided into redshift bins:$z \approx 0.0375-0.145$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ (panels left to right).
-Stellar mass completeness limits are imposed on the target galaxy population (Section \ref{sec:target}) while the $M_{r}$ limits are imposed on the EDP (Section \ref{sec:environment}).
-The lowest redshift bin ($z \approx 0.0375-0.145$; leftmost panel) contain our galaxy sample and EDP selected from SDSS.
-The rest contain galaxies and EDP selected from PRIMUS.} \label{fig:targetEDP}
+        \caption{Absolute magnitude $M_{r}$ versus redshift for the target galaxy population (black) with the 
+Environment Defining Population (red) plotted on top. Both samples are divided into redshift bins:$0.0375-0.145$, 
+$0.2-0.4$, $0.4-0.6$, and $0.6-0.8$. Stellar mass completeness limits are imposed on the target galaxy population (Section \ref{sec:target}) 
+while the $M_{r}$ limits are imposed on the EDP (Section \ref{sec:environment}).}
     \end{center}
@@
 \subsection{SDSS-GALEX} \label{sec:sdss}
-For our low redshift sample, we use spectroscopic redshifts and high fidelity $ugriz$ photometry from the SDSS Data Release 7 (DR7; \cite{Abazajian:2009aa}).
-More specifically we select galaxies from the New York University Value-Added Galaxy Catalog (SDSS VAGC) that satisfy the main sample criterion and have galaxy extinction corrected Petrosian magnitudes $14.5 < r < 17.6$ and spectroscopic redshifts within $0.01 < z < 0.2$ (\cite{Blanton:2005aa}).
-We further narrow down the SDSS VAGC sample to only galaxies with medium depth observations with total exposure time greater than $1 \; \rm{ks}$ from {\em GALEX} Release 6.
-This SDSS-{\em GALEX} sample contains $167,727$ galaxies.
+For galaxies at low redshifts we use the SDSS Data Release 7 (DR7; \cite{Abazajian:2009aa}). 
+From the SDSS DR7 data, which provides high fidelity $ugriz$ photometry and spectroscopic redshift, we specifically use galaxies from the New York University 
+Value-Added Galaxy Catalog that satisfy the main sample criterion and have galaxy extinction corrected Petrosian magnitudes $14.5 < r < 17.6$ 
+and spectroscopic redshits within $0.01<z<0.2$ (\cite{Blanton:2005aa}). 
+Within this sample, we select galaxies with medium depth observations from GALEX. 
+This is done by first retrieving the positions of all {\em GALEX} tiles from GALEX Release 6 with total exposure time greater than $1$ ks and then constructing 
+a joint angular selection function of the SDSS-{\em GALEX} Sample. 
+This results in a final sample of $167,727$ SDSS galaxies with {\em GALEX} imaging.
 
-Using the MAST/CasJobs\footnote{http://galex.stsci.edu/casjobs} interface and a $4''$ diameter search radius, we obtain the NUV and FNU photometry for the SDSS-{\em GALEX} galaxies.
-For optical photometry, we use the $ugriz$ bands from the SDSS \texttt{model} magnitudes scaled to the $r$-band \texttt{cmodel} magnitude.
-These photometric bands are then supplemented with integrated $JHK_s$ magnitudes from the 2MASS Extended Source Catalog (XSC; \cite{Jarrett:2000aa}) and with photometry at $3.4$ and $4.6 \mu \rm{m}$ from the WISE All-Sky Data Release\footnote{http://wise2.ipac.caltech.edu/docs/release/allsky}.
-Further details regarding the SDSS-{\em GALEX} sample photometry can be found in Section 2.4 of \cite{Moustakas:2013aa}.
-As we did with the PRIMUS data above, we use \texttt{iSEDfit} with the above observed photometry to obtain the stellar masses and star formation rates for the SDSS-{\em GALEX} sample.
+For this final sample, we use the MAST/CasJobs\footnote{http://galex.stsci.edu/casjobs} interface and a $4''$ diamater search radius to obtain the NUV and FUV photometry. 
+For the optical photometry we use $ugriz$ bands (from the SDSS \texttt{model} magnitudes) scaled to the $r$-band \texttt{cmodel} magnitude. 
+We supplement the above UV and optical photometry with integrated $JHK_s$ magnitudes from the 2MASS Extended Source Catalog (XSC; \cite{Jarrett:2000aa}) and with photometry at $3.4$ 
+and $4.6 \mu \rm{m}$ from the WISE All-Sky Data Release\footnote{http://wise2.ipac.caltech.edu/docs/release/allsky}. 
+Further details on the photometry of the SDSS data used in this paper is provided in \cite{Moustakas:2013aa} Section 2.4.
 
-\subsection{Galaxy Sample} \label{sec:target} 
-Using the low redshift SDSS-{\em GALEX} and intermediate redshift PRIMUS data described above, in this section, we define our galaxy sample which will be used to compute the SMFs and QFs.
-For PRIMUS, we begin with the selection criteria imposed in \cite{Moustakas:2013aa} for their parent sample.
-We take the statistically complete {\em primary} sample from the PRIMUS data (\cite{Coil:2011aa}) and impose magnitude limits on optical selection bands as specified in \cite{Moustakas:2013aa} Table 1.
-These limits are in different optical selection bands and have distinct values for the five PRIMUS target fields.
-We then exclude stars and broad-line AGN to only select objects spectroscopically classified as galaxies, with high-quality spectroscopic redshifts ($Q \geq 3$).
-In addition we impose a redshift range of $ 0.2 < z < 0.8$ for the PRIMUS galaxy sample, where $ z > 0.2$ is selected due to limitations from sample variance and $ z < 0.8$ is selected due to the lack of sufficient statistics in subsamples defined below.
+To obtain the stellar masses and SFRs for the SDSS data we use \texttt{iSEDfit}, as we did for the PRIMUS data in Section \ref{sec:primus}.  
+However, we use twelve photometric bands: {\em GALEX} FUV and NUV, SDSS $ugriz$, 2MASS $JHK_{s}$, and WISE $3.4$ and $4.6 \mu \rm{m}$.
 
-For the PRIMUS objects that meet the above criteria, we assign statistical weights (described in \cite{Coil:2011aa} and \cite{Cool:2013aa}) in order to correct for targeting incompleteness and redshift failures.
-The statistical weight, $w_i$, for each galaxy is given by
+\subsection{Target Galaxy Sample} \label{sec:target} 
+In this section we will define the target galaxy sample 
+used to compute the SMFs and QFs. The population 
+at $z \sim 0.5$ is derived from PRIMUS data and the 
+population at $z \sim 0.1$ is derived from SDSS-{\em GALEX} 
+data, both described above. For the intermediate redshift 
+population, we begin with the selection criteria imposed 
+in \cite{Moustakas:2013aa} for their parent sample. We 
+take the statistically complete {\em primary} sample from 
+the PRIMUS data (\cite{Coil:2011aa}) and impose magnitude 
+limits on optical selection bands as specified in 
+\cite{Moustakas:2013aa} Table 1. These limits are in different 
+optical selection bands and have distinct values for the 
+five PRIMUS target fields. We then exclude stars and 
+broad-line AGN to only select objects spectroscopically 
+classified as galaxies, with high-quality spectroscopic redshifts 
+($Q \geq 3$) within the redshift range $0.2 - 0.8$. For 
+each of these objects we assign statistical weights (described 
+in \cite{Coil:2011aa} and \cite{Cool:2013aa}) in order to correct 
+for targeting incompleteness and redshift failures. The 
+statistical weight, $w_i$, for each galaxy is given by
 \begin{equation}
@@
 \end{equation}
-Equation (1) in \cite{Moustakas:2013aa}.
-Given that our ultimate interest is in deriving the SMFs and QFs from our sample, we impose stellar mass limits in order to derive a stellar mass complete galaxy sample.
+Equation (1) in \cite{Moustakas:2013aa}. Then to account 
+for stellar mass incompleteness, we impose derived stellar 
+mass limits to the sample.
 
-Stellar mass completeness limits for a magnitude-limited survey such as PRIMUS is a function of redshift, the apparent magnitude limit of the survey, and the typical stellar mass-to-light ratio of galaxies near the flux limit.
-As done in \cite{Moustakas:2013aa}, we follow \cite{Pozzetti:2010aa} to empirically determine the stellar mass completeness limits.
-For each of the target galaxies we compute $\mathcal{M}_{\rm{lim}}$ using $\rm{log} \; \mathcal{M}_{\rm{lim}} = \rm{log} \; \mathcal{M} + 0.4 ( m - m_{\rm{lim}})$, where $\mathcal{M}$ is the stellar mass of the galaxy in $\mathcal{M_{\odot}}$, $\mathcal{M}_{\rm{lim}}$ is the stellar mass of each galaxy if its magnitude was equal to the survey magnitude limit, $m$ is observed apparent magnitude in the selection band, and $m_{\rm{lim}}$ is the magnitude limit for our five fields mentioned above.
-We construct a cumulative distribution of $\mathcal{M}_{\rm{lim}}$ for the $15\%$ faintest galaxies in $\Delta z=0.04$ bins.
-In each of these redshift bins, we calculate the minimum stellar mass that includes $95 \%$ of the galaxies.
-Separately for quiescent and star-forming galaxies, we fit quadratic polynomials to the minimum stellar masses versus redshift (galaxies are classified into star-forming or quiescent in the following section).
-Finally, we use the polynomials to obtain the minimum stellar masses at the center of redshift bins, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$, which are then used as PRIMUS stellar mass completeness limits.
+Stellar mass completeness limits for a magnitude-limited 
+survey such as PRIMUS is a function of redshift, apparent 
+magnitude limit of the survey, and the typical stellar 
+mass-to-light ratio of galaxies near the flux limit. As done 
+in \cite{Moustakas:2013aa}, we follow \cite{Pozzetti:2010aa} 
+to empirically determine the stellar mass completeness limits.
+Briefly, for each of the target galaxies we compute 
+$\mathcal{M}_{\rm{lim}}$ using $\rm{log} \; \mathcal{M}_{\rm{lim}} = \rm{log} \; \mathcal{M} + 0.4 ( m - m_{\rm{lim}})$.
+$\mathcal{M}$ is the stellar mass of the galaxy in $\mathcal{M_{\odot}}$, 
+$\mathcal{M}_{\rm{lim}}$ is the stellar mass of each galaxy 
+if its magnitude was equal to the survey magnitude limit, 
+$m$ is observed apparent magnitude in the selection band, 
+and $m_{\rm{lim}}$ is the magnitude limit for our five 
+fields mentioned above. We construct a cumulative 
+distribution of $\mathcal{M}_{\rm{lim}}$ for the $15\%$ 
+faintest galaxies in $\Delta z=0.04$ bins. In each of these 
+redshift bins, we calculate the minimum stellar mass that 
+includes $95 \%$ of the galaxies. Separately for quiescent 
+and star-forming galaxies, we fit quadratic polynomials to 
+the minimum stellar masses versus redshift (galaxies are 
+classified into star-forming or quiescent in the following section).
+Finally, we use the polynomials to obtain the minimum stellar 
+masses at the center of redshift bins, $0.2-0.4$, $0.4-0.6$, 
+and $0.6-0.8$, which are then used as PRIMUS stellar mass
+completeness limits.
 
-To derive the low redshift portion of our galaxy sample, we start by limiting the SDSS-{\em GALEX} data to objects within $0.0375 < z < 0.145$, a redshift range later imposed on the volume-limited Environment Defining Population (Section \ref{sec:environment}).
-To account for the targeting incompleteness of the SDSS-{\em GALEX} sample, we use the statistical weight estimates provided by the NYU-VAGC catalog.
-Furthermore, to derive a stellar mass complete sample, we impose a uniform stellar mass limit of $10^9.8 \; \mathcal{M}_{\odot}$, which is determined from the mass-to-light ratio completeness limit of the SDSS-{\em GALEX} sample within the imposed redshift limit.
+For our target galaxy population at low redshift we start with 
+the SDSS-{\em GALEX} data. We limit our population within 
+the redshift range $0.0375-0.145$ due to redshift limits later 
+imposed on the volume-limited Environment Defining Population 
+(Section \ref{sec:environment}). To account for targeting 
+completeness of this sample, we use the statistical weight 
+estimates provided by the NYU-VAGC. Then to account for 
+stellar mass incompleteness, we impose a uniform stellar mass 
+limit of $10^9.8 \mathcal{M}_{\odot}$, a limit determined by the 
+stellar mass-to-light ratio completeness of the NYU-VAGC 
+sample given the redshift limits.
 
-The absolute magnitude ($M_{r}$) versus redshift for the galaxy sample (black squares) is plotted in Figure \ref{fig:targetEDP}.
-The left-most panel corresponds to the target sample derived from the SDSS-{\em GALEX} data and the rest correspond to the target sample derived from the PRIMUS data divided in bins with $\Delta z \sim 0.2$.
+The absolute magnitude ($M_{r}$) versus redshift for the 
+target galaxy population (black squares) is plotted in Figure 
+\ref{fig:targetEDP}. The left-most panel corresponds to the
+target sample derived from the SDSS-{\em GALEX} data and
+the rest correspond to the target sample derived from the 
+PRIMUS data divided in bins with $\Delta z \sim 0.2$.
 
@@
 With the galaxy sample defined in the previous section, we now classify the galaxies as quiescent or star-forming using an evolving cut based on specific star-formation rate utilized in \cite{Moustakas:2013aa} Section 3.2.
-This classification method utilizes the star-forming (SF) sequence, which is the correlation between star-formation rate (SFR) and stellar mass in star-forming galaxies observed at least until $z \sim 2$ (\cite{Noeske:2007aa}).
-The PRIMUS sample displays a well-defined SF sequence within the redshift range of our galaxy sample.
-Then using the power-law slope for the SF sequence derived by \cite{Salim:2007aa} (SFR $\propto \mathcal{M}^{0.65}$) and the minimum of the quiescent/star-forming bimodality, determined empirically, we obtain the following equation to classify the target galaxies (Equation 2 in \cite{Moustakas:2013aa}):
+To summarize, this classification method utilizes the star-forming (SF) sequence, which is the correlation between star-formation rate (SFR) and stellar mass in star-forming 
+galaxies observed at least until $z \sim 2$.
+The PRIMUS sample displays a well-defined SF sequence within the redshift range of our target population.
+Using the power-law slope for the SF sequence derived by \cite{Salim:2007aa} (SFR $\propto \mathcal{M}^{0.65}$) and the minimum of the quiescent/star-forming bimodality, 
+determined empirically, we obtain the following equation to classify the target galaxies (Equation 2 in \cite{Moustakas:2013aa}):
 \begin{equation}
+\label{eq:qsfclass} 
 \rm{log}(\rm{SFR}_{\rm{min}}) = -0.49 + 0.64 \rm{log}(\mathcal{M} - 10) +1.07(z-0.1), 
-\end{equation} \label{eq:qsfclass} 
+\end{equation}
 where $\mathcal{M}$ is the stellar mass of the galaxy.
-If the target galaxy SFR and stellar mass lies above Equation \ref{eq:qsfclass} we classify it as star-forming; if below, as quiescent (\cite{Moustakas:2013aa} Figure 1.).
+If the target galaxy SFR and stellar mass place the galaxy above Equation \ref{eq:qsfclass} we classify it as star-forming; if below, as quiescent (\cite{Moustakas:2013aa} Figure 1.).
 
@@
 \subsection{Galaxy Environment} \label{sec:environment}
-In addition to dividing the galaxy sample into quiescent and star-forming galaxies, we also classify the galaxies into high and low density environments.In this section, we measure the environment for our galaxy sample.
-We define the environment of a galaxy as the number of neighboring galaxies within a fixed aperture centered around it.
-We use a fixed aperture measurement of environment because, as \cite{Muldrew:2012aa} finds in their comparison of different environment definition using simulations, it provides a better probe of the entire halo in comparison to other environment definitions such as nearest neighbor, which provides a better tracer at inter-halo scales.
-For our aperture, we use a cylinder of dimensions: $R_{\rm{ap}} = 2 \; \rm{Mpc}/h$ and $H_{\rm{ap}} = 25 \; \rm{Mpc}/h$.
-Though spherical apertures are often used in literature (e.g.
-\cite{Croton:2005aa}), we use a cylindrical aperture in order to account for the PRIMUS redshift errors and redshift space distortions (i.e.
-"Finger of God" effect).
-\cite{Cooper:2005aa} finds that $\pm 1000 \; \rm{km} \rm{s^{-1}}$ optimally reduces the effects of redshift space distortions and PRIMUS $\sigma_z \sim 0.0085$ at $z \sim 0.7$, so aperture height of $25 \; \rm{Mpc}/h$ successfully accounts for both of these effects.
-Furthermore, our choice of cylinder radius was motivated by scale dependence analyses in literature (\cite{Blanton:2006aa}, \cite{Wilman:2010aa}, and \cite{Muldrew:2012aa}), which suggest that galactic properties such as color and quenched fractions are dependent on halo-scale properties such as host dark matter halo mass.
-\cite{Wilman:2010aa}, which uses environment defined by annuli of different radii, find positive correlation for quenched fraction and color on scales $< 1 \; \rm{Mpc}$ and anti-correlation on scales $> 3 \; \rm{Mpc}$.
-Our choice of $2 \rm{Mpc}/h$ provides sufficient sample size of galaxies in dense environments, for robust statistics, while tracing galactic properties within the halo scale.
-When we extend our analysis to cylindrical apertures with $R_{\rm{ap}} = 1 \; \rm{Mpc}/h$, we find that the change does not qualitatively change our results (difference in $f_{Q} < 0.05$).
+In addition to the quiescent/star-forming classification, in this section, 
+we measure the environment for our target galaxies. We define the 
+environment of a galaxy as the number of neighboring galaxies 
+contained within a fixed aperture centered around it. We use a fixed 
+aperture environment because, as \cite{Muldrew:2012aa} finds in 
+their comparison of different environment definition using simulations, 
+it provides a better probe of the entire halo in comparison to other 
+environment definitions such as nearest neighbor, which provides 
+a better tracer at inter-halo scales. For our aperture, 
+we use a cylinder of dimensions: $R_{\rm{ap}} = 2 \; \rm{Mpc}/h$ and 
+$H_{\rm{ap}} = 25 \; \rm{Mpc}/h$. Though spherical apertures are 
+often used in literature (e.g. \cite{Croton:2005aa}), we use a 
+cylindrical aperture in order to account for the PRIMUS redshift errors 
+and redshift space distortions (i.e. "Finger of God" effect). \cite{Cooper:2005aa} 
+finds that $\pm 1000 \; \rm{km} \rm{s^{-1}}$ optimally reduces the 
+effects of redshift space distortions and PRIMUS $\sigma_z \sim 
+0.0085$ at $z \sim 0.7$, so aperture height of $25 \; \rm{Mpc}/h$ 
+successfully accounts for both of these effects. Furthermore, our 
+choice of cylinder radius was motivated by scale dependence 
+analyses in literature (\cite{Blanton:2006aa}, \cite{Wilman:2010aa}, 
+and \cite{Muldrew:2012aa}), which suggest that galactic properties 
+such as color and quenched fractions are dependent on halo-scale 
+properties such as host dark matter halo mass. \cite{Wilman:2010aa}, 
+which uses environment defined by annuli of different radii, find 
+positive correlation for quenched fraction and color on scales 
+$< 1 \; \rm{Mpc}$ and anti-correlation on scales $> 3 \; \rm{Mpc}$. 
+Our choice of $2 \rm{Mpc}/h$ provides sufficient sample size of 
+galaxies in dense environments, for robust statistics, while 
+tracing galactic properties within the halo scale. When we extend our 
+analysis to cylindrical apertures with $R_{\rm{ap}} = 1 \; \rm{Mpc}/h$, 
+we find that the change in $R_{\rm{ap}}$ does not significantly change 
+our results (difference in $f_{Q} < 0.05$). 
 %Similar fixed aperture methods have also been used in \cite{Croton:2005aa} for galaxies in the 2dF Galaxy Redshift 

### 2014-07-10 qfenv_paper/qf_environment.tex
Minor additions.

--- 2014-05-30 qfenv_paper/qf_environment.tex
@@
 \section{Summary} \label{sec:summary}
-Using a stellar mass complete galaxy sample, we demonstrate that the quiescent fraction increases over cosmic time for $ z < 0.8$.
+Using a stellar mass complete galaxy sample, we demonstrate that the quiescent fraction increases over cosmic time for $z < 0.8$.
 Furthermore with a consistently measured galaxy environment from robust spectroscopic redshift, we demonstrate that the quiescent fraction in high density environments is always greater than the fraction in low density environments.
@@
         \item Alberts et al. 2013 
+        \item Tinker et al. 2011
+        \item Geha et al. 2012
     \end{itemize}

### 2014-07-10 qfenv_paper/qf_environment.tex
New figures

@@
         \leavevmode
-        \epsscale{1.0}
-	\plotone{fig_EDP_absmag_redshift.png}
+        \epsscale{1.2}
+	\plotone{fig_edp_sdss_z005_012_primus_z02_10_Mr_redshift.png}
         \caption{Absolute magnitude $M_{r}$ versus redshift for the target galaxy population (black squares) with the Environment Defining Population (red circles) plotted on top.
@@
     \leavevmode
-     \epsfig{file=fig_smf_cylr2h25_thresh75_bin0_25_lit_2envbin_primuszerr.eps,height=0.75\textwidth,angle=90}
+    \epsfig{file=fig_smf_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lit_2envbin_primuszerr.eps,height=0.75\textwidth,angle=90}
      \caption{Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) target galaxies in 
@@
         \leavevmode
-        \epsfig{file=fig_qf_cylr2h25_thresh75_bin0_25_lit_primuszerr.eps,height=0.75\textwidth,angle=90}
+        \epsfig{file=fig_qf_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lit_primuszerr.eps,height=0.75\textwidth,angle=90}
         \caption{Evolution of the quiescent fraction $f_{\rm{Q}}$ for galaxies in low (left) and high (rights) density environments for $z < 0.8$.
@@
         \epsscale{1.0}
-        \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_25_fidmass10_5_primuszerr.eps,height=0.45\textwidth}
+        \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_fidmass10_5_lit_primuszerr.eps,height=0.45\textwidth}
         \caption{The evolution of the quiescent fraction at fiducial mass, $f_{Q}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$, for low (square) and high (circle) density environments within the redshift range $z = 0.0 - 0.8$.
@@
 Using a stellar mass complete galaxy sample, we demonstrate that the quiescent fraction increases over cosmic time for $z < 0.8$.
-Furthermore with a consistently measured galaxy environment from robust spectroscopic redshift, we demonstrate that the quiescent fraction in high density environments is always greater than the fraction in low density environments.
+Furthermore with a consistently measured galaxy environment from robust spectroscopic redshifts, we demonstrate that the quiescent fraction in high density environments is always greater than the fraction in low density environments.
 While the difference in quiescent fraction between the two environments is significant, it remains constant throughout the redshift range suggesting that the evolution of the quiescent fraction is independent of environment.
@@
         \item Alberts et al. 2013 
+        \begin{itemize}
+        		\item SFR, SSFR evolution 
+        \end{itemize}
         \item Tinker et al. 2011
+        \begin{itemize}
+        		\item Properties of galaxies at fixed halo mass are independent of density measured on scales larger than the halo radius
+		\item The dependence of the quenched fraction of galaxies on large scale environment can be explained by the variations of the halo mass function with environment and by disentangling the relative contributions of central and satellite galaxies.
+		\item Different between lowest redshift $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})_{high}$ and $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})_{low}$ is similar to the $\Delta f_{\rm{Q}}$ between low $\rho/\bar{\rho}$ and high $\rho/\bar{\rho}$.
+Except the size of the aperture is very different.
+		\item Compare high environment $f_{\rm{Q}}$ to solid lines in Tinker et al. 2011?
+        \end{itemize}
         \item Geha et al. 2012
+        \begin{itemize}
+        		\item Compare low environment and central galaxies? 
+		\item SDSS bin does not extend to Geha paper
+	\end{itemize}
+	\item Iovino et al. 2010
+	\item Kovac et al. 2013
+	\item Peng et al. 2010
     \end{itemize}

### 2014-07-14 qfenv_paper/qf_environment.tex
New figures and More Discussion

--- 2014-07-10 qfenv_paper/qf_environment.tex
@@
 
+%Compare SMFs at low environment vs high environment and remark that the SMFs are significantly different. With far more mass galaxies in high env than in low env.
+
 \section{Quiescent Fraction} \label{sec:qf_const}
 The SMFs calculated in the previous section describe the stellar mass distribution of our galaxy population and reveal the evolution of this distribution over comic time.
-When we compute the quiescent fractions we compare the quiescent and the star-forming populations and quantify the fraction of galaxies that have depleted their star-formation.
-By adding environment classifications to our analysis, we investigate the effects of the environment on the quiescent fraction and its evolution.
-Moreover, by analyzing the quiescent fraction, we are able to reveal the environment dependence of quenching mechanisms.
+We compare the quiescent and the star-forming populations, using the SMFs, in order to quantify the fraction of galaxies that have depleted their star-formation - the quiescent fraction.
+Adding environment classifications to our analysis, we investigate the effects of environment on the quiescent fraction and its evolution.
+By comparing the quiescent fraction evolution between high and low environments we are able to isolate and quantify the effects of environment dependent external quenching mechanisms as opposed to the internal mechanisms that operate within the galaxy.
 
@@
 
-In both high and low density environments, Figure \ref{fig:qf} shows a clear increase in $f_{\rm{Q}}$ with decrease in redshift at all stellar masses.
-Qualitatively, this $f_{\rm{Q}}$ evolution exhibits a noticeable mass dependence.
-More specifically, the $f_{\rm{Q}}$ in low density environments shows a greater evolution between redshift bins at high masses than at low masses.
-On the other hand, the $f_{\rm{Q}}$ in high density environments shows a greater evolution between redshift bins at low masses than at high masses.
+In both panels, $f_{\rm{Q}}$ increases monotonically as a function of mass for all redshift bins.
+This result is strongly consistent with the well established trend that generally more massive galaxies are more likely to be quenched.
+Furthermore, the results are also consistent with previous measurements of the quiescent fraction.
+Using a group-finding algorithm on the SDSS DR7 catalog, \cite{Tinker:2011aa} presented the relationship between $f_{\rm{Q}}$ and overdensity for galaxies within the mass range $\rm{log} \; \mathcal{M}_{*} = [9.8, 10.1]$.
+The \cite{Tinker:2011aa} $f_{\rm{Q}}$ values at the lowest and highest overdensity values, $f_{\rm{Q}} \sim 0.4$ and $f_{\rm{Q}} \sim 0.6$ respectively, are consistent with our SDSS sample low and high density environment $f_{\rm{Q}}$ at the lowest mass bin $\rm{log} \; \mathcal{M} \sim 10.2$.
+Likewise at higher redshifts, our high and low environment $f_{\rm{Q}}$ results are in general agreement with the $F_{\rm{blue}}$ values for group and isolated galaxies from the zCOSMOS Redshift Survey, as presented in \cite{Iovino:2010aa}.
+
+Though our $f_{\rm{Q}}$ results do not extend beyond masses lower than $10^{9.5} \mathcal{M}_{\odot}$, if we loosely extrapolate the monotonic relation between $f_{\rm{Q}}$ and stellar mass for the low density environment SDSS sample to lower masses, $f_{\rm{Q}}$ extends to $0$ for $\mathcal{M}_{*} < 10^{9.0} \mathcal{M}_{\odot}$.
+This is broadly consistent with the stellar mass threshold ($10^9 \mathcal{M}_{\odot}$) for quenching of field galaxies presented by \cite{Geha:2012aa}.
+
+In addition to its relation with mass, in Figure \ref{fig:qf}, $f_{\rm{Q}}$ increases as redshift decreases for all masses and environments.
+Though restricted by the stellar mass limits, the $f_{\rm{Q}}$ evolution exhibits a slight mass dependence.
+$f_{\rm{Q}}$ in low density environments shows a greater evolution between redshift bins at high masses than at low masses.
+In contrast, the $f_{\rm{Q}}$ in high density environments shows a greater evolution between redshift bins at low masses than at high masses.
+
+%Remark on the difference between low environment and high environment.
 
@@
 \section{Summary} \label{sec:summary}
-Using a stellar mass complete galaxy sample, we demonstrate that the quiescent fraction increases over cosmic time for $z < 0.8$.
-Furthermore with a consistently measured galaxy environment from robust spectroscopic redshift, we demonstrate that the quiescent fraction in high density environments is always greater than the fraction in low density environments.
-While the difference in quiescent fraction between the two environments is significant, it remains constant throughout the redshift range suggesting that the evolution of the quiescent fraction is independent of environment.
+Using a stellar mass complete galaxy sampled derived from SDSS and PRIMUS accompanied by a consistently measured galaxy environment from robust spectroscopic redshifts, we demonstrate that the quiescent fraction increases over cosmic time for $ z < 0.8$, regardless of environment.
+During this epoch the quiescent fraction in high density environments is consistently greater than the quiescent fraction in low density environments.
+Furthermore, when we fit the quiescent fraction at a fiducial mass ($\mathcal{M}_{\rm{fid}}$), we find that the evolution of the quiescent fraction from $z \sim 0.8$ to $z \sim 0.1$ is similar for high and low density environments.
 
-\begin{itemize}
-    \item Comparison to other works. 
-    \begin{itemize}
-        \item Alberts et al. 2013 
-        \item Tinker et al. 2011
-        \item Geha et al. 2012
-    \end{itemize}
-\end{itemize}
+1. SMFs in low and high environment are different for both SF and Q
+2. Mass dependence of QF
+3. redshift dependence of Qf
+4. environment dependence of QF
+5. QF fit
 

### 2014-07-15 qfenv_paper/qf_environment.tex
Changes to QF section
Included preliminary (and poorly written) discussion.

@@
 The target galaxy sample defined above has so far been classified into quiescent or star-forming and low or high density environments.
-We further divide these subsamples into bins of redshift: $0.0375-0.145$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ for a total 16 subsamples.
-In this section, we calculate the SMF for each of these 16 subsamples.
+We further divide these subsamples into redshift bins: $0.0375-0.145$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ for a total 16 subsamples.
+In this section, we calculate the SMF for each of these subsamples.
 
@@
 The equation above is same as Equation 3.
-in \cite{Moustakas:2013aa} except for $V_{\rm{max,avail}}$ instead than $V_{\rm{max}}$, to account for the edge effects of the survey discussed in Section \ref{sec:edgeeffect}.
+in \cite{Moustakas:2013aa} except that we use $V_{\rm{max,avail}}$ instead than $V_{\rm{max}}$, to account for the edge effects of the survey discussed in Section \ref{sec:edgeeffect}.
 $w_i$ is the statistical weight of galaxy $i$ and $\Phi(\rm{log}\: \mathcal{M}) \Delta(\rm{log}\: \mathcal{M})$ is the number of galaxies ($N$) per unit volume within the stellar mass range $[\rm{log} \:\mathcal{M}, \rm{log} \:\mathcal{M}+\Delta(\rm{log} \:\mathcal{M})]$.
@@
 This is not to be confused with the \texttt{ransack} sample in Section \ref{sec:edgeeffect}.
-We then impose the same edge effect cutoffs we applied to our galaxy sample, using the same \texttt{ransack} environment calculation method from above.
+We then impose the same edge effect cutoffs we applied to our galaxy sample, using the same \texttt{ransack} environment calculation method, also discuseed in Section \ref{sec:edgeeffect}.
 At redshift bins of $\Delta z \sim 0.01$, we compute the fraction of random points that remain in the bin after the edge effect cutoffs: $f_{\rm{edge}}$.
@@
 For the SDSS target galaxies we divide the field into a 12 $\times$ 9 rectangular $RA$ and $Dec$ grid and calculate the SMFs after excluding one grid each time.
-Then using the calculated SMFs we calculate the uncertainty:
+Using the calculated SMFs we calculate the uncertainty:
 \begin{equation}
@@
 The SMFs calculated in the previous section describe the stellar mass distribution of our galaxy population and reveal the evolution of this distribution over comic time.
-We compare the quiescent and the star-forming populations, using the SMFs, in order to quantify the fraction of galaxies that have depleted their star-formation - the quiescent fraction.
-Adding environment classifications to our analysis, we investigate the effects of environment on the quiescent fraction and its evolution.
-By comparing the quiescent fraction evolution between high and low environments we are able to isolate and quantify the effects of environment dependent external quenching mechanisms as opposed to the internal mechanisms that operate within the galaxy.
+We compare the quiescent and the star-forming populations, using the SMFs, and quantify the fraction of galaxies that have depleted their star-formation - the quiescent fraction.
+Adding environment classification to our analysis, we investigate the effects of environment on the quiescent fraction and its evolution.
+By comparing the evolution between high and low environments we are able to isolate and quantify the effects of environment dependent external quenching mechanisms as opposed to the internal mechanisms that operate within the galaxy.
 
@@
 
-In both panels, $f_{\rm{Q}}$ increases monotonically as a function of mass for all redshift bins.
-This result is strongly consistent with the well established trend that generally more massive galaxies are more likely to be quenched.
+In both panels, the $f_{\rm{Q}}$s reveal a clear mass dependence where $f_{\mr{Q}}$ increases monotonically as a function of mass for all redshift bins.
+This result strongly supports the well established trend that more massive galaxies are more likely to be quenched.
+In addition, $f_{\rm{Q}}$ increases as redshift decreases at all masses and in both environments, suggesting that over cosmic time an increasing portion of galaxies have ceased their star-formation and have become quiescent galaxies.
+
+While both high and low density environment $f_{\rm{Q}}$ exhibit a similar mass dependence and increase over cosmic time, for each redshift bin there is a significant difference where $f_{\rm{Q}}(\mathcal{M})$ in high density environments is greater than $f_{\rm{Q}}(\mathcal{M})$.
+In other words, galaxies in high density environments are more likely to be quenched than galaxies in low density environments.This reflects the long observed morphology-density relation (\cite{dresseler84a}; \cite{desai07a}) as well as the color-density relation (citation).
+In addition, our $f_{Q}$ evolution over cosmic time also agrees with recent measurements of SFR evolution over cosmic time in \cite{Alberts:2014aa} and the SSFR-density relation in \cite{cooper08a}.
+
+Although a clear comparison between redshift bins is limited due to the stellar mass completeness limits, Figure \ref{fig:qf} illustrates a slight mass dependence in the $f_{\rm{Q}}$ evolution.
+$f_{\rm{Q}}$ in low density environments shows a greater evolution between redshift bins at high masses than at low masses.
+In contrast, the $f_{\rm{Q}}$ in high density environments shows a greater evolution between redshift bins at low masses than at high masses.
+
 Furthermore, the results are also consistent with previous measurements of the quiescent fraction.
 Using a group-finding algorithm on the SDSS DR7 catalog, \cite{Tinker:2011aa} presented the relationship between $f_{\rm{Q}}$ and overdensity for galaxies within the mass range $\rm{log} \; \mathcal{M}_{*} = [9.8, 10.1]$.
-The \cite{Tinker:2011aa} $f_{\rm{Q}}$ values at the lowest and highest overdensity values, $f_{\rm{Q}} \sim 0.4$ and $f_{\rm{Q}} \sim 0.6$ respectively, are consistent with our SDSS sample low and high density environment $f_{\rm{Q}}$ at the lowest mass bin $\rm{log} \; \mathcal{M} \sim 10.2$.
+The \cite{Tinker:2011aa} $f_{\rm{Q}}$ values at the lowest and highest overdensities, $f_{\rm{Q}} \sim 0.4, \sim 0.6$ respectively, are consistent with our SDSS low and high density environment $f_{\rm{Q}}$ at the lowest mass bin $\rm{log} \; \mathcal{M}_{*} \sim 10.2$.
 Likewise at higher redshifts, our high and low environment $f_{\rm{Q}}$ results are in general agreement with the $F_{\rm{blue}}$ values for group and isolated galaxies from the zCOSMOS Redshift Survey, as presented in \cite{Iovino:2010aa}.
+\cite{Iovino:2010aa} constructs a mass complete sample of isolated galaxies and group galaxies from the \cite{Knobel:2009aa} Group Catalog and compares $F_{\rm{blue}}$ for the two environments.
 
@@
 This is broadly consistent with the stellar mass threshold ($10^9 \mathcal{M}_{\odot}$) for quenching of field galaxies presented by \cite{Geha:2012aa}.
-
-In addition to its relation with mass, in Figure \ref{fig:qf}, $f_{\rm{Q}}$ increases as redshift decreases for all masses and environments.
-Though restricted by the stellar mass limits, the $f_{\rm{Q}}$ evolution exhibits a slight mass dependence.
-$f_{\rm{Q}}$ in low density environments shows a greater evolution between redshift bins at high masses than at low masses.
-In contrast, the $f_{\rm{Q}}$ in high density environments shows a greater evolution between redshift bins at low masses than at high masses.
 

### 2014-07-17 qfenv_paper/qf_environment.tex
More edits on QF Section

--- 2014-07-14 qfenv_paper/qf_environment.tex
@@
 
-%Compare SMFs at low environment vs high environment and remark that the SMFs are significantly different. With far more mass galaxies in high env than in low env.
+%Compare SMFs at low environment vs high environment and remark that the SMFs are significantly different. 
+%Remark on the clear mass-density relation: more massive galaxies in high environment 
+% Compare to Bolzonella et al. 2010 and perhaps even Bundy et al. 2006 results
+% Agree with previous works on mass segregation results from VVDS, DEEP2, and etc.
 
 \section{Quiescent Fraction} \label{sec:qf_const}
-The SMFs calculated in the previous section describe the stellar mass distribution of our galaxy population and reveal the evolution of this distribution over comic time.
-We compare the quiescent and the star-forming populations, using the SMFs, in order to quantify the fraction of galaxies that have depleted their star-formation - the quiescent fraction.
-Adding environment classifications to our analysis, we investigate the effects of environment on the quiescent fraction and its evolution.
-By comparing the quiescent fraction evolution between high and low environments we are able to isolate and quantify the effects of environment dependent external quenching mechanisms as opposed to the internal mechanisms that operate within the galaxy.
+The SMFs calculated in the previous section illustrate the stellar mass distribution of our galaxy population and its evolution over comic time.
+In this section, using the SMFs of our subsamples, we compare the quiescent and the star-forming populations using the quiescent fraction - the fraction of galaxies that have depleted their star-formation.
+With the sufficient statistics available from SDSS and PRIMUS, we evaluate the quiescent fraction in bins of stellar mass and redshift for low and high density environments.
+By analyzing the quiescent fraction with respect to mass, redshift, and environment we are able to compare the redshift evolution of the quiescent fraction for a complete mass range in our environments.
+Through this comparison we reveal the subtle effects of environment in quenching star formation that are often obscured by the underlying correlations among galactic properties such as color-mass and mass-density relations (\cite{Cooper:2010aa}).
+Furthermore by quantifying the environmental effects of star-formation quenching, we are able to provide constraints on the various proposed quenching mechanisms that operate on the scale of our environment measure, such as strangulation and ram-pressure stripping (CITECITE).
 
-From the SMF number densities ($\Phi$) the quiescent fraction is computed as follows, 
+From the SMF number densities ($\Phi$) computed in the previous section, the quiescent fraction is computed as follows, 
 \begin{equation}
@@
 
-%Remark on the difference between low environment and high environment.
+% color-mass relation, mass-density relation, color-density relation, SFR-density relation, SSFR-density relation,
 
+% SDSS QF matches with SDSS QF of Tinker et al.
+2010 who uses a group catalog.
+The PRIMUS QF values match reasonably well with zCOSMOS 10k in Iovino et al.
+2010 and zCOSMOS 20k in Kovac et al.
+2014, once disparities between color classification and SFR classifications are taken into account.
+
+% The mass dependence of each subsample QF: reflects the color-mass relation and the morphology-mass relation
+% The "color-mass" relation holds for both low and high environment galaxies.
+While others in literature (Cucciati et al.
+2010) found that the mass dependence was less apparent in high environment, this does not hold true for the SDSS and PRIMUS data.
+Although this could be due to the contamination in our environment measurements since there are large redshift errors.
+% Emphasize that due to the limited mass range from mass completeness limits, the conclusions on mass dependence should be taken with a grain of salt. 
+% The redshift evolution of the QF in each 
 \begin{figure}

### 2014-07-21 qfenv_paper/qf_environment.tex
Major changes to QF section

@@
 With the sufficient statistics available from SDSS and PRIMUS, we evaluate the quiescent fraction in bins of stellar mass and redshift for low and high density environments.
-By analyzing the quiescent fraction with respect to mass, redshift, and environment we are able to compare the redshift evolution of the quiescent fraction for a complete mass range in our environments.
-Through this comparison we reveal the subtle effects of environment in quenching star formation that are often obscured by the underlying correlations among galactic properties such as color-mass and mass-density relations (\cite{Cooper:2010aa}).
-Furthermore by quantifying the environmental effects of star-formation quenching, we are able to provide constraints on the various proposed quenching mechanisms that operate on the scale of our environment measure, such as strangulation and ram-pressure stripping (CITECITE).
+More specifically, by analyzing the quiescent fraction with respect to mass, redshift, and environment we are able to compare the quiescent fraction evolution over redshift for galaxies in low and high density environments.
+Through this comparison we reveal the subtle environmental effects in quenching star formation that are often obscured by the underlying correlations among galactic properties such as color-mass and mass-density relations (\cite{Cooper:2010aa}).
+Furthermore by quantifying the environmental effects of star-formation quenching, we are able to provide constraints on the various proposed quenching mechanisms, such as strangulation and ram-pressure stripping (CITECITE), that operate on the scale of our environment measure.
 
@@
 
-In both panels, $f_{\rm{Q}}$ increases monotonically as a function of mass for all redshift bins.
-This result is strongly consistent with the well established trend that generally more massive galaxies are more likely to be quenched.
-Furthermore, the results are also consistent with previous measurements of the quiescent fraction.
-Using a group-finding algorithm on the SDSS DR7 catalog, \cite{Tinker:2011aa} presented the relationship between $f_{\rm{Q}}$ and overdensity for galaxies within the mass range $\rm{log} \; \mathcal{M}_{*} = [9.8, 10.1]$.
+Most noticeably, $f_{\rm{Q}}$ increases monotonically as a function of mass regardless of redshift bin or environment.
+In other words, for all subsamples, galaxies in higher mass bins are more likely to have quenched its star-formation.
+With the roughly linear correlation between galaxy SFR to galaxy color and morphology, we find that this trend reflects the well established color-mass and morphology-mass relations: more massive galaxies are more likely to be red or early-type (\cite{Blanton:2009aa}).
+
+Focusing on the redshift evolution of $f_{\rm{Q}}$, we find that for both environments and over our mass range $f_{\rm{Q}}$ increases as redshift decreases.
+For high density environment, this is analogous to the Butcher-Omeler Effect (\cite{Butcher:1984aa}), which states that galaxy populations in groups or clusters have higher $f_{\rm{blue}}$, or lower $f_{\rm{Q}}$, at higher redshift.
+For all environments a larger portion of our galaxy population has quenched its star-formation over time.
+Coupled with the decline of SFR in the star-forming population (\cite{Noeske:2007aa}; \cite{cooper08a}), our results strongly support the observed decline of global star-formation in the universe (\cite{hopkins06a}).
+
+Also, by comparing the stellar masses at which $f_{\rm{Q}} = 0.5$ for each subsample, we find that this mass decreases over cosmic time.
+This corresponds to the well-known mass-downsizing pattern (\cite{bundy06a}).
+Furthermore, the mass-downsizing trend observed in each of our environment subsample is generally consistent with the trend observed in zCOSMOS Redshift Survey for isolated and group galaxies (\cite{Iovino:2010aa}).
+
+We compare our $f_{\rm{Q}}$ results to previous $f_{\rm{Q}}$ or $f_{\rm{red}}$ measurements for analogous environment classifications in literature.
+For our lowest redshift bin, we find that our $f_{\rm{Q}}$ values for low and high environments are consistent with previous $f_{\rm{Q}}/f_{\rm{red}}$ measurements for SDSS galaxies as a function of environment.
+For example, \cite{Tinker:2011aa}, using a group-finding algorithm on the SDSS DR7, presents the relationship between $f_{\rm{Q}}$ and overdensity for galaxies within the mass range $\rm{log} \; \mathcal{M}_{*} = [9.8, 10.1]$.
 The \cite{Tinker:2011aa} $f_{\rm{Q}}$ values at the lowest and highest overdensity values, $f_{\rm{Q}} \sim 0.4$ and $f_{\rm{Q}} \sim 0.6$ respectively, are consistent with our SDSS sample low and high density environment $f_{\rm{Q}}$ at the lowest mass bin $\rm{log} \; \mathcal{M} \sim 10.2$.
-Likewise at higher redshifts, our high and low environment $f_{\rm{Q}}$ results are in general agreement with the $F_{\rm{blue}}$ values for group and isolated galaxies from the zCOSMOS Redshift Survey, as presented in \cite{Iovino:2010aa}.
+At higher mass ranges, our $f_{\rm{Q}}$ results for low and high density environments are consistent with \cite{Baldry:2006aa} $f_{\rm{red}}$ values for lowest and highest environment density, which they measure using projected neighbor density.
 
-Though our $f_{\rm{Q}}$ results do not extend beyond masses lower than $10^{9.5} \mathcal{M}_{\odot}$, if we loosely extrapolate the monotonic relation between $f_{\rm{Q}}$ and stellar mass for the low density environment SDSS sample to lower masses, $f_{\rm{Q}}$ extends to $0$ for $\mathcal{M}_{*} < 10^{9.0} \mathcal{M}_{\odot}$.
-This is broadly consistent with the stellar mass threshold ($10^9 \mathcal{M}_{\odot}$) for quenching of field galaxies presented by \cite{Geha:2012aa}.
+At higher redshifts, we compare our PRIMUS $f_{\rm{Q}}$ results to the $f_{\rm{red}}$ (or $1-f_{\rm{blue}}$) results from the zCOSMOS Redshift Survey (\cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, \cite{Kovac:2014aa}), which roughly covers the same redshift range as PRIMUS.
+\cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, and \cite{Kovac:2014aa} using a mass-complete galaxy sample derived from zCOSMOS and environment determined using a group catalog, 3D local density contrast, and overdensity respectively, compare $f_{\rm{red}}$ for different environments.
 
-In addition to its relation with mass, in Figure \ref{fig:qf}, $f_{\rm{Q}}$ increases as redshift decreases for all masses and environments.
-Though restricted by the stellar mass limits, the $f_{\rm{Q}}$ evolution exhibits a slight mass dependence.
-$f_{\rm{Q}}$ in low density environments shows a greater evolution between redshift bins at high masses than at low masses.
-In contrast, the $f_{\rm{Q}}$ in high density environments shows a greater evolution between redshift bins at low masses than at high masses.
+The $f_{\rm{blue}}$ values for group and isolated galaxies from \cite{Iovino:2010aa} are generally inconsistent with our $f_{\rm{Q}}$ values in high and low density environments.
+Similarly, the $f_{\rm{red}}$ values for high and low overdensities from \cite{Kovac:2014aa} disagree with our $f_{\rm{Q}}$ values in high and low density environments.
 
-% color-mass relation, mass-density relation, color-density relation, SFR-density relation, SSFR-density relation,
+Also, the zCOSMOS results, which are mostly consistent with each other, indicate that the $f_{\rm{red}}$ values in high density environments are greater than in low density environments.
+The same trend is observed in the PRIMUS results and will be discussed in detail later in the section.
+Furthermore, \cite{Iovino:2010aa} in their analysis finds clear mass dependence in the $f_{\rm{red}}$ evolution where $f_{\rm{red}}$ evolves by a greater amount for lower mass galaxies in both group and isolated galaxies.
 
-% SDSS QF matches with SDSS QF of Tinker et al.
-2010 who uses a group catalog.
-The PRIMUS QF values match reasonably well with zCOSMOS 10k in Iovino et al.
-2010 and zCOSMOS 20k in Kovac et al.
-2014, once disparities between color classification and SFR classifications are taken into account.
+ %explain the zCOSMOS results briefly. Mention the general discrepancies while highlighting the large statistics offered by PRIMUS
+%If we impose the f_Q vs f_red discrepancies plotting in Kovac et al.
+2014, can we explain the discrepancies between Iovino et al.
+2010 and PRIMUS?
+Is Iovino et al.
+2010 and Kovac et al.
+2014 consistent with one another?
+%Note the clear mass dependence in essentially all the zCOSMOS results 
+%color-density relation?
 
-% The mass dependence of each subsample QF: reflects the color-mass relation and the morphology-mass relation
-% The "color-mass" relation holds for both low and high environment galaxies.
-While others in literature (Cucciati et al.
-2010) found that the mass dependence was less apparent in high environment, this does not hold true for the SDSS and PRIMUS data.
-Although this could be due to the contamination in our environment measurements since there are large redshift errors.
-% Emphasize that due to the limited mass range from mass completeness limits, the conclusions on mass dependence should be taken with a grain of salt. 
-% The redshift evolution of the QF in each 
+In contrast to the zCOSMOS results, for each panels in Figure \ref{fig:qf}, qualitatively, we see little mass dependence on the $f_{\rm{Q}}$ evolution.
+However, due to the distinct stellar mass completeness limits imposed at each redshift bin of our sample, we require a more quantitative comparison of the $f_{\rm{Q}}$ redshift evolution.
+Consequently, we fit each subsample $f_{\rm{Q}}$ to a power-law parameterization as a function of stellar mass,
+
 \begin{figure}
@@
 
-While Figure \ref{fig:qf} show the apparent trends, quantitative comparisons of $f_{\rm{Q}}$ for different density environment over redshift is made challenging by the distinct stellar mass limits at each redshift bin.
-In order to quantify the quiescent fraction over the stellar mass complete rate, we fit each $f_{\rm{Q}}$ to a power-law parameterization as a function of stellar mass,
 \begin{equation} 
@@
 The value $10^{10.5} \: \mathcal{M}_{\odot}$ in the equation represents an empirically selected fiducial mass $\mathcal{M}_{\rm{fid}}$ within the stellar mass limits where there is a sufficiently large number of galaxies.
-This fiducial mass serves to highlight and quantify the $f_{\rm{Q}}$ evolution for different redshifts and using $\mathcal{M}_{\rm{fid}} = 10^{11} \mathcal{M}_\odot$ does not notably alter the results.
+This fiducial mass serves to highlight and quantify the $f_{\rm{Q}}$ evolution for different redshifts.
 Figure \ref{fig:qffit} shows the evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ for low (diamond) and high (circle) density environments.
-For both density environments, $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ increases as redshift decreases similar to the trend we noted qualitatively.
-In addition, throughout the redshift range, high density environment $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ is significantly greater than the low density environment $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$.
-However when we compute $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})_{\rm{high}} - f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})_{\rm{low}}$, we find the difference remains constant throughout the redshift range ($ < 0.15$ throughout redshift range).
-Furthermore, the total evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ show no strong environment dependence.
+
+The same fitting was performed using $\mathcal{M}_{\rm{fid}} = 10^{11} \mathcal{M}_\odot$; however, aside from a general shift in all $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ values by roughly $\sim 0.2$, we observe the same evolutionary trends.
+
+From Figure \ref{fig:qffit}, we note that for both environments $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ increases as redshift decreases.
+This highlights the general increase of $f_{\rm{Q}}(\mathcal{M})$ as redshift decreases noted earlier.
+More importantly it quantifies the total evolution of $f_{\rm{Q}}$ since $z \sim 0.8$ for both low and high density environments.
+Remarkably, the total evolution of $f_{\rm{Q}}$ remains constant for both environments.
+In other words, the total evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ show no strong environment dependence.
+
+%Discuss how this is not due to contamination by environment classifications.
+
+In addition, throughout the redshift range, high density environment has a significantly greater $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ than the low density environment.
+
+%PRIMUS results are roughly in agreement with zCOSMOS 10k (Iovino et al.
+2010) and zCOMOS 20k (Kovac et al.
+2014) once the difference between f_red and f_Q are taken into account.
+Discuss some general specific values.
+% Previous results, primarily from zCOSMOS 10k and 20k, have found a significant mass dependence in the f_{Q} evolution with f_{Q} increasing significantly more over redshift at lower masses.
+At higher masses these results find little evolution in f_Q.
+Though our f_{Q} values are in good agreement with these results, for the mass ranges probed in our analysis, we find little mass dependence in the f_Q evolution.
+
+% color-mass relation, mass-density relation, color-density relation, SFR-density relation, SSFR-density relation,
+
+% The "color-mass" relation holds for both low and high environment galaxies.
+While others in literature (Cucciati et al.
+2010) found that the mass dependence was less apparent in high environment, this does not hold true for the SDSS and PRIMUS data.
+Although this could be due to the contamination in our environment measurements since there are large redshift errors.
+% Emphasize that due to the limited mass range from mass completeness limits, the conclusions on mass dependence should be taken with a grain of salt. 
+% The redshift evolution of the QF in each
 

### 2014-07-22 qfenv_paper/qf_environment.tex
more qf section

@@
 
-%Section heading
+%Section `ing
 \section{Introduction}
@@
 The SMFs calculated in the previous section illustrate the stellar mass distribution of our galaxy population and its evolution over comic time.
-In this section, using the SMFs of our subsamples, we compare the quiescent and the star-forming populations using the quiescent fraction - the fraction of galaxies that have depleted their star-formation.
+In this section, using the SMFs of our subsamples, we compare the quiescent and the star-forming populations by calculating quiescent fraction - the fraction of galaxies that have depleted their star-formation.
 With the sufficient statistics available from SDSS and PRIMUS, we evaluate the quiescent fraction in bins of stellar mass and redshift for low and high density environments.
@@
 
-Most noticeably, $f_{\rm{Q}}$ increases monotonically as a function of mass regardless of redshift bin or environment.
+Most noticeably, $f_{\rm{Q}}$ increases monotonically as a function of mass at all redshift bin and environment.
 In other words, for all subsamples, galaxies in higher mass bins are more likely to have quenched its star-formation.
-With the roughly linear correlation between galaxy SFR to galaxy color and morphology, we find that this trend reflects the well established color-mass and morphology-mass relations: more massive galaxies are more likely to be red or early-type (\cite{Blanton:2009aa}).
+With the roughly linear correlation between galaxy SFR to galaxy color and morphology, we find that this trend reflects the well established color-mass and morphology-mass relations: more massive galaxies are more likely to be red or early-type (\cite{blanton09a}).
 
@@
 For all environments a larger portion of our galaxy population has quenched its star-formation over time.
-Coupled with the decline of SFR in the star-forming population (\cite{Noeske:2007aa}; \cite{cooper08a}), our results strongly support the observed decline of global star-formation in the universe (\cite{hopkins06a}).
+Coupled with the decline of SFR in the star-forming population (\cite{Noeske:2007aa}; \cite{cooper08a}), our results strongly agree with the observed decline of global star-formation in the universe (\cite{hopkins06a}).
 
-Also, by comparing the stellar masses at which $f_{\rm{Q}} = 0.5$ for each subsample, we find that this mass decreases over cosmic time.
-This corresponds to the well-known mass-downsizing pattern (\cite{bundy06a}).
-Furthermore, the mass-downsizing trend observed in each of our environment subsample is generally consistent with the trend observed in zCOSMOS Redshift Survey for isolated and group galaxies (\cite{Iovino:2010aa}).
+In addition, when we compare the stellar masses at which $f_{\rm{Q}} = 0.5$ for each subsample, we find that this mass decreases over cosmic time.
+This corresponds to the well-known mass-downsizing pattern in the literature (e.g.
+\cite{bundy06a}).
+Furthermore, the mass-downsizing trend observed in each of our environment subsample is consistent with the trend observed in zCOSMOS Redshift Survey for isolated and group galaxies (\cite{Iovino:2010aa}).
+%Remark on how the M_{50-50}?
+is lower for high environment f_{Q}, and that it generally increases with redshift.
+A trend also observed in the t_{5050} considerations.
 
-We compare our $f_{\rm{Q}}$ results to previous $f_{\rm{Q}}$ or $f_{\rm{red}}$ measurements for analogous environment classifications in literature.
+Finally, we compare our $f_{\rm{Q}}$ results to previous $f_{\rm{Q}}/f_{\rm{red}}$ measurements for analogous environment classifications.
 For our lowest redshift bin, we find that our $f_{\rm{Q}}$ values for low and high environments are consistent with previous $f_{\rm{Q}}/f_{\rm{red}}$ measurements for SDSS galaxies as a function of environment.
@@
 The \cite{Tinker:2011aa} $f_{\rm{Q}}$ values at the lowest and highest overdensity values, $f_{\rm{Q}} \sim 0.4$ and $f_{\rm{Q}} \sim 0.6$ respectively, are consistent with our SDSS sample low and high density environment $f_{\rm{Q}}$ at the lowest mass bin $\rm{log} \; \mathcal{M} \sim 10.2$.
-At higher mass ranges, our $f_{\rm{Q}}$ results for low and high density environments are consistent with \cite{Baldry:2006aa} $f_{\rm{red}}$ values for lowest and highest environment density, which they measure using projected neighbor density.
+At higher mass ranges, our $f_{\rm{Q}}$ results are consistent with \cite{Baldry:2006aa}.
+\cite{Baldry:2006aa} using project neighbor density environment measures ($\rm{log} \;  \Sigma$) in order to obtain $f_{\rm{Q}}(\mathcal{M})$ for a range of environmental densities.
+Although the different environment measurement makes a direct comparison unclear, $f_{\rm{Q}}$ for higher environments ($\rm{log} \; \Sigma > 0.2$) in \cite{Baldry:2006aa} is roughly $f_{\rm{Q}} \sim 0.6$ at $\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}$ and $f_{\rm{Q}} \sim 0.9$ at $\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}$, in agreement our high density environment.
+Likewise, for lower environments in \cite{Baldry:2006aa} ($\rm{log} \; \Sigma < -0.4$) $f_{\rm{Q}} \sim 0.4$ at $\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}$ and $f_{\rm{Q}} \sim 0.8$ at $\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}$, which agrees with our low density environment $f_{\rm{Q}}$.
 
-At higher redshifts, we compare our PRIMUS $f_{\rm{Q}}$ results to the $f_{\rm{red}}$ (or $1-f_{\rm{blue}}$) results from the zCOSMOS Redshift Survey (\cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, \cite{Kovac:2014aa}), which roughly covers the same redshift range as PRIMUS.
-\cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, and \cite{Kovac:2014aa} using a mass-complete galaxy sample derived from zCOSMOS and environment determined using a group catalog, 3D local density contrast, and overdensity respectively, compare $f_{\rm{red}}$ for different environments.
+For $z > 0.2$, we compare our PRIMUS $f_{\rm{Q}}$ results to the $f_{\rm{red}}$ (or $1-f_{\rm{blue}}$) results from the zCOSMOS Redshift Survey (\cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, \cite{Kovac:2014aa}), which approximately covers the same redshift range as PRIMUS.
+\cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, and \cite{Kovac:2014aa} using a mass-complete galaxy sample derived from zCOSMOS and a group catalog, 3D local density contrast, and overdensity environment measurements, respectively, compare $f_{\rm{red}}$ with respect to environment.
+The $f_{\rm{blue}}$ for group and isolated galaxies from \cite{Iovino:2010aa} are generally inconsistent with our $1-f_{\rm{Q}}$ for high and low density environments.
+Similarly, $f_{\rm{red}}$ for high and low overdensities in \cite{Kovac:2014aa} are  greater overall than the PRIMUS $f_{\rm{Q}}$ values in high and low density environments.
+However, \cite{Kovac:2014aa} illustrates that there is a significant difference between classifying the quenched population using color and SFR: $f_{\rm{Q}}$ defined by color is greater than $f_{\rm{Q}}$ defined by SFR by $\sim 0.2$.
+Although the difference does not propagate evenly for the environment classification, once we approximately account for the difference $f_{\rm{red}}$ in \cite{Kovac:2014aa} is generally consistent with our $f_{\rm{Q}}$ results for both high and low density environments.
+%Highlight that PRIMUS has more statistics?
 
-The $f_{\rm{blue}}$ values for group and isolated galaxies from \cite{Iovino:2010aa} are generally inconsistent with our $f_{\rm{Q}}$ values in high and low density environments.
-Similarly, the $f_{\rm{red}}$ values for high and low overdensities from \cite{Kovac:2014aa} disagree with our $f_{\rm{Q}}$ values in high and low density environments.
-
-Also, the zCOSMOS results, which are mostly consistent with each other, indicate that the $f_{\rm{red}}$ values in high density environments are greater than in low density environments.
+Additionally, the zCOSMOS results indicate that the $f_{\rm{red}}$ values in high density environments are greater overall than in low density environments.
 The same trend is observed in the PRIMUS results and will be discussed in detail later in the section.
-Furthermore, \cite{Iovino:2010aa} in their analysis finds clear mass dependence in the $f_{\rm{red}}$ evolution where $f_{\rm{red}}$ evolves by a greater amount for lower mass galaxies in both group and isolated galaxies.
-
- %explain the zCOSMOS results briefly. Mention the general discrepancies while highlighting the large statistics offered by PRIMUS
-%If we impose the f_Q vs f_red discrepancies plotting in Kovac et al.
-2014, can we explain the discrepancies between Iovino et al.
-2010 and PRIMUS?
-Is Iovino et al.
-2010 and Kovac et al.
-2014 consistent with one another?
-%Note the clear mass dependence in essentially all the zCOSMOS results 
-%color-density relation?
-
-In contrast to the zCOSMOS results, for each panels in Figure \ref{fig:qf}, qualitatively, we see little mass dependence on the $f_{\rm{Q}}$ evolution.
-However, due to the distinct stellar mass completeness limits imposed at each redshift bin of our sample, we require a more quantitative comparison of the $f_{\rm{Q}}$ redshift evolution.
-Consequently, we fit each subsample $f_{\rm{Q}}$ to a power-law parameterization as a function of stellar mass,
+Another significant trend observed in the zCOSMOS results is the significant mass dependence of the $f_{\rm{red}}$ and $f_{\rm{blue}}$ evolution.
+\cite{Iovino:2010aa} by examining $f_{\rm{blue}}(z)$ in different mass bins for group and isolated galaxies find significantly larger $f_{\rm{blue}}$ evolution for lower masses.
+In fact, \cite{Iovino:2010aa} finds no evolution in $f_{\rm{blue}}$ for $\mathcal{M} > 10^{10.9} \mathcal{M}_{\odot}$ for both group and isolated galaxies over $0.4 \lesssim z \lesssim 0.9$.
+On the other hand, in the lowest mass bin ($10^{10.0} \mathcal{M}_{\odot} < \mathcal{M} < 10^{10.5} \mathcal{M}_{\odot}$) \cite{Iovino:2010aa} finds $f_{\rm{blue}}(z \sim 0.4) - f_{\rm{blue}}(z \sim 0.2) \sim 0.2$ for isolated galaxies and  $f_{\rm{blue}}(z \sim 0.4) - f_{\rm{blue}}(z \sim 0.2) \sim 0.1$ for group galaxies.
+In contrast, in each panels in Figure \ref{fig:qf}, we qualitatively find little mass dependence on the $f_{\rm{Q}}$ evolution for either low or high density environments.
+However, due to the distinct stellar mass completeness limits imposed at each redshift bin of our sample, subtle effects such as the mass dependence of the $f_{\rm{Q}}$ evolution are difficult to discern.
+In order to more quantitatively compare the $f_{\rm{Q}}$ evolution, we fit $f_{\rm{Q}}$ for each subsample to a power-law parameterization as a function of stellar mass,
 
@@
 
-The same fitting was performed using $\mathcal{M}_{\rm{fid}} = 10^{11} \mathcal{M}_\odot$; however, aside from a general shift in all $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ values by roughly $\sim 0.2$, we observe the same evolutionary trends.
+Figure \ref{fig:qffit} illustrates that throughout the entire redshift range, high density environment has a significantly greater $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ than the lower density environment.
+This is in strong agreement with the zCOSMOS results from \cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, and \cite{Kovac:2014aa}.
+Therefore, for $z < 1.0$, galaxy populations in higher density environments have higher quenched fractions.
+
+The same fitting was performed using $\mathcal{M}_{\rm{fid}} = 10^{11} \mathcal{M}_\odot$; however, aside from an overall shift in $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ by $\sim 0.2$, we observe the same evolutionary trends.
+$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{11}\mathcal{M}_{\odot})$ for both low and high density environments increases by $\sim 0.2$ from as redshift decreases from $z \sim 0.7$ to $z \sim 0.1$.
+This suggests that the total amount of $f_{\rm{Q}}$ evolution at $\mathcal{M} \sim This further supports our previous suggestion that there is little mass dependence in our $f_{\rm{Q}}$ evolution.
+Although our sample from PRIMUS provides larger statistics, due to the limited mass ranges probed in our mass-complete sample ($\mathcal{M} > 10^{10.5} \mathcal{M}_{\odot}$ for our $z \sim 0.7$ bin) it is difficult to dismiss the mass dependence observed in the zCOSMOS results.
+
+In addition, throughout the redshift range, high density environment has a significantly greater $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ than the low density environment.
 
@@
 
-In addition, throughout the redshift range, high density environment has a significantly greater $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ than the low density environment.
-
-%PRIMUS results are roughly in agreement with zCOSMOS 10k (Iovino et al.
-2010) and zCOMOS 20k (Kovac et al.
-2014) once the difference between f_red and f_Q are taken into account.
-Discuss some general specific values.
-% Previous results, primarily from zCOSMOS 10k and 20k, have found a significant mass dependence in the f_{Q} evolution with f_{Q} increasing significantly more over redshift at lower masses.
-At higher masses these results find little evolution in f_Q.
-Though our f_{Q} values are in good agreement with these results, for the mass ranges probed in our analysis, we find little mass dependence in the f_Q evolution.
-
-% color-mass relation, mass-density relation, color-density relation, SFR-density relation, SSFR-density relation,
-
 % The "color-mass" relation holds for both low and high environment galaxies.
@@
 Although this could be due to the contamination in our environment measurements since there are large redshift errors.
-% Emphasize that due to the limited mass range from mass completeness limits, the conclusions on mass dependence should be taken with a grain of salt. 
-% The redshift evolution of the QF in each
 
@@
 
-1. SMFs in low and high environment are different for both SF and Q
-2. Mass dependence of QF
-3. redshift dependence of Qf
-4. environment dependence of QF
-5. QF fit
+\begin{itemize}
+	\item 1. SMFs in low and high environment are different for both SF and Q
+	\item 2. Mass dependence of QF
+	\item 3. redshift dependence of Qf
+	\item 4. environment dependence of QF
+	\item 5. QF fit 
+\end{itemize}
 

### 2014-07-24 qfenv_paper/qf_environment.tex
more qf section additions

@@
 The SMFs calculated in the previous section illustrate the stellar mass distribution of our galaxy population and its evolution over comic time.
-In this section, using the SMFs of our subsamples, we compare the quiescent and the star-forming populations by calculating quiescent fraction - the fraction of galaxies that have depleted their star-formation.
+In this section, using the SMFs of our subsamples, we compare the quiescent and the star-forming populations by calculating the fraction of galaxies that have quenched their star-formation, the quiescent fraction.
 With the sufficient statistics available from SDSS and PRIMUS, we evaluate the quiescent fraction in bins of stellar mass and redshift for low and high density environments.
-More specifically, by analyzing the quiescent fraction with respect to mass, redshift, and environment we are able to compare the quiescent fraction evolution over redshift for galaxies in low and high density environments.
+More specifically, by analyzing the quiescent fraction with respect to mass, redshift, and environment we are able to compare the quiescent fraction evolution in low and high density environments.
 Through this comparison we reveal the subtle environmental effects in quenching star formation that are often obscured by the underlying correlations among galactic properties such as color-mass and mass-density relations (\cite{Cooper:2010aa}).
-Furthermore by quantifying the environmental effects of star-formation quenching, we are able to provide constraints on the various proposed quenching mechanisms, such as strangulation and ram-pressure stripping (CITECITE), that operate on the scale of our environment measure.
+Furthermore by quantifying the environmental effects of star-formation quenching, we are able to provide constraints on the various proposed environmental quenching mechanisms, such as strangulation and ram-pressure stripping (CITECITE).
 
@@
 
-Most noticeably, $f_{\rm{Q}}$ increases monotonically as a function of mass at all redshift bin and environment.
+Most noticeably in Figure \ref{fig:qf}, $f_{\rm{Q}}$ increases monotonically as a function of mass at all redshift bin and environment.
 In other words, for all subsamples, galaxies in higher mass bins are more likely to have quenched its star-formation.
@@
 
-Focusing on the redshift evolution of $f_{\rm{Q}}$, we find that for both environments and over our mass range $f_{\rm{Q}}$ increases as redshift decreases.
+Focusing on the redshift evolution of $f_{\rm{Q}}$, we find that for both environments $f_{\rm{Q}}$ increases as redshift decreases.
 For high density environment, this is analogous to the Butcher-Omeler Effect (\cite{Butcher:1984aa}), which states that galaxy populations in groups or clusters have higher $f_{\rm{blue}}$, or lower $f_{\rm{Q}}$, at higher redshift.
@@
 Coupled with the decline of SFR in the star-forming population (\cite{Noeske:2007aa}; \cite{cooper08a}), our results strongly agree with the observed decline of global star-formation in the universe (\cite{hopkins06a}).
+%Maybe Stacey et al.
+2014 is relevant here?
 
@@
 For our lowest redshift bin, we find that our $f_{\rm{Q}}$ values for low and high environments are consistent with previous $f_{\rm{Q}}/f_{\rm{red}}$ measurements for SDSS galaxies as a function of environment.
-For example, \cite{Tinker:2011aa}, using a group-finding algorithm on the SDSS DR7, presents the relationship between $f_{\rm{Q}}$ and overdensity for galaxies within the mass range $\rm{log} \; \mathcal{M}_{*} = [9.8, 10.1]$.
-The \cite{Tinker:2011aa} $f_{\rm{Q}}$ values at the lowest and highest overdensity values, $f_{\rm{Q}} \sim 0.4$ and $f_{\rm{Q}} \sim 0.6$ respectively, are consistent with our SDSS sample low and high density environment $f_{\rm{Q}}$ at the lowest mass bin $\rm{log} \; \mathcal{M} \sim 10.2$.
-At higher mass ranges, our $f_{\rm{Q}}$ results are consistent with \cite{Baldry:2006aa}.
-\cite{Baldry:2006aa} using project neighbor density environment measures ($\rm{log} \;  \Sigma$) in order to obtain $f_{\rm{Q}}(\mathcal{M})$ for a range of environmental densities.
-Although the different environment measurement makes a direct comparison unclear, $f_{\rm{Q}}$ for higher environments ($\rm{log} \; \Sigma > 0.2$) in \cite{Baldry:2006aa} is roughly $f_{\rm{Q}} \sim 0.6$ at $\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}$ and $f_{\rm{Q}} \sim 0.9$ at $\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}$, in agreement our high density environment.
-Likewise, for lower environments in \cite{Baldry:2006aa} ($\rm{log} \; \Sigma < -0.4$) $f_{\rm{Q}} \sim 0.4$ at $\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}$ and $f_{\rm{Q}} \sim 0.8$ at $\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}$, which agrees with our low density environment $f_{\rm{Q}}$.
+For example, \cite{Tinker:2011aa}, using a group-finding algorithm on the SDSS DR7, presents the relationship between $f_{\rm{Q}}$ and overdensity for galaxies within the mass range $\rm{log} \; \mathcal{M} = [9.8, 10.1]$.
+The \cite{Tinker:2011aa} $f_{\rm{Q}}$ at the lowest and highest overdensities, $f_{\rm{Q}} \sim 0.4$ and $f_{\rm{Q}} \sim 0.6$ respectively, are consistent with our $f_{\rm{Q}}$ for low and high density environment at the lowest mass bin ($\rm{log} \; \mathcal{M} \sim 10.2$).
+At higher masses, our $f_{\rm{Q}}$ results are consistent with \cite{Baldry:2006aa}.
+\cite{Baldry:2006aa} uses project neighbor density environment measures ($\rm{log} \;  \Sigma$) to obtain $f_{\rm{Q}}(\mathcal{M})$ for a range of environmental densities.
+Although the different environment measurements make a direct comparison unclear, at higher environments ($\rm{log} \; \Sigma > 0.2$) in \cite{Baldry:2006aa} $f_{\rm{Q}} \sim 0.6$ at $\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}$ and $f_{\rm{Q}} \sim 0.9$ at $\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}$, in agreement our high density environment.
+Likewise, for lower environments in \cite{Baldry:2006aa} ($\rm{log} \; \Sigma < -0.4$) $f_{\rm{Q}} \sim 0.4$ at $\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}$ and $f_{\rm{Q}} \sim 0.8$ at $\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}$, which also agree with our low density environment $f_{\rm{Q}}$.
 
@@
 Similarly, $f_{\rm{red}}$ for high and low overdensities in \cite{Kovac:2014aa} are  greater overall than the PRIMUS $f_{\rm{Q}}$ values in high and low density environments.
-However, \cite{Kovac:2014aa} illustrates that there is a significant difference between classifying the quenched population using color and SFR: $f_{\rm{Q}}$ defined by color is greater than $f_{\rm{Q}}$ defined by SFR by $\sim 0.2$.
-Although the difference does not propagate evenly for the environment classification, once we approximately account for the difference $f_{\rm{red}}$ in \cite{Kovac:2014aa} is generally consistent with our $f_{\rm{Q}}$ results for both high and low density environments.
-%Highlight that PRIMUS has more statistics?
+However, \cite{Kovac:2014aa} points out that there is a significant difference between classifying the quenched population using color and SFR.
+$f_{\rm{Q}}$ defined by color is greater than $f_{\rm{Q}}$ defined by SFR by roughly $0.2$.
+Although the propagation of this difference for different environments is not explored in \cite{Kovac:2014aa}, if we account for the difference evenly for $f_{\rm{red}}$ at all environments, the \cite{Kovac:2014aa} results are generally consistent with our $f_{\rm{Q}}$ at high and low density environments.
 
@@
 Another significant trend observed in the zCOSMOS results is the significant mass dependence of the $f_{\rm{red}}$ and $f_{\rm{blue}}$ evolution.
-\cite{Iovino:2010aa} by examining $f_{\rm{blue}}(z)$ in different mass bins for group and isolated galaxies find significantly larger $f_{\rm{blue}}$ evolution for lower masses.
-In fact, \cite{Iovino:2010aa} finds no evolution in $f_{\rm{blue}}$ for $\mathcal{M} > 10^{10.9} \mathcal{M}_{\odot}$ for both group and isolated galaxies over $0.4 \lesssim z \lesssim 0.9$.
+\cite{Iovino:2010aa} by examining $f_{\rm{blue}}(z)$ in different mass bins for group and isolated galaxies find significantly larger $f_{\rm{blue}}$ evolution at lower masses.
+In fact, \cite{Iovino:2010aa} finds no evolution in $f_{\rm{blue}}$ for $\mathcal{M} > 10^{10.9} \mathcal{M}_{\odot}$ for both group and isolated galaxies over the redshift range $0.4 < z < 0.9$.
 On the other hand, in the lowest mass bin ($10^{10.0} \mathcal{M}_{\odot} < \mathcal{M} < 10^{10.5} \mathcal{M}_{\odot}$) \cite{Iovino:2010aa} finds $f_{\rm{blue}}(z \sim 0.4) - f_{\rm{blue}}(z \sim 0.2) \sim 0.2$ for isolated galaxies and  $f_{\rm{blue}}(z \sim 0.4) - f_{\rm{blue}}(z \sim 0.2) \sim 0.1$ for group galaxies.
-In contrast, in each panels in Figure \ref{fig:qf}, we qualitatively find little mass dependence on the $f_{\rm{Q}}$ evolution for either low or high density environments.
+In contrast, in each of the panels of Figure \ref{fig:qf}, we qualitatively find little mass dependence on the $f_{\rm{Q}}$ evolution for either low or high density environments.
 However, due to the distinct stellar mass completeness limits imposed at each redshift bin of our sample, subtle effects such as the mass dependence of the $f_{\rm{Q}}$ evolution are difficult to discern.
+
 In order to more quantitatively compare the $f_{\rm{Q}}$ evolution, we fit $f_{\rm{Q}}$ for each subsample to a power-law parameterization as a function of stellar mass,
@@
 \end{figure}
-%fiducial mass may be 11.0 depending on what we want.
 
@@
 This is in strong agreement with the zCOSMOS results from \cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, and \cite{Kovac:2014aa}.
-Therefore, for $z < 1.0$, galaxy populations in higher density environments have higher quenched fractions.
+For $z < 1.0$, galaxy populations in higher density environments have higher quenched fractions.
+%Color-density dependence in Cucciati?
 
-The same fitting was performed using $\mathcal{M}_{\rm{fid}} = 10^{11} \mathcal{M}_\odot$; however, aside from an overall shift in $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ by $\sim 0.2$, we observe the same evolutionary trends.
-$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{11}\mathcal{M}_{\odot})$ for both low and high density environments increases by $\sim 0.2$ from as redshift decreases from $z \sim 0.7$ to $z \sim 0.1$.
-This suggests that the total amount of $f_{\rm{Q}}$ evolution at $\mathcal{M} \sim This further supports our previous suggestion that there is little mass dependence in our $f_{\rm{Q}}$ evolution.
-Although our sample from PRIMUS provides larger statistics, due to the limited mass ranges probed in our mass-complete sample ($\mathcal{M} > 10^{10.5} \mathcal{M}_{\odot}$ for our $z \sim 0.7$ bin) it is difficult to dismiss the mass dependence observed in the zCOSMOS results.
+The same fitting procedure was performed using $\mathcal{M}_{\rm{fid}} = 10^{11} \mathcal{M}_\odot$; however, aside from an overall shift in $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ by $\sim 0.2$, we observe the same evolutionary trends.
+$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{11}\mathcal{M}_{\odot})$ for both low and high density environments increase by $\sim 0.2$ as redshift decreases from $\sim 0.7$ to $\sim 0.1$, just as \ref{fig:qffit}.
+Increasing the fiducial mass to $10^{11} \mathcal{M}_{\odot}$ also does not change the total evolution for either environments.
+In contrast, as mentioned above, \cite{Iovino:2010aa} finds significantly less $f_{\rm{Q}}$ evolution for $\mathcal{M} \sim 10^{11.0} \mathcal{M}_{\odot}$ than in $\mathcal{M} \sim 10^{10.5} \mathcal{M}_{\odot}$.
+Furthermore, changing the fiducial mass does not significant change the difference in $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ between the environments.
+This is again in disagreement with \cite{Iovino:2010aa}, which finds a significant redshift dependent difference in $f_{\rm{blue}}$ between group and isolated galaxies at $\mathcal{M} \sim 10^{10.5} \mathcal{M}_{\odot}$, but finds no difference at $\mathcal{M} \sim 10^{11} \mathcal{M}_{\odot}$.
+As suggested earlier, our $f_{\rm{Q}}$ results show little mass dependence in our $f_{\rm{Q}}$ evolution.
+Although our sample from SDSS and PRIMUS provides significantly larger statistics, due to the limited mass ranges probed in our mass-complete sample (e.g.
+$\mathcal{M} > 10^{10.5} \mathcal{M}_{\odot}$ for our $z \sim 0.7$ bin) it is difficult to dismiss the mass dependence observed in the zCOSMOS results.
 
-In addition, throughout the redshift range, high density environment has a significantly greater $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ than the low density environment.
-
-From Figure \ref{fig:qffit}, we note that for both environments $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ increases as redshift decreases.
+Finally, from Figure \ref{fig:qffit}, we note that for both environments $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ increases as redshift decreases.
 This highlights the general increase of $f_{\rm{Q}}(\mathcal{M})$ as redshift decreases noted earlier.
-More importantly it quantifies the total evolution of $f_{\rm{Q}}$ since $z \sim 0.8$ for both low and high density environments.
-Remarkably, the total evolution of $f_{\rm{Q}}$ remains constant for both environments.
-In other words, the total evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ show no strong environment dependence.
-
-%Discuss how this is not due to contamination by environment classifications.
-
-% The "color-mass" relation holds for both low and high environment galaxies.
-While others in literature (Cucciati et al.
-2010) found that the mass dependence was less apparent in high environment, this does not hold true for the SDSS and PRIMUS data.
-Although this could be due to the contamination in our environment measurements since there are large redshift errors.
+More importantly, it quantifies the total evolution of $f_{\rm{Q}}$ since $z \sim 0.8$ for both low and high density environments.
+Remarkably, the $f_{\rm{Q}}$ evolves by the same amount for both environments.
+In other words, the total evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ show little environment dependence.
+This disagrees with the $f_{\rm{blue}}$ results from \cite{Iovino:2010aa}, which show a clear distinction between group and isolated galaxies.
+In \cite{Iovino:2010aa}, $f_{\rm{blue}}$ for isolated galaxies decrease much faster than $f_{\rm{blue}}$ for group galaxies.
+At $\mathcal{M} \sim 10.5$, \cite{Iovino:2010aa} finds that $f_{\rm{blue}}$ for isolated galaxy decreases by 0.3 from z~0.6 to 0.3, while for $f_{\rm{blue}}$ for group galaxies only decrease by 0.1 in the same redshift limit, showing a clear dependence in environment.
+% Considering our definition of environment may be susceptible to contamination, we considered more stringent classification of both low and high density environments. However,
 

### 2014-07-24 qfenv_paper/qf_environment.tex
More discussions on QF and additions to the SMF.

@@
 Once we obtain environment measurements for all the galaxies in our galaxy sample, we classify galaxies with $n_{\rm{env}} < 1$ to be "low" environment density and galaxies with $n_{\rm{env}} > 3$ to be "high" environment densities.
-The high environment cutoff was selected in order to reduce contamination from galaxies in low environment densities while maintaining sufficient
+The high environment cutoff was selected in order to reduce contamination from galaxies in low environment densities while maintaining sufficient statistics.
+
+The analysis we describe below uses a fixed cylindrical aperture with dimensions $R_{\rm{ap}} = 2 \: \rm{Mpc}$ and $H_{\rm{ap}} = 25 \: \rm{Mpc}$ to measure environment; the same analysis was extended for varying aperture dimensions $R_{\rm{ap}} = 1, 2, 3 \: \rm{Mpc}$ and $H_{\rm{ap}} = 25, 50 \: \rm{Mpc}$.
+Minor adjustments to the environment classification thresholds were adopted in these analyses for the smaller apertures ($r_{\rm{ap}} = 0.5, 1 \rm{Mpc}$ and $r_{\rm{ap}} = 25 \rm{Mpc}$).
+The results obtained from using these different are consistent with the results later discussed in this paper.
 
@@
 
-We present the SMFs for 16 target galaxy subsamples classified into quiescent/star-forming (orange/blue, bottom/top panels) and high/low environment density (left/right panels) in Figure \ref{fig:smf}.
+In Figure \ref{fig:smf}, we present the SMFs for 16 target galaxy subsamples classified into quiescent/star-forming (orange/blue, bottom/top panels) and high/low environment density (left/right panels).
 The redshift evolution of the SMFs in each of these panels are indicated by a darker shade for lower redshift bins.
-The sample variance uncertainties are incorporated in the width of the SMFs.
+The sample variance uncertainties are illustrated through the width of the SMFs.
+
+In order to consistently measure environment throughout our entire sample we impose PRIMUS redshift errors on our SDSS galaxies.
+However, we observe a significant difference between the SDSS and PRIMUS samples in the fractional contribution of each environment classification within the redshift bin.
+For each of the PRIMUS redshift bins, approximately $50 \%$ of galaxies in the redshift bin are in low density environments and roughly $30 \%$ are in high density environments.
+In contrast, in the SDSS redshift bin, $38 \%$ of galaxies in the redshift bin are in low density environments and $45 \%$ are in high density environments.
+As a result, we note that the SMF redshift evolution is inconsistent when transition from the PRIMUS sample to the SDSS sample at $z \sim 0.2$.
+
+Yet, just from the PRIMUS samples alone, we probe a sufficient redshift range to observe certain trends in the SMF evolution for each of the panels in Figure \ref{fig:smf}.
 
@@
 %Remark on the clear mass-density relation: more massive galaxies in high environment 
-% Compare to Bolzonella et al. 2010 and perhaps even Bundy et al. 2006 results
+% Compare to Bolzonella et al. 2010 and  Bundy et al. 2006 results
 % Agree with previous works on mass segregation results from VVDS, DEEP2, and etc.
@@
 Through this comparison we reveal the subtle environmental effects in quenching star formation that are often obscured by the underlying correlations among galactic properties such as color-mass and mass-density relations (\cite{Cooper:2010aa}).
-Furthermore by quantifying the environmental effects of star-formation quenching, we are able to provide constraints on the various proposed environmental quenching mechanisms, such as strangulation and ram-pressure stripping (CITECITE).
+Furthermore by quantifying the environmental effects of star-formation quenching, we are able to provide constraints on the various proposed environmental quenching mechanisms, such as strangulation and ram-pressure stripping (\cite{McCarthy:2008aa}).
 
@@
 In order to more quantitatively compare the $f_{\rm{Q}}$ evolution, we fit $f_{\rm{Q}}$ for each subsample to a power-law parameterization as a function of stellar mass, 
-
 \begin{figure}
@@
 Figure \ref{fig:qffit} illustrates that throughout the entire redshift range, high density environment has a significantly greater $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ than the lower density environment.
-This is in strong agreement with the zCOSMOS results from \cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, and \cite{Kovac:2014aa}.
+This is in strong agreement with the zCOSMOS results from \cite{Cucciati:2010aa} and \cite{Kovac:2014aa}.
 For $z < 1.0$, galaxy populations in higher density environments have higher quenched fractions.
-%Color-density dependence in Cucciati?
+As galaxy color and SFR are related, our results support the existence of the color-density relation (\cite{Cucciati:2010aa}; \cite{Cooper:2010aa}) in favor of the idea that the color-density relation is a merely a reflection of the mass-density or morphology-density relation (\cite{Scodeggio:2009aa}, \cite{Tasca:2009aa}).
 
 The same fitting procedure was performed using $\mathcal{M}_{\rm{fid}} = 10^{11} \mathcal{M}_\odot$; however, aside from an overall shift in $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ by $\sim 0.2$, we observe the same evolutionary trends.
-$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{11}\mathcal{M}_{\odot})$ for both low and high density environments increase by $\sim 0.2$ as redshift decreases from $\sim 0.7$ to $\sim 0.1$, just as \ref{fig:qffit}.
-Increasing the fiducial mass to $10^{11} \mathcal{M}_{\odot}$ also does not change the total evolution for either environments.
-In contrast, as mentioned above, \cite{Iovino:2010aa} finds significantly less $f_{\rm{Q}}$ evolution for $\mathcal{M} \sim 10^{11.0} \mathcal{M}_{\odot}$ than in $\mathcal{M} \sim 10^{10.5} \mathcal{M}_{\odot}$.
-Furthermore, changing the fiducial mass does not significant change the difference in $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ between the environments.
-This is again in disagreement with \cite{Iovino:2010aa}, which finds a significant redshift dependent difference in $f_{\rm{blue}}$ between group and isolated galaxies at $\mathcal{M} \sim 10^{10.5} \mathcal{M}_{\odot}$, but finds no difference at $\mathcal{M} \sim 10^{11} \mathcal{M}_{\odot}$.
-As suggested earlier, our $f_{\rm{Q}}$ results show little mass dependence in our $f_{\rm{Q}}$ evolution.
+$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{11}\mathcal{M}_{\odot})$ for both low and high density environments each increase by $\sim 0.2$ as redshift decreases from $\sim 0.7$ to $\sim 0.1$, just as Figure \ref{fig:qffit}.
+Evidently, increasing the fiducial mass to $10^{11} \mathcal{M}_{\odot}$ does not change the total evolution for either environments.
+On the other hand, \cite{Iovino:2010aa}, for both group and isolated galaxies, finds significantly less $f_{\rm{Q}}$ evolution for $\mathcal{M} \sim 10^{11.0} \mathcal{M}_{\odot}$ than in $\mathcal{M} \sim 10^{10.5} \mathcal{M}_{\odot}$.
+Furthermore, \cite{Iovino:2010aa} also finds that the difference in $f_{\rm{blue}}$ evolution between group and isolated galaxies ($f_{\rm{blue}, \rm{isolated}}(z) - f_{\rm{blue}, \rm{group}}(z))$ is much greater at $\mathcal{M} \sim 10^{10.5} \mathcal{M}_{\odot}$ than at $\mathcal{M} \sim 10^{11} \mathcal{M}_{\odot}$, where they find almost no difference.
+In contrast, we find that changing the fiducial mass does not significantly alter the difference in $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$.
+The zCOSMOS results find a clear mass dependence in the $f_{\rm{blue}}$ evolution; however, the consistency in evolutionary trends when the fiducial mass is change reveal that our $f_{\rm{Q}}$ evolution exhibits little mass dependence.
 Although our sample from SDSS and PRIMUS provides significantly larger statistics, due to the limited mass ranges probed in our mass-complete sample (e.g.
@@
 This highlights the general increase of $f_{\rm{Q}}(\mathcal{M})$ as redshift decreases noted earlier.
-More importantly, it quantifies the total evolution of $f_{\rm{Q}}$ since $z \sim 0.8$ for both low and high density environments.
-Remarkably, the $f_{\rm{Q}}$ evolves by the same amount for both environments.
+More importantly, we quantify the total evolution of $f_{\rm{Q}}$ for both low and high density environments through $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}}, z \sim 0.1) - f_{\rm{Q}}(\mathcal{M}_{\rm{fid}}, z \sim 0.7)$ for both environments.
+Remarkably, $f_{\rm{Q}}$ evolves by the same amount for both environments.
 In other words, the total evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ show little environment dependence.
@@
 In \cite{Iovino:2010aa}, $f_{\rm{blue}}$ for isolated galaxies decrease much faster than $f_{\rm{blue}}$ for group galaxies.
-At $\mathcal{M} \sim 10.5$, \cite{Iovino:2010aa} finds that $f_{\rm{blue}}$ for isolated galaxy decreases by 0.3 from z~0.6 to 0.3, while for $f_{\rm{blue}}$ for group galaxies only decrease by 0.1 in the same redshift limit, showing a clear dependence in environment.
-% Considering our definition of environment may be susceptible to contamination, we considered more stringent classification of both low and high density environments. However,
+At $\mathcal{M} \sim 10.5$, \cite{Iovino:2010aa} finds that $f_{\rm{blue}}$ for isolated galaxy decreases by 0.3 from $z \sim 0.6$ to 0.3, while for $f_{\rm{blue}}$ for group galaxies only decrease by 0.1 in the same redshift limit, showing a clear dependence in environment.
+Considering that fixed aperture definition of environment is susceptible to contamination due to PRIMUS redshift errors, we consider more stringent classification of high density environments extending the cut-off to $n_{\rm{env}} > 6, 9$.
+While a more stringent classification increases the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ overall as well as the uncertainties, it does not reveal reveal any significant environment dependence in the $f_{\rm{Q}}$ evolution.
+Therefore, the potential contamination in our environment measurements cannot explain the lack of environment dependence in the $f_{\rm{Q}}$ evolution.
 
-The analysis described in this paper use a fixed cylindrical aperture with dimensions $R_{\rm{ap}} = 2 \: \rm{Mpc}$ and $H_{\rm{ap}} = 25 \: \rm{Mpc}$ to measure environment, the same analysis was extended for varying aperture dimensions $R_{\rm{ap}} = 1, 2, 3 \: \rm{Mpc}$ and $H_{\rm{ap}} = 25, 50 \: \rm{Mpc}$.
-Minor adjustments to the environment classification thresholds were adopted in these analyses for the smaller apertures ($r_{\rm{ap}} = 0.5, 1 \rm{Mpc}$ and $r_{\rm{ap}} = 25 \rm{Mpc}$).
-The results obtained from using these different are consistent with the results displayed in this paper.
+Many physical mechanisms have been proposed to explain the quenching of star-formation observed in our universe.
+Often star-formation quenching is parameterized using two distinct mechanisms: mass-dependent and environment dependent mechanisms (Baldry et al.
+2006 Peng et al.
+2010).
+By the mass-dependence in all $f_{\rm{Q}}$ in Figure \ref{fig:qf} we conclude that galaxy stellar mass plays a significant role in quenching.
+Furthermore, from the fact that $f_Q$ in high density environments is always greater than $f_Q$ in low density environments, our results also reflect the environment dependence in quenching.
+However, in many of the proposed environment dependent quenching mechanisms, the quenching time scale is proposed to decrease.
+This would result in an increase in the quenched fraction that's faster than the increase in low density environment $f_Q$.
+We find that this is not the case.
+% What does this have to say about physical processes in groups and clusters that affect quenching?
 
@@
 
+We thank ...
 %

### 2014-07-25 qfenv_paper/qf_environment.tex
edits to SMF section

@@
 In contrast, in the SDSS redshift bin, $38 \%$ of galaxies in the redshift bin are in low density environments and $45 \%$ are in high density environments.
-As a result, we note that the SMF redshift evolution is inconsistent when transition from the PRIMUS sample to the SDSS sample at $z \sim 0.2$.
+As a result, we caution that the SMF redshift evolution is inconsistent when transition from the PRIMUS sample to the SDSS sample at $z \sim 0.2$.
 
-Yet, just from the PRIMUS samples alone, we probe a sufficient redshift range to observe certain trends in the SMF evolution for each of the panels in Figure \ref{fig:smf}.
+Yet, just from the PRIMUS samples alone, we probe a sufficient redshift range to observe notable trends in the SMF evolution for each of the panels in Figure \ref{fig:smf}.
 

### 2014-07-25 qfenv_paper/qf_environment.tex
Finished preliminary analysis for SMF and QF.
Also has summary outline?

--- 2014-07-24 qfenv_paper/qf_environment.tex
@@
 We classify the galaxies as quiescent or star-forming, based on an evolving specific star formation cut, and as low or high density environments, based on fixed cylindrical aperture environment measurements on a volume-limited {\em Environment Definition Population} (from PRIMUS and SDSS).
+
 For each of these subsamples, we examine the stellar mass function (SMF) evolution and compute the $f_{\rm{Q}}(\mathcal{M}_{*})$.
@@
     \begin{tabular}{lllll} \hline \hline              
-      &$z$ &Environment        &Quiescent  &Star-forming  \\ \hline 
-  SDSS      &$0.0375-0.145$ &High           &5470                       &4501                           \\
-            &               &Low            &5419                       &8927                           \\
-            &               &               &                       &                           \\ \hline
-  PRIMUS    &$0.2-0.4$      &High           &322                    &583                           \\
-            &               &Low            &768                    &2516                           \\
-            &               &               &                       &                           \\ \hline
-  PRIMUS    &$0.4-0.6$      &High           &350                       &675                           \\
-            &               &Low            &871                       &2385                           \\
-            &               &               &                       &                           \\ \hline
-  PRIMUS    &$0.6-0.8$      &High           &347                       &430                           \\
-            &               &Low            &833                       &1847                           \\
-            &               &               &                       &                           \\ \hline
-  PRIMUS    &$0.8-1.0$      &High           &136                       &232                           \\
-            &               &Low            &373                       &810                           \\
-            &               &               &                       &                           \\ \hline
-  \multicolumn{5}{l}{}                                             \\       
+    $z$ &Environment        &Quiescent  &Star-forming  \\ \hline 
+$0.0375-0.145$ &High           &5470                       &4501                           \\
+               &Low            &5419                       &8927                           \\
+               &               &                       &                           \\ \hline
+$0.2-0.4$      &High           &322                    &583                           \\
+               &Low            &768                    &2516                           \\
+               &               &                       &                           \\ \hline
+$0.4-0.6$      &High           &350                       &675                           \\
+               &Low            &871                       &2385                           \\
+               &               &                       &                           \\ \hline
+$0.6-0.8$      &High           &347                       &430                           \\
+               &Low            &833                       &1847                           \\
+               &               &                       &                           \\ \hline
+  \multicolumn{4}{l}{}                                             \\       
     \end{tabular} 
@@
 \subsection{Galaxy Sample} \label{sec:target} 
+\begin{figure*}
+  \begin{center}
+    \leavevmode
+    \epsfig{file=fig_envcount_cylr2h25_thresh75_sdss_z0_05_0_12_primuszerr_masslimit_histogram.png,height=0.5\textwidth}
+     \caption{Environment measure distribution for our galaxy sample.}      \label{fig:envcount}
+    \end{center}
+\end{figure*}
+
 Using the low redshift SDSS-{\em GALEX} and intermediate redshift PRIMUS data described above, in this section, we define our galaxy sample which will be used to compute the SMFs and QFs.
@@
 
-In order to consistently measure environment throughout our entire sample we impose PRIMUS redshift errors on our SDSS galaxies.
-However, we observe a significant difference between the SDSS and PRIMUS samples in the fractional contribution of each environment classification within the redshift bin.
+Although we imposed PRIMUS redshift errors on our SDSS galaxies in order to consistently measure environment throughout our entire sample, we observe a significant discrepancy between the SDSS and PRIMUS samples in the fractional contribution of each environment classification within the redshift bin.
 For each of the PRIMUS redshift bins, approximately $50 \%$ of galaxies in the redshift bin are in low density environments and roughly $30 \%$ are in high density environments.
 In contrast, in the SDSS redshift bin, $38 \%$ of galaxies in the redshift bin are in low density environments and $45 \%$ are in high density environments.
-As a result, we note that the SMF redshift evolution is inconsistent when transition from the PRIMUS sample to the SDSS sample at $z \sim 0.2$.
+As a result, we caution that the SMF redshift evolution is inconsistent during the transition from the PRIMUS sample to the SDSS sample at $z \sim 0.2$.
 
-Yet, just from the PRIMUS samples alone, we probe a sufficient redshift range to observe certain trends in the SMF evolution for each of the panels in Figure \ref{fig:smf}.
+Yet, from the PRIMUS samples alone, we probe a sufficient redshift to observe notable trends in the SMF evolution for each of the panels in Figure \ref{fig:smf}.
+Later we compare these trends to SMF results from DEEP2 (\cite{bundy06a}) and zCOSMOS (\cite{Bolzonella:2010aa}).
+In panel (a), star-forming galaxies in low density environments, we find a significant decrease in the high mass end of the SMF ($\mathcal{M} > 10^{10.75} \mathcal{M}_{\odot}$).
+In contrast at lower masses ($\mathcal{M} < 10^{10.5} \mathcal{M}_{\odot}$) we observe a notable increase in the SMF.
+In panel (b), star-forming galaxies in high density environments, we notice a possible decrease above the knee of the SMF ($\mathcal{M} \sim 10^{10.7} \mathcal{M}_{\odot}$) accompanied by an increase below the knee.
+For the quiescent population in low density environment, shown in panel (c) of Figure \ref{fig:smf}, we notice an increase in $\Phi$ for lower masses, but we do not notice any clear SMF evolution at the massive end.
+Lastly for the quiescent population in high density environments, panel (d), we find significant increase in $\Phi$ at all masses.
 
-Examining the SMF evolution from $z \sim 0.7$ to $z \sim 0.1$, we find that in high density environments both the star-forming and quiescent SMFs increase at $\mathcal{M}_{*}$ below the knee of mass function ($\rm{log}\: \mathcal{M}_{*}/\mathcal{M}_{\odot} < 10.75$ for star-forming; $\rm{log}\: \mathcal{M}_{*}/\mathcal{M}_{\odot} < 11.0$ for quiescent).
-Meanwhile, at masses above the knee the SMFs for high density environments exhibit little change over the entire cosmic time range.
+In comparison to \cite{bundy06a} and \cite{Bolzonella:2010aa}, some of the noted trends are not immediately evident.
+However, this is mostly due to the conflicting mass limits proposed in each study.
+Not to mention, only part of the redshift range probed by \cite{bundy06a} overlap with our results.
+Overall, we find that the trends we note in the SMF evolution above are in good agreement with results from DEEP2 and zCOSMOS.
 
-At low density environments, the quiescent SMF remains relatively constant for galaxies with $\rm{log}\: \mathcal{M}_{*}/\mathcal{M}_{\odot} < 10.75$.
-At higher stellar masses, however, the quiescent low density environment SMF decreases notably.
-Finally, the low density environment star-forming SMF shows a decrease at all stellar mass ranges over the redshift range.
-We caution readers and reserve any detailed analysis of the SMF evolution to future work due to the improvements in photometry that significantly alter the lowest redshift bin SMFs mentioned in Section \ref{sec:sdss}.
+Observing the evolutionary trends in SMF for each of these sub-populations simultaneously provides a naive narrative of the different galaxy evolutionary tracks involving environment and quenching.
+For example, the decrease in the massive star-forming galaxies in low density environment over cosmic time can be attributed to the transition of those galaxies to any of the other panels.
+The star-forming galaxies in low density environments that have quenched their star formation over time are possibly responsible for the increase of the quiescent, low density environment SMF over time.
+The star-forming galaxies that fall into higher density environments explain the increase in the star-forming high density environment SMF below the knee.
+Finally, star-forming galaxies in high density environments that have quenched their star-formation, quiescent galaxies that have transitioned from low to high density environments, and star-forming galaxies in low density environments that quench their star-formation while infalling to high density environments all contribute to the overall increase of the high environment quiescent SMF.
 
-%Compare SMFs at low environment vs high environment and remark that the SMFs are significantly different. 
-%Remark on the clear mass-density relation: more massive galaxies in high environment 
-% Compare to Bolzonella et al. 2010 and  Bundy et al. 2006 results
-% Agree with previous works on mass segregation results from VVDS, DEEP2, and etc.
+In addition to the evolution over cosmic time, we observe noticeable trends when we compare the SMFs for star-forming and quiescent galaxies between the two environments.
+Comparison of the SMFs in low versus high density environments reveal a noticeable relation between mass and density, with SMFs in high density environments having more massive galaxies.
+We further confirm this trend when we compare the median mass between the two environments to find that the median mass for galaxies in high density environments is significantly greater than in low density environments.
+The relationship between mass and environment observed in our SMFs mirror the well-established mass-density relation and observed mass segregation with environment in the literature (\cite{bundy06a}; \cite{Scodeggio:2009aa}; \cite{Bolzonella:2010aa}).
+
+We caution readers and reserve detailed analysis of the SMFs to future work due to the improvements in photometry that significantly alter the SDSS SMFs mentioned in Section \ref{sec:sdss}. 
+% There is also the issue with the SMF evolution: the uneven fractional contribution of the population and each environment classification.
 
@@
 Many physical mechanisms have been proposed to explain the quenching of star-formation observed in our universe.
-Often star-formation quenching is parameterized using two distinct mechanisms: mass-dependent and environment dependent mechanisms (Baldry et al.
-2006 Peng et al.
-2010).
-By the mass-dependence in all $f_{\rm{Q}}$ in Figure \ref{fig:qf} we conclude that galaxy stellar mass plays a significant role in quenching.
-Furthermore, from the fact that $f_Q$ in high density environments is always greater than $f_Q$ in low density environments, our results also reflect the environment dependence in quenching.
-However, in many of the proposed environment dependent quenching mechanisms, the quenching time scale is proposed to decrease.
+Often star-formation quenching is classified into two distinct mechanisms: mass-dependent and environment dependent mechanisms (\cite{Baldry:2006aa}; \cite{Peng:2010aa}).
+From the mass-dependence presented in all $f_{\rm{Q}}$ in Figure \ref{fig:qf}, we concur that galaxy stellar mass plays a significant role in quenching.
+Furthermore, since $f_Q$ in high density environments is always greater than $f_Q$ in low density environments, our results also reflect the environment dependence in quenching.
+%However, in many of the proposed environment dependent quenching mechanisms, the quenching time scale is proposed to decrease.
 This would result in an increase in the quenched fraction that's faster than the increase in low density environment $f_Q$.
@@
 \section{Summary} \label{sec:summary}
-Using a stellar mass complete galaxy sampled derived from SDSS and PRIMUS accompanied by a consistently measured galaxy environment from robust spectroscopic redshifts, we demonstrate that the quiescent fraction increases over cosmic time for $ z < 0.8$, regardless of environment.
+Using a stellar mass complete galaxy sampled derived from SDSS and PRIMUS accompanied by a consistently measured galaxy environment from robust spectroscopic redshifts, we measure the stellar mass functions for star-forming and quiescent in low and high density environments over the redshift range $z < 0.8$.
+From these stellar mass functions, we compare the proportion of quiescent galaxies within the subsamples by computing quiescent fraction for each of them.
+Afterwards, in order to better quantify the evolution of the quiescent fraction over cosmic time, we fit our quiescent fraction anchored at a fiducial mass.
+From our analyses we find the following notable results.
+
+\begin{enumerate}
+	\item By noting the SMF evolution for each of our subsamples, we loosely trace the evolutionary tracks our galaxy population tracing the general evolutionary tracks of quenching mechanisms and galaxies infalling into high density environments.
+	\item From the SMFs, we find that our galaxy population in high density environments, both star-forming and quiescent, have a higher median mass, thus confirming the mass density relation and mass-segregation in different environments.
+	\item In all of our subsamples, we find a clear mass dependence in $f_{\rm{Q}}$. $f_{\rm{Q}}$ increases monotonically with galaxy stellar mass. 
+	\item Both from the $f_{\rm{Q}}$ evolution and $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ values, $f_{\rm{Q}}$ increases with redshift. 
+	\item We conclude, by fitting our $f_{\rm{Q}}$, that $f_{\rm{Q}}$ in high density environments is greater than $f_{\rm{Q}}$ in low density environments regardless of mass and redshift.
+This result confirms the environmental dependence of quenching mechanisms stated previously in literature.
+	\item Comparison of the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ evolution for high and low density environments that the total evolution is independent of environment. 
+\end{enumerate}
+
+%  demonstrate that the quiescent fraction increases over cosmic time for $ z < 0.8$, regardless of environment.
 During this epoch the quiescent fraction in high density environments is consistently greater than the quiescent fraction in low density environments.
@@
 
-\begin{itemize}
-	\item 1. SMFs in low and high environment are different for both SF and Q
-	\item 2. Mass dependence of QF
-	\item 3. redshift dependence of Qf
-	\item 4. environment dependence of QF
-	\item 5. QF fit 
-\end{itemize}
-
-We thank ...
+We thank people...
 %

### 2014-07-28 qfenv_paper/qf_environment.tex
minor edit

@@
 In Section \ref{sec:smf} we examine the stellar mass function evolution for star-forming/quiescent and high/low density environment subsamples.
-In Section \ref{sec:qf_const} compare the quiescent fraction evolution in high and low density environments.
-In Section \ref{sec:summary} we summarize our results and discuss implications of the results on quenching mechanisms.
+In Section \ref{sec:qf_const} we compare the quiescent fraction evolution for high and low density environments and discuss implications of the results on quenching mechanisms.
+In Section \ref{sec:summary} we summarize our results.
 
 Throughout the paper we assume cosmology with $\Omega_{m} = 0.3, \Omega_{\Lambda} = 0.7$, and $H_0 = 70 \rm{km} \; \rm{s}^{-1} \rm{Mpc}^{-1}$.
-%%% INCLUDE OUTLINE OF PAPER
 
 \section{Sample Selection} \label{sec:sample}
-We are interested in quantifying the effects of galaxy environment on the evolution of the quiescent fraction over the redshift range $ z < 1.0$.
-For our analysis, we require a sample with sufficient depth to probe the redshift range and robust redshifts to measure galaxy environment.
-PRIMUS, with its $\sim 120,000$ spectroscopic redshifts provides ideal data at intermediate redshifts for our analysis.
+In order to quantify the effects of galaxy environment on the evolution of the quenched population over the redshift range $z < 1.0$, we require a sample with sufficient depth and robustness to probe the redshift range and to measure galaxy environment.
+PRIMUS with its $\sim 120,000$ spectroscopic redshifts provides ideal data at intermediate redshifts for our analysis.
 In addition, we anchor our analysis of the intermediate redshift sample with a low redshift sample derived from SDSS.

### 2014-08-04 qfenv_paper/qf_environment.tex
Sections 1-2.5 Edited.
Continue editing edge effects section

@@
 \title{PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 1$}
-\author{ChangHoon Hahn, Michael Blanton, Alison Coil, Richard Cool, Daniel Eisenstein, John Moustakas, Ken Wong, Guangtun Zhu}
+\author{
+ChangHoon~Hahn\altaffilmark{1}, 
+Michael~Blanton\altaffilmark{1}, 
+Alison~Coil\altaffilmark{2}, 
+Richard~Cool\altaffilmark{3}, 
+Daniel Eisenstein\altaffilmark{4},
+John Moustakas\altaffilmark{4}, 
+Ken Wong\altaffilmark{3}, 
+Guangtun Zhu\altaffilmark{3}
+}
+\altaffiltext{1}{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Place, New York, NY 10003}
+\altaffiltext{2}{Center for Astrophysics and Space Sciences, Department of Physics, University of California, 9500 Gilman Dr., La Jolla, CA 92093}
+\altaffiltext{3}{MMT Observatory, University of Arizona, 1540 E Second Street, Tucson AZ 85721}
+\altaffiltext{4}{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
 
@@
 
-%Section `ing
 \section{Introduction}
@@
 
-In Section \ref{sec:sample} we present a brief description of the PRIMUS and SDSS data, our sample construction, and galaxy environment measurements.
-In Section \ref{sec:smf} we examine the stellar mass function evolution for star-forming/quiescent and high/low density environment subsamples.
-In Section \ref{sec:qf_const} we compare the quiescent fraction evolution for high and low density environments and discuss implications of the results on quenching mechanisms.
-In Section \ref{sec:summary} we summarize our results.
+In Section \ref{sec:sample} we present a brief description of the PRIMUS and SDSS data, our mass complete sample construction, and galaxy environment measurements.
+After dividing our galaxy sample into subsamples of star-forming or quiescent and high or low density environments, we compute and examine the evolution of the stellar mass functions for our subsamples.
+In Section \ref{sec:qf_const}, we calculate the quiescent fraction and compare the evolution of the quiescent fraction between high and low density environments.
+In Section \ref{sec:discussion} we discuss the trends observed in the stellar mass function and quiescent fraction evolution and discuss implications of the results on quenching mechanisms.
+Finally in Section \ref{sec:summary} we summarize our results.
 
@@
 \section{Sample Selection} \label{sec:sample}
-In order to quantify the effects of galaxy environment on the evolution of the quenched population over the redshift range $z < 1.0$, we require a sample with sufficient depth and robustness to probe the redshift range and to measure galaxy environment.
+We are interested in quantifying the effects of galaxy environment on the evolution of the quenched population over the redshift range $z < 1.0$.
+For our analysis, we require a sample with sufficient depth and robustness to probe the redshift range and to measure galaxy environment.
 PRIMUS with its $\sim 120,000$ spectroscopic redshifts provides ideal data at intermediate redshifts for our analysis.
-In addition, we anchor our analysis of the intermediate redshift sample with a low redshift sample derived from SDSS.
+In addition, we anchor our analysis at intermediate redshifts with a low redshift sample derived from the Sloan Digital Sky Survey (\cite{York:2000aa}).
 
@@
 \subsection{PRIMUS} \label{sec:primus}
-For our sample at intermediate redshifts we use multiwavelength imaging and spectroscopic redshifts from PRIMUS, a faint galaxy survey with $\sim 120,000$ precise spectroscopic redshifts ($\sigma_z/(1+z) \approx 0.5 \%$) within the range $z \approx 0-1.2$.
+At intermediate redshifts we use multiwavelength imaging and spectroscopic redshifts from PRIMUS, a faint galaxy survey with $\sim 120,000$ precise spectroscopic redshifts ($\sigma_z/(1+z) \approx 0.5 \%$) within the range $z \approx 0-1.2$.
 The survey was conducted using a IMACS spectrograph on a Magellan I Baade $6.5$ m telescope with a slitmask and low dispersion prism.
@@
 \texttt{iSEDfit}, uses the redshift and the observed photometry of the galaxies to determine the statistical likelihood of a large ensemble of generated model SEDs.
-The model SEDs are generated using Flexible Stellar Population Synthesis (FSPS) models (\cite{Conroy:2010aa}) based on \cite{Chabrier:2003aa} IMF, along with other prior parameters beyond the scope of this paper.
-For details we refer readers to Section 4.1 and Appendix A.
+The model SEDs are generated using Flexible Stellar Population Synthesis (FSPS) models (\cite{Conroy:2010aa}) based on \cite{Chabrier:2003aa} IMF, along with other prior parameters discussed in Section 4.1 and Appendix A.
 of \cite{Moustakas:2013aa}.
@@
 \subsection{SDSS-GALEX} \label{sec:sdss}
-For our low redshift sample, we use spectroscopic redshifts and high fidelity $ugriz$ photometry from the SDSS Data Release 7 (DR7; \cite{Abazajian:2009aa}).
-More specifically we select galaxies from the New York University Value-Added Galaxy Catalog (SDSS VAGC) that satisfy the main sample criterion and have galaxy extinction corrected Petrosian magnitudes $14.5 < r < 17.6$ and spectroscopic redshifts within $0.01 < z < 0.2$ (\cite{Blanton:2005aa}).
-We further narrow down the SDSS VAGC sample to only galaxies with medium depth observations with total exposure time greater than $1 \; \rm{ks}$ from {\em GALEX} Release 6.
-This SDSS-{\em GALEX} sample contains $167,727$ galaxies.
+At low redshifts, we use spectroscopic redshifts and high fidelity $ugriz$ photometry from the SDSS Data Release 7 (DR7; \cite{Abazajian:2009aa}).
+More specifically we select galaxies from the New York University Value-Added Galaxy Catalog (hereafter SDSS VAGC) that satisfy the main sample criterion and have galaxy extinction corrected Petrosian magnitudes $14.5 < r < 17.6$ and spectroscopic redshifts within $0.01 < z < 0.2$ (\cite{Blanton:2005aa}).
+We further restrict the SDSS VAGC sample to only galaxies with medium depth observations with total exposure time greater than $1 \; \rm{ks}$ from {\em GALEX} Release 6.
+This leaves $167,727$ galaxies.
 
-Using the MAST/CasJobs\footnote{http://galex.stsci.edu/casjobs} interface and a $4''$ diameter search radius, we obtain the NUV and FNU photometry for the SDSS-{\em GALEX} galaxies.
+Next, we use the MAST/CasJobs\footnote{http://galex.stsci.edu/casjobs} interface and a $4''$ diameter search radius, to obtain the NUV and FNU photometry for the SDSS-{\em GALEX} galaxies.
 For optical photometry, we use the $ugriz$ bands from the SDSS \texttt{model} magnitudes scaled to the $r$-band \texttt{cmodel} magnitude.
@@
 Further details regarding the SDSS-{\em GALEX} sample photometry can be found in Section 2.4 of \cite{Moustakas:2013aa}.
-As we did with the PRIMUS data above, we use \texttt{iSEDfit} with the above observed photometry to obtain the stellar masses and star formation rates for the SDSS-{\em GALEX} sample.
+As previously done on the PRIMUS data in Section \ref{sec:primus}, we use \texttt{iSEDfit} to obtain the stellar masses and star formation rates for the SDSS-{\em GALEX} sample.
 
@@
 
-In order to quantify the effects of these photometric underestimations in our analysis, we replace our SDSS fluxes in the $ugriz$ band with $ugriz$ fluxes from the NASA-Sloan Atlas (NSA) catalog, which incorporate the background subtraction improvements presented in \cite{Blanton:2011aa} and are single-Seric fit fluxes rather than the standard SDSS \texttt{cmodel} fluxes.
-Using the ratio of the luminosity derived from the improved photometry over the luminosity derived from the standard SDSS VAGC photometry, we impose a correction on the stellar mass values obtained from \texttt{iSEDfit} assuming a constant mass-to-light ratio.
+In order to quantify the effects of these photometric underestimations in our analysis, we replace our SDSS fluxes in the $ugriz$ band with $ugriz$ fluxes from the NASA-Sloan Atlas (NSA) catalog, which incorporate the improved background subtraction presented in \cite{Blanton:2011aa} and uses single-Seric fit fluxes rather than the standard SDSS \texttt{cmodel} fluxes.
+Using the ratio of the luminosity derived from the improved photometry over the luminosity derived from the standard SDSS VAGC photometry, we impose a preliminary correction on the stellar mass values obtained from \texttt{iSEDfit} assuming a consistent mass-to-light ratio.
 This mass correction leads to a significant increase in the stellar mass function for $\mathcal{M} > 10^{11} \mathcal{M}_{\odot}$ that matches the results from \cite{Bernardi:2013aa}.
@@
 \end{figure*}
-
-Using the low redshift SDSS-{\em GALEX} and intermediate redshift PRIMUS data described above, in this section, we define our galaxy sample which will be used to compute the SMFs and QFs.
-For PRIMUS, we begin with the selection criteria imposed in \cite{Moustakas:2013aa} for their parent sample.
-We take the statistically complete {\em primary} sample from the PRIMUS data (\cite{Coil:2011aa}) and impose magnitude limits on optical selection bands as specified in \cite{Moustakas:2013aa} Table 1.
+From the low redshift SDSS-{\em GALEX} and intermediate redshift PRIMUS data, in this section, we define our mass complete galaxy sample.
+We begin by imposing the parent sample selection criteria from \cite{Moustakas:2013aa}.
+More specifically, we take the statistically complete {\em primary} sample from the PRIMUS data (\cite{Coil:2011aa}) and impose magnitude limits on optical selection bands as specified in \cite{Moustakas:2013aa} Table 1.
 These limits are in different optical selection bands and have distinct values for the five PRIMUS target fields.
 We then exclude stars and broad-line AGN to only select objects spectroscopically classified as galaxies, with high-quality spectroscopic redshifts ($Q \geq 3$).
-In addition we impose a redshift range of $ 0.2 < z < 0.8$ for the PRIMUS galaxy sample, where $ z > 0.2$ is selected due to limitations from sample variance and $ z < 0.8$ is selected due to the lack of sufficient statistics in subsamples defined below.
+Lastly, we impose a redshift range of $ 0.2 < z < 0.8$ for the PRIMUS galaxy sample, where $ z > 0.2$ is selected due to limitations from sample variance and $ z < 0.8$ is selected due to the lack of sufficient statistics in subsamples defined below.
 
@@
 Equation (1) in \cite{Moustakas:2013aa}.
-Given that our ultimate interest is in deriving the SMFs and QFs from our sample, we impose stellar mass limits in order to derive a stellar mass complete galaxy sample.
+Since we are ultimately interested in a mass complete galaxy sample to derive SMFs and QFs, next we impose stellar mass completeness limits to our galaxy sample.
 
@@
 As done in \cite{Moustakas:2013aa}, we follow \cite{Pozzetti:2010aa} to empirically determine the stellar mass completeness limits.
-For each of the target galaxies we compute $\mathcal{M}_{\rm{lim}}$ using $\rm{log} \; \mathcal{M}_{\rm{lim}} = \rm{log} \; \mathcal{M} + 0.4 ( m - m_{\rm{lim}})$, where $\mathcal{M}$ is the stellar mass of the galaxy in $\mathcal{M_{\odot}}$, $\mathcal{M}_{\rm{lim}}$ is the stellar mass of each galaxy if its magnitude was equal to the survey magnitude limit, $m$ is observed apparent magnitude in the selection band, and $m_{\rm{lim}}$ is the magnitude limit for our five fields mentioned above.
+For each of the target galaxies we compute $\mathcal{M}_{\rm{lim}}$ using $\rm{log} \; \mathcal{M}_{\rm{lim}} = \rm{log} \; \mathcal{M} + 0.4 ( m - m_{\rm{lim}})$, where $\mathcal{M}$ is the stellar mass of the galaxy in $\mathcal{M_{\odot}}$, $\mathcal{M}_{\rm{lim}}$ is the stellar mass of each galaxy if its magnitude was equal to the survey magnitude limit, $m$ is the observed apparent magnitude in the selection band, and $m_{\rm{lim}}$ is the magnitude limit for our five fields.
 We construct a cumulative distribution of $\mathcal{M}_{\rm{lim}}$ for the $15\%$ faintest galaxies in $\Delta z=0.04$ bins.
 In each of these redshift bins, we calculate the minimum stellar mass that includes $95 \%$ of the galaxies.
-Separately for quiescent and star-forming galaxies, we fit quadratic polynomials to the minimum stellar masses versus redshift (galaxies are classified into star-forming or quiescent in the following section).
+Separately for quiescent and star-forming galaxies, we fit quadratic polynomials to the minimum stellar masses versus redshift (star-forming or quiescent classification is described in the following section).
 Finally, we use the polynomials to obtain the minimum stellar masses at the center of redshift bins, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$, which are then used as PRIMUS stellar mass completeness limits.
 
-To derive the low redshift portion of our galaxy sample, we start by limiting the SDSS-{\em GALEX} data to objects within $0.0375 < z < 0.145$, a redshift range later imposed on the volume-limited Environment Defining Population (Section \ref{sec:environment}).
+For the low redshift portion of our galaxy sample, we start by limiting the SDSS-{\em GALEX} data to objects within $0.05 < z < 0.12$, a redshift range later imposed on the volume-limited Environment Defining Population (Section \ref{sec:environment}).
 To account for the targeting incompleteness of the SDSS-{\em GALEX} sample, we use the statistical weight estimates provided by the NYU-VAGC catalog.
-Furthermore, to derive a stellar mass complete sample, we impose a uniform stellar mass limit of $10^9.8 \; \mathcal{M}_{\odot}$, which is determined from the mass-to-light ratio completeness limit of the SDSS-{\em GALEX} sample within the imposed redshift limit.
+Furthermore, we determine a uniform stellar mass completeness limit of $10^{10.2} \mathcal{M}_{\odot}$ above the stellar mass-to-light ratio of the SDSS-{\rm GALEX} data within the imposed redshift limits.
+We then apply this mass limit in order to obtain our mass-complete galaxy sample at low redshift.
 
-With the stellar mass completeness limits above, we have a stellar mass complete sample derived from SDSS-{\em GALEX} and PRIMUS.
-However since our sample is derived from two different surveys, we must account for the disparity in the redshift uncertainty.
+We now have a stellar mass complete sample derived from SDSS-{\em GALEX} and PRIMUS data.
+Since our sample is derived from two different surveys, we account for the disparity in the redshift uncertainty.
 While PRIMUS provides precise spectroscopic redshifts with $\sigma_{z}/(1+z) \approx 0.5 \%$, due to the higher redshift ranges it probes the uncertainties are significantly greater than that of the SDSS-{\em GALEX} redshifts.
-The differences in redshift uncertainties becomes especially important in environment classifications (environment measurements and classification is later discussed in Section \ref{sec:environment}).
-In order to have comparable contamination in environment classifications, we apply PRIMUS redshift uncertainties to our galaxy sample selected from SDSS-{\em GALEX}.
-For each SDSS-{\em GALEX} galaxy in our sample, we compute its $\sigma_z$ by randomly sampling within three standard deviations of a normal distribution where the standard deviation is derived from the $z_{\rm{SDSS}-GALEX}$ of the galaxy, $\sigma = 0.005 (1+z_{\rm{SDSS}- GALEX})$
+In order to have comparable environment measures throughout our redshift range, we apply PRIMUS redshift uncertainties to our galaxy sample selected from SDSS-{\em GALEX}.
+For each SDSS-{\em GALEX} galaxy, we adjust its redshift by randomly sampling a normal distribution with standard deviation $\sigma = 0.005 (1+z_{\rm{SDSS}-GALEX})$, where $z_{\rm{SDSS}-GALEX}$ is the redshift of the galaxy.
 
-The absolute magnitude ($M_{r}$) versus redshift for the galaxy sample (black squares) is plotted in Figure \ref{fig:targetEDP}.
-The left-most panel corresponds to the portion of the sample derived from the SDSS-{\em GALEX} data and the rest correspond to the target sample derived from the PRIMUS data divided in bins with $\Delta z \sim 0.2$.
+We present the absolute magnitude ($M_{r}$) versus redshift for the galaxy sample (black squares) in Figure \ref{fig:targetEDP}.
+The left-most panel corresponds to the sample derived from the SDSS-{\em GALEX} data and the rest correspond to the target sample derived from the PRIMUS data divided in bins with $\Delta z \sim 0.2$.
 
 \subsection{Classifying Quiescent and Star-Forming Galaxies} \label{sec:sfq}
-With the galaxy sample defined in the previous section, we now classify the galaxies as quiescent or star-forming using an evolving cut based on specific star-formation rate utilized in \cite{Moustakas:2013aa} Section 3.2.
+We now classify our mass complete galaxy sample into quiescent or star-forming using an evolving cut based on specific star-formation rate utilized in \cite{Moustakas:2013aa} Section 3.2.
 This classification method utilizes the star-forming (SF) sequence, which is the correlation between star-formation rate (SFR) and stellar mass in star-forming galaxies observed at least until $z \sim 2$ (\cite{Noeske:2007aa}).
 The PRIMUS sample displays a well-defined SF sequence within the redshift range of our galaxy sample.
-Then using the power-law slope for the SF sequence derived by \cite{Salim:2007aa} (SFR $\propto \mathcal{M}^{0.65}$) and the minimum of the quiescent/star-forming bimodality, determined empirically, we obtain the following equation to classify the target galaxies (Equation 2 in \cite{Moustakas:2013aa}):
+Then using the power-law slope for the SF sequence from \cite{Salim:2007aa} (SFR $\propto \mathcal{M}^{0.65}$) and the minimum of the quiescent/star-forming bimodality, determined empirically, we obtain the following equation to classify the target galaxies (Equation 2 in \cite{Moustakas:2013aa}):
 \begin{equation}
@@
 \subsection{Galaxy Environment} \label{sec:environment}
-With the galaxy sample divided into quiescent and star-forming galaxies above, we now classify the galaxies into high and low density environments.
-In this section, we describe our method for measuring the environment for our galaxy sample.
-First, we define the environment of a galaxy as the number of neighboring {\em Environment Defining Population} galaxies (defined below) within a fixed aperture centered around it.
+We define the environment of a galaxy as the number of neighboring {\em Environment Defining Population} galaxies (defined below) within a fixed aperture centered around it.
 We use a fixed aperture measurement of environment because, as \cite{Muldrew:2012aa} finds in their comparison of different environment definition using simulations, it provides a better probe of the entire halo in comparison to other definitions of environment such as nearest neighbor, which provides a better tracer at inter-halo scales.
+
 For our aperture, we use a cylinder of dimensions: $R_{\rm{ap}} = 2 \; \rm{Mpc}/h$ and $H_{\rm{ap}} = 25 \; \rm{Mpc}/h$.
@@
 "Finger of God" effect).
-\cite{Cooper:2005aa} finds that $\pm 1000 \; \rm{km} \; \rm{s^{-1}}$ optimally reduces the effects of redshift space distortions and the PRIMUS redshift uncertainty at $z \sim 0.7$ corresponds to $\sigma_z < 0.01$, so aperture height of $25 \; \rm{Mpc}/h$ accounts for both of these effects.
+\cite{Cooper:2005aa} finds that $\pm 1000 \; \rm{km} \; \rm{s^{-1}}$ optimally reduces the effects of redshift space distortions.
+The PRIMUS redshift uncertainty at $z \sim 0.7$ corresponds to $\sigma_z < 0.01$, so our aperture height choice of $25 \; \rm{Mpc}/h$ accounts for both of these effects.
 Our choice of cylinder radius was motivated by scale dependence analyses in literature (\cite{Blanton:2006aa}, \cite{Wilman:2010aa}, and \cite{Muldrew:2012aa}), which suggest that galactic properties such as color and quenched fractions are dependent on halo-scale properties such as host dark matter halo mass.
@@
 Our choice of $2 \rm{Mpc}/h$ provides sufficient sample size of galaxies in dense environments, for robust statistics, while tracing galactic properties within the halo scale.
-When we extend our analysis to cylindrical apertures with $R_{\rm{ap}} = 1 \; \rm{Mpc}/h$, we find that the change does not qualitatively change our results (difference in $f_{Q} < 0.05$).
+
+%When we extend our analysis to cylindrical apertures with $R_{\rm{ap}} = 1 \; \rm{Mpc}/h$, we find that the change does not qualitatively change our results (difference in $f_{Q} < 0.05$). 
 %Similar fixed aperture methods have also been used in \cite{Croton:2005aa} for galaxies in the 2dF Galaxy Redshift 
@@
 
-Using the fixed aperture environment definition, we now measure the environment for our galaxy sample.
-First, we construct a volume limited {\em Environment Defining Population} (EDP) with absolute magnitude cut-offs ($M_{r}$) at redshift bin of $\Delta z \sim 0.2$.
+Before we measure the environment for our galaxy sample, we first construct a volume limited {\em Environment Defining Population} (EDP) with absolute magnitude cut-offs ($M_{r}$) at redshift bin of $\Delta z \sim 0.2$.
 The $M_{r}$ cut-offs for the EDP are selected such that the cumulative number density over $M_{r}$ for all redshift bins are equal.
@@
 In constructing the EDP for the PRIMUS (hereafter PRIMUS EDP) we use the same PRIMUS data used to select our galaxy sample (described in Section \ref{sec:target}).
-We restrict the PRIMUS galaxies to $0.2 < z < 0.8$ and divide them into bins of $\Delta z = 0.2$.
-Before we consider the cumulative number densities in these bins, we first determine the $M_r$ limit for the highest redshift bin ($0.6-0.8$) by examining the $M_{r}$ distribution with bin size $\Delta M_{r} = 0.25$ and select $M_{r,\rm{lim}}$ near the peak of the distribution where bins with $M_{r} > M_{r,\rm{lim}}$ have fewer galaxies than the bin at $M_{r, \rm{lim}}$.
+We again restrict the PRIMUS galaxies to $0.2 < z < 0.8$ and divide them into bins of $\Delta z = 0.2$.
+Before we consider the cumulative number densities in the redshift bins, we first determine the $M_r$ limit for the highest redshift bin ($0.6-0.8$) by examining the $M_{r}$ distribution with bin size $\Delta M_{r} = 0.25$ and select $M_{r,\rm{lim}}$ near the peak of the distribution where bins with $M_{r} > M_{r,\rm{lim}}$ have fewer galaxies than the bin at $M_{r, \rm{lim}}$.
 We conservatively choose $M_{r, \rm{lim}}(0.6 < z < 0.8)$ to be $M_{r} = -20.75$.
-Then for the lower redshift bins, we impose absolute magnitude limits ($M_{r,\rm{lim}}$) such that the cumulative number density of the bin ordered by $M_{r}$ is equal to the cumulative number density of the highest redshift bin at $M_{r, \rm{lim}}(0.6 < z < 0.8) = -20.75$.
-In these cumulative number density calculations, we account for the statistical weights of the galaxies (Section \ref{sec:primus} and \ref{sec:sdss}).
+Then for the lower redshift bins, we impose absolute magnitude limits ($M_{r,\rm{lim}}$) such that the cumulative number density, calculated with the galaxy statistical weights, of the bin ordered by $M_{r}$ is equal to the cumulative number density of the highest redshift bin at $M_{r, \rm{lim}}(0.6 < z < 0.8) = -20.75$.
 
@@
 Instead, since FUV, NUV values are not necessary for EDP, we extend the parent data of the SDSS EDP to the entire SDSS VAGC, including galaxies outside of the {\em GALEX} window function.
-Furthermore, we impose a redshift range of $0.0375-0.145$ on the SDSS EDP.
+Furthermore, we impose a redshift range of $0.05-0.12$ on the SDSS EDP.
 This redshift range was empirically determined to account for the lack of faint galaxies at $z \sim 0.2$ and the lack of bright galaxies at $z \sim 0.01$ in the SDSS VAGC.
 The lower bound was determined by the bright limit and the upper bound by the faint limit of the $M_r$ versus redshift distribution.
-As with the PRIMUS redshift bins, we determine the SDSS EDP $M_{r; \rm{lim}}$ by matching the cumulative number density of the highest redshift bin.
-We get $M_{r,\rm{lim}} = -20.57$, $-20.73$, $-20.80$ and $-20.95$ for the redshift bins $0.0375-0.145$, $0.2-0.4$, $0.4-0.6$, $0.6-0.8$, respectively.
+As with the PRIMUS redshift bins, we determine the SDSS EDP $M_{r, \rm{lim}}$ by matching the cumulative number density of the highest redshift bin.
+For redshift bins $0.05-0.12$, $0.2-0.4$, $0.4-0.6$, $0.6-0.8$ we get $M_{r,\rm{lim}} = -20.57$, $-20.73$, $-20.80$ and $-20.95$, respectively.
 These absolute magnitude limits are illustrated in Figure \ref{fig:targetEDP}, which show clear $M_r$ cutoffs in the $M_{r}$ distribution versus redshift for the EDP (red circles) on top of the target galaxy sample (black).
 
-Finally we measure the environment for each galaxy in our sampling by counting the number of EDP galaxies, $n_{\rm{env}}$ with $RA$, $Dec$, and $z$ within our cylindrical aperture centered around it.
-Note that $n_{\rm{env}}$ accounts for the statistical weights of the EDP galaxies.
+For our SDSS-{\em GALEX} galaxy sample, in Section \ref{sec:target}, we imposed PRIMUS redshift errors in order to establish a consistent measurement of environment throughout our redshift range.
+We appropriately impose equivalent redshift adjustments for the SDSS EDP.
+So for the SDSS EDP galaxies that are within the SDSS-{\em GALEX} sample, we adjust the redshift by an identical amount.
+For the rest, we apply the same redshift adjustment procedure described in Section \ref{sec:target} in order to obtain PRIMUS level redshift uncertainties.
+
+Finally we measure the environment for each galaxy in our galaxy sample by counting the number of EDP galaxies, $n_{\rm{env}}$ with $RA$, $Dec$, and $z$ within our cylindrical aperture centered around it.
+$n_{\rm{env}}$ accounts for the statistical weights of the EDP galaxies.
 Once we obtain environment measurements for all the galaxies in our galaxy sample, we classify galaxies with $n_{\rm{env}} < 1$ to be "low" environment density and galaxies with $n_{\rm{env}} > 3$ to be "high" environment densities.
@@
 
-The analysis we describe below uses a fixed cylindrical aperture with dimensions $R_{\rm{ap}} = 2 \: \rm{Mpc}$ and $H_{\rm{ap}} = 25 \: \rm{Mpc}$ to measure environment; the same analysis was extended for varying aperture dimensions $R_{\rm{ap}} = 1, 2, 3 \: \rm{Mpc}$ and $H_{\rm{ap}} = 25, 50 \: \rm{Mpc}$.
-Minor adjustments to the environment classification thresholds were adopted in these analyses for the smaller apertures ($r_{\rm{ap}} = 0.5, 1 \rm{Mpc}$ and $r_{\rm{ap}} = 25 \rm{Mpc}$).
-The results obtained from using these different are consistent with the results later discussed in this paper.
-
+The analysis we describe below uses a fixed cylindrical aperture with dimensions $R_{\rm{ap}} = 2 \: \rm{Mpc}$ and $H_{\rm{ap}} = 25 \: \rm{Mpc}$ to measure environment.
+The same analysis was extended for varying aperture dimensions $R_{\rm{ap}} = 1, 2, 3 \: \rm{Mpc}$ and $H_{\rm{ap}} = 25, 50 \: \rm{Mpc}$.
+We also adjusted the environment classification thresholds for these analyses.
+The results obtained from using different apertures and environment classification thresholds are consistent with the results later presented.
 \begin{figure*}
@@
 In this case, $n_{env}$ only reflects the fraction of the environment within the survey geometry.
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%% CONTINUE EDITING!%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 To account for these edge effects, we use a Monte Carlo method to impose edge cutoffs on our galaxy sample.
@@
 
+\section{Discussion} \label{sec:discussion}
+
 \section{Summary} \label{sec:summary}

### 2014-08-05 qfenv_paper/qf_environment.tex
Further edits and new envcount dist figure

@@
 Finally in Section \ref{sec:edgeeffect}, we correct our galaxy sample and environment measurements for edge effects of the surveys. 
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% PRIMUS
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{PRIMUS} \label{sec:primus}
@@
 	\plotone{fig_edp_sdss_z005_012_primus_z02_10_Mr_redshift.png}
-        \caption{Absolute magnitude $M_{r}$ versus redshift for the target galaxy population (black squares) with the Environment Defining Population (red circles) plotted on top.
-Both samples are divided into redshift bins:$z \approx 0.0375-0.145$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ (panels left to right).
-Stellar mass completeness limits are imposed on the target galaxy population (Section \ref{sec:target}) while the $M_{r}$ limits are imposed on the EDP (Section \ref{sec:environment}).
-The lowest redshift bin ($z \approx 0.0375-0.145$; leftmost panel) contain our galaxy sample and EDP selected from SDSS.
-The rest contain galaxies and EDP selected from PRIMUS.} \label{fig:targetEDP}
+        \caption{Absolute magnitude $M_{r}$ versus redshift for our mass complete galaxy sample (black squares) with the Environment Defining Population (red circles) plotted on top.
+Both samples are divided into redshift bins:$z \approx 0.05-0.12$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ (panels left to right).
+The lowest redshift bin ($z \approx 0.05-0.12$; leftmost panel) contain our galaxy sample and EDP selected from SDSS.
+The rest contain galaxies and EDP selected from PRIMUS.
+The redshift limits for the lowest redshift bin are empirically selected based on the bright and faint limits of SDSS galaxies.
+Stellar mass completeness limits, specified in Section \ref{sec:target}, are imposed on the galaxy population.
+Meanwhile, $M_{r}$ limits are applied to the EDP such that the number density in each panel are equivalent (Section \ref{sec:environment}).} \label{fig:targetEDP}
     \end{center}
 \end{figure*}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% SDSS-GALEX
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{SDSS-GALEX} \label{sec:sdss}
@@
 The effects of the discussed photometry methods on the luminosity function and stellar mass function will be examined in detail in future work.
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% GALAXY SAMPLE
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Galaxy Sample} \label{sec:target} 
@@
     \epsfig{file=fig_envcount_cylr2h25_thresh75_sdss_z0_05_0_12_primuszerr_masslimit_histogram.png,height=0.5\textwidth}
-     \caption{Environment measure distribution for our galaxy sample.}      \label{fig:envcount}
+     \caption{Normalized distribution of environment measurements ($n_{\rm{env}}$) for our mass complete galaxy sample.
+The star-forming galaxies contribution to the distribution is colored blue and diagonally patterned.
+The contribution of the distribution from quiescent galaxies is colored in red.
+Each redshift panel is divided into three sections of by the environment classification threshold (vertical black lines): low density environment $n_{\rm{env}} < 1.5$ and high density environment $n_{\rm{env}} > 3.5$.
+The percentages of the redshift bin contained in the environment classifications are presented above the distribution.
+For example at $0.2 < z < 0.4$, $56.0 \%$ of galaxies in the redshift bin have low density environments while $29.0\%$ of galaxies in the redshift bin have high density environments.
+}      \label{fig:envcount}
     \end{center}
 \end{figure*}
+
 From the low redshift SDSS-{\em GALEX} and intermediate redshift PRIMUS data, in this section, we define our mass complete galaxy sample.
@@
 The left-most panel corresponds to the sample derived from the SDSS-{\em GALEX} data and the rest correspond to the target sample derived from the PRIMUS data divided in bins with $\Delta z \sim 0.2$.
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% CLASSIFYING QUIESCENT AND STAR-FORMING GALAXIES
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Classifying Quiescent and Star-Forming Galaxies} \label{sec:sfq}
@@
 \end{figure*}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% GALAXY ENVIRONMENT
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Galaxy Environment} \label{sec:environment}
@@
 \end{figure*}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% EDGE EFFECTS
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Edge Effects} \label{sec:edgeeffect}
@@
 In this case, $n_{env}$ only reflects the fraction of the environment within the survey geometry.
+
+To account for these edge effects, we use a Monte Carlo method to impose edge cutoffs on our galaxy sample.
+We first construct a \texttt{ransack} sample of  $N_{\rm{ransack}} = 1,000,000$ points with $RA$ and $Dec$ randomly selected within the window function of the EDP (so SDSS EDP and PRIMUS EDP separately).
+We then compute the angular separation, $\theta_{i, \rm{ap}}$ that corresponds to $R_{\rm{ap}}$ (Section \ref{sec:environment}) at the redshift of each sample galaxy $i$.
+For each sample galaxy we count the number of \texttt{ransack} points within $\theta_{i, \rm{ap}}$ of the galaxy: $n_{i,\rm{ransack}}$.
+Afterwards, we compare $n_{i,\rm{ransack}}$ to the expected value computed from the angular area of the environment defining aperture and the EDP window function:
+\begin{equation} \label{eq:ransack}
+E_{i}[n_{\rm{ransack}}] = \frac{N_{\rm{ransack}}}{A_{\rm{EDP}}}\times {\pi \theta_{i, \rm{ap}}^2} \times f_{\rm{thresh}}. 
+\end{equation} 
+$A_{\rm{EDP}}$ is the total angular area of the EDP window function and $f_{\rm{thresh}}$ is the fractional threshold for the edge effect cut-off.
+For $R_{\rm{ap}}= 2\;\rm{Mpc}$, $f_{\rm{thresh}} = 0.75$.
+If $n_{i, \rm{ransack}} > E_{i}[n_{\rm{ransack}}]$ then galaxy $i$ remains in our sample; otherwise, it is discarded.
+
+Once the edge effect cuts are applied, we are left with the final galaxy sample.
+In Figure \ref{fig:envcount} we present the distribution of environment measurements ($n_{\rm{env}}$) for our final galaxy sample in redshift bins: $0.05 - 0.12$, $0.2 - 0.4$, $0.4-0.6$, and $0.6-0.8$.
+The quiescent galaxy contributions are colored in red while the star-forming galaxy contributions are colored in blue and patterned.
+The low and high density environment classifications are represented by black vertical lines that divide the distribution at $n_{\rm{env}} = 1.5$ and $n_{\rm{env}} = 3.5$.
+The percentage of the total galaxies in the redshift bin that are in these environment densities are labeled on the figure.
+
+Although we imposed PRIMUS redshift errors on our SDSS galaxies in order to consistently measure environment throughout our entire sample, we note a significant discrepancy between the SDSS and PRIMUS samples in the fractional contribution of each environment classification within the redshift bin.
+For each of the PRIMUS redshift bins, approximately $50 \%$ of galaxies in the redshift bin are in low density environments and roughly $30 \%$ are in high density environments.
+In contrast, in the SDSS redshift bin, $38 \%$ of galaxies in the redshift bin are in low density environments and $45 \%$ are in high density environments.
+We remind the reader that this is due to the different mass-completeness limits imposed on our galaxy sample for each redshift bins.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%% CONTINUE EDITING!%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-To account for these edge effects, we use a Monte Carlo method to impose edge cutoffs on our galaxy sample.
-We begin by computing the angular separation, $\theta_{\rm{ap}}$ that corresponds to the radius of the fixed aperture (used to measure environment) at the redshifts of the galaxies.
-Then we compute the environment, $n_{\rm{ransack}}$, of our galaxy sample with the EDP replaced by a \texttt{ransack} sample of $N_{\rm{ransack}} = 1,000,000$ points with $RA$ and $Dec$ randomly selected within the window function of the EDP.
-We compare the $n_{\rm{ransack}}$ values to the expected value computed based on the angular area of the environment defining aperture and the EDP window function:
-\begin{equation} \label{eq:ransack}
-E[n_{\rm{ransack}}] = \frac{N_{\rm{ransack}}}{A_{\rm{EDP}}}\times {\pi \theta_{\rm{ap}}^2} \times f_{\rm{thresh}}. 
-\end{equation} 
-$A_{\rm{EDP}}$ is the total angular area of the EDP window function and $f_{\rm{thresh}}$ is the fractional threshold for the edge effect cut-off, which we vary based on $R_{\rm{ap}}$ (listed in Table \ref{tab:aperture}).
-If $n_{\rm{ransack}}$ for a target galaxy is greater than $E[n_{\rm{ransack}}]$ then the galaxy remains in our sample; otherwise, it is discarded.
-
+% STELLAR MASS FUNCTION
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Stellar Mass Function} \label{sec:smf}
-The target galaxy sample defined above has so far been classified into quiescent or star-forming and low or high density environments.
-We further divide these subsamples into redshift bins: $0.0375-0.145$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ for a total 16 subsamples.
+Our galaxy sample has so far been classified into quiescent or star-forming and low or high density environments.
+We further divide these subsamples into redshift bins: $0.05-0.12$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ for a total 16 subsamples.
 In this section, we calculate the SMF for each of these subsamples.
@@
 \end{equation}
+$w_i$ is the statistical weight of galaxy $i$ and $\Phi(\rm{log}\: \mathcal{M}) \Delta(\rm{log}\: \mathcal{M})$ is the number of galaxies ($N$) per unit volume within the stellar mass range $[\rm{log} \:\mathcal{M}, \rm{log} \:\mathcal{M}+\Delta(\rm{log} \:\mathcal{M})]$.
 The equation above is same as Equation 3.
 in \cite{Moustakas:2013aa} except that we use $V_{\rm{max,avail}}$ instead than $V_{\rm{max}}$, to account for the edge effects of the survey discussed in Section \ref{sec:edgeeffect}.
-$w_i$ is the statistical weight of galaxy $i$ and $\Phi(\rm{log}\: \mathcal{M}) \Delta(\rm{log}\: \mathcal{M})$ is the number of galaxies ($N$) per unit volume within the stellar mass range $[\rm{log} \:\mathcal{M}, \rm{log} \:\mathcal{M}+\Delta(\rm{log} \:\mathcal{M})]$.
 
@@
 
-To calculate $V_{\rm{max,avail},i}$, we generate a sample of points with random $RA$, $Dec$ within the window function of our galaxy sample (SDSS-{\em GALEX} window function and the five PRIMUS fields) and random $z$ within the redshift range.
-This is not to be confused with the \texttt{ransack} sample in Section \ref{sec:edgeeffect}.
-We then impose the same edge effect cutoffs we applied to our galaxy sample, using the same \texttt{ransack} environment calculation method, also discuseed in Section \ref{sec:edgeeffect}.
-At redshift bins of $\Delta z \sim 0.01$, we compute the fraction of random points that remain in the bin after the edge effect cutoffs: $f_{\rm{edge}}$.
+To calculate $V_{\rm{max,avail},i}$, we use a similar Monte Carlo method as the edge effect cutoffs in Section \ref{sec:edgeeffect}.
+First, we generate a sample of points with random $RA$, $Dec$ within the window function of our galaxy sample (SDSS-{\em GALEX} window function and the five PRIMUS fields) and random $z$ within the redshift range.
+These points are not to be confused with the \texttt{ransack} sample in Section \ref{sec:edgeeffect}.
+We apply the edge effect cutoffs on these random points as we did for our galaxy sample using the same \texttt{ransack} method in Section \ref{sec:edgeeffect}.
+At redshift bins of $\Delta z \sim 0.01$, we calculate the fraction of the random points that remain in the bin after the edge effect cutoffs over the total number of random points in the bin: $f_{\rm{edge}}$.
 We then apply this factor to compute $V_{\rm{max,avail}} = V_{\rm{max}} \times f_{\rm{edge}}$.
@@
 
-In order to calculate the uncertainty of the SMFs from the sample variance, we use a standard jackknife technique (as done in \cite{Moustakas:2013aa}).
+To calculate the uncertainty of the SMFs from the sample variance, we use a standard jackknife technique (as done in \cite{Moustakas:2013aa}).
 For the PRIMUS galaxies, we calculate SMFs after excluding one of the five target fields at a time.
-For the SDSS target galaxies we divide the field into a 12 $\times$ 9 rectangular $RA$ and $Dec$ grid and calculate the SMFs after excluding one grid each time.
-Using the calculated SMFs we calculate the uncertainty:
+For the SDSS target galaxies we divide the field into a 12 $\times$ 9 rectangular $RA$ and $Dec$ grid and calculate the SMFs after excluding one grid at a time.
+From the calculated SMFs we calculate the uncertainty:
 \begin{equation}
@@
 \end{equation} 
-$M$ in this equation is the number of jack knife SMFs in the stellar mass bin. $\langle \Phi^j \rangle$ is the mean number density of galaxies 
-in each stellar mass bin for all of the jack knife $\Phi^j$s.
+$M$ in this equation is the number of jack knife SMFs in the stellar mass bin.
+$\langle \Phi^j \rangle$ is the mean number density of galaxies in each stellar mass bin for all of the jack knife $\Phi^j$s.
 
-In Figure \ref{fig:smf}, we present the SMFs for 16 target galaxy subsamples classified into quiescent/star-forming (orange/blue, bottom/top panels) and high/low environment density (left/right panels).
+In Figure \ref{fig:smf}, we present the SMFs of the quiescent/star-forming (orange/blue, bottom/top panels) and high/low density environment (left/right panels) subsamples.
 The redshift evolution of the SMFs in each of these panels are indicated by a darker shade for lower redshift bins.
-The sample variance uncertainties are illustrated through the width of the SMFs.
+The width of the SMFs represent the sample variance uncertainties.
 
-Although we imposed PRIMUS redshift errors on our SDSS galaxies in order to consistently measure environment throughout our entire sample, we observe a significant discrepancy between the SDSS and PRIMUS samples in the fractional contribution of each environment classification within the redshift bin.
-For each of the PRIMUS redshift bins, approximately $50 \%$ of galaxies in the redshift bin are in low density environments and roughly $30 \%$ are in high density environments.
-In contrast, in the SDSS redshift bin, $38 \%$ of galaxies in the redshift bin are in low density environments and $45 \%$ are in high density environments.
 As a result, we caution that the SMF redshift evolution is inconsistent during the transition from the PRIMUS sample to the SDSS sample at $z \sim 0.2$.

### 2014-08-07 qfenv_paper/qf_environment.tex
Moved things to discussion section
SMF evol section

@@
 Daniel Eisenstein\altaffilmark{4},
-John Moustakas\altaffilmark{4}, 
-Ken Wong\altaffilmark{3}, 
-Guangtun Zhu\altaffilmark{3}
+John Moustakas\altaffilmark{5}, 
+Ken Wong\altaffilmark{6}, 
+Guangtun Zhu\altaffilmark{7}
 }
@@
 \altaffiltext{4}{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
-
+\altaffiltext{5}{Department of Physics and Astronomy, Siena College, 515 Loudon Road, Loudonville, NY 12211}
+\altaffiltext{6}{Steward Observatory, University of Arizona, 933 North Cherry Avenue, Tucson, AZ 85721} 
+\altaffiltext{7}{Department of Physics and Astronomy, The Johns Hopkins University, 3400 North Charles Street, Baltimore, MD 21218} 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% ABSTRACT
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{abstract}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% INTRODUCTION
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
@@
 We further divide these subsamples into redshift bins: $0.05-0.12$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ for a total 16 subsamples.
-In this section, we calculate the SMF for each of these subsamples.
+In Section \ref{sec:smfcalc}, we calculate the SMF for each of these subsamples.
+Then we examine the evolution of active and quiescent subsample SMFs in different environments in Section \ref{sec:smfevol}.
 
+\subsection{Stellar Mass Function Calculations} \label{sec:smfcalc} 
 To calculate the SMFs we employ a non-parametric $1/{V_{\rm{max}}}$ estimator commonly used for galaxy luminosity functions and stellar mass functions, as done in \cite{Moustakas:2013aa} and discussed in the review \cite{Johnston:2011aa}.
@@
 
+\subsection{Evolution of the Stellar Mass Function in Different Environments} \label{sec:smfevol}
 In Figure \ref{fig:smf}, we present the SMFs of the quiescent/star-forming (orange/blue, bottom/top panels) and high/low density environment (left/right panels) subsamples.
@@
 The width of the SMFs represent the sample variance uncertainties.
+%%%%%%% REWRITE AFTER REVISED SMF RESULTS
+%As a result, we caution that the SMF redshift evolution is inconsistent during the transition from the PRIMUS sample to the SDSS sample at $z \sim 0.2$.
 
-As a result, we caution that the SMF redshift evolution is inconsistent during the transition from the PRIMUS sample to the SDSS sample at $z \sim 0.2$.
-
-Yet, from the PRIMUS samples alone, we probe a sufficient redshift to observe notable trends in the SMF evolution for each of the panels in Figure \ref{fig:smf}.
-Later we compare these trends to SMF results from DEEP2 (\cite{bundy06a}) and zCOSMOS (\cite{Bolzonella:2010aa}).
+%Yet, from the PRIMUS samples alone, we probe a sufficient redshift to observe notable trends in the SMF evolution for each of the panels in Figure \ref{fig:smf}. 
 In panel (a), star-forming galaxies in low density environments, we find a significant decrease in the high mass end of the SMF ($\mathcal{M} > 10^{10.75} \mathcal{M}_{\odot}$).
@@
 
-We caution readers and reserve detailed analysis of the SMFs to future work due to the improvements in photometry that significantly alter the SDSS SMFs mentioned in Section \ref{sec:sdss}. 
+%We caution readers and reserve detailed analysis of the SMFs to future work due to the improvements in photometry that significantly alter the SDSS SMFs mentioned in Section \ref{sec:sdss}. 
 % There is also the issue with the SMF evolution: the uneven fractional contribution of the population and each environment classification.
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% QUIESCENT FRACTION
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Quiescent Fraction} \label{sec:qf_const}
@@
 
-Finally, we compare our $f_{\rm{Q}}$ results to previous $f_{\rm{Q}}/f_{\rm{red}}$ measurements for analogous environment classifications.
-For our lowest redshift bin, we find that our $f_{\rm{Q}}$ values for low and high environments are consistent with previous $f_{\rm{Q}}/f_{\rm{red}}$ measurements for SDSS galaxies as a function of environment.
-For example, \cite{Tinker:2011aa}, using a group-finding algorithm on the SDSS DR7, presents the relationship between $f_{\rm{Q}}$ and overdensity for galaxies within the mass range $\rm{log} \; \mathcal{M} = [9.8, 10.1]$.
-The \cite{Tinker:2011aa} $f_{\rm{Q}}$ at the lowest and highest overdensities, $f_{\rm{Q}} \sim 0.4$ and $f_{\rm{Q}} \sim 0.6$ respectively, are consistent with our $f_{\rm{Q}}$ for low and high density environment at the lowest mass bin ($\rm{log} \; \mathcal{M} \sim 10.2$).
-At higher masses, our $f_{\rm{Q}}$ results are consistent with \cite{Baldry:2006aa}.
-\cite{Baldry:2006aa} uses project neighbor density environment measures ($\rm{log} \;  \Sigma$) to obtain $f_{\rm{Q}}(\mathcal{M})$ for a range of environmental densities.
-Although the different environment measurements make a direct comparison unclear, at higher environments ($\rm{log} \; \Sigma > 0.2$) in \cite{Baldry:2006aa} $f_{\rm{Q}} \sim 0.6$ at $\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}$ and $f_{\rm{Q}} \sim 0.9$ at $\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}$, in agreement our high density environment.
-Likewise, for lower environments in \cite{Baldry:2006aa} ($\rm{log} \; \Sigma < -0.4$) $f_{\rm{Q}} \sim 0.4$ at $\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}$ and $f_{\rm{Q}} \sim 0.8$ at $\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}$, which also agree with our low density environment $f_{\rm{Q}}$.
-
-For $z > 0.2$, we compare our PRIMUS $f_{\rm{Q}}$ results to the $f_{\rm{red}}$ (or $1-f_{\rm{blue}}$) results from the zCOSMOS Redshift Survey (\cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, \cite{Kovac:2014aa}), which approximately covers the same redshift range as PRIMUS.
-\cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, and \cite{Kovac:2014aa} using a mass-complete galaxy sample derived from zCOSMOS and a group catalog, 3D local density contrast, and overdensity environment measurements, respectively, compare $f_{\rm{red}}$ with respect to environment.
-The $f_{\rm{blue}}$ for group and isolated galaxies from \cite{Iovino:2010aa} are generally inconsistent with our $1-f_{\rm{Q}}$ for high and low density environments.
-Similarly, $f_{\rm{red}}$ for high and low overdensities in \cite{Kovac:2014aa} are  greater overall than the PRIMUS $f_{\rm{Q}}$ values in high and low density environments.
-However, \cite{Kovac:2014aa} points out that there is a significant difference between classifying the quenched population using color and SFR.
-$f_{\rm{Q}}$ defined by color is greater than $f_{\rm{Q}}$ defined by SFR by roughly $0.2$.
-Although the propagation of this difference for different environments is not explored in \cite{Kovac:2014aa}, if we account for the difference evenly for $f_{\rm{red}}$ at all environments, the \cite{Kovac:2014aa} results are generally consistent with our $f_{\rm{Q}}$ at high and low density environments.
-
-Additionally, the zCOSMOS results indicate that the $f_{\rm{red}}$ values in high density environments are greater overall than in low density environments.
-The same trend is observed in the PRIMUS results and will be discussed in detail later in the section.
-Another significant trend observed in the zCOSMOS results is the significant mass dependence of the $f_{\rm{red}}$ and $f_{\rm{blue}}$ evolution.
-\cite{Iovino:2010aa} by examining $f_{\rm{blue}}(z)$ in different mass bins for group and isolated galaxies find significantly larger $f_{\rm{blue}}$ evolution at lower masses.
-In fact, \cite{Iovino:2010aa} finds no evolution in $f_{\rm{blue}}$ for $\mathcal{M} > 10^{10.9} \mathcal{M}_{\odot}$ for both group and isolated galaxies over the redshift range $0.4 < z < 0.9$.
-On the other hand, in the lowest mass bin ($10^{10.0} \mathcal{M}_{\odot} < \mathcal{M} < 10^{10.5} \mathcal{M}_{\odot}$) \cite{Iovino:2010aa} finds $f_{\rm{blue}}(z \sim 0.4) - f_{\rm{blue}}(z \sim 0.2) \sim 0.2$ for isolated galaxies and  $f_{\rm{blue}}(z \sim 0.4) - f_{\rm{blue}}(z \sim 0.2) \sim 0.1$ for group galaxies.
-In contrast, in each of the panels of Figure \ref{fig:qf}, we qualitatively find little mass dependence on the $f_{\rm{Q}}$ evolution for either low or high density environments.
-However, due to the distinct stellar mass completeness limits imposed at each redshift bin of our sample, subtle effects such as the mass dependence of the $f_{\rm{Q}}$ evolution are difficult to discern.
-
-In order to more quantitatively compare the $f_{\rm{Q}}$ evolution, we fit $f_{\rm{Q}}$ for each subsample to a power-law parameterization as a function of stellar mass, 
 \begin{figure}
@@
 
+In order to more quantitatively compare the $f_{\rm{Q}}$ evolution, we fit $f_{\rm{Q}}$ for each subsample to a power-law parameterization as a function of stellar mass, 
 \begin{equation} 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% DISCUSSION
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Discussion} \label{sec:discussion}
+
+Finally, we compare our $f_{\rm{Q}}$ results to previous $f_{\rm{Q}}/f_{\rm{red}}$ measurements for analogous environment classifications.
+For our lowest redshift bin, we find that our $f_{\rm{Q}}$ values for low and high environments are consistent with previous $f_{\rm{Q}}/f_{\rm{red}}$ measurements for SDSS galaxies as a function of environment.
+For example, \cite{Tinker:2011aa}, using a group-finding algorithm on the SDSS DR7, presents the relationship between $f_{\rm{Q}}$ and overdensity for galaxies within the mass range $\rm{log} \; \mathcal{M} = [9.8, 10.1]$.
+The \cite{Tinker:2011aa} $f_{\rm{Q}}$ at the lowest and highest overdensities, $f_{\rm{Q}} \sim 0.4$ and $f_{\rm{Q}} \sim 0.6$ respectively, are consistent with our $f_{\rm{Q}}$ for low and high density environment at the lowest mass bin ($\rm{log} \; \mathcal{M} \sim 10.2$).
+At higher masses, our $f_{\rm{Q}}$ results are consistent with \cite{Baldry:2006aa}.
+\cite{Baldry:2006aa} uses project neighbor density environment measures ($\rm{log} \;  \Sigma$) to obtain $f_{\rm{Q}}(\mathcal{M})$ for a range of environmental densities.
+Although the different environment measurements make a direct comparison unclear, at higher environments ($\rm{log} \; \Sigma > 0.2$) in \cite{Baldry:2006aa} $f_{\rm{Q}} \sim 0.6$ at $\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}$ and $f_{\rm{Q}} \sim 0.9$ at $\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}$, in agreement our high density environment.
+Likewise, for lower environments in \cite{Baldry:2006aa} ($\rm{log} \; \Sigma < -0.4$) $f_{\rm{Q}} \sim 0.4$ at $\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}$ and $f_{\rm{Q}} \sim 0.8$ at $\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}$, which also agree with our low density environment $f_{\rm{Q}}$.
+
+For $z > 0.2$, we compare our PRIMUS $f_{\rm{Q}}$ results to the $f_{\rm{red}}$ (or $1-f_{\rm{blue}}$) results from the zCOSMOS Redshift Survey (\cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, \cite{Kovac:2014aa}), which approximately covers the same redshift range as PRIMUS.
+\cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, and \cite{Kovac:2014aa} using a mass-complete galaxy sample derived from zCOSMOS and a group catalog, 3D local density contrast, and overdensity environment measurements, respectively, compare $f_{\rm{red}}$ with respect to environment.
+The $f_{\rm{blue}}$ for group and isolated galaxies from \cite{Iovino:2010aa} are generally inconsistent with our $1-f_{\rm{Q}}$ for high and low density environments.
+Similarly, $f_{\rm{red}}$ for high and low overdensities in \cite{Kovac:2014aa} are  greater overall than the PRIMUS $f_{\rm{Q}}$ values in high and low density environments.
+However, \cite{Kovac:2014aa} points out that there is a significant difference between classifying the quenched population using color and SFR.
+$f_{\rm{Q}}$ defined by color is greater than $f_{\rm{Q}}$ defined by SFR by roughly $0.2$.
+Although the propagation of this difference for different environments is not explored in \cite{Kovac:2014aa}, if we account for the difference evenly for $f_{\rm{red}}$ at all environments, the \cite{Kovac:2014aa} results are generally consistent with our $f_{\rm{Q}}$ at high and low density environments.
+
+Additionally, the zCOSMOS results indicate that the $f_{\rm{red}}$ values in high density environments are greater overall than in low density environments.
+The same trend is observed in the PRIMUS results and will be discussed in detail later in the section.
+Another significant trend observed in the zCOSMOS results is the significant mass dependence of the $f_{\rm{red}}$ and $f_{\rm{blue}}$ evolution.
+\cite{Iovino:2010aa} by examining $f_{\rm{blue}}(z)$ in different mass bins for group and isolated galaxies find significantly larger $f_{\rm{blue}}$ evolution at lower masses.
+In fact, \cite{Iovino:2010aa} finds no evolution in $f_{\rm{blue}}$ for $\mathcal{M} > 10^{10.9} \mathcal{M}_{\odot}$ for both group and isolated galaxies over the redshift range $0.4 < z < 0.9$.
+On the other hand, in the lowest mass bin ($10^{10.0} \mathcal{M}_{\odot} < \mathcal{M} < 10^{10.5} \mathcal{M}_{\odot}$) \cite{Iovino:2010aa} finds $f_{\rm{blue}}(z \sim 0.4) - f_{\rm{blue}}(z \sim 0.2) \sim 0.2$ for isolated galaxies and  $f_{\rm{blue}}(z \sim 0.4) - f_{\rm{blue}}(z \sim 0.2) \sim 0.1$ for group galaxies.
+In contrast, in each of the panels of Figure \ref{fig:qf}, we qualitatively find little mass dependence on the $f_{\rm{Q}}$ evolution for either low or high density environments.
+However, due to the distinct stellar mass completeness limits imposed at each redshift bin of our sample, subtle effects such as the mass dependence of the $f_{\rm{Q}}$ evolution are difficult to discern.
+
 Many physical mechanisms have been proposed to explain the quenching of star-formation observed in our universe.
@@
 % What does this have to say about physical processes in groups and clusters that affect quenching?
-
-\section{Discussion} \label{sec:discussion}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% SUMMARY
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Summary} \label{sec:summary}

### 2014-08-11 qfenv_paper/qf_environment.tex
updated plots and text

@@
 Throughout the paper we assume cosmology with $\Omega_{m} = 0.3, \Omega_{\Lambda} = 0.7$, and $H_0 = 70 \rm{km} \; \rm{s}^{-1} \rm{Mpc}^{-1}$.
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% SAMPLE SELECTION
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Sample Selection} \label{sec:sample}
@@
 Finally in Section \ref{sec:edgeeffect}, we correct our galaxy sample and environment measurements for edge effects of the surveys.
+
+\begin{figure*}
+    \begin{center}
+        \leavevmode
+        \epsscale{1.2}
+	\plotone{fig_edp_sdss_z005_012_primus_z02_10_Mr_redshift.png}
+        \caption{Absolute magnitude $M_{r}$ versus redshift for our mass complete galaxy sample (black squares) with the Environment Defining Population (red circles) plotted on top.
+Both samples are divided into redshift bins:$z \approx 0.05-0.12$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ (panels left to right).
+The lowest redshift bin ($z \approx 0.05-0.12$; leftmost panel) contain our galaxy sample and EDP selected from SDSS.
+The rest contain galaxies and EDP selected from PRIMUS.
+The redshift limits for the lowest redshift bin are empirically selected based on the bright and faint limits of SDSS galaxies.
+Stellar mass completeness limits, specified in Section \ref{sec:target}, are imposed on the galaxy population.
+Meanwhile, $M_{r}$ limits are applied to the EDP such that the number density in each panel are equivalent (Section \ref{sec:environment}).} \label{fig:targetEDP}
+    \end{center}
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
     $z$ &Environment        &Quiescent  &Star-forming  \\ \hline 
-$0.0375-0.145$ &High           &5470                       &4501                           \\
-               &Low            &5419                       &8927                           \\
+$0.05-0.12$ &Low           &12859                       &14443                           \\
+               &High            &18952                       &13387                           \\ 
                               &               &                       &                           \\ \hline
-$0.2-0.4$      &High           &322                    &583                           \\
-               &Low            &768                    &2516                           \\
+$0.2-0.4$      &Low           &1158                    &3445                           \\
+               &High            &817                    &1531                           \\
                &               &                       &                           \\ \hline
-$0.4-0.6$      &High           &350                       &675                           \\
-               &Low            &871                       &2385                           \\
+$0.4-0.6$      &Low           &1315                       &3390                           \\
+               &High            &848                       &1499                           \\
                &               &                       &                           \\ \hline
-$0.6-0.8$      &High           &347                       &430                           \\
-               &Low            &833                       &1847                           \\
+$0.6-0.8$      &Low           &1158                       &2303                           \\
+               &High            &900                       &1275                           \\
                &               &                       &                           \\ \hline
   \multicolumn{4}{l}{}                                             \\       
-    \end{tabular} 
+    \end{tabular} \par
+    \bigskip 
+    {\bf Notes}: Number of galaxies in the mass complete subsamples derived in Section \ref{sec:sample}.
+The subsamples are classified based on environment and star formation rate.
+The lowest redshift bin is derived from SDSS; the rest are from PRIMUS.
   \end{center}
@@
 
-\begin{figure*}
-    \begin{center}
-        \leavevmode
-        \epsscale{1.2}
-	\plotone{fig_edp_sdss_z005_012_primus_z02_10_Mr_redshift.png}
-        \caption{Absolute magnitude $M_{r}$ versus redshift for our mass complete galaxy sample (black squares) with the Environment Defining Population (red circles) plotted on top.
-Both samples are divided into redshift bins:$z \approx 0.05-0.12$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ (panels left to right).
-The lowest redshift bin ($z \approx 0.05-0.12$; leftmost panel) contain our galaxy sample and EDP selected from SDSS.
-The rest contain galaxies and EDP selected from PRIMUS.
-The redshift limits for the lowest redshift bin are empirically selected based on the bright and faint limits of SDSS galaxies.
-Stellar mass completeness limits, specified in Section \ref{sec:target}, are imposed on the galaxy population.
-Meanwhile, $M_{r}$ limits are applied to the EDP such that the number density in each panel are equivalent (Section \ref{sec:environment}).} \label{fig:targetEDP}
-    \end{center}
-\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The results obtained from using different apertures and environment classification thresholds are consistent with the results later presented.
-\begin{figure*}
-    \begin{center}
-        \leavevmode
-        \epsfig{file=fig_qf_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lit_primuszerr.eps,height=0.75\textwidth,angle=90}
-        \caption{Evolution of the quiescent fraction $f_{\rm{Q}}$ for galaxies in low (left) and high (rights) density environments for $z < 0.8$.
-$f_{\rm{Q}}$s were calculated using the SMFs in Figure\ref{fig:smf}, as described in text.
-Darker shading indicates lower redshift.}         \label{fig:qf}
-    \end{center}
-\end{figure*}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The width of the SMFs represent the sample variance uncertainties.
-%%%%%%% REWRITE AFTER REVISED SMF RESULTS
-%As a result, we caution that the SMF redshift evolution is inconsistent during the transition from the PRIMUS sample to the SDSS sample at $z \sim 0.2$.
 
-%Yet, from the PRIMUS samples alone, we probe a sufficient redshift to observe notable trends in the SMF evolution for each of the panels in Figure \ref{fig:smf}. 
+While a detailed comparison of the SMFs in each panel for different epochs are complicated due to the different stellar mass completeness limits, we present some notable trends in each panel.
 In panel (a), star-forming galaxies in low density environments, we find a significant decrease in the high mass end of the SMF ($\mathcal{M} > 10^{10.75} \mathcal{M}_{\odot}$).
@@
 
-%We caution readers and reserve detailed analysis of the SMFs to future work due to the improvements in photometry that significantly alter the SDSS SMFs mentioned in Section \ref{sec:sdss}. 
-% There is also the issue with the SMF evolution: the uneven fractional contribution of the population and each environment classification.
+While our mass complete subsample coupled with robust environment measurement allows us to compare SMF evolution for each of our subsamples over $z < 1.0$, we caution readers and reserve detailed analysis of the SMFs to future work due to the improvements in photometry that significantly alter the SDSS SMFs mentioned in Section \ref{sec:sdss}.
 
+\begin{figure*}
+    \begin{center}
+        \leavevmode
+        \epsfig{file=fig_qf_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lit_primuszerr.eps,height=0.75\textwidth,angle=90}
+        \caption{Evolution of the quiescent fraction $f_{\rm{Q}}$ for galaxies in low (left) and high (rights) density environments for $z < 0.8$.
+$f_{\rm{Q}}$s were calculated using the SMFs in Figure\ref{fig:smf}, as described in text.
+Darker shading indicates lower redshift.}         \label{fig:qf}
+    \end{center}
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 In this section, using the SMFs of our subsamples, we compare the quiescent and the star-forming populations by calculating the fraction of galaxies that have quenched their star-formation, the quiescent fraction.
-With the sufficient statistics available from SDSS and PRIMUS, we evaluate the quiescent fraction in bins of stellar mass and redshift for low and high density environments.
+With the sufficient statistics available from SDSS and PRIMUS, we evaluate the quiescent fraction in bins of stellar mass and redshift for low and high density environments (Section \label{sec:qfevol}).
 More specifically, by analyzing the quiescent fraction with respect to mass, redshift, and environment we are able to compare the quiescent fraction evolution in low and high density environments.
@@
 Furthermore by quantifying the environmental effects of star-formation quenching, we are able to provide constraints on the various proposed environmental quenching mechanisms, such as strangulation and ram-pressure stripping (\cite{McCarthy:2008aa}).
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% EVOLUTION OF THE QUIESCENT FRACTION
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Evolution of the Quiescent Fraction} \label{sec:qfevol}
 From the SMF number densities ($\Phi$) computed in the previous section, the quiescent fraction is computed as follows, 
@@
 As in Figure \ref{fig:smf}, the darker shading represent lower redshift bins.
+The width of the quiescent fraction represents the uncertainty from sample variance.
+As done in Section \ref{sec:smfevol} for the stellar mass function, we use the standard jack-knife technique
 
@@
 
+Finally, we compare our $f_{\rm{Q}}$ results to previous $f_{\rm{Q}}/f_{\rm{red}}$ measurements for analogous environment classifications.
+For our lowest redshift bin, we find that our $f_{\rm{Q}}$ values for low and high environments are consistent with previous $f_{\rm{Q}}/f_{\rm{red}}$ measurements for SDSS galaxies as a function of environment.
+For example, \cite{Tinker:2011aa}, using a group-finding algorithm on the SDSS DR7, presents the relationship between $f_{\rm{Q}}$ and overdensity for galaxies within the mass range $\rm{log} \; \mathcal{M} = [9.8, 10.1]$.
+The \cite{Tinker:2011aa} $f_{\rm{Q}}$ at the lowest and highest overdensities, $f_{\rm{Q}} \sim 0.4$ and $f_{\rm{Q}} \sim 0.6$ respectively, are consistent with our $f_{\rm{Q}}$ for low and high density environment at the lowest mass bin ($\rm{log} \; \mathcal{M} \sim 10.2$).
+At higher masses, our $f_{\rm{Q}}$ results are consistent with \cite{Baldry:2006aa}.
+\cite{Baldry:2006aa} uses project neighbor density environment measures ($\rm{log} \;  \Sigma$) to obtain $f_{\rm{Q}}(\mathcal{M})$ for a range of environmental densities.
+Although the different environment measurements make a direct comparison unclear, at higher environments ($\rm{log} \; \Sigma > 0.2$) in \cite{Baldry:2006aa} $f_{\rm{Q}} \sim 0.6$ at $\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}$ and $f_{\rm{Q}} \sim 0.9$ at $\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}$, in agreement our high density environment.
+Likewise, for lower environments in \cite{Baldry:2006aa} ($\rm{log} \; \Sigma < -0.4$) $f_{\rm{Q}} \sim 0.4$ at $\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}$ and $f_{\rm{Q}} \sim 0.8$ at $\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}$, which also agree with our low density environment $f_{\rm{Q}}$.
+
+For $z > 0.2$, we compare our PRIMUS $f_{\rm{Q}}$ results to the $f_{\rm{red}}$ (or $1-f_{\rm{blue}}$) results from the zCOSMOS Redshift Survey (\cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, \cite{Kovac:2014aa}), which approximately covers the same redshift range as PRIMUS.
+\cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, and \cite{Kovac:2014aa} using a mass-complete galaxy sample derived from zCOSMOS and a group catalog, 3D local density contrast, and overdensity environment measurements, respectively, compare $f_{\rm{red}}$ with respect to environment.
+The $f_{\rm{blue}}$ for group and isolated galaxies from \cite{Iovino:2010aa} are generally inconsistent with our $1-f_{\rm{Q}}$ for high and low density environments.
+Similarly, $f_{\rm{red}}$ for high and low overdensities in \cite{Kovac:2014aa} are  greater overall than the PRIMUS $f_{\rm{Q}}$ values in high and low density environments.
+However, \cite{Kovac:2014aa} points out that there is a significant difference between classifying the quenched population using color and SFR.
+$f_{\rm{Q}}$ defined by color is greater than $f_{\rm{Q}}$ defined by SFR by roughly $0.2$.
+Although the propagation of this difference for different environments is not explored in \cite{Kovac:2014aa}, if we account for the difference evenly for $f_{\rm{red}}$ at all environments, the \cite{Kovac:2014aa} results are generally consistent with our $f_{\rm{Q}}$ at high and low density environments.
+
+Additionally, the zCOSMOS results indicate that the $f_{\rm{red}}$ values in high density environments are greater overall than in low density environments.
+The same trend is observed in the PRIMUS results and will be discussed in detail later in Section \label{sec:env_qf_evol}.
+Another significant trend observed in the zCOSMOS results is the significant mass dependence of the $f_{\rm{red}}$ and $f_{\rm{blue}}$ evolution.
+\cite{Iovino:2010aa} by examining $f_{\rm{blue}}(z)$ in different mass bins for group and isolated galaxies find significantly larger $f_{\rm{blue}}$ evolution at lower masses.
+In fact, \cite{Iovino:2010aa} finds no evolution in $f_{\rm{blue}}$ for $\mathcal{M} > 10^{10.9} \mathcal{M}_{\odot}$ for both group and isolated galaxies over the redshift range $0.4 < z < 0.9$.
+On the other hand, in the lowest mass bin ($10^{10.0} \mathcal{M}_{\odot} < \mathcal{M} < 10^{10.5} \mathcal{M}_{\odot}$) \cite{Iovino:2010aa} finds $f_{\rm{blue}}(z \sim 0.4) - f_{\rm{blue}}(z \sim 0.2) \sim 0.2$ for isolated galaxies and  $f_{\rm{blue}}(z \sim 0.4) - f_{\rm{blue}}(z \sim 0.2) \sim 0.1$ for group galaxies.
+In contrast, in each of the panels of Figure \ref{fig:qf}, we qualitatively find little mass dependence on the $f_{\rm{Q}}$ evolution for either low or high density environments.
+However, due to the distinct stellar mass completeness limits imposed at each redshift bin of our sample, subtle effects such as the mass dependence of the $f_{\rm{Q}}$ evolution are difficult to discern.
+
 \begin{figure}
@@
 
-In order to more quantitatively compare the $f_{\rm{Q}}$ evolution, we fit $f_{\rm{Q}}$ for each subsample to a power-law parameterization as a function of stellar mass, 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% ENVIRONMENTAL EFFECTS ON THE QUIESCENT FRACTION EVOLUTION
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Environmental Effects on the Quiescent Fraction Evolution} \label{sec:env_qf_evol}
+In order to more quantitatively compare the $f_{\rm{Q}}$ evolution for different epochs and environments, we fit $f_{\rm{Q}}$ for each subsample to a power-law parameterization as a function of stellar mass,
 \begin{equation} 
@@
 Therefore, the potential contamination in our environment measurements cannot explain the lack of environment dependence in the $f_{\rm{Q}}$ evolution.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% DISCUSSION
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion} \label{sec:discussion}
-
-Finally, we compare our $f_{\rm{Q}}$ results to previous $f_{\rm{Q}}/f_{\rm{red}}$ measurements for analogous environment classifications.
-For our lowest redshift bin, we find that our $f_{\rm{Q}}$ values for low and high environments are consistent with previous $f_{\rm{Q}}/f_{\rm{red}}$ measurements for SDSS galaxies as a function of environment.
-For example, \cite{Tinker:2011aa}, using a group-finding algorithm on the SDSS DR7, presents the relationship between $f_{\rm{Q}}$ and overdensity for galaxies within the mass range $\rm{log} \; \mathcal{M} = [9.8, 10.1]$.
-The \cite{Tinker:2011aa} $f_{\rm{Q}}$ at the lowest and highest overdensities, $f_{\rm{Q}} \sim 0.4$ and $f_{\rm{Q}} \sim 0.6$ respectively, are consistent with our $f_{\rm{Q}}$ for low and high density environment at the lowest mass bin ($\rm{log} \; \mathcal{M} \sim 10.2$).
-At higher masses, our $f_{\rm{Q}}$ results are consistent with \cite{Baldry:2006aa}.
-\cite{Baldry:2006aa} uses project neighbor density environment measures ($\rm{log} \;  \Sigma$) to obtain $f_{\rm{Q}}(\mathcal{M})$ for a range of environmental densities.
-Although the different environment measurements make a direct comparison unclear, at higher environments ($\rm{log} \; \Sigma > 0.2$) in \cite{Baldry:2006aa} $f_{\rm{Q}} \sim 0.6$ at $\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}$ and $f_{\rm{Q}} \sim 0.9$ at $\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}$, in agreement our high density environment.
-Likewise, for lower environments in \cite{Baldry:2006aa} ($\rm{log} \; \Sigma < -0.4$) $f_{\rm{Q}} \sim 0.4$ at $\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}$ and $f_{\rm{Q}} \sim 0.8$ at $\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}$, which also agree with our low density environment $f_{\rm{Q}}$.
-
-For $z > 0.2$, we compare our PRIMUS $f_{\rm{Q}}$ results to the $f_{\rm{red}}$ (or $1-f_{\rm{blue}}$) results from the zCOSMOS Redshift Survey (\cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, \cite{Kovac:2014aa}), which approximately covers the same redshift range as PRIMUS.
-\cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, and \cite{Kovac:2014aa} using a mass-complete galaxy sample derived from zCOSMOS and a group catalog, 3D local density contrast, and overdensity environment measurements, respectively, compare $f_{\rm{red}}$ with respect to environment.
-The $f_{\rm{blue}}$ for group and isolated galaxies from \cite{Iovino:2010aa} are generally inconsistent with our $1-f_{\rm{Q}}$ for high and low density environments.
-Similarly, $f_{\rm{red}}$ for high and low overdensities in \cite{Kovac:2014aa} are  greater overall than the PRIMUS $f_{\rm{Q}}$ values in high and low density environments.
-However, \cite{Kovac:2014aa} points out that there is a significant difference between classifying the quenched population using color and SFR.
-$f_{\rm{Q}}$ defined by color is greater than $f_{\rm{Q}}$ defined by SFR by roughly $0.2$.
-Although the propagation of this difference for different environments is not explored in \cite{Kovac:2014aa}, if we account for the difference evenly for $f_{\rm{red}}$ at all environments, the \cite{Kovac:2014aa} results are generally consistent with our $f_{\rm{Q}}$ at high and low density environments.
-
-Additionally, the zCOSMOS results indicate that the $f_{\rm{red}}$ values in high density environments are greater overall than in low density environments.
-The same trend is observed in the PRIMUS results and will be discussed in detail later in the section.
-Another significant trend observed in the zCOSMOS results is the significant mass dependence of the $f_{\rm{red}}$ and $f_{\rm{blue}}$ evolution.
-\cite{Iovino:2010aa} by examining $f_{\rm{blue}}(z)$ in different mass bins for group and isolated galaxies find significantly larger $f_{\rm{blue}}$ evolution at lower masses.
-In fact, \cite{Iovino:2010aa} finds no evolution in $f_{\rm{blue}}$ for $\mathcal{M} > 10^{10.9} \mathcal{M}_{\odot}$ for both group and isolated galaxies over the redshift range $0.4 < z < 0.9$.
-On the other hand, in the lowest mass bin ($10^{10.0} \mathcal{M}_{\odot} < \mathcal{M} < 10^{10.5} \mathcal{M}_{\odot}$) \cite{Iovino:2010aa} finds $f_{\rm{blue}}(z \sim 0.4) - f_{\rm{blue}}(z \sim 0.2) \sim 0.2$ for isolated galaxies and  $f_{\rm{blue}}(z \sim 0.4) - f_{\rm{blue}}(z \sim 0.2) \sim 0.1$ for group galaxies.
-In contrast, in each of the panels of Figure \ref{fig:qf}, we qualitatively find little mass dependence on the $f_{\rm{Q}}$ evolution for either low or high density environments.
-However, due to the distinct stellar mass completeness limits imposed at each redshift bin of our sample, subtle effects such as the mass dependence of the $f_{\rm{Q}}$ evolution are difficult to discern.
 

### 2014-08-12 qfenv_paper/qf_environment.tex
updated figures and edits

@@
     \end{tabular} \par
+    \end{center}
+%    \bigskip 
+    {\bf Notes}: Number of galaxies in the mass complete subsamples derived in Section \ref{sec:sample}.
+The subsamples are classified based on environment $n_{\rm{env}}$ and star formation rate (star-forming or quiescent).
+The lowest redshift bin is derived from SDSS; the rest are from PRIMUS.
     \bigskip
-    {\bf Notes}: Number of galaxies in the mass complete subsamples derived in Section \ref{sec:sample}.
-The subsamples are classified based on environment and star formation rate.
-The lowest redshift bin is derived from SDSS; the rest are from PRIMUS.
-  \end{center}
 \end{table}
@@
     \leavevmode
-    \epsfig{file=fig_envcount_cylr2h25_thresh75_sdss_z0_05_0_12_primuszerr_masslimit_histogram.png,height=0.5\textwidth}
-     \caption{Normalized distribution of environment measurements ($n_{\rm{env}}$) for our mass complete galaxy sample.
+    \epsfig{file=fig_envcount_cylr2h25_thresh75_sdss_z0_05_0_12_primuszerr_masslimit_edgecut_histogram.png,height=0.5\textwidth}
+     \caption{Normalized distribution of environment measurements ($n_{\rm{env}}$) for our mass complete galaxy sample within the edges.
 The star-forming galaxies contribution to the distribution is colored blue and diagonally patterned.
-The contribution of the distribution from quiescent galaxies is colored in red.
-Each redshift panel is divided into three sections of by the environment classification threshold (vertical black lines): low density environment $n_{\rm{env}} < 1.5$ and high density environment $n_{\rm{env}} > 3.5$.
+The contribution from quiescent galaxies is colored in red.
+Each redshift panel is divided into three sections of by the environment classification cutoffs (vertical black lines): low density environment $n_{\rm{env}} < 1.5$ and high density environment $n_{\rm{env}} > 3.5$.
 The percentages of the redshift bin contained in the environment classifications are presented above the distribution.
@@
 Then we examine the evolution of active and quiescent subsample SMFs in different environments in Section \ref{sec:smfevol}.
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% STELLAR MASS FUNCTION CALCULATIONS
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Stellar Mass Function Calculations} \label{sec:smfcalc} 
@@
 In this section, using the SMFs of our subsamples, we compare the quiescent and the star-forming populations by calculating the fraction of galaxies that have quenched their star-formation, the quiescent fraction.
-With the sufficient statistics available from SDSS and PRIMUS, we evaluate the quiescent fraction in bins of stellar mass and redshift for low and high density environments (Section \label{sec:qfevol}).
+
+With the suffic ient statistics available from SDSS and PRIMUS, we evaluate the quiescent fraction in bins of stellar mass and redshift for low and high density environments (Section \ref{sec:qfevol}).
 More specifically, by analyzing the quiescent fraction with respect to mass, redshift, and environment we are able to compare the quiescent fraction evolution in low and high density environments.
-Through this comparison we reveal the subtle environmental effects in quenching star formation that are often obscured by the underlying correlations among galactic properties such as color-mass and mass-density relations (\cite{Cooper:2010aa}).
+Through this comparison, in Section \ref{sec:env_qf_evol}, we reveal the subtle environmental effects in quenching star formation that are often obscured by the underlying correlations among galactic properties such as color-mass and mass-density relations (\cite{Cooper:2010aa}).
 Furthermore by quantifying the environmental effects of star-formation quenching, we are able to provide constraints on the various proposed environmental quenching mechanisms, such as strangulation and ram-pressure stripping (\cite{McCarthy:2008aa}).
@@
 We compute $f_{\rm{Q}}$ for high and low density environments for all redshift bins as plotted in Figure \ref{fig:qf}, which shows the evolution of $f_{\rm{Q}}$ for high (right) and low (left) density environments.
-As in Figure \ref{fig:smf}, the darker shading represent lower redshift bins.
-The width of the quiescent fraction represents the uncertainty from sample variance.
-As done in Section \ref{sec:smfevol} for the stellar mass function, we use the standard jack-knife technique
+As in Figure \ref{fig:smf}, the evolution of the quiescent fraction over cosmic time is represented in the shading: darker with lower redshift.
+In order to calculate the uncertainty for the quiescent fraction, we follow the same steps in the standard jackknife technique as we did for the SMF in Section \ref{sec:smfcalc}.
+We represent the quiescent fraction uncertainty by the width in Figure \ref{fig:qf}.
 
-Most noticeably in Figure \ref{fig:qf}, $f_{\rm{Q}}$ increases monotonically as a function of mass at all redshift bin and environment.
+Most noticeably in Figure \ref{fig:qf}, we find $f_{\rm{Q}}$ increases monotonically as a function of mass at all redshift bin and environment.
 In other words, for all subsamples, galaxies in higher mass bins are more likely to have quenched its star-formation.
@@
 
-Finally, we compare our $f_{\rm{Q}}$ results to previous $f_{\rm{Q}}/f_{\rm{red}}$ measurements for analogous environment classifications.
-For our lowest redshift bin, we find that our $f_{\rm{Q}}$ values for low and high environments are consistent with previous $f_{\rm{Q}}/f_{\rm{red}}$ measurements for SDSS galaxies as a function of environment.
+Finally, we compare our $f_{\rm{Q}}$ results to previous $f_{\rm{Q}}$ (or $f_{\rm{red}}$) measurements for analogous environment classifications.
+For our lowest redshift bin, we find that our $f_{\rm{Q}}$ values for low and high environments are consistent with previous $f_{\rm{Q}}$ (or $f_{\rm{red}}$) measurements as a function of environment for SDSS galaxies.
 For example, \cite{Tinker:2011aa}, using a group-finding algorithm on the SDSS DR7, presents the relationship between $f_{\rm{Q}}$ and overdensity for galaxies within the mass range $\rm{log} \; \mathcal{M} = [9.8, 10.1]$.
 The \cite{Tinker:2011aa} $f_{\rm{Q}}$ at the lowest and highest overdensities, $f_{\rm{Q}} \sim 0.4$ and $f_{\rm{Q}} \sim 0.6$ respectively, are consistent with our $f_{\rm{Q}}$ for low and high density environment at the lowest mass bin ($\rm{log} \; \mathcal{M} \sim 10.2$).
+
 At higher masses, our $f_{\rm{Q}}$ results are consistent with \cite{Baldry:2006aa}.
 \cite{Baldry:2006aa} uses project neighbor density environment measures ($\rm{log} \;  \Sigma$) to obtain $f_{\rm{Q}}(\mathcal{M})$ for a range of environmental densities.
-Although the different environment measurements make a direct comparison unclear, at higher environments ($\rm{log} \; \Sigma > 0.2$) in \cite{Baldry:2006aa} $f_{\rm{Q}} \sim 0.6$ at $\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}$ and $f_{\rm{Q}} \sim 0.9$ at $\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}$, in agreement our high density environment.
-Likewise, for lower environments in \cite{Baldry:2006aa} ($\rm{log} \; \Sigma < -0.4$) $f_{\rm{Q}} \sim 0.4$ at $\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}$ and $f_{\rm{Q}} \sim 0.8$ at $\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}$, which also agree with our low density environment $f_{\rm{Q}}$.
+Although the different environment measurements make a direct comparison unclear, at higher environments ($\rm{log} \; \Sigma > 0.2$) in \cite{Baldry:2006aa} $f_{\rm{Q}}(\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}) \sim 0.6$ and $f_{\rm{Q}}(\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}) \sim 0.9$, in agreement our high density environment.
+Likewise, for lower environments ($\rm{log} \; \Sigma < -0.4$ in \cite{Baldry:2006aa}) $f_{\rm{Q}}(\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}) \sim 0.4$ and $f_{\rm{Q}}(\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}) \sim 0.8$, which also agree with our low density environment $f_{\rm{Q}}$.
 
@@
 $f_{\rm{Q}}$ defined by color is greater than $f_{\rm{Q}}$ defined by SFR by roughly $0.2$.
-Although the propagation of this difference for different environments is not explored in \cite{Kovac:2014aa}, if we account for the difference evenly for $f_{\rm{red}}$ at all environments, the \cite{Kovac:2014aa} results are generally consistent with our $f_{\rm{Q}}$ at high and low density environments.
+Although the propagation of this difference for different environments is not explored in \cite{Kovac:2014aa}, if we account for the difference uniformly for $f_{\rm{red}}$ at all environments, the \cite{Kovac:2014aa} results are generally consistent with our $f_{\rm{Q}}$ at high and low density environments.
 
 Additionally, the zCOSMOS results indicate that the $f_{\rm{red}}$ values in high density environments are greater overall than in low density environments.
-The same trend is observed in the PRIMUS results and will be discussed in detail later in Section \label{sec:env_qf_evol}.
+The same trend is observed in the PRIMUS results and will be discussed in detail later in Section \ref{sec:env_qf_evol}.
 Another significant trend observed in the zCOSMOS results is the significant mass dependence of the $f_{\rm{red}}$ and $f_{\rm{blue}}$ evolution.
@@
 In order to more quantitatively compare the $f_{\rm{Q}}$ evolution for different epochs and environments, we fit $f_{\rm{Q}}$ for each subsample to a power-law parameterization as a function of stellar mass,
-\begin{equation} 
+\begin{equation} \label{eq:qffit}
 f_{\rm{Q}}(\mathcal{M}_{*}) = a \: \rm{log} \; \left(\frac{ \mathcal{M}_{*}}{10^{10.5} \: \mathcal{M}_{\odot}} \right)+b,
@@
 Figure \ref{fig:qffit} shows the evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ for low (diamond) and high (circle) density environments.
+
+\begin{table} 
+  \caption{Best Fit Parameters for $f_{\rm{Q}}(\mathcal{M}_{*})$}
+  \label{tab:bestfitparam}
+  \begin{center}
+    \leavevmode
+    \begin{tabular}{lllll} \hline \hline              
+    $z_1 < z < z_2$ &Environment        &a  &b  \\ \hline 
+$0.05 < z< 0.12$ &Low           &12859                       &14443                           \\
+               &High            &18952                       &13387                           \\ 
+                              &               &                       &                           \\ \hline
+$0.2 < z <0.4$      &Low           &1158                    &3445                           \\
+               &High            &817                    &1531                           \\
+               &               &                       &                           \\ \hline
+$0.4 < z < 0.6$      &Low           &1315                       &3390                           \\
+               &High            &848                       &1499                           \\
+               &               &                       &                           \\ \hline
+$0.6 < z < 0.8$      &Low           &1158                       &2303                           \\
+               &High            &900                       &1275                           \\
+               &               &                       &                           \\ \hline
+  \multicolumn{4}{l}{}                                             \\       
+    \end{tabular} \par
+    \end{center}
+%    \bigskip 
+    {\bf Notes}: Best fit parameters in Equation \ref{eq:qffit} for each subsample $f_{\rm{Q}}(\mathcal{M}_{*})$ in Figure \ref{fig:qf}.  
+\end{table}
 
@@
 % What does this have to say about physical processes in groups and clusters that affect quenching?
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-We thank people...
+We thank people and funding...
 %

### 2014-08-14 qfenv_paper/qf_environment.tex
new table

@@
 \begin{table} 
-  \caption{Best Fit Parameters for $f_{\rm{Q}}(\mathcal{M}_{*})$}
+  \caption{Best Fit Parameters for $f_{\rm{Q}}(\mathcal{M}_{*})$ Fit}
   \label{tab:bestfitparam}
@@
     $z_1 < z < z_2$ &Environment        &a  &b  \\ \hline 
-$0.05 < z< 0.12$ &Low           &12859                       &14443                           \\
+$0.05 < z< 0.12$ &Low           &$0.3612 \pm 0.015$	&$0.482 \pm 0.006$                           \\
                &High            &18952                       &13387                           \\ 

### 2014-08-15 qfenv_paper/qf_environment.tex
Fixed the Abstract

@@
 We investigate the effects of galaxy environment on the evolution of the quiescent fraction ($f_{\rm{Q}}$) from $z =0.8 $ to $ 0.0$ using spectroscopic redshifts and multi-wavelength imaging data from PRism MUlti-object Survey (PRIMUS) and the Sloan Digitial Sky Survey (SDSS).
-Our stellar mass limited galaxy sample consists of $\sim 40000$ PRIMUS galaxies within $z = 0.2-0.8$ and $\sim 130000$ SDSS galaxies within $z = 0.0375-0.145$.
+Our stellar mass limited galaxy sample consists of $\sim 40000$ PRIMUS galaxies within $z = 0.2-0.8$ and $\sim 130000$ SDSS galaxies within $z = 0.05-0.12$.
 We classify the galaxies as quiescent or star-forming, based on an evolving specific star formation cut, and as low or high density environments, based on fixed cylindrical aperture environment measurements on a volume-limited {\em Environment Definition Population} (from PRIMUS and SDSS).
 
-For each of these subsamples, we examine the stellar mass function (SMF) evolution and compute the $f_{\rm{Q}}(\mathcal{M}_{*})$.
-We find that in both low and high density environments the quiescent fraction increases with cosmic time over the probed redshift range.
-Moreover, the difference between the quiescent fraction in low and high density environments remains constant throughout the redshift range.
-These results suggest that the evolution of the quiescent fraction is independent of environment and provide constraints on quenching mechanisms in high density environments such as groups and clusters.
+For quiescent and star-forming galaxies in low or high density environments, we examine the evolution of their stellar mass function (SMF) evolution.
+Then using the SMFs we compute the $f_{\rm{Q}}(\mathcal{M}_{*})$ and quantify the evolution of $f_{\rm{Q}}(\mathcal{M}_{*})$ within our redshift range.
+We find that in both low and high density environments the quiescent fraction increases with cosmic time.
+Moreover, we illustrate that galaxy populations in high density environments have significantly higher quiescent fractions than galaxy populations in low density environments.
+Furthermore, by comparing the quiescent fraction evolutions, we find that the quiescent fraction evolves noticeably more for galaxy populations in high density environments.
+These results suggest that quenching due to the environment has a moderate effect on the quiescent fraction evolution and provide constraints on quenching mechanisms in high density environments such as groups and clusters.
 \end{abstract}

### 2014-08-18 qfenv_paper/qf_environment.tex
shiny new figures

@@
     \leavevmode
-    \epsfig{file=fig_smf_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lit_2envbin_primuszerr.eps,height=0.75\textwidth,angle=90}
+    \epsfig{file=fig_smf_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_2envbin_lowenv0_5_highenv3_0_lit_primuszerr.eps, height=0.75\textwidth,angle=90}
      \caption{Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) target galaxies in 
@@
         \leavevmode
-        \epsfig{file=fig_qf_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lit_primuszerr.eps,height=0.75\textwidth,angle=90}
+        \epsfig{file=fig_qf_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_lit_primuszerr.eps, height=0.75\textwidth,angle=90}
         \caption{Evolution of the quiescent fraction $f_{\rm{Q}}$ for galaxies in low (left) and high (rights) density environments for $z < 0.8$.
@@
 
-With the suffic ient statistics available from SDSS and PRIMUS, we evaluate the quiescent fraction in bins of stellar mass and redshift for low and high density environments (Section \ref{sec:qfevol}).
+With the sufficient statistics available from SDSS and PRIMUS, we evaluate the quiescent fraction in bins of stellar mass and redshift for low and high density environments (Section \ref{sec:qfevol}).
 More specifically, by analyzing the quiescent fraction with respect to mass, redshift, and environment we are able to compare the quiescent fraction evolution in low and high density environments.
@@
         \epsscale{1.0}
-        \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_fidmass10_5_lit_primuszerr.eps,height=0.45\textwidth}
+        \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmass10_5_lit_primuszerr.eps, height=0.45\textwidth}
         \caption{The evolution of the quiescent fraction at fiducial mass, $f_{Q}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$, for low (square) and high (circle) density environments within the redshift range $z = 0.0 - 0.8$.
@@
     $z_1 < z < z_2$ &Environment        &a  &b  \\ \hline 
-$0.05 < z< 0.12$ &Low           &$0.3612 \pm 0.015$	&$0.482 \pm 0.006$                           \\
-               &High            &18952                       &13387                           \\ 
+$0.05 < z< 0.12$ &$n_{\rm{env}} < 0.5$           &$0.3612 \pm 0.015$	&$0.482 \pm 0.006$                           \\
+               &$n_{\rm{env}} > 3$            &18952                       &13387                           \\ 
                               &               &                       &                           \\ \hline
@@
 Therefore, the potential contamination in our environment measurements cannot explain the lack of environment dependence in the $f_{\rm{Q}}$ evolution.
+
+\begin{figure}
+    \begin{center}
+        \leavevmode
+        \epsscale{1.0}
+        \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmass10_5_lit_primuszerr_zcosmoscomp_envthresh_kovacoffset.eps, height=0.45\textwidth}
+        \caption{The evolution of the quiescent fraction at fiducial mass, $f_{Q}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$, for low (square) and high (circle) density environments within the redshift range $z = 0.0 - 0.8$.}         \label{fig:qffit}
+    \end{center}
+\end{figure}
 

### 2014-08-18 qfenv_paper/qf_environment.tex
New figures and edits on qf calculation section

@@
     \leavevmode
-    \epsfig{file=fig_envcount_cylr2h25_thresh75_sdss_z0_05_0_12_primuszerr_masslimit_edgecut_histogram.png,height=0.5\textwidth}
+    \epsfig{file=fig_envcount_cylr2h25_thresh75_sdss_z0_05_0_12_primus_z0_21_0_lowenv0_5_highenv3_0_primuszerr_masslimit_edgecut_histogram.png, height=0.5\textwidth}
      \caption{Normalized distribution of environment measurements ($n_{\rm{env}}$) for our mass complete galaxy sample within the edges.
@@
 The contribution from quiescent galaxies is colored in red.
-Each redshift panel is divided into three sections of by the environment classification cutoffs (vertical black lines): low density environment $n_{\rm{env}} < 1.5$ and high density environment $n_{\rm{env}} > 3.5$.
+Each redshift panel is divided into three sections of by the environment classification cutoffs (vertical black lines): low density environment $n_{\rm{env}} < 0.5$ and high density environment $n_{\rm{env}} > 3.0$.
 The percentages of the redshift bin contained in the environment classifications are presented above the distribution.
@@
 $f_{\rm{Q}}$s were calculated using the SMFs in Figure\ref{fig:smf}, as described in text.
-Darker shading indicates lower redshift.}         \label{fig:qf}
+Darker shading indicates lower redshift and the width represents the standard jackknife uncertainty.}         \label{fig:qf}
     \end{center}
@@
 \end{equation}
-$\Phi_{Q}$ and $\Phi_{SF}$ are the total number of galaxies per unit volume in stellar mass bin of $\Delta(\rm{log} \: \mathcal{M}) = 0.25$ for the quiescent and star-forming subsamples, respectively (Equation \ref{eq:phi}).
+$\Phi_{Q}$ and $\Phi_{SF}$ are the total number of galaxies per unit volume in stellar mass bin of $\Delta(\rm{log} \: \mathcal{M}) = 0.20 \: {\it dex}$ for the quiescent and star-forming subsamples, respectively (Equation \ref{eq:phi}).
 We compute $f_{\rm{Q}}$ for high and low density environments for all redshift bins as plotted in Figure \ref{fig:qf}, which shows the evolution of $f_{\rm{Q}}$ for high (right) and low (left) density environments.
-As in Figure \ref{fig:smf}, the evolution of the quiescent fraction over cosmic time is represented in the shading: darker with lower redshift.
-In order to calculate the uncertainty for the quiescent fraction, we follow the same steps in the standard jackknife technique as we did for the SMF in Section \ref{sec:smfcalc}.
-We represent the quiescent fraction uncertainty by the width in Figure \ref{fig:qf}.
+As in Figure \ref{fig:smf}, the evolution of the quiescent fraction over cosmic time is represented in the shading (darker with lower redshift) and the uncertainty is represented by the width.
+We use the standard jackknife technique, following the same steps as the SMF uncertainty in Section \ref{sec:smfcalc}, in order to calculate the uncertainty for the quiescent fraction.
 
@@
 For all environments a larger portion of our galaxy population has quenched its star-formation over time.
-Coupled with the decline of SFR in the star-forming population (\cite{Noeske:2007aa}; \cite{cooper08a}), our results strongly agree with the observed decline of global star-formation in the universe (\cite{hopkins06a}).
+Coupled with the decline of SFR in the star-forming population (\cite{Noeske:2007aa}; \cite{cooper08a}), our results are in agreement with the observed decline of global star-formation in the universe (\cite{hopkins06a}).
 %Maybe Stacey et al.
@@
 
-In addition, when we compare the stellar masses at which $f_{\rm{Q}} = 0.5$ for each subsample, we find that this mass decreases over cosmic time.
+In addition, when we compare the stellar masses at which $f_{\rm{Q}} = 0.5$ for each subsample, the so-called $\mathcal{M}_{50-50}$, we find that this quantity decreases over cosmic time.
 This corresponds to the well-known mass-downsizing pattern in the literature (e.g.
@@
 Finally, we compare our $f_{\rm{Q}}$ results to previous $f_{\rm{Q}}$ (or $f_{\rm{red}}$) measurements for analogous environment classifications.
-For our lowest redshift bin, we find that our $f_{\rm{Q}}$ values for low and high environments are consistent with previous $f_{\rm{Q}}$ (or $f_{\rm{red}}$) measurements as a function of environment for SDSS galaxies.
+For our lowest redshift bin, we find that our $f_{\rm{Q}}$ for low and high environments are consistent with previous SDSS $f_{\rm{Q}}$ (or $f_{\rm{red}}$) measurements as a function of environment.
 For example, \cite{Tinker:2011aa}, using a group-finding algorithm on the SDSS DR7, presents the relationship between $f_{\rm{Q}}$ and overdensity for galaxies within the mass range $\rm{log} \; \mathcal{M} = [9.8, 10.1]$.
-The \cite{Tinker:2011aa} $f_{\rm{Q}}$ at the lowest and highest overdensities, $f_{\rm{Q}} \sim 0.4$ and $f_{\rm{Q}} \sim 0.6$ respectively, are consistent with our $f_{\rm{Q}}$ for low and high density environment at the lowest mass bin ($\rm{log} \; \mathcal{M} \sim 10.2$).
+The \cite{Tinker:2011aa} $f_{\rm{Q}}$ at the lowest and highest overdensities, $f_{\rm{Q}} \sim 0.4$ and $f_{\rm{Q}} \sim 0.6$ respectively, are consistent with our $f_{\rm{Q}}$ for low and high density environment at the lower mass limit ($\rm{log} \; \mathcal{M} \sim 10.2$).
 
@@
 The $f_{\rm{blue}}$ for group and isolated galaxies from \cite{Iovino:2010aa} are generally inconsistent with our $1-f_{\rm{Q}}$ for high and low density environments.
+
 Similarly, $f_{\rm{red}}$ for high and low overdensities in \cite{Kovac:2014aa} are  greater overall than the PRIMUS $f_{\rm{Q}}$ values in high and low density environments.
 However, \cite{Kovac:2014aa} points out that there is a significant difference between classifying the quenched population using color and SFR.
-$f_{\rm{Q}}$ defined by color is greater than $f_{\rm{Q}}$ defined by SFR by roughly $0.2$.
-Although the propagation of this difference for different environments is not explored in \cite{Kovac:2014aa}, if we account for the difference uniformly for $f_{\rm{red}}$ at all environments, the \cite{Kovac:2014aa} results are generally consistent with our $f_{\rm{Q}}$ at high and low density environments.
+For their lower redshift bin ($0.1 < z < 0.4$) they find that their $f_{\rm{Q}}$ defined by color is greater than $f_{\rm{Q}}$ defined by SFR by roughly $0.2$.
+And for their higher redshift bin ($0.4 < z < 0.7$) they find a difference of $0.15-0.19$.
+Although the propagation of this difference for different environments is not explored in \cite{Kovac:2014aa}, if we account for the difference uniformly for $f_{\rm{red}}$ at all environments, the \cite{Kovac:2014aa} results in their lower redshift bin ($0.1< z < 0.4$) are generally consistent with our $f_{\rm{Q}}$ at high and low density environments.
+In their higher redshift bin ($0.4 < z < 0.7$), even accounting for the difference in galaxy classification, \cite{Kovac:2014aa} finds a significantly higher $f_{\rm{Q}}$.
 
-Additionally, the zCOSMOS results indicate that the $f_{\rm{red}}$ values in high density environments are greater overall than in low density environments.
+We previously addressed that for both low and high density environments, $f_{\rm{Q}}$ increases as redshift decreases.
+This general trend is in good agreement with\cite{Iovino:2010aa}, which finds a similar increase in $1-f_{\rm{red}}$ over cosmic time for $\mathcal{M} < 10^{10.9} \mathcal{M}_{\odot}$.
+However, our $f_{\rm{Q}}$ redshift evolution disagrees with \cite{Kovac:2014aa}, which presents a general decrease in $f_{\rm{red}}$ over cosmic time for low environment.
+
+The zCOSMOS results also find that $f_{\rm{red}}$ in high density environments are greater overall than in low density environments.
 The same trend is observed in the PRIMUS results and will be discussed in detail later in Section \ref{sec:env_qf_evol}.
@@
         \epsscale{1.0}
-        \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmass10_5_lit_primuszerr.eps, height=0.45\textwidth}
-        \caption{The evolution of the quiescent fraction at fiducial mass, $f_{Q}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$, for low (square) and high (circle) density environments within the redshift range $z = 0.0 - 0.8$.
+        \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmasscomp11_0_10_5_lit_primuszerr.eps, height=0.45\textwidth}
+        \caption{The evolution of the quiescent fraction at fiducial mass, $f_{Q}(\mathcal{M}_{\rm{fid}})$, for low (blue) and high (red) density environments within the redshift range $z = 0.0 - 0.8$.
+We present the $f_{Q}(\mathcal{M}_{\rm{fid}})$ evolution for $\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot$ (solid fill) and $10^{11} \mathcal{M}_\odot$ (patterned fill) with the uncertainty of the best-fit parameter $b$ in Equation \ref{eq:qffit} represented by the width of the evolution.
 There is a significant increase in $f_{Q}(\mathcal{M}_{\rm{fid}})$ with decrease in redshift for both environments.
 In addition, over the entire redshift range, high density environment $f_{Q}(\mathcal{M}_{\rm{fid}})$ is greater than low density environment $f_{Q}(\mathcal{M}_{\rm{fid}})$.
-However the difference in $f_{Q}(\mathcal{M}_{\rm{fid}})$ for the two environments remains constant throughout suggesting that while the quiescent fraction is higher in dense environments, the evolution of the quiescent fraction is independent of environment.}         \label{fig:qffit}
+For the environment cut-offs ($n_{\rm{env}} < 0.5$ for low and $n_{\rm{env}} > 3.0$ for high), there is no significant difference in the slope of the evolution between the environments.}         \label{fig:qffit}
     \end{center}
@@
 \begin{equation} \label{eq:qffit}
-f_{\rm{Q}}(\mathcal{M}_{*}) = a \: \rm{log} \; \left(\frac{ \mathcal{M}_{*}}{10^{10.5} \: \mathcal{M}_{\odot}} \right)+b,
+f_{\rm{Q}}(\mathcal{M}_{*}) = a \: \rm{log} \; \left(\frac{ \mathcal{M}_{*}}{\mathcal{M}_{\rm{fid}}} \right)+b,
 \end{equation}
 where $a$ are $b$ are best-fit parameters using {\em MPFIT} (\cite{Markwardt:2009aa}).
-The value $10^{10.5} \: \mathcal{M}_{\odot}$ in the equation represents an empirically selected fiducial mass $\mathcal{M}_{\rm{fid}}$ within the stellar mass limits where there is a sufficiently large number of galaxies.
+$\mathcal{M}_{\rm{fid}}$ represents the empirically selected fiducial mass within the stellar mass limits where there is a sufficiently large number of galaxies.
+We primarily focus on $\mathcal{M}_{\rm{fid}} = 10^{10.5} \: \mathcal{M}_{\odot}$.
 This fiducial mass serves to highlight and quantify the $f_{\rm{Q}}$ evolution for different redshifts.
-Figure \ref{fig:qffit} shows the evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ for low (diamond) and high (circle) density environments.
+Figure \ref{fig:qffit} shows the evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ for low (blue) and high (red) density environments for $\mathcal{M}_{\rm{fid}} = 10^{10.5} \: \mathcal{M}_{\odot}$ (solid fill) and $10^{11} \: \mathcal{M}_{\odot}$ (pattern fill).
 
@@
 %    \bigskip 
-    {\bf Notes}: Best fit parameters in Equation \ref{eq:qffit} for each subsample $f_{\rm{Q}}(\mathcal{M}_{*})$ in Figure \ref{fig:qf}.  
+    {\bf Notes}: Best fit parameters in Equation \ref{eq:qffit} for each subsample $f_{\rm{Q}}(\mathcal{M}_{*})$ in Figure \ref{fig:qf} for $\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_{\odot}$.
 \end{table}
@@
 This is in strong agreement with the zCOSMOS results from \cite{Cucciati:2010aa} and \cite{Kovac:2014aa}.
-For $z < 1.0$, galaxy populations in higher density environments have higher quenched fractions.
-As galaxy color and SFR are related, our results support the existence of the color-density relation (\cite{Cucciati:2010aa}; \cite{Cooper:2010aa}) in favor of the idea that the color-density relation is a merely a reflection of the mass-density or morphology-density relation (\cite{Scodeggio:2009aa}, \cite{Tasca:2009aa}).
+Galaxy populations in higher density environments at $z < 1.0$ have higher quenched fractions.
+As galaxy color serves as a proxy for SFR, our results support the existence of the color-density relation (\cite{Cucciati:2010aa}; \cite{Cooper:2010aa}) and debunk the suggestions that the color-density relation is a merely a reflection of the mass-density or morphology-density relation (\cite{Scodeggio:2009aa}, \cite{Tasca:2009aa}).
 
-The same fitting procedure was performed using $\mathcal{M}_{\rm{fid}} = 10^{11} \mathcal{M}_\odot$; however, aside from an overall shift in $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ by $\sim 0.2$, we observe the same evolutionary trends.
-$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{11}\mathcal{M}_{\odot})$ for both low and high density environments each increase by $\sim 0.2$ as redshift decreases from $\sim 0.7$ to $\sim 0.1$, just as Figure \ref{fig:qffit}.
-Evidently, increasing the fiducial mass to $10^{11} \mathcal{M}_{\odot}$ does not change the total evolution for either environments.
-On the other hand, \cite{Iovino:2010aa}, for both group and isolated galaxies, finds significantly less $f_{\rm{Q}}$ evolution for $\mathcal{M} \sim 10^{11.0} \mathcal{M}_{\odot}$ than in $\mathcal{M} \sim 10^{10.5} \mathcal{M}_{\odot}$.
-Furthermore, \cite{Iovino:2010aa} also finds that the difference in $f_{\rm{blue}}$ evolution between group and isolated galaxies ($f_{\rm{blue}, \rm{isolated}}(z) - f_{\rm{blue}, \rm{group}}(z))$ is much greater at $\mathcal{M} \sim 10^{10.5} \mathcal{M}_{\odot}$ than at $\mathcal{M} \sim 10^{11} \mathcal{M}_{\odot}$, where they find almost no difference.
-In contrast, we find that changing the fiducial mass does not significantly alter the difference in $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$.
+For $\mathcal{M}_{\rm{fid}} = 10^{11} \mathcal{M}_\odot$, aside from an overall shift in $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ by $\sim 0.2$, we observe the same evolutionary trends.
+$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{11}\mathcal{M}_{\odot})$ for both low and high density environments each increase by $\sim 0.2$ as redshift decreases from $\sim 0.7$ to $\sim 0.1$, keeping the slope the same.
+Evidently, increasing the fiducial mass to $10^{11} \mathcal{M}_{\odot}$ does not significantly alter the total evolution for either environments.
+
+On the other hand, \cite{Iovino:2010aa} finds significantly less $f_{\rm{Q}}$ evolution for $\mathcal{M} \sim 10^{11.0} \mathcal{M}_{\odot}$ than in $\mathcal{M} \sim 10^{10.5} \mathcal{M}_{\odot}$,  for both group and isolated galaxies.
+In fact for their highest mass bin ($10^{10.9} - 10^{11.4} \mathcal{M}_{\odot}$), they find no evolution for both environments within $z \sim 0.3 - 0.8$.
+Furthermore, \cite{Iovino:2010aa} also finds that the difference in $f_{\rm{blue}}$ evolution between group and isolated galaxies ($f_{\rm{blue}, \rm{isolated}}(z) - f_{\rm{blue}, \rm{group}}(z))$ is much greater at $\mathcal{M} \sim 10^{10.5} \mathcal{M}_{\odot}$ than at $\mathcal{M} \sim 10^{11} \mathcal{M}_{\odot}$, where they find no difference.
+So in their highest mass bin, $f_{\rm{blue}}$ remains constant at $\sim 0.1$ within $z \sim 0.3 - 0.8$ for both group and isolated galaxy populations.
+As noted earlier, changing the fiducial mass in our analysis does not significantly alter the difference in $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ between the low and high density environments.
+
 The zCOSMOS results find a clear mass dependence in the $f_{\rm{blue}}$ evolution; however, the consistency in evolutionary trends when the fiducial mass is change reveal that our $f_{\rm{Q}}$ evolution exhibits little mass dependence.
@@
         \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmass10_5_lit_primuszerr_zcosmoscomp_envthresh_kovacoffset.eps, height=0.45\textwidth}
-        \caption{The evolution of the quiescent fraction at fiducial mass, $f_{Q}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$, for low (square) and high (circle) density environments within the redshift range $z = 0.0 - 0.8$.}         \label{fig:qffit}
+        \caption{$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$ evolution compared to $f_{\rm{red}}(\mathcal{M}_{*} \sim 10^{10.5} \; \mathcal{M}_{\odot})$ in the literature: \cite{Iovino:2010aa} (square) and \cite{Kovac:2014aa} (triangle) from zCOSMOS and \cite{Baldry:2006aa} (diamond) from SDSS.
+These $f_{\rm{red}}$ values are calculated from the best-fit parameterizations presented in the respective works.
+High density environment is represented in red and low density environment is represented in blue.
+For \cite{Kovac:2014aa} we apply the offset between the color-based and SFR-based galaxy classification in order to plot the $f_{\rm{Q}}$ estimates.
+Furthermore, we also plot the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$ evolution of our sample with varying environment cut-offs specified on the top right.
+As in Figure \ref{fig:qffit} the width of the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$ evolution represent the uncertainty in the best-fit parameters of Equation \ref{eq:qffit}.}         \label{fig:qffit_comp}
     \end{center}
@@
 \end{table*}
+
+\begin{figure*}
+    \begin{center}
+        \leavevmode
+        \epsscale{1.0}
+        \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmass11_0_lit_primuszerr.eps, height=0.45\textwidth}
+        \caption{The evolution of the quiescent fraction at fiducial mass, $f_{Q}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$, for low (square) and high (circle) density environments within the redshift range $z = 0.0 - 0.8$.}
+    \end{center}
+\end{figure*}
+
+\begin{figure*}
+    \begin{center}
+        \leavevmode
+        \epsscale{1.0}
+        \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmass11_0_lit_primuszerr_zcosmoscomp_envthresh_kovacoffset.eps, height=0.45\textwidth}
+        \caption{The evolution of the quiescent fraction at fiducial mass, $f_{Q}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$, for low (square) and high (circle) density environments within the redshift range $z = 0.0 - 0.8$.}         \label{fig:qffit_comp}
+    \end{center}
+\end{figure*}
+
 \end{document}

### 2014-08-19 qfenv_paper/qf_environment.tex
Edits on QFcalc and QFevol

@@
 $\Phi_{Q}$ and $\Phi_{SF}$ are the total number of galaxies per unit volume in stellar mass bin of $\Delta(\rm{log} \: \mathcal{M}) = 0.20 \: {\it dex}$ for the quiescent and star-forming subsamples, respectively (Equation \ref{eq:phi}).
-We compute $f_{\rm{Q}}$ for high and low density environments for all redshift bins as plotted in Figure \ref{fig:qf}, which shows the evolution of $f_{\rm{Q}}$ for high (right) and low (left) density environments.
+We compute $f_{\rm{Q}}$ for high and low density environments for all redshift bins as plotted in Figure \ref{fig:qf}, which shows the evolution of $f_{\rm{Q}}$ for high (right panel) and low (left panel) density environments.
 As in Figure \ref{fig:smf}, the evolution of the quiescent fraction over cosmic time is represented in the shading (darker with lower redshift) and the uncertainty is represented by the width.
-We use the standard jackknife technique, following the same steps as the SMF uncertainty in Section \ref{sec:smfcalc}, in order to calculate the uncertainty for the quiescent fraction.
+For the uncertainty in the quiescent fraction, we use the standard jackknife technique, following the same steps as the SMF uncertainty in Section \ref{sec:smfcalc}.
 
@@
 For high density environment, this is analogous to the Butcher-Omeler Effect (\cite{Butcher:1984aa}), which states that galaxy populations in groups or clusters have higher $f_{\rm{blue}}$, or lower $f_{\rm{Q}}$, at higher redshift.
-For all environments a larger portion of our galaxy population has quenched its star-formation over time.
+For all environments, a larger portion of our galaxy population has quenched its star-formation over time.
 Coupled with the decline of SFR in the star-forming population (\cite{Noeske:2007aa}; \cite{cooper08a}), our results are in agreement with the observed decline of global star-formation in the universe (\cite{hopkins06a}).
@@
 
-Finally, we compare our $f_{\rm{Q}}$ results to previous $f_{\rm{Q}}$ (or $f_{\rm{red}}$) measurements for analogous environment classifications.
+Finally, we compare our $f_{\rm{Q}}$ results to previous $f_{\rm{Q}}$ (or $f_{\rm{red}}$) measurements with analogous environment classifications.
 For our lowest redshift bin, we find that our $f_{\rm{Q}}$ for low and high environments are consistent with previous SDSS $f_{\rm{Q}}$ (or $f_{\rm{red}}$) measurements as a function of environment.
@@
 \cite{Baldry:2006aa} uses project neighbor density environment measures ($\rm{log} \;  \Sigma$) to obtain $f_{\rm{Q}}(\mathcal{M})$ for a range of environmental densities.
-Although the different environment measurements make a direct comparison unclear, at higher environments ($\rm{log} \; \Sigma > 0.2$) in \cite{Baldry:2006aa} $f_{\rm{Q}}(\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}) \sim 0.6$ and $f_{\rm{Q}}(\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}) \sim 0.9$, in agreement our high density environment.
+Although in these comparisons, the different environment measurements make direct comparisons unclear, at higher environments ($\rm{log} \; \Sigma > 0.2$ in \cite{Baldry:2006aa}) $f_{\rm{Q}}(\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}) \sim 0.6$ and $f_{\rm{Q}}(\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}) \sim 0.9$, in agreement our high density environment.
 Likewise, for lower environments ($\rm{log} \; \Sigma < -0.4$ in \cite{Baldry:2006aa}) $f_{\rm{Q}}(\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}) \sim 0.4$ and $f_{\rm{Q}}(\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}) \sim 0.8$, which also agree with our low density environment $f_{\rm{Q}}$.
 
-For $z > 0.2$, we compare our PRIMUS $f_{\rm{Q}}$ results to the $f_{\rm{red}}$ (or $1-f_{\rm{blue}}$) results from the zCOSMOS Redshift Survey (\cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, \cite{Kovac:2014aa}), which approximately covers the same redshift range as PRIMUS.
+For $z > 0.2$, we compare our PRIMUS $f_{\rm{Q}}$ results to the $f_{\rm{red}}$ (or $1-f_{\rm{blue}}$) results from the zCOSMOS Redshift Survey (\cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, \cite{Kovac:2014aa}), which covers a similar redshift range as PRIMUS.
 \cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, and \cite{Kovac:2014aa} using a mass-complete galaxy sample derived from zCOSMOS and a group catalog, 3D local density contrast, and overdensity environment measurements, respectively, compare $f_{\rm{red}}$ with respect to environment.
@@
 For their lower redshift bin ($0.1 < z < 0.4$) they find that their $f_{\rm{Q}}$ defined by color is greater than $f_{\rm{Q}}$ defined by SFR by roughly $0.2$.
-And for their higher redshift bin ($0.4 < z < 0.7$) they find a difference of $0.15-0.19$.
-Although the propagation of this difference for different environments is not explored in \cite{Kovac:2014aa}, if we account for the difference uniformly for $f_{\rm{red}}$ at all environments, the \cite{Kovac:2014aa} results in their lower redshift bin ($0.1< z < 0.4$) are generally consistent with our $f_{\rm{Q}}$ at high and low density environments.
-In their higher redshift bin ($0.4 < z < 0.7$), even accounting for the difference in galaxy classification, \cite{Kovac:2014aa} finds a significantly higher $f_{\rm{Q}}$.
+While for their higher redshift bin ($0.4 < z < 0.7$) they find a difference of $0.15-0.19$.
+Although the propagation of this difference for different environments is not explored in \cite{Kovac:2014aa}, if we naively account for the difference uniformly for $f_{\rm{red}}$ at all environments, the \cite{Kovac:2014aa} results in their lower redshift bin are generally consistent with our $f_{\rm{Q}}$ at high and low density environments.
+However, in their higher redshift bin even accounting for the difference in galaxy classification, \cite{Kovac:2014aa} finds a significantly higher $f_{\rm{Q}}$.
 
 We previously addressed that for both low and high density environments, $f_{\rm{Q}}$ increases as redshift decreases.
-This general trend is in good agreement with\cite{Iovino:2010aa}, which finds a similar increase in $1-f_{\rm{red}}$ over cosmic time for $\mathcal{M} < 10^{10.9} \mathcal{M}_{\odot}$.
-However, our $f_{\rm{Q}}$ redshift evolution disagrees with \cite{Kovac:2014aa}, which presents a general decrease in $f_{\rm{red}}$ over cosmic time for low environment.
+This general trend is in good agreement with \cite{Iovino:2010aa}, which finds a similar increase in $1-f_{\rm{blue}}$ over cosmic time for $\mathcal{M} < 10^{10.9} \mathcal{M}_{\odot}$.
+However, in contrast to our $f_{\rm{Q}}$ redshift evolution, \cite{Kovac:2014aa} presents a notable decrease in $f_{\rm{red}}$ over cosmic time for low environment.
+Even for their galaxies in high density environments, \cite{Kovac:2014aa} finds no significant increase in $f_{\rm{red}}$ with cosmic time.
 
@@
 \end{equation}
-where $a$ are $b$ are best-fit parameters using {\em MPFIT} (\cite{Markwardt:2009aa}).
-$\mathcal{M}_{\rm{fid}}$ represents the empirically selected fiducial mass within the stellar mass limits where there is a sufficiently large number of galaxies.
+where $a$ and $b$ are best-fit parameters using {\em MPFIT} (\cite{Markwardt:2009aa}) and $\mathcal{M}_{\rm{fid}}$ represents the empirically selected fiducial mass within the stellar mass limits where there is a sufficiently large number of galaxies.
 We primarily focus on $\mathcal{M}_{\rm{fid}} = 10^{10.5} \: \mathcal{M}_{\odot}$.
 This fiducial mass serves to highlight and quantify the $f_{\rm{Q}}$ evolution for different redshifts.
-Figure \ref{fig:qffit} shows the evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ for low (blue) and high (red) density environments for $\mathcal{M}_{\rm{fid}} = 10^{10.5} \: \mathcal{M}_{\odot}$ (solid fill) and $10^{11} \: \mathcal{M}_{\odot}$ (pattern fill).
+
+In Figure \ref{fig:qffit} we present the evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ at low (blue) and high (red) density environments for $\mathcal{M}_{\rm{fid}} = 10^{10.5} \: \mathcal{M}_{\odot}$ (solid fill) and $10^{11} \: \mathcal{M}_{\odot}$ (pattern fill).
+Then in Figure \ref{fig:qffit_comp} we explore more stringent environment cut-offs for the high density environment (specified in the top right legend and represented by shading).
+In addition, we plot best-fit parameterization of $f_{\rm{red}}$ for high and low density environment from zCOSMOS, \cite{Iovino:2010aa} (square) and \cite{Kovac:2014aa} (triangle), and SDSS, \cite{Baldry:2006aa} (diamond).
+From \cite{Iovino:2010aa} we calculate $f_{\rm{red}} = 1-f_{\rm{blue}}$ using the best-fit $f_{\rm{blue}}$ from the mass bin $\mathcal{M} = 10^{10.3} - 10^{10.8} \mathcal{M}_{\odot}$.
+From \cite{Kovac:2014aa} we plot an estimated $f_{\rm{Q}}$ by applying the difference between SFR based and color based galaxy classifications to the best-fit $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ for low ($\delta = 0.0$) and high density environment ($\delta = 1.5$).
+Similarly, from \cite{Baldry:2006aa} we plot $f_{\rm{Q}}$ derived from the best-fit $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ for low ($\delta = 0.0$) and high density environment ($\delta = 1.0$).
 
@@
 
-Figure \ref{fig:qffit} illustrates that throughout the entire redshift range, high density environment has a significantly greater $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ than the lower density environment.
-This is in strong agreement with the zCOSMOS results from \cite{Cucciati:2010aa} and \cite{Kovac:2014aa}.
-Galaxy populations in higher density environments at $z < 1.0$ have higher quenched fractions.
-As galaxy color serves as a proxy for SFR, our results support the existence of the color-density relation (\cite{Cucciati:2010aa}; \cite{Cooper:2010aa}) and debunk the suggestions that the color-density relation is a merely a reflection of the mass-density or morphology-density relation (\cite{Scodeggio:2009aa}, \cite{Tasca:2009aa}).
-
-For $\mathcal{M}_{\rm{fid}} = 10^{11} \mathcal{M}_\odot$, aside from an overall shift in $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ by $\sim 0.2$, we observe the same evolutionary trends.
-$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{11}\mathcal{M}_{\odot})$ for both low and high density environments each increase by $\sim 0.2$ as redshift decreases from $\sim 0.7$ to $\sim 0.1$, keeping the slope the same.
-Evidently, increasing the fiducial mass to $10^{11} \mathcal{M}_{\odot}$ does not significantly alter the total evolution for either environments.
-
-On the other hand, \cite{Iovino:2010aa} finds significantly less $f_{\rm{Q}}$ evolution for $\mathcal{M} \sim 10^{11.0} \mathcal{M}_{\odot}$ than in $\mathcal{M} \sim 10^{10.5} \mathcal{M}_{\odot}$,  for both group and isolated galaxies.
-In fact for their highest mass bin ($10^{10.9} - 10^{11.4} \mathcal{M}_{\odot}$), they find no evolution for both environments within $z \sim 0.3 - 0.8$.
-Furthermore, \cite{Iovino:2010aa} also finds that the difference in $f_{\rm{blue}}$ evolution between group and isolated galaxies ($f_{\rm{blue}, \rm{isolated}}(z) - f_{\rm{blue}, \rm{group}}(z))$ is much greater at $\mathcal{M} \sim 10^{10.5} \mathcal{M}_{\odot}$ than at $\mathcal{M} \sim 10^{11} \mathcal{M}_{\odot}$, where they find no difference.
-So in their highest mass bin, $f_{\rm{blue}}$ remains constant at $\sim 0.1$ within $z \sim 0.3 - 0.8$ for both group and isolated galaxy populations.
-As noted earlier, changing the fiducial mass in our analysis does not significantly alter the difference in $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ between the low and high density environments.
-
-The zCOSMOS results find a clear mass dependence in the $f_{\rm{blue}}$ evolution; however, the consistency in evolutionary trends when the fiducial mass is change reveal that our $f_{\rm{Q}}$ evolution exhibits little mass dependence.
-Although our sample from SDSS and PRIMUS provides significantly larger statistics, due to the limited mass ranges probed in our mass-complete sample (e.g.
-$\mathcal{M} > 10^{10.5} \mathcal{M}_{\odot}$ for our $z \sim 0.7$ bin) it is difficult to dismiss the mass dependence observed in the zCOSMOS results.
-
-Finally, from Figure \ref{fig:qffit}, we note that for both environments $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ increases as redshift decreases.
-This highlights the general increase of $f_{\rm{Q}}(\mathcal{M})$ as redshift decreases noted earlier.
-More importantly, we quantify the total evolution of $f_{\rm{Q}}$ for both low and high density environments through $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}}, z \sim 0.1) - f_{\rm{Q}}(\mathcal{M}_{\rm{fid}}, z \sim 0.7)$ for both environments.
-Remarkably, $f_{\rm{Q}}$ evolves by the same amount for both environments.
-In other words, the total evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ show little environment dependence.
-This disagrees with the $f_{\rm{blue}}$ results from \cite{Iovino:2010aa}, which show a clear distinction between group and isolated galaxies.
-In \cite{Iovino:2010aa}, $f_{\rm{blue}}$ for isolated galaxies decrease much faster than $f_{\rm{blue}}$ for group galaxies.
-At $\mathcal{M} \sim 10.5$, \cite{Iovino:2010aa} finds that $f_{\rm{blue}}$ for isolated galaxy decreases by 0.3 from $z \sim 0.6$ to 0.3, while for $f_{\rm{blue}}$ for group galaxies only decrease by 0.1 in the same redshift limit, showing a clear dependence in environment.
-Considering that fixed aperture definition of environment is susceptible to contamination due to PRIMUS redshift errors, we consider more stringent classification of high density environments extending the cut-off to $n_{\rm{env}} > 6, 9$.
-While a more stringent classification increases the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ overall as well as the uncertainties, it does not reveal reveal any significant environment dependence in the $f_{\rm{Q}}$ evolution.
-Therefore, the potential contamination in our environment measurements cannot explain the lack of environment dependence in the $f_{\rm{Q}}$ evolution.
-
 \begin{figure}
@@
         \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmass10_5_lit_primuszerr_zcosmoscomp_envthresh_kovacoffset.eps, height=0.45\textwidth}
-        \caption{$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$ evolution compared to $f_{\rm{red}}(\mathcal{M}_{*} \sim 10^{10.5} \; \mathcal{M}_{\odot})$ in the literature: \cite{Iovino:2010aa} (square) and \cite{Kovac:2014aa} (triangle) from zCOSMOS and \cite{Baldry:2006aa} (diamond) from SDSS.
+        \caption{$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}}=10^{10.5} \mathcal{M}_\odot)$ evolution compared to $f_{\rm{red}}(\mathcal{M}_{*}=10^{10.5} \; \mathcal{M}_{\odot})$ in the literature: \cite{Iovino:2010aa} (square) and \cite{Kovac:2014aa} (triangle) from zCOSMOS and \cite{Baldry:2006aa} (diamond) from SDSS.
 These $f_{\rm{red}}$ values are calculated from the best-fit parameterizations presented in the respective works.
@@
 For \cite{Kovac:2014aa} we apply the offset between the color-based and SFR-based galaxy classification in order to plot the $f_{\rm{Q}}$ estimates.
-Furthermore, we also plot the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$ evolution of our sample with varying environment cut-offs specified on the top right.
+We also plot the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$ evolution of our sample with varying environment cut-offs specified on the top right.
 As in Figure \ref{fig:qffit} the width of the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$ evolution represent the uncertainty in the best-fit parameters of Equation \ref{eq:qffit}.}         \label{fig:qffit_comp}
@@
 \end{figure}
+
+Both Figure \ref{fig:qffit} and Figure \ref{fig:qffit_comp} illustrate that throughout the entire redshift range, high density environment has a significantly greater $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ than the lower density environment.
+This is in strong agreement with the zCOSMOS results from \cite{Cucciati:2010aa} and \cite{Kovac:2014aa} and suggests that galaxy populations in higher density environments at $z < 1.0$ have higher quenched fractions.
+As galaxy color serves as a proxy for SFR, our results support the existence of the color-density relation (\cite{Cucciati:2010aa}; \cite{Cooper:2010aa}) and debunk the suggestions that the color-density relation is a merely a reflection of the mass-density or morphology-density relation (\cite{Scodeggio:2009aa}, \cite{Tasca:2009aa}).
+
+In Figure \ref{fig:qffit}, for $\mathcal{M}_{\rm{fid}} = 10^{11} \mathcal{M}_\odot$, aside from an overall shift in $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ by $\sim 0.2$, we observe the same evolutionary trends.
+$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{11}\mathcal{M}_{\odot})$ for both low and high density environments each increase by $\sim 0.2$ as redshift decreases from $\sim 0.7$ to $\sim 0.1$, keeping the slope of the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ evolution the same.
+Evidently, increasing the fiducial mass to $10^{11} \mathcal{M}_{\odot}$ does not significantly alter the total evolution for either environments.
+
+The similarity of the evolutionary trends at $\mathcal{M}_{\rm{fid}} = 10^{10.5} \: \mathcal{M}_{\odot}$ and $10^{11} \: \mathcal{M}_{\odot}$ conflicts with \cite{Iovino:2010aa} who find contrasting $f_{\rm{Q}}$ evolutions at $\mathcal{M} \sim 10^{11.0} \mathcal{M}_{\odot}$ and $\mathcal{M} \sim 10^{10.5} \mathcal{M}_{\odot}$,  for both group and isolated galaxies.
+In fact at their highest mass bin ($10^{10.9} - 10^{11.4} \mathcal{M}_{\odot}$), \cite{Iovino:2010aa} find no evolution for both environments: $f_{\rm{blue}}$ remains constant at $\sim 0.1$ within $z = 0.3 - 0.8$ for both group and isolated galaxy populations.
+Meanwhile in their mass bin most comparable to our $\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_{\odot}$, they present an evolution of $\Delta f_{\rm{red}} \sim 0.1$ over $z = 0.5$ to $0.25$ for group galaxies and $\Delta f_{\rm{red}} \sim 0.3$ over $z = 0.55$ to $0.3$.
+Furthermore, while we find that the $f_{\rm{Q}}(z)_{\rm{high}} - f_{\rm{Q}}(z)_{\rm{low}}$ remains relatively constant at $\sim 0.1$ over the redshift range for both fiducial masses, \cite{Iovino:2010aa} finds $f_{\rm{blue}}(z)_{ \rm{isolated}} - f_{\rm{blue}}(z)_{\rm{group}}$ is much more significant at $\mathcal{M} \sim 10^{10.5} \mathcal{M}_{\odot}$ than at $\mathcal{M} \sim 10^{11} \mathcal{M}_{\odot}$, where they find no difference.
+
+zCOSMOS results find a clear mass dependence in the $f_{\rm{blue}}$ evolution; however, the consistency in evolutionary trends when the fiducial mass is changed reveal that our $f_{\rm{Q}}$ evolution exhibits little mass dependence.
+Although our sample from SDSS and PRIMUS provides significantly larger statistics, due to the limited mass ranges probed in our mass-complete sample (e.g.
+$\mathcal{M} > 10^{10.5} \mathcal{M}_{\odot}$ for our $z \sim 0.7$ bin) it is difficult to dismiss the mass dependence observed in the zCOSMOS results.
+
+Another trend we observe in both Figure \ref{fig:qffit} Figure \ref{fig:qffit_comp}, is that for both environments $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ increases as redshift decreases.
+This highlights the general increase of $f_{\rm{Q}}(\mathcal{M})$ as redshift decreases noted earlier.
+More importantly, by fitting our $f_{\rm{Q}}$ evolution and obtaining the value at the fiducial mass, we are able to quantify the total evolution of $f_{\rm{Q}}$ for both low and high density environments through $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}}, z \sim 0.1) - f_{\rm{Q}}(\mathcal{M}_{\rm{fid}}, z \sim 0.7)$ for both environments.
+In Figure \ref{fig:qffit}, we find that $f_{\rm{Q}}$ evolves by a similar amount for both environments.
+
+Considering that fixed aperture definition of environment is susceptible to contamination due to PRIMUS redshift errors, in Figure \ref{fig:qffit_comp}, we consider more stringent classification of high density environments extending the cut-off to $n_{\rm{env}} > 6, 9$.
+A more stringent classification significantly increases the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ overall.
+The decrease in sample size that accompanies a purer high environment sample also increase the uncertainties.
+More importantly, a purer high environment classification reveals a more significant environment dependence of the $f_{\rm{Q}}$ evolution.
+With a purer the high environment classification, we find a steeper slope in the $f_{\rm{Q}}$ and a greater total $f_{\rm{Q}}$ evolution.
+From $ z \sim 0.7$, for the low density environment ($n_{\rm{env}} < 0.5$) $f_{\rm{Q}}$ increases by roughly $0.1$.
+At the highest environments, $f_{\rm{Q}}$ increases by roughly $0.25$.
+Therefore, the total evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ show moderate environment dependence.
+
+An environment dependence of the $f_{\rm{Q}}$ evolution is also observed in \cite{Iovino:2010aa} - also plotted in Figure \ref{fig:qffit_comp}.
+However, in addition to a much more pronounced distinction between the group and isolated $f_{\rm{Q}}$ evolution, they find the opposite environment dependence.
+Unlike our results, which find a greater $f_{\rm{Q}}$ evolution at higher density environments, \cite{Iovino:2010aa} finds a much greater evolution for isolated galaxies.
+
+\cite{Kovac:2014aa} finds a similar environment dependence on the total $f_{\rm{Q}}$ evolution to our results, with a greater $f_{\rm{Q}}$ evolution for high density environments.
+Unfortunately, contrary to our results, \cite{Kovac:2014aa} finds that $f_{\rm{Q}}$ decreases for both environments over cosmic time.
+The negative slope of the $f_{\rm{Q}}$ evolution is enhanced in Figure \ref{fig:qffit_comp} due to the galaxy classification correction we impose.
+However even without the correction (not shown), in their best-fit values, \cite{Kovac:2014aa} finds a decreasing $f_{\rm{Q}}$ evolution.
+%Discuss possible reasons for the difference between zCOSMOS results and our results. Point out the sample sizes and square degree coverage.
 
@@
 This result confirms the environmental dependence of quenching mechanisms stated previously in literature.
-	\item Comparison of the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ evolution for high and low density environments that the total evolution is independent of environment. 
+	\item Comparison of the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ evolution for high and low density environments that the total evolution has a moderate dependence on environment. 
 \end{enumerate}
@@
         \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmass11_0_lit_primuszerr_zcosmoscomp_envthresh_kovacoffset.eps, height=0.45\textwidth}
-        \caption{The evolution of the quiescent fraction at fiducial mass, $f_{Q}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$, for low (square) and high (circle) density environments within the redshift range $z = 0.0 - 0.8$.}         \label{fig:qffit_comp}
+        \caption{The evolution of the quiescent fraction at fiducial mass, $f_{Q}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$, for low (square) and high (circle) density environments within the redshift range $z = 0.0 - 0.8$.}
     \end{center}

### 2014-08-21 qfenv_paper/qf_environment.tex
Mike's edits part 1

@@
 \begin{abstract}
-We investigate the effects of galaxy environment on the evolution of the quiescent fraction ($f_{\rm{Q}}$) from $z =0.8 $ to $ 0.0$ using spectroscopic redshifts and multi-wavelength imaging data from PRism MUlti-object Survey (PRIMUS) and the Sloan Digitial Sky Survey (SDSS).
-Our stellar mass limited galaxy sample consists of $\sim 40000$ PRIMUS galaxies within $z = 0.2-0.8$ and $\sim 130000$ SDSS galaxies within $z = 0.05-0.12$.
-We classify the galaxies as quiescent or star-forming, based on an evolving specific star formation cut, and as low or high density environments, based on fixed cylindrical aperture environment measurements on a volume-limited {\em Environment Definition Population} (from PRIMUS and SDSS).
-
+We investigate the effects of galaxy environment on the evolution of the quiescent fraction ($f_{\rm{Q}}$) from $z =0.8 $ to $ 0.0$ using spectroscopic redshifts and multi-wavelength imaging data from the PRism MUlti-object Survey (PRIMUS) and the Sloan Digitial Sky Survey (SDSS).
+Our stellar mass limited galaxy sample consists of $\sim 40000$ PRIMUS galaxies within $z = 0.2-0.8$ and $\sim 130,000$ SDSS galaxies within $z = 0.05-0.12$.
+We classify the galaxies as quiescent or star-forming based on an evolving specific star formation cut, and as low or high density environments based on fixed cylindrical aperture environment measurements on a volume-limited Environment Definition Population (from PRIMUS and SDSS).
 For quiescent and star-forming galaxies in low or high density environments, we examine the evolution of their stellar mass function (SMF) evolution.
@@
 strongly decreasing function of galaxy stellar mass; at the extreme,
-the lowest masses ($<10^{9}$ $M_\odot$) galaxies are quenched only in
+the lowest mass ($<10^{9}$ $M_\odot$) galaxies are quenched only in
 dense regions, and never in isolation (\citealt{geha12a}).  These
@@
 same relative numbers as today (\citealt{bundy06a, borch06a,
-taylor09a, moustakas13a}. Furthermore, at those redshifts we can also
+taylor09a, Moustakas:2013aa}). Furthermore, at those redshifts we can also
 detect the dependence of galaxy properties on environment, with lower
@@
 individual galaxies (\cite{Noeske:2007aa}). There is evidence that a
-large fraction of the decline associated with strongly
+large fraction of the decline is associated with strongly
 infrared-emitting starbursts (\citealt{bell05a, magnelli09a}).  The
@@
 of the stellar mass function of quiescent and star-forming galaxies
-(\cite{Blanton:2006aa},\citealt{bundy06a, borch06a, moustakas13a}).  These
+(\citealt{Blanton:2006aa, bundy06a, borch06a, Moustakas:2013aa}).  These
 findings leave little room for the participation of
@@
 galaxies in all environments. The most straightforward investigation
-of would directly determine the star-forming properties of galaxies as
+would directly determine the star-forming properties of galaxies as
 a function of environment, stellar mass and redshift in a single,
@@
 \section{Sample Selection} \label{sec:sample}
-We are interested in quantifying the effects of galaxy environment on the evolution of the quenched population over the redshift range $z < 1.0$.
+We are interested in quantifying the effects of galaxy environment on the evolution of the quenched fraction over the redshift range $0 < z < 1$.
 For our analysis, we require a sample with sufficient depth and robustness to probe the redshift range and to measure galaxy environment.
-PRIMUS with its $\sim 120,000$ spectroscopic redshifts provides ideal data at intermediate redshifts for our analysis.
+PRIMUS with its $\sim 120,000$ spectroscopic redshifts provides a large data set at intermediate redshifts for our analysis.
 In addition, we anchor our analysis at intermediate redshifts with a low redshift sample derived from the Sloan Digital Sky Survey (\cite{York:2000aa}).
@@
 Then in Section \ref{sec:target} we define our stellar mass complete galaxy sample.
-Afterwards, in Section \ref{sec:sfq}, we classify our sample galaxies as quiescent or star-forming then calculate the environment using a volume-limited {\em Environment Defining Population} in Section \ref{sec:environment}.
+Afterwards, in Section \ref{sec:sfq}, we classify our sample galaxies as quiescent or star-forming then calculate the environment using a volume-limited Environment Defining Population in Section \ref{sec:environment}.
 Finally in Section \ref{sec:edgeeffect}, we correct our galaxy sample and environment measurements for edge effects of the surveys.
@@
 \subsection{PRIMUS} \label{sec:primus}
-At intermediate redshifts we use multiwavelength imaging and spectroscopic redshifts from PRIMUS, a faint galaxy survey with $\sim 120,000$ precise spectroscopic redshifts ($\sigma_z/(1+z) \approx 0.5 \%$) within the range $z \approx 0-1.2$.
-The survey was conducted using a IMACS spectrograph on a Magellan I Baade $6.5$ m telescope with a slitmask and low dispersion prism.
-For details on the PRIMUS observation methods such as survey design, targeting, and data summary, we refer readers to the survey papers: \cite{Coil:2011aa} and \cite{Cool:2013aa}.
+At intermediate redshifts we use multiwavelength imaging and spectroscopic redshifts from PRIMUS, a faint galaxy survey with $\sim 120,000$ redshifts ($\sigma_z/(1+z) \approx 0.5 \%$) within the range $z \approx 0-1.2$.
+The survey was conducted using the IMACS spectrograph on the Magellan I Baade $6.5$ m telescope with a slitmask and low dispersion prism.
+For details on the PRIMUS observation methods such as survey design, targeting, and data summary, we refer readers to the survey papers (\citealt{Coil:2011aa, Cool:2013aa}).
 
-While the PRIMUS survey targeted seven distinct extragalactic deep fields for a total of $\sim 9 \; \rm{deg}^2$, we restrict our sample to five fields that have $GALEX$ and {\em Spitzer}/IRAC imaging (similar to the sample selection in \cite{Moustakas:2013aa}).
-Four of these fields are a part of the {\em Spitzer} Wide-area Infrared Extragalactic Survey (SWIRE\footnote{http://swire.ipac.caltech.edu/swire/swire.html} ): the European Large Area ISO Survey - South $1$ field (ELAIS-S1\footnote{http://dipastro.pd.astro.it/esis}), the Chanddra Deep Field South SWIRE field (CDFS), and the XMM Large Scale Structure Survey field (XMM-LSS).
-The XMM-LSS consists of two separate but spatially adjacent fields: the Subaru/XMM-Newton DEEP Survey fied (XMM-SXDSS\footnote{http://www.naoj.org/cience/SubaruProject/SDS}) and the Canadian-France-Hawaii Telescope Legacy Survey field (XMM-CFHTLS\footnote{http://www.cfht.hawaii.edu/Science/CFHLS}).
+While the PRIMUS survey targeted seven distinct extragalactic deep fields for a total of $\sim 9 \; \rm{deg}^2$, we restrict our sample to five fields that have $GALEX$ and {\em Spitzer}/IRAC imaging (similar to the sample selection in \citealt{Moustakas:2013aa}).
+Four of these fields are a part of the {\em Spitzer} Wide-area Infrared Extragalactic Survey (SWIRE\footnote{http://swire.ipac.caltech.edu/swire/swire.html}): the European Large Area ISO Survey - South $1$ field (ELAIS-S1\footnote{http://dipastro.pd.astro.it/esis}), the Chandra Deep Field South SWIRE field (CDFS), and the XMM Large Scale Structure Survey field (XMM-LSS).
+The XMM-LSS consists of two separate but spatially adjacent fields: the Subaru/XMM-Newton DEEP Survey field (XMM-SXDSS\footnote{http://www.naoj.org/cience/SubaruProject/SDS}) and the Canadian-France-Hawaii Telescope Legacy Survey field (XMM-CFHTLS\footnote{http://www.cfht.hawaii.edu/Science/CFHLS}).
 Our fifth and final field is the Cosmic Evolution Survey (COSMOS\footnote{http://cosmos.astro.caltech.edu}) field.
-For all of our fields we have near-UV (NUV) and far-UV (FUV) photometry from the {\em GALEX} Deep Imaging Survey (DIS; \cite{Martin:2005aa}; \cite{Morrissey:2005aa}) as well as ground-based optical and {\em Spitzer}/IRAC mid-infrared photometric catalogs.
+For all of our fields we have near-UV (NUV) and far-UV (FUV) photometry from the {\em GALEX} Deep Imaging Survey (DIS; \citealt{Martin:2005aa, Morrissey:2005aa}) as well as ground-based optical and {\em Spitzer}/IRAC mid-infrared photometric catalogs.
 \cite{Moustakas:2013aa} provides detailed descriptions of integrated flux calculations in the photometric bands for each of our fields.
 
-Finally, from the spectroscopic redshift and broad wavelength photometry we use \texttt{iSEDfit}, a Bayesian SED modeling code, to calculate stellar masses and star formation rates (SFRs) for our sample galaxies.
-\texttt{iSEDfit}, uses the redshift and the observed photometry of the galaxies to determine the statistical likelihood of a large ensemble of generated model SEDs.
-The model SEDs are generated using Flexible Stellar Population Synthesis (FSPS) models (\cite{Conroy:2010aa}) based on \cite{Chabrier:2003aa} IMF, along with other prior parameters discussed in Section 4.1 and Appendix A.
-of \cite{Moustakas:2013aa}.
+Finally, using the spectroscopic redshift and broad wavelength photometry we apply \texttt{iSEDfit}, a Bayesian SED modeling code, to calculate stellar masses and star formation rates (SFRs) for our sample galaxies (\citealt{Moustakas:2013aa}).
+\texttt{iSEDfit} uses the redshift and the observed photometry of the galaxies to determine the statistical likelihood of a large ensemble of generated model SEDs.
+The model SEDs are generated using Flexible Stellar Population Synthesis (FSPS) models (\citealt{Conroy:2010aa}) based on the \cite{Chabrier:2003aa} IMF, along with other prior parameters discussed in Section 4.1 and Appendix A of \cite{Moustakas:2013aa}.
 For the observed photometry, we use the {\em GALEX} FUV and NUV, the two shortest IRAC bands at $3.6$ and $4.5 \mu \rm{m}$ (the two longer-wavelength IRAC channels are excluded because \texttt{iSEDfit} does not model hot dust or polycyclic aromatic hydrocarbons emission lines), and the optical bands.
@@
     \leavevmode
-    \begin{tabular}{lllll} \hline \hline              
-    $z$ &Environment        &Quiescent  &Star-forming  \\ \hline 
+    \begin{tabular}{l l l l l l l } \hline \hline              
+    $z$ &$n_{\rm{env}}$        &Quiescent  &Star-forming  & $\mathcal{M}_{\rm{lim}}$ & $M_{\rm{r}}$ cut-off \\ \hline 
 $0.05-0.12$ &Low           &12859                       &14443                           \\
@@
 \subsection{SDSS-GALEX} \label{sec:sdss}
-At low redshifts, we use spectroscopic redshifts and high fidelity $ugriz$ photometry from the SDSS Data Release 7 (DR7; \cite{Abazajian:2009aa}).
-More specifically we select galaxies from the New York University Value-Added Galaxy Catalog (hereafter SDSS VAGC) that satisfy the main sample criterion and have galaxy extinction corrected Petrosian magnitudes $14.5 < r < 17.6$ and spectroscopic redshifts within $0.01 < z < 0.2$ (\cite{Blanton:2005aa}).
-We further restrict the SDSS VAGC sample to only galaxies with medium depth observations with total exposure time greater than $1 \; \rm{ks}$ from {\em GALEX} Release 6.
+At low redshifts, we use spectroscopic redshifts and $ugriz$ photometry from the SDSS Data Release 7 (DR7; \citealt{Abazajian:2009aa}).
+More specifically we select galaxies from the New York University Value-Added Galaxy Catalog (hereafter VAGC) that satisfy the main sample criterion and have galaxy extinction corrected Petrosian magnitudes $14.5 < r < 17.6$ and spectroscopic redshifts within $0.01 < z < 0.2$ (\citealt{Blanton:2005aa}).
+We further restrict the VAGC sample to only galaxies with medium depth observations with total exposure time greater than $1 \; \rm{ks}$ from {\em GALEX} Release 6.
 This leaves $167,727$ galaxies.
 
-Next, we use the MAST/CasJobs\footnote{http://galex.stsci.edu/casjobs} interface and a $4''$ diameter search radius, to obtain the NUV and FNU photometry for the SDSS-{\em GALEX} galaxies.
+Next, we use the MAST/CasJobs\footnote{http://galex.stsci.edu/casjobs} interface and a $4''$ diameter search radius, to obtain the NUV and FUV photometry for the SDSS-{\em GALEX} galaxies.
 For optical photometry, we use the $ugriz$ bands from the SDSS \texttt{model} magnitudes scaled to the $r$-band \texttt{cmodel} magnitude.
-These photometric bands are then supplemented with integrated $JHK_s$ magnitudes from the 2MASS Extended Source Catalog (XSC; \cite{Jarrett:2000aa}) and with photometry at $3.4$ and $4.6 \mu \rm{m}$ from the WISE All-Sky Data Release\footnote{http://wise2.ipac.caltech.edu/docs/release/allsky}.
+These photometric bands are then supplemented with integrated $JHK_s$ magnitudes from the 2MASS Extended Source Catalog (XSC; \citealt{Jarrett:2000aa}) and with photometry at $3.4$ and $4.6 \mu \rm{m}$ from the WISE All-Sky Data Release\footnote{http://wise2.ipac.caltech.edu/docs/release/allsky}.
 Further details regarding the SDSS-{\em GALEX} sample photometry can be found in Section 2.4 of \cite{Moustakas:2013aa}.
@@
 
-While the SDSS-{\em GALEX} data discussed above is derived from SDSS VAGC Data Release 7, since the release of the catalog, there have been significant improvements in the photometry.
-Notably, \cite{Blanton:2011aa} find that the background subtractions in SDSS Data Release 7 has a size dependent bias in the galaxy fluxes, where galaxy fluxes are underestimated by $\sim 1.5$ mag for galaxies with $r_{50} \sim 100 $ arcsec.
-In addition \cite{Bernardi:2013aa} find that the luminosity, and ultimately stellar mass, is underestimated when they are derived from the SDSS \texttt{cmodel} magnitudes in comparison to \texttt{PyMorph} single-Sersic and Sersic-Exponential fits to the surface brightness profiles.
+While the SDSS-{\em GALEX} data discussed above is derived from VAGC Data Release 7, since the release of the catalog, there have been significant improvements in the photometry.
+Notably, \cite{Blanton:2011aa} find that the background subtractions in SDSS Data Release 7 has a size dependent bias in the galaxy fluxes.
+In addition \cite{Bernardi:2013aa} find that the luminosity, and ultimately stellar mass, is underestimated when they are derived from the SDSS \texttt{cmodel} magnitudes in comparison to \texttt{PyMorph} single-S\'{e}rsic and Sersic-Exponential fits to the surface brightness profiles.
 
 In order to quantify the effects of these photometric underestimations in our analysis, we replace our SDSS fluxes in the $ugriz$ band with $ugriz$ fluxes from the NASA-Sloan Atlas (NSA) catalog, which incorporate the improved background subtraction presented in \cite{Blanton:2011aa} and uses single-Seric fit fluxes rather than the standard SDSS \texttt{cmodel} fluxes.
-Using the ratio of the luminosity derived from the improved photometry over the luminosity derived from the standard SDSS VAGC photometry, we impose a preliminary correction on the stellar mass values obtained from \texttt{iSEDfit} assuming a consistent mass-to-light ratio.
-This mass correction leads to a significant increase in the stellar mass function for $\mathcal{M} > 10^{11} \mathcal{M}_{\odot}$ that matches the results from \cite{Bernardi:2013aa}.
-However, the effect of the mass correction was negligible for the quiescent fraction evolution results.
+Using the ratio of the luminosity derived from the improved photometry over the luminosity derived from the standard VAGCVAGC photometry, we apply a preliminary correction to the stellar mass values obtained from \texttt{iSEDfit} assuming a consistent mass-to-light ratio.
+This mass correction leads to a significant increase in the stellar mass function for $\mathcal{M} > 10^{11} \mathcal{M}_{\odot}$; however, the effect of the mass correction was negligible for the quiescent fraction evolution results.
 As a result, we do not discuss the issues with photometric measurements any further in this paper.
@@
 We begin by imposing the parent sample selection criteria from \cite{Moustakas:2013aa}.
-More specifically, we take the statistically complete {\em primary} sample from the PRIMUS data (\cite{Coil:2011aa}) and impose magnitude limits on optical selection bands as specified in \cite{Moustakas:2013aa} Table 1.
+More specifically, we take the statistically complete {\em primary} sample from the PRIMUS data (\citealt{Coil:2011aa}) and impose magnitude limits on optical selection bands as specified in \cite{Moustakas:2013aa} Table 1.
 These limits are in different optical selection bands and have distinct values for the five PRIMUS target fields.
@@
 
-For the PRIMUS objects that meet the above criteria, we assign statistical weights (described in \cite{Coil:2011aa} and \cite{Cool:2013aa}) in order to correct for targeting incompleteness and redshift failures.
+For the PRIMUS objects that meet the above criteria, we assign statistical weights (described in \citealt{Coil:2011aa} and \citealt{Cool:2013aa}) in order to correct for targeting incompleteness and redshift failures.
 The statistical weight, $w_i$, for each galaxy is given by
@@
 \end{equation}
-Equation (1) in \cite{Moustakas:2013aa}.
+as in Equation (1) in \cite{Moustakas:2013aa}.
 Since we are ultimately interested in a mass complete galaxy sample to derive SMFs and QFs, next we impose stellar mass completeness limits to our galaxy sample.
 
-Stellar mass completeness limits for a magnitude-limited survey such as PRIMUS is a function of redshift, the apparent magnitude limit of the survey, and the typical stellar mass-to-light ratio of galaxies near the flux limit.
-As done in \cite{Moustakas:2013aa}, we follow \cite{Pozzetti:2010aa} to empirically determine the stellar mass completeness limits.
-For each of the target galaxies we compute $\mathcal{M}_{\rm{lim}}$ using $\rm{log} \; \mathcal{M}_{\rm{lim}} = \rm{log} \; \mathcal{M} + 0.4 ( m - m_{\rm{lim}})$, where $\mathcal{M}$ is the stellar mass of the galaxy in $\mathcal{M_{\odot}}$, $\mathcal{M}_{\rm{lim}}$ is the stellar mass of each galaxy if its magnitude was equal to the survey magnitude limit, $m$ is the observed apparent magnitude in the selection band, and $m_{\rm{lim}}$ is the magnitude limit for our five fields.
+Stellar mass completeness limits for a magnitude-limited survey such as PRIMUS are functions of redshift, the apparent magnitude limit of the survey, and the typical stellar mass-to-light ratio of galaxies near the flux limit.
+As in \cite{Moustakas:2013aa}, we follow \cite{Pozzetti:2010aa} to empirically determine the stellar mass completeness limits.
+For each of the target galaxies we compute $\mathcal{M}_{\rm{lim}}$ using $\rm{log} \; \mathcal{M}_{\mathrm{lim}} = \mathrm{log} \; \mathcal{M} + 0.4 (m - m_{\mathrm{lim}})$, where $\mathcal{M}$ is the stellar mass of the galaxy in $\mathcal{M_{\odot}}$, $\mathcal{M}_{\rm{lim}}$ is the stellar mass of each galaxy if its magnitude was equal to the survey magnitude limit, $m$ is the observed apparent magnitude in the selection band, and $m_{\rm{lim}}$ is the magnitude limit for our five fields.
 We construct a cumulative distribution of $\mathcal{M}_{\rm{lim}}$ for the $15\%$ faintest galaxies in $\Delta z=0.04$ bins.
@@
 To account for the targeting incompleteness of the SDSS-{\em GALEX} sample, we use the statistical weight estimates provided by the NYU-VAGC catalog.
-Furthermore, we determine a uniform stellar mass completeness limit of $10^{10.2} \mathcal{M}_{\odot}$ above the stellar mass-to-light ratio of the SDSS-{\rm GALEX} data within the imposed redshift limits.
+Furthermore, we determine a uniform stellar mass completeness limit of $10^{10.2} \mathcal{M}_{\odot}$ above the stellar mass-to-light ratio of the SDSS-{\em GALEX} data within the imposed redshift limits.
 We then apply this mass limit in order to obtain our mass-complete galaxy sample at low redshift.
@@
 
-For the EDP of the SDSS-{\em GALEX} galaxy sample (hereafter SDSS EDP), we do not use the SDSS-{\em GALEX} parent data which uses the geometry of the combined angular selection function of the SDSS VAGC and {\em GALEX} (Section \ref{sec:sdss}).
-Instead, since FUV, NUV values are not necessary for EDP, we extend the parent data of the SDSS EDP to the entire SDSS VAGC, including galaxies outside of the {\em GALEX} window function.
+For the EDP of the SDSS-{\em GALEX} galaxy sample (hereafter SDSS EDP), we do not use the SDSS-{\em GALEX} parent data which uses the geometry of the combined angular selection function of the VAGC and {\em GALEX} (Section \ref{sec:sdss}).
+Instead, since FUV, NUV values are not necessary for EDP, we extend the parent data of the SDSS EDP to the entire VAGC, including galaxies outside of the {\em GALEX} window function.
 Furthermore, we impose a redshift range of $0.05-0.12$ on the SDSS EDP.
-This redshift range was empirically determined to account for the lack of faint galaxies at $z \sim 0.2$ and the lack of bright galaxies at $z \sim 0.01$ in the SDSS VAGC.
+This redshift range was empirically determined to account for the lack of faint galaxies at $z \sim 0.2$ and the lack of bright galaxies at $z \sim 0.01$ in the VAGC.
 The lower bound was determined by the bright limit and the upper bound by the faint limit of the $M_r$ versus redshift distribution.

### 2014-08-21 qfenv_paper/qf_environment.tex
Mike's edit's part 2

@@
 
-Throughout the paper we assume cosmology with $\Omega_{m} = 0.3, \Omega_{\Lambda} = 0.7$, and $H_0 = 70 \rm{km} \; \rm{s}^{-1} \rm{Mpc}^{-1}$.
+Throughout the paper we assume cosmology with $\Omega_{m} = 0.3, \Omega_{\Lambda} = 0.7$, and $H_0 = 70 \: \rm{km} \; \rm{s}^{-1} \rm{Mpc}^{-1}$.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Since our sample is derived from two different surveys, we account for the disparity in the redshift uncertainty.
-While PRIMUS provides precise spectroscopic redshifts with $\sigma_{z}/(1+z) \approx 0.5 \%$, due to the higher redshift ranges it probes the uncertainties are significantly greater than that of the SDSS-{\em GALEX} redshifts.
+While PRIMUS provides a large number of redshifts out to $z = 1$, due to using a prism instead of a grating, the uncertainties are significantly larger ($\sigma_{z}/(1+z) \approx 0.5 \%$) than that of the SDSS-{\em GALEX} redshifts.
 In order to have comparable environment measures throughout our redshift range, we apply PRIMUS redshift uncertainties to our galaxy sample selected from SDSS-{\em GALEX}.
-For each SDSS-{\em GALEX} galaxy, we adjust its redshift by randomly sampling a normal distribution with standard deviation $\sigma = 0.005 (1+z_{\rm{SDSS}-GALEX})$, where $z_{\rm{SDSS}-GALEX}$ is the redshift of the galaxy.
+For each SDSS-{\em GALEX} galaxy, we adjust its redshift by randomly sampling a Gaussian distribution with standard deviation $\sigma = 0.005 (1+z_{\rm{SDSS}-GALEX})$, where $z_{\rm{SDSS}-GALEX}$ is the redshift of the galaxy.
 
@@
 We now classify our mass complete galaxy sample into quiescent or star-forming using an evolving cut based on specific star-formation rate utilized in \cite{Moustakas:2013aa} Section 3.2.
-This classification method utilizes the star-forming (SF) sequence, which is the correlation between star-formation rate (SFR) and stellar mass in star-forming galaxies observed at least until $z \sim 2$ (\cite{Noeske:2007aa}).
+This classification method uses the star-forming (SF) sequence, which is the correlation between star-formation rate (SFR) and stellar mass in star-forming galaxies observed at least until $z \sim 2$ (\citealt{Noeske:2007aa}).
 The PRIMUS sample displays a well-defined SF sequence within the redshift range of our galaxy sample.
-Then using the power-law slope for the SF sequence from \cite{Salim:2007aa} (SFR $\propto \mathcal{M}^{0.65}$) and the minimum of the quiescent/star-forming bimodality, determined empirically, we obtain the following equation to classify the target galaxies (Equation 2 in \cite{Moustakas:2013aa}):
+Using the power-law slope for the SF sequence from \cite{Salim:2007aa} (SFR $\propto \mathcal{M}^{0.65}$) and the minimum of the quiescent/star-forming bimodality, determined empirically, we obtain the following equation to classify the target galaxies (Equation 2 in \citealt{Moustakas:2013aa}):
 \begin{equation}

### 2014-08-21 qfenv_paper/qf_environment.tex
Mike's revision part 1 finished

@@
     \begin{tabular}{l l l l l l l } \hline \hline              
-    $z$ &$n_{\rm{env}}$        &Quiescent  &Star-forming  & $\mathcal{M}_{\rm{lim}}$ & $M_{\rm{r}}$ cut-off \\ \hline 
+    $z$ &$n_{\rm{env}}$        &Quiescent  &Star-forming  & $\mathcal{M}_{\rm{lim}}$ & $M_{\rm{r}, lim}$ \\ \hline 
 $0.05-0.12$ &Low           &12859                       &14443                           \\
@@
 where $\mathcal{M}$ is the stellar mass of the galaxy.
-If the target galaxy SFR and stellar mass lies above Equation \ref{eq:qsfclass} we classify it as star-forming; if below, as quiescent (\cite{Moustakas:2013aa} Figure 1.).
+If the target galaxy SFR and stellar mass lie above Equation \ref{eq:qsfclass} we classify it as star-forming; if below, as quiescent (\citealt{Moustakas:2013aa} Figure 1.).
 
@@
 \subsection{Galaxy Environment} \label{sec:environment}
-We define the environment of a galaxy as the number of neighboring {\em Environment Defining Population} galaxies (defined below) within a fixed aperture centered around it.
-We use a fixed aperture measurement of environment because, as \cite{Muldrew:2012aa} finds in their comparison of different environment definition using simulations, it provides a better probe of the entire halo in comparison to other definitions of environment such as nearest neighbor, which provides a better tracer at inter-halo scales.
+We define the environment of a galaxy as the number of neighboring Environment Defining Population galaxies (defined below) within a fixed aperture centered around it.
+We use a fixed aperture measurement of environment in order to probe environment on the halo scale, as \cite{Muldrew:2012aa} finds in their comparison of different environment definition using simulations.
 
-For our aperture, we use a cylinder of dimensions: $R_{\rm{ap}} = 2 \; \rm{Mpc}/h$ and $H_{\rm{ap}} = 25 \; \rm{Mpc}/h$.
+For our aperture, we use a cylinder of dimensions: $R_{\rm{ap}} = 2 \; h^{-1} \rm{Mpc}$ and $H_{\rm{ap}} = 25 \; h^{-1}\rm{Mpc}$.
 Though spherical apertures are often used in literature (e.g.
-\cite{Croton:2005aa}), we use a cylindrical aperture in order to account for the PRIMUS redshift errors and redshift space distortions (i.e.
-"Finger of God" effect).
+\citealt{Croton:2005aa}), we use a cylindrical aperture in order to account for the PRIMUS redshift errors and redshift space distortions (i.e.
+``Finger of God" effect).
 \cite{Cooper:2005aa} finds that $\pm 1000 \; \rm{km} \; \rm{s^{-1}}$ optimally reduces the effects of redshift space distortions.
 The PRIMUS redshift uncertainty at $z \sim 0.7$ corresponds to $\sigma_z < 0.01$, so our aperture height choice of $25 \; \rm{Mpc}/h$ accounts for both of these effects.
-Our choice of cylinder radius was motivated by scale dependence analyses in literature (\cite{Blanton:2006aa}, \cite{Wilman:2010aa}, and \cite{Muldrew:2012aa}), which suggest that galactic properties such as color and quenched fractions are dependent on halo-scale properties such as host dark matter halo mass.
+Our choice of cylinder radius was motivated by scale dependence analyses in literature (\citealt{Blanton:2006aa, Wilman:2010aa, Muldrew:2012aa}), which suggest that galactic properties such as color and quenched fractions are dependent on halo-scale properties such as host dark matter halo mass.
 \cite{Wilman:2010aa}, which uses environment defined by annuli of different radii, find positive correlation for quenched fraction and color on scales $< 1 \; \rm{Mpc}$ and anti-correlation on scales $> 3 \; \rm{Mpc}$.
@@
 
-Before we measure the environment for our galaxy sample, we first construct a volume limited {\em Environment Defining Population} (EDP) with absolute magnitude cut-offs ($M_{r}$) at redshift bin of $\Delta z \sim 0.2$.
+Before we measure the environment for our galaxy sample, we first construct a volume limited Environment Defining Population (EDP) with absolute magnitude cut-offs ($M_{r}$) at redshift bin of $\Delta z \sim 0.2$.
 The $M_{r}$ cut-offs for the EDP are selected such that the cumulative number density over $M_{r}$ for all redshift bins are equal.
-In addition to providing a reasonable comparison of environment measurements for wide redshift range, it also seeks to construct an EDP that contains similar galaxy populations through the redshift range (i.e.
+In addition to providing a reasonable comparison of environment measurements for wide redshift range, we make this choice in order to construct an EDP that contains similar galaxy populations through the redshift range (i.e.
 accounts for the progenitor bias).
@@
 
-For the EDP of the SDSS-{\em GALEX} galaxy sample (hereafter SDSS EDP), we do not use the SDSS-{\em GALEX} parent data which uses the geometry of the combined angular selection function of the VAGC and {\em GALEX} (Section \ref{sec:sdss}).
-Instead, since FUV, NUV values are not necessary for EDP, we extend the parent data of the SDSS EDP to the entire VAGC, including galaxies outside of the {\em GALEX} window function.
+For the EDP of the SDSS-{\em GALEX} galaxy sample (hereafter SDSS EDP), we do not use the SDSS-{\em GALEX} parent data, which uses the geometry of the combined angular selection function of the VAGC and {\em GALEX} (Section \ref{sec:sdss}).
+Instead, since FUV, NUV values are not necessary for the EDP, we extend the parent data of the SDSS EDP to the entire NYU VAGC, including galaxies outside of the {\em GALEX} window function.
 Furthermore, we impose a redshift range of $0.05-0.12$ on the SDSS EDP.
-This redshift range was empirically determined to account for the lack of faint galaxies at $z \sim 0.2$ and the lack of bright galaxies at $z \sim 0.01$ in the VAGC.
-The lower bound was determined by the bright limit and the upper bound by the faint limit of the $M_r$ versus redshift distribution.
+This redshift range was determined to account for the lack of faint galaxies at $z \sim 0.2$ and the lack of bright galaxies at $z \sim 0.01$ in the VAGC.
 As with the PRIMUS redshift bins, we determine the SDSS EDP $M_{r, \rm{lim}}$ by matching the cumulative number density of the highest redshift bin.
@@
 
-For our SDSS-{\em GALEX} galaxy sample, in Section \ref{sec:target}, we imposed PRIMUS redshift errors in order to establish a consistent measurement of environment throughout our redshift range.
-We appropriately impose equivalent redshift adjustments for the SDSS EDP.
+For our SDSS-{\em GALEX} galaxy sample, in Section \ref{sec:target}, we apply PRIMUS redshift errors in order to establish a consistent measurement of environment throughout our redshift range.
+We appropriately apply equivalent redshift adjustments for the SDSS EDP.
 So for the SDSS EDP galaxies that are within the SDSS-{\em GALEX} sample, we adjust the redshift by an identical amount.
@@
 $n_{\rm{env}}$ accounts for the statistical weights of the EDP galaxies.
-Once we obtain environment measurements for all the galaxies in our galaxy sample, we classify galaxies with $n_{\rm{env}} < 1$ to be "low" environment density and galaxies with $n_{\rm{env}} > 3$ to be "high" environment densities.
+Once we obtain environment measurements for all the galaxies in our galaxy sample, we classify galaxies with $n_{\rm{env}} < 0.5$ to be ``low" environment density and galaxies with $n_{\rm{env}} > 3$ to be ``high" environment densities.
 The high environment cutoff was selected in order to reduce contamination from galaxies in low environment densities while maintaining sufficient statistics.
@@
 We also adjusted the environment classification thresholds for these analyses.
-The results obtained from using different apertures and environment classification thresholds are consistent with the results later presented.
+The results obtained from using different apertures and environment classification thresholds are consistent with the results presented below.
 
@@
 To account for these edge effects, we use a Monte Carlo method to impose edge cutoffs on our galaxy sample.
-We first construct a \texttt{ransack} sample of  $N_{\rm{ransack}} = 1,000,000$ points with $RA$ and $Dec$ randomly selected within the window function of the EDP (so SDSS EDP and PRIMUS EDP separately).
+First, using \texttt{ransack} from \cite{Swanson:2008aa}, we construct a random sample of  $N_{\rm{ransack}} = 1,000,000$ points with $RA$ and $Dec$ randomly selected within the window function of the EDP (SDSS EDP and PRIMUS EDP separately).
 We then compute the angular separation, $\theta_{i, \rm{ap}}$ that corresponds to $R_{\rm{ap}}$ (Section \ref{sec:environment}) at the redshift of each sample galaxy $i$.
@@
 \begin{equation} \label{eq:ransack}
-E_{i}[n_{\rm{ransack}}] = \frac{N_{\rm{ransack}}}{A_{\rm{EDP}}}\times {\pi \theta_{i, \rm{ap}}^2} \times f_{\rm{thresh}}. 
+<n_{\rm{ransack}}>_{i} = \frac{N_{\rm{ransack}}}{A_{\rm{EDP}}}\times {\pi \theta_{i, \rm{ap}}^2} \times f_{\rm{thresh}}. 
 \end{equation} 

### 2014-08-21 qfenv_paper/qf_environment.tex
zcosmos degrees

@@
 
-The analysis we describe below uses a fixed cylindrical aperture with dimensions $R_{\rm{ap}} = 2 \: \rm{Mpc}$ and $H_{\rm{ap}} = 25 \: \rm{Mpc}$ to measure environment.
-The same analysis was extended for varying aperture dimensions $R_{\rm{ap}} = 1, 2, 3 \: \rm{Mpc}$ and $H_{\rm{ap}} = 25, 50 \: \rm{Mpc}$.
+The analysis we describe below uses a fixed cylindrical aperture with dimensions $R_{\rm{ap}} = 2 \:h^{-1}\rm{Mpc}$ and $H_{\rm{ap}} = 25 \:h^{-1}\rm{Mpc}$ to measure environment.
+The same analysis was extended for varying aperture dimensions $R_{\rm{ap}} = 1, 2, 3 \: h^{-1}\rm{Mpc}$ and $H_{\rm{ap}} = 25, 50 \:h^{-1}\rm{Mpc}$.
 We also adjusted the environment classification thresholds for these analyses.
@@
 $A_{\rm{EDP}}$ is the total angular area of the EDP window function and $f_{\rm{thresh}}$ is the fractional threshold for the edge effect cut-off.
-For $R_{\rm{ap}}= 2\;\rm{Mpc}$, $f_{\rm{thresh}} = 0.75$.
-If $n_{i, \rm{ransack}} > E_{i}[n_{\rm{ransack}}]$ then galaxy $i$ remains in our sample; otherwise, it is discarded.
+For $R_{\rm{ap}}= 2\;h^{-1} \rm{Mpc}$, $f_{\rm{thresh}} = 0.75$.
+If $n_{i, \rm{ransack}}$ is greater than $<n_{\rm{ransack}}>_i$ then galaxy $i$ remains in our sample; otherwise, it is discarded.
 
@@
 %Discuss possible reasons for the difference between zCOSMOS results and our results. Point out the sample sizes and square degree coverage. 
+% Kovac: 1.7 deg^2, 0.1 < z < 0.4 2340 and 0.4 < z < 0.7 2448. Most of the data points have errors of +/- 0.1, at least +/-0.05
+% Iovino: 1.7 deg^2  617 galaxies in 10.3 < M < 10.8 and 0.1 < z < 0.6. Errors are +/1 0.1
 

### 2014-08-21 qfenv_paper/qf_environment.tex
EDP updated, more edits, removed parenthesis

@@
 \def \Hbp {H$\beta ^\prime$}
+\def \lowenvthresh {0.5}
+\def \highenvthresh {3.0}
 
@@
 We investigate the effects of galaxy environment on the evolution of the quiescent fraction ($f_{\rm{Q}}$) from $z =0.8 $ to $ 0.0$ using spectroscopic redshifts and multi-wavelength imaging data from the PRism MUlti-object Survey (PRIMUS) and the Sloan Digitial Sky Survey (SDSS).
-Our stellar mass limited galaxy sample consists of $\sim 40000$ PRIMUS galaxies within $z = 0.2-0.8$ and $\sim 130,000$ SDSS galaxies within $z = 0.05-0.12$.
+Our stellar mass limited galaxy sample consists of $\sim 13,000$ PRIMUS galaxies within $z = 0.2-0.8$ and $\sim 64,000$ SDSS galaxies within $z = 0.05-0.12$.
 We classify the galaxies as quiescent or star-forming based on an evolving specific star formation cut, and as low or high density environments based on fixed cylindrical aperture environment measurements on a volume-limited Environment Definition Population (from PRIMUS and SDSS).
@@
         \epsscale{1.2}
-	\plotone{fig_edp_sdss_z005_012_primus_z02_10_Mr_redshift.png}
+	\plotone{fig_edp_sdss_z0_05_0_12_primus_z0_2_1_0_Mr_redshift.png}
         \caption{Absolute magnitude $M_{r}$ versus redshift for our mass complete galaxy sample (black squares) with the Environment Defining Population (red circles) plotted on top.
@@
 
-While the PRIMUS survey targeted seven distinct extragalactic deep fields for a total of $\sim 9 \; \rm{deg}^2$, we restrict our sample to five fields that have $GALEX$ and {\em Spitzer}/IRAC imaging (similar to the sample selection in \citealt{Moustakas:2013aa}).
+While the PRIMUS survey targeted seven distinct extragalactic deep fields for a total of $\sim 9 \; \rm{deg}^2$, we restrict our sample to five fields that have $GALEX$ and {\em Spitzer}/IRAC imaging for a total of $\sim 5.5 \; \rm{deg}^2$ (similar to the sample selection in \citealt{Moustakas:2013aa}).
 Four of these fields are a part of the {\em Spitzer} Wide-area Infrared Extragalactic Survey (SWIRE\footnote{http://swire.ipac.caltech.edu/swire/swire.html}): the European Large Area ISO Survey - South $1$ field (ELAIS-S1\footnote{http://dipastro.pd.astro.it/esis}), the Chandra Deep Field South SWIRE field (CDFS), and the XMM Large Scale Structure Survey field (XMM-LSS).
@@
 For the observed photometry, we use the {\em GALEX} FUV and NUV, the two shortest IRAC bands at $3.6$ and $4.5 \mu \rm{m}$ (the two longer-wavelength IRAC channels are excluded because \texttt{iSEDfit} does not model hot dust or polycyclic aromatic hydrocarbons emission lines), and the optical bands.
-
-\begin{table} %Subject to significant change based on the classification of environment
-  \caption{Galaxy Subsamples}
-  \label{tab:subsample}
-  \begin{center}
-    \leavevmode
-    \begin{tabular}{l l l l l l l } \hline \hline              
-    $z$ &$n_{\rm{env}}$        &Quiescent  &Star-forming  & $\mathcal{M}_{\rm{lim}}$ & $M_{\rm{r}, lim}$ \\ \hline 
-$0.05-0.12$ &Low           &12859                       &14443                           \\
-               &High            &18952                       &13387                           \\ 
-                              &               &                       &                           \\ \hline
-$0.2-0.4$      &Low           &1158                    &3445                           \\
-               &High            &817                    &1531                           \\
-               &               &                       &                           \\ \hline
-$0.4-0.6$      &Low           &1315                       &3390                           \\
-               &High            &848                       &1499                           \\
-               &               &                       &                           \\ \hline
-$0.6-0.8$      &Low           &1158                       &2303                           \\
-               &High            &900                       &1275                           \\
-               &               &                       &                           \\ \hline
-  \multicolumn{4}{l}{}                                             \\       
-    \end{tabular} \par
-    \end{center}
-%    \bigskip 
-    {\bf Notes}: Number of galaxies in the mass complete subsamples derived in Section \ref{sec:sample}.
-The subsamples are classified based on environment $n_{\rm{env}}$ and star formation rate (star-forming or quiescent).
-The lowest redshift bin is derived from SDSS; the rest are from PRIMUS.
-    \bigskip
-\end{table}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Galaxy Sample} \label{sec:target} 
-\begin{figure*}
+\begin{table*} 
+  \caption{Galaxy Subsamples}
+  \label{tab:subsample}
   \begin{center}
     \leavevmode
-    \epsfig{file=fig_envcount_cylr2h25_thresh75_sdss_z0_05_0_12_primus_z0_21_0_lowenv0_5_highenv3_0_primuszerr_masslimit_edgecut_histogram.png, height=0.5\textwidth}
-     \caption{Normalized distribution of environment measurements ($n_{\rm{env}}$) for our mass complete galaxy sample within the edges.
-The star-forming galaxies contribution to the distribution is colored blue and diagonally patterned.
-The contribution from quiescent galaxies is colored in red.
-Each redshift panel is divided into three sections of by the environment classification cutoffs (vertical black lines): low density environment $n_{\rm{env}} < 0.5$ and high density environment $n_{\rm{env}} > 3.0$.
-The percentages of the redshift bin contained in the environment classifications are presented above the distribution.
-For example at $0.2 < z < 0.4$, $56.0 \%$ of galaxies in the redshift bin have low density environments while $29.0\%$ of galaxies in the redshift bin have high density environments.
-}      \label{fig:envcount}
+    \begin{tabular}{ccccccc} \hline \hline              
+     &\multicolumn{1}{c}{$n_{\rm{env}}$}        & \multicolumn{2}{c}{$N_{\rm{gal}}$}  & \multicolumn{2}{c}{$\mathcal{M}_{\rm{lim}}$} & $M_{\rm{r}, lim}$ \\ 
+    & & Quiescent & Star-Forming & Quiescent & Star-Forming &  \\ \hline 
+$0.05 < z < 0.12$ & $n_{\rm{env}} < \lowenvthresh $ & 4969 & 5943 & $10^{10.2} \mathcal{M}_{\odot}$ & $10^{10.2} \mathcal{M}_{\odot}$ & -20.98 \\
+               & $n_{\rm{env}} > \highenvthresh $ &17488 & 12244 &                          \\ 
+                              & all          &$33968$                       & $30058$                          \\ \hline
+$0.2 < z < 0.4$      &$n_{\rm{env}} < \lowenvthresh $           &282                    &1020 & $10^{9.8} \mathcal{M}_{\odot}$ & $10^{9.8} \mathcal{M}_{\odot}$ &-21.10 \\
+               &$n_{\rm{env}} > \highenvthresh $            &410                    &850                           \\
+               & all                & $995$                      & $2628$                          \\ \hline
+$0.4 < z < 0.6$      &$n_{\rm{env}} < \lowenvthresh $           &426                       &1226 & $10^{10.3} \mathcal{M}_{\odot}$ & $10^{10.3} \mathcal{M}_{\odot}$ & -21.06 \\
+               &$n_{\rm{env}} > \highenvthresh $            &543                       &983                           \\
+               & all               & $1462$                      & $3334$                          \\ \hline
+$0.6 < z < 0.8$      &$n_{\rm{env}} < \lowenvthresh $           &389                       &932  & $10^{10.7} \mathcal{M}_{\odot}$ & $10^{10.6} \mathcal{M}_{\odot}$ & -20.90 \\
+               &$n_{\rm{env}} > \highenvthresh $            &642                       &907                           \\
+               & all              & $1590$                      & $2852$                          \\ \hline
+Total &      & \multicolumn{2}{c}{76887} & \\ \hline
+  \multicolumn{4}{l}{}                                             \\       
+    \end{tabular} \par
     \end{center}
-\end{figure*}
+%    \bigskip 
+    {\bf Notes}: Number of galaxies ($N_{\rm{gal}}$) in the mass complete subsamples within the edges of the survey (Section \ref{sec:sample}).
+The subsamples are classified based on environment $n_{\rm{env}}$ and star formation rate (star-forming or quiescent).
+The lowest redshift bin is derived from SDSS; the rest are from PRIMUS.
+We also list the stellar mass completeness limit $\mathcal{M}_{\rm{lim}}$ for our sample and the $r$-band absolute magnitude limits $M_{\rm{r}, lim}$ for the Environment Defining Population.
+    \bigskip
+\end{table*}
 
@@
 If the target galaxy SFR and stellar mass lie above Equation \ref{eq:qsfclass} we classify it as star-forming; if below, as quiescent (\citealt{Moustakas:2013aa} Figure 1.).
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% GALAXY ENVIRONMENT
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Galaxy Sample} \label{sec:target} 
 \begin{figure*}
@@
     \leavevmode
-    \epsfig{file=fig_smf_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_2envbin_lowenv0_5_highenv3_0_lit_primuszerr.eps, height=0.75\textwidth,angle=90}
-     \caption{Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) target galaxies in 
-low (left) and high (right) environments from redshift range $z=0-0.8$. The environment of each galaxy  
-was calculated using a cylindrical aperture size of $R=2 \: \rm{Mpc}$ and $H=25 \: \rm{Mpc}$ and  
-classification based on the cut-offs specified in Table \ref{tab:aperture}. The SMFs use mass bins of 
-width $\Delta \rm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.25$. In each panel we use shades of blue 
-(star-forming) and orange (quiescent) to represent the SMF at different redshift, higher redshifts being
-progressively lighter.}      \label{fig:smf}
+    \epsfig{file=fig_envcount_cylr2h25_thresh75_sdss_z0_05_0_12_primus_z0_21_0_lowenv0_5_highenv3_0_primuszerr_masslimit_edgecut_histogram.png, height=0.5\textwidth}
+     \caption{Normalized distribution of environment measurements ($n_{\rm{env}}$) for our mass complete galaxy sample within the edges.
+The star-forming galaxies contribution to the distribution is colored blue and diagonally patterned.
+The contribution from quiescent galaxies is colored in red.
+Each redshift panel is divided into three sections of by the environment classification cutoffs (vertical black lines): low density environment $n_{\rm{env}} < 0.5$ and high density environment $n_{\rm{env}} > 3.0$.
+The percentages of the redshift bin contained in the environment classifications are presented above the distribution.
+For example at $0.2 < z < 0.4$, $56.0 \%$ of galaxies in the redshift bin have low density environments while $29.0\%$ of galaxies in the redshift bin have high density environments.
+}      \label{fig:envcount}
     \end{center}
 \end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% GALAXY ENVIRONMENT
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Galaxy Environment} \label{sec:environment}
@@
 Before we consider the cumulative number densities in the redshift bins, we first determine the $M_r$ limit for the highest redshift bin ($0.6-0.8$) by examining the $M_{r}$ distribution with bin size $\Delta M_{r} = 0.25$ and select $M_{r,\rm{lim}}$ near the peak of the distribution where bins with $M_{r} > M_{r,\rm{lim}}$ have fewer galaxies than the bin at $M_{r, \rm{lim}}$.
-We conservatively choose $M_{r, \rm{lim}}(0.6 < z < 0.8)$ to be $M_{r} = -20.75$.
-Then for the lower redshift bins, we impose absolute magnitude limits ($M_{r,\rm{lim}}$) such that the cumulative number density, calculated with the galaxy statistical weights, of the bin ordered by $M_{r}$ is equal to the cumulative number density of the highest redshift bin at $M_{r, \rm{lim}}(0.6 < z < 0.8) = -20.75$.
+We conservatively choose $M_{r, \rm{lim}}(0.6 < z < 0.8)$ to be $M_{r} = -20.98$.
+Then for the lower redshift bins, we impose absolute magnitude limits ($M_{r,\rm{lim}}$) such that the cumulative number density, calculated with the galaxy statistical weights, of the bin ordered by $M_{r}$ is equal to the cumulative number density of the highest redshift bin at $M_{r, \rm{lim}}(0.6 < z < 0.8) = -20.98$.
 
@@
 As with the PRIMUS redshift bins, we determine the SDSS EDP $M_{r, \rm{lim}}$ by matching the cumulative number density of the highest redshift bin.
-For redshift bins $0.05-0.12$, $0.2-0.4$, $0.4-0.6$, $0.6-0.8$ we get $M_{r,\rm{lim}} = -20.57$, $-20.73$, $-20.80$ and $-20.95$, respectively.
+For redshift bins $0.05-0.12$, $0.2-0.4$, $0.4-0.6$, $0.6-0.8$ we get $M_{r,\rm{lim}} = -20.90$, $-21.06$, $-21.10$ and $-20.98$, respectively.
 These absolute magnitude limits are illustrated in Figure \ref{fig:targetEDP}, which show clear $M_r$ cutoffs in the $M_{r}$ distribution versus redshift for the EDP (red circles) on top of the target galaxy sample (black).
@@
 We remind the reader that this is due to the different mass-completeness limits imposed on our galaxy sample for each redshift bins.
+\begin{figure*}
+  \begin{center}
+    \leavevmode
+    \epsfig{file=fig_smf_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_2envbin_lowenv0_5_highenv3_0_lit_primuszerr.eps, height=0.75\textwidth,angle=90}
+     \caption{Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) target galaxies in 
+low (left) and high (right) environments from redshift range $z=0-0.8$. The environment of each galaxy  
+was calculated using a cylindrical aperture size of $R=2 \: \rm{Mpc}$ and $H=25 \: \rm{Mpc}$ and  
+classification based on the cut-offs specified in Table \ref{tab:aperture}. The SMFs use mass bins of 
+width $\Delta \rm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.25$. In each panel we use shades of blue 
+(star-forming) and orange (quiescent) to represent the SMF at different redshift, higher redshifts being
+progressively lighter.}      \label{fig:smf}
+    \end{center}
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-To calculate the uncertainty of the SMFs from the sample variance, we use a standard jackknife technique (as done in \cite{Moustakas:2013aa}).
+To calculate the uncertainty of the SMFs from the sample variance, we use a standard jackknife technique (as done in \citealt{Moustakas:2013aa}).
 For the PRIMUS galaxies, we calculate SMFs after excluding one of the five target fields at a time.
@@
 We further confirm this trend when we compare the median mass between the two environments to find that the median mass for galaxies in high density environments is significantly greater than in low density environments.
-The relationship between mass and environment observed in our SMFs mirror the well-established mass-density relation and observed mass segregation with environment in the literature (\cite{bundy06a}; \cite{Scodeggio:2009aa}; \cite{Bolzonella:2010aa}).
+The relationship between mass and environment observed in our SMFs mirror the well-established mass-density relation and observed mass segregation with environment in the literature (\citealt{bundy06a, Scodeggio:2009aa, Bolzonella:2010aa}).
 
@@
 More specifically, by analyzing the quiescent fraction with respect to mass, redshift, and environment we are able to compare the quiescent fraction evolution in low and high density environments.
-Through this comparison, in Section \ref{sec:env_qf_evol}, we reveal the subtle environmental effects in quenching star formation that are often obscured by the underlying correlations among galactic properties such as color-mass and mass-density relations (\cite{Cooper:2010aa}).
-Furthermore by quantifying the environmental effects of star-formation quenching, we are able to provide constraints on the various proposed environmental quenching mechanisms, such as strangulation and ram-pressure stripping (\cite{McCarthy:2008aa}).
+Through this comparison, in Section \ref{sec:env_qf_evol}, we reveal the subtle environmental effects in quenching star formation that are often obscured by the underlying correlations among galactic properties such as color-mass and mass-density relations (\citealt{Cooper:2010aa}).
+Furthermore by quantifying the environmental effects of star-formation quenching, we are able to provide constraints on the various proposed environmental quenching mechanisms, such as strangulation and ram-pressure stripping (\citealt{McCarthy:2008aa}).
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 In other words, for all subsamples, galaxies in higher mass bins are more likely to have quenched its star-formation.
-With the roughly linear correlation between galaxy SFR to galaxy color and morphology, we find that this trend reflects the well established color-mass and morphology-mass relations: more massive galaxies are more likely to be red or early-type (\cite{blanton09a}).
+With the roughly linear correlation between galaxy SFR to galaxy color and morphology, we find that this trend reflects the well established color-mass and morphology-mass relations: more massive galaxies are more likely to be red or early-type (\citealt{blanton09a}).
 
 Focusing on the redshift evolution of $f_{\rm{Q}}$, we find that for both environments $f_{\rm{Q}}$ increases as redshift decreases.
-For high density environment, this is analogous to the Butcher-Omeler Effect (\cite{Butcher:1984aa}), which states that galaxy populations in groups or clusters have higher $f_{\rm{blue}}$, or lower $f_{\rm{Q}}$, at higher redshift.
+For high density environment, this is analogous to the Butcher-Omeler Effect (\citealt{Butcher:1984aa}), which states that galaxy populations in groups or clusters have higher $f_{\rm{blue}}$, or lower $f_{\rm{Q}}$, at higher redshift.
 For all environments, a larger portion of our galaxy population has quenched its star-formation over time.
-Coupled with the decline of SFR in the star-forming population (\cite{Noeske:2007aa}; \cite{cooper08a}), our results are in agreement with the observed decline of global star-formation in the universe (\cite{hopkins06a}).
+Coupled with the decline of SFR in the star-forming population (\citealt{Noeske:2007aa, cooper08a}), our results are in agreement with the observed decline of global star-formation in the universe (\citealt{hopkins06a}).
 %Maybe Stacey et al.
@@
 This corresponds to the well-known mass-downsizing pattern in the literature (e.g.
-\cite{bundy06a}).
-Furthermore, the mass-downsizing trend observed in each of our environment subsample is consistent with the trend observed in zCOSMOS Redshift Survey for isolated and group galaxies (\cite{Iovino:2010aa}).
+\citealt{bundy06a}).
+Furthermore, the mass-downsizing trend observed in each of our environment subsample is consistent with the trend observed in zCOSMOS Redshift Survey for isolated and group galaxies (\citealt{Iovino:2010aa}).
 %Remark on how the M_{50-50}?
@@
 \cite{Baldry:2006aa} uses project neighbor density environment measures ($\rm{log} \;  \Sigma$) to obtain $f_{\rm{Q}}(\mathcal{M})$ for a range of environmental densities.
-Although in these comparisons, the different environment measurements make direct comparisons unclear, at higher environments ($\rm{log} \; \Sigma > 0.2$ in \cite{Baldry:2006aa}) $f_{\rm{Q}}(\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}) \sim 0.6$ and $f_{\rm{Q}}(\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}) \sim 0.9$, in agreement our high density environment.
-Likewise, for lower environments ($\rm{log} \; \Sigma < -0.4$ in \cite{Baldry:2006aa}) $f_{\rm{Q}}(\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}) \sim 0.4$ and $f_{\rm{Q}}(\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}) \sim 0.8$, which also agree with our low density environment $f_{\rm{Q}}$.
+Although in these comparisons, the different environment measurements make direct comparisons unclear, at higher environments ($\rm{log} \; \Sigma > 0.2$ in \citealt{Baldry:2006aa}) $f_{\rm{Q}}(\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}) \sim 0.6$ and $f_{\rm{Q}}(\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}) \sim 0.9$, in agreement our high density environment.
+Likewise, for lower environments ($\rm{log} \; \Sigma < -0.4$ in \citealt{Baldry:2006aa}) $f_{\rm{Q}}(\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}) \sim 0.4$ and $f_{\rm{Q}}(\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}) \sim 0.8$, which also agree with our low density environment $f_{\rm{Q}}$.
 
-For $z > 0.2$, we compare our PRIMUS $f_{\rm{Q}}$ results to the $f_{\rm{red}}$ (or $1-f_{\rm{blue}}$) results from the zCOSMOS Redshift Survey (\cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, \cite{Kovac:2014aa}), which covers a similar redshift range as PRIMUS.
+For $z > 0.2$, we compare our PRIMUS $f_{\rm{Q}}$ results to the $f_{\rm{red}}$ (or $1-f_{\rm{blue}}$) results from the zCOSMOS Redshift Survey (\citealt{Iovino:2010aa, Cucciati:2010aa, Kovac:2014aa}), which covers a similar redshift range as PRIMUS.
 \cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, and \cite{Kovac:2014aa} using a mass-complete galaxy sample derived from zCOSMOS and a group catalog, 3D local density contrast, and overdensity environment measurements, respectively, compare $f_{\rm{red}}$ with respect to environment.
@@
 
+\begin{table} 
+  \caption{Best Fit Parameters for $f_{\rm{Q}}(\mathcal{M}_{*})$ Fit}
+  \label{tab:bestfitparam}
+  \begin{center}
+    \leavevmode
+    \begin{tabular}{clcc} \hline \hline              
+    $z_1 < z < z_2$ &Environment        &a  &b  \\ \hline 
+$0.05 < z< 0.12$ &$n_{\rm{env}} < \lowenvthresh$ & $0.392 \pm 0.020$ & $0.482 \pm 0.006$ \\
+               &$n_{\rm{env}} > \highenvthresh$ & $0.289 \pm 0.015$ & $0.605 \pm 0.008$ \\ 
+                              &               &                       &                           \\ \hline   
+$0.2 < z <0.4$ & $n_{\rm{env}} < \lowenvthresh$ & $0.289 \pm 0.039$ & $0.395 \pm 0.016$ \\
+               &$n_{\rm{env}} > \highenvthresh$ & $0.383 \pm 0.016$ & $0.504 \pm 0.010$ \\
+               &               &                       &                           \\ \hline
+$0.4 < z < 0.6$      &$n_{\rm{env}} < \lowenvthresh$ & $0.248 \pm 0.042$ & $0.374 \pm 0.018$ \\
+               &$n_{\rm{env}} > \highenvthresh$ & $0.317 \pm 0.034$ & $0.435 \pm 0.013$ \\
+               &               &                       &                           \\ \hline
+$0.6 < z < 0.8$      &$n_{\rm{env}} < \lowenvthresh$ & $0.267 \pm 0.058$ & $0.343 \pm 0.025$ \\
+               &$n_{\rm{env}} > \highenvthresh$            & $0.412 \pm 0.023$ & $0.457 \pm 0.018$ \\
+               &               &                       &                           \\ \hline
+  \multicolumn{4}{l}{}                                             \\       
+    \end{tabular} \par
+    \end{center}
+%    \bigskip 
+    {\bf Notes}: Best fit parameters in Equation \ref{eq:qffit} for each subsample $f_{\rm{Q}}(\mathcal{M}_{*})$ in Figure \ref{fig:qf} for $\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_{\odot}$.
+\end{table}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{equation}
-where $a$ and $b$ are best-fit parameters using {\em MPFIT} (\cite{Markwardt:2009aa}) and $\mathcal{M}_{\rm{fid}}$ represents the empirically selected fiducial mass within the stellar mass limits where there is a sufficiently large number of galaxies.
+where $a$ and $b$ are best-fit parameters using {\em MPFIT} (\citealt{Markwardt:2009aa}) and $\mathcal{M}_{\rm{fid}}$ represents the empirically selected fiducial mass within the stellar mass limits where there is a sufficiently large number of galaxies.
 We primarily focus on $\mathcal{M}_{\rm{fid}} = 10^{10.5} \: \mathcal{M}_{\odot}$.
@@
 Similarly, from \cite{Baldry:2006aa} we plot $f_{\rm{Q}}$ derived from the best-fit $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ for low ($\delta = 0.0$) and high density environment ($\delta = 1.0$).
-
-\begin{table} 
-  \caption{Best Fit Parameters for $f_{\rm{Q}}(\mathcal{M}_{*})$ Fit}
-  \label{tab:bestfitparam}
-  \begin{center}
-    \leavevmode
-    \begin{tabular}{lllll} \hline \hline              
-    $z_1 < z < z_2$ &Environment        &a  &b  \\ \hline 
-$0.05 < z< 0.12$ &$n_{\rm{env}} < 0.5$           &$0.3612 \pm 0.015$	&$0.482 \pm 0.006$                           \\
-               &$n_{\rm{env}} > 3$            &18952                       &13387                           \\ 
-                              &               &                       &                           \\ \hline
-$0.2 < z <0.4$      &Low           &1158                    &3445                           \\
-               &High            &817                    &1531                           \\
-               &               &                       &                           \\ \hline
-$0.4 < z < 0.6$      &Low           &1315                       &3390                           \\
-               &High            &848                       &1499                           \\
-               &               &                       &                           \\ \hline
-$0.6 < z < 0.8$      &Low           &1158                       &2303                           \\
-               &High            &900                       &1275                           \\
-               &               &                       &                           \\ \hline
-  \multicolumn{4}{l}{}                                             \\       
-    \end{tabular} \par
-    \end{center}
-%    \bigskip 
-    {\bf Notes}: Best fit parameters in Equation \ref{eq:qffit} for each subsample $f_{\rm{Q}}(\mathcal{M}_{*})$ in Figure \ref{fig:qf} for $\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_{\odot}$.
-\end{table}
 
@@
 This is in strong agreement with the zCOSMOS results from \cite{Cucciati:2010aa} and \cite{Kovac:2014aa} and suggests that galaxy populations in higher density environments at $z < 1.0$ have higher quenched fractions.
-As galaxy color serves as a proxy for SFR, our results support the existence of the color-density relation (\cite{Cucciati:2010aa}; \cite{Cooper:2010aa}) and debunk the suggestions that the color-density relation is a merely a reflection of the mass-density or morphology-density relation (\cite{Scodeggio:2009aa}, \cite{Tasca:2009aa}).
+As galaxy color serves as a proxy for SFR, our results support the existence of the color-density relation (\citealt{Cucciati:2010aa, Cooper:2010aa}) and debunk the suggestions that the color-density relation is a merely a reflection of the mass-density or morphology-density relation (\citealt{Scodeggio:2009aa, Tasca:2009aa}).
 
@@
 
-\cite{Kovac:2014aa} finds a similar environment dependence on the total $f_{\rm{Q}}$ evolution to our results, with a greater $f_{\rm{Q}}$ evolution for high density environments.
+\cite{Kovac:2014aa} finds a similar environment dependence on the total $f_{\rm{Q}}$ evolution as our results, with a greater $f_{\rm{Q}}$ evolution for high density environments.
 Unfortunately, contrary to our results, \cite{Kovac:2014aa} finds that $f_{\rm{Q}}$ decreases for both environments over cosmic time.
-The negative slope of the $f_{\rm{Q}}$ evolution is enhanced in Figure \ref{fig:qffit_comp} due to the galaxy classification correction we impose.
-However even without the correction (not shown), in their best-fit values, \cite{Kovac:2014aa} finds a decreasing $f_{\rm{Q}}$ evolution.
-%Discuss possible reasons for the difference between zCOSMOS results and our results. Point out the sample sizes and square degree coverage. 
+The negative slope of the $f_{\rm{Q}}$ evolution is enhanced in Figure \ref{fig:qffit_comp} due to the galaxy classification correction we impose, but even without the correction (not shown), in their best-fit values, \cite{Kovac:2014aa} finds a decreasing $f_{\rm{Q}}$ evolution.
+
+While the zCOSMOS survey provides more precise spectroscopic redshift than our sample derived from PRIMUS, our sample provides significantly larger statistics.
+As listed in Table \ref{tab:subsample}, our sample consists of $64,026$ galaxies from SDSS and $12,861$ galaxies from PRIMUS totaling $76887$ galaxies.
+Meanwhile \cite{Iovino:2010aa} has $914$ galaxies with $\mathcal{M} > 10^{10.3} \mathcal{M}_{\odot}$ and $0.1 < z < 0.6$ and $1033$ galaxies with $\mathcal{M} > 10^{10.6} \mathcal{M}_{\odot}$ and $0.1 < z < 0.8$.
+But for the actual sample used to obtain the best-fit $f_{\rm{Q}}$ values in Figure \ref{fig:qffit_comp} \cite{Iovino:2010aa} has $617$ galaxies.
+The more recent \cite{Kovac:2014aa} provides larger statistics with $2340$ galaxies with $0.1 < z < 0.4$ and $2448$ galaxies with $0.4 < z < 0.7$; however falls short of our SDSS-{\em GALEX} and PRIMUS sample.
+Furthermore, our sample derived from SDSS-{\em GALEX} and PRIMUS cover $2505 \rm{deg}^2$ and $5.5 \rm{deg}^2$ respectively.
+Compared to zCOSMOS, which covers $1.7 \rm{deg}^2$ of the sky, our sample provides significantly greater sky coverage and thus less affected by cosmic variance.
+% zCOSMOS has more precise redshift but PRIMUS has it beat in terms of sample size and coverage of the sky 5.5 deg^2 vs 1.7 deg^2
 % Kovac: 1.7 deg^2, 0.1 < z < 0.4 2340 and 0.4 < z < 0.7 2448. Most of the data points have errors of +/- 0.1, at least +/-0.05
@@
 Many physical mechanisms have been proposed to explain the quenching of star-formation observed in our universe.
-Often star-formation quenching is classified into two distinct mechanisms: mass-dependent and environment dependent mechanisms (\cite{Baldry:2006aa}; \cite{Peng:2010aa}).
+Often star-formation quenching is classified into two distinct mechanisms: mass-dependent and environment dependent mechanisms (\citealt{Baldry:2006aa, Peng:2010aa}).
 From the mass-dependence presented in all $f_{\rm{Q}}$ in Figure \ref{fig:qf}, we concur that galaxy stellar mass plays a significant role in quenching.
@@
 	\item From the SMFs, we find that our galaxy population in high density environments, both star-forming and quiescent, have a higher median mass, thus confirming the mass density relation and mass-segregation in different environments.
-	\item In all of our subsamples, we find a clear mass dependence in $f_{\rm{Q}}$. $f_{\rm{Q}}$ increases monotonically with galaxy stellar mass. 
-	\item Both from the $f_{\rm{Q}}$ evolution and $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ values, $f_{\rm{Q}}$ increases with redshift. 
+	\item In all of our subsamples, $f_{\rm{Q}}$ increases monotonically with galaxy stellar mass showing a clear mass dependence. 
+	\item $f_{\rm{Q}}$ increases with redshift for both low and high density environments.
 	\item We conclude, by fitting our $f_{\rm{Q}}$, that $f_{\rm{Q}}$ in high density environments is greater than $f_{\rm{Q}}$ in low density environments regardless of mass and redshift.

### 2014-08-21 qfenv_paper/qf_environment.tex
Change of title

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Summary} \label{sec:summary}
+\section{Summary and Discussion} \label{sec:summary}
 Using a stellar mass complete galaxy sampled derived from SDSS and PRIMUS accompanied by a consistently measured galaxy environment from robust spectroscopic redshifts, we measure the stellar mass functions for star-forming and quiescent in low and high density environments over the redshift range $z < 0.8$.

### 2014-09-08 qfenv_paper/qf_environment.tex
Some changes to section 3

@@
 
-\title{PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 1$}
+\title{PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 0.8$}
 \author{
@@
 
-In comparison to \cite{bundy06a} and \cite{Bolzonella:2010aa}, some of the noted trends are not immediately evident.
+In comparison to results from DEEP2 (\citealt{bundy06a}) and zCOSMOS (\citealt{Bolzonella:2010aa}), some of the noted trends are not immediately evident.
 However, this is mostly due to the conflicting mass limits proposed in each study.
-Not to mention, only part of the redshift range probed by \cite{bundy06a} overlap with our results.
-Overall, we find that the trends we note in the SMF evolution above are in good agreement with results from DEEP2 and zCOSMOS.
+In addition, only part of the redshift range probed by \cite{bundy06a} overlap with our results.
+Overall, we find that the trends we note in the SMF evolution above are in good agreement with \cite{bundy06a} and \cite{Bolzonella:2010aa}.
 
-Observing the evolutionary trends in SMF for each of these sub-populations simultaneously provides a naive narrative of the different galaxy evolutionary tracks involving environment and quenching.
-For example, the decrease in the massive star-forming galaxies in low density environment over cosmic time can be attributed to the transition of those galaxies to any of the other panels.
+Observing the evolutionary trends in SMF for each of these sub-populations provides a narrative of the different galaxy evolutionary tracks involving environment and quenching.
+For example, the decrease in the massive star-forming galaxies in low density environments over cosmic time can be attributed to the transition of those galaxies to any of the other panels.
 The star-forming galaxies in low density environments that have quenched their star formation over time are possibly responsible for the increase of the quiescent, low density environment SMF over time.
@@
 
-While our mass complete subsample coupled with robust environment measurement allows us to compare SMF evolution for each of our subsamples over $z < 1.0$, we caution readers and reserve detailed analysis of the SMFs to future work due to the improvements in photometry that significantly alter the SDSS SMFs mentioned in Section \ref{sec:sdss}.
+While our mass complete subsample coupled with robust environment measurement allows us to compare SMF evolution for each of our subsamples out to $z=0.8$, we caution readers and reserve detailed analysis of the SMFs to future work due to the improvements in photometry that significantly alter the SDSS SMFs mentioned in Section \ref{sec:sdss}.
 
@@
 \section{Quiescent Fraction} \label{sec:qf_const}
-The SMFs calculated in the previous section illustrate the stellar mass distribution of our galaxy population and its evolution over comic time.
+The SMFs calculated in the previous section illustrate the stellar mass distribution of our galaxy population and its evolution over cosmic time.
 In this section, using the SMFs of our subsamples, we compare the quiescent and the star-forming populations by calculating the fraction of galaxies that have quenched their star-formation, the quiescent fraction.
@@
 \end{equation}
-$\Phi_{Q}$ and $\Phi_{SF}$ are the total number of galaxies per unit volume in stellar mass bin of $\Delta(\rm{log} \: \mathcal{M}) = 0.20 \: {\it dex}$ for the quiescent and star-forming subsamples, respectively (Equation \ref{eq:phi}).
+$\Phi_{Q}$ and $\Phi_{SF}$ are the total number of galaxies per unit volume in stellar mass bin of $\Delta(\rm{log} \: \mathcal{M}) = 0.20 \: dex$ for the quiescent and star-forming subsamples, respectively (Equation \ref{eq:phi}).
 We compute $f_{\rm{Q}}$ for high and low density environments for all redshift bins as plotted in Figure \ref{fig:qf}, which shows the evolution of $f_{\rm{Q}}$ for high (right panel) and low (left panel) density environments.

### 2014-09-10 qfenv_paper/qf_environment.tex
Major changes to Section 4 organization
Made Comparison to Literature section.
Addressed comments by Mike Blanton.
Comparison to literature section not finished!

@@
     \leavevmode
-    \epsfig{file=fig_smf_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_2envbin_lowenv0_5_highenv3_0_lit_primuszerr.eps, height=0.75\textwidth,angle=90}
+    \epsfig{file=fig_smf_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_2envbin_lowenv0_5_highenv3_0_lit_primuszerr.eps, height=0.75\textwidth,angle=0}
      \caption{Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) target galaxies in 
@@
 
-With the sufficient statistics available from SDSS and PRIMUS, we evaluate the quiescent fraction in bins of stellar mass and redshift for low and high density environments (Section \ref{sec:qfevol}).
+While the fractional relation of the star-forming and quiescent populations has been investigated in the past, with limited statistics, disentangling the environmental effects f rom underlying correlations among observable galaxy properties such as the color-mass or mass-density relations (\citealt{Cooper:2010aa}) remains a challenge.
+With the sufficient statistics available from SDSS and PRIMUS, we evaluate the quiescent fraction in bins of stellar mass, redshift, and environment in Section \ref{sec:qfevol}.
+By analyzing the quiescent fraction with respect to these properties, in Section \ref{sec:env_qf_evol} we explicitly compare the quiescent fraction evolution in low and high density environments.
+Our comparison reveal the subtle environmental effects on the quiescent fraction evolution.
+Furthermore, by quantifying this environmental effect, we are able constrain the role of environmental quenching in galaxy evolution.
+%With the sufficient statistics available from SDSS and PRIMUS, we evaluate the quiescent fraction in bins of stellar mass and redshift for low and high density environments (Section \ref{sec:qfevol}).
 More specifically, by analyzing the quiescent fraction with respect to mass, redshift, and environment we are able to compare the quiescent fraction evolution in low and high density environments.
@@
 \end{equation}
-$\Phi_{Q}$ and $\Phi_{SF}$ are the total number of galaxies per unit volume in stellar mass bin of $\Delta(\rm{log} \: \mathcal{M}) = 0.20 \: dex$ for the quiescent and star-forming subsamples, respectively (Equation \ref{eq:phi}).
+$\Phi_{Q}$ and $\Phi_{SF}$ are the total number of galaxies per unit volume in stellar mass bin of $\Delta(\rm{log} \: \mathcal{M}) = 0.20 \: \mathrm{dex}$ for the quiescent and star-forming subsamples, respectively (Equation \ref{eq:phi}).
 We compute $f_{\rm{Q}}$ for high and low density environments for all redshift bins as plotted in Figure \ref{fig:qf}, which shows the evolution of $f_{\rm{Q}}$ for high (right panel) and low (left panel) density environments.
@@
 Focusing on the redshift evolution of $f_{\rm{Q}}$, we find that for both environments $f_{\rm{Q}}$ increases as redshift decreases.
-For high density environment, this is analogous to the Butcher-Omeler Effect (\citealt{Butcher:1984aa}), which states that galaxy populations in groups or clusters have higher $f_{\rm{blue}}$, or lower $f_{\rm{Q}}$, at higher redshift.
+For high density environments, this is analogous to the Butcher-Oemler Effect (\citealt{Butcher:1984aa}), which states that galaxy populations in groups or clusters have higher $f_{\rm{blue}}$, or lower $f_{\rm{Q}}$, at higher redshift.
 For all environments, a larger portion of our galaxy population has quenched its star-formation over time.
@@
 
-Finally, we compare our $f_{\rm{Q}}$ results to previous $f_{\rm{Q}}$ (or $f_{\rm{red}}$) measurements with analogous environment classifications.
-For our lowest redshift bin, we find that our $f_{\rm{Q}}$ for low and high environments are consistent with previous SDSS $f_{\rm{Q}}$ (or $f_{\rm{red}}$) measurements as a function of environment.
-For example, \cite{Tinker:2011aa}, using a group-finding algorithm on the SDSS DR7, presents the relationship between $f_{\rm{Q}}$ and overdensity for galaxies within the mass range $\rm{log} \; \mathcal{M} = [9.8, 10.1]$.
-The \cite{Tinker:2011aa} $f_{\rm{Q}}$ at the lowest and highest overdensities, $f_{\rm{Q}} \sim 0.4$ and $f_{\rm{Q}} \sim 0.6$ respectively, are consistent with our $f_{\rm{Q}}$ for low and high density environment at the lower mass limit ($\rm{log} \; \mathcal{M} \sim 10.2$).
+Finally, we compare between our low and high density environment $f_{\rm{Q}}$s at each redshift bin interval.
+For our lowest redshift bin, we find that $f_{\rm{Q}}$ at low density environments ranges from $\sim 0.4$ to $\sim 0.8$ for $10^{10.2} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11.5} \mathcal{M}_{\odot}$.
+Over the same mass range, $f_{\rm{Q}}$ at high density environment ranges from $\sim 0.55$ to $\sim 0.9$.
+Evidently for our SDSS sample, $f_{\rm{Q}}$ in high density environment is notably higher.
 
-At higher masses, our $f_{\rm{Q}}$ results are consistent with \cite{Baldry:2006aa}.
-\cite{Baldry:2006aa} uses project neighbor density environment measures ($\rm{log} \;  \Sigma$) to obtain $f_{\rm{Q}}(\mathcal{M})$ for a range of environmental densities.
-Although in these comparisons, the different environment measurements make direct comparisons unclear, at higher environments ($\rm{log} \; \Sigma > 0.2$ in \citealt{Baldry:2006aa}) $f_{\rm{Q}}(\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}) \sim 0.6$ and $f_{\rm{Q}}(\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}) \sim 0.9$, in agreement our high density environment.
-Likewise, for lower environments ($\rm{log} \; \Sigma < -0.4$ in \citealt{Baldry:2006aa}) $f_{\rm{Q}}(\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}) \sim 0.4$ and $f_{\rm{Q}}(\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}) \sim 0.8$, which also agree with our low density environment $f_{\rm{Q}}$.
+For our PRIMUS sample at $z \sim 0.3$, over $10^{9.5} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11} \mathcal{M}_{\odot}$ $f_{\rm{Q}}$ ranges from $\sim 0.15$ to $\sim 0.55$ for low density environment, while at high density environment $f_{\rm{Q}}$ ranges from $\sim 0.2$ to $\sim 0.7$.
+Similarly, at $z \sim 0.5$, over $10^{10} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11.2} \mathcal{M}_{\odot}$ $f_{\rm{Q}}$ ranges from $\sim 0.25$ to $\sim 0.55$ for low density environment and $f_{\rm{Q}}$ ranges from $\sim 0.3$ to $\sim 0.7$.
+Finally in our highest redshift bin $z \sim 0.7$, over the mass range $10^{10.5} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11.5} \mathcal{M}_{\odot}$, $f_{\rm{Q}}$ ranges from $\sim 0.3$ to $\sim 0.55$ for low density and $\sim 0.45$ to $\sim 0.8$ for high density.
+For the entire redshift range of our sample, $f_{\rm{Q}}$ in high density environment is higher than $f_{\rm{Q}}$ in low density environments.
 
-For $z > 0.2$, we compare our PRIMUS $f_{\rm{Q}}$ results to the $f_{\rm{red}}$ (or $1-f_{\rm{blue}}$) results from the zCOSMOS Redshift Survey (\citealt{Iovino:2010aa, Cucciati:2010aa, Kovac:2014aa}), which covers a similar redshift range as PRIMUS.
-\cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, and \cite{Kovac:2014aa} using a mass-complete galaxy sample derived from zCOSMOS and a group catalog, 3D local density contrast, and overdensity environment measurements, respectively, compare $f_{\rm{red}}$ with respect to environment.
-The $f_{\rm{blue}}$ for group and isolated galaxies from \cite{Iovino:2010aa} are generally inconsistent with our $1-f_{\rm{Q}}$ for high and low density environments.
-
-Similarly, $f_{\rm{red}}$ for high and low overdensities in \cite{Kovac:2014aa} are  greater overall than the PRIMUS $f_{\rm{Q}}$ values in high and low density environments.
-However, \cite{Kovac:2014aa} points out that there is a significant difference between classifying the quenched population using color and SFR.
-For their lower redshift bin ($0.1 < z < 0.4$) they find that their $f_{\rm{Q}}$ defined by color is greater than $f_{\rm{Q}}$ defined by SFR by roughly $0.2$.
-While for their higher redshift bin ($0.4 < z < 0.7$) they find a difference of $0.15-0.19$.
-Although the propagation of this difference for different environments is not explored in \cite{Kovac:2014aa}, if we naively account for the difference uniformly for $f_{\rm{red}}$ at all environments, the \cite{Kovac:2014aa} results in their lower redshift bin are generally consistent with our $f_{\rm{Q}}$ at high and low density environments.
-However, in their higher redshift bin even accounting for the difference in galaxy classification, \cite{Kovac:2014aa} finds a significantly higher $f_{\rm{Q}}$.
-
-We previously addressed that for both low and high density environments, $f_{\rm{Q}}$ increases as redshift decreases.
-This general trend is in good agreement with \cite{Iovino:2010aa}, which finds a similar increase in $1-f_{\rm{blue}}$ over cosmic time for $\mathcal{M} < 10^{10.9} \mathcal{M}_{\odot}$.
-However, in contrast to our $f_{\rm{Q}}$ redshift evolution, \cite{Kovac:2014aa} presents a notable decrease in $f_{\rm{red}}$ over cosmic time for low environment.
-Even for their galaxies in high density environments, \cite{Kovac:2014aa} finds no significant increase in $f_{\rm{red}}$ with cosmic time.
-
-The zCOSMOS results also find that $f_{\rm{red}}$ in high density environments are greater overall than in low density environments.
-The same trend is observed in the PRIMUS results and will be discussed in detail later in Section \ref{sec:env_qf_evol}.
-Another significant trend observed in the zCOSMOS results is the significant mass dependence of the $f_{\rm{red}}$ and $f_{\rm{blue}}$ evolution.
-\cite{Iovino:2010aa} by examining $f_{\rm{blue}}(z)$ in different mass bins for group and isolated galaxies find significantly larger $f_{\rm{blue}}$ evolution at lower masses.
-In fact, \cite{Iovino:2010aa} finds no evolution in $f_{\rm{blue}}$ for $\mathcal{M} > 10^{10.9} \mathcal{M}_{\odot}$ for both group and isolated galaxies over the redshift range $0.4 < z < 0.9$.
-On the other hand, in the lowest mass bin ($10^{10.0} \mathcal{M}_{\odot} < \mathcal{M} < 10^{10.5} \mathcal{M}_{\odot}$) \cite{Iovino:2010aa} finds $f_{\rm{blue}}(z \sim 0.4) - f_{\rm{blue}}(z \sim 0.2) \sim 0.2$ for isolated galaxies and  $f_{\rm{blue}}(z \sim 0.4) - f_{\rm{blue}}(z \sim 0.2) \sim 0.1$ for group galaxies.
-In contrast, in each of the panels of Figure \ref{fig:qf}, we qualitatively find little mass dependence on the $f_{\rm{Q}}$ evolution for either low or high density environments.
-However, due to the distinct stellar mass completeness limits imposed at each redshift bin of our sample, subtle effects such as the mass dependence of the $f_{\rm{Q}}$ evolution are difficult to discern.
+While there is a significant difference in $f_{\rm{Q}}$ between the environments, since the difference is observed from our highest redshift bin it is not necessarily a result of environment dependent quenching mechanisms.
+In order to isolate the environmental dependence on star-formation quenching, in the following section we quantitatively compare the evolution of the quiescent fraction between the different environments.
 
@@
 We present the $f_{Q}(\mathcal{M}_{\rm{fid}})$ evolution for $\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot$ (solid fill) and $10^{11} \mathcal{M}_\odot$ (patterned fill) with the uncertainty of the best-fit parameter $b$ in Equation \ref{eq:qffit} represented by the width of the evolution.
-There is a significant increase in $f_{Q}(\mathcal{M}_{\rm{fid}})$ with decrease in redshift for both environments.
-In addition, over the entire redshift range, high density environment $f_{Q}(\mathcal{M}_{\rm{fid}})$ is greater than low density environment $f_{Q}(\mathcal{M}_{\rm{fid}})$.
+While the high density $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ is greater than low density environment $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ over the entire redshift range of our sample, there is a significant increase in $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ over cosmic time for both environments.
 For the environment cut-offs ($n_{\rm{env}} < 0.5$ for low and $n_{\rm{env}} > 3.0$ for high), there is no significant difference in the slope of the evolution between the environments.}         \label{fig:qffit}
@@
 We primarily focus on $\mathcal{M}_{\rm{fid}} = 10^{10.5} \: \mathcal{M}_{\odot}$.
-This fiducial mass serves to highlight and quantify the $f_{\rm{Q}}$ evolution for different redshifts.
 
 In Figure \ref{fig:qffit} we present the evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ at low (blue) and high (red) density environments for $\mathcal{M}_{\rm{fid}} = 10^{10.5} \: \mathcal{M}_{\odot}$ (solid fill) and $10^{11} \: \mathcal{M}_{\odot}$ (pattern fill).
-Then in Figure \ref{fig:qffit_comp} we explore more stringent environment cut-offs for the high density environment (specified in the top right legend and represented by shading).
-In addition, we plot best-fit parameterization of $f_{\rm{red}}$ for high and low density environment from zCOSMOS, \cite{Iovino:2010aa} (square) and \cite{Kovac:2014aa} (triangle), and SDSS, \cite{Baldry:2006aa} (diamond).
-From \cite{Iovino:2010aa} we calculate $f_{\rm{red}} = 1-f_{\rm{blue}}$ using the best-fit $f_{\rm{blue}}$ from the mass bin $\mathcal{M} = 10^{10.3} - 10^{10.8} \mathcal{M}_{\odot}$.
-From \cite{Kovac:2014aa} we plot an estimated $f_{\rm{Q}}$ by applying the difference between SFR based and color based galaxy classifications to the best-fit $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ for low ($\delta = 0.0$) and high density environment ($\delta = 1.5$).
-Similarly, from \cite{Baldry:2006aa} we plot $f_{\rm{Q}}$ derived from the best-fit $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ for low ($\delta = 0.0$) and high density environment ($\delta = 1.0$).
+The width of the evolution represents the uncertainty derived from {\em MPFIT}.
+As noted earlier in Section \ref{sec:qfevol}, $f_{\rm{Q}}$ in high density environment is significantly greater than $f_{\rm{Q}}$ in low density environment for both fiducial mass choices.
+Throughout our sample's redshift range $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})_{\mathrm{high}} - f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})_{\mathrm{low}} \sim 0.1$
+
+In addition, the $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ evolution illustrates that the quiescent fraction at low redshift increases over cosmic time: $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.1) - f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.7) \sim 0.1$.
+This significant quiescent fraction evolution suggests that internal mechanisms independent of environment are responsible for a significant amount of star-formation quenching.
+The $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ evolution in high density environment ($f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.1) - f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.7) \sim 0.12$) shows little additional evolution.
+
+When we increase our choice of $\mathcal{M}_{\rm{fid}}$ to $10^{11} \mathcal{M}_\odot$, aside from an overall shift in $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ by $\sim 0.2$, we observe the same evolutionary trends.
+$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{11}\mathcal{M}_{\odot})$ for both low and high density environments each increase by $\sim 0.1$ from $z \sim 0.7$ to $\sim 0.1$.
+Evidently, increasing the fiducial mass to $10^{11} \mathcal{M}_{\odot}$ does not significantly alter the evolutionary trends in either environments.
+Although the varying stellar mass completeness at each redshift bin limits the masses we probe for the $f_{\rm{Q}}$ evolution, our $f_{\rm{Q}}$ evolution exhibits little mass dependence.
+
+Considering that our fixed aperture definition of environment is susceptible to contamination due to PRIMUS redshift errors, in Figure \ref{fig:qffit_comp}, we impose more stringent high density environment classifications, extending the cut off to $n_{\mathrm{env}} > 6$ and $9$ (specified in the top right legend and represented by the color of the shading).
+Aside from the increase in uncertainties that accompany a decrease in sample size from a purer high environment sample, we find an extension of the $f_{\rm{Q}}$ difference between the environments we stated earlier.
+A more stringent high environment classification significantly increases the overall $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$: $f_{\mathrm{Q}, n_{\mathrm{env}}>9} > f_{\mathrm{Q}, n_{\mathrm{env}}>6} > f_{\mathrm{Q}, n_{\mathrm{env}}>3} > f_{\mathrm{Q}, n_{\mathrm{env}}<0.5} $.
+
+More importantly, a purer high environment classification reveals a more significant environment dependence on the $f_{\rm{Q}}$ evolution.
+While the difference between the $f_{\rm{Q}}$ evolution in low and high density environment is negligible for the $n_{\rm{env}} > 3$ cut-off, there is a notable difference in $f_{\mathrm{Q}}$ evolution between our highest cut-off $n_{\rm{env}} > 9$ and our low density environment.
+$f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.1) - f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.7) \sim 0.2$ for $n_{\rm{env}} > 9$ versus $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.1) - f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.7) \sim 0.1$ for low density environment as we listed earlier.
+In addition to the environment independent internal quenching mechanisms that can explain the $f_{\rm{Q}}$ evolution at low density environments, there may be other environment dependent mechanisms that can account for the moderate environment dependence of the $f_{\rm{Q}}$ evolution.
+Our measured difference in the $f_{\rm{Q}}$ evolution between environments provides a strict constraint for any environmental quenching models.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% COMPARISON TO LITERATURE
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Comparison to Literature}
+Although a direct comparison with other results is impossible due to our sample specific methodology, a number of results from literature have investigated the quiescent fraction.
+In this section we compare our $f_{\rm{Q}}$ results from above to a number of these results, specifically from SDSS and zCOSMOS, with comparably defined samples and analogous environment classifications.
+
+For our lowest redshift bin SDSS sample, we find that our $f_{\rm{Q}}$ for low and high environments are consistent with other SDSS $f_{\rm{Q}}$ (or $f_{\rm{red}}$) measurements as a function of environment.
+For example, \cite{Baldry:2006aa} uses project neighbor density environment measures ($\rm{log} \;  \Sigma$) to obtain $f_{\rm{Q}}(\mathcal{M})$ for a range of environmental densities.
+Although the different environment measurements make direct comparisons unclear, in their corresponding higher environments ($\rm{log} \; \Sigma > 0.2$ in \citealt{Baldry:2006aa}) $f_{\rm{Q}}(\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}) \sim 0.6$ and $f_{\rm{Q}}(\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}) \sim 0.9$, which is in agreement with our high density environment.
+Likewise, for lower environments ($\rm{log} \; \Sigma < -0.4$ in \citealt{Baldry:2006aa}) $f_{\rm{Q}}(\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}) \sim 0.4$ and $f_{\rm{Q}}(\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}) \sim 0.8$, which also agree with our low density environment $f_{\rm{Q}}$.
+
+More recently, \cite{Tinker:2011aa}, using a group-finding algorithm on the SDSS DR7, presents the relationship between $f_{\rm{Q}}$ and overdensity for galaxies within the mass range $\rm{log} \; \mathcal{M} = [9.8, 10.1]$.
+The \cite{Tinker:2011aa} $f_{\rm{Q}}$ at the lowest and highest overdensities, $f_{\rm{Q}} \sim 0.4$ and $f_{\rm{Q}} \sim 0.6$ respectively, are consistent with our $f_{\rm{Q}}$ for low and high density environment at the lower mass limit ($\rm{log} \; \mathcal{M} \sim 10.2$).
+
+A modified \cite{Tinker:2011aa} sample is used in \cite{geha12a} to obtain $f_{\rm{Q}}$ for isolated galaxies over a wider mass range ($10^{7.4} \mathcal{M}_\odot$ to $10^{11.2} \mathcal{M}_{\odot}$).
+Provided that \cite{geha12a} probe a slightly lower redshift range ($ z \le 0.06$), \cite{geha12a} present a consistent $f_{\rm{Q}}$ range as our SDSS $f_{\rm{Q}}$.
+Within the overlapping mass range, at the low mass end \cite{geha12a} find $f_{\rm{Q}}(\mathcal{M}_{*} \sim 10^{10.2} \mathcal{M}_{\odot}) \sim 0.3$ and at the high mass end they find $f_{\rm{Q}}(\mathcal{M}_{*} \sim 10^{11.2} \mathcal{M}_{\odot}) \sim 0.8$.
+Both of these values agree with our lowest redshift $f_{\rm{Q}}$ results.
+
+For $z > 0.2$, we compare our PRIMUS $f_{\rm{Q}}$ results to the $f_{\rm{red}}$ (or $1-f_{\rm{blue}}$) results from the zCOSMOS Redshift Survey (\citealt{Iovino:2010aa, Cucciati:2010aa, Kovac:2014aa}), which covers a similar redshift range as PRIMUS.
+\cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, and \cite{Kovac:2014aa} using a mass-complete galaxy sample derived from zCOSMOS and a group catalog, 3D local density contrast, and overdensity environment measurements, respectively, compare $f_{\rm{red}}$ with respect to environment.
+The $f_{\rm{blue}}$ for group and isolated galaxies from \cite{Iovino:2010aa} are generally inconsistent with our $1-f_{\rm{Q}}$ for high and low density environments.
+
+Similarly, $f_{\rm{red}}$ for high and low overdensities in \cite{Kovac:2014aa} are  greater overall than the PRIMUS $f_{\rm{Q}}$ values in high and low density environments.
+However, \cite{Kovac:2014aa} points out that there is a significant difference between classifying the quenched population using color and SFR.
+For their lower redshift bin ($0.1 < z < 0.4$) they find that their $f_{\rm{Q}}$ defined by color is greater than $f_{\rm{Q}}$ defined by SFR by roughly $0.2$.
+While for their higher redshift bin ($0.4 < z < 0.7$) they find a difference of $0.15-0.19$.
+Although \cite{Kovac:2014aa} does not elaborate on how the galaxy classification discrepancy applies to the different environments, if we simply account for the difference uniformly for $f_{\rm{red}}$ at all environments, the \cite{Kovac:2014aa} results in their lower redshift bin are roughly consistent with our $f_{\rm{Q}}$ at high and low density environments.
+However, in their higher redshift bin even accounting for the difference in galaxy classification, \cite{Kovac:2014aa} finds a significantly higher $f_{\rm{Q}}$.
+
+As we did for our $f_{\rm{Q}}$ analysis above, we extend our $f_{\rm{Q}}$ comparison to focus on the evolution of the quiescent fraction at $\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_{\odot}$.
+In Figure \ref{fig:qffit_comp}, we plot  best-fit parameterization of $f_{\rm{red}}$ for high and low density environment from zCOSMOS, \cite{Iovino:2010aa} (square) and \cite{Kovac:2014aa} (triangle), and SDSS, \cite{Baldry:2006aa} (diamond).
+From \cite{Iovino:2010aa} we calculate $f_{\rm{red}} = 1-f_{\rm{blue}}$ using the best-fit $f_{\rm{blue}}$ from the mass bin $\mathcal{M} = 10^{10.3} - 10^{10.8} \mathcal{M}_{\odot}$.
+From \cite{Kovac:2014aa} we plot an estimated $f_{\rm{Q}}$ by applying the difference between SFR based and color based galaxy classifications to the best-fit $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ for low ($\delta = 0.0$) and high density environment ($\delta = 1.5$).
+Similarly, from \cite{Baldry:2006aa} we plot $f_{\rm{Q}}$ derived from the best-fit $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ for low ($\delta = 0.0$) and high density environment ($\delta = 1.0$).
+We also plot $f_{\rm{Q}}(\mathcal{M} \sim 10^{10.5} \mathcal{M}_{\odot})$ from \cite{geha12a}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In addition to the overall range of the $f_{\rm{Q}}$, in Section \ref{sec:qfevol} we addressed that for both low and high density environments, $f_{\rm{Q}}$ increases as redshift decreases.
+This general trend is in good agreement with \cite{Iovino:2010aa}, which finds a similar increase in $1-f_{\rm{blue}}$ over cosmic time for $\mathcal{M} < 10^{10.9} \mathcal{M}_{\odot}$.
+However, in contrast to our $f_{\rm{Q}}$ redshift evolution, \cite{Kovac:2014aa} presents a notable decrease in $f_{\rm{red}}$ over cosmic time for low environment.
+Even for their galaxies in high density environments, \cite{Kovac:2014aa} finds no significant increase in $f_{\rm{red}}$ with cosmic time.
+
 Both Figure \ref{fig:qffit} and Figure \ref{fig:qffit_comp} illustrate that throughout the entire redshift range, high density environment has a significantly greater $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ than the lower density environment.
@@
 
-In Figure \ref{fig:qffit}, for $\mathcal{M}_{\rm{fid}} = 10^{11} \mathcal{M}_\odot$, aside from an overall shift in $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ by $\sim 0.2$, we observe the same evolutionary trends.
-$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{11}\mathcal{M}_{\odot})$ for both low and high density environments each increase by $\sim 0.2$ as redshift decreases from $\sim 0.7$ to $\sim 0.1$, keeping the slope of the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ evolution the same.
-Evidently, increasing the fiducial mass to $10^{11} \mathcal{M}_{\odot}$ does not significantly alter the total evolution for either environments.
+The zCOSMOS results also find that $f_{\rm{red}}$ in high density environments are greater overall than in low density environments.
+The same trend is observed in the PRIMUS results and will be discussed in detail later in Section \ref{sec:env_qf_evol}.
+Another significant trend observed in the zCOSMOS results is the significant mass dependence of the $f_{\rm{red}}$ and $f_{\rm{blue}}$ evolution.
+\cite{Iovino:2010aa} by examining $f_{\rm{blue}}(z)$ in different mass bins for group and isolated galaxies find significantly larger $f_{\rm{blue}}$ evolution at lower masses.
+In fact, \cite{Iovino:2010aa} finds no evolution in $f_{\rm{blue}}$ for $\mathcal{M} > 10^{10.9} \mathcal{M}_{\odot}$ for both group and isolated galaxies over the redshift range $0.4 < z < 0.9$.
+On the other hand, in the lowest mass bin ($10^{10.0} \mathcal{M}_{\odot} < \mathcal{M} < 10^{10.5} \mathcal{M}_{\odot}$) \cite{Iovino:2010aa} finds $f_{\rm{blue}}(z \sim 0.4) - f_{\rm{blue}}(z \sim 0.2) \sim 0.2$ for isolated galaxies and  $f_{\rm{blue}}(z \sim 0.4) - f_{\rm{blue}}(z \sim 0.2) \sim 0.1$ for group galaxies.
+In contrast, in each of the panels of Figure \ref{fig:qf}, we qualitatively find little mass dependence on the $f_{\rm{Q}}$ evolution for either low or high density environments.
+However, due to the distinct stellar mass completeness limits imposed at each redshift bin of our sample, subtle effects such as the mass dependence of the $f_{\rm{Q}}$ evolution are difficult to discern.
 

### 2014-09-10 qfenv_paper/qf_environment.tex
Additional changes to Comparison to Literature sec

@@
 
-In addition, the $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ evolution illustrates that the quiescent fraction at low redshift increases over cosmic time: $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.1) - f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.7) \sim 0.1$.
-This significant quiescent fraction evolution suggests that internal mechanisms independent of environment are responsible for a significant amount of star-formation quenching.
-The $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ evolution in high density environment ($f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.1) - f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.7) \sim 0.12$) shows little additional evolution.
+In addition, the $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ evolution illustrates that the quiescent fraction in low density environment increases over cosmic time: $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.1) - f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.7) \sim 0.1$.
+This significant quiescent fraction evolution for low density environment suggests that internal mechanisms, independent of environment, are responsible for a significant amount of star-formation quenching.
+Meanwhile, the $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ evolution in high density environment ($f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.1) - f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.7) \sim 0.12$) shows little additional evolution.
 
@@
 
+In Figure \ref{fig:qffit_comp}, we plot  best-fit parameterization of $f_{\rm{red}}$ for high and low density environment from zCOSMOS, \cite{Iovino:2010aa} (square) and \cite{Kovac:2014aa} (triangle), and SDSS, \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross).
+From \cite{Iovino:2010aa} we calculate $f_{\rm{red}} = 1-f_{\rm{blue}}$ using the best-fit $f_{\rm{blue}}$ from the mass bin $\mathcal{M} = 10^{10.3} - 10^{10.8} \mathcal{M}_{\odot}$.
+From \cite{Kovac:2014aa} we plot an estimated $f_{\rm{Q}}$ by applying the residual between SFR based and color based galaxy classifications to the best-fit $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ for low ($\delta = 0.0$) and high density environment ($\delta = 1.5$).
+Similarly, from \cite{Baldry:2006aa} we plot $f_{\rm{Q}}$ derived from the best-fit $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ for low ($\delta = 0.0$) and high density environment ($\delta = 1.0$).
+For \cite{geha12a}, we plot $f_{\rm{Q}}$ in their mass bin closest to $10^{10.5} \mathcal{M}_{\odot}$, $\mathcal{M} \sim 10^{10.55} \mathcal{M}_{\odot}$.
+%Add sentence about how the varying environment classification helps with the comparison.
+
 For our lowest redshift bin SDSS sample, we find that our $f_{\rm{Q}}$ for low and high environments are consistent with other SDSS $f_{\rm{Q}}$ (or $f_{\rm{red}}$) measurements as a function of environment.
@@
 
-As we did for our $f_{\rm{Q}}$ analysis above, we extend our $f_{\rm{Q}}$ comparison to focus on the evolution of the quiescent fraction at $\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_{\odot}$.
-In Figure \ref{fig:qffit_comp}, we plot  best-fit parameterization of $f_{\rm{red}}$ for high and low density environment from zCOSMOS, \cite{Iovino:2010aa} (square) and \cite{Kovac:2014aa} (triangle), and SDSS, \cite{Baldry:2006aa} (diamond).
-From \cite{Iovino:2010aa} we calculate $f_{\rm{red}} = 1-f_{\rm{blue}}$ using the best-fit $f_{\rm{blue}}$ from the mass bin $\mathcal{M} = 10^{10.3} - 10^{10.8} \mathcal{M}_{\odot}$.
-From \cite{Kovac:2014aa} we plot an estimated $f_{\rm{Q}}$ by applying the difference between SFR based and color based galaxy classifications to the best-fit $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ for low ($\delta = 0.0$) and high density environment ($\delta = 1.5$).
-Similarly, from \cite{Baldry:2006aa} we plot $f_{\rm{Q}}$ derived from the best-fit $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ for low ($\delta = 0.0$) and high density environment ($\delta = 1.0$).
-We also plot $f_{\rm{Q}}(\mathcal{M} \sim 10^{10.5} \mathcal{M}_{\odot})$ from \cite{geha12a}.
+In Figure \ref{fig:qf}, observing the $f_{\rm{Q}}$ evolution with respect mass reveal, qualitatively, little mass dependence in the evolution.
+Moreover, in Figure \ref{fig:qffit}, we illustrated that adjusting the fiducial mass only shifted the overall $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$, but did change the $f_{\rm{Q}}$ evolutionary trend.
+The consistency in the $f_{\rm{Q}}$ evolutionary trends when the fiducial mass is changed suggest that $f_{\rm{Q}}$ evolution exhibit little mass dependence.
+In contrast to the weak mass dependence we observe in our results, \cite{Iovino:2010aa} find significantly different $f_{\rm{Q}}$ evolutions at $\mathcal{M} \sim 10^{11} \mathcal{M}_{\odot}$ and $\mathcal{M} \sim 10^{10.5} \mathcal{M}_{\odot}$, for both group and isolated galaxies.
+In fact at their highest mass bin ($10^{10.9} - 10^{11.4} \mathcal{M}_{\odot}$, \cite{Iovino:2010aa} find no evolution for both environments: constant $f_{\mathrm{blue}} \sim 0.1$ over $z = 0.3 - 0.8$ for both group and isolated galaxy populations.
+
+Meanwhile in their mass bin most comparable to $\mathcal{M}_{\rm{fid}} \sim 10^10.5 \mathcal{M}_{\odot}$ ($10^{10.3} \mathcal{M}_{\odot} - 10^{10.8} \mathcal{M}_{\odot}$), \cite{Iovino:2010aa} finds that $f_{\rm{blue}}$ evolves by $\sim 0.1$ from $z = 0.5$ to $0.25$ for group galaxies and by $\sim 0.3$ from $z=0.55$ to $0.3$ for isolated galaxies as presented in Figure \ref{fig:qffit_comp}.
+Altogether, with mass bins beyond the fiducial masses we explore, \cite{Iovino:2010aa} find a strong mass dependence with $f_{\rm{Q}}$ evolving significantly more in lower mass bins.
+While our sample from PRIMUS provides larger statistics than zCOSMOS, the mass-completeness limits we impose on our sample limits the mass range we probe (e.g.
+$\mathcal{M} > 10^{10.5} \mathcal{M}_{\odot}$ for our $z \sim 0.7$ bin).
+Consequently our results cannot dismiss mass dependence in the $f_{\rm{Q}}$ evolution at lower masses.
+
+In Figure \ref{fig:qffit} and Figure \ref{fig:qffit_comp} we quantified that throughout our redshift range, high density environment has a significantly greater $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ than the low density environment.
+Our findings are in agreement with the zCOSMOS results from \cite{Cucciati:2010aa} and \cite{Kovac:2014aa}.
+As illustrated in Figure \ref{fig:qffit_comp}, both \cite{Cucciati:2010aa} and \cite{Kovac:2014aa} find $f_{\rm{Q}}$ in high density environment significantly greater than $f_{\rm{Q}}$ at low density environment.
+Moreover, since galaxy color serves as a proxy for SFR, our results support the existence of the color-density relation (\citealt{Cucciati:2010aa, Cooper:2010aa}) and debunks the suggestion that the color-density relation is merely a reflection of the mass-density as \cite{Scodeggio:2009aa} suggests for $0.2 < z< 1.4$ in the Vimos VLT Deep Survey.
+% Purposely not mentioning the lack of morphology-density relation for M>10^10.5Msun galaxies as argued in Tasca et al. 2009 in order to not bring up morphology.
+
+In Section \ref{sec:qffit}, we pointed out that $f_{\rm{Q}}$ in low density environment evolved over cosmic time.
+From this trend we deduce that internal, environment independent, quenching mechanisms contribute to star-formation quenching in galaxy evolution.
+\cite{Iovino:2010aa} from zCOSMOS, plotted in Figure \ref{fig:qffit_comp}, also find that $f_{\rm{Q}}$ in low density environment increases over decrease in redshift.
+On the other hand \cite{Kovac:2014aa}, also from zCOSMOS, presents that $f_{\rm{Q}}$ in low density environment decreases over cosmic time.
+This disagreement persists even when we account for the galaxy classification discrepancies in Figure \ref{fig:qffit_comp}.
+
+Furthermore, in Section \ref{sec:qffit}, by comparing the $f_{\rm{Q}}$ evolution between the lowest density environment and the highest density environment, we found moderate evidence for the existence of environment dependent quenching mechanisms.
 
@@
 Even for their galaxies in high density environments, \cite{Kovac:2014aa} finds no significant increase in $f_{\rm{red}}$ with cosmic time.
-
-Both Figure \ref{fig:qffit} and Figure \ref{fig:qffit_comp} illustrate that throughout the entire redshift range, high density environment has a significantly greater $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ than the lower density environment.
-This is in strong agreement with the zCOSMOS results from \cite{Cucciati:2010aa} and \cite{Kovac:2014aa} and suggests that galaxy populations in higher density environments at $z < 1.0$ have higher quenched fractions.
-As galaxy color serves as a proxy for SFR, our results support the existence of the color-density relation (\citealt{Cucciati:2010aa, Cooper:2010aa}) and debunk the suggestions that the color-density relation is a merely a reflection of the mass-density or morphology-density relation (\citealt{Scodeggio:2009aa, Tasca:2009aa}).
-
-The zCOSMOS results also find that $f_{\rm{red}}$ in high density environments are greater overall than in low density environments.
-The same trend is observed in the PRIMUS results and will be discussed in detail later in Section \ref{sec:env_qf_evol}.
-Another significant trend observed in the zCOSMOS results is the significant mass dependence of the $f_{\rm{red}}$ and $f_{\rm{blue}}$ evolution.
-\cite{Iovino:2010aa} by examining $f_{\rm{blue}}(z)$ in different mass bins for group and isolated galaxies find significantly larger $f_{\rm{blue}}$ evolution at lower masses.
-In fact, \cite{Iovino:2010aa} finds no evolution in $f_{\rm{blue}}$ for $\mathcal{M} > 10^{10.9} \mathcal{M}_{\odot}$ for both group and isolated galaxies over the redshift range $0.4 < z < 0.9$.
-On the other hand, in the lowest mass bin ($10^{10.0} \mathcal{M}_{\odot} < \mathcal{M} < 10^{10.5} \mathcal{M}_{\odot}$) \cite{Iovino:2010aa} finds $f_{\rm{blue}}(z \sim 0.4) - f_{\rm{blue}}(z \sim 0.2) \sim 0.2$ for isolated galaxies and  $f_{\rm{blue}}(z \sim 0.4) - f_{\rm{blue}}(z \sim 0.2) \sim 0.1$ for group galaxies.
-In contrast, in each of the panels of Figure \ref{fig:qf}, we qualitatively find little mass dependence on the $f_{\rm{Q}}$ evolution for either low or high density environments.
-However, due to the distinct stellar mass completeness limits imposed at each redshift bin of our sample, subtle effects such as the mass dependence of the $f_{\rm{Q}}$ evolution are difficult to discern.
-
-The similarity of the evolutionary trends at $\mathcal{M}_{\rm{fid}} = 10^{10.5} \: \mathcal{M}_{\odot}$ and $10^{11} \: \mathcal{M}_{\odot}$ conflicts with \cite{Iovino:2010aa} who find contrasting $f_{\rm{Q}}$ evolutions at $\mathcal{M} \sim 10^{11.0} \mathcal{M}_{\odot}$ and $\mathcal{M} \sim 10^{10.5} \mathcal{M}_{\odot}$,  for both group and isolated galaxies.
-In fact at their highest mass bin ($10^{10.9} - 10^{11.4} \mathcal{M}_{\odot}$), \cite{Iovino:2010aa} find no evolution for both environments: $f_{\rm{blue}}$ remains constant at $\sim 0.1$ within $z = 0.3 - 0.8$ for both group and isolated galaxy populations.
-Meanwhile in their mass bin most comparable to our $\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_{\odot}$, they present an evolution of $\Delta f_{\rm{red}} \sim 0.1$ over $z = 0.5$ to $0.25$ for group galaxies and $\Delta f_{\rm{red}} \sim 0.3$ over $z = 0.55$ to $0.3$.
-Furthermore, while we find that the $f_{\rm{Q}}(z)_{\rm{high}} - f_{\rm{Q}}(z)_{\rm{low}}$ remains relatively constant at $\sim 0.1$ over the redshift range for both fiducial masses, \cite{Iovino:2010aa} finds $f_{\rm{blue}}(z)_{ \rm{isolated}} - f_{\rm{blue}}(z)_{\rm{group}}$ is much more significant at $\mathcal{M} \sim 10^{10.5} \mathcal{M}_{\odot}$ than at $\mathcal{M} \sim 10^{11} \mathcal{M}_{\odot}$, where they find no difference.
-
-zCOSMOS results find a clear mass dependence in the $f_{\rm{blue}}$ evolution; however, the consistency in evolutionary trends when the fiducial mass is changed reveal that our $f_{\rm{Q}}$ evolution exhibits little mass dependence.
-Although our sample from SDSS and PRIMUS provides significantly larger statistics, due to the limited mass ranges probed in our mass-complete sample (e.g.
-$\mathcal{M} > 10^{10.5} \mathcal{M}_{\odot}$ for our $z \sim 0.7$ bin) it is difficult to dismiss the mass dependence observed in the zCOSMOS results.
-
-Another trend we observe in both Figure \ref{fig:qffit} Figure \ref{fig:qffit_comp}, is that for both environments $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ increases as redshift decreases.
-This highlights the general increase of $f_{\rm{Q}}(\mathcal{M})$ as redshift decreases noted earlier.
-More importantly, by fitting our $f_{\rm{Q}}$ evolution and obtaining the value at the fiducial mass, we are able to quantify the total evolution of $f_{\rm{Q}}$ for both low and high density environments through $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}}, z \sim 0.1) - f_{\rm{Q}}(\mathcal{M}_{\rm{fid}}, z \sim 0.7)$ for both environments.
-In Figure \ref{fig:qffit}, we find that $f_{\rm{Q}}$ evolves by a similar amount for both environments.
-
-Considering that fixed aperture definition of environment is susceptible to contamination due to PRIMUS redshift errors, in Figure \ref{fig:qffit_comp}, we consider more stringent classification of high density environments extending the cut-off to $n_{\rm{env}} > 6, 9$.
-A more stringent classification significantly increases the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ overall.
-The decrease in sample size that accompanies a purer high environment sample also increase the uncertainties.
-More importantly, a purer high environment classification reveals a more significant environment dependence of the $f_{\rm{Q}}$ evolution.
-With a purer the high environment classification, we find a steeper slope in the $f_{\rm{Q}}$ and a greater total $f_{\rm{Q}}$ evolution.
-From $ z \sim 0.7$, for the low density environment ($n_{\rm{env}} < 0.5$) $f_{\rm{Q}}$ increases by roughly $0.1$.
-At the highest environments, $f_{\rm{Q}}$ increases by roughly $0.25$.
-Therefore, the total evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ show moderate environment dependence.
 

### 2014-09-11 qfenv_paper/qf_environment.tex
more edits to the comparison to lit

@@
 \subsection{Comparison to Literature}
-Although a direct comparison with other results is impossible due to our sample specific methodology, a number of results from literature have investigated the quiescent fraction.
-In this section we compare our $f_{\rm{Q}}$ results from above to a number of these results, specifically from SDSS and zCOSMOS, with comparably defined samples and analogous environment classifications.
+Although a direct comparison with other results is difficult due to our sample specific methodology, a number of results from literature have investigated the quiescent fraction in comparable fashions.
+In this section we compare our $f_{\rm{Q}}$ results from above to a number of these results, specifically from SDSS and zCOSMOS, with similarly defined samples and analogous environment classifications.
 
@@
 
-Furthermore, in Section \ref{sec:qffit}, by comparing the $f_{\rm{Q}}$ evolution between the lowest density environment and the highest density environment, we found moderate evidence for the existence of environment dependent quenching mechanisms.
+Furthermore, in Section \ref{sec:qffit}, our comparison of the $f_{\rm{Q}}$ evolution between the lowest density environment and the highest density environment revealed a modicum of evidence for the existence of environment dependent quenching mechanisms.
+The same comparison on zCOSMOS results (\citealt{Iovino:2010aa, Kovac:2014aa}) present trends inconsistent with our findings.
+First, comparing the high (red) and low (blue) density environments for \cite{Iovino:2010aa} in Figure \ref{fig:qffit_comp} shows that there is indeed pronounced discrepancies between the $f_{\rm{Q}}$ evolution in different environments.
+Group galaxies in \cite{Iovino:2010aa} have higher overall $f_{\rm{Q}}$ than isolated galaxies.
+However, unlike our results, which find a greater $f_{\rm{Q}}$ evolution at higher density environments, \cite{Iovino:2010aa} finds the opposite environment dependence that there is a significantly greater $f_{\rm{Q}}$ evolution for isolated galaxies.
+
+Next, \cite{Kovac:2014aa} also find that overall $f_{\rm{Q}}$ in high density is greater than low density environments.
+Like their low density environment $f_{\rm{Q}}$ evolution, $f_{\rm{Q}}$ in high density environment decreases over cosmic time between their two redshift bins.
+Although the decrease in $f_{\rm{Q}}$ over cosmic time conflicts with our results, \cite{Kovac:2014aa} finds a greater (less negative) $f_{\rm{Q}}$ evolution in high density environment over low density environment, suggesting an environment dependence that is in the same direction as our results.
+We note that the negative slopes of the $f_{\rm{Q}}$ evolution in both environments are enhanced in Figure \ref{fig:qffit_comp} due to the galaxy classification correction we impose to the \cite{Kovac:2014aa} results.
+However, even without the correction (not shown), in their best-fit $f_{\rm{Q}}$ results, the same evolutionary trends mentioned above are observed.
+
+While the zCOSMOS survey provides more precise spectroscopic redshift than PRIMUS, our sample provides a significantly larger statistics.
+As listed in Table \ref{tab:subsample}, even after our edge effect cuts and stellar mass completeness limits, our sample consists of $12,861$ galaxies from PRIMUS over $0.2< z< 0.8$ and $64,026$ galaxies from SDSS over $0.05 < z < 0.12$.
+Meanwhile, \cite{Iovino:2010aa} has $914$ galaxies with $\mathcal{M} > 10^{10.3} \mathcal{M}_{\odot}$ over $0.1 < z < 0.6$ and $1033$ galaxies with $\mathcal{M} > 10^{10.6} \mathcal{M}_{\odot}$ over $0.1 < z < 0.8$.
+But for the actual sample used to obtain the best-fit $f_{\rm{Q}}$ values in Figure \ref{fig:qffit_comp} \cite{Iovino:2010aa} has $617$ galaxies.
+In comparison, our PRIMUS sample alone contains $> 20$ times the number of galaxies.
+Given the difference in sample size, much of the evolutionary trend discrepancy between the \cite{Iovino:2010aa} results and our results could be attributed to the limited statics in \cite{Iovino:2010aa}.
+
+The more recent \cite{Kovac:2014aa} provides larger statistics with $2,340$ galaxies in their lower redshift bin ($0.1 < z < 0.4$) and $2,448$ galaxies in their higher redshift bin ($0.4 < z < 0.7$).
+Although the sample falls short of our PRIMUS sample, which contains over two times the number of galaxies, it contains sufficient statistics for a more s
+
+In addition to the number of galaxies, our sample covers a larger portion of the sky.
+Our SDSS-{\em GALEX} sample covers $2,505 \rm{deg}^2$.
+More comparably, our PRIMUS sample covers $5.5 \rm{deg}^2$, which is over 3 times the sky coverage of zCOSMOS, $1.7 \rm{deg}^2$.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-In addition to the overall range of the $f_{\rm{Q}}$, in Section \ref{sec:qfevol} we addressed that for both low and high density environments, $f_{\rm{Q}}$ increases as redshift decreases.
-This general trend is in good agreement with \cite{Iovino:2010aa}, which finds a similar increase in $1-f_{\rm{blue}}$ over cosmic time for $\mathcal{M} < 10^{10.9} \mathcal{M}_{\odot}$.
-However, in contrast to our $f_{\rm{Q}}$ redshift evolution, \cite{Kovac:2014aa} presents a notable decrease in $f_{\rm{red}}$ over cosmic time for low environment.
-Even for their galaxies in high density environments, \cite{Kovac:2014aa} finds no significant increase in $f_{\rm{red}}$ with cosmic time.
-
-An environment dependence of the $f_{\rm{Q}}$ evolution is also observed in \cite{Iovino:2010aa} - also plotted in Figure \ref{fig:qffit_comp}.
-However, in addition to a much more pronounced distinction between the group and isolated $f_{\rm{Q}}$ evolution, they find the opposite environment dependence.
-Unlike our results, which find a greater $f_{\rm{Q}}$ evolution at higher density environments, \cite{Iovino:2010aa} finds a much greater evolution for isolated galaxies.
-
-\cite{Kovac:2014aa} finds a similar environment dependence on the total $f_{\rm{Q}}$ evolution as our results, with a greater $f_{\rm{Q}}$ evolution for high density environments.
-Unfortunately, contrary to our results, \cite{Kovac:2014aa} finds that $f_{\rm{Q}}$ decreases for both environments over cosmic time.
-The negative slope of the $f_{\rm{Q}}$ evolution is enhanced in Figure \ref{fig:qffit_comp} due to the galaxy classification correction we impose, but even without the correction (not shown), in their best-fit values, \cite{Kovac:2014aa} finds a decreasing $f_{\rm{Q}}$ evolution.
 
@@
 But for the actual sample used to obtain the best-fit $f_{\rm{Q}}$ values in Figure \ref{fig:qffit_comp} \cite{Iovino:2010aa} has $617$ galaxies.
-The more recent \cite{Kovac:2014aa} provides larger statistics with $2340$ galaxies with $0.1 < z < 0.4$ and $2448$ galaxies with $0.4 < z < 0.7$; however falls short of our SDSS-{\em GALEX} and PRIMUS sample.
+The more recent \cite{Kovac:2014aa} provides larger statistics with $2340$ galaxies with $0.1 < z < 0.4$ and $2448$ galaxies with $0.4 < z < 0.7$; however falls short of our PRIMUS sample.
 Furthermore, our sample derived from SDSS-{\em GALEX} and PRIMUS cover $2505 \rm{deg}^2$ and $5.5 \rm{deg}^2$ respectively.

### 2014-09-11 qfenv_paper/qf_environment.tex
Completed draft!

@@
 Moreover, we illustrate that galaxy populations in high density environments have significantly higher quiescent fractions than galaxy populations in low density environments.
-Furthermore, by comparing the quiescent fraction evolutions, we find that the quiescent fraction evolves noticeably more for galaxy populations in high density environments.
-These results suggest that quenching due to the environment has a moderate effect on the quiescent fraction evolution and provide constraints on quenching mechanisms in high density environments such as groups and clusters.
+Furthermore, by comparing the quiescent fraction evolutions in the environments, we find that the quiescent fraction evolves noticeably more for galaxy populations in high density environments.
+These results suggest that environment dependent quenching has a moderate effect on the quiescent fraction evolution.
+Furthermore our results provide constraints on the effect of environment on star-formation quenching.
 \end{abstract}
@@
         \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmass10_5_lit_primuszerr_zcosmoscomp_envthresh_kovacoffset.eps, height=0.45\textwidth}
-        \caption{$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}}=10^{10.5} \mathcal{M}_\odot)$ evolution compared to $f_{\rm{red}}(\mathcal{M}_{*}=10^{10.5} \; \mathcal{M}_{\odot})$ in the literature: \cite{Iovino:2010aa} (square) and \cite{Kovac:2014aa} (triangle) from zCOSMOS and \cite{Baldry:2006aa} (diamond) from SDSS.
-These $f_{\rm{red}}$ values are calculated from the best-fit parameterizations presented in the respective works.
+        \caption{$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}}=10^{10.5} \mathcal{M}_\odot)$ evolution compared to $f_{\rm{red}}(\mathcal{M}_{*}=10^{10.5} \; \mathcal{M}_{\odot})$ in the literature: \cite{Iovino:2010aa} (square) and \cite{Kovac:2014aa} (triangle) from zCOSMOS and \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross) from SDSS.
+The $f_{\rm{red}}$ values from \cite{Iovino:2010aa}, \cite{Kovac:2014aa}, and \cite{Baldry:2006aa} are calculated from the best-fit parameterizations presented in the respective works.
+The $f_{\rm{Q}}$ value from \cite{geha12a} is the $f_{\rm{Q}}$ value at $\mathcal{M} = 10^{10.55} \mathcal{M}_{\odot}$.
 High density environment is represented in red and low density environment is represented in blue.
@@
 Similarly, from \cite{Baldry:2006aa} we plot $f_{\rm{Q}}$ derived from the best-fit $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ for low ($\delta = 0.0$) and high density environment ($\delta = 1.0$).
-For \cite{geha12a}, we plot $f_{\rm{Q}}$ in their mass bin closest to $10^{10.5} \mathcal{M}_{\odot}$, $\mathcal{M} \sim 10^{10.55} \mathcal{M}_{\odot}$.
-%Add sentence about how the varying environment classification helps with the comparison.
+For \cite{geha12a}, we plot $f_{\rm{Q}}$ in their mass bin closest to $10^{10.5} \mathcal{M}_{\odot}$, $\mathcal{M} = 10^{10.55} \mathcal{M}_{\odot}$.
 
@@
 Likewise, for lower environments ($\rm{log} \; \Sigma < -0.4$ in \citealt{Baldry:2006aa}) $f_{\rm{Q}}(\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}) \sim 0.4$ and $f_{\rm{Q}}(\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}) \sim 0.8$, which also agree with our low density environment $f_{\rm{Q}}$.
+The \cite{Baldry:2006aa} points (diamond) in Figure \ref{fig:qffit_comp} reflect this agreement.
 
@@
 Within the overlapping mass range, at the low mass end \cite{geha12a} find $f_{\rm{Q}}(\mathcal{M}_{*} \sim 10^{10.2} \mathcal{M}_{\odot}) \sim 0.3$ and at the high mass end they find $f_{\rm{Q}}(\mathcal{M}_{*} \sim 10^{11.2} \mathcal{M}_{\odot}) \sim 0.8$.
-Both of these values agree with our lowest redshift $f_{\rm{Q}}$ results.
+Both of these values agree with our lowest redshift $f_{\rm{Q}}$ results in low density environment.
+Figure \ref{fig:qffit_comp} illustrates the $f_{\rm{Q}}$ agreement for $\mathcal{M}_{*} = 10^{10.5} \mathcal{M}_{\odot}$.
 
@@
 
-In Section \ref{sec:qffit}, we pointed out that $f_{\rm{Q}}$ in low density environment evolved over cosmic time.
+In Section \ref{sec:env_qf_evol}, we pointed out that $f_{\rm{Q}}$ in low density environment evolved over cosmic time.
 From this trend we deduce that internal, environment independent, quenching mechanisms contribute to star-formation quenching in galaxy evolution.
@@
 
-Furthermore, in Section \ref{sec:qffit}, our comparison of the $f_{\rm{Q}}$ evolution between the lowest density environment and the highest density environment revealed a modicum of evidence for the existence of environment dependent quenching mechanisms.
+Furthermore, in Section \ref{sec:env_qf_evol}, our comparison of the $f_{\rm{Q}}$ evolution between the lowest density environment and the highest density environment revealed a modicum of evidence for the existence of environment dependent quenching mechanisms.
 The same comparison on zCOSMOS results (\citealt{Iovino:2010aa, Kovac:2014aa}) present trends inconsistent with our findings.
@@
 
-While the zCOSMOS survey provides more precise spectroscopic redshift than PRIMUS, our sample provides a significantly larger statistics.
-As listed in Table \ref{tab:subsample}, even after our edge effect cuts and stellar mass completeness limits, our sample consists of $12,861$ galaxies from PRIMUS over $0.2< z< 0.8$ and $64,026$ galaxies from SDSS over $0.05 < z < 0.12$.
+While the zCOSMOS survey provides more precise spectroscopic redshifts than PRIMUS, our sample provides a significantly larger statistics.
+In addition, our sample covers a larger portion of the sky.
+Our SDSS-{\em GALEX} sample covers $2,505 \;\rm{deg}^2$.
+More comparably, our PRIMUS sample covers $5.5 \;\rm{deg}^2$, which is over 3 times the sky coverage of zCOSMOS, $1.7 \;\rm{deg}^2$.
+With a significantly greater sky coverage our sample is less susceptible to cosmic variance.
+
+As listed in Table \ref{tab:subsample}, after our edge effect cuts and stellar mass completeness limits, our sample consists of $12,861$ galaxies from PRIMUS over $0.2< z< 0.8$ and $64,026$ galaxies from SDSS over $0.05 < z < 0.12$.
 Meanwhile, \cite{Iovino:2010aa} has $914$ galaxies with $\mathcal{M} > 10^{10.3} \mathcal{M}_{\odot}$ over $0.1 < z < 0.6$ and $1033$ galaxies with $\mathcal{M} > 10^{10.6} \mathcal{M}_{\odot}$ over $0.1 < z < 0.8$.
@@
 In comparison, our PRIMUS sample alone contains $> 20$ times the number of galaxies.
-Given the difference in sample size, much of the evolutionary trend discrepancy between the \cite{Iovino:2010aa} results and our results could be attributed to the limited statics in \cite{Iovino:2010aa}.
+While there is a considerable difference in the overall $f_{\rm{Q}}$ between our results and those of \cite{Iovino:2010aa}, the use of different methodologies, particularly for galaxy classification and environment measurements, make the comparisons ambiguous.
+On the other hand, the discrepancies in the $f_{\rm{Q}}$ evolutionary trends with our results may be explained by the limited statistics in the \cite{Iovino:2010aa} sample.
 
 The more recent \cite{Kovac:2014aa} provides larger statistics with $2,340$ galaxies in their lower redshift bin ($0.1 < z < 0.4$) and $2,448$ galaxies in their higher redshift bin ($0.4 < z < 0.7$).
-Although the sample falls short of our PRIMUS sample, which contains over two times the number of galaxies, it contains sufficient statistics for a more s
-
-In addition to the number of galaxies, our sample covers a larger portion of the sky.
-Our SDSS-{\em GALEX} sample covers $2,505 \rm{deg}^2$.
-More comparably, our PRIMUS sample covers $5.5 \rm{deg}^2$, which is over 3 times the sky coverage of zCOSMOS, $1.7 \rm{deg}^2$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-While the zCOSMOS survey provides more precise spectroscopic redshift than our sample derived from PRIMUS, our sample provides significantly larger statistics.
-As listed in Table \ref{tab:subsample}, our sample consists of $64,026$ galaxies from SDSS and $12,861$ galaxies from PRIMUS totaling $76887$ galaxies.
-Meanwhile \cite{Iovino:2010aa} has $914$ galaxies with $\mathcal{M} > 10^{10.3} \mathcal{M}_{\odot}$ and $0.1 < z < 0.6$ and $1033$ galaxies with $\mathcal{M} > 10^{10.6} \mathcal{M}_{\odot}$ and $0.1 < z < 0.8$.
-But for the actual sample used to obtain the best-fit $f_{\rm{Q}}$ values in Figure \ref{fig:qffit_comp} \cite{Iovino:2010aa} has $617$ galaxies.
-The more recent \cite{Kovac:2014aa} provides larger statistics with $2340$ galaxies with $0.1 < z < 0.4$ and $2448$ galaxies with $0.4 < z < 0.7$; however falls short of our PRIMUS sample.
-Furthermore, our sample derived from SDSS-{\em GALEX} and PRIMUS cover $2505 \rm{deg}^2$ and $5.5 \rm{deg}^2$ respectively.
-Compared to zCOSMOS, which covers $1.7 \rm{deg}^2$ of the sky, our sample provides significantly greater sky coverage and thus less affected by cosmic variance.
+Although their sample falls short of our PRIMUS sample, which contains over two times the number of galaxies, the \cite{Kovac:2010aa} sample provides a more stable comparison.
+Once their results are adjusted for the different galaxy classification, we find that their overall $f_{\rm{Q}}$ is more or less consistent with our overall $f_{\rm{Q}}$.
+However, it is difficult to explain the significant discrepancies in the $f_{\rm{Q}}$ evolutionary trends.
 % zCOSMOS has more precise redshift but PRIMUS has it beat in terms of sample size and coverage of the sky 5.5 deg^2 vs 1.7 deg^2
@@
 % Iovino: 1.7 deg^2  617 galaxies in 10.3 < M < 10.8 and 0.1 < z < 0.6. Errors are +/1 0.1
-
-Many physical mechanisms have been proposed to explain the quenching of star-formation observed in our universe.
-Often star-formation quenching is classified into two distinct mechanisms: mass-dependent and environment dependent mechanisms (\citealt{Baldry:2006aa, Peng:2010aa}).
-From the mass-dependence presented in all $f_{\rm{Q}}$ in Figure \ref{fig:qf}, we concur that galaxy stellar mass plays a significant role in quenching.
-Furthermore, since $f_Q$ in high density environments is always greater than $f_Q$ in low density environments, our results also reflect the environment dependence in quenching.
-%However, in many of the proposed environment dependent quenching mechanisms, the quenching time scale is proposed to decrease.
-This would result in an increase in the quenched fraction that's faster than the increase in low density environment $f_Q$.
-We find that this is not the case.
-% What does this have to say about physical processes in groups and clusters that affect quenching?
 
@@
 \section{Summary and Discussion} \label{sec:summary}
-Using a stellar mass complete galaxy sampled derived from SDSS and PRIMUS accompanied by a consistently measured galaxy environment from robust spectroscopic redshifts, we measure the stellar mass functions for star-forming and quiescent in low and high density environments over the redshift range $z < 0.8$.
-From these stellar mass functions, we compare the proportion of quiescent galaxies within the subsamples by computing quiescent fraction for each of them.
+Using a stellar mass complete galaxy sampled derived from SDSS and PRIMUS accompanied by a consistently measured galaxy environment from robust spectroscopic redshifts, we measure the stellar mass functions for star-forming and quiescent in low and high density environments over the redshift range $0.05 < z < 0.8$.
+From these stellar mass functions, we compare the proportion of galaxies that have quenched their star-formation within the subsamples by computing quiescent fraction for each of them.
 Afterwards, in order to better quantify the evolution of the quiescent fraction over cosmic time, we fit our quiescent fraction anchored at a fiducial mass.
@@
 \begin{enumerate}
-	\item By noting the SMF evolution for each of our subsamples, we loosely trace the evolutionary tracks our galaxy population tracing the general evolutionary tracks of quenching mechanisms and galaxies infalling into high density environments.
-	\item From the SMFs, we find that our galaxy population in high density environments, both star-forming and quiescent, have a higher median mass, thus confirming the mass density relation and mass-segregation in different environments.
-	\item In all of our subsamples, $f_{\rm{Q}}$ increases monotonically with galaxy stellar mass showing a clear mass dependence. 
-	\item $f_{\rm{Q}}$ increases with redshift for both low and high density environments.
-	\item We conclude, by fitting our $f_{\rm{Q}}$, that $f_{\rm{Q}}$ in high density environments is greater than $f_{\rm{Q}}$ in low density environments regardless of mass and redshift.
-This result confirms the environmental dependence of quenching mechanisms stated previously in literature.
-	\item Comparison of the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ evolution for high and low density environments that the total evolution has a moderate dependence on environment. 
+	\item By measuring the SMF evolution for each of our subsamples, we approximately trace the evolutionary tracks our galaxy population tracing the tracks of quenching mechanisms and galaxies infalling into high density environments.
+	\item From the SMFs, we find that our galaxy population in high density environments, both star-forming and quiescent, have a higher median mass, thus confirming the mass density relation and mass-segregation in different environments throughout our sample's redshift range.
+	\item For all subsamples, $f_{\rm{Q}}$ increases monotonically with galaxy stellar mass showing a clear mass dependence and supporting well established color-mass and morphology mass relations. 
+	\item $f_{\rm{Q}}$ increases significantly with redshift for both low and high density environments.
+For high density environment, this trend is the Butcher-Oemler effect.
+Furthermore, the $f_{\rm{Q}}$ evolution in low density environment suggest the existence of internal environment-independent quenching mechanisms.
+	\item By fitting our $f_{\rm{Q}}$s, we illustrate that $f_{\rm{Q}}$ in high density environments is greater than $f_{\rm{Q}}$ in low density environments regardless of mass and redshift.
+This result reflects the well known trend that galaxies in high density environment are statistically redder, have lower SFRs, and more massive.
+	\item Comparison of the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ evolution for a range of environment classifications reveal that the since $z = 0.8$, $f_{\rm{Q}}$ has evolved by a greater amount in higher density environments.
+For our purest high environment sample ($n_{\rm{env}} > 9$), the total $f_{\rm{Q}}$ evolution is $\sim 0.1$ greater than the total $f_{\rm{Q}}$ evolution in low density environment, revealing a moderate dependence in environment.
 \end{enumerate}
 
-%  demonstrate that the quiescent fraction increases over cosmic time for $ z < 0.8$, regardless of environment.
-During this epoch the quiescent fraction in high density environments is consistently greater than the quiescent fraction in low density environments.
-Furthermore, when we fit the quiescent fraction at a fiducial mass ($\mathcal{M}_{\rm{fid}}$), we find that the evolution of the quiescent fraction from $z \sim 0.8$ to $z \sim 0.1$ is similar for high and low density environments.
+Many physical mechanisms have been proposed to explain the quenching of star-formation observed in our universe.
+Recently star-formation quenching has often been classified into internal or external mechanisms, and sometimes more specifically into mass-dependent and environment-dependent mechanisms (\citealt{Baldry:2006aa, Peng:2010aa}).
+The significant redshift evolution of the $f_{\rm{Q}}$ in low density environment confirms the existence of internal mechanisms that quench star-forming in galaxies.
 
-We thank people and funding...
+Furthermore, the greater $f_{\rm{Q}}$ evolution in high density environment over low density environment demonstrates that in addition to the internal quenching mechanisms, in high density environments such as groups and clusters, environment-quenching also contributes to star-formation quenching.
+Although our results do not specifically shed light on which quenching mechanism (e.g.
+strangulation, ram-pressure stripping, etc.) occur in high density environments, they impose strict constraints on the total contribution of environment quenching that any environment quenching model must satisfy.
+More importantly, our results provide limit on the role of environment quenching in galaxy evolution.
+
+\bigskip 
+We thank people ...
+
+Support for this work was provided by ...
+
+something something, details details
+
+The SDSS is managed by the Astrophysical Research Con- sortium for the Participating Institutions.
+The Participating In- stitutions are the American Museum of Natural History, As- trophysical Institute Potsdam, University of Basel, University of Cambridge, Case Western Reserve University, University of Chicago, Drexel University, Fermilab, the Institute for Ad- vanced Study, the Japan Participation Group, Johns Hopkins University, the Joint Institute for Nuclear Astrophysics, the Kavli Institute for Particle Astrophysics and Cosmology, the Korean Scientist Group, the Chinese Academy of Sciences (LAMOST), Los Alamos National Laboratory, the Max-Planck- Institute for Astronomy (MPIA), the Max-Planck-Institute for Astrophysics (MPA), New Mexico State University, Ohio State University, University of Pittsburgh, University of Portsmouth, Princeton University, the United States Naval Observatory, and the University of Washington.
 %
@@
 \bibliography{PRIMUS}
-
-\appendix
-\begin{table*} %Will contain much more information on environments. 
-  \caption{Environment Defining Aperture Dimensions}
-  \label{tab:aperture}
-  \begin{center}
-    \leavevmode
-    \begin{tabular}{llllll} \hline \hline              
-  Radius (Mpc)          &Height (Mpc)      & Edge Effect Cutoff &High Env (galaxies) &Low Env (galaxies) \\ \hline 
-  1.0 &50 & 80\% & 1.5 & 0.0          \\
-  2.0 &50 & 75\% & 4.0 & 0.0          \\ \hline
-  \multicolumn{5}{l}{}                                             \\       
-    \end{tabular}
-  \end{center}
-\end{table*}
-
-\begin{figure*}
-    \begin{center}
-        \leavevmode
-        \epsscale{1.0}
-        \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmass11_0_lit_primuszerr.eps, height=0.45\textwidth}
-        \caption{The evolution of the quiescent fraction at fiducial mass, $f_{Q}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$, for low (square) and high (circle) density environments within the redshift range $z = 0.0 - 0.8$.}
-    \end{center}
-\end{figure*}
-
-\begin{figure*}
-    \begin{center}
-        \leavevmode
-        \epsscale{1.0}
-        \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmass11_0_lit_primuszerr_zcosmoscomp_envthresh_kovacoffset.eps, height=0.45\textwidth}
-        \caption{The evolution of the quiescent fraction at fiducial mass, $f_{Q}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$, for low (square) and high (circle) density environments within the redshift range $z = 0.0 - 0.8$.}
-    \end{center}
-\end{figure*}
-
 \end{document}

### 2014-09-12 qfenv_paper/qf_environment.tex
not-noteworthy changes

@@
 environmentally-driven quenching in the global census of
-star-formation.  As \citet{cooper08a} and others have pointed out,
+star-formation.  As \cite{cooper08a} and others have pointed out,
 because the environmental dependence of total star-formation rates at
@@
 In Section \ref{sec:sample} we present a brief description of the PRIMUS and SDSS data, our mass complete sample construction, and galaxy environment measurements.
-After dividing our galaxy sample into subsamples of star-forming or quiescent and high or low density environments, we compute and examine the evolution of the stellar mass functions for our subsamples.
-In Section \ref{sec:qf_const}, we calculate the quiescent fraction and compare the evolution of the quiescent fraction between high and low density environments.
-In Section \ref{sec:discussion} we discuss the trends observed in the stellar mass function and quiescent fraction evolution and discuss implications of the results on quenching mechanisms.
+After dividing our galaxy sample into subsamples of star-forming or quiescent and high or low density environments, we compute and examine the evolution of the stellar mass functions for our subsamples in Section \ref{sec:smf}.
+Afterwards, in Section \ref{sec:qf_const}, we calculate the quiescent fraction, analyze the evolution of the quiescent fraction, quantify the effects of environment on the quiescent fraction evolution, and discuss the implications of our quiescent fraction results on star-formation quenching.
 Finally in Section \ref{sec:summary} we summarize our results.

### 2014-09-14 qfenv_paper/qf_environment.tex
Nitya's edits on intro

@@
 decline does not appear to be due to the quenching of a large
-fractions of the star-forming population, as reflected in observations
+fraction of the star-forming population, as reflected in observations
 of the stellar mass function of quiescent and star-forming galaxies
@@
 galaxies in all environments. The most straightforward investigation
-would directly determine the star-forming properties of galaxies as
+would be to directly determine the star-forming properties of galaxies as
 a function of environment, stellar mass and redshift in a single,
@@
 
-Meanwhile in their mass bin most comparable to $\mathcal{M}_{\rm{fid}} \sim 10^10.5 \mathcal{M}_{\odot}$ ($10^{10.3} \mathcal{M}_{\odot} - 10^{10.8} \mathcal{M}_{\odot}$), \cite{Iovino:2010aa} finds that $f_{\rm{blue}}$ evolves by $\sim 0.1$ from $z = 0.5$ to $0.25$ for group galaxies and by $\sim 0.3$ from $z=0.55$ to $0.3$ for isolated galaxies as presented in Figure \ref{fig:qffit_comp}.
+Meanwhile in their mass bin most comparable to $\mathcal{M}_{\rm{fid}} \sim 10^{10.5} \mathcal{M}_{\odot}$ ($10^{10.3} \mathcal{M}_{\odot} - 10^{10.8} \mathcal{M}_{\odot}$), \cite{Iovino:2010aa} finds that $f_{\rm{blue}}$ evolves by $\sim 0.1$ from $z = 0.5$ to $0.25$ for group galaxies and by $\sim 0.3$ from $z=0.55$ to $0.3$ for isolated galaxies as presented in Figure \ref{fig:qffit_comp}.
 Altogether, with mass bins beyond the fiducial masses we explore, \cite{Iovino:2010aa} find a strong mass dependence with $f_{\rm{Q}}$ evolving significantly more in lower mass bins.
@@
 The more recent \cite{Kovac:2014aa} provides larger statistics with $2,340$ galaxies in their lower redshift bin ($0.1 < z < 0.4$) and $2,448$ galaxies in their higher redshift bin ($0.4 < z < 0.7$).
-Although their sample falls short of our PRIMUS sample, which contains over two times the number of galaxies, the \cite{Kovac:2010aa} sample provides a more stable comparison.
+Although their sample falls short of our PRIMUS sample, which contains over two times the number of galaxies, the \cite{Kovac:2014aa} sample provides a more stable comparison.
 Once their results are adjusted for the different galaxy classification, we find that their overall $f_{\rm{Q}}$ is more or less consistent with our overall $f_{\rm{Q}}$.

### 2014-10-07 qfenv_paper/qf_environment.tex
some clarifications added

--- 2014-09-12 qfenv_paper/qf_environment.tex
@@
 
-Throughout the paper we assume cosmology with $\Omega_{m} = 0.3, \Omega_{\Lambda} = 0.7$, and $H_0 = 70 \: \rm{km} \; \rm{s}^{-1} \rm{Mpc}^{-1}$.
+Throughout the paper we assume cosmology with $\Omega_{m} = 0.3, \Omega_{\Lambda} = 0.7$, and $H_0 = 70\;h\: \rm{km} \; \rm{s}^{-1} \rm{Mpc}^{-1}$ with $h = 0.7$.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
         \caption{Absolute magnitude $M_{r}$ versus redshift for our mass complete galaxy sample (black squares) with the Environment Defining Population (red circles) plotted on top.
-Both samples are divided into redshift bins:$z \approx 0.05-0.12$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ (panels left to right).
+Both samples are divided into redshift bins: $z \approx 0.05-0.12$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ (panels left to right).
 The lowest redshift bin ($z \approx 0.05-0.12$; leftmost panel) contain our galaxy sample and EDP selected from SDSS.
@@
 This mass correction leads to a significant increase in the stellar mass function for $\mathcal{M} > 10^{11} \mathcal{M}_{\odot}$; however, the effect of the mass correction was negligible for the quiescent fraction evolution results.
-As a result, we do not discuss the issues with photometric measurements any further in this paper.
+As a result, we do not include the mass corrections and do not discuss the issues with photometric measurements any further in this paper.
 The effects of the discussed photometry methods on the luminosity function and stellar mass function will be examined in detail in future work.
@@
 We also adjusted the environment classification thresholds for these analyses.
-The results obtained from using different apertures and environment classification thresholds are consistent with the results presented below.
+The results obtained from using different apertures and environment classification thresholds are qualitatively consistent with the results presented below.
 

### 2014-10-09 qfenv_paper/qf_environment.tex
Changed H0 = 100 to H0 = 70

@@
 
-Throughout the paper we assume cosmology with $\Omega_{m} = 0.3, \Omega_{\Lambda} = 0.7$, and $H_0 = 70\;h\: \rm{km} \; \rm{s}^{-1} \rm{Mpc}^{-1}$ with $h = 0.7$.
+Throughout the paper we assume cosmology with $\Omega_{m} = 0.3, \Omega_{\Lambda} = 0.7$, and $H_0 = 70\: \rm{km} \; \rm{s}^{-1} \rm{Mpc}^{-1}$.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-For our aperture, we use a cylinder of dimensions: $R_{\rm{ap}} = 2 \; h^{-1} \rm{Mpc}$ and $H_{\rm{ap}} = 25 \; h^{-1}\rm{Mpc}$.
+For our aperture, we use a cylinder of dimensions: $R_{\rm{ap}} = 2.9 \rm{Mpc}$ and $H_{\rm{ap}} = 36 \rm{Mpc}$.
 Though spherical apertures are often used in literature (e.g.
@@
 \cite{Cooper:2005aa} finds that $\pm 1000 \; \rm{km} \; \rm{s^{-1}}$ optimally reduces the effects of redshift space distortions.
-The PRIMUS redshift uncertainty at $z \sim 0.7$ corresponds to $\sigma_z < 0.01$, so our aperture height choice of $25 \; \rm{Mpc}/h$ accounts for both of these effects.
+The PRIMUS redshift uncertainty at $z \sim 0.7$ corresponds to $\sigma_z < 0.01$, so our aperture height choice of $36 \; \rm{Mpc}$ accounts for both of these effects.
 Our choice of cylinder radius was motivated by scale dependence analyses in literature (\citealt{Blanton:2006aa, Wilman:2010aa, Muldrew:2012aa}), which suggest that galactic properties such as color and quenched fractions are dependent on halo-scale properties such as host dark matter halo mass.
-\cite{Wilman:2010aa}, which uses environment defined by annuli of different radii, find positive correlation for quenched fraction and color on scales $< 1 \; \rm{Mpc}$ and anti-correlation on scales $> 3 \; \rm{Mpc}$.
-Our choice of $2 \rm{Mpc}/h$ provides sufficient sample size of galaxies in dense environments, for robust statistics, while tracing galactic properties within the halo scale.
+\cite{Wilman:2010aa}, which uses environment defined by annuli of different radii, find positive correlation for quenched fraction and color on scales $< 1 \; \rm{Mpc}$.
+Our choice of $2.9 \rm{Mpc}$ provides sufficient sample size of galaxies in dense environments, for robust statistics, while tracing galactic properties within the halo scale.
 
@@
 
-The analysis we describe below uses a fixed cylindrical aperture with dimensions $R_{\rm{ap}} = 2 \:h^{-1}\rm{Mpc}$ and $H_{\rm{ap}} = 25 \:h^{-1}\rm{Mpc}$ to measure environment.
-The same analysis was extended for varying aperture dimensions $R_{\rm{ap}} = 1, 2, 3 \: h^{-1}\rm{Mpc}$ and $H_{\rm{ap}} = 25, 50 \:h^{-1}\rm{Mpc}$.
+The analysis we describe below uses a fixed cylindrical aperture with dimensions $R_{\rm{ap}} = 2.9 \:\rm{Mpc}$ and $H_{\rm{ap}} = 36 \:\rm{Mpc}$ to measure environment.
+The same analysis was extended for varying aperture dimensions $R_{\rm{ap}} = 1.4, 2.9, 4.3 \: \rm{Mpc}$ and $H_{\rm{ap}} = 36, 71 \:\rm{Mpc}$.
 We also adjusted the environment classification thresholds for these analyses.
@@
 $A_{\rm{EDP}}$ is the total angular area of the EDP window function and $f_{\rm{thresh}}$ is the fractional threshold for the edge effect cut-off.
-For $R_{\rm{ap}}= 2\;h^{-1} \rm{Mpc}$, $f_{\rm{thresh}} = 0.75$.
+For $R_{\rm{ap}}= 2.9 \;\rm{Mpc}$, $f_{\rm{thresh}} = 0.75$.
 If $n_{i, \rm{ransack}}$ is greater than $<n_{\rm{ransack}}>_i$ then galaxy $i$ remains in our sample; otherwise, it is discarded.
@@
 low (left) and high (right) environments from redshift range $z=0-0.8$. The environment of each galaxy  
-was calculated using a cylindrical aperture size of $R=2 \: \rm{Mpc}$ and $H=25 \: \rm{Mpc}$ and  
+was calculated using a cylindrical aperture size of $R=2.9 \: \rm{Mpc}$ and $H=36 \: \rm{Mpc}$ and  
 classification based on the cut-offs specified in Table \ref{tab:aperture}. The SMFs use mass bins of 

### 2014-10-15 qfenv_paper/qf_environment.tex
blanton edits

--- 2014-10-07 qfenv_paper/qf_environment.tex
@@
 \begin{abstract}
-We investigate the effects of galaxy environment on the evolution of the quiescent fraction ($f_{\rm{Q}}$) from $z =0.8 $ to $ 0.0$ using spectroscopic redshifts and multi-wavelength imaging data from the PRism MUlti-object Survey (PRIMUS) and the Sloan Digitial Sky Survey (SDSS).
-Our stellar mass limited galaxy sample consists of $\sim 13,000$ PRIMUS galaxies within $z = 0.2-0.8$ and $\sim 64,000$ SDSS galaxies within $z = 0.05-0.12$.
-We classify the galaxies as quiescent or star-forming based on an evolving specific star formation cut, and as low or high density environments based on fixed cylindrical aperture environment measurements on a volume-limited Environment Definition Population (from PRIMUS and SDSS).
-For quiescent and star-forming galaxies in low or high density environments, we examine the evolution of their stellar mass function (SMF) evolution.
-Then using the SMFs we compute the $f_{\rm{Q}}(\mathcal{M}_{*})$ and quantify the evolution of $f_{\rm{Q}}(\mathcal{M}_{*})$ within our redshift range.
-We find that in both low and high density environments the quiescent fraction increases with cosmic time.
-Moreover, we illustrate that galaxy populations in high density environments have significantly higher quiescent fractions than galaxy populations in low density environments.
-Furthermore, by comparing the quiescent fraction evolutions in the environments, we find that the quiescent fraction evolves noticeably more for galaxy populations in high density environments.
-These results suggest that environment dependent quenching has a moderate effect on the quiescent fraction evolution.
-Furthermore our results provide constraints on the effect of environment on star-formation quenching.
+We investigate the effects of galaxy environment on the evolution of
+the quiescent fraction ($f_{\rm{Q}}$) from $z =0.8 $ to $ 0.0$ using
+spectroscopic redshifts and multi-wavelength imaging data from the
+PRism MUlti-object Survey (PRIMUS) and the Sloan Digitial Sky Survey
+(SDSS). Our stellar mass limited galaxy sample consists of $\sim
+13,000$ PRIMUS galaxies within $z = 0.2-0.8$ and $\sim 64,000$ SDSS
+galaxies within $z = 0.05-0.12$. We classify the galaxies as quiescent
+or star-forming based on an evolving specific star formation cut, and
+as low or high density environments based on fixed cylindrical
+aperture environment measurements on a volume-limited Environment
+Defining Population (from PRIMUS and SDSS). For quiescent and
+star-forming galaxies in low or high density environments, we examine
+the evolution of their stellar mass function (SMF). Then using the
+SMFs we compute $f_{\rm{Q}}(\mathcal{M}_{*})$ and quantify its
+evolution within our redshift range. As expected, the quiescent
+fraction is higher at higher masses and in denser environments. The
+quiescent fraction rises with cosmic time for all masses and
+environments. At a fiducial mass of $10^{10.5}M_\odot$, between $z\sim
+0.7$ and $0.1$, the quiescent fraction's rise varies from 0.15 at the
+lowest environments to 0.25 at the highest environments we measure.
+These results suggest that for a minority of galaxies their cessation
+of star formation might be associated with external influences on
+them. However, in the recent Universe a substantial fraction of the
+galaxies that cease forming stars do so due to internal processes.
 \end{abstract}
@@
 strongly decreasing function of galaxy stellar mass; at the extreme,
-the lowest mass ($<10^{9}$ $M_\odot$) galaxies are quenched only in
+the lowest mass ($<10^{9}$ $M_\odot$) galaxies end their
+star formation only in
 dense regions, and never in isolation (\citealt{geha12a}).  These
@@
 appears dominated by decreases in the rates of star-formation of
-individual galaxies (\cite{Noeske:2007aa}). There is evidence that a
-large fraction of the decline is associated with strongly
+individual galaxies (\citealt{Noeske:2007aa}). There is evidence that
+a large fraction of the decline is associated with strongly
 infrared-emitting starbursts (\citealt{bell05a, magnelli09a}).  The
-decline does not appear to be due to the quenching of a large
-fraction of the star-forming population, as reflected in observations
-of the stellar mass function of quiescent and star-forming galaxies
-(\citealt{Blanton:2006aa, bundy06a, borch06a, Moustakas:2013aa}).  These
-findings leave little room for the participation of
-environmentally-driven quenching in the global census of
-star-formation.  As \cite{cooper08a} and others have pointed out,
-because the environmental dependence of total star-formation rates at
-fixed redshift is relatively small, environmentally effects are
-unlikely to cause the overall star-formation rate decline.
+decline does not appear to be due to a complete cessation of star
+formation for a large fraction of the star-forming population, as
+reflected in observations of the stellar mass function of quiescent
+and star-forming galaxies (\citealt{Blanton:2006aa, bundy06a,
+  borch06a, Moustakas:2013aa}).  These findings leave little room for
+the participation of environmentally-driven cessation of star
+formation in the global census of star-formation.  As \cite{cooper08a}
+and others have pointed out, because the environmental dependence of
+total star-formation rates at fixed redshift is relatively small,
+environmentally effects are unlikely to cause the overall
+star-formation rate decline.
 
@@
 galaxies in all environments. The most straightforward investigation
-would be to directly determine the star-forming properties of galaxies as
-a function of environment, stellar mass and redshift in a single,
+would be to directly determine the star-forming properties of galaxies
+as a function of environment, stellar mass and redshift in a single,
 consistently analyzed data set. This analysis can reveal how galaxies
-are quenched in the universe over time, quantitatively establish the
+end their star formation over time, quantitatively establish the
 contribution of environmental effects to the overall trends, and
@@
 of sufficiently large samples. In this paper, we apply this approach
-using the Prism Multi-object Survey (PRIMUS; \cite{Coil:2011aa}, 
-\cite{Cool:2013aa}), the largest available redshift survey covering the epochs
-between $0<z<1$.
+using the Prism Multi-object Survey (PRIMUS; \citealt{Coil:2011aa},
+\citealt{Cool:2013aa}), the largest available redshift survey covering
+the epochs between $0<z<1$.
 
-In Section \ref{sec:sample} we present a brief description of the PRIMUS and SDSS data, our mass complete sample construction, and galaxy environment measurements.
-After dividing our galaxy sample into subsamples of star-forming or quiescent and high or low density environments, we compute and examine the evolution of the stellar mass functions for our subsamples in Section \ref{sec:smf}.
-Afterwards, in Section \ref{sec:qf_const}, we calculate the quiescent fraction, analyze the evolution of the quiescent fraction, quantify the effects of environment on the quiescent fraction evolution, and discuss the implications of our quiescent fraction results on star-formation quenching.
-Finally in Section \ref{sec:summary} we summarize our results.
+In Section \ref{sec:sample} we present a brief description of the
+PRIMUS and SDSS data, our mass complete sample construction, and
+galaxy environment measurements. After dividing our galaxy sample into
+subsamples of star-forming or quiescent and high or low density
+environments, we compute and examine the evolution of the stellar mass
+functions for our subsamples in Section \ref{sec:smf}. In
+Section \ref{sec:qf_const}, we calculate the quiescent fraction,
+analyze the evolution of the quiescent fraction, quantify the effects
+of environment on the quiescent fraction evolution, and discuss the
+implications of our quiescent fraction results on the cessation of
+star-formation in galaxies. Finally in Section \ref{sec:summary} we
+summarize our results.
 
-Throughout the paper we assume cosmology with $\Omega_{m} = 0.3, \Omega_{\Lambda} = 0.7$, and $H_0 = 70\;h\: \rm{km} \; \rm{s}^{-1} \rm{Mpc}^{-1}$ with $h = 0.7$.
+Throughout the paper we assume a cosmology with $\Omega_{m} = 0.3,
+\Omega_{\Lambda} = 0.7$, and $H_0 = 70 \: \rm{km} \; \rm{s}^{-1}
+\rm{Mpc}^{-1}$. All magnitudes are AB-relative.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Sample Selection} \label{sec:sample}
-We are interested in quantifying the effects of galaxy environment on the evolution of the quenched fraction over the redshift range $0 < z < 1$.
+We are interested in quantifying the effects of galaxy environment on
+the evolution of the quiescent fraction over the redshift range $0 < z < 1$.
 For our analysis, we require a sample with sufficient depth and robustness to probe the redshift range and to measure galaxy environment.
@@
 
-In Section \ref{sec:primus} and Section \ref{sec:sdss} we provide a brief summary of the PRIMUS data and the SDSS data used for our sample selection.
-Then in Section \ref{sec:target} we define our stellar mass complete galaxy sample.
-Afterwards, in Section \ref{sec:sfq}, we classify our sample galaxies as quiescent or star-forming then calculate the environment using a volume-limited Environment Defining Population in Section \ref{sec:environment}.
-Finally in Section \ref{sec:edgeeffect}, we correct our galaxy sample and environment measurements for edge effects of the surveys.
+In Section \ref{sec:primus} and Section \ref{sec:sdss} we provide a
+brief summary of the PRIMUS data and the SDSS data used for our sample
+selection.  In Section \ref{sec:sfq}, we classify our sample galaxies
+as quiescent or star-forming.  In Section \ref{sec:target} we define
+our stellar mass complete galaxy sample.  We calculate the environment
+using a volume-limited Environment Defining Population in Section
+\ref{sec:environment}.  Finally, in Section \ref{sec:edgeeffect}, we
+account for edge effects in the surveys.
 
@@
         \caption{Absolute magnitude $M_{r}$ versus redshift for our mass complete galaxy sample (black squares) with the Environment Defining Population (red circles) plotted on top.
-Both samples are divided into redshift bins: $z \approx 0.05-0.12$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ (panels left to right).
+Both samples are divided into redshift bins:$z \approx 0.05-0.12$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ (panels left to right).
 The lowest redshift bin ($z \approx 0.05-0.12$; leftmost panel) contain our galaxy sample and EDP selected from SDSS.
@@
 \subsection{PRIMUS} \label{sec:primus}
-At intermediate redshifts we use multiwavelength imaging and spectroscopic redshifts from PRIMUS, a faint galaxy survey with $\sim 120,000$ redshifts ($\sigma_z/(1+z) \approx 0.5 \%$) within the range $z \approx 0-1.2$.
-The survey was conducted using the IMACS spectrograph on the Magellan I Baade $6.5$ m telescope with a slitmask and low dispersion prism.
+At intermediate redshifts we use multiwavelength imaging and
+spectroscopic redshifts from PRIMUS, a faint galaxy survey with $\sim
+120,000$ redshifts ($\sigma_z/(1+z) \approx 0.5 \%$) within the range
+$z \approx 0-1.2$. The survey was conducted using the IMACS
+spectrograph on the Magellan I Baade $6.5$-m telescope with a slitmask and low dispersion prism.
 For details on the PRIMUS observation methods such as survey design, targeting, and data summary, we refer readers to the survey papers (\citealt{Coil:2011aa, Cool:2013aa}).
@@
 
-While the SDSS-{\em GALEX} data discussed above is derived from VAGC Data Release 7, since the release of the catalog, there have been significant improvements in the photometry.
-Notably, \cite{Blanton:2011aa} find that the background subtractions in SDSS Data Release 7 has a size dependent bias in the galaxy fluxes.
-In addition \cite{Bernardi:2013aa} find that the luminosity, and ultimately stellar mass, is underestimated when they are derived from the SDSS \texttt{cmodel} magnitudes in comparison to \texttt{PyMorph} single-S\'{e}rsic and Sersic-Exponential fits to the surface brightness profiles.
+The SDSS-{\em GALEX} data discussed above is derived from the NYU-VAGC
+based on SDSS Data Release 7, using the standard SDSS photometric
+measurements. Several investigators have found that the background
+subtraction techniques used in the standard photometric catalogs
+introduce a size dependent bias in the galaxy fluxes and consequently
+stellar masses (\citealt{west05a, blanton05b, lauer07a, bernardi07a,
+  hyde09a, west10a}).
 
-In order to quantify the effects of these photometric underestimations in our analysis, we replace our SDSS fluxes in the $ugriz$ band with $ugriz$ fluxes from the NASA-Sloan Atlas (NSA) catalog, which incorporate the improved background subtraction presented in \cite{Blanton:2011aa} and uses single-Seric fit fluxes rather than the standard SDSS \texttt{cmodel} fluxes.
-Using the ratio of the luminosity derived from the improved photometry over the luminosity derived from the standard VAGCVAGC photometry, we apply a preliminary correction to the stellar mass values obtained from \texttt{iSEDfit} assuming a consistent mass-to-light ratio.
-This mass correction leads to a significant increase in the stellar mass function for $\mathcal{M} > 10^{11} \mathcal{M}_{\odot}$; however, the effect of the mass correction was negligible for the quiescent fraction evolution results.
-As a result, we do not include the mass corrections and do not discuss the issues with photometric measurements any further in this paper.
-The effects of the discussed photometry methods on the luminosity function and stellar mass function will be examined in detail in future work.
+In order to quantify the effects of these photometric underestimations
+in our analysis, we tried replacing our SDSS fluxes in the $ugriz$
+band with $ugriz$ fluxes from the NASA-Sloan Atlas (NSA) catalog,
+which incorporate the improved background subtraction presented in
+\cite{Blanton:2011aa} and uses single-Seric fit fluxes rather than the
+standard SDSS \texttt{cmodel} fluxes. Using the ratio of the
+luminosity derived from the improved photometry over the luminosity
+derived from the standard NYU-VAGC photometry, we apply a preliminary
+correction to the stellar mass values obtained from \texttt{iSEDfit}
+assuming a consistent mass-to-light ratio. This mass correction leads
+to a significant increase in the stellar mass function for
+$\mathcal{M} > 10^{11} \mathcal{M}_{\odot}$; however, the effect of
+the mass correction was negligible for the quiescent fraction
+evolution results. As a result, for the results presented here we use
+the standard SDSS fluxes and we do not discuss the issues with
+photometric measurements any further in this paper. We note that a
+thorough investigation of these issues to understand their effect on
+the stellar mass function requires a reanalysis of both the SDSS
+photometry and the deeper photometry used for PRIMUS targeting.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-From the low redshift SDSS-{\em GALEX} and intermediate redshift PRIMUS data, in this section, we define our mass complete galaxy sample.
-We begin by imposing the parent sample selection criteria from \cite{Moustakas:2013aa}.
-More specifically, we take the statistically complete {\em primary} sample from the PRIMUS data (\citealt{Coil:2011aa}) and impose magnitude limits on optical selection bands as specified in \cite{Moustakas:2013aa} Table 1.
-These limits are in different optical selection bands and have distinct values for the five PRIMUS target fields.
-We then exclude stars and broad-line AGN to only select objects spectroscopically classified as galaxies, with high-quality spectroscopic redshifts ($Q \geq 3$).
-Lastly, we impose a redshift range of $ 0.2 < z < 0.8$ for the PRIMUS galaxy sample, where $ z > 0.2$ is selected due to limitations from sample variance and $ z < 0.8$ is selected due to the lack of sufficient statistics in subsamples defined below.
+From the low redshift SDSS-{\em GALEX} and intermediate redshift
+PRIMUS data we define our mass complete galaxy
+sample. We begin by imposing the parent sample selection criteria from
+\cite{Moustakas:2013aa}. More specifically, we take the statistically
+complete {\em primary} sample from the PRIMUS data
+(\citealt{Coil:2011aa}) and impose magnitude limits on optical
+selection bands as specified in \cite{Moustakas:2013aa} Table 1. These
+limits are in different optical selection bands and have distinct
+values for the five PRIMUS target fields. We then exclude stars and
+broad-line AGN to only select objects spectroscopically classified as
+galaxies, with high-quality spectroscopic redshifts ($Q \geq
+3$). Lastly, we impose a redshift range of $ 0.2 < z < 0.8$ for the
+PRIMUS galaxy sample, where $ z > 0.2$ is selected due to limitations
+from sample variance and $ z < 0.8$ is selected due to the lack of
+sufficient statistics in subsamples defined below.
 
@@
 as in Equation (1) in \cite{Moustakas:2013aa}.
-Since we are ultimately interested in a mass complete galaxy sample to derive SMFs and QFs, next we impose stellar mass completeness limits to our galaxy sample.
 
+Since we are ultimately interested in a mass complete galaxy sample to
+derive SMFs and QFs, next we impose stellar mass completeness limits
+to our galaxy sample.
 Stellar mass completeness limits for a magnitude-limited survey such as PRIMUS are functions of redshift, the apparent magnitude limit of the survey, and the typical stellar mass-to-light ratio of galaxies near the flux limit.
 As in \cite{Moustakas:2013aa}, we follow \cite{Pozzetti:2010aa} to empirically determine the stellar mass completeness limits.
-For each of the target galaxies we compute $\mathcal{M}_{\rm{lim}}$ using $\rm{log} \; \mathcal{M}_{\mathrm{lim}} = \mathrm{log} \; \mathcal{M} + 0.4 (m - m_{\mathrm{lim}})$, where $\mathcal{M}$ is the stellar mass of the galaxy in $\mathcal{M_{\odot}}$, $\mathcal{M}_{\rm{lim}}$ is the stellar mass of each galaxy if its magnitude was equal to the survey magnitude limit, $m$ is the observed apparent magnitude in the selection band, and $m_{\rm{lim}}$ is the magnitude limit for our five fields.
+For each of the target galaxies we compute $\mathcal{M}_{\rm{lim}}$ using $\log \; \mathcal{M}_{\mathrm{lim}} = \log \; \mathcal{M} + 0.4 (m - m_{\mathrm{lim}})$, where $\mathcal{M}$ is the stellar mass of the galaxy in $\mathcal{M_{\odot}}$, $\mathcal{M}_{\rm{lim}}$ is the stellar mass of each galaxy if its magnitude was equal to the survey magnitude limit, $m$ is the observed apparent magnitude in the selection band, and $m_{\rm{lim}}$ is the magnitude limit for our five fields.
 We construct a cumulative distribution of $\mathcal{M}_{\rm{lim}}$ for the $15\%$ faintest galaxies in $\Delta z=0.04$ bins.
@@
 
-We now have a stellar mass complete sample derived from SDSS-{\em GALEX} and PRIMUS data.
-Since our sample is derived from two different surveys, we account for the disparity in the redshift uncertainty.
-While PRIMUS provides a large number of redshifts out to $z = 1$, due to using a prism instead of a grating, the uncertainties are significantly larger ($\sigma_{z}/(1+z) \approx 0.5 \%$) than that of the SDSS-{\em GALEX} redshifts.
-In order to have comparable environment measures throughout our redshift range, we apply PRIMUS redshift uncertainties to our galaxy sample selected from SDSS-{\em GALEX}.
-For each SDSS-{\em GALEX} galaxy, we adjust its redshift by randomly sampling a Gaussian distribution with standard deviation $\sigma = 0.005 (1+z_{\rm{SDSS}-GALEX})$, where $z_{\rm{SDSS}-GALEX}$ is the redshift of the galaxy.
+We now have a stellar mass complete sample derived from SDSS-{\em
+  GALEX} and PRIMUS data. Since our sample is derived from two
+different surveys, we account for the disparity in the redshift
+uncertainty. While PRIMUS provides a large number of redshifts out to
+$z = 1$, due to its use of a low dispersion prism, the redshift
+uncertainties are significantly larger ($\sigma_{z}/(1+z) \approx 0.5
+\%$) than that of the SDSS-{\em GALEX} redshifts. In order to have
+comparable environment measures throughout our redshift range, we
+apply PRIMUS redshift uncertainties to our galaxy sample selected from
+SDSS-{\em GALEX}. For each SDSS-{\em GALEX} galaxy, we adjust its
+redshift by randomly sampling a Gaussian distribution with standard
+deviation $\sigma = 0.005 (1+z_{\rm{SDSS}-GALEX})$, where
+$z_{\rm{SDSS}-GALEX}$ is the redshift of the galaxy.
 
@@
 The contribution from quiescent galaxies is colored in red.
-Each redshift panel is divided into three sections of by the environment classification cutoffs (vertical black lines): low density environment $n_{\rm{env}} < 0.5$ and high density environment $n_{\rm{env}} > 3.0$.
+Each redshift panel is divided into three sections by the environment classification cutoffs (vertical black lines): low density environment $n_{\rm{env}} < 0.5$ and high density environment $n_{\rm{env}} > 3.0$.
 The percentages of the redshift bin contained in the environment classifications are presented above the distribution.
@@
 
-For our aperture, we use a cylinder of dimensions: $R_{\rm{ap}} = 2 \; h^{-1} \rm{Mpc}$ and $H_{\rm{ap}} = 25 \; h^{-1}\rm{Mpc}$.
-Though spherical apertures are often used in literature (e.g.
-\citealt{Croton:2005aa}), we use a cylindrical aperture in order to account for the PRIMUS redshift errors and redshift space distortions (i.e.
-``Finger of God" effect).
-\cite{Cooper:2005aa} finds that $\pm 1000 \; \rm{km} \; \rm{s^{-1}}$ optimally reduces the effects of redshift space distortions.
-The PRIMUS redshift uncertainty at $z \sim 0.7$ corresponds to $\sigma_z < 0.01$, so our aperture height choice of $25 \; \rm{Mpc}/h$ accounts for both of these effects.
-Our choice of cylinder radius was motivated by scale dependence analyses in literature (\citealt{Blanton:2006aa, Wilman:2010aa, Muldrew:2012aa}), which suggest that galactic properties such as color and quenched fractions are dependent on halo-scale properties such as host dark matter halo mass.
-\cite{Wilman:2010aa}, which uses environment defined by annuli of different radii, find positive correlation for quenched fraction and color on scales $< 1 \; \rm{Mpc}$ and anti-correlation on scales $> 3 \; \rm{Mpc}$.
-Our choice of $2 \rm{Mpc}/h$ provides sufficient sample size of galaxies in dense environments, for robust statistics, while tracing galactic properties within the halo scale.
+For our aperture, we use a cylinder of dimensions: $R_{\rm{ap}} = 2 \;
+h^{-1} \rm{Mpc}$ and $H_{\rm{ap}} = 25 \; h^{-1}\rm{Mpc}$.  We use a
+cylindrical aperture in order to account for the PRIMUS redshift
+errors and redshift space distortions (i.e. ``Finger of God"
+effect). \cite{Cooper:2005aa} finds that $\pm 1000 \; \rm{km} \;
+\rm{s^{-1}}$ optimally reduces the effects of redshift space
+distortions. The PRIMUS redshift uncertainty at $z \sim 0.7$
+corresponds to $\sigma_z < 0.01$, so our aperture height choice of $25
+\; \rm{Mpc}/h$ accounts for both of these effects. Our choice of
+cylinder radius was motivated by scale dependence analyses in the
+literature (\citealt{Blanton:2006aa, Wilman:2010aa, Muldrew:2012aa}),
+which suggest that galactic properties such as color and quiescent
+fractions are most strongly dependent on scales $< 2$ Mpc, around the
+host dark matter halo sizes.
+
+% Not sure we need to note this detail; the anticorrelation is small.
+%\cite{Wilman:2010aa}, which uses environment defined by annuli of
+%different radii, find positive correlation for quiescent fraction and
+%color on scales $< 1 \; \rm{Mpc}$ and anti-correlation on scales $> 3
+%\; \rm{Mpc}$. Our choice of $2 \rm{Mpc}/h$ provides sufficient sample
+%size of galaxies in dense environments, for robust statistics, while
+%tracing galactic properties within the halo scale.
 
@@
 
-Before we measure the environment for our galaxy sample, we first construct a volume limited Environment Defining Population (EDP) with absolute magnitude cut-offs ($M_{r}$) at redshift bin of $\Delta z \sim 0.2$.
-The $M_{r}$ cut-offs for the EDP are selected such that the cumulative number density over $M_{r}$ for all redshift bins are equal.
-In addition to providing a reasonable comparison of environment measurements for wide redshift range, we make this choice in order to construct an EDP that contains similar galaxy populations through the redshift range (i.e.
-accounts for the progenitor bias).
-As \cite{Behroozi:2013aa} and \cite{Leja:2013aa} find in their analysis of the cumulative number density method, though it does not precisely account for the scatter in mass accretion or galaxy-galaxy mergers, it provides a reasonable means to compare galaxy populations over a wide range of cosmic time.
+Before we measure the environment for our galaxy sample, we first
+construct a volume limited Environment Defining Population (EDP) with
+absolute magnitude cut-offs ($M_{r}$) in redshift bins with $\Delta z
+\sim 0.2$. The $M_{r}$ cut-offs for the EDP are selected such that the
+cumulative number density over $M_{r}$ for all redshift bins are
+equal.  We make this choice in order to construct an EDP that contains
+similar galaxy populations through the redshift range (i.e. accounts
+for the progenitor bias). In their analysis of this method,
+\cite{Behroozi:2013aa} and \cite{Leja:2013aa} find that although it
+does not precisely account for the scatter in mass accretion or
+galaxy-galaxy mergers, it provides a reasonable means to compare
+galaxy populations over a wide range of cosmic time.
 
-In constructing the EDP for the PRIMUS (hereafter PRIMUS EDP) we use the same PRIMUS data used to select our galaxy sample (described in Section \ref{sec:target}).
+In constructing the PRIMUS EDP we use the same PRIMUS data used to select our galaxy sample (described in Section \ref{sec:target}).
 We again restrict the PRIMUS galaxies to $0.2 < z < 0.8$ and divide them into bins of $\Delta z = 0.2$.
@@
 
-For the EDP of the SDSS-{\em GALEX} galaxy sample (hereafter SDSS EDP), we do not use the SDSS-{\em GALEX} parent data, which uses the geometry of the combined angular selection function of the VAGC and {\em GALEX} (Section \ref{sec:sdss}).
-Instead, since FUV, NUV values are not necessary for the EDP, we extend the parent data of the SDSS EDP to the entire NYU VAGC, including galaxies outside of the {\em GALEX} window function.
-Furthermore, we impose a redshift range of $0.05-0.12$ on the SDSS EDP.
-This redshift range was determined to account for the lack of faint galaxies at $z \sim 0.2$ and the lack of bright galaxies at $z \sim 0.01$ in the VAGC.
-As with the PRIMUS redshift bins, we determine the SDSS EDP $M_{r, \rm{lim}}$ by matching the cumulative number density of the highest redshift bin.
-For redshift bins $0.05-0.12$, $0.2-0.4$, $0.4-0.6$, $0.6-0.8$ we get $M_{r,\rm{lim}} = -20.90$, $-21.06$, $-21.10$ and $-20.98$, respectively.
-These absolute magnitude limits are illustrated in Figure \ref{fig:targetEDP}, which show clear $M_r$ cutoffs in the $M_{r}$ distribution versus redshift for the EDP (red circles) on top of the target galaxy sample (black).
+For the SDSS EDP, we do not use the SDSS-{\em GALEX} parent data,
+which is limited to the combined angular selection window of the
+VAGC and {\em GALEX} (Section \ref{sec:sdss}). Instead, since FUV, NUV
+values are not necessary for the EDP, we extend the parent data of the
+SDSS EDP to the entire NYU VAGC, including galaxies outside of the
+{\em GALEX} window function. Furthermore, we impose a redshift range
+of $0.05-0.12$ on the SDSS EDP. This redshift range was determined to
+account for the lack of faint galaxies at $z \sim 0.2$ and the lack of
+bright galaxies at $z \sim 0.01$ in the VAGC. As with the PRIMUS
+redshift bins, we determine the SDSS EDP $M_{r, \rm{lim}}$ by matching
+the cumulative number density of the highest redshift bin. For
+redshift bins $0.05-0.12$, $0.2-0.4$, $0.4-0.6$, $0.6-0.8$ we get
+$M_{r,\rm{lim}} = -20.90$, $-21.06$, $-21.10$ and $-20.98$,
+respectively. These absolute magnitude limits are illustrated in
+Figure \ref{fig:targetEDP}, which show clear $M_r$ cutoffs in the
+$M_{r}$ distribution versus redshift for the EDP (red circles) on top
+of the target galaxy sample (black).
 
@@
 
-Finally we measure the environment for each galaxy in our galaxy sample by counting the number of EDP galaxies, $n_{\rm{env}}$ with $RA$, $Dec$, and $z$ within our cylindrical aperture centered around it.
-$n_{\rm{env}}$ accounts for the statistical weights of the EDP galaxies.
-Once we obtain environment measurements for all the galaxies in our galaxy sample, we classify galaxies with $n_{\rm{env}} < 0.5$ to be ``low" environment density and galaxies with $n_{\rm{env}} > 3$ to be ``high" environment densities.
-The high environment cutoff was selected in order to reduce contamination from galaxies in low environment densities while maintaining sufficient statistics.
+Finally we measure the environment for each galaxy in our galaxy
+sample by counting the number of EDP galaxies, $n_{\rm{env}}$ with RA,
+Dec, and $z$ within our cylindrical aperture centered around
+it. $n_{\rm{env}}$ accounts for the statistical weights of the EDP
+galaxies. Once we obtain environment measurements for all the galaxies
+in our galaxy sample, we classify galaxies with $n_{\rm{env}} < 0.5$
+to be ``low" environment density and galaxies with $n_{\rm{env}} > 3$
+to be ``high" environment densities. The high environment cutoff was
+selected in order to reduce contamination from galaxies in low
+environment densities while maintaining sufficient statistics. In
+Section \ref{sec:env_qf_evol} we will also explore higher density
+cutoffs for $n_{\rm{env}}$.
 
-The analysis we describe below uses a fixed cylindrical aperture with dimensions $R_{\rm{ap}} = 2 \:h^{-1}\rm{Mpc}$ and $H_{\rm{ap}} = 25 \:h^{-1}\rm{Mpc}$ to measure environment.
-The same analysis was extended for varying aperture dimensions $R_{\rm{ap}} = 1, 2, 3 \: h^{-1}\rm{Mpc}$ and $H_{\rm{ap}} = 25, 50 \:h^{-1}\rm{Mpc}$.
-We also adjusted the environment classification thresholds for these analyses.
-The results obtained from using different apertures and environment classification thresholds are qualitatively consistent with the results presented below.
+The analysis we describe below uses a fixed cylindrical aperture with
+dimensions $R_{\rm{ap}} = 2 \:h^{-1}\rm{Mpc}$ and $H_{\rm{ap}} = 25
+\:h^{-1}\rm{Mpc}$ to measure environment. The same analysis was
+extended for varying aperture dimensions $R_{\rm{ap}} = 1, 2, 3 \:
+h^{-1}\rm{Mpc}$ and $H_{\rm{ap}} = 25, 50 \:h^{-1}\rm{Mpc}$. We also
+adjusted the environment classification thresholds for these
+analyses. The results obtained from using different apertures and
+environment classification thresholds are qualitatively consistent with the results presented below.
 
@@
 To account for these edge effects, we use a Monte Carlo method to impose edge cutoffs on our galaxy sample.
-First, using \texttt{ransack} from \cite{Swanson:2008aa}, we construct a random sample of  $N_{\rm{ransack}} = 1,000,000$ points with $RA$ and $Dec$ randomly selected within the window function of the EDP (SDSS EDP and PRIMUS EDP separately).
+First, using \texttt{ransack} from \cite{Swanson:2008aa}, we construct a random sample of  $N_{\rm{ransack}} = 1,000,000$ points with RA and Dec randomly selected within the window function of the EDP (SDSS EDP and PRIMUS EDP separately).
 We then compute the angular separation, $\theta_{i, \rm{ap}}$ that corresponds to $R_{\rm{ap}}$ (Section \ref{sec:environment}) at the redshift of each sample galaxy $i$.
@@
 \begin{equation} \label{eq:ransack}
-<n_{\rm{ransack}}>_{i} = \frac{N_{\rm{ransack}}}{A_{\rm{EDP}}}\times {\pi \theta_{i, \rm{ap}}^2} \times f_{\rm{thresh}}. 
+\langle n_{\rm{ransack}}\rangle_{i} = \frac{N_{\rm{ransack}}}{A_{\rm{EDP}}}\times {\pi \theta_{i, \rm{ap}}^2} \times f_{\rm{thresh}}. 
 \end{equation} 
@@
 The quiescent galaxy contributions are colored in red while the star-forming galaxy contributions are colored in blue and patterned.
-The low and high density environment classifications are represented by black vertical lines that divide the distribution at $n_{\rm{env}} = 1.5$ and $n_{\rm{env}} = 3.5$.
+The low and high density environment classifications are represented by black vertical lines that divide the distribution at $n_{\rm{env}} = 0.5$ and $n_{\rm{env}} = 3.5$.
 The percentage of the total galaxies in the redshift bin that are in these environment densities are labeled on the figure.
@@
      \caption{Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) target galaxies in 
-low (left) and high (right) environments from redshift range $z=0-0.8$. The environment of each galaxy  
+low (left) and high (right) environments in the redshift range
+$z=0$--$0.8$. The environment of each galaxy  
 was calculated using a cylindrical aperture size of $R=2 \: \rm{Mpc}$ and $H=25 \: \rm{Mpc}$ and  
@@
 \section{Stellar Mass Function} \label{sec:smf}
-Our galaxy sample has so far been classified into quiescent or star-forming and low or high density environments.
-We further divide these subsamples into redshift bins: $0.05-0.12$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ for a total 16 subsamples.
+Our galaxy sample has so far been classified into quiescent or
+star-forming and low or high density environments. We further divide
+these subsamples into redshift bins: $0.05-0.12$, $0.2-0.4$,
+$0.4-0.6$, and $0.6-0.8$ for a total of 16 subsamples.
 In Section \ref{sec:smfcalc}, we calculate the SMF for each of these subsamples.
@@
 \end{equation}
-$w_i$ is the statistical weight of galaxy $i$ and $\Phi(\rm{log}\: \mathcal{M}) \Delta(\rm{log}\: \mathcal{M})$ is the number of galaxies ($N$) per unit volume within the stellar mass range $[\rm{log} \:\mathcal{M}, \rm{log} \:\mathcal{M}+\Delta(\rm{log} \:\mathcal{M})]$.
-The equation above is same as Equation 3.
-in \cite{Moustakas:2013aa} except that we use $V_{\rm{max,avail}}$ instead than $V_{\rm{max}}$, to account for the edge effects of the survey discussed in Section \ref{sec:edgeeffect}.
+$w_i$ is the statistical weight of galaxy $i$ and $\Phi(\rm{log}\:
+\mathcal{M}) \Delta(\rm{log}\: \mathcal{M})$ is the number of galaxies
+($N$) per unit volume within the stellar mass range $[\rm{log}
+  \:\mathcal{M}, \rm{log} \:\mathcal{M}+\Delta(\rm{log}
+  \:\mathcal{M})]$.
+The equation above is the same as Equation 3 in \cite{Moustakas:2013aa} except that we use $V_{\rm{max,avail}}$ instead than $V_{\rm{max}}$, to account for the edge effects of the survey discussed in Section \ref{sec:edgeeffect}.
 
-$V_{\rm{max},i}$ is the maximum cosmological volume where it is possible to observe galaxy $i$ given the apparent magnitude limits of the survey.
-However in Section \ref{sec:edgeeffect} we remove galaxies that lie on the edge from our sample.
-In doing so we reduce the maximum cosmological volume where a galaxy can be observed, thereby reducing $V_{\rm{max},i}$.
-We introduce the term $V_{\rm{max,avail},i}$ for the $V_{\rm{max},i}$ value that accounts for the survey edge effects.
+$V_{\rm{max},i}$ is the maximum cosmological volume where it is
+possible to observe galaxy $i$ given the apparent magnitude limits of
+the survey. However in Section \ref{sec:edgeeffect} we remove galaxies
+that lie on the edge from our sample. In doing so we reduce the
+maximum cosmological volume where a galaxy can be observed, thereby
+reducing the fraction of $V_{\rm{max},i}$ that is actually available
+in the sample. We introduce the term $V_{\rm{max,avail},i}$ to express
+the maximum volume accounting for these survey edge effects.
 
-To calculate $V_{\rm{max,avail},i}$, we use a similar Monte Carlo method as the edge effect cutoffs in Section \ref{sec:edgeeffect}.
-First, we generate a sample of points with random $RA$, $Dec$ within the window function of our galaxy sample (SDSS-{\em GALEX} window function and the five PRIMUS fields) and random $z$ within the redshift range.
-These points are not to be confused with the \texttt{ransack} sample in Section \ref{sec:edgeeffect}.
-We apply the edge effect cutoffs on these random points as we did for our galaxy sample using the same \texttt{ransack} method in Section \ref{sec:edgeeffect}.
-At redshift bins of $\Delta z \sim 0.01$, we calculate the fraction of the random points that remain in the bin after the edge effect cutoffs over the total number of random points in the bin: $f_{\rm{edge}}$.
-We then apply this factor to compute $V_{\rm{max,avail}} = V_{\rm{max}} \times f_{\rm{edge}}$.
-The $V_{\rm{max}}$ in the equation above are computed following the method described in \cite{Moustakas:2013aa} Section 4.2 with the same redshift-dependent $K$-correction from observed SED and luminosity evolution model.
+To calculate $V_{\rm{max,avail},i}$, we use a similar Monte Carlo
+method as the edge effect cutoffs in Section
+\ref{sec:edgeeffect}. First, we generate a sample of points with
+random RA, Dec within the window function of our galaxy sample
+(SDSS-{\em GALEX} window function and the five PRIMUS fields) and
+random $z$ within the redshift range. These points are not to be
+confused with the \texttt{ransack} sample in Section
+\ref{sec:edgeeffect}. We apply the edge effect cutoffs on these random
+points as we did for our galaxy sample using the same method as in
+Section \ref{sec:edgeeffect}. Within redshift bins of $\Delta z \sim
+0.01$, we calculate the fraction of the random points that remain in
+the bin after the edge effect cutoffs over the total number of random
+points in the bin: $f_{\rm{edge}}$. We then apply this factor to
+compute $V_{\rm{max,avail}} = V_{\rm{max}} \times f_{\rm{edge}}$. The
+$V_{\rm{max}}$ values in the equation above are computed following the
+method described in \cite{Moustakas:2013aa} Section 4.2 with the same
+redshift-dependent $K$-correction from observed SED and luminosity
+evolution model.
 
@@
 For the PRIMUS galaxies, we calculate SMFs after excluding one of the five target fields at a time.
-For the SDSS target galaxies we divide the field into a 12 $\times$ 9 rectangular $RA$ and $Dec$ grid and calculate the SMFs after excluding one grid at a time.
+For the SDSS target galaxies we divide the field into a 12 $\times$ 9 rectangular RA and Dec grid and calculate the SMFs after excluding one grid at a time.
 From the calculated SMFs we calculate the uncertainty:
@@
 
-While a detailed comparison of the SMFs in each panel for different epochs are complicated due to the different stellar mass completeness limits, we present some notable trends in each panel.
+While a detailed comparison of the SMFs in each panel for different
+epochs is complicated due to the different stellar mass completeness limits, we present some notable trends in each panel.
 In panel (a), star-forming galaxies in low density environments, we find a significant decrease in the high mass end of the SMF ($\mathcal{M} > 10^{10.75} \mathcal{M}_{\odot}$).
@@
 
-Observing the evolutionary trends in SMF for each of these sub-populations provides a narrative of the different galaxy evolutionary tracks involving environment and quenching.
-For example, the decrease in the massive star-forming galaxies in low density environments over cosmic time can be attributed to the transition of those galaxies to any of the other panels.
-The star-forming galaxies in low density environments that have quenched their star formation over time are possibly responsible for the increase of the quiescent, low density environment SMF over time.
-The star-forming galaxies that fall into higher density environments explain the increase in the star-forming high density environment SMF below the knee.
-Finally, star-forming galaxies in high density environments that have quenched their star-formation, quiescent galaxies that have transitioned from low to high density environments, and star-forming galaxies in low density environments that quench their star-formation while infalling to high density environments all contribute to the overall increase of the high environment quiescent SMF.
+Observing the evolutionary trends in SMF for each of these
+sub-populations provides a narrative of the different galaxy
+evolutionary tracks involving environment and the end of star
+formation. For example, the decrease in the massive star-forming
+galaxies in low density environments over cosmic time can be
+attributed to the transition of those galaxies to any of the other
+panels. The star-forming galaxies in low density environments that
+have ended star formation over time are possibly responsible
+for the increase of the quiescent, low density environment SMF over
+time. The star-forming galaxies that fall into higher density
+environments explain the increase in the star-forming high density
+environment SMF below the knee. Finally, star-forming galaxies in high
+density environments that have ended their star-formation,
+quiescent galaxies that have transitioned from low to high density
+environments, and star-forming galaxies in low density environments
+that end their star-formation while infalling to high density
+environments all contribute to the overall increase of the high
+environment quiescent SMF.
 
-In addition to the evolution over cosmic time, we observe noticeable trends when we compare the SMFs for star-forming and quiescent galaxies between the two environments.
-Comparison of the SMFs in low versus high density environments reveal a noticeable relation between mass and density, with SMFs in high density environments having more massive galaxies.
-We further confirm this trend when we compare the median mass between the two environments to find that the median mass for galaxies in high density environments is significantly greater than in low density environments.
-The relationship between mass and environment observed in our SMFs mirror the well-established mass-density relation and observed mass segregation with environment in the literature (\citealt{bundy06a, Scodeggio:2009aa, Bolzonella:2010aa}).
+In addition to the evolution over cosmic time, we observe noticeable
+trends when we compare the SMFs for star-forming and quiescent
+galaxies between the two environments. Comparison of the SMFs in low
+versus high density environments reveal a noticeable relation between
+mass and density, with SMFs in high density environments having more
+massive galaxies. We further confirm this trend when we compare the
+median mass between the two environments to find that the median mass
+for galaxies in high density environments is significantly greater
+than in low density environments. The relationship between mass and
+environment observed in our SMFs reflect the well-established
+mass-density relation and observed mass segregation with environment
+in the literature (\citealt{norberg02a, zehavi02a, blanton05b,
+  bundy06a, Scodeggio:2009aa, Bolzonella:2010aa}).
 
-While our mass complete subsample coupled with robust environment measurement allows us to compare SMF evolution for each of our subsamples out to $z=0.8$, we caution readers and reserve detailed analysis of the SMFs to future work due to the improvements in photometry that significantly alter the SDSS SMFs mentioned in Section \ref{sec:sdss}.
+While our mass complete subsample coupled with robust environment
+measurement allows us to compare SMF evolution for each of our
+subsamples out to $z=0.8$, we caution readers regarding the
+photometric biases affecting the SDSS imaging (and perhaps the other
+imaging sources) and reserve detailed analysis of the SMFs for 
+future investigation.
 
@@
         \epsfig{file=fig_qf_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_lit_primuszerr.eps, height=0.75\textwidth,angle=90}
-        \caption{Evolution of the quiescent fraction $f_{\rm{Q}}$ for galaxies in low (left) and high (rights) density environments for $z < 0.8$.
-$f_{\rm{Q}}$s were calculated using the SMFs in Figure\ref{fig:smf}, as described in text.
-Darker shading indicates lower redshift and the width represents the standard jackknife uncertainty.}         \label{fig:qf}
+        \caption{Evolution of the quiescent fraction $f_{\rm{Q}}$ for
+          galaxies in low (left) and high (right) density
+          environments for $z < 0.8$. $f_{\rm{Q}}$s were calculated
+          using the SMFs in Figure \ref{fig:smf}, as described in text. Darker shading indicates lower redshift and the width represents the standard jackknife uncertainty.}         \label{fig:qf}
     \end{center}
@@
 \section{Quiescent Fraction} \label{sec:qf_const}
-The SMFs calculated in the previous section illustrate the stellar mass distribution of our galaxy population and its evolution over cosmic time.
-In this section, using the SMFs of our subsamples, we compare the quiescent and the star-forming populations by calculating the fraction of galaxies that have quenched their star-formation, the quiescent fraction.
+The SMFs calculated in the previous section illustrate the stellar
+mass distribution of our galaxy population and its evolution over
+cosmic time. In this section, using the SMFs of our subsamples, we
+compare the quiescent and the star-forming populations by calculating
+the fraction of galaxies that have ended their star-formation, the quiescent fraction.
 
-While the fractional relation of the star-forming and quiescent populations has been investigated in the past, with limited statistics, disentangling the environmental effects f rom underlying correlations among observable galaxy properties such as the color-mass or mass-density relations (\citealt{Cooper:2010aa}) remains a challenge.
-With the sufficient statistics available from SDSS and PRIMUS, we evaluate the quiescent fraction in bins of stellar mass, redshift, and environment in Section \ref{sec:qfevol}.
-By analyzing the quiescent fraction with respect to these properties, in Section \ref{sec:env_qf_evol} we explicitly compare the quiescent fraction evolution in low and high density environments.
-Our comparison reveal the subtle environmental effects on the quiescent fraction evolution.
-Furthermore, by quantifying this environmental effect, we are able constrain the role of environmental quenching in galaxy evolution.
+While the fractional relation of the star-forming and quiescent
+populations has been investigated in the past, with limited
+statistics, disentangling the environmental effects from underlying
+correlations among observable galaxy properties such as the color-mass
+or mass-density relations (\citealt{Cooper:2010aa}) remains a
+challenge. With the better statistics available from SDSS and
+PRIMUS, we evaluate the quiescent fraction in bins of stellar mass,
+redshift, and environment in Section \ref{sec:qfevol}. By analyzing
+the quiescent fraction with respect to these properties, in Section
+\ref{sec:env_qf_evol} we explicitly compare the quiescent fraction
+evolution in low and high density environments. Our comparison reveal
+the subtle environmental effects on the quiescent fraction
+evolution. Furthermore, by quantifying this environmental effect, we
+are able constrain the role of environmental effects on how galaxies
+end their star formation.
 %With the sufficient statistics available from SDSS and PRIMUS, we evaluate the quiescent fraction in bins of stellar mass and redshift for low and high density environments (Section \ref{sec:qfevol}).
@@
 \end{equation}
-$\Phi_{Q}$ and $\Phi_{SF}$ are the total number of galaxies per unit volume in stellar mass bin of $\Delta(\rm{log} \: \mathcal{M}) = 0.20 \: \mathrm{dex}$ for the quiescent and star-forming subsamples, respectively (Equation \ref{eq:phi}).
-We compute $f_{\rm{Q}}$ for high and low density environments for all redshift bins as plotted in Figure \ref{fig:qf}, which shows the evolution of $f_{\rm{Q}}$ for high (right panel) and low (left panel) density environments.
-As in Figure \ref{fig:smf}, the evolution of the quiescent fraction over cosmic time is represented in the shading (darker with lower redshift) and the uncertainty is represented by the width.
-For the uncertainty in the quiescent fraction, we use the standard jackknife technique, following the same steps as the SMF uncertainty in Section \ref{sec:smfcalc}.
+$\Phi_{Q}$ and $\Phi_{SF}$ are the total number of galaxies per unit
+volume in stellar mass bin of $\Delta(\rm{log} \: \mathcal{M}) = 0.20
+\: \mathrm{dex}$ for the quiescent and star-forming subsamples,
+respectively (Equation \ref{eq:phi}). We compute $f_{\rm{Q}}$ for high
+and low density environments for all redshift bins as plotted in
+Figure \ref{fig:qf}, which shows the evolution of $f_{\rm{Q}}$ for
+high (right panel) and low (left panel) density environments. As in
+Figure \ref{fig:smf}, the evolution of the quiescent fraction over
+cosmic time is represented in the shading (darker with lower redshift)
+and the uncertainty is represented by the width. For the uncertainty
+in the quiescent fraction, we use the standard jackknife technique,
+following the same steps as for the SMF uncertainty in Section \ref{sec:smfcalc}.
 
-Most noticeably in Figure \ref{fig:qf}, we find $f_{\rm{Q}}$ increases monotonically as a function of mass at all redshift bin and environment.
-In other words, for all subsamples, galaxies in higher mass bins are more likely to have quenched its star-formation.
+Most noticeably in Figure \ref{fig:qf}, we find $f_{\rm{Q}}$ increases
+monotonically as a function of mass at all redshifts and
+environments. In other words, for all subsamples, galaxies in higher
+mass bins are more likely to have ended its star-formation.
 With the roughly linear correlation between galaxy SFR to galaxy color and morphology, we find that this trend reflects the well established color-mass and morphology-mass relations: more massive galaxies are more likely to be red or early-type (\citealt{blanton09a}).
 
-Focusing on the redshift evolution of $f_{\rm{Q}}$, we find that for both environments $f_{\rm{Q}}$ increases as redshift decreases.
-For high density environments, this is analogous to the Butcher-Oemler Effect (\citealt{Butcher:1984aa}), which states that galaxy populations in groups or clusters have higher $f_{\rm{blue}}$, or lower $f_{\rm{Q}}$, at higher redshift.
-For all environments, a larger portion of our galaxy population has quenched its star-formation over time.
-Coupled with the decline of SFR in the star-forming population (\citealt{Noeske:2007aa, cooper08a}), our results are in agreement with the observed decline of global star-formation in the universe (\citealt{hopkins06a}).
-%Maybe Stacey et al.
-2014 is relevant here?
+Focusing on the redshift evolution of $f_{\rm{Q}}$, we find that for
+both environments $f_{\rm{Q}}$ increases as redshift decreases. For
+high density environments, this is analogous to the Butcher-Oemler
+Effect (\citealt{Butcher:1984aa}), which states that galaxy
+populations in groups or clusters have higher $f_{\rm{blue}}$, or
+lower $f_{\rm{Q}}$, at higher redshift. This evolution occurs with
+roughly the same amplitude in low environments as well.
 
-In addition, when we compare the stellar masses at which $f_{\rm{Q}} = 0.5$ for each subsample, the so-called $\mathcal{M}_{50-50}$, we find that this quantity decreases over cosmic time.
-This corresponds to the well-known mass-downsizing pattern in the literature (e.g.
-\citealt{bundy06a}).
-Furthermore, the mass-downsizing trend observed in each of our environment subsample is consistent with the trend observed in zCOSMOS Redshift Survey for isolated and group galaxies (\citealt{Iovino:2010aa}).
-%Remark on how the M_{50-50}?
-is lower for high environment f_{Q}, and that it generally increases with redshift.
-A trend also observed in the t_{5050} considerations.
+In addition, when we compare the stellar masses at which $f_{\rm{Q}} =
+0.5$ for each subsample, the so-called $\mathcal{M}_{50-50}$, we find
+that this quantity decreases over cosmic time. This corresponds to the
+well-known mass-downsizing pattern found by previous investigators
+(e.g. \citealt{bundy06a}). Furthermore, the mass-downsizing trend
+observed in each of our environment subsample is qualitatively
+consistent with the trend observed in zCOSMOS Redshift Survey for
+isolated and group galaxies (\citealt{Iovino:2010aa}).
 
-Finally, we compare between our low and high density environment $f_{\rm{Q}}$s at each redshift bin interval.
-For our lowest redshift bin, we find that $f_{\rm{Q}}$ at low density environments ranges from $\sim 0.4$ to $\sim 0.8$ for $10^{10.2} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11.5} \mathcal{M}_{\odot}$.
-Over the same mass range, $f_{\rm{Q}}$ at high density environment ranges from $\sim 0.55$ to $\sim 0.9$.
-Evidently for our SDSS sample, $f_{\rm{Q}}$ in high density environment is notably higher.
+%Remark on how the M_{50-50}? is lower for high environment f_{Q}, and that it generally increases with redshift. A trend also observed in the t_{5050} considerations.
+
+Finally, we compare between our low and high density environment
+$f_{\rm{Q}}$s at each redshift bin interval. For our lowest redshift
+bin, we find that $f_{\rm{Q}}$ at low density environments ranges from
+$\sim 0.4$ to $\sim 0.8$ for $10^{10.2} \mathcal{M}_{\odot} <
+\mathcal{M}_{*} < 10^{11.5} \mathcal{M}_{\odot}$. Over the same mass
+range, $f_{\rm{Q}}$ at high density environment ranges from $\sim
+0.55$ to $\sim 0.9$. Evidently for our SDSS sample, $f_{\rm{Q}}$ in
+high density environments is notably higher.
 
@@
 
-While there is a significant difference in $f_{\rm{Q}}$ between the environments, since the difference is observed from our highest redshift bin it is not necessarily a result of environment dependent quenching mechanisms.
-In order to isolate the environmental dependence on star-formation quenching, in the following section we quantitatively compare the evolution of the quiescent fraction between the different environments.
+While there is a significant difference in $f_{\rm{Q}}$ between the
+environments, since the difference is observed from our highest
+redshift bin it is not necessarily a result of environment dependent
+mechanisms for ending star formation. In order to isolate any
+environmental dependence, in the following section we quantitatively
+compare the evolution of the quiescent fraction between the different
+environments.
 
@@
         \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmasscomp11_0_10_5_lit_primuszerr.eps, height=0.45\textwidth}
-        \caption{The evolution of the quiescent fraction at fiducial mass, $f_{Q}(\mathcal{M}_{\rm{fid}})$, for low (blue) and high (red) density environments within the redshift range $z = 0.0 - 0.8$.
-We present the $f_{Q}(\mathcal{M}_{\rm{fid}})$ evolution for $\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot$ (solid fill) and $10^{11} \mathcal{M}_\odot$ (patterned fill) with the uncertainty of the best-fit parameter $b$ in Equation \ref{eq:qffit} represented by the width of the evolution.
+        \caption{The evolution of the quiescent fraction at fiducial
+          mass, $f_{Q}(\mathcal{M}_{\rm{fid}})$, for low (blue) and
+          high (red) density environments within the redshift range $z
+          = 0.0 - 0.8$. We present the $f_{Q}(\mathcal{M}_{\rm{fid}})$
+          evolution for $\mathcal{M}_{\rm{fid}} = 10^{10.5}
+          \mathcal{M}_\odot$ (solid fill) and $10^{11}
+          \mathcal{M}_\odot$ (patterned fill) with the uncertainty of
+          the best-fit parameter $b$ in Equation \ref{eq:qffit}
+          represented by the width of the line.
 While the high density $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ is greater than low density environment $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ over the entire redshift range of our sample, there is a significant increase in $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ over cosmic time for both environments.
@@
 
-In Figure \ref{fig:qffit} we present the evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ at low (blue) and high (red) density environments for $\mathcal{M}_{\rm{fid}} = 10^{10.5} \: \mathcal{M}_{\odot}$ (solid fill) and $10^{11} \: \mathcal{M}_{\odot}$ (pattern fill).
-The width of the evolution represents the uncertainty derived from {\em MPFIT}.
-As noted earlier in Section \ref{sec:qfevol}, $f_{\rm{Q}}$ in high density environment is significantly greater than $f_{\rm{Q}}$ in low density environment for both fiducial mass choices.
-Throughout our sample's redshift range $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})_{\mathrm{high}} - f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})_{\mathrm{low}} \sim 0.1$
+In Figure \ref{fig:qffit} we present the evolution of
+$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$
+at low (blue) and high (red) density environments for
+$\mathcal{M}_{\rm{fid}} = 10^{10.5} \: \mathcal{M}_{\odot}$ (solid
+fill) and $10^{11} \: \mathcal{M}_{\odot}$ (pattern fill). The width
+of the evolution represents the uncertainty derived from {\em
+  MPFIT}. As noted earlier in Section \ref{sec:qfevol}, $f_{\rm{Q}}$
+in high density environments is significantly greater than
+$f_{\rm{Q}}$ in low density environments for both fiducial mass
+choices. Throughout our sample's redshift range
+$f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})_{\mathrm{high}} -
+f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})_{\mathrm{low}} \sim 0.1$.
 
-In addition, the $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ evolution illustrates that the quiescent fraction in low density environment increases over cosmic time: $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.1) - f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.7) \sim 0.1$.
-This significant quiescent fraction evolution for low density environment suggests that internal mechanisms, independent of environment, are responsible for a significant amount of star-formation quenching.
+In addition, the $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$
+evolution illustrates that the quiescent fraction in low density
+environment increases over cosmic time:
+$f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.1) -
+f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.7) \sim 0.1$. This
+significant quiescent fraction evolution for low density environment
+suggests that internal mechanisms, independent of environment, are
+responsible for a significant amount of star-formation cessation.
 Meanwhile, the $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ evolution in high density environment ($f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.1) - f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.7) \sim 0.12$) shows little additional evolution.
 
-When we increase our choice of $\mathcal{M}_{\rm{fid}}$ to $10^{11} \mathcal{M}_\odot$, aside from an overall shift in $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ by $\sim 0.2$, we observe the same evolutionary trends.
-$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{11}\mathcal{M}_{\odot})$ for both low and high density environments each increase by $\sim 0.1$ from $z \sim 0.7$ to $\sim 0.1$.
-Evidently, increasing the fiducial mass to $10^{11} \mathcal{M}_{\odot}$ does not significantly alter the evolutionary trends in either environments.
-Although the varying stellar mass completeness at each redshift bin limits the masses we probe for the $f_{\rm{Q}}$ evolution, our $f_{\rm{Q}}$ evolution exhibits little mass dependence.
+When we increase our choice of $\mathcal{M}_{\rm{fid}}$ to $10^{11}
+\mathcal{M}_\odot$, aside from an overall shift in
+$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ by $\sim 0.2$, we observe the
+same evolutionary trends. $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} =
+10^{11}\mathcal{M}_{\odot})$ for both low and high density
+environments each increase by $\sim 0.1$ from at all redshifts we
+study. Evidently, increasing the fiducial mass to $10^{11}
+\mathcal{M}_{\odot}$ does not significantly alter the evolutionary
+trends in either environment. Although the varying stellar mass
+completeness at each redshift bin limits the masses we probe for the
+$f_{\rm{Q}}$ evolution, our $f_{\rm{Q}}$ evolution exhibits little
+mass dependence.
 
-Considering that our fixed aperture definition of environment is susceptible to contamination due to PRIMUS redshift errors, in Figure \ref{fig:qffit_comp}, we impose more stringent high density environment classifications, extending the cut off to $n_{\mathrm{env}} > 6$ and $9$ (specified in the top right legend and represented by the color of the shading).
-Aside from the increase in uncertainties that accompany a decrease in sample size from a purer high environment sample, we find an extension of the $f_{\rm{Q}}$ difference between the environments we stated earlier.
-A more stringent high environment classification significantly increases the overall $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$: $f_{\mathrm{Q}, n_{\mathrm{env}}>9} > f_{\mathrm{Q}, n_{\mathrm{env}}>6} > f_{\mathrm{Q}, n_{\mathrm{env}}>3} > f_{\mathrm{Q}, n_{\mathrm{env}}<0.5} $.
+Because our fixed aperture definition of environment is susceptible to
+contamination due to PRIMUS redshift errors, we consider in Figure
+\ref{fig:qffit_comp} more stringent high density environment
+classifications, extending the cut off to $n_{\mathrm{env}} > 6$ and
+$9$ (specified in the top right legend and represented by the color of
+the shading). Aside from the increase in uncertainties that accompany
+the decrease in sample size of the purer high environment sample, we
+find an extension of the $f_{\rm{Q}}$ difference between the
+environments we stated earlier. A more stringent high environment
+classification significantly increases the overall
+$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$, which rises monotonically with
+the $n_{\mathrm{env}}$ limit.
 
-More importantly, a purer high environment classification reveals a more significant environment dependence on the $f_{\rm{Q}}$ evolution.
-While the difference between the $f_{\rm{Q}}$ evolution in low and high density environment is negligible for the $n_{\rm{env}} > 3$ cut-off, there is a notable difference in $f_{\mathrm{Q}}$ evolution between our highest cut-off $n_{\rm{env}} > 9$ and our low density environment.
-$f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.1) - f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.7) \sim 0.2$ for $n_{\rm{env}} > 9$ versus $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.1) - f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.7) \sim 0.1$ for low density environment as we listed earlier.
-In addition to the environment independent internal quenching mechanisms that can explain the $f_{\rm{Q}}$ evolution at low density environments, there may be other environment dependent mechanisms that can account for the moderate environment dependence of the $f_{\rm{Q}}$ evolution.
-Our measured difference in the $f_{\rm{Q}}$ evolution between environments provides a strict constraint for any environmental quenching models.
+More importantly, a purer high environment classification reveals a
+more significant environment dependence on the $f_{\rm{Q}}$
+evolution. While the difference between the $f_{\rm{Q}}$ evolution in
+low and high density environment is negligible for the $n_{\rm{env}} >
+3$ cut-off, there is a notable difference in $f_{\mathrm{Q}}$
+evolution between our highest cut-off $n_{\rm{env}} > 9$ and our low
+density environment. $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z
+\sim 0.1) - f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.7)
+\sim 0.2$ for $n_{\rm{env}} > 9$ versus
+$f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.1) -
+f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.7) \sim 0.1$ for
+low density environment as we listed earlier. In addition to the
+environment independent internal mechanisms that can explain the
+$f_{\rm{Q}}$ evolution at low density environments, there may be other
+environment dependent mechanisms that can account for the moderate
+environment dependence of the $f_{\rm{Q}}$ evolution. Our measured
+difference in the $f_{\rm{Q}}$ evolution between environments provides
+an important constraint for any environmental models for ending star
+formation.
 
@@
 \subsection{Comparison to Literature}
-Although a direct comparison with other results is difficult due to our sample specific methodology, a number of results from literature have investigated the quiescent fraction in comparable fashions.
+Although a direct comparison with other results is difficult due to
+our sample specific methodology, a number of results from the literature have investigated the quiescent fraction in comparable fashions.
 In this section we compare our $f_{\rm{Q}}$ results from above to a number of these results, specifically from SDSS and zCOSMOS, with similarly defined samples and analogous environment classifications.
 
-In Figure \ref{fig:qffit_comp}, we plot  best-fit parameterization of $f_{\rm{red}}$ for high and low density environment from zCOSMOS, \cite{Iovino:2010aa} (square) and \cite{Kovac:2014aa} (triangle), and SDSS, \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross).
-From \cite{Iovino:2010aa} we calculate $f_{\rm{red}} = 1-f_{\rm{blue}}$ using the best-fit $f_{\rm{blue}}$ from the mass bin $\mathcal{M} = 10^{10.3} - 10^{10.8} \mathcal{M}_{\odot}$.
-From \cite{Kovac:2014aa} we plot an estimated $f_{\rm{Q}}$ by applying the residual between SFR based and color based galaxy classifications to the best-fit $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ for low ($\delta = 0.0$) and high density environment ($\delta = 1.5$).
-Similarly, from \cite{Baldry:2006aa} we plot $f_{\rm{Q}}$ derived from the best-fit $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ for low ($\delta = 0.0$) and high density environment ($\delta = 1.0$).
-For \cite{geha12a}, we plot $f_{\rm{Q}}$ in their mass bin closest to $10^{10.5} \mathcal{M}_{\odot}$, $\mathcal{M} = 10^{10.55} \mathcal{M}_{\odot}$.
+In Figure \ref{fig:qffit_comp}, we plot  best-fit parameterization of
+$f_{\rm{red}}$ for high and low density environment from zCOSMOS,
+\cite{Iovino:2010aa} (square) and \cite{Kovac:2014aa} (triangle), and
+SDSS, \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross). From
+\cite{Iovino:2010aa} we calculate $f_{\rm{red}} = 1-f_{\rm{blue}}$
+using the best-fit $f_{\rm{blue}}$ from the mass bin $\mathcal{M} =
+10^{10.3} - 10^{10.8} \mathcal{M}_{\odot}$. From \cite{Kovac:2014aa}
+we plot an estimated $f_{\rm{Q}}$ by applying the residual between SFR
+based and color based galaxy classifications to the best-fit
+$f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ for
+low ($\delta = 0.0$) and high density environments ($\delta =
+1.5$). Similarly, from \cite{Baldry:2006aa} we plot $f_{\rm{Q}}$
+derived from the best-fit $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5}
+\mathcal{M}_{\odot}$ for low ($\delta = 0.0$) and high density
+environment ($\delta = 1.0$). For \cite{geha12a}, we plot $f_{\rm{Q}}$
+for their isolated galaxy sample in their mass bin closest to $10^{10.5} \mathcal{M}_{\odot}$, $\mathcal{M} = 10^{10.55} \mathcal{M}_{\odot}$.
 
-For our lowest redshift bin SDSS sample, we find that our $f_{\rm{Q}}$ for low and high environments are consistent with other SDSS $f_{\rm{Q}}$ (or $f_{\rm{red}}$) measurements as a function of environment.
-For example, \cite{Baldry:2006aa} uses project neighbor density environment measures ($\rm{log} \;  \Sigma$) to obtain $f_{\rm{Q}}(\mathcal{M})$ for a range of environmental densities.
-Although the different environment measurements make direct comparisons unclear, in their corresponding higher environments ($\rm{log} \; \Sigma > 0.2$ in \citealt{Baldry:2006aa}) $f_{\rm{Q}}(\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}) \sim 0.6$ and $f_{\rm{Q}}(\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}) \sim 0.9$, which is in agreement with our high density environment.
-Likewise, for lower environments ($\rm{log} \; \Sigma < -0.4$ in \citealt{Baldry:2006aa}) $f_{\rm{Q}}(\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}) \sim 0.4$ and $f_{\rm{Q}}(\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}) \sim 0.8$, which also agree with our low density environment $f_{\rm{Q}}$.
-The \cite{Baldry:2006aa} points (diamond) in Figure \ref{fig:qffit_comp} reflect this agreement.
+For our lowest redshift bin SDSS sample, we find that our $f_{\rm{Q}}$
+for low and high environments are consistent with other SDSS
+$f_{\rm{Q}}$ (or $f_{\rm{red}}$) measurements as a function of
+environment. For example, \cite{Baldry:2006aa} uses projected neighbor
+density environment measures ($\rm{log} \; \Sigma$) to obtain
+$f_{\rm{Q}}(\mathcal{M})$ for a range of environmental
+densities. Although the different environment measurements make direct
+comparisons difficult, in their corresponding higher environments
+($\rm{log} \; \Sigma > 0.2$ in \citealt{Baldry:2006aa})
+$f_{\rm{Q}}(\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}) \sim 0.6$
+and $f_{\rm{Q}}(\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}) \sim
+0.9$, which is in agreement with our high density
+environment. Likewise, for lower environments ($\rm{log} \; \Sigma <
+-0.4$ in \citealt{Baldry:2006aa}) $f_{\rm{Q}}(\mathcal{M} \sim
+10^{10.2} \mathcal{M}_{\odot}) \sim 0.4$ and $f_{\rm{Q}}(\mathcal{M}
+\sim 10^{11.5} \mathcal{M}_{\odot}) \sim 0.8$, which also agree with
+our low density environment $f_{\rm{Q}}$. The \cite{Baldry:2006aa}
+points (diamond) in Figure \ref{fig:qffit_comp} reflect this
+agreement.
 
@@
 
-A modified \cite{Tinker:2011aa} sample is used in \cite{geha12a} to obtain $f_{\rm{Q}}$ for isolated galaxies over a wider mass range ($10^{7.4} \mathcal{M}_\odot$ to $10^{11.2} \mathcal{M}_{\odot}$).
-Provided that \cite{geha12a} probe a slightly lower redshift range ($ z \le 0.06$), \cite{geha12a} present a consistent $f_{\rm{Q}}$ range as our SDSS $f_{\rm{Q}}$.
-Within the overlapping mass range, at the low mass end \cite{geha12a} find $f_{\rm{Q}}(\mathcal{M}_{*} \sim 10^{10.2} \mathcal{M}_{\odot}) \sim 0.3$ and at the high mass end they find $f_{\rm{Q}}(\mathcal{M}_{*} \sim 10^{11.2} \mathcal{M}_{\odot}) \sim 0.8$.
-Both of these values agree with our lowest redshift $f_{\rm{Q}}$ results in low density environment.
-Figure \ref{fig:qffit_comp} illustrates the $f_{\rm{Q}}$ agreement for $\mathcal{M}_{*} = 10^{10.5} \mathcal{M}_{\odot}$.
+A modified \cite{Tinker:2011aa} sample is used in \cite{geha12a} to
+obtain $f_{\rm{Q}}$ for isolated galaxies over a wider mass range
+($10^{7.4} \mathcal{M}_\odot$ to $10^{11.2}
+\mathcal{M}_{\odot}$). Although \cite{geha12a} probe a slightly lower
+redshift range ($ z \le 0.06$), their $f_{\rm{Q}}$ is consistent with
+our low density sample. Within the overlapping mass range, at the low
+mass end \cite{geha12a} find $f_{\rm{Q}}(\mathcal{M}_{*} \sim
+10^{10.2} \mathcal{M}_{\odot}) \sim 0.3$ and at the high mass end they
+find $f_{\rm{Q}}(\mathcal{M}_{*} \sim 10^{11.2} \mathcal{M}_{\odot})
+\sim 0.8$. Both of these values agree with our lowest redshift
+$f_{\rm{Q}}$ results in low density environment. Figure
+\ref{fig:qffit_comp} illustrates the $f_{\rm{Q}}$ agreement for
+$\mathcal{M}_{*} = 10^{10.5} \mathcal{M}_{\odot}$.
 
@@
 
-Similarly, $f_{\rm{red}}$ for high and low overdensities in \cite{Kovac:2014aa} are  greater overall than the PRIMUS $f_{\rm{Q}}$ values in high and low density environments.
-However, \cite{Kovac:2014aa} points out that there is a significant difference between classifying the quenched population using color and SFR.
+Similarly, $f_{\rm{red}}$ for high and low overdensities in
+\cite{Kovac:2014aa} are  greater overall than the PRIMUS $f_{\rm{Q}}$
+values in high and low density environments. However,
+\cite{Kovac:2014aa} points out that there is a significant difference
+between classifying the quiescent population using color and SFR.
 For their lower redshift bin ($0.1 < z < 0.4$) they find that their $f_{\rm{Q}}$ defined by color is greater than $f_{\rm{Q}}$ defined by SFR by roughly $0.2$.
@@
 
-In Figure \ref{fig:qf}, observing the $f_{\rm{Q}}$ evolution with respect mass reveal, qualitatively, little mass dependence in the evolution.
-Moreover, in Figure \ref{fig:qffit}, we illustrated that adjusting the fiducial mass only shifted the overall $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$, but did change the $f_{\rm{Q}}$ evolutionary trend.
-The consistency in the $f_{\rm{Q}}$ evolutionary trends when the fiducial mass is changed suggest that $f_{\rm{Q}}$ evolution exhibit little mass dependence.
-In contrast to the weak mass dependence we observe in our results, \cite{Iovino:2010aa} find significantly different $f_{\rm{Q}}$ evolutions at $\mathcal{M} \sim 10^{11} \mathcal{M}_{\odot}$ and $\mathcal{M} \sim 10^{10.5} \mathcal{M}_{\odot}$, for both group and isolated galaxies.
-In fact at their highest mass bin ($10^{10.9} - 10^{11.4} \mathcal{M}_{\odot}$, \cite{Iovino:2010aa} find no evolution for both environments: constant $f_{\mathrm{blue}} \sim 0.1$ over $z = 0.3 - 0.8$ for both group and isolated galaxy populations.
+In Figure \ref{fig:qf}, the $f_{\rm{Q}}$ evolution with respect to
+mass reveals, qualitatively, little mass dependence in the
+evolution. Moreover, in Figure \ref{fig:qffit}, we illustrated that
+adjusting the fiducial mass only shifted the overall
+$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$, but did not change the
+$f_{\rm{Q}}$ evolutionary trend. The consistency in the $f_{\rm{Q}}$
+evolutionary trends when the fiducial mass is changed suggest that
+$f_{\rm{Q}}$ evolution exhibit little mass dependence. In contrast to
+the weak mass dependence we observe in our results,
+\cite{Iovino:2010aa} find significantly different $f_{\rm{Q}}$
+evolution at $\mathcal{M} \sim 10^{11} \mathcal{M}_{\odot}$ and
+$\mathcal{M} \sim 10^{10.5} \mathcal{M}_{\odot}$, for both group and
+isolated galaxies. In fact at their highest mass bin ($10^{10.9} -
+10^{11.4} \mathcal{M}_{\odot}$, \cite{Iovino:2010aa} find no evolution
+for both environments: constant $f_{\mathrm{blue}} \sim 0.1$ over $z =
+0.3 - 0.8$ for both group and isolated galaxy populations.
 
-Meanwhile in their mass bin most comparable to $\mathcal{M}_{\rm{fid}} \sim 10^{10.5} \mathcal{M}_{\odot}$ ($10^{10.3} \mathcal{M}_{\odot} - 10^{10.8} \mathcal{M}_{\odot}$), \cite{Iovino:2010aa} finds that $f_{\rm{blue}}$ evolves by $\sim 0.1$ from $z = 0.5$ to $0.25$ for group galaxies and by $\sim 0.3$ from $z=0.55$ to $0.3$ for isolated galaxies as presented in Figure \ref{fig:qffit_comp}.
-Altogether, with mass bins beyond the fiducial masses we explore, \cite{Iovino:2010aa} find a strong mass dependence with $f_{\rm{Q}}$ evolving significantly more in lower mass bins.
-While our sample from PRIMUS provides larger statistics than zCOSMOS, the mass-completeness limits we impose on our sample limits the mass range we probe (e.g.
-$\mathcal{M} > 10^{10.5} \mathcal{M}_{\odot}$ for our $z \sim 0.7$ bin).
-Consequently our results cannot dismiss mass dependence in the $f_{\rm{Q}}$ evolution at lower masses.
+Meanwhile in their mass bin most comparable to $\mathcal{M}_{\rm{fid}}
+\sim 10^{10.5} \mathcal{M}_{\odot}$ ($10^{10.3} \mathcal{M}_{\odot} -
+10^{10.8} \mathcal{M}_{\odot}$), \cite{Iovino:2010aa} finds that
+$f_{\rm{blue}}$ evolves by $\sim 0.1$ from $z = 0.5$ to $0.25$ for
+group galaxies and by $\sim 0.3$ from $z=0.55$ to $0.3$ for isolated
+galaxies as presented in Figure \ref{fig:qffit_comp}. Altogether, with
+mass bins beyond the fiducial masses we explore, \cite{Iovino:2010aa}
+find a strong mass dependence with $f_{\rm{Q}}$ evolving significantly
+more in lower mass bins. While our sample from PRIMUS provides larger
+statistics than zCOSMOS, the mass-completeness limits we impose on our
+sample limits the mass range we probe (e.g. $\mathcal{M} > 10^{10.5}
+\mathcal{M}_{\odot}$ for our $z \sim 0.7$ bin). Consequently our
+results cannot rule out mass dependence in the $f_{\rm{Q}}$ evolution
+at lower masses.
 
-In Figure \ref{fig:qffit} and Figure \ref{fig:qffit_comp} we quantified that throughout our redshift range, high density environment has a significantly greater $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ than the low density environment.
-Our findings are in agreement with the zCOSMOS results from \cite{Cucciati:2010aa} and \cite{Kovac:2014aa}.
-As illustrated in Figure \ref{fig:qffit_comp}, both \cite{Cucciati:2010aa} and \cite{Kovac:2014aa} find $f_{\rm{Q}}$ in high density environment significantly greater than $f_{\rm{Q}}$ at low density environment.
-Moreover, since galaxy color serves as a proxy for SFR, our results support the existence of the color-density relation (\citealt{Cucciati:2010aa, Cooper:2010aa}) and debunks the suggestion that the color-density relation is merely a reflection of the mass-density as \cite{Scodeggio:2009aa} suggests for $0.2 < z< 1.4$ in the Vimos VLT Deep Survey.
+In Figure \ref{fig:qffit} and Figure \ref{fig:qffit_comp} we
+quantified that throughout our redshift range, high density
+environments have a significantly greater
+$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ than the low density
+environments. This finding is in agreement with the zCOSMOS results
+from \cite{Cucciati:2010aa} and \cite{Kovac:2014aa}. As illustrated in
+Figure \ref{fig:qffit_comp}, both \cite{Cucciati:2010aa} and
+\cite{Kovac:2014aa} find $f_{\rm{Q}}$ in high density environment
+significantly greater than $f_{\rm{Q}}$ at low density
+environment. Moreover, since galaxy color serves as a proxy for SFR,
+our results support the existence of the color-density relation
+(\citealt{Cucciati:2010aa, Cooper:2010aa}) and is not consistent with
+the color-density relation begin merely a reflection of the
+mass-density relationship, as \cite{Scodeggio:2009aa} suggest it is
+based on the Vimos VLT Deep Survey ($0.2 < z< 1.4$).
+
 % Purposely not mentioning the lack of morphology-density relation for M>10^10.5Msun galaxies as argued in Tasca et al. 2009 in order to not bring up morphology.
 
-In Section \ref{sec:env_qf_evol}, we pointed out that $f_{\rm{Q}}$ in low density environment evolved over cosmic time.
-From this trend we deduce that internal, environment independent, quenching mechanisms contribute to star-formation quenching in galaxy evolution.
-\cite{Iovino:2010aa} from zCOSMOS, plotted in Figure \ref{fig:qffit_comp}, also find that $f_{\rm{Q}}$ in low density environment increases over decrease in redshift.
+In Section \ref{sec:env_qf_evol}, we pointed out that $f_{\rm{Q}}$ in
+low density environments evolves over cosmic time. From this trend we
+deduce that internal, environment independent, mechanisms contribute
+to ending star-formation in galaxy evolution. \cite{Iovino:2010aa}
+from zCOSMOS, plotted in Figure \ref{fig:qffit_comp}, also find that
+$f_{\rm{Q}}$ in low density environment increases with decreasing redshift.
 On the other hand \cite{Kovac:2014aa}, also from zCOSMOS, presents that $f_{\rm{Q}}$ in low density environment decreases over cosmic time.
@@
 
-Furthermore, in Section \ref{sec:env_qf_evol}, our comparison of the $f_{\rm{Q}}$ evolution between the lowest density environment and the highest density environment revealed a modicum of evidence for the existence of environment dependent quenching mechanisms.
-The same comparison on zCOSMOS results (\citealt{Iovino:2010aa, Kovac:2014aa}) present trends inconsistent with our findings.
-First, comparing the high (red) and low (blue) density environments for \cite{Iovino:2010aa} in Figure \ref{fig:qffit_comp} shows that there is indeed pronounced discrepancies between the $f_{\rm{Q}}$ evolution in different environments.
-Group galaxies in \cite{Iovino:2010aa} have higher overall $f_{\rm{Q}}$ than isolated galaxies.
-However, unlike our results, which find a greater $f_{\rm{Q}}$ evolution at higher density environments, \cite{Iovino:2010aa} finds the opposite environment dependence that there is a significantly greater $f_{\rm{Q}}$ evolution for isolated galaxies.
+Furthermore, in Section \ref{sec:env_qf_evol}, our comparison of the
+$f_{\rm{Q}}$ evolution between the lowest density environment and the
+highest density environment revealed a modicum of evidence for the
+existence of environment dependent mechanisms. The same comparison
+with zCOSMOS results (\citealt{Iovino:2010aa, Kovac:2014aa}) present
+trends inconsistent with our findings. First, comparing the high (red)
+and low (blue) density environments for \cite{Iovino:2010aa} in Figure
+\ref{fig:qffit_comp} shows that there are indeed pronounced
+discrepancies between the $f_{\rm{Q}}$ evolution in different
+environments. Group galaxies in \cite{Iovino:2010aa} have higher
+overall $f_{\rm{Q}}$ than isolated galaxies. However, unlike our
+results, which find a greater $f_{\rm{Q}}$ evolution at higher density
+environments, \cite{Iovino:2010aa} finds the opposite environment
+dependence that there is a significantly greater $f_{\rm{Q}}$
+evolution for isolated galaxies.
 
-Next, \cite{Kovac:2014aa} also find that overall $f_{\rm{Q}}$ in high density is greater than low density environments.
-Like their low density environment $f_{\rm{Q}}$ evolution, $f_{\rm{Q}}$ in high density environment decreases over cosmic time between their two redshift bins.
-Although the decrease in $f_{\rm{Q}}$ over cosmic time conflicts with our results, \cite{Kovac:2014aa} finds a greater (less negative) $f_{\rm{Q}}$ evolution in high density environment over low density environment, suggesting an environment dependence that is in the same direction as our results.
-We note that the negative slopes of the $f_{\rm{Q}}$ evolution in both environments are enhanced in Figure \ref{fig:qffit_comp} due to the galaxy classification correction we impose to the \cite{Kovac:2014aa} results.
-However, even without the correction (not shown), in their best-fit $f_{\rm{Q}}$ results, the same evolutionary trends mentioned above are observed.
+Next, \cite{Kovac:2014aa} also find that overall $f_{\rm{Q}}$ is
+greater in high density than in low density environments. Like their
+low density environment $f_{\rm{Q}}$ evolution, $f_{\rm{Q}}$ in high
+density environment decreases over cosmic time between their two
+redshift bins. Although the decrease in $f_{\rm{Q}}$ over cosmic time
+conflicts with our results, \cite{Kovac:2014aa} finds a greater (less
+negative) $f_{\rm{Q}}$ evolution in high density environments relative
+to low density environments, suggesting an environment dependence that
+is in the same direction as our results. We note that the negative
+slopes of the $f_{\rm{Q}}$ evolution in both environments are enhanced
+in Figure \ref{fig:qffit_comp} due to the galaxy classification
+correction we impose to the \cite{Kovac:2014aa} results. However, even
+without the correction (not shown), in their best-fit $f_{\rm{Q}}$
+results, the same evolutionary trends mentioned above are observed.
 
@@
 
-As listed in Table \ref{tab:subsample}, after our edge effect cuts and stellar mass completeness limits, our sample consists of $12,861$ galaxies from PRIMUS over $0.2< z< 0.8$ and $64,026$ galaxies from SDSS over $0.05 < z < 0.12$.
-Meanwhile, \cite{Iovino:2010aa} has $914$ galaxies with $\mathcal{M} > 10^{10.3} \mathcal{M}_{\odot}$ over $0.1 < z < 0.6$ and $1033$ galaxies with $\mathcal{M} > 10^{10.6} \mathcal{M}_{\odot}$ over $0.1 < z < 0.8$.
-But for the actual sample used to obtain the best-fit $f_{\rm{Q}}$ values in Figure \ref{fig:qffit_comp} \cite{Iovino:2010aa} has $617$ galaxies.
-In comparison, our PRIMUS sample alone contains $> 20$ times the number of galaxies.
-While there is a considerable difference in the overall $f_{\rm{Q}}$ between our results and those of \cite{Iovino:2010aa}, the use of different methodologies, particularly for galaxy classification and environment measurements, make the comparisons ambiguous.
-On the other hand, the discrepancies in the $f_{\rm{Q}}$ evolutionary trends with our results may be explained by the limited statistics in the \cite{Iovino:2010aa} sample.
+As listed in Table \ref{tab:subsample}, after our edge effect cuts and
+stellar mass completeness limits, our sample consists of $12,861$
+galaxies from PRIMUS over $0.2< z< 0.8$ and $64,026$ galaxies from
+SDSS over $0.05 < z < 0.12$. Meanwhile, \cite{Iovino:2010aa} has $914$
+galaxies with $\mathcal{M} > 10^{10.3} \mathcal{M}_{\odot}$ over $0.1
+< z < 0.6$ and $1033$ galaxies with $\mathcal{M} > 10^{10.6}
+\mathcal{M}_{\odot}$ over $0.1 < z < 0.8$. For the actual sample used
+to obtain the best-fit $f_{\rm{Q}}$ values in Figure
+\ref{fig:qffit_comp} \cite{Iovino:2010aa} has $617$ galaxies. In
+comparison, our PRIMUS sample alone contains $> 20$ times the number
+of galaxies. While there is a considerable difference in the overall
+$f_{\rm{Q}}$ between our results and those of \cite{Iovino:2010aa},
+the use of different methodologies, particularly for galaxy
+classification and environment measurements, make the comparisons
+ambiguous. On the other hand, the discrepancies in the $f_{\rm{Q}}$
+evolutionary trends with our results may be explained by the limited
+statistics in the \cite{Iovino:2010aa} sample.
 
-The more recent \cite{Kovac:2014aa} provides larger statistics with $2,340$ galaxies in their lower redshift bin ($0.1 < z < 0.4$) and $2,448$ galaxies in their higher redshift bin ($0.4 < z < 0.7$).
-Although their sample falls short of our PRIMUS sample, which contains over two times the number of galaxies, the \cite{Kovac:2014aa} sample provides a more stable comparison.
-Once their results are adjusted for the different galaxy classification, we find that their overall $f_{\rm{Q}}$ is more or less consistent with our overall $f_{\rm{Q}}$.
-However, it is difficult to explain the significant discrepancies in the $f_{\rm{Q}}$ evolutionary trends.
+The more recent \cite{Kovac:2014aa} provides larger statistics with
+$2,340$ galaxies in their lower redshift bin ($0.1 < z < 0.4$) and
+$2,448$ galaxies in their higher redshift bin ($0.4 < z <
+0.7$). Although their sample is smaller than the PRIMUS sample, which
+contains over two times the number of galaxies, the
+\cite{Kovac:2014aa} sample provides a more stable comparison.  Once
+their results are adjusted for the different galaxy classification, we
+find that their overall $f_{\rm{Q}}$ is more or less consistent with
+our overall $f_{\rm{Q}}$. However, it is difficult to explain the
+significant discrepancies in the $f_{\rm{Q}}$ evolutionary trends.
 % zCOSMOS has more precise redshift but PRIMUS has it beat in terms of sample size and coverage of the sky 5.5 deg^2 vs 1.7 deg^2
@@
 \section{Summary and Discussion} \label{sec:summary}
-Using a stellar mass complete galaxy sampled derived from SDSS and PRIMUS accompanied by a consistently measured galaxy environment from robust spectroscopic redshifts, we measure the stellar mass functions for star-forming and quiescent in low and high density environments over the redshift range $0.05 < z < 0.8$.
-From these stellar mass functions, we compare the proportion of galaxies that have quenched their star-formation within the subsamples by computing quiescent fraction for each of them.
-Afterwards, in order to better quantify the evolution of the quiescent fraction over cosmic time, we fit our quiescent fraction anchored at a fiducial mass.
-From our analyses we find the following notable results.
+Using a stellar mass complete galaxy sample derived from SDSS and
+PRIMUS accompanied by a consistently measured galaxy environment from
+robust spectroscopic redshifts, we measure the stellar mass functions
+for star-forming and quiescent galaxies in low and high density
+environments over the redshift range $0.05 < z < 0.8$. From these
+stellar mass functions, we compare the proportion of galaxies that
+have ended their star-formation within the subsamples by computing the
+quiescent fraction for each of them. In order to better quantify the
+evolution of the quiescent fraction over cosmic time, we fit our
+quiescent fraction anchored at a fiducial mass.
 
+From our analyses we find the following notable results. The first
+three demonstrate that previous findings that are well known in the
+local universe are applicable out to $z\sim 0.7$. The last two are
+consistent with the findings of \cite{peng10a} but provide increased
+detail on the environmental dependence of galaxy evolution:
 \begin{enumerate}
-	\item By measuring the SMF evolution for each of our subsamples, we approximately trace the evolutionary tracks our galaxy population tracing the tracks of quenching mechanisms and galaxies infalling into high density environments.
-	\item From the SMFs, we find that our galaxy population in high density environments, both star-forming and quiescent, have a higher median mass, thus confirming the mass density relation and mass-segregation in different environments throughout our sample's redshift range.
-	\item For all subsamples, $f_{\rm{Q}}$ increases monotonically with galaxy stellar mass showing a clear mass dependence and supporting well established color-mass and morphology mass relations. 
-	\item $f_{\rm{Q}}$ increases significantly with redshift for both low and high density environments.
-For high density environment, this trend is the Butcher-Oemler effect.
-Furthermore, the $f_{\rm{Q}}$ evolution in low density environment suggest the existence of internal environment-independent quenching mechanisms.
-	\item By fitting our $f_{\rm{Q}}$s, we illustrate that $f_{\rm{Q}}$ in high density environments is greater than $f_{\rm{Q}}$ in low density environments regardless of mass and redshift.
-This result reflects the well known trend that galaxies in high density environment are statistically redder, have lower SFRs, and more massive.
-	\item Comparison of the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ evolution for a range of environment classifications reveal that the since $z = 0.8$, $f_{\rm{Q}}$ has evolved by a greater amount in higher density environments.
-For our purest high environment sample ($n_{\rm{env}} > 9$), the total $f_{\rm{Q}}$ evolution is $\sim 0.1$ greater than the total $f_{\rm{Q}}$ evolution in low density environment, revealing a moderate dependence in environment.
+% NOT SURE WHAT THIS ONE WAS SAYING:
+% \item By measuring the SMF evolution for each of our subsamples, we
+%    approximately trace the evolutionary tracks our galaxy population
+%    tracing the tracks of mechanisms for ending star formation and
+%    galaxies infalling into high density environments.
+	\item From the SMFs, we find that the galaxy population in high
+    density environments, both star-forming and quiescent, have a
+    higher median mass, thus confirming the mass-density relation and
+    mass-segregation in different environments throughout our sample's
+    redshift range.
+	\item For all subsamples, $f_{\rm{Q}}$ increases monotonically with
+    galaxy stellar mass, showing a clear mass dependence and
+    reflecting the well-established color-mass and morphology-mass
+    relations.
+	\item We illustrate that $f_{\rm{Q}}$ in high density environments
+    is greater than $f_{\rm{Q}}$ in low density environments
+    regardless of mass and out to redshift $z\sim 0.7$. This result
+    reflects the well known trend that galaxies in high density
+    environment are statistically redder, have lower SFRs, and are
+    more massive.
+	\item $f_{\rm{Q}}$ increases significantly with redshift for both
+    low and high density environments. For high density environment,
+    this trend is the Butcher-Oemler effect. Furthermore, the
+    $f_{\rm{Q}}$ evolution in low density environment suggest the
+    existence of internal environment-independent mechanisms for
+    ending star formation.
+	\item Comparison of the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$
+    evolution for a range of environment classifications reveals that
+    the since $z = 0.8$, $f_{\rm{Q}}$ has evolved by a greater amount
+    in the highest density environments. For our purest high
+    environment sample ($n_{\rm{env}} > 9$), the total $f_{\rm{Q}}$
+    evolution is $\sim 0.1$ greater than the total $f_{\rm{Q}}$
+    evolution in low density environment, revealing a moderate
+    dependence on environment.
 \end{enumerate}
 
-Many physical mechanisms have been proposed to explain the quenching of star-formation observed in our universe.
-Recently star-formation quenching has often been classified into internal or external mechanisms, and sometimes more specifically into mass-dependent and environment-dependent mechanisms (\citealt{Baldry:2006aa, Peng:2010aa}).
-The significant redshift evolution of the $f_{\rm{Q}}$ in low density environment confirms the existence of internal mechanisms that quench star-forming in galaxies.
+Many physical mechanisms have been proposed to explain the cessation
+of star-formation observed in many galaxies. Recently star-formation
+cessation has often been classified into internal or external
+mechanisms, and sometimes more specifically into mass-dependent and
+environment-dependent mechanisms (\citealt{Baldry:2006aa,
+  Peng:2010aa}). The significant redshift evolution of the
+$f_{\rm{Q}}$ in low density environments confirms the existence of
+internal mechanisms that end star-forming in galaxies.
 
-Furthermore, the greater $f_{\rm{Q}}$ evolution in high density environment over low density environment demonstrates that in addition to the internal quenching mechanisms, in high density environments such as groups and clusters, environment-quenching also contributes to star-formation quenching.
-Although our results do not specifically shed light on which quenching mechanism (e.g.
-strangulation, ram-pressure stripping, etc.) occur in high density environments, they impose strict constraints on the total contribution of environment quenching that any environment quenching model must satisfy.
-More importantly, our results provide limit on the role of environment quenching in galaxy evolution.
+Furthermore, the greater $f_{\rm{Q}}$ evolution in the highest density
+environment relative to low density environments suggests that in
+addition to the internal mechanisms, in high density environments such
+as groups and clusters, environment-dependent effects may also
+contribute to the end of star-formation. Our results do not
+specifically shed light on which mechanism (e.g. strangulation,
+ram-pressure stripping, etc.) occur in high density environments. In
+addition, the mechanism could yet be indirect; for example, the
+galaxies in higher density environments could yet end star-formation
+primarily due internal processes that affect the galaxies that end up
+in groups and clusters more greatly.  Nevertheless, our results impose
+important constraints on the total possible contribution of
+environment dependent mechanisms that models must satisfy, providing a
+limit on the role of environment in ending star formation in
+galaxies.
 

### 2014-10-15 qfenv_paper/qf_environment.tex

@@
 
-For our aperture, we use a cylinder of dimensions: $R_{\rm{ap}} = 2 \;
-h^{-1} \rm{Mpc}$ and $H_{\rm{ap}} = 25 \; h^{-1}\rm{Mpc}$.  We use a
+For our aperture, we use a cylinder of dimensions: $R_{\rm{ap}} =
+2.9\;
+\rm{Mpc}$ and $H_{\rm{ap}} = 36\; \rm{Mpc}$.  We use a
 cylindrical aperture in order to account for the PRIMUS redshift
@@
 distortions. The PRIMUS redshift uncertainty at $z \sim 0.7$
-corresponds to $\sigma_z < 0.01$, so our aperture height choice of $25
-\; \rm{Mpc}/h$ accounts for both of these effects. Our choice of
+corresponds to $\sigma_z < 0.01$, so our aperture height choice of
+$36\;
+\rm{Mpc}$ accounts for both of these effects. Our choice of
 cylinder radius was motivated by scale dependence analyses in the
@@
 
-Finally we measure the environment for each galaxy in our galaxy
+Finally, we measure the environment for each galaxy in our galaxy
 sample by counting the number of EDP galaxies, $n_{\rm{env}}$ with RA,
@@
 The analysis we describe below uses a fixed cylindrical aperture with
-dimensions $R_{\rm{ap}} = 2 \:h^{-1}\rm{Mpc}$ and $H_{\rm{ap}} = 25
-\:h^{-1}\rm{Mpc}$ to measure environment. The same analysis was
-extended for varying aperture dimensions $R_{\rm{ap}} = 1, 2, 3 \:
-h^{-1}\rm{Mpc}$ and $H_{\rm{ap}} = 25, 50 \:h^{-1}\rm{Mpc}$. We also
+dimensions $R_{\rm{ap}} = 2.9 \;rm{Mpc}$ and $H_{\rm{ap}} = 36
+\;\rm{Mpc}$ to measure environment. The same analysis was
+extended for varying aperture dimensions $R_{\rm{ap}} = 1.4, 2.9, 4.3 \:
+\rm{Mpc}$ and $H_{\rm{ap}} = 36, 71 \;\rm{Mpc}$. We also
 adjusted the environment classification thresholds for these
@@
 $z=0$--$0.8$. The environment of each galaxy  
-was calculated using a cylindrical aperture size of $R=2 \: \rm{Mpc}$ and $H=25 \: \rm{Mpc}$ and  
+was calculated using a cylindrical aperture size of $R=2.9 \:
+\rm{Mpc}$ and $H=36 \: \rm{Mpc}$ and  
 classification based on the cut-offs specified in Table \ref{tab:aperture}. The SMFs use mass bins of 

### 2014-10-20 qfenv_paper/qf_environment.tex
multipanel qf fit literature comparison figures

@@
 
-\begin{figure}
+\begin{figure*}
     \begin{center}
@@
         \epsscale{1.0}
-        \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmass10_5_lit_primuszerr_zcosmoscomp_envthresh_kovacoffset.eps, height=0.45\textwidth}
-        \caption{$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}}=10^{10.5} \mathcal{M}_\odot)$ evolution compared to $f_{\rm{red}}(\mathcal{M}_{*}=10^{10.5} \; \mathcal{M}_{\odot})$ in the literature: \cite{Iovino:2010aa} (square) and \cite{Kovac:2014aa} (triangle) from zCOSMOS and \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross) from SDSS.
-The $f_{\rm{red}}$ values from \cite{Iovino:2010aa}, \cite{Kovac:2014aa}, and \cite{Baldry:2006aa} are calculated from the best-fit parameterizations presented in the respective works.
+        \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmass10_5_lit_primuszerr_baldry_geha_iovino_kovac_peng_envthresh_kovacoffset.eps, height=\textwidth, angle=90}
+        \caption{$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}}=10^{10.5} \mathcal{M}_\odot)$ evolution compared to $f_{\rm{red}}(\mathcal{M}_{*}=10^{10.5} \; \mathcal{M}_{\odot})$ in the literature: \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross) from SDSS (panel a), \cite{Iovino:2010aa} (empty square) and \cite{Kovac:2014aa} (triangle) from zCOSMOS (panel b), and \cite{Peng:2010aa} (filled square) from SDSS and zCOSMOS (panel c).
+The $f_{\rm{red}}$ values from \cite{Iovino:2010aa}, \cite{Kovac:2014aa}, \cite{Baldry:2006aa}, and \cite{Peng:2010aa} are calculated from the best-fit parameterizations presented in the respective works.
 The $f_{\rm{Q}}$ value from \cite{geha12a} is the $f_{\rm{Q}}$ value at $\mathcal{M} = 10^{10.55} \mathcal{M}_{\odot}$.
@@
     \end{center}
-\end{figure}
+\end{figure*}
 

### 2014-10-21 qfenv_paper/qf_environment.tex
Some edits to bib. Commented out Bundy + Bolzonela

@@
 The analysis we describe below uses a fixed cylindrical aperture with
-dimensions $R_{\rm{ap}} = 2.9 \;rm{Mpc}$ and $H_{\rm{ap}} = 36
+dimensions $R_{\rm{ap}} = 2.9 \; \rm{Mpc}$ and $H_{\rm{ap}} = 36
 \;\rm{Mpc}$ to measure environment. The same analysis was
@@
 $z=0$--$0.8$. The environment of each galaxy  
-was calculated using a cylindrical aperture size of $R=2.9 \:
-\rm{Mpc}$ and $H=36 \: \rm{Mpc}$ and  
-classification based on the cut-offs specified in Table \ref{tab:aperture}. The SMFs use mass bins of 
-width $\Delta \rm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.25$. In each panel we use shades of blue 
+was calculated using a cylindrical aperture size of $R=2.9 \: \rm{Mpc}$ and $H=36 \: \rm{Mpc}$ and  
+classified as low environment when $n_{\mathrm{env}} < 0.5$ and as high environment when $n_{\mathrm{env}} > 3.0$. The SMFs use mass bins of 
+width $\Delta \rm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.2$. In each panel we use shades of blue 
 (star-forming) and orange (quiescent) to represent the SMF at different redshift, higher redshifts being
@@
 In panel (a), star-forming galaxies in low density environments, we find a significant decrease in the high mass end of the SMF ($\mathcal{M} > 10^{10.75} \mathcal{M}_{\odot}$).
-In contrast at lower masses ($\mathcal{M} < 10^{10.5} \mathcal{M}_{\odot}$) we observe a notable increase in the SMF.
+At lower masses ($\mathcal{M} < 10^{10.5} \mathcal{M}_{\odot}$) we observe no noticeable trend in the SMF.
 In panel (b), star-forming galaxies in high density environments, we notice a possible decrease above the knee of the SMF ($\mathcal{M} \sim 10^{10.7} \mathcal{M}_{\odot}$) accompanied by an increase below the knee.
-For the quiescent population in low density environment, shown in panel (c) of Figure \ref{fig:smf}, we notice an increase in $\Phi$ for lower masses, but we do not notice any clear SMF evolution at the massive end.
-Lastly for the quiescent population in high density environments, panel (d), we find significant increase in $\Phi$ at all masses.
-
-In comparison to results from DEEP2 (\citealt{bundy06a}) and zCOSMOS (\citealt{Bolzonella:2010aa}), some of the noted trends are not immediately evident.
+For the quiescent population in low density environment, shown in panel (c) of Figure \ref{fig:smf}, we do not notice any clear SMF evolution throughout the mass range.
+Lastly for the quiescent population in high density environments, panel (d), we find significant increase in $\Phi$ for lower masses but no notable trend at higher masses.
+
+%In comparison to results from DEEP2 (\citealt{bundy06a}) and zCOSMOS (\citealt{Bolzonella:2010aa}), some of the noted trends are not immediately evident.
 However, this is mostly due to the conflicting mass limits proposed in each study.
@@
         \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmass10_5_lit_primuszerr_baldry_geha_iovino_kovac_peng_envthresh_kovacoffset.eps, height=\textwidth, angle=90}
-        \caption{$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}}=10^{10.5} \mathcal{M}_\odot)$ evolution compared to $f_{\rm{red}}(\mathcal{M}_{*}=10^{10.5} \; \mathcal{M}_{\odot})$ in the literature: \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross) from SDSS (panel a), \cite{Iovino:2010aa} (empty square) and \cite{Kovac:2014aa} (triangle) from zCOSMOS (panel b), and \cite{Peng:2010aa} (filled square) from SDSS and zCOSMOS (panel c).
+        \caption{$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}}=10^{10.5} \mathcal{M}_\odot)$ evolution compared to $f_{\rm{red}}(\mathcal{M}_{*}=10^{10.5} \; \mathcal{M}_{\odot})$ in the literature: \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross) from SDSS (panel a), \cite{Iovino:2010aa} (empty square) and \cite{Kovac:2014aa} (triangle) from zCOSMOS (panel b), and \cite{Peng:2010aa} (filled square) from both SDSS and zCOSMOS (panel c).
 The $f_{\rm{red}}$ values from \cite{Iovino:2010aa}, \cite{Kovac:2014aa}, \cite{Baldry:2006aa}, and \cite{Peng:2010aa} are calculated from the best-fit parameterizations presented in the respective works.
@@
 local universe are applicable out to $z\sim 0.7$. The last two are
-consistent with the findings of \cite{peng10a} but provide increased
+consistent with the findings of \cite{Peng:2010aa} but provide increased
 detail on the environmental dependence of galaxy evolution:

### 2014-10-22 qfenv_paper/qf_environment.tex
Added some Peng+2010 description to text

@@
 In Figure \ref{fig:qffit_comp}, we plot  best-fit parameterization of
-$f_{\rm{red}}$ for high and low density environment from zCOSMOS,
-\cite{Iovino:2010aa} (square) and \cite{Kovac:2014aa} (triangle), and
-SDSS, \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross). From
+$f_{\rm{red}}$ for high and low density environment from SDSS (panel a), \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross), zCOSMOS (panel b),
+\cite{Iovino:2010aa} (empty square) and \cite{Kovac:2014aa} (triangle), and \cite{Peng:2010aa} (filled square; panel c) from both surveys. From
 \cite{Iovino:2010aa} we calculate $f_{\rm{red}} = 1-f_{\rm{blue}}$
@@
 for their isolated galaxy sample in their mass bin closest to $10^{10.5} \mathcal{M}_{\odot}$, $\mathcal{M} = 10^{10.55} \mathcal{M}_{\odot}$.
+Finally for \cite{Peng:2010aa}, we plot the parameterized $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ using the specified best-fit parameters in low ($\delta =0.0$) and high ($\delta = 1.4$) density environments.
 
@@
 $\mathcal{M}_{*} = 10^{10.5} \mathcal{M}_{\odot}$.
+
+%\cite{Peng:2010aa} computes the comoving density field for the SDSS DR7 and zCOSMOS galaxies in order to calculate $f_{\mathrm{red}}$ as a function of mass and environment.
+If we compare our $f_{\mathrm{Q}}$ to the best-fit parameterization $f_{\mathrm{red}}$ for their SDSS subsample we find that
 

### 2014-11-15 qfenv_paper/qf_environment.tex
alisoncoil_edits part 1

@@
 \def \highenvthresh {3.0}
+\def \apradius{2.5}
+\def \apheight{35}
 
@@
 Michael~Blanton\altaffilmark{1}, 
-Alison~Coil\altaffilmark{2}, 
-Richard~Cool\altaffilmark{3}, 
-Daniel Eisenstein\altaffilmark{4},
-John Moustakas\altaffilmark{5}, 
+John Moustakas\altaffilmark{2},
+Alison~Coil\altaffilmark{3}, 
+Richard~Cool\altaffilmark{4}, 
+Daniel Eisenstein\altaffilmark{5},
 Ken Wong\altaffilmark{6}, 
@@
 \altaffiltext{1}{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Place, New York, NY 10003}
-\altaffiltext{2}{Center for Astrophysics and Space Sciences, Department of Physics, University of California, 9500 Gilman Dr., La Jolla, CA 92093}
-\altaffiltext{3}{MMT Observatory, University of Arizona, 1540 E Second Street, Tucson AZ 85721}
-\altaffiltext{4}{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
-\altaffiltext{5}{Department of Physics and Astronomy, Siena College, 515 Loudon Road, Loudonville, NY 12211}
+\altaffiltext{2}{Department of Physics and Astronomy, Siena College, 515 Loudon Road, Loudonville, NY 12211}
+\altaffiltext{3}{Center for Astrophysics and Space Sciences, Department of Physics, University of California, 9500 Gilman Dr., La Jolla, CA 92093}
+\altaffiltext{4}{MMT Observatory, University of Arizona, 1540 E Second Street, Tucson AZ 85721}
+\altaffiltext{5}{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
 \altaffiltext{6}{Steward Observatory, University of Arizona, 933 North Cherry Avenue, Tucson, AZ 85721} 
@@
 quiescent fraction rises with cosmic time for all masses and
-environments. At a fiducial mass of $10^{10.5}M_\odot$, between $z\sim
-0.7$ and $0.1$, the quiescent fraction's rise varies from 0.15 at the
-lowest environments to 0.25 at the highest environments we measure.
+environments. At a fiducial mass of $10^{10.5}M_\odot$, from $z\sim
+0.7$ to $0.1$, the quiescent fraction rises by $15\%$ at the
+lowest environments and by $25\%$ at the highest environments we measure.
 These results suggest that for a minority of galaxies their cessation
-of star formation might be associated with external influences on
+of star formation is due to external influences on
 them. However, in the recent Universe a substantial fraction of the
@@
 Nevertheless, the evolution of the role of environment is a relatively
-subtle effect and difficult to study.  Although history of galaxies
+subtle effect and difficult to study.  Although the history of galaxies
 prior to $z\sim 1$ appears to have been one of rapid assembly, since
@@
 the evolution of the quiescent fraction over the redshift range $0 < z < 1$.
-For our analysis, we require a sample with sufficient depth and robustness to probe the redshift range and to measure galaxy environment.
+For our analysis, we require a sample with sufficient depth and high quality spectroscopic redshift to probe the redshift range and to measure galaxy environment.
 PRIMUS with its $\sim 120,000$ spectroscopic redshifts provides a large data set at intermediate redshifts for our analysis.
-In addition, we anchor our analysis at intermediate redshifts with a low redshift sample derived from the Sloan Digital Sky Survey (\cite{York:2000aa}).
+In addition, we anchor our analysis with a low redshift sample derived from the Sloan Digital Sky Survey (\cite{York:2000aa}).
 
@@
 introduce a size dependent bias in the galaxy fluxes and consequently
-stellar masses (\citealt{west05a, blanton05b, lauer07a, bernardi07a,
-  hyde09a, west10a}).
+stellar masses (\citealt{West:2005aa, Blanton:2005ab, Lauer:2007aa, Bernardi:2007aa,
+  Hyde:2009aa, West:2010aa}).
 
@@
 
+\subsection{Stellar Mass Complete Galaxy Sample} \label{sec:masscomp}
 From the low redshift SDSS-{\em GALEX} and intermediate redshift
@@
 Stellar mass completeness limits for a magnitude-limited survey such as PRIMUS are functions of redshift, the apparent magnitude limit of the survey, and the typical stellar mass-to-light ratio of galaxies near the flux limit.
-As in \cite{Moustakas:2013aa}, we follow \cite{Pozzetti:2010aa} to empirically determine the stellar mass completeness limits.
+We use the same procedure as \cite{Moustakas:2013aa}, which follows \cite{Pozzetti:2010aa}, to empircally determine the stellar mass completeness limits.
 For each of the target galaxies we compute $\mathcal{M}_{\rm{lim}}$ using $\log \; \mathcal{M}_{\mathrm{lim}} = \log \; \mathcal{M} + 0.4 (m - m_{\mathrm{lim}})$, where $\mathcal{M}$ is the stellar mass of the galaxy in $\mathcal{M_{\odot}}$, $\mathcal{M}_{\rm{lim}}$ is the stellar mass of each galaxy if its magnitude was equal to the survey magnitude limit, $m$ is the observed apparent magnitude in the selection band, and $m_{\rm{lim}}$ is the magnitude limit for our five fields.
@@
 To account for the targeting incompleteness of the SDSS-{\em GALEX} sample, we use the statistical weight estimates provided by the NYU-VAGC catalog.
-Furthermore, we determine a uniform stellar mass completeness limit of $10^{10.2} \mathcal{M}_{\odot}$ above the stellar mass-to-light ratio of the SDSS-{\em GALEX} data within the imposed redshift limits.
+Furthermore, we determine a uniform stellar mass completeness limit of $10^{10.2} \mathcal{M}_{\odot}$ above the stellar mass-to-light ratio completeness limit of the SDSS-{\em GALEX} data within the imposed redshift limits (\citealt{Blanton:2005ab, Baldry:2008aa, Moustakas:2013aa}).
 We then apply this mass limit in order to obtain our mass-complete galaxy sample at low redshift.
@@
 
-We present the absolute magnitude ($M_{r}$) versus redshift for the galaxy sample (black squares) in Figure \ref{fig:targetEDP}.
+%We present the absolute magnitude ($M_{r}$) versus redshift for the galaxy sample (black squares) in Figure \ref{fig:targetEDP}.
 The left-most panel corresponds to the sample derived from the SDSS-{\em GALEX} data and the rest correspond to the target sample derived from the PRIMUS data divided in bins with $\Delta z \sim 0.2$.
@@
 We now classify our mass complete galaxy sample into quiescent or star-forming using an evolving cut based on specific star-formation rate utilized in \cite{Moustakas:2013aa} Section 3.2.
-This classification method uses the star-forming (SF) sequence, which is the correlation between star-formation rate (SFR) and stellar mass in star-forming galaxies observed at least until $z \sim 2$ (\citealt{Noeske:2007aa}).
+This classification method uses the star-forming (SF) sequence, which is the correlation between star-formation rate (SFR) and stellar mass in star-forming galaxies observed at least until $z \sim 2$ (\citealt{Noeske:2007aa, Karim:2011aa}).
 The PRIMUS sample displays a well-defined SF sequence within the redshift range of our galaxy sample.
@@
 The contribution from quiescent galaxies is colored in red.
-Each redshift panel is divided into three sections by the environment classification cutoffs (vertical black lines): low density environment $n_{\rm{env}} < 0.5$ and high density environment $n_{\rm{env}} > 3.0$.
+Each redshift panel is divided into three sections by the environment classification cutoffs (black veritcal lines): low density environment $n_{\rm{env}} < 0.5$ and high density environment $n_{\rm{env}} > 3.0$.
 The percentages of the redshift bin contained in the environment classifications are presented above the distribution.
-For example at $0.2 < z < 0.4$, $56.0 \%$ of galaxies in the redshift bin have low density environments while $29.0\%$ of galaxies in the redshift bin have high density environments.
-}      \label{fig:envcount}
+For example at $0.2 < z < 0.4$, $36.0 \%$ of galaxies in the redshift bin are in low density environments while $35.0\%$ of galaxies in the redshift bin are in high density environments.
+The significant difference between the SDSS distribution and the PRIMUS distribution above is due to the difference in stellar mass completeness limit imposed in our galaxy sample.}      \label{fig:envcount}
     \end{center}
@@
 For our aperture, we use a cylinder of dimensions: $R_{\rm{ap}} =
-2.9\;
-\rm{Mpc}$ and $H_{\rm{ap}} = 36\; \rm{Mpc}$.  We use a
+\apradius\;
+\rm{Mpc}$ and $H_{\rm{ap}} = \apheight\; \rm{Mpc}$.  We use a
 cylindrical aperture in order to account for the PRIMUS redshift
@@
 corresponds to $\sigma_z < 0.01$, so our aperture height choice of
-$36\;
+$\apheight\;
 \rm{Mpc}$ accounts for both of these effects. Our choice of
@@
 Before we consider the cumulative number densities in the redshift bins, we first determine the $M_r$ limit for the highest redshift bin ($0.6-0.8$) by examining the $M_{r}$ distribution with bin size $\Delta M_{r} = 0.25$ and select $M_{r,\rm{lim}}$ near the peak of the distribution where bins with $M_{r} > M_{r,\rm{lim}}$ have fewer galaxies than the bin at $M_{r, \rm{lim}}$.
-We conservatively choose $M_{r, \rm{lim}}(0.6 < z < 0.8)$ to be $M_{r} = -20.98$.
-Then for the lower redshift bins, we impose absolute magnitude limits ($M_{r,\rm{lim}}$) such that the cumulative number density, calculated with the galaxy statistical weights, of the bin ordered by $M_{r}$ is equal to the cumulative number density of the highest redshift bin at $M_{r, \rm{lim}}(0.6 < z < 0.8) = -20.98$.
+We conservatively choose $M_{r, \rm{lim}}(0.6 < z < 0.8)$ to be $M_{r} = -21.0$.
+Then for the lower redshift bins, we impose absolute magnitude limits ($M_{r,\rm{lim}}$) such that the cumulative number density, calculated with the galaxy statistical weights, of the bin ordered by $M_{r}$ is equal to the cumulative number density of the highest redshift bin at $M_{r, \rm{lim}}(0.6 < z < 0.8) = -21.0$.
 
@@
 The analysis we describe below uses a fixed cylindrical aperture with
-dimensions $R_{\rm{ap}} = 2.9 \; \rm{Mpc}$ and $H_{\rm{ap}} = 36
+dimensions $R_{\rm{ap}} = \apradius \; \rm{Mpc}$ and $H_{\rm{ap}} = \apheight
 \;\rm{Mpc}$ to measure environment. The same analysis was
-extended for varying aperture dimensions $R_{\rm{ap}} = 1.4, 2.9, 4.3 \:
-\rm{Mpc}$ and $H_{\rm{ap}} = 36, 71 \;\rm{Mpc}$. We also
+extended for varying aperture dimensions $R_{\rm{ap}} = 1.5, \apradius, 3.0 \:
+\rm{Mpc}$ and $H_{\rm{ap}} = \apheight, 70 \;\rm{Mpc}$. We also
 adjusted the environment classification thresholds for these
@@
 mass-density relation and observed mass segregation with environment
-in the literature (\citealt{norberg02a, zehavi02a, blanton05b,
+in the literature (\citealt{norberg02a, zehavi02a, Blanton:2005ab,
   bundy06a, Scodeggio:2009aa, Bolzonella:2010aa}).

### 2014-11-17 qfenv_paper/qf_environment.tex
Alison Coil edit part 2

@@
 SMFs we compute $f_{\rm{Q}}(\mathcal{M}_{*})$ and quantify its
-evolution within our redshift range. As expected, the quiescent
+evolution within our redshift range. We find that the quiescent
 fraction is higher at higher masses and in denser environments. The
@@
 surroundings, with a strong dependence of the quiescent fraction of
-galaxies on their local environment (e.g. \citealt{hubble36a,
+galaxies on their local environment (e.g. \citealt{hubble36,
 oemler74a, dressler80a, hermit96a, guzzo97a}; for a recent review see
@@
 The percentages of the redshift bin contained in the environment classifications are presented above the distribution.
-For example at $0.2 < z < 0.4$, $36.0 \%$ of galaxies in the redshift bin are in low density environments while $35.0\%$ of galaxies in the redshift bin are in high density environments.
-The significant difference between the SDSS distribution and the PRIMUS distribution above is due to the difference in stellar mass completeness limit imposed in our galaxy sample.}      \label{fig:envcount}
+For example at $0.2 < z < 0.4$, $\apheight.0 \%$ of galaxies in the redshift bin are in low density environments while $35.0\%$ of galaxies in the redshift bin are in high density environments.
+We note that the significant difference between the SDSS distribution and the PRIMUS distribution above is due to the difference in stellar mass completeness limit imposed in our galaxy sample.}      \label{fig:envcount}
     \end{center}
@@
 respectively. These absolute magnitude limits are illustrated in
-Figure \ref{fig:targetEDP}, which show clear $M_r$ cutoffs in the
-$M_{r}$ distribution versus redshift for the EDP (red circles) on top
-of the target galaxy sample (black).
+Figure \ref{fig:targetEDP}, where we present the absolute magnitude ($M_{r}$) versus redshift for the galaxy sample (black squares) ad the EDP (red circles). 
+The left-most panel corresponds to the sample derived from the SDSS-{\em GALEX} data and the rest correspond to the target sample derived from the PRIMUS data divided in bins with $\Delta z \sim 0.2$.
+Figure \ref{fig:targetEDP} shows clear $M_r$ cutoffs in the
+$M_{r}$ distribution versus redshift for the EDP on top
+of the target galaxy sample.
 
@@
 $A_{\rm{EDP}}$ is the total angular area of the EDP window function and $f_{\rm{thresh}}$ is the fractional threshold for the edge effect cut-off.
-For $R_{\rm{ap}}= 2.9 \;\rm{Mpc}$, $f_{\rm{thresh}} = 0.75$.
+For $R_{\rm{ap}}= \apradius \;\rm{Mpc}$, $f_{\rm{thresh}} = 0.75$.
 If $n_{i, \rm{ransack}}$ is greater than $<n_{\rm{ransack}}>_i$ then galaxy $i$ remains in our sample; otherwise, it is discarded.
@@
 In contrast, in the SDSS redshift bin, $38 \%$ of galaxies in the redshift bin are in low density environments and $45 \%$ are in high density environments.
-We remind the reader that this is due to the different mass-completeness limits imposed on our galaxy sample for each redshift bins.
+We remind the reader that this is due to the different mass-completeness limits imposed on our galaxy sample for each redshift bins and does not affect our results.
 \begin{figure*}
@@
 $z=0$--$0.8$. The environment of each galaxy  
-was calculated using a cylindrical aperture size of $R=2.9 \: \rm{Mpc}$ and $H=36 \: \rm{Mpc}$ and  
+was calculated using a cylindrical aperture size of $R=\apradius \: \rm{Mpc}$ and $H=\apheight \: \rm{Mpc}$ and  
 classified as low environment when $n_{\mathrm{env}} < 0.5$ and as high environment when $n_{\mathrm{env}} > 3.0$. The SMFs use mass bins of 
@@
 method described in \cite{Moustakas:2013aa} Section 4.2 with the same
-redshift-dependent $K$-correction from observed SED and luminosity
+redshift-dependent $K$-correction from the observed SED and luminosity
 evolution model.
 
-To calculate the uncertainty of the SMFs from the sample variance, we use a standard jackknife technique (as done in \citealt{Moustakas:2013aa}).
+To calculate the uncertainty of the SMFs from the sample variance, we use a standard jackknife technique (following \citealt{Moustakas:2013aa}).
 For the PRIMUS galaxies, we calculate SMFs after excluding one of the five target fields at a time.
@@
 than in low density environments. The relationship between mass and
-environment observed in our SMFs reflect the well-established
+environment observed in our SMFs reflects the well-established
 mass-density relation and observed mass segregation with environment
@@
 While our mass complete subsample coupled with robust environment
-measurement allows us to compare SMF evolution for each of our
+measurements allows us to compare SMF evolution for each of our
 subsamples out to $z=0.8$, we caution readers regarding the
@@
 monotonically as a function of mass at all redshifts and
-environments. In other words, for all subsamples, galaxies in higher
-mass bins are more likely to have ended its star-formation.
+environments. In other words, for galaxies in all environments and at all redshifts, galaxies with higher
+masses are more likely to have ceased their star-formation.
 With the roughly linear correlation between galaxy SFR to galaxy color and morphology, we find that this trend reflects the well established color-mass and morphology-mass relations: more massive galaxies are more likely to be red or early-type (\citealt{blanton09a}).
@@
 range, $f_{\rm{Q}}$ at high density environment ranges from $\sim
-0.55$ to $\sim 0.9$. Evidently for our SDSS sample, $f_{\rm{Q}}$ in
+0.55$ to $\sim 0.9$. For our SDSS sample, $f_{\rm{Q}}$ in
 high density environments is notably higher.
@@
 f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.7) \sim 0.1$. This
-significant quiescent fraction evolution for low density environment
+significant quiescent fraction evolution for low density environments
 suggests that internal mechanisms, independent of environment, are
@@
 environments each increase by $\sim 0.1$ from at all redshifts we
-study. Evidently, increasing the fiducial mass to $10^{11}
+study. Increasing the fiducial mass to $10^{11}
 \mathcal{M}_{\odot}$ does not significantly alter the evolutionary
@@
 f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.7) \sim 0.1$ for
-low density environment as we listed earlier. In addition to the
+low density environment. In addition to the
 environment independent internal mechanisms that can explain the
-$f_{\rm{Q}}$ evolution at low density environments, there may be other
+$f_{\rm{Q}}$ evolution in low density environments, there may be other
 environment dependent mechanisms that can account for the moderate
@@
 In Figure \ref{fig:qffit_comp}, we plot  best-fit parameterization of
-$f_{\rm{red}}$ for high and low density environment from SDSS (panel a), \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross), zCOSMOS (panel b),
-\cite{Iovino:2010aa} (empty square) and \cite{Kovac:2014aa} (triangle), and \cite{Peng:2010aa} (filled square; panel c) from both surveys. From
+$f_{\rm{red}}$ for high and low density environment from SDSS (panel a), zCOSMOS (panel b), and \cite{Peng:2010aa} (filled square; panel c) from both surveys. From
+%$f_{\rm{red}}$ for high and low density environment from SDSS (panel a), \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross), zCOSMOS (panel b),
+%\cite{Iovino:2010aa} (empty square) and \cite{Kovac:2014aa} (triangle), and \cite{Peng:2010aa} (filled square; panel c) from both surveys. From
 \cite{Iovino:2010aa} we calculate $f_{\rm{red}} = 1-f_{\rm{blue}}$
@@
 evolutionary trends when the fiducial mass is changed suggest that
-$f_{\rm{Q}}$ evolution exhibit little mass dependence. In contrast to
+$f_{\rm{Q}}$ evolution exhibit little mass dependence within the 
+mass range probed in our analysis. In contrast to
 the weak mass dependence we observe in our results,
@@
 
-In Section \ref{sec:env_qf_evol}, we pointed out that $f_{\rm{Q}}$ in
+In Section \ref{sec:env_qf_evol}, we showed that $f_{\rm{Q}}$ in
 low density environments evolves over cosmic time. From this trend we
@@
 Our SDSS-{\em GALEX} sample covers $2,505 \;\rm{deg}^2$.
-More comparably, our PRIMUS sample covers $5.5 \;\rm{deg}^2$, which is over 3 times the sky coverage of zCOSMOS, $1.7 \;\rm{deg}^2$.
-With a significantly greater sky coverage our sample is less susceptible to cosmic variance.
+More comparably, our PRIMUS sample covers $5.5 \;\rm{deg}^2$, which is over 3 times the sky coverage of zCOSMOS ($1.7 \;\rm{deg}^2$).
+With a significantly greater sky coverage in five separate fields, our sample is less susceptible to cosmic variance.
 
@@
 specifically shed light on which mechanism (e.g. strangulation,
-ram-pressure stripping, etc.) occur in high density environments. In
-addition, the mechanism could yet be indirect; for example, the
-galaxies in higher density environments could yet end star-formation
+ram-pressure stripping, etc.) occur in high density environments. Not to 
+mention, the mechanism could yet be indirect; for example, the
+galaxies in higher density environments could end star-formation
 primarily due internal processes that affect the galaxies that end up
@@
 Support for this work was provided by ... 
-
+%"ALC acknowledges support from NSF CAREER award"
 something something, details details

### 2014-11-18 qfenv_paper/qf_environment.tex
primus group edits part 1
Partially address comments by Guangtun, Ramin, and Alison.
Updated most of the figures to new aperture size.

@@
 spectroscopic redshifts and multi-wavelength imaging data from the
-PRism MUlti-object Survey (PRIMUS) and the Sloan Digitial Sky Survey
+PRIsm MUlti-object Survey (PRIMUS) and the Sloan Digitial Sky Survey
 (SDSS). Our stellar mass limited galaxy sample consists of $\sim
@@
 as low or high density environments based on fixed cylindrical
-aperture environment measurements on a volume-limited Environment
-Defining Population (from PRIMUS and SDSS). For quiescent and
+aperture environment measurements on a volume-limited environment
+defining population (from PRIMUS and SDSS). For quiescent and
 star-forming galaxies in low or high density environments, we examine
@@
 surroundings, with a strong dependence of the quiescent fraction of
-galaxies on their local environment (e.g. \citealt{hubble36,
+galaxies on their local environment (e.g. \citealt{hubble36a,
 oemler74a, dressler80a, hermit96a, guzzo97a}; for a recent review see
@@
 PRIMUS with its $\sim 120,000$ spectroscopic redshifts provides a large data set at intermediate redshifts for our analysis.
-In addition, we anchor our analysis with a low redshift sample derived from the Sloan Digital Sky Survey (\cite{York:2000aa}).
+In addition, we anchor our analysis with a low redshift sample derived from the Sloan Digital Sky Survey (\citealt{York:2000aa}).
 
@@
 
-\subsection{Stellar Mass Complete Galaxy Sample} \label{sec:masscomp}
+\subsection{Stellar Mass Complete Galaxy Sample} \label{sec:target} 
 From the low redshift SDSS-{\em GALEX} and intermediate redshift
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Galaxy Sample} \label{sec:target} 
 \begin{figure*}
@@
 We define the environment of a galaxy as the number of neighboring Environment Defining Population galaxies (defined below) within a fixed aperture centered around it.
-We use a fixed aperture measurement of environment in order to probe environment on the halo scale, as \cite{Muldrew:2012aa} finds in their comparison of different environment definition using simulations.
+We use a fixed aperture measurement of environment to quantify environment with an aperture sufficiently large to encompass massive halos (\citealt{Muldrew:2012aa, Skibba:2013aa}).
+%We use a fixed aperture measurement of environment in order to probe environment on the halo scale, as \cite{Muldrew:2012aa} finds in their comparison of different environment definition using simulations.
 
@@
 errors and redshift space distortions (i.e. ``Finger of God"
-effect). \cite{Cooper:2005aa} finds that $\pm 1000 \; \rm{km} \;
-\rm{s^{-1}}$ optimally reduces the effects of redshift space
+effect). As \cite{Cooper:2005aa} and \cite{Gallazzi:2009aa} find, 
+$\pm 1000 \; \rm{km} \;\rm{s^{-1}}$ optimally reduces the effects of redshift space
 distortions. The PRIMUS redshift uncertainty at $z \sim 0.7$
@@
     \leavevmode
-    \epsfig{file=fig_smf_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_2envbin_lowenv0_5_highenv3_0_lit_primuszerr.eps, height=0.75\textwidth,angle=0}
+    \epsfig{file=fig_smf_cylr2_50000h35_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_2envbin_lowenv0_5_highenv3_0_lit_primuszerr.eps, height=0.75\textwidth,angle=90}
      \caption{Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) target galaxies in 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Stellar Mass Function} \label{sec:smf}
+\section{Results: Stellar Mass Function} \label{sec:smf}
 Our galaxy sample has so far been classified into quiescent or
@@
 \subsection{Stellar Mass Function Calculations} \label{sec:smfcalc} 
-To calculate the SMFs we employ a non-parametric $1/{V_{\rm{max}}}$ estimator commonly used for galaxy luminosity functions and stellar mass functions, as done in \cite{Moustakas:2013aa} and discussed in the review \cite{Johnston:2011aa}.
+To calculate the SMFs we employ a non-parametric $1/{V_{\rm{max}}}$ estimator commonly used for galaxy luminosity functions and stellar mass functions in order to account for Malmquist bias, as done in \cite{Moustakas:2013aa} and discussed in the review \cite{Johnston:2011aa}.
 The differential SMF is given by the following equation:
@@
 \begin{equation}
-\sigma^j = \sqrt{\frac{M-1}{M} \sum\limits_{k=1}^{M} (\Phi^j_k - \langle \Phi^j \rangle)^2}
+\sigma^j = \sqrt{\frac{N-1}{N} \sum\limits_{k=1}^{M} (\Phi^j_k - \langle \Phi^j \rangle)^2}
 \end{equation} 
-$M$ in this equation is the number of jack knife SMFs in the stellar mass bin.
-$\langle \Phi^j \rangle$ is the mean number density of galaxies in each stellar mass bin for all of the jack knife $\Phi^j$s.
+$N$ in this equation is the number of jackknife SMFs in the stellar mass bin.
+$\langle \Phi^j \rangle$ is the mean number density of galaxies in each stellar mass bin for all of the jackknife $\Phi^j$s.
 
@@
 mass and density, with SMFs in high density environments having more
-massive galaxies. We further confirm this trend when we compare the
+massive galaxies. We further confirm this trend w hen we compare the
 median mass between the two environments to find that the median mass
@@
         \leavevmode
-        \epsfig{file=fig_qf_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_lit_primuszerr.eps, height=0.75\textwidth,angle=90}
+        \epsfig{file=fig_qf_cylr2_50000h35_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_lit_primuszerr.eps, height=0.75\textwidth,angle=90}
         \caption{Evolution of the quiescent fraction $f_{\rm{Q}}$ for
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Quiescent Fraction} \label{sec:qf_const}
+\section{Results: Quiescent Fraction} \label{sec:qf_const}
 The SMFs calculated in the previous section illustrate the stellar
@@
 \begin{equation}
-f_{\rm{Q}} = \frac{\Phi_{Q}}{\Phi_{SF}+\Phi_{Q}}.
+f_{\rm{Q}} ( \mathcal{M}_{*}, z)= \frac{\Phi_{Q}}{\Phi_{SF}+\Phi_{Q}}.
 \end{equation}
@@
         \epsscale{1.0}
-        \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmasscomp11_0_10_5_lit_primuszerr.eps, height=0.45\textwidth}
+        \epsfig{file=fig_qffit_cylr2_50000h35_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmasscomp11_0_10_5_lit_primuszerr.eps, height=0.45\textwidth}
         \caption{The evolution of the quiescent fraction at fiducial
@@
         \epsscale{1.0}
-        \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmass10_5_lit_primuszerr_baldry_geha_iovino_kovac_peng_envthresh_kovacoffset.eps, height=\textwidth, angle=90}
+        \epsfig{file=fig_qffit_cylr2_50000h35_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmass10_5_lit_primuszerr_baldry_geha_iovino_kovac_peng_envthresh_kovacoffset.eps, height=\textwidth, angle=90}
         \caption{$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}}=10^{10.5} \mathcal{M}_\odot)$ evolution compared to $f_{\rm{red}}(\mathcal{M}_{*}=10^{10.5} \; \mathcal{M}_{\odot})$ in the literature: \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross) from SDSS (panel a), \cite{Iovino:2010aa} (empty square) and \cite{Kovac:2014aa} (triangle) from zCOSMOS (panel b), and \cite{Peng:2010aa} (filled square) from both SDSS and zCOSMOS (panel c).
@@
 In Figure \ref{fig:qffit_comp}, we plot  best-fit parameterization of
-$f_{\rm{red}}$ for high and low density environment from SDSS (panel a), zCOSMOS (panel b), and \cite{Peng:2010aa} (filled square; panel c) from both surveys. From
+$f_{\rm{red}}$ for high and low density environment from SDSS (panel a), zCOSMOS (panel b), and \cite{Peng:2010aa} (filled square; panel c) from both surveys. 
 %$f_{\rm{red}}$ for high and low density environment from SDSS (panel a), \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross), zCOSMOS (panel b),
 %\cite{Iovino:2010aa} (empty square) and \cite{Kovac:2014aa} (triangle), and \cite{Peng:2010aa} (filled square; panel c) from both surveys. From
-\cite{Iovino:2010aa} we calculate $f_{\rm{red}} = 1-f_{\rm{blue}}$
+From \cite{Iovino:2010aa} (empty square; panel b in Figure \ref{fig:qffit_comp}), we calculate $f_{\rm{red}} = 1-f_{\rm{blue}}$
 using the best-fit $f_{\rm{blue}}$ from the mass bin $\mathcal{M} =
-10^{10.3} - 10^{10.8} \mathcal{M}_{\odot}$. From \cite{Kovac:2014aa}
+10^{10.3} - 10^{10.8} \mathcal{M}_{\odot}$. From \cite{Kovac:2014aa} (triangle; panel b in Figure \ref{fig:qffit_comp})
 we plot an estimated $f_{\rm{Q}}$ by applying the residual between SFR
@@
 low ($\delta = 0.0$) and high density environments ($\delta =
-1.5$). Similarly, from \cite{Baldry:2006aa} we plot $f_{\rm{Q}}$
+1.5$). Similarly, from \cite{Baldry:2006aa} (diamond; panel a in Figure \ref{fig:qffit_comp}) we plot $f_{\rm{Q}}$
 derived from the best-fit $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5}
 \mathcal{M}_{\odot}$ for low ($\delta = 0.0$) and high density
-environment ($\delta = 1.0$). For \cite{geha12a}, we plot $f_{\rm{Q}}$
+environment ($\delta = 1.0$). For \cite{geha12a} (cross; panel a in Figure \ref{fig:qffit_comp}), we plot $f_{\rm{Q}}$
 for their isolated galaxy sample in their mass bin closest to $10^{10.5} \mathcal{M}_{\odot}$, $\mathcal{M} = 10^{10.55} \mathcal{M}_{\odot}$.
-Finally for \cite{Peng:2010aa}, we plot the parameterized $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ using the specified best-fit parameters in low ($\delta =0.0$) and high ($\delta = 1.4$) density environments.
+Finally for \cite{Peng:2010aa} (square; panel c in Figure \ref{fig:qffit_comp}), we plot the parameterized $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ using the specified best-fit parameters in low ($\delta =0.0$) and high ($\delta = 1.4$) density environments.
 
@@
 This disagreement persists even when we account for the galaxy classification discrepancies in Figure \ref{fig:qffit_comp}.
+Although the uncertainties for the parameterized $f_{\rm{Q}}$ are not shown in Figure \ref{fig:qffit_comp}, once they are accounted for, \cite{Kovac:2014aa} find that $f_{\rm{Q}}$ evolves insignificantly over cosmic time.
 
@@
 in Figure \ref{fig:qffit_comp} due to the galaxy classification
-correction we impose to the \cite{Kovac:2014aa} results. However, even
-without the correction (not shown), in their best-fit $f_{\rm{Q}}$
-results, the same evolutionary trends mentioned above are observed.
+correction we impose to the \cite{Kovac:2014aa} results.
+Furthermore, significant overdensities have been observed in the COSMOS field at $z \sim 0.35$ and $ z \sim 0.7$ that may further affect the zCOSMOS results (\citealt{Lilly:2009aa, Kovac:2010ab}).
+% Removed in order to tone down the criticism of 
+%However, even without the correction (not shown), in their best-fit $f_{\rm{Q}}$ results, the same evolutionary trends mentioned above are observed.
 
@@
 More comparably, our PRIMUS sample covers $5.5 \;\rm{deg}^2$, which is over 3 times the sky coverage of zCOSMOS ($1.7 \;\rm{deg}^2$).
-With a significantly greater sky coverage in five separate fields, our sample is less susceptible to cosmic variance.
+Moreover, our PRIMUS sample is constructed from five independent fields which allows us to reduce the effects of cosmic variance.
 

### 2014-11-18 qfenv_paper/qf_environment.tex
Figure edits

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
+\begin{figure}
   \begin{center}
     \leavevmode
-    \epsfig{file=fig_envcount_cylr2h25_thresh75_sdss_z0_05_0_12_primus_z0_21_0_lowenv0_5_highenv3_0_primuszerr_masslimit_edgecut_histogram.png, height=0.5\textwidth}
+    \epsfig{file=fig_envcount_cylr2_5h35_thresh75_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_primuszerr_masslimit_edgecut_histogram.png, width=0.45\textwidth}
     \caption{Normalized distribution of environment measurements ($n_{\rm{env}}$) for our mass complete galaxy sample within the edges.
+A fixed cylindrical aperture of $R_{\rm{ap}} =\apradius\;\rm{Mpc}$ and $H_{\rm{ap}} = \apheight\; \rm{Mpc}$ is used to measure environment.
+The star-forming galaxies contribution to the distribution is colored blue and diagonally patterned.
+The contribution from quiescent galaxies is colored in red.
+For each redshift panel, galaxies with $n_{\mathrm{env}} < 0.5$ are in low density environments and galaxies with $n_{\rm{env}} > 3.0$ are in high density environment.
+We note that the significant difference among the SDSS distribution and the PRIMUS distributions above is due to the different stellar mass completeness limits imposed on each redshift bin of our galaxy sample.}      \label{fig:envcount}
+     %\caption{Normalized distribution of environment measurements ($n_{\rm{env}}$) for our mass complete galaxy sample within the edges.
 The star-forming galaxies contribution to the distribution is colored blue and diagonally patterned.
@@
     \end{center}
-\end{figure*}
+\end{figure}
 

### 2014-11-19 qfenv_paper/qf_environment.tex
Minor EDP issue fixed
EDP Mr binsize reduced which caused minor adjustments in EDP. Tightened
SMF, but did nothing to QF.

@@
 Before we measure the environment for our galaxy sample, we first
-construct a volume limited Environment Defining Population (EDP) with
+construct a volume limited environment defining population (EDP) with
 absolute magnitude cut-offs ($M_{r}$) in redshift bins with $\Delta z

### 2014-11-21 qfenv_paper/qf_environment.tex
Chang Edits
- Included expected n_env statement in Environment Section
- Adjusted SMF discussion slightly, after SMF changes from new aperture
size.

--- 2014-11-18 qfenv_paper/qf_environment.tex
@@
 aperture environment measurements on a volume-limited environment
-defining population (from PRIMUS and SDSS). For quiescent and
+defining population. For quiescent and
 star-forming galaxies in low or high density environments, we examine
@@
 We define the environment of a galaxy as the number of neighboring Environment Defining Population galaxies (defined below) within a fixed aperture centered around it.
-We use a fixed aperture measurement of environment to quantify environment with an aperture sufficiently large to encompass massive halos (\citealt{Muldrew:2012aa, Skibba:2013aa}).
+We use fixed aperture measurements in order to quantify galaxy environment with an aperture sufficiently large to encompass massive halos (\citealt{Muldrew:2012aa, Skibba:2013aa}).
 %We use a fixed aperture measurement of environment in order to probe environment on the halo scale, as \cite{Muldrew:2012aa} finds in their comparison of different environment definition using simulations.
@@
 We conservatively choose $M_{r, \rm{lim}}(0.6 < z < 0.8)$ to be $M_{r} = -21.0$.
-Then for the lower redshift bins, we impose absolute magnitude limits ($M_{r,\rm{lim}}$) such that the cumulative number density, calculated with the galaxy statistical weights, of the bin ordered by $M_{r}$ is equal to the cumulative number density of the highest redshift bin at $M_{r, \rm{lim}}(0.6 < z < 0.8) = -21.0$.
+Then for the lower redshift bins, we impose absolute magnitude limits ($M_{r,\rm{lim}}$) such that the cumulative number density, calculated with the galaxy statistical weights, of the bin ordered by $M_{r}$ is equal to the cumulative number density of the highest redshift bin at $M_{r, \rm{lim}}(0.6 < z < 0.8) = -20.97$.
 
@@
 the cumulative number density of the highest redshift bin. For
-redshift bins $0.05-0.12$, $0.2-0.4$, $0.4-0.6$, $0.6-0.8$ we get
-$M_{r,\rm{lim}} = -20.90$, $-21.06$, $-21.10$ and $-20.98$,
+redshift bins $z = 0.05-0.12$, $0.2-0.4$, $0.4-0.6$, $0.6-0.8$ we get
+$M_{r,\rm{lim}} = -20.95$, $-21.03$, $-20.98$ and $-20.97$,
 respectively. These absolute magnitude limits are illustrated in
@@
 it. $n_{\rm{env}}$ accounts for the statistical weights of the EDP
-galaxies. Once we obtain environment measurements for all the galaxies
+galaxies. 
+For our galaxy sample, the expected $n_{\rm{env}}$ given the constant number density in 
+each of our EDP redshift bin and volume of our cylindrical aperture is $< n_{\rm{env}} > = 1.3$. 
+Once we obtain environment measurements for all the galaxies
 in our galaxy sample, we classify galaxies with $n_{\rm{env}} < 0.5$
@@
 At lower masses ($\mathcal{M} < 10^{10.5} \mathcal{M}_{\odot}$) we observe no noticeable trend in the SMF.
-In panel (b), star-forming galaxies in high density environments, we notice a possible decrease above the knee of the SMF ($\mathcal{M} \sim 10^{10.7} \mathcal{M}_{\odot}$) accompanied by an increase below the knee.
-For the quiescent population in low density environment, shown in panel (c) of Figure \ref{fig:smf}, we do not notice any clear SMF evolution throughout the mass range.
+In panel (b), star-forming galaxies in high density environments, we do not observe any clear trends above the knee of the SMF ($\mathcal{M} \sim 10^{10.7} \mathcal{M}_{\odot}$) but an increase in SMF below the knee.
+For the quiescent population in low density environment, shown in panel (c) of Figure \ref{fig:smf}, we observe a potential decrease at high masses ($\mathcal{M} > 10^{10.7} \mathcal{M}_{\odot}$).
 Lastly for the quiescent population in high density environments, panel (d), we find significant increase in $\Phi$ for lower masses but no notable trend at higher masses.
+%do not notice any clear SMF evolution throughout the mass range.
 
@@
 mass and density, with SMFs in high density environments having more
-massive galaxies. We further confirm this trend w hen we compare the
+massive galaxies, especially evident in our lowest redshift bin. 
+We further confirm this trend when we compare the
+%massive galaxies. We further confirm this trend w hen we compare the
 median mass between the two environments to find that the median mass

### 2014-11-21 qfenv_paper/qf_environment.tex
Thorough edit part 1

@@
 field found in studies of the morphology-density relation
-(\citealt{dressler84a, desai07a}).  Clearly understanding the
+(\citealt{dressler84a, Fasano:2000aa, Smith:2005aa, desai07a}).  Clearly understanding the
 properties of galaxies in the present-day universe requires a careful
@@
 (\citealt{cooper08a, patel09a, kovac10a}).
+% Mention something about the build up of the red sequence?
 
@@
 of sufficiently large samples. In this paper, we apply this approach
-using the Prism Multi-object Survey (PRIMUS; \citealt{Coil:2011aa},
+using the PRIism MUlti-object Survey (PRIMUS; \citealt{Coil:2011aa},
 \citealt{Cool:2013aa}), the largest available redshift survey covering
@@
 the evolution of the quiescent fraction over the redshift range $0 < z < 1$.
-For our analysis, we require a sample with sufficient depth and high quality spectroscopic redshift to probe the redshift range and to measure galaxy environment.
+For our analysis, we require a sample with sufficient depth and high quality spectroscopic redshift to probe the redshift range and to robustly measure galaxy environment.
 PRIMUS with its $\sim 120,000$ spectroscopic redshifts provides a large data set at intermediate redshifts for our analysis.
@@
 brief summary of the PRIMUS data and the SDSS data used for our sample
-selection.  In Section \ref{sec:sfq}, we classify our sample galaxies
-as quiescent or star-forming.  In Section \ref{sec:target} we define
-our stellar mass complete galaxy sample.  We calculate the environment
+selection. In Section \ref{sec:target} we define our stellar mass complete galaxy sample.  
+Then, in Section \ref{sec:sfq}, we classify our sample galaxies as quiescent or star-forming. 
+We calculate the environment
 using a volume-limited Environment Defining Population in Section
@@
 \cite{Moustakas:2013aa} provides detailed descriptions of integrated flux calculations in the photometric bands for each of our fields.
+Furthermore, we derive the {\em K-corrections} from the photometry using \texttt{K-correct} (v4.2; \citealt{Blanton:2007aa}).
 
@@
 We now classify our mass complete galaxy sample into quiescent or star-forming using an evolving cut based on specific star-formation rate utilized in \cite{Moustakas:2013aa} Section 3.2.
-This classification method uses the star-forming (SF) sequence, which is the correlation between star-formation rate (SFR) and stellar mass in star-forming galaxies observed at least until $z \sim 2$ (\citealt{Noeske:2007aa, Karim:2011aa}).
+This classification method uses the star-forming (SF) sequence, which is the correlation between star-formation rate (SFR) and stellar mass in star-forming galaxies observed at least until $z \sim 2$ (\citealt{Noeske:2007aa, Williams:2009aa, Karim:2011aa}).
 The PRIMUS sample displays a well-defined SF sequence within the redshift range of our galaxy sample.
 Using the power-law slope for the SF sequence from \cite{Salim:2007aa} (SFR $\propto \mathcal{M}^{0.65}$) and the minimum of the quiescent/star-forming bimodality, determined empirically, we obtain the following equation to classify the target galaxies (Equation 2 in \citealt{Moustakas:2013aa}):
-\begin{equation}
+\begin{equation} \label{eq:qsfclass} 
 \rm{log}(\rm{SFR}_{\rm{min}}) = -0.49 + 0.64 \rm{log}(\mathcal{M} - 10) +1.07(z-0.1), 
-\end{equation} \label{eq:qsfclass} 
+\end{equation} 
 where $\mathcal{M}$ is the stellar mass of the galaxy.

### 2014-11-24 qfenv_paper/qf_environment.tex
Chang edits
Updated figures, tables, and texts. Everything except intro!

@@
 ChangHoon~Hahn\altaffilmark{1}, 
-Michael~Blanton\altaffilmark{1}, 
-John Moustakas\altaffilmark{2},
-Alison~Coil\altaffilmark{3}, 
-Richard~Cool\altaffilmark{4}, 
-Daniel Eisenstein\altaffilmark{5},
-Ken Wong\altaffilmark{6}, 
-Guangtun Zhu\altaffilmark{7}
+Michael R.~Blanton\altaffilmark{1}, 
+John~Moustakas\altaffilmark{2},
+Alison L.~Coil\altaffilmark{3}, 
+Richard J.~Cool\altaffilmark{4}, 
+Daniel J.~Eisenstein\altaffilmark{5},
+Kenneth C.~Wong\altaffilmark{6}, 
+Guangtun~Zhu\altaffilmark{7}
 }
@@
     & & Quiescent & Star-Forming & Quiescent & Star-Forming &  \\ \hline 
-$0.05 < z < 0.12$ & $n_{\rm{env}} < \lowenvthresh $ & 4969 & 5943 & $10^{10.2} \mathcal{M}_{\odot}$ & $10^{10.2} \mathcal{M}_{\odot}$ & -20.98 \\
-               & $n_{\rm{env}} > \highenvthresh $ &17488 & 12244 &                          \\ 
-                              & all          &$33968$                       & $30058$                          \\ \hline
-$0.2 < z < 0.4$      &$n_{\rm{env}} < \lowenvthresh $           &282                    &1020 & $10^{9.8} \mathcal{M}_{\odot}$ & $10^{9.8} \mathcal{M}_{\odot}$ &-21.10 \\
-               &$n_{\rm{env}} > \highenvthresh $            &410                    &850                           \\
-               & all                & $995$                      & $2628$                          \\ \hline
-$0.4 < z < 0.6$      &$n_{\rm{env}} < \lowenvthresh $           &426                       &1226 & $10^{10.3} \mathcal{M}_{\odot}$ & $10^{10.3} \mathcal{M}_{\odot}$ & -21.06 \\
-               &$n_{\rm{env}} > \highenvthresh $            &543                       &983                           \\
-               & all               & $1462$                      & $3334$                          \\ \hline
-$0.6 < z < 0.8$      &$n_{\rm{env}} < \lowenvthresh $           &389                       &932  & $10^{10.7} \mathcal{M}_{\odot}$ & $10^{10.6} \mathcal{M}_{\odot}$ & -20.90 \\
-               &$n_{\rm{env}} > \highenvthresh $            &642                       &907                           \\
-               & all              & $1590$                      & $2852$                          \\ \hline
-Total &      & \multicolumn{2}{c}{76887} & \\ \hline
+$0.05 < z < 0.12$ & $n_{\rm{env}} < \lowenvthresh $ & 6533 & 7508 & $10^{10.2} \mathcal{M}_{\odot}$ & $10^{10.2} \mathcal{M}_{\odot}$ & -20.95 \\
+               & $n_{\rm{env}} > \highenvthresh $ &14673 & 9717 &                          \\ 
+                              & all          &$33553$                       & $29864$                          \\ \hline
+$0.2 < z < 0.4$      &$n_{\rm{env}} < \lowenvthresh $           &363                    &1231 & $10^{9.8} \mathcal{M}_{\odot}$ & $10^{9.8} \mathcal{M}_{\odot}$ &-21.03 \\
+               &$n_{\rm{env}} > \highenvthresh $            &379                    &756                           \\
+               & all                & $1086$                      & $2879$                          \\ \hline
+$0.4 < z < 0.6$      &$n_{\rm{env}} < \lowenvthresh $           &536                       &1498 & $10^{10.3} \mathcal{M}_{\odot}$ & $10^{10.3} \mathcal{M}_{\odot}$ & -20.98 \\
+               &$n_{\rm{env}} > \highenvthresh $            &490                       &854                           \\
+               & all               & $1560$                      & $3577$                          \\ \hline
+$0.6 < z < 0.8$      &$n_{\rm{env}} < \lowenvthresh $           &567                       &1254  & $10^{10.7} \mathcal{M}_{\odot}$ & $10^{10.6} \mathcal{M}_{\odot}$ & -20.97 \\
+               &$n_{\rm{env}} > \highenvthresh $            &498                       &671                           \\
+               & all              & $1668$                      & $2964$                          \\ \hline
+Total &      & \multicolumn{2}{c}{77151} & \\ \hline
   \multicolumn{4}{l}{}                                             \\       
@@
     {\bf Notes}: Number of galaxies ($N_{\rm{gal}}$) in the mass complete subsamples within the edges of the survey (Section \ref{sec:sample}).
-The subsamples are classified based on environment $n_{\rm{env}}$ and star formation rate (star-forming or quiescent).
+The subsamples are classified based on environment ($n_{\rm{env}}$) and star formation rate (star-forming or quiescent).
 The lowest redshift bin is derived from SDSS; the rest are from PRIMUS.
-We also list the stellar mass completeness limit $\mathcal{M}_{\rm{lim}}$ for our sample and the $r$-band absolute magnitude limits $M_{\rm{r}, lim}$ for the Environment Defining Population.
+We also list the stellar mass completeness limit, $\mathcal{M}_{\rm{lim}}$, for our sample along with the $r$-band absolute magnitude limits, $M_{\rm{r}, lim}$, for the Environment Defining Population.
     \bigskip
@@
 We use the same procedure as \cite{Moustakas:2013aa}, which follows \cite{Pozzetti:2010aa}, to empircally determine the stellar mass completeness limits.
-For each of the target galaxies we compute $\mathcal{M}_{\rm{lim}}$ using $\log \; \mathcal{M}_{\mathrm{lim}} = \log \; \mathcal{M} + 0.4 (m - m_{\mathrm{lim}})$, where $\mathcal{M}$ is the stellar mass of the galaxy in $\mathcal{M_{\odot}}$, $\mathcal{M}_{\rm{lim}}$ is the stellar mass of each galaxy if its magnitude was equal to the survey magnitude limit, $m$ is the observed apparent magnitude in the selection band, and $m_{\rm{lim}}$ is the magnitude limit for our five fields.
+For each of the target galaxies we compute $\mathcal{M}_{\rm{lim}}$ using $\log \; \mathcal{M}_{\mathrm{lim}} = \log \; \mathcal{M} + 0.4\;(m - m_{\mathrm{lim}})$, where $\mathcal{M}$ is the stellar mass of the galaxy in $\mathcal{M_{\odot}}$, $\mathcal{M}_{\rm{lim}}$ is the stellar mass of each galaxy if its magnitude was equal to the survey magnitude limit, $m$ is the observed apparent magnitude in the selection band, and $m_{\rm{lim}}$ is the magnitude limit for our five fields.
 We construct a cumulative distribution of $\mathcal{M}_{\rm{lim}}$ for the $15\%$ faintest galaxies in $\Delta z=0.04$ bins.
@@
 redshift by randomly sampling a Gaussian distribution with standard
-deviation $\sigma = 0.005 (1+z_{\rm{SDSS}-GALEX})$, where
-$z_{\rm{SDSS}-GALEX}$ is the redshift of the galaxy.
+deviation $\sigma = 0.005 (1+z_{\mathrm{SDSS}-GALEX})$, where
+$z_{\mathrm{SDSS}-GALEX}$ is the redshift of the galaxy.
 
@@
     \epsfig{file=fig_envcount_cylr2_5h35_thresh75_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_primuszerr_masslimit_edgecut_histogram.png, width=0.45\textwidth}
-    \caption{Normalized distribution of environment measurements ($n_{\rm{env}}$) for our mass complete galaxy sample within the edges.
+    \caption{Normalized distribution of environment measurements ($n_{\rm{env}}$) for our mass complete galaxy sample within the survey edges.
 A fixed cylindrical aperture of $R_{\rm{ap}} =\apradius\;\rm{Mpc}$ and $H_{\rm{ap}} = \apheight\; \rm{Mpc}$ is used to measure environment.
-The star-forming galaxies contribution to the distribution is colored blue and diagonally patterned.
+The star-forming galaxies contribution to the distribution is colored in blue and diagonally patterned.
 The contribution from quiescent galaxies is colored in red.
-For each redshift panel, galaxies with $n_{\mathrm{env}} < 0.5$ are in low density environments and galaxies with $n_{\rm{env}} > 3.0$ are in high density environment.
+Galaxies with $n_{\mathrm{env}} < 0.5$ are in low density environments and galaxies with $n_{\rm{env}} > 3.0$ are in high density environment.
 We note that the significant difference among the SDSS distribution and the PRIMUS distributions above is due to the different stellar mass completeness limits imposed on each redshift bin of our galaxy sample.}      \label{fig:envcount}
@@
 We again restrict the PRIMUS galaxies to $0.2 < z < 0.8$ and divide them into bins of $\Delta z = 0.2$.
-Before we consider the cumulative number densities in the redshift bins, we first determine the $M_r$ limit for the highest redshift bin ($0.6-0.8$) by examining the $M_{r}$ distribution with bin size $\Delta M_{r} = 0.25$ and select $M_{r,\rm{lim}}$ near the peak of the distribution where bins with $M_{r} > M_{r,\rm{lim}}$ have fewer galaxies than the bin at $M_{r, \rm{lim}}$.
-We conservatively choose $M_{r, \rm{lim}}(0.6 < z < 0.8)$ to be $M_{r} = -21.0$.
-Then for the lower redshift bins, we impose absolute magnitude limits ($M_{r,\rm{lim}}$) such that the cumulative number density, calculated with the galaxy statistical weights, of the bin ordered by $M_{r}$ is equal to the cumulative number density of the highest redshift bin at $M_{r, \rm{lim}}(0.6 < z < 0.8) = -20.97$.
+Before we consider the cumulative number densities in the redshift bins, we first determine the $M_r$ limit for the highest redshift bin ($z = 0.6-0.8$) by examining the $M_{r}$ distribution with bin size $\Delta M_{r} = 0.25$ and select $M_{r,\rm{lim}}$ near the peak of the distribution where bins with $M_{r} > M_{r,\rm{lim}}$ have fewer galaxies than the bin at $M_{r, \rm{lim}}$.
+We conservatively choose $M_{r, \rm{lim}}(0.6 < z < 0.8)$ to be $M_{r} = -20.97$.
+Then for the lower redshift bins, we impose absolute magnitude limits ($M_{r,\rm{lim}}$) such that the cumulative number density, calculated with the galaxy statistical weights, of the bin ordered by $M_{r}$ is equal to the cumulative number density of the highest redshift bin with $M_{r, \rm{lim}}(0.6 < z < 0.8) = -20.97$.
 
@@
 values are not necessary for the EDP, we extend the parent data of the
-SDSS EDP to the entire NYU VAGC, including galaxies outside of the
+SDSS EDP to the entire NYU-VAGC, including galaxies outside of the
 {\em GALEX} window function. Furthermore, we impose a redshift range
@@
 $M_{r}$ distribution versus redshift for the EDP on top
-of the target galaxy sample.
+of our galaxy sample.
 
@@
 Finally, we measure the environment for each galaxy in our galaxy
-sample by counting the number of EDP galaxies, $n_{\rm{env}}$ with RA,
+sample by counting the number of EDP galaxies, $n_{\rm{env}}$, with RA,
 Dec, and $z$ within our cylindrical aperture centered around
@@
 galaxies. 
-For our galaxy sample, the expected $n_{\rm{env}}$ given the constant number density in 
-each of our EDP redshift bin and volume of our cylindrical aperture is $< n_{\rm{env}} > = 1.3$. 
+For our galaxy sample, the expected $n_{\rm{env}}$ given the uniform number density in 
+each of our EDP redshift bin and volume of our cylindrical aperture is $\langle n_{\rm{env}} \rangle = 1.3$. 
 Once we obtain environment measurements for all the galaxies
 in our galaxy sample, we classify galaxies with $n_{\rm{env}} < 0.5$
-to be ``low" environment density and galaxies with $n_{\rm{env}} > 3$
-to be ``high" environment densities. The high environment cutoff was
+to be in ``low" environment densities and galaxies with $n_{\rm{env}} > 3$
+to be in ``high" environment densities. The high environment cutoff was
 selected in order to reduce contamination from galaxies in low
@@
 \;\rm{Mpc}$ to measure environment. The same analysis was
-extended for varying aperture dimensions $R_{\rm{ap}} = 1.5, \apradius, 3.0 \:
-\rm{Mpc}$ and $H_{\rm{ap}} = \apheight, 70 \;\rm{Mpc}$. We also
-adjusted the environment classification thresholds for these
-analyses. The results obtained from using different apertures and
-environment classification thresholds are qualitatively consistent with the results presented below.
+extended for varying aperture dimensions $R_{\rm{ap}} = 1.5, \: \apradius, \:3.0 \:
+\rm{Mpc}$ and $H_{\rm{ap}} = \apheight, \; 70 \;\rm{Mpc}$ with adjusted environment classifications. 
+The results obtained from using different apertures and
+environment classifications are qualitatively consistent with the results presented below.
 
@@
 For $R_{\rm{ap}}= \apradius \;\rm{Mpc}$, $f_{\rm{thresh}} = 0.75$.
-If $n_{i, \rm{ransack}}$ is greater than $<n_{\rm{ransack}}>_i$ then galaxy $i$ remains in our sample; otherwise, it is discarded.
-
+If $n_{i, \rm{ransack}} > \langle n_{\rm{ransack}} \rangle_i$ then galaxy $i$ remains in our sample; otherwise, it is discarded.
 Once the edge effect cuts are applied, we are left with the final galaxy sample.
-In Figure \ref{fig:envcount} we present the distribution of environment measurements ($n_{\rm{env}}$) for our final galaxy sample in redshift bins: $0.05 - 0.12$, $0.2 - 0.4$, $0.4-0.6$, and $0.6-0.8$.
+For our SDSS-{\em GALEX} galaxy sample, $\sim 12 \%$ of galaxies are removed from the edge effect cuts.
+For our PRIMUS galaxy sample, $\sim 40 \%$ of galaxies are removed from the edge effect cuts.
+
+In Figure \ref{fig:envcount} we present the distribution of environment measurements ($n_{\rm{env}}$) for our final galaxy sample in redshift bins: $z = 0.05 - 0.12$, $0.2 - 0.4$, $0.4-0.6$, and $0.6-0.8$.
 The quiescent galaxy contributions are colored in red while the star-forming galaxy contributions are colored in blue and patterned.
-The low and high density environment classifications are represented by black vertical lines that divide the distribution at $n_{\rm{env}} = 0.5$ and $n_{\rm{env}} = 3.5$.
-The percentage of the total galaxies in the redshift bin that are in these environment densities are labeled on the figure.
-
-Although we imposed PRIMUS redshift errors on our SDSS galaxies in order to consistently measure environment throughout our entire sample, we note a significant discrepancy between the SDSS and PRIMUS samples in the fractional contribution of each environment classification within the redshift bin.
-For each of the PRIMUS redshift bins, approximately $50 \%$ of galaxies in the redshift bin are in low density environments and roughly $30 \%$ are in high density environments.
-In contrast, in the SDSS redshift bin, $38 \%$ of galaxies in the redshift bin are in low density environments and $45 \%$ are in high density environments.
-We remind the reader that this is due to the different mass-completeness limits imposed on our galaxy sample for each redshift bins and does not affect our results.
+We classify galaxies with $n_{\mathrm{env}} < 0.5$ to be in low density environments and galaxies with $n_{\mathrm{env}} > 3.0$ to be in high density environments.
+
+Although we imposed PRIMUS redshift errors on our SDSS galaxies in order to consistently measure environment throughout our entire sample, we note a significant discrepancy between the $n_{\mathrm{env}}$ distributions of the SDSS and PRIMUS samples.
+For example, in each of the PRIMUS redshift bins, $\sim 40 \%$ of galaxies in the redshift bin are in low density environments and roughly $30 \%$ are in high density environments.
+In contrast, in the SDSS redshift bin, $\sim 20 \%$ of galaxies in the redshift bin are in low density environments and $\sim 35 \%$ are in high density environments.
+We remind the reader that this is mainly due to the varying stellar mass-completeness limits imposed on our galaxy sample for each redshift bins and does not affect our results.
 \begin{figure*}
@@
     \epsfig{file=fig_smf_cylr2_50000h35_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_2envbin_lowenv0_5_highenv3_0_lit_primuszerr.eps, height=0.75\textwidth,angle=90}
-     \caption{Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) target galaxies in 
-low (left) and high (right) environments in the redshift range
+     \caption{Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) galaxies in 
+low (left) and high (right) density environments throughout the redshift range
 $z=0$--$0.8$. The environment of each galaxy  
@@
 the survey. However in Section \ref{sec:edgeeffect} we remove galaxies
-that lie on the edge from our sample. In doing so we reduce the
+that lie on the survey edges from our sample. In doing so, we reduce the
 maximum cosmological volume where a galaxy can be observed, thereby
@@
 in the sample. We introduce the term $V_{\rm{max,avail},i}$ to express
-the maximum volume accounting for these survey edge effects.
+the maximum volume accounting for the survey edge effects.
 
@@
 confused with the \texttt{ransack} sample in Section
-\ref{sec:edgeeffect}. We apply the edge effect cutoffs on these random
+\ref{sec:edgeeffect}. We apply the edge effect cuts on these random
 points as we did for our galaxy sample using the same method as in
@@
 0.01$, we calculate the fraction of the random points that remain in
-the bin after the edge effect cutoffs over the total number of random
+the bin after the edge effect cuts over the total number of random
 points in the bin: $f_{\rm{edge}}$. We then apply this factor to
@@
 The redshift evolution of the SMFs in each of these panels are indicated by a darker shade for lower redshift bins.
-The width of the SMFs represent the sample variance uncertainties.
+The width of the SMFs represent the sample variance uncertainties derived in Section \ref{sec:smfcalc}.
 
 While a detailed comparison of the SMFs in each panel for different
-epochs is complicated due to the different stellar mass completeness limits, we present some notable trends in each panel.
-In panel (a), star-forming galaxies in low density environments, we find a significant decrease in the high mass end of the SMF ($\mathcal{M} > 10^{10.75} \mathcal{M}_{\odot}$).
-At lower masses ($\mathcal{M} < 10^{10.5} \mathcal{M}_{\odot}$) we observe no noticeable trend in the SMF.
+epochs is complicated by the different stellar mass completeness limits, we present some notable trends in each panel.
+In panel (a), star-forming galaxies in low density environments, we find a significant decrease in the high mass end of the SMF ($\mathcal{M} > 10^{10.75} \mathcal{M}_{\odot}$) over cosmic time.
+Meanwhile at lower masses ($\mathcal{M} < 10^{10.5} \mathcal{M}_{\odot}$), we observe no noticeable trend in the SMF.
 In panel (b), star-forming galaxies in high density environments, we do not observe any clear trends above the knee of the SMF ($\mathcal{M} \sim 10^{10.7} \mathcal{M}_{\odot}$) but an increase in SMF below the knee.
-For the quiescent population in low density environment, shown in panel (c) of Figure \ref{fig:smf}, we observe a potential decrease at high masses ($\mathcal{M} > 10^{10.7} \mathcal{M}_{\odot}$).
-Lastly for the quiescent population in high density environments, panel (d), we find significant increase in $\Phi$ for lower masses but no notable trend at higher masses.
+For the quiescent population in low density environment, panel (c), we observe a potential decrease at high masses ($\mathcal{M} > 10^{10.7} \mathcal{M}_{\odot}$).
+Lastly for the quiescent population in high density environments, panel (d), we find significant increase in $\Phi$ for lower masses but little trend at higher masses.
 %do not notice any clear SMF evolution throughout the mass range.
@@
 Overall, we find that the trends we note in the SMF evolution above are in good agreement with \cite{bundy06a} and \cite{Bolzonella:2010aa}.
+
+\begin{figure*}
+    \begin{center}
+        \leavevmode
+        \epsfig{file=fig_qf_cylr2_50000h35_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_lit_primuszerr.eps, height=0.75\textwidth,angle=90}
+        \caption{Evolution of the quiescent fraction $f_{\rm{Q}}$ for
+          galaxies in low (left) and high (right) density
+          environments for $z < 0.8$. $f_{\rm{Q}}$s were calculated
+          using the SMFs in Figure \ref{fig:smf}, as described in Section \ref{sec:qfevol}.
+Darker shading indicates lower redshift and the width represents the standard jackknife uncertainty.}         \label{fig:qf}
+    \end{center}
+\end{figure*}
 
@@
 
-\begin{figure*}
-    \begin{center}
-        \leavevmode
-        \epsfig{file=fig_qf_cylr2_50000h35_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_lit_primuszerr.eps, height=0.75\textwidth,angle=90}
-        \caption{Evolution of the quiescent fraction $f_{\rm{Q}}$ for
-          galaxies in low (left) and high (right) density
-          environments for $z < 0.8$. $f_{\rm{Q}}$s were calculated
-          using the SMFs in Figure \ref{fig:smf}, as described in text. Darker shading indicates lower redshift and the width represents the standard jackknife uncertainty.}         \label{fig:qf}
-    \end{center}
-\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 monotonically as a function of mass at all redshifts and
-environments. In other words, for galaxies in all environments and at all redshifts, galaxies with higher
+environments. In other words, for galaxies in any environment and at all redshifts, galaxies with higher
 masses are more likely to have ceased their star-formation.
@@
 bin, we find that $f_{\rm{Q}}$ at low density environments ranges from
-$\sim 0.4$ to $\sim 0.8$ for $10^{10.2} \mathcal{M}_{\odot} <
+$\sim 0.4$ to $\sim 0.9$ for $10^{10.2} \mathcal{M}_{\odot} <
 \mathcal{M}_{*} < 10^{11.5} \mathcal{M}_{\odot}$. Over the same mass
@@
 
-For our PRIMUS sample at $z \sim 0.3$, over $10^{9.5} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11} \mathcal{M}_{\odot}$ $f_{\rm{Q}}$ ranges from $\sim 0.15$ to $\sim 0.55$ for low density environment, while at high density environment $f_{\rm{Q}}$ ranges from $\sim 0.2$ to $\sim 0.7$.
-Similarly, at $z \sim 0.5$, over $10^{10} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11.2} \mathcal{M}_{\odot}$ $f_{\rm{Q}}$ ranges from $\sim 0.25$ to $\sim 0.55$ for low density environment and $f_{\rm{Q}}$ ranges from $\sim 0.3$ to $\sim 0.7$.
-Finally in our highest redshift bin $z \sim 0.7$, over the mass range $10^{10.5} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11.5} \mathcal{M}_{\odot}$, $f_{\rm{Q}}$ ranges from $\sim 0.3$ to $\sim 0.55$ for low density and $\sim 0.45$ to $\sim 0.8$ for high density.
+For our PRIMUS sample at $z \sim 0.3$, over $10^{9.5} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11} \mathcal{M}_{\odot}$ $f_{\rm{Q}}$ ranges from $\sim 0.2$ to $\sim 0.6$ for low density environment, while at high density environment $f_{\rm{Q}}$ ranges from $\sim 0.2$ to $\sim 0.8$.
+Similarly, at $z \sim 0.5$, over $10^{10} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11.2} \mathcal{M}_{\odot}$ $f_{\rm{Q}}$ ranges from $\sim 0.3$ to $\sim 0.6$ for low density environment and $f_{\rm{Q}}$ ranges from $\sim 0.3$ to $\sim 0.7$.
+Finally in our highest redshift bin $z \sim 0.7$, over the mass range $10^{10.5} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11.5} \mathcal{M}_{\odot}$, $f_{\rm{Q}}$ ranges from $\sim 0.35$ to $\sim 0.6$ for low density and $\sim 0.45$ to $\sim 0.8$ for high density.
 For the entire redshift range of our sample, $f_{\rm{Q}}$ in high density environment is higher than $f_{\rm{Q}}$ in low density environments.
@@
 environments, since the difference is observed from our highest
-redshift bin it is not necessarily a result of environment dependent
+redshift bin, it is not necessarily a result of environment dependent
 mechanisms for ending star formation. In order to isolate any
@@
     $z_1 < z < z_2$ &Environment        &a  &b  \\ \hline 
-$0.05 < z< 0.12$ &$n_{\rm{env}} < \lowenvthresh$ & $0.392 \pm 0.020$ & $0.482 \pm 0.006$ \\
-               &$n_{\rm{env}} > \highenvthresh$ & $0.289 \pm 0.015$ & $0.605 \pm 0.008$ \\ 
+$0.05 < z< 0.12$ &$n_{\rm{env}} < \lowenvthresh$ & $0.410 \pm 0.018$ & $0.469 \pm 0.007$ \\
+               &$n_{\rm{env}} > \highenvthresh$ & $0.270 \pm 0.016$ & $0.620 \pm 0.008$ \\ 
                               &               &                       &                           \\ \hline   
-$0.2 < z <0.4$ & $n_{\rm{env}} < \lowenvthresh$ & $0.289 \pm 0.039$ & $0.395 \pm 0.016$ \\
-               &$n_{\rm{env}} > \highenvthresh$ & $0.383 \pm 0.016$ & $0.504 \pm 0.010$ \\
+$0.2 < z <0.4$ & $n_{\rm{env}} < \lowenvthresh$ & $0.340 \pm 0.032$ & $0.432 \pm 0.015$ \\
+               &$n_{\rm{env}} > \highenvthresh$ & $0.432 \pm 0.018$ & $0.544 \pm 0.010$ \\
                &               &                       &                           \\ \hline
-$0.4 < z < 0.6$      &$n_{\rm{env}} < \lowenvthresh$ & $0.248 \pm 0.042$ & $0.374 \pm 0.018$ \\
-               &$n_{\rm{env}} > \highenvthresh$ & $0.317 \pm 0.034$ & $0.435 \pm 0.013$ \\
+$0.4 < z < 0.6$      &$n_{\rm{env}} < \lowenvthresh$ & $0.263 \pm 0.038$ & $0.381 \pm 0.018$ \\
+               &$n_{\rm{env}} > \highenvthresh$ & $0.289 \pm 0.018$ & $0.446 \pm 0.013$ \\
                &               &                       &                           \\ \hline
-$0.6 < z < 0.8$      &$n_{\rm{env}} < \lowenvthresh$ & $0.267 \pm 0.058$ & $0.343 \pm 0.025$ \\
-               &$n_{\rm{env}} > \highenvthresh$            & $0.412 \pm 0.023$ & $0.457 \pm 0.018$ \\
+$0.6 < z < 0.8$      &$n_{\rm{env}} < \lowenvthresh$ & $0.284 \pm 0.036$ & $0.352 \pm 0.019$ \\
+               &$n_{\rm{env}} > \highenvthresh$            & $0.468 \pm 0.065$ & $0.429 \pm 0.023$ \\
                &               &                       &                           \\ \hline
@@
 10^{11}\mathcal{M}_{\odot})$ for both low and high density
-environments each increase by $\sim 0.1$ from at all redshifts we
+environments each increase by $\sim 0.2$ from at all redshifts we
 study. Increasing the fiducial mass to $10^{11}
@@
 \ref{fig:qffit_comp} more stringent high density environment
-classifications, extending the cut off to $n_{\mathrm{env}} > 6$ and
-$9$ (specified in the top right legend and represented by the color of
+classifications, extending the cut off to $n_{\mathrm{env}} > 5$ and
+$7$ (specified in the top right legend and represented by the color of
 the shading). Aside from the increase in uncertainties that accompany
@@
 3$ cut-off, there is a notable difference in $f_{\mathrm{Q}}$
-evolution between our highest cut-off $n_{\rm{env}} > 9$ and our low
+evolution between our highest cut-off $n_{\rm{env}} > 7$ and our low
 density environment. $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z
 \sim 0.1) - f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.7)
-\sim 0.2$ for $n_{\rm{env}} > 9$ versus
+\sim 0.25$ for $n_{\rm{env}} > 7$ versus
 $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.1) -
@@
 
+\def \iovinopanel {b}
+\def \kovacpanel {c}
+\def \pengpanel {d}
 \begin{figure*}
@@
         \epsscale{1.0}
-        \epsfig{file=fig_qffit_cylr2_50000h35_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmass10_5_lit_primuszerr_baldry_geha_iovino_kovac_peng_envthresh_kovacoffset.eps, height=\textwidth, angle=90}
-        \caption{$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}}=10^{10.5} \mathcal{M}_\odot)$ evolution compared to $f_{\rm{red}}(\mathcal{M}_{*}=10^{10.5} \; \mathcal{M}_{\odot})$ in the literature: \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross) from SDSS (panel a), \cite{Iovino:2010aa} (empty square) and \cite{Kovac:2014aa} (triangle) from zCOSMOS (panel b), and \cite{Peng:2010aa} (filled square) from both SDSS and zCOSMOS (panel c).
+        \epsfig{file=fig_qffit_cylr2_50000h35_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmass10_5_lit_primuszerr_baldry_geha_iovino_kovac_peng_envthresh_kovacoffset_4panel.eps, height=\textwidth, angle=90}
+        \caption{$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}}=10^{10.5} \mathcal{M}_\odot)$ evolution compared to $f_{\rm{red}}(\mathcal{M}_{*}=10^{10.5} \; \mathcal{M}_{\odot})$ in the literature: \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross) from SDSS (panel a), \cite{Iovino:2010aa} (empty square; panel \iovinopanel) and \cite{Kovac:2014aa} (triangle; panel \kovacpanel) from zCOSMOS, and \cite{Peng:2010aa} (filled square) from both SDSS and zCOSMOS (panel \pengpanel).
 The $f_{\rm{red}}$ values from \cite{Iovino:2010aa}, \cite{Kovac:2014aa}, \cite{Baldry:2006aa}, and \cite{Peng:2010aa} are calculated from the best-fit parameterizations presented in the respective works.
@@
 In Figure \ref{fig:qffit_comp}, we plot  best-fit parameterization of
-$f_{\rm{red}}$ for high and low density environment from SDSS (panel a), zCOSMOS (panel b), and \cite{Peng:2010aa} (filled square; panel c) from both surveys. 
+$f_{\rm{red}}$ for high and low density environment from SDSS (panel a), zCOSMOS (panel \iovinopanel$ $ and \kovacpanel), and \cite{Peng:2010aa} (filled square; panel d) from both surveys. 
 %$f_{\rm{red}}$ for high and low density environment from SDSS (panel a), \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross), zCOSMOS (panel b),
 %\cite{Iovino:2010aa} (empty square) and \cite{Kovac:2014aa} (triangle), and \cite{Peng:2010aa} (filled square; panel c) from both surveys. From
-From \cite{Iovino:2010aa} (empty square; panel b in Figure \ref{fig:qffit_comp}), we calculate $f_{\rm{red}} = 1-f_{\rm{blue}}$
+From \cite{Iovino:2010aa} (empty square; panel \iovinopanel$ $ in Figure \ref{fig:qffit_comp}), we calculate $f_{\rm{red}} = 1-f_{\rm{blue}}$
 using the best-fit $f_{\rm{blue}}$ from the mass bin $\mathcal{M} =
-10^{10.3} - 10^{10.8} \mathcal{M}_{\odot}$. From \cite{Kovac:2014aa} (triangle; panel b in Figure \ref{fig:qffit_comp})
+10^{10.3} - 10^{10.8} \mathcal{M}_{\odot}$. From \cite{Kovac:2014aa} (triangle; panel \kovacpanel$ $ in Figure \ref{fig:qffit_comp})
 we plot an estimated $f_{\rm{Q}}$ by applying the residual between SFR
@@
 for their isolated galaxy sample in their mass bin closest to $10^{10.5} \mathcal{M}_{\odot}$, $\mathcal{M} = 10^{10.55} \mathcal{M}_{\odot}$.
-Finally for \cite{Peng:2010aa} (square; panel c in Figure \ref{fig:qffit_comp}), we plot the parameterized $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ using the specified best-fit parameters in low ($\delta =0.0$) and high ($\delta = 1.4$) density environments.
+Finally for \cite{Peng:2010aa} (square; panel \pengpanel$ $ in Figure \ref{fig:qffit_comp}), we plot the parameterized $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ using their best-fit parameters for low ($\delta =0.0$) and high ($\delta = 1.4$) density environments.
 
@@
 \cite{Kovac:2014aa} points out that there is a significant difference
-between classifying the quiescent population using color and SFR.
-For their lower redshift bin ($0.1 < z < 0.4$) they find that their $f_{\rm{Q}}$ defined by color is greater than $f_{\rm{Q}}$ defined by SFR by roughly $0.2$.
+between classifying the quiescent population using color and SFR due to dust-reddening in star-forming galaxies.
+For their lower redshift bin ($0.1 < z < 0.4$) \cite{Kovac:2014aa} find that their $f_{\rm{Q}}$ defined by color is greater than $f_{\rm{Q}}$ defined by SFR by roughly $0.2$.
 While for their higher redshift bin ($0.4 < z < 0.7$) they find a difference of $0.15-0.19$.
 Although \cite{Kovac:2014aa} does not elaborate on how the galaxy classification discrepancy applies to the different environments, if we simply account for the difference uniformly for $f_{\rm{red}}$ at all environments, the \cite{Kovac:2014aa} results in their lower redshift bin are roughly consistent with our $f_{\rm{Q}}$ at high and low density environments.
-However, in their higher redshift bin even accounting for the difference in galaxy classification, \cite{Kovac:2014aa} finds a significantly higher $f_{\rm{Q}}$.
+Even accounting for the dust-reddening of $f_{\rm{red}}$, \cite{Kovac:2014aa} finds a significantly higher $f_{\rm{Q}}$ in their higher redshift bin.
 
@@
 isolated galaxies. In fact at their highest mass bin ($10^{10.9} -
-10^{11.4} \mathcal{M}_{\odot}$, \cite{Iovino:2010aa} find no evolution
+10^{11.4} \mathcal{M}_{\odot}$), \cite{Iovino:2010aa} find no evolution
 for both environments: constant $f_{\mathrm{blue}} \sim 0.1$ over $z =
@@
 group galaxies and by $\sim 0.3$ from $z=0.55$ to $0.3$ for isolated
-galaxies as presented in Figure \ref{fig:qffit_comp}. Altogether, with
+galaxies as presented in panel (\iovinopanel) of Figure \ref{fig:qffit_comp}. Altogether, with
 mass bins beyond the fiducial masses we explore, \cite{Iovino:2010aa}
@@
 from \cite{Cucciati:2010aa} and \cite{Kovac:2014aa}. As illustrated in
-Figure \ref{fig:qffit_comp}, both \cite{Cucciati:2010aa} and
-\cite{Kovac:2014aa} find $f_{\rm{Q}}$ in high density environment
+panel (\kovacpanel) of Figure \ref{fig:qffit_comp}, \cite{Kovac:2014aa} finds $f_{\rm{Q}}$ in high density environment
 significantly greater than $f_{\rm{Q}}$ at low density
@@
 (\citealt{Cucciati:2010aa, Cooper:2010aa}) and is not consistent with
-the color-density relation begin merely a reflection of the
+the color-density relation being merely a reflection of the
 mass-density relationship, as \cite{Scodeggio:2009aa} suggest it is
@@
 to ending star-formation in galaxy evolution. \cite{Iovino:2010aa}
-from zCOSMOS, plotted in Figure \ref{fig:qffit_comp}, also find that
+from zCOSMOS, plotted in Figure \ref{fig:qffit_comp}  panel (\iovinopanel), also find that
 $f_{\rm{Q}}$ in low density environment increases with decreasing redshift.
 On the other hand \cite{Kovac:2014aa}, also from zCOSMOS, presents that $f_{\rm{Q}}$ in low density environment decreases over cosmic time.
-This disagreement persists even when we account for the galaxy classification discrepancies in Figure \ref{fig:qffit_comp}.
-Although the uncertainties for the parameterized $f_{\rm{Q}}$ are not shown in Figure \ref{fig:qffit_comp}, once they are accounted for, \cite{Kovac:2014aa} find that $f_{\rm{Q}}$ evolves insignificantly over cosmic time.
+While the uncertainties for the parameterized $f_{\rm{Q}}$ are not listed, and thus not shown in Figure \ref{fig:qffit_comp}, once they are accounted for, \cite{Kovac:2014aa} find little $f_{\rm{Q}}$ evolution over cosmic time.
+However, once we account for the dust-reddening of the $f_{\rm{red}}$, we find a more significant decrease over cosmic time (Figure \ref{fig:qffit_comp} panel \kovacpanel).
 
@@
 slopes of the $f_{\rm{Q}}$ evolution in both environments are enhanced
-in Figure \ref{fig:qffit_comp} due to the galaxy classification
-correction we impose to the \cite{Kovac:2014aa} results.
-Furthermore, significant overdensities have been observed in the COSMOS field at $z \sim 0.35$ and $ z \sim 0.7$ that may further affect the zCOSMOS results (\citealt{Lilly:2009aa, Kovac:2010ab}).
+in Figure \ref{fig:qffit_comp} due to the dust-reddening
+correction we impose to the \cite{Kovac:2014aa} $f_{\mathrm{red}}$ results.
+
 % Removed in order to tone down the criticism of 
@@
 
-While the zCOSMOS survey provides more precise spectroscopic redshifts than PRIMUS, our sample provides a significantly larger statistics.
+While the zCOSMOS survey provides more precise spectroscopic redshifts than PRIMUS, our sample provides significantly larger statistics.
 In addition, our sample covers a larger portion of the sky.
@@
 More comparably, our PRIMUS sample covers $5.5 \;\rm{deg}^2$, which is over 3 times the sky coverage of zCOSMOS ($1.7 \;\rm{deg}^2$).
-Moreover, our PRIMUS sample is constructed from five independent fields which allows us to reduce the effects of cosmic variance.
+Furthermore, our PRIMUS sample is constructed from five independent fields which allows us to significantly reduce the effects of cosmic variance.
 
 As listed in Table \ref{tab:subsample}, after our edge effect cuts and
-stellar mass completeness limits, our sample consists of $12,861$
-galaxies from PRIMUS over $0.2< z< 0.8$ and $64,026$ galaxies from
+stellar mass completeness limits, our sample consists of $13,734$
+galaxies from PRIMUS over $0.2< z< 0.8$ and $63,417$ galaxies from
 SDSS over $0.05 < z < 0.12$. Meanwhile, \cite{Iovino:2010aa} has $914$
@@
 the use of different methodologies, particularly for galaxy
-classification and environment measurements, make the comparisons
+classification and environment measurements, make such comparisons
 ambiguous. On the other hand, the discrepancies in the $f_{\rm{Q}}$
@@
 0.7$). Although their sample is smaller than the PRIMUS sample, which
-contains over two times the number of galaxies, the
+contains over twice times the number of galaxies, the
 \cite{Kovac:2014aa} sample provides a more stable comparison.  Once
-their results are adjusted for the different galaxy classification, we
+their results are adjusted for the dust-reddening, we
 find that their overall $f_{\rm{Q}}$ is more or less consistent with
@@
 significant discrepancies in the $f_{\rm{Q}}$ evolutionary trends.
+The significant overdenities observed in the COSMOS field at $z \sim 0.35$ and $z \sim 0.7$ (\citealt{Lilly:2009aa, Kovac:2010ab}) may have a significant effect on the zCOSMOS results and offer a possible explanation for the discrepancies.
 % zCOSMOS has more precise redshift but PRIMUS has it beat in terms of sample size and coverage of the sky 5.5 deg^2 vs 1.7 deg^2
@@
 \begin{enumerate}
-% NOT SURE WHAT THIS ONE WAS SAYING:
-% \item By measuring the SMF evolution for each of our subsamples, we
-%    approximately trace the evolutionary tracks our galaxy population
-%    tracing the tracks of mechanisms for ending star formation and
-%    galaxies infalling into high density environments.
 	\item From the SMFs, we find that the galaxy population in high
@@
     in the highest density environments. For our purest high
-    environment sample ($n_{\rm{env}} > 9$), the total $f_{\rm{Q}}$
+    environment sample ($n_{\rm{env}} > 7$), the total $f_{\rm{Q}}$
     evolution is $\sim 0.1$ greater than the total $f_{\rm{Q}}$
@@
 contribute to the end of star-formation. Our results do not
-specifically shed light on which mechanism (e.g. strangulation,
+specifically shed light on which mechanisms (e.g. strangulation,
 ram-pressure stripping, etc.) occur in high density environments. Not to 
@@
 galaxies in higher density environments could end star-formation
-primarily due internal processes that affect the galaxies that end up
+primarily due internal processes, which affect the galaxies that end up
 in groups and clusters more greatly.  Nevertheless, our results impose
@@
 \bigskip 
-We thank people ...
-
-Support for this work was provided by ... 
-%"ALC acknowledges support from NSF CAREER award"
-something something, details details
-
-The SDSS is managed by the Astrophysical Research Con- sortium for the Participating Institutions.
-The Participating In- stitutions are the American Museum of Natural History, As- trophysical Institute Potsdam, University of Basel, University of Cambridge, Case Western Reserve University, University of Chicago, Drexel University, Fermilab, the Institute for Ad- vanced Study, the Japan Participation Group, Johns Hopkins University, the Joint Institute for Nuclear Astrophysics, the Kavli Institute for Particle Astrophysics and Cosmology, the Korean Scientist Group, the Chinese Academy of Sciences (LAMOST), Los Alamos National Laboratory, the Max-Planck- Institute for Astronomy (MPIA), the Max-Planck-Institute for Astrophysics (MPA), New Mexico State University, Ohio State University, University of Pittsburgh, University of Portsmouth, Princeton University, the United States Naval Observatory, and the University of Washington.
+We thank Ramin Skibba for feedback on the manuscript. We gratefully acknowledge insightful conversations with Katarina Kova\u{c} and Ying-Jie Peng. 
+We also thank Marla Geha for providing published quiescent fraction results in electronic format.
+
+Support for this work was provided by .... ALC acknowledges support from NSF CAREER award
+
+The SDSS is managed by the Astrophysical Research Consortium for the Participating Institutions.
+The Participating Institutions are the American Museum of Natural History, Astrophysical Institute Potsdam, University of Basel, University of Cambridge, Case Western Reserve University, University of Chicago, Drexel University, Fermilab, the Institute for Advanced Study, the Japan Participation Group, Johns Hopkins University, the Joint Institute for Nuclear Astrophysics, the Kavli Institute for Particle Astrophysics and Cosmology, the Korean Scientist Group, the Chinese Academy of Sciences (LAMOST), Los Alamos National Laboratory, the Max-Planck- Institute for Astronomy (MPIA), the Max-Planck-Institute for Astrophysics (MPA), New Mexico State University, Ohio State University, University of Pittsburgh, University of Portsmouth, Princeton University, the United States Naval Observatory, and the University of Washington.
 %

### 2014-11-27 qfenv_paper/qf_environment.tex
Included Ramin in author list

@@
 Daniel J.~Eisenstein\altaffilmark{5},
+Ramin A.~Skibba\altaffilmark{3}
 Kenneth C.~Wong\altaffilmark{6}, 
@@
 that time the galaxy population has continued to evolve, but less
-dramatically. Although there are detectable changes in the population,
+dramatically.
+
+Although there are detectable changes in the population,
 the major classes of galaxies existed at $z\sim 1$, in roughly the
@@
 \bigskip 
-We thank Ramin Skibba for feedback on the manuscript. We gratefully acknowledge insightful conversations with Katarina Kova\u{c} and Ying-Jie Peng. 
+We gratefully acknowledge insightful conversations with Katarina Kova\u{c} and Ying-Jie Peng. 
 We also thank Marla Geha for providing published quiescent fraction results in electronic format.

### 2014-12-08 qfenv_paper/qf_environment.tex
Re-drafted intro (Incomplete)

@@
 \section{Introduction}
-Galaxies, in their detailed properties, carry the imprints of their
-surroundings, with a strong dependence of the quiescent fraction of
-galaxies on their local environment (e.g. \citealt{hubble36a,
-oemler74a, dressler80a, hermit96a, guzzo97a}; for a recent review see
-\citealt{blanton09a}).  The strength of this dependence is itself a
-strongly decreasing function of galaxy stellar mass; at the extreme,
-the lowest mass ($<10^{9}$ $M_\odot$) galaxies end their
-star formation only in
-dense regions, and never in isolation (\citealt{geha12a}).  These
-effects vary with redshift at least in the densest clusters, as
-observed in the changing fraction of late-type spirals relative to the
-field found in studies of the morphology-density relation
-(\citealt{dressler84a, Fasano:2000aa, Smith:2005aa, desai07a}).  Clearly understanding the
-properties of galaxies in the present-day universe requires a careful
-investigation of the role of environment, and how that role changes
-over time.
-
-Nevertheless, the evolution of the role of environment is a relatively
-subtle effect and difficult to study.  Although the history of galaxies
-prior to $z\sim 1$ appears to have been one of rapid assembly, since
-that time the galaxy population has continued to evolve, but less
-dramatically.
-
-Although there are detectable changes in the population,
-the major classes of galaxies existed at $z\sim 1$, in roughly the
-same relative numbers as today (\citealt{bundy06a, borch06a,
-taylor09a, Moustakas:2013aa}). Furthermore, at those redshifts we can also
-detect the dependence of galaxy properties on environment, with lower
-star-formation rate early-type galaxies populating the denser regions
-(\citealt{cooper08a, patel09a, kovac10a}).
-% Mention something about the build up of the red sequence?
-
-The most dramatic change in galaxy properties during the past eight
-billion years has been a remarkable decline in the star-formation rate
-of galaxies in the Universe (\citealt{hopkins06a}).  This decline
-appears dominated by decreases in the rates of star-formation of
-individual galaxies (\citealt{Noeske:2007aa}). There is evidence that
-a large fraction of the decline is associated with strongly
-infrared-emitting starbursts (\citealt{bell05a, magnelli09a}).  The
-decline does not appear to be due to a complete cessation of star
-formation for a large fraction of the star-forming population, as
-reflected in observations of the stellar mass function of quiescent
-and star-forming galaxies (\citealt{Blanton:2006aa, bundy06a,
-  borch06a, Moustakas:2013aa}).  These findings leave little room for
-the participation of environmentally-driven cessation of star
-formation in the global census of star-formation.  As \cite{cooper08a}
-and others have pointed out, because the environmental dependence of
-total star-formation rates at fixed redshift is relatively small,
-environmentally effects are unlikely to cause the overall
-star-formation rate decline.
-
-Thus, the impact of environment on galaxy formation has to be
-interpreted on top of the background of this overall decline affecting
-galaxies in all environments. The most straightforward investigation
-would be to directly determine the star-forming properties of galaxies
+Galaxies, in their detailed properties, carry the imprints of their surroundings, with a strong dependence of the quiescent fraction of galaxies on their local environment (e.g.
+\citealt{hubble36a, oemler74a, dressler80a, hermit96a, guzzo97a}; for a recent review see \citealt{blanton09a}).
+The strength of this dependence is itself a strongly decreasing function of galaxy stellar mass; at the extreme, the lowest mass ($<10^{9}$ $M_\odot$) galaxies end their star formation only in dense regions, and never in isolation (\citealt{geha12a}).
+These effects vary with redshift at least in the densest clusters, as observed in the changing fraction of late-type spirals relative to the field found in studies of the morphology-density relation (\citealt{dressler84a, Fasano:2000aa, Smith:2005aa, desai07a}).
+Clearly understanding the properties of galaxies in the present-day universe requires a careful investigation of the role of environment, and how that role changes over time.
+
+%Moreover, at $z < 1$ lower star-formation rate early-type galaxies are found populating the denser regions (\citealt{cooper08a, patel09a, kovac10a}).
+
+Nevertheless, the evolution of the role of environment is a relatively subtle effect and must be interpreted on top of the changes in overall the galaxy population.
+For instance, the most dramatic change in galaxy properties during the past eight billion years has been the remarkable decline in the star-formation rate of galaxies in the Universe (\citealt{hopkins06a}).
+This decline appears dominated by decreases in the rates of star-formation of individual galaxies (\citealt{Noeske:2007aa}).
+There is evidence that a large fraction of the decline is associated with strongly infrared-emitting starbursts (\citealt{bell05a, magnelli09a}).
+As \cite{cooper08a} and others have pointed out, because the environmental dependence of total star-formation rates at fixed redshift is relatively small, environmentally effects are unlikely to cause the overall star-formation rate decline.
+
+Furthermore, during this universal decline, the major classes of galaxies that have existed at $z \sim 1$ remain firmly in place since (\citealt{bundy06a, borch06a, taylor09a, Moustakas:2013aa}).
+Although these classes have remained roughly the same relative number during this time, detailed observations of the stellar mass function find detectable changes in the quiescent and star-forming galaxy populations.
+There is a significant decline in the number density of massive/luminous star-forming galaxies accompanied by an increase in the number density of quiescent galaxies (\citealt{Bell:2004aa, Blanton:2006aa, bundy06a,  borch06a, Moustakas:2013aa}).
+The evolution of these two populations suggest a build up of the quiescent population caused by the cessation of star formation for some star-forming galaxies over time.
+
+Of the numerous mechanisms that have been proposed to explain this cessation, some suggest that star-formation is quenched due to internal processes such as supernovae or active galactic nuclei that suppresses cold gas accretion (CITECITE).
+Other models suggest that environment dependent external processes such as ram-pressure stripping (CITE), strangulation (CITE), or harassment (CITE) contribute to the cessation.
+While discrepancies persist between these theoretical models and observations, many of the environment dependent processes have found observational support (CITECITE) suggesting that environment may play a role in ceasing star-formation.
+
+%Nevertheless, the evolution of the role of environment is a relatively subtle effect and difficult to study.
+Although the history of galaxies prior to $z\sim 1$ appears to have been one of rapid assembly, since that time the galaxy population has continued to evolve, but less dramatically.
+Although there are detectable changes in the population, the major classes of galaxies existed at $z\sim 1$, in roughly the same relative numbers as today (\citealt{bundy06a, borch06a, taylor09a, Moustakas:2013aa}).
+Furthermore, at those redshifts we can also detect the dependence of galaxy properties on environment, with lower star-formation rate early-type galaxies populating the denser regions (\citealt{cooper08a, patel09a, kovac10a}).
+
+%The most dramatic change in galaxy properties during the past eight billion years has been a remarkable decline in the star-formation rate of galaxies in the Universe (\citealt{hopkins06a}).
+This decline  appears dominated by decreases in the rates of star-formation of individual galaxies (\citealt{Noeske:2007aa}).
+There is evidence that a large fraction of the decline is associated with strongly infrared-emitting starbursts (\citealt{bell05a, magnelli09a}).
+The decline does not appear to be due to a complete cessation of star formation for a large fraction of the star-forming population, as reflected in observations of the stellar mass function of quiescent and star-forming galaxies (\citealt{Blanton:2006aa, bundy06a,   borch06a, Moustakas:2013aa}).
+These findings leave little room for the participation of environmentally-driven cessation of star formation in the global census of star-formation.
+As \cite{cooper08a} and others have pointed out, because the environmental dependence of total star-formation rates at fixed redshift is relatively small, environmentally effects are unlikely to cause the overall star-formation rate decline.
+
+%Thus, the impact of environment on galaxy formation has to be interpreted on top of the background of the build up of the red sequence during the overall decline in star-formation rate affecting galaxies in all environments.
+The most straightforward investigation would be to directly determine the star-forming properties of galaxies as a function of environment, stellar mass and redshift in a single, consistently analyzed data set.
+
+In this paper we take the most straightforward investigation
+by directly determining the star-forming properties of galaxies
 as a function of environment, stellar mass and redshift in a single,

### 2014-12-10 qfenv_paper/qf_environment.tex
Intro draft
Significant changes to intro

@@
 The strength of this dependence is itself a strongly decreasing function of galaxy stellar mass; at the extreme, the lowest mass ($<10^{9}$ $M_\odot$) galaxies end their star formation only in dense regions, and never in isolation (\citealt{geha12a}).
-These effects vary with redshift at least in the densest clusters, as observed in the changing fraction of late-type spirals relative to the field found in studies of the morphology-density relation (\citealt{dressler84a, Fasano:2000aa, Smith:2005aa, desai07a}).
+These effects also vary with redshift at least in the densest clusters, as observed in the changing fraction of late-type spirals relative to the field, found in studies of the morphology-density relation (\citealt{dressler84a, Fasano:2000aa, Smith:2005aa, desai07a}).
 Clearly understanding the properties of galaxies in the present-day universe requires a careful investigation of the role of environment, and how that role changes over time.
@@
 
-Nevertheless, the evolution of the role of environment is a relatively subtle effect and must be interpreted on top of the changes in overall the galaxy population.
+Nevertheless, the evolution of the role of environment is a relatively subtle effect and must be interpreted within the context of the evolving galaxy population.
 For instance, the most dramatic change in galaxy properties during the past eight billion years has been the remarkable decline in the star-formation rate of galaxies in the Universe (\citealt{hopkins06a}).
@@
 There is evidence that a large fraction of the decline is associated with strongly infrared-emitting starbursts (\citealt{bell05a, magnelli09a}).
-As \cite{cooper08a} and others have pointed out, because the environmental dependence of total star-formation rates at fixed redshift is relatively small, environmentally effects are unlikely to cause the overall star-formation rate decline.
-
-Furthermore, during this universal decline, the major classes of galaxies that have existed at $z \sim 1$ remain firmly in place since (\citealt{bundy06a, borch06a, taylor09a, Moustakas:2013aa}).
-Although these classes have remained roughly the same relative number during this time, detailed observations of the stellar mass function find detectable changes in the quiescent and star-forming galaxy populations.
-There is a significant decline in the number density of massive/luminous star-forming galaxies accompanied by an increase in the number density of quiescent galaxies (\citealt{Bell:2004aa, Blanton:2006aa, bundy06a,  borch06a, Moustakas:2013aa}).
-The evolution of these two populations suggest a build up of the quiescent population caused by the cessation of star formation for some star-forming galaxies over time.
-
-Of the numerous mechanisms that have been proposed to explain this cessation, some suggest that star-formation is quenched due to internal processes such as supernovae or active galactic nuclei that suppresses cold gas accretion (CITECITE).
-Other models suggest that environment dependent external processes such as ram-pressure stripping (CITE), strangulation (CITE), or harassment (CITE) contribute to the cessation.
-While discrepancies persist between these theoretical models and observations, many of the environment dependent processes have found observational support (CITECITE) suggesting that environment may play a role in ceasing star-formation.
+As \cite{cooper08a} and others have pointed out, because the environmental dependence of total star-formation rates at fixed redshift is relatively small, environmental effects are unlikely to cause the overall star-formation rate decline.
+
+During this period, the major classes of galaxies that we observe today have already been firmly in place (\citealt{bundy06a, borch06a, taylor09a, Moustakas:2013aa}).
+Though not as dramatic as the history of galaxies prior to $z \sim 1$, detailed observations of the stellar mass function find significant evolution of the quiescent and star-forming galaxy populations.
+Since $z \sim 1$, the significant decline in the number density of massive/luminous star-forming galaxies is accompanied by an increase in the number density of quiescent galaxies  (\citealt{Blanton:2006aa, bundy06a,  borch06a, Moustakas:2013aa}).
+On the color-magnitude diagram, this corresponds to the doubling of the red sequence over this period (\citealt{Bell:2004aa, borch06a, Faber:2007aa}).
+The correspondence of these changes in the galaxy population suggest the existence of a mechanism that causes the cessation of star-formation in star-forming galaxies.
+
+Of the numerous mechanisms that have been proposed to explain this cessation, favored models suggest that internal processes such as supernovae or active galactic nuclei heat the gas within the galaxy, which consequently suppress the cold gas supply used for star-formation (\citealt{Keres:2005aa, Croton:2006aa, Dekel:2008aa}).
+Other models propose that environment dependent external processes such as ram-pressure stripping (\citealt{Gunn:1972aa, Bekki:2009aa}), strangulation (\citealt{Larson:1980aa, Balogh:2000aa}), or harassment (\citealt{Moore:1998aa}) contribute to the cessation.
+Many of these proposed processes have received observational support.
+\cite{Weinmann:2006aa} and \cite{Peng:2010aa}, for example, credit internal processes for quenching star-formation, especially in massive galaxies.
+Similarly, a number of observations support the existence of environment dependent external processes (\citealt{Iovino:2010aa, geha12a, Kovac:2014aa}).
+\cite{Peng:2010aa} and others further argue that internal and external processes both contribute to the cessation of star-formation with internal processes more dominant in massive galaxies and external processes dominating the less massive regime.
+While discrepancies persist between theoretical models and observations, a large number of observations suggest that environment plays a significant role in ceasing star-formation.
 
@@
 %The most dramatic change in galaxy properties during the past eight billion years has been a remarkable decline in the star-formation rate of galaxies in the Universe (\citealt{hopkins06a}).
-This decline  appears dominated by decreases in the rates of star-formation of individual galaxies (\citealt{Noeske:2007aa}).
+This decline  appears dominated by decreases in the rates of star-formation of individual galaxi es (\citealt{Noeske:2007aa}).
 There is evidence that a large fraction of the decline is associated with strongly infrared-emitting starbursts (\citealt{bell05a, magnelli09a}).

### 2014-12-10 qfenv_paper/qf_environment.tex
Intro slightly reworded

@@
 During this period, the major classes of galaxies that we observe today have already been firmly in place (\citealt{bundy06a, borch06a, taylor09a, Moustakas:2013aa}).
-Though not as dramatic as the history of galaxies prior to $z \sim 1$, detailed observations of the stellar mass function find significant evolution of the quiescent and star-forming galaxy populations.
-Since $z \sim 1$, the significant decline in the number density of massive/luminous star-forming galaxies is accompanied by an increase in the number density of quiescent galaxies  (\citealt{Blanton:2006aa, bundy06a,  borch06a, Moustakas:2013aa}).
+Though not as dramatic as the history of galaxies prior to $z \sim 1$, detailed observations of the stellar mass function find significant evolution of the galaxy population with the decline in the number density of massive star-forming galaxies accompanied by an increase in the number density of quiescent galaxies (\citealt{Blanton:2006aa, bundy06a,  borch06a, Moustakas:2013aa}).
 On the color-magnitude diagram, this corresponds to the doubling of the red sequence over this period (\citealt{Bell:2004aa, borch06a, Faber:2007aa}).
-The correspondence of these changes in the galaxy population suggest the existence of a mechanism that causes the cessation of star-formation in star-forming galaxies.
-
-Of the numerous mechanisms that have been proposed to explain this cessation, favored models suggest that internal processes such as supernovae or active galactic nuclei heat the gas within the galaxy, which consequently suppress the cold gas supply used for star-formation (\citealt{Keres:2005aa, Croton:2006aa, Dekel:2008aa}).
+These changes in galaxy population are likely a result of physical processes that cause the cessation of star-formation in star-forming galaxies.
+
+Of the numerous mechanisms that have been proposed to explain this cessation, favored models suggest that internal processes such as supernovae or active galactic nuclei heat the gas within the galaxy, which consequently suppresses the cold gas supply used for star-formation (\citealt{Keres:2005aa, Croton:2006aa, Dekel:2008aa}).
 Other models propose that environment dependent external processes such as ram-pressure stripping (\citealt{Gunn:1972aa, Bekki:2009aa}), strangulation (\citealt{Larson:1980aa, Balogh:2000aa}), or harassment (\citealt{Moore:1998aa}) contribute to the cessation.

### 2014-12-12 qfenv_paper/qf_environment.tex
Iovino error bars removed
Text appropriately corrected for panel change.

@@
 \def \iovinopanel {b}
-\def \kovacpanel {c}
-\def \pengpanel {d}
+\def \kovacpanel {b}
+\def \pengpanel {c}
 \begin{figure*}
@@
         \epsscale{1.0}
-        \epsfig{file=fig_qffit_cylr2_50000h35_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmass10_5_lit_primuszerr_baldry_geha_iovino_kovac_peng_envthresh_kovacoffset_4panel.eps, height=\textwidth, angle=90}
-        \caption{$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}}=10^{10.5} \mathcal{M}_\odot)$ evolution compared to $f_{\rm{red}}(\mathcal{M}_{*}=10^{10.5} \; \mathcal{M}_{\odot})$ in the literature: \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross) from SDSS (panel a), \cite{Iovino:2010aa} (empty square; panel \iovinopanel) and \cite{Kovac:2014aa} (triangle; panel \kovacpanel) from zCOSMOS, and \cite{Peng:2010aa} (filled square) from both SDSS and zCOSMOS (panel \pengpanel).
+        \epsfig{file=fig_qffit_cylr2_50000h35_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmass10_5_lit_primuszerr_baldry_geha_iovino_kovac_peng_envthresh_kovacoffset.eps, height=\textwidth, angle=90}
+        \caption{$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}}=10^{10.5} \mathcal{M}_\odot)$ evolution compared to $f_{\rm{red}}(\mathcal{M}_{*}=10^{10.5} \; \mathcal{M}_{\odot})$ in the literature: \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross) from SDSS (panel a), \cite{Iovino:2010aa} (empty square; panel \iovinopanel) and \cite{Kovac:2014aa} (triangle; panel \kovacpanel) from zCOSMOS, and \cite{Peng:2010aa} from both SDSS and zCOSMOS (panel \pengpanel).
 The $f_{\rm{red}}$ values from \cite{Iovino:2010aa}, \cite{Kovac:2014aa}, \cite{Baldry:2006aa}, and \cite{Peng:2010aa} are calculated from the best-fit parameterizations presented in the respective works.
@@
 High density environment is represented in red and low density environment is represented in blue.
+The uncertainties in the \cite{Iovino:2010aa} best-fit $f_{\rm{red}}$ is omitted due to insufficient information on the cross correlation terms of the fit parameters.
 For \cite{Kovac:2014aa} we apply the offset between the color-based and SFR-based galaxy classification in order to plot the $f_{\rm{Q}}$ estimates.
@@
 In Figure \ref{fig:qffit_comp}, we plot  best-fit parameterization of
-$f_{\rm{red}}$ for high and low density environment from SDSS (panel a), zCOSMOS (panel \iovinopanel$ $ and \kovacpanel), and \cite{Peng:2010aa} (filled square; panel d) from both surveys. 
+$f_{\rm{red}}$ for high and low density environment from SDSS (panel a), zCOSMOS (panel \iovinopanel), and \cite{Peng:2010aa} (filled square; panel d) from both surveys. 
 %$f_{\rm{red}}$ for high and low density environment from SDSS (panel a), \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross), zCOSMOS (panel b),

### 2014-12-18 qfenv_paper/qf_environment.tex
Chang Intro Edit
included numbers from moustakas+2013
and expanded further on internal/external

@@
 Though not as dramatic as the history of galaxies prior to $z \sim 1$, detailed observations of the stellar mass function find significant evolution of the galaxy population with the decline in the number density of massive star-forming galaxies accompanied by an increase in the number density of quiescent galaxies (\citealt{Blanton:2006aa, bundy06a,  borch06a, Moustakas:2013aa}).
+\cite{Moustakas:2013aa}, for instance, find that since $z \sim 1.0$ the $\sim 50\%$ decline in the number density of massive star-forming galaxies ($\mathcal{M}_{*} > 10^{11} \mathcal{M}_{\odot}$) is complemented by the rise in number density of intermediate-mass quiescent galaxies ($\mathcal{M}_{*} \approx 10^{9.5} - 10^{10}\mathcal{M}_{\odot}$), by a factor of $ 2-3$, and massive quiescent galaxies ($\mathcal{M}_{*} > 10^{11} \mathcal{M}_{\odot}$ ), by $\sim 20\%$.
 On the color-magnitude diagram, this corresponds to the doubling of the red sequence over this period (\citealt{Bell:2004aa, borch06a, Faber:2007aa}).
@@
 Other models propose that environment dependent external processes such as ram-pressure stripping (\citealt{Gunn:1972aa, Bekki:2009aa}), strangulation (\citealt{Larson:1980aa, Balogh:2000aa}), or harassment (\citealt{Moore:1998aa}) contribute to the cessation.
-Many of these proposed processes have received observational support.
-\cite{Weinmann:2006aa} and \cite{Peng:2010aa}, for example, credit internal processes for quenching star-formation, especially in massive galaxies.
-Similarly, a number of observations support the existence of environment dependent external processes (\citealt{Iovino:2010aa, geha12a, Kovac:2014aa}).
+
+Observations such as \cite{Weinmann:2006aa} and \cite{Peng:2010aa} credit some of these proposed internal processes for the cessation of star-formation, especially in massive galaxies.
+Meanwhile, observations of galaxy properties such as color and morphology correlating with environment suggest that environment may play a role in ceasing star-formation (\citealt{blanton09a} and references therein).
+However, it remains to be discerned whether these trends reflect the underlying differences among galaxy populations in different environments or if they are in fact effects of environment dependent external processes, which cause galaxies that would otherwise continue forming stars to cease their star-formation.
+
+%Similarly, a number of observations support the existence of environment dependent external processes (\citealt{Iovino:2010aa, geha12a, Kovac:2014aa}).
 \cite{Peng:2010aa} and others further argue that internal and external processes both contribute to the cessation of star-formation with internal processes more dominant in massive galaxies and external processes dominating the less massive regime.
 While discrepancies persist between theoretical models and observations, a large number of observations suggest that environment plays a significant role in ceasing star-formation.
+
+%Some of these proposed internal processes have received observational support.
+\cite{Weinmann:2006aa} and \cite{Peng:2010aa}, for example, credit internal processes for quenching star-formation, especially in massive galaxies.
 

### 2014-12-19 qfenv_paper/qf_environment.tex
mike intro edit

@@
 Meanwhile, observations of galaxy properties such as color and morphology correlating with environment suggest that environment may play a role in ceasing star-formation (\citealt{blanton09a} and references therein).
-However, it remains to be discerned whether these trends reflect the underlying differences among galaxy populations in different environments or if they are in fact effects of environment dependent external processes, which cause galaxies that would otherwise continue forming stars to cease their star-formation.
+However, it remains to be determined whether the environmental trends in galaxy properties reflect the direct effect of external environment on the galaxies' evolution (e.g.
+ram pressure, tidal forces, mergers) or reflect statistical differences in the histories of galaxies in different environments (e.g.
+an earlier formation time in dense regions).
+
+%However, it remains to be discerned whether these trends reflect the underlying differences among galaxy populations in different environments or if they are in fact effects of environment dependent external processes, which cause galaxies that would otherwise continue forming stars to cease their star-formation.
 

### 2014-12-19 qfenv_paper/qf_environment.tex
Final edits to draft
Still need funding info

@@
 We investigate the effects of galaxy environment on the evolution of
-the quiescent fraction ($f_{\rm{Q}}$) from $z =0.8 $ to $ 0.0$ using
+the quiescent fraction ($f_{\mathrm{Q}}$) from $z =0.8 $ to $ 0.0$ using
 spectroscopic redshifts and multi-wavelength imaging data from the
@@
 the evolution of their stellar mass function (SMF). Then using the
-SMFs we compute $f_{\rm{Q}}(\mathcal{M}_{*})$ and quantify its
+SMFs we compute $f_{\mathrm{Q}}(\mathcal{M}_{*})$ and quantify its
 evolution within our redshift range. We find that the quiescent
@@
 Throughout the paper we assume a cosmology with $\Omega_{m} = 0.3,
-\Omega_{\Lambda} = 0.7$, and $H_0 = 70 \: \rm{km} \; \rm{s}^{-1}
-\rm{Mpc}^{-1}$. All magnitudes are AB-relative.
+\Omega_{\Lambda} = 0.7$, and $H_0 = 70 \: \mathrm{km} \; \mathrm{s}^{-1}
+\mathrm{Mpc}^{-1}$. All magnitudes are AB-relative.
 
@@
 In Section \ref{sec:primus} and Section \ref{sec:sdss} we provide a
-brief summary of the PRIMUS data and the SDSS data used for our sample
+brief summary of the PRIMUS and SDSS data used for our sample
 selection. In Section \ref{sec:target} we define our stellar mass complete galaxy sample.  
-Then, in Section \ref{sec:sfq}, we classify our sample galaxies as quiescent or star-forming. 
+Then, in Section \ref{sec:sfq}, we classify the sample galaxies as quiescent or star-forming. 
 We calculate the environment
@@
         \caption{Absolute magnitude $M_{r}$ versus redshift for our mass complete galaxy sample (black squares) with the Environment Defining Population (red circles) plotted on top.
-Both samples are divided into redshift bins: $z \approx 0.05-0.12$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ (panels left to right).
+Both samples are divided into redshift bins: $z = 0.05-0.12$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ (panels left to right).
 The lowest redshift bin ($z \approx 0.05-0.12$; leftmost panel) contain our galaxy sample and EDP selected from SDSS.
@@
 The redshift limits for the lowest redshift bin are empirically selected based on the bright and faint limits of SDSS galaxies.
-Stellar mass completeness limits, specified in Section \ref{sec:target}, are imposed on the galaxy population.
+Stellar mass completeness limits, described in Section \ref{sec:target}, are imposed on the galaxy population.
 Meanwhile, $M_{r}$ limits are applied to the EDP such that the number density in each panel are equivalent (Section \ref{sec:environment}).} \label{fig:targetEDP}
@@
 
-While the PRIMUS survey targeted seven distinct extragalactic deep fields for a total of $\sim 9 \; \rm{deg}^2$, we restrict our sample to five fields that have $GALEX$ and {\em Spitzer}/IRAC imaging for a total of $\sim 5.5 \; \rm{deg}^2$ (similar to the sample selection in \citealt{Moustakas:2013aa}).
+While the PRIMUS survey targeted seven distinct extragalactic deep fields for a total of $\sim 9 \; \mathrm{deg}^2$, we restrict our sample to five fields that have $GALEX$ and {\em Spitzer}/IRAC imaging for a total of $\sim 5.5 \; \mathrm{deg}^2$ (similar to the sample selection in \citealt{Moustakas:2013aa}).
 Four of these fields are a part of the {\em Spitzer} Wide-area Infrared Extragalactic Survey (SWIRE\footnote{http://swire.ipac.caltech.edu/swire/swire.html}): the European Large Area ISO Survey - South $1$ field (ELAIS-S1\footnote{http://dipastro.pd.astro.it/esis}), the Chandra Deep Field South SWIRE field (CDFS), and the XMM Large Scale Structure Survey field (XMM-LSS).
@@
 The model SEDs are generated using Flexible Stellar Population Synthesis (FSPS) models (\citealt{Conroy:2010aa}) based on the \cite{Chabrier:2003aa} IMF, along with other prior parameters discussed in Section 4.1 and Appendix A of \cite{Moustakas:2013aa}.
-For the observed photometry, we use the {\em GALEX} FUV and NUV, the two shortest IRAC bands at $3.6$ and $4.5 \mu \rm{m}$ (the two longer-wavelength IRAC channels are excluded because \texttt{iSEDfit} does not model hot dust or polycyclic aromatic hydrocarbons emission lines), and the optical bands.
+For the observed photometry, we use the {\em GALEX} FUV and NUV, the two shortest IRAC bands at $3.6$ and $4.5 \mu \mathrm{m}$ (the two longer-wavelength IRAC channels are excluded because \texttt{iSEDfit} does not model hot dust or polycyclic aromatic hydrocarbons emission lines), and the optical bands.
 
@@
 More specifically we select galaxies from the New York University Value-Added Galaxy Catalog (hereafter VAGC) that satisfy the main sample criterion and have galaxy extinction corrected Petrosian magnitudes $14.5 < r < 17.6$ and spectroscopic redshifts within $0.01 < z < 0.2$ (\citealt{Blanton:2005aa}).
-We further restrict the VAGC sample to only galaxies with medium depth observations with total exposure time greater than $1 \; \rm{ks}$ from {\em GALEX} Release 6.
+We further restrict the VAGC sample to only galaxies with medium depth observations with total exposure time greater than $1 \; \mathrm{ks}$ from {\em GALEX} Release 6.
 This leaves $167,727$ galaxies.
@@
 For optical photometry, we use the $ugriz$ bands from the SDSS \texttt{model} magnitudes scaled to the $r$-band \texttt{cmodel} magnitude.
-These photometric bands are then supplemented with integrated $JHK_s$ magnitudes from the 2MASS Extended Source Catalog (XSC; \citealt{Jarrett:2000aa}) and with photometry at $3.4$ and $4.6 \mu \rm{m}$ from the WISE All-Sky Data Release\footnote{http://wise2.ipac.caltech.edu/docs/release/allsky}.
+These photometric bands are then supplemented with integrated $JHK_s$ magnitudes from the 2MASS Extended Source Catalog (XSC; \citealt{Jarrett:2000aa}) and with photometry at $3.4$ and $4.6 \mu \mathrm{m}$ from the WISE All-Sky Data Release\footnote{http://wise2.ipac.caltech.edu/docs/release/allsky}.
 Further details regarding the SDSS-{\em GALEX} sample photometry can be found in Section 2.4 of \cite{Moustakas:2013aa}.
@@
     \begin{tabular}{ccccccc} \hline \hline              
-     &\multicolumn{1}{c}{$n_{\rm{env}}$}        & \multicolumn{2}{c}{$N_{\rm{gal}}$}  & \multicolumn{2}{c}{$\mathcal{M}_{\rm{lim}}$} & $M_{\rm{r}, lim}$ \\ 
+     &\multicolumn{1}{c}{$n_{\mathrm{env}}$}        & \multicolumn{2}{c}{$N_{\mathrm{gal}}$}  & \multicolumn{2}{c}{$\mathcal{M}_{\mathrm{lim}}$} & $M_{\mathrm{r}, lim}$ \\ 
     & & Quiescent & Star-Forming & Quiescent & Star-Forming &  \\ \hline 
-$0.05 < z < 0.12$ & $n_{\rm{env}} < \lowenvthresh $ & 6533 & 7508 & $10^{10.2} \mathcal{M}_{\odot}$ & $10^{10.2} \mathcal{M}_{\odot}$ & -20.95 \\
-               & $n_{\rm{env}} > \highenvthresh $ &14673 & 9717 &                          \\ 
+$0.05 < z < 0.12$ & $n_{\mathrm{env}} < \lowenvthresh $ & 6533 & 7508 & $10^{10.2} \mathcal{M}_{\odot}$ & $10^{10.2} \mathcal{M}_{\odot}$ & -20.95 \\
+               & $n_{\mathrm{env}} > \highenvthresh $ &14673 & 9717 &                          \\ 
                               & all          &$33553$                       & $29864$                          \\ \hline
-$0.2 < z < 0.4$      &$n_{\rm{env}} < \lowenvthresh $           &363                    &1231 & $10^{9.8} \mathcal{M}_{\odot}$ & $10^{9.8} \mathcal{M}_{\odot}$ &-21.03 \\
-               &$n_{\rm{env}} > \highenvthresh $            &379                    &756                           \\
+$0.2 < z < 0.4$      &$n_{\mathrm{env}} < \lowenvthresh $           &363                    &1231 & $10^{9.8} \mathcal{M}_{\odot}$ & $10^{9.8} \mathcal{M}_{\odot}$ &-21.03 \\
+               &$n_{\mathrm{env}} > \highenvthresh $            &379                    &756                           \\
                & all                & $1086$                      & $2879$                          \\ \hline
-$0.4 < z < 0.6$      &$n_{\rm{env}} < \lowenvthresh $           &536                       &1498 & $10^{10.3} \mathcal{M}_{\odot}$ & $10^{10.3} \mathcal{M}_{\odot}$ & -20.98 \\
-               &$n_{\rm{env}} > \highenvthresh $            &490                       &854                           \\
+$0.4 < z < 0.6$      &$n_{\mathrm{env}} < \lowenvthresh $           &536                       &1498 & $10^{10.3} \mathcal{M}_{\odot}$ & $10^{10.3} \mathcal{M}_{\odot}$ & -20.98 \\
+               &$n_{\mathrm{env}} > \highenvthresh $            &490                       &854                           \\
                & all               & $1560$                      & $3577$                          \\ \hline
-$0.6 < z < 0.8$      &$n_{\rm{env}} < \lowenvthresh $           &567                       &1254  & $10^{10.7} \mathcal{M}_{\odot}$ & $10^{10.6} \mathcal{M}_{\odot}$ & -20.97 \\
-               &$n_{\rm{env}} > \highenvthresh $            &498                       &671                           \\
+$0.6 < z < 0.8$      &$n_{\mathrm{env}} < \lowenvthresh $           &567                       &1254  & $10^{10.7} \mathcal{M}_{\odot}$ & $10^{10.6} \mathcal{M}_{\odot}$ & -20.97 \\
+               &$n_{\mathrm{env}} > \highenvthresh $            &498                       &671                           \\
                & all              & $1668$                      & $2964$                          \\ \hline
@@
 %    \bigskip 
-    {\bf Notes}: Number of galaxies ($N_{\rm{gal}}$) in the mass complete subsamples within the edges of the survey (Section \ref{sec:sample}).
-The subsamples are classified based on environment ($n_{\rm{env}}$) and star formation rate (star-forming or quiescent).
+    {\bf Notes}: Number of galaxies ($N_{\mathrm{gal}}$) in the mass complete subsamples within the edges of the survey (Section \ref{sec:sample}).
+The subsamples are classified based on environment ($n_{\mathrm{env}}$) and star formation rate (star-forming or quiescent).
 The lowest redshift bin is derived from SDSS; the rest are from PRIMUS.
-We also list the stellar mass completeness limit, $\mathcal{M}_{\rm{lim}}$, for our sample along with the $r$-band absolute magnitude limits, $M_{\rm{r}, lim}$, for the Environment Defining Population.
+We also list the stellar mass completeness limit, $\mathcal{M}_{\mathrm{lim}}$, for our sample along with the $r$-band absolute magnitude limits, $M_{\mathrm{r}, lim}$, for the Environment Defining Population.
     \bigskip
@@
 \begin{equation}
-w_{i} = (f_{\rm{target}} \times f_{\rm{collision}} \times f_{\rm{success}})^{-1},
+w_{i} = (f_{\mathrm{target}} \times f_{\mathrm{collision}} \times f_{\mathrm{success}})^{-1},
 \end{equation}
@@
 We use the same procedure as \cite{Moustakas:2013aa}, which follows \cite{Pozzetti:2010aa}, to empircally determine the stellar mass completeness limits.
-For each of the target galaxies we compute $\mathcal{M}_{\rm{lim}}$ using $\log \; \mathcal{M}_{\mathrm{lim}} = \log \; \mathcal{M} + 0.4\;(m - m_{\mathrm{lim}})$, where $\mathcal{M}$ is the stellar mass of the galaxy in $\mathcal{M_{\odot}}$, $\mathcal{M}_{\rm{lim}}$ is the stellar mass of each galaxy if its magnitude was equal to the survey magnitude limit, $m$ is the observed apparent magnitude in the selection band, and $m_{\rm{lim}}$ is the magnitude limit for our five fields.
-We construct a cumulative distribution of $\mathcal{M}_{\rm{lim}}$ for the $15\%$ faintest galaxies in $\Delta z=0.04$ bins.
+For each of the target galaxies we compute $\mathcal{M}_{\mathrm{lim}}$ using $\log \; \mathcal{M}_{\mathrm{lim}} = \log \; \mathcal{M} + 0.4\;(m - m_{\mathrm{lim}})$, where $\mathcal{M}$ is the stellar mass of the galaxy in $\mathcal{M_{\odot}}$, $\mathcal{M}_{\mathrm{lim}}$ is the stellar mass of each galaxy if its magnitude was equal to the survey magnitude limit, $m$ is the observed apparent magnitude in the selection band, and $m_{\mathrm{lim}}$ is the magnitude limit for our five fields.
+We construct a cumulative distribution of $\mathcal{M}_{\mathrm{lim}}$ for the $15\%$ faintest galaxies in $\Delta z=0.04$ bins.
 In each of these redshift bins, we calculate the minimum stellar mass that includes $95 \%$ of the galaxies.
@@
 uncertainties are significantly larger ($\sigma_{z}/(1+z) \approx 0.5
-\%$) than that of the SDSS-{\em GALEX} redshifts. In order to have
+\%$) than the uncertainties of the SDSS-{\em GALEX} redshifts. In order to have
 comparable environment measures throughout our redshift range, we
@@
 \begin{equation} \label{eq:qsfclass} 
-\rm{log}(\rm{SFR}_{\rm{min}}) = -0.49 + 0.64 \rm{log}(\mathcal{M} - 10) +1.07(z-0.1), 
+\mathrm{log}(\mathrm{SFR}_{\mathrm{min}}) = -0.49 + 0.64 \mathrm{log}(\mathcal{M} - 10) +1.07(z-0.1), 
 \end{equation} 
@@
     \epsfig{file=fig_envcount_cylr2_5h35_thresh75_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_primuszerr_masslimit_edgecut_histogram.png, width=0.45\textwidth}
-    \caption{Normalized distribution of environment measurements ($n_{\rm{env}}$) for our mass complete galaxy sample within the survey edges.
-A fixed cylindrical aperture of $R_{\rm{ap}} =\apradius\;\rm{Mpc}$ and $H_{\rm{ap}} = \apheight\; \rm{Mpc}$ is used to measure environment.
+    \caption{Normalized distribution of environment measurements ($n_{\mathrm{env}}$) for our mass complete galaxy sample within the survey edges.
+A fixed cylindrical aperture of $R_{\mathrm{ap}} =\apradius\;\mathrm{Mpc}$ and $H_{\mathrm{ap}} = \apheight\; \mathrm{Mpc}$ is used to measure environment.
 The star-forming galaxies contribution to the distribution is colored in blue and diagonally patterned.
 The contribution from quiescent galaxies is colored in red.
-Galaxies with $n_{\mathrm{env}} < 0.5$ are in low density environments and galaxies with $n_{\rm{env}} > 3.0$ are in high density environment.
+Galaxies with $n_{\mathrm{env}} < 0.5$ are in low density environments and galaxies with $n_{\mathrm{env}} > 3.0$ are in high density environment.
 We note that the significant difference among the SDSS distribution and the PRIMUS distributions above is due to the different stellar mass completeness limits imposed on each redshift bin of our galaxy sample.}      \label{fig:envcount}
-     %\caption{Normalized distribution of environment measurements ($n_{\rm{env}}$) for our mass complete galaxy sample within the edges.
+     %\caption{Normalized distribution of environment measurements ($n_{\mathrm{env}}$) for our mass complete galaxy sample within the edges.
 The star-forming galaxies contribution to the distribution is colored blue and diagonally patterned.
 The contribution from quiescent galaxies is colored in red.
-Each redshift panel is divided into three sections by the environment classification cutoffs (black veritcal lines): low density environment $n_{\rm{env}} < 0.5$ and high density environment $n_{\rm{env}} > 3.0$.
+Each redshift panel is divided into three sections by the environment classification cutoffs (black veritcal lines): low density environment $n_{\mathrm{env}} < 0.5$ and high density environment $n_{\mathrm{env}} > 3.0$.
 The percentages of the redshift bin contained in the environment classifications are presented above the distribution.
@@
 
-For our aperture, we use a cylinder of dimensions: $R_{\rm{ap}} =
+For our aperture, we use a cylinder of dimensions: $R_{\mathrm{ap}} =
 \apradius\;
-\rm{Mpc}$ and $H_{\rm{ap}} = \apheight\; \rm{Mpc}$.  We use a
-cylindrical aperture in order to account for the PRIMUS redshift
+\mathrm{Mpc}$ and $H_{\mathrm{ap}} = \apheight\; \mathrm{Mpc}$.  We use a
+cylindrical aperture to account for the PRIMUS redshift
 errors and redshift space distortions (i.e. ``Finger of God"
 effect). As \cite{Cooper:2005aa} and \cite{Gallazzi:2009aa} find, 
-$\pm 1000 \; \rm{km} \;\rm{s^{-1}}$ optimally reduces the effects of redshift space
+$\pm 1000 \; \mathrm{km} \;\mathrm{s^{-1}}$ optimally reduces the effects of redshift space
 distortions. The PRIMUS redshift uncertainty at $z \sim 0.7$
-corresponds to $\sigma_z < 0.01$, so our aperture height choice of
-$\apheight\;
-\rm{Mpc}$ accounts for both of these effects. Our choice of
+corresponds to $\sigma_z < 0.01$, so our choice of $\apheight\;
+\mathrm{Mpc}$ for the aperture height accounts for both of these effects. Our choice of
 cylinder radius was motivated by scale dependence analyses in the
@@
 %different radii, find positive correlation for quiescent fraction and
-%color on scales $< 1 \; \rm{Mpc}$ and anti-correlation on scales $> 3
-%\; \rm{Mpc}$. Our choice of $2 \rm{Mpc}/h$ provides sufficient sample
+%color on scales $< 1 \; \mathrm{Mpc}$ and anti-correlation on scales $> 3
+%\; \mathrm{Mpc}$. Our choice of $2 \mathrm{Mpc}/h$ provides sufficient sample
 %size of galaxies in dense environments, for robust statistics, while
@@
 
-%When we extend our analysis to cylindrical apertures with $R_{\rm{ap}} = 1 \; \rm{Mpc}/h$, we find that the change does not qualitatively change our results (difference in $f_{Q} < 0.05$). 
+%When we extend our analysis to cylindrical apertures with $R_{\mathrm{ap}} = 1 \; \mathrm{Mpc}/h$, we find that the change does not qualitatively change our results (difference in $f_{Q} < 0.05$). 
 %Similar fixed aperture methods have also been used in \cite{Croton:2005aa} for galaxies in the 2dF Galaxy Redshift 
@@
 We again restrict the PRIMUS galaxies to $0.2 < z < 0.8$ and divide them into bins of $\Delta z = 0.2$.
-Before we consider the cumulative number densities in the redshift bins, we first determine the $M_r$ limit for the highest redshift bin ($z = 0.6-0.8$) by examining the $M_{r}$ distribution with bin size $\Delta M_{r} = 0.25$ and select $M_{r,\rm{lim}}$ near the peak of the distribution where bins with $M_{r} > M_{r,\rm{lim}}$ have fewer galaxies than the bin at $M_{r, \rm{lim}}$.
-We conservatively choose $M_{r, \rm{lim}}(0.6 < z < 0.8)$ to be $M_{r} = -20.97$.
-Then for the lower redshift bins, we impose absolute magnitude limits ($M_{r,\rm{lim}}$) such that the cumulative number density, calculated with the galaxy statistical weights, of the bin ordered by $M_{r}$ is equal to the cumulative number density of the highest redshift bin with $M_{r, \rm{lim}}(0.6 < z < 0.8) = -20.97$.
+Before we consider the cumulative number densities in the redshift bins, we first determine the $M_r$ limit for the highest redshift bin ($z = 0.6-0.8$) by examining the $M_{r}$ distribution with bin size $\Delta M_{r} = 0.25$ and select $M_{r,\mathrm{lim}}$ near the peak of the distribution where bins with $M_{r} > M_{r,\mathrm{lim}}$ have fewer galaxies than the bin at $M_{r, \mathrm{lim}}$.
+We conservatively choose $M_{r, \mathrm{lim}}(0.6 < z < 0.8)$ to be $M_{r} = -20.97$.
+Then for the lower redshift bins, we impose absolute magnitude limits ($M_{r,\mathrm{lim}}$) such that the cumulative number density, calculated with the galaxy statistical weights, of the bin ordered by $M_{r}$ is equal to the cumulative number density of the highest redshift bin with $M_{r, \mathrm{lim}}(0.6 < z < 0.8) = -20.97$.
 
@@
 bright galaxies at $z \sim 0.01$ in the VAGC. As with the PRIMUS
-redshift bins, we determine the SDSS EDP $M_{r, \rm{lim}}$ by matching
+redshift bins, we determine the SDSS EDP $M_{r, \mathrm{lim}}$ by matching
 the cumulative number density of the highest redshift bin. For
 redshift bins $z = 0.05-0.12$, $0.2-0.4$, $0.4-0.6$, $0.6-0.8$ we get
-$M_{r,\rm{lim}} = -20.95$, $-21.03$, $-20.98$ and $-20.97$,
+$M_{r,\mathrm{lim}} = -20.95$, $-21.03$, $-20.98$ and $-20.97$,
 respectively. These absolute magnitude limits are illustrated in
 Figure \ref{fig:targetEDP}, where we present the absolute magnitude ($M_{r}$) versus redshift for the galaxy sample (black squares) ad the EDP (red circles). 
-The left-most panel corresponds to the sample derived from the SDSS-{\em GALEX} data and the rest correspond to the target sample derived from the PRIMUS data divided in bins with $\Delta z \sim 0.2$.
+The left-most panel corresponds to the samples derived from the SDSS-{\em GALEX} data while the rest correspond to samples derived from the PRIMUS data divided in bins with $\Delta z \sim 0.2$. 
 Figure \ref{fig:targetEDP} shows clear $M_r$ cutoffs in the
@@
 We appropriately apply equivalent redshift adjustments for the SDSS EDP.
-So for the SDSS EDP galaxies that are within the SDSS-{\em GALEX} sample, we adjust the redshift by an identical amount.
+For the SDSS EDP galaxies that are also contained within the SDSS-{\em GALEX} sample, we adjust the redshift by an identical amount.
 For the rest, we apply the same redshift adjustment procedure described in Section \ref{sec:target} in order to obtain PRIMUS level redshift uncertainties.
@@
 Finally, we measure the environment for each galaxy in our galaxy
-sample by counting the number of EDP galaxies, $n_{\rm{env}}$, with RA,
+sample by counting the number of EDP galaxies, $n_{\mathrm{env}}$, with RA,
 Dec, and $z$ within our cylindrical aperture centered around
-it. $n_{\rm{env}}$ accounts for the statistical weights of the EDP
+it. $n_{\mathrm{env}}$ accounts for the statistical weights of the EDP
 galaxies. 
-For our galaxy sample, the expected $n_{\rm{env}}$ given the uniform number density in 
-each of our EDP redshift bin and volume of our cylindrical aperture is $\langle n_{\rm{env}} \rangle = 1.3$. 
+For our galaxy sample, the expected $n_{\mathrm{env}}$ given the uniform number density in 
+each of our EDP redshift bin and volume of our cylindrical aperture is $\langle n_{\mathrm{env}} \rangle = 1.3$. 
 Once we obtain environment measurements for all the galaxies
-in our galaxy sample, we classify galaxies with $n_{\rm{env}} < 0.5$
-to be in ``low" environment densities and galaxies with $n_{\rm{env}} > 3$
+in our galaxy sample, we classify galaxies with $n_{\mathrm{env}} < 0.5$
+to be in ``low" environment densities and galaxies with $n_{\mathrm{env}} > 3$
 to be in ``high" environment densities. The high environment cutoff was
@@
 Section \ref{sec:env_qf_evol} we will also explore higher density
-cutoffs for $n_{\rm{env}}$.
+cutoffs for $n_{\mathrm{env}}$.
 
 The analysis we describe below uses a fixed cylindrical aperture with
-dimensions $R_{\rm{ap}} = \apradius \; \rm{Mpc}$ and $H_{\rm{ap}} = \apheight
-\;\rm{Mpc}$ to measure environment. The same analysis was
-extended for varying aperture dimensions $R_{\rm{ap}} = 1.5, \: \apradius, \:3.0 \:
-\rm{Mpc}$ and $H_{\rm{ap}} = \apheight, \; 70 \;\rm{Mpc}$ with adjusted environment classifications. 
+dimensions $R_{\mathrm{ap}} = \apradius \; \mathrm{Mpc}$ and $H_{\mathrm{ap}} = \apheight
+\;\mathrm{Mpc}$ to measure environment. The same analysis was
+extended for varying aperture dimensions $R_{\mathrm{ap}} = 1.5, \: \apradius, \:3.0 \:
+\mathrm{Mpc}$ and $H_{\mathrm{ap}} = \apheight, \; 70 \;\mathrm{Mpc}$ with adjusted environment classifications. 
 The results obtained from using different apertures and
@@
 For galaxies located near the edge of the survey, part of the fixed aperture encompassing it will lie outside the survey regions.
-In this case, $n_{env}$ only reflects the fraction of the environment within the survey geometry.
+In this scenario, $n_{env}$ only reflects the fraction of the environment within the survey geometry.
 
 To account for these edge effects, we use a Monte Carlo method to impose edge cutoffs on our galaxy sample.
-First, using \texttt{ransack} from \cite{Swanson:2008aa}, we construct a random sample of  $N_{\rm{ransack}} = 1,000,000$ points with RA and Dec randomly selected within the window function of the EDP (SDSS EDP and PRIMUS EDP separately).
-We then compute the angular separation, $\theta_{i, \rm{ap}}$ that corresponds to $R_{\rm{ap}}$ (Section \ref{sec:environment}) at the redshift of each sample galaxy $i$.
-For each sample galaxy we count the number of \texttt{ransack} points within $\theta_{i, \rm{ap}}$ of the galaxy: $n_{i,\rm{ransack}}$.
-Afterwards, we compare $n_{i,\rm{ransack}}$ to the expected value computed from the angular area of the environment defining aperture and the EDP window function:
+First, using \texttt{ransack} from \cite{Swanson:2008aa}, we construct a random sample of  $N_{\mathrm{ransack}} = 1,000,000$ points with RA and Dec randomly selected within the window function of the EDP (SDSS EDP and PRIMUS EDP separately).
+We then compute the angular separation, $\theta_{i, \mathrm{ap}}$ that corresponds to $R_{\mathrm{ap}}$ (Section \ref{sec:environment}) at the redshift of each sample galaxy $i$.
+For each sample galaxy we count the number of \texttt{ransack} points within $\theta_{i, \mathrm{ap}}$ of the galaxy: $n_{i,\mathrm{ransack}}$.
+Afterwards, we compare $n_{i,\mathrm{ransack}}$ to the expected value computed from the angular area of the environment defining aperture and the EDP window function:
 \begin{equation} \label{eq:ransack}
-\langle n_{\rm{ransack}}\rangle_{i} = \frac{N_{\rm{ransack}}}{A_{\rm{EDP}}}\times {\pi \theta_{i, \rm{ap}}^2} \times f_{\rm{thresh}}. 
+\langle n_{\mathrm{ransack}}\rangle_{i} = \frac{N_{\mathrm{ransack}}}{A_{\mathrm{EDP}}}\times {\pi \theta_{i, \mathrm{ap}}^2} \times f_{\mathrm{thresh}}. 
 \end{equation} 
-$A_{\rm{EDP}}$ is the total angular area of the EDP window function and $f_{\rm{thresh}}$ is the fractional threshold for the edge effect cut-off.
-For $R_{\rm{ap}}= \apradius \;\rm{Mpc}$, $f_{\rm{thresh}} = 0.75$.
-If $n_{i, \rm{ransack}} > \langle n_{\rm{ransack}} \rangle_i$ then galaxy $i$ remains in our sample; otherwise, it is discarded.
+$A_{\mathrm{EDP}}$ is the total angular area of the EDP window function and $f_{\mathrm{thresh}}$ is the fractional threshold for the edge effect cut-off.
+For $R_{\mathrm{ap}}= \apradius \;\mathrm{Mpc}$, we use $f_{\mathrm{thresh}} = 0.75$.
+If $n_{i, \mathrm{ransack}} > \langle n_{\mathrm{ransack}} \rangle_i$ then galaxy $i$ remains in our sample; otherwise, it is discarded.
 Once the edge effect cuts are applied, we are left with the final galaxy sample.
@@
 
-In Figure \ref{fig:envcount} we present the distribution of environment measurements ($n_{\rm{env}}$) for our final galaxy sample in redshift bins: $z = 0.05 - 0.12$, $0.2 - 0.4$, $0.4-0.6$, and $0.6-0.8$.
+In Figure \ref{fig:envcount} we present the distribution of environment measurements ($n_{\mathrm{env}}$) for our final galaxy sample in redshift bins: $z = 0.05 - 0.12$, $0.2 - 0.4$, $0.4-0.6$, and $0.6-0.8$.
 The quiescent galaxy contributions are colored in red while the star-forming galaxy contributions are colored in blue and patterned.
@@
 
-Although we imposed PRIMUS redshift errors on our SDSS galaxies in order to consistently measure environment throughout our entire sample, we note a significant discrepancy between the $n_{\mathrm{env}}$ distributions of the SDSS and PRIMUS samples.
+Although we imposed PRIMUS redshift errors on our SDSS galaxies to consistently measure environment throughout our entire sample, we note a significant discrepancy between the $n_{\mathrm{env}}$ distributions of the SDSS and PRIMUS samples.
 For example, in each of the PRIMUS redshift bins, $\sim 40 \%$ of galaxies in the redshift bin are in low density environments and roughly $30 \%$ are in high density environments.
@@
 $z=0$--$0.8$. The environment of each galaxy  
-was calculated using a cylindrical aperture size of $R=\apradius \: \rm{Mpc}$ and $H=\apheight \: \rm{Mpc}$ and  
+was calculated using a cylindrical aperture size of $R=\apradius \: \mathrm{Mpc}$ and $H=\apheight \: \mathrm{Mpc}$ and  
 classified as low environment when $n_{\mathrm{env}} < 0.5$ and as high environment when $n_{\mathrm{env}} > 3.0$. The SMFs use mass bins of 
-width $\Delta \rm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.2$. In each panel we use shades of blue 
+width $\Delta \mathrm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.2$. In each panel we use shades of blue 
 (star-forming) and orange (quiescent) to represent the SMF at different redshift, higher redshifts being
@@
 \subsection{Stellar Mass Function Calculations} \label{sec:smfcalc} 
-To calculate the SMFs we employ a non-parametric $1/{V_{\rm{max}}}$ estimator commonly used for galaxy luminosity functions and stellar mass functions in order to account for Malmquist bias, as done in \cite{Moustakas:2013aa} and discussed in the review \cite{Johnston:2011aa}.
+To calculate the SMFs we employ a non-parametric $1/{V_{\mathrm{max}}}$ estimator commonly used for galaxy luminosity functions and stellar mass functions in order to account for Malmquist bias, as done in \cite{Moustakas:2013aa} and discussed in the review \cite{Johnston:2011aa}.
 The differential SMF is given by the following equation:
 \begin{equation} \label{eq:phi}
-\Phi(\rm{log}\: \mathcal{M}) \Delta(\rm{log} \:\mathcal{M}) = \sum\limits_{i=1}^{N} \frac{w_i}{V_{\rm{max,avail},i}}. 
+\Phi(\mathrm{log}\: \mathcal{M}) \Delta(\mathrm{log} \:\mathcal{M}) = \sum\limits_{i=1}^{N} \frac{w_i}{V_{\mathrm{max,avail},i}}. 
 \end{equation}
-$w_i$ is the statistical weight of galaxy $i$ and $\Phi(\rm{log}\:
-\mathcal{M}) \Delta(\rm{log}\: \mathcal{M})$ is the number of galaxies
-($N$) per unit volume within the stellar mass range $[\rm{log}
-  \:\mathcal{M}, \rm{log} \:\mathcal{M}+\Delta(\rm{log}
-  \:\mathcal{M})]$.
-The equation above is the same as Equation 3 in \cite{Moustakas:2013aa} except that we use $V_{\rm{max,avail}}$ instead than $V_{\rm{max}}$, to account for the edge effects of the survey discussed in Section \ref{sec:edgeeffect}.
-
-$V_{\rm{max},i}$ is the maximum cosmological volume where it is
+$w_i$ is the statistical weight of galaxy $i$ and $\Phi(\mathrm{log}\:
+\mathcal{M}) \Delta(\mathrm{log}\: \mathcal{M})$ is the number of galaxies
+($N$) per unit volume within the stellar mass range $[\mathrm{log}
+  \mathcal{M},\: \mathrm{log} \mathcal{M}+\Delta(\mathrm{log}\mathcal{M})]$.
+The equation above is the same as Equation 3 in \cite{Moustakas:2013aa} except that we use $V_{\mathrm{max,avail}}$ instead than $V_{\mathrm{max}}$, to account for the edge effects of the survey discussed in Section \ref{sec:edgeeffect}.
+
+$V_{\mathrm{max},i}$ is the maximum cosmological volume where it is
 possible to observe galaxy $i$ given the apparent magnitude limits of
@@
 maximum cosmological volume where a galaxy can be observed, thereby
-reducing the fraction of $V_{\rm{max},i}$ that is actually available
-in the sample. We introduce the term $V_{\rm{max,avail},i}$ to express
+reducing the fraction of $V_{\mathrm{max},i}$ that is actually available
+in the sample. We introduce the term $V_{\mathrm{max,avail},i}$ to express
 the maximum volume accounting for the survey edge effects.
 
-To calculate $V_{\rm{max,avail},i}$, we use a similar Monte Carlo
+To calculate $V_{\mathrm{max,avail},i}$, we use a similar Monte Carlo
 method as the edge effect cutoffs in Section
@@
 the bin after the edge effect cuts over the total number of random
-points in the bin: $f_{\rm{edge}}$. We then apply this factor to
-compute $V_{\rm{max,avail}} = V_{\rm{max}} \times f_{\rm{edge}}$. The
-$V_{\rm{max}}$ values in the equation above are computed following the
+points in the bin: $f_{\mathrm{edge}}$. We then apply this factor to
+compute $V_{\mathrm{max,avail}} = V_{\mathrm{max}} \times f_{\mathrm{edge}}$. The
+$V_{\mathrm{max}}$ values in the equation above are computed following the
 method described in \cite{Moustakas:2013aa} Section 4.2 with the same
@@
 In panel (b), star-forming galaxies in high density environments, we do not observe any clear trends above the knee of the SMF ($\mathcal{M} \sim 10^{10.7} \mathcal{M}_{\odot}$) but an increase in SMF below the knee.
-For the quiescent population in low density environment, panel (c), we observe a potential decrease at high masses ($\mathcal{M} > 10^{10.7} \mathcal{M}_{\odot}$).
+For the quiescent population in low density environment, panel (c), we observe a potential decrease at higher masses ($\mathcal{M} > 10^{10.7} \mathcal{M}_{\odot}$).
 Lastly for the quiescent population in high density environments, panel (d), we find significant increase in $\Phi$ for lower masses but little trend at higher masses.
@@
         \epsfig{file=fig_qf_cylr2_50000h35_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_lit_primuszerr.eps, height=0.75\textwidth,angle=90}
-        \caption{Evolution of the quiescent fraction $f_{\rm{Q}}$ for
+        \caption{Evolution of the quiescent fraction $f_{\mathrm{Q}}$ for
           galaxies in low (left) and high (right) density
-          environments for $z < 0.8$. $f_{\rm{Q}}$s were calculated
+          environments for $z < 0.8$. $f_{\mathrm{Q}}$s were calculated
           using the SMFs in Figure \ref{fig:smf}, as described in Section \ref{sec:qfevol}.
@@
 \begin{equation}
-f_{\rm{Q}} ( \mathcal{M}_{*}, z)= \frac{\Phi_{Q}}{\Phi_{SF}+\Phi_{Q}}.
+f_{\mathrm{Q}} ( \mathcal{M}_{*}, z)= \frac{\Phi_{Q}}{\Phi_{SF}+\Phi_{Q}}.
 \end{equation}
 $\Phi_{Q}$ and $\Phi_{SF}$ are the total number of galaxies per unit
-volume in stellar mass bin of $\Delta(\rm{log} \: \mathcal{M}) = 0.20
+volume in stellar mass bin of $\Delta(\mathrm{log} \: \mathcal{M}) = 0.20
 \: \mathrm{dex}$ for the quiescent and star-forming subsamples,
-respectively (Equation \ref{eq:phi}). We compute $f_{\rm{Q}}$ for high
+respectively (Equation \ref{eq:phi}). We compute $f_{\mathrm{Q}}$ for high
 and low density environments for all redshift bins as plotted in
-Figure \ref{fig:qf}, which shows the evolution of $f_{\rm{Q}}$ for
+Figure \ref{fig:qf}, which shows the evolution of $f_{\mathrm{Q}}$ for
 high (right panel) and low (left panel) density environments. As in
@@
 
-Most noticeably in Figure \ref{fig:qf}, we find $f_{\rm{Q}}$ increases
+Most noticeably in Figure \ref{fig:qf}, we find $f_{\mathrm{Q}}$ increases
 monotonically as a function of mass at all redshifts and
-environments. In other words, for galaxies in any environment and at all redshifts, galaxies with higher
+environments. In other words, for galaxies in any environment since $ z \sim 0.8$, galaxies with higher
 masses are more likely to have ceased their star-formation.
@@
 
-Focusing on the redshift evolution of $f_{\rm{Q}}$, we find that for
-both environments $f_{\rm{Q}}$ increases as redshift decreases. For
+Focusing on the redshift evolution of $f_{\mathrm{Q}}$, we find that for
+both environments $f_{\mathrm{Q}}$ increases as redshift decreases. For
 high density environments, this is analogous to the Butcher-Oemler
 Effect (\citealt{Butcher:1984aa}), which states that galaxy
-populations in groups or clusters have higher $f_{\rm{blue}}$, or
-lower $f_{\rm{Q}}$, at higher redshift. This evolution occurs with
+populations in groups or clusters have higher $f_{\mathrm{blue}}$ 
+(lower $f_{\mathrm{Q}}$) at higher redshift. This evolution occurs with
 roughly the same amplitude in low environments as well.
 
-In addition, when we compare the stellar masses at which $f_{\rm{Q}} =
+In addition, when we compare the stellar masses at which $f_{\mathrm{Q}} =
 0.5$ for each subsample, the so-called $\mathcal{M}_{50-50}$, we find
@@
 Finally, we compare between our low and high density environment
-$f_{\rm{Q}}$s at each redshift bin interval. For our lowest redshift
-bin, we find that $f_{\rm{Q}}$ at low density environments ranges from
+$f_{\mathrm{Q}}$s at each redshift bin interval. For our lowest redshift
+bin, we find that $f_{\mathrm{Q}}$ at low density environments ranges from
 $\sim 0.4$ to $\sim 0.9$ for $10^{10.2} \mathcal{M}_{\odot} <
 \mathcal{M}_{*} < 10^{11.5} \mathcal{M}_{\odot}$. Over the same mass
-range, $f_{\rm{Q}}$ at high density environment ranges from $\sim
-0.55$ to $\sim 0.9$. For our SDSS sample, $f_{\rm{Q}}$ in
+range, $f_{\mathrm{Q}}$ at high density environment ranges from $\sim
+0.55$ to $\sim 0.9$. For our SDSS sample, $f_{\mathrm{Q}}$ in
 high density environments is notably higher.
 
-For our PRIMUS sample at $z \sim 0.3$, over $10^{9.5} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11} \mathcal{M}_{\odot}$ $f_{\rm{Q}}$ ranges from $\sim 0.2$ to $\sim 0.6$ for low density environment, while at high density environment $f_{\rm{Q}}$ ranges from $\sim 0.2$ to $\sim 0.8$.
-Similarly, at $z \sim 0.5$, over $10^{10} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11.2} \mathcal{M}_{\odot}$ $f_{\rm{Q}}$ ranges from $\sim 0.3$ to $\sim 0.6$ for low density environment and $f_{\rm{Q}}$ ranges from $\sim 0.3$ to $\sim 0.7$.
-Finally in our highest redshift bin $z \sim 0.7$, over the mass range $10^{10.5} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11.5} \mathcal{M}_{\odot}$, $f_{\rm{Q}}$ ranges from $\sim 0.35$ to $\sim 0.6$ for low density and $\sim 0.45$ to $\sim 0.8$ for high density.
-For the entire redshift range of our sample, $f_{\rm{Q}}$ in high density environment is higher than $f_{\rm{Q}}$ in low density environments.
-
-While there is a significant difference in $f_{\rm{Q}}$ between the
+For our PRIMUS sample at $z \sim 0.3$, over $10^{9.5} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11} \mathcal{M}_{\odot}$ $f_{\mathrm{Q}}$ ranges from $\sim 0.2$ to $\sim 0.65$ for low density environment, while at high density environment $f_{\mathrm{Q}}$ ranges from $\sim 0.2$ to $\sim 0.8$.
+Similarly, at $z \sim 0.5$, over $10^{10} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11.2} \mathcal{M}_{\odot}$ $f_{\mathrm{Q}}$ ranges from $\sim 0.3$ to $\sim 0.6$ for low density environment and $f_{\mathrm{Q}}$ ranges from $\sim 0.3$ to $\sim 0.7$.
+Finally in our highest redshift bin $z \sim 0.7$, over the mass range $10^{10.5} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11.5} \mathcal{M}_{\odot}$, $f_{\mathrm{Q}}$ ranges from $\sim 0.35$ to $\sim 0.6$ for low density and $\sim 0.45$ to $\sim 0.8$ for high density.
+For the entire redshift range of our sample, $f_{\mathrm{Q}}$ in high density environment is higher than $f_{\mathrm{Q}}$ in low density environments.
+
+While there is a significant difference in $f_{\mathrm{Q}}$ between the
 environments, since the difference is observed from our highest
@@
         \caption{The evolution of the quiescent fraction at fiducial
-          mass, $f_{Q}(\mathcal{M}_{\rm{fid}})$, for low (blue) and
+          mass, $f_{Q}(\mathcal{M}_{\mathrm{fid}})$, for low (blue) and
           high (red) density environments within the redshift range $z
-          = 0.0 - 0.8$. We present the $f_{Q}(\mathcal{M}_{\rm{fid}})$
-          evolution for $\mathcal{M}_{\rm{fid}} = 10^{10.5}
+          = 0.0 - 0.8$. We present the $f_{Q}(\mathcal{M}_{\mathrm{fid}})$
+          evolution for $\mathcal{M}_{\mathrm{fid}} = 10^{10.5}
           \mathcal{M}_\odot$ (solid fill) and $10^{11}
@@
 While the high density $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ is greater than low density environment $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ over the entire redshift range of our sample, there is a significant increase in $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ over cosmic time for both environments.
-For the environment cut-offs ($n_{\rm{env}} < 0.5$ for low and $n_{\rm{env}} > 3.0$ for high), there is no significant difference in the slope of the evolution between the environments.}         \label{fig:qffit}
+For the environment cut-offs ($n_{\mathrm{env}} < 0.5$ for low and $n_{\mathrm{env}} > 3.0$ for high), there is no significant difference in the slope of the evolution between the environments.}         \label{fig:qffit}
     \end{center}
@@
 \begin{table} 
-  \caption{Best Fit Parameters for $f_{\rm{Q}}(\mathcal{M}_{*})$ Fit}
+  \caption{Best Fit Parameters for $f_{\mathrm{Q}}(\mathcal{M}_{*})$ Fit}
   \label{tab:bestfitparam}
@@
     $z_1 < z < z_2$ &Environment        &a  &b  \\ \hline 
-$0.05 < z< 0.12$ &$n_{\rm{env}} < \lowenvthresh$ & $0.410 \pm 0.018$ & $0.469 \pm 0.007$ \\
-               &$n_{\rm{env}} > \highenvthresh$ & $0.270 \pm 0.016$ & $0.620 \pm 0.008$ \\ 
+$0.05 < z< 0.12$ &$n_{\mathrm{env}} < \lowenvthresh$ & $0.410 \pm 0.018$ & $0.469 \pm 0.007$ \\
+               &$n_{\mathrm{env}} > \highenvthresh$ & $0.270 \pm 0.016$ & $0.620 \pm 0.008$ \\ 
                               &               &                       &                           \\ \hline   
-$0.2 < z <0.4$ & $n_{\rm{env}} < \lowenvthresh$ & $0.340 \pm 0.032$ & $0.432 \pm 0.015$ \\
-               &$n_{\rm{env}} > \highenvthresh$ & $0.432 \pm 0.018$ & $0.544 \pm 0.010$ \\
+$0.2 < z <0.4$ & $n_{\mathrm{env}} < \lowenvthresh$ & $0.340 \pm 0.032$ & $0.432 \pm 0.015$ \\
+               &$n_{\mathrm{env}} > \highenvthresh$ & $0.432 \pm 0.018$ & $0.544 \pm 0.010$ \\
                &               &                       &                           \\ \hline
-$0.4 < z < 0.6$      &$n_{\rm{env}} < \lowenvthresh$ & $0.263 \pm 0.038$ & $0.381 \pm 0.018$ \\
-               &$n_{\rm{env}} > \highenvthresh$ & $0.289 \pm 0.018$ & $0.446 \pm 0.013$ \\
+$0.4 < z < 0.6$      &$n_{\mathrm{env}} < \lowenvthresh$ & $0.263 \pm 0.038$ & $0.381 \pm 0.018$ \\
+               &$n_{\mathrm{env}} > \highenvthresh$ & $0.289 \pm 0.018$ & $0.446 \pm 0.013$ \\
                &               &                       &                           \\ \hline
-$0.6 < z < 0.8$      &$n_{\rm{env}} < \lowenvthresh$ & $0.284 \pm 0.036$ & $0.352 \pm 0.019$ \\
-               &$n_{\rm{env}} > \highenvthresh$            & $0.468 \pm 0.065$ & $0.429 \pm 0.023$ \\
+$0.6 < z < 0.8$      &$n_{\mathrm{env}} < \lowenvthresh$ & $0.284 \pm 0.036$ & $0.352 \pm 0.019$ \\
+               &$n_{\mathrm{env}} > \highenvthresh$            & $0.468 \pm 0.065$ & $0.429 \pm 0.023$ \\
                &               &                       &                           \\ \hline
@@
 %    \bigskip 
-    {\bf Notes}: Best fit parameters in Equation \ref{eq:qffit} for each subsample $f_{\rm{Q}}(\mathcal{M}_{*})$ in Figure \ref{fig:qf} for $\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_{\odot}$.
+    {\bf Notes}: Best fit parameters in Equation \ref{eq:qffit} for each subsample $f_{\mathrm{Q}}(\mathcal{M}_{*})$ in Figure \ref{fig:qf} for $\mathcal{M}_{\mathrm{fid}} = 10^{10.5} \mathcal{M}_{\odot}$.
 \end{table}
@@
 \subsection{Environmental Effects on the Quiescent Fraction Evolution} \label{sec:env_qf_evol}
-In order to more quantitatively compare the $f_{\rm{Q}}$ evolution for different epochs and environments, we fit $f_{\rm{Q}}$ for each subsample to a power-law parameterization as a function of stellar mass,
+In order to more quantitatively compare the $f_{\mathrm{Q}}$ evolution for different epochs and environments, we fit $f_{\mathrm{Q}}$ for each subsample to a power-law parameterization as a function of stellar mass,
 \begin{equation} \label{eq:qffit}
-f_{\rm{Q}}(\mathcal{M}_{*}) = a \: \rm{log} \; \left(\frac{ \mathcal{M}_{*}}{\mathcal{M}_{\rm{fid}}} \right)+b,
+f_{\mathrm{Q}}(\mathcal{M}_{*}) = a \: \mathrm{log} \; \left(\frac{ \mathcal{M}_{*}}{\mathcal{M}_{\mathrm{fid}}} \right)+b,
 \end{equation}
-where $a$ and $b$ are best-fit parameters using {\em MPFIT} (\citealt{Markwardt:2009aa}) and $\mathcal{M}_{\rm{fid}}$ represents the empirically selected fiducial mass within the stellar mass limits where there is a sufficiently large number of galaxies.
-We primarily focus on $\mathcal{M}_{\rm{fid}} = 10^{10.5} \: \mathcal{M}_{\odot}$.
+where $a$ and $b$ are best-fit parameters using {\em MPFIT} (\citealt{Markwardt:2009aa}) and $\mathcal{M}_{\mathrm{fid}}$ represents the empirically selected fiducial mass within the stellar mass limits where there is a sufficiently large number of galaxies.
+We primarily focus on $\mathcal{M}_{\mathrm{fid}} = 10^{10.5} \: \mathcal{M}_{\odot}$.
 
 In Figure \ref{fig:qffit} we present the evolution of
-$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$
+$f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$
 at low (blue) and high (red) density environments for
-$\mathcal{M}_{\rm{fid}} = 10^{10.5} \: \mathcal{M}_{\odot}$ (solid
+$\mathcal{M}_{\mathrm{fid}} = 10^{10.5} \: \mathcal{M}_{\odot}$ (solid
 fill) and $10^{11} \: \mathcal{M}_{\odot}$ (pattern fill). The width
 of the evolution represents the uncertainty derived from {\em
-  MPFIT}. As noted earlier in Section \ref{sec:qfevol}, $f_{\rm{Q}}$
+  MPFIT}. As noted earlier in Section \ref{sec:qfevol}, $f_{\mathrm{Q}}$
 in high density environments is significantly greater than
-$f_{\rm{Q}}$ in low density environments for both fiducial mass
+$f_{\mathrm{Q}}$ in low density environments for both fiducial mass
 choices. Throughout our sample's redshift range
@@
 
-When we increase our choice of $\mathcal{M}_{\rm{fid}}$ to $10^{11}
+When we increase our choice of $\mathcal{M}_{\mathrm{fid}}$ to $10^{11}
 \mathcal{M}_\odot$, aside from an overall shift in
-$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ by $\sim 0.2$, we observe the
-same evolutionary trends. $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} =
+$f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ by $\sim 0.2$, we observe the
+same evolutionary trends. $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}} =
 10^{11}\mathcal{M}_{\odot})$ for both low and high density
@@
 completeness at each redshift bin limits the masses we probe for the
-$f_{\rm{Q}}$ evolution, our $f_{\rm{Q}}$ evolution exhibits little
+$f_{\mathrm{Q}}$ evolution, our $f_{\mathrm{Q}}$ evolution exhibits little
 mass dependence.
@@
 the decrease in sample size of the purer high environment sample, we
-find an extension of the $f_{\rm{Q}}$ difference between the
+find an extension of the $f_{\mathrm{Q}}$ difference between the
 environments we stated earlier. A more stringent high environment
 classification significantly increases the overall
-$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$, which rises monotonically with
+$f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$, which rises monotonically with
 the $n_{\mathrm{env}}$ limit.
@@
 More importantly, a purer high environment classification reveals a
-more significant environment dependence on the $f_{\rm{Q}}$
-evolution. While the difference between the $f_{\rm{Q}}$ evolution in
-low and high density environment is negligible for the $n_{\rm{env}} >
+more significant environment dependence on the $f_{\mathrm{Q}}$
+evolution. While the difference between the $f_{\mathrm{Q}}$ evolution in
+low and high density environment is negligible for the $n_{\mathrm{env}} >
 3$ cut-off, there is a notable difference in $f_{\mathrm{Q}}$
-evolution between our highest cut-off $n_{\rm{env}} > 7$ and our low
+evolution between our highest cut-off $n_{\mathrm{env}} > 7$ and our low
 density environment. $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z
 \sim 0.1) - f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.7)
-\sim 0.25$ for $n_{\rm{env}} > 7$ versus
+\sim 0.25$ for $n_{\mathrm{env}} > 7$ versus
 $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.1) -
@@
 environment independent internal mechanisms that can explain the
-$f_{\rm{Q}}$ evolution in low density environments, there may be other
+$f_{\mathrm{Q}}$ evolution in low density environments, there may be other
 environment dependent mechanisms that can account for the moderate
-environment dependence of the $f_{\rm{Q}}$ evolution. Our measured
-difference in the $f_{\rm{Q}}$ evolution between environments provides
+environment dependence of the $f_{\mathrm{Q}}$ evolution. Our measured
+difference in the $f_{\mathrm{Q}}$ evolution between environments provides
 an important constraint for any environmental models for ending star
@@
         \epsfig{file=fig_qffit_cylr2_50000h35_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmass10_5_lit_primuszerr_baldry_geha_iovino_kovac_peng_envthresh_kovacoffset.eps, height=\textwidth, angle=90}
-        \caption{$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}}=10^{10.5} \mathcal{M}_\odot)$ evolution compared to $f_{\rm{red}}(\mathcal{M}_{*}=10^{10.5} \; \mathcal{M}_{\odot})$ in the literature: \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross) from SDSS (panel a), \cite{Iovino:2010aa} (empty square; panel \iovinopanel) and \cite{Kovac:2014aa} (triangle; panel \kovacpanel) from zCOSMOS, and \cite{Peng:2010aa} from both SDSS and zCOSMOS (panel \pengpanel).
-The $f_{\rm{red}}$ values from \cite{Iovino:2010aa}, \cite{Kovac:2014aa}, \cite{Baldry:2006aa}, and \cite{Peng:2010aa} are calculated from the best-fit parameterizations presented in the respective works.
-The $f_{\rm{Q}}$ value from \cite{geha12a} is the $f_{\rm{Q}}$ value at $\mathcal{M} = 10^{10.55} \mathcal{M}_{\odot}$.
+        \caption{$f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}=10^{10.5} \mathcal{M}_\odot)$ evolution compared to $f_{\mathrm{red}}(\mathcal{M}_{*} \sim 10^{10.5} \; \mathcal{M}_{\odot})$ in the literature: \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross) from SDSS (panel a), \cite{Iovino:2010aa} (empty square) and \cite{Kovac:2014aa} (triangle) from zCOSMOS (panel \kovacpanel), and \cite{Peng:2010aa} from both SDSS and zCOSMOS (panel \pengpanel).
+The $f_{\mathrm{red}}$ values from \cite{Iovino:2010aa}, \cite{Kovac:2014aa}, \cite{Baldry:2006aa}, and \cite{Peng:2010aa} are calculated from the best-fit parameterizations presented in the respective works.
 High density environment is represented in red and low density environment is represented in blue.
-The uncertainties in the \cite{Iovino:2010aa} best-fit $f_{\rm{red}}$ is omitted due to insufficient information on the cross correlation terms of the fit parameters.
-For \cite{Kovac:2014aa} we apply the offset between the color-based and SFR-based galaxy classification in order to plot the $f_{\rm{Q}}$ estimates.
-We also plot the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$ evolution of our sample with varying environment cut-offs specified on the top right.
-As in Figure \ref{fig:qffit} the width of the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$ evolution represent the uncertainty in the best-fit parameters of Equation \ref{eq:qffit}.}         \label{fig:qffit_comp}
+The $f_{\mathrm{Q}}$ value from \cite{geha12a} is the $f_{\mathrm{Q}}$ value at $\mathcal{M} = 10^{10.55} \mathcal{M}_{\odot}$.
+Uncertainties in the \cite{Iovino:2010aa} best-fit $f_{\mathrm{red}}$ is omitted due to insufficient information on the cross correlation terms of the fit parameters.
+For \cite{Kovac:2014aa} we apply the offset between the color-based and SFR-based galaxy classification in order to plot the $f_{\mathrm{Q}}$ estimates.
+We also plot the $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}} = 10^{10.5} \mathcal{M}_\odot)$ evolution of our sample with varying environment cut-offs specified on the top right.
+As in Figure \ref{fig:qffit} the width of the $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}} = 10^{10.5} \mathcal{M}_\odot)$ evolution represent the uncertainty in the best-fit parameters of Equation \ref{eq:qffit}.}         \label{fig:qffit_comp}
     \end{center}
@@
 our sample specific methodology, a number of results from the literature have investigated the quiescent fraction in comparable fashions.
-In this section we compare our $f_{\rm{Q}}$ results from above to a number of these results, specifically from SDSS and zCOSMOS, with similarly defined samples and analogous environment classifications.
+In this section we compare our $f_{\mathrm{Q}}$ results from above to a number of these results, specifically from SDSS and zCOSMOS, with similarly defined samples and analogous environment classifications.
 
 In Figure \ref{fig:qffit_comp}, we plot  best-fit parameterization of
-$f_{\rm{red}}$ for high and low density environment from SDSS (panel a), zCOSMOS (panel \iovinopanel), and \cite{Peng:2010aa} (filled square; panel d) from both surveys. 
-%$f_{\rm{red}}$ for high and low density environment from SDSS (panel a), \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross), zCOSMOS (panel b),
+$f_{\mathrm{red}}$ for high and low density environment from SDSS (panel a), zCOSMOS (panel \iovinopanel), and \cite{Peng:2010aa} (filled square; panel d) from both surveys. 
+%$f_{\mathrm{red}}$ for high and low density environment from SDSS (panel a), \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross), zCOSMOS (panel b),
 %\cite{Iovino:2010aa} (empty square) and \cite{Kovac:2014aa} (triangle), and \cite{Peng:2010aa} (filled square; panel c) from both surveys. From
-From \cite{Iovino:2010aa} (empty square; panel \iovinopanel$ $ in Figure \ref{fig:qffit_comp}), we calculate $f_{\rm{red}} = 1-f_{\rm{blue}}$
-using the best-fit $f_{\rm{blue}}$ from the mass bin $\mathcal{M} =
-10^{10.3} - 10^{10.8} \mathcal{M}_{\odot}$. From \cite{Kovac:2014aa} (triangle; panel \kovacpanel$ $ in Figure \ref{fig:qffit_comp})
-we plot an estimated $f_{\rm{Q}}$ by applying the residual between SFR
+From \cite{Iovino:2010aa} (empty square; panel \iovinopanel), we calculate $f_{\mathrm{red}} = 1-f_{\mathrm{blue}}$
+using the best-fit $f_{\mathrm{blue}}$ from the mass bin $\mathcal{M} =
+10^{10.3} - 10^{10.8} \mathcal{M}_{\odot}$. From \cite{Kovac:2014aa} (triangle; panel \kovacpanel)
+we plot an estimated $f_{\mathrm{Q}}$ by applying the residual between SFR
 based and color based galaxy classifications to the best-fit
-$f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ for
+$f_{\mathrm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ for
 low ($\delta = 0.0$) and high density environments ($\delta =
-1.5$). Similarly, from \cite{Baldry:2006aa} (diamond; panel a in Figure \ref{fig:qffit_comp}) we plot $f_{\rm{Q}}$
-derived from the best-fit $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5}
+1.5$). Similarly, from \cite{Baldry:2006aa} (diamond; panel a) we plot $f_{\mathrm{Q}}$
+derived from the best-fit $f_{\mathrm{red}}$ at $\mathcal{M} = 10^{10.5}
 \mathcal{M}_{\odot}$ for low ($\delta = 0.0$) and high density
-environment ($\delta = 1.0$). For \cite{geha12a} (cross; panel a in Figure \ref{fig:qffit_comp}), we plot $f_{\rm{Q}}$
+environment ($\delta = 1.0$). For \cite{geha12a} (cross; panel a), we plot $f_{\mathrm{Q}}$
 for their isolated galaxy sample in their mass bin closest to $10^{10.5} \mathcal{M}_{\odot}$, $\mathcal{M} = 10^{10.55} \mathcal{M}_{\odot}$.
-Finally for \cite{Peng:2010aa} (square; panel \pengpanel$ $ in Figure \ref{fig:qffit_comp}), we plot the parameterized $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ using their best-fit parameters for low ($\delta =0.0$) and high ($\delta = 1.4$) density environments.
-
-For our lowest redshift bin SDSS sample, we find that our $f_{\rm{Q}}$
+Finally for \cite{Peng:2010aa} (square; panel \pengpanel), we plot the parameterized $f_{\mathrm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ using their best-fit parameters for low ($\delta =0.0$) and high ($\delta = 1.4$) density environments.
+
+For our lowest redshift bin SDSS sample, we find that our $f_{\mathrm{Q}}$
 for low and high environments are consistent with other SDSS
-$f_{\rm{Q}}$ (or $f_{\rm{red}}$) measurements as a function of
+$f_{\mathrm{Q}}$ (or $f_{\mathrm{red}}$) measurements as a function of
 environment. For example, \cite{Baldry:2006aa} uses projected neighbor
-density environment measures ($\rm{log} \; \Sigma$) to obtain
-$f_{\rm{Q}}(\mathcal{M})$ for a range of environmental
+density environment measures ($\mathrm{log} \; \Sigma$) to obtain
+$f_{\mathrm{Q}}(\mathcal{M})$ for a range of environmental
 densities. Although the different environment measurements make direct
 comparisons difficult, in their corresponding higher environments
-($\rm{log} \; \Sigma > 0.2$ in \citealt{Baldry:2006aa})
-$f_{\rm{Q}}(\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}) \sim 0.6$
-and $f_{\rm{Q}}(\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}) \sim
+($\mathrm{log} \; \Sigma > 0.2$ in \citealt{Baldry:2006aa})
+$f_{\mathrm{Q}}(\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}) \sim 0.6$
+and $f_{\mathrm{Q}}(\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}) \sim
 0.9$, which is in agreement with our high density
-environment. Likewise, for lower environments ($\rm{log} \; \Sigma <
--0.4$ in \citealt{Baldry:2006aa}) $f_{\rm{Q}}(\mathcal{M} \sim
-10^{10.2} \mathcal{M}_{\odot}) \sim 0.4$ and $f_{\rm{Q}}(\mathcal{M}
+environment. Likewise, for lower environments ($\mathrm{log} \; \Sigma <
+-0.4$ in \citealt{Baldry:2006aa}) $f_{\mathrm{Q}}(\mathcal{M} \sim
+10^{10.2} \mathcal{M}_{\odot}) \sim 0.4$ and $f_{\mathrm{Q}}(\mathcal{M}
 \sim 10^{11.5} \mathcal{M}_{\odot}) \sim 0.8$, which also agree with
-our low density environment $f_{\rm{Q}}$. The \cite{Baldry:2006aa}
+our low density environment $f_{\mathrm{Q}}$. The \cite{Baldry:2006aa}
 points (diamond) in Figure \ref{fig:qffit_comp} reflect this
@@
 
-More recently, \cite{Tinker:2011aa}, using a group-finding algorithm on the SDSS DR7, presents the relationship between $f_{\rm{Q}}$ and overdensity for galaxies within the mass range $\rm{log} \; \mathcal{M} = [9.8, 10.1]$.
-The \cite{Tinker:2011aa} $f_{\rm{Q}}$ at the lowest and highest overdensities, $f_{\rm{Q}} \sim 0.4$ and $f_{\rm{Q}} \sim 0.6$ respectively, are consistent with our $f_{\rm{Q}}$ for low and high density environment at the lower mass limit ($\rm{log} \; \mathcal{M} \sim 10.2$).
+More recently, \cite{Tinker:2011aa}, using a group-finding algorithm on the SDSS DR7, presents the relationship between $f_{\mathrm{Q}}$ and overdensity for galaxies within the mass range $\mathrm{log} \; \mathcal{M} = [9.8, 10.1]$.
+The \cite{Tinker:2011aa} $f_{\mathrm{Q}}$ at the lowest and highest overdensities, $f_{\mathrm{Q}} \sim 0.4$ and $f_{\mathrm{Q}} \sim 0.6$ respectively, are consistent with our $f_{\mathrm{Q}}$ for low and high density environment at the lower mass limit ($\mathrm{log} \; \mathcal{M} \sim 10.2$).
 
 A modified \cite{Tinker:2011aa} sample is used in \cite{geha12a} to
-obtain $f_{\rm{Q}}$ for isolated galaxies over a wider mass range
+obtain $f_{\mathrm{Q}}$ for isolated galaxies over a wider mass range
 ($10^{7.4} \mathcal{M}_\odot$ to $10^{11.2}
 \mathcal{M}_{\odot}$). Although \cite{geha12a} probe a slightly lower
-redshift range ($ z \le 0.06$), their $f_{\rm{Q}}$ is consistent with
+redshift range ($ z \le 0.06$), their $f_{\mathrm{Q}}$ is consistent with
 our low density sample. Within the overlapping mass range, at the low
-mass end \cite{geha12a} find $f_{\rm{Q}}(\mathcal{M}_{*} \sim
+mass end \cite{geha12a} find $f_{\mathrm{Q}}(\mathcal{M}_{*} \sim
 10^{10.2} \mathcal{M}_{\odot}) \sim 0.3$ and at the high mass end they
-find $f_{\rm{Q}}(\mathcal{M}_{*} \sim 10^{11.2} \mathcal{M}_{\odot})
+find $f_{\mathrm{Q}}(\mathcal{M}_{*} \sim 10^{11.2} \mathcal{M}_{\odot})
 \sim 0.8$. Both of these values agree with our lowest redshift
-$f_{\rm{Q}}$ results in low density environment. Figure
-\ref{fig:qffit_comp} illustrates the $f_{\rm{Q}}$ agreement for
+$f_{\mathrm{Q}}$ results in low density environment. Figure
+\ref{fig:qffit_comp} illustrates the $f_{\mathrm{Q}}$ agreement for
 $\mathcal{M}_{*} = 10^{10.5} \mathcal{M}_{\odot}$.
@@
 
-For $z > 0.2$, we compare our PRIMUS $f_{\rm{Q}}$ results to the $f_{\rm{red}}$ (or $1-f_{\rm{blue}}$) results from the zCOSMOS Redshift Survey (\citealt{Iovino:2010aa, Cucciati:2010aa, Kovac:2014aa}), which covers a similar redshift range as PRIMUS.
-\cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, and \cite{Kovac:2014aa} using a mass-complete galaxy sample derived from zCOSMOS and a group catalog, 3D local density contrast, and overdensity environment measurements, respectively, compare $f_{\rm{red}}$ with respect to environment.
-The $f_{\rm{blue}}$ for group and isolated galaxies from \cite{Iovino:2010aa} are generally inconsistent with our $1-f_{\rm{Q}}$ for high and low density environments.
-
-Similarly, $f_{\rm{red}}$ for high and low overdensities in
-\cite{Kovac:2014aa} are  greater overall than the PRIMUS $f_{\rm{Q}}$
+For $z > 0.2$, we compare our PRIMUS $f_{\mathrm{Q}}$ results to the $f_{\mathrm{red}}$ (or $1-f_{\mathrm{blue}}$) results from the zCOSMOS Redshift Survey (\citealt{Iovino:2010aa, Kovac:2014aa}), which covers a similar redshift range as PRIMUS.
+\cite{Iovino:2010aa}, and \cite{Kovac:2014aa} using a mass-complete galaxy sample derived from zCOSMOS and a group catalog, 3D local density contrast, and overdensity environment measurements, respectively, compare $f_{\mathrm{red}}$ with respect to environment.
+The $f_{\mathrm{blue}}$ for group and isolated galaxies from \cite{Iovino:2010aa} are generally inconsistent with our $1-f_{\mathrm{Q}}$ for high and low density environments.
+
+Similarly, $f_{\mathrm{red}}$ for high and low overdensities in
+\cite{Kovac:2014aa} are  greater overall than the PRIMUS $f_{\mathrm{Q}}$
 values in high and low density environments. However,
@@
 between classifying the quiescent population using color and SFR due to dust-reddening in star-forming galaxies.
-For their lower redshift bin ($0.1 < z < 0.4$) \cite{Kovac:2014aa} find that their $f_{\rm{Q}}$ defined by color is greater than $f_{\rm{Q}}$ defined by SFR by roughly $0.2$.
-While for their higher redshift bin ($0.4 < z < 0.7$) they find a difference of $0.15-0.19$.
-Although \cite{Kovac:2014aa} does not elaborate on how the galaxy classification discrepancy applies to the different environments, if we simply account for the difference uniformly for $f_{\rm{red}}$ at all environments, the \cite{Kovac:2014aa} results in their lower redshift bin are roughly consistent with our $f_{\rm{Q}}$ at high and low density environments.
-Even accounting for the dust-reddening of $f_{\rm{red}}$, \cite{Kovac:2014aa} finds a significantly higher $f_{\rm{Q}}$ in their higher redshift bin.
-
-In Figure \ref{fig:qf}, the $f_{\rm{Q}}$ evolution with respect to
+For their lower redshift bin ($0.1 < z < 0.4$) \cite{Kovac:2014aa} find that their $f_{\mathrm{Q}}$ defined by color is greater than $f_{\mathrm{Q}}$ defined by SFR by roughly $0.2$.
+While for their higher redshift bin ($0.4 < z < 0.7$) the difference is $0.15-0.19$.
+Although \cite{Kovac:2014aa} does not elaborate on how the galaxy classification discrepancy applies to the different environments, if we simply account for the difference uniformly for $f_{\mathrm{red}}$ at all environments, the \cite{Kovac:2014aa} results in their lower redshift bin are roughly consistent with our $f_{\mathrm{Q}}$ at high and low density environments.
+Even accounting for the dust-reddening of $f_{\mathrm{red}}$, \cite{Kovac:2014aa} finds a significantly higher $f_{\mathrm{Q}}$ in their higher redshift bin.
+
+In Figure \ref{fig:qf}, the $f_{\mathrm{Q}}$ evolution with respect to
 mass reveals, qualitatively, little mass dependence in the
@@
 adjusting the fiducial mass only shifted the overall
-$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$, but did not change the
-$f_{\rm{Q}}$ evolutionary trend. The consistency in the $f_{\rm{Q}}$
-evolutionary trends when the fiducial mass is changed suggest that
-$f_{\rm{Q}}$ evolution exhibit little mass dependence within the 
+$f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$, but did not change the
+$f_{\mathrm{Q}}$ evolutionary trend. The consistency in the $f_{\mathrm{Q}}$
+evolutionary trends over change in fiducial mass suggests that
+$f_{\mathrm{Q}}$ evolution exhibit little mass dependence within the 
 mass range probed in our analysis. In contrast to
 the weak mass dependence we observe in our results,
-\cite{Iovino:2010aa} find significantly different $f_{\rm{Q}}$
+\cite{Iovino:2010aa} find significantly different $f_{\mathrm{Q}}$
 evolution at $\mathcal{M} \sim 10^{11} \mathcal{M}_{\odot}$ and
@@
 
-Meanwhile in their mass bin most comparable to $\mathcal{M}_{\rm{fid}}
+Meanwhile in their mass bin most comparable to $\mathcal{M}_{\mathrm{fid}}
 \sim 10^{10.5} \mathcal{M}_{\odot}$ ($10^{10.3} \mathcal{M}_{\odot} -
 10^{10.8} \mathcal{M}_{\odot}$), \cite{Iovino:2010aa} finds that
-$f_{\rm{blue}}$ evolves by $\sim 0.1$ from $z = 0.5$ to $0.25$ for
+$f_{\mathrm{blue}}$ evolves by $\sim 0.1$ from $z = 0.5$ to $0.25$ for
 group galaxies and by $\sim 0.3$ from $z=0.55$ to $0.3$ for isolated
@@
 mass bins beyond the fiducial masses we explore, \cite{Iovino:2010aa}
-find a strong mass dependence with $f_{\rm{Q}}$ evolving significantly
+find a strong mass dependence with $f_{\mathrm{Q}}$ evolving significantly
 more in lower mass bins. While our sample from PRIMUS provides larger
@@
 \mathcal{M}_{\odot}$ for our $z \sim 0.7$ bin). Consequently our
-results cannot rule out mass dependence in the $f_{\rm{Q}}$ evolution
+results cannot rule out mass dependence in the $f_{\mathrm{Q}}$ evolution
 at lower masses.
@@
 environments have a significantly greater
-$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ than the low density
+$f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ than the low density
 environments. This finding is in agreement with the zCOSMOS results
 from \cite{Cucciati:2010aa} and \cite{Kovac:2014aa}. As illustrated in
-panel (\kovacpanel) of Figure \ref{fig:qffit_comp}, \cite{Kovac:2014aa} finds $f_{\rm{Q}}$ in high density environment
-significantly greater than $f_{\rm{Q}}$ at low density
+panel (\kovacpanel) of Figure \ref{fig:qffit_comp}, \cite{Kovac:2014aa} finds $f_{\mathrm{Q}}$ in high density environment
+significantly greater than $f_{\mathrm{Q}}$ at low density
 environment. Moreover, since galaxy color serves as a proxy for SFR,
@@
 
-In Section \ref{sec:env_qf_evol}, we showed that $f_{\rm{Q}}$ in
+In Section \ref{sec:env_qf_evol}, we showed that $f_{\mathrm{Q}}$ in
 low density environments evolves over cosmic time. From this trend we
@@
 from zCOSMOS, plotted in Figure \ref{fig:qffit_comp}  panel (\iovinopanel), also find that
-$f_{\rm{Q}}$ in low density environment increases with decreasing redshift.
-On the other hand \cite{Kovac:2014aa}, also from zCOSMOS, presents that $f_{\rm{Q}}$ in low density environment decreases over cosmic time.
-While the uncertainties for the parameterized $f_{\rm{Q}}$ are not listed, and thus not shown in Figure \ref{fig:qffit_comp}, once they are accounted for, \cite{Kovac:2014aa} find little $f_{\rm{Q}}$ evolution over cosmic time.
-However, once we account for the dust-reddening of the $f_{\rm{red}}$, we find a more significant decrease over cosmic time (Figure \ref{fig:qffit_comp} panel \kovacpanel).
+$f_{\mathrm{Q}}$ in low density environment increases with decreasing redshift.
+On the other hand \cite{Kovac:2014aa}, also from zCOSMOS, presents that $f_{\mathrm{Q}}$ in low density environment decreases over cosmic time.
+While the uncertainties for the parameterized $f_{\mathrm{Q}}$ are not listed, and thus not shown in Figure \ref{fig:qffit_comp}, once they are accounted for, \cite{Kovac:2014aa} find no significant $f_{\mathrm{Q}}$ evolution over cosmic time.
+However, once we account for the dust-reddening of the $f_{\mathrm{red}}$, we find a more significant decrease over cosmic time (Figure \ref{fig:qffit_comp} panel \kovacpanel).
 
 Furthermore, in Section \ref{sec:env_qf_evol}, our comparison of the
-$f_{\rm{Q}}$ evolution between the lowest density environment and the
+$f_{\mathrm{Q}}$ evolution between the lowest density environment and the
 highest density environment revealed a modicum of evidence for the
@@
 \ref{fig:qffit_comp} shows that there are indeed pronounced
-discrepancies between the $f_{\rm{Q}}$ evolution in different
+discrepancies between the $f_{\mathrm{Q}}$ evolution in different
 environments. Group galaxies in \cite{Iovino:2010aa} have higher
-overall $f_{\rm{Q}}$ than isolated galaxies. However, unlike our
-results, which find a greater $f_{\rm{Q}}$ evolution at higher density
+overall $f_{\mathrm{Q}}$ than isolated galaxies. However, unlike our
+results, which find a greater $f_{\mathrm{Q}}$ evolution at higher density
 environments, \cite{Iovino:2010aa} finds the opposite environment
-dependence that there is a significantly greater $f_{\rm{Q}}$
+dependence that there is a significantly greater $f_{\mathrm{Q}}$
 evolution for isolated galaxies.
 
-Next, \cite{Kovac:2014aa} also find that overall $f_{\rm{Q}}$ is
+Next, \cite{Kovac:2014aa} also find that overall $f_{\mathrm{Q}}$ is
 greater in high density than in low density environments. Like their
-low density environment $f_{\rm{Q}}$ evolution, $f_{\rm{Q}}$ in high
+low density environment $f_{\mathrm{Q}}$ evolution, $f_{\mathrm{Q}}$ in high
 density environment decreases over cosmic time between their two
-redshift bins. Although the decrease in $f_{\rm{Q}}$ over cosmic time
+redshift bins. Although the decrease in $f_{\mathrm{Q}}$ over cosmic time
 conflicts with our results, \cite{Kovac:2014aa} finds a greater (less
-negative) $f_{\rm{Q}}$ evolution in high density environments relative
+negative) $f_{\mathrm{Q}}$ evolution in high density environments relative
 to low density environments, suggesting an environment dependence that
 is in the same direction as our results. We note that the negative
-slopes of the $f_{\rm{Q}}$ evolution in both environments are enhanced
+slopes of the $f_{\mathrm{Q}}$ evolution in both environments are enhanced
 in Figure \ref{fig:qffit_comp} due to the dust-reddening
@@
 % Removed in order to tone down the criticism of 
-%However, even without the correction (not shown), in their best-fit $f_{\rm{Q}}$ results, the same evolutionary trends mentioned above are observed.
+%However, even without the correction (not shown), in their best-fit $f_{\mathrm{Q}}$ results, the same evolutionary trends mentioned above are observed.
 
@@
 In addition, our sample covers a larger portion of the sky.
-Our SDSS-{\em GALEX} sample covers $2,505 \;\rm{deg}^2$.
-More comparably, our PRIMUS sample covers $5.5 \;\rm{deg}^2$, which is over 3 times the sky coverage of zCOSMOS ($1.7 \;\rm{deg}^2$).
+Our SDSS-{\em GALEX} sample covers $2,505 \;\mathrm{deg}^2$.
+More comparably, our PRIMUS sample covers $5.5 \;\mathrm{deg}^2$, over 3 times the sky coverage of zCOSMOS ($1.7 \;\mathrm{deg}^2$).
 Furthermore, our PRIMUS sample is constructed from five independent fields which allows us to significantly reduce the effects of cosmic variance.
@@
 \mathcal{M}_{\odot}$ over $0.1 < z < 0.8$. For the actual sample used
-to obtain the best-fit $f_{\rm{Q}}$ values in Figure
+to obtain the best-fit $f_{\mathrm{Q}}$ values in Figure
 \ref{fig:qffit_comp} \cite{Iovino:2010aa} has $617$ galaxies. In
@@
 of galaxies. While there is a considerable difference in the overall
-$f_{\rm{Q}}$ between our results and those of \cite{Iovino:2010aa},
+$f_{\mathrm{Q}}$ between our results and those of \cite{Iovino:2010aa},
 the use of different methodologies, particularly for galaxy
 classification and environment measurements, make such comparisons
-ambiguous. On the other hand, the discrepancies in the $f_{\rm{Q}}$
+ambiguous. On the other hand, the discrepancies in the $f_{\mathrm{Q}}$
 evolutionary trends with our results may be explained by the limited
@@
 their results are adjusted for the dust-reddening, we
-find that their overall $f_{\rm{Q}}$ is more or less consistent with
-our overall $f_{\rm{Q}}$. However, it is difficult to explain the
-significant discrepancies in the $f_{\rm{Q}}$ evolutionary trends.
+find that their overall $f_{\mathrm{Q}}$ is more or less consistent with
+our overall $f_{\mathrm{Q}}$. However, it is difficult to explain the
+significant discrepancies in the $f_{\mathrm{Q}}$ evolutionary trends.
 The significant overdenities observed in the COSMOS field at $z \sim 0.35$ and $z \sim 0.7$ (\citealt{Lilly:2009aa, Kovac:2010ab}) may have a significant effect on the zCOSMOS results and offer a possible explanation for the discrepancies.
@@
     redshift range.
-	\item For all subsamples, $f_{\rm{Q}}$ increases monotonically with
+	\item For all subsamples, $f_{\mathrm{Q}}$ increases monotonically with
     galaxy stellar mass, showing a clear mass dependence and
@@
     relations.
-	\item We illustrate that $f_{\rm{Q}}$ in high density environments
-    is greater than $f_{\rm{Q}}$ in low density environments
+	\item We illustrate that $f_{\mathrm{Q}}$ in high density environments
+    is greater than $f_{\mathrm{Q}}$ in low density environments
     regardless of mass and out to redshift $z\sim 0.7$. This result
@@
     more massive.
-	\item $f_{\rm{Q}}$ increases significantly with redshift for both
+	\item $f_{\mathrm{Q}}$ increases significantly with redshift for both
     low and high density environments. For high density environment,
     this trend is the Butcher-Oemler effect. Furthermore, the
-    $f_{\rm{Q}}$ evolution in low density environment suggest the
+    $f_{\mathrm{Q}}$ evolution in low density environment suggest the
     existence of internal environment-independent mechanisms for
     ending star formation.
-	\item Comparison of the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$
+	\item Comparison of the $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$
     evolution for a range of environment classifications reveals that
-    the since $z = 0.8$, $f_{\rm{Q}}$ has evolved by a greater amount
+    the since $z = 0.8$, $f_{\mathrm{Q}}$ has evolved by a greater amount
     in the highest density environments. For our purest high
-    environment sample ($n_{\rm{env}} > 7$), the total $f_{\rm{Q}}$
-    evolution is $\sim 0.1$ greater than the total $f_{\rm{Q}}$
+    environment sample ($n_{\mathrm{env}} > 7$), the total $f_{\mathrm{Q}}$
+    evolution is $\sim 0.1$ greater than the total $f_{\mathrm{Q}}$
     evolution in low density environment, revealing a moderate
@@
   Peng:2010aa}). The significant redshift evolution of the
-$f_{\rm{Q}}$ in low density environments confirms the existence of
+$f_{\mathrm{Q}}$ in low density environments confirms the existence of
 internal mechanisms that end star-forming in galaxies.
 
-Furthermore, the greater $f_{\rm{Q}}$ evolution in the highest density
+Furthermore, the greater $f_{\mathrm{Q}}$ evolution in the highest density
 environment relative to low density environments suggests that in
@@
 \bigskip 
-We gratefully acknowledge insightful conversations with Katarina Kova\u{c} and Ying-Jie Peng. 
-We also thank Marla Geha for providing published quiescent fraction results in electronic format.
+We acknowledge Katarina Kova\u{c} and Ying-Jie Peng for  insightful discussions. We also thank Marla Geha for providing published quiescent fraction results in electronic format.
 

### 2014-12-19 qfenv_paper/qf_environment.tex
Funding + acknowledgements

@@
 (SDSS). Our stellar mass limited galaxy sample consists of $\sim
-13,000$ PRIMUS galaxies within $z = 0.2-0.8$ and $\sim 64,000$ SDSS
+14,000$ PRIMUS galaxies within $z = 0.2-0.8$ and $\sim 64,000$ SDSS
 galaxies within $z = 0.05-0.12$. We classify the galaxies as quiescent
@@
 \bigskip 
-We acknowledge Katarina Kova\u{c} and Ying-Jie Peng for  insightful discussions. We also thank Marla Geha for providing published quiescent fraction results in electronic format.
-
-Support for this work was provided by .... ALC acknowledges support from NSF CAREER award
-
+CH and MB were supported by NSF-AST-1109432 and NSF-AST-0908354.
+MB was also supported by NSF-AST-1211644.
+ALC acknowledges support from NSF CAREER award.
+We acknowledge Katarina Kova\u{c} and Ying-Jie Peng for  insightful discussions.
+We also thank Marla Geha for providing published quiescent fraction results in electronic format.
+
+The Galaxy Evolution Explorer (GALEX) is a NASA Small Explorer, launched in April 2003, whose mission was developed in cooperation with the Centre National d?Etudes Spatiales of France and the Korean Ministry of Science and Technology.
+Funding for the SDSS and SDSS-II has been provided by the Alfred P.
+Sloan Foundation, the Participating Institutions, the National Science Foundation, the U.S.
+Department of Energy, the National Aeronautics and Space Administration, the Japanese Monbukagakusho, the Max Planck Society, and the Higher Education Funding Council for England.
+The SDSS Web Site is http://www.sdss.org.
 The SDSS is managed by the Astrophysical Research Consortium for the Participating Institutions.
-The Participating Institutions are the American Museum of Natural History, Astrophysical Institute Potsdam, University of Basel, University of Cambridge, Case Western Reserve University, University of Chicago, Drexel University, Fermilab, the Institute for Advanced Study, the Japan Participation Group, Johns Hopkins University, the Joint Institute for Nuclear Astrophysics, the Kavli Institute for Particle Astrophysics and Cosmology, the Korean Scientist Group, the Chinese Academy of Sciences (LAMOST), Los Alamos National Laboratory, the Max-Planck- Institute for Astronomy (MPIA), the Max-Planck-Institute for Astrophysics (MPA), New Mexico State University, Ohio State University, University of Pittsburgh, University of Portsmouth, Princeton University, the United States Naval Observatory, and the University of Washington.
+
 %

### 2014-12-24 qfenv_paper/ApJ submission/cover_apj.tex
draft for submission

\documentclass{letter}
\usepackage{setspace}

\begin{document}

\begin{flushleft}
\begin{singlespace}
Department of Physics\\
New York University\\
4 Washington Place, Room 424\\
New York, NY 10003
\end{singlespace}

\vspace{0.5cm}

Dec 22, 2014

\vspace{0.5cm}

Dear Editor,

Please find enclosed our paper "PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at \lowercase{\textit{z}}$<0.8$," which we are submitting exclusively to the Astrophysical Journal.  Please contact me for any correspondence concerning our manuscript, my email address is \texttt{chh327@nyu.edu}.

\vspace{0.5cm}

Sincerely,

ChangHoon Hahn
\end{flushleft}

\end{document}

### 2014-12-24 qfenv_paper/ApJ submission/qf_environment.tex
draft for submission

--- 2014-12-19 qfenv_paper/qf_environment.tex
@@
 \usepackage{amsmath}
-\usepackage{natbib}
 \usepackage{footnote}
@@
 
-\title{PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 0.8$}
+\title{PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at \lowercase{\textit{z}}$<0.8$}
 \author{
@@
 }
-\altaffiltext{1}{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Place, New York, NY 10003}
+\altaffiltext{1}{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Place, New York, NY 10003; chh327@nyu.edu}
 \altaffiltext{2}{Department of Physics and Astronomy, Siena College, 515 Loudon Road, Loudonville, NY 12211}
@@
 \altaffiltext{6}{Steward Observatory, University of Arizona, 933 North Cherry Avenue, Tucson, AZ 85721} 
-\altaffiltext{7}{Department of Physics and Astronomy, The Johns Hopkins University, 3400 North Charles Street, Baltimore, MD 21218} 
+\altaffiltext{7}{Hubble Fellow; Department of Physics and Astronomy, The Johns Hopkins University, 3400 North Charles Street, Baltimore, MD 21218} 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{abstract}
-
+\keywords{cosmology: observations --- galaxies: evolution --- galaxies: groups --- galaxies: star formation}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
         \leavevmode
-        \epsscale{1.2}
-	\plotone{fig_edp_sdss_z0_05_0_12_primus_z0_2_1_0_Mr_redshift.png}
+	\includegraphics[scale=0.475]{fig1.pdf}
         \caption{Absolute magnitude $M_{r}$ versus redshift for our mass complete galaxy sample (black squares) with the Environment Defining Population (red circles) plotted on top.
@@
     \leavevmode
-    \epsfig{file=fig_envcount_cylr2_5h35_thresh75_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_primuszerr_masslimit_edgecut_histogram.png, width=0.45\textwidth}
+    \includegraphics[scale=0.48]{fig2.pdf}
     \caption{Normalized distribution of environment measurements ($n_{\mathrm{env}}$) for our mass complete galaxy sample within the survey edges.
@@
     \leavevmode
-    \epsfig{file=fig_smf_cylr2_50000h35_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_2envbin_lowenv0_5_highenv3_0_lit_primuszerr.eps, height=0.75\textwidth,angle=90}
+    \epsfig{file=fig3.eps, height=0.75\textwidth,angle=90}
      \caption{Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) galaxies in 
@@
         \leavevmode
-        \epsfig{file=fig_qf_cylr2_50000h35_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_lit_primuszerr.eps, height=0.75\textwidth,angle=90}
+        \epsfig{file=fig4.eps, height=0.75\textwidth,angle=90}
         \caption{Evolution of the quiescent fraction $f_{\mathrm{Q}}$ for
@@
         \epsscale{1.0}
-        \epsfig{file=fig_qffit_cylr2_50000h35_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmasscomp11_0_10_5_lit_primuszerr.eps, height=0.45\textwidth}
+        \epsfig{file=fig5, height=0.45\textwidth}
         \caption{The evolution of the quiescent fraction at fiducial
@@
         \epsscale{1.0}
-        \epsfig{file=fig_qffit_cylr2_50000h35_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmass10_5_lit_primuszerr_baldry_geha_iovino_kovac_peng_envthresh_kovacoffset.eps, height=\textwidth, angle=90}
+        \epsfig{file=fig6.eps, height=\textwidth, angle=90}
         \caption{$f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}=10^{10.5} \mathcal{M}_\odot)$ evolution compared to $f_{\mathrm{red}}(\mathcal{M}_{*} \sim 10^{10.5} \; \mathcal{M}_{\odot})$ in the literature: \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross) from SDSS (panel a), \cite{Iovino:2010aa} (empty square) and \cite{Kovac:2014aa} (triangle) from zCOSMOS (panel \kovacpanel), and \cite{Peng:2010aa} from both SDSS and zCOSMOS (panel \pengpanel).
@@
 
-The Galaxy Evolution Explorer (GALEX) is a NASA Small Explorer, launched in April 2003, whose mission was developed in cooperation with the Centre National d?Etudes Spatiales of France and the Korean Ministry of Science and Technology.
+Funding for PRIMUS has been provided by NSF grants AST-0607701, 0908246, 0908442, 0908354, and NASA grant 08-ADP08-0019.
+The Galaxy Evolution Explorer (GALEX) is a NASA Small Explorer, launched in April 2003, whose mission was developed in cooperation with the Centre National d`Etudes Spatiales of France and the Korean Ministry of Science and Technology.
 Funding for the SDSS and SDSS-II has been provided by the Alfred P.
@@
 %
-\bibliography{PRIMUS}
+\bibliographystyle{apj}
+\begin{thebibliography}{}
+\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+
+\bibitem[{{Abazajian} {et~al.}(2009){Abazajian}, {Adelman-McCarthy},
+  {Ag{\"u}eros}, {Allam}, {Allende Prieto}, {An}, {Anderson}, {Anderson},
+  {Annis}, {Bahcall}, \& et~al.}]{Abazajian:2009aa}
+{Abazajian}, K.~N., {Adelman-McCarthy}, J.~K., {Ag{\"u}eros}, M.~A., {et~al.}
+  2009, \apjs, 182, 543
+
+\bibitem[{{Baldry} {et~al.}(2006){Baldry}, {Balogh}, {Bower}, {Glazebrook},
+  {Nichol}, {Bamford}, \& {Budavari}}]{Baldry:2006aa}
+{Baldry}, I.~K., {Balogh}, M.~L., {Bower}, R.~G., {et~al.} 2006, \mnras, 373,
+  469
+
+\bibitem[{{Baldry} {et~al.}(2008){Baldry}, {Glazebrook}, \&
+  {Driver}}]{Baldry:2008aa}
+{Baldry}, I.~K., {Glazebrook}, K., \& {Driver}, S.~P. 2008, \mnras, 388, 945
+
+\bibitem[{{Balogh} {et~al.}(2000){Balogh}, {Navarro}, \&
+  {Morris}}]{Balogh:2000aa}
+{Balogh}, M.~L., {Navarro}, J.~F., \& {Morris}, S.~L. 2000, \apj, 540, 113
+
+\bibitem[{{Behroozi} {et~al.}(2013){Behroozi}, {Marchesini}, {Wechsler},
+  {Muzzin}, {Papovich}, \& {Stefanon}}]{Behroozi:2013aa}
+{Behroozi}, P.~S., {Marchesini}, D., {Wechsler}, R.~H., {et~al.} 2013, \apjl,
+  777, L10
+
+\bibitem[{{Bekki}(2009)}]{Bekki:2009aa}
+{Bekki}, K. 2009, \mnras, 399, 2221
+
+\bibitem[{{Bell} {et~al.}(2004){Bell}, {Wolf}, {Meisenheimer}, {Rix}, {Borch},
+  {Dye}, {Kleinheinrich}, {Wisotzki}, \& {McIntosh}}]{Bell:2004aa}
+{Bell}, E.~F., {Wolf}, C., {Meisenheimer}, K., {et~al.} 2004, \apj, 608, 752
+
+\bibitem[{{Bell} {et~al.}(2005){Bell}, {Papovich}, {Wolf}, {Le Floc'h},
+  {Caldwell}, {Barden}, {Egami}, {McIntosh}, {Meisenheimer},
+  {P{\'e}rez-Gonz{\'a}lez}, {Rieke}, {Rieke}, {Rigby}, \& {Rix}}]{bell05a}
+{Bell}, E.~F., {Papovich}, C., {Wolf}, C., {et~al.} 2005, \apj, 625, 23
+
+\bibitem[{{Bernardi} {et~al.}(2007){Bernardi}, {Hyde}, {Sheth}, {Miller}, \&
+  {Nichol}}]{Bernardi:2007aa}
+{Bernardi}, M., {Hyde}, J.~B., {Sheth}, R.~K., {Miller}, C.~J., \& {Nichol},
+  R.~C. 2007, \aj, 133, 1741
+
+\bibitem[{{Blanton} {et~al.}(2006){Blanton}, {Eisenstein}, {Hogg}, \&
+  {Zehavi}}]{Blanton:2006aa}
+{Blanton}, M.~R., {Eisenstein}, D., {Hogg}, D.~W., \& {Zehavi}, I. 2006, \apj,
+  645, 977
+
+\bibitem[{{Blanton} {et~al.}(2011){Blanton}, {Kazin}, {Muna}, {Weaver}, \&
+  {Price-Whelan}}]{Blanton:2011aa}
+{Blanton}, M.~R., {Kazin}, E., {Muna}, D., {Weaver}, B.~A., \& {Price-Whelan},
+  A. 2011, \aj, 142, 31
+
+\bibitem[{{Blanton} {et~al.}(2005{\natexlab{a}}){Blanton}, {Lupton},
+  {Schlegel}, {Strauss}, {Brinkmann}, {Fukugita}, \&
+  {Loveday}}]{Blanton:2005ab}
+{Blanton}, M.~R., {Lupton}, R.~H., {Schlegel}, D.~J., {et~al.}
+  2005{\natexlab{a}}, \apj, 631, 208
+
+\bibitem[{{Blanton} \& {Moustakas}(2009)}]{blanton09a}
+{Blanton}, M.~R., \& {Moustakas}, J. 2009, \araa, 47, 159
+
+\bibitem[{{Blanton} \& {Roweis}(2007)}]{Blanton:2007aa}
+{Blanton}, M.~R., \& {Roweis}, S. 2007, \aj, 133, 734
+
+\bibitem[{{Blanton} {et~al.}(2005{\natexlab{b}}){Blanton}, {Schlegel},
+  {Strauss}, {Brinkmann}, {Finkbeiner}, {Fukugita}, {Gunn}, {Hogg},
+  {Ivezi{\'c}}, {Knapp}, {Lupton}, {Munn}, {Schneider}, {Tegmark}, \&
+  {Zehavi}}]{Blanton:2005aa}
+{Blanton}, M.~R., {Schlegel}, D.~J., {Strauss}, M.~A., {et~al.}
+  2005{\natexlab{b}}, \aj, 129, 2562
+
+\bibitem[{{Bolzonella} {et~al.}(2010){Bolzonella}, {Kova{\v c}}, {Pozzetti},
+  {Zucca}, {Cucciati}, {Lilly}, {Peng}, {Iovino}, {Zamorani}, {Vergani},
+  {Tasca}, {Lamareille}, {Oesch}, {Caputi}, {Kampczyk}, {Bardelli}, {Maier},
+  {Abbas}, {Knobel}, {Scodeggio}, {Carollo}, {Contini}, {Kneib}, {Le
+  F{\`e}vre}, {Mainieri}, {Renzini}, {Bongiorno}, {Coppa}, {de la Torre}, {de
+  Ravel}, {Franzetti}, {Garilli}, {Le Borgne}, {Le Brun}, {Mignoli},
+  {Pell{\'o}}, {Perez-Montero}, {Ricciardelli}, {Silverman}, {Tanaka},
+  {Tresse}, {Bottini}, {Cappi}, {Cassata}, {Cimatti}, {Guzzo}, {Koekemoer},
+  {Leauthaud}, {Maccagni}, {Marinoni}, {McCracken}, {Memeo}, {Meneux},
+  {Porciani}, {Scaramella}, {Aussel}, {Capak}, {Halliday}, {Ilbert},
+  {Kartaltepe}, {Salvato}, {Sanders}, {Scarlata}, {Scoville}, {Taniguchi}, \&
+  {Thompson}}]{Bolzonella:2010aa}
+{Bolzonella}, M., {Kova{\v c}}, K., {Pozzetti}, L., {et~al.} 2010, \aap, 524,
+  A76
+
+\bibitem[{{Borch} {et~al.}(2006){Borch}, {Meisenheimer}, {Bell}, {Rix}, {Wolf},
+  {Dye}, {Kleinheinrich}, {Kovacs}, \& {Wisotzki}}]{borch06a}
+{Borch}, A., {Meisenheimer}, K., {Bell}, E.~F., {et~al.} 2006, \aap, 453, 869
+
+\bibitem[{{Bundy} {et~al.}(2006){Bundy}, {Ellis}, {Conselice}, {Taylor},
+  {Cooper}, {Willmer}, {Weiner}, {Coil}, {Noeske}, \& {Eisenhardt}}]{bundy06a}
+{Bundy}, K., {Ellis}, R.~S., {Conselice}, C.~J., {et~al.} 2006, \apj, 651, 120
+
+\bibitem[{{Butcher} \& {Oemler}(1984)}]{Butcher:1984aa}
+{Butcher}, H., \& {Oemler}, Jr., A. 1984, \apj, 285, 426
+
+\bibitem[{{Chabrier}(2003)}]{Chabrier:2003aa}
+{Chabrier}, G. 2003, \pasp, 115, 763
+
+\bibitem[{{Coil} {et~al.}(2011){Coil}, {Blanton}, {Burles}, {Cool},
+  {Eisenstein}, {Moustakas}, {Wong}, {Zhu}, {Aird}, {Bernstein}, {Bolton}, \&
+  {Hogg}}]{Coil:2011aa}
+{Coil}, A.~L., {Blanton}, M.~R., {Burles}, S.~M., {et~al.} 2011, \apj, 741, 8
+
+\bibitem[{{Conroy} \& {Gunn}(2010)}]{Conroy:2010aa}
+{Conroy}, C., \& {Gunn}, J.~E. 2010, {FSPS: Flexible Stellar Population
+  Synthesis}, astrophysics Source Code Library, ascl:1010.043
+
+\bibitem[{{Cool} {et~al.}(2013){Cool}, {Moustakas}, {Blanton}, {Burles},
+  {Coil}, {Eisenstein}, {Wong}, {Zhu}, {Aird}, {Bernstein}, {Bolton}, {Hogg},
+  \& {Mendez}}]{Cool:2013aa}
+{Cool}, R.~J., {Moustakas}, J., {Blanton}, M.~R., {et~al.} 2013, \apj, 767, 118
+
+\bibitem[{{Cooper} {et~al.}(2005){Cooper}, {Newman}, {Madgwick}, {Gerke},
+  {Yan}, \& {Davis}}]{Cooper:2005aa}
+{Cooper}, M.~C., {Newman}, J.~A., {Madgwick}, D.~S., {et~al.} 2005, \apj, 634,
+  833
+
+\bibitem[{{Cooper} {et~al.}(2008){Cooper}, {Newman}, {Weiner}, {Yan},
+  {Willmer}, {Bundy}, {Coil}, {Conselice}, {Davis}, {Faber}, {Gerke},
+  {Guhathakurta}, {Koo}, \& {Noeske}}]{cooper08a}
+{Cooper}, M.~C., {Newman}, J.~A., {Weiner}, B.~J., {et~al.} 2008, \mnras, 383,
+  1058
+
+\bibitem[{{Cooper} {et~al.}(2010){Cooper}, {Coil}, {Gerke}, {Newman}, {Bundy},
+  {Conselice}, {Croton}, {Davis}, {Faber}, {Guhathakurta}, {Koo}, {Lin},
+  {Weiner}, {Willmer}, \& {Yan}}]{Cooper:2010aa}
+{Cooper}, M.~C., {Coil}, A.~L., {Gerke}, B.~F., {et~al.} 2010, \mnras, 409, 337
+
+\bibitem[{{Croton} {et~al.}(2006){Croton}, {Springel}, {White}, {De Lucia},
+  {Frenk}, {Gao}, {Jenkins}, {Kauffmann}, {Navarro}, \&
+  {Yoshida}}]{Croton:2006aa}
+{Croton}, D.~J., {Springel}, V., {White}, S.~D.~M., {et~al.} 2006, \mnras, 365,
+  11
+
+\bibitem[{{Cucciati} {et~al.}(2010){Cucciati}, {Iovino}, {Kova{\v c}},
+  {Scodeggio}, {Lilly}, {Bolzonella}, {Bardelli}, {Vergani}, {Tasca}, {Zucca},
+  {Zamorani}, {Pozzetti}, {Knobel}, {Oesch}, {Lamareille}, {Caputi},
+  {Kampczyk}, {Tresse}, {Maier}, {Carollo}, {Contini}, {Kneib}, {Le F{\`e}vre},
+  {Mainieri}, {Renzini}, {Bongiorno}, {Coppa}, {de la Torre}, {de Ravel},
+  {Franzetti}, {Garilli}, {Le Borgne}, {Le Brun}, {Mignoli}, {Pell{\`o}},
+  {Peng}, {Perez-Montero}, {Ricciardelli}, {Silverman}, {Tanaka}, {Koekemoer},
+  {Scoville}, {Abbas}, {Bottini}, {Cappi}, {Cassata}, {Cimatti}, {Guzzo},
+  {Leauthaud}, {Maccagni}, {Marinoni}, {McCracken}, {Memeo}, {Meneux},
+  {Porciani}, \& {Scaramella}}]{Cucciati:2010aa}
+{Cucciati}, O., {Iovino}, A., {Kova{\v c}}, K., {et~al.} 2010, \aap, 524, A2
+
+\bibitem[{{Dekel} \& {Birnboim}(2008)}]{Dekel:2008aa}
+{Dekel}, A., \& {Birnboim}, Y. 2008, \mnras, 383, 119
+
+\bibitem[{{Desai} {et~al.}(2007){Desai}, {Dalcanton}, {Arag{\'o}n-Salamanca},
+  {Jablonka}, {Poggianti}, {Gogarten}, {Simard}, {Milvang-Jensen}, {Rudnick},
+  {Zaritsky}, {Clowe}, {Halliday}, {Pell{\'o}}, {Saglia}, \&
+  {White}}]{desai07a}
+{Desai}, V., {Dalcanton}, J.~J., {Arag{\'o}n-Salamanca}, A., {et~al.} 2007,
+  \apj, 660, 1151
+
+\bibitem[{Dressler(1980)}]{dressler80a}
+Dressler, A. 1980, \apj, 236, 351
+
+\bibitem[{{Dressler}(1984)}]{dressler84a}
+{Dressler}, A. 1984, \araa, 22, 185
+
+\bibitem[{{Faber} {et~al.}(2007){Faber}, {Willmer}, {Wolf}, {Koo}, {Weiner},
+  {Newman}, {Im}, {Coil}, {Conroy}, {Cooper}, {Davis}, {Finkbeiner}, {Gerke},
+  {Gebhardt}, {Groth}, {Guhathakurta}, {Harker}, {Kaiser}, {Kassin},
+  {Kleinheinrich}, {Konidaris}, {Kron}, {Lin}, {Luppino}, {Madgwick},
+  {Meisenheimer}, {Noeske}, {Phillips}, {Sarajedini}, {Schiavon}, {Simard},
+  {Szalay}, {Vogt}, \& {Yan}}]{Faber:2007aa}
+{Faber}, S.~M., {Willmer}, C.~N.~A., {Wolf}, C., {et~al.} 2007, \apj, 665, 265
+
+\bibitem[{{Fasano} {et~al.}(2000){Fasano}, {Poggianti}, {Couch}, {Bettoni},
+  {Kj{\ae}rgaard}, \& {Moles}}]{Fasano:2000aa}
+{Fasano}, G., {Poggianti}, B.~M., {Couch}, W.~J., {et~al.} 2000, \apj, 542, 673
+
+\bibitem[{{Gallazzi} {et~al.}(2009){Gallazzi}, {Bell}, {Wolf}, {Gray},
+  {Papovich}, {Barden}, {Peng}, {Meisenheimer}, {Heymans}, {van Kampen},
+  {Gilmour}, {Balogh}, {McIntosh}, {Bacon}, {Barazza}, {B{\"o}hm}, {Caldwell},
+  {H{\"a}ubler}, {Jahnke}, {Jogee}, {Lane}, {Robaina}, {Sanchez}, {Taylor},
+  {Wisotzki}, \& {Zheng}}]{Gallazzi:2009aa}
+{Gallazzi}, A., {Bell}, E.~F., {Wolf}, C., {et~al.} 2009, \apj, 690, 1883
+
+\bibitem[{{Geha} {et~al.}(2012){Geha}, {Blanton}, {Yan}, \& {Tinker}}]{geha12a}
+{Geha}, M., {Blanton}, M.~R., {Yan}, R., \& {Tinker}, J.~L. 2012, \apj, 757, 85
+
+\bibitem[{{Gunn} \& {Gott}(1972)}]{Gunn:1972aa}
+{Gunn}, J.~E., \& {Gott}, III, J.~R. 1972, \apj, 176, 1
+
+\bibitem[{Guzzo {et~al.}(1997)Guzzo, Strauss, Fisher, Giovanelli, \&
+  Haynes}]{guzzo97a}
+Guzzo, L., Strauss, M.~A., Fisher, K.~B., Giovanelli, R., \& Haynes, M.~P.
+  1997, \apj, 489, 37
+
+\bibitem[{Hermit {et~al.}(1996)Hermit, Santiago, Lahav, Strauss, Davis,
+  Dressler, \& Huchra}]{hermit96a}
+Hermit, S., Santiago, B.~X., Lahav, O., {et~al.} 1996, \mnras, 283, 709
+
+\bibitem[{{Hopkins} \& {Beacom}(2006)}]{hopkins06a}
+{Hopkins}, A.~M., \& {Beacom}, J.~F. 2006, \apj, 651, 142
+
+\bibitem[{Hubble(1936)}]{hubble36a}
+Hubble, E.~P. 1936, The Realm of the Nebulae (New Haven: Yale University Press)
+
+\bibitem[{{Hyde} \& {Bernardi}(2009)}]{Hyde:2009aa}
+{Hyde}, J.~B., \& {Bernardi}, M. 2009, \mnras, 394, 1978
+
+\bibitem[{{Iovino} {et~al.}(2010){Iovino}, {Cucciati}, {Scodeggio}, {Knobel},
+  {Kova{\v c}}, {Lilly}, {Bolzonella}, {Tasca}, {Zamorani}, {Zucca}, {Caputi},
+  {Pozzetti}, {Oesch}, {Lamareille}, {Halliday}, {Bardelli}, {Finoguenov},
+  {Guzzo}, {Kampczyk}, {Maier}, {Tanaka}, {Vergani}, {Carollo}, {Contini},
+  {Kneib}, {Le F{\`e}vre}, {Mainieri}, {Renzini}, {Bongiorno}, {Coppa}, {de la
+  Torre}, {de Ravel}, {Franzetti}, {Garilli}, {Le Borgne}, {Le Brun},
+  {Mignoli}, {Pell{\`o}}, {Peng}, {Perez-Montero}, {Ricciardelli}, {Silverman},
+  {Tresse}, {Abbas}, {Bottini}, {Cappi}, {Cassata}, {Cimatti}, {Koekemoer},
+  {Leauthaud}, {Maccagni}, {Marinoni}, {McCracken}, {Memeo}, {Meneux},
+  {Porciani}, {Scaramella}, {Schiminovich}, \& {Scoville}}]{Iovino:2010aa}
+{Iovino}, A., {Cucciati}, O., {Scodeggio}, M., {et~al.} 2010, \aap, 509, A40
+
+\bibitem[{{Jarrett} {et~al.}(2000){Jarrett}, {Chester}, {Cutri}, {Schneider},
+  {Skrutskie}, \& {Huchra}}]{Jarrett:2000aa}
+{Jarrett}, T.~H., {Chester}, T., {Cutri}, R., {et~al.} 2000, \aj, 119, 2498
+
+\bibitem[{{Johnston}(2011)}]{Johnston:2011aa}
+{Johnston}, R. 2011, \aapr, 19, 41
+
+\bibitem[{{Karim} {et~al.}(2011){Karim}, {Schinnerer},
+  {Mart{\'{\i}}nez-Sansigre}, {Sargent}, {van der Wel}, {Rix}, {Ilbert},
+  {Smol{\v c}i{\'c}}, {Carilli}, {Pannella}, {Koekemoer}, {Bell}, \&
+  {Salvato}}]{Karim:2011aa}
+{Karim}, A., {Schinnerer}, E., {Mart{\'{\i}}nez-Sansigre}, A., {et~al.} 2011,
+  \apj, 730, 61
+
+\bibitem[{{Kere{\v s}} {et~al.}(2005){Kere{\v s}}, {Katz}, {Weinberg}, \&
+  {Dav{\'e}}}]{Keres:2005aa}
+{Kere{\v s}}, D., {Katz}, N., {Weinberg}, D.~H., \& {Dav{\'e}}, R. 2005,
+  \mnras, 363, 2
+
+\bibitem[{{Kova{\v c}} {et~al.}(2010){Kova{\v c}}, {Lilly}, {Cucciati},
+  {Porciani}, {Iovino}, {Zamorani}, {Oesch}, {Bolzonella}, {Knobel},
+  {Finoguenov}, {Peng}, {Carollo}, {Pozzetti}, {Caputi}, {Silverman}, {Tasca},
+  {Scodeggio}, {Vergani}, {Scoville}, {Capak}, {Contini}, {Kneib}, {Le
+  F{\`e}vre}, {Mainieri}, {Renzini}, {Bardelli}, {Bongiorno}, {Coppa}, {de la
+  Torre}, {de Ravel}, {Franzetti}, {Garilli}, {Guzzo}, {Kampczyk},
+  {Lamareille}, {Le Borgne}, {Le Brun}, {Maier}, {Mignoli}, {Pello}, {Perez
+  Montero}, {Ricciardelli}, {Tanaka}, {Tresse}, {Zucca}, {Abbas}, {Bottini},
+  {Cappi}, {Cassata}, {Cimatti}, {Fumana}, {Koekemoer}, {Maccagni}, {Marinoni},
+  {McCracken}, {Memeo}, {Meneux}, \& {Scaramella}}]{Kovac:2010ab}
+{Kova{\v c}}, K., {Lilly}, S.~J., {Cucciati}, O., {et~al.} 2010, \apj, 708, 505
+
+\bibitem[{{Kova{\v c}} {et~al.}(2014){Kova{\v c}}, {Lilly}, {Knobel},
+  {Bschorr}, {Peng}, {Carollo}, {Contini}, {Kneib}, {Le F{\'e}vre}, {Mainieri},
+  {Renzini}, {Scodeggio}, {Zamorani}, {Bardelli}, {Bolzonella}, {Bongiorno},
+  {Caputi}, {Cucciati}, {de la Torre}, {de Ravel}, {Franzetti}, {Garilli},
+  {Iovino}, {Kampczyk}, {Lamareille}, {Le Borgne}, {Le Brun}, {Maier},
+  {Mignoli}, {Oesch}, {Pello}, {Montero}, {Presotto}, {Silverman}, {Tanaka},
+  {Tasca}, {Tresse}, {Vergani}, {Zucca}, {Aussel}, {Koekemoer}, {Le Floc'h},
+  {Moresco}, \& {Pozzetti}}]{Kovac:2014aa}
+{Kova{\v c}}, K., {Lilly}, S.~J., {Knobel}, C., {et~al.} 2014, \mnras, 438, 717
+
+\bibitem[{{Larson} {et~al.}(1980){Larson}, {Tinsley}, \&
+  {Caldwell}}]{Larson:1980aa}
+{Larson}, R.~B., {Tinsley}, B.~M., \& {Caldwell}, C.~N. 1980, \apj, 237, 692
+
+\bibitem[{{Lauer} {et~al.}(2007){Lauer}, {Faber}, {Richstone}, {Gebhardt},
+  {Tremaine}, {Postman}, {Dressler}, {Aller}, {Filippenko}, {Green}, {Ho},
+  {Kormendy}, {Magorrian}, \& {Pinkney}}]{Lauer:2007aa}
+{Lauer}, T.~R., {Faber}, S.~M., {Richstone}, D., {et~al.} 2007, \apj, 662, 808
+
+\bibitem[{{Leja} {et~al.}(2013){Leja}, {van Dokkum}, \& {Franx}}]{Leja:2013aa}
+{Leja}, J., {van Dokkum}, P., \& {Franx}, M. 2013, \apj, 766, 33
+
+\bibitem[{{Lilly} {et~al.}(2009){Lilly}, {Le Brun}, {Maier}, {Mainieri},
+  {Mignoli}, {Scodeggio}, {Zamorani}, {Carollo}, {Contini}, {Kneib}, {Le
+  F{\`e}vre}, {Renzini}, {Bardelli}, {Bolzonella}, {Bongiorno}, {Caputi},
+  {Coppa}, {Cucciati}, {de la Torre}, {de Ravel}, {Franzetti}, {Garilli},
+  {Iovino}, {Kampczyk}, {Kovac}, {Knobel}, {Lamareille}, {Le Borgne}, {Pello},
+  {Peng}, {P{\'e}rez-Montero}, {Ricciardelli}, {Silverman}, {Tanaka}, {Tasca},
+  {Tresse}, {Vergani}, {Zucca}, {Ilbert}, {Salvato}, {Oesch}, {Abbas},
+  {Bottini}, {Capak}, {Cappi}, {Cassata}, {Cimatti}, {Elvis}, {Fumana},
+  {Guzzo}, {Hasinger}, {Koekemoer}, {Leauthaud}, {Maccagni}, {Marinoni},
+  {McCracken}, {Memeo}, {Meneux}, {Porciani}, {Pozzetti}, {Sanders},
+  {Scaramella}, {Scarlata}, {Scoville}, {Shopbell}, \&
+  {Taniguchi}}]{Lilly:2009aa}
+{Lilly}, S.~J., {Le Brun}, V., {Maier}, C., {et~al.} 2009, \apjs, 184, 218
+
+\bibitem[{{Magnelli} {et~al.}(2009){Magnelli}, {Elbaz}, {Chary}, {Dickinson},
+  {Le Borgne}, {Frayer}, \& {Willmer}}]{magnelli09a}
+{Magnelli}, B., {Elbaz}, D., {Chary}, R.~R., {et~al.} 2009, \aap, 496, 57
+
+\bibitem[{{Markwardt}(2009)}]{Markwardt:2009aa}
+{Markwardt}, C.~B. 2009, in Astronomical Society of the Pacific Conference
+  Series, Vol. 411, Astronomical Data Analysis Software and Systems XVIII, ed.
+  D.~A. {Bohlender}, D.~{Durand}, \& P.~{Dowler}, 251
+
+\bibitem[{{Martin} {et~al.}(2005){Martin}, {Fanson}, {Schiminovich},
+  {Morrissey}, {Friedman}, {Barlow}, {Conrow}, {Grange}, {Jelinsky},
+  {Milliard}, {Siegmund}, {Bianchi}, {Byun}, {Donas}, {Forster}, {Heckman},
+  {Lee}, {Madore}, {Malina}, {Neff}, {Rich}, {Small}, {Surber}, {Szalay},
+  {Welsh}, \& {Wyder}}]{Martin:2005aa}
+{Martin}, D.~C., {Fanson}, J., {Schiminovich}, D., {et~al.} 2005, \apjl, 619,
+  L1
+
+\bibitem[{{Moore} {et~al.}(1998){Moore}, {Lake}, \& {Katz}}]{Moore:1998aa}
+{Moore}, B., {Lake}, G., \& {Katz}, N. 1998, \apj, 495, 139
+
+\bibitem[{{Morrissey} {et~al.}(2005){Morrissey}, {Schiminovich}, {Barlow},
+  {Martin}, {Blakkolb}, {Conrow}, {Cooke}, {Erickson}, {Fanson}, {Friedman},
+  {Grange}, {Jelinsky}, {Lee}, {Liu}, {Mazer}, {McLean}, {Milliard}, {Randall},
+  {Schmitigal}, {Sen}, {Siegmund}, {Surber}, {Vaughan}, {Viton}, {Welsh},
+  {Bianchi}, {Byun}, {Donas}, {Forster}, {Heckman}, {Lee}, {Madore}, {Malina},
+  {Neff}, {Rich}, {Small}, {Szalay}, \& {Wyder}}]{Morrissey:2005aa}
+{Morrissey}, P., {Schiminovich}, D., {Barlow}, T.~A., {et~al.} 2005, \apjl,
+  619, L7
+
+\bibitem[{{Moustakas} {et~al.}(2013){Moustakas}, {Coil}, {Aird}, {Blanton},
+  {Cool}, {Eisenstein}, {Mendez}, {Wong}, {Zhu}, \&
+  {Arnouts}}]{Moustakas:2013aa}
+{Moustakas}, J., {Coil}, A.~L., {Aird}, J., {et~al.} 2013, \apj, 767, 50
+
+\bibitem[{{Muldrew} {et~al.}(2012){Muldrew}, {Croton}, {Skibba}, {Pearce},
+  {Ann}, {Baldry}, {Brough}, {Choi}, {Conselice}, {Cowan}, {Gallazzi}, {Gray},
+  {Gr{\"u}tzbauch}, {Li}, {Park}, {Pilipenko}, {Podgorzec}, {Robotham},
+  {Wilman}, {Yang}, {Zhang}, \& {Zibetti}}]{Muldrew:2012aa}
+{Muldrew}, S.~I., {Croton}, D.~J., {Skibba}, R.~A., {et~al.} 2012, \mnras, 419,
+  2670
+
+\bibitem[{{Noeske} {et~al.}(2007){Noeske}, {Weiner}, {Faber}, {Papovich},
+  {Koo}, {Somerville}, {Bundy}, {Conselice}, {Newman}, {Schiminovich}, {Le
+  Floc'h}, {Coil}, {Rieke}, {Lotz}, {Primack}, {Barmby}, {Cooper}, {Davis},
+  {Ellis}, {Fazio}, {Guhathakurta}, {Huang}, {Kassin}, {Martin}, {Phillips},
+  {Rich}, {Small}, {Willmer}, \& {Wilson}}]{Noeske:2007aa}
+{Noeske}, K.~G., {Weiner}, B.~J., {Faber}, S.~M., {et~al.} 2007, \apjl, 660,
+  L43
+
+\bibitem[{Norberg {et~al.}(2002)}]{norberg02a}
+Norberg, P., {et~al.} 2002, \mnras, 332, 827
+
+\bibitem[{Oemler(1974)}]{oemler74a}
+Oemler, A. 1974, \apj, 194, 1
+
+\bibitem[{{Peng} {et~al.}(2010){Peng}, {Lilly}, {Kova{\v c}}, {Bolzonella},
+  {Pozzetti}, {Renzini}, {Zamorani}, {Ilbert}, {Knobel}, {Iovino}, {Maier},
+  {Cucciati}, {Tasca}, {Carollo}, {Silverman}, {Kampczyk}, {de Ravel},
+  {Sanders}, {Scoville}, {Contini}, {Mainieri}, {Scodeggio}, {Kneib}, {Le
+  F{\`e}vre}, {Bardelli}, {Bongiorno}, {Caputi}, {Coppa}, {de la Torre},
+  {Franzetti}, {Garilli}, {Lamareille}, {Le Borgne}, {Le Brun}, {Mignoli},
+  {Perez Montero}, {Pello}, {Ricciardelli}, {Tanaka}, {Tresse}, {Vergani},
+  {Welikala}, {Zucca}, {Oesch}, {Abbas}, {Barnes}, {Bordoloi}, {Bottini},
+  {Cappi}, {Cassata}, {Cimatti}, {Fumana}, {Hasinger}, {Koekemoer},
+  {Leauthaud}, {Maccagni}, {Marinoni}, {McCracken}, {Memeo}, {Meneux}, {Nair},
+  {Porciani}, {Presotto}, \& {Scaramella}}]{Peng:2010aa}
+{Peng}, Y.-j., {Lilly}, S.~J., {Kova{\v c}}, K., {et~al.} 2010, \apj, 721, 193
+
+\bibitem[{{Pozzetti} {et~al.}(2010){Pozzetti}, {Bolzonella}, {Zucca},
+  {Zamorani}, {Lilly}, {Renzini}, {Moresco}, {Mignoli}, {Cassata}, {Tasca},
+  {Lamareille}, {Maier}, {Meneux}, {Halliday}, {Oesch}, {Vergani}, {Caputi},
+  {Kova{\v c}}, {Cimatti}, {Cucciati}, {Iovino}, {Peng}, {Carollo}, {Contini},
+  {Kneib}, {Le F{\'e}vre}, {Mainieri}, {Scodeggio}, {Bardelli}, {Bongiorno},
+  {Coppa}, {de la Torre}, {de Ravel}, {Franzetti}, {Garilli}, {Kampczyk},
+  {Knobel}, {Le Borgne}, {Le Brun}, {Pell{\`o}}, {Perez Montero},
+  {Ricciardelli}, {Silverman}, {Tanaka}, {Tresse}, {Abbas}, {Bottini}, {Cappi},
+  {Guzzo}, {Koekemoer}, {Leauthaud}, {Maccagni}, {Marinoni}, {McCracken},
+  {Memeo}, {Porciani}, {Scaramella}, {Scarlata}, \&
+  {Scoville}}]{Pozzetti:2010aa}
+{Pozzetti}, L., {Bolzonella}, M., {Zucca}, E., {et~al.} 2010, \aap, 523, A13
+
+\bibitem[{{Salim} {et~al.}(2007){Salim}, {Rich}, {Charlot}, {Brinchmann},
+  {Johnson}, {Schiminovich}, {Seibert}, {Mallery}, {Heckman}, {Forster},
+  {Friedman}, {Martin}, {Morrissey}, {Neff}, {Small}, {Wyder}, {Bianchi},
+  {Donas}, {Lee}, {Madore}, {Milliard}, {Szalay}, {Welsh}, \&
+  {Yi}}]{Salim:2007aa}
+{Salim}, S., {Rich}, R.~M., {Charlot}, S., {et~al.} 2007, \apjs, 173, 267
+
+\bibitem[{{Scodeggio} {et~al.}(2009){Scodeggio}, {Vergani}, {Cucciati},
+  {Iovino}, {Franzetti}, {Garilli}, {Lamareille}, {Bolzonella}, {Pozzetti},
+  {Abbas}, {Marinoni}, {Contini}, {Bottini}, {Le Brun}, {Le F{\`e}vre},
+  {Maccagni}, {Scaramella}, {Tresse}, {Vettolani}, {Zanichelli}, {Adami},
+  {Arnouts}, {Bardelli}, {Cappi}, {Charlot}, {Ciliegi}, {Foucaud}, {Gavignaud},
+  {Guzzo}, {Ilbert}, {McCracken}, {Marano}, {Mazure}, {Meneux}, {Merighi},
+  {Paltani}, {Pell{\`o}}, {Pollo}, {Radovich}, {Zamorani}, {Zucca}, {Bondi},
+  {Bongiorno}, {Brinchmann}, {de La Torre}, {de Ravel}, {Gregorini}, {Memeo},
+  {Perez-Montero}, {Mellier}, {Temporin}, \& {Walcher}}]{Scodeggio:2009aa}
+{Scodeggio}, M., {Vergani}, D., {Cucciati}, O., {et~al.} 2009, \aap, 501, 21
+
+\bibitem[{{Skibba} {et~al.}(2013){Skibba}, {Sheth}, {Croton}, {Muldrew},
+  {Abbas}, {Pearce}, \& {Shattow}}]{Skibba:2013aa}
+{Skibba}, R.~A., {Sheth}, R.~K., {Croton}, D.~J., {et~al.} 2013, \mnras, 429,
+  458
+
+\bibitem[{{Smith} {et~al.}(2005){Smith}, {Treu}, {Ellis}, {Moran}, \&
+  {Dressler}}]{Smith:2005aa}
+{Smith}, G.~P., {Treu}, T., {Ellis}, R.~S., {Moran}, S.~M., \& {Dressler}, A.
+  2005, \apj, 620, 78
+
+\bibitem[{{Swanson} {et~al.}(2008){Swanson}, {Tegmark}, {Hamilton}, \&
+  {Hill}}]{Swanson:2008aa}
+{Swanson}, M.~E.~C., {Tegmark}, M., {Hamilton}, A.~J.~S., \& {Hill}, J.~C.
+  2008, \mnras, 387, 1391
+
+\bibitem[{{Taylor} {et~al.}(2009){Taylor}, {Franx}, {van Dokkum}, {Bell},
+  {Brammer}, {Rudnick}, {Wuyts}, {Gawiser}, {Lira}, {Urry}, \&
+  {Rix}}]{taylor09a}
+{Taylor}, E.~N., {Franx}, M., {van Dokkum}, P.~G., {et~al.} 2009, \apj, 694,
+  1171
+
+\bibitem[{{Tinker} {et~al.}(2011){Tinker}, {Wetzel}, \&
+  {Conroy}}]{Tinker:2011aa}
+{Tinker}, J., {Wetzel}, A., \& {Conroy}, C. 2011, ArXiv e-prints,
+  arXiv:1107.5046
+
+\bibitem[{{Weinmann} {et~al.}(2006){Weinmann}, {van den Bosch}, {Yang}, {Mo},
+  {Croton}, \& {Moore}}]{Weinmann:2006aa}
+{Weinmann}, S.~M., {van den Bosch}, F.~C., {Yang}, X., {et~al.} 2006, \mnras,
+  372, 1161
+
+\bibitem[{{West}(2005)}]{West:2005aa}
+{West}, A.~A. 2005, PhD thesis, University of Washington, Washington, USA
+
+\bibitem[{{West} {et~al.}(2010){West}, {Garcia-Appadoo}, {Dalcanton}, {Disney},
+  {Rockosi}, {Ivezi{\'c}}, {Bentz}, \& {Brinkmann}}]{West:2010aa}
+{West}, A.~A., {Garcia-Appadoo}, D.~A., {Dalcanton}, J.~J., {et~al.} 2010,
+  \apj, 139, 315
+
+\bibitem[{{Williams} {et~al.}(2009){Williams}, {Quadri}, {Franx}, {van Dokkum},
+  \& {Labb{\'e}}}]{Williams:2009aa}
+{Williams}, R.~J., {Quadri}, R.~F., {Franx}, M., {van Dokkum}, P., \&
+  {Labb{\'e}}, I. 2009, \apj, 691, 1879
+
+\bibitem[{{Wilman} {et~al.}(2010){Wilman}, {Zibetti}, \&
+  {Budav{\'a}ri}}]{Wilman:2010aa}
+{Wilman}, D.~J., {Zibetti}, S., \& {Budav{\'a}ri}, T. 2010, \mnras, 406, 1701
+
+\bibitem[{{York} {et~al.}(2000){York}, {Adelman}, {Anderson}, {Anderson},
+  {Annis}, {Bahcall}, {Bakken}, {Barkhouser}, {Bastian}, {Berman}, {Boroski},
+  {Bracker}, {Briegel}, {Briggs}, {Brinkmann}, {Brunner}, {Burles}, {Carey},
+  {Carr}, {Castander}, {Chen}, {Colestock}, {Connolly}, {Crocker}, {Csabai},
+  {Czarapata}, {Davis}, {Doi}, {Dombeck}, {Eisenstein}, {Ellman}, {Elms},
+  {Evans}, {Fan}, {Federwitz}, {Fiscelli}, {Friedman}, {Frieman}, {Fukugita},
+  {Gillespie}, {Gunn}, {Gurbani}, {de Haas}, {Haldeman}, {Harris}, {Hayes},
+  {Heckman}, {Hennessy}, {Hindsley}, {Holm}, {Holmgren}, {Huang}, {Hull},
+  {Husby}, {Ichikawa}, {Ichikawa}, {Ivezi{\'c}}, {Kent}, {Kim}, {Kinney},
+  {Klaene}, {Kleinman}, {Kleinman}, {Knapp}, {Korienek}, {Kron}, {Kunszt},
+  {Lamb}, {Lee}, {Leger}, {Limmongkol}, {Lindenmeyer}, {Long}, {Loomis},
+  {Loveday}, {Lucinio}, {Lupton}, {MacKinnon}, {Mannery}, {Mantsch}, {Margon},
+  {McGehee}, {McKay}, {Meiksin}, {Merelli}, {Monet}, {Munn}, {Narayanan},
+  {Nash}, {Neilsen}, {Neswold}, {Newberg}, {Nichol}, {Nicinski}, {Nonino},
+  {Okada}, {Okamura}, {Ostriker}, {Owen}, {Pauls}, {Peoples}, {Peterson},
+  {Petravick}, {Pier}, {Pope}, {Pordes}, {Prosapio}, {Rechenmacher}, {Quinn},
+  {Richards}, {Richmond}, {Rivetta}, {Rockosi}, {Ruthmansdorfer}, {Sandford},
+  {Schlegel}, {Schneider}, {Sekiguchi}, {Sergey}, {Shimasaku}, {Siegmund},
+  {Smee}, {Smith}, {Snedden}, {Stone}, {Stoughton}, {Strauss}, {Stubbs},
+  {SubbaRao}, {Szalay}, {Szapudi}, {Szokoly}, {Thakar}, {Tremonti}, {Tucker},
+  {Uomoto}, {Vanden Berk}, {Vogeley}, {Waddell}, {Wang}, {Watanabe},
+  {Weinberg}, {Yanny}, {Yasuda}, \& {SDSS Collaboration}}]{York:2000aa}
+{York}, D.~G., {Adelman}, J., {Anderson}, Jr., J.~E., {et~al.} 2000, \aj, 120,
+  1579
+
+\bibitem[{Zehavi {et~al.}(2002)}]{zehavi02a}
+Zehavi, I., {et~al.} 2002, \apj, 571, 172
+
+\end{thebibliography}
+
 \end{document}

### 2014-12-24 qfenv_paper/qf_env_apj.tex
prepping ApJ submission
draft for submission

--- 2014-12-19 qfenv_paper/qf_environment.tex
@@
-\documentclass{emulateapj}
+\documentclass[manuscript]{aastex}
 \bibliographystyle{apj}
@@
 %internal short cuts
-\def \HgA {H$\gamma_A$}
-\def \Hbp {H$\beta ^\prime$}
 \def \lowenvthresh {0.5}
@@
 Kenneth C.~Wong\altaffilmark{6}, 
-Guangtun~Zhu\altaffilmark{7}
+Guangtun~Zhu\altaffilmark{7,8}
 }
-\altaffiltext{1}{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Place, New York, NY 10003}
+\altaffiltext{1}{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Place, New York, NY 10003; chh327@nyu.edu}
 \altaffiltext{2}{Department of Physics and Astronomy, Siena College, 515 Loudon Road, Loudonville, NY 12211}
@@
 
+\keywords{cosmology:observations --- galaxies: evolution --- galaxies:groups --- galaxies: star formation}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 an earlier formation time in dense regions).
-
-%However, it remains to be discerned whether these trends reflect the underlying differences among galaxy populations in different environments or if they are in fact effects of environment dependent external processes, which cause galaxies that would otherwise continue forming stars to cease their star-formation.
-
-%Similarly, a number of observations support the existence of environment dependent external processes (\citealt{Iovino:2010aa, geha12a, Kovac:2014aa}).
-\cite{Peng:2010aa} and others further argue that internal and external processes both contribute to the cessation of star-formation with internal processes more dominant in massive galaxies and external processes dominating the less massive regime.
-While discrepancies persist between theoretical models and observations, a large number of observations suggest that environment plays a significant role in ceasing star-formation.
-
-%Some of these proposed internal processes have received observational support.
-\cite{Weinmann:2006aa} and \cite{Peng:2010aa}, for example, credit internal processes for quenching star-formation, especially in massive galaxies.
-
-%Nevertheless, the evolution of the role of environment is a relatively subtle effect and difficult to study.
-Although the history of galaxies prior to $z\sim 1$ appears to have been one of rapid assembly, since that time the galaxy population has continued to evolve, but less dramatically.
-Although there are detectable changes in the population, the major classes of galaxies existed at $z\sim 1$, in roughly the same relative numbers as today (\citealt{bundy06a, borch06a, taylor09a, Moustakas:2013aa}).
-Furthermore, at those redshifts we can also detect the dependence of galaxy properties on environment, with lower star-formation rate early-type galaxies populating the denser regions (\citealt{cooper08a, patel09a, kovac10a}).
-
-%The most dramatic change in galaxy properties during the past eight billion years has been a remarkable decline in the star-formation rate of galaxies in the Universe (\citealt{hopkins06a}).
-This decline  appears dominated by decreases in the rates of star-formation of individual galaxi es (\citealt{Noeske:2007aa}).
-There is evidence that a large fraction of the decline is associated with strongly infrared-emitting starbursts (\citealt{bell05a, magnelli09a}).
-The decline does not appear to be due to a complete cessation of star formation for a large fraction of the star-forming population, as reflected in observations of the stellar mass function of quiescent and star-forming galaxies (\citealt{Blanton:2006aa, bundy06a,   borch06a, Moustakas:2013aa}).
-These findings leave little room for the participation of environmentally-driven cessation of star formation in the global census of star-formation.
-As \cite{cooper08a} and others have pointed out, because the environmental dependence of total star-formation rates at fixed redshift is relatively small, environmentally effects are unlikely to cause the overall star-formation rate decline.
-
-%Thus, the impact of environment on galaxy formation has to be interpreted on top of the background of the build up of the red sequence during the overall decline in star-formation rate affecting galaxies in all environments.
-The most straightforward investigation would be to directly determine the star-forming properties of galaxies as a function of environment, stellar mass and redshift in a single, consistently analyzed data set.
 
@@
 
-\begin{figure*}
-    \begin{center}
-        \leavevmode
-        \epsscale{1.2}
-	\plotone{fig_edp_sdss_z0_05_0_12_primus_z0_2_1_0_Mr_redshift.png}
-        \caption{Absolute magnitude $M_{r}$ versus redshift for our mass complete galaxy sample (black squares) with the Environment Defining Population (red circles) plotted on top.
-Both samples are divided into redshift bins: $z = 0.05-0.12$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ (panels left to right).
-The lowest redshift bin ($z \approx 0.05-0.12$; leftmost panel) contain our galaxy sample and EDP selected from SDSS.
-The rest contain galaxies and EDP selected from PRIMUS.
-The redshift limits for the lowest redshift bin are empirically selected based on the bright and faint limits of SDSS galaxies.
-Stellar mass completeness limits, described in Section \ref{sec:target}, are imposed on the galaxy population.
-Meanwhile, $M_{r}$ limits are applied to the EDP such that the number density in each panel are equivalent (Section \ref{sec:environment}).} \label{fig:targetEDP}
-    \end{center}
-\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table*} 
-  \caption{Galaxy Subsamples}
-  \label{tab:subsample}
-  \begin{center}
-    \leavevmode
-    \begin{tabular}{ccccccc} \hline \hline              
-     &\multicolumn{1}{c}{$n_{\mathrm{env}}$}        & \multicolumn{2}{c}{$N_{\mathrm{gal}}$}  & \multicolumn{2}{c}{$\mathcal{M}_{\mathrm{lim}}$} & $M_{\mathrm{r}, lim}$ \\ 
-    & & Quiescent & Star-Forming & Quiescent & Star-Forming &  \\ \hline 
-$0.05 < z < 0.12$ & $n_{\mathrm{env}} < \lowenvthresh $ & 6533 & 7508 & $10^{10.2} \mathcal{M}_{\odot}$ & $10^{10.2} \mathcal{M}_{\odot}$ & -20.95 \\
-               & $n_{\mathrm{env}} > \highenvthresh $ &14673 & 9717 &                          \\ 
-                              & all          &$33553$                       & $29864$                          \\ \hline
-$0.2 < z < 0.4$      &$n_{\mathrm{env}} < \lowenvthresh $           &363                    &1231 & $10^{9.8} \mathcal{M}_{\odot}$ & $10^{9.8} \mathcal{M}_{\odot}$ &-21.03 \\
-               &$n_{\mathrm{env}} > \highenvthresh $            &379                    &756                           \\
-               & all                & $1086$                      & $2879$                          \\ \hline
-$0.4 < z < 0.6$      &$n_{\mathrm{env}} < \lowenvthresh $           &536                       &1498 & $10^{10.3} \mathcal{M}_{\odot}$ & $10^{10.3} \mathcal{M}_{\odot}$ & -20.98 \\
-               &$n_{\mathrm{env}} > \highenvthresh $            &490                       &854                           \\
-               & all               & $1560$                      & $3577$                          \\ \hline
-$0.6 < z < 0.8$      &$n_{\mathrm{env}} < \lowenvthresh $           &567                       &1254  & $10^{10.7} \mathcal{M}_{\odot}$ & $10^{10.6} \mathcal{M}_{\odot}$ & -20.97 \\
-               &$n_{\mathrm{env}} > \highenvthresh $            &498                       &671                           \\
-               & all              & $1668$                      & $2964$                          \\ \hline
-Total &      & \multicolumn{2}{c}{77151} & \\ \hline
-  \multicolumn{4}{l}{}                                             \\       
-    \end{tabular} \par
-    \end{center}
-%    \bigskip 
-    {\bf Notes}: Number of galaxies ($N_{\mathrm{gal}}$) in the mass complete subsamples within the edges of the survey (Section \ref{sec:sample}).
-The subsamples are classified based on environment ($n_{\mathrm{env}}$) and star formation rate (star-forming or quiescent).
-The lowest redshift bin is derived from SDSS; the rest are from PRIMUS.
-We also list the stellar mass completeness limit, $\mathcal{M}_{\mathrm{lim}}$, for our sample along with the $r$-band absolute magnitude limits, $M_{\mathrm{r}, lim}$, for the Environment Defining Population.
-    \bigskip
-\end{table*}
-
 \subsection{Stellar Mass Complete Galaxy Sample} \label{sec:target} 
@@
 
-%We present the absolute magnitude ($M_{r}$) versus redshift for the galaxy sample (black squares) in Figure \ref{fig:targetEDP}.
-The left-most panel corresponds to the sample derived from the SDSS-{\em GALEX} data and the rest correspond to the target sample derived from the PRIMUS data divided in bins with $\Delta z \sim 0.2$.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-  \begin{center}
-    \leavevmode
-    \epsfig{file=fig_envcount_cylr2_5h35_thresh75_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_primuszerr_masslimit_edgecut_histogram.png, width=0.45\textwidth}
-    \caption{Normalized distribution of environment measurements ($n_{\mathrm{env}}$) for our mass complete galaxy sample within the survey edges.
-A fixed cylindrical aperture of $R_{\mathrm{ap}} =\apradius\;\mathrm{Mpc}$ and $H_{\mathrm{ap}} = \apheight\; \mathrm{Mpc}$ is used to measure environment.
-The star-forming galaxies contribution to the distribution is colored in blue and diagonally patterned.
-The contribution from quiescent galaxies is colored in red.
-Galaxies with $n_{\mathrm{env}} < 0.5$ are in low density environments and galaxies with $n_{\mathrm{env}} > 3.0$ are in high density environment.
-We note that the significant difference among the SDSS distribution and the PRIMUS distributions above is due to the different stellar mass completeness limits imposed on each redshift bin of our galaxy sample.}      \label{fig:envcount}
-     %\caption{Normalized distribution of environment measurements ($n_{\mathrm{env}}$) for our mass complete galaxy sample within the edges.
-The star-forming galaxies contribution to the distribution is colored blue and diagonally patterned.
-The contribution from quiescent galaxies is colored in red.
-Each redshift panel is divided into three sections by the environment classification cutoffs (black veritcal lines): low density environment $n_{\mathrm{env}} < 0.5$ and high density environment $n_{\mathrm{env}} > 3.0$.
-The percentages of the redshift bin contained in the environment classifications are presented above the distribution.
-For example at $0.2 < z < 0.4$, $\apheight.0 \%$ of galaxies in the redshift bin are in low density environments while $35.0\%$ of galaxies in the redshift bin are in high density environments.
-We note that the significant difference between the SDSS distribution and the PRIMUS distribution above is due to the difference in stellar mass completeness limit imposed in our galaxy sample.}      \label{fig:envcount}
-    \end{center}
-\end{figure}
-
 \subsection{Galaxy Environment} \label{sec:environment}
@@
 host dark matter halo sizes.
-
-% Not sure we need to note this detail; the anticorrelation is small.
-%\cite{Wilman:2010aa}, which uses environment defined by annuli of
-%different radii, find positive correlation for quiescent fraction and
-%color on scales $< 1 \; \mathrm{Mpc}$ and anti-correlation on scales $> 3
-%\; \mathrm{Mpc}$. Our choice of $2 \mathrm{Mpc}/h$ provides sufficient sample
-%size of galaxies in dense environments, for robust statistics, while
-%tracing galactic properties within the halo scale.
-
-%When we extend our analysis to cylindrical apertures with $R_{\mathrm{ap}} = 1 \; \mathrm{Mpc}/h$, we find that the change does not qualitatively change our results (difference in $f_{Q} < 0.05$). 
-%Similar fixed aperture methods have also been used in \cite{Croton:2005aa} for galaxies in the 2dF Galaxy Redshift 
-%Survey (\cite{Colless:2003aa}) and in \cite{Muldrew:2012aa} for a mock galaxy catalogue generated from embedding 
-%galaxies onto the Millenium Dark Matter Simulation (\cite{Springel:2005aa}).
 
@@
 We remind the reader that this is mainly due to the varying stellar mass-completeness limits imposed on our galaxy sample for each redshift bins and does not affect our results.
-\begin{figure*}
-  \begin{center}
-    \leavevmode
-    \epsfig{file=fig_smf_cylr2_50000h35_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_2envbin_lowenv0_5_highenv3_0_lit_primuszerr.eps, height=0.75\textwidth,angle=90}
-     \caption{Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) galaxies in 
-low (left) and high (right) density environments throughout the redshift range
-$z=0$--$0.8$. The environment of each galaxy  
-was calculated using a cylindrical aperture size of $R=\apradius \: \mathrm{Mpc}$ and $H=\apheight \: \mathrm{Mpc}$ and  
-classified as low environment when $n_{\mathrm{env}} < 0.5$ and as high environment when $n_{\mathrm{env}} > 3.0$. The SMFs use mass bins of 
-width $\Delta \mathrm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.2$. In each panel we use shades of blue 
-(star-forming) and orange (quiescent) to represent the SMF at different redshift, higher redshifts being
-progressively lighter.}      \label{fig:smf}
-    \end{center}
-\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Overall, we find that the trends we note in the SMF evolution above are in good agreement with \cite{bundy06a} and \cite{Bolzonella:2010aa}.
-
-\begin{figure*}
-    \begin{center}
-        \leavevmode
-        \epsfig{file=fig_qf_cylr2_50000h35_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_lit_primuszerr.eps, height=0.75\textwidth,angle=90}
-        \caption{Evolution of the quiescent fraction $f_{\mathrm{Q}}$ for
-          galaxies in low (left) and high (right) density
-          environments for $z < 0.8$. $f_{\mathrm{Q}}$s were calculated
-          using the SMFs in Figure \ref{fig:smf}, as described in Section \ref{sec:qfevol}.
-Darker shading indicates lower redshift and the width represents the standard jackknife uncertainty.}         \label{fig:qf}
-    \end{center}
-\end{figure*}
 
@@
 
-\begin{figure}
-    \begin{center}
-        \leavevmode
-        \epsscale{1.0}
-        \epsfig{file=fig_qffit_cylr2_50000h35_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmasscomp11_0_10_5_lit_primuszerr.eps, height=0.45\textwidth}
-        \caption{The evolution of the quiescent fraction at fiducial
-          mass, $f_{Q}(\mathcal{M}_{\mathrm{fid}})$, for low (blue) and
-          high (red) density environments within the redshift range $z
-          = 0.0 - 0.8$. We present the $f_{Q}(\mathcal{M}_{\mathrm{fid}})$
-          evolution for $\mathcal{M}_{\mathrm{fid}} = 10^{10.5}
-          \mathcal{M}_\odot$ (solid fill) and $10^{11}
-          \mathcal{M}_\odot$ (patterned fill) with the uncertainty of
-          the best-fit parameter $b$ in Equation \ref{eq:qffit}
-          represented by the width of the line.
-While the high density $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ is greater than low density environment $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ over the entire redshift range of our sample, there is a significant increase in $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ over cosmic time for both environments.
-For the environment cut-offs ($n_{\mathrm{env}} < 0.5$ for low and $n_{\mathrm{env}} > 3.0$ for high), there is no significant difference in the slope of the evolution between the environments.}         \label{fig:qffit}
-    \end{center}
-\end{figure}
-
-\begin{table} 
-  \caption{Best Fit Parameters for $f_{\mathrm{Q}}(\mathcal{M}_{*})$ Fit}
-  \label{tab:bestfitparam}
-  \begin{center}
-    \leavevmode
-    \begin{tabular}{clcc} \hline \hline              
-    $z_1 < z < z_2$ &Environment        &a  &b  \\ \hline 
-$0.05 < z< 0.12$ &$n_{\mathrm{env}} < \lowenvthresh$ & $0.410 \pm 0.018$ & $0.469 \pm 0.007$ \\
-               &$n_{\mathrm{env}} > \highenvthresh$ & $0.270 \pm 0.016$ & $0.620 \pm 0.008$ \\ 
-                              &               &                       &                           \\ \hline   
-$0.2 < z <0.4$ & $n_{\mathrm{env}} < \lowenvthresh$ & $0.340 \pm 0.032$ & $0.432 \pm 0.015$ \\
-               &$n_{\mathrm{env}} > \highenvthresh$ & $0.432 \pm 0.018$ & $0.544 \pm 0.010$ \\
-               &               &                       &                           \\ \hline
-$0.4 < z < 0.6$      &$n_{\mathrm{env}} < \lowenvthresh$ & $0.263 \pm 0.038$ & $0.381 \pm 0.018$ \\
-               &$n_{\mathrm{env}} > \highenvthresh$ & $0.289 \pm 0.018$ & $0.446 \pm 0.013$ \\
-               &               &                       &                           \\ \hline
-$0.6 < z < 0.8$      &$n_{\mathrm{env}} < \lowenvthresh$ & $0.284 \pm 0.036$ & $0.352 \pm 0.019$ \\
-               &$n_{\mathrm{env}} > \highenvthresh$            & $0.468 \pm 0.065$ & $0.429 \pm 0.023$ \\
-               &               &                       &                           \\ \hline
-  \multicolumn{4}{l}{}                                             \\       
-    \end{tabular} \par
-    \end{center}
-%    \bigskip 
-    {\bf Notes}: Best fit parameters in Equation \ref{eq:qffit} for each subsample $f_{\mathrm{Q}}(\mathcal{M}_{*})$ in Figure \ref{fig:qf} for $\mathcal{M}_{\mathrm{fid}} = 10^{10.5} \mathcal{M}_{\odot}$.
-\end{table}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \def \pengpanel {c}
-\begin{figure*}
-    \begin{center}
-        \leavevmode
-        \epsscale{1.0}
-        \epsfig{file=fig_qffit_cylr2_50000h35_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmass10_5_lit_primuszerr_baldry_geha_iovino_kovac_peng_envthresh_kovacoffset.eps, height=\textwidth, angle=90}
-        \caption{$f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}=10^{10.5} \mathcal{M}_\odot)$ evolution compared to $f_{\mathrm{red}}(\mathcal{M}_{*} \sim 10^{10.5} \; \mathcal{M}_{\odot})$ in the literature: \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross) from SDSS (panel a), \cite{Iovino:2010aa} (empty square) and \cite{Kovac:2014aa} (triangle) from zCOSMOS (panel \kovacpanel), and \cite{Peng:2010aa} from both SDSS and zCOSMOS (panel \pengpanel).
-The $f_{\mathrm{red}}$ values from \cite{Iovino:2010aa}, \cite{Kovac:2014aa}, \cite{Baldry:2006aa}, and \cite{Peng:2010aa} are calculated from the best-fit parameterizations presented in the respective works.
-High density environment is represented in red and low density environment is represented in blue.
-The $f_{\mathrm{Q}}$ value from \cite{geha12a} is the $f_{\mathrm{Q}}$ value at $\mathcal{M} = 10^{10.55} \mathcal{M}_{\odot}$.
-Uncertainties in the \cite{Iovino:2010aa} best-fit $f_{\mathrm{red}}$ is omitted due to insufficient information on the cross correlation terms of the fit parameters.
-For \cite{Kovac:2014aa} we apply the offset between the color-based and SFR-based galaxy classification in order to plot the $f_{\mathrm{Q}}$ estimates.
-We also plot the $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}} = 10^{10.5} \mathcal{M}_\odot)$ evolution of our sample with varying environment cut-offs specified on the top right.
-As in Figure \ref{fig:qffit} the width of the $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}} = 10^{10.5} \mathcal{M}_\odot)$ evolution represent the uncertainty in the best-fit parameters of Equation \ref{eq:qffit}.}         \label{fig:qffit_comp}
-    \end{center}
-\end{figure*}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \bibliography{PRIMUS}
+
+\clearpage
+\begin{figure*}
+    \begin{center}
+        \leavevmode
+        \epsscale{1.0}
+	\plotone{fig_edp_sdss_z0_05_0_12_primus_z0_2_1_0_Mr_redshift.png}
+        \caption{Absolute magnitude $M_{r}$ versus redshift for our mass complete galaxy sample (black squares) with the Environment Defining Population (red circles) plotted on top.
+Both samples are divided into redshift bins: $z = 0.05-0.12$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ (panels left to right).
+The lowest redshift bin ($z \approx 0.05-0.12$; leftmost panel) contain our galaxy sample and EDP selected from SDSS.
+The rest contain galaxies and EDP selected from PRIMUS.
+The redshift limits for the lowest redshift bin are empirically selected based on the bright and faint limits of SDSS galaxies.
+Stellar mass completeness limits, described in Section \ref{sec:target}, are imposed on the galaxy population.
+Meanwhile, $M_{r}$ limits are applied to the EDP such that the number density in each panel are equivalent (Section \ref{sec:environment}).} \label{fig:targetEDP}
+    \end{center}
+\end{figure*}
+
+\clearpage
+
+\begin{table*} 
+  \caption{Galaxy Subsamples} \label{tab:subsample}
+  \begin{center}
+    \leavevmode
+    \begin{tabular}{ccccccc} \hline \hline              
+     &\multicolumn{1}{c}{$n_{\mathrm{env}}$}        & \multicolumn{2}{c}{$N_{\mathrm{gal}}$}  & \multicolumn{2}{c}{$\mathcal{M}_{\mathrm{lim}}$} & $M_{\mathrm{r}, lim}$ \\ 
+    & & Quiescent & Star-Forming & Quiescent & Star-Forming &  \\ \hline 
+$0.05 < z < 0.12$ & $n_{\mathrm{env}} < \lowenvthresh $ & 6533 & 7508 & $10^{10.2} \mathcal{M}_{\odot}$ & $10^{10.2} \mathcal{M}_{\odot}$ & -20.95 \\
+               & $n_{\mathrm{env}} > \highenvthresh $ &14673 & 9717 &                          \\ 
+                              & all          &$33553$                       & $29864$                          \\ \hline
+$0.2 < z < 0.4$      &$n_{\mathrm{env}} < \lowenvthresh $           &363                    &1231 & $10^{9.8} \mathcal{M}_{\odot}$ & $10^{9.8} \mathcal{M}_{\odot}$ &-21.03 \\
+               &$n_{\mathrm{env}} > \highenvthresh $            &379                    &756                           \\
+               & all                & $1086$                      & $2879$                          \\ \hline
+$0.4 < z < 0.6$      &$n_{\mathrm{env}} < \lowenvthresh $           &536                       &1498 & $10^{10.3} \mathcal{M}_{\odot}$ & $10^{10.3} \mathcal{M}_{\odot}$ & -20.98 \\
+               &$n_{\mathrm{env}} > \highenvthresh $            &490                       &854                           \\
+               & all               & $1560$                      & $3577$                          \\ \hline
+$0.6 < z < 0.8$      &$n_{\mathrm{env}} < \lowenvthresh $           &567                       &1254  & $10^{10.7} \mathcal{M}_{\odot}$ & $10^{10.6} \mathcal{M}_{\odot}$ & -20.97 \\
+               &$n_{\mathrm{env}} > \highenvthresh $            &498                       &671                           \\
+               & all              & $1668$                      & $2964$                          \\ \hline
+Total &      & \multicolumn{2}{c}{77151} & \\ \hline
+  \multicolumn{4}{l}{}                                             \\       
+    \end{tabular} \par
+    \end{center}
+    \tablecomments{Number of galaxies ($N_{\mathrm{gal}}$) in the mass complete subsamples within the edges of the survey (Section \ref{sec:sample}).
+The subsamples are classified based on environment ($n_{\mathrm{env}}$) and star formation rate (star-forming or quiescent).
+The lowest redshift bin is derived from SDSS; the rest are from PRIMUS.
+We also list the stellar mass completeness limit, $\mathcal{M}_{\mathrm{lim}}$, for our sample along with the $r$-band absolute magnitude limits, $M_{\mathrm{r}, lim}$, for the Environment Defining Population.
+}
+    \bigskip
+\end{table*}
+
+\clearpage
+
+\begin{figure}
+  \begin{center}
+    \leavevmode
+    \epsfig{file=fig_envcount_cylr2_5h35_thresh75_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_primuszerr_masslimit_edgecut_histogram.png, width=\textwidth}
+    \caption{Normalized distribution of environment measurements ($n_{\mathrm{env}}$) for our mass complete galaxy sample within the survey edges.
+A fixed cylindrical aperture of $R_{\mathrm{ap}} =\apradius\;\mathrm{Mpc}$ and $H_{\mathrm{ap}} = \apheight\; \mathrm{Mpc}$ is used to measure environment.
+The star-forming galaxies contribution to the distribution is colored in blue and diagonally patterned.
+The contribution from quiescent galaxies is colored in red.
+Galaxies with $n_{\mathrm{env}} < 0.5$ are in low density environments and galaxies with $n_{\mathrm{env}} > 3.0$ are in high density environment.
+We note that the significant difference among the SDSS distribution and the PRIMUS distributions above is due to the different stellar mass completeness limits imposed on each redshift bin of our galaxy sample.}      \label{fig:envcount}
+     %\caption{Normalized distribution of environment measurements ($n_{\mathrm{env}}$) for our mass complete galaxy sample within the edges.
+The star-forming galaxies contribution to the distribution is colored blue and diagonally patterned.
+The contribution from quiescent galaxies is colored in red.
+Each redshift panel is divided into three sections by the environment classification cutoffs (black veritcal lines): low density environment $n_{\mathrm{env}} < 0.5$ and high density environment $n_{\mathrm{env}} > 3.0$.
+The percentages of the redshift bin contained in the environment classifications are presented above the distribution.
+For example at $0.2 < z < 0.4$, $\apheight.0 \%$ of galaxies in the redshift bin are in low density environments while $35.0\%$ of galaxies in the redshift bin are in high density environments.
+We note that the significant difference between the SDSS distribution and the PRIMUS distribution above is due to the difference in stellar mass completeness limit imposed in our galaxy sample.}      \label{fig:envcount}
+    \end{center}
+\end{figure}
+
+\begin{figure*}
+  \begin{center}
+    \leavevmode
+    \epsfig{file=fig_smf_cylr2_50000h35_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_2envbin_lowenv0_5_highenv3_0_lit_primuszerr.eps, height=\textwidth,angle=90}
+     \caption{Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) galaxies in 
+low (left) and high (right) density environments throughout the redshift range
+$z=0$--$0.8$. The environment of each galaxy  
+was calculated using a cylindrical aperture size of $R=\apradius \: \mathrm{Mpc}$ and $H=\apheight \: \mathrm{Mpc}$ and  
+classified as low environment when $n_{\mathrm{env}} < 0.5$ and as high environment when $n_{\mathrm{env}} > 3.0$. The SMFs use mass bins of 
+width $\Delta \mathrm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.2$. In each panel we use shades of blue 
+(star-forming) and orange (quiescent) to represent the SMF at different redshift, higher redshifts being
+progressively lighter.}      \label{fig:smf}
+    \end{center}
+\end{figure*}
+
+\begin{figure*}
+    \begin{center}
+        \leavevmode
+        \epsfig{file=fig_qf_cylr2_50000h35_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_lit_primuszerr.eps, height=\textwidth,angle=90}
+        \caption{Evolution of the quiescent fraction $f_{\mathrm{Q}}$ for
+          galaxies in low (left) and high (right) density
+          environments for $z < 0.8$. $f_{\mathrm{Q}}$s were calculated
+          using the SMFs in Figure \ref{fig:smf}, as described in Section \ref{sec:qfevol}.
+Darker shading indicates lower redshift and the width represents the standard jackknife uncertainty.}         \label{fig:qf}
+    \end{center}
+\end{figure*}
+
+\begin{figure}
+\begin{center}
+\epsscale{0.8}
+\epsfig{file=fig_qffit_cylr2_50000h35_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmasscomp11_0_10_5_lit_primuszerr.eps, height=0.8\textwidth}
+\caption{The evolution of the quiescent fraction at fiducial mass, $f_{Q}(\mathcal{M}_{\mathrm{fid}})$, for low (blue) and high (red) density environments within the redshift range $z = 0.0 - 0.8$.
+We present the $f_{Q}(\mathcal{M}_{\mathrm{fid}})$ evolution for $\mathcal{M}_{\mathrm{fid}} = 10^{10.5} \mathcal{M}_\odot$ (solid fill) and $10^{11} \mathcal{M}_\odot$ (patterned fill) with the uncertainty of the best-fit parameter $b$ in Equation \ref{eq:qffit} represented by the width of the line.
+While the high density $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ is greater than low density environment $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ over the entire redshift range of our sample, there is a significant increase in $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ over cosmic time for both environments.
+For the environment cut-offs ($n_{\mathrm{env}} < 0.5$ for low and $n_{\mathrm{env}} > 3.0$ for high), there is no significant difference in the slope of the evolution between the environments.}         \label{fig:qffit}
+\end{center}
+\end{figure}
+
+\clearpage
+\begin{table} 
+  \caption{Best Fit Parameters for $f_{\mathrm{Q}}(\mathcal{M}_{*})$ Fit}
+  \label{tab:bestfitparam}
+  \begin{center}
+    \leavevmode
+    \begin{tabular}{clcc} \hline \hline              
+    $z_1 < z < z_2$ &Environment        &a  &b  \\ \hline 
+$0.05 < z< 0.12$ &$n_{\mathrm{env}} < \lowenvthresh$ & $0.410 \pm 0.018$ & $0.469 \pm 0.007$ \\
+               &$n_{\mathrm{env}} > \highenvthresh$ & $0.270 \pm 0.016$ & $0.620 \pm 0.008$ \\ 
+                              &               &                       &                           \\ \hline   
+$0.2 < z <0.4$ & $n_{\mathrm{env}} < \lowenvthresh$ & $0.340 \pm 0.032$ & $0.432 \pm 0.015$ \\
+               &$n_{\mathrm{env}} > \highenvthresh$ & $0.432 \pm 0.018$ & $0.544 \pm 0.010$ \\
+               &               &                       &                           \\ \hline
+$0.4 < z < 0.6$      &$n_{\mathrm{env}} < \lowenvthresh$ & $0.263 \pm 0.038$ & $0.381 \pm 0.018$ \\
+               &$n_{\mathrm{env}} > \highenvthresh$ & $0.289 \pm 0.018$ & $0.446 \pm 0.013$ \\
+               &               &                       &                           \\ \hline
+$0.6 < z < 0.8$      &$n_{\mathrm{env}} < \lowenvthresh$ & $0.284 \pm 0.036$ & $0.352 \pm 0.019$ \\
+               &$n_{\mathrm{env}} > \highenvthresh$            & $0.468 \pm 0.065$ & $0.429 \pm 0.023$ \\
+               &               &                       &                           \\ \hline
+  \multicolumn{4}{l}{}                                             \\       
+    \end{tabular} \par
+    \end{center}
+	\tablecomments{Best fit parameters in Equation \ref{eq:qffit} for each subsample $f_{\mathrm{Q}}(\mathcal{M}_{*})$ in Figure \ref{fig:qf} for $\mathcal{M}_{\mathrm{fid}} = 10^{10.5} \mathcal{M}_{\odot}$.}
+\end{table}
+\clearpage
+
+\begin{figure*}
+    \begin{center}
+        \leavevmode
+        \epsscale{1.0}
+\epsfig{file=fig_qffit_cylr2_50000h35_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmass10_5_lit_primuszerr_baldry_geha_iovino_kovac_peng_envthresh_kovacoffset.eps, height=\textwidth, angle=90}
+        \caption{$f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}=10^{10.5} \mathcal{M}_\odot)$ evolution compared to $f_{\mathrm{red}}(\mathcal{M}_{*} \sim 10^{10.5} \; \mathcal{M}_{\odot})$ in the literature: \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross) from SDSS (panel a), \cite{Iovino:2010aa} (empty square) and \cite{Kovac:2014aa} (triangle) from zCOSMOS (panel \kovacpanel), and \cite{Peng:2010aa} from both SDSS and zCOSMOS (panel \pengpanel).
+The $f_{\mathrm{red}}$ values from \cite{Iovino:2010aa}, \cite{Kovac:2014aa}, \cite{Baldry:2006aa}, and \cite{Peng:2010aa} are calculated from the best-fit parameterizations presented in the respective works.
+High density environment is represented in red and low density environment is represented in blue.
+The $f_{\mathrm{Q}}$ value from \cite{geha12a} is the $f_{\mathrm{Q}}$ value at $\mathcal{M} = 10^{10.55} \mathcal{M}_{\odot}$.
+Uncertainties in the \cite{Iovino:2010aa} best-fit $f_{\mathrm{red}}$ is omitted due to insufficient information on the cross correlation terms of the fit parameters.
+For \cite{Kovac:2014aa} we apply the offset between the color-based and SFR-based galaxy classification in order to plot the $f_{\mathrm{Q}}$ estimates.
+We also plot the $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}} = 10^{10.5} \mathcal{M}_\odot)$ evolution of our sample with varying environment cut-offs specified on the top right.
+As in Figure \ref{fig:qffit} the width of the $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}} = 10^{10.5} \mathcal{M}_\odot)$ evolution represent the uncertainty in the best-fit parameters of Equation \ref{eq:qffit}.}         \label{fig:qffit_comp}
+    \end{center}
+\end{figure*}
+
 \end{document}

### 2014-12-24 qfenv_paper/qf_environment.tex
Title change

@@
 
-\title{PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 0.8$}
+\title{PRIMUS: Effect of Galaxy Environment on the Quiescent Fraction Evolution at $z < 0.8$}
 \author{
@@
 \end{abstract}
-
+\keywords{cosmology:observations --- galaxies: evolution --- galaxies:groups --- galaxies: star formation}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %
+\bibliographystyle{apj}
 \bibliography{PRIMUS}

### 2015-03-11 qfenv_paper/ApJ submission/qf_environment.tex
Title change
minor changes

@@
 
-\title{PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at \lowercase{\textit{z}}$<0.8$}
+\title{PRIMUS: Effect of Galaxy Environment on the Quiescent Fraction Evolution at \lowercase{\textit{z}}$<0.8$}
 \author{
@@
 of star formation is due to external influences on
-them. However, in the recent Universe a substantial fraction of the
+them. In other words, in the recent Universe a substantial fraction of the
 galaxies that cease forming stars do so due to internal processes.
@@
     \leavevmode
-    \epsfig{file=fig3.eps, height=0.75\textwidth,angle=90}
+    \epsfig{file=fig3.pdf, height=0.75\textwidth,angle=90}
      \caption{Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) galaxies in 
@@
         \leavevmode
-        \epsfig{file=fig4.eps, height=0.75\textwidth,angle=90}
+        \epsfig{file=fig4.pdf, height=0.75\textwidth,angle=90}
         \caption{Evolution of the quiescent fraction $f_{\mathrm{Q}}$ for
@@
         \epsscale{1.0}
-        \epsfig{file=fig5, height=0.45\textwidth}
+        \epsfig{file=fig5.pdf, height=0.45\textwidth}
         \caption{The evolution of the quiescent fraction at fiducial
@@
         \epsscale{1.0}
-        \epsfig{file=fig6.eps, height=\textwidth, angle=90}
+        \epsfig{file=fig6.pdf, height=\textwidth, angle=90}
         \caption{$f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}=10^{10.5} \mathcal{M}_\odot)$ evolution compared to $f_{\mathrm{red}}(\mathcal{M}_{*} \sim 10^{10.5} \; \mathcal{M}_{\odot})$ in the literature: \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross) from SDSS (panel a), \cite{Iovino:2010aa} (empty square) and \cite{Kovac:2014aa} (triangle) from zCOSMOS (panel \kovacpanel), and \cite{Peng:2010aa} from both SDSS and zCOSMOS (panel \pengpanel).

### 2015-03-11 qfenv_paper/hahn_qfenv_abstract.tex
minor changes

--- 2014-12-24 qfenv_paper/qf_env_apj.tex
@@
-\documentclass[manuscript]{aastex}
+\documentclass{emulateapj}
 \bibliographystyle{apj}
@@
 %internal short cuts
+\def \HgA {H$\gamma_A$}
+\def \Hbp {H$\beta ^\prime$}
 \def \lowenvthresh {0.5}
@@
 Kenneth C.~Wong\altaffilmark{6}, 
-Guangtun~Zhu\altaffilmark{7,8}
+Guangtun~Zhu\altaffilmark{7}
 }
@@
 \end{abstract}
-
-\keywords{cosmology:observations --- galaxies: evolution --- galaxies:groups --- galaxies: star formation}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% INTRODUCTION
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-Galaxies, in their detailed properties, carry the imprints of their surroundings, with a strong dependence of the quiescent fraction of galaxies on their local environment (e.g.
-\citealt{hubble36a, oemler74a, dressler80a, hermit96a, guzzo97a}; for a recent review see \citealt{blanton09a}).
-The strength of this dependence is itself a strongly decreasing function of galaxy stellar mass; at the extreme, the lowest mass ($<10^{9}$ $M_\odot$) galaxies end their star formation only in dense regions, and never in isolation (\citealt{geha12a}).
-These effects also vary with redshift at least in the densest clusters, as observed in the changing fraction of late-type spirals relative to the field, found in studies of the morphology-density relation (\citealt{dressler84a, Fasano:2000aa, Smith:2005aa, desai07a}).
-Clearly understanding the properties of galaxies in the present-day universe requires a careful investigation of the role of environment, and how that role changes over time.
-
-%Moreover, at $z < 1$ lower star-formation rate early-type galaxies are found populating the denser regions (\citealt{cooper08a, patel09a, kovac10a}).
-
-Nevertheless, the evolution of the role of environment is a relatively subtle effect and must be interpreted within the context of the evolving galaxy population.
-For instance, the most dramatic change in galaxy properties during the past eight billion years has been the remarkable decline in the star-formation rate of galaxies in the Universe (\citealt{hopkins06a}).
-This decline appears dominated by decreases in the rates of star-formation of individual galaxies (\citealt{Noeske:2007aa}).
-There is evidence that a large fraction of the decline is associated with strongly infrared-emitting starbursts (\citealt{bell05a, magnelli09a}).
-As \cite{cooper08a} and others have pointed out, because the environmental dependence of total star-formation rates at fixed redshift is relatively small, environmental effects are unlikely to cause the overall star-formation rate decline.
-
-During this period, the major classes of galaxies that we observe today have already been firmly in place (\citealt{bundy06a, borch06a, taylor09a, Moustakas:2013aa}).
-Though not as dramatic as the history of galaxies prior to $z \sim 1$, detailed observations of the stellar mass function find significant evolution of the galaxy population with the decline in the number density of massive star-forming galaxies accompanied by an increase in the number density of quiescent galaxies (\citealt{Blanton:2006aa, bundy06a,  borch06a, Moustakas:2013aa}).
-\cite{Moustakas:2013aa}, for instance, find that since $z \sim 1.0$ the $\sim 50\%$ decline in the number density of massive star-forming galaxies ($\mathcal{M}_{*} > 10^{11} \mathcal{M}_{\odot}$) is complemented by the rise in number density of intermediate-mass quiescent galaxies ($\mathcal{M}_{*} \approx 10^{9.5} - 10^{10}\mathcal{M}_{\odot}$), by a factor of $ 2-3$, and massive quiescent galaxies ($\mathcal{M}_{*} > 10^{11} \mathcal{M}_{\odot}$ ), by $\sim 20\%$.
-On the color-magnitude diagram, this corresponds to the doubling of the red sequence over this period (\citealt{Bell:2004aa, borch06a, Faber:2007aa}).
-These changes in galaxy population are likely a result of physical processes that cause the cessation of star-formation in star-forming galaxies.
-
-Of the numerous mechanisms that have been proposed to explain this cessation, favored models suggest that internal processes such as supernovae or active galactic nuclei heat the gas within the galaxy, which consequently suppresses the cold gas supply used for star-formation (\citealt{Keres:2005aa, Croton:2006aa, Dekel:2008aa}).
-Other models propose that environment dependent external processes such as ram-pressure stripping (\citealt{Gunn:1972aa, Bekki:2009aa}), strangulation (\citealt{Larson:1980aa, Balogh:2000aa}), or harassment (\citealt{Moore:1998aa}) contribute to the cessation.
-
-Observations such as \cite{Weinmann:2006aa} and \cite{Peng:2010aa} credit some of these proposed internal processes for the cessation of star-formation, especially in massive galaxies.
-Meanwhile, observations of galaxy properties such as color and morphology correlating with environment suggest that environment may play a role in ceasing star-formation (\citealt{blanton09a} and references therein).
-However, it remains to be determined whether the environmental trends in galaxy properties reflect the direct effect of external environment on the galaxies' evolution (e.g.
-ram pressure, tidal forces, mergers) or reflect statistical differences in the histories of galaxies in different environments (e.g.
-an earlier formation time in dense regions).
-
-In this paper we take the most straightforward investigation
-by directly determining the star-forming properties of galaxies
-as a function of environment, stellar mass and redshift in a single,
-consistently analyzed data set. This analysis can reveal how galaxies
-end their star formation over time, quantitatively establish the
-contribution of environmental effects to the overall trends, and
-reveal whether those trends happen equally in all environments.
-However, such an analysis has not been done previously due to the lack
-of sufficiently large samples. In this paper, we apply this approach
-using the PRIism MUlti-object Survey (PRIMUS; \citealt{Coil:2011aa},
-\citealt{Cool:2013aa}), the largest available redshift survey covering
-the epochs between $0<z<1$.
-
-In Section \ref{sec:sample} we present a brief description of the
-PRIMUS and SDSS data, our mass complete sample construction, and
-galaxy environment measurements. After dividing our galaxy sample into
-subsamples of star-forming or quiescent and high or low density
-environments, we compute and examine the evolution of the stellar mass
-functions for our subsamples in Section \ref{sec:smf}. In
-Section \ref{sec:qf_const}, we calculate the quiescent fraction,
-analyze the evolution of the quiescent fraction, quantify the effects
-of environment on the quiescent fraction evolution, and discuss the
-implications of our quiescent fraction results on the cessation of
-star-formation in galaxies. Finally in Section \ref{sec:summary} we
-summarize our results.
-
-Throughout the paper we assume a cosmology with $\Omega_{m} = 0.3,
-\Omega_{\Lambda} = 0.7$, and $H_0 = 70 \: \mathrm{km} \; \mathrm{s}^{-1}
-\mathrm{Mpc}^{-1}$. All magnitudes are AB-relative.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% SAMPLE SELECTION
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Sample Selection} \label{sec:sample}
-We are interested in quantifying the effects of galaxy environment on
-the evolution of the quiescent fraction over the redshift range $0 < z < 1$.
-For our analysis, we require a sample with sufficient depth and high quality spectroscopic redshift to probe the redshift range and to robustly measure galaxy environment.
-PRIMUS with its $\sim 120,000$ spectroscopic redshifts provides a large data set at intermediate redshifts for our analysis.
-In addition, we anchor our analysis with a low redshift sample derived from the Sloan Digital Sky Survey (\citealt{York:2000aa}).
-
-In Section \ref{sec:primus} and Section \ref{sec:sdss} we provide a
-brief summary of the PRIMUS and SDSS data used for our sample
-selection. In Section \ref{sec:target} we define our stellar mass complete galaxy sample.  
-Then, in Section \ref{sec:sfq}, we classify the sample galaxies as quiescent or star-forming. 
-We calculate the environment
-using a volume-limited Environment Defining Population in Section
-\ref{sec:environment}.  Finally, in Section \ref{sec:edgeeffect}, we
-account for edge effects in the surveys.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% PRIMUS
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{PRIMUS} \label{sec:primus}
-At intermediate redshifts we use multiwavelength imaging and
-spectroscopic redshifts from PRIMUS, a faint galaxy survey with $\sim
-120,000$ redshifts ($\sigma_z/(1+z) \approx 0.5 \%$) within the range
-$z \approx 0-1.2$. The survey was conducted using the IMACS
-spectrograph on the Magellan I Baade $6.5$-m telescope with a slitmask and low dispersion prism.
-For details on the PRIMUS observation methods such as survey design, targeting, and data summary, we refer readers to the survey papers (\citealt{Coil:2011aa, Cool:2013aa}).
-
-While the PRIMUS survey targeted seven distinct extragalactic deep fields for a total of $\sim 9 \; \mathrm{deg}^2$, we restrict our sample to five fields that have $GALEX$ and {\em Spitzer}/IRAC imaging for a total of $\sim 5.5 \; \mathrm{deg}^2$ (similar to the sample selection in \citealt{Moustakas:2013aa}).
-Four of these fields are a part of the {\em Spitzer} Wide-area Infrared Extragalactic Survey (SWIRE\footnote{http://swire.ipac.caltech.edu/swire/swire.html}): the European Large Area ISO Survey - South $1$ field (ELAIS-S1\footnote{http://dipastro.pd.astro.it/esis}), the Chandra Deep Field South SWIRE field (CDFS), and the XMM Large Scale Structure Survey field (XMM-LSS).
-The XMM-LSS consists of two separate but spatially adjacent fields: the Subaru/XMM-Newton DEEP Survey field (XMM-SXDSS\footnote{http://www.naoj.org/cience/SubaruProject/SDS}) and the Canadian-France-Hawaii Telescope Legacy Survey field (XMM-CFHTLS\footnote{http://www.cfht.hawaii.edu/Science/CFHLS}).
-Our fifth and final field is the Cosmic Evolution Survey (COSMOS\footnote{http://cosmos.astro.caltech.edu}) field.
-For all of our fields we have near-UV (NUV) and far-UV (FUV) photometry from the {\em GALEX} Deep Imaging Survey (DIS; \citealt{Martin:2005aa, Morrissey:2005aa}) as well as ground-based optical and {\em Spitzer}/IRAC mid-infrared photometric catalogs.
-\cite{Moustakas:2013aa} provides detailed descriptions of integrated flux calculations in the photometric bands for each of our fields.
-Furthermore, we derive the {\em K-corrections} from the photometry using \texttt{K-correct} (v4.2; \citealt{Blanton:2007aa}).
-
-Finally, using the spectroscopic redshift and broad wavelength photometry we apply \texttt{iSEDfit}, a Bayesian SED modeling code, to calculate stellar masses and star formation rates (SFRs) for our sample galaxies (\citealt{Moustakas:2013aa}).
-\texttt{iSEDfit} uses the redshift and the observed photometry of the galaxies to determine the statistical likelihood of a large ensemble of generated model SEDs.
-The model SEDs are generated using Flexible Stellar Population Synthesis (FSPS) models (\citealt{Conroy:2010aa}) based on the \cite{Chabrier:2003aa} IMF, along with other prior parameters discussed in Section 4.1 and Appendix A of \cite{Moustakas:2013aa}.
-For the observed photometry, we use the {\em GALEX} FUV and NUV, the two shortest IRAC bands at $3.6$ and $4.5 \mu \mathrm{m}$ (the two longer-wavelength IRAC channels are excluded because \texttt{iSEDfit} does not model hot dust or polycyclic aromatic hydrocarbons emission lines), and the optical bands.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% SDSS-GALEX
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{SDSS-GALEX} \label{sec:sdss}
-At low redshifts, we use spectroscopic redshifts and $ugriz$ photometry from the SDSS Data Release 7 (DR7; \citealt{Abazajian:2009aa}).
-More specifically we select galaxies from the New York University Value-Added Galaxy Catalog (hereafter VAGC) that satisfy the main sample criterion and have galaxy extinction corrected Petrosian magnitudes $14.5 < r < 17.6$ and spectroscopic redshifts within $0.01 < z < 0.2$ (\citealt{Blanton:2005aa}).
-We further restrict the VAGC sample to only galaxies with medium depth observations with total exposure time greater than $1 \; \mathrm{ks}$ from {\em GALEX} Release 6.
-This leaves $167,727$ galaxies.
-
-Next, we use the MAST/CasJobs\footnote{http://galex.stsci.edu/casjobs} interface and a $4''$ diameter search radius, to obtain the NUV and FUV photometry for the SDSS-{\em GALEX} galaxies.
-For optical photometry, we use the $ugriz$ bands from the SDSS \texttt{model} magnitudes scaled to the $r$-band \texttt{cmodel} magnitude.
-These photometric bands are then supplemented with integrated $JHK_s$ magnitudes from the 2MASS Extended Source Catalog (XSC; \citealt{Jarrett:2000aa}) and with photometry at $3.4$ and $4.6 \mu \mathrm{m}$ from the WISE All-Sky Data Release\footnote{http://wise2.ipac.caltech.edu/docs/release/allsky}.
-Further details regarding the SDSS-{\em GALEX} sample photometry can be found in Section 2.4 of \cite{Moustakas:2013aa}.
-As previously done on the PRIMUS data in Section \ref{sec:primus}, we use \texttt{iSEDfit} to obtain the stellar masses and star formation rates for the SDSS-{\em GALEX} sample.
-
-The SDSS-{\em GALEX} data discussed above is derived from the NYU-VAGC
-based on SDSS Data Release 7, using the standard SDSS photometric
-measurements. Several investigators have found that the background
-subtraction techniques used in the standard photometric catalogs
-introduce a size dependent bias in the galaxy fluxes and consequently
-stellar masses (\citealt{West:2005aa, Blanton:2005ab, Lauer:2007aa, Bernardi:2007aa,
-  Hyde:2009aa, West:2010aa}).
-
-In order to quantify the effects of these photometric underestimations
-in our analysis, we tried replacing our SDSS fluxes in the $ugriz$
-band with $ugriz$ fluxes from the NASA-Sloan Atlas (NSA) catalog,
-which incorporate the improved background subtraction presented in
-\cite{Blanton:2011aa} and uses single-Seric fit fluxes rather than the
-standard SDSS \texttt{cmodel} fluxes. Using the ratio of the
-luminosity derived from the improved photometry over the luminosity
-derived from the standard NYU-VAGC photometry, we apply a preliminary
-correction to the stellar mass values obtained from \texttt{iSEDfit}
-assuming a consistent mass-to-light ratio. This mass correction leads
-to a significant increase in the stellar mass function for
-$\mathcal{M} > 10^{11} \mathcal{M}_{\odot}$; however, the effect of
-the mass correction was negligible for the quiescent fraction
-evolution results. As a result, for the results presented here we use
-the standard SDSS fluxes and we do not discuss the issues with
-photometric measurements any further in this paper. We note that a
-thorough investigation of these issues to understand their effect on
-the stellar mass function requires a reanalysis of both the SDSS
-photometry and the deeper photometry used for PRIMUS targeting.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% GALAXY SAMPLE
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Stellar Mass Complete Galaxy Sample} \label{sec:target} 
-From the low redshift SDSS-{\em GALEX} and intermediate redshift
-PRIMUS data we define our mass complete galaxy
-sample. We begin by imposing the parent sample selection criteria from
-\cite{Moustakas:2013aa}. More specifically, we take the statistically
-complete {\em primary} sample from the PRIMUS data
-(\citealt{Coil:2011aa}) and impose magnitude limits on optical
-selection bands as specified in \cite{Moustakas:2013aa} Table 1. These
-limits are in different optical selection bands and have distinct
-values for the five PRIMUS target fields. We then exclude stars and
-broad-line AGN to only select objects spectroscopically classified as
-galaxies, with high-quality spectroscopic redshifts ($Q \geq
-3$). Lastly, we impose a redshift range of $ 0.2 < z < 0.8$ for the
-PRIMUS galaxy sample, where $ z > 0.2$ is selected due to limitations
-from sample variance and $ z < 0.8$ is selected due to the lack of
-sufficient statistics in subsamples defined below.
-
-For the PRIMUS objects that meet the above criteria, we assign statistical weights (described in \citealt{Coil:2011aa} and \citealt{Cool:2013aa}) in order to correct for targeting incompleteness and redshift failures.
-The statistical weight, $w_i$, for each galaxy is given by
-\begin{equation}
-w_{i} = (f_{\mathrm{target}} \times f_{\mathrm{collision}} \times f_{\mathrm{success}})^{-1},
-\end{equation}
-as in Equation (1) in \cite{Moustakas:2013aa}.
-
-Since we are ultimately interested in a mass complete galaxy sample to
-derive SMFs and QFs, next we impose stellar mass completeness limits
-to our galaxy sample.
-Stellar mass completeness limits for a magnitude-limited survey such as PRIMUS are functions of redshift, the apparent magnitude limit of the survey, and the typical stellar mass-to-light ratio of galaxies near the flux limit.
-We use the same procedure as \cite{Moustakas:2013aa}, which follows \cite{Pozzetti:2010aa}, to empircally determine the stellar mass completeness limits.
-For each of the target galaxies we compute $\mathcal{M}_{\mathrm{lim}}$ using $\log \; \mathcal{M}_{\mathrm{lim}} = \log \; \mathcal{M} + 0.4\;(m - m_{\mathrm{lim}})$, where $\mathcal{M}$ is the stellar mass of the galaxy in $\mathcal{M_{\odot}}$, $\mathcal{M}_{\mathrm{lim}}$ is the stellar mass of each galaxy if its magnitude was equal to the survey magnitude limit, $m$ is the observed apparent magnitude in the selection band, and $m_{\mathrm{lim}}$ is the magnitude limit for our five fields.
-We construct a cumulative distribution of $\mathcal{M}_{\mathrm{lim}}$ for the $15\%$ faintest galaxies in $\Delta z=0.04$ bins.
-In each of these redshift bins, we calculate the minimum stellar mass that includes $95 \%$ of the galaxies.
-Separately for quiescent and star-forming galaxies, we fit quadratic polynomials to the minimum stellar masses versus redshift (star-forming or quiescent classification is described in the following section).
-Finally, we use the polynomials to obtain the minimum stellar masses at the center of redshift bins, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$, which are then used as PRIMUS stellar mass completeness limits.
-
-For the low redshift portion of our galaxy sample, we start by limiting the SDSS-{\em GALEX} data to objects within $0.05 < z < 0.12$, a redshift range later imposed on the volume-limited Environment Defining Population (Section \ref{sec:environment}).
-To account for the targeting incompleteness of the SDSS-{\em GALEX} sample, we use the statistical weight estimates provided by the NYU-VAGC catalog.
-Furthermore, we determine a uniform stellar mass completeness limit of $10^{10.2} \mathcal{M}_{\odot}$ above the stellar mass-to-light ratio completeness limit of the SDSS-{\em GALEX} data within the imposed redshift limits (\citealt{Blanton:2005ab, Baldry:2008aa, Moustakas:2013aa}).
-We then apply this mass limit in order to obtain our mass-complete galaxy sample at low redshift.
-
-We now have a stellar mass complete sample derived from SDSS-{\em
-  GALEX} and PRIMUS data. Since our sample is derived from two
-different surveys, we account for the disparity in the redshift
-uncertainty. While PRIMUS provides a large number of redshifts out to
-$z = 1$, due to its use of a low dispersion prism, the redshift
-uncertainties are significantly larger ($\sigma_{z}/(1+z) \approx 0.5
-\%$) than the uncertainties of the SDSS-{\em GALEX} redshifts. In order to have
-comparable environment measures throughout our redshift range, we
-apply PRIMUS redshift uncertainties to our galaxy sample selected from
-SDSS-{\em GALEX}. For each SDSS-{\em GALEX} galaxy, we adjust its
-redshift by randomly sampling a Gaussian distribution with standard
-deviation $\sigma = 0.005 (1+z_{\mathrm{SDSS}-GALEX})$, where
-$z_{\mathrm{SDSS}-GALEX}$ is the redshift of the galaxy.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% CLASSIFYING QUIESCENT AND STAR-FORMING GALAXIES
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Classifying Quiescent and Star-Forming Galaxies} \label{sec:sfq}
-We now classify our mass complete galaxy sample into quiescent or star-forming using an evolving cut based on specific star-formation rate utilized in \cite{Moustakas:2013aa} Section 3.2.
-This classification method uses the star-forming (SF) sequence, which is the correlation between star-formation rate (SFR) and stellar mass in star-forming galaxies observed at least until $z \sim 2$ (\citealt{Noeske:2007aa, Williams:2009aa, Karim:2011aa}).
-The PRIMUS sample displays a well-defined SF sequence within the redshift range of our galaxy sample.
-Using the power-law slope for the SF sequence from \cite{Salim:2007aa} (SFR $\propto \mathcal{M}^{0.65}$) and the minimum of the quiescent/star-forming bimodality, determined empirically, we obtain the following equation to classify the target galaxies (Equation 2 in \citealt{Moustakas:2013aa}):
-\begin{equation} \label{eq:qsfclass} 
-\mathrm{log}(\mathrm{SFR}_{\mathrm{min}}) = -0.49 + 0.64 \mathrm{log}(\mathcal{M} - 10) +1.07(z-0.1), 
-\end{equation} 
-where $\mathcal{M}$ is the stellar mass of the galaxy.
-If the target galaxy SFR and stellar mass lie above Equation \ref{eq:qsfclass} we classify it as star-forming; if below, as quiescent (\citealt{Moustakas:2013aa} Figure 1.).
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% GALAXY ENVIRONMENT
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Galaxy Environment} \label{sec:environment}
-We define the environment of a galaxy as the number of neighboring Environment Defining Population galaxies (defined below) within a fixed aperture centered around it.
-We use fixed aperture measurements in order to quantify galaxy environment with an aperture sufficiently large to encompass massive halos (\citealt{Muldrew:2012aa, Skibba:2013aa}).
-%We use a fixed aperture measurement of environment in order to probe environment on the halo scale, as \cite{Muldrew:2012aa} finds in their comparison of different environment definition using simulations.
-
-For our aperture, we use a cylinder of dimensions: $R_{\mathrm{ap}} =
-\apradius\;
-\mathrm{Mpc}$ and $H_{\mathrm{ap}} = \apheight\; \mathrm{Mpc}$.  We use a
-cylindrical aperture to account for the PRIMUS redshift
-errors and redshift space distortions (i.e. ``Finger of God"
-effect). As \cite{Cooper:2005aa} and \cite{Gallazzi:2009aa} find, 
-$\pm 1000 \; \mathrm{km} \;\mathrm{s^{-1}}$ optimally reduces the effects of redshift space
-distortions. The PRIMUS redshift uncertainty at $z \sim 0.7$
-corresponds to $\sigma_z < 0.01$, so our choice of $\apheight\;
-\mathrm{Mpc}$ for the aperture height accounts for both of these effects. Our choice of
-cylinder radius was motivated by scale dependence analyses in the
-literature (\citealt{Blanton:2006aa, Wilman:2010aa, Muldrew:2012aa}),
-which suggest that galactic properties such as color and quiescent
-fractions are most strongly dependent on scales $< 2$ Mpc, around the
-host dark matter halo sizes.
-
-Before we measure the environment for our galaxy sample, we first
-construct a volume limited Environment Defining Population (EDP) with
-absolute magnitude cut-offs ($M_{r}$) in redshift bins with $\Delta z
-\sim 0.2$. The $M_{r}$ cut-offs for the EDP are selected such that the
-cumulative number density over $M_{r}$ for all redshift bins are
-equal.  We make this choice in order to construct an EDP that contains
-similar galaxy populations through the redshift range (i.e. accounts
-for the progenitor bias). In their analysis of this method,
-\cite{Behroozi:2013aa} and \cite{Leja:2013aa} find that although it
-does not precisely account for the scatter in mass accretion or
-galaxy-galaxy mergers, it provides a reasonable means to compare
-galaxy populations over a wide range of cosmic time.
-
-In constructing the PRIMUS EDP we use the same PRIMUS data used to select our galaxy sample (described in Section \ref{sec:target}).
-We again restrict the PRIMUS galaxies to $0.2 < z < 0.8$ and divide them into bins of $\Delta z = 0.2$.
-Before we consider the cumulative number densities in the redshift bins, we first determine the $M_r$ limit for the highest redshift bin ($z = 0.6-0.8$) by examining the $M_{r}$ distribution with bin size $\Delta M_{r} = 0.25$ and select $M_{r,\mathrm{lim}}$ near the peak of the distribution where bins with $M_{r} > M_{r,\mathrm{lim}}$ have fewer galaxies than the bin at $M_{r, \mathrm{lim}}$.
-We conservatively choose $M_{r, \mathrm{lim}}(0.6 < z < 0.8)$ to be $M_{r} = -20.97$.
-Then for the lower redshift bins, we impose absolute magnitude limits ($M_{r,\mathrm{lim}}$) such that the cumulative number density, calculated with the galaxy statistical weights, of the bin ordered by $M_{r}$ is equal to the cumulative number density of the highest redshift bin with $M_{r, \mathrm{lim}}(0.6 < z < 0.8) = -20.97$.
-
-For the SDSS EDP, we do not use the SDSS-{\em GALEX} parent data,
-which is limited to the combined angular selection window of the
-VAGC and {\em GALEX} (Section \ref{sec:sdss}). Instead, since FUV, NUV
-values are not necessary for the EDP, we extend the parent data of the
-SDSS EDP to the entire NYU-VAGC, including galaxies outside of the
-{\em GALEX} window function. Furthermore, we impose a redshift range
-of $0.05-0.12$ on the SDSS EDP. This redshift range was determined to
-account for the lack of faint galaxies at $z \sim 0.2$ and the lack of
-bright galaxies at $z \sim 0.01$ in the VAGC. As with the PRIMUS
-redshift bins, we determine the SDSS EDP $M_{r, \mathrm{lim}}$ by matching
-the cumulative number density of the highest redshift bin. For
-redshift bins $z = 0.05-0.12$, $0.2-0.4$, $0.4-0.6$, $0.6-0.8$ we get
-$M_{r,\mathrm{lim}} = -20.95$, $-21.03$, $-20.98$ and $-20.97$,
-respectively. These absolute magnitude limits are illustrated in
-Figure \ref{fig:targetEDP}, where we present the absolute magnitude ($M_{r}$) versus redshift for the galaxy sample (black squares) ad the EDP (red circles). 
-The left-most panel corresponds to the samples derived from the SDSS-{\em GALEX} data while the rest correspond to samples derived from the PRIMUS data divided in bins with $\Delta z \sim 0.2$. 
-Figure \ref{fig:targetEDP} shows clear $M_r$ cutoffs in the
-$M_{r}$ distribution versus redshift for the EDP on top
-of our galaxy sample.
-
-For our SDSS-{\em GALEX} galaxy sample, in Section \ref{sec:target}, we apply PRIMUS redshift errors in order to establish a consistent measurement of environment throughout our redshift range.
-We appropriately apply equivalent redshift adjustments for the SDSS EDP.
-For the SDSS EDP galaxies that are also contained within the SDSS-{\em GALEX} sample, we adjust the redshift by an identical amount.
-For the rest, we apply the same redshift adjustment procedure described in Section \ref{sec:target} in order to obtain PRIMUS level redshift uncertainties.
-
-Finally, we measure the environment for each galaxy in our galaxy
-sample by counting the number of EDP galaxies, $n_{\mathrm{env}}$, with RA,
-Dec, and $z$ within our cylindrical aperture centered around
-it. $n_{\mathrm{env}}$ accounts for the statistical weights of the EDP
-galaxies. 
-For our galaxy sample, the expected $n_{\mathrm{env}}$ given the uniform number density in 
-each of our EDP redshift bin and volume of our cylindrical aperture is $\langle n_{\mathrm{env}} \rangle = 1.3$. 
-Once we obtain environment measurements for all the galaxies
-in our galaxy sample, we classify galaxies with $n_{\mathrm{env}} < 0.5$
-to be in ``low" environment densities and galaxies with $n_{\mathrm{env}} > 3$
-to be in ``high" environment densities. The high environment cutoff was
-selected in order to reduce contamination from galaxies in low
-environment densities while maintaining sufficient statistics. In
-Section \ref{sec:env_qf_evol} we will also explore higher density
-cutoffs for $n_{\mathrm{env}}$.
-
-The analysis we describe below uses a fixed cylindrical aperture with
-dimensions $R_{\mathrm{ap}} = \apradius \; \mathrm{Mpc}$ and $H_{\mathrm{ap}} = \apheight
-\;\mathrm{Mpc}$ to measure environment. The same analysis was
-extended for varying aperture dimensions $R_{\mathrm{ap}} = 1.5, \: \apradius, \:3.0 \:
-\mathrm{Mpc}$ and $H_{\mathrm{ap}} = \apheight, \; 70 \;\mathrm{Mpc}$ with adjusted environment classifications. 
-The results obtained from using different apertures and
-environment classifications are qualitatively consistent with the results presented below.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% EDGE EFFECTS
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Edge Effects} \label{sec:edgeeffect}
-One of the challenges in obtaining accurate galaxy environments using a fixed aperture method is accounting for the edges of the survey.
-For galaxies located near the edge of the survey, part of the fixed aperture encompassing it will lie outside the survey regions.
-In this scenario, $n_{env}$ only reflects the fraction of the environment within the survey geometry.
-
-To account for these edge effects, we use a Monte Carlo method to impose edge cutoffs on our galaxy sample.
-First, using \texttt{ransack} from \cite{Swanson:2008aa}, we construct a random sample of  $N_{\mathrm{ransack}} = 1,000,000$ points with RA and Dec randomly selected within the window function of the EDP (SDSS EDP and PRIMUS EDP separately).
-We then compute the angular separation, $\theta_{i, \mathrm{ap}}$ that corresponds to $R_{\mathrm{ap}}$ (Section \ref{sec:environment}) at the redshift of each sample galaxy $i$.
-For each sample galaxy we count the number of \texttt{ransack} points within $\theta_{i, \mathrm{ap}}$ of the galaxy: $n_{i,\mathrm{ransack}}$.
-Afterwards, we compare $n_{i,\mathrm{ransack}}$ to the expected value computed from the angular area of the environment defining aperture and the EDP window function:
-\begin{equation} \label{eq:ransack}
-\langle n_{\mathrm{ransack}}\rangle_{i} = \frac{N_{\mathrm{ransack}}}{A_{\mathrm{EDP}}}\times {\pi \theta_{i, \mathrm{ap}}^2} \times f_{\mathrm{thresh}}. 
-\end{equation} 
-$A_{\mathrm{EDP}}$ is the total angular area of the EDP window function and $f_{\mathrm{thresh}}$ is the fractional threshold for the edge effect cut-off.
-For $R_{\mathrm{ap}}= \apradius \;\mathrm{Mpc}$, we use $f_{\mathrm{thresh}} = 0.75$.
-If $n_{i, \mathrm{ransack}} > \langle n_{\mathrm{ransack}} \rangle_i$ then galaxy $i$ remains in our sample; otherwise, it is discarded.
-Once the edge effect cuts are applied, we are left with the final galaxy sample.
-For our SDSS-{\em GALEX} galaxy sample, $\sim 12 \%$ of galaxies are removed from the edge effect cuts.
-For our PRIMUS galaxy sample, $\sim 40 \%$ of galaxies are removed from the edge effect cuts.
-
-In Figure \ref{fig:envcount} we present the distribution of environment measurements ($n_{\mathrm{env}}$) for our final galaxy sample in redshift bins: $z = 0.05 - 0.12$, $0.2 - 0.4$, $0.4-0.6$, and $0.6-0.8$.
-The quiescent galaxy contributions are colored in red while the star-forming galaxy contributions are colored in blue and patterned.
-We classify galaxies with $n_{\mathrm{env}} < 0.5$ to be in low density environments and galaxies with $n_{\mathrm{env}} > 3.0$ to be in high density environments.
-
-Although we imposed PRIMUS redshift errors on our SDSS galaxies to consistently measure environment throughout our entire sample, we note a significant discrepancy between the $n_{\mathrm{env}}$ distributions of the SDSS and PRIMUS samples.
-For example, in each of the PRIMUS redshift bins, $\sim 40 \%$ of galaxies in the redshift bin are in low density environments and roughly $30 \%$ are in high density environments.
-In contrast, in the SDSS redshift bin, $\sim 20 \%$ of galaxies in the redshift bin are in low density environments and $\sim 35 \%$ are in high density environments.
-We remind the reader that this is mainly due to the varying stellar mass-completeness limits imposed on our galaxy sample for each redshift bins and does not affect our results.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% STELLAR MASS FUNCTION
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results: Stellar Mass Function} \label{sec:smf}
-Our galaxy sample has so far been classified into quiescent or
-star-forming and low or high density environments. We further divide
-these subsamples into redshift bins: $0.05-0.12$, $0.2-0.4$,
-$0.4-0.6$, and $0.6-0.8$ for a total of 16 subsamples.
-In Section \ref{sec:smfcalc}, we calculate the SMF for each of these subsamples.
-Then we examine the evolution of active and quiescent subsample SMFs in different environments in Section \ref{sec:smfevol}.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% STELLAR MASS FUNCTION CALCULATIONS
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Stellar Mass Function Calculations} \label{sec:smfcalc} 
-To calculate the SMFs we employ a non-parametric $1/{V_{\mathrm{max}}}$ estimator commonly used for galaxy luminosity functions and stellar mass functions in order to account for Malmquist bias, as done in \cite{Moustakas:2013aa} and discussed in the review \cite{Johnston:2011aa}.
-The differential SMF is given by the following equation:
-\begin{equation} \label{eq:phi}
-\Phi(\mathrm{log}\: \mathcal{M}) \Delta(\mathrm{log} \:\mathcal{M}) = \sum\limits_{i=1}^{N} \frac{w_i}{V_{\mathrm{max,avail},i}}. 
-\end{equation}
-$w_i$ is the statistical weight of galaxy $i$ and $\Phi(\mathrm{log}\:
-\mathcal{M}) \Delta(\mathrm{log}\: \mathcal{M})$ is the number of galaxies
-($N$) per unit volume within the stellar mass range $[\mathrm{log}
-  \mathcal{M},\: \mathrm{log} \mathcal{M}+\Delta(\mathrm{log}\mathcal{M})]$.
-The equation above is the same as Equation 3 in \cite{Moustakas:2013aa} except that we use $V_{\mathrm{max,avail}}$ instead than $V_{\mathrm{max}}$, to account for the edge effects of the survey discussed in Section \ref{sec:edgeeffect}.
-
-$V_{\mathrm{max},i}$ is the maximum cosmological volume where it is
-possible to observe galaxy $i$ given the apparent magnitude limits of
-the survey. However in Section \ref{sec:edgeeffect} we remove galaxies
-that lie on the survey edges from our sample. In doing so, we reduce the
-maximum cosmological volume where a galaxy can be observed, thereby
-reducing the fraction of $V_{\mathrm{max},i}$ that is actually available
-in the sample. We introduce the term $V_{\mathrm{max,avail},i}$ to express
-the maximum volume accounting for the survey edge effects.
-
-To calculate $V_{\mathrm{max,avail},i}$, we use a similar Monte Carlo
-method as the edge effect cutoffs in Section
-\ref{sec:edgeeffect}. First, we generate a sample of points with
-random RA, Dec within the window function of our galaxy sample
-(SDSS-{\em GALEX} window function and the five PRIMUS fields) and
-random $z$ within the redshift range. These points are not to be
-confused with the \texttt{ransack} sample in Section
-\ref{sec:edgeeffect}. We apply the edge effect cuts on these random
-points as we did for our galaxy sample using the same method as in
-Section \ref{sec:edgeeffect}. Within redshift bins of $\Delta z \sim
-0.01$, we calculate the fraction of the random points that remain in
-the bin after the edge effect cuts over the total number of random
-points in the bin: $f_{\mathrm{edge}}$. We then apply this factor to
-compute $V_{\mathrm{max,avail}} = V_{\mathrm{max}} \times f_{\mathrm{edge}}$. The
-$V_{\mathrm{max}}$ values in the equation above are computed following the
-method described in \cite{Moustakas:2013aa} Section 4.2 with the same
-redshift-dependent $K$-correction from the observed SED and luminosity
-evolution model.
-
-To calculate the uncertainty of the SMFs from the sample variance, we use a standard jackknife technique (following \citealt{Moustakas:2013aa}).
-For the PRIMUS galaxies, we calculate SMFs after excluding one of the five target fields at a time.
-For the SDSS target galaxies we divide the field into a 12 $\times$ 9 rectangular RA and Dec grid and calculate the SMFs after excluding one grid at a time.
-From the calculated SMFs we calculate the uncertainty:
-\begin{equation}
-\sigma^j = \sqrt{\frac{N-1}{N} \sum\limits_{k=1}^{M} (\Phi^j_k - \langle \Phi^j \rangle)^2}
-\end{equation} 
-$N$ in this equation is the number of jackknife SMFs in the stellar mass bin.
-$\langle \Phi^j \rangle$ is the mean number density of galaxies in each stellar mass bin for all of the jackknife $\Phi^j$s.
-
-\subsection{Evolution of the Stellar Mass Function in Different Environments} \label{sec:smfevol}
-In Figure \ref{fig:smf}, we present the SMFs of the quiescent/star-forming (orange/blue, bottom/top panels) and high/low density environment (left/right panels) subsamples.
-The redshift evolution of the SMFs in each of these panels are indicated by a darker shade for lower redshift bins.
-The width of the SMFs represent the sample variance uncertainties derived in Section \ref{sec:smfcalc}.
-
-While a detailed comparison of the SMFs in each panel for different
-epochs is complicated by the different stellar mass completeness limits, we present some notable trends in each panel.
-In panel (a), star-forming galaxies in low density environments, we find a significant decrease in the high mass end of the SMF ($\mathcal{M} > 10^{10.75} \mathcal{M}_{\odot}$) over cosmic time.
-Meanwhile at lower masses ($\mathcal{M} < 10^{10.5} \mathcal{M}_{\odot}$), we observe no noticeable trend in the SMF.
-In panel (b), star-forming galaxies in high density environments, we do not observe any clear trends above the knee of the SMF ($\mathcal{M} \sim 10^{10.7} \mathcal{M}_{\odot}$) but an increase in SMF below the knee.
-For the quiescent population in low density environment, panel (c), we observe a potential decrease at higher masses ($\mathcal{M} > 10^{10.7} \mathcal{M}_{\odot}$).
-Lastly for the quiescent population in high density environments, panel (d), we find significant increase in $\Phi$ for lower masses but little trend at higher masses.
-%do not notice any clear SMF evolution throughout the mass range.
-
-%In comparison to results from DEEP2 (\citealt{bundy06a}) and zCOSMOS (\citealt{Bolzonella:2010aa}), some of the noted trends are not immediately evident.
-However, this is mostly due to the conflicting mass limits proposed in each study.
-In addition, only part of the redshift range probed by \cite{bundy06a} overlap with our results.
-Overall, we find that the trends we note in the SMF evolution above are in good agreement with \cite{bundy06a} and \cite{Bolzonella:2010aa}.
-
-Observing the evolutionary trends in SMF for each of these
-sub-populations provides a narrative of the different galaxy
-evolutionary tracks involving environment and the end of star
-formation. For example, the decrease in the massive star-forming
-galaxies in low density environments over cosmic time can be
-attributed to the transition of those galaxies to any of the other
-panels. The star-forming galaxies in low density environments that
-have ended star formation over time are possibly responsible
-for the increase of the quiescent, low density environment SMF over
-time. The star-forming galaxies that fall into higher density
-environments explain the increase in the star-forming high density
-environment SMF below the knee. Finally, star-forming galaxies in high
-density environments that have ended their star-formation,
-quiescent galaxies that have transitioned from low to high density
-environments, and star-forming galaxies in low density environments
-that end their star-formation while infalling to high density
-environments all contribute to the overall increase of the high
-environment quiescent SMF.
-
-In addition to the evolution over cosmic time, we observe noticeable
-trends when we compare the SMFs for star-forming and quiescent
-galaxies between the two environments. Comparison of the SMFs in low
-versus high density environments reveal a noticeable relation between
-mass and density, with SMFs in high density environments having more
-massive galaxies, especially evident in our lowest redshift bin. 
-We further confirm this trend when we compare the
-%massive galaxies. We further confirm this trend w hen we compare the
-median mass between the two environments to find that the median mass
-for galaxies in high density environments is significantly greater
-than in low density environments. The relationship between mass and
-environment observed in our SMFs reflects the well-established
-mass-density relation and observed mass segregation with environment
-in the literature (\citealt{norberg02a, zehavi02a, Blanton:2005ab,
-  bundy06a, Scodeggio:2009aa, Bolzonella:2010aa}).
-
-While our mass complete subsample coupled with robust environment
-measurements allows us to compare SMF evolution for each of our
-subsamples out to $z=0.8$, we caution readers regarding the
-photometric biases affecting the SDSS imaging (and perhaps the other
-imaging sources) and reserve detailed analysis of the SMFs for 
-future investigation.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% QUIESCENT FRACTION
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results: Quiescent Fraction} \label{sec:qf_const}
-The SMFs calculated in the previous section illustrate the stellar
-mass distribution of our galaxy population and its evolution over
-cosmic time. In this section, using the SMFs of our subsamples, we
-compare the quiescent and the star-forming populations by calculating
-the fraction of galaxies that have ended their star-formation, the quiescent fraction.
-
-While the fractional relation of the star-forming and quiescent
-populations has been investigated in the past, with limited
-statistics, disentangling the environmental effects from underlying
-correlations among observable galaxy properties such as the color-mass
-or mass-density relations (\citealt{Cooper:2010aa}) remains a 
-challenge. With the better statistics available from SDSS and
-PRIMUS, we evaluate the quiescent fraction in bins of stellar mass,
-redshift, and environment in Section \ref{sec:qfevol}. By analyzing
-the quiescent fraction with respect to these properties, in Section
-\ref{sec:env_qf_evol} we explicitly compare the quiescent fraction
-evolution in low and high density environments. Our comparison reveal
-the subtle environmental effects on the quiescent fraction
-evolution. Furthermore, by quantifying this environmental effect, we
-are able constrain the role of environmental effects on how galaxies
-end their star formation.
-%With the sufficient statistics available from SDSS and PRIMUS, we evaluate the quiescent fraction in bins of stellar mass and redshift for low and high density environments (Section \ref{sec:qfevol}).
-More specifically, by analyzing the quiescent fraction with respect to mass, redshift, and environment we are able to compare the quiescent fraction evolution in low and high density environments.
-Through this comparison, in Section \ref{sec:env_qf_evol}, we reveal the subtle environmental effects in quenching star formation that are often obscured by the underlying correlations among galactic properties such as color-mass and mass-density relations (\citealt{Cooper:2010aa}).
-Furthermore by quantifying the environmental effects of star-formation quenching, we are able to provide constraints on the various proposed environmental quenching mechanisms, such as strangulation and ram-pressure stripping (\citealt{McCarthy:2008aa}).
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% EVOLUTION OF THE QUIESCENT FRACTION
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Evolution of the Quiescent Fraction} \label{sec:qfevol}
-From the SMF number densities ($\Phi$) computed in the previous section, the quiescent fraction is computed as follows, 
-\begin{equation}
-f_{\mathrm{Q}} ( \mathcal{M}_{*}, z)= \frac{\Phi_{Q}}{\Phi_{SF}+\Phi_{Q}}.
-\end{equation}
-$\Phi_{Q}$ and $\Phi_{SF}$ are the total number of galaxies per unit
-volume in stellar mass bin of $\Delta(\mathrm{log} \: \mathcal{M}) = 0.20
-\: \mathrm{dex}$ for the quiescent and star-forming subsamples,
-respectively (Equation \ref{eq:phi}). We compute $f_{\mathrm{Q}}$ for high
-and low density environments for all redshift bins as plotted in
-Figure \ref{fig:qf}, which shows the evolution of $f_{\mathrm{Q}}$ for
-high (right panel) and low (left panel) density environments. As in
-Figure \ref{fig:smf}, the evolution of the quiescent fraction over
-cosmic time is represented in the shading (darker with lower redshift)
-and the uncertainty is represented by the width. For the uncertainty
-in the quiescent fraction, we use the standard jackknife technique,
-following the same steps as for the SMF uncertainty in Section \ref{sec:smfcalc}.
-
-Most noticeably in Figure \ref{fig:qf}, we find $f_{\mathrm{Q}}$ increases
-monotonically as a function of mass at all redshifts and
-environments. In other words, for galaxies in any environment since $ z \sim 0.8$, galaxies with higher
-masses are more likely to have ceased their star-formation.
-With the roughly linear correlation between galaxy SFR to galaxy color and morphology, we find that this trend reflects the well established color-mass and morphology-mass relations: more massive galaxies are more likely to be red or early-type (\citealt{blanton09a}).
-
-Focusing on the redshift evolution of $f_{\mathrm{Q}}$, we find that for
-both environments $f_{\mathrm{Q}}$ increases as redshift decreases. For
-high density environments, this is analogous to the Butcher-Oemler
-Effect (\citealt{Butcher:1984aa}), which states that galaxy
-populations in groups or clusters have higher $f_{\mathrm{blue}}$ 
-(lower $f_{\mathrm{Q}}$) at higher redshift. This evolution occurs with
-roughly the same amplitude in low environments as well.
-
-In addition, when we compare the stellar masses at which $f_{\mathrm{Q}} =
-0.5$ for each subsample, the so-called $\mathcal{M}_{50-50}$, we find
-that this quantity decreases over cosmic time. This corresponds to the
-well-known mass-downsizing pattern found by previous investigators
-(e.g. \citealt{bundy06a}). Furthermore, the mass-downsizing trend
-observed in each of our environment subsample is qualitatively
-consistent with the trend observed in zCOSMOS Redshift Survey for
-isolated and group galaxies (\citealt{Iovino:2010aa}).
-
-%Remark on how the M_{50-50}? is lower for high environment f_{Q}, and that it generally increases with redshift. A trend also observed in the t_{5050} considerations.
-
-Finally, we compare between our low and high density environment
-$f_{\mathrm{Q}}$s at each redshift bin interval. For our lowest redshift
-bin, we find that $f_{\mathrm{Q}}$ at low density environments ranges from
-$\sim 0.4$ to $\sim 0.9$ for $10^{10.2} \mathcal{M}_{\odot} <
-\mathcal{M}_{*} < 10^{11.5} \mathcal{M}_{\odot}$. Over the same mass
-range, $f_{\mathrm{Q}}$ at high density environment ranges from $\sim
-0.55$ to $\sim 0.9$. For our SDSS sample, $f_{\mathrm{Q}}$ in
-high density environments is notably higher.
-
-For our PRIMUS sample at $z \sim 0.3$, over $10^{9.5} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11} \mathcal{M}_{\odot}$ $f_{\mathrm{Q}}$ ranges from $\sim 0.2$ to $\sim 0.65$ for low density environment, while at high density environment $f_{\mathrm{Q}}$ ranges from $\sim 0.2$ to $\sim 0.8$.
-Similarly, at $z \sim 0.5$, over $10^{10} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11.2} \mathcal{M}_{\odot}$ $f_{\mathrm{Q}}$ ranges from $\sim 0.3$ to $\sim 0.6$ for low density environment and $f_{\mathrm{Q}}$ ranges from $\sim 0.3$ to $\sim 0.7$.
-Finally in our highest redshift bin $z \sim 0.7$, over the mass range $10^{10.5} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11.5} \mathcal{M}_{\odot}$, $f_{\mathrm{Q}}$ ranges from $\sim 0.35$ to $\sim 0.6$ for low density and $\sim 0.45$ to $\sim 0.8$ for high density.
-For the entire redshift range of our sample, $f_{\mathrm{Q}}$ in high density environment is higher than $f_{\mathrm{Q}}$ in low density environments.
-
-While there is a significant difference in $f_{\mathrm{Q}}$ between the
-environments, since the difference is observed from our highest
-redshift bin, it is not necessarily a result of environment dependent
-mechanisms for ending star formation. In order to isolate any
-environmental dependence, in the following section we quantitatively
-compare the evolution of the quiescent fraction between the different
-environments.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% ENVIRONMENTAL EFFECTS ON THE QUIESCENT FRACTION EVOLUTION
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Environmental Effects on the Quiescent Fraction Evolution} \label{sec:env_qf_evol}
-In order to more quantitatively compare the $f_{\mathrm{Q}}$ evolution for different epochs and environments, we fit $f_{\mathrm{Q}}$ for each subsample to a power-law parameterization as a function of stellar mass,
-\begin{equation} \label{eq:qffit}
-f_{\mathrm{Q}}(\mathcal{M}_{*}) = a \: \mathrm{log} \; \left(\frac{ \mathcal{M}_{*}}{\mathcal{M}_{\mathrm{fid}}} \right)+b,
-\end{equation}
-where $a$ and $b$ are best-fit parameters using {\em MPFIT} (\citealt{Markwardt:2009aa}) and $\mathcal{M}_{\mathrm{fid}}$ represents the empirically selected fiducial mass within the stellar mass limits where there is a sufficiently large number of galaxies.
-We primarily focus on $\mathcal{M}_{\mathrm{fid}} = 10^{10.5} \: \mathcal{M}_{\odot}$.
-
-In Figure \ref{fig:qffit} we present the evolution of
-$f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$
-at low (blue) and high (red) density environments for
-$\mathcal{M}_{\mathrm{fid}} = 10^{10.5} \: \mathcal{M}_{\odot}$ (solid
-fill) and $10^{11} \: \mathcal{M}_{\odot}$ (pattern fill). The width
-of the evolution represents the uncertainty derived from {\em
-  MPFIT}. As noted earlier in Section \ref{sec:qfevol}, $f_{\mathrm{Q}}$
-in high density environments is significantly greater than
-$f_{\mathrm{Q}}$ in low density environments for both fiducial mass
-choices. Throughout our sample's redshift range
-$f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})_{\mathrm{high}} -
-f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})_{\mathrm{low}} \sim 0.1$.
-
-In addition, the $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$
-evolution illustrates that the quiescent fraction in low density
-environment increases over cosmic time:
-$f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.1) -
-f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.7) \sim 0.1$. This
-significant quiescent fraction evolution for low density environments
-suggests that internal mechanisms, independent of environment, are
-responsible for a significant amount of star-formation cessation.
-Meanwhile, the $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ evolution in high density environment ($f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.1) - f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.7) \sim 0.12$) shows little additional evolution.
-
-When we increase our choice of $\mathcal{M}_{\mathrm{fid}}$ to $10^{11}
-\mathcal{M}_\odot$, aside from an overall shift in
-$f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ by $\sim 0.2$, we observe the
-same evolutionary trends. $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}} =
-10^{11}\mathcal{M}_{\odot})$ for both low and high density
-environments each increase by $\sim 0.2$ from at all redshifts we
-study. Increasing the fiducial mass to $10^{11}
-\mathcal{M}_{\odot}$ does not significantly alter the evolutionary
-trends in either environment. Although the varying stellar mass
-completeness at each redshift bin limits the masses we probe for the
-$f_{\mathrm{Q}}$ evolution, our $f_{\mathrm{Q}}$ evolution exhibits little
-mass dependence.
-
-Because our fixed aperture definition of environment is susceptible to
-contamination due to PRIMUS redshift errors, we consider in Figure
-\ref{fig:qffit_comp} more stringent high density environment
-classifications, extending the cut off to $n_{\mathrm{env}} > 5$ and
-$7$ (specified in the top right legend and represented by the color of
-the shading). Aside from the increase in uncertainties that accompany
-the decrease in sample size of the purer high environment sample, we
-find an extension of the $f_{\mathrm{Q}}$ difference between the
-environments we stated earlier. A more stringent high environment
-classification significantly increases the overall
-$f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$, which rises monotonically with
-the $n_{\mathrm{env}}$ limit.
-
-More importantly, a purer high environment classification reveals a
-more significant environment dependence on the $f_{\mathrm{Q}}$
-evolution. While the difference between the $f_{\mathrm{Q}}$ evolution in
-low and high density environment is negligible for the $n_{\mathrm{env}} >
-3$ cut-off, there is a notable difference in $f_{\mathrm{Q}}$
-evolution between our highest cut-off $n_{\mathrm{env}} > 7$ and our low
-density environment. $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z
-\sim 0.1) - f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.7)
-\sim 0.25$ for $n_{\mathrm{env}} > 7$ versus
-$f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.1) -
-f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.7) \sim 0.1$ for
-low density environment. In addition to the
-environment independent internal mechanisms that can explain the
-$f_{\mathrm{Q}}$ evolution in low density environments, there may be other
-environment dependent mechanisms that can account for the moderate
-environment dependence of the $f_{\mathrm{Q}}$ evolution. Our measured
-difference in the $f_{\mathrm{Q}}$ evolution between environments provides
-an important constraint for any environmental models for ending star
-formation.
-
-\def \iovinopanel {b}
-\def \kovacpanel {b}
-\def \pengpanel {c}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% COMPARISON TO LITERATURE
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Comparison to Literature}
-Although a direct comparison with other results is difficult due to
-our sample specific methodology, a number of results from the literature have investigated the quiescent fraction in comparable fashions.
-In this section we compare our $f_{\mathrm{Q}}$ results from above to a number of these results, specifically from SDSS and zCOSMOS, with similarly defined samples and analogous environment classifications.
-
-In Figure \ref{fig:qffit_comp}, we plot  best-fit parameterization of
-$f_{\mathrm{red}}$ for high and low density environment from SDSS (panel a), zCOSMOS (panel \iovinopanel), and \cite{Peng:2010aa} (filled square; panel d) from both surveys. 
-%$f_{\mathrm{red}}$ for high and low density environment from SDSS (panel a), \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross), zCOSMOS (panel b),
-%\cite{Iovino:2010aa} (empty square) and \cite{Kovac:2014aa} (triangle), and \cite{Peng:2010aa} (filled square; panel c) from both surveys. From
-From \cite{Iovino:2010aa} (empty square; panel \iovinopanel), we calculate $f_{\mathrm{red}} = 1-f_{\mathrm{blue}}$
-using the best-fit $f_{\mathrm{blue}}$ from the mass bin $\mathcal{M} =
-10^{10.3} - 10^{10.8} \mathcal{M}_{\odot}$. From \cite{Kovac:2014aa} (triangle; panel \kovacpanel)
-we plot an estimated $f_{\mathrm{Q}}$ by applying the residual between SFR
-based and color based galaxy classifications to the best-fit
-$f_{\mathrm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ for
-low ($\delta = 0.0$) and high density environments ($\delta =
-1.5$). Similarly, from \cite{Baldry:2006aa} (diamond; panel a) we plot $f_{\mathrm{Q}}$
-derived from the best-fit $f_{\mathrm{red}}$ at $\mathcal{M} = 10^{10.5}
-\mathcal{M}_{\odot}$ for low ($\delta = 0.0$) and high density
-environment ($\delta = 1.0$). For \cite{geha12a} (cross; panel a), we plot $f_{\mathrm{Q}}$
-for their isolated galaxy sample in their mass bin closest to $10^{10.5} \mathcal{M}_{\odot}$, $\mathcal{M} = 10^{10.55} \mathcal{M}_{\odot}$.
-Finally for \cite{Peng:2010aa} (square; panel \pengpanel), we plot the parameterized $f_{\mathrm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ using their best-fit parameters for low ($\delta =0.0$) and high ($\delta = 1.4$) density environments.
-
-For our lowest redshift bin SDSS sample, we find that our $f_{\mathrm{Q}}$
-for low and high environments are consistent with other SDSS
-$f_{\mathrm{Q}}$ (or $f_{\mathrm{red}}$) measurements as a function of
-environment. For example, \cite{Baldry:2006aa} uses projected neighbor
-density environment measures ($\mathrm{log} \; \Sigma$) to obtain
-$f_{\mathrm{Q}}(\mathcal{M})$ for a range of environmental
-densities. Although the different environment measurements make direct
-comparisons difficult, in their corresponding higher environments
-($\mathrm{log} \; \Sigma > 0.2$ in \citealt{Baldry:2006aa})
-$f_{\mathrm{Q}}(\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}) \sim 0.6$
-and $f_{\mathrm{Q}}(\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}) \sim
-0.9$, which is in agreement with our high density
-environment. Likewise, for lower environments ($\mathrm{log} \; \Sigma <
--0.4$ in \citealt{Baldry:2006aa}) $f_{\mathrm{Q}}(\mathcal{M} \sim
-10^{10.2} \mathcal{M}_{\odot}) \sim 0.4$ and $f_{\mathrm{Q}}(\mathcal{M}
-\sim 10^{11.5} \mathcal{M}_{\odot}) \sim 0.8$, which also agree with
-our low density environment $f_{\mathrm{Q}}$. The \cite{Baldry:2006aa}
-points (diamond) in Figure \ref{fig:qffit_comp} reflect this
-agreement.
-
-More recently, \cite{Tinker:2011aa}, using a group-finding algorithm on the SDSS DR7, presents the relationship between $f_{\mathrm{Q}}$ and overdensity for galaxies within the mass range $\mathrm{log} \; \mathcal{M} = [9.8, 10.1]$.
-The \cite{Tinker:2011aa} $f_{\mathrm{Q}}$ at the lowest and highest overdensities, $f_{\mathrm{Q}} \sim 0.4$ and $f_{\mathrm{Q}} \sim 0.6$ respectively, are consistent with our $f_{\mathrm{Q}}$ for low and high density environment at the lower mass limit ($\mathrm{log} \; \mathcal{M} \sim 10.2$).
-
-A modified \cite{Tinker:2011aa} sample is used in \cite{geha12a} to
-obtain $f_{\mathrm{Q}}$ for isolated galaxies over a wider mass range
-($10^{7.4} \mathcal{M}_\odot$ to $10^{11.2}
-\mathcal{M}_{\odot}$). Although \cite{geha12a} probe a slightly lower
-redshift range ($ z \le 0.06$), their $f_{\mathrm{Q}}$ is consistent with
-our low density sample. Within the overlapping mass range, at the low
-mass end \cite{geha12a} find $f_{\mathrm{Q}}(\mathcal{M}_{*} \sim
-10^{10.2} \mathcal{M}_{\odot}) \sim 0.3$ and at the high mass end they
-find $f_{\mathrm{Q}}(\mathcal{M}_{*} \sim 10^{11.2} \mathcal{M}_{\odot})
-\sim 0.8$. Both of these values agree with our lowest redshift
-$f_{\mathrm{Q}}$ results in low density environment. Figure
-\ref{fig:qffit_comp} illustrates the $f_{\mathrm{Q}}$ agreement for
-$\mathcal{M}_{*} = 10^{10.5} \mathcal{M}_{\odot}$.
-
-%\cite{Peng:2010aa} computes the comoving density field for the SDSS DR7 and zCOSMOS galaxies in order to calculate $f_{\mathrm{red}}$ as a function of mass and environment.
-If we compare our $f_{\mathrm{Q}}$ to the best-fit parameterization $f_{\mathrm{red}}$ for their SDSS subsample we find that
-
-For $z > 0.2$, we compare our PRIMUS $f_{\mathrm{Q}}$ results to the $f_{\mathrm{red}}$ (or $1-f_{\mathrm{blue}}$) results from the zCOSMOS Redshift Survey (\citealt{Iovino:2010aa, Kovac:2014aa}), which covers a similar redshift range as PRIMUS.
-\cite{Iovino:2010aa}, and \cite{Kovac:2014aa} using a mass-complete galaxy sample derived from zCOSMOS and a group catalog, 3D local density contrast, and overdensity environment measurements, respectively, compare $f_{\mathrm{red}}$ with respect to environment.
-The $f_{\mathrm{blue}}$ for group and isolated galaxies from \cite{Iovino:2010aa} are generally inconsistent with our $1-f_{\mathrm{Q}}$ for high and low density environments.
-
-Similarly, $f_{\mathrm{red}}$ for high and low overdensities in
-\cite{Kovac:2014aa} are  greater overall than the PRIMUS $f_{\mathrm{Q}}$
-values in high and low density environments. However,
-\cite{Kovac:2014aa} points out that there is a significant difference
-between classifying the quiescent population using color and SFR due to dust-reddening in star-forming galaxies.
-For their lower redshift bin ($0.1 < z < 0.4$) \cite{Kovac:2014aa} find that their $f_{\mathrm{Q}}$ defined by color is greater than $f_{\mathrm{Q}}$ defined by SFR by roughly $0.2$.
-While for their higher redshift bin ($0.4 < z < 0.7$) the difference is $0.15-0.19$.
-Although \cite{Kovac:2014aa} does not elaborate on how the galaxy classification discrepancy applies to the different environments, if we simply account for the difference uniformly for $f_{\mathrm{red}}$ at all environments, the \cite{Kovac:2014aa} results in their lower redshift bin are roughly consistent with our $f_{\mathrm{Q}}$ at high and low density environments.
-Even accounting for the dust-reddening of $f_{\mathrm{red}}$, \cite{Kovac:2014aa} finds a significantly higher $f_{\mathrm{Q}}$ in their higher redshift bin.
-
-In Figure \ref{fig:qf}, the $f_{\mathrm{Q}}$ evolution with respect to
-mass reveals, qualitatively, little mass dependence in the
-evolution. Moreover, in Figure \ref{fig:qffit}, we illustrated that
-adjusting the fiducial mass only shifted the overall
-$f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$, but did not change the
-$f_{\mathrm{Q}}$ evolutionary trend. The consistency in the $f_{\mathrm{Q}}$
-evolutionary trends over change in fiducial mass suggests that
-$f_{\mathrm{Q}}$ evolution exhibit little mass dependence within the 
-mass range probed in our analysis. In contrast to
-the weak mass dependence we observe in our results,
-\cite{Iovino:2010aa} find significantly different $f_{\mathrm{Q}}$
-evolution at $\mathcal{M} \sim 10^{11} \mathcal{M}_{\odot}$ and
-$\mathcal{M} \sim 10^{10.5} \mathcal{M}_{\odot}$, for both group and
-isolated galaxies. In fact at their highest mass bin ($10^{10.9} -
-10^{11.4} \mathcal{M}_{\odot}$), \cite{Iovino:2010aa} find no evolution
-for both environments: constant $f_{\mathrm{blue}} \sim 0.1$ over $z =
-0.3 - 0.8$ for both group and isolated galaxy populations.
-
-Meanwhile in their mass bin most comparable to $\mathcal{M}_{\mathrm{fid}}
-\sim 10^{10.5} \mathcal{M}_{\odot}$ ($10^{10.3} \mathcal{M}_{\odot} -
-10^{10.8} \mathcal{M}_{\odot}$), \cite{Iovino:2010aa} finds that
-$f_{\mathrm{blue}}$ evolves by $\sim 0.1$ from $z = 0.5$ to $0.25$ for
-group galaxies and by $\sim 0.3$ from $z=0.55$ to $0.3$ for isolated
-galaxies as presented in panel (\iovinopanel) of Figure \ref{fig:qffit_comp}. Altogether, with
-mass bins beyond the fiducial masses we explore, \cite{Iovino:2010aa}
-find a strong mass dependence with $f_{\mathrm{Q}}$ evolving significantly
-more in lower mass bins. While our sample from PRIMUS provides larger
-statistics than zCOSMOS, the mass-completeness limits we impose on our
-sample limits the mass range we probe (e.g. $\mathcal{M} > 10^{10.5}
-\mathcal{M}_{\odot}$ for our $z \sim 0.7$ bin). Consequently our
-results cannot rule out mass dependence in the $f_{\mathrm{Q}}$ evolution
-at lower masses.
-
-In Figure \ref{fig:qffit} and Figure \ref{fig:qffit_comp} we
-quantified that throughout our redshift range, high density
-environments have a significantly greater
-$f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ than the low density
-environments. This finding is in agreement with the zCOSMOS results
-from \cite{Cucciati:2010aa} and \cite{Kovac:2014aa}. As illustrated in
-panel (\kovacpanel) of Figure \ref{fig:qffit_comp}, \cite{Kovac:2014aa} finds $f_{\mathrm{Q}}$ in high density environment
-significantly greater than $f_{\mathrm{Q}}$ at low density
-environment. Moreover, since galaxy color serves as a proxy for SFR,
-our results support the existence of the color-density relation
-(\citealt{Cucciati:2010aa, Cooper:2010aa}) and is not consistent with
-the color-density relation being merely a reflection of the
-mass-density relationship, as \cite{Scodeggio:2009aa} suggest it is
-based on the Vimos VLT Deep Survey ($0.2 < z< 1.4$).
-
-% Purposely not mentioning the lack of morphology-density relation for M>10^10.5Msun galaxies as argued in Tasca et al. 2009 in order to not bring up morphology.
-
-In Section \ref{sec:env_qf_evol}, we showed that $f_{\mathrm{Q}}$ in
-low density environments evolves over cosmic time. From this trend we
-deduce that internal, environment independent, mechanisms contribute
-to ending star-formation in galaxy evolution. \cite{Iovino:2010aa}
-from zCOSMOS, plotted in Figure \ref{fig:qffit_comp}  panel (\iovinopanel), also find that
-$f_{\mathrm{Q}}$ in low density environment increases with decreasing redshift.
-On the other hand \cite{Kovac:2014aa}, also from zCOSMOS, presents that $f_{\mathrm{Q}}$ in low density environment decreases over cosmic time.
-While the uncertainties for the parameterized $f_{\mathrm{Q}}$ are not listed, and thus not shown in Figure \ref{fig:qffit_comp}, once they are accounted for, \cite{Kovac:2014aa} find no significant $f_{\mathrm{Q}}$ evolution over cosmic time.
-However, once we account for the dust-reddening of the $f_{\mathrm{red}}$, we find a more significant decrease over cosmic time (Figure \ref{fig:qffit_comp} panel \kovacpanel).
-
-Furthermore, in Section \ref{sec:env_qf_evol}, our comparison of the
-$f_{\mathrm{Q}}$ evolution between the lowest density environment and the
-highest density environment revealed a modicum of evidence for the
-existence of environment dependent mechanisms. The same comparison
-with zCOSMOS results (\citealt{Iovino:2010aa, Kovac:2014aa}) present
-trends inconsistent with our findings. First, comparing the high (red)
-and low (blue) density environments for \cite{Iovino:2010aa} in Figure
-\ref{fig:qffit_comp} shows that there are indeed pronounced
-discrepancies between the $f_{\mathrm{Q}}$ evolution in different
-environments. Group galaxies in \cite{Iovino:2010aa} have higher
-overall $f_{\mathrm{Q}}$ than isolated galaxies. However, unlike our
-results, which find a greater $f_{\mathrm{Q}}$ evolution at higher density
-environments, \cite{Iovino:2010aa} finds the opposite environment
-dependence that there is a significantly greater $f_{\mathrm{Q}}$
-evolution for isolated galaxies.
-
-Next, \cite{Kovac:2014aa} also find that overall $f_{\mathrm{Q}}$ is
-greater in high density than in low density environments. Like their
-low density environment $f_{\mathrm{Q}}$ evolution, $f_{\mathrm{Q}}$ in high
-density environment decreases over cosmic time between their two
-redshift bins. Although the decrease in $f_{\mathrm{Q}}$ over cosmic time
-conflicts with our results, \cite{Kovac:2014aa} finds a greater (less
-negative) $f_{\mathrm{Q}}$ evolution in high density environments relative
-to low density environments, suggesting an environment dependence that
-is in the same direction as our results. We note that the negative
-slopes of the $f_{\mathrm{Q}}$ evolution in both environments are enhanced
-in Figure \ref{fig:qffit_comp} due to the dust-reddening
-correction we impose to the \cite{Kovac:2014aa} $f_{\mathrm{red}}$ results.
-
-% Removed in order to tone down the criticism of 
-%However, even without the correction (not shown), in their best-fit $f_{\mathrm{Q}}$ results, the same evolutionary trends mentioned above are observed.
-
-While the zCOSMOS survey provides more precise spectroscopic redshifts than PRIMUS, our sample provides significantly larger statistics.
-In addition, our sample covers a larger portion of the sky.
-Our SDSS-{\em GALEX} sample covers $2,505 \;\mathrm{deg}^2$.
-More comparably, our PRIMUS sample covers $5.5 \;\mathrm{deg}^2$, over 3 times the sky coverage of zCOSMOS ($1.7 \;\mathrm{deg}^2$).
-Furthermore, our PRIMUS sample is constructed from five independent fields which allows us to significantly reduce the effects of cosmic variance.
-
-As listed in Table \ref{tab:subsample}, after our edge effect cuts and
-stellar mass completeness limits, our sample consists of $13,734$
-galaxies from PRIMUS over $0.2< z< 0.8$ and $63,417$ galaxies from
-SDSS over $0.05 < z < 0.12$. Meanwhile, \cite{Iovino:2010aa} has $914$
-galaxies with $\mathcal{M} > 10^{10.3} \mathcal{M}_{\odot}$ over $0.1
-< z < 0.6$ and $1033$ galaxies with $\mathcal{M} > 10^{10.6}
-\mathcal{M}_{\odot}$ over $0.1 < z < 0.8$. For the actual sample used
-to obtain the best-fit $f_{\mathrm{Q}}$ values in Figure
-\ref{fig:qffit_comp} \cite{Iovino:2010aa} has $617$ galaxies. In
-comparison, our PRIMUS sample alone contains $> 20$ times the number
-of galaxies. While there is a considerable difference in the overall
-$f_{\mathrm{Q}}$ between our results and those of \cite{Iovino:2010aa},
-the use of different methodologies, particularly for galaxy
-classification and environment measurements, make such comparisons
-ambiguous. On the other hand, the discrepancies in the $f_{\mathrm{Q}}$
-evolutionary trends with our results may be explained by the limited
-statistics in the \cite{Iovino:2010aa} sample.
-
-The more recent \cite{Kovac:2014aa} provides larger statistics with
-$2,340$ galaxies in their lower redshift bin ($0.1 < z < 0.4$) and
-$2,448$ galaxies in their higher redshift bin ($0.4 < z <
-0.7$). Although their sample is smaller than the PRIMUS sample, which
-contains over twice times the number of galaxies, the
-\cite{Kovac:2014aa} sample provides a more stable comparison.  Once
-their results are adjusted for the dust-reddening, we
-find that their overall $f_{\mathrm{Q}}$ is more or less consistent with
-our overall $f_{\mathrm{Q}}$. However, it is difficult to explain the
-significant discrepancies in the $f_{\mathrm{Q}}$ evolutionary trends.
-The significant overdenities observed in the COSMOS field at $z \sim 0.35$ and $z \sim 0.7$ (\citealt{Lilly:2009aa, Kovac:2010ab}) may have a significant effect on the zCOSMOS results and offer a possible explanation for the discrepancies.
-% zCOSMOS has more precise redshift but PRIMUS has it beat in terms of sample size and coverage of the sky 5.5 deg^2 vs 1.7 deg^2
-% Kovac: 1.7 deg^2, 0.1 < z < 0.4 2340 and 0.4 < z < 0.7 2448. Most of the data points have errors of +/- 0.1, at least +/-0.05
-% Iovino: 1.7 deg^2  617 galaxies in 10.3 < M < 10.8 and 0.1 < z < 0.6. Errors are +/1 0.1
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% SUMMARY
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Summary and Discussion} \label{sec:summary}
-Using a stellar mass complete galaxy sample derived from SDSS and
-PRIMUS accompanied by a consistently measured galaxy environment from
-robust spectroscopic redshifts, we measure the stellar mass functions
-for star-forming and quiescent galaxies in low and high density
-environments over the redshift range $0.05 < z < 0.8$. From these
-stellar mass functions, we compare the proportion of galaxies that
-have ended their star-formation within the subsamples by computing the
-quiescent fraction for each of them. In order to better quantify the
-evolution of the quiescent fraction over cosmic time, we fit our
-quiescent fraction anchored at a fiducial mass.
-
-From our analyses we find the following notable results. The first
-three demonstrate that previous findings that are well known in the
-local universe are applicable out to $z\sim 0.7$. The last two are
-consistent with the findings of \cite{Peng:2010aa} but provide increased
-detail on the environmental dependence of galaxy evolution:
-\begin{enumerate}
-	\item From the SMFs, we find that the galaxy population in high
-    density environments, both star-forming and quiescent, have a
-    higher median mass, thus confirming the mass-density relation and
-    mass-segregation in different environments throughout our sample's
-    redshift range.
-	\item For all subsamples, $f_{\mathrm{Q}}$ increases monotonically with
-    galaxy stellar mass, showing a clear mass dependence and
-    reflecting the well-established color-mass and morphology-mass
-    relations.
-	\item We illustrate that $f_{\mathrm{Q}}$ in high density environments
-    is greater than $f_{\mathrm{Q}}$ in low density environments
-    regardless of mass and out to redshift $z\sim 0.7$. This result
-    reflects the well known trend that galaxies in high density
-    environment are statistically redder, have lower SFRs, and are
-    more massive.
-	\item $f_{\mathrm{Q}}$ increases significantly with redshift for both
-    low and high density environments. For high density environment,
-    this trend is the Butcher-Oemler effect. Furthermore, the
-    $f_{\mathrm{Q}}$ evolution in low density environment suggest the
-    existence of internal environment-independent mechanisms for
-    ending star formation.
-	\item Comparison of the $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$
-    evolution for a range of environment classifications reveals that
-    the since $z = 0.8$, $f_{\mathrm{Q}}$ has evolved by a greater amount
-    in the highest density environments. For our purest high
-    environment sample ($n_{\mathrm{env}} > 7$), the total $f_{\mathrm{Q}}$
-    evolution is $\sim 0.1$ greater than the total $f_{\mathrm{Q}}$
-    evolution in low density environment, revealing a moderate
-    dependence on environment.
-\end{enumerate}
-
-Many physical mechanisms have been proposed to explain the cessation
-of star-formation observed in many galaxies. Recently star-formation
-cessation has often been classified into internal or external
-mechanisms, and sometimes more specifically into mass-dependent and
-environment-dependent mechanisms (\citealt{Baldry:2006aa,
-  Peng:2010aa}). The significant redshift evolution of the
-$f_{\mathrm{Q}}$ in low density environments confirms the existence of
-internal mechanisms that end star-forming in galaxies.
-
-Furthermore, the greater $f_{\mathrm{Q}}$ evolution in the highest density
-environment relative to low density environments suggests that in
-addition to the internal mechanisms, in high density environments such
-as groups and clusters, environment-dependent effects may also
-contribute to the end of star-formation. Our results do not
-specifically shed light on which mechanisms (e.g. strangulation,
-ram-pressure stripping, etc.) occur in high density environments. Not to 
-mention, the mechanism could yet be indirect; for example, the
-galaxies in higher density environments could end star-formation
-primarily due internal processes, which affect the galaxies that end up
-in groups and clusters more greatly.  Nevertheless, our results impose
-important constraints on the total possible contribution of
-environment dependent mechanisms that models must satisfy, providing a
-limit on the role of environment in ending star formation in
-galaxies.
-
-\bigskip 
-CH and MB were supported by NSF-AST-1109432 and NSF-AST-0908354.
-MB was also supported by NSF-AST-1211644.
-ALC acknowledges support from NSF CAREER award.
-We acknowledge Katarina Kova\u{c} and Ying-Jie Peng for  insightful discussions.
-We also thank Marla Geha for providing published quiescent fraction results in electronic format.
-
-The Galaxy Evolution Explorer (GALEX) is a NASA Small Explorer, launched in April 2003, whose mission was developed in cooperation with the Centre National d?Etudes Spatiales of France and the Korean Ministry of Science and Technology.
-Funding for the SDSS and SDSS-II has been provided by the Alfred P.
-Sloan Foundation, the Participating Institutions, the National Science Foundation, the U.S.
-Department of Energy, the National Aeronautics and Space Administration, the Japanese Monbukagakusho, the Max Planck Society, and the Higher Education Funding Council for England.
-The SDSS Web Site is http://www.sdss.org.
-The SDSS is managed by the Astrophysical Research Consortium for the Participating Institutions.
-
-%
-% References
-%
-\bibliography{PRIMUS}
-
-\clearpage
-\begin{figure*}
-    \begin{center}
-        \leavevmode
-        \epsscale{1.0}
-	\plotone{fig_edp_sdss_z0_05_0_12_primus_z0_2_1_0_Mr_redshift.png}
-        \caption{Absolute magnitude $M_{r}$ versus redshift for our mass complete galaxy sample (black squares) with the Environment Defining Population (red circles) plotted on top.
-Both samples are divided into redshift bins: $z = 0.05-0.12$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ (panels left to right).
-The lowest redshift bin ($z \approx 0.05-0.12$; leftmost panel) contain our galaxy sample and EDP selected from SDSS.
-The rest contain galaxies and EDP selected from PRIMUS.
-The redshift limits for the lowest redshift bin are empirically selected based on the bright and faint limits of SDSS galaxies.
-Stellar mass completeness limits, described in Section \ref{sec:target}, are imposed on the galaxy population.
-Meanwhile, $M_{r}$ limits are applied to the EDP such that the number density in each panel are equivalent (Section \ref{sec:environment}).} \label{fig:targetEDP}
-    \end{center}
-\end{figure*}
-
-\clearpage
-
-\begin{table*} 
-  \caption{Galaxy Subsamples} \label{tab:subsample}
-  \begin{center}
-    \leavevmode
-    \begin{tabular}{ccccccc} \hline \hline              
-     &\multicolumn{1}{c}{$n_{\mathrm{env}}$}        & \multicolumn{2}{c}{$N_{\mathrm{gal}}$}  & \multicolumn{2}{c}{$\mathcal{M}_{\mathrm{lim}}$} & $M_{\mathrm{r}, lim}$ \\ 
-    & & Quiescent & Star-Forming & Quiescent & Star-Forming &  \\ \hline 
-$0.05 < z < 0.12$ & $n_{\mathrm{env}} < \lowenvthresh $ & 6533 & 7508 & $10^{10.2} \mathcal{M}_{\odot}$ & $10^{10.2} \mathcal{M}_{\odot}$ & -20.95 \\
-               & $n_{\mathrm{env}} > \highenvthresh $ &14673 & 9717 &                          \\ 
-                              & all          &$33553$                       & $29864$                          \\ \hline
-$0.2 < z < 0.4$      &$n_{\mathrm{env}} < \lowenvthresh $           &363                    &1231 & $10^{9.8} \mathcal{M}_{\odot}$ & $10^{9.8} \mathcal{M}_{\odot}$ &-21.03 \\
-               &$n_{\mathrm{env}} > \highenvthresh $            &379                    &756                           \\
-               & all                & $1086$                      & $2879$                          \\ \hline
-$0.4 < z < 0.6$      &$n_{\mathrm{env}} < \lowenvthresh $           &536                       &1498 & $10^{10.3} \mathcal{M}_{\odot}$ & $10^{10.3} \mathcal{M}_{\odot}$ & -20.98 \\
-               &$n_{\mathrm{env}} > \highenvthresh $            &490                       &854                           \\
-               & all               & $1560$                      & $3577$                          \\ \hline
-$0.6 < z < 0.8$      &$n_{\mathrm{env}} < \lowenvthresh $           &567                       &1254  & $10^{10.7} \mathcal{M}_{\odot}$ & $10^{10.6} \mathcal{M}_{\odot}$ & -20.97 \\
-               &$n_{\mathrm{env}} > \highenvthresh $            &498                       &671                           \\
-               & all              & $1668$                      & $2964$                          \\ \hline
-Total &      & \multicolumn{2}{c}{77151} & \\ \hline
-  \multicolumn{4}{l}{}                                             \\       
-    \end{tabular} \par
-    \end{center}
-    \tablecomments{Number of galaxies ($N_{\mathrm{gal}}$) in the mass complete subsamples within the edges of the survey (Section \ref{sec:sample}).
-The subsamples are classified based on environment ($n_{\mathrm{env}}$) and star formation rate (star-forming or quiescent).
-The lowest redshift bin is derived from SDSS; the rest are from PRIMUS.
-We also list the stellar mass completeness limit, $\mathcal{M}_{\mathrm{lim}}$, for our sample along with the $r$-band absolute magnitude limits, $M_{\mathrm{r}, lim}$, for the Environment Defining Population.
-}
-    \bigskip
-\end{table*}
-
-\clearpage
-
-\begin{figure}
-  \begin{center}
-    \leavevmode
-    \epsfig{file=fig_envcount_cylr2_5h35_thresh75_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_primuszerr_masslimit_edgecut_histogram.png, width=\textwidth}
-    \caption{Normalized distribution of environment measurements ($n_{\mathrm{env}}$) for our mass complete galaxy sample within the survey edges.
-A fixed cylindrical aperture of $R_{\mathrm{ap}} =\apradius\;\mathrm{Mpc}$ and $H_{\mathrm{ap}} = \apheight\; \mathrm{Mpc}$ is used to measure environment.
-The star-forming galaxies contribution to the distribution is colored in blue and diagonally patterned.
-The contribution from quiescent galaxies is colored in red.
-Galaxies with $n_{\mathrm{env}} < 0.5$ are in low density environments and galaxies with $n_{\mathrm{env}} > 3.0$ are in high density environment.
-We note that the significant difference among the SDSS distribution and the PRIMUS distributions above is due to the different stellar mass completeness limits imposed on each redshift bin of our galaxy sample.}      \label{fig:envcount}
-     %\caption{Normalized distribution of environment measurements ($n_{\mathrm{env}}$) for our mass complete galaxy sample within the edges.
-The star-forming galaxies contribution to the distribution is colored blue and diagonally patterned.
-The contribution from quiescent galaxies is colored in red.
-Each redshift panel is divided into three sections by the environment classification cutoffs (black veritcal lines): low density environment $n_{\mathrm{env}} < 0.5$ and high density environment $n_{\mathrm{env}} > 3.0$.
-The percentages of the redshift bin contained in the environment classifications are presented above the distribution.
-For example at $0.2 < z < 0.4$, $\apheight.0 \%$ of galaxies in the redshift bin are in low density environments while $35.0\%$ of galaxies in the redshift bin are in high density environments.
-We note that the significant difference between the SDSS distribution and the PRIMUS distribution above is due to the difference in stellar mass completeness limit imposed in our galaxy sample.}      \label{fig:envcount}
-    \end{center}
-\end{figure}
-
-\begin{figure*}
-  \begin{center}
-    \leavevmode
-    \epsfig{file=fig_smf_cylr2_50000h35_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_2envbin_lowenv0_5_highenv3_0_lit_primuszerr.eps, height=\textwidth,angle=90}
-     \caption{Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) galaxies in 
-low (left) and high (right) density environments throughout the redshift range
-$z=0$--$0.8$. The environment of each galaxy  
-was calculated using a cylindrical aperture size of $R=\apradius \: \mathrm{Mpc}$ and $H=\apheight \: \mathrm{Mpc}$ and  
-classified as low environment when $n_{\mathrm{env}} < 0.5$ and as high environment when $n_{\mathrm{env}} > 3.0$. The SMFs use mass bins of 
-width $\Delta \mathrm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.2$. In each panel we use shades of blue 
-(star-forming) and orange (quiescent) to represent the SMF at different redshift, higher redshifts being
-progressively lighter.}      \label{fig:smf}
-    \end{center}
-\end{figure*}
-
-\begin{figure*}
-    \begin{center}
-        \leavevmode
-        \epsfig{file=fig_qf_cylr2_50000h35_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_lit_primuszerr.eps, height=\textwidth,angle=90}
-        \caption{Evolution of the quiescent fraction $f_{\mathrm{Q}}$ for
-          galaxies in low (left) and high (right) density
-          environments for $z < 0.8$. $f_{\mathrm{Q}}$s were calculated
-          using the SMFs in Figure \ref{fig:smf}, as described in Section \ref{sec:qfevol}.
-Darker shading indicates lower redshift and the width represents the standard jackknife uncertainty.}         \label{fig:qf}
-    \end{center}
-\end{figure*}
-
-\begin{figure}
-\begin{center}
-\epsscale{0.8}
-\epsfig{file=fig_qffit_cylr2_50000h35_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmasscomp11_0_10_5_lit_primuszerr.eps, height=0.8\textwidth}
-\caption{The evolution of the quiescent fraction at fiducial mass, $f_{Q}(\mathcal{M}_{\mathrm{fid}})$, for low (blue) and high (red) density environments within the redshift range $z = 0.0 - 0.8$.
-We present the $f_{Q}(\mathcal{M}_{\mathrm{fid}})$ evolution for $\mathcal{M}_{\mathrm{fid}} = 10^{10.5} \mathcal{M}_\odot$ (solid fill) and $10^{11} \mathcal{M}_\odot$ (patterned fill) with the uncertainty of the best-fit parameter $b$ in Equation \ref{eq:qffit} represented by the width of the line.
-While the high density $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ is greater than low density environment $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ over the entire redshift range of our sample, there is a significant increase in $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ over cosmic time for both environments.
-For the environment cut-offs ($n_{\mathrm{env}} < 0.5$ for low and $n_{\mathrm{env}} > 3.0$ for high), there is no significant difference in the slope of the evolution between the environments.}         \label{fig:qffit}
-\end{center}
-\end{figure}
-
-\clearpage
-\begin{table} 
-  \caption{Best Fit Parameters for $f_{\mathrm{Q}}(\mathcal{M}_{*})$ Fit}
-  \label{tab:bestfitparam}
-  \begin{center}
-    \leavevmode
-    \begin{tabular}{clcc} \hline \hline              
-    $z_1 < z < z_2$ &Environment        &a  &b  \\ \hline 
-$0.05 < z< 0.12$ &$n_{\mathrm{env}} < \lowenvthresh$ & $0.410 \pm 0.018$ & $0.469 \pm 0.007$ \\
-               &$n_{\mathrm{env}} > \highenvthresh$ & $0.270 \pm 0.016$ & $0.620 \pm 0.008$ \\ 
-                              &               &                       &                           \\ \hline   
-$0.2 < z <0.4$ & $n_{\mathrm{env}} < \lowenvthresh$ & $0.340 \pm 0.032$ & $0.432 \pm 0.015$ \\
-               &$n_{\mathrm{env}} > \highenvthresh$ & $0.432 \pm 0.018$ & $0.544 \pm 0.010$ \\
-               &               &                       &                           \\ \hline
-$0.4 < z < 0.6$      &$n_{\mathrm{env}} < \lowenvthresh$ & $0.263 \pm 0.038$ & $0.381 \pm 0.018$ \\
-               &$n_{\mathrm{env}} > \highenvthresh$ & $0.289 \pm 0.018$ & $0.446 \pm 0.013$ \\
-               &               &                       &                           \\ \hline
-$0.6 < z < 0.8$      &$n_{\mathrm{env}} < \lowenvthresh$ & $0.284 \pm 0.036$ & $0.352 \pm 0.019$ \\
-               &$n_{\mathrm{env}} > \highenvthresh$            & $0.468 \pm 0.065$ & $0.429 \pm 0.023$ \\
-               &               &                       &                           \\ \hline
-  \multicolumn{4}{l}{}                                             \\       
-    \end{tabular} \par
-    \end{center}
-	\tablecomments{Best fit parameters in Equation \ref{eq:qffit} for each subsample $f_{\mathrm{Q}}(\mathcal{M}_{*})$ in Figure \ref{fig:qf} for $\mathcal{M}_{\mathrm{fid}} = 10^{10.5} \mathcal{M}_{\odot}$.}
-\end{table}
-\clearpage
-
-\begin{figure*}
-    \begin{center}
-        \leavevmode
-        \epsscale{1.0}
-\epsfig{file=fig_qffit_cylr2_50000h35_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmass10_5_lit_primuszerr_baldry_geha_iovino_kovac_peng_envthresh_kovacoffset.eps, height=\textwidth, angle=90}
-        \caption{$f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}=10^{10.5} \mathcal{M}_\odot)$ evolution compared to $f_{\mathrm{red}}(\mathcal{M}_{*} \sim 10^{10.5} \; \mathcal{M}_{\odot})$ in the literature: \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross) from SDSS (panel a), \cite{Iovino:2010aa} (empty square) and \cite{Kovac:2014aa} (triangle) from zCOSMOS (panel \kovacpanel), and \cite{Peng:2010aa} from both SDSS and zCOSMOS (panel \pengpanel).
-The $f_{\mathrm{red}}$ values from \cite{Iovino:2010aa}, \cite{Kovac:2014aa}, \cite{Baldry:2006aa}, and \cite{Peng:2010aa} are calculated from the best-fit parameterizations presented in the respective works.
-High density environment is represented in red and low density environment is represented in blue.
-The $f_{\mathrm{Q}}$ value from \cite{geha12a} is the $f_{\mathrm{Q}}$ value at $\mathcal{M} = 10^{10.55} \mathcal{M}_{\odot}$.
-Uncertainties in the \cite{Iovino:2010aa} best-fit $f_{\mathrm{red}}$ is omitted due to insufficient information on the cross correlation terms of the fit parameters.
-For \cite{Kovac:2014aa} we apply the offset between the color-based and SFR-based galaxy classification in order to plot the $f_{\mathrm{Q}}$ estimates.
-We also plot the $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}} = 10^{10.5} \mathcal{M}_\odot)$ evolution of our sample with varying environment cut-offs specified on the top right.
-As in Figure \ref{fig:qffit} the width of the $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}} = 10^{10.5} \mathcal{M}_\odot)$ evolution represent the uncertainty in the best-fit parameters of Equation \ref{eq:qffit}.}         \label{fig:qffit_comp}
-    \end{center}
-\end{figure*}
-
+\section*{}
 \end{document}

### 2015-03-18 qfenv_paper/ApJ submission/qf_environment.tex
address referee report
responses to minor comments on ref report

@@
 uncertainties are significantly larger ($\sigma_{z}/(1+z) \approx 0.5
-\%$) than the uncertainties of the SDSS-{\em GALEX} redshifts. In order to have
+\%$) than the uncertainties of the SDSS redshifts. In order to have
 comparable environment measures throughout our redshift range, we
@@
 redshift by randomly sampling a Gaussian distribution with standard
-deviation $\sigma = 0.005 (1+z_{\mathrm{SDSS}-GALEX})$, where
-$z_{\mathrm{SDSS}-GALEX}$ is the redshift of the galaxy.
+deviation $\sigma = 0.005 (1+z_\mathrm{SDSS})$, where
+$z_\mathrm{SDSS}$ is the SDSS redshift of the galaxy.
 
@@
 
-For our aperture, we use a cylinder of dimensions: $R_{\mathrm{ap}} =
-\apradius\;
-\mathrm{Mpc}$ and $H_{\mathrm{ap}} = \apheight\; \mathrm{Mpc}$.  We use a
+For our aperture, we use a cylinder of dimensions: $R_{\mathrm{ap}} = \apradius\;
+\mathrm{Mpc}$ and $H_{\mathrm{ap}} = \apheight\; \mathrm{Mpc}$. 
+We note that $H_\mathrm{ap}$ is the full height of the cylinder and $R_\mathrm{ap}$ 
+and $H_\mathrm{ap}$ are comoving distances. We use a
 cylindrical aperture to account for the PRIMUS redshift
@@
     \leavevmode
-    \epsfig{file=fig3.pdf, height=0.75\textwidth,angle=90}
+    \epsfig{file=fig3.pdf, height=0.75\textwidth}
      \caption{Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) galaxies in 
@@
 For our PRIMUS sample at $z \sim 0.3$, over $10^{9.5} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11} \mathcal{M}_{\odot}$ $f_{\mathrm{Q}}$ ranges from $\sim 0.2$ to $\sim 0.65$ for low density environment, while at high density environment $f_{\mathrm{Q}}$ ranges from $\sim 0.2$ to $\sim 0.8$.
-Similarly, at $z \sim 0.5$, over $10^{10} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11.2} \mathcal{M}_{\odot}$ $f_{\mathrm{Q}}$ ranges from $\sim 0.3$ to $\sim 0.6$ for low density environment and $f_{\mathrm{Q}}$ ranges from $\sim 0.3$ to $\sim 0.7$.
+Similarly, at $z \sim 0.5$, over $10^{10} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11.2} \mathcal{M}_{\odot}$ $f_{\mathrm{Q}}$ ranges from $\sim 0.3$ to $\sim 0.6$ for low density environment and $f_{\mathrm{Q}}$ ranges from $\sim 0.3$ to $\sim 0.7$ for high density environments.
 Finally in our highest redshift bin $z \sim 0.7$, over the mass range $10^{10.5} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11.5} \mathcal{M}_{\odot}$, $f_{\mathrm{Q}}$ ranges from $\sim 0.35$ to $\sim 0.6$ for low density and $\sim 0.45$ to $\sim 0.8$ for high density.
@@
     is greater than $f_{\mathrm{Q}}$ in low density environments
-    regardless of mass and out to redshift $z\sim 0.7$. This result
+    for $\mathcal{M} \sim 10^{10.5} -10^{11} \mathcal{M}_\odot$ and out to redshift $z\sim 0.7$. This result
     reflects the well known trend that galaxies in high density

### 2015-03-19 qfenv_paper/ApJ submission/qf_environment.tex
More referee report responses

@@
 \def \Hbp {H$\beta ^\prime$}
-\def \lowenvthresh {0.5}
+\def \lowenvthresh {0.0}
 \def \highenvthresh {3.0}
@@
 
-\title{PRIMUS: Effect of Galaxy Environment on the Quiescent Fraction Evolution at \lowercase{\textit{z}}$<0.8$}
+\title{PRIMUS: Effects of Galaxy Environment on the Quiescent Fraction Evolution at \lowercase{\textit{z}}$<0.8$}
 \author{
@@
 of star formation is due to external influences on
-them. In other words, in the recent Universe a substantial fraction of the
+them. {\bf In other words}, in the recent Universe a substantial fraction of the
 galaxies that cease forming stars do so due to internal processes.
@@
 \texttt{iSEDfit} uses the redshift and the observed photometry of the galaxies to determine the statistical likelihood of a large ensemble of generated model SEDs.
-The model SEDs are generated using Flexible Stellar Population Synthesis (FSPS) models (\citealt{Conroy:2010aa}) based on the \cite{Chabrier:2003aa} IMF, along with other prior parameters discussed in Section 4.1 and Appendix A of \cite{Moustakas:2013aa}.
+The model SEDs are generated using Flexible Stellar Population Synthesis (FSPS) models (\citealt{Conroy:2010aa}) based on the \cite{Chabrier:2003aa} IMF, along with {\bf a time dependent dust attenuation curve of \cite{Charlot:2000aa} and }other prior parameters discussed in Section 4.1 and Appendix A of \cite{Moustakas:2013aa}.
 For the observed photometry, we use the {\em GALEX} FUV and NUV, the two shortest IRAC bands at $3.6$ and $4.5 \mu \mathrm{m}$ (the two longer-wavelength IRAC channels are excluded because \texttt{iSEDfit} does not model hot dust or polycyclic aromatic hydrocarbons emission lines), and the optical bands.
@@
     & & Quiescent & Star-Forming & Quiescent & Star-Forming &  \\ \hline 
-$0.05 < z < 0.12$ & $n_{\mathrm{env}} < \lowenvthresh $ & 6533 & 7508 & $10^{10.2} \mathcal{M}_{\odot}$ & $10^{10.2} \mathcal{M}_{\odot}$ & -20.95 \\
+$0.05 < z < 0.12$ & $n_{\mathrm{env}} = \lowenvthresh $ & 6533 & 7508 & $10^{10.2} \mathcal{M}_{\odot}$ & $10^{10.2} \mathcal{M}_{\odot}$ & -20.95 \\
                & $n_{\mathrm{env}} > \highenvthresh $ &14673 & 9717 &                          \\ 
                               & all          &$33553$                       & $29864$                          \\ \hline
-$0.2 < z < 0.4$      &$n_{\mathrm{env}} < \lowenvthresh $           &363                    &1231 & $10^{9.8} \mathcal{M}_{\odot}$ & $10^{9.8} \mathcal{M}_{\odot}$ &-21.03 \\
+$0.2 < z < 0.4$      &$n_{\mathrm{env}} = \lowenvthresh $           &363                    &1231 & $10^{9.8} \mathcal{M}_{\odot}$ & $10^{9.8} \mathcal{M}_{\odot}$ &-21.03 \\
                &$n_{\mathrm{env}} > \highenvthresh $            &379                    &756                           \\
                & all                & $1086$                      & $2879$                          \\ \hline
-$0.4 < z < 0.6$      &$n_{\mathrm{env}} < \lowenvthresh $           &536                       &1498 & $10^{10.3} \mathcal{M}_{\odot}$ & $10^{10.3} \mathcal{M}_{\odot}$ & -20.98 \\
+$0.4 < z < 0.6$      &$n_{\mathrm{env}} = \lowenvthresh $           &536                       &1498 & $10^{10.3} \mathcal{M}_{\odot}$ & $10^{10.3} \mathcal{M}_{\odot}$ & -20.98 \\
                &$n_{\mathrm{env}} > \highenvthresh $            &490                       &854                           \\
                & all               & $1560$                      & $3577$                          \\ \hline
-$0.6 < z < 0.8$      &$n_{\mathrm{env}} < \lowenvthresh $           &567                       &1254  & $10^{10.7} \mathcal{M}_{\odot}$ & $10^{10.6} \mathcal{M}_{\odot}$ & -20.97 \\
+$0.6 < z < 0.8$      &$n_{\mathrm{env}} = \lowenvthresh $           &567                       &1254  & $10^{10.7} \mathcal{M}_{\odot}$ & $10^{10.6} \mathcal{M}_{\odot}$ & -20.97 \\
                &$n_{\mathrm{env}} > \highenvthresh $            &498                       &671                           \\
@@
 apply PRIMUS redshift uncertainties to our galaxy sample selected from
-SDSS-{\em GALEX}. For each SDSS-{\em GALEX} galaxy, we adjust its
+SDSS-{\em GALEX}. {\bf For each SDSS-{\em GALEX} galaxy, we adjust its
 redshift by randomly sampling a Gaussian distribution with standard
 deviation $\sigma = 0.005 (1+z_\mathrm{SDSS})$, where
-$z_\mathrm{SDSS}$ is the SDSS redshift of the galaxy.
+$z_\mathrm{SDSS}$ is the SDSS redshift of the galaxy.}
 
@@
 The contribution from quiescent galaxies is colored in red.
-Galaxies with $n_{\mathrm{env}} < 0.5$ are in low density environments and galaxies with $n_{\mathrm{env}} > 3.0$ are in high density environment.
+{\bf Galaxies with $n_{\mathrm{env}} = 0.0$ are in low density environments} and galaxies with $n_{\mathrm{env}} > 3.0$ are in high density environment.
 We note that the significant difference among the SDSS distribution and the PRIMUS distributions above is due to the different stellar mass completeness limits imposed on each redshift bin of our galaxy sample.}      \label{fig:envcount}
@@
 \mathrm{Mpc}$ and $H_{\mathrm{ap}} = \apheight\; \mathrm{Mpc}$. 
-We note that $H_\mathrm{ap}$ is the full height of the cylinder and $R_\mathrm{ap}$ 
-and $H_\mathrm{ap}$ are comoving distances. We use a
+{\bf We note that $H_\mathrm{ap}$ is the full height of the cylinder and $R_\mathrm{ap}$ 
+and $H_\mathrm{ap}$ are comoving distances.} We use a
 cylindrical aperture to account for the PRIMUS redshift
@@
 Once we obtain environment measurements for all the galaxies
-in our galaxy sample, we classify galaxies with $n_{\mathrm{env}} < 0.5$
-to be in ``low" environment densities and galaxies with $n_{\mathrm{env}} > 3$
+in our galaxy sample, {\bf we classify galaxies with $n_{\mathrm{env}} = 0.0$
+to be in ``low" environment densities} and galaxies with $n_{\mathrm{env}} > 3$
 to be in ``high" environment densities. The high environment cutoff was
@@
 The quiescent galaxy contributions are colored in red while the star-forming galaxy contributions are colored in blue and patterned.
-We classify galaxies with $n_{\mathrm{env}} < 0.5$ to be in low density environments and galaxies with $n_{\mathrm{env}} > 3.0$ to be in high density environments.
+We classify {\bf galaxies with $n_{\mathrm{env}} = 0.0$ to be in low density environments} and galaxies with $n_{\mathrm{env}} > 3.0$ to be in high density environments.
 
@@
 was calculated using a cylindrical aperture size of $R=\apradius \: \mathrm{Mpc}$ and $H=\apheight \: \mathrm{Mpc}$ and  
-classified as low environment when $n_{\mathrm{env}} < 0.5$ and as high environment when $n_{\mathrm{env}} > 3.0$. The SMFs use mass bins of 
+{\bf classified as low environment when $n_{\mathrm{env}} = 0.0$ and }as high environment when $n_{\mathrm{env}} > 3.0$. The SMFs use mass bins of 
 width $\Delta \mathrm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.2$. In each panel we use shades of blue 
@@
 While the high density $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ is greater than low density environment $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ over the entire redshift range of our sample, there is a significant increase in $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ over cosmic time for both environments.
-For the environment cut-offs ($n_{\mathrm{env}} < 0.5$ for low and $n_{\mathrm{env}} > 3.0$ for high), there is no significant difference in the slope of the evolution between the environments.}         \label{fig:qffit}
+{\bf For the environment cut-offs ($n_{\mathrm{env}} =0.0 $ for low }and $n_{\mathrm{env}} > 3.0$ for high), there is no significant difference in the slope of the evolution between the environments.}         \label{fig:qffit}
     \end{center}
@@
     $z_1 < z < z_2$ &Environment        &a  &b  \\ \hline 
-$0.05 < z< 0.12$ &$n_{\mathrm{env}} < \lowenvthresh$ & $0.410 \pm 0.018$ & $0.469 \pm 0.007$ \\
+$0.05 < z< 0.12$ &$n_{\mathrm{env}} = \lowenvthresh$ & $0.410 \pm 0.018$ & $0.469 \pm 0.007$ \\
                &$n_{\mathrm{env}} > \highenvthresh$ & $0.270 \pm 0.016$ & $0.620 \pm 0.008$ \\ 
                               &               &                       &                           \\ \hline   
-$0.2 < z <0.4$ & $n_{\mathrm{env}} < \lowenvthresh$ & $0.340 \pm 0.032$ & $0.432 \pm 0.015$ \\
+$0.2 < z <0.4$ & $n_{\mathrm{env}} = \lowenvthresh$ & $0.340 \pm 0.032$ & $0.432 \pm 0.015$ \\
                &$n_{\mathrm{env}} > \highenvthresh$ & $0.432 \pm 0.018$ & $0.544 \pm 0.010$ \\
                &               &                       &                           \\ \hline
-$0.4 < z < 0.6$      &$n_{\mathrm{env}} < \lowenvthresh$ & $0.263 \pm 0.038$ & $0.381 \pm 0.018$ \\
+$0.4 < z < 0.6$      &$n_{\mathrm{env}} = \lowenvthresh$ & $0.263 \pm 0.038$ & $0.381 \pm 0.018$ \\
                &$n_{\mathrm{env}} > \highenvthresh$ & $0.289 \pm 0.018$ & $0.446 \pm 0.013$ \\
                &               &                       &                           \\ \hline
-$0.6 < z < 0.8$      &$n_{\mathrm{env}} < \lowenvthresh$ & $0.284 \pm 0.036$ & $0.352 \pm 0.019$ \\
+$0.6 < z < 0.8$      &$n_{\mathrm{env}} = \lowenvthresh$ & $0.284 \pm 0.036$ & $0.352 \pm 0.019$ \\
                &$n_{\mathrm{env}} > \highenvthresh$            & $0.468 \pm 0.065$ & $0.429 \pm 0.023$ \\

### 2015-03-20 qfenv_paper/ApJ submission/qf_environment.tex
more changes to address ref report

@@
 spectrograph on the Magellan I Baade $6.5$-m telescope with a slitmask and low dispersion prism.
-For details on the PRIMUS observation methods such as survey design, targeting, and data summary, we refer readers to the survey papers (\citealt{Coil:2011aa, Cool:2013aa}).
+For details on the PRIMUS observation methods such as survey design, targeting, and data summary, {\bf we refer readers to the \cite{Coil:2011aa}.
+For details on redshift fitting, redshift precision and survey completeness we refer readers to \cite{Cool:2013aa}.}
 
@@
 Four of these fields are a part of the {\em Spitzer} Wide-area Infrared Extragalactic Survey (SWIRE\footnote{http://swire.ipac.caltech.edu/swire/swire.html}): the European Large Area ISO Survey - South $1$ field (ELAIS-S1\footnote{http://dipastro.pd.astro.it/esis}), the Chandra Deep Field South SWIRE field (CDFS), and the XMM Large Scale Structure Survey field (XMM-LSS).
-The XMM-LSS consists of two separate but spatially adjacent fields: the Subaru/XMM-Newton DEEP Survey field (XMM-SXDSS\footnote{http://www.naoj.org/cience/SubaruProject/SDS}) and the Canadian-France-Hawaii Telescope Legacy Survey field (XMM-CFHTLS\footnote{http://www.cfht.hawaii.edu/Science/CFHLS}).
+The XMM-LSS consists of two separate but spatially adjacent fields: the Subaru/XMM-Newton DEEP Survey field (XMM-SXDS\footnote{http://www.naoj.org/cience/SubaruProject/SDS}) and the Canadian-France-Hawaii Telescope Legacy Survey field (XMM-CFHTLS\footnote{http://www.cfht.hawaii.edu/Science/CFHLS}).
 Our fifth and final field is the Cosmic Evolution Survey (COSMOS\footnote{http://cosmos.astro.caltech.edu}) field.
@@
 For the entire redshift range of our sample, $f_{\mathrm{Q}}$ in high density environment is higher than $f_{\mathrm{Q}}$ in low density environments.
+
+{\bf We note that for $\mathcal{M}_* < 10^{10} \mathcal{M}_{\odot}$ at $z \sim 0.3$, we find no significant difference between $f_\mathrm{Q}$ in low and high density environments.
+Similar quiescent/red fraction studies (e.g.
+\citealt{Baldry:2006aa, Cucciati:2010aa}) find, at these redshifts and mass range, a greater environment dependence in $f_\mathrm{Q}$.
+However we note that, at $\mathcal{M}_* < 10^{10} \mathcal{M}_{\odot}$ at $z \sim 0.3$, only three of the five PRIMUS fields used in our analysis (XMM-SXDS, XMM-CFHTLS, and COSMOS; see Section \ref{sec:primus}) contribute galaxies to our sample.
+As a result our jack-knife uncertainties, which are calculated by excluding one PRIMUS field at a time, underestimate the uncertainty from cosmic variance especially since the PRIMUS fields XMM-SXDS and XMM-CFHTLS are adjacent fields.
+A rough estimate of the cosmic variances using the expressions derived in \cite{Driver:2010aa} put cosmic variance uncertainties $> 60 \%$.
+This estimate does not take into account the unique geometry of the PRIMUS fields or the edge-cuts, which only increase the cosmic variance uncertainties.
+Therefore, the quiescent fraction comparison at $z \sim 0.3$ for $\mathcal{M}_{*} < 10^{10} \mathcal{M}_\odot$ cannot be accurately made from our PRIMUS sample.}
 
@@
 
+\bibitem[{{Driver} {et~al.}(2010){Driver}, \&{Robotham}}]{Driver:2010aa}
+{Driver}, S.~P. and {Robotham}, A.~S.~G. 2010, \mnras, 407, 2131
+
 \bibitem[{{Faber} {et~al.}(2007){Faber}, {Willmer}, {Wolf}, {Koo}, {Weiner},

### 2015-03-20 qfenv_paper/qf_environment.tex
more changes to address ref report

@@
 
-\title{PRIMUS: Effect of Galaxy Environment on the Quiescent Fraction Evolution at $z < 0.8$}
+\title{PRIMUS: Effects of Galaxy Environment on the Quiescent Fraction Evolution at \lowercase{\textit{z}}$<0.8$}
 \author{
@@
 of star formation is due to external influences on
-them. However, in the recent Universe a substantial fraction of the
+them. {\bf In other words}, in the recent Universe a substantial fraction of the
 galaxies that cease forming stars do so due to internal processes.
 \end{abstract}
-\keywords{cosmology:observations --- galaxies: evolution --- galaxies:groups --- galaxies: star formation}
+\keywords{cosmology: observations --- galaxies: evolution --- galaxies: groups --- galaxies: star formation}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 uncertainties are significantly larger ($\sigma_{z}/(1+z) \approx 0.5
-\%$) than the uncertainties of the SDSS-{\em GALEX} redshifts. In order to have
+\%$) than the uncertainties of the SDSS redshifts. In order to have
 comparable environment measures throughout our redshift range, we
 apply PRIMUS redshift uncertainties to our galaxy sample selected from
-SDSS-{\em GALEX}. For each SDSS-{\em GALEX} galaxy, we adjust its
+SDSS-{\em GALEX}. {\bf For each SDSS-{\em GALEX} galaxy, we adjust its
 redshift by randomly sampling a Gaussian distribution with standard
-deviation $\sigma = 0.005 (1+z_{\mathrm{SDSS}-GALEX})$, where
-$z_{\mathrm{SDSS}-GALEX}$ is the redshift of the galaxy.
+deviation $\sigma = 0.005 (1+z_\mathrm{SDSS})$, where
+$z_\mathrm{SDSS}$ is the SDSS redshift of the galaxy.}
 
@@
 
-For our aperture, we use a cylinder of dimensions: $R_{\mathrm{ap}} =
-\apradius\;
-\mathrm{Mpc}$ and $H_{\mathrm{ap}} = \apheight\; \mathrm{Mpc}$.  We use a
+For our aperture, we use a cylinder of dimensions: $R_{\mathrm{ap}} = \apradius\;
+\mathrm{Mpc}$ and $H_{\mathrm{ap}} = \apheight\; \mathrm{Mpc}$. 
+{\bf We note that $H_\mathrm{ap}$ is the full height of the cylinder and $R_\mathrm{ap}$ 
+and $H_\mathrm{ap}$ are comoving distances.} We use a
 cylindrical aperture to account for the PRIMUS redshift
@@
     \leavevmode
-    \epsfig{file=fig_smf_cylr2_50000h35_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_2envbin_lowenv0_5_highenv3_0_lit_primuszerr.eps, height=0.75\textwidth,angle=90}
+    \epsfig{file=fig3.pdf, height=0.75\textwidth}
      \caption{Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) galaxies in 
@@
         \leavevmode
-        \epsfig{file=fig_qf_cylr2_50000h35_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_lit_primuszerr.eps, height=0.75\textwidth,angle=90}
+        \epsfig{file=fig4.pdf, height=0.75\textwidth,angle=90}
         \caption{Evolution of the quiescent fraction $f_{\mathrm{Q}}$ for
@@
 For our PRIMUS sample at $z \sim 0.3$, over $10^{9.5} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11} \mathcal{M}_{\odot}$ $f_{\mathrm{Q}}$ ranges from $\sim 0.2$ to $\sim 0.65$ for low density environment, while at high density environment $f_{\mathrm{Q}}$ ranges from $\sim 0.2$ to $\sim 0.8$.
-Similarly, at $z \sim 0.5$, over $10^{10} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11.2} \mathcal{M}_{\odot}$ $f_{\mathrm{Q}}$ ranges from $\sim 0.3$ to $\sim 0.6$ for low density environment and $f_{\mathrm{Q}}$ ranges from $\sim 0.3$ to $\sim 0.7$.
+Similarly, at $z \sim 0.5$, over $10^{10} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11.2} \mathcal{M}_{\odot}$ $f_{\mathrm{Q}}$ ranges from $\sim 0.3$ to $\sim 0.6$ for low density environment and $f_{\mathrm{Q}}$ ranges from $\sim 0.3$ to $\sim 0.7$ for high density environments.
 Finally in our highest redshift bin $z \sim 0.7$, over the mass range $10^{10.5} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11.5} \mathcal{M}_{\odot}$, $f_{\mathrm{Q}}$ ranges from $\sim 0.35$ to $\sim 0.6$ for low density and $\sim 0.45$ to $\sim 0.8$ for high density.
 For the entire redshift range of our sample, $f_{\mathrm{Q}}$ in high density environment is higher than $f_{\mathrm{Q}}$ in low density environments.
+
+{\bf We note that for $\mathcal{M}_* < 10^{10} \mathcal{M}_{\odot}$ at $z \sim 0.3$, we find no significant difference between $f_\mathrm{Q}$ in low and high density environments.
+Similar quiescent/red fraction studies (e.g.
+\citealt{Baldry:2006aa, Cucciati:2010aa}) find, at these redshifts and mass range, a greater environment dependence in $f_\mathrm{Q}$.
+However we note that, at $\mathcal{M}_* < 10^{10} \mathcal{M}_{\odot}$ at $z \sim 0.3$, only three of the five PRIMUS fields used in our analysis (XMM-SXDS, XMM-CFHTLS, and COSMOS; see Section \ref{sec:primus}) contribute galaxies to our sample.
+As a result our jack-knife uncertainties, which are calculated by excluding one PRIMUS field at a time, underestimate the uncertainty from cosmic variance especially since the PRIMUS fields XMM-SXDS and XMM-CFHTLS are adjacent fields.
+A rough estimate of the cosmic variances using the expressions derived in \cite{Driver:2010aa} put cosmic variance uncertainties $> 60 \%$.
+This estimate does not take into account the unique geometry of the PRIMUS fields or the edge-cuts, which only increase the cosmic variance uncertainties.
+Therefore, the quiescent fraction comparison at $z \sim 0.3$ for $\mathcal{M}_{*} < 10^{10} \mathcal{M}_\odot$ cannot be accurately made from our PRIMUS sample.}
 
@@
         \epsscale{1.0}
-        \epsfig{file=fig_qffit_cylr2_50000h35_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmasscomp11_0_10_5_lit_primuszerr.eps, height=0.45\textwidth}
+        \epsfig{file=fig5.pdf, height=0.45\textwidth}
         \caption{The evolution of the quiescent fraction at fiducial
@@
         \epsscale{1.0}
-        \epsfig{file=fig_qffit_cylr2_50000h35_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmass10_5_lit_primuszerr_baldry_geha_iovino_kovac_peng_envthresh_kovacoffset.eps, height=\textwidth, angle=90}
+        \epsfig{file=fig6.pdf, height=\textwidth, angle=90}
         \caption{$f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}=10^{10.5} \mathcal{M}_\odot)$ evolution compared to $f_{\mathrm{red}}(\mathcal{M}_{*} \sim 10^{10.5} \; \mathcal{M}_{\odot})$ in the literature: \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross) from SDSS (panel a), \cite{Iovino:2010aa} (empty square) and \cite{Kovac:2014aa} (triangle) from zCOSMOS (panel \kovacpanel), and \cite{Peng:2010aa} from both SDSS and zCOSMOS (panel \pengpanel).
@@
 \bibliographystyle{apj}
-\bibliography{PRIMUS}
+\begin{thebibliography}{}
+\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+
+\bibitem[{{Abazajian} {et~al.}(2009){Abazajian}, {Adelman-McCarthy},
+  {Ag{\"u}eros}, {Allam}, {Allende Prieto}, {An}, {Anderson}, {Anderson},
+  {Annis}, {Bahcall}, \& et~al.}]{Abazajian:2009aa}
+{Abazajian}, K.~N., {Adelman-McCarthy}, J.~K., {Ag{\"u}eros}, M.~A., {et~al.}
+  2009, \apjs, 182, 543
+
+\bibitem[{{Baldry} {et~al.}(2006){Baldry}, {Balogh}, {Bower}, {Glazebrook},
+  {Nichol}, {Bamford}, \& {Budavari}}]{Baldry:2006aa}
+{Baldry}, I.~K., {Balogh}, M.~L., {Bower}, R.~G., {et~al.} 2006, \mnras, 373,
+  469
+
+\bibitem[{{Baldry} {et~al.}(2008){Baldry}, {Glazebrook}, \&
+  {Driver}}]{Baldry:2008aa}
+{Baldry}, I.~K., {Glazebrook}, K., \& {Driver}, S.~P. 2008, \mnras, 388, 945
+
+\bibitem[{{Balogh} {et~al.}(2000){Balogh}, {Navarro}, \&
+  {Morris}}]{Balogh:2000aa}
+{Balogh}, M.~L., {Navarro}, J.~F., \& {Morris}, S.~L. 2000, \apj, 540, 113
+
+\bibitem[{{Behroozi} {et~al.}(2013){Behroozi}, {Marchesini}, {Wechsler},
+  {Muzzin}, {Papovich}, \& {Stefanon}}]{Behroozi:2013aa}
+{Behroozi}, P.~S., {Marchesini}, D., {Wechsler}, R.~H., {et~al.} 2013, \apjl,
+  777, L10
+
+\bibitem[{{Bekki}(2009)}]{Bekki:2009aa}
+{Bekki}, K. 2009, \mnras, 399, 2221
+
+\bibitem[{{Bell} {et~al.}(2004){Bell}, {Wolf}, {Meisenheimer}, {Rix}, {Borch},
+  {Dye}, {Kleinheinrich}, {Wisotzki}, \& {McIntosh}}]{Bell:2004aa}
+{Bell}, E.~F., {Wolf}, C., {Meisenheimer}, K., {et~al.} 2004, \apj, 608, 752
+
+\bibitem[{{Bell} {et~al.}(2005){Bell}, {Papovich}, {Wolf}, {Le Floc'h},
+  {Caldwell}, {Barden}, {Egami}, {McIntosh}, {Meisenheimer},
+  {P{\'e}rez-Gonz{\'a}lez}, {Rieke}, {Rieke}, {Rigby}, \& {Rix}}]{bell05a}
+{Bell}, E.~F., {Papovich}, C., {Wolf}, C., {et~al.} 2005, \apj, 625, 23
+
+\bibitem[{{Bernardi} {et~al.}(2007){Bernardi}, {Hyde}, {Sheth}, {Miller}, \&
+  {Nichol}}]{Bernardi:2007aa}
+{Bernardi}, M., {Hyde}, J.~B., {Sheth}, R.~K., {Miller}, C.~J., \& {Nichol},
+  R.~C. 2007, \aj, 133, 1741
+
+\bibitem[{{Blanton} {et~al.}(2006){Blanton}, {Eisenstein}, {Hogg}, \&
+  {Zehavi}}]{Blanton:2006aa}
+{Blanton}, M.~R., {Eisenstein}, D., {Hogg}, D.~W., \& {Zehavi}, I. 2006, \apj,
+  645, 977
+
+\bibitem[{{Blanton} {et~al.}(2011){Blanton}, {Kazin}, {Muna}, {Weaver}, \&
+  {Price-Whelan}}]{Blanton:2011aa}
+{Blanton}, M.~R., {Kazin}, E., {Muna}, D., {Weaver}, B.~A., \& {Price-Whelan},
+  A. 2011, \aj, 142, 31
+
+\bibitem[{{Blanton} {et~al.}(2005{\natexlab{a}}){Blanton}, {Lupton},
+  {Schlegel}, {Strauss}, {Brinkmann}, {Fukugita}, \&
+  {Loveday}}]{Blanton:2005ab}
+{Blanton}, M.~R., {Lupton}, R.~H., {Schlegel}, D.~J., {et~al.}
+  2005{\natexlab{a}}, \apj, 631, 208
+
+\bibitem[{{Blanton} \& {Moustakas}(2009)}]{blanton09a}
+{Blanton}, M.~R., \& {Moustakas}, J. 2009, \araa, 47, 159
+
+\bibitem[{{Blanton} \& {Roweis}(2007)}]{Blanton:2007aa}
+{Blanton}, M.~R., \& {Roweis}, S. 2007, \aj, 133, 734
+
+\bibitem[{{Blanton} {et~al.}(2005{\natexlab{b}}){Blanton}, {Schlegel},
+  {Strauss}, {Brinkmann}, {Finkbeiner}, {Fukugita}, {Gunn}, {Hogg},
+  {Ivezi{\'c}}, {Knapp}, {Lupton}, {Munn}, {Schneider}, {Tegmark}, \&
+  {Zehavi}}]{Blanton:2005aa}
+{Blanton}, M.~R., {Schlegel}, D.~J., {Strauss}, M.~A., {et~al.}
+  2005{\natexlab{b}}, \aj, 129, 2562
+
+\bibitem[{{Bolzonella} {et~al.}(2010){Bolzonella}, {Kova{\v c}}, {Pozzetti},
+  {Zucca}, {Cucciati}, {Lilly}, {Peng}, {Iovino}, {Zamorani}, {Vergani},
+  {Tasca}, {Lamareille}, {Oesch}, {Caputi}, {Kampczyk}, {Bardelli}, {Maier},
+  {Abbas}, {Knobel}, {Scodeggio}, {Carollo}, {Contini}, {Kneib}, {Le
+  F{\`e}vre}, {Mainieri}, {Renzini}, {Bongiorno}, {Coppa}, {de la Torre}, {de
+  Ravel}, {Franzetti}, {Garilli}, {Le Borgne}, {Le Brun}, {Mignoli},
+  {Pell{\'o}}, {Perez-Montero}, {Ricciardelli}, {Silverman}, {Tanaka},
+  {Tresse}, {Bottini}, {Cappi}, {Cassata}, {Cimatti}, {Guzzo}, {Koekemoer},
+  {Leauthaud}, {Maccagni}, {Marinoni}, {McCracken}, {Memeo}, {Meneux},
+  {Porciani}, {Scaramella}, {Aussel}, {Capak}, {Halliday}, {Ilbert},
+  {Kartaltepe}, {Salvato}, {Sanders}, {Scarlata}, {Scoville}, {Taniguchi}, \&
+  {Thompson}}]{Bolzonella:2010aa}
+{Bolzonella}, M., {Kova{\v c}}, K., {Pozzetti}, L., {et~al.} 2010, \aap, 524,
+  A76
+
+\bibitem[{{Borch} {et~al.}(2006){Borch}, {Meisenheimer}, {Bell}, {Rix}, {Wolf},
+  {Dye}, {Kleinheinrich}, {Kovacs}, \& {Wisotzki}}]{borch06a}
+{Borch}, A., {Meisenheimer}, K., {Bell}, E.~F., {et~al.} 2006, \aap, 453, 869
+
+\bibitem[{{Bundy} {et~al.}(2006){Bundy}, {Ellis}, {Conselice}, {Taylor},
+  {Cooper}, {Willmer}, {Weiner}, {Coil}, {Noeske}, \& {Eisenhardt}}]{bundy06a}
+{Bundy}, K., {Ellis}, R.~S., {Conselice}, C.~J., {et~al.} 2006, \apj, 651, 120
+
+\bibitem[{{Butcher} \& {Oemler}(1984)}]{Butcher:1984aa}
+{Butcher}, H., \& {Oemler}, Jr., A. 1984, \apj, 285, 426
+
+\bibitem[{{Chabrier}(2003)}]{Chabrier:2003aa}
+{Chabrier}, G. 2003, \pasp, 115, 763
+
+\bibitem[{{Coil} {et~al.}(2011){Coil}, {Blanton}, {Burles}, {Cool},
+  {Eisenstein}, {Moustakas}, {Wong}, {Zhu}, {Aird}, {Bernstein}, {Bolton}, \&
+  {Hogg}}]{Coil:2011aa}
+{Coil}, A.~L., {Blanton}, M.~R., {Burles}, S.~M., {et~al.} 2011, \apj, 741, 8
+
+\bibitem[{{Conroy} \& {Gunn}(2010)}]{Conroy:2010aa}
+{Conroy}, C., \& {Gunn}, J.~E. 2010, {FSPS: Flexible Stellar Population
+  Synthesis}, astrophysics Source Code Library, ascl:1010.043
+
+\bibitem[{{Cool} {et~al.}(2013){Cool}, {Moustakas}, {Blanton}, {Burles},
+  {Coil}, {Eisenstein}, {Wong}, {Zhu}, {Aird}, {Bernstein}, {Bolton}, {Hogg},
+  \& {Mendez}}]{Cool:2013aa}
+{Cool}, R.~J., {Moustakas}, J., {Blanton}, M.~R., {et~al.} 2013, \apj, 767, 118
+
+\bibitem[{{Cooper} {et~al.}(2005){Cooper}, {Newman}, {Madgwick}, {Gerke},
+  {Yan}, \& {Davis}}]{Cooper:2005aa}
+{Cooper}, M.~C., {Newman}, J.~A., {Madgwick}, D.~S., {et~al.} 2005, \apj, 634,
+  833
+
+\bibitem[{{Cooper} {et~al.}(2008){Cooper}, {Newman}, {Weiner}, {Yan},
+  {Willmer}, {Bundy}, {Coil}, {Conselice}, {Davis}, {Faber}, {Gerke},
+  {Guhathakurta}, {Koo}, \& {Noeske}}]{cooper08a}
+{Cooper}, M.~C., {Newman}, J.~A., {Weiner}, B.~J., {et~al.} 2008, \mnras, 383,
+  1058
+
+\bibitem[{{Cooper} {et~al.}(2010){Cooper}, {Coil}, {Gerke}, {Newman}, {Bundy},
+  {Conselice}, {Croton}, {Davis}, {Faber}, {Guhathakurta}, {Koo}, {Lin},
+  {Weiner}, {Willmer}, \& {Yan}}]{Cooper:2010aa}
+{Cooper}, M.~C., {Coil}, A.~L., {Gerke}, B.~F., {et~al.} 2010, \mnras, 409, 337
+
+\bibitem[{{Croton} {et~al.}(2006){Croton}, {Springel}, {White}, {De Lucia},
+  {Frenk}, {Gao}, {Jenkins}, {Kauffmann}, {Navarro}, \&
+  {Yoshida}}]{Croton:2006aa}
+{Croton}, D.~J., {Springel}, V., {White}, S.~D.~M., {et~al.} 2006, \mnras, 365,
+  11
+
+\bibitem[{{Cucciati} {et~al.}(2010){Cucciati}, {Iovino}, {Kova{\v c}},
+  {Scodeggio}, {Lilly}, {Bolzonella}, {Bardelli}, {Vergani}, {Tasca}, {Zucca},
+  {Zamorani}, {Pozzetti}, {Knobel}, {Oesch}, {Lamareille}, {Caputi},
+  {Kampczyk}, {Tresse}, {Maier}, {Carollo}, {Contini}, {Kneib}, {Le F{\`e}vre},
+  {Mainieri}, {Renzini}, {Bongiorno}, {Coppa}, {de la Torre}, {de Ravel},
+  {Franzetti}, {Garilli}, {Le Borgne}, {Le Brun}, {Mignoli}, {Pell{\`o}},
+  {Peng}, {Perez-Montero}, {Ricciardelli}, {Silverman}, {Tanaka}, {Koekemoer},
+  {Scoville}, {Abbas}, {Bottini}, {Cappi}, {Cassata}, {Cimatti}, {Guzzo},
+  {Leauthaud}, {Maccagni}, {Marinoni}, {McCracken}, {Memeo}, {Meneux},
+  {Porciani}, \& {Scaramella}}]{Cucciati:2010aa}
+{Cucciati}, O., {Iovino}, A., {Kova{\v c}}, K., {et~al.} 2010, \aap, 524, A2
+
+\bibitem[{{Dekel} \& {Birnboim}(2008)}]{Dekel:2008aa}
+{Dekel}, A., \& {Birnboim}, Y. 2008, \mnras, 383, 119
+
+\bibitem[{{Desai} {et~al.}(2007){Desai}, {Dalcanton}, {Arag{\'o}n-Salamanca},
+  {Jablonka}, {Poggianti}, {Gogarten}, {Simard}, {Milvang-Jensen}, {Rudnick},
+  {Zaritsky}, {Clowe}, {Halliday}, {Pell{\'o}}, {Saglia}, \&
+  {White}}]{desai07a}
+{Desai}, V., {Dalcanton}, J.~J., {Arag{\'o}n-Salamanca}, A., {et~al.} 2007,
+  \apj, 660, 1151
+
+\bibitem[{Dressler(1980)}]{dressler80a}
+Dressler, A. 1980, \apj, 236, 351
+
+\bibitem[{{Dressler}(1984)}]{dressler84a}
+{Dressler}, A. 1984, \araa, 22, 185
+
+\bibitem[{{Faber} {et~al.}(2007){Faber}, {Willmer}, {Wolf}, {Koo}, {Weiner},
+  {Newman}, {Im}, {Coil}, {Conroy}, {Cooper}, {Davis}, {Finkbeiner}, {Gerke},
+  {Gebhardt}, {Groth}, {Guhathakurta}, {Harker}, {Kaiser}, {Kassin},
+  {Kleinheinrich}, {Konidaris}, {Kron}, {Lin}, {Luppino}, {Madgwick},
+  {Meisenheimer}, {Noeske}, {Phillips}, {Sarajedini}, {Schiavon}, {Simard},
+  {Szalay}, {Vogt}, \& {Yan}}]{Faber:2007aa}
+{Faber}, S.~M., {Willmer}, C.~N.~A., {Wolf}, C., {et~al.} 2007, \apj, 665, 265
+
+\bibitem[{{Fasano} {et~al.}(2000){Fasano}, {Poggianti}, {Couch}, {Bettoni},
+  {Kj{\ae}rgaard}, \& {Moles}}]{Fasano:2000aa}
+{Fasano}, G., {Poggianti}, B.~M., {Couch}, W.~J., {et~al.} 2000, \apj, 542, 673
+
+\bibitem[{{Gallazzi} {et~al.}(2009){Gallazzi}, {Bell}, {Wolf}, {Gray},
+  {Papovich}, {Barden}, {Peng}, {Meisenheimer}, {Heymans}, {van Kampen},
+  {Gilmour}, {Balogh}, {McIntosh}, {Bacon}, {Barazza}, {B{\"o}hm}, {Caldwell},
+  {H{\"a}ubler}, {Jahnke}, {Jogee}, {Lane}, {Robaina}, {Sanchez}, {Taylor},
+  {Wisotzki}, \& {Zheng}}]{Gallazzi:2009aa}
+{Gallazzi}, A., {Bell}, E.~F., {Wolf}, C., {et~al.} 2009, \apj, 690, 1883
+
+\bibitem[{{Geha} {et~al.}(2012){Geha}, {Blanton}, {Yan}, \& {Tinker}}]{geha12a}
+{Geha}, M., {Blanton}, M.~R., {Yan}, R., \& {Tinker}, J.~L. 2012, \apj, 757, 85
+
+\bibitem[{{Gunn} \& {Gott}(1972)}]{Gunn:1972aa}
+{Gunn}, J.~E., \& {Gott}, III, J.~R. 1972, \apj, 176, 1
+
+\bibitem[{Guzzo {et~al.}(1997)Guzzo, Strauss, Fisher, Giovanelli, \&
+  Haynes}]{guzzo97a}
+Guzzo, L., Strauss, M.~A., Fisher, K.~B., Giovanelli, R., \& Haynes, M.~P.
+  1997, \apj, 489, 37
+
+\bibitem[{Hermit {et~al.}(1996)Hermit, Santiago, Lahav, Strauss, Davis,
+  Dressler, \& Huchra}]{hermit96a}
+Hermit, S., Santiago, B.~X., Lahav, O., {et~al.} 1996, \mnras, 283, 709
+
+\bibitem[{{Hopkins} \& {Beacom}(2006)}]{hopkins06a}
+{Hopkins}, A.~M., \& {Beacom}, J.~F. 2006, \apj, 651, 142
+
+\bibitem[{Hubble(1936)}]{hubble36a}
+Hubble, E.~P. 1936, The Realm of the Nebulae (New Haven: Yale University Press)
+
+\bibitem[{{Hyde} \& {Bernardi}(2009)}]{Hyde:2009aa}
+{Hyde}, J.~B., \& {Bernardi}, M. 2009, \mnras, 394, 1978
+
+\bibitem[{{Iovino} {et~al.}(2010){Iovino}, {Cucciati}, {Scodeggio}, {Knobel},
+  {Kova{\v c}}, {Lilly}, {Bolzonella}, {Tasca}, {Zamorani}, {Zucca}, {Caputi},
+  {Pozzetti}, {Oesch}, {Lamareille}, {Halliday}, {Bardelli}, {Finoguenov},
+  {Guzzo}, {Kampczyk}, {Maier}, {Tanaka}, {Vergani}, {Carollo}, {Contini},
+  {Kneib}, {Le F{\`e}vre}, {Mainieri}, {Renzini}, {Bongiorno}, {Coppa}, {de la
+  Torre}, {de Ravel}, {Franzetti}, {Garilli}, {Le Borgne}, {Le Brun},
+  {Mignoli}, {Pell{\`o}}, {Peng}, {Perez-Montero}, {Ricciardelli}, {Silverman},
+  {Tresse}, {Abbas}, {Bottini}, {Cappi}, {Cassata}, {Cimatti}, {Koekemoer},
+  {Leauthaud}, {Maccagni}, {Marinoni}, {McCracken}, {Memeo}, {Meneux},
+  {Porciani}, {Scaramella}, {Schiminovich}, \& {Scoville}}]{Iovino:2010aa}
+{Iovino}, A., {Cucciati}, O., {Scodeggio}, M., {et~al.} 2010, \aap, 509, A40
+
+\bibitem[{{Jarrett} {et~al.}(2000){Jarrett}, {Chester}, {Cutri}, {Schneider},
+  {Skrutskie}, \& {Huchra}}]{Jarrett:2000aa}
+{Jarrett}, T.~H., {Chester}, T., {Cutri}, R., {et~al.} 2000, \aj, 119, 2498
+
+\bibitem[{{Johnston}(2011)}]{Johnston:2011aa}
+{Johnston}, R. 2011, \aapr, 19, 41
+
+\bibitem[{{Karim} {et~al.}(2011){Karim}, {Schinnerer},
+  {Mart{\'{\i}}nez-Sansigre}, {Sargent}, {van der Wel}, {Rix}, {Ilbert},
+  {Smol{\v c}i{\'c}}, {Carilli}, {Pannella}, {Koekemoer}, {Bell}, \&
+  {Salvato}}]{Karim:2011aa}
+{Karim}, A., {Schinnerer}, E., {Mart{\'{\i}}nez-Sansigre}, A., {et~al.} 2011,
+  \apj, 730, 61
+
+\bibitem[{{Kere{\v s}} {et~al.}(2005){Kere{\v s}}, {Katz}, {Weinberg}, \&
+  {Dav{\'e}}}]{Keres:2005aa}
+{Kere{\v s}}, D., {Katz}, N., {Weinberg}, D.~H., \& {Dav{\'e}}, R. 2005,
+  \mnras, 363, 2
+
+\bibitem[{{Kova{\v c}} {et~al.}(2010){Kova{\v c}}, {Lilly}, {Cucciati},
+  {Porciani}, {Iovino}, {Zamorani}, {Oesch}, {Bolzonella}, {Knobel},
+  {Finoguenov}, {Peng}, {Carollo}, {Pozzetti}, {Caputi}, {Silverman}, {Tasca},
+  {Scodeggio}, {Vergani}, {Scoville}, {Capak}, {Contini}, {Kneib}, {Le
+  F{\`e}vre}, {Mainieri}, {Renzini}, {Bardelli}, {Bongiorno}, {Coppa}, {de la
+  Torre}, {de Ravel}, {Franzetti}, {Garilli}, {Guzzo}, {Kampczyk},
+  {Lamareille}, {Le Borgne}, {Le Brun}, {Maier}, {Mignoli}, {Pello}, {Perez
+  Montero}, {Ricciardelli}, {Tanaka}, {Tresse}, {Zucca}, {Abbas}, {Bottini},
+  {Cappi}, {Cassata}, {Cimatti}, {Fumana}, {Koekemoer}, {Maccagni}, {Marinoni},
+  {McCracken}, {Memeo}, {Meneux}, \& {Scaramella}}]{Kovac:2010ab}
+{Kova{\v c}}, K., {Lilly}, S.~J., {Cucciati}, O., {et~al.} 2010, \apj, 708, 505
+
+\bibitem[{{Kova{\v c}} {et~al.}(2014){Kova{\v c}}, {Lilly}, {Knobel},
+  {Bschorr}, {Peng}, {Carollo}, {Contini}, {Kneib}, {Le F{\'e}vre}, {Mainieri},
+  {Renzini}, {Scodeggio}, {Zamorani}, {Bardelli}, {Bolzonella}, {Bongiorno},
+  {Caputi}, {Cucciati}, {de la Torre}, {de Ravel}, {Franzetti}, {Garilli},
+  {Iovino}, {Kampczyk}, {Lamareille}, {Le Borgne}, {Le Brun}, {Maier},
+  {Mignoli}, {Oesch}, {Pello}, {Montero}, {Presotto}, {Silverman}, {Tanaka},
+  {Tasca}, {Tresse}, {Vergani}, {Zucca}, {Aussel}, {Koekemoer}, {Le Floc'h},
+  {Moresco}, \& {Pozzetti}}]{Kovac:2014aa}
+{Kova{\v c}}, K., {Lilly}, S.~J., {Knobel}, C., {et~al.} 2014, \mnras, 438, 717
+
+\bibitem[{{Larson} {et~al.}(1980){Larson}, {Tinsley}, \&
+  {Caldwell}}]{Larson:1980aa}
+{Larson}, R.~B., {Tinsley}, B.~M., \& {Caldwell}, C.~N. 1980, \apj, 237, 692
+
+\bibitem[{{Lauer} {et~al.}(2007){Lauer}, {Faber}, {Richstone}, {Gebhardt},
+  {Tremaine}, {Postman}, {Dressler}, {Aller}, {Filippenko}, {Green}, {Ho},
+  {Kormendy}, {Magorrian}, \& {Pinkney}}]{Lauer:2007aa}
+{Lauer}, T.~R., {Faber}, S.~M., {Richstone}, D., {et~al.} 2007, \apj, 662, 808
+
+\bibitem[{{Leja} {et~al.}(2013){Leja}, {van Dokkum}, \& {Franx}}]{Leja:2013aa}
+{Leja}, J., {van Dokkum}, P., \& {Franx}, M. 2013, \apj, 766, 33
+
+\bibitem[{{Lilly} {et~al.}(2009){Lilly}, {Le Brun}, {Maier}, {Mainieri},
+  {Mignoli}, {Scodeggio}, {Zamorani}, {Carollo}, {Contini}, {Kneib}, {Le
+  F{\`e}vre}, {Renzini}, {Bardelli}, {Bolzonella}, {Bongiorno}, {Caputi},
+  {Coppa}, {Cucciati}, {de la Torre}, {de Ravel}, {Franzetti}, {Garilli},
+  {Iovino}, {Kampczyk}, {Kovac}, {Knobel}, {Lamareille}, {Le Borgne}, {Pello},
+  {Peng}, {P{\'e}rez-Montero}, {Ricciardelli}, {Silverman}, {Tanaka}, {Tasca},
+  {Tresse}, {Vergani}, {Zucca}, {Ilbert}, {Salvato}, {Oesch}, {Abbas},
+  {Bottini}, {Capak}, {Cappi}, {Cassata}, {Cimatti}, {Elvis}, {Fumana},
+  {Guzzo}, {Hasinger}, {Koekemoer}, {Leauthaud}, {Maccagni}, {Marinoni},
+  {McCracken}, {Memeo}, {Meneux}, {Porciani}, {Pozzetti}, {Sanders},
+  {Scaramella}, {Scarlata}, {Scoville}, {Shopbell}, \&
+  {Taniguchi}}]{Lilly:2009aa}
+{Lilly}, S.~J., {Le Brun}, V., {Maier}, C., {et~al.} 2009, \apjs, 184, 218
+
+\bibitem[{{Magnelli} {et~al.}(2009){Magnelli}, {Elbaz}, {Chary}, {Dickinson},
+  {Le Borgne}, {Frayer}, \& {Willmer}}]{magnelli09a}
+{Magnelli}, B., {Elbaz}, D., {Chary}, R.~R., {et~al.} 2009, \aap, 496, 57
+
+\bibitem[{{Markwardt}(2009)}]{Markwardt:2009aa}
+{Markwardt}, C.~B. 2009, in Astronomical Society of the Pacific Conference
+  Series, Vol. 411, Astronomical Data Analysis Software and Systems XVIII, ed.
+  D.~A. {Bohlender}, D.~{Durand}, \& P.~{Dowler}, 251
+
+\bibitem[{{Martin} {et~al.}(2005){Martin}, {Fanson}, {Schiminovich},
+  {Morrissey}, {Friedman}, {Barlow}, {Conrow}, {Grange}, {Jelinsky},
+  {Milliard}, {Siegmund}, {Bianchi}, {Byun}, {Donas}, {Forster}, {Heckman},
+  {Lee}, {Madore}, {Malina}, {Neff}, {Rich}, {Small}, {Surber}, {Szalay},
+  {Welsh}, \& {Wyder}}]{Martin:2005aa}
+{Martin}, D.~C., {Fanson}, J., {Schiminovich}, D., {et~al.} 2005, \apjl, 619,
+  L1
+
+\bibitem[{{Moore} {et~al.}(1998){Moore}, {Lake}, \& {Katz}}]{Moore:1998aa}
+{Moore}, B., {Lake}, G., \& {Katz}, N. 1998, \apj, 495, 139
+
+\bibitem[{{Morrissey} {et~al.}(2005){Morrissey}, {Schiminovich}, {Barlow},
+  {Martin}, {Blakkolb}, {Conrow}, {Cooke}, {Erickson}, {Fanson}, {Friedman},
+  {Grange}, {Jelinsky}, {Lee}, {Liu}, {Mazer}, {McLean}, {Milliard}, {Randall},
+  {Schmitigal}, {Sen}, {Siegmund}, {Surber}, {Vaughan}, {Viton}, {Welsh},
+  {Bianchi}, {Byun}, {Donas}, {Forster}, {Heckman}, {Lee}, {Madore}, {Malina},
+  {Neff}, {Rich}, {Small}, {Szalay}, \& {Wyder}}]{Morrissey:2005aa}
+{Morrissey}, P., {Schiminovich}, D., {Barlow}, T.~A., {et~al.} 2005, \apjl,
+  619, L7
+
+\bibitem[{{Moustakas} {et~al.}(2013){Moustakas}, {Coil}, {Aird}, {Blanton},
+  {Cool}, {Eisenstein}, {Mendez}, {Wong}, {Zhu}, \&
+  {Arnouts}}]{Moustakas:2013aa}
+{Moustakas}, J., {Coil}, A.~L., {Aird}, J., {et~al.} 2013, \apj, 767, 50
+
+\bibitem[{{Muldrew} {et~al.}(2012){Muldrew}, {Croton}, {Skibba}, {Pearce},
+  {Ann}, {Baldry}, {Brough}, {Choi}, {Conselice}, {Cowan}, {Gallazzi}, {Gray},
+  {Gr{\"u}tzbauch}, {Li}, {Park}, {Pilipenko}, {Podgorzec}, {Robotham},
+  {Wilman}, {Yang}, {Zhang}, \& {Zibetti}}]{Muldrew:2012aa}
+{Muldrew}, S.~I., {Croton}, D.~J., {Skibba}, R.~A., {et~al.} 2012, \mnras, 419,
+  2670
+
+\bibitem[{{Noeske} {et~al.}(2007){Noeske}, {Weiner}, {Faber}, {Papovich},
+  {Koo}, {Somerville}, {Bundy}, {Conselice}, {Newman}, {Schiminovich}, {Le
+  Floc'h}, {Coil}, {Rieke}, {Lotz}, {Primack}, {Barmby}, {Cooper}, {Davis},
+  {Ellis}, {Fazio}, {Guhathakurta}, {Huang}, {Kassin}, {Martin}, {Phillips},
+  {Rich}, {Small}, {Willmer}, \& {Wilson}}]{Noeske:2007aa}
+{Noeske}, K.~G., {Weiner}, B.~J., {Faber}, S.~M., {et~al.} 2007, \apjl, 660,
+  L43
+
+\bibitem[{Norberg {et~al.}(2002)}]{norberg02a}
+Norberg, P., {et~al.} 2002, \mnras, 332, 827
+
+\bibitem[{Oemler(1974)}]{oemler74a}
+Oemler, A. 1974, \apj, 194, 1
+
+\bibitem[{{Peng} {et~al.}(2010){Peng}, {Lilly}, {Kova{\v c}}, {Bolzonella},
+  {Pozzetti}, {Renzini}, {Zamorani}, {Ilbert}, {Knobel}, {Iovino}, {Maier},
+  {Cucciati}, {Tasca}, {Carollo}, {Silverman}, {Kampczyk}, {de Ravel},
+  {Sanders}, {Scoville}, {Contini}, {Mainieri}, {Scodeggio}, {Kneib}, {Le
+  F{\`e}vre}, {Bardelli}, {Bongiorno}, {Caputi}, {Coppa}, {de la Torre},
+  {Franzetti}, {Garilli}, {Lamareille}, {Le Borgne}, {Le Brun}, {Mignoli},
+  {Perez Montero}, {Pello}, {Ricciardelli}, {Tanaka}, {Tresse}, {Vergani},
+  {Welikala}, {Zucca}, {Oesch}, {Abbas}, {Barnes}, {Bordoloi}, {Bottini},
+  {Cappi}, {Cassata}, {Cimatti}, {Fumana}, {Hasinger}, {Koekemoer},
+  {Leauthaud}, {Maccagni}, {Marinoni}, {McCracken}, {Memeo}, {Meneux}, {Nair},
+  {Porciani}, {Presotto}, \& {Scaramella}}]{Peng:2010aa}
+{Peng}, Y.-j., {Lilly}, S.~J., {Kova{\v c}}, K., {et~al.} 2010, \apj, 721, 193
+
+\bibitem[{{Pozzetti} {et~al.}(2010){Pozzetti}, {Bolzonella}, {Zucca},
+  {Zamorani}, {Lilly}, {Renzini}, {Moresco}, {Mignoli}, {Cassata}, {Tasca},
+  {Lamareille}, {Maier}, {Meneux}, {Halliday}, {Oesch}, {Vergani}, {Caputi},
+  {Kova{\v c}}, {Cimatti}, {Cucciati}, {Iovino}, {Peng}, {Carollo}, {Contini},
+  {Kneib}, {Le F{\'e}vre}, {Mainieri}, {Scodeggio}, {Bardelli}, {Bongiorno},
+  {Coppa}, {de la Torre}, {de Ravel}, {Franzetti}, {Garilli}, {Kampczyk},
+  {Knobel}, {Le Borgne}, {Le Brun}, {Pell{\`o}}, {Perez Montero},
+  {Ricciardelli}, {Silverman}, {Tanaka}, {Tresse}, {Abbas}, {Bottini}, {Cappi},
+  {Guzzo}, {Koekemoer}, {Leauthaud}, {Maccagni}, {Marinoni}, {McCracken},
+  {Memeo}, {Porciani}, {Scaramella}, {Scarlata}, \&
+  {Scoville}}]{Pozzetti:2010aa}
+{Pozzetti}, L., {Bolzonella}, M., {Zucca}, E., {et~al.} 2010, \aap, 523, A13
+
+\bibitem[{{Salim} {et~al.}(2007){Salim}, {Rich}, {Charlot}, {Brinchmann},
+  {Johnson}, {Schiminovich}, {Seibert}, {Mallery}, {Heckman}, {Forster},
+  {Friedman}, {Martin}, {Morrissey}, {Neff}, {Small}, {Wyder}, {Bianchi},
+  {Donas}, {Lee}, {Madore}, {Milliard}, {Szalay}, {Welsh}, \&
+  {Yi}}]{Salim:2007aa}
+{Salim}, S., {Rich}, R.~M., {Charlot}, S., {et~al.} 2007, \apjs, 173, 267
+
+\bibitem[{{Scodeggio} {et~al.}(2009){Scodeggio}, {Vergani}, {Cucciati},
+  {Iovino}, {Franzetti}, {Garilli}, {Lamareille}, {Bolzonella}, {Pozzetti},
+  {Abbas}, {Marinoni}, {Contini}, {Bottini}, {Le Brun}, {Le F{\`e}vre},
+  {Maccagni}, {Scaramella}, {Tresse}, {Vettolani}, {Zanichelli}, {Adami},
+  {Arnouts}, {Bardelli}, {Cappi}, {Charlot}, {Ciliegi}, {Foucaud}, {Gavignaud},
+  {Guzzo}, {Ilbert}, {McCracken}, {Marano}, {Mazure}, {Meneux}, {Merighi},
+  {Paltani}, {Pell{\`o}}, {Pollo}, {Radovich}, {Zamorani}, {Zucca}, {Bondi},
+  {Bongiorno}, {Brinchmann}, {de La Torre}, {de Ravel}, {Gregorini}, {Memeo},
+  {Perez-Montero}, {Mellier}, {Temporin}, \& {Walcher}}]{Scodeggio:2009aa}
+{Scodeggio}, M., {Vergani}, D., {Cucciati}, O., {et~al.} 2009, \aap, 501, 21
+
+\bibitem[{{Skibba} {et~al.}(2013){Skibba}, {Sheth}, {Croton}, {Muldrew},
+  {Abbas}, {Pearce}, \& {Shattow}}]{Skibba:2013aa}
+{Skibba}, R.~A., {Sheth}, R.~K., {Croton}, D.~J., {et~al.} 2013, \mnras, 429,
+  458
+
+\bibitem[{{Smith} {et~al.}(2005){Smith}, {Treu}, {Ellis}, {Moran}, \&
+  {Dressler}}]{Smith:2005aa}
+{Smith}, G.~P., {Treu}, T., {Ellis}, R.~S., {Moran}, S.~M., \& {Dressler}, A.
+  2005, \apj, 620, 78
+
+\bibitem[{{Swanson} {et~al.}(2008){Swanson}, {Tegmark}, {Hamilton}, \&
+  {Hill}}]{Swanson:2008aa}
+{Swanson}, M.~E.~C., {Tegmark}, M., {Hamilton}, A.~J.~S., \& {Hill}, J.~C.
+  2008, \mnras, 387, 1391
+
+\bibitem[{{Taylor} {et~al.}(2009){Taylor}, {Franx}, {van Dokkum}, {Bell},
+  {Brammer}, {Rudnick}, {Wuyts}, {Gawiser}, {Lira}, {Urry}, \&
+  {Rix}}]{taylor09a}
+{Taylor}, E.~N., {Franx}, M., {van Dokkum}, P.~G., {et~al.} 2009, \apj, 694,
+  1171
+
+\bibitem[{{Tinker} {et~al.}(2011){Tinker}, {Wetzel}, \&
+  {Conroy}}]{Tinker:2011aa}
+{Tinker}, J., {Wetzel}, A., \& {Conroy}, C. 2011, ArXiv e-prints,
+  arXiv:1107.5046
+
+\bibitem[{{Weinmann} {et~al.}(2006){Weinmann}, {van den Bosch}, {Yang}, {Mo},
+  {Croton}, \& {Moore}}]{Weinmann:2006aa}
+{Weinmann}, S.~M., {van den Bosch}, F.~C., {Yang}, X., {et~al.} 2006, \mnras,
+  372, 1161
+
+\bibitem[{{West}(2005)}]{West:2005aa}
+{West}, A.~A. 2005, PhD thesis, University of Washington, Washington, USA
+
+\bibitem[{{West} {et~al.}(2010){West}, {Garcia-Appadoo}, {Dalcanton}, {Disney},
+  {Rockosi}, {Ivezi{\'c}}, {Bentz}, \& {Brinkmann}}]{West:2010aa}
+{West}, A.~A., {Garcia-Appadoo}, D.~A., {Dalcanton}, J.~J., {et~al.} 2010,
+  \apj, 139, 315
+
+\bibitem[{{Williams} {et~al.}(2009){Williams}, {Quadri}, {Franx}, {van Dokkum},
+  \& {Labb{\'e}}}]{Williams:2009aa}
+{Williams}, R.~J., {Quadri}, R.~F., {Franx}, M., {van Dokkum}, P., \&
+  {Labb{\'e}}, I. 2009, \apj, 691, 1879
+
+\bibitem[{{Wilman} {et~al.}(2010){Wilman}, {Zibetti}, \&
+  {Budav{\'a}ri}}]{Wilman:2010aa}
+{Wilman}, D.~J., {Zibetti}, S., \& {Budav{\'a}ri}, T. 2010, \mnras, 406, 1701
+
+\bibitem[{{York} {et~al.}(2000){York}, {Adelman}, {Anderson}, {Anderson},
+  {Annis}, {Bahcall}, {Bakken}, {Barkhouser}, {Bastian}, {Berman}, {Boroski},
+  {Bracker}, {Briegel}, {Briggs}, {Brinkmann}, {Brunner}, {Burles}, {Carey},
+  {Carr}, {Castander}, {Chen}, {Colestock}, {Connolly}, {Crocker}, {Csabai},
+  {Czarapata}, {Davis}, {Doi}, {Dombeck}, {Eisenstein}, {Ellman}, {Elms},
+  {Evans}, {Fan}, {Federwitz}, {Fiscelli}, {Friedman}, {Frieman}, {Fukugita},
+  {Gillespie}, {Gunn}, {Gurbani}, {de Haas}, {Haldeman}, {Harris}, {Hayes},
+  {Heckman}, {Hennessy}, {Hindsley}, {Holm}, {Holmgren}, {Huang}, {Hull},
+  {Husby}, {Ichikawa}, {Ichikawa}, {Ivezi{\'c}}, {Kent}, {Kim}, {Kinney},
+  {Klaene}, {Kleinman}, {Kleinman}, {Knapp}, {Korienek}, {Kron}, {Kunszt},
+  {Lamb}, {Lee}, {Leger}, {Limmongkol}, {Lindenmeyer}, {Long}, {Loomis},
+  {Loveday}, {Lucinio}, {Lupton}, {MacKinnon}, {Mannery}, {Mantsch}, {Margon},
+  {McGehee}, {McKay}, {Meiksin}, {Merelli}, {Monet}, {Munn}, {Narayanan},
+  {Nash}, {Neilsen}, {Neswold}, {Newberg}, {Nichol}, {Nicinski}, {Nonino},
+  {Okada}, {Okamura}, {Ostriker}, {Owen}, {Pauls}, {Peoples}, {Peterson},
+  {Petravick}, {Pier}, {Pope}, {Pordes}, {Prosapio}, {Rechenmacher}, {Quinn},
+  {Richards}, {Richmond}, {Rivetta}, {Rockosi}, {Ruthmansdorfer}, {Sandford},
+  {Schlegel}, {Schneider}, {Sekiguchi}, {Sergey}, {Shimasaku}, {Siegmund},
+  {Smee}, {Smith}, {Snedden}, {Stone}, {Stoughton}, {Strauss}, {Stubbs},
+  {SubbaRao}, {Szalay}, {Szapudi}, {Szokoly}, {Thakar}, {Tremonti}, {Tucker},
+  {Uomoto}, {Vanden Berk}, {Vogeley}, {Waddell}, {Wang}, {Watanabe},
+  {Weinberg}, {Yanny}, {Yasuda}, \& {SDSS Collaboration}}]{York:2000aa}
+{York}, D.~G., {Adelman}, J., {Anderson}, Jr., J.~E., {et~al.} 2000, \aj, 120,
+  1579
+
+\bibitem[{Zehavi {et~al.}(2002)}]{zehavi02a}
+Zehavi, I., {et~al.} 2002, \apj, 571, 172
+
+\end{thebibliography}
+
 \end{document}

### 2015-03-20 qfenv_paper/ApJ submission/referee_response.txt
referee responses almost done

Dear Editor,

We thank the referee for the thorough review of our work and for the constructive report that improved the quality of the paper.

Please find below responses to the referee’s comments for the submission along with a number of changes made to our paper.

Thank you, 
ChangHoon Hahn

-
ChangHoon Hahn
Center for Cosmology and Particle Physics
New York University 
4 Washington Place 
New York, NY 10003
chh327@nyu.edu

================================================================================
        February 2, 2015

        Mr. ChangHoon Hahn
        Center for Cosmology and Particle Physics
        New York University
        4 Washington Place
        New York, NY 10003

        Title: PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at z < 0.8

        Dear Mr. Hahn,

        I have received the referee's report on your above submission to The
        Astrophysical Journal, and appended it below. As you will see, the
        referee thinks that your article is interesting and that it will merit
        publication once you have addressed the issues raised in the
        report.

        When you resubmit the manuscript, please include a detailed cover
        letter containing the (mandatory) listing of the changes you've made to
        the text and your responses to the report.

        Click the link below to upload your revised manuscript;         
        http://apj.msubmit.net/cgi-bin/main.plex?el=A6Ew1TL6A3CfGS1J7A9ftdhSCRuGAD5aB2tFkIbuQxBwZ
        Alternatively, you may also log into your account at the EJ Press web
        site, http://apj.msubmit.net. Please use your user's login name:
        chahah. You can then ask for a new password via the Unknown/Forgotten
        Password link if you have forgotten your password.

        Reviewers find it helpful if the changes in the text of the manuscript
        are easily distinguishable from the rest of the text. Therefore we ask
        you to print changes in bold face. The highlighting can be removed
        easily after the review.

        The Astrophysical Journal has adopted a new policy that manuscript
        files become inactive, and are considered to have been withdrawn, six
        months after the most recent referee's report goes to the authors,
        provided a revised version has not been received by that time.

        If you have any questions, feel free to contact me.

        Sincerely,
        Lee Armus
        ApJ Scientific Editor
        California Institute of Technology
        apjla@ipac.caltech.edu
        ---------------------------------------------------------------------- 
        Referee Report 
        Reviewer's Comments:
        Report on 'PRIMUS: Galaxy Environment on the Quiescent Fraction
        Evolution at z < 0.8' by Hahn et al.

        The authors have used the large PRIMUS redshift survey to
        determine the quiescent fraction as a function of environment,
        mass and redshift, with SDSS used for the lowest redshift
        bin. This is topical as it pertains to discussions of how
        galaxies become quiescent - often called quenching. This study is
        new in that it utilizes the largest redshift survey over the
        range 0.2 < z < 0.8. Having said that, the drawback of this
        particular survey is that the cosmological redshift uncertainties
        are significantly larger than one would expect from peculiar
        velocities because of the low-dispersion spectra used. This
        increases the noise and systematic uncertainties in quantifying
        environments. Overall the paper is sufficiently clear and
        original to warrant publication. I would recommend some further
        investigation into the environment measures and whether this
        might introduce some systematic trends, as well as some minor
        changes.

        Major comments:

        The environmental measures make use of long cylinders, with the
        length along the redshift direction. The height is noted as being
        35 Mpc. This may actually be +-35 Mpc. At z=0.7, an average
        redshift uncertainty of 0.005*(1+0.7) corresponds to 25 Mpc. The
        half height of the cylinder then corresponds to 1.4 sigma (or
        only 0.7 sigma if the cylinder is +- 17.5 Mpc). The authors
        should investigate whether the uncertainties of the PRIMUS
        redshifts vary as a function of redshift, and whether the
        uncertainties depend on galaxy type (star forming or
        quiescent). This potentially affects the quiescent fraction as a
        function of environment as certain types of galaxies might be
        more likely to be scattered out of higher density environments.

RESPONSE: 
The height represents the full height of the cylindrical aperture (+/— 17.5
Mpc). We select the dimensions to minimize aperture height while accounting for
the redshift uncertainties, especially at our sample's highest redshift bin z~0.7.

Cool et al. 2013 specifically compare redshift accuracy and success rate of
PRIMUS galaxies to high resolution spectroscopic redshifts from COSMOS, DEEP2,
and VVDS. They do not note any significant redshift dependence or dependence
with observed-frame color. We now explicitly refer to Cool et al. (2010) in
Section 2.1.

In addition, Moustakas et al. 2013 emphasize in their Section 3.1 after
extensive comparison to high resolution spectroscopic redshift that the
redshift success in PRIMUS is not a strong function of galaxy type. Also, when
we compare a subsample of the data used in our analysis to high resolution
spectroscopic redshifts we find no significant dependence on galaxy type or
redshift (no significant variations in the dispersion of delta z/(1+z) or the
outlier rate between quiescent and star-forming populations).

        Even though the lowest masses are generally not discussed in the
        paper, there is a concern that the galaxies at 10^9.5 and 10^10
        solar masses show little dependence on environment in the PRIMUS
        sample, especially over redshifts 0.2-0.4. Other authors have
        shown that the environmental dependence is getting larger below
        10^10.5. The SDSS data cutoff at 10^10.4 in Figure 4. The authors
        could look at a 0.02 to 0.05 redshift sample to test whether the
        SDSS trend continues and shows quite a different trend to the
        PRIMUS 0.2-0.4 sample as suggested by the high-density
        environment data presented in Figure 4. One would not expect a
        big change in behaviour between z=0 and z=0.3, and one
        explanation for the difference could be the redshift
        uncertainties in PRIMUS and how they depend on galaxy
        type. Noting that the SDSS uncertainties that have been
        artificially included are 0.005 in 1+z with a Gaussian
        distribution, which is unlikely to have exactly the same form as
        the PRIMUS redshift uncertainties.

RESPONSE: 
We added a discussion on the lack of environment dependence in the quiescent
fraction at z ~ 0.3 for M* < 10^10 solar masses near the end of Section 4.1.

Although we observe little environment dependence at these redshifts and mass
range, we note that the uncertainties calculated from our jack-knife technique
underestimate the total uncertainty contribution from cosmic variance.

At these M* < 10^10 solar masses, only three out of the five targeted PRIMUS
Fields (XMM-SXDS, XMM-CFHTLS, and COSMOS) contribute galaxies, with XMM-SXDS
and XMM-CFHTLS being spatially adjacent. A rough estimate of the cosmic
variances for these three fields using the expressions derived in Driver et al.
(2010) put cosmic variance uncertainties > 60%. This estimate does not take
into account the unique geometry of the PRIMUS fields or the edge-cuts we
impose, which only increase the cosmic variance uncertainties. Therefore, the
quiescent fraction comparison at z ~ 0.3 for M* < 10^10 solar masses cannot be
accurately made using our PRIMUS sample.

A comparison to the low mass SDSS quiescent fraction is currently made
difficult by the mass-to-light ratio and the bright and faint limits of the
SDSS data. Future investigation, which will correct for the photometric biases
of the SDSS data will also extend the low mass limit of the quiescent fraction
analysis using data from the NASA Sloan Atlas Catalog.

        Note on above, I think it is fine for this paper to focus on
        fiducial points of 10^10.5 and 10^11 solar masses, it is just
        that looking to lower masses may indicate a problem with the
        methodology.

        Minor comments:

        Last sentence of abstract: 'However' is the wrong joining term; 'In
        other words' would be more appropriate.

‘However’ has been corrected to ‘In other words’.

        Section 2.1: How does iSEDFIT deal with dust obscuration? How
        successful might it be? A couple or more sentences on this would be
        useful.

We now explicitly mention that the time-dependent dust attention curve of
Charlot & Fall (2000) is used by iSEDfit to deal with dust obscurations in
Section 2.1. We also now explicitly refer reads to Moustakas et al. (2013) for
further details on the effects of prior parameter choices on the extracted
physical properties of galaxies.

        Section 2.3: GALEX does not provide redshifts. When referring to
        redshifts, they should not be called SDSS-GALEX redshifts. It is only
        an SDSS-GALEX sample.

We now correctly specify that the redshifts from the SDSS-GALEX sample are SDSS
redshifts in Section 2.4.

        Section 2.5: State whether 35 Mpc is half height or full height of
        cylinder. I presume these are comoving Mpc, state this.

We now specifically state that H_ap is the full height of the cylinder and that
the aperture dimensions are comoving distances in Section 2.5.

        There is perhaps surprisingly no evolution in M_{r,lim}. Has there been
        an evolution correction applied for M_r?

No, we do not apply any evolution correction to the absolute magnitude values.

        N_{env}. Can this have a value between 0 and 1? I would have thought
        all the weights would be >=1. Therefore better to state the low-density
        environment as n_{env} = 0.

No, n_{env} cannot have a value between 0 and 1. We have corrected the
low-density environment cut-off to n_{env} = 0 throughout the text and in all
the figures.

        Section 2.6: Why does this need to use random points? Why not a finely
        spaced regular grid in RA and DEC?

We use random points due to the convenience of the ransack commands, which
generates random points given a survey geometry. We believe that the referee's
suggestion of a finely spaced regulard grid would not make a significant
difference in accounting for the edge effects.

        End of page 9: missing text after $\sim0.3$ to $\sim0.7$ [for high density].

Corrected.

        Page 12 and elsewhere: The caveat that PRIMUS has more galaxies, and
        therefore better statistics than zCOSMOS is that the environmental
        measures are possibly significantly less reliable because of redshift
        uncertainties. I think this should be pointed out a couple of more
        times than is done currently within the text. There is also the issue
        of overall redshift completeness (targeting and redshift success
        combined), how does PRIMUS compare with zCOSMOS in this regard?

We now explicitly state, in Section 4.3, that our galaxy environment measures
are susceptible to contamination due to PRIMUS redshift uncertainties. We also
emphasize the role of the redshift uncertainties in motivating the more
stringent high density environment classifications in Section 4.2.

As suggested by referee, we also discuss the overall redshift completeness
of PRIMUS versus zCOSMOS in Section 4.3.

        Section 5, item 3: Note the mass range over which the results are valid.

We now explicitly state that the mass range (10^10.5-10^11.0 M_sun) where the
results are valid.

------------------------------------------------------------------------------------
OTHER CHANGES:

- Title has been changed to “Effects of Galaxy Environment on the Quiescent
  Fraction Evolution at z < 0.8”

- Typo in Section 2.1 of one of the PRIMUS fields has been corrected.

### 2015-03-20 qfenv_paper/ApJ submission/qf_environment.tex
referee responses almost done

@@
 
-\title{PRIMUS: Effects of Galaxy Environment on the Quiescent Fraction Evolution at \lowercase{\textit{z}}$<0.8$}
+\title{PRIMUS: {\bf Effects of} Galaxy Environment on the Quiescent Fraction Evolution at \lowercase{\textit{z}}$<0.8$}
 \author{
@@
 Four of these fields are a part of the {\em Spitzer} Wide-area Infrared Extragalactic Survey (SWIRE\footnote{http://swire.ipac.caltech.edu/swire/swire.html}): the European Large Area ISO Survey - South $1$ field (ELAIS-S1\footnote{http://dipastro.pd.astro.it/esis}), the Chandra Deep Field South SWIRE field (CDFS), and the XMM Large Scale Structure Survey field (XMM-LSS).
-The XMM-LSS consists of two separate but spatially adjacent fields: the Subaru/XMM-Newton DEEP Survey field (XMM-SXDS\footnote{http://www.naoj.org/cience/SubaruProject/SDS}) and the Canadian-France-Hawaii Telescope Legacy Survey field (XMM-CFHTLS\footnote{http://www.cfht.hawaii.edu/Science/CFHLS}).
+The XMM-LSS consists of two separate but spatially adjacent fields: the Subaru/XMM-Newton DEEP Survey field ({\bf XMM-SXDS}\footnote{http://www.naoj.org/cience/SubaruProject/SDS}) and the Canadian-France-Hawaii Telescope Legacy Survey field (XMM-CFHTLS\footnote{http://www.cfht.hawaii.edu/Science/CFHLS}).
 Our fifth and final field is the Cosmic Evolution Survey (COSMOS\footnote{http://cosmos.astro.caltech.edu}) field.
@@
 The model SEDs are generated using Flexible Stellar Population Synthesis (FSPS) models (\citealt{Conroy:2010aa}) based on the \cite{Chabrier:2003aa} IMF, along with {\bf a time dependent dust attenuation curve of \cite{Charlot:2000aa} and }other prior parameters discussed in Section 4.1 and Appendix A of \cite{Moustakas:2013aa}.
+{\bf For details on the effects of prior parameter choices of iSEDfit on physical properties of galaxies we refer readers to the Appendix of \cite{Moustakas:2013aa}}.
 For the observed photometry, we use the {\em GALEX} FUV and NUV, the two shortest IRAC bands at $3.6$ and $4.5 \mu \mathrm{m}$ (the two longer-wavelength IRAC channels are excluded because \texttt{iSEDfit} does not model hot dust or polycyclic aromatic hydrocarbons emission lines), and the optical bands.
@@
 
-Because our fixed aperture definition of environment is susceptible to
-contamination due to PRIMUS redshift errors, we consider in Figure
+{\bf However, the uncertainties in the PRIMUS redshifts may contaminate 
+our fixed aperture measurements of galaxy environment. Consequently,} we consider in Figure
 \ref{fig:qffit_comp} more stringent high density environment
@@
 
-While the zCOSMOS survey provides more precise spectroscopic redshifts than PRIMUS, our sample provides significantly larger statistics.
+{\bf We note that due to the redshift uncertainties in PRIMUS, our galaxy environment measures to more susceptible to contamination.
+Furthermore, as discussed in \cite{Coil:2011aa} and \cite{Cool:2013aa}, PRIMUS has a targeting fraction of $\sim 80 \%$ and redshift success rate of $> 75 \%$.
+zCOSMOS, in comparison, has $88 \%$ redshift completeness for the entire sample and $95 \%$ complete within the redshift range $0.5 < z < 0.8$ (\citealt{Lilly:2009aa}).}While the zCOSMOS survey provides more precise spectroscopic redshifts than PRIMUS, our sample provides significantly larger statistics.
 In addition, our sample covers a larger portion of the sky.
@@
 
+\bibitem[{{Charlot} \& {Fall}(2000)}]{Charlot:2000aa}
+{Charlot}, S. and {Fall}, S.~M. 2000, \apj, 539, 718
+
 \bibitem[{{Coil} {et~al.}(2011){Coil}, {Blanton}, {Burles}, {Cool},

### 2015-03-23 qfenv_paper/ApJ submission/qf_environment.tex
Edits of referee response

@@
 spectrograph on the Magellan I Baade $6.5$-m telescope with a slitmask and low dispersion prism.
-For details on the PRIMUS observation methods such as survey design, targeting, and data summary, {\bf we refer readers to the \cite{Coil:2011aa}.
+For details on the PRIMUS observation methods such as survey design, targeting, and data summary, {\bf we refer readers to \cite{Coil:2011aa}.
 For details on redshift fitting, redshift precision and survey completeness we refer readers to \cite{Cool:2013aa}.}
@@
 \citealt{Baldry:2006aa, Cucciati:2010aa}) find, at these redshifts and mass range, a greater environment dependence in $f_\mathrm{Q}$.
-However we note that, at $\mathcal{M}_* < 10^{10} \mathcal{M}_{\odot}$ at $z \sim 0.3$, only three of the five PRIMUS fields used in our analysis (XMM-SXDS, XMM-CFHTLS, and COSMOS; see Section \ref{sec:primus}) contribute galaxies to our sample.
-As a result our jack-knife uncertainties, which are calculated by excluding one PRIMUS field at a time, underestimate the uncertainty from cosmic variance especially since the PRIMUS fields XMM-SXDS and XMM-CFHTLS are adjacent fields.
+However we note for $\mathcal{M}_* < 10^{10} \mathcal{M}_{\odot}$ at $z \sim 0.3$, only three of the five PRIMUS fields used in our analysis (XMM-SXDS, XMM-CFHTLS, and COSMOS; see Section \ref{sec:primus}) contribute galaxies to our sample.
+As a result our jack-knife uncertainties, which are calculated by excluding one PRIMUS field at a time, underestimate the uncertainty from cosmic variance especially since the XMM-SXDS and XMM-CFHTLS PRIMUS fields are adjacent to one another.
 A rough estimate of the cosmic variances using the expressions derived in \cite{Driver:2010aa} put cosmic variance uncertainties $> 60 \%$.
@@
 
-{\bf We note that due to the redshift uncertainties in PRIMUS, our galaxy environment measures to more susceptible to contamination.
+{\bf Due to the redshift uncertainties in PRIMUS, our galaxy environment measures are more susceptible to contamination.
 Furthermore, as discussed in \cite{Coil:2011aa} and \cite{Cool:2013aa}, PRIMUS has a targeting fraction of $\sim 80 \%$ and redshift success rate of $> 75 \%$.
@@
     is greater than $f_{\mathrm{Q}}$ in low density environments
-    for $\mathcal{M} \sim 10^{10.5} -10^{11} \mathcal{M}_\odot$ and out to redshift $z\sim 0.7$. This result
+    {\bf for $\mathcal{M} \sim 10^{10.5} -10^{11} \mathcal{M}_\odot$ and out to redshift $z\sim 0.7$}. This result
     reflects the well known trend that galaxies in high density

### 2015-03-24 qfenv_paper/ApJ submission/referee_response.txt
Edits of referee response
Added fc_paper draft

@@
 Charlot & Fall (2000) is used by iSEDfit to deal with dust obscurations in
-Section 2.1. We also now explicitly refer reads to Moustakas et al. (2013) for
+Section 2.1. We also now explicitly refer readers to Moustakas et al. (2013) for
 further details on the effects of prior parameter choices on the extracted
@@
 generates random points given a survey geometry. We believe that the referee's
-suggestion of a finely spaced regulard grid would not make a significant
+suggestion of a finely spaced regular grid would not make a significant
 difference in accounting for the edge effects.
@@
 
-As suggested by referee, we also discuss the overall redshift completeness
+As suggested by the referee, we also discuss the overall redshift completeness
 of PRIMUS versus zCOSMOS in Section 4.3.

### 2015-03-24 fc_paper/fc_paper.tex
Added fc_paper draft

\documentclass{emulateapj}
\bibliographystyle{apj}

%define general packages
\usepackage{epsfig}
\usepackage{rotating}
\usepackage{amsmath}
\usepackage{footnote}
\usepackage{setspace}
\usepackage{courier}

\begin{document}

\title{Fiber Collision Correction Method for BOSS Power Spectrum}

\author{ChangHoon~Hahn\altaffilmark{1}, 
Michael R.~Blanton\altaffilmark{1}, 
Roman~Scoccimarro\altaffilmark{1}} 
\altaffiltext{1}{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Place, New York, NY 10003; chh327@nyu.edu}

\begin{abstract}
Redshift surveys, including BOSS, use fiber fed spectrographs. A fiber is used for each galaxy in order obtain its redshift. However, due to the physical size of the fibers, if galaxies are located in close proximity to each other on the sky (not necessary along the line-of-sight) two separate fibers cannot be placed adjacently in order to separately extra the spectroscopic information. In such a scenario, the redshift of fiber-collided galaxies are not individually resolved and only a single redshift for them can be calculated. Though this only accounts for $< 5\%$ of the BOSS redshift survey, its effect on the statistical measures such as the powerspectrum and bispectrum is sufficient in small scales to warrant a detailed correction scheme.
\end{abstract}
\keywords{cosmology: observations --- }

\section{Introduction} 
\begin{itemize}
\item fiber-fed multi-object spectroscopic surveys allow us to collect large redshift data, which is why it?s the favorite of cosmology surveys
\item moving from statistics dominated regime to systematics dominated regime
\end{itemize}

Redshift surveys, including BOSS, use fiber fed spectrographs. A fiber is used for each galaxy in order obtain its redshift. However, due to the physical size of the fibers, if galaxies are located in close proximity to each other on the sky (not necessary along the line-of-sight) two separate fibers cannot be placed adjacently in order to separately extra the spectroscopic information. In such a scenario, the redshift of fiber-collided galaxies are not individually resolved and only a single redshift for them can be calculated. Though this only accounts for $< 5\%$ of the BOSS redshift survey, its effect on the statistical measures such as the powerspectrum and bispectrum is sufficient in small scales to warrant a detailed correction scheme.

Fiber-collision corrections such as that proposed by \cite{Guo:2012aa} have been applied to correct for the two point correlation function. Guo et al. (2012) estimates the total contribution of fiber-collided galaxies to the two point correlation function by examining the pair statistics in overlapping tiling regions of the survey. Unfortunately, this method cannot be easily extended for the fourier counter parts to the two-point and three-point correlation functions due to the complex geometry of the overlapping regions. Consequently, we propose a fiber-collision correction method that uses the distribution of the line-of-sight displacement between resolved fiber-collided galaxies and proper accounting of fiber-collisions in the shot-noise correction term of the powerspectrum/bispectrum estimator.

In the following sections, we present our fiber-collision correction results using a series of simulations. Ultimately, we apply our correction to the BOSS data. 
% Include cosmology assumption and out line of paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Fiber-collided Mock Catalogues
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Fiber-collided Mock Catalogues} \label{sec:catalog}
For various purposes such as calculating the covariance matrix or estimating cosmic variance, simulated mock catalogues play a crucial role in measuring clustering statistics of observed galaxy data (\citealt{Scoccimarro:2002aa, Anderson:2012aa, Manera:2013aa}). They also provide a means of understanding systematic effects such as fiber-collisions (CITE CITE). By using mock catalogues, we can test how these effects influence clustering results and devise correction methods that attempt to account for these effects.

A direct way of understanding the effects of fiber-collisions on clustering statistics in observations is to first apply fiber-collisions to mock catalogues then compare the clustering statistics obtained from mock catalogues with and without the fiber collisions. Afterwards, correction methods for fiber-collisions can be applied to the fiber-collided mocks and the merit of the correction method can be quantified by how successfully they can reproduce the clustering statistics of the original mock catalogues without fiber-collisions. The optimal correction method can then be applied to the observed data with some assurance that it accounts for fiber-collisions and improves the clustering measurements.

When applying the fiber-collisions to the mock catalogues, it is essential to apply them in the same manner they affect the observational data. For BOSS, galaxies within $62"$ are fiber-collided (\citealt{Anderson:2012aa}). In reality, this simple criteria is further complicated by the tiling scheme of observing plates that create overlapping regions, which have a higher success rate in resolving galaxy spectra within the fiber-collision angular scale (\citealt{Guo:2012aa}). Furthermore, fiber-collisions are only one of the systematic effects that influence BOSS data. Systematic effects include the unique geometry of the BOSS survey, the variable completeness in different sectors of the survey, and redshift failures (\citealt{Anderson:2012aa}).

\def \cmasscolor{black}
\def \ldgcolor{blue}
\def \qpmcolor{orange}
\def \tmcolor{green}
\begin{figure}
\begin{center}
\includegraphics[scale=0.45]{fcpaper_z_dist.png} \label{fig:zdist}
\caption{Normalized galaxy redshift distribution for Las Damas (\ldgcolor), QPM (\qpmcolor), and Tiling Mock (\tmcolor) mock catalogues. The normalized redshift distribution of BOSS DR12 CMASS is also plotted (\cmasscolor). Bin size of $\Delta z = 0.025$ was used to compute the distributions. Las Damas mock catalogue has a constant number density of galaxies throughout its redshift range ($0.16 < z < 0.44$). QPM and Tiling Mock catalogues, on the other hand, trace the BOSS CMASS redshift distribution ($0.43 < z < 0.7$).}
% perhaps the range should be wider and make it full text width that way the tail can be portrayed better. Keep the same aspect ratio. 
\end{center}
\end{figure}

Effects of fiber-collisions must be understood and interpreted in conjunction with these systematic effects and to ultimately test our fiber-collision correction method we use LasDamas (\citealt{McBride:2009aa}), Quick Particle Mesh (\citealt{White:2014aa}), and Tiling mock catalogues. These mocks have already been used in interpreting observational results for BOSS and are generated through different prescriptions. Therefore they provide complementary tests fiber-collisions and our correction method tailored for BOSS. 
% Include brief detail on what each mock has to offer

Each of these mock catalogues use some sort of N-body dark matter simulation along with a HOD prescription to populate the dark matter halos with ``galaxies". More specifically, the LasDamas Galaxy mock catalogues is constructed from the N-body Large Suite of Dark Matter Simulations (LasDamas). The N-body LasDamas simulations uses a spatially flat $\Lambda$CDM cosmology with $\Omega_\mathrm{m} = 0.25$, $\Omega_\Lambda = 0.75$, $\Omega_\mathrm{b} = 0.04$, $\sigma_8 = 0.8$, $n_\mathrm{s} = 1$ and $h=0.7$. The dark matter halos are then identified using a friends-of-friends (FOF) algorithm (\citealt{Davis:1985aa}) with a linking length $b = 0.2 $ times the mean interparticle separation. The over-densities of dark matter halos are then populated with galaxies using the halo occupation distribution (HOD) framework to construct the galaxy mock catalogues (\citealt{McBride:2009aa}). The HOD prescription is specified so that the galaxy mock catalogues reproduce the correlation function of the SDSS sample. % Detail about the geometry and redshift range 
\begin{itemize}
\item above description is not entirely correct because that was LasDamas for Guo+2011
\item SDSS-II Geometry
\item lower redshift range
\end{itemize}

Next, the QPM mock galaxy catalogues uses a "quick particle mesh" method, which uses a low resolution particle-mesh N-body solver to evolve particles within a period simulation volume. The particles are assigned halo masses  in order to match the halo mass function and large-scale bias of halos of high resolution simulations. Afterward the \cite{Tinker:2012aa} HOD parameterization is used to populate the halos. The mock galaxy sample is then trimmed to the BOSS CMASS survey footprint, downsamped based on angular sky completeness (sector completeness) and radial selection. The QPM mock galaxy catalogue is generated using the following $\Lambda$CDM cosmology: $\Omega_\mathrm{m} = 0.25$, $\Omega_\Lambda = 0.25$, $\Omega_\mathrm{b} = 0.04$, $\sigma_8 = 0.8$, $n_\mathrm{s} = 1$ and $h=0.7$. For a detailed description of the QPM galaxy mock catalogues we refer readers to \cite{White:2014aa}.

Finally the Tiling Mock catalogue is generated using 
\begin{itemize}
\item documentation for tiling mock? 
\end{itemize}

In Figure \ref{fig:zdist}, we plot the redshift distribution for LasDamas, QPM, and Tiling Mock catalogues along with the redshift distribution of BOSS DR12 galaxies. The redshift distributions illustrate the constant $\bar{n}(z)$ for the LasDamas mock catalogue, while the QPM and Tiling mock $\bar{n}(z)$ distributions trace the observed BOSS redshift distribution.

% insert transition that mentions how the main clustering statistics we focus on in this paper is the Power Spectrum
In order to measure the power spectrum for these mock catalogues, we use the standard \cite{Feldman:1994aa} (FKP) estimator. Throughout the paper we use the following formalisms from \cite{Feldman:1994aa}.
\begin{equation} \label{eq:fkppk}
P({\bf k}) = <|F({\bf k})|^2> - \frac{(1+\alpha) \int d^3r \;\bar{n}({\bf r})w_{\mathrm{FKP}}^2({\bf r})} {\int d^3r \; \bar{n}^2({\bf r})w_{\mathrm{FKP}}^2({\bf r})},
\end{equation}  
where
\begin{equation}
F({\bf r}) = \frac{w_\mathrm{FKP}({\bf r}) [n_g({\bf r}) - \alpha n_r({\bf r})]} {[\int d^3r \; \bar{n}^2({\bf r})w_\mathrm{FKP}^2({\bf r})]^{\frac{1}{2}}} 
\end{equation}
and the second term represents the constant shot-noise contribution to the power due to the discrete density field of our galaxies. More specifically, $n_g$ is the galaxy density, $n_r$ is the density of the synthetic random catalogue, $\alpha$ is the ratio of the number of galaxies over the number of synthetic random galaxies, $\bar{n}$ is the mean density of the galaxies, and $w_{\mathrm{FKP}}$ is the minimum variance weight derived in \cite{Feldman:1994aa}: 
\begin{equation}
w_{\mathrm{FKP}} ({\bf r}) = \frac{1}{1+\bar{n}({\bf r}) P_0}
\end{equation}
where $P_0$ is the power spectrum amplitude at which the error is minimized. We use $P_0 = 20000\; \mathrm{Mpc}^3/h^3$ for our analysis, which corresponds to $k \sim 0.1\; h/\mathrm{Mpc}$.

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{fcpaper_pk_comp.png} 
\caption{Average power spectrum $\overline{P(k)}$ for BOSS DR12 (black) and the mock catalogues Las Damas (blue), QPM (orange), and Tiling Mock (green), listed in Section \ref{sec:catalog} using the FKP $P(k)$ estimator. The width of the $P(k)$ for Las Damas and QPM represent the sample variance ($\Delta P(k)/\overline{P(k)}$) calculated from the multiple mock catalogues. We emphasize that fiber-collisions were not applied to the mock catalogues for the $P(k)$ measurements. Meanwhile, galaxy weights (Equation \ref{eq:weight}) are applied to the BOSS DR12 $P(k)$ measurement. We remind readers that the $\overline{P(k)}$ of the LasDamas mock catalogues is an outlier because of the different redshift range compared to the other mock catalogues.} \label{fig:mockpk}
\end{center}
\end{figure}

For LasDamas, QPM, and Tiling mock catalogues we use the above FKP estimator to measure the power spectrum, Figure \ref{fig:mockpk}. For the $P(k)$ in Figure \ref{fig:mockpk}, we do not apply the fiber-collisions to the catalogues. Therefore, there are no complications from using the exact formulation of Equation \ref{eq:fkppk}. However, when we calculate $P(k)$ for BOSS DR12 data in Figure \ref{fig:mockpk} (\cmasscolor), the systematic weights assigned to the galaxies that account for sector completeness, redshift failures, and fiber-collisions, 
\begin{equation} \label{eq:weight}
w_\mathrm{tot} = w_\mathrm{sys} (w_\mathrm{rf} + w_\mathrm{fc} -1), 
\end{equation}
must be taken account (\citealt{Anderson:2012aa, Beutler:2014aa}). Hence, instead of the galaxy density $n_g({\bf r})$ we use a weighted galaxy density $n'_g({\bf r}) = n_g({\bf r}) w({\bf r})$ and instead of $\alpha = N_{\mathrm{gal}}/N_\mathrm{ran}$ we use $\alpha ' = N'_\mathrm{gal}/N_\mathrm{ran}$ where $N'_\mathrm{gal} = \sum_\mathrm{gal} w_\mathrm{tot}$. For LasDamas and QPM, which have multiple mock catalogues, we compute the sample variance of the power spectrum
\begin{equation} \label{eq:pk_var}
\Delta P (k)= \sqrt{\frac{1}{N_\mathrm{mock}} \sum\limits_i^{N_\mathrm{mock}} (P_i(k)- \overline{P(k)})^2 }. 
\end{equation}
$\Delta P(k)$ is represented by the width of the $P(k)$ in Figure \ref{fig:mockpk}.

\begin{figure*}
\begin{center}
\includegraphics[scale=0.575]{fcpaper_dlos_dist.png}
\caption{Normalized distribution of $d_{\mathrm{LOS}}$ for Las Damas (\ldgcolor), QPM (\qpmcolor), and Tiling Mock (\tmcolor) mock catalogues. The normalized $d_{\mathrm{LOS}}$ distribution of BOSS DR12 is also plotted (\cmasscolor). Bin size of $\Delta d = 0.2$ was used to compute these $d_{\mathrm{LOS}}$ distributions. We focus on the peak of the distribution (discussed in \ref{sec:dlos}).} \label{fig:d_los}
% perhaps the range should be wider and make it full text width that way the tail can be portrayed better. Keep the same aspect ratio. 
\end{center}
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Fiber-collision Correction Method
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Fiber-collision Correction Method} \label{sec:fc_corr}
To account for the systematic effects of fiber-collisions \cite{Anderson:2012aa}, for the BOSS galaxy data, most recently used a nearest-neighbor galaxy weighting scheme. For galaxies without resolved spectroscopic redshifts due to fiber-collisions, the entire statistical weight of the galaxy was assigned to its nearest-neighbor. This method assumes that all galaxies with angular separations $< 62 "$ are correlated. In other words, that galaxies within the fiber-collision angular scale reside in the same group or cluster. Consequently, galaxies that have angular separations $< 62"$ purely by coincidence (hereafter referred to as ``chance alignments") are incorrectly assumed to be gravitationally correlated and displaced significantly from its true position. Even for fiber-collided galaxies that reside in the same group or cluster, upweighting the nearest neighbor ignores halo-scale line-of-sight displacements.

While the nearest-neighbor method provides a reasonable estimate at large scales, in Section \ref{sec:dlos} we demonstrate that at small scales it's effects on the power spectrum are significant and outweigh sample variance. Furthermore, in Section \ref{sec:dlos}, we present an improved method to account for correlated fiber-collided galaxies using the line-of-sight displacement between close galaxy pairs. Then in Section \ref{sec:shotnoise}, we present corrections to the power spectrum estimator that further accounts for fiber-collisions through the shot-noise correction term in the estimator.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% LOS DISPLACEMENT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Line-of-Sight Displacement of Fiber-collided Pairs} \label{sec:dlos}
It is impossible to determine in observed galaxy data whether fiber-collided galaxies without resolved spectroscopic redshift are either correlated or chance alignments. Fortunately, using just the close galaxy pairs with resolved redshifts (especially in the overlapping regions mentioned in Section \ref{sec:catalog}), it is possible to model the fraction of galaxy pairs that are corrected and uncorrelated.

Meanwhile, for simulated mock catalogues, described in Section \ref{sec:catalog}, modeling the fiber-collided galaxy pairs is a trivial task since fiber-collisions are post-processed after the simulated galaxy positions are generated. Hence all redshift values are resolved regardless of angular proximity. With both redshifts of the fiber-collided pair galaxies, we are able to emulate the observed data by assigning nearest neighbor galaxy weights (as done in \citealt{Anderson:2012aa}). So for a close galaxy pair, one galaxy (``the nearest neighbor") will have the statistical weight of both galaxies, while the other has a statistical weight of $0$. Furthermore, having the redshift values of close galaxy pairs in mock catalogues, allows us to model the correlated and uncorrelated fiber-collided pairs.

In order to determine whether or not fiber-collided pairs are correlated, we examine the comoving line-of-sight displacement ($d_{\mathrm{LOS}}$) of fiber-collided galaxy pairs. We calculate the $d_{\mathrm{LOS}}$ by taking the difference of the line-of-sight comoving distance from the resolved redshifts: 
\begin{equation}
d_{\mathrm{LOS}} = D_{\mathrm{C}} (z_1) - D_{\mathrm{C}} (z_2). 
\end{equation}
$D_{\mathrm{C}}(z)$ is the line-of-sight comoving distance at redshift $z$ (\citealt{Hogg:1999aa}). $z_1$ and $z_2$ represent the resolved redshifts of the galaxies in the fiber-collided pair.

After calculating the $d_{\mathrm{LOS}}$ for each of the fiber-collided pairs, in Figure \ref{fig:d_los} we present the distribution of $d_{\mathrm{LOS}}$ for LasDamas (\ldgcolor), QPM (\qpmcolor), Tiling Mock (\tmcolor), and BOSS DR12 (\cmasscolor). All of the $d_{\mathrm{LOS}}$ distributions contain two distinct components: a peak approximately within the range $-10\;\mathrm{Mpc} < d_{\mathrm{LOS}} < 10\;\mathrm{Mpc}$ and a flat component (hereafter "tail" component) that extends to $d_{\mathrm{LOS}}$ that encompasses the survey depth (entire range of the distribution not displayed in Figure \ref{fig:d_los}). We note that for the BOSS data, since we cannot compute the $d_\mathrm{LOS}$ for fiber-collided pairs without resolved spectra, the $d_\mathrm{LOS}$ distribution represents the $d_\mathrm{LOS}$ from close galaxy pairs with resolved spectroscopic redshifts, often from overlapping regions of the BOSS survey.

Galaxies that are in the same groups or clusters, due to their gravitational interactions at halo-scales, are more likely to be in close angular proximity with each other. These galaxies in over-dense regions cause the peak in the $d_{\mathrm{LOS}}$ distribution. While the ``tail" component is composed of galaxy pairs that are arbitrarily in close angular proximity even when they are not correlated.

Focusing on the peak of the distribution, we note that it closely traces an exponential function. Therefore, we fit an exponential of the form, 
\begin{equation} \label{eq:peak} 
p(d_{\mathrm{LOS}}) = A \; e^{-|d_{\mathrm{LOS}}|/\sigma}
\end{equation}
 for a mathematical prescription of the $d_{\mathrm{LOS}}$ distribution peak as a function of the displacement for each of the data catalogues in Figure \ref{fig:d_los}. The best-fit $\sigma$ and $A$ parameters are obtained by fitting Equation \ref{eq:peak} to the $d_{\mathrm{LOS}}$ distribution peaks using MPFIT (\citealt{Markwardt:2009aa}). We list the values of $\sigma$ obtained for the mock catalogues in Table \ref{tab:mpfit}. Both Table \ref{tab:mpfit} and Figure \ref{fig:d_los} illustrate that the $d_{\mathrm{LOS}}$ distributions for the mock catalogues closely trace the distribution of the BOSS DR12, which further goes to support our use of mock catalogues to test our fiber-collision correction method.

 \begin{table} 
 \caption{$d_{\mathrm{LOS}}$ Distribution Best-fit Parameters} \label{tab:mpfit}
 \begin{spacing}{1.5}
 \begin{center}
 \leavevmode
 \begin{tabular}{ccc} \hline \hline
Catalogue &$\sigma$ ($h^{-1}\mathrm{Mpc}$) & $f_{\mathrm{peak}}$\\ \hline
Las Damas 	& 6.85	& 0.71 \\ 
QPM 		& 4.98	& 0.65 \\ 
Tiling Mock 	& 5.38	& 0.57 \\ 
BOSS DR12 	& 7.6		& 0.65 \\ \hline
\end{tabular} \par
\end{center}
\end{spacing}
%    \bigskip 
{\bf Notes}: Best-fit parameter $\sigma$ and peak fraction $f_{\mathrm{peak}}$ for the $d_{\mathrm{LOS}}$ distributions in Figure \ref{fig:d_los}. 
\end{table}

Using the exponential fits to the peak of the $d_{\mathrm{LOS}}$ distribution, we can also estimate the fraction of fiber-collided pairs that are within the peak: 
\begin{equation}
f_{\mathrm{peak}} = \frac{\sum\limits_{\mathrm{peak}} p(d_{\mathrm{LOS}})}{N_{\mathrm{pairs}}}, 
\end{equation}
where $N_{\mathrm{pairs}}$ is the total number of fiber-collided pairs. As mentioned above, this portion of fiber-collided pairs are galaxy pairs that are correlated. We list the $f_{\mathrm{peak}}$ values for each of the data catalogues in Table \ref{tab:mpfit}. The $f_\mathrm{peak}$ values for the mock catalogue are also in good agreement with the BOSS DR12 $f_\mathrm{peak}$.

As stated earlier, the current method of accounting for fiber-collisions uses the nearest-neighbor upweighting scheme (hereafter NN-upweighting). For this method to be completely correct, the $d_{\mathrm{LOS}}$ distribution would have to be a delta function, which as Figure \ref{fig:d_los} demonstrates is not the case. By simply incorporating the peak of the $d_{\mathrm{LOS}}$ distribution, we are able to significantly improve clustering statistics on small scales. Rather than placing the fiber-collided galaxy on top of its nearest neighbor, as NN-upweighting does, placing the fiber-collided galaxy at displacement sampled from the $d_{\mathrm{LOS}}$ distribution, away from the nearest neighbor better accounts for the small scale clustering measurements. On mock catalogues, we test this by first applying the NN upweighting in the same way as it is applied in the BOSS DR12 catalogue to the mock catalogues. We then sample a displacement $d_i$ from $p(d_\mathrm{LOS})$ (Equation \ref{eq:peak}) for each fiber-collided pair. Afterwards we ``place" the fiber-collided galaxy a distance $d_i$ from the upweighted galaxy and reduce the statistical weight of the upweighted galaxy (the nearest-neighbor) by 1. We refer to this method as ``$d_\mathrm{LOS}$-peak.

\begin{figure*}
\begin{center}
\includegraphics[scale=0.55]{fcpaper_pk_peakonly_comp.png} 
\caption{The ratio of $P(k)$ using the nearest-neighbor upweighting (blue) and $d_\mathrm{LOS}$ distribution peak fiber-collision correction (orange) over the true $P(k)$ for LasDamas (left panel), QPM (middle panel), and Tiling Mock (right panel) catalogues. }\label{fig:peakonly}
\end{center}
\end{figure*}

The $d_\mathrm{LOS}$-peak correction method is only part of our correction scheme we present in this paper. Nonetheless, we test it by applying it to the mock catalogues and comparing the resulting power spectrums. For each of the mock catalogues (Las Damas, QPM, and Tiling Mock) we use the FKP power spectrum estimator from before to compute the power spectrums of the original mock data, the mock data with NN-upweighting, and the mock data with the $d_\mathrm{LOS}$-peak correction. We note that both the NN-upweighting and the $d_\mathrm{LOS}$-peak correction methods alter the redshift distribution of our samples by a negligible amount $< 1\%$. Therefore, the synthetic random catalogues and the $\bar{n}(z)$ values do not need to be adjusted in the FKP $P(k)$ calculations.

Since we are interested in how well these fiber-collision considerations can reproduce the power spectrum without fiber collisions (the ``true" power spectrum, unsullied by systematic effects), in Figure \ref{fig:peakonly} we plot the ratio of the average power spectrum $P(k)$ computed from corrected mock catalogues over the average $P(k)$ from the original mock catalogues, $\overline{P_{\mathrm{corr}}(k)}/\overline{P_\mathrm{true}(k)}$. The ratio for the NN upweighting scheme is plotted in blue while the ratio for the $d_{\mathrm{LOS}}$-peak correction scheme is plotted in orange. Also plotted is $\Delta P_\mathrm{true}(k) / \overline{P_\mathrm{true}(k)}$ (black; dashed) in order to compare the ratios to sample variance of the mock catalogues. For all mocks, the $P(k)$ from the NN upweighting scheme is greater than $P_\mathrm{true}(k)$ by $> 10 \%$ at $ k \sim 0.3\; h/\mathrm{Mpc}$. In comparison, $P(k)$ from the $d_\mathrm{LOS}$-peak correction method is $\sim 5\%$ greater than $P_\mathrm{true}(k)$ - a significant improvement.

Comparing the NN-upweighting and the $d_\mathrm{LOS}$-peak methods to the sample variance ($\Delta P_\mathrm{true}(k) / \overline{P_\mathrm{true}(k)}$), reveal that neither of these methods provide a sufficient correction for the fiber-collision at $k > 0.1\; h/\mathrm{Mpc}$. The $P(k)$s obtained from these methods are dominated by systematics on small scales. Furthermore, the $d_\mathrm{LOS}$-peak method only statistically accounts for correlated pairs and does not consider uncorrelated pairs. Using the entire $d_\mathrm{LOS}$ distribution in order to account for uncorrelated pairs results in an overall reduction of $P(k)$ since the method displaces some close pairs that are actually correlated pairs as uncorrelated pairs and the other way around. Therefore, a more robust fiber-collision correction method is required. 
%detailed examination of peak only figure

\begin{figure*}
\begin{center}
\includegraphics[scale=0.55]{fcpaper_pk_shotnoiseonly_comp.png}
\caption{The ratio of $\overline{P_\mathrm{SN}(k)}$ computed using the shot-noise correction term given by Eq. \ref{eq:fkp_shotnoise} (blue), Eq. \ref{eq:my_shotnoise} (green), $P^\mathrm{Beutler}_\mathrm{shot}$ (red), and $P^{\mathrm{Gil-Marin}}_\mathrm{shot}$ (purple) over $\overline{P_\mathrm{true}(k)}$ for LasDamas (left panel), QPM (middle panel), and Tiling Mock (right panel) catalogues with nearest-neighbor fiber-collision weights. Also plotted for comparison, is $\Delta P_\mathrm{true}/P_\mathrm{true}(k)$. For fiber-collisions  $\overline{P_\mathrm{SN}(k)}$ computed using $P^\mathrm{Beutler}_\mathrm{shot}$ only marginally improves the $\overline{P_\mathrm{SN}(k)}$ computed using $P^\mathrm{FKP}_\mathrm{shot}$. Both $\overline{P_\mathrm{SN}(k)}$s significantly overestimates the power spectrum. On the other hand $\overline{P_\mathrm{SN}(k)}$ computed using Eq. \ref{eq:my_shotnoise} significantly underestimates the power spectrum. At $k \sim 0.3\;h/\mathrm{Mpc}$, only $\overline{P_\mathrm{SN}(k)}$ computed using $P^\mathrm{Gil-Marin}_\mathrm{shot}$ reduces the effect of fiber-collisions below sample variance. } \label{fig:shotnoise}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SHOT NOISE CORRECTION 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Shot Noise Correction} \label{sec:shotnoise} 
Both the NN-upweighting and the $d_\mathrm{LOS}$-peak correction schemes do not sufficiently account for the systematic effects of fiber-collisions in the power spectrum. In this section we introduce the other part of our fiber-collision correction method that involve the shot-noise correction term of the power spectrum estimator. 
%Besides illustrating the short comings of the NN-upweighting scheme and also the $d_\mathrm{LOS}$ distribution peak correction scheme, in Section \ref{sec:dlos}, we briefly mentioned that the \cite{Feldman:1994aa} power spectrum estimator was used to compute the power spectrum.  % possibly insert summary of the actual power spectrum estimator calculation

In Section \ref{sec:catalog}, we described the FKP power spectrum estimator used to compute the power spectrums of Figure \ref{fig:mockpk}. In their estimator, to account for the discreteness of the density field, they subtract the shot-noise contribution to the power spectrum (Equation \ref{eq:fkppk}): 
\begin{equation} \label{eq:fkp_shotnoise}
P_\mathrm{shot} = \frac{ (1+\alpha) \int d^3r \;\bar{n}({\bf r})w^2({\bf r})}{\int d^3r \;\bar{n}^2({\bf r})w^2({\bf r})}. 
\end{equation}
In practice, the integrals in Equation \ref{eq:fkp_shotnoise} can be written in terms of discrete sums over the random catalogue. The spacial integral $\int d^3r \; \bar{n}({\bf r}) ...$ can be computed as the discrete sum $\alpha \sum_{\mathrm{ran}}...$. With this conversion,
\begin{equation}
P^\mathrm{FKP}_\mathrm{shot} = \frac{(1+\alpha) \alpha \sum\limits_{\mathrm{random}} w_\mathrm{FKP}^2({\bf r})}{\alpha \sum\limits_{\mathrm{random}}w_\mathrm{FKP}^2({\bf r})}.
\end{equation} 
In the FKP derivation, they do not take systematic weights of galaxies into account.

The spatial integral $\int d^3r \;\bar{n}({\bf r})...$ can also be computed using the mock catalogues rather than the synthetic random catalogues, as $\sum_{\mathrm{gal}} w_g...$ where $w_g$ represents the statistical weight assigned to the galaxies (\citealt{Cole:2005aa, Yamamoto:2006aa, Beutler:2014aa, Gil-Marin:2014aa}). Then the shot-noise component can be expressed as: 
\begin{equation} \label{eq:fkpweight}
P_\mathrm{shot} = \frac{ \sum\limits_{\mathrm{galaxy}} w^2_\mathrm{FKP}w^2_g({\bf r})- \alpha^2 \sum\limits_{\mathrm{random}} w_\mathrm{FKP}^2({\bf r})}{\alpha \sum\limits_{\mathrm{random}}w_\mathrm{FKP}^2({\bf r})}.
\end{equation}
In this form, systematic weights for galaxies can be accounted for in $w_g$ and $\alpha$.

Following the latter formulation, most recently, both \cite{Beutler:2014aa} and \cite{Gil-Marin:2014aa} formulate $P_\mathrm{shot}$ to account for systematic bias in their analysis of BOSS data. However, they treat systematic weights differently in their derivation. Keeping in mind the weights listed in Eq. \ref{eq:weight} for the BOSS data, \cite{Beutler:2014aa} derives
\begin{equation} \label{eq:florian}
P^\mathrm{Beutler}_\mathrm{shot} = \frac{\sum\limits_{\mathrm{galaxy}} w^2_\mathrm{FKP}w_\mathrm{tot}({\bf r})w_\mathrm{sys}({\bf r}) - \alpha'^2 \sum\limits_{\mathrm{random}} w_\mathrm{FKP}^2({\bf r})}{\alpha' \sum\limits_{\mathrm{random}}w_\mathrm{FKP}^2({\bf r})}.
\end{equation}
$\alpha' = \sum_\mathrm{gal} w_\mathrm{tot} / N_\mathrm{ran}$.

On the other hand, \cite{Gil-Marin:2014aa}, in a formulation designed to account for fiber-collisions derives $P_\mathrm{shot}$ using two separate components: one for correlated pairs and the other chance alignments. For the shot-noise contribution to the power from correlated pairs (referred to as ``true pairs" in \citealt{Gil-Marin:2014aa}) is equivalent to $P^\mathrm{Beu2tler}_\mathrm{shot}$ in \cite{Beutler:2014aa}. For chance alignments (referred to as ``false pairs" in \citealt{Gil-Marin:2014aa}), the shot-noise contribution is derived as, 
\begin{equation}
P^\mathrm{False}_\mathrm{shot} = \frac{\sum\limits_{\mathrm{galaxy}} w^2_\mathrm{FKP}w^2_\mathrm{tot}({\bf r}) - \alpha'^2 \sum\limits_{\mathrm{random}} w_\mathrm{FKP}^2({\bf r})}{\alpha' \sum\limits_{\mathrm{random}}w_\mathrm{FKP}^2({\bf r})}.
\end{equation}
Then the total $P_\mathrm{shot}$ is calculated as a combination of $P^\mathrm{True}_\mathrm{shot}$ and $P^\mathrm{False}_\mathrm{shot}$: 
\begin{equation}
P^\mathrm{Gil-Marin}_\mathrm{shot} = (1- x_\mathrm{PS}) P^{True}_\mathrm{shot} + x_\mathrm{PS} P^{False}_\mathrm{shot}
\end{equation}
For the BOSS $P(k)$ \cite{Gil-Marin:2014aa} quotes $x_\mathrm{PS} = 0.58$. %motivation for the true/false pairs?

In our $P(k)$ calculations we use the FKP estimator with the shot-noise correction term computed as Eq. \ref{eq:fkpweight} with $w_\mathrm{g} = w_\mathrm{tot}$, which gives us, 
\begin{equation} \label{eq:ourshot}
P^\mathrm{Hahn\;et\;al.}_\mathrm{shot} = \frac{\sum\limits_{\mathrm{galaxy}} w^2_\mathrm{FKP}w^2_\mathrm{tot}({\bf r}) - \alpha'^2 \sum\limits_{\mathrm{random}} w_\mathrm{FKP}^2({\bf r})}{\alpha' \sum\limits_{\mathrm{random}}w_\mathrm{FKP}^2({\bf r})}.
\end{equation}
We note that this equation is equivalent to the shot-noise contribution from ``false pairs" in \cite{Gil-Marin:2014aa}. 
%In \cite{Gil-Marin:2014aa}, they justify the use of the two separate shot-noise terms with the argument that, if the fiber-collided pairs are true pairs it would not modify %insert reason 
%While the $P(k)$ using the \cite{Gil-Marin:2014aa} shot-noise term does in fact correct for fiber-collisions significantly (below), since the parameter is determined in mock catalogues, the value cannot be validated in the actual BOSS data .

In order to compare the different $P_\mathrm{shot}$ derivations, we apply each of them ($P^\mathrm{FKP}_\mathrm{shot}$,$P^\mathrm{Hahn}_\mathrm{shot}$, $P^\mathrm{Beutler}_\mathrm{shot}$, and $P^\mathrm{Gil-Marin}_\mathrm{shot}$) to the mock catalogues with nearest-neighbor fiber-collision weights applied to them. This comparison ignores a number of systematic effects listed in Eq. \ref{eq:weight} ($w_\mathrm{sys}$ and $w_\mathrm{rf}$); however, we are particularly interested in fiber-collisions. So in Equations 9-15, we use $w_\mathrm{sys} = 1$ and $w_\mathrm{tot} = w_\mathrm{fc}$. We compute the $P_\mathrm{SN}(k)$s using the various $P(k)$ estimators with different $P_\mathrm{shot}$ equations for each of the mock catalogues. Afterwards we compute the $\overline{P_\mathrm{SN}(k)}$s for the mock catalogues and take the ratio of them over the average $P_\mathrm{true}(k)$ using the standard FKP $P(k)$ estimator. Without systematic weights, the different $P_\mathrm{shot}$ equations are equivalent, so our choice of the standard FKP $P(k)$ estimator for $\overline{P_\mathrm{true}(k)}$ does not affect the comparison.

In Figure \ref{fig:shotnoise}, we present $\overline{P_\mathrm{SN}(k)}/\overline{P_\mathrm{true}(k)}$ computed using different shot noise correction term equations: $P^\mathrm{FKP}_\mathrm{shot}$,$P^\mathrm{Hahn}_\mathrm{shot}$, $P^\mathrm{Beutler}_\mathrm{shot}$, and $P^\mathrm{Gil-Marin}_\mathrm{shot}$. The $\overline{P(k)}$ of the NN-upweighted mocks using the standard FKP estimator is the same quantity as presented in Figure \ref{fig:peakonly} and as we noted earlier, overestimates the $\overline{P_\mathrm{true}(k)}$. $\overline{P_\mathrm{FKP}(k)}$ is greater than $\overline{P_\mathrm{true}(k)}$ by $> 15 \%$ at $k \sim 0.3\; h/\mathrm{Mpc}$. The $\overline{P(k)}$ measured using $P^\mathrm{Beutler}_\mathrm{shot}$ does not improve this overestimation in any of the mocks. On the other hand, the $\overline{P(k)}$ using just our shot noise equation significantly underestimates the $\overline{P_\mathrm{true}(k)}$. At $k \sim 0.3 \; h/\mathrm{Mpc}$, $\overline{P(k)}/\overline{P_\mathrm{true}(k)} - 1 = \sim -0.03 \%, \sim -0.08 \%, \;\mathrm{and} \sim -0.09$ for LasDamas, QPM, and Tiling Mock respectively. Finally, the $\overline{P(k)}$ measured using $P^\mathrm{Gil-Marin}_\mathrm{shot}$ reproduces $\overline{P_\mathrm{true}(k)}$ most accurately. % Insert some more specifics about Hector's accuracy

As we plotted in Figure \ref{fig:peakonly}, we plot the sample variance ($\Delta P/\bar{P}$) for each of the mock catalogues in Figure \ref{fig:shotnoise}. Only $\overline{P(k)}$ computed using $P^\mathrm{Gil-Marin}_\mathrm{shot}$ is able to reduce the effects of fiber-collisions below the sample variance.

With these alterations to the power spectrum estimator in mind, we present our fiber-collision correction method in the following section .

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% RESULT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results} 
\subsection{Fiber-Collision Correction Method} \label{sec:apply} 
\begin{figure*}
\begin{center}
\includegraphics[scale=0.55]{fcpaper_pk_peakshotnoise_mpfit_comp.png} 
\caption{The ratio of $\overline{P(k)}$ computed using our fiber-collision correction method described in Section \ref{sec:apply} over $\overline{P_\mathrm{true}(k)}$ for LasDamas (left panel), QPM (middle panel), and Tiling Mock (right panel) catalogues with nearest-neighbor fiber-collision weights (red). Also plotted for comparison, is $\Delta P_\mathrm{true}/P_\mathrm{true}(k)$. We note that the $\overline{P(k)}$ ratio for our correction method is significantly lower than the $\Delta P_\mathrm{true}/P_\mathrm{true}(k)$.}\label{fig:peaksn}
\end{center}
\end{figure*}

In Section \ref{sec:dlos} we derive a method to account for fiber-collisions using the peak of the $d_\mathrm{LOS}$ distribution. Then in Section \ref{sec:shotnoise} we compare the various formulations for the shot-noise correction term and presented our formulation. We now utilize both methods to devise our fiber-collision correction method.

We begin with the nearest-neighbor upweighted mock catalogues. With the nearest-neighbor fiber-collision weights, these mock catalogues accurately imitate the effects of fiber-collision on the real BOSS data. Then as described in Section \ref{sec:dlos}, we calculate the $d_\mathrm{LOS}$ distribution of all fiber-collided pairs in each mock catalogue. Using the $d_\mathrm{LOS}$ distribution, we compute the fraction of close pairs that are contained within the peak of the distribution ($f_\mathrm{peak}$; Section \ref{sec:dlos}). We then select $f_\mathrm{peak}$ of the close pairs and treat them as correlated pairs that lie in the peak of the $d_\mathrm{LOS}$ distribution. We refer to these close pairs as ``peak-assigned" close pairs.

Each of these ``peak-assigned" close pairs, due to the nearest-neighbor up-weighting, consist of a galaxy with $w_\mathrm{fc} > 1$ (the ``nearest-neighbor" galaxy) and another galaxy with $w_\mathrm{fc} = 0$ (the ``collided" galaxy). We disregard the collided galaxy. For each of the nearest-neighbor galaxies, we sample a value $d$ from the peak of the $d_\mathrm{LOS}$ distribution and place a galaxy with $w_\mathrm{fc} = 1$ at a comoving distance $d$ away from the nearest-neighbor galaxy. At the same time, we reduce the fiber-collision weight of the nearest-neighbor galaxy by $1$. This process is repeated until the nearest-neighbor galaxy has $w_\mathrm{fc} =1$.

For the remaining close pairs that are not ``peak-assigned", we keep the nearest-neighbor fiber collision weights. The resulting mock catalogue has $f_\mathrm{peak}$ fewer galaxies with $w_\mathrm{cp} > 1$ compared to the NN-upweighted mock catalogues that we started from; however, the total statistical weight of the mock catalogue is conserved.

Next, we use the FKP estimator with the shot-noise correction term described in Section \ref{sec:shotnoise} Eq. \ref{eq:ourshot} to calculate the $P(k)$ for our newly corrected mock catalogues. In Figure \ref{fig:peaksn} we present the ratio of the $\overline{P(k)}$ computed using our fiber-collision correction method over $P_\mathrm{true}(k)$. To assess the merit of the fiber-collision correction scheme, we once again over-plotted the sample variance of the mock catalogues. For Las Damas, at $k \sim 0.3 \; h/\mathrm{Mpc}$, $P(k)/P_\mathrm{true}(k) - 1 \sim 0.5 \%$ and throughout the $k$ range, $0.3 \% < P(k)/P_\mathrm{true}(k) - 1 < 1.3 \%$. For QPM, at $k \sim 0.3 \; h/\mathrm{Mpc}$, $P(k)/P_\mathrm{true}(k) - 1 \sim 0.04 \%$ and throughout the $k$ range, $0.3 \% < P(k)/P_\mathrm{true}(k) - 1 < 1.3 \%$. % provide some specifics on the range of the P(k) ratio 
Furthermore for the Las Damas and QPM catalogues, the $P(k)$ ratio is significantly below the sample variance throughout the entire $k$ range probed.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Goodness of fit
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Goodness-of-fit} \label{sec:litcomp}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% CHI-SQUARED FIGURE 
\begin{figure*} 
\begin{center}
\includegraphics[scale=0.55]{fcpaper_pk_chisquared_comparison.png} 
\caption{$\chi^2 (k_\mathrm{max})$ for $P_\mathrm{NN-upweight}$ (blue), $P_\mathrm{Beutler}$ (light blue), $P_\mathrm{Gil-Marin}$ (orange), and $P_\mathrm{Hahn}$ (yellow) using the Las Damas (left panel), QPM (centerl panel), and Tiling (right panel) mock catalogues. Equation \ref{eq:chi2} was used to compute the $\chi^2(k_\mathrm{max})$. }\label{fig:peaksnchi2}
\end{center}
\end{figure*}

The correction method we present in this paper corrects for the effect of fiber-collisions to the extent where $P_\mathrm{corr}(k)$ measurements are no longer dominated by systematic effects at $k > 0.2 \; h/\mathrm{Mpc}$. With this in mind, we quantify the goodness-of-fit for all the corrected $P(k)$s to $P_\mathrm{true}(k)$ by comparing the the following $\chi^2$ to one another: 
\begin{equation}
\chi^2 (k_\mathrm{max}) = \frac{1}{N_{k_\mathrm{max}}} \sum\limits_{k< k_\mathrm{max}} \frac{(\overline{P_\mathrm{corr}(k)} - \overline{P_\mathrm{true}(k))^2}}{\Delta P_\mathrm{true} (k)^2}. \label{eq:chi2}
\end{equation}
$N_{k_\mathrm{max}}$ is the number of $k$ bins in the $P(k)$ calculation with $k < k_\mathrm{max}$. $\overline{P_\mathrm{corr}(k)}$ is the average fiber-collision corrected powerspectrum of all realizations for each catalogue. $\Delta P_\mathrm{true}(k)$ is the standard deviation of $P_\mathrm{true}(k)$ computed from all realizations of each mock catalogue. We calculate $\chi^2$ as a function of $k_\mathrm{max}$ in order to determine the accumulated $\chi^2$ to a specific scale ($k_\mathrm{max}$). In doing so, we determine the scale to which a power spectrum analysis can be extended to without suffering the significant effects of fiber-collisions.

For the Tiling Mock catalogue, since there is only one realization, the variance ($\Delta P_\mathrm{true} (k)$) cannot be computed independently. However, for an estimate of the $\chi^2$, we use $\Delta P_\mathrm{true}^\mathrm{Tiling\;Mock}(k)$ from $\Delta P_\mathrm{true} (k)$ of the QPM mock catalogue scaled by the ratio of the power spectrum:
\begin{equation}
\Delta P_\mathrm{true}^\mathrm{Tiling}(k) = \Delta P_\mathrm{true}^{QPM}(k) \times \frac{P_\mathrm{true}^\mathrm{Tiling}(k)}{\overline{P^\mathrm{QPM}_\mathrm{true}(k)}}.
\end{equation}

In Figure \ref{fig:peaksnchi2}, we present the $\chi^2(k_\mathrm{max})$ for $P(k)$ using the following fiber collision correction methods: NN-upweight, \cite{Beutler:2014aa}, \cite{Gil-Marin:2014aa}, and our method from Section \ref{sec:apply}. The comparison is made using the Las Damas (left panel), QPM (center panel) and Tiling (right panel) mock catalogues. First in the Las Damas panel, at scales $k < 5 \times 10^{-2} \; h/\mathrm{Mpc}$, $\chi^2 < 10^{-3}$ for all correction methods, which suggests that all correction methods sufficiently correct for fiber-collisions and provide a reasonable fit to $P_\mathrm{true}(k)$ at these larger scale. In approaching smaller scales the $\chi^2$ for all correction methods increase. However, throughout the entire $k_\mathrm{max}$ range, our correction method provides a notably lower $\chi^2$ in comparison to the other correction methods. This is especially clear at $k \sim 0.3 \; h/\mathrm{Mpc}$, where $\chi^2_\mathrm{NN-upweight} \approx 0.33$, $\chi^2_\mathrm{Beutler} \approx 0.33$, and $\chi^2_\mathrm{Gil-Marin} \approx 0.17$ while $\chi^2 \approx 0.019$ for our method.

Next in the central QPM panel, at large scales ($k < 2 \times 10^{-2} \; h/\mathrm{Mpc}$) all corrected $P(k)$ once again provide a reasonable reconstruction of $P_\mathrm{true}(k)$ with $\chi^2 \approx 10^{-2}$. Then for $2 \times 10^{-2} < k_\mathrm{max} < 5 \times 10^{-2}\; h/\mathrm{Mpc}$, NN-upweight and \cite{Beutler:2014aa} correction methods have the lower $\chi^2$s than \cite{Gil-Marin:2014aa} and our correction methods. However, at smaller scales, the $\chi^2$s of NN-upweight and \cite{Beutler:2014aa} quickly increase beyond the $\chi^2$s of \cite{Gil-Marin:2014aa} and our methods. Meanwhile, throughout the entire $k_\mathrm{max}$ range our correction method has a lower $\chi^2$ than the correction method of \cite{Gil-Marin:2014aa}. The difference in $\chi^2$ is again most remarkable at the smallest scales: $\chi^2 (k_\mathrm{max} \sim 0.3) \approx 7.3,\;11, \;0.068, \;\mathrm{and} \; 0.0063$ for NN-upweight, \cite{Beutler:2014aa}, \cite{Gil-Marin:2014aa} and our correction method respectively.

Finally in the right panel (Tiling Mock), we find that $\chi^2(k_\mathrm{max})$ increases in a near monotonic fashion as a function of $k_\mathrm{max}$. For $k_\mathrm{max} < 4\times10^{-2} \; h/\mathrm{Mpc}$, there are no significant differences between the $\chi^2$s of all the correction methods. Then from $4\times10^{-2} < k_\mathrm{max} < 1.5\times 10^{-2} \; h/\mathrm{Mpc}$, $\chi^2$s of NN-upweight and \cite{Beutelr:2014aa} are notably lower than the $\chi^2$s of \cite{Gil-Marin:2014aa} and our method. However at smaller scales, the $\chi^2$s of NN-upweight and \cite{Beutelr:2014aa} quickly rise beyond the other $\chi^2$s, ultimately both reach $\chi^2(k_\mathrm{max} \sim 0.3) \approx 13.5$. In the meantime, $\chi^2(k_\mathrm{max} \sim 0.3) \approx 0.32$ for \cite{Gil-Marin:2014aa} and $\chi^2(k_\mathrm{max} \sim 0.3) \approx 0.15$ for our correction method. Moreover, through the entire $k_\mathrm{max}$ our method has a lower $\chi^2$ than \cite{Gil-Marin:2014aa}. With only one realization of the Tiling Mocks and scaled $\Delta P$, a detailed comparison of the $\chi^2$ values is impossible. Yet the $\chi^2(k_\mathrm{max})$ results for our correction provide realistic assurance that the correction method can be applied to the actually BOSS data.

Overall, regardless of catalogue, for scales $k_\mathrm{max} < 3 \times 10^{-2} \;h/\mathrm{Mpc}$, the $\chi^2$ for all fiber-collision corrected $P(k)$ are negligible. Then, with the exception of the Las Damas catalogue, at intermediate scales of $3 \times 10^{-2} < k_\mathrm{max} < 0.15 \; h/\mathrm{Mpc}$ the NN-upweight and \cite{Beutler:2014aa} methods show the lowest $\chi^2$s. At the smallest scales, however, these corrections methods no longer provide a good fit to $\overline{P_\mathrm{true}(k)}$. A detailed comparison at the small scales ($k > 1.5 \times 10^{-1} \;h/\mathrm{Mpc}$) demonstrates that the fiber-collision correction we present in this paper significantly better reproduces the true power spectrum than any of the other fiber-collision correction methods. Furthermore, Figure \ref{fig:peaksnchi2} illustrates that throughout the entire $k_\mathrm{max}$ is able to reasonably reproduces $P_\mathrm{true}(k)$ at all scales.

% Detailed comparison to Gil-Marin that talk about how the xps value he calculates is only validated through mock catalogues, but our method can be validated with the overlapping regions of the real data.

\section{Summary and Discussion} 
Using simulated mock catalogues for SDSS data with realistically imposed fiber-collisions, we quantify the systematic effects of fiber-collisions on galaxy clustering statistics, in particular the power spectrum. Although fiber-collisions have little significant effect on the power spectrum at large scales, its effect quickly overtakes the sample variance at scales smaller than $k \sim 0.1 \;h/\mathrm{Mpc}$. At the smallest scales that we explore in this paper, $k \sim 0.3$, fiber-collisions have over a $10 \%$ effect on the power spectrum. Consequently, at these small scales the uncertainties for power spectrum measurements are dominated by systematic effects from fiber-collisions.

Fortunately, through the fiber-collided mock catalogues we are able to model the distribution of the line-of-sight displacement between fiber-collided pairs. Combining this model with a modified shot-noise term in the power spectrum estimator, we devise a new fiber-collision correction method that is able to reconstruct the true power spectrum from fiber-collided data even to $k \sim 0.3 \;h/\mathrm{Mpc}$. Throughout the entire $k$ range explored in our analysis, our correction method reconstructs $P_\mathrm{True}(k)$ safely within the sample variance.

Furthermore, we compare our method to the most common nearest-neighbor correction method and recent correction methods presented in \cite{Beutler:2014aa} and \cite{Gil-Marin:2014aa} to demonstrate that our method most successfully reproduces the true power spectrum at small scales for all the Las Damas, QPM, and Tiling mock catalogues. As an added advantage, our correction method can also be validated by actual data rather than only through the mock catalogues thereby making it's application to actual data further reliable.

The fiber-collision correction method we present will enable us to extend our galaxy clustering analysis to smaller scales for SDSS-III BOSS and future surveys such as eBOSS or any other large fiber-fed surveys. Our fiber-collision correction method can also be extend to higher order clustering statistics such as the bispectrum, which we will explore in future work.

\bigskip
We thank something something

% No need for different sections, just present the different results 
\bibliographystyle{apj}
\bibliography{fc_paper}
\end{document}

### 2015-03-24 fc_paper/fc_paper.tex
Abstract written

@@
 \begin{abstract}
-Redshift surveys, including BOSS, use fiber fed spectrographs.
-A fiber is used for each galaxy in order obtain its redshift.
-However, due to the physical size of the fibers, if galaxies are located in close proximity to each other on the sky (not necessary along the line-of-sight) two separate fibers cannot be placed adjacently in order to separately extra the spectroscopic information.
-In such a scenario, the redshift of fiber-collided galaxies are not individually resolved and only a single redshift for them can be calculated.
-Though this only accounts for $< 5\%$ of the BOSS redshift survey, its effect on the statistical measures such as the powerspectrum and bispectrum is sufficient in small scales to warrant a detailed correction scheme.
+With their ability to collect large amounts of redshift data, fiber-fed multi-object spectroscopic surveys dominate cosmological studies.
+However, the physical size of the fibers limit the ability of these surveys from successfully collecting redshifts from galaxies within the fiber-collision angular scale.
+These fiber-collisions ultimately leads to systematic effects on galaxy clustering measurements.
+Using simulated mock catalogues already extensively used in interpreting large-scale structure clustering measurements of the Sloan Digital Sky Survey, we investigate the effects of fiber-collisions on the power spectrum in particular.
+We compare current fiber-collision correction methods in the literature and assess their success in reconstructing the true power spectrum for the mock catalogues.
+We then present our fiber-collision correction method.
+Our method uses the distribution of the line-of-sight displacements between resolved fiber-collided pairs in order to statistically reconstruct clustering on small scales along with a proper accounting of fiber-collisions in the shot-noise correction term of the power spectrum estimator.
+Using our method, we reproduce the true power spectrum for the mock catalogues with residuals of $\sim 1\%$ at $k \sim 0.3 \; h/\mathrm{Mpc}$.
+Finally, comparison to other fiber-collision correction methods reveal that the method better reproduces the true power spectrum especially at small scales, with the added advantage that the method can be validated and calibrated in actual data.
 \end{abstract}
-\keywords{cosmology: observations --- }
+\keywords{cosmology: observations -- cosmology: large-scale structure of universe -- galaxies: distances and redshift -- galaxies: halos -- galaxies: statistics}
 
 \section{Introduction} 
-\begin{itemize}
-\item fiber-fed multi-object spectroscopic surveys allow us to collect large redshift data, which is why it?s the favorite of cosmology surveys
-\item moving from statistics dominated regime to systematics dominated regime
-\end{itemize}
+Through the tens of million redshifts obtained through redshift surveys, cosmological measurements are no longer dominated by uncertainties from statistical precision, but from systematic effects of the measurements.
+Most of these cosmology focused redshift surveys, such as the 2dF Galaxy Redshift Survey (2dFGRS; CITE CITE) and the Baryon Oscillation Spectroscopic Survey (BOSS; CITECITE) and future redshift surveys such as the Extended Baryon Oscillation Spectroscopic Survey (eBOSS; CITE CITE) use fiber fed spectrographs.
+For each galaxy, a fiber is used to obtain a spectroscopic redshift.
+However, due to the physical size of the fibers even with efficient targeting strategies (e.g.
+\citealt{Blanton:2003ab} for SDSS), if galaxies are located within the fiber-collision angular scale from each other on the sky, two separate fibers cannot be placed adjacently to separately extract the spectroscopic information.
+In these cases, the redshifts of fiber-collided galaxies are not individually resolved and only a single redshift is measured.
+Furthermore, as we probe to higher redshifts in our cosmological studies, the fiber-collision angular scale correspond to a larger comoving scale thereby affecting our measurements on larger scales.
 
-Redshift surveys, including BOSS, use fiber fed spectrographs.
-A fiber is used for each galaxy in order obtain its redshift.
-However, due to the physical size of the fibers, if galaxies are located in close proximity to each other on the sky (not necessary along the line-of-sight) two separate fibers cannot be placed adjacently in order to separately extra the spectroscopic information.
-In such a scenario, the redshift of fiber-collided galaxies are not individually resolved and only a single redshift for them can be calculated.
-Though this only accounts for $< 5\%$ of the BOSS redshift survey, its effect on the statistical measures such as the powerspectrum and bispectrum is sufficient in small scales to warrant a detailed correction scheme.
+Though this only accounts for a small fraction of the redshifts ($< 5\%$ of the BOSS redshift survey) its effect on clustering measurements such as the power spectrum is significant and must be understood as our cosmological measurements become more detailed and sophisticated.
 
@@
 % Include cosmology assumption and out line of paper
+\begin{itemize}
+\item Even advancements in fiber positioners won't eliminate the fiber-collision issues in high density regions \cite{Morales:2012aa}. 
+\item Fibercollision gets worse in comoving scales 
+\item \cite{Zehavi:2002aa} FC in SDSS (example of the upweighting method) only works for fiber-collision scales and fails below it
+\item Perhaps the use of robotic fiber positioner technology in future surveys such as the Dark Energy Survey Instrument (DESI; \citealt{Schlegel:2011aa, Makarem:2014aa}) will render fiber-collisions obsolete, until then accounting for the systematic effects remains an unavoidable challenge for clustering statistics.
+\end{itemize}
 
@@
 For various purposes such as calculating the covariance matrix or estimating cosmic variance, simulated mock catalogues play a crucial role in measuring clustering statistics of observed galaxy data (\citealt{Scoccimarro:2002aa, Anderson:2012aa, Manera:2013aa}).
-They also provide a means of understanding systematic effects such as fiber-collisions (CITE CITE).
+They also provide a means of understanding systematic effects such as fiber-collisions (\citealt{Yoon:2008aa, Guo:2012aa} LIST MORE).
 By using mock catalogues, we can test how these effects influence clustering results and devise correction methods that attempt to account for these effects.
@@
 For $k_\mathrm{max} < 4\times10^{-2} \; h/\mathrm{Mpc}$, there are no significant differences between the $\chi^2$s of all the correction methods.
-Then from $4\times10^{-2} < k_\mathrm{max} < 1.5\times 10^{-2} \; h/\mathrm{Mpc}$, $\chi^2$s of NN-upweight and \cite{Beutelr:2014aa} are notably lower than the $\chi^2$s of \cite{Gil-Marin:2014aa} and our method.
-However at smaller scales, the $\chi^2$s of NN-upweight and \cite{Beutelr:2014aa} quickly rise beyond the other $\chi^2$s, ultimately both reach $\chi^2(k_\mathrm{max} \sim 0.3) \approx 13.5$.
+Then from $4\times10^{-2} < k_\mathrm{max} < 1.5\times 10^{-2} \; h/\mathrm{Mpc}$, $\chi^2$s of NN-upweight and \cite{Beutler:2014aa} are notably lower than the $\chi^2$s of \cite{Gil-Marin:2014aa} and our method.
+However at smaller scales, the $\chi^2$s of NN-upweight and \cite{Beutler:2014aa} quickly rise beyond the other $\chi^2$s, ultimately both reach $\chi^2(k_\mathrm{max} \sim 0.3) \approx 13.5$.
 In the meantime, $\chi^2(k_\mathrm{max} \sim 0.3) \approx 0.32$ for \cite{Gil-Marin:2014aa} and $\chi^2(k_\mathrm{max} \sim 0.3) \approx 0.15$ for our correction method.

### 2015-03-24 fc_paper/fc_paper.tex
writing intro

@@
 With their ability to collect large amounts of redshift data, fiber-fed multi-object spectroscopic surveys dominate cosmological studies.
-However, the physical size of the fibers limit the ability of these surveys from successfully collecting redshifts from galaxies within the fiber-collision angular scale.
+However, the physical size of the fibers limit the ability of these surveys from successfully collecting redshifts from galaxies within the angular fiber-collision scale.
 These fiber-collisions ultimately leads to systematic effects on galaxy clustering measurements.
@@
 \section{Introduction} 
-Through the tens of million redshifts obtained through redshift surveys, cosmological measurements are no longer dominated by uncertainties from statistical precision, but from systematic effects of the measurements.
-Most of these cosmology focused redshift surveys, such as the 2dF Galaxy Redshift Survey (2dFGRS; CITE CITE) and the Baryon Oscillation Spectroscopic Survey (BOSS; CITECITE) and future redshift surveys such as the Extended Baryon Oscillation Spectroscopic Survey (eBOSS; CITE CITE) use fiber fed spectrographs.
+Through the tens of millions of redshifts obtained through redshift surveys, cosmological measurements such as galaxy clustering statistics are no longer dominated by uncertainties from statistical precision, but from systematic effects of the measurements.
+These redshift surveys, such as the 2dF Galaxy Redshift Survey (2dFGRS; \citealt{Colless:1999aa}) and the Sloan Digital Sky Survey-III Baryon Oscillation Spectroscopic Survey (SDSS-III BOSS; \citealt{Anderson:2012aa, Dawson:2013aa}) and future redshift surveys such as the Extended Baryon Oscillation Spectroscopic Survey (eBOSS; CITE CITE) mostly use fiber fed spectrographs.
+
 For each galaxy, a fiber is used to obtain a spectroscopic redshift.
@@
 In these cases, the redshifts of fiber-collided galaxies are not individually resolved and only a single redshift is measured.
+
 Furthermore, as we probe to higher redshifts in our cosmological studies, the fiber-collision angular scale correspond to a larger comoving scale thereby affecting our measurements on larger scales.
+SDSS-III BOSS, in particular, has an angular fiber-collision scale of $62"$, which corresponds to $\sim 0.4 \;\mathrm{Mpc}/h$ at the center of the redshift bin, and fiber-collided galaxies account for $< 5\%$ of the galaxy sample.
+Although fiber-collided galaxies account for a relatively small fraction of the redshifts its effect on clustering measurements such as the power spectrum is significant and must be understood as clustering measurements probe to smaller scales and as we explore higher order statistics such as the three-point correlation function or the bispectrum.
+Perhaps with the use of robotic fiber positioner technology in future surveys such as the Dark Energy Survey Instrument (DESI; \citealt{Schlegel:2011aa, Morales:2012aa, Makarem:2014aa}) will render fiber-collisions obsolete.
+However, until then accounting for the systematic effects remains an unavoidable challenge for clustering statistics.
 
-Though this only accounts for a small fraction of the redshifts ($< 5\%$ of the BOSS redshift survey) its effect on clustering measurements such as the power spectrum is significant and must be understood as our cosmological measurements become more detailed and sophisticated.
+% Talk about the upweighting scheme and cite the different works that currently use the nearest neighbor upweighting method. 
+To correct for the systematic effects of fiber collisions, a common method used in clustering statistics is the nearest neighbor method (\citealt{Zehavi:2002aa, Berlind:2006aa, Anderson:2012aa}).
+For fiber-collided galaxies without resolved redshifts, the method assigns the statistical weight of the fiber-collided galaxy to its nearest angular neighbor.
+This method has been
 
-Fiber-collision corrections such as that proposed by \cite{Guo:2012aa} have been applied to correct for the two point correlation function.
-Guo et al.
-(2012) estimates the total contribution of fiber-collided galaxies to the two point correlation function by examining the pair statistics in overlapping tiling regions of the survey.
-Unfortunately, this method cannot be easily extended for the fourier counter parts to the two-point and three-point correlation functions due to the complex geometry of the overlapping regions.
-Consequently, we propose a fiber-collision correction method that uses the distribution of the line-of-sight displacement between resolved fiber-collided galaxies and proper accounting of fiber-collisions in the shot-noise correction term of the powerspectrum/bispectrum estimator.
-
-In the following sections, we present our fiber-collision correction results using a series of simulations. Ultimately, we apply our correction to the BOSS data. 
-% Include cosmology assumption and out line of paper
 \begin{itemize}
-\item Even advancements in fiber positioners won't eliminate the fiber-collision issues in high density regions \cite{Morales:2012aa}. 
-\item Fibercollision gets worse in comoving scales 
-\item \cite{Zehavi:2002aa} FC in SDSS (example of the upweighting method) only works for fiber-collision scales and fails below it
-\item Perhaps the use of robotic fiber positioner technology in future surveys such as the Dark Energy Survey Instrument (DESI; \citealt{Schlegel:2011aa, Makarem:2014aa}) will render fiber-collisions obsolete, until then accounting for the systematic effects remains an unavoidable challenge for clustering statistics.
+\item A paragraph that list fiber collision corrections listed in \cite{Guo:2012aa} \cite{Zehavi:2002aa}. List all clusteirng statistics measurement that uses this.
+\item talk about shot-noise correction term adjustments
 \end{itemize}
 
+Recently \cite{Guo:2012aa} proposed a fiber-collision correction method for the two-point correlation function (2PCF) of the BOSS galaxies that is able to SOME PRECISION.
+\cite{Guo:2012aa} estimates the total contribution of fiber-collided galaxies to the two point correlation function by examining the pair statistics in overlapping tiling regions of the survey, where a smaller fraction of galaxies suffer from fiber-collisions.
+Unfortunately, this method cannot be applied to the Fourier counter part of the 2PCF due to the complex geometry of the overlapping regions.
+Consequently, we propose a fiber-collision correction method that uses the distribution of the line-of-sight displacement between resolved fiber-collided galaxies and proper accounting of fiber-collisions in the shot-noise correction term of the power spectrum estimator.
+
+In Section \ref{sec:catalog}, we present a brief description of the fiber-collided simulated mock catalogues that we use to quantify the systematic effect of fiber-collisions and to test and compare correction methods throughout the paper.
+After discussing the two components of our correction method in Section \ref{sec:fc_corr}, we present it in Section \ref{sec:apply}.
+We also test our correction method on the mock catalogues and compare it to other correction methods in Section \ref{sec:apply}.
+Finally in Section \ref{sec:summary} we summarize and discuss our results.
+% Include cosmology assumption and out line of paper
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\section{Summary and Discussion} 
+\section{Summary and Discussion} \label{sec:summary}
 Using simulated mock catalogues for SDSS data with realistically imposed fiber-collisions, we quantify the systematic effects of fiber-collisions on galaxy clustering statistics, in particular the power spectrum.

### 2015-03-25 fc_paper/fc_paper.tex
Abstract updated, intro updated
Finished edits up to Section 2.

--- 2015-03-24 fc_paper/fc_paper.tex
@@
 \begin{abstract}
-Redshift surveys, including BOSS, use fiber fed spectrographs.
-A fiber is used for each galaxy in order obtain its redshift.
-However, due to the physical size of the fibers, if galaxies are located in close proximity to each other on the sky (not necessary along the line-of-sight) two separate fibers cannot be placed adjacently in order to separately extra the spectroscopic information.
-In such a scenario, the redshift of fiber-collided galaxies are not individually resolved and only a single redshift for them can be calculated.
-Though this only accounts for $< 5\%$ of the BOSS redshift survey, its effect on the statistical measures such as the powerspectrum and bispectrum is sufficient in small scales to warrant a detailed correction scheme.
+Fiber-fed multi-object spectroscopic surveys, with their ability to collect an unprecedented number of redshifts, dominate cosmological studies.
+However, the physical size of the fibers limit these surveys from successfully collecting redshifts from galaxies within the angular fiber-collision scale, which ultimately lead to significant systematic effects on galaxy clustering measurements.
+Using simulated mock catalogues, which have been extensively used in interpreting large-scale structure clustering results (such as the correlation function and power spectrum) of the Sloan Digital Sky Survey, we investigate the effects of fiber-collisions on the galaxy power spectrum in particular.
+We compare the methods currently used to correct for fiber-collisions in the literature and assess their success in reconstructing the true power spectrum for mock catalogues.
+
+We present our fiber-collision correction method, which statistically reconstructs the clustering of fiber-collided pairs, using the distribution of the line-of-sight displacements between resolved fiber-collided pairs, and properly accounts for fiber-collisions in the shot-noise correction term of the power spectrum estimator.
+Using our method, we successfully reproduce the true power spectrum for the mock catalogues with residuals of $\sim 1\%$ at $k \sim 0.3 \; h/\mathrm{Mpc}$ and $< 10\%$ at $k \sim 0.8 \; h/\mathrm{Mpc}$.
+Our comparisons to other correction methods demonstrate that our method most accurately reconstructs the true power spectrum from fiber-collided data especially at small scales ($k > 0.1\; h/\mathrm{Mpc}$), with the added advantage that the method can be validated and calibrated in actual observations.
+With statistical precision no longer obstructing galaxy clustering measurements, our correction method will allows us constrain systematic effects of fiber-collisions and extend power spectrum measurements to smaller scales.
 \end{abstract}
-\keywords{cosmology: observations --- }
+\keywords{cosmology: observations -- cosmology: large-scale structure of universe -- galaxies: distances and redshift -- galaxies: halos -- galaxies: statistics}
 
 \section{Introduction} 
-\begin{itemize}
-\item fiber-fed multi-object spectroscopic surveys allow us to collect large redshift data, which is why it?s the favorite of cosmology surveys
-\item moving from statistics dominated regime to systematics dominated regime
-\end{itemize}
+Through the millions of redshifts obtained through redshift surveys, cosmological measurements such as galaxy clustering statistics are no longer dominated by uncertainties from statistical precision, but from systematic effects of the measurements.
+These redshift surveys, such as the 2dF Galaxy Redshift Survey (2dFGRS; \citealt{Colless:1999aa}) and the Sloan Digital Sky Survey-III Baryon Oscillation Spectroscopic Survey (SDSS-III BOSS; \citealt{Anderson:2012aa, Dawson:2013aa}) and future redshift surveys such as the Extended Baryon Oscillation Spectroscopic Survey (eBOSS; CITE CITE) use fiber fed spectrographs.
 
-Redshift surveys, including BOSS, use fiber fed spectrographs.
-A fiber is used for each galaxy in order obtain its redshift.
-However, due to the physical size of the fibers, if galaxies are located in close proximity to each other on the sky (not necessary along the line-of-sight) two separate fibers cannot be placed adjacently in order to separately extra the spectroscopic information.
-In such a scenario, the redshift of fiber-collided galaxies are not individually resolved and only a single redshift for them can be calculated.
-Though this only accounts for $< 5\%$ of the BOSS redshift survey, its effect on the statistical measures such as the powerspectrum and bispectrum is sufficient in small scales to warrant a detailed correction scheme.
+For each galaxy, a fiber is used to obtain a spectroscopic redshift.
+However, due to the physical size of the fibers even with efficient targeting strategies (e.g.
+\citealt{Blanton:2003ab} for SDSS), if galaxies are located within the fiber-collision angular scale from one another on the sky, separate fibers cannot be placed adjacently to separately extract the spectroscopic information (\citealt{Yoon:2008aa} {\bf CITE MORE}).
+In these situations, the redshifts of fiber-collided galaxies are not individually resolved and only a single redshift is measured.
+With redshifts of galaxies in close angular proximities missing from the sample, any clustering statistic probing these scales will be systematically affected.
 
-Fiber-collision corrections such as that proposed by \cite{Guo:2012aa} have been applied to correct for the two point correlation function.
-Guo et al.
-(2012) estimates the total contribution of fiber-collided galaxies to the two point correlation function by examining the pair statistics in overlapping tiling regions of the survey.
-Unfortunately, this method cannot be easily extended for the fourier counter parts to the two-point and three-point correlation functions due to the complex geometry of the overlapping regions.
-Consequently, we propose a fiber-collision correction method that uses the distribution of the line-of-sight displacement between resolved fiber-collided galaxies and proper accounting of fiber-collisions in the shot-noise correction term of the powerspectrum/bispectrum estimator.
+As our cosmological surveys extend further to higher redshifts, the systematic effect becomes worse as the fiber-collision angular scale corresponds to a larger comoving scale, thereby affecting our measurements on larger scales.
+SDSS-III BOSS, in particular, has an angular fiber-collision scale of $62"$.
+This corresponds to $\sim 0.4 \;\mathrm{Mpc}/h$ at the center of the survey redshift redshift range, and fiber-collided galaxies account for $\sim 5\%$ of the galaxy sample (\citealt{Anderson:2012aa}).
+Although this accounts for a relatively small fraction of redshifts, its effect on clustering measurements such as the power spectrum is significant and must be understood as these measurements probe to smaller scales and as higher order statistics such as the three-point correlation function or the bispectrum are used in cosmological studies.
+Perhaps with the use of robotic fiber positioner technology in future surveys such as the Dark Energy Survey Instrument (DESI; \citealt{Schlegel:2011aa, Morales:2012aa, Makarem:2014aa}) will render fiber-collisions obsolete.
+However, until then accounting for the systematic effects remains an unavoidable challenge for clustering statistics.
 
-In the following sections, we present our fiber-collision correction results using a series of simulations. Ultimately, we apply our correction to the BOSS data. 
-% Include cosmology assumption and out line of paper
+To correct for fiber collisions, one common approach used in clustering statistics is the nearest neighbor method (\citealt{Zehavi:2002aa, Berlind:2006aa, Anderson:2012aa}).
+For fiber-collided galaxies without resolved redshifts, the method assigns the statistical weight of the fiber-collided galaxy to its nearest angular neighbor.
+This provides a reasonable correction for the fiber-collision effects at scales much larger than the fiber-collision scales; however the correction falls short near the fiber-collision scale.
+In fact, as \cite{Zehavi:2005aa} find, fiber-collisions affect the two-point correlation function (2PCF) measurements even on scales significantly larger than the fiber-collision scale ( $> 1\;\mathrm{Mpc}/h$).
+For power spectrum measurements in BOSS, the nearest neighbor method has often been supplemented with adjustments in the constant shot-noise term of the power spectrum estimator to correct for fiber-collisions (\citealt{Beutler:2014aa, Gil-Marin:2014aa}).
+While this shot-noise term adjustment has been calibrated within the mock catalogues used to interpret the BOSS clustering results, validating these methods for observations remains a challenge.
+
+Recently \cite{Guo:2012aa}, focusing on SDSS-III BOSS like samples, proposed a fiber-collision correction method for the 2PCF that is able to reasonably correct for fiber-collisions above and below the collision scale.
+\cite{Guo:2012aa} estimates the total contribution of fiber-collided galaxies to the two point correlation function by examining the pair statistics in overlapping tiling regions of the survey, where a smaller fraction of galaxies suffer from fiber-collisions.
+Unfortunately, this method cannot be applied to the Fourier clustering measurements due to the complex geometry of the overlapping regions.
+As a result, we propose a fiber-collision correction method that, first, improves upon the nearest neighbor method by using the distribution of the line-of-sight displacement between resolved fiber-collided galaxies to statistically reconstruct the clustering of fiber-collided galaxies; and proper accounts for fiber-collisions in the shot-noise correction term of the power spectrum estimator.
+
+In Section \ref{sec:catalog}, we present a brief description of the simulated mock catalogues with realistic applied fiber-collisions and power spectrum estimator used throughout the paper.
+Then during our discussion of the two components of our correction method in Section \ref{sec:fc_corr}, we quantify the effects of fiber-collisions of power spectrum measurements and test and compare common correction methods.
+Afterwards, we present our correction method in Section \ref{sec:apply}, test it on the mock catalogues, and compare it to other correction methods.
+Finally in Section \ref{sec:summary} we summarize and discuss our results.
 
@@
 \section{Fiber-collided Mock Catalogues} \label{sec:catalog}
-For various purposes such as calculating the covariance matrix or estimating cosmic variance, simulated mock catalogues play a crucial role in measuring clustering statistics of observed galaxy data (\citealt{Scoccimarro:2002aa, Anderson:2012aa, Manera:2013aa}).
-They also provide a means of understanding systematic effects such as fiber-collisions (CITE CITE).
-By using mock catalogues, we can test how these effects influence clustering results and devise correction methods that attempt to account for these effects.
+For various purposes such as calculating covariance matrices or estimating cosmic variance, simulated mock catalogues play a crucial role in interpreting clustering measurements of observed galaxies (\citealt{Scoccimarro:2002aa, Anderson:2012aa, Manera:2013aa}).
+They also provide a means of understanding systematic effects such as fiber-collisions (\citealt{Guo:2012aa, Manera:2013aa} {\bf LIST MORE}) since systematic effects can be simulated on the mock catalogues.
+This allows us to test how these effects influence clustering measurements and devise correction methods that attempt to account for these effects.
 
 A direct way of understanding the effects of fiber-collisions on clustering statistics in observations is to first apply fiber-collisions to mock catalogues then compare the clustering statistics obtained from mock catalogues with and without the fiber collisions.
-Afterwards, correction methods for fiber-collisions can be applied to the fiber-collided mocks and the merit of the correction method can be quantified by how successfully they can reproduce the clustering statistics of the original mock catalogues without fiber-collisions.
+Correction methods for fiber-collisions can then be applied to the fiber-collided mocks and the merit of the correction method can be quantified by how successfully they reproduce the clustering statistics of the original mock catalogues without fiber-collisions.
 The optimal correction method can then be applied to the observed data with some assurance that it accounts for fiber-collisions and improves the clustering measurements.
@@
 
-Effects of fiber-collisions must be understood and interpreted in conjunction with these systematic effects and to ultimately test our fiber-collision correction method we use LasDamas (\citealt{McBride:2009aa}), Quick Particle Mesh (\citealt{White:2014aa}), and Tiling mock catalogues.
-These mocks have already been used in interpreting observational results for BOSS and are generated through different prescriptions.
+Effects of fiber-collisions must be understood and interpreted in conjunction with these systematic effects.
+Therefore, in this paper, we use LasDamas (\citealt{McBride:2009aa, McBride:2011aa}), Quick Particle Mesh (\citealt{White:2014aa}), and Tiling mock catalogues, which have already been extensively used in interpreting clustering results for SDSS and BOSS and are generated through different prescriptions.
 Therefore they provide complementary tests fiber-collisions and our correction method tailored for BOSS.
+
+Each of these mock catalogues use some sort of N-body dark matter simulation along with a HOD prescription to populate the dark matter halos with ``galaxies".
 % Include brief detail on what each mock has to offer
 
-Each of these mock catalogues use some sort of N-body dark matter simulation along with a HOD prescription to populate the dark matter halos with ``galaxies".
-More specifically, the LasDamas Galaxy mock catalogues is constructed from the N-body Large Suite of Dark Matter Simulations (LasDamas).
+The LasDamas Galaxy mock catalogues is constructed from the Oriana N-body Large Suite of Dark Matter Simulations (LasDamas) with $1280^3$ particles with a box with side length, $L_\mathrm{Box} = 2400\;\mathrm{Mpc}/h$.
 The N-body LasDamas simulations uses a spatially flat $\Lambda$CDM cosmology with $\Omega_\mathrm{m} = 0.25$, $\Omega_\Lambda = 0.75$, $\Omega_\mathrm{b} = 0.04$, $\sigma_8 = 0.8$, $n_\mathrm{s} = 1$ and $h=0.7$.
 The dark matter halos are then identified using a friends-of-friends (FOF) algorithm (\citealt{Davis:1985aa}) with a linking length $b = 0.2 $ times the mean interparticle separation.
-The over-densities of dark matter halos are then populated with galaxies using the halo occupation distribution (HOD) framework to construct the galaxy mock catalogues (\citealt{McBride:2009aa}).
-The HOD prescription is specified so that the galaxy mock catalogues reproduce the correlation function of the SDSS sample.
-% Detail about the geometry and redshift range
-\begin{itemize}
-\item above description is not entirely correct because that was LasDamas for Guo+2011
-\item SDSS-II Geometry
-\item lower redshift range
-\end{itemize}
+The over-densities of dark matter halos are then populated with galaxies using the halo occupation distribution (HOD) framework to construct the galaxy mock catalogues (\citealt{McBride:2009aa, McBride:2011aa}).
+The HOD prescription is specified so that the galaxy mock catalogues reproduce the galaxy number density and projected correlation function of the observed SDSS Luminous Red Galaxy sample with $M_g < -21.8$.
+The LasDamas galaxy mock catalogues have 40 realizations that spans the redshift range, $0.16 < z < 0.44$ and are restricted to the survey geometry of SDSS Data Release 7.
+They also include redshift space distortions from velocities, but do not model fiber-collisions.
+
+To model the fiber-collisions of the observed galaxies in BOSS, we impose fiber-collisions at the angular scale of $62''$.
+Once we identify galaxies within $62''$ of each other, we arbitrary select one of the galaxies and assign the statistical weights of the other galaxies within $62''$ of it.
+Roughly $\sim 2.5 \%$ of the galaxies in the LasDamas mock catalogues are affected by fiber-collisions.
 
@@
 The mock galaxy sample is then trimmed to the BOSS CMASS survey footprint, downsamped based on angular sky completeness (sector completeness) and radial selection.
-The QPM mock galaxy catalogue is generated using the following $\Lambda$CDM cosmology: $\Omega_\mathrm{m} = 0.25$, $\Omega_\Lambda = 0.25$, $\Omega_\mathrm{b} = 0.04$, $\sigma_8 = 0.8$, $n_\mathrm{s} = 1$ and $h=0.7$.
+Furthermore, QPM mocks model the fiber-collisions of the BOSS CMASS sample ($62''$ angular fiber-collision scale).
+The QPM galaxy mock catalogue uses the following $\Lambda$CDM cosmology: $\Omega_\mathrm{m} = 0.29$, $\Omega_\Lambda = 0.71$, $\sigma_8 = 0.8$, $n_\mathrm{s} = 0.97$ and $h=0.7$.
+We use 1000 realizations of the QPM galaxy mock catalogue.
 For a detailed description of the QPM galaxy mock catalogues we refer readers to \cite{White:2014aa}.
@@
 Finally the Tiling Mock catalogue is generated using
-\begin{itemize}
-\item documentation for tiling mock? 
-\end{itemize}
+
+{\bf INSERT TILING MOCK DESCRIPTION HERE}
 
 In Figure \ref{fig:zdist}, we plot the redshift distribution for LasDamas, QPM, and Tiling Mock catalogues along with the redshift distribution of BOSS DR12 galaxies.
-The redshift distributions illustrate the constant $\bar{n}(z)$ for the LasDamas mock catalogue, while the QPM and Tiling mock $\bar{n}(z)$ distributions trace the observed BOSS redshift distribution.
+The LasDamas mock catalogue, which is modeled after the SDSS LRG sample has a constant $\bar{n}(z)$ while the QPM and Tiling mock redshift distributions closely trace the observed BOSS redshift distribution.
 
 % insert transition that mentions how the main clustering statistics we focus on in this paper is the Power Spectrum
-In order to measure the power spectrum for these mock catalogues, we use the standard \cite{Feldman:1994aa} (FKP) estimator.
-Throughout the paper we use the following formalisms from \cite{Feldman:1994aa}.
+In order to measure the power spectrum for these mock catalogues in our investigation, we use the standard \cite{Feldman:1994aa} (FKP) estimator.
+Throughout the paper we use the following formalisms from \cite{Feldman:1994aa}:
 \begin{equation} \label{eq:fkppk}
@@
 and the second term represents the constant shot-noise contribution to the power due to the discrete density field of our galaxies.
-More specifically, $n_g$ is the galaxy density, $n_r$ is the density of the synthetic random catalogue, $\alpha$ is the ratio of the number of galaxies over the number of synthetic random galaxies, $\bar{n}$ is the mean density of the galaxies, and $w_{\mathrm{FKP}}$ is the minimum variance weight derived in \cite{Feldman:1994aa}:
+$n_g$ is the galaxy density, $n_r$ is the density of the synthetic random catalogue, $\alpha$ is the ratio of the number of galaxies over the number of synthetic random galaxies, $\bar{n}$ is the mean density of the galaxies, and $w_{\mathrm{FKP}}$ is the minimum variance weight derived in \cite{Feldman:1994aa}:
 \begin{equation}
@@
 \caption{Average power spectrum $\overline{P(k)}$ for BOSS DR12 (black) and the mock catalogues Las Damas (blue), QPM (orange), and Tiling Mock (green), listed in Section \ref{sec:catalog} using the FKP $P(k)$ estimator.
-The width of the $P(k)$ for Las Damas and QPM represent the sample variance ($\Delta P(k)/\overline{P(k)}$) calculated from the multiple mock catalogues.
+The width of the $P(k)$ for Las Damas and QPM represent the sample variance ($\Delta P(k)$) calculated from the multiple realizations of the mock catalogues.
 We emphasize that fiber-collisions were not applied to the mock catalogues for the $P(k)$ measurements.
 Meanwhile, galaxy weights (Equation \ref{eq:weight}) are applied to the BOSS DR12 $P(k)$ measurement.
-We remind readers that the $\overline{P(k)}$ of the LasDamas mock catalogues is an outlier because of the different redshift range compared to the other mock catalogues.} \label{fig:mockpk}
+We remind readers that the LasDamas mock catalogue has an overall greater $\overline{P(k)}$ due to the fact that the catalogue spans the SDSS LRG sample redshift range instead of the BOSS redshift range of the other mock catalogues.} \label{fig:mockpk}
 \end{center}
@@
 
-For LasDamas, QPM, and Tiling mock catalogues we use the above FKP estimator to measure the power spectrum, Figure \ref{fig:mockpk}.
+For LasDamas, QPM, and Tiling mock catalogues we use the above FKP estimator to measure the power spectrum in Figure \ref{fig:mockpk}.
 For the $P(k)$ in Figure \ref{fig:mockpk}, we do not apply the fiber-collisions to the catalogues.
 Therefore, there are no complications from using the exact formulation of Equation \ref{eq:fkppk}.
-However, when we calculate $P(k)$ for BOSS DR12 data in Figure \ref{fig:mockpk} (\cmasscolor), the systematic weights assigned to the galaxies that account for sector completeness, redshift failures, and fiber-collisions,
+When we calculate $P(k)$ for BOSS Data Release 12 data (\cmasscolor) in Figure \ref{fig:mockpk}, however, the systematic weights assigned to the galaxies that account for sector completeness, redshift failures, and fiber-collisions,
 \begin{equation} \label{eq:weight}
@@
 Hence, instead of the galaxy density $n_g({\bf r})$ we use a weighted galaxy density $n'_g({\bf r}) = n_g({\bf r}) w({\bf r})$ and instead of $\alpha = N_{\mathrm{gal}}/N_\mathrm{ran}$ we use $\alpha ' = N'_\mathrm{gal}/N_\mathrm{ran}$ where $N'_\mathrm{gal} = \sum_\mathrm{gal} w_\mathrm{tot}$.
-For LasDamas and QPM, which have multiple mock catalogues, we compute the sample variance of the power spectrum
+For LasDamas and QPM, which have multiple realizations, we compute the sample variance of the power spectrum
 \begin{equation} \label{eq:pk_var}
-\Delta P (k)= \sqrt{\frac{1}{N_\mathrm{mock}} \sum\limits_i^{N_\mathrm{mock}} (P_i(k)- \overline{P(k)})^2 }. 
+\Delta P (k)= \sqrt{\frac{1}{N_\mathrm{realization}} \sum\limits_i^{N_\mathrm{realization}} (P_i(k)- \overline{P(k)})^2 }. 
 \end{equation}
+$N_\mathrm{realization}$ is the total number of realizations (40 for LasDamas and 1000 for QPM) and $P_i(k)$ is the power spectrum for each realization.
 $\Delta P(k)$ is represented by the width of the $P(k)$ in Figure \ref{fig:mockpk}.

### 2015-03-30 fc_paper/fc_paper.tex
First round of edits on the entire paper!

@@
 Through the millions of redshifts obtained through redshift surveys, cosmological measurements such as galaxy clustering statistics are no longer dominated by uncertainties from statistical precision, but from systematic effects of the measurements.
-These redshift surveys, such as the 2dF Galaxy Redshift Survey (2dFGRS; \citealt{Colless:1999aa}) and the Sloan Digital Sky Survey-III Baryon Oscillation Spectroscopic Survey (SDSS-III BOSS; \citealt{Anderson:2012aa, Dawson:2013aa}) and future redshift surveys such as the Extended Baryon Oscillation Spectroscopic Survey (eBOSS; CITE CITE) use fiber fed spectrographs.
+These redshift surveys, such as the 2dF Galaxy Redshift Survey (2dFGRS; \citealt{Colless:1999aa}) and the Sloan Digital Sky Survey-III Baryon Oscillation Spectroscopic Survey (SDSS-III BOSS; \citealt{Anderson:2012aa, Dawson:2013aa}) and future redshift surveys such as the Extended Baryon Oscillation Spectroscopic Survey (eBOSS; {\bf WHO DO CITE?}) use fiber fed spectrographs.
 
@@
 In Figure \ref{fig:zdist}, we plot the redshift distribution for LasDamas, QPM, and Tiling Mock catalogues along with the redshift distribution of BOSS DR12 galaxies.
-The LasDamas mock catalogue, which is modeled after the SDSS LRG sample has a constant $\bar{n}(z)$ while the QPM and Tiling mock redshift distributions closely trace the observed BOSS redshift distribution.
+The LasDamas mock catalogue, which is modeled after the SDSS LRG sample has a constant $\bar{n}(z)$ over the redshift $0.16 < z< 0.44$, while the QPM and Tiling mock redshift distributions closely trace the observed BOSS redshift distribution (roughly $0.43 < z < 0.7$).
 
-% insert transition that mentions how the main clustering statistics we focus on in this paper is the Power Spectrum
-In order to measure the power spectrum for these mock catalogues in our investigation, we use the standard \cite{Feldman:1994aa} (FKP) estimator.
-Throughout the paper we use the following formalisms from \cite{Feldman:1994aa}:
+\subsection{Power Spectrum Estimator} 
+In this paper, we focus on the effects of fiber-collisions on the galaxy power spectrum out of the various clustering measurements.
+Throughout the paper, when we measure the power spectrum, we use the standard \cite{Feldman:1994aa} (hereafter FKP) estimator and the following formalisms from the FKP paper:
 \begin{equation} \label{eq:fkppk}
@@
 
-For LasDamas, QPM, and Tiling mock catalogues we use the above FKP estimator to measure the power spectrum in Figure \ref{fig:mockpk}.
-For the $P(k)$ in Figure \ref{fig:mockpk}, we do not apply the fiber-collisions to the catalogues.
-Therefore, there are no complications from using the exact formulation of Equation \ref{eq:fkppk}.
-When we calculate $P(k)$ for BOSS Data Release 12 data (\cmasscolor) in Figure \ref{fig:mockpk}, however, the systematic weights assigned to the galaxies that account for sector completeness, redshift failures, and fiber-collisions,
+For LasDamas, QPM, and Tiling mock catalogues we use the FKP estimator described above to measure the power spectrum in Figure \ref{fig:mockpk}.
+The fiber-collisions described in Section \ref{sec:catalog} are not applied to the mock catalogues used to calculated the $P(k)$ in Figure \ref{fig:mockpk}.
+Without fiber-collisions, we are able to use the exact formulation of Equation \ref{eq:fkppk} in the FKP $P(k)$ estimator.
+
+For the BOSS Data Release 12 $P(k)$ (\cmasscolor) in Figure \ref{fig:mockpk}, systematic weights are assigned to the galaxies in order to account for sector completeness, redshift failures, and fiber-collisions.
+Each galaxy has a statistical weight determined by,
 \begin{equation} \label{eq:weight}
@@
 \end{equation} 
-must be taken account (\citealt{Anderson:2012aa, Beutler:2014aa}).
-Hence, instead of the galaxy density $n_g({\bf r})$ we use a weighted galaxy density $n'_g({\bf r}) = n_g({\bf r}) w({\bf r})$ and instead of $\alpha = N_{\mathrm{gal}}/N_\mathrm{ran}$ we use $\alpha ' = N'_\mathrm{gal}/N_\mathrm{ran}$ where $N'_\mathrm{gal} = \sum_\mathrm{gal} w_\mathrm{tot}$.
+(\citealt{Anderson:2012aa, Beutler:2014aa}).
+As a result, we modify Equation \ref{eq:fkppk} to obtain the power spectrum.
+Instead of the galaxy density term $n_g({\bf r})$ we use a weighted galaxy density term $n'_g({\bf r}) = n_g({\bf r}) w({\bf r})$, which includes the systematic weights for each galaxy.
+Also, instead of $\alpha = N_{\mathrm{gal}}/N_\mathrm{ran}$ we use $\alpha ' = N'_\mathrm{gal}/N_\mathrm{ran}$ where $N'_\mathrm{gal} = \sum_\mathrm{gal} w_\mathrm{tot}$.
+
 For LasDamas and QPM, which have multiple realizations, we compute the sample variance of the power spectrum
@@
 Bin size of $\Delta d = 0.2$ was used to compute these $d_{\mathrm{LOS}}$ distributions.
-We focus on the peak of the distribution (discussed in \ref{sec:dlos}).} \label{fig:d_los}
+Although we focus on the peak of the distribution (discussed in \ref{sec:dlos}), the $d_\mathrm{LOS}$ distribution extends to $\sim \pm 500 \; \mathrm{Mpc}$ (not shown above).} \label{fig:d_los}
 % perhaps the range should be wider and make it full text width that way the tail can be portrayed better. Keep the same aspect ratio. 
@@
 \section{Fiber-collision Correction Method} \label{sec:fc_corr}
-To account for the systematic effects of fiber-collisions \cite{Anderson:2012aa}, for the BOSS galaxy data, most recently used a nearest-neighbor galaxy weighting scheme.
-For galaxies without resolved spectroscopic redshifts due to fiber-collisions, the entire statistical weight of the galaxy was assigned to its nearest-neighbor.
-This method assumes that all galaxies with angular separations $< 62 "$ are correlated.
-In other words, that galaxies within the fiber-collision angular scale reside in the same group or cluster.
-Consequently, galaxies that have angular separations $< 62"$ purely by coincidence (hereafter referred to as ``chance alignments") are incorrectly assumed to be gravitationally correlated and displaced significantly from its true position.
-Even for fiber-collided galaxies that reside in the same group or cluster, upweighting the nearest neighbor ignores halo-scale line-of-sight displacements.
+As mentioned above, a common approach in accounting for fiber-collisions in clustering measurements has been to use the nearest angular neighbor method (\citealt{Zehavi:2002aa, Berlind:2006aa, Anderson:2012aa}).
+For galaxies without resolved spectroscopic redshifts due to fiber-collisions, the entire statistical weight of the galaxy is assigned to its nearest angular neighbor.
+This method assumes that all galaxies with angular fiber-collision scale ($< 62 "$ for BOSS) are correlated.
+In other words, the method assumes that galaxies within the fiber-collision angular scale reside in the same halo.
+Consequently, galaxies within the angular fiber-collision scale purely by coincidence (hereafter referred to as ``chance alignments") are incorrectly assumed to be gravitationally correlated, so when their statistical weight is added to its nearest angular neighbor, they are in fact displaced significantly from its true position.
+For BOSS, the nearest angular neighbor method can displace galaxies by up to $500 \;\mathrm{Mpc}$.
+Even for fiber-collided galaxies that reside in the same group or cluster, upweighting the nearest neighbor ignores halo-scale line-of-sight displacements and places the fiber-collided galaxies on top of each other.
 
-While the nearest-neighbor method provides a reasonable estimate at large scales, in Section \ref{sec:dlos} we demonstrate that at small scales it's effects on the power spectrum are significant and outweigh sample variance.
-Furthermore, in Section \ref{sec:dlos}, we present an improved method to account for correlated fiber-collided galaxies using the line-of-sight displacement between close galaxy pairs.
-Then in Section \ref{sec:shotnoise}, we present corrections to the power spectrum estimator that further accounts for fiber-collisions through the shot-noise correction term in the estimator.
+Although the nearest-neighbor method provides a reasonable estimate at large scales, as we demonstrate in Section \ref{sec:dlos}, at small scales its effects on the power spectrum are significant and dominate sample variance.
+Afterwards, in Section \ref{sec:dlos}, we present an improved method to account for correlated fiber-collided galaxies using the line-of-sight displacement between close galaxy pairs.
+Then in Section \ref{sec:shotnoise}, we present adjustments to the FKP power spectrum estimator that properly accounts for fiber-collisions through the shot-noise correction term in the estimator.
 
@@
 It is impossible to determine in observed galaxy data whether fiber-collided galaxies without resolved spectroscopic redshift are either correlated or chance alignments.
-Fortunately, using just the close galaxy pairs with resolved redshifts (especially in the overlapping regions mentioned in Section \ref{sec:catalog}), it is possible to model the fraction of galaxy pairs that are corrected and uncorrelated.
+Fortunately, using the close galaxy pairs with resolved redshifts (mainly in the overlapping regions mentioned in Section \ref{sec:catalog}), it is possible to model the fraction of galaxy pairs that are corrected and uncorrelated.
 
-Meanwhile, for simulated mock catalogues, described in Section \ref{sec:catalog}, modeling the fiber-collided galaxy pairs is a trivial task since fiber-collisions are post-processed after the simulated galaxy positions are generated.
+Meanwhile, for simulated mock catalogues, described in Section \ref{sec:catalog}, modeling the fiber-collided galaxy pairs is a much more direct task since fiber-collisions are post-processed after the simulated galaxy positions are generated.
 Hence all redshift values are resolved regardless of angular proximity.
-With both redshifts of the fiber-collided pair galaxies, we are able to emulate the observed data by assigning nearest neighbor galaxy weights (as done in \citealt{Anderson:2012aa}).
+With both redshifts of the fiber-collided pair galaxies, the fiber-collisions we impose, or are already imposed, on the mock catalogues in Section \ref{sec:catalog} emulate the observed data by assigning nearest neighbor galaxy weights.
 So for a close galaxy pair, one galaxy (``the nearest neighbor") will have the statistical weight of both galaxies, while the other has a statistical weight of $0$.
@@
 
-After calculating the $d_{\mathrm{LOS}}$ for each of the fiber-collided pairs, in Figure \ref{fig:d_los} we present the distribution of $d_{\mathrm{LOS}}$ for LasDamas (\ldgcolor), QPM (\qpmcolor), Tiling Mock (\tmcolor), and BOSS DR12 (\cmasscolor).
-All of the $d_{\mathrm{LOS}}$ distributions contain two distinct components: a peak approximately within the range $-10\;\mathrm{Mpc} < d_{\mathrm{LOS}} < 10\;\mathrm{Mpc}$ and a flat component (hereafter "tail" component) that extends to $d_{\mathrm{LOS}}$ that encompasses the survey depth (entire range of the distribution not displayed in Figure \ref{fig:d_los}).
-We note that for the BOSS data, since we cannot compute the $d_\mathrm{LOS}$ for fiber-collided pairs without resolved spectra, the $d_\mathrm{LOS}$ distribution represents the $d_\mathrm{LOS}$ from close galaxy pairs with resolved spectroscopic redshifts, often from overlapping regions of the BOSS survey.
+After calculating the $d_{\mathrm{LOS}}$ for every fiber-collided pairs, in Figure \ref{fig:d_los} we present the distribution of $d_{\mathrm{LOS}}$ for LasDamas (\ldgcolor), QPM (\qpmcolor), Tiling Mock (\tmcolor), and BOSS DR12 (\cmasscolor).
+All of the $d_{\mathrm{LOS}}$ distributions contain two components: a peak contained within the range $-20\;\mathrm{Mpc} < d_{\mathrm{LOS}} < 20\;\mathrm{Mpc}$ and a flat component (hereafter "tail" component) outside the peak that extends to $d_{\mathrm{LOS}} \sim \pm 500 \;\mathrm{Mpc}$ (entire range of the distribution not displayed in Figure \ref{fig:d_los}).
+For the BOSS data, since we cannot compute the $d_\mathrm{LOS}$ for fiber-collided pairs without resolved spectra, the $d_\mathrm{LOS}$ distribution only reflects the $d_\mathrm{LOS}$ from fiber-colldied pairs {\em with} resolved spectroscopic redshifts, mostly from tile overlapping regions of the BOSS survey.
 
-Galaxies that are in the same groups or clusters, due to their gravitational interactions at halo-scales, are more likely to be in close angular proximity with each other.
+Galaxies within the same halo, due to their gravitational interactions at halo-scales, are more likely to be in close angular proximity with each other.
 These galaxies in over-dense regions cause the peak in the $d_{\mathrm{LOS}}$ distribution.
-While the ``tail" component is composed of galaxy pairs that are arbitrarily in close angular proximity even when they are not correlated.
+While the ``tail" component is composed of chance alignment galaxy pairs that are arbitrarily in close angular proximity even when they are not correlated.
 
-Focusing on the peak of the distribution, we note that it closely traces an exponential function. Therefore, we fit an exponential of the form, 
+Focusing on the peak of the distribution, we note that it closely traces an Gaussian function. Therefore, we fit a Gaussian of the form, 
 \begin{equation} \label{eq:peak} 
-p(d_{\mathrm{LOS}}) = A \; e^{-|d_{\mathrm{LOS}}|/\sigma}
+p(d_{\mathrm{LOS}}) = A \; e^{-{d_{\mathrm{LOS}}^2}/{2\sigma^2}}
 \end{equation}
@@
 We list the values of $\sigma$ obtained for the mock catalogues in Table \ref{tab:mpfit}.
-Both Table \ref{tab:mpfit} and Figure \ref{fig:d_los} illustrate that the $d_{\mathrm{LOS}}$ distributions for the mock catalogues closely trace the distribution of the BOSS DR12, which further goes to support our use of mock catalogues to test our fiber-collision correction method.
+Both Table \ref{tab:mpfit} and Figure \ref{fig:d_los} illustrate that the $d_{\mathrm{LOS}}$ distributions for the mock catalogues closely trace the distribution of the BOSS DR12, which further goes to support the use of mock catalogues in our investigation of fiber-collisions.
 
@@
  \begin{tabular}{ccc} \hline \hline
-Catalogue &$\sigma$ ($h^{-1}\mathrm{Mpc}$) & $f_{\mathrm{peak}}$\\ \hline
+Catalogue &$\sigma$ ($\mathrm{Mpc}$) & $f_{\mathrm{peak}}$\\ \hline
 Las Damas 	& 6.85	& 0.71 \\ 
@@
 
-Using the exponential fits to the peak of the $d_{\mathrm{LOS}}$ distribution, we can also estimate the fraction of fiber-collided pairs that are within the peak: 
+Using the best-fit to the peak of the $d_{\mathrm{LOS}}$ distribution, we estimate the fraction of fiber-collided pairs that are within the peak: 
 \begin{equation}
@@
 
-As stated earlier, the current method of accounting for fiber-collisions uses the nearest-neighbor upweighting scheme (hereafter NN-upweighting).
-For this method to be completely correct, the $d_{\mathrm{LOS}}$ distribution would have to be a delta function, which as Figure \ref{fig:d_los} demonstrates is not the case.
+For the most commonly used nearest angular neighbor method (hereafter NN) to be completely correct, the $d_{\mathrm{LOS}}$ distribution in Figure \ref{fig:d_los} would have to be a delta function, which is clearly not the case.
 By simply incorporating the peak of the $d_{\mathrm{LOS}}$ distribution, we are able to significantly improve clustering statistics on small scales.
-Rather than placing the fiber-collided galaxy on top of its nearest neighbor, as NN-upweighting does, placing the fiber-collided galaxy at displacement sampled from the $d_{\mathrm{LOS}}$ distribution, away from the nearest neighbor better accounts for the small scale clustering measurements.
-On mock catalogues, we test this by first applying the NN upweighting in the same way as it is applied in the BOSS DR12 catalogue to the mock catalogues.
+Rather than placing the fiber-collided galaxy on top of its nearest angular neighbor as NN does, placing the fiber-collided galaxy at a displacement sampled from the $d_{\mathrm{LOS}}$ distribution, away from its nearest neighbor better accounts for the small scale in clustering measurements.
+On mock catalogues, we test this by first applying the NN to the mock catalogues.
 We then sample a displacement $d_i$ from $p(d_\mathrm{LOS})$ (Equation \ref{eq:peak}) for each fiber-collided pair.
-Afterwards we ``place" the fiber-collided galaxy a distance $d_i$ from the upweighted galaxy and reduce the statistical weight of the upweighted galaxy (the nearest-neighbor) by 1.
-We refer to this method as ``$d_\mathrm{LOS}$-peak.
+Afterwards we ``place" the fiber-collided galaxy a distance $d_i$ from the nearest neighbor galaxy and reduce the statistical weight of the the nearest-neighbor by 1.
+We refer to this method as ``$d_\mathrm{LOS}$-peak".
 
@@
 \includegraphics[scale=0.55]{fcpaper_pk_peakonly_comp.png} 
-\caption{The ratio of $P(k)$ using the nearest-neighbor upweighting (blue) and $d_\mathrm{LOS}$ distribution peak fiber-collision correction (orange) over the true $P(k)$ for LasDamas (left panel), QPM (middle panel), and Tiling Mock (right panel) catalogues.
-}\label{fig:peakonly}
+\caption{The ratio of $\overline{P(k)}$ using the nearest-neighbor (NN) correction (blue) and $d_\mathrm{LOS}$-peak correction (orange) over the true $\overline{P(k)}$ for LasDamas (left panel), QPM (middle panel), and Tiling Mock (right panel) catalogues.
+The ratio of the sample variance to the true $\overline{P(k)}$, $\Delta P_\mathrm{true}(k) / \overline{P_\mathrm{true}(k)}$ (black; dashed), is plotted for comparison.
+The NN correction and $d_\mathrm{LOS}$-peak correction methods are described in Section \ref{sec:dlos}.
+Incorporating the $d_{\mathrm{LOS}}$ distribution significantly improves the correction of fiber-collisions; however, both methods dominate the sample variance at $k > 0.3 \; h/\mathrm{Mpc}$.}\label{fig:peakonly}
 \end{center}
@@
 
-The $d_\mathrm{LOS}$-peak correction method is only part of our correction scheme we present in this paper.
+The $d_\mathrm{LOS}$-peak correction is the first part of our correction method we present in this paper.
 Nonetheless, we test it by applying it to the mock catalogues and comparing the resulting power spectrums.
-For each of the mock catalogues (Las Damas, QPM, and Tiling Mock) we use the FKP power spectrum estimator from before to compute the power spectrums of the original mock data, the mock data with NN-upweighting, and the mock data with the $d_\mathrm{LOS}$-peak correction.
-We note that both the NN-upweighting and the $d_\mathrm{LOS}$-peak correction methods alter the redshift distribution of our samples by a negligible amount $< 1\%$.
+For each of the mock catalogues (Las Damas, QPM, and Tiling Mock) we use the FKP power spectrum estimator from before to compute the power spectrums of the original mock data, the mock data with the NN correction, and the mock data with the $d_\mathrm{LOS}$-peak correction.
+We note that both the NN and the $d_\mathrm{LOS}$-peak correction methods alter the redshift distribution of our samples by a negligible amount $< 1\%$.
 Therefore, the synthetic random catalogues and the $\bar{n}(z)$ values do not need to be adjusted in the FKP $P(k)$ calculations.
 
-Since we are interested in how well these fiber-collision considerations can reproduce the power spectrum without fiber collisions (the ``true" power spectrum, unsullied by systematic effects), in Figure \ref{fig:peakonly} we plot the ratio of the average power spectrum $P(k)$ computed from corrected mock catalogues over the average $P(k)$ from the original mock catalogues, $\overline{P_{\mathrm{corr}}(k)}/\overline{P_\mathrm{true}(k)}$.
-The ratio for the NN upweighting scheme is plotted in blue while the ratio for the $d_{\mathrm{LOS}}$-peak correction scheme is plotted in orange.
-Also plotted is $\Delta P_\mathrm{true}(k) / \overline{P_\mathrm{true}(k)}$ (black; dashed) in order to compare the ratios to sample variance of the mock catalogues.
-For all mocks, the $P(k)$ from the NN upweighting scheme is greater than $P_\mathrm{true}(k)$ by $> 10 \%$ at $ k \sim 0.3\; h/\mathrm{Mpc}$.
-In comparison, $P(k)$ from the $d_\mathrm{LOS}$-peak correction method is $\sim 5\%$ greater than $P_\mathrm{true}(k)$ - a significant improvement.
+Since we are interested in how well fiber-collision correction methods can reproduce the power spectrum without fiber collisions (i.e.
+``true" power spectrum, unsullied by systematic effects), in Figure \ref{fig:peakonly} we plot the ratio of the average power spectrum $\overline{P(k)}$ (averaged over the realizations) computed from corrected mock catalogues over the $\overline{P(k)}$ from the original mock catalogues: $\overline{P_{\mathrm{corr}}(k)}/\overline{P_\mathrm{true}(k)}$.
+The ratio for the NN method is plotted in blue while the ratio for the $d_{\mathrm{LOS}}$-peak correction is plotted in orange.
+We also plot $\Delta P_\mathrm{true}(k) / \overline{P_\mathrm{true}(k)}$ (black; dashed) in order to compare the ratios to sample variance of the mock catalogues.
+At large scales ($k < 0.1 \; h/\mathrm{Mpc}$), for all mock catalogues, both fiber-collision methods are able to reasonably reconstruct the true power spectrum.
+At small scales on the other than, the NN corrected $\overline{P(k)}$ is greater than $\overline{P_\mathrm{true}(k)}$ by $> 10 \%$ at $ k \sim 0.3\; h/\mathrm{Mpc}$.
+In comparison, the $d_\mathrm{LOS}$-peak corrected $\overline{P(k)}$ is $\sim 5\%$ greater than $P_\mathrm{true}(k)$ at $k \sim 0.3 \; h/\mathrm{Mpc}$ - a significant improvement.
+{\bf include more description of even smaller scales when the figures are ready}.
 
-Comparing the NN-upweighting and the $d_\mathrm{LOS}$-peak methods to the sample variance ($\Delta P_\mathrm{true}(k) / \overline{P_\mathrm{true}(k)}$), reveal that neither of these methods provide a sufficient correction for the fiber-collision at $k > 0.1\; h/\mathrm{Mpc}$.
-The $P(k)$s obtained from these methods are dominated by systematics on small scales.
-Furthermore, the $d_\mathrm{LOS}$-peak method only statistically accounts for correlated pairs and does not consider uncorrelated pairs.
-Using the entire $d_\mathrm{LOS}$ distribution in order to account for uncorrelated pairs results in an overall reduction of $P(k)$ since the method displaces some close pairs that are actually correlated pairs as uncorrelated pairs and the other way around.
-Therefore, a more robust fiber-collision correction method is required.
-%detailed examination of peak only figure
+Comparing the NN method and the $d_\mathrm{LOS}$-peak correction to the sample variance ratio ($\Delta P_\mathrm{true}(k) / \overline{P_\mathrm{true}(k)}$), reveal that neither of these methods sufficiently correct for fiber-collision at $k > 0.1\; h/\mathrm{Mpc}$.
+The $P(k)$s obtained from these methods are clearly dominated by the systematic effects of fiber-collisions on small scales.
+Although the $d_\mathrm{LOS}$-peak method we propose provides an improvement from the NN method through our statistical treatment of correlated pairs within the peak of the $d_\mathrm{LOS}$ distribution, there is still room for improvement since it does not properly account for chance alignments (uncorrelated fiber-collision pairs).
+Unfortunately, an extension of the $d_\mathrm{LOS}$-peak method to the entire $d_\mathrm{LOS}$ distribution range is not feasible is not feasible because such a correction results in an overall reduction of the $P(k)$.
+This is caused by the statistical sampling of the $d_\mathrm{LOS}$, which displaces fiber-collided pairs that are actually correlated pairs as chance alignments and the other way around.
+Therefore, in the following section we provide more robust correction method to account for the chance alignment fiber-collided pairs.
 
@@
 \ref{eq:fkp_shotnoise} (blue), Eq.
-\ref{eq:my_shotnoise} (green), $P^\mathrm{Beutler}_\mathrm{shot}$ (red), and $P^{\mathrm{Gil-Marin}}_\mathrm{shot}$ (purple) over $\overline{P_\mathrm{true}(k)}$ for LasDamas (left panel), QPM (middle panel), and Tiling Mock (right panel) catalogues with nearest-neighbor fiber-collision weights.
+\ref{eq:ourshot} (green), $P^\mathrm{Beutler+}_\mathrm{shot}$ (red), and $P^{\mathrm{Gil-Marin+}}_\mathrm{shot}$ (purple) over $\overline{P_\mathrm{true}(k)}$ for LasDamas (left panel), QPM (middle panel), and Tiling Mock (right panel) catalogues with nearest-neighbor fiber-collision weights.
 Also plotted for comparison, is $\Delta P_\mathrm{true}/P_\mathrm{true}(k)$.
-For fiber-collisions  $\overline{P_\mathrm{SN}(k)}$ computed using $P^\mathrm{Beutler}_\mathrm{shot}$ only marginally improves the $\overline{P_\mathrm{SN}(k)}$ computed using $P^\mathrm{FKP}_\mathrm{shot}$.
-Both $\overline{P_\mathrm{SN}(k)}$s significantly overestimates the power spectrum.
+$\overline{P_\mathrm{SN}(k)}$ computed using Eq.
+\ref{eq:fkp_shotnoise} shot-noise correction is identical to the NN method $\overline{P_\mathrm{corr}(k)}$ presented in Figure \ref{fig:peakonly} and significantly overestimates $\overline{P_\mathrm{true}(k)}$ at $k > 0.1 \; h/\mathrm{Mpc}$.
+$\overline{P_\mathrm{SN}(k)}$ using $P^\mathrm{Beutler+}_\mathrm{shot}$ also overestimates $\overline{P_\mathrm{true}(k)}$ at $k > 0.1 \; h/\mathrm{Mpc}$.
 On the other hand $\overline{P_\mathrm{SN}(k)}$ computed using Eq.
-\ref{eq:my_shotnoise} significantly underestimates the power spectrum.
-At $k \sim 0.3\;h/\mathrm{Mpc}$, only $\overline{P_\mathrm{SN}(k)}$ computed using $P^\mathrm{Gil-Marin}_\mathrm{shot}$ reduces the effect of fiber-collisions below sample variance.
+\ref{eq:ourshot} significantly underestimates the power spectrum at $k > 0.1 \; h/\mathrm{Mpc}$.
+At these small scales, only $\overline{P_\mathrm{SN}(k)}$ computed using $P^\mathrm{Gil-Marin+}_\mathrm{shot}$ provides a reasonable correction for fiber-collisions ($\overline{P^\mathrm{Gil-Marin-SN}(k)}/\overline{P_\mathrm{true}(k)} -1 \sim 2.5 \%$), reducing its effect below sample variance.
 } \label{fig:shotnoise}
@@
 \subsection{Shot Noise Correction} \label{sec:shotnoise} 
-Both the NN-upweighting and the $d_\mathrm{LOS}$-peak correction schemes do not sufficiently account for the systematic effects of fiber-collisions in the power spectrum.
-In this section we introduce the other part of our fiber-collision correction method that involve the shot-noise correction term of the power spectrum estimator.
-%Besides illustrating the short comings of the NN-upweighting scheme and also the $d_\mathrm{LOS}$ distribution peak correction scheme, in Section \ref{sec:dlos}, we briefly mentioned that the \cite{Feldman:1994aa} power spectrum estimator was used to compute the power spectrum.
-% possibly insert summary of the actual power spectrum estimator calculation
+Both the NN method and the $d_\mathrm{LOS}$-peak correction do not sufficiently account for the systematic effects of fiber-collisions in the power spectrum.
+In this section we introduce the other part of our fiber-collision correction method that involve the shot-noise correction term of the FKP power spectrum estimator.
+By adjusting the shot noise term of the FKP estimator, we present a more robust correction method that accounts for the chance aligned fiber-collided pairs.
 
@@
 In their estimator, to account for the discreteness of the density field, they subtract the shot-noise contribution to the power spectrum (Equation \ref{eq:fkppk}):
-\begin{equation} \label{eq:fkp_shotnoise}
+\begin{equation}
 P_\mathrm{shot} = \frac{ (1+\alpha) \int d^3r \;\bar{n}({\bf r})w^2({\bf r})}{\int d^3r \;\bar{n}^2({\bf r})w^2({\bf r})}. 
@@
 With this conversion,
-\begin{equation}
+\begin{equation} \label{eq:fkp_shotnoise}
 P^\mathrm{FKP}_\mathrm{shot} = \frac{(1+\alpha) \alpha \sum\limits_{\mathrm{random}} w_\mathrm{FKP}^2({\bf r})}{\alpha \sum\limits_{\mathrm{random}}w_\mathrm{FKP}^2({\bf r})}.
@@
 \end{equation}
-In this form, systematic weights for galaxies can be accounted for in $w_g$ and $\alpha$.
+In this form, systematic weights for galaxies can be accounted for in the $w_g$ and $\alpha$ terms.
 
 Following the latter formulation, most recently, both \cite{Beutler:2014aa} and \cite{Gil-Marin:2014aa} formulate $P_\mathrm{shot}$ to account for systematic bias in their analysis of BOSS data.
-However, they treat systematic weights differently in their derivation.
+However, systematic weights are treated differently in each of their derivation.
 Keeping in mind the weights listed in Eq.
@@
 \begin{equation} \label{eq:florian}
-P^\mathrm{Beutler}_\mathrm{shot} = \frac{\sum\limits_{\mathrm{galaxy}} w^2_\mathrm{FKP}w_\mathrm{tot}({\bf r})w_\mathrm{sys}({\bf r}) - \alpha'^2 \sum\limits_{\mathrm{random}} w_\mathrm{FKP}^2({\bf r})}{\alpha' \sum\limits_{\mathrm{random}}w_\mathrm{FKP}^2({\bf r})}.
+P^\mathrm{Beutler+}_\mathrm{shot} = \frac{\sum\limits_{\mathrm{galaxy}} w^2_\mathrm{FKP}w_\mathrm{tot}({\bf r})w_\mathrm{sys}({\bf r}) - \alpha'^2 \sum\limits_{\mathrm{random}} w_\mathrm{FKP}^2({\bf r})}{\alpha' \sum\limits_{\mathrm{random}}w_\mathrm{FKP}^2({\bf r})}.
 \end{equation}
@@
 On the other hand, \cite{Gil-Marin:2014aa}, in a formulation designed to account for fiber-collisions derives $P_\mathrm{shot}$ using two separate components: one for correlated pairs and the other chance alignments.
-For the shot-noise contribution to the power from correlated pairs (referred to as ``true pairs" in \citealt{Gil-Marin:2014aa}) is equivalent to $P^\mathrm{Beu2tler}_\mathrm{shot}$ in \cite{Beutler:2014aa}.
+The shot-noise contribution to the power from correlated pairs (referred to as ``true pairs" in \citealt{Gil-Marin:2014aa}) is equivalent to Eq.
+\ref{eq:florian} above.
 For chance alignments (referred to as ``false pairs" in \citealt{Gil-Marin:2014aa}), the shot-noise contribution is derived as,
-\begin{equation}
+\begin{equation} \label{eq:gm_falsepairs}
 P^\mathrm{False}_\mathrm{shot} = \frac{\sum\limits_{\mathrm{galaxy}} w^2_\mathrm{FKP}w^2_\mathrm{tot}({\bf r}) - \alpha'^2 \sum\limits_{\mathrm{random}} w_\mathrm{FKP}^2({\bf r})}{\alpha' \sum\limits_{\mathrm{random}}w_\mathrm{FKP}^2({\bf r})}.
@@
 Then the total $P_\mathrm{shot}$ is calculated as a combination of $P^\mathrm{True}_\mathrm{shot}$ and $P^\mathrm{False}_\mathrm{shot}$: 
-\begin{equation}
-P^\mathrm{Gil-Marin}_\mathrm{shot} = (1- x_\mathrm{PS}) P^{True}_\mathrm{shot} + x_\mathrm{PS} P^{False}_\mathrm{shot}
+\begin{equation} \label{eq:gm_shot}
+P^\mathrm{Gil-Marin+}_\mathrm{shot} = (1- x_\mathrm{PS}) P^{True}_\mathrm{shot} + x_\mathrm{PS} P^{False}_\mathrm{shot}
 \end{equation}
-For the BOSS $P(k)$ \cite{Gil-Marin:2014aa} quotes $x_\mathrm{PS} = 0.58$. %motivation for the true/false pairs?
+For the BOSS $P(k)$ \cite{Gil-Marin:2014aa} quotes $x_\mathrm{PS} = 0.58$.
 
@@
 \begin{equation} \label{eq:ourshot}
-P^\mathrm{Hahn\;et\;al.}_\mathrm{shot} = \frac{\sum\limits_{\mathrm{galaxy}} w^2_\mathrm{FKP}w^2_\mathrm{tot}({\bf r}) - \alpha'^2 \sum\limits_{\mathrm{random}} w_\mathrm{FKP}^2({\bf r})}{\alpha' \sum\limits_{\mathrm{random}}w_\mathrm{FKP}^2({\bf r})}.
+P^\mathrm{Hahn+}_\mathrm{shot} = \frac{\sum\limits_{\mathrm{galaxy}} w^2_\mathrm{FKP}w^2_\mathrm{tot}({\bf r}) - \alpha'^2 \sum\limits_{\mathrm{random}} w_\mathrm{FKP}^2({\bf r})}{\alpha' \sum\limits_{\mathrm{random}}w_\mathrm{FKP}^2({\bf r})}.
 \end{equation}
-We note that this equation is equivalent to the shot-noise contribution from ``false pairs" in \cite{Gil-Marin:2014aa}. 
+The difference between Eq.
+\ref{eq:ourshot} and Eq.
+\ref{eq:florian} is in the first term of the numerator, where Eq.
+\ref{eq:florian} accounts for fiber-collisions in the $w_{\mathrm{tot}}$ term while Eq.
+\ref{eq:ourshot} accounts for fiber-collisions in the $w_\mathrm{tot}^2$ term.
+Eq.
+\ref{eq:ourshot} is equivalent to the shot-noise contribution from ``false pairs" in \cite{Gil-Marin:2014aa}.
 %In \cite{Gil-Marin:2014aa}, they justify the use of the two separate shot-noise terms with the argument that, if the fiber-collided pairs are true pairs it would not modify %insert reason 
@@
 
-In order to compare the different $P_\mathrm{shot}$ derivations, we apply each of them ($P^\mathrm{FKP}_\mathrm{shot}$,$P^\mathrm{Hahn}_\mathrm{shot}$, $P^\mathrm{Beutler}_\mathrm{shot}$, and $P^\mathrm{Gil-Marin}_\mathrm{shot}$) to the mock catalogues with nearest-neighbor fiber-collision weights applied to them.
-This comparison ignores a number of systematic effects listed in Eq.
-\ref{eq:weight} ($w_\mathrm{sys}$ and $w_\mathrm{rf}$); however, we are particularly interested in fiber-collisions.
-So in Equations 9-15, we use $w_\mathrm{sys} = 1$ and $w_\mathrm{tot} = w_\mathrm{fc}$.
+In order to compare the different $P_\mathrm{shot}$ derivations, we apply each of them ($P^\mathrm{FKP}_\mathrm{shot}$, $P^\mathrm{Hahn+}_\mathrm{shot}$, $P^\mathrm{Beutler+}_\mathrm{shot}$ and $P^\mathrm{Gil-Marin+}_\mathrm{shot}$) to the fiber-collided mock catalogues with nearest-neighbor weights.
+$P^\mathrm{FKP}_\mathrm{shot}$, $P^\mathrm{Hahn+}_\mathrm{shot}$, $P^\mathrm{Beutler+}_\mathrm{shot}$ and $P^\mathrm{Gil-Marin+}_\mathrm{shot}$ are calculated using Eq.
+\ref{eq:fkp_shotnoise}, \ref{eq:ourshot}, \ref{eq:florian} and \ref{eq:gm_shot}, respectively.
+Since we are particularly interested in fiber-collisions, our comparison ignores the other contributions to systematic effects listed in Eq.
+\ref{eq:weight} ($w_\mathrm{sys}$ and $w_\mathrm{rf}$).
+So in Equations 9 - 15, we use $w_\mathrm{sys} = 1$ and $w_\mathrm{tot} = w_\mathrm{fc}$.
 We compute the $P_\mathrm{SN}(k)$s using the various $P(k)$ estimators with different $P_\mathrm{shot}$ equations for each of the mock catalogues.
-Afterwards we compute the $\overline{P_\mathrm{SN}(k)}$s for the mock catalogues and take the ratio of them over the average $P_\mathrm{true}(k)$ using the standard FKP $P(k)$ estimator.
-Without systematic weights, the different $P_\mathrm{shot}$ equations are equivalent, so our choice of the standard FKP $P(k)$ estimator for $\overline{P_\mathrm{true}(k)}$ does not affect the comparison.
+Afterwards we compute the $\overline{P_\mathrm{SN}(k)}$s for the mock catalogues by averaging over the realizations, and then take the ratio over $\overline{P_\mathrm{true}(k)}$ calculated using the standard FKP $P(k)$ estimator.
 
-In Figure \ref{fig:shotnoise}, we present $\overline{P_\mathrm{SN}(k)}/\overline{P_\mathrm{true}(k)}$ computed using different shot noise correction term equations: $P^\mathrm{FKP}_\mathrm{shot}$,$P^\mathrm{Hahn}_\mathrm{shot}$, $P^\mathrm{Beutler}_\mathrm{shot}$, and $P^\mathrm{Gil-Marin}_\mathrm{shot}$.
-The $\overline{P(k)}$ of the NN-upweighted mocks using the standard FKP estimator is the same quantity as presented in Figure \ref{fig:peakonly} and as we noted earlier, overestimates the $\overline{P_\mathrm{true}(k)}$.
-$\overline{P_\mathrm{FKP}(k)}$ is greater than $\overline{P_\mathrm{true}(k)}$ by $> 15 \%$ at $k \sim 0.3\; h/\mathrm{Mpc}$.
-The $\overline{P(k)}$ measured using $P^\mathrm{Beutler}_\mathrm{shot}$ does not improve this overestimation in any of the mocks.
-On the other hand, the $\overline{P(k)}$ using just our shot noise equation significantly underestimates the $\overline{P_\mathrm{true}(k)}$.
-At $k \sim 0.3 \; h/\mathrm{Mpc}$, $\overline{P(k)}/\overline{P_\mathrm{true}(k)} - 1 = \sim -0.03 \%, \sim -0.08 \%, \;\mathrm{and} \sim -0.09$ for LasDamas, QPM, and Tiling Mock respectively.
-Finally, the $\overline{P(k)}$ measured using $P^\mathrm{Gil-Marin}_\mathrm{shot}$ reproduces $\overline{P_\mathrm{true}(k)}$ most accurately.
-% Insert some more specifics about Hector's accuracy
+In Figure \ref{fig:shotnoise}, we present $\overline{P_\mathrm{SN}(k)}/\overline{P_\mathrm{true}(k)}$ computed using $P^\mathrm{FKP}_\mathrm{shot}$, $P^\mathrm{Hahn+}_\mathrm{shot}$, $P^\mathrm{Beutler+}_\mathrm{shot}$ and $P^\mathrm{Gil-Marin+}_\mathrm{shot}$ shot noise correction term equations.
+We note that $\overline{P_\mathrm{SN}(k)}$ calculated using $P^\mathrm{FKP}_\mathrm{shot}$ is the same quantity as the NN corrected $\overline{P(k)}$ in Figure \ref{fig:peakonly}.
+As before, it over estimates the $\overline{P_\mathrm{true}(k)}$ by $> 10 \%$ for all mocks at $k \sim 0.3 \; h/\mathrm{Mpc}$.
+$\overline{P(k)}$ measured using $P^\mathrm{Beutler+}_\mathrm{shot}$ (Eq.
+\ref{eq:florian}) does not significantly improve this overestimation in any of the mock catalogues.
 
+On the other hand, the $\overline{P(k)}$ using Eq.
+\ref{eq:ourshot} significantly underestimates the $\overline{P_\mathrm{true}(k)}$.
+At $k \sim 0.3 \; h/\mathrm{Mpc}$, $\overline{P^\mathrm{Hahn-SN}(k)}/\overline{P_\mathrm{true}(k)} - 1 = \sim -3 \%, \sim -8 \%, \;\mathrm{and} \sim -9$ for LasDamas, QPM, and Tiling Mock respectively.
+Finally, $\overline{P(k)}$ measured using $P^\mathrm{Gil-Marin}_\mathrm{shot}$ reproduces $\overline{P_\mathrm{true}(k)}$ most accurately in the comparison of Figure \ref{fig:shotnoise}.
+At $k \sim 0.3 \; h/\mathrm{Mpc}$, $\overline{P^\mathrm{Gil-Marin-SN}(k)}/\overline{P_\mathrm{true}(k)} -1 \sim 2.5 \%$.
 As we plotted in Figure \ref{fig:peakonly}, we plot the sample variance ($\Delta P/\bar{P}$) for each of the mock catalogues in Figure \ref{fig:shotnoise}.
@@
 
-With these alterations to the power spectrum estimator in mind, we present our fiber-collision correction method in the following section .
+The shot-noise correction term we present in Eq.
+\ref{eq:ourshot} should only correct for the shot-noise contribution to the power spectrum from chance alignment fiber-collided pairs - not from correlated pairs.
+Because we apply the shot-noise correction to all fiber-collided pairs in Figure \ref{fig:shotnoise}, the shot-noise correction term over-subtracting to underestimate the true power spectrum is expected.
+In the following section we present our fiber-collision correction method, that combines the $d_\mathrm{LOS}$-peak correction of Section \ref{sec:dlos} and Eq.
+\ref{eq:ourshot} from this section.
 
@@
 Also plotted for comparison, is $\Delta P_\mathrm{true}/P_\mathrm{true}(k)$.
-We note that the $\overline{P(k)}$ ratio for our correction method is significantly lower than the $\Delta P_\mathrm{true}/P_\mathrm{true}(k)$.}\label{fig:peaksn}
+At $k \sim 0.3 \; h/\mathrm{Mpc}$, the $\overline{P(k)}$ ratio of our correction method $\sim 0.5 \%$, which is significantly better than the correction methods of \cite{Anderson:2012aa}, \cite{Beutler:2014aa} and \cite{Gil-Marin:2014aa}.
+Moreover, the $\overline{P(k)}$ ratio for our correction method is significantly lower than the $\Delta P_\mathrm{true}/P_\mathrm{true}(k)$ throughout the probed $k$ values.}\label{fig:peaksn}
 \end{center}
@@
 
-In Section \ref{sec:dlos} we derive a method to account for fiber-collisions using the peak of the $d_\mathrm{LOS}$ distribution.
-Then in Section \ref{sec:shotnoise} we compare the various formulations for the shot-noise correction term and presented our formulation.
-We now utilize both methods to devise our fiber-collision correction method.
+In Section \ref{sec:dlos} we derive a method to better statistically reconstruct the clustering of correlated fiber-collided pairs using using the peak of the $d_\mathrm{LOS}$ distribution.
+Then in Section \ref{sec:shotnoise} we presented our formulation of the shot-noise correction term, which accounts for the added discreteness from fiber-collsions.
+We now combine these two methods in order to present our fiber-collision correction method.
 
-We begin with the nearest-neighbor upweighted mock catalogues.
-With the nearest-neighbor fiber-collision weights, these mock catalogues accurately imitate the effects of fiber-collision on the real BOSS data.
+We begin with once again with the fiber-collided mock catalogues with the nearest-neighbor weights.
+These mock catalogues accurately imitate the effects of fiber-collision on the actual observed BOSS data.
 Then as described in Section \ref{sec:dlos}, we calculate the $d_\mathrm{LOS}$ distribution of all fiber-collided pairs in each mock catalogue.
-Using the $d_\mathrm{LOS}$ distribution, we compute the fraction of close pairs that are contained within the peak of the distribution ($f_\mathrm{peak}$; Section \ref{sec:dlos}).
-We then select $f_\mathrm{peak}$ of the close pairs and treat them as correlated pairs that lie in the peak of the $d_\mathrm{LOS}$ distribution.
-We refer to these close pairs as ``peak-assigned" close pairs.
+From the $d_\mathrm{LOS}$ distribution, we compute the fraction of fiber-collided pairs within the peak of the distribution ($f_\mathrm{peak}$; Section \ref{sec:dlos}).
+We then select $f_\mathrm{peak}$ of the fiber-collided pairs and designate them as correlated pairs that lie in the peak of the $d_\mathrm{LOS}$ distribution.
+We refer to these fiber-collided pairs as ``peak-assigned" pairs.
 
-Each of these ``peak-assigned" close pairs, due to the nearest-neighbor up-weighting, consist of a galaxy with $w_\mathrm{fc} > 1$ (the ``nearest-neighbor" galaxy) and another galaxy with $w_\mathrm{fc} = 0$ (the ``collided" galaxy).
+Each of these ``peak-assigned" pairs, due to the nearest-neighbor weights, consist of a galaxy with $w_\mathrm{fc} > 1$ (the ``nearest-neighbor" galaxy) and another galaxy with $w_\mathrm{fc} = 0$ (the ``collided" galaxy).
 We disregard the collided galaxy.
-For each of the nearest-neighbor galaxies, we sample a value $d$ from the peak of the $d_\mathrm{LOS}$ distribution and place a galaxy with $w_\mathrm{fc} = 1$ at a comoving distance $d$ away from the nearest-neighbor galaxy.
-At the same time, we reduce the fiber-collision weight of the nearest-neighbor galaxy by $1$.
+For each of the nearest-neighbor galaxies, we sample a value $d_\mathrm{peak-assigned}$ from the peak of the $d_\mathrm{LOS}$ distribution and place a galaxy with $w_\mathrm{fc} = 1$ at a comoving distance $d_\mathrm{peak-assigned}$ away from the nearest-neighbor galaxy.
+At the same time, we reduce $w_\mathrm{fc}$ of the nearest-neighbor galaxy (the one that was originally up-weighted) by $1$.
 This process is repeated until the nearest-neighbor galaxy has $w_\mathrm{fc} =1$.
 
-For the remaining close pairs that are not ``peak-assigned", we keep the nearest-neighbor fiber collision weights.
-The resulting mock catalogue has $f_\mathrm{peak}$ fewer galaxies with $w_\mathrm{cp} > 1$ compared to the NN-upweighted mock catalogues that we started from; however, the total statistical weight of the mock catalogue is conserved.
+For the remaining fiber-collided pairs that are not ``peak-assigned" ($1-f_\mathrm{peak}$ of the fiber-collided pairs), we keep the nearest-neighbor fiber collision weights.
+The resulting mock catalogue has $f_\mathrm{peak}$ fewer galaxies with $w_\mathrm{cp} > 1$ compared to the fiber-collided mock catalogues with nearest-neighbor weights that we started from; however, the total statistical weight of the mock catalogue is conserved.
 
-Next, we use the FKP estimator with the shot-noise correction term described in Section \ref{sec:shotnoise} Eq.
-\ref{eq:ourshot} to calculate the $P(k)$ for our newly corrected mock catalogues.
+Next, we use the FKP estimator with the Eq.
+\ref{eq:ourshot} shot-noise correction term described in Section \ref{sec:shotnoise} to calculate the $P(k)$ for our newly corrected mock catalogues.
 In Figure \ref{fig:peaksn} we present the ratio of the $\overline{P(k)}$ computed using our fiber-collision correction method over $P_\mathrm{true}(k)$.
@@
 % provide some specifics on the range of the P(k) ratio
-Furthermore for the Las Damas and QPM catalogues, the $P(k)$ ratio is significantly below the sample variance throughout the entire $k$ range probed.
+Moreover for the mock catalogues where we do have sample variance measurements (LasDamas and QPM), the $P(k)$ ratio is significantly below the sample variance throughout the entire $k$ range probed.
 
@@
 \end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% CHI-SQUARED FIGURE
 
-The correction method we present in this paper corrects for the effect of fiber-collisions to the extent where $P_\mathrm{corr}(k)$ measurements are no longer dominated by systematic effects at $k > 0.2 \; h/\mathrm{Mpc}$.
-With this in mind, we quantify the goodness-of-fit for all the corrected $P(k)$s to $P_\mathrm{true}(k)$ by comparing the the following $\chi^2$ to one another:
+The correction method we present in this paper corrects for the effect of fiber-collisions to the extent where $P_\mathrm{corr}(k)$ measurements are no longer dominated by systematic effects at the scales probed in our calculations ($k < 0.3 \; h/\mathrm{Mpc}$).
+However, to further quantify how accurately our correction method is able to reproduce the true power spectrum, we quantify the goodness-of-fit for all the corrected $P(k)$s to $P_\mathrm{true}(k)$ by calculating the following $\chi^2$:
 \begin{equation}
@@
 We calculate $\chi^2$ as a function of $k_\mathrm{max}$ in order to determine the accumulated $\chi^2$ to a specific scale ($k_\mathrm{max}$).
-In doing so, we determine the scale to which a power spectrum analysis can be extended to without suffering the significant effects of fiber-collisions.
+In doing so, we determine the scale to which a power spectrum analysis can be extended to without fiber-collisions dominating the measurement.
 
 For the Tiling Mock catalogue, since there is only one realization, the variance ($\Delta P_\mathrm{true} (k)$) cannot be computed independently.
-However, for an estimate of the $\chi^2$, we use $\Delta P_\mathrm{true}^\mathrm{Tiling\;Mock}(k)$ from $\Delta P_\mathrm{true} (k)$ of the QPM mock catalogue scaled by the ratio of the power spectrum:
+However, for an estimate of the $\chi^2$, we estimate $\Delta P_\mathrm{true}^\mathrm{Tiling\;Mock}(k)$ from $\Delta P_\mathrm{true} (k)$ of the QPM mock catalogue scaled by the ratio of the power spectrums:
 \begin{equation}
-\Delta P_\mathrm{true}^\mathrm{Tiling}(k) = \Delta P_\mathrm{true}^{QPM}(k) \times \frac{P_\mathrm{true}^\mathrm{Tiling}(k)}{\overline{P^\mathrm{QPM}_\mathrm{true}(k)}}.
+\Delta P_\mathrm{true}^\mathrm{Tiling}(k) = \Delta P_\mathrm{true}^\mathrm{QPM}(k) \times \frac{P_\mathrm{true}^\mathrm{Tiling}(k)}{\overline{P^\mathrm{QPM}_\mathrm{true}(k)}}.
 \end{equation}
 
-In Figure \ref{fig:peaksnchi2}, we present the $\chi^2(k_\mathrm{max})$ for $P(k)$ using the following fiber collision correction methods: NN-upweight, \cite{Beutler:2014aa}, \cite{Gil-Marin:2014aa}, and our method from Section \ref{sec:apply}.
-The comparison is made using the Las Damas (left panel), QPM (center panel) and Tiling (right panel) mock catalogues.
-First in the Las Damas panel, at scales $k < 5 \times 10^{-2} \; h/\mathrm{Mpc}$, $\chi^2 < 10^{-3}$ for all correction methods, which suggests that all correction methods sufficiently correct for fiber-collisions and provide a reasonable fit to $P_\mathrm{true}(k)$ at these larger scale.
+In Figure \ref{fig:peaksnchi2}, we present the $\chi^2(k_\mathrm{max})$ for $P(k)$ using the following fiber collision correction methods: the NN correction, \cite{Beutler:2014aa}, \cite{Gil-Marin:2014aa}, and our method from Section \ref{sec:apply}.
+The comparison is made using the LasDamas (left panel), QPM (center panel) and Tiling (right panel) mock catalogues.
+First in the LasDamas panel, at scales larger than $k < 5 \times 10^{-2} \; h/\mathrm{Mpc}$, $\chi^2 < 10^{-3}$ for all correction methods, which suggests that all correction methods sufficiently correct for fiber-collisions and reasonably reconstructs $P_\mathrm{true}(k)$ at these scale.
 In approaching smaller scales the $\chi^2$ for all correction methods increase.
 However, throughout the entire $k_\mathrm{max}$ range, our correction method provides a notably lower $\chi^2$ in comparison to the other correction methods.
-This is especially clear at $k \sim 0.3 \; h/\mathrm{Mpc}$, where $\chi^2_\mathrm{NN-upweight} \approx 0.33$, $\chi^2_\mathrm{Beutler} \approx 0.33$, and $\chi^2_\mathrm{Gil-Marin} \approx 0.17$ while $\chi^2 \approx 0.019$ for our method.
+This is especially clear at $k \sim 0.3 \; h/\mathrm{Mpc}$, where $\chi^2_\mathrm{NN} \approx 0.33$, $\chi^2_\mathrm{Beutler} \approx 0.33$, and $\chi^2_\mathrm{Gil-Marin} \approx 0.17$ while $\chi^2 \approx 0.019$ for our method.
 
-Next in the central QPM panel, at large scales ($k < 2 \times 10^{-2} \; h/\mathrm{Mpc}$) all corrected $P(k)$ once again provide a reasonable reconstruction of $P_\mathrm{true}(k)$ with $\chi^2 \approx 10^{-2}$.
-Then for $2 \times 10^{-2} < k_\mathrm{max} < 5 \times 10^{-2}\; h/\mathrm{Mpc}$, NN-upweight and \cite{Beutler:2014aa} correction methods have the lower $\chi^2$s than \cite{Gil-Marin:2014aa} and our correction methods.
-However, at smaller scales, the $\chi^2$s of NN-upweight and \cite{Beutler:2014aa} quickly increase beyond the $\chi^2$s of \cite{Gil-Marin:2014aa} and our methods.
-Meanwhile, throughout the entire $k_\mathrm{max}$ range our correction method has a lower $\chi^2$ than the correction method of \cite{Gil-Marin:2014aa}.
-The difference in $\chi^2$ is again most remarkable at the smallest scales: $\chi^2 (k_\mathrm{max} \sim 0.3) \approx 7.3,\;11, \;0.068, \;\mathrm{and} \; 0.0063$ for NN-upweight, \cite{Beutler:2014aa}, \cite{Gil-Marin:2014aa} and our correction method respectively.
+Next in the QPM panel (center), at scales larger than ($k < 2 \times 10^{-2} \; h/\mathrm{Mpc}$) all corrected $P(k)$ once again provide a reasonable reconstruction of $P_\mathrm{true}(k)$ with $\chi^2 \approx 10^{-2}$.
+Then for $2 \times 10^{-2} < k_\mathrm{max} < 5 \times 10^{-2}\; h/\mathrm{Mpc}$, the NN and \cite{Beutler:2014aa} correction methods have the lower $\chi^2$s than \cite{Gil-Marin:2014aa} and our correction methods.
+However, as $k$ increases, the $\chi^2$s for NN and \cite{Beutler:2014aa} quickly surpasses the $\chi^2$s of \cite{Gil-Marin:2014aa} and our method.
+Meanwhile, throughout the entire $k_\mathrm{max}$ range probed, our correction method has a significantly lower $\chi^2$ than the correction method of \cite{Gil-Marin:2014aa}.
+The difference in $\chi^2$ is again most remarkable at the smallest scales: $\chi^2 (k_\mathrm{max} \sim 0.3) \approx 7.3,\;11, \;0.068, \;\mathrm{and} \; 0.0063$ for NN, \cite{Beutler:2014aa}, \cite{Gil-Marin:2014aa} and our correction method respectively.
 
 Finally in the right panel (Tiling Mock), we find that $\chi^2(k_\mathrm{max})$ increases in a near monotonic fashion as a function of $k_\mathrm{max}$.
-For $k_\mathrm{max} < 4\times10^{-2} \; h/\mathrm{Mpc}$, there are no significant differences between the $\chi^2$s of all the correction methods.
-Then from $4\times10^{-2} < k_\mathrm{max} < 1.5\times 10^{-2} \; h/\mathrm{Mpc}$, $\chi^2$s of NN-upweight and \cite{Beutler:2014aa} are notably lower than the $\chi^2$s of \cite{Gil-Marin:2014aa} and our method.
-However at smaller scales, the $\chi^2$s of NN-upweight and \cite{Beutler:2014aa} quickly rise beyond the other $\chi^2$s, ultimately both reach $\chi^2(k_\mathrm{max} \sim 0.3) \approx 13.5$.
+For $k_\mathrm{max} < 4\times10^{-2} \; h/\mathrm{Mpc}$, there are no significant differences between the $\chi^2$s of any of the correction methods.
+Then at intermediate scales of $4\times10^{-2} < k_\mathrm{max} < 1.5\times 10^{-2} \; h/\mathrm{Mpc}$, $\chi^2$s of NN and \cite{Beutler:2014aa} are notably lower than the $\chi^2$s of \cite{Gil-Marin:2014aa} and our method.
+However like the other mock catalogues at smaller scales, the $\chi^2$s of NN and \cite{Beutler:2014aa} quickly increase beyond the other $\chi^2$s, ultimately both reach $\chi^2(k_\mathrm{max} \sim 0.3) \approx 13.5$.
 In the meantime, $\chi^2(k_\mathrm{max} \sim 0.3) \approx 0.32$ for \cite{Gil-Marin:2014aa} and $\chi^2(k_\mathrm{max} \sim 0.3) \approx 0.15$ for our correction method.
-Moreover, through the entire $k_\mathrm{max}$ our method has a lower $\chi^2$ than \cite{Gil-Marin:2014aa}.
+Throughout the entire $k_\mathrm{max}$ our method has a lower $\chi^2$ than \cite{Gil-Marin:2014aa}.
 With only one realization of the Tiling Mocks and scaled $\Delta P$, a detailed comparison of the $\chi^2$ values is impossible.
@@
 Overall, regardless of catalogue, for scales $k_\mathrm{max} < 3 \times 10^{-2} \;h/\mathrm{Mpc}$, the $\chi^2$ for all fiber-collision corrected $P(k)$ are negligible.
-Then, with the exception of the Las Damas catalogue, at intermediate scales of $3 \times 10^{-2} < k_\mathrm{max} < 0.15 \; h/\mathrm{Mpc}$ the NN-upweight and \cite{Beutler:2014aa} methods show the lowest $\chi^2$s.
-At the smallest scales, however, these corrections methods no longer provide a good fit to $\overline{P_\mathrm{true}(k)}$.
+Then, with the exception of the Las Damas catalogue, at intermediate scales of $3 \times 10^{-2} < k_\mathrm{max} < 0.15 \; h/\mathrm{Mpc}$ the NN and \cite{Beutler:2014aa} methods show the lowest $\chi^2$s.
+However at these intermediate scales, all of the correction methods reasonably reconstruction of the true power spectrum with $\chi^2 < 1$.
+At the smallest scales, NN and \cite{Beutler:2014aa} corrections methods no longer provide a sufficient fit to $\overline{P_\mathrm{true}(k)}$.
 A detailed comparison at the small scales ($k > 1.5 \times 10^{-1} \;h/\mathrm{Mpc}$) demonstrates that the fiber-collision correction we present in this paper significantly better reproduces the true power spectrum than any of the other fiber-collision correction methods.
-Furthermore, Figure \ref{fig:peaksnchi2} illustrates that throughout the entire $k_\mathrm{max}$ is able to reasonably reproduces $P_\mathrm{true}(k)$ at all scales.
-
+Furthermore, Figure \ref{fig:peaksnchi2} illustrates that throughout the entire $k_\mathrm{max}$, our correction method is able to reasonably reproduce $P_\mathrm{true}(k)$ at all scales.
 % Detailed comparison to Gil-Marin that talk about how the xps value he calculates is only validated through mock catalogues, but our method can be validated with the overlapping regions of the real data.
@@
 \section{Summary and Discussion} \label{sec:summary}
-Using simulated mock catalogues for SDSS data with realistically imposed fiber-collisions, we quantify the systematic effects of fiber-collisions on galaxy clustering statistics, in particular the power spectrum.
+Using simulated mock catalogues for SDSS data with realistically imposed fiber-collisions, we quantify the systematic effects of fiber-collisions on galaxy clustering measurements - in particular the power spectrum.
 Although fiber-collisions have little significant effect on the power spectrum at large scales, its effect quickly overtakes the sample variance at scales smaller than $k \sim 0.1 \;h/\mathrm{Mpc}$.
 At the smallest scales that we explore in this paper, $k \sim 0.3$, fiber-collisions have over a $10 \%$ effect on the power spectrum.
-Consequently, at these small scales the uncertainties for power spectrum measurements are dominated by systematic effects from fiber-collisions.
+Consequently, at these small scales measurements of the power spectrum is dominated by the uncertainties from systematic effects of fiber-collisions.
 
 Fortunately, through the fiber-collided mock catalogues we are able to model the distribution of the line-of-sight displacement between fiber-collided pairs.
-Combining this model with a modified shot-noise term in the power spectrum estimator, we devise a new fiber-collision correction method that is able to reconstruct the true power spectrum from fiber-collided data even to $k \sim 0.3 \;h/\mathrm{Mpc}$.
-Throughout the entire $k$ range explored in our analysis, our correction method reconstructs $P_\mathrm{True}(k)$ safely within the sample variance.
+Using this model, we are able to statistically reconstruct the clustering fiber-collided galaxies that reside in the same halo.
+Combining this correction with a modification of the shot-noise term in the power spectrum estimator to properly account for the discreteness added by the nearest-neighbor weights of chance aligned fiber-collided pairs, we devise a new fiber-collision correction method that is able to reconstruct the true power spectrum from fiber-collided data even to $k \sim 0.3 \;h/\mathrm{Mpc}$.
+Throughout the entire $k$ range explored in our analysis, our correction method reconstructs $P_\mathrm{true}(k)$ safely within the sample variance.
 
-Furthermore, we compare our method to the most common nearest-neighbor correction method and recent correction methods presented in \cite{Beutler:2014aa} and \cite{Gil-Marin:2014aa} to demonstrate that our method most successfully reproduces the true power spectrum at small scales for all the Las Damas, QPM, and Tiling mock catalogues.
+Furthermore, we compare our method to the most common nearest-neighbor correction method and recent correction methods presented in \cite{Beutler:2014aa} and \cite{Gil-Marin:2014aa} to demonstrate that our method most successfully reproduces the true power spectrum at small scales and reliably at all scales for all the Las Damas, QPM, and Tiling mock catalogues.
 As an added advantage, our correction method can also be validated by actual data rather than only through the mock catalogues thereby making it's application to actual data further reliable.
 
-The fiber-collision correction method we present will enable us to extend our galaxy clustering analysis to smaller scales for SDSS-III BOSS and future surveys such as eBOSS or any other large fiber-fed surveys.
-Our fiber-collision correction method can also be extend to higher order clustering statistics such as the bispectrum, which we will explore in future work.
+The fiber-collision correction method we present will enable us to extend our galaxy clustering analysis to smaller scales for SDSS-III BOSS and future surveys such as eBOSS or any other large fiber-fed surveys the suffer from systematic effects of fiber-collisions.
+Our fiber-collision correction method can also be extend to higher order clustering statistics such as the quadrupole of the power spectrum and the bispectrum, which we will explore in future work.
 

### 2015-03-31 fc_paper/fc_paper.tex
minor edit

@@
 
-Furthermore, we compare our method to the most common nearest-neighbor correction method and recent correction methods presented in \cite{Beutler:2014aa} and \cite{Gil-Marin:2014aa} to demonstrate that our method most successfully reproduces the true power spectrum at small scales and reliably at all scales for all the Las Damas, QPM, and Tiling mock catalogues.
+Furthermore, we compare our method to the most common nearest-neighbor correction method and recent correction methods presented in \cite{Beutler:2014aa} and \cite{Gil-Marin:2014aa} to demonstrate that our method most successfully reproduces the true power spectrum at small scales and most reliably at all scales for all the Las Damas, QPM, and Tiling mock catalogues.
 As an added advantage, our correction method can also be validated by actual data rather than only through the mock catalogues thereby making it's application to actual data further reliable.

### 2015-03-31 fc_paper/fc_paper.tex
Round 2 of edits throughout the paper.
Still needs updated numbers from Ngrid=960

--- 2015-03-30 fc_paper/fc_paper.tex
@@
 Fiber-fed multi-object spectroscopic surveys, with their ability to collect an unprecedented number of redshifts, dominate cosmological studies.
-However, the physical size of the fibers limit these surveys from successfully collecting redshifts from galaxies within the angular fiber-collision scale, which ultimately lead to significant systematic effects on galaxy clustering measurements.
-Using simulated mock catalogues, which have been extensively used in interpreting large-scale structure clustering results (such as the correlation function and power spectrum) of the Sloan Digital Sky Survey, we investigate the effects of fiber-collisions on the galaxy power spectrum in particular.
-We compare the methods currently used to correct for fiber-collisions in the literature and assess their success in reconstructing the true power spectrum for mock catalogues.
+However the physical size of fibers limit these surveys from successfully collecting redshifts from galaxies that are within the angular fiber-collision scale of one another, which ultimately lead to significant systematic effects on galaxy clustering measurements.
+Using simulated mock catalogues, extensively used in interpreting large-scale structure clustering results of the Sloan Digital Sky Survey, we investigate the effects of fiber-collisions on the galaxy power spectrum and compare the methods currently used to correct for fiber-collisions in the literature and assess their success in reconstructing the true power spectrum.
 
-We present our fiber-collision correction method, which statistically reconstructs the clustering of fiber-collided pairs, using the distribution of the line-of-sight displacements between resolved fiber-collided pairs, and properly accounts for fiber-collisions in the shot-noise correction term of the power spectrum estimator.
-Using our method, we successfully reproduce the true power spectrum for the mock catalogues with residuals of $\sim 1\%$ at $k \sim 0.3 \; h/\mathrm{Mpc}$ and $< 10\%$ at $k \sim 0.8 \; h/\mathrm{Mpc}$.
-Our comparisons to other correction methods demonstrate that our method most accurately reconstructs the true power spectrum from fiber-collided data especially at small scales ($k > 0.1\; h/\mathrm{Mpc}$), with the added advantage that the method can be validated and calibrated in actual observations.
-With statistical precision no longer obstructing galaxy clustering measurements, our correction method will allows us constrain systematic effects of fiber-collisions and extend power spectrum measurements to smaller scales.
+We present our fiber-collision correction method, which first statistically reconstructs the clustering of fiber-collided pairs by modeling the distribution of the line-of-sight displacements between them, and then properly accounts for fiber-collisions in the shot-noise correction term of the power spectrum estimator.
+Using our method, we successfully reproduce the true power spectrum for the mock catalogues with residuals of $< 1\%$ at $k \sim 0.3 \; h/\mathrm{Mpc}$ and $< 10\%$ at $k \sim 0.8 \; h/\mathrm{Mpc}$.
+Our comparisons to other correction methods demonstrate that our method most accurately reconstructs the true power spectrum from fiber-collided galaxy data especially at small scales ($k > 0.1\; h/\mathrm{Mpc}$), with the added advantage that our method can be validated and calibrated in observed data.
+With statistical uncertainty no longer dominating galaxy clustering measurements, our correction method will allows us constrain a main contributor to systematic effects and extend power spectrum measurements to smaller scales.
 \end{abstract}
@@
 Through the millions of redshifts obtained through redshift surveys, cosmological measurements such as galaxy clustering statistics are no longer dominated by uncertainties from statistical precision, but from systematic effects of the measurements.
-These redshift surveys, such as the 2dF Galaxy Redshift Survey (2dFGRS; \citealt{Colless:1999aa}) and the Sloan Digital Sky Survey-III Baryon Oscillation Spectroscopic Survey (SDSS-III BOSS; \citealt{Anderson:2012aa, Dawson:2013aa}) and future redshift surveys such as the Extended Baryon Oscillation Spectroscopic Survey (eBOSS; {\bf WHO DO CITE?}) use fiber fed spectrographs.
+These surveys, such as the 2dF Galaxy Redshift Survey (2dFGRS; \citealt{Colless:1999aa}) and the Sloan Digital Sky Survey-III Baryon Oscillation Spectroscopic Survey (SDSS-III BOSS; \citealt{Anderson:2012aa, Dawson:2013aa}) and future surveys such as the Extended Baryon Oscillation Spectroscopic Survey (eBOSS; {\bf WHO DO CITE?}) use fiber-fed spectrographs.
 
@@
 
-As our cosmological surveys extend further to higher redshifts, the systematic effect becomes worse as the fiber-collision angular scale corresponds to a larger comoving scale, thereby affecting our measurements on larger scales.
+As our cosmological surveys extend further to higher redshifts, the systematic effect becomes more severe as the fiber-collision angular scale corresponds to a larger comoving scale, thereby affecting our measurements on larger scales.
 SDSS-III BOSS, in particular, has an angular fiber-collision scale of $62"$.
-This corresponds to $\sim 0.4 \;\mathrm{Mpc}/h$ at the center of the survey redshift redshift range, and fiber-collided galaxies account for $\sim 5\%$ of the galaxy sample (\citealt{Anderson:2012aa}).
+This corresponds to $\sim 0.4 \;\mathrm{Mpc}/h$ at the center of the survey's redshift redshift range; fiber-collided galaxies account for $\sim 5\%$ of the galaxy sample (\citealt{Anderson:2012aa}).
 Although this accounts for a relatively small fraction of redshifts, its effect on clustering measurements such as the power spectrum is significant and must be understood as these measurements probe to smaller scales and as higher order statistics such as the three-point correlation function or the bispectrum are used in cosmological studies.
@@
 For power spectrum measurements in BOSS, the nearest neighbor method has often been supplemented with adjustments in the constant shot-noise term of the power spectrum estimator to correct for fiber-collisions (\citealt{Beutler:2014aa, Gil-Marin:2014aa}).
-While this shot-noise term adjustment has been calibrated within the mock catalogues used to interpret the BOSS clustering results, validating these methods for observations remains a challenge.
+While this shot-noise term adjustment has been calibrated within the mock catalogues used to interpret the BOSS clustering results there is no way to validate and calibrate these methods independently for observations.
+Methods of this kind rely entirely on the accuracy of the mock catalogues to constrain fiber-collisions, which is especially concerning since fiber-collisions systematically affect small scales and mock catalogues may not be realiable at such small scales (\citealt{Heitmann:2008aa, Schneider:2015aa}).
 
@@
 Unfortunately, this method cannot be applied to the Fourier clustering measurements due to the complex geometry of the overlapping regions.
-As a result, we propose a fiber-collision correction method that, first, improves upon the nearest neighbor method by using the distribution of the line-of-sight displacement between resolved fiber-collided galaxies to statistically reconstruct the clustering of fiber-collided galaxies; and proper accounts for fiber-collisions in the shot-noise correction term of the power spectrum estimator.
+As a result, we propose a fiber-collision correction method that, first, improves upon the nearest neighbor method by using the distribution of the line-of-sight displacement between resolved fiber-collided galaxies to statistically reconstruct the clustering of fiber-collided galaxies; and properly accounts for fiber-collisions in the shot-noise correction term of the power spectrum estimator.
 
-In Section \ref{sec:catalog}, we present a brief description of the simulated mock catalogues with realistic applied fiber-collisions and power spectrum estimator used throughout the paper.
-Then during our discussion of the two components of our correction method in Section \ref{sec:fc_corr}, we quantify the effects of fiber-collisions of power spectrum measurements and test and compare common correction methods.
-Afterwards, we present our correction method in Section \ref{sec:apply}, test it on the mock catalogues, and compare it to other correction methods.
+In Section \ref{sec:catalog}, we present a brief description of the simulated mock catalogues with realistically applied fiber-collisions and the power spectrum estimator used throughout the paper.
+Then during our discussion of the two components of our correction method in Section \ref{sec:fc_corr}, we quantify the effects of fiber-collisions of power spectrum measurements and test and compare correction methods in the literature.
+Afterwards, we present our correction method, test it on the mock catalogues, and compare it to other correction methods in Section \ref{sec:results}.
 Finally in Section \ref{sec:summary} we summarize and discuss our results.
@@
 \includegraphics[scale=0.45]{fcpaper_z_dist.png} \label{fig:zdist}
-\caption{Normalized galaxy redshift distribution for Las Damas (\ldgcolor), QPM (\qpmcolor), and Tiling Mock (\tmcolor) mock catalogues.
+\caption{Normalized galaxy redshift distribution for LasDamas (\ldgcolor), QPM (\qpmcolor), and Tiling Mock (\tmcolor) mock catalogues.
 The normalized redshift distribution of BOSS DR12 CMASS is also plotted (\cmasscolor).
-Bin size of $\Delta z = 0.025$ was used to compute the distributions.
-Las Damas mock catalogue has a constant number density of galaxies throughout its redshift range ($0.16 < z < 0.44$).
+Bin size of $\Delta z = 0.025$ was used to compute the each of the distributions.
+LasDamas mock catalogue has a constant number density of galaxies throughout $0.16 < z < 0.44$, the redshift range of SDSS LRG sample.
 QPM and Tiling Mock catalogues, on the other hand, trace the BOSS CMASS redshift distribution ($0.43 < z < 0.7$).}
@@
 
-Effects of fiber-collisions must be understood and interpreted in conjunction with these systematic effects.
+Effects of fiber-collisions must be understood and interpreted in conjunction with these other systematic effects.
 Therefore, in this paper, we use LasDamas (\citealt{McBride:2009aa, McBride:2011aa}), Quick Particle Mesh (\citealt{White:2014aa}), and Tiling mock catalogues, which have already been extensively used in interpreting clustering results for SDSS and BOSS and are generated through different prescriptions.
-Therefore they provide complementary tests fiber-collisions and our correction method tailored for BOSS.
-
-Each of these mock catalogues use some sort of N-body dark matter simulation along with a HOD prescription to populate the dark matter halos with ``galaxies".
+Therefore they provide complementary data sets to measure the effects of fiber-collisions and to test our correction method tailored for BOSS.
+%Each of these mock catalogues use some sort of N-body dark matter simulation along with a HOD prescription to populate the dark matter halos with ``galaxies".
 % Include brief detail on what each mock has to offer
@@
 
-Next, the QPM mock galaxy catalogues uses a "quick particle mesh" method, which uses a low resolution particle-mesh N-body solver to evolve particles within a period simulation volume.
+Next, the QPM mock galaxy catalogues uses a ``quick particle mesh" method, which uses a low resolution particle-mesh N-body solver to evolve particles within a period simulation volume.
 The particles are assigned halo masses  in order to match the halo mass function and large-scale bias of halos of high resolution simulations.
@@
 In Figure \ref{fig:zdist}, we plot the redshift distribution for LasDamas, QPM, and Tiling Mock catalogues along with the redshift distribution of BOSS DR12 galaxies.
-The LasDamas mock catalogue, which is modeled after the SDSS LRG sample has a constant $\bar{n}(z)$ over the redshift $0.16 < z< 0.44$, while the QPM and Tiling mock redshift distributions closely trace the observed BOSS redshift distribution (roughly $0.43 < z < 0.7$).
+The LasDamas mock catalogue, which is constructed based on the SDSS LRG sample has a constant $\bar{n}(z)$ over the redshift $0.16 < z< 0.44$, while the QPM and Tiling mock redshift distributions closely trace the observed BOSS redshift distribution (roughly $0.43 < z < 0.7$).
 
-\subsection{Power Spectrum Estimator} 
-In this paper, we focus on the effects of fiber-collisions on the galaxy power spectrum out of the various clustering measurements.
+\subsection{Power Spectrum Estimator} \label{sec:pk_est}
+In this paper, we focus on the effects of fiber-collisions on the galaxy power spectrum out of the other clustering measurements.
 Throughout the paper, when we measure the power spectrum, we use the standard \cite{Feldman:1994aa} (hereafter FKP) estimator and the following formalisms from the FKP paper:
@@
 \includegraphics[scale=0.5]{fcpaper_pk_comp.png} 
-\caption{Average power spectrum $\overline{P(k)}$ for BOSS DR12 (black) and the mock catalogues Las Damas (blue), QPM (orange), and Tiling Mock (green), listed in Section \ref{sec:catalog} using the FKP $P(k)$ estimator.
-The width of the $P(k)$ for Las Damas and QPM represent the sample variance ($\Delta P(k)$) calculated from the multiple realizations of the mock catalogues.
+\caption{Average power spectrum $\overline{P(k)}$ for BOSS DR12 (black) and the mock catalogues LasDamas (blue), QPM (orange), and Tiling Mock (green), listed in Section \ref{sec:catalog} using the FKP $P(k)$ estimator.
+The width of the $P(k)$ for LasDamas and QPM represent the sample variance ($\Delta P(k)$) calculated from the multiple realizations of the mock catalogues.
 We emphasize that fiber-collisions were not applied to the mock catalogues for the $P(k)$ measurements.
@@
 For LasDamas, QPM, and Tiling mock catalogues we use the FKP estimator described above to measure the power spectrum in Figure \ref{fig:mockpk}.
-The fiber-collisions described in Section \ref{sec:catalog} are not applied to the mock catalogues used to calculated the $P(k)$ in Figure \ref{fig:mockpk}.
-Without fiber-collisions, we are able to use the exact formulation of Equation \ref{eq:fkppk} in the FKP $P(k)$ estimator.
+The fiber-collisions described previously are not applied to the mock catalogues in the $P(k)$ calculations for Figure \ref{fig:mockpk}.
+Without fiber-collisions, we use the exact formulation of Equation \ref{eq:fkppk} in the FKP power spectrum estimator.
 
-For the BOSS Data Release 12 $P(k)$ (\cmasscolor) in Figure \ref{fig:mockpk}, systematic weights are assigned to the galaxies in order to account for sector completeness, redshift failures, and fiber-collisions.
+We also plot the $P(k)$ from the BOSS Data Release 12 CMASS data (\cmasscolor) in Figure \ref{fig:mockpk}.
+For BOSS DR12 CMASS, systematic weights are assigned to the galaxies in order to account for sector completeness, redshift failures, and fiber-collisions.
 Each galaxy has a statistical weight determined by,
@@
 (\citealt{Anderson:2012aa, Beutler:2014aa}).
-As a result, we modify Equation \ref{eq:fkppk} to obtain the power spectrum.
+As a result, we modify Equation \ref{eq:fkppk} when we calculate the power spectrum.
 Instead of the galaxy density term $n_g({\bf r})$ we use a weighted galaxy density term $n'_g({\bf r}) = n_g({\bf r}) w({\bf r})$, which includes the systematic weights for each galaxy.
@@
 \includegraphics[scale=0.575]{fcpaper_dlos_dist.png}
-\caption{Normalized distribution of $d_{\mathrm{LOS}}$ for Las Damas (\ldgcolor), QPM (\qpmcolor), and Tiling Mock (\tmcolor) mock catalogues.
+\caption{Normalized distribution of $d_{\mathrm{LOS}}$ for LasDamas (\ldgcolor), QPM (\qpmcolor), and Tiling Mock (\tmcolor) mock catalogues.
 The normalized $d_{\mathrm{LOS}}$ distribution of BOSS DR12 is also plotted (\cmasscolor).
-Bin size of $\Delta d = 0.2$ was used to compute these $d_{\mathrm{LOS}}$ distributions.
-Although we focus on the peak of the distribution (discussed in \ref{sec:dlos}), the $d_\mathrm{LOS}$ distribution extends to $\sim \pm 500 \; \mathrm{Mpc}$ (not shown above).} \label{fig:d_los}
+Bin size of $\Delta d = 0.2$ was used to compute the $d_{\mathrm{LOS}}$ distributions.
+The $d_\mathrm{LOS}$ distribution extends to $\sim \pm 500 \; \mathrm{Mpc}$ (not shown above).
+We focus on the peak of the distribution $-20 \; \mathrm{Mpc} < d_\mathrm{LOS} < 20 \;\mathrm{Mpc}$ (discussed in \ref{sec:dlos}).} \label{fig:d_los}
 % perhaps the range should be wider and make it full text width that way the tail can be portrayed better. Keep the same aspect ratio. 
@@
 For galaxies without resolved spectroscopic redshifts due to fiber-collisions, the entire statistical weight of the galaxy is assigned to its nearest angular neighbor.
-This method assumes that all galaxies with angular fiber-collision scale ($< 62 "$ for BOSS) are correlated.
-In other words, the method assumes that galaxies within the fiber-collision angular scale reside in the same halo.
-Consequently, galaxies within the angular fiber-collision scale purely by coincidence (hereafter referred to as ``chance alignments") are incorrectly assumed to be gravitationally correlated, so when their statistical weight is added to its nearest angular neighbor, they are in fact displaced significantly from its true position.
+This method assumes that all galaxies within the angular fiber-collision scale ($< 62 "$ for BOSS) are correlated with one another.
+In other words, the method assumes that galaxies within the fiber-collision angular scale reside in the same halo so displacing one and placing it on top of the other does not significantly alter the clustering statistics.
+One consequence of this method however is that galaxies within the angular fiber-collision scale purely by coincidence (hereafter referred to as ``chance alignments") are incorrectly assumed to be gravitationally correlated, so when their statistical weight is added to its nearest angular neighbor, they are in fact displaced significantly from its true position.
 For BOSS, the nearest angular neighbor method can displace galaxies by up to $500 \;\mathrm{Mpc}$.
-Even for fiber-collided galaxies that reside in the same group or cluster, upweighting the nearest neighbor ignores halo-scale line-of-sight displacements and places the fiber-collided galaxies on top of each other.
+Furthermore even for fiber-collided galaxies that reside in the same group or cluster, up-weighting the nearest neighbor ignores halo-scale line-of-sight displacements, which as we present in Section \ref{sec:dlos}, are significant.
 
-Although the nearest-neighbor method provides a reasonable estimate at large scales, as we demonstrate in Section \ref{sec:dlos}, at small scales its effects on the power spectrum are significant and dominate sample variance.
-Afterwards, in Section \ref{sec:dlos}, we present an improved method to account for correlated fiber-collided galaxies using the line-of-sight displacement between close galaxy pairs.
-Then in Section \ref{sec:shotnoise}, we present adjustments to the FKP power spectrum estimator that properly accounts for fiber-collisions through the shot-noise correction term in the estimator.
+Although the nearest-neighbor method provides a reasonable estimate at large scales, in Section \ref{sec:dlos} we demonstrate that at small scales its effects on the power spectrum are significant and dominate sample variance.
+We present an improved method to account for correlated fiber-collided galaxies using the line-of-sight displacement between fiber-collided pairs.
+Then in Section \ref{sec:shotnoise}, we present modifications to the FKP power spectrum estimator in order to properly account for fiber-collisions through the shot-noise correction term in the estimator.
 
@@
 \subsection{Line-of-Sight Displacement of Fiber-collided Pairs} \label{sec:dlos}
-It is impossible to determine in observed galaxy data whether fiber-collided galaxies without resolved spectroscopic redshift are either correlated or chance alignments.
-Fortunately, using the close galaxy pairs with resolved redshifts (mainly in the overlapping regions mentioned in Section \ref{sec:catalog}), it is possible to model the fraction of galaxy pairs that are corrected and uncorrelated.
+It is impossible to determine from observed galaxy data whether fiber-collided galaxies without resolved spectroscopic redshift are correlated or chance alignments.
+Fortunately, using the fiber-collided pairs with resolved redshifts (mainly in the overlapping regions mentioned in Section \ref{sec:catalog}), it is possible to model the line-of-sight displacement of the fiber-collided pairs and the fraction of galaxy pairs that are corrected and uncorrelated.
 
-Meanwhile, for simulated mock catalogues, described in Section \ref{sec:catalog}, modeling the fiber-collided galaxy pairs is a much more direct task since fiber-collisions are post-processed after the simulated galaxy positions are generated.
-Hence all redshift values are resolved regardless of angular proximity.
-With both redshifts of the fiber-collided pair galaxies, the fiber-collisions we impose, or are already imposed, on the mock catalogues in Section \ref{sec:catalog} emulate the observed data by assigning nearest neighbor galaxy weights.
-So for a close galaxy pair, one galaxy (``the nearest neighbor") will have the statistical weight of both galaxies, while the other has a statistical weight of $0$.
-Furthermore, having the redshift values of close galaxy pairs in mock catalogues, allows us to model the correlated and uncorrelated fiber-collided pairs.
+For simulated mock catalogues, described in Section \ref{sec:catalog}, modeling the fiber-collided galaxy pairs is a much more direct task since fiber-collisions are post-processed after the simulated galaxy positions are generated.
+All redshift values are provided for all galaxies regardless of angular proximity and the fiber-collisions imposed on the mock catalogues are represented through the galaxies' ``fiber-collision weights" ($w_\mathrm{fc}$).
+So for a fiber-collided pair, one galaxy (``the nearest neighbor") will have the fiber-collision weight of both galaxies, while the other has $w_\mathrm{fc} = 0$.
+Nonetheless, with redshifts of both fiber-collided pair galaxies in mock catalogues, we can model the correlated and uncorrelated fiber-collided pairs in order to better correct for fiber-collisions.
 
-In order to determine whether or not fiber-collided pairs are correlated, we examine the comoving line-of-sight displacement ($d_{\mathrm{LOS}}$) of fiber-collided galaxy pairs.
+To determine whether or not fiber-collided pairs are correlated, we examine the comoving line-of-sight displacement ($d_{\mathrm{LOS}}$) of fiber-collided galaxy pairs.
 We calculate the $d_{\mathrm{LOS}}$ by taking the difference of the line-of-sight comoving distance from the resolved redshifts:
@@
 Catalogue &$\sigma$ ($\mathrm{Mpc}$) & $f_{\mathrm{peak}}$\\ \hline
-Las Damas 	& 6.85	& 0.71 \\ 
+LasDamas 	& 6.85	& 0.71 \\ 
 QPM 		& 4.98	& 0.65 \\ 
@@
 We list the $f_{\mathrm{peak}}$ values for each of the data catalogues in Table \ref{tab:mpfit}.
-The $f_\mathrm{peak}$ values for the mock catalogue are also in good agreement with the BOSS DR12 $f_\mathrm{peak}$.
+The $f_\mathrm{peak}$ values for the mock catalogue are also in reasonable agreement with the BOSS DR12 $f_\mathrm{peak}$.
 
-For the most commonly used nearest angular neighbor method (hereafter NN) to be completely correct, the $d_{\mathrm{LOS}}$ distribution in Figure \ref{fig:d_los} would have to be a delta function, which is clearly not the case.
+For the most commonly used nearest angular neighbor method (hereafter NN method) to be entirely correct, the $d_{\mathrm{LOS}}$ distribution in Figure \ref{fig:d_los} would have to be a delta function, which is clearly not the case.
 By simply incorporating the peak of the $d_{\mathrm{LOS}}$ distribution, we are able to significantly improve clustering statistics on small scales.
-Rather than placing the fiber-collided galaxy on top of its nearest angular neighbor as NN does, placing the fiber-collided galaxy at a displacement sampled from the $d_{\mathrm{LOS}}$ distribution, away from its nearest neighbor better accounts for the small scale in clustering measurements.
+Rather than placing the fiber-collided galaxy on top of its nearest angular neighbor as NN correction does, placing the fiber-collided galaxy at a displacement sampled from the $d_{\mathrm{LOS}}$ distribution away from its nearest neighbor better accounts for the small scale in clustering measurements.
 On mock catalogues, we test this by first applying the NN to the mock catalogues.
 We then sample a displacement $d_i$ from $p(d_\mathrm{LOS})$ (Equation \ref{eq:peak}) for each fiber-collided pair.
-Afterwards we ``place" the fiber-collided galaxy a distance $d_i$ from the nearest neighbor galaxy and reduce the statistical weight of the the nearest-neighbor by 1.
+Afterwards we ``place" the fiber-collided galaxy a distance $d_i$ from the nearest neighbor galaxy assign $w_\mathrm{fc} = 1$ and reduce the $w_\mathrm{fc}$ of the the nearest-neighbor by 1.
 We refer to this method as ``$d_\mathrm{LOS}$-peak".
@@
 \includegraphics[scale=0.55]{fcpaper_pk_peakonly_comp.png} 
-\caption{The ratio of $\overline{P(k)}$ using the nearest-neighbor (NN) correction (blue) and $d_\mathrm{LOS}$-peak correction (orange) over the true $\overline{P(k)}$ for LasDamas (left panel), QPM (middle panel), and Tiling Mock (right panel) catalogues.
-The ratio of the sample variance to the true $\overline{P(k)}$, $\Delta P_\mathrm{true}(k) / \overline{P_\mathrm{true}(k)}$ (black; dashed), is plotted for comparison.
+\caption{The ratio of $\overline{P_\mathrm{corr} (k)}$ using the nearest-neighbor (NN) correction (blue) and $d_\mathrm{LOS}$-peak correction (orange) over the true $\overline{P(k)}$ for LasDamas (left panel), QPM (middle panel), and Tiling Mock (right panel) catalogues.
 The NN correction and $d_\mathrm{LOS}$-peak correction methods are described in Section \ref{sec:dlos}.
-Incorporating the $d_{\mathrm{LOS}}$ distribution significantly improves the correction of fiber-collisions; however, both methods dominate the sample variance at $k > 0.3 \; h/\mathrm{Mpc}$.}\label{fig:peakonly}
+We also plot the ratio of the sample variance to the true $\overline{P_\mathrm{truee}(k)}$, $\Delta P_\mathrm{true}(k) / \overline{P_\mathrm{true}(k)}$ (black; dashed) for comparison.
+Incorporating the $d_{\mathrm{LOS}}$ distribution significantly improves the correction of fiber-collisions for $k > 0.1 \; h/\mathrm{Mpc}$; however, neither method is able to constrain the systematic effects of fiber-collisions significantly below the sample variance at $k > 0.2 \; h/\mathrm{Mpc}$.}\label{fig:peakonly}
 \end{center}
@@
 Nonetheless, we test it by applying it to the mock catalogues and comparing the resulting power spectrums.
-For each of the mock catalogues (Las Damas, QPM, and Tiling Mock) we use the FKP power spectrum estimator from before to compute the power spectrums of the original mock data, the mock data with the NN correction, and the mock data with the $d_\mathrm{LOS}$-peak correction.
+For each of the mock catalogues (LasDamas, QPM, and Tiling Mock) we use the FKP power spectrum estimator from Section \ref{sec:pk_est} to compute the power spectrums of the mock catalogues without fiber-collisions, with fiber-collisions corrected using NN method, and with fiber-collisions corrected using the $d_\mathrm{LOS}$-peak correction.
 We note that both the NN and the $d_\mathrm{LOS}$-peak correction methods alter the redshift distribution of our samples by a negligible amount $< 1\%$.
@@
 Since we are interested in how well fiber-collision correction methods can reproduce the power spectrum without fiber collisions (i.e.
-``true" power spectrum, unsullied by systematic effects), in Figure \ref{fig:peakonly} we plot the ratio of the average power spectrum $\overline{P(k)}$ (averaged over the realizations) computed from corrected mock catalogues over the $\overline{P(k)}$ from the original mock catalogues: $\overline{P_{\mathrm{corr}}(k)}/\overline{P_\mathrm{true}(k)}$.
+``true" power spectrum, unsullied by systematic effects), in Figure \ref{fig:peakonly} we plot the ratio of the average power spectrum $\overline{P(k)}$ (averaged over the realizations) computed from fiber-collided mock catalogues with corrections over the $\overline{P(k)}$ from the fiber-collision-less original mock catalogues: $\overline{P_{\mathrm{corr}}(k)}/\overline{P_\mathrm{true}(k)}$.
 The ratio for the NN method is plotted in blue while the ratio for the $d_{\mathrm{LOS}}$-peak correction is plotted in orange.
 We also plot $\Delta P_\mathrm{true}(k) / \overline{P_\mathrm{true}(k)}$ (black; dashed) in order to compare the ratios to sample variance of the mock catalogues.
+$\Delta P_\mathrm{true}(k)$ is computed using Eq.
+\ref{eq:pk_var}.
 At large scales ($k < 0.1 \; h/\mathrm{Mpc}$), for all mock catalogues, both fiber-collision methods are able to reasonably reconstruct the true power spectrum.
-At small scales on the other than, the NN corrected $\overline{P(k)}$ is greater than $\overline{P_\mathrm{true}(k)}$ by $> 10 \%$ at $ k \sim 0.3\; h/\mathrm{Mpc}$.
-In comparison, the $d_\mathrm{LOS}$-peak corrected $\overline{P(k)}$ is $\sim 5\%$ greater than $P_\mathrm{true}(k)$ at $k \sim 0.3 \; h/\mathrm{Mpc}$ - a significant improvement.
+At small scales on the other hand, the $\overline{P_\mathrm{NN}(k)}$ is greater than $\overline{P_\mathrm{true}(k)}$ by $> 10 \%$ at $ k \sim 0.3\; h/\mathrm{Mpc}$.
+In comparison, the $d_\mathrm{LOS}$-peak method significantly improves this residual to $\sim 5\%$ greater than $P_\mathrm{true}(k)$ at $k \sim 0.3 \; h/\mathrm{Mpc}$.
 {\bf include more description of even smaller scales when the figures are ready}.
 
-Comparing the NN method and the $d_\mathrm{LOS}$-peak correction to the sample variance ratio ($\Delta P_\mathrm{true}(k) / \overline{P_\mathrm{true}(k)}$), reveal that neither of these methods sufficiently correct for fiber-collision at $k > 0.1\; h/\mathrm{Mpc}$.
-The $P(k)$s obtained from these methods are clearly dominated by the systematic effects of fiber-collisions on small scales.
-Although the $d_\mathrm{LOS}$-peak method we propose provides an improvement from the NN method through our statistical treatment of correlated pairs within the peak of the $d_\mathrm{LOS}$ distribution, there is still room for improvement since it does not properly account for chance alignments (uncorrelated fiber-collision pairs).
-Unfortunately, an extension of the $d_\mathrm{LOS}$-peak method to the entire $d_\mathrm{LOS}$ distribution range is not feasible is not feasible because such a correction results in an overall reduction of the $P(k)$.
-This is caused by the statistical sampling of the $d_\mathrm{LOS}$, which displaces fiber-collided pairs that are actually correlated pairs as chance alignments and the other way around.
+When we compare the NN method and the $d_\mathrm{LOS}$-peak correction to the sample variance ratio ($\Delta P_\mathrm{true}(k) / \overline{P_\mathrm{true}(k)}$), we find that neither of these methods sufficiently correct for fiber-collisions at $k > 0.1\; h/\mathrm{Mpc}$.
+The $P(k)$s obtained from these methods are dominated by the systematic effects of fiber-collisions on small scales.
+Although the $d_\mathrm{LOS}$-peak method improves upon the NN method by statistical reconstructing the clustering of correlated fiber-collided pairs within the peak of the $d_\mathrm{LOS}$ distribution, there is still room for improvement since the method does not yet properly account for chance alignments (uncorrelated fiber-collision pairs).
+Unfortunately, an extension of the $d_\mathrm{LOS}$-peak method to the entire $d_\mathrm{LOS}$ distribution range is not feasible because such a correction results in an overall reduction of the $P(k)$.
+This is caused by the statistical sampling of the $d_\mathrm{LOS}$, which would inevitably displace some fiber-collided pairs that are actually correlated pairs as chance alignments and the other way around.
 Therefore, in the following section we provide more robust correction method to account for the chance alignment fiber-collided pairs.
@@
 \ref{eq:fkp_shotnoise} (blue), Eq.
-\ref{eq:ourshot} (green), $P^\mathrm{Beutler+}_\mathrm{shot}$ (red), and $P^{\mathrm{Gil-Marin+}}_\mathrm{shot}$ (purple) over $\overline{P_\mathrm{true}(k)}$ for LasDamas (left panel), QPM (middle panel), and Tiling Mock (right panel) catalogues with nearest-neighbor fiber-collision weights.
-Also plotted for comparison, is $\Delta P_\mathrm{true}/P_\mathrm{true}(k)$.
+\ref{eq:ourshot} (green), $P^\mathrm{B2014}_\mathrm{shot}$ (red), and $P^{\mathrm{GM2014}}_\mathrm{shot}$ (purple) over $\overline{P_\mathrm{true}(k)}$ for LasDamas (left panel), QPM (middle panel), and Tiling Mock (right panel) catalogues.
+We also plot $\Delta P_\mathrm{true}/P_\mathrm{true}(k)$ to compare with the sample variance ratio.
 $\overline{P_\mathrm{SN}(k)}$ computed using Eq.
-\ref{eq:fkp_shotnoise} shot-noise correction is identical to the NN method $\overline{P_\mathrm{corr}(k)}$ presented in Figure \ref{fig:peakonly} and significantly overestimates $\overline{P_\mathrm{true}(k)}$ at $k > 0.1 \; h/\mathrm{Mpc}$.
-$\overline{P_\mathrm{SN}(k)}$ using $P^\mathrm{Beutler+}_\mathrm{shot}$ also overestimates $\overline{P_\mathrm{true}(k)}$ at $k > 0.1 \; h/\mathrm{Mpc}$.
+\ref{eq:fkp_shotnoise} shot-noise correction is identical to the NN method $\overline{P_\mathrm{corr}(k)}$ presented in Figure \ref{fig:peakonly} and as before significantly overestimates $\overline{P_\mathrm{true}(k)}$ at $k > 0.1 \; h/\mathrm{Mpc}$.
+$\overline{P_\mathrm{SN}(k)}$ using $P^\mathrm{B2014}_\mathrm{shot}$ equivalently overestimates $\overline{P_\mathrm{true}(k)}$ at $k > 0.1 \; h/\mathrm{Mpc}$.
 On the other hand $\overline{P_\mathrm{SN}(k)}$ computed using Eq.
-\ref{eq:ourshot} significantly underestimates the power spectrum at $k > 0.1 \; h/\mathrm{Mpc}$.
-At these small scales, only $\overline{P_\mathrm{SN}(k)}$ computed using $P^\mathrm{Gil-Marin+}_\mathrm{shot}$ provides a reasonable correction for fiber-collisions ($\overline{P^\mathrm{Gil-Marin-SN}(k)}/\overline{P_\mathrm{true}(k)} -1 \sim 2.5 \%$), reducing its effect below sample variance.
+\ref{eq:ourshot} significantly underestimates the power spectrum at $k > 0.1 \; h/\mathrm{Mpc}$ with $\overline{P^\mathrm{Eq.15}_\mathrm{SN}}/\overline{P_\mathrm{true}}(k \sim 0.3) -1 \sim -3 \%, -8 \%, \;\mathrm{and} -9$ for LasDamas, QPM, and Tiling Mock respectively.
+$\overline{P_\mathrm{SN}(k)}$ computed using $P^\mathrm{GM2014}_\mathrm{shot}$ provides the best correction for fiber-collisions ($\overline{P^\mathrm{GM2014}_\mathrm{SN}}/\overline{P_\mathrm{true}}(k \sim 0.3) -1 \sim 2.5 \%$).
+However at these small scales, even for $\overline{P^\mathrm{GM2014}_\mathrm{SN}}$ the effect of fiber-collisions is comparable to sample variance at $k \sim 0.3 \;h/\mathrm{Mpc}$.
 } \label{fig:shotnoise}
@@
 In this section we introduce the other part of our fiber-collision correction method that involve the shot-noise correction term of the FKP power spectrum estimator.
-By adjusting the shot noise term of the FKP estimator, we present a more robust correction method that accounts for the chance aligned fiber-collided pairs.
+By modifying the shot noise term of the FKP estimator to account for fiber-collisions, we present a more robust correction method that accounts for the chance aligned fiber-collided pairs.
 
@@
 In their estimator, to account for the discreteness of the density field, they subtract the shot-noise contribution to the power spectrum (Equation \ref{eq:fkppk}):
-\begin{equation}
+\begin{equation} \label{eq:fkp_sn_int}
 P_\mathrm{shot} = \frac{ (1+\alpha) \int d^3r \;\bar{n}({\bf r})w^2({\bf r})}{\int d^3r \;\bar{n}^2({\bf r})w^2({\bf r})}. 
 \end{equation}
-In practice, the integrals in Equation \ref{eq:fkp_shotnoise} can be written in terms of discrete sums over the random catalogue.
+In practice, the integrals in Equation \ref{eq:fkp_sn_int} can be written in terms of discrete sums over the random catalogue.
 The spacial integral $\int d^3r \; \bar{n}({\bf r}) ...$ can be computed as the discrete sum $\alpha \sum_{\mathrm{ran}}...$.
@@
 \end{equation} 
-In the FKP derivation, they do not take systematic weights of galaxies into account.
+However, in the FKP derivation, they do not take systematic weights of galaxies into account.
 
@@
 \begin{equation} \label{eq:florian}
-P^\mathrm{Beutler+}_\mathrm{shot} = \frac{\sum\limits_{\mathrm{galaxy}} w^2_\mathrm{FKP}w_\mathrm{tot}({\bf r})w_\mathrm{sys}({\bf r}) - \alpha'^2 \sum\limits_{\mathrm{random}} w_\mathrm{FKP}^2({\bf r})}{\alpha' \sum\limits_{\mathrm{random}}w_\mathrm{FKP}^2({\bf r})}.
+P^\mathrm{B2014}_\mathrm{shot} = \frac{\sum\limits_{\mathrm{galaxy}} w^2_\mathrm{FKP}w_\mathrm{tot}({\bf r})w_\mathrm{sys}({\bf r}) - \alpha'^2 \sum\limits_{\mathrm{random}} w_\mathrm{FKP}^2({\bf r})}{\alpha' \sum\limits_{\mathrm{random}}w_\mathrm{FKP}^2({\bf r})},
 \end{equation}
-$\alpha' = \sum_\mathrm{gal} w_\mathrm{tot} / N_\mathrm{ran}$.
+where $\alpha' = \sum_\mathrm{gal} w_\mathrm{tot} / N_\mathrm{ran}$.
 
@@
 The shot-noise contribution to the power from correlated pairs (referred to as ``true pairs" in \citealt{Gil-Marin:2014aa}) is equivalent to Eq.
-\ref{eq:florian} above.
+\ref{eq:florian} above ($P_\mathrm{shot}$ in \cite{Beutler:2014aa}).
 For chance alignments (referred to as ``false pairs" in \citealt{Gil-Marin:2014aa}), the shot-noise contribution is derived as,
@@
 \begin{equation} \label{eq:gm_shot}
-P^\mathrm{Gil-Marin+}_\mathrm{shot} = (1- x_\mathrm{PS}) P^{True}_\mathrm{shot} + x_\mathrm{PS} P^{False}_\mathrm{shot}
+P^\mathrm{GM2014}_\mathrm{shot} = (1- x_\mathrm{PS}) P^{True}_\mathrm{shot} + x_\mathrm{PS} P^{False}_\mathrm{shot}
 \end{equation}
-For the BOSS $P(k)$ \cite{Gil-Marin:2014aa} quotes $x_\mathrm{PS} = 0.58$.
+For analyzing BOSS $P(k)$ \cite{Gil-Marin:2014aa} uses $x_\mathrm{PS} = 0.58$.
+The $x_\mathrm{PS}$ is calculated from the weighted galaxy catalogue of \cite{Manera:2013aa}, not the observed BOSS data, and it is the value that optimizes the fit of the fiber-collision corrected $P(k)$ to the $P_\mathrm{true}(k)$ .
 
@@
 \end{equation}
-The difference between Eq.
+We note that the difference between Eq.
 \ref{eq:ourshot} and Eq.
-\ref{eq:florian} is in the first term of the numerator, where Eq.
-\ref{eq:florian} accounts for fiber-collisions in the $w_{\mathrm{tot}}$ term while Eq.
+\ref{eq:florian} lies in the first term of the numerator.
+In this term, for Eq.
+\ref{eq:florian}, $w_\mathrm{fc}$ is only included in $w_\mathrm{tot}$ and not in the $w_\mathrm{sys}$ term.
+However, Eq.
 \ref{eq:ourshot} accounts for fiber-collisions in the $w_\mathrm{tot}^2$ term.
-Eq.
+Also, Eq.
 \ref{eq:ourshot} is equivalent to the shot-noise contribution from ``false pairs" in \cite{Gil-Marin:2014aa}.
@@
 
-In order to compare the different $P_\mathrm{shot}$ derivations, we apply each of them ($P^\mathrm{FKP}_\mathrm{shot}$, $P^\mathrm{Hahn+}_\mathrm{shot}$, $P^\mathrm{Beutler+}_\mathrm{shot}$ and $P^\mathrm{Gil-Marin+}_\mathrm{shot}$) to the fiber-collided mock catalogues with nearest-neighbor weights.
-$P^\mathrm{FKP}_\mathrm{shot}$, $P^\mathrm{Hahn+}_\mathrm{shot}$, $P^\mathrm{Beutler+}_\mathrm{shot}$ and $P^\mathrm{Gil-Marin+}_\mathrm{shot}$ are calculated using Eq.
+In order to compare the different $P_\mathrm{shot}$ derivations, we apply each of them ($P^\mathrm{FKP}_\mathrm{shot}$, $P^\mathrm{Hahn+}_\mathrm{shot}$, $P^\mathrm{B2014}_\mathrm{shot}$ and $P^\mathrm{GM2014}_\mathrm{shot}$) to the fiber-collided mock catalogues with nearest-neighbor weights.
+To clarify, $P^\mathrm{FKP}_\mathrm{shot}$, $P^\mathrm{Hahn+}_\mathrm{shot}$, $P^\mathrm{B2014}_\mathrm{shot}$ and $P^\mathrm{GM2014}_\mathrm{shot}$ are calculated using Eq.
 \ref{eq:fkp_shotnoise}, \ref{eq:ourshot}, \ref{eq:florian} and \ref{eq:gm_shot}, respectively.
-Since we are particularly interested in fiber-collisions, our comparison ignores the other contributions to systematic effects listed in Eq.
-\ref{eq:weight} ($w_\mathrm{sys}$ and $w_\mathrm{rf}$).
-So in Equations 9 - 15, we use $w_\mathrm{sys} = 1$ and $w_\mathrm{tot} = w_\mathrm{fc}$.
-We compute the $P_\mathrm{SN}(k)$s using the various $P(k)$ estimators with different $P_\mathrm{shot}$ equations for each of the mock catalogues.
-Afterwards we compute the $\overline{P_\mathrm{SN}(k)}$s for the mock catalogues by averaging over the realizations, and then take the ratio over $\overline{P_\mathrm{true}(k)}$ calculated using the standard FKP $P(k)$ estimator.
+In our considerations of systematic effects beside fiber-collisions in Eq.
+\ref{eq:weight}, we note that only the QPM mock catalogue assigns $w_\mathrm{sys}$ (systematic weights due to sector completeness) to its galaxies and none of the mock catalogues assign $w_\mathrm{rf}$ to their galaxies.
+Therefore in Equations 9 - 15, for LasDamas and Tiling mock catalogues we use $w_\mathrm{sys} = w_\mathrm{rf} = 1$ so $w_\mathrm{tot} = w_\mathrm{fc}$ and for QPM mocks, we use $w_\mathrm{tot} = w_\mathrm{sys} w_\mathrm{fc}$.
+We compute the $P_\mathrm{SN}(k)$s using the FKP estimator with different $P_\mathrm{shot}$ prescriptions for each of the mock catalogues.
+We then average the power spectrum over the realizations to get $\overline{P_\mathrm{SN}(k)}$s for the mock catalogues, and then take the ratio over $\overline{P_\mathrm{true}(k)}$.
 
-In Figure \ref{fig:shotnoise}, we present $\overline{P_\mathrm{SN}(k)}/\overline{P_\mathrm{true}(k)}$ computed using $P^\mathrm{FKP}_\mathrm{shot}$, $P^\mathrm{Hahn+}_\mathrm{shot}$, $P^\mathrm{Beutler+}_\mathrm{shot}$ and $P^\mathrm{Gil-Marin+}_\mathrm{shot}$ shot noise correction term equations.
-We note that $\overline{P_\mathrm{SN}(k)}$ calculated using $P^\mathrm{FKP}_\mathrm{shot}$ is the same quantity as the NN corrected $\overline{P(k)}$ in Figure \ref{fig:peakonly}.
-As before, it over estimates the $\overline{P_\mathrm{true}(k)}$ by $> 10 \%$ for all mocks at $k \sim 0.3 \; h/\mathrm{Mpc}$.
-$\overline{P(k)}$ measured using $P^\mathrm{Beutler+}_\mathrm{shot}$ (Eq.
+In Figure \ref{fig:shotnoise}, we present $\overline{P_\mathrm{SN}(k)}/\overline{P_\mathrm{true}(k)}$ computed using $P^\mathrm{FKP}_\mathrm{shot}$, $P^\mathrm{Eq.\ref{eq:ourshot}}_\mathrm{shot}$, $P^\mathrm{B2014}_\mathrm{shot}$ and $P^\mathrm{GM2014}_\mathrm{shot}$ shot noise correction term equations.
+$\overline{P_\mathrm{SN}(k)}$ calculated using $P^\mathrm{FKP}_\mathrm{shot}$ is the identical to the NN corrected $\overline{P(k)}$ in Figure \ref{fig:peakonly}.
+Hence as before, it over estimates the $\overline{P_\mathrm{true}(k)}$ by $> 10 \%$ for all mocks at $k \sim 0.3 \; h/\mathrm{Mpc}$.
+$\overline{P(k)}$ measured using $P^\mathrm{B2014}_\mathrm{shot}$ (Eq.
 \ref{eq:florian}) does not significantly improve this overestimation in any of the mock catalogues.
+In fact for LasDamas and Tiling mock catalogues, since $w_\mathrm{sys} = 1$, $P^\mathrm{FKP}_\mathrm{shot} = P^\mathrm{B2014}_\mathrm{shot}$.
+Even for QPM, which assigns $w_\mathrm{sys}$ to its galaxies there are no significant improvements from using $P^\mathrm{B2014}_\mathrm{shot}$ over $P^\mathrm{FKP}_\mathrm{shot}$.
 
-On the other hand, the $\overline{P(k)}$ using Eq.
-\ref{eq:ourshot} significantly underestimates the $\overline{P_\mathrm{true}(k)}$.
-At $k \sim 0.3 \; h/\mathrm{Mpc}$, $\overline{P^\mathrm{Hahn-SN}(k)}/\overline{P_\mathrm{true}(k)} - 1 = \sim -3 \%, \sim -8 \%, \;\mathrm{and} \sim -9$ for LasDamas, QPM, and Tiling Mock respectively.
-Finally, $\overline{P(k)}$ measured using $P^\mathrm{Gil-Marin}_\mathrm{shot}$ reproduces $\overline{P_\mathrm{true}(k)}$ most accurately in the comparison of Figure \ref{fig:shotnoise}.
-At $k \sim 0.3 \; h/\mathrm{Mpc}$, $\overline{P^\mathrm{Gil-Marin-SN}(k)}/\overline{P_\mathrm{true}(k)} -1 \sim 2.5 \%$.
-As we plotted in Figure \ref{fig:peakonly}, we plot the sample variance ($\Delta P/\bar{P}$) for each of the mock catalogues in Figure \ref{fig:shotnoise}.
-Only $\overline{P(k)}$ computed using $P^\mathrm{Gil-Marin}_\mathrm{shot}$ is able to reduce the effects of fiber-collisions below the sample variance.
+On the other hand, $\overline{P(k)}$ using Eq.
+\ref{eq:ourshot} significantly is significantly lower than the $\overline{P_\mathrm{true}(k)}$.
+$\overline{P^\mathrm{Eq.\ref{eq:ourshot}}_\mathrm{SN}}/\overline{P_\mathrm{true}}(k\sim0.3) - 1 \sim -3 \%, -8 \%, \;\mathrm{and} -9$ for LasDamas, QPM, and Tiling Mock respectively.
+Finally, $\overline{P(k)}$ measured using $P^\mathrm{GM2014}_\mathrm{shot}$ reproduces $\overline{P_\mathrm{true}(k)}$ most accurately in the comparison of Figure \ref{fig:shotnoise}.
+$\overline{P^\mathrm{GM2014}_\mathrm{SN}}/\overline{P_\mathrm{true}}(k\sim 0.3) -1 \sim 2.5 \%$.
+As in Figure \ref{fig:peakonly}, we again plot the sample variance ($\Delta P/\bar{P}$) for each of the mock catalogues in Figure \ref{fig:shotnoise} for comparison.
+$\overline{P(k)}$ computed using $P^\mathrm{Gil-Marin}_\mathrm{shot}$ is able to best constrain the effects of fiber-collisions in our comparison.
+However, even $\overline{P^\mathrm{GM2014}_\mathrm{SN}}$ is unable to significantly reduce the effects of fiber-collisions below the sample variance, especially near $k \sim 0.3 \;h/\mathrm{Mpc}$.
 
@@
 \ref{eq:ourshot} should only correct for the shot-noise contribution to the power spectrum from chance alignment fiber-collided pairs - not from correlated pairs.
-Because we apply the shot-noise correction to all fiber-collided pairs in Figure \ref{fig:shotnoise}, the shot-noise correction term over-subtracting to underestimate the true power spectrum is expected.
+Because we apply the shot-noise correction to all fiber-collided pairs indiscriminately in Figure \ref{fig:shotnoise}, the shot-noise correction term over-subtracts the power spectrum as we find in Figure \ref{fig:shotnoise}.
 In the following section we present our fiber-collision correction method, that combines the $d_\mathrm{LOS}$-peak correction of Section \ref{sec:dlos} and Eq.
@@
 
+\begin{figure*}
+\begin{center}
+\includegraphics[scale=0.55]{fcpaper_pk_peakshotnoise_mpfit_comp.png} 
+\caption{The ratio of $\overline{P(k)}$ computed using our fiber-collision correction method presented in Section \ref{sec:apply} over $\overline{P_\mathrm{true}(k)}$ for LasDamas (left panel), QPM (middle panel), and Tiling Mock (right panel) catalogues with nearest-neighbor fiber-collision weights (red).
+We again plot $\Delta P_\mathrm{true}/P_\mathrm{true}(k)$ for comparison.
+$\overline{P_\mathrm{corr}}/\overline{P_\mathrm{true}}(k \sim 0.3 \; h/\mathrm{Mpc})-1 \sim 0.5\%$ for our fiber-collision correction.
+This is significantly better than the correction methods of \cite{Anderson:2012aa}, \cite{Beutler:2014aa} and \cite{Gil-Marin:2014aa} in Figure \ref{fig:shotnoise}.
+Moreover, for LasDamas and QPM, our correction method is able to correct for the effects of fiber-collisions, significantly below the $\Delta P_\mathrm{true}/P_\mathrm{true}(k)$ throughout the probed $k$ range, even at the smallest scales.
+}\label{fig:peaksn}
+\end{center}
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results} 
+\section{Results} \label{sec:results}
 \subsection{Fiber-Collision Correction Method} \label{sec:apply}
-\begin{figure*}
-\begin{center}
-\includegraphics[scale=0.55]{fcpaper_pk_peakshotnoise_mpfit_comp.png} 
-\caption{The ratio of $\overline{P(k)}$ computed using our fiber-collision correction method described in Section \ref{sec:apply} over $\overline{P_\mathrm{true}(k)}$ for LasDamas (left panel), QPM (middle panel), and Tiling Mock (right panel) catalogues with nearest-neighbor fiber-collision weights (red).
-Also plotted for comparison, is $\Delta P_\mathrm{true}/P_\mathrm{true}(k)$.
-At $k \sim 0.3 \; h/\mathrm{Mpc}$, the $\overline{P(k)}$ ratio of our correction method $\sim 0.5 \%$, which is significantly better than the correction methods of \cite{Anderson:2012aa}, \cite{Beutler:2014aa} and \cite{Gil-Marin:2014aa}.
-Moreover, the $\overline{P(k)}$ ratio for our correction method is significantly lower than the $\Delta P_\mathrm{true}/P_\mathrm{true}(k)$ throughout the probed $k$ values.}\label{fig:peaksn}
-\end{center}
-\end{figure*}
+In Section \ref{sec:dlos} we derive a method to better statistically reconstruct the clustering of correlated fiber-collided pairs using using the peak of the $d_\mathrm{LOS}$ distribution.
+Then in Section \ref{sec:shotnoise} we presented our formulation of the shot-noise correction term, which accounts for the added discreteness from chance aligned fiber-collision pairs.
+We now combine these two methods and present our fiber-collision correction method.
 
-In Section \ref{sec:dlos} we derive a method to better statistically reconstruct the clustering of correlated fiber-collided pairs using using the peak of the $d_\mathrm{LOS}$ distribution.
-Then in Section \ref{sec:shotnoise} we presented our formulation of the shot-noise correction term, which accounts for the added discreteness from fiber-collsions.
-We now combine these two methods in order to present our fiber-collision correction method.
-
-We begin with once again with the fiber-collided mock catalogues with the nearest-neighbor weights.
-These mock catalogues accurately imitate the effects of fiber-collision on the actual observed BOSS data.
+We begin once again with the fiber-collided mock catalogues with the nearest-neighbor weights that accurately imitate the effects of fiber-collision on the actual observed BOSS data.
 Then as described in Section \ref{sec:dlos}, we calculate the $d_\mathrm{LOS}$ distribution of all fiber-collided pairs in each mock catalogue.
 From the $d_\mathrm{LOS}$ distribution, we compute the fraction of fiber-collided pairs within the peak of the distribution ($f_\mathrm{peak}$; Section \ref{sec:dlos}).
-We then select $f_\mathrm{peak}$ of the fiber-collided pairs and designate them as correlated pairs that lie in the peak of the $d_\mathrm{LOS}$ distribution.
+We then select $f_\mathrm{peak}$ of the fiber-collided pairs and designate them as correlated pairs that lie within the peak of the $d_\mathrm{LOS}$ distribution.
 We refer to these fiber-collided pairs as ``peak-assigned" pairs.
 
-Each of these ``peak-assigned" pairs, due to the nearest-neighbor weights, consist of a galaxy with $w_\mathrm{fc} > 1$ (the ``nearest-neighbor" galaxy) and another galaxy with $w_\mathrm{fc} = 0$ (the ``collided" galaxy).
+Each of these ``peak-assigned" pairs, by the nearest-neighbor weights, consist of a galaxy with $w_\mathrm{fc} > 1$ (the ``nearest-neighbor" galaxy) and another with $w_\mathrm{fc} = 0$ (the ``collided" galaxy).
 We disregard the collided galaxy.
-For each of the nearest-neighbor galaxies, we sample a value $d_\mathrm{peak-assigned}$ from the peak of the $d_\mathrm{LOS}$ distribution and place a galaxy with $w_\mathrm{fc} = 1$ at a comoving distance $d_\mathrm{peak-assigned}$ away from the nearest-neighbor galaxy.
+For each of the nearest-neighbor galaxies, we sample a value $d_\mathrm{peak-assigned}$ from the Gaussian best-fit to the $d_\mathrm{LOS}$ distribution peak and place a galaxy with $w_\mathrm{fc} = 1$ at a comoving distance $d_\mathrm{peak-assigned}$ away from the nearest-neighbor galaxy.
 At the same time, we reduce $w_\mathrm{fc}$ of the nearest-neighbor galaxy (the one that was originally up-weighted) by $1$.
-This process is repeated until the nearest-neighbor galaxy has $w_\mathrm{fc} =1$.
+This process is repeated until the nearest-neighbor galaxy has $w_\mathrm{fc} =1$ in the case of triplets or higher.
 
-For the remaining fiber-collided pairs that are not ``peak-assigned" ($1-f_\mathrm{peak}$ of the fiber-collided pairs), we keep the nearest-neighbor fiber collision weights.
-The resulting mock catalogue has $f_\mathrm{peak}$ fewer galaxies with $w_\mathrm{cp} > 1$ compared to the fiber-collided mock catalogues with nearest-neighbor weights that we started from; however, the total statistical weight of the mock catalogue is conserved.
+We keep the nearest-neighbor fiber-collision weights imposed in the beginning for the remaining fiber-collided pairs that are not ``peak-assigned" ($1-f_\mathrm{peak}$ of the fiber-collided pairs).
+The resulting mock catalogue has $f_\mathrm{peak}$ fewer galaxies with $w_\mathrm{cp} > 1$ compared to the fiber-collided mock catalogues with nearest-neighbor weights that we started from; however, the total statistical weight ($\sum_\mathrm{gal} w_\mathrm{tot}$) of the mock catalogue is conserved.
 
 Next, we use the FKP estimator with the Eq.
-\ref{eq:ourshot} shot-noise correction term described in Section \ref{sec:shotnoise} to calculate the $P(k)$ for our newly corrected mock catalogues.
-In Figure \ref{fig:peaksn} we present the ratio of the $\overline{P(k)}$ computed using our fiber-collision correction method over $P_\mathrm{true}(k)$.
-To assess the merit of the fiber-collision correction scheme, we once again over-plotted the sample variance of the mock catalogues.
-For Las Damas, at $k \sim 0.3 \; h/\mathrm{Mpc}$, $P(k)/P_\mathrm{true}(k) - 1 \sim 0.5 \%$ and throughout the $k$ range, $0.3 \% < P(k)/P_\mathrm{true}(k) - 1 < 1.3 \%$.
+\ref{eq:ourshot} shot-noise correction term described in Section \ref{sec:shotnoise} to calculate the $P(k)$ for our $d_\mathrm{LOS}$-peak corrected mock catalogues.
+In Figure \ref{fig:peaksn}, we present the ratio of the $\overline{P(k)}$ computed using our fiber-collision correction method over $\overline{P_\mathrm{true}(k)}$.
+To assess the merit of the fiber-collision correction, we once again over-plot the sample variance of the mock catalogues.
+For LasDamas, at $k \sim 0.3 \; h/\mathrm{Mpc}$, $P(k)/P_\mathrm{true}(k) - 1 \sim 0.5 \%$ and throughout the $k$ range, $0.3 \% < P(k)/P_\mathrm{true}(k) - 1 < 1.3 \%$.
 For QPM, at $k \sim 0.3 \; h/\mathrm{Mpc}$, $P(k)/P_\mathrm{true}(k) - 1 \sim 0.04 \%$ and throughout the $k$ range, $0.3 \% < P(k)/P_\mathrm{true}(k) - 1 < 1.3 \%$.
-% provide some specifics on the range of the P(k) ratio
-Moreover for the mock catalogues where we do have sample variance measurements (LasDamas and QPM), the $P(k)$ ratio is significantly below the sample variance throughout the entire $k$ range probed.
+{\bf include numbers here when Ngrid=960 is done}.
+Moreover for the mock catalogues with sample variance measurements (LasDamas and QPM), the $P(k)$ ratio is significantly below the sample variance throughout the entire $k$ range probed and even at $k\sim 0.3\;h/\mathrm{Mpc}$.
 
@@
 \includegraphics[scale=0.55]{fcpaper_pk_chisquared_comparison.png} 
-\caption{$\chi^2 (k_\mathrm{max})$ for $P_\mathrm{NN-upweight}$ (blue), $P_\mathrm{Beutler}$ (light blue), $P_\mathrm{Gil-Marin}$ (orange), and $P_\mathrm{Hahn}$ (yellow) using the Las Damas (left panel), QPM (centerl panel), and Tiling (right panel) mock catalogues.
+\caption{$\chi^2 (k_\mathrm{max})$ for $P_\mathrm{NN-upweight}$ (blue), $P_\mathrm{Beutler}$ (light blue), $P_\mathrm{Gil-Marin}$ (orange), and $P_\mathrm{Hahn}$ (yellow) using the LasDamas (left panel), QPM (centerl panel), and Tiling (right panel) mock catalogues.
 Equation \ref{eq:chi2} was used to compute the $\chi^2(k_\mathrm{max})$.
@@
 
-The correction method we present in this paper corrects for the effect of fiber-collisions to the extent where $P_\mathrm{corr}(k)$ measurements are no longer dominated by systematic effects at the scales probed in our calculations ($k < 0.3 \; h/\mathrm{Mpc}$).
-However, to further quantify how accurately our correction method is able to reproduce the true power spectrum, we quantify the goodness-of-fit for all the corrected $P(k)$s to $P_\mathrm{true}(k)$ by calculating the following $\chi^2$:
+The correction method we present in this paper corrects for the effect of fiber-collisions to the extent where $P_\mathrm{corr}(k)$ measurements are no longer dominated by systematic effects at the scales probed in our calculations, even for the smallest scales of $k \sim 0.3 \; h/\mathrm{Mpc}$.
+However, to further quantify how accurately our correction method is able to reproduce the true power spectrum and correct for the effects of fiber-collisions, we quantify the goodness-of-fit for all the corrected $P(k)$s to $P_\mathrm{true}(k)$ by calculating the following $\chi^2$:
 \begin{equation}
@@
 For the Tiling Mock catalogue, since there is only one realization, the variance ($\Delta P_\mathrm{true} (k)$) cannot be computed independently.
-However, for an estimate of the $\chi^2$, we estimate $\Delta P_\mathrm{true}^\mathrm{Tiling\;Mock}(k)$ from $\Delta P_\mathrm{true} (k)$ of the QPM mock catalogue scaled by the ratio of the power spectrums:
+However, for an estimate of the $\chi^2$, we estimate $\Delta P_\mathrm{true}^\mathrm{Tiling\;Mock}(k)$ from $\Delta P^\mathrm{QPM}_\mathrm{true} (k)$ scaled by the ratio of the power spectrums:
 \begin{equation}
@@
 
-In Figure \ref{fig:peaksnchi2}, we present the $\chi^2(k_\mathrm{max})$ for $P(k)$ using the following fiber collision correction methods: the NN correction, \cite{Beutler:2014aa}, \cite{Gil-Marin:2014aa}, and our method from Section \ref{sec:apply}.
+In Figure \ref{fig:peaksnchi2}, we present the $\chi^2(k_\mathrm{max})$ for $P(k)$ using the following fiber collision correction methods: the NN correction (also \citealt{Anderson:2012aa}), \cite{Beutler:2014aa}, \cite{Gil-Marin:2014aa}, and our method from Section \ref{sec:apply}.
 The comparison is made using the LasDamas (left panel), QPM (center panel) and Tiling (right panel) mock catalogues.
-First in the LasDamas panel, at scales larger than $k < 5 \times 10^{-2} \; h/\mathrm{Mpc}$, $\chi^2 < 10^{-3}$ for all correction methods, which suggests that all correction methods sufficiently correct for fiber-collisions and reasonably reconstructs $P_\mathrm{true}(k)$ at these scale.
+First in the LasDamas panel, at scales larger than $k_\mathrm{max} < 5 \times 10^{-2} \; h/\mathrm{Mpc}$, $\chi^2 < 10^{-3}$ for all correction methods, which suggests that all correction methods sufficiently correct for fiber-collisions and reasonably reconstructs $P_\mathrm{true}(k)$ at these scale.
 In approaching smaller scales the $\chi^2$ for all correction methods increase.
 However, throughout the entire $k_\mathrm{max}$ range, our correction method provides a notably lower $\chi^2$ in comparison to the other correction methods.
-This is especially clear at $k \sim 0.3 \; h/\mathrm{Mpc}$, where $\chi^2_\mathrm{NN} \approx 0.33$, $\chi^2_\mathrm{Beutler} \approx 0.33$, and $\chi^2_\mathrm{Gil-Marin} \approx 0.17$ while $\chi^2 \approx 0.019$ for our method.
+This is especially clear at $k_\mathrm{max} \sim 0.3 \; h/\mathrm{Mpc}$, where $\chi^2_\mathrm{NN} \approx 0.33$, $\chi^2_\mathrm{B2014} \approx 0.33$, and $\chi^2_\mathrm{GM2014} \approx 0.17$ while $\chi^2 \approx 0.019$ for our method.
 
-Next in the QPM panel (center), at scales larger than ($k < 2 \times 10^{-2} \; h/\mathrm{Mpc}$) all corrected $P(k)$ once again provide a reasonable reconstruction of $P_\mathrm{true}(k)$ with $\chi^2 \approx 10^{-2}$.
+Next in the QPM panel (center), at scales larger than $k_\mathrm{max} < 2 \times 10^{-2} \; h/\mathrm{Mpc}$ all corrected $P(k)$ again provide a reasonable reconstruction of $P_\mathrm{true}(k)$ with $\chi^2 \approx 10^{-2}$.
 Then for $2 \times 10^{-2} < k_\mathrm{max} < 5 \times 10^{-2}\; h/\mathrm{Mpc}$, the NN and \cite{Beutler:2014aa} correction methods have the lower $\chi^2$s than \cite{Gil-Marin:2014aa} and our correction methods.
-However, as $k$ increases, the $\chi^2$s for NN and \cite{Beutler:2014aa} quickly surpasses the $\chi^2$s of \cite{Gil-Marin:2014aa} and our method.
+However, as $k_\mathrm{max}$ increases, the $\chi^2$s for NN and \cite{Beutler:2014aa} quickly surpasses the $\chi^2$s of \cite{Gil-Marin:2014aa} and our method.
 Meanwhile, throughout the entire $k_\mathrm{max}$ range probed, our correction method has a significantly lower $\chi^2$ than the correction method of \cite{Gil-Marin:2014aa}.
@@
 
-Finally in the right panel (Tiling Mock), we find that $\chi^2(k_\mathrm{max})$ increases in a near monotonic fashion as a function of $k_\mathrm{max}$.
+Finally for the Tiling mock catalogue (right panel), we find that $\chi^2(k_\mathrm{max})$ increases in a near monotonic fashion as a function of $k_\mathrm{max}$.
 For $k_\mathrm{max} < 4\times10^{-2} \; h/\mathrm{Mpc}$, there are no significant differences between the $\chi^2$s of any of the correction methods.
@@
 Throughout the entire $k_\mathrm{max}$ our method has a lower $\chi^2$ than \cite{Gil-Marin:2014aa}.
-With only one realization of the Tiling Mocks and scaled $\Delta P$, a detailed comparison of the $\chi^2$ values is impossible.
+With only one realization of the Tiling mock catalogue and scaled $\Delta P$, a detailed comparison of the $\chi^2$ values is difficult.
 Yet the $\chi^2(k_\mathrm{max})$ results for our correction provide realistic assurance that the correction method can be applied to the actually BOSS data.
@@
 Overall, regardless of catalogue, for scales $k_\mathrm{max} < 3 \times 10^{-2} \;h/\mathrm{Mpc}$, the $\chi^2$ for all fiber-collision corrected $P(k)$ are negligible.
-Then, with the exception of the Las Damas catalogue, at intermediate scales of $3 \times 10^{-2} < k_\mathrm{max} < 0.15 \; h/\mathrm{Mpc}$ the NN and \cite{Beutler:2014aa} methods show the lowest $\chi^2$s.
-However at these intermediate scales, all of the correction methods reasonably reconstruction of the true power spectrum with $\chi^2 < 1$.
+Then, with the exception of the LasDamas catalogue, at intermediate scales of $3 \times 10^{-2} < k_\mathrm{max} < 0.15 \; h/\mathrm{Mpc}$ the NN and \cite{Beutler:2014aa} methods show the lowest $\chi^2$s.
+However at these intermediate scales, all of the correction methods reasonably reconstruction of the true power spectrum with $\chi^2 \ll 1$.
 At the smallest scales, NN and \cite{Beutler:2014aa} corrections methods no longer provide a sufficient fit to $\overline{P_\mathrm{true}(k)}$.
@@
 Using simulated mock catalogues for SDSS data with realistically imposed fiber-collisions, we quantify the systematic effects of fiber-collisions on galaxy clustering measurements - in particular the power spectrum.
-Although fiber-collisions have little significant effect on the power spectrum at large scales, its effect quickly overtakes the sample variance at scales smaller than $k \sim 0.1 \;h/\mathrm{Mpc}$.
+Although fiber-collisions have little significant effect on the power spectrum at large scales, its effect quickly overtakes the sample variance at scales smaller than $k > 0.1 \;h/\mathrm{Mpc}$.
 At the smallest scales that we explore in this paper, $k \sim 0.3$, fiber-collisions have over a $10 \%$ effect on the power spectrum.
-Consequently, at these small scales measurements of the power spectrum is dominated by the uncertainties from systematic effects of fiber-collisions.
+Consequently at these small scales, measurements of the power spectrum is dominated by the uncertainties from systematic effects of fiber-collisions.
 
-Fortunately, through the fiber-collided mock catalogues we are able to model the distribution of the line-of-sight displacement between fiber-collided pairs.
+Fortunately, through the fiber-collided mock catalogues used in this paper, we are able to model the distribution of the line-of-sight displacement between fiber-collided pairs.
 Using this model, we are able to statistically reconstruct the clustering fiber-collided galaxies that reside in the same halo.
@@
 
-Furthermore, we compare our method to the most common nearest-neighbor correction method and recent correction methods presented in \cite{Beutler:2014aa} and \cite{Gil-Marin:2014aa} to demonstrate that our method most successfully reproduces the true power spectrum at small scales and reliably at all scales for all the Las Damas, QPM, and Tiling mock catalogues.
-As an added advantage, our correction method can also be validated by actual data rather than only through the mock catalogues thereby making it's application to actual data further reliable.
+Furthermore, we compare our method to the most common nearest-neighbor correction method (\citealt{Zehavi:2002aa, Berlind:2006aa, Anderson:2012aa}) and recent correction methods presented in \cite{Beutler:2014aa} and \cite{Gil-Marin:2014aa} to demonstrate that our method most successfully reproduces the true power spectrum at small scales and most reliably at all scales for all the LasDamas, QPM, and Tiling mock catalogues.
+Furthermore, while the correction method of \cite{Gil-Marin:2014aa} is comparable our correction method, the parameter $x_\mathrm{PS}$ used in the method is calculated solely through a weighted galaxy mock catalogue.
+As an added advantage, our correction method can also be validated by the observed data rather than only through the mock catalogues.
+Therefore our correction method does not depend on the accuracy of the mock catalogues, thereby making it's application to observations further reliable.
 

### 2015-04-16 fc_paper/fc_paper.tex
First edits after Mike's comments
No substance change yet.

@@
 
-\title{Fiber Collision Correction Method for BOSS Power Spectrum}
+\title{A Fiber Collision Correction Method for the BOSS Power Spectrum}
 
 \author{ChangHoon~Hahn\altaffilmark{1}, 
-Michael R.~Blanton\altaffilmark{1}, 
-Roman~Scoccimarro\altaffilmark{1}} 
+Roman~Scoccimarro\altaffilmark{1}, 
+Michael R.~Blanton\altaffilmark{1}, others} 
 \altaffiltext{1}{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Place, New York, NY 10003; chh327@nyu.edu}
@@
 Fiber-fed multi-object spectroscopic surveys, with their ability to collect an unprecedented number of redshifts, dominate cosmological studies.
-However the physical size of fibers limit these surveys from successfully collecting redshifts from galaxies that are within the angular fiber-collision scale of one another, which ultimately lead to significant systematic effects on galaxy clustering measurements.
-Using simulated mock catalogues, extensively used in interpreting large-scale structure clustering results of the Sloan Digital Sky Survey, we investigate the effects of fiber-collisions on the galaxy power spectrum and compare the methods currently used to correct for fiber-collisions in the literature and assess their success in reconstructing the true power spectrum.
+However physical constraints limit these surveys from successfully collecting redshifts from galaxies that are too close to each other on the focal plane, which ultimately leads to significant systematic effects on galaxy clustering measurements.
+Using simulated mock catalogs, extensively used in interpreting large-scale structure clustering results of the Sloan Digital Sky Survey, we investigate the effects of fiber collisions on the galaxy power spectrum and compare the methods currently used to correct for fiber collisions in the literature and assess their success in reconstructing the true power spectrum.
 
-We present our fiber-collision correction method, which first statistically reconstructs the clustering of fiber-collided pairs by modeling the distribution of the line-of-sight displacements between them, and then properly accounts for fiber-collisions in the shot-noise correction term of the power spectrum estimator.
-Using our method, we successfully reproduce the true power spectrum for the mock catalogues with residuals of $< 1\%$ at $k \sim 0.3 \; h/\mathrm{Mpc}$ and $< 10\%$ at $k \sim 0.8 \; h/\mathrm{Mpc}$.
-Our comparisons to other correction methods demonstrate that our method most accurately reconstructs the true power spectrum from fiber-collided galaxy data especially at small scales ($k > 0.1\; h/\mathrm{Mpc}$), with the added advantage that our method can be validated and calibrated in observed data.
-With statistical uncertainty no longer dominating galaxy clustering measurements, our correction method will allows us constrain a main contributor to systematic effects and extend power spectrum measurements to smaller scales.
+We present our fiber collision correction method, which first statistically reconstructs the clustering of fiber collided pairs by modeling the distribution of the line-of-sight displacements between them using cases where both redshifts are obtained.
+The method properly accounts for fiber collisions in the shot-noise correction term of the power spectrum estimator.
+Using our method, we successfully reproduce the true power spectrum for the mock catalogs with residuals of $< 1\%$ at $k \sim 0.3 \; h/\mathrm{Mpc}$ and $< 10\%$ at $k \sim 0.8 \; h/\mathrm{Mpc}$.
+Our comparisons to other existing correction methods demonstrate that our method most accurately reconstructs the true power spectrum from fiber collided galaxy data especially at small scales ($k > 0.1\; h/\mathrm{Mpc}$), with the added advantage that our method can be validated and calibrated in observed data.
+With statistical uncertainty no longer dominating galaxy clustering measurements, our correction method will allow us to extend power spectrum measurements to smaller scales than previously possible.
 \end{abstract}
@@
 \section{Introduction} 
-Through the millions of redshifts obtained through redshift surveys, cosmological measurements such as galaxy clustering statistics are no longer dominated by uncertainties from statistical precision, but from systematic effects of the measurements.
-These surveys, such as the 2dF Galaxy Redshift Survey (2dFGRS; \citealt{Colless:1999aa}) and the Sloan Digital Sky Survey-III Baryon Oscillation Spectroscopic Survey (SDSS-III BOSS; \citealt{Anderson:2012aa, Dawson:2013aa}) and future surveys such as the Extended Baryon Oscillation Spectroscopic Survey (eBOSS; {\bf WHO DO CITE?}) use fiber-fed spectrographs.
+As of 2015, millions of redshifts to distant galaxies have been obtained through redshift surveys.
+Cosmological measurements such as galaxy clustering statistics are no longer dominated by uncertainties from statistical precision, but from systematic effects of the measurements.
+These surveys, such as the 2dF Galaxy Redshift Survey (2dFGRS; \citealt{Colless:1999aa}) and the Sloan Digital Sky Survey III Baryon Oscillation Spectroscopic Survey (SDSS-III BOSS; \citealt{Anderson:2012aa, Dawson:2013aa}) and future surveys such as the Extended Baryon Oscillation Spectroscopic Survey (eBOSS; {\bf WHO DO CITE?}) use fiber-fed spectrographs.
 
 For each galaxy, a fiber is used to obtain a spectroscopic redshift.
-However, due to the physical size of the fibers even with efficient targeting strategies (e.g.
-\citealt{Blanton:2003ab} for SDSS), if galaxies are located within the fiber-collision angular scale from one another on the sky, separate fibers cannot be placed adjacently to separately extract the spectroscopic information (\citealt{Yoon:2008aa} {\bf CITE MORE}).
-In these situations, the redshifts of fiber-collided galaxies are not individually resolved and only a single redshift is measured.
+However, due to the physical size of the fiber housing, if two galaxies are located within the fiber collision angular scale from one another on the sky, separate fibers cannot be placed adjacently to observe them simultaneously (\citealt{Yoon:2008aa} {\bf CITE MORE}).
+In these situations, only a single redshift is measured.
 With redshifts of galaxies in close angular proximities missing from the sample, any clustering statistic probing these scales will be systematically affected.
 
-As our cosmological surveys extend further to higher redshifts, the systematic effect becomes more severe as the fiber-collision angular scale corresponds to a larger comoving scale, thereby affecting our measurements on larger scales.
-SDSS-III BOSS, in particular, has an angular fiber-collision scale of $62"$.
-This corresponds to $\sim 0.4 \;\mathrm{Mpc}/h$ at the center of the survey's redshift redshift range; fiber-collided galaxies account for $\sim 5\%$ of the galaxy sample (\citealt{Anderson:2012aa}).
-Although this accounts for a relatively small fraction of redshifts, its effect on clustering measurements such as the power spectrum is significant and must be understood as these measurements probe to smaller scales and as higher order statistics such as the three-point correlation function or the bispectrum are used in cosmological studies.
-Perhaps with the use of robotic fiber positioner technology in future surveys such as the Dark Energy Survey Instrument (DESI; \citealt{Schlegel:2011aa, Morales:2012aa, Makarem:2014aa}) will render fiber-collisions obsolete.
-However, until then accounting for the systematic effects remains an unavoidable challenge for clustering statistics.
+As our cosmological surveys extend further to higher redshifts, the systematic effect becomes more severe because the fiber collision angular scale corresponds to a larger comoving scale, thereby affecting our measurements on larger scales.
+SDSS-III BOSS, in particular, has an angular fiber collision scale of $62''$.
+This corresponds to $\sim 0.4 \;\mathrm{Mpc}/h$ at the center of the survey's redshift redshift range; fiber collided galaxies account for $\sim 5\%$ of the galaxy sample (\citealt{Anderson:2012aa}).
+Although this accounts for a relatively small fraction of redshifts, its effect on clustering measurements such as the power spectrum is significant.
+They must to be accounted for to probe smaller scales and higher order statistics such as the three-point correlation function or the bispectrum.
+Even with the use of robotic fiber positioner technology in future surveys such as the Dark Energy Survey Instrument (DESI; \citealt{Schlegel:2011aa, Morales:2012aa, Makarem:2014aa})
+% What is the fiber positioner areas called??
+will render fiber collisions obsolete. Therefore, accounting for the systematic effects remains an unavoidable challenge for clustering statistics.
 
 To correct for fiber collisions, one common approach used in clustering statistics is the nearest neighbor method (\citealt{Zehavi:2002aa, Berlind:2006aa, Anderson:2012aa}).
-For fiber-collided galaxies without resolved redshifts, the method assigns the statistical weight of the fiber-collided galaxy to its nearest angular neighbor.
-This provides a reasonable correction for the fiber-collision effects at scales much larger than the fiber-collision scales; however the correction falls short near the fiber-collision scale.
-In fact, as \cite{Zehavi:2005aa} find, fiber-collisions affect the two-point correlation function (2PCF) measurements even on scales significantly larger than the fiber-collision scale ( $> 1\;\mathrm{Mpc}/h$).
-For power spectrum measurements in BOSS, the nearest neighbor method has often been supplemented with adjustments in the constant shot-noise term of the power spectrum estimator to correct for fiber-collisions (\citealt{Beutler:2014aa, Gil-Marin:2014aa}).
-While this shot-noise term adjustment has been calibrated within the mock catalogues used to interpret the BOSS clustering results there is no way to validate and calibrate these methods independently for observations.
-Methods of this kind rely entirely on the accuracy of the mock catalogues to constrain fiber-collisions, which is especially concerning since fiber-collisions systematically affect small scales and mock catalogues may not be realiable at such small scales (\citealt{Heitmann:2008aa, Schneider:2015aa}).
+For fiber collided galaxies without resolved redshifts, the method assigns the statistical weight of the fiber collided galaxy to its nearest angular neighbor.
+This provides a reasonable correction for the fiber collision effects at scales much larger than the fiber collision scales; however the correction falls short near the fiber collision scale.
+In fact, as \cite{Zehavi:2005aa} find, fiber collisions affect the two-point correlation function (2PCF) measurements even on scales significantly larger than the fiber collision scale ( $> 1\;\mathrm{Mpc}/h$).
+For power spectrum measurements in BOSS, the nearest neighbor method has often been supplemented with adjustments in the constant shot-noise term of the power spectrum estimator to correct for fiber collisions (\citealt{Beutler:2014aa, Gil-Marin:2014aa}).
+While this shot-noise term adjustment has been calibrated within the mock catalogs used to interpret the BOSS clustering results there is no way to validate and calibrate these methods independently for observations.
+Methods of this kind rely entirely on the accuracy of the mock catalogs to constrain fiber collisions, which is especially concerning since fiber collisions systematically affect small scales and mock catalogs may not be realiable at such small scales (\citealt{Heitmann:2008aa, Schneider:2015aa}).
 
-Recently \cite{Guo:2012aa}, focusing on SDSS-III BOSS like samples, proposed a fiber-collision correction method for the 2PCF that is able to reasonably correct for fiber-collisions above and below the collision scale.
-\cite{Guo:2012aa} estimates the total contribution of fiber-collided galaxies to the two point correlation function by examining the pair statistics in overlapping tiling regions of the survey, where a smaller fraction of galaxies suffer from fiber-collisions.
-Unfortunately, this method cannot be applied to the Fourier clustering measurements due to the complex geometry of the overlapping regions.
-As a result, we propose a fiber-collision correction method that, first, improves upon the nearest neighbor method by using the distribution of the line-of-sight displacement between resolved fiber-collided galaxies to statistically reconstruct the clustering of fiber-collided galaxies; and properly accounts for fiber-collisions in the shot-noise correction term of the power spectrum estimator.
+Recently \cite{Guo:2012aa}, focusing on SDSS-III BOSS like samples, proposed a fiber collision correction method for the 2PCF that is able to reasonably correct for fiber collisions above and below the collision scale.
+\cite{Guo:2012aa} estimates the total contribution of fiber collided galaxies to the two point correlation function by examining the pair statistics in overlapping tiling regions of the survey, where a smaller fraction of galaxies suffer from fiber collisions.
+Unfortunately, due to the complex geometry of the overlapping regions, this method is difficult to apply to Fourier clustering measurements.
+As a result, we propose a fiber collision correction method that, first, improves upon the nearest neighbor method by using the distribution of the line-of-sight displacement between resolved fiber collided galaxies to statistically reconstruct the clustering of fiber collided galaxies; and properly accounts for fiber collisions in the shot-noise correction term of the power spectrum estimator.
 
-In Section \ref{sec:catalog}, we present a brief description of the simulated mock catalogues with realistically applied fiber-collisions and the power spectrum estimator used throughout the paper.
-Then during our discussion of the two components of our correction method in Section \ref{sec:fc_corr}, we quantify the effects of fiber-collisions of power spectrum measurements and test and compare correction methods in the literature.
-Afterwards, we present our correction method, test it on the mock catalogues, and compare it to other correction methods in Section \ref{sec:results}.
+In Section \ref{sec:catalog}, we present a brief description of the simulated mock catalogs with realistically applied fiber collisions and the power spectrum estimator used throughout the paper.
+Then during our discussion of the two components of our correction method in Section \ref{sec:fc_corr}, we quantify the effects of fiber collisions of power spectrum measurements and test and compare correction methods in the literature.
+Afterwards, we present our correction method, test it on the mock catalogs, and compare it to other correction methods in Section \ref{sec:results}.
 Finally in Section \ref{sec:summary} we summarize and discuss our results.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Fiber-collided Mock Catalogues
+% fiber collided Mock catalogs
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Fiber-collided Mock Catalogues} \label{sec:catalog}
-For various purposes such as calculating covariance matrices or estimating cosmic variance, simulated mock catalogues play a crucial role in interpreting clustering measurements of observed galaxies (\citealt{Scoccimarro:2002aa, Anderson:2012aa, Manera:2013aa}).
-They also provide a means of understanding systematic effects such as fiber-collisions (\citealt{Guo:2012aa, Manera:2013aa} {\bf LIST MORE}) since systematic effects can be simulated on the mock catalogues.
+\section{fiber collided Mock catalogs} \label{sec:catalog}
+For various purposes such as calculating covariance matrices or estimating cosmic variance, simulated mock catalogs play a crucial role in interpreting clustering measurements of observed galaxies (\citealt{Scoccimarro:2002aa, Anderson:2012aa, Manera:2013aa}).
+They also provide a means of understanding systematic effects such as fiber collisions (\citealt{Guo:2012aa, Manera:2013aa} {\bf LIST MORE}) since systematic effects can be simulated on the mock catalogs.
 This allows us to test how these effects influence clustering measurements and devise correction methods that attempt to account for these effects.
 
-A direct way of understanding the effects of fiber-collisions on clustering statistics in observations is to first apply fiber-collisions to mock catalogues then compare the clustering statistics obtained from mock catalogues with and without the fiber collisions.
-Correction methods for fiber-collisions can then be applied to the fiber-collided mocks and the merit of the correction method can be quantified by how successfully they reproduce the clustering statistics of the original mock catalogues without fiber-collisions.
-The optimal correction method can then be applied to the observed data with some assurance that it accounts for fiber-collisions and improves the clustering measurements.
+A direct way of understanding the effects of fiber collisions on clustering statistics in observations is to first apply fiber collisions to mock catalogs and then compare the clustering statistics obtained from mock catalogs with and without the fiber collisions.
+Correction methods for fiber collisions can then be applied to the fiber collided mocks and the merit of the correction method can be quantified by how successfully they reproduce the clustering statistics of the original mock catalogs without fiber collisions.
+The optimal correction method can then be applied to the observed data with some assurance that it accounts for fiber collisions and improves the clustering measurements.
 
-When applying the fiber-collisions to the mock catalogues, it is essential to apply them in the same manner they affect the observational data.
-For BOSS, galaxies within $62"$ are fiber-collided (\citealt{Anderson:2012aa}).
-In reality, this simple criteria is further complicated by the tiling scheme of observing plates that create overlapping regions, which have a higher success rate in resolving galaxy spectra within the fiber-collision angular scale (\citealt{Guo:2012aa}).
-Furthermore, fiber-collisions are only one of the systematic effects that influence BOSS data.
+When applying the fiber collisions to the mock catalogs, it is essential to apply them in the same manner they affect the observational data.
+For BOSS, galaxies within $62"$ are fiber collided (\citealt{Anderson:2012aa}).
+In reality, this simple criteria is further complicated by the tiling scheme of observing plates that create overlapping regions, which have a higher success rate in resolving galaxy spectra within the fiber collision angular scale (\citealt{Guo:2012aa}).
+Furthermore, fiber collisions are only one of the systematic effects that influence BOSS data.
 Systematic effects include the unique geometry of the BOSS survey, the variable completeness in different sectors of the survey, and redshift failures (\citealt{Anderson:2012aa}).
@@
 \includegraphics[scale=0.45]{fcpaper_z_dist.png} \label{fig:zdist}
-\caption{Normalized galaxy redshift distribution for LasDamas (\ldgcolor), QPM (\qpmcolor), and Tiling Mock (\tmcolor) mock catalogues.
+\caption{Normalized galaxy redshift distribution for LasDamas (\ldgcolor), QPM (\qpmcolor), and Tiling Mock (\tmcolor) mock catalogs.
 The normalized redshift distribution of BOSS DR12 CMASS is also plotted (\cmasscolor).
 Bin size of $\Delta z = 0.025$ was used to compute the each of the distributions.
-LasDamas mock catalogue has a constant number density of galaxies throughout $0.16 < z < 0.44$, the redshift range of SDSS LRG sample.
-QPM and Tiling Mock catalogues, on the other hand, trace the BOSS CMASS redshift distribution ($0.43 < z < 0.7$).}
+LasDamas mock catalog has a constant number density of galaxies throughout $0.16 < z < 0.44$, the redshift range of SDSS LRG sample.
+QPM and Tiling Mock catalogs, on the other hand, trace the BOSS CMASS redshift distribution ($0.43 < z < 0.7$).}
 % perhaps the range should be wider and make it full text width that way the tail can be portrayed better. Keep the same aspect ratio. 
@@
 
-Effects of fiber-collisions must be understood and interpreted in conjunction with these other systematic effects.
-Therefore, in this paper, we use LasDamas (\citealt{McBride:2009aa, McBride:2011aa}), Quick Particle Mesh (\citealt{White:2014aa}), and Tiling mock catalogues, which have already been extensively used in interpreting clustering results for SDSS and BOSS and are generated through different prescriptions.
-Therefore they provide complementary data sets to measure the effects of fiber-collisions and to test our correction method tailored for BOSS.
-%Each of these mock catalogues use some sort of N-body dark matter simulation along with a HOD prescription to populate the dark matter halos with ``galaxies".
+Effects of fiber collisions must be understood and interpreted in conjunction with these other systematic effects.
+Therefore, in this paper, we use LasDamas (\citealt{McBride:2009aa, McBride:2011aa}), Quick Particle Mesh (\citealt{White:2014aa}), and Tiling mock catalogs ({\bf CITATIONS?}), which have already been extensively used in interpreting clustering results for SDSS and BOSS and are generated through different prescriptions.
+Therefore they provide unique data sets to measure the effects of fiber collisions and to test our correction method tailored for BOSS.
+%Each of these mock catalogs use some sort of N-body dark matter simulation along with a HOD prescription to populate the dark matter halos with ``galaxies".
 % Include brief detail on what each mock has to offer
 
-The LasDamas Galaxy mock catalogues is constructed from the Oriana N-body Large Suite of Dark Matter Simulations (LasDamas) with $1280^3$ particles with a box with side length, $L_\mathrm{Box} = 2400\;\mathrm{Mpc}/h$.
-The N-body LasDamas simulations uses a spatially flat $\Lambda$CDM cosmology with $\Omega_\mathrm{m} = 0.25$, $\Omega_\Lambda = 0.75$, $\Omega_\mathrm{b} = 0.04$, $\sigma_8 = 0.8$, $n_\mathrm{s} = 1$ and $h=0.7$.
+The LasDamas Galaxy mock catalogs are constructed from the Oriana N-body Large Suite of Dark Matter Simulations (LasDamas) with $1280^3$ particles with a box with side length, $L_\mathrm{Box} = 2400\;\mathrm{Mpc}/h$.
+The N-body LasDamas simulations use a spatially flat $\Lambda$CDM cosmology with $\Omega_\mathrm{m} = 0.25$, $\Omega_\Lambda = 0.75$, $\Omega_\mathrm{b} = 0.04$, $\sigma_8 = 0.8$, $n_\mathrm{s} = 1$ and $h=0.7$.
 The dark matter halos are then identified using a friends-of-friends (FOF) algorithm (\citealt{Davis:1985aa}) with a linking length $b = 0.2 $ times the mean interparticle separation.
-The over-densities of dark matter halos are then populated with galaxies using the halo occupation distribution (HOD) framework to construct the galaxy mock catalogues (\citealt{McBride:2009aa, McBride:2011aa}).
-The HOD prescription is specified so that the galaxy mock catalogues reproduce the galaxy number density and projected correlation function of the observed SDSS Luminous Red Galaxy sample with $M_g < -21.8$.
-The LasDamas galaxy mock catalogues have 40 realizations that spans the redshift range, $0.16 < z < 0.44$ and are restricted to the survey geometry of SDSS Data Release 7.
-They also include redshift space distortions from velocities, but do not model fiber-collisions.
+The over-densities of dark matter halos are then populated with galaxies using the halo occupation distribution (HOD) framework to construct the galaxy mock catalogs (\citealt{McBride:2009aa, McBride:2011aa}).
+The HOD prescription is specified so that the galaxy mock catalogs reproduce the galaxy number density and projected correlation function of the observed SDSS Luminous Red Galaxy sample with $M_g < -21.8$.
+The LasDamas galaxy mock catalogs have 40 realizations, each of which spans the redshift range, $0.16 < z < 0.44$ and are restricted to the survey geometry of SDSS Data Release 7.
+They also include redshift space distortions from velocities, but do not model fiber collisions.
 
-To model the fiber-collisions of the observed galaxies in BOSS, we impose fiber-collisions at the angular scale of $62''$.
+To model the fiber collisions of the observed galaxies in BOSS, we impose fiber collisions at the angular scale of $62''$.
 Once we identify galaxies within $62''$ of each other, we arbitrary select one of the galaxies and assign the statistical weights of the other galaxies within $62''$ of it.
-Roughly $\sim 2.5 \%$ of the galaxies in the LasDamas mock catalogues are affected by fiber-collisions.
+Roughly $\sim 2.5 \%$ of the galaxies in the LasDamas mock catalogs are affected by fiber collisions.
 
-Next, the QPM mock galaxy catalogues uses a ``quick particle mesh" method, which uses a low resolution particle-mesh N-body solver to evolve particles within a period simulation volume.
+Next, the QPM mock galaxy catalogs uses a ``quick particle mesh" method, which uses a low resolution particle-mesh N-body solver to evolve particles within a period simulation volume.
 The particles are assigned halo masses  in order to match the halo mass function and large-scale bias of halos of high resolution simulations.
 Afterward the \cite{Tinker:2012aa} HOD parameterization is used to populate the halos.
-The mock galaxy sample is then trimmed to the BOSS CMASS survey footprint, downsamped based on angular sky completeness (sector completeness) and radial selection.
-Furthermore, QPM mocks model the fiber-collisions of the BOSS CMASS sample ($62''$ angular fiber-collision scale).
-The QPM galaxy mock catalogue uses the following $\Lambda$CDM cosmology: $\Omega_\mathrm{m} = 0.29$, $\Omega_\Lambda = 0.71$, $\sigma_8 = 0.8$, $n_\mathrm{s} = 0.97$ and $h=0.7$.
-We use 1000 realizations of the QPM galaxy mock catalogue.
-For a detailed description of the QPM galaxy mock catalogues we refer readers to \cite{White:2014aa}.
+The mock galaxy sample is then trimmed to the BOSS CMASS survey footprint, downsampled based on angular sky completeness (sector completeness) and radial selection.
+Furthermore, QPM mocks model the fiber collisions of the BOSS CMASS sample ($62''$ angular fiber collision scale).
+The QPM galaxy mock catalog uses the following $\Lambda$CDM cosmology: $\Omega_\mathrm{m} = 0.29$, $\Omega_\Lambda = 0.71$, $\sigma_8 = 0.8$, $n_\mathrm{s} = 0.97$ and $h=0.7$.
+We use 1000 realizations of the QPM galaxy mock catalog.
+For a detailed description of the QPM galaxy mock catalogs we refer readers to \cite{White:2014aa}.
 
-Finally the Tiling Mock catalogue is generated using
+Finally the Tiling Mock catalog is generated using
 
@@
 
-In Figure \ref{fig:zdist}, we plot the redshift distribution for LasDamas, QPM, and Tiling Mock catalogues along with the redshift distribution of BOSS DR12 galaxies.
-The LasDamas mock catalogue, which is constructed based on the SDSS LRG sample has a constant $\bar{n}(z)$ over the redshift $0.16 < z< 0.44$, while the QPM and Tiling mock redshift distributions closely trace the observed BOSS redshift distribution (roughly $0.43 < z < 0.7$).
+In Figure \ref{fig:zdist}, we plot the redshift distribution for LasDamas, QPM, and Tiling Mock catalogs along with the redshift distribution of BOSS DR12 galaxies.
+The LasDamas mock catalog, which is constructed based on the SDSS LRG sample has a constant $\bar{n}(z)$ over the redshift $0.16 < z< 0.44$, while the QPM and Tiling mock redshift distributions closely trace the observed BOSS redshift distribution (roughly $0.43 < z < 0.7$).
 
 \subsection{Power Spectrum Estimator} \label{sec:pk_est}
-In this paper, we focus on the effects of fiber-collisions on the galaxy power spectrum out of the other clustering measurements.
+In this paper, we focus on the effects of fiber collisions on the galaxy power spectrum out of the other clustering measurements.
 Throughout the paper, when we measure the power spectrum, we use the standard \cite{Feldman:1994aa} (hereafter FKP) estimator and the following formalisms from the FKP paper:
@@
 and the second term represents the constant shot-noise contribution to the power due to the discrete density field of our galaxies.
-$n_g$ is the galaxy density, $n_r$ is the density of the synthetic random catalogue, $\alpha$ is the ratio of the number of galaxies over the number of synthetic random galaxies, $\bar{n}$ is the mean density of the galaxies, and $w_{\mathrm{FKP}}$ is the minimum variance weight derived in \cite{Feldman:1994aa}:
+$n_g$ is the galaxy density, $n_r$ is the density of the synthetic random catalog, $\alpha$ is the ratio of the number of galaxies over the number of synthetic random galaxies, $\bar{n}$ is the mean density of the galaxies, and $w_{\mathrm{FKP}}$ is the minimum variance weight derived in \cite{Feldman:1994aa}:
 \begin{equation}
@@
 \includegraphics[scale=0.5]{fcpaper_pk_comp.png} 
-\caption{Average power spectrum $\overline{P(k)}$ for BOSS DR12 (black) and the mock catalogues LasDamas (blue), QPM (orange), and Tiling Mock (green), listed in Section \ref{sec:catalog} using the FKP $P(k)$ estimator.
-The width of the $P(k)$ for LasDamas and QPM represent the sample variance ($\Delta P(k)$) calculated from the multiple realizations of the mock catalogues.
-We emphasize that fiber-collisions were not applied to the mock catalogues for the $P(k)$ measurements.
+\caption{Average power spectrum $\overline{P(k)}$ for BOSS DR12 (black) and the mock catalogs LasDamas (blue), QPM (orange), and Tiling Mock (green), listed in Section \ref{sec:catalog} using the FKP $P(k)$ estimator.
+The width of the $P(k)$ for LasDamas and QPM represent the sample variance ($\Delta P(k)$) calculated from the multiple realizations of the mock catalogs.
+We emphasize that fiber collisions were not applied to the mock catalogs for the $P(k)$ measurements.
 Meanwhile, galaxy weights (Equation \ref{eq:weight}) are applied to the BOSS DR12 $P(k)$ measurement.
-We remind readers that the LasDamas mock catalogue has an overall greater $\overline{P(k)}$ due to the fact that the catalogue spans the SDSS LRG sample redshift range instead of the BOSS redshift range of the other mock catalogues.} \label{fig:mockpk}
+We remind readers that the LasDamas mock catalog has an overall greater $\overline{P(k)}$ due to the fact that the catalog spans the SDSS LRG sample redshift range instead of the BOSS redshift range of the other mock catalogs.} \label{fig:mockpk}
 \end{center}
@@
 
-For LasDamas, QPM, and Tiling mock catalogues we use the FKP estimator described above to measure the power spectrum in Figure \ref{fig:mockpk}.
-The fiber-collisions described previously are not applied to the mock catalogues in the $P(k)$ calculations for Figure \ref{fig:mockpk}.
-Without fiber-collisions, we use the exact formulation of Equation \ref{eq:fkppk} in the FKP power spectrum estimator.
+For LasDamas, QPM, and Tiling mock catalogs we use the FKP estimator described above to measure the power spectrum in Figure \ref{fig:mockpk}.
+The fiber collisions described previously are not applied to the mock catalogs in the $P(k)$ calculations for Figure \ref{fig:mockpk}.
+Without fiber collisions, we use the exact formulation of Equation \ref{eq:fkppk} in the FKP power spectrum estimator.
 
 We also plot the $P(k)$ from the BOSS Data Release 12 CMASS data (\cmasscolor) in Figure \ref{fig:mockpk}.
-For BOSS DR12 CMASS, systematic weights are assigned to the galaxies in order to account for sector completeness, redshift failures, and fiber-collisions.
+For BOSS DR12 CMASS, systematic weights are assigned to the galaxies in order to account for sector completeness, redshift failures, and fiber collisions.
 Each galaxy has a statistical weight determined by,
@@
 \includegraphics[scale=0.575]{fcpaper_dlos_dist.png}
-\caption{Normalized distribution of $d_{\mathrm{LOS}}$ for LasDamas (\ldgcolor), QPM (\qpmcolor), and Tiling Mock (\tmcolor) mock catalogues.
+\caption{Normalized distribution of $d_{\mathrm{LOS}}$ for LasDamas (\ldgcolor), QPM (\qpmcolor), and Tiling Mock (\tmcolor) mock catalogs.
 The normalized $d_{\mathrm{LOS}}$ distribution of BOSS DR12 is also plotted (\cmasscolor).
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Fiber-collision Correction Method
+% fiber collision Correction Method
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Fiber-collision Correction Method} \label{sec:fc_corr}
-As mentioned above, a common approach in accounting for fiber-collisions in clustering measurements has been to use the nearest angular neighbor method (\citealt{Zehavi:2002aa, Berlind:2006aa, Anderson:2012aa}).
-For galaxies without resolved spectroscopic redshifts due to fiber-collisions, the entire statistical weight of the galaxy is assigned to its nearest angular neighbor.
-This method assumes that all galaxies within the angular fiber-collision scale ($< 62 "$ for BOSS) are correlated with one another.
-In other words, the method assumes that galaxies within the fiber-collision angular scale reside in the same halo so displacing one and placing it on top of the other does not significantly alter the clustering statistics.
-One consequence of this method however is that galaxies within the angular fiber-collision scale purely by coincidence (hereafter referred to as ``chance alignments") are incorrectly assumed to be gravitationally correlated, so when their statistical weight is added to its nearest angular neighbor, they are in fact displaced significantly from its true position.
+\section{fiber collision Correction Method} \label{sec:fc_corr}
+As mentioned above, a common approach in accounting for fiber collisions in clustering measurements has been to use the nearest angular neighbor method (\citealt{Zehavi:2002aa, Berlind:2006aa, Anderson:2012aa}).
+For galaxies without resolved spectroscopic redshifts due to fiber collisions, the entire statistical weight of the galaxy is assigned to its nearest angular neighbor.
+This method effectively assumes that all galaxies within the angular fiber collision scale ($< 62 "$ for BOSS) are correlated with one another.
+In other words, the method assumes that galaxies within the fiber collision angular scale reside in the same halo so displacing one and placing it on top of the other does not significantly alter the clustering statistics.
+One consequence of this method however is that galaxies within the angular fiber collision scale purely by coincidence (hereafter referred to as ``chance alignments") are incorrectly assumed to be gravitationally correlated, so when their statistical weight is added to its nearest angular neighbor, they are in fact displaced significantly from their true position.
 For BOSS, the nearest angular neighbor method can displace galaxies by up to $500 \;\mathrm{Mpc}$.
-Furthermore even for fiber-collided galaxies that reside in the same group or cluster, up-weighting the nearest neighbor ignores halo-scale line-of-sight displacements, which as we present in Section \ref{sec:dlos}, are significant.
+Furthermore even for fiber collided galaxies that reside in the same group or cluster, up-weighting the nearest neighbor ignores halo-scale line-of-sight displacements, which as we present in Section \ref{sec:dlos}, are significant.
 
 Although the nearest-neighbor method provides a reasonable estimate at large scales, in Section \ref{sec:dlos} we demonstrate that at small scales its effects on the power spectrum are significant and dominate sample variance.
-We present an improved method to account for correlated fiber-collided galaxies using the line-of-sight displacement between fiber-collided pairs.
-Then in Section \ref{sec:shotnoise}, we present modifications to the FKP power spectrum estimator in order to properly account for fiber-collisions through the shot-noise correction term in the estimator.
+We present an improved method to account for correlated fiber collided galaxies using the line-of-sight displacement between fiber collided pairs.
+Then in Section \ref{sec:shotnoise}, we present modifications to the FKP power spectrum estimator in order to properly account for fiber collisions through the shot-noise correction term in the estimator.
+
+% MAKE SURE IT IS CLEAR THAT OUR CORRECTION METHOD COMBINES THE TWO.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Line-of-Sight Displacement of Fiber-collided Pairs} \label{sec:dlos}
-It is impossible to determine from observed galaxy data whether fiber-collided galaxies without resolved spectroscopic redshift are correlated or chance alignments.
-Fortunately, using the fiber-collided pairs with resolved redshifts (mainly in the overlapping regions mentioned in Section \ref{sec:catalog}), it is possible to model the line-of-sight displacement of the fiber-collided pairs and the fraction of galaxy pairs that are corrected and uncorrelated.
+\subsection{Line-of-Sight Displacement of fiber collided Pairs} \label{sec:dlos}
+It is impossible to determine definitely from observed galaxy data whether individual fiber collided galaxies without resolved spectroscopic redshift are correlated or chance alignments.
+Fortunately, using the fiber collided pairs with resolved redshifts (mainly in the overlapping regions mentioned in Section \ref{sec:catalog}), it is possible to model the line-of-sight displacement of the fiber collided pairs and the fraction of galaxy pairs that are corrected and uncorrelated.
 
-For simulated mock catalogues, described in Section \ref{sec:catalog}, modeling the fiber-collided galaxy pairs is a much more direct task since fiber-collisions are post-processed after the simulated galaxy positions are generated.
-All redshift values are provided for all galaxies regardless of angular proximity and the fiber-collisions imposed on the mock catalogues are represented through the galaxies' ``fiber-collision weights" ($w_\mathrm{fc}$).
-So for a fiber-collided pair, one galaxy (``the nearest neighbor") will have the fiber-collision weight of both galaxies, while the other has $w_\mathrm{fc} = 0$.
-Nonetheless, with redshifts of both fiber-collided pair galaxies in mock catalogues, we can model the correlated and uncorrelated fiber-collided pairs in order to better correct for fiber-collisions.
+For simulated mock catalogs, described in Section \ref{sec:catalog}, modeling the fiber collided galaxy pairs is a much more direct task since fiber collisions are post-processed after the simulated galaxy positions are generated.
+All redshift values are provided for all galaxies regardless of angular proximity and the fiber collisions imposed on the mock catalogs are represented through the galaxies' ``fiber collision weights" ($w_\mathrm{fc}$).
+So for a fiber collided pair, one galaxy (``the nearest neighbor") will have the fiber collision weight of both galaxies, while the other has $w_\mathrm{fc} = 0$.
+Nonetheless, with redshifts of both fiber collided pair galaxies in mock catalogs, we can model the correlated and uncorrelated fiber collided pairs in order to better correct for fiber collisions.
 
-To determine whether or not fiber-collided pairs are correlated, we examine the comoving line-of-sight displacement ($d_{\mathrm{LOS}}$) of fiber-collided galaxy pairs.
+To determine whether or not fiber collided pairs are correlated, we examine the comoving line-of-sight displacement ($d_{\mathrm{LOS}}$) of fiber collided galaxy pairs.
 We calculate the $d_{\mathrm{LOS}}$ by taking the difference of the line-of-sight comoving distance from the resolved redshifts:
@@
 \end{equation}
-$D_{\mathrm{C}}(z)$ is the line-of-sight comoving distance at redshift $z$ (\citealt{Hogg:1999aa}). $z_1$ and $z_2$ represent the resolved redshifts of the galaxies in the fiber-collided pair.
+$D_{\mathrm{C}}(z)$ is the line-of-sight comoving distance at redshift $z$ (\citealt{Hogg:1999aa}). $z_1$ and $z_2$ represent the resolved redshifts of the galaxies in the fiber collided pair.
 
-After calculating the $d_{\mathrm{LOS}}$ for every fiber-collided pairs, in Figure \ref{fig:d_los} we present the distribution of $d_{\mathrm{LOS}}$ for LasDamas (\ldgcolor), QPM (\qpmcolor), Tiling Mock (\tmcolor), and BOSS DR12 (\cmasscolor).
+After calculating the $d_{\mathrm{LOS}}$ for every fiber collided pairs, in Figure \ref{fig:d_los} we present the distribution of $d_{\mathrm{LOS}}$ for LasDamas (\ldgcolor), QPM (\qpmcolor), Tiling Mock (\tmcolor), and BOSS DR12 (\cmasscolor).
 All of the $d_{\mathrm{LOS}}$ distributions contain two components: a peak contained within the range $-20\;\mathrm{Mpc} < d_{\mathrm{LOS}} < 20\;\mathrm{Mpc}$ and a flat component (hereafter "tail" component) outside the peak that extends to $d_{\mathrm{LOS}} \sim \pm 500 \;\mathrm{Mpc}$ (entire range of the distribution not displayed in Figure \ref{fig:d_los}).
-For the BOSS data, since we cannot compute the $d_\mathrm{LOS}$ for fiber-collided pairs without resolved spectra, the $d_\mathrm{LOS}$ distribution only reflects the $d_\mathrm{LOS}$ from fiber-colldied pairs {\em with} resolved spectroscopic redshifts, mostly from tile overlapping regions of the BOSS survey.
+For the BOSS data, since we cannot compute the $d_\mathrm{LOS}$ for fiber collided pairs without spectra, the $d_\mathrm{LOS}$ distribution only reflects the $d_\mathrm{LOS}$ from fiber collided pairs {\em with} resolved spectroscopic redshifts, mostly from tile overlapping regions of the BOSS survey.
 
@@
 These galaxies in over-dense regions cause the peak in the $d_{\mathrm{LOS}}$ distribution.
-While the ``tail" component is composed of chance alignment galaxy pairs that are arbitrarily in close angular proximity even when they are not correlated.
+The ``tail" component is composed of chance alignment galaxy pairs that happen to be in close angular proximity.
 
@@
 \end{equation}
- for a mathematical prescription of the $d_{\mathrm{LOS}}$ distribution peak as a function of the displacement for each of the data catalogues in Figure \ref{fig:d_los}.
+ for a mathematical prescription of the $d_{\mathrm{LOS}}$ distribution peak as a function of the displacement for each of the data catalogs in Figure \ref{fig:d_los}.
 The best-fit $\sigma$ and $A$ parameters are obtained by fitting Equation \ref{eq:peak} to the $d_{\mathrm{LOS}}$ distribution peaks using MPFIT (\citealt{Markwardt:2009aa}).
-We list the values of $\sigma$ obtained for the mock catalogues in Table \ref{tab:mpfit}.
-Both Table \ref{tab:mpfit} and Figure \ref{fig:d_los} illustrate that the $d_{\mathrm{LOS}}$ distributions for the mock catalogues closely trace the distribution of the BOSS DR12, which further goes to support the use of mock catalogues in our investigation of fiber-collisions.
+We list the values of $\sigma$ obtained for the mock catalogs in Table \ref{tab:mpfit}.
+Both Table \ref{tab:mpfit} and Figure \ref{fig:d_los} illustrate that the $d_{\mathrm{LOS}}$ distributions for the mock catalogs closely trace the distribution of the BOSS DR12, which further goes to support the use of mock catalogs in our investigation of fiber collisions.
 
@@
  \begin{tabular}{ccc} \hline \hline
-Catalogue &$\sigma$ ($\mathrm{Mpc}$) & $f_{\mathrm{peak}}$\\ \hline
+catalog &$\sigma$ ($\mathrm{Mpc}$) & $f_{\mathrm{peak}}$\\ \hline
 LasDamas 	& 6.85	& 0.71 \\ 
@@
 
-Using the best-fit to the peak of the $d_{\mathrm{LOS}}$ distribution, we estimate the fraction of fiber-collided pairs that are within the peak: 
+Using the best-fit to the peak of the $d_{\mathrm{LOS}}$ distribution, we estimate the fraction of fiber collided pairs that are within the peak: 
 \begin{equation}
@@
 \end{equation}
-where $N_{\mathrm{pairs}}$ is the total number of fiber-collided pairs.
-As mentioned above, this portion of fiber-collided pairs are galaxy pairs that are correlated.
-We list the $f_{\mathrm{peak}}$ values for each of the data catalogues in Table \ref{tab:mpfit}.
-The $f_\mathrm{peak}$ values for the mock catalogue are also in reasonable agreement with the BOSS DR12 $f_\mathrm{peak}$.
+where $N_{\mathrm{pairs}}$ is the total number of fiber collided pairs.
+As mentioned above, this portion of fiber collided pairs are galaxy pairs that are correlated.
+We list the $f_{\mathrm{peak}}$ values for each of the data catalogs in Table \ref{tab:mpfit}.
+The $f_\mathrm{peak}$ values for the mock catalog are also in reasonable agreement with the BOSS DR12 $f_\mathrm{peak}$.
 
@@
 By simply incorporating the peak of the $d_{\mathrm{LOS}}$ distribution, we are able to significantly improve clustering statistics on small scales.
-Rather than placing the fiber-collided galaxy on top of its nearest angular neighbor as NN correction does, placing the fiber-collided galaxy at a displacement sampled from the $d_{\mathrm{LOS}}$ distribution away from its nearest neighbor better accounts for the small scale in clustering measurements.
-On mock catalogues, we test this by first applying the NN to the mock catalogues.
-We then sample a displacement $d_i$ from $p(d_\mathrm{LOS})$ (Equation \ref{eq:peak}) for each fiber-collided pair.
-Afterwards we ``place" the fiber-collided galaxy a distance $d_i$ from the nearest neighbor galaxy assign $w_\mathrm{fc} = 1$ and reduce the $w_\mathrm{fc}$ of the the nearest-neighbor by 1.
+Rather than placing the fiber collided galaxy on top of its nearest angular neighbor as NN correction does, placing the fiber collided galaxy at a displacement sampled from the $d_{\mathrm{LOS}}$ distribution away from its nearest neighbor better accounts for the small scale in clustering measurements.
+On mock catalogs, we test this by first applying the NN to the mock catalogs.
+We then sample a displacement $d_i$ from $p(d_\mathrm{LOS})$ (Equation \ref{eq:peak}) for each fiber collided pair.
+Afterwards we ``place" the fiber collided galaxy a distance $d_i$ from the nearest neighbor galaxy assign $w_\mathrm{fc} = 1$ and reduce the $w_\mathrm{fc}$ of the the nearest-neighbor by 1.
 We refer to this method as ``$d_\mathrm{LOS}$-peak".
@@
 \includegraphics[scale=0.55]{fcpaper_pk_peakonly_comp.png} 
-\caption{The ratio of $\overline{P_\mathrm{corr} (k)}$ using the nearest-neighbor (NN) correction (blue) and $d_\mathrm{LOS}$-peak correction (orange) over the true $\overline{P(k)}$ for LasDamas (left panel), QPM (middle panel), and Tiling Mock (right panel) catalogues.
+\caption{The ratio of $\overline{P_\mathrm{corr} (k)}$ using the nearest-neighbor (NN) correction (blue) and $d_\mathrm{LOS}$-peak correction (orange) over the true $\overline{P(k)}$ for LasDamas (left panel), QPM (middle panel), and Tiling Mock (right panel) catalogs.
 The NN correction and $d_\mathrm{LOS}$-peak correction methods are described in Section \ref{sec:dlos}.
 We also plot the ratio of the sample variance to the true $\overline{P_\mathrm{truee}(k)}$, $\Delta P_\mathrm{true}(k) / \overline{P_\mathrm{true}(k)}$ (black; dashed) for comparison.
-Incorporating the $d_{\mathrm{LOS}}$ distribution significantly improves the correction of fiber-collisions for $k > 0.1 \; h/\mathrm{Mpc}$; however, neither method is able to constrain the systematic effects of fiber-collisions significantly below the sample variance at $k > 0.2 \; h/\mathrm{Mpc}$.}\label{fig:peakonly}
+Incorporating the $d_{\mathrm{LOS}}$ distribution significantly improves the correction of fiber collisions for $k > 0.1 \; h/\mathrm{Mpc}$; however, neither method is able to constrain the systematic effects of fiber collisions significantly below the sample variance at $k > 0.2 \; h/\mathrm{Mpc}$.}\label{fig:peakonly}
 \end{center}
@@
 The $d_\mathrm{LOS}$-peak correction is the first part of our correction method we present in this paper.
-Nonetheless, we test it by applying it to the mock catalogues and comparing the resulting power spectrums.
-For each of the mock catalogues (LasDamas, QPM, and Tiling Mock) we use the FKP power spectrum estimator from Section \ref{sec:pk_est} to compute the power spectrums of the mock catalogues without fiber-collisions, with fiber-collisions corrected using NN method, and with fiber-collisions corrected using the $d_\mathrm{LOS}$-peak correction.
+We test it by applying it to the mock catalogs and comparing the resulting power spectrums.
+For each of the mock catalogs (LasDamas, QPM, and Tiling Mock) we use the FKP power spectrum estimator from Section \ref{sec:pk_est} to compute the power spectrums of the mock catalogs without fiber collisions, with fiber collisions corrected using NN method, and with fiber collisions corrected using the $d_\mathrm{LOS}$-peak correction.
 We note that both the NN and the $d_\mathrm{LOS}$-peak correction methods alter the redshift distribution of our samples by a negligible amount $< 1\%$.
-Therefore, the synthetic random catalogues and the $\bar{n}(z)$ values do not need to be adjusted in the FKP $P(k)$ calculations.
+Therefore, the synthetic random catalogs and the $\bar{n}(z)$ values do not need to be adjusted in the FKP $P(k)$ calculations in our case.
 
-Since we are interested in how well fiber-collision correction methods can reproduce the power spectrum without fiber collisions (i.e.
-``true" power spectrum, unsullied by systematic effects), in Figure \ref{fig:peakonly} we plot the ratio of the average power spectrum $\overline{P(k)}$ (averaged over the realizations) computed from fiber-collided mock catalogues with corrections over the $\overline{P(k)}$ from the fiber-collision-less original mock catalogues: $\overline{P_{\mathrm{corr}}(k)}/\overline{P_\mathrm{true}(k)}$.
+Since we are interested in how well fiber collision correction methods can reproduce the power spectrum without fiber collisions (i.e.
+``true" power spectrum, unsullied by systematic effects), in Figure \ref{fig:peakonly} we plot the ratio of the average power spectrum $\overline{P(k)}$ (averaged over the realizations) computed from fiber collided mock catalogs with corrections over the $\overline{P(k)}$ from the fiber collision-less original mock catalogs: $\overline{P_{\mathrm{corr}}(k)}/\overline{P_\mathrm{true}(k)}$.
 The ratio for the NN method is plotted in blue while the ratio for the $d_{\mathrm{LOS}}$-peak correction is plotted in orange.
-We also plot $\Delta P_\mathrm{true}(k) / \overline{P_\mathrm{true}(k)}$ (black; dashed) in order to compare the ratios to sample variance of the mock catalogues.
+We also plot $\Delta P_\mathrm{true}(k) / \overline{P_\mathrm{true}(k)}$ (black; dashed) in order to compare the ratios to sample variance of the mock catalogs.
 $\Delta P_\mathrm{true}(k)$ is computed using Eq.
 \ref{eq:pk_var}.
-At large scales ($k < 0.1 \; h/\mathrm{Mpc}$), for all mock catalogues, both fiber-collision methods are able to reasonably reconstruct the true power spectrum.
+At large scales ($k < 0.1 \; h/\mathrm{Mpc}$), for all mock catalogs, both fiber collision methods are able to reasonably reconstruct the true power spectrum.
 At small scales on the other hand, the $\overline{P_\mathrm{NN}(k)}$ is greater than $\overline{P_\mathrm{true}(k)}$ by $> 10 \%$ at $ k \sim 0.3\; h/\mathrm{Mpc}$.
@@
 
-When we compare the NN method and the $d_\mathrm{LOS}$-peak correction to the sample variance ratio ($\Delta P_\mathrm{true}(k) / \overline{P_\mathrm{true}(k)}$), we find that neither of these methods sufficiently correct for fiber-collisions at $k > 0.1\; h/\mathrm{Mpc}$.
-The $P(k)$s obtained from these methods are dominated by the systematic effects of fiber-collisions on small scales.
-Although the $d_\mathrm{LOS}$-peak method improves upon the NN method by statistical reconstructing the clustering of correlated fiber-collided pairs within the peak of the $d_\mathrm{LOS}$ distribution, there is still room for improvement since the method does not yet properly account for chance alignments (uncorrelated fiber-collision pairs).
+When we compare the NN method and the $d_\mathrm{LOS}$-peak correction to the sample variance ratio ($\Delta P_\mathrm{true}(k) / \overline{P_\mathrm{true}(k)}$), we find that neither of these methods sufficiently correct for fiber collisions at $k > 0.1\; h/\mathrm{Mpc}$.
+The $P(k)$s obtained from these methods are dominated by the systematic effects of fiber collisions on small scales.
+Although the $d_\mathrm{LOS}$-peak method improves upon the NN method by statistical reconstructing the clustering of correlated fiber collided pairs within the peak of the $d_\mathrm{LOS}$ distribution, there is still room for improvement since the method does not yet properly account for chance alignments (uncorrelated fiber collision pairs).
 Unfortunately, an extension of the $d_\mathrm{LOS}$-peak method to the entire $d_\mathrm{LOS}$ distribution range is not feasible because such a correction results in an overall reduction of the $P(k)$.
-This is caused by the statistical sampling of the $d_\mathrm{LOS}$, which would inevitably displace some fiber-collided pairs that are actually correlated pairs as chance alignments and the other way around.
-Therefore, in the following section we provide more robust correction method to account for the chance alignment fiber-collided pairs.
+This is caused by the statistical sampling of the $d_\mathrm{LOS}$, which would inevitably displace some fiber collided pairs that are actually correlated pairs as chance alignments and the other way around.
+Therefore, in the following section we provide more robust correction method to account for the chance alignment fiber collided pairs.
 
@@
 \ref{eq:fkp_shotnoise} (blue), Eq.
-\ref{eq:ourshot} (green), $P^\mathrm{B2014}_\mathrm{shot}$ (red), and $P^{\mathrm{GM2014}}_\mathrm{shot}$ (purple) over $\overline{P_\mathrm{true}(k)}$ for LasDamas (left panel), QPM (middle panel), and Tiling Mock (right panel) catalogues.
+\ref{eq:ourshot} (green), $P^\mathrm{B2014}_\mathrm{shot}$ (red), and $P^{\mathrm{GM2014}}_\mathrm{shot}$ (purple) over $\overline{P_\mathrm{true}(k)}$ for LasDamas (left panel), QPM (middle panel), and Tiling Mock (right panel) catalogs.
 We also plot $\Delta P_\mathrm{true}/P_\mathrm{true}(k)$ to compare with the sample variance ratio.
@@
 \ref{eq:ourshot} significantly underestimates the power spectrum at $k > 0.1 \; h/\mathrm{Mpc}$ with $\overline{P^\mathrm{Eq.15}_\mathrm{SN}}/\overline{P_\mathrm{true}}(k \sim 0.3) -1 \sim -3 \%, -8 \%, \;\mathrm{and} -9$ for LasDamas, QPM, and Tiling Mock respectively.
-$\overline{P_\mathrm{SN}(k)}$ computed using $P^\mathrm{GM2014}_\mathrm{shot}$ provides the best correction for fiber-collisions ($\overline{P^\mathrm{GM2014}_\mathrm{SN}}/\overline{P_\mathrm{true}}(k \sim 0.3) -1 \sim 2.5 \%$).
-However at these small scales, even for $\overline{P^\mathrm{GM2014}_\mathrm{SN}}$ the effect of fiber-collisions is comparable to sample variance at $k \sim 0.3 \;h/\mathrm{Mpc}$.
+$\overline{P_\mathrm{SN}(k)}$ computed using $P^\mathrm{GM2014}_\mathrm{shot}$ provides the best correction for fiber collisions ($\overline{P^\mathrm{GM2014}_\mathrm{SN}}/\overline{P_\mathrm{true}}(k \sim 0.3) -1 \sim 2.5 \%$).
+However at these small scales, even for $\overline{P^\mathrm{GM2014}_\mathrm{SN}}$ the effect of fiber collisions is comparable to sample variance at $k \sim 0.3 \;h/\mathrm{Mpc}$.
 } \label{fig:shotnoise}
@@
 \subsection{Shot Noise Correction} \label{sec:shotnoise} 
-Both the NN method and the $d_\mathrm{LOS}$-peak correction do not sufficiently account for the systematic effects of fiber-collisions in the power spectrum.
-In this section we introduce the other part of our fiber-collision correction method that involve the shot-noise correction term of the FKP power spectrum estimator.
-By modifying the shot noise term of the FKP estimator to account for fiber-collisions, we present a more robust correction method that accounts for the chance aligned fiber-collided pairs.
+Both the NN method and the $d_\mathrm{LOS}$-peak correction do not sufficiently account for the systematic effects of fiber collisions in the power spectrum.
+In this section we introduce the other part of our fiber collision correction method that involve the shot-noise correction term of the FKP power spectrum estimator.
+By modifying the shot noise term of the FKP estimator to account for fiber collisions, we present a more robust correction method that accounts for the chance aligned fiber collided pairs.
 
@@
 \end{equation}
-In practice, the integrals in Equation \ref{eq:fkp_sn_int} can be written in terms of discrete sums over the random catalogue.
-The spacial integral $\int d^3r \; \bar{n}({\bf r}) ...$ can be computed as the discrete sum $\alpha \sum_{\mathrm{ran}}...$.
+In practice, the integrals in Equation \ref{eq:fkp_sn_int} can be written in terms of discrete sums over the random catalog.
+The spatial integral $\int d^3r \; \bar{n}({\bf r}) ...$ can be computed as the discrete sum $\alpha \sum_{\mathrm{ran}}...$.
 With this conversion,
@@
 
-The spatial integral $\int d^3r \;\bar{n}({\bf r})...$ can also be computed using the mock catalogues rather than the synthetic random catalogues, as $\sum_{\mathrm{gal}} w_g...$ where $w_g$ represents the statistical weight assigned to the galaxies (\citealt{Cole:2005aa, Yamamoto:2006aa, Beutler:2014aa, Gil-Marin:2014aa}).
+The spatial integral $\int d^3r \;\bar{n}({\bf r})...$ can also be computed using the mock catalogs rather than the synthetic random catalogs, as $\sum_{\mathrm{gal}} w_g...$ where $w_g$ represents the statistical weight assigned to the galaxies (\citealt{Cole:2005aa, Yamamoto:2006aa, Beutler:2014aa, Gil-Marin:2014aa}).
 Then the shot-noise component can be expressed as:
@@
 
-On the other hand, \cite{Gil-Marin:2014aa}, in a formulation designed to account for fiber-collisions derives $P_\mathrm{shot}$ using two separate components: one for correlated pairs and the other chance alignments.
+On the other hand, \cite{Gil-Marin:2014aa}, in a formulation designed to account for fiber collisions derives $P_\mathrm{shot}$ using two separate components: one for correlated pairs and the other chance alignments.
 The shot-noise contribution to the power from correlated pairs (referred to as ``true pairs" in \citealt{Gil-Marin:2014aa}) is equivalent to Eq.
@@
 For analyzing BOSS $P(k)$ \cite{Gil-Marin:2014aa} uses $x_\mathrm{PS} = 0.58$.
-The $x_\mathrm{PS}$ is calculated from the weighted galaxy catalogue of \cite{Manera:2013aa}, not the observed BOSS data, and it is the value that optimizes the fit of the fiber-collision corrected $P(k)$ to the $P_\mathrm{true}(k)$ .
+The $x_\mathrm{PS}$ is calculated from the weighted galaxy catalog of \cite{Manera:2013aa}, not the observed BOSS data, and it is the value that optimizes the fit of the fiber collision corrected $P(k)$ to the $P_\mathrm{true}(k)$ .
 
@@
 However, Eq.
-\ref{eq:ourshot} accounts for fiber-collisions in the $w_\mathrm{tot}^2$ term.
+\ref{eq:ourshot} accounts for fiber collisions in the $w_\mathrm{tot}^2$ term.
 Also, Eq.
 \ref{eq:ourshot} is equivalent to the shot-noise contribution from ``false pairs" in \cite{Gil-Marin:2014aa}.
-%In \cite{Gil-Marin:2014aa}, they justify the use of the two separate shot-noise terms with the argument that, if the fiber-collided pairs are true pairs it would not modify %insert reason 
-%While the $P(k)$ using the \cite{Gil-Marin:2014aa} shot-noise term does in fact correct for fiber-collisions significantly (below), since the parameter is determined in mock catalogues, the value cannot be validated in the actual BOSS data .
+%In \cite{Gil-Marin:2014aa}, they justify the use of the two separate shot-noise terms with the argument that, if the fiber collided pairs are true pairs it would not modify %insert reason 
+%While the $P(k)$ using the \cite{Gil-Marin:2014aa} shot-noise term does in fact correct for fiber collisions significantly (below), since the parameter is determined in mock catalogs, the value cannot be validated in the actual BOSS data .
 
-In order to compare the different $P_\mathrm{shot}$ derivations, we apply each of them ($P^\mathrm{FKP}_\mathrm{shot}$, $P^\mathrm{Hahn+}_\mathrm{shot}$, $P^\mathrm{B2014}_\mathrm{shot}$ and $P^\mathrm{GM2014}_\mathrm{shot}$) to the fiber-collided mock catalogues with nearest-neighbor weights.
+In order to compare the different $P_\mathrm{shot}$ derivations, we apply each of them ($P^\mathrm{FKP}_\mathrm{shot}$, $P^\mathrm{Hahn+}_\mathrm{shot}$, $P^\mathrm{B2014}_\mathrm{shot}$ and $P^\mathrm{GM2014}_\mathrm{shot}$) to the fiber collided mock catalogs with nearest-neighbor weights.
 To clarify, $P^\mathrm{FKP}_\mathrm{shot}$, $P^\mathrm{Hahn+}_\mathrm{shot}$, $P^\mathrm{B2014}_\mathrm{shot}$ and $P^\mathrm{GM2014}_\mathrm{shot}$ are calculated using Eq.
 \ref{eq:fkp_shotnoise}, \ref{eq:ourshot}, \ref{eq:florian} and \ref{eq:gm_shot}, respectively.
-In our considerations of systematic effects beside fiber-collisions in Eq.
-\ref{eq:weight}, we note that only the QPM mock catalogue assigns $w_\mathrm{sys}$ (systematic weights due to sector completeness) to its galaxies and none of the mock catalogues assign $w_\mathrm{rf}$ to their galaxies.
-Therefore in Equations 9 - 15, for LasDamas and Tiling mock catalogues we use $w_\mathrm{sys} = w_\mathrm{rf} = 1$ so $w_\mathrm{tot} = w_\mathrm{fc}$ and for QPM mocks, we use $w_\mathrm{tot} = w_\mathrm{sys} w_\mathrm{fc}$.
-We compute the $P_\mathrm{SN}(k)$s using the FKP estimator with different $P_\mathrm{shot}$ prescriptions for each of the mock catalogues.
-We then average the power spectrum over the realizations to get $\overline{P_\mathrm{SN}(k)}$s for the mock catalogues, and then take the ratio over $\overline{P_\mathrm{true}(k)}$.
+In our considerations of systematic effects beside fiber collisions in Eq.
+\ref{eq:weight}, we note that only the QPM mock catalog assigns $w_\mathrm{sys}$ (systematic weights due to sector completeness) to its galaxies and none of the mock catalogs assign $w_\mathrm{rf}$ to their galaxies.
+Therefore in Equations 9 - 15, for LasDamas and Tiling mock catalogs we use $w_\mathrm{sys} = w_\mathrm{rf} = 1$ so $w_\mathrm{tot} = w_\mathrm{fc}$ and for QPM mocks, we use $w_\mathrm{tot} = w_\mathrm{sys} w_\mathrm{fc}$.
+We compute the $P_\mathrm{SN}(k)$s using the FKP estimator with different $P_\mathrm{shot}$ prescriptions for each of the mock catalogs.
+We then average the power spectrum over the realizations to get $\overline{P_\mathrm{SN}(k)}$s for the mock catalogs, and then take the ratio over $\overline{P_\mathrm{true}(k)}$.
 
@@
 $\overline{P(k)}$ measured using $P^\mathrm{B2014}_\mathrm{shot}$ (Eq.
-\ref{eq:florian}) does not significantly improve this overestimation in any of the mock catalogues.
-In fact for LasDamas and Tiling mock catalogues, since $w_\mathrm{sys} = 1$, $P^\mathrm{FKP}_\mathrm{shot} = P^\mathrm{B2014}_\mathrm{shot}$.
+\ref{eq:florian}) does not significantly improve this overestimation in any of the mock catalogs.
+In fact for LasDamas and Tiling mock catalogs, since $w_\mathrm{sys} = 1$, $P^\mathrm{FKP}_\mathrm{shot} = P^\mathrm{B2014}_\mathrm{shot}$.
 Even for QPM, which assigns $w_\mathrm{sys}$ to its galaxies there are no significant improvements from using $P^\mathrm{B2014}_\mathrm{shot}$ over $P^\mathrm{FKP}_\mathrm{shot}$.
@@
 $\overline{P^\mathrm{GM2014}_\mathrm{SN}}/\overline{P_\mathrm{true}}(k\sim 0.3) -1 \sim 2.5 \%$.
-As in Figure \ref{fig:peakonly}, we again plot the sample variance ($\Delta P/\bar{P}$) for each of the mock catalogues in Figure \ref{fig:shotnoise} for comparison.
-$\overline{P(k)}$ computed using $P^\mathrm{Gil-Marin}_\mathrm{shot}$ is able to best constrain the effects of fiber-collisions in our comparison.
-However, even $\overline{P^\mathrm{GM2014}_\mathrm{SN}}$ is unable to significantly reduce the effects of fiber-collisions below the sample variance, especially near $k \sim 0.3 \;h/\mathrm{Mpc}$.
+As in Figure \ref{fig:peakonly}, we again plot the sample variance ($\Delta P/\bar{P}$) for each of the mock catalogs in Figure \ref{fig:shotnoise} for comparison.
+$\overline{P(k)}$ computed using $P^\mathrm{Gil-Marin}_\mathrm{shot}$ is able to best constrain the effects of fiber collisions in our comparison.
+However, even $\overline{P^\mathrm{GM2014}_\mathrm{SN}}$ is unable to significantly reduce the effects of fiber collisions below the sample variance, especially near $k \sim 0.3 \;h/\mathrm{Mpc}$.
 
 The shot-noise correction term we present in Eq.
-\ref{eq:ourshot} should only correct for the shot-noise contribution to the power spectrum from chance alignment fiber-collided pairs - not from correlated pairs.
-Because we apply the shot-noise correction to all fiber-collided pairs indiscriminately in Figure \ref{fig:shotnoise}, the shot-noise correction term over-subtracts the power spectrum as we find in Figure \ref{fig:shotnoise}.
-In the following section we present our fiber-collision correction method, that combines the $d_\mathrm{LOS}$-peak correction of Section \ref{sec:dlos} and Eq.
+\ref{eq:ourshot} should only correct for the shot-noise contribution to the power spectrum from chance alignment fiber collided pairs - not from correlated pairs.
+Because we apply the shot-noise correction to all fiber collided pairs indiscriminately in Figure \ref{fig:shotnoise}, the shot-noise correction term over-subtracts the power spectrum as we find in Figure \ref{fig:shotnoise}.
+In the following section we present our fiber collision correction method, that combines the $d_\mathrm{LOS}$-peak correction of Section \ref{sec:dlos} and Eq.
 \ref{eq:ourshot} from this section.
@@
 \includegraphics[scale=0.55]{fcpaper_pk_peakshotnoise_mpfit_comp.png} 
-\caption{The ratio of $\overline{P(k)}$ computed using our fiber-collision correction method presented in Section \ref{sec:apply} over $\overline{P_\mathrm{true}(k)}$ for LasDamas (left panel), QPM (middle panel), and Tiling Mock (right panel) catalogues with nearest-neighbor fiber-collision weights (red).
+\caption{The ratio of $\overline{P(k)}$ computed using our fiber collision correction method presented in Section \ref{sec:apply} over $\overline{P_\mathrm{true}(k)}$ for LasDamas (left panel), QPM (middle panel), and Tiling Mock (right panel) catalogs with nearest-neighbor fiber collision weights (red).
 We again plot $\Delta P_\mathrm{true}/P_\mathrm{true}(k)$ for comparison.
-$\overline{P_\mathrm{corr}}/\overline{P_\mathrm{true}}(k \sim 0.3 \; h/\mathrm{Mpc})-1 \sim 0.5\%$ for our fiber-collision correction.
+$\overline{P_\mathrm{corr}}/\overline{P_\mathrm{true}}(k \sim 0.3 \; h/\mathrm{Mpc})-1 \sim 0.5\%$ for our fiber collision correction.
 This is significantly better than the correction methods of \cite{Anderson:2012aa}, \cite{Beutler:2014aa} and \cite{Gil-Marin:2014aa} in Figure \ref{fig:shotnoise}.
-Moreover, for LasDamas and QPM, our correction method is able to correct for the effects of fiber-collisions, significantly below the $\Delta P_\mathrm{true}/P_\mathrm{true}(k)$ throughout the probed $k$ range, even at the smallest scales.
+Moreover, for LasDamas and QPM, our correction method is able to correct for the effects of fiber collisions, significantly below the $\Delta P_\mathrm{true}/P_\mathrm{true}(k)$ throughout the probed $k$ range, even at the smallest scales.
 }\label{fig:peaksn}
@@
 \section{Results} \label{sec:results}
-\subsection{Fiber-Collision Correction Method} \label{sec:apply}
-In Section \ref{sec:dlos} we derive a method to better statistically reconstruct the clustering of correlated fiber-collided pairs using using the peak of the $d_\mathrm{LOS}$ distribution.
-Then in Section \ref{sec:shotnoise} we presented our formulation of the shot-noise correction term, which accounts for the added discreteness from chance aligned fiber-collision pairs.
-We now combine these two methods and present our fiber-collision correction method.
+\subsection{fiber collision Correction Method} \label{sec:apply}
+In Section \ref{sec:dlos} we derive a method to better statistically reconstruct the clustering of correlated fiber collided pairs using using the peak of the $d_\mathrm{LOS}$ distribution.
+Then in Section \ref{sec:shotnoise} we presented our formulation of the shot-noise correction term, which accounts for the added discreteness from chance aligned fiber collision pairs.
+We now combine these two methods and present our fiber collision correction method.
 
-We begin once again with the fiber-collided mock catalogues with the nearest-neighbor weights that accurately imitate the effects of fiber-collision on the actual observed BOSS data.
-Then as described in Section \ref{sec:dlos}, we calculate the $d_\mathrm{LOS}$ distribution of all fiber-collided pairs in each mock catalogue.
-From the $d_\mathrm{LOS}$ distribution, we compute the fraction of fiber-collided pairs within the peak of the distribution ($f_\mathrm{peak}$; Section \ref{sec:dlos}).
-We then select $f_\mathrm{peak}$ of the fiber-collided pairs and designate them as correlated pairs that lie within the peak of the $d_\mathrm{LOS}$ distribution.
-We refer to these fiber-collided pairs as ``peak-assigned" pairs.
+We begin once again with the fiber collided mock catalogs with the nearest-neighbor weights that accurately imitate the effects of fiber collision on the actual observed BOSS data.
+Then as described in Section \ref{sec:dlos}, we calculate the $d_\mathrm{LOS}$ distribution of all fiber collided pairs in each mock catalog.
+From the $d_\mathrm{LOS}$ distribution, we compute the fraction of fiber collided pairs within the peak of the distribution ($f_\mathrm{peak}$; Section \ref{sec:dlos}).
+We then select $f_\mathrm{peak}$ of the fiber collided pairs and designate them as correlated pairs that lie within the peak of the $d_\mathrm{LOS}$ distribution.
+We refer to these fiber collided pairs as ``peak-assigned" pairs.
 
@@
 
-We keep the nearest-neighbor fiber-collision weights imposed in the beginning for the remaining fiber-collided pairs that are not ``peak-assigned" ($1-f_\mathrm{peak}$ of the fiber-collided pairs).
-The resulting mock catalogue has $f_\mathrm{peak}$ fewer galaxies with $w_\mathrm{cp} > 1$ compared to the fiber-collided mock catalogues with nearest-neighbor weights that we started from; however, the total statistical weight ($\sum_\mathrm{gal} w_\mathrm{tot}$) of the mock catalogue is conserved.
+We keep the nearest-neighbor fiber collision weights imposed in the beginning for the remaining fiber collided pairs that are not ``peak-assigned" ($1-f_\mathrm{peak}$ of the fiber collided pairs).
+The resulting mock catalog has $f_\mathrm{peak}$ fewer galaxies with $w_\mathrm{cp} > 1$ compared to the fiber collided mock catalogs with nearest-neighbor weights that we started from; however, the total statistical weight ($\sum_\mathrm{gal} w_\mathrm{tot}$) of the mock catalog is conserved.
 
 Next, we use the FKP estimator with the Eq.
-\ref{eq:ourshot} shot-noise correction term described in Section \ref{sec:shotnoise} to calculate the $P(k)$ for our $d_\mathrm{LOS}$-peak corrected mock catalogues.
-In Figure \ref{fig:peaksn}, we present the ratio of the $\overline{P(k)}$ computed using our fiber-collision correction method over $\overline{P_\mathrm{true}(k)}$.
-To assess the merit of the fiber-collision correction, we once again over-plot the sample variance of the mock catalogues.
+\ref{eq:ourshot} shot-noise correction term described in Section \ref{sec:shotnoise} to calculate the $P(k)$ for our $d_\mathrm{LOS}$-peak corrected mock catalogs.
+In Figure \ref{fig:peaksn}, we present the ratio of the $\overline{P(k)}$ computed using our fiber collision correction method over $\overline{P_\mathrm{true}(k)}$.
+To assess the merit of the fiber collision correction, we once again over-plot the sample variance of the mock catalogs.
 For LasDamas, at $k \sim 0.3 \; h/\mathrm{Mpc}$, $P(k)/P_\mathrm{true}(k) - 1 \sim 0.5 \%$ and throughout the $k$ range, $0.3 \% < P(k)/P_\mathrm{true}(k) - 1 < 1.3 \%$.
@@
 {\bf include numbers here when Ngrid=960 is done}.
-Moreover for the mock catalogues with sample variance measurements (LasDamas and QPM), the $P(k)$ ratio is significantly below the sample variance throughout the entire $k$ range probed and even at $k\sim 0.3\;h/\mathrm{Mpc}$.
+Moreover for the mock catalogs with sample variance measurements (LasDamas and QPM), the $P(k)$ ratio is significantly below the sample variance throughout the entire $k$ range probed and even at $k\sim 0.3\;h/\mathrm{Mpc}$.
 
@@
 \includegraphics[scale=0.55]{fcpaper_pk_chisquared_comparison.png} 
-\caption{$\chi^2 (k_\mathrm{max})$ for $P_\mathrm{NN-upweight}$ (blue), $P_\mathrm{Beutler}$ (light blue), $P_\mathrm{Gil-Marin}$ (orange), and $P_\mathrm{Hahn}$ (yellow) using the LasDamas (left panel), QPM (centerl panel), and Tiling (right panel) mock catalogues.
+\caption{$\chi^2 (k_\mathrm{max})$ for $P_\mathrm{NN-upweight}$ (blue), $P_\mathrm{Beutler}$ (light blue), $P_\mathrm{Gil-Marin}$ (orange), and $P_\mathrm{Hahn}$ (yellow) using the LasDamas (left panel), QPM (centerl panel), and Tiling (right panel) mock catalogs.
 Equation \ref{eq:chi2} was used to compute the $\chi^2(k_\mathrm{max})$.
@@
 
-The correction method we present in this paper corrects for the effect of fiber-collisions to the extent where $P_\mathrm{corr}(k)$ measurements are no longer dominated by systematic effects at the scales probed in our calculations, even for the smallest scales of $k \sim 0.3 \; h/\mathrm{Mpc}$.
-However, to further quantify how accurately our correction method is able to reproduce the true power spectrum and correct for the effects of fiber-collisions, we quantify the goodness-of-fit for all the corrected $P(k)$s to $P_\mathrm{true}(k)$ by calculating the following $\chi^2$:
+The correction method we present in this paper corrects for the effect of fiber collisions to the extent where $P_\mathrm{corr}(k)$ measurements are no longer dominated by systematic effects at the scales probed in our calculations, even for the smallest scales of $k \sim 0.3 \; h/\mathrm{Mpc}$.
+However, to further quantify how accurately our correction method is able to reproduce the true power spectrum and correct for the effects of fiber collisions, we quantify the goodness-of-fit for all the corrected $P(k)$s to $P_\mathrm{true}(k)$ by calculating the following $\chi^2$:
 \begin{equation}
@@
 $N_{k_\mathrm{max}}$ is the number of $k$ bins in the $P(k)$ calculation with $k < k_\mathrm{max}$.
-$\overline{P_\mathrm{corr}(k)}$ is the average fiber-collision corrected powerspectrum of all realizations for each catalogue.
-$\Delta P_\mathrm{true}(k)$ is the standard deviation of $P_\mathrm{true}(k)$ computed from all realizations of each mock catalogue.
+$\overline{P_\mathrm{corr}(k)}$ is the average fiber collision corrected powerspectrum of all realizations for each catalog.
+$\Delta P_\mathrm{true}(k)$ is the standard deviation of $P_\mathrm{true}(k)$ computed from all realizations of each mock catalog.
 We calculate $\chi^2$ as a function of $k_\mathrm{max}$ in order to determine the accumulated $\chi^2$ to a specific scale ($k_\mathrm{max}$).
-In doing so, we determine the scale to which a power spectrum analysis can be extended to without fiber-collisions dominating the measurement.
+In doing so, we determine the scale to which a power spectrum analysis can be extended to without fiber collisions dominating the measurement.
 
-For the Tiling Mock catalogue, since there is only one realization, the variance ($\Delta P_\mathrm{true} (k)$) cannot be computed independently.
+For the Tiling Mock catalog, since there is only one realization, the variance ($\Delta P_\mathrm{true} (k)$) cannot be computed independently.
 However, for an estimate of the $\chi^2$, we estimate $\Delta P_\mathrm{true}^\mathrm{Tiling\;Mock}(k)$ from $\Delta P^\mathrm{QPM}_\mathrm{true} (k)$ scaled by the ratio of the power spectrums:
@@
 In Figure \ref{fig:peaksnchi2}, we present the $\chi^2(k_\mathrm{max})$ for $P(k)$ using the following fiber collision correction methods: the NN correction (also \citealt{Anderson:2012aa}), \cite{Beutler:2014aa}, \cite{Gil-Marin:2014aa}, and our method from Section \ref{sec:apply}.
-The comparison is made using the LasDamas (left panel), QPM (center panel) and Tiling (right panel) mock catalogues.
-First in the LasDamas panel, at scales larger than $k_\mathrm{max} < 5 \times 10^{-2} \; h/\mathrm{Mpc}$, $\chi^2 < 10^{-3}$ for all correction methods, which suggests that all correction methods sufficiently correct for fiber-collisions and reasonably reconstructs $P_\mathrm{true}(k)$ at these scale.
+The comparison is made using the LasDamas (left panel), QPM (center panel) and Tiling (right panel) mock catalogs.
+First in the LasDamas panel, at scales larger than $k_\mathrm{max} < 5 \times 10^{-2} \; h/\mathrm{Mpc}$, $\chi^2 < 10^{-3}$ for all correction methods, which suggests that all correction methods sufficiently correct for fiber collisions and reasonably reconstructs $P_\mathrm{true}(k)$ at these scale.
 In approaching smaller scales the $\chi^2$ for all correction methods increase.
@@
 
-Finally for the Tiling mock catalogue (right panel), we find that $\chi^2(k_\mathrm{max})$ increases in a near monotonic fashion as a function of $k_\mathrm{max}$.
+Finally for the Tiling mock catalog (right panel), we find that $\chi^2(k_\mathrm{max})$ increases in a near monotonic fashion as a function of $k_\mathrm{max}$.
 For $k_\mathrm{max} < 4\times10^{-2} \; h/\mathrm{Mpc}$, there are no significant differences between the $\chi^2$s of any of the correction methods.
 Then at intermediate scales of $4\times10^{-2} < k_\mathrm{max} < 1.5\times 10^{-2} \; h/\mathrm{Mpc}$, $\chi^2$s of NN and \cite{Beutler:2014aa} are notably lower than the $\chi^2$s of \cite{Gil-Marin:2014aa} and our method.
-However like the other mock catalogues at smaller scales, the $\chi^2$s of NN and \cite{Beutler:2014aa} quickly increase beyond the other $\chi^2$s, ultimately both reach $\chi^2(k_\mathrm{max} \sim 0.3) \approx 13.5$.
+However like the other mock catalogs at smaller scales, the $\chi^2$s of NN and \cite{Beutler:2014aa} quickly increase beyond the other $\chi^2$s, ultimately both reach $\chi^2(k_\mathrm{max} \sim 0.3) \approx 13.5$.
 In the meantime, $\chi^2(k_\mathrm{max} \sim 0.3) \approx 0.32$ for \cite{Gil-Marin:2014aa} and $\chi^2(k_\mathrm{max} \sim 0.3) \approx 0.15$ for our correction method.
 Throughout the entire $k_\mathrm{max}$ our method has a lower $\chi^2$ than \cite{Gil-Marin:2014aa}.
-With only one realization of the Tiling mock catalogue and scaled $\Delta P$, a detailed comparison of the $\chi^2$ values is difficult.
+With only one realization of the Tiling mock catalog and scaled $\Delta P$, a detailed comparison of the $\chi^2$ values is difficult.
 Yet the $\chi^2(k_\mathrm{max})$ results for our correction provide realistic assurance that the correction method can be applied to the actually BOSS data.
 
-Overall, regardless of catalogue, for scales $k_\mathrm{max} < 3 \times 10^{-2} \;h/\mathrm{Mpc}$, the $\chi^2$ for all fiber-collision corrected $P(k)$ are negligible.
-Then, with the exception of the LasDamas catalogue, at intermediate scales of $3 \times 10^{-2} < k_\mathrm{max} < 0.15 \; h/\mathrm{Mpc}$ the NN and \cite{Beutler:2014aa} methods show the lowest $\chi^2$s.
+Overall, regardless of catalog, for scales $k_\mathrm{max} < 3 \times 10^{-2} \;h/\mathrm{Mpc}$, the $\chi^2$ for all fiber collision corrected $P(k)$ are negligible.
+Then, with the exception of the LasDamas catalog, at intermediate scales of $3 \times 10^{-2} < k_\mathrm{max} < 0.15 \; h/\mathrm{Mpc}$ the NN and \cite{Beutler:2014aa} methods show the lowest $\chi^2$s.
 However at these intermediate scales, all of the correction methods reasonably reconstruction of the true power spectrum with $\chi^2 \ll 1$.
 At the smallest scales, NN and \cite{Beutler:2014aa} corrections methods no longer provide a sufficient fit to $\overline{P_\mathrm{true}(k)}$.
-A detailed comparison at the small scales ($k > 1.5 \times 10^{-1} \;h/\mathrm{Mpc}$) demonstrates that the fiber-collision correction we present in this paper significantly better reproduces the true power spectrum than any of the other fiber-collision correction methods.
+A detailed comparison at the small scales ($k > 1.5 \times 10^{-1} \;h/\mathrm{Mpc}$) demonstrates that the fiber collision correction we present in this paper significantly better reproduces the true power spectrum than any of the other fiber collision correction methods.
 Furthermore, Figure \ref{fig:peaksnchi2} illustrates that throughout the entire $k_\mathrm{max}$, our correction method is able to reasonably reproduce $P_\mathrm{true}(k)$ at all scales.
-% Detailed comparison to Gil-Marin that talk about how the xps value he calculates is only validated through mock catalogues, but our method can be validated with the overlapping regions of the real data.
+% Detailed comparison to Gil-Marin that talk about how the xps value he calculates is only validated through mock catalogs, but our method can be validated with the overlapping regions of the real data.
 
 \section{Summary and Discussion} \label{sec:summary}
-Using simulated mock catalogues for SDSS data with realistically imposed fiber-collisions, we quantify the systematic effects of fiber-collisions on galaxy clustering measurements - in particular the power spectrum.
-Although fiber-collisions have little significant effect on the power spectrum at large scales, its effect quickly overtakes the sample variance at scales smaller than $k > 0.1 \;h/\mathrm{Mpc}$.
-At the smallest scales that we explore in this paper, $k \sim 0.3$, fiber-collisions have over a $10 \%$ effect on the power spectrum.
-Consequently at these small scales, measurements of the power spectrum is dominated by the uncertainties from systematic effects of fiber-collisions.
+Using simulated mock catalogs for SDSS data with realistically imposed fiber collisions, we quantify the systematic effects of fiber collisions on galaxy clustering measurements - in particular the power spectrum.
+Although fiber collisions have little significant effect on the power spectrum at large scales, their effect quickly overtakes the sample variance at scales smaller than $k > 0.1 \;h/\mathrm{Mpc}$.
+At the smallest scales that we explore in this paper, $k \sim 0.3  \;h/\mathrm{Mpc}$, fiber collisions have over a $10 \%$ effect on the power spectrum.
+Consequently at these small scales, measurements of the power spectrum is dominated by the uncertainties from systematic effects of fiber collisions.
 
-Fortunately, through the fiber-collided mock catalogues used in this paper, we are able to model the distribution of the line-of-sight displacement between fiber-collided pairs.
-Using this model, we are able to statistically reconstruct the clustering fiber-collided galaxies that reside in the same halo.
-Combining this correction with a modification of the shot-noise term in the power spectrum estimator to properly account for the discreteness added by the nearest-neighbor weights of chance aligned fiber-collided pairs, we devise a new fiber-collision correction method that is able to reconstruct the true power spectrum from fiber-collided data even to $k \sim 0.3 \;h/\mathrm{Mpc}$.
+Fortunately, using the fiber collided mock catalogs used in this paper, we are able to model the distribution of the line-of-sight displacement between fiber collided pairs.
+With this model, we are able to statistically reconstruct the clustering fiber collided galaxies that reside in the same halo.
+Combining this correction with a modification of the shot-noise term in the power spectrum estimator to properly account for the discreteness added by the nearest-neighbor weights of chance aligned fiber collided pairs, we devise a new fiber collision correction method that is able to reconstruct the true power spectrum from fiber collided data even to $k \sim 0.3 \;h/\mathrm{Mpc}$.
 Throughout the entire $k$ range explored in our analysis, our correction method reconstructs $P_\mathrm{true}(k)$ safely within the sample variance.
 
-Furthermore, we compare our method to the most common nearest-neighbor correction method (\citealt{Zehavi:2002aa, Berlind:2006aa, Anderson:2012aa}) and recent correction methods presented in \cite{Beutler:2014aa} and \cite{Gil-Marin:2014aa} to demonstrate that our method most successfully reproduces the true power spectrum at small scales and most reliably at all scales for all the LasDamas, QPM, and Tiling mock catalogues.
-Furthermore, while the correction method of \cite{Gil-Marin:2014aa} is comparable our correction method, the parameter $x_\mathrm{PS}$ used in the method is calculated solely through a weighted galaxy mock catalogue.
-As an added advantage, our correction method can also be validated by the observed data rather than only through the mock catalogues.
-Therefore our correction method does not depend on the accuracy of the mock catalogues, thereby making it's application to observations further reliable.
+Furthermore, we compare our method to the most common nearest-neighbor correction method (\citealt{Zehavi:2002aa, Berlind:2006aa, Anderson:2012aa}) and recent correction methods presented in \cite{Beutler:2014aa} and \cite{Gil-Marin:2014aa} to demonstrate that our method most successfully reproduces the true power spectrum at small scales and most reliably at all scales for all the LasDamas, QPM, and Tiling mock catalogs.
+Furthermore, while the correction method of \cite{Gil-Marin:2014aa} is comparable our correction method, the parameter $x_\mathrm{PS}$ used in the method is calculated solely through a weighted galaxy mock catalog.
+As an added advantage, our correction method can also be callibrated by the observed data rather than only through the mock catalogs.
+Therefore our correction method does not depend on the accuracy of the mock catalogs, thereby making it's application to observations further reliable.
 
-The fiber-collision correction method we present will enable us to extend our galaxy clustering analysis to smaller scales for SDSS-III BOSS and future surveys such as eBOSS or any other large fiber-fed surveys the suffer from systematic effects of fiber-collisions.
-Our fiber-collision correction method can also be extend to higher order clustering statistics such as the quadrupole of the power spectrum and the bispectrum, which we will explore in future work.
+The fiber collision correction method we present will enable us to extend our galaxy clustering analysis to smaller scales for SDSS-III BOSS and future surveys such as eBOSS or any other large fiber-fed surveys the suffer from systematic effects of fiber collisions.
+Our fiber collision correction method can also be extend to higher order clustering statistics such as the quadrupole of the power spectrum and the bispectrum, which we will explore in future work.
 

### 2015-04-20 qfenv_paper/ApJ submission/referee_response2.txt
Referee Report #2

Dear Editor,

We once again thank the referee for the thorough review of our work and
for the constructive report.

Please find below responses to the referee's comment along with changes
made to our paper.

Thank you, 
ChangHoon Hahn

================================================================================
        April 11, 2015

        Mr. ChangHoon Hahn
        Center for Cosmology and Particle Physics
        New York University
        4 Washington Place
        New York, NY 10003

        Title: PRIMUS: Effects of Galaxy Environment on the Quiescent
        Fraction Evolution at z < 0.8, ApJ97613R1

        Dear Mr. Hahn,

        The revised version of your paper cited above was sent back to
        the referee, who is mostly satisfied with the changes you have
        made. He/she just has a few remaining comments (appended below),
        which I would like you to take into consideration.

        When you resubmit the manuscript, please include a detailed
        cover letter containing the (mandatory) listing of the changes
        you've made to the text and your responses to the report.

        Click the link below to upload your revised manuscript; 
        http://apj.msubmit.net/cgi-bin/main.plex?el=A1Ew7DXK1A4CfGS3J7A9ftduFQ0I1nKsyQ3P8J1nY5FIQZ
        Alternatively, you may also log into your account at the EJ
        Press web site, http://apj.msubmit.net. Please use your user's
        login name: chahah. You can then ask for a new password via the
        Unknown/Forgotten Password link if you have forgotten your
        password.

        Reviewers find it helpful if the changes in the text of the
        manuscript are easily distinguishable from the rest of the text.
        Therefore we ask you to print changes in bold face. The
        highlighting can be removed easily after the review.

        The Astrophysical Journal has adopted a new policy that
        manuscript files become inactive, and are considered to have
        been withdrawn, six months after the most recent referee's
        report goes to the authors, provided a revised version has not
        been received by that time.

        If you have any questions, feel free to contact me.

        Sincerely,
        Lee Armus
        ApJ Scientific Editor
        California Institute of Technology
        apjla@ipac.caltech.edu

        ---------------------------------------------------------------------- 
        Referee Report
        Reviewer's Comments:

        I have looked at the changes. I think the argument about the
        cosmic variance affecting the quiescent fraction is overstated -
        some of it irrelevant. The cosmic variance has a much larger
        effect on the number counts than on the fraction of quiescent
        galaxies in high density environments; the latter is not
        estimated by cosmic variance calculators/equations. I agree the
        jack-knife method may underestimate the errors. Alternatively
        perhaps the stellar mass limits are not strict enough when
        estimating the quiescent fraction, since the 'missed galaxies'
        will preferentially be quiescent. I recommend the authors think
        about this a bit more; or at least remove the text about the
        cosmic variance. This should equally affect the >10^10 sample
        for the z=0.3 bin.

RESPONSE: 
We have removed the text discussing the cosmic variance.

        You now undersell PRIMUS versus zCOSMOS. The targeting
        completeness for zCOSMOS is much lower, see Fig. 5 of Lilly et
        al. 2009 for the 10k sample. What is most relevant is combined
        targeting completeness and redshift success - even a rough
        estimate for zCOSMOS would be a useful comparison - and would be
        a favourable metric for PRIMUS I think.

RESPONSE: 
We now explicitly mention the targeting completeness (spatial sampling
rate) of zCOSMOS in addition to the redshift completeness and list an
estimate of the overall completeness rate of zCOSMOS mentioned in Knobel
et al. (2012).

--------------------------------------------------------------------------------
OTHER CHANGES:

- We now state that Iovino et al. (2010) remark that the uncertainties
  in the quiescent fraction fits are too large to make any conclusions
  about the quiescent fraction evolution.

### 2015-04-20 qfenv_paper/ApJ submission/qf_environment.tex
Referee Report #2

--- 2015-03-20 qfenv_paper/ApJ submission/qf_environment.tex
@@
 of star formation is due to external influences on
-them. {\bf In other words}, in the recent Universe a substantial fraction of the
+them. In other words, in the recent Universe a substantial fraction of the
 galaxies that cease forming stars do so due to internal processes.
@@
 spectrograph on the Magellan I Baade $6.5$-m telescope with a slitmask and low dispersion prism.
-For details on the PRIMUS observation methods such as survey design, targeting, and data summary, {\bf we refer readers to the \cite{Coil:2011aa}.
-For details on redshift fitting, redshift precision and survey completeness we refer readers to \cite{Cool:2013aa}.}
+For details on the PRIMUS observation methods such as survey design, targeting, and data summary, we refer readers to \cite{Coil:2011aa}.
+For details on redshift fitting, redshift precision and survey completeness we refer readers to \cite{Cool:2013aa}.
 
@@
 \texttt{iSEDfit} uses the redshift and the observed photometry of the galaxies to determine the statistical likelihood of a large ensemble of generated model SEDs.
-The model SEDs are generated using Flexible Stellar Population Synthesis (FSPS) models (\citealt{Conroy:2010aa}) based on the \cite{Chabrier:2003aa} IMF, along with {\bf a time dependent dust attenuation curve of \cite{Charlot:2000aa} and }other prior parameters discussed in Section 4.1 and Appendix A of \cite{Moustakas:2013aa}.
+The model SEDs are generated using Flexible Stellar Population Synthesis (FSPS) models (\citealt{Conroy:2010aa}) based on the \cite{Chabrier:2003aa} IMF, along with a time dependent dust attenuation curve of \cite{Charlot:2000aa} and other prior parameters discussed in Section 4.1 and Appendix A of \cite{Moustakas:2013aa}.
+For details on the effects of prior parameter choices of iSEDfit on physical properties of galaxies we refer readers to the Appendix of \cite{Moustakas:2013aa}.
 For the observed photometry, we use the {\em GALEX} FUV and NUV, the two shortest IRAC bands at $3.6$ and $4.5 \mu \mathrm{m}$ (the two longer-wavelength IRAC channels are excluded because \texttt{iSEDfit} does not model hot dust or polycyclic aromatic hydrocarbons emission lines), and the optical bands.
@@
 apply PRIMUS redshift uncertainties to our galaxy sample selected from
-SDSS-{\em GALEX}. {\bf For each SDSS-{\em GALEX} galaxy, we adjust its
+SDSS-{\em GALEX}. For each SDSS-{\em GALEX} galaxy, we adjust its
 redshift by randomly sampling a Gaussian distribution with standard
 deviation $\sigma = 0.005 (1+z_\mathrm{SDSS})$, where
-$z_\mathrm{SDSS}$ is the SDSS redshift of the galaxy.}
+$z_\mathrm{SDSS}$ is the SDSS redshift of the galaxy.
 
@@
 The contribution from quiescent galaxies is colored in red.
-{\bf Galaxies with $n_{\mathrm{env}} = 0.0$ are in low density environments} and galaxies with $n_{\mathrm{env}} > 3.0$ are in high density environment.
+Galaxies with $n_{\mathrm{env}} = 0.0$ are in low density environments and galaxies with $n_{\mathrm{env}} > 3.0$ are in high density environment.
 We note that the significant difference among the SDSS distribution and the PRIMUS distributions above is due to the different stellar mass completeness limits imposed on each redshift bin of our galaxy sample.}      \label{fig:envcount}
@@
 For our aperture, we use a cylinder of dimensions: $R_{\mathrm{ap}} = \apradius\;
-\mathrm{Mpc}$ and $H_{\mathrm{ap}} = \apheight\; \mathrm{Mpc}$. 
-{\bf We note that $H_\mathrm{ap}$ is the full height of the cylinder and $R_\mathrm{ap}$ 
-and $H_\mathrm{ap}$ are comoving distances.} We use a
+\mathrm{Mpc}$ and $H_{\mathrm{ap}} = \apheight\; \mathrm{Mpc}$. We note that $H_\mathrm{ap}$ is the full height of the cylinder and $R_\mathrm{ap}$ 
+and $H_\mathrm{ap}$ are comoving distances. We use a
 cylindrical aperture to account for the PRIMUS redshift
@@
 Once we obtain environment measurements for all the galaxies
-in our galaxy sample, {\bf we classify galaxies with $n_{\mathrm{env}} = 0.0$
-to be in ``low" environment densities} and galaxies with $n_{\mathrm{env}} > 3$
+in our galaxy sample, we classify galaxies with $n_{\mathrm{env}} = 0.0$
+to be in ``low" environment densities and galaxies with $n_{\mathrm{env}} > 3$
 to be in ``high" environment densities. The high environment cutoff was
@@
 The quiescent galaxy contributions are colored in red while the star-forming galaxy contributions are colored in blue and patterned.
-We classify {\bf galaxies with $n_{\mathrm{env}} = 0.0$ to be in low density environments} and galaxies with $n_{\mathrm{env}} > 3.0$ to be in high density environments.
+We classify galaxies with $n_{\mathrm{env}} = 0.0$ to be in low density environments and galaxies with $n_{\mathrm{env}} > 3.0$ to be in high density environments.
 
@@
 $z=0$--$0.8$. The environment of each galaxy  
-was calculated using a cylindrical aperture size of $R=\apradius \: \mathrm{Mpc}$ and $H=\apheight \: \mathrm{Mpc}$ and  
-{\bf classified as low environment when $n_{\mathrm{env}} = 0.0$ and }as high environment when $n_{\mathrm{env}} > 3.0$. The SMFs use mass bins of 
+was calculated using a cylindrical aperture size of $R=\apradius \: \mathrm{Mpc}$ and $H=\apheight \: \mathrm{Mpc}$ and classified as low environment when $n_{\mathrm{env}} = 0.0$ and as high environment when $n_{\mathrm{env}} > 3.0$.
+The SMFs use mass bins of
 width $\Delta \mathrm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.2$. In each panel we use shades of blue 
@@
 \citealt{Baldry:2006aa, Cucciati:2010aa}) find, at these redshifts and mass range, a greater environment dependence in $f_\mathrm{Q}$.
-However we note that, at $\mathcal{M}_* < 10^{10} \mathcal{M}_{\odot}$ at $z \sim 0.3$, only three of the five PRIMUS fields used in our analysis (XMM-SXDS, XMM-CFHTLS, and COSMOS; see Section \ref{sec:primus}) contribute galaxies to our sample.
-As a result our jack-knife uncertainties, which are calculated by excluding one PRIMUS field at a time, underestimate the uncertainty from cosmic variance especially since the PRIMUS fields XMM-SXDS and XMM-CFHTLS are adjacent fields.
-A rough estimate of the cosmic variances using the expressions derived in \cite{Driver:2010aa} put cosmic variance uncertainties $> 60 \%$.
-This estimate does not take into account the unique geometry of the PRIMUS fields or the edge-cuts, which only increase the cosmic variance uncertainties.
-Therefore, the quiescent fraction comparison at $z \sim 0.3$ for $\mathcal{M}_{*} < 10^{10} \mathcal{M}_\odot$ cannot be accurately made from our PRIMUS sample.}
+Our classification of star-forming/quiescent galaxies may contribute to this discrepancy with other quiescent fraction studies.
+We also note that for $\mathcal{M}_* < 10^{10} \mathcal{M}_{\odot}$ at $z \sim 0.3$, only three of the five PRIMUS fields used in our analysis (XMM-SXDS, XMM-CFHTLS, and COSMOS; see Section \ref{sec:primus}) contribute galaxies to our sample.
+As a result our jack-knife method, which calculates uncertainty by excluding one PRIMUS field at a time, may underestimate the uncertainty thereby making an accurate comparison difficult at low masses.
+For our analysis, we focus on $\mathcal{M}_* > 10^{10} \mathcal{M}_\odot$.
+}
 
@@
 While the high density $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ is greater than low density environment $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ over the entire redshift range of our sample, there is a significant increase in $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ over cosmic time for both environments.
-{\bf For the environment cut-offs ($n_{\mathrm{env}} =0.0 $ for low }and $n_{\mathrm{env}} > 3.0$ for high), there is no significant difference in the slope of the evolution between the environments.}         \label{fig:qffit}
+For the environment cut-offs ($n_{\mathrm{env}} =0.0 $ for low and $n_{\mathrm{env}} > 3.0$ for high), there is no significant difference in the slope of the evolution between the environments.}         \label{fig:qffit}
     \end{center}
@@
 
-Because our fixed aperture definition of environment is susceptible to
-contamination due to PRIMUS redshift errors, we consider in Figure
+However, the uncertainties in the PRIMUS redshifts may contaminate 
+our fixed aperture measurements of galaxy environment. Consequently, we consider in Figure
 \ref{fig:qffit_comp} more stringent high density environment
@@
 environments. Group galaxies in \cite{Iovino:2010aa} have higher
-overall $f_{\mathrm{Q}}$ than isolated galaxies. However, unlike our
+overall $f_{\mathrm{Q}}$ than isolated galaxies. {\bf However, unlike our
 results, which find a greater $f_{\mathrm{Q}}$ evolution at higher density
-environments, \cite{Iovino:2010aa} finds the opposite environment
+environments, $f_\mathrm{Q}$ in \cite{Iovino:2010aa} shows the opposite environment
 dependence that there is a significantly greater $f_{\mathrm{Q}}$
-evolution for isolated galaxies.
+evolution for isolated galaxies. Once the large uncertainties in the $f_\mathrm{Q}$ 
+fit are taken into account, \cite{Iovino:2010aa} state that the $f_\mathrm{Q}$ is difficult to measure from their sample. }
 
@@
 
-% Removed in order to tone down the criticism of 
 %However, even without the correction (not shown), in their best-fit $f_{\mathrm{Q}}$ results, the same evolutionary trends mentioned above are observed.
 
-While the zCOSMOS survey provides more precise spectroscopic redshifts than PRIMUS, our sample provides significantly larger statistics.
-In addition, our sample covers a larger portion of the sky.
-Our SDSS-{\em GALEX} sample covers $2,505 \;\mathrm{deg}^2$.
+{\bf Due to the redshift uncertainties in PRIMUS, our galaxy environment measures are more susceptible to contamination.
+As discussed in \cite{Coil:2011aa} and \cite{Cool:2013aa}, PRIMUS has redshift success rate of $> 75 \%$; in comparison, zCOSMOS has $88 \%$ redshift completeness for the entire sample and $95 \%$ complete within the redshift range $0.5 < z < 0.8$ (\citealt{Lilly:2009aa}).
+Although the zCOSMOS survey provides more precise spectroscopic redshifts, PRIMUS has higher overall completeness due to its high targeting fraction of $\sim 80 \%$.
+zCOSMOS has a spatial sampling rate of $\sim 30-50\%$ and a overall completeness rate of $48 - 52 \%$ (\citealt{Knobel:2012aa}).
+Our sample also provides larger statistics and covers a larger portion of the sky.} Our SDSS-{\em GALEX} sample covers $2,505 \;\mathrm{deg}^2$.
 More comparably, our PRIMUS sample covers $5.5 \;\mathrm{deg}^2$, over 3 times the sky coverage of zCOSMOS ($1.7 \;\mathrm{deg}^2$).
@@
   \mnras, 363, 2
+
+\bibitem[{{Knobel} {et~al.}(2012){Knobel}, {Lilly}, {Iovino}, {Kova{\v c}}, {Bschorr}, {Presotto}, {Oesch}, {Kampczyk}, {Carollo}, {Contini}, {Kneib}, {Le Fevre}, {Mainieri}, {Renzini}, {Scodeggio}, {Zamorani}, {Bardelli}, {Bolzonella}, {Bongiorno}, {Caputi}, {Cucciati}, O.
+and {de la Torre}, {de Ravel}, {Franzetti}, {Garilli}, {Lamareille}, {Le Borgne}, {Le Brun}, {Maier}, {Mignoli}, {Pello}, {Peng}, {Perez Montero}, {Silverman}, {Tanaka}, {Tasca}, {Tresse}, {Vergani}, {Zucca}, {Barnes}, {Bordoloi}, {Cappi}, {Cimatti}, {Coppa}, {Koekemoer}, {López-Sanjuan}, {McCracken}, {Moresco}, {Nair}, {Pozzetti}, \& {Welikala}}]{Knobel:2012aa}
+{Knobel}, C., {Lilly}, S.~J., {Iovino}, A., {et~al.} 2012, \apj, 753, 121
 

### 2015-12-15 fc_paper/fc_paper.tex
Draft being edited to include new quadrupole results!

@@
 
-\title{A Fiber Collision Correction Method for the BOSS Power Spectrum}
+\title{Accounting for Fiber Collisions in the Galaxy Power Spectrum Measurements}
 
@@
 Roman~Scoccimarro\altaffilmark{1}, 
-Michael R.~Blanton\altaffilmark{1}, others} 
+Michael R.~Blanton\altaffilmark{1}, 
+moreauthors} 
 \altaffiltext{1}{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Place, New York, NY 10003; chh327@nyu.edu}
@@
 Fiber-fed multi-object spectroscopic surveys, with their ability to collect an unprecedented number of redshifts, dominate cosmological studies.
-However physical constraints limit these surveys from successfully collecting redshifts from galaxies that are too close to each other on the focal plane, which ultimately leads to significant systematic effects on galaxy clustering measurements.
-Using simulated mock catalogs, extensively used in interpreting large-scale structure clustering results of the Sloan Digital Sky Survey, we investigate the effects of fiber collisions on the galaxy power spectrum and compare the methods currently used to correct for fiber collisions in the literature and assess their success in reconstructing the true power spectrum.
+However physical constraints, which limit these surveys from successfully collecting redshifts from galaxies too close to each other on the focal plane, ultimately lead to significant systematic effects on galaxy clustering measurements.
+Using simulated mock catalogs, extensively used in interpreting large-scale structure clustering results of the Sloan Digital Sky Survey, we investigate the effects of fiber collisions on the galaxy power spectrum monopole and quadrupole and compare methods currently used to correct for fiber collisions in the literature and assess their success in reconstructing the true power spectrum.
 
-We present our fiber collision correction method, which first statistically reconstructs the clustering of fiber collided pairs by modeling the distribution of the line-of-sight displacements between them using cases where both redshifts are obtained.
+We present two methods to account for fiber collisions in the power spectrum.
+The first method statistically reconstructs the clustering of fiber collided galaxy pairs by modeling the distribution of the line-of-sight displacement between them using cases where both redshifts are obtained.
 The method properly accounts for fiber collisions in the shot-noise correction term of the power spectrum estimator.
-Using our method, we successfully reproduce the true power spectrum for the mock catalogs with residuals of $< 1\%$ at $k \sim 0.3 \; h/\mathrm{Mpc}$ and $< 10\%$ at $k \sim 0.8 \; h/\mathrm{Mpc}$.
-Our comparisons to other existing correction methods demonstrate that our method most accurately reconstructs the true power spectrum from fiber collided galaxy data especially at small scales ($k > 0.1\; h/\mathrm{Mpc}$), with the added advantage that our method can be validated and calibrated in observed data.
-With statistical uncertainty no longer dominating galaxy clustering measurements, our correction method will allow us to extend power spectrum measurements to smaller scales than previously possible.
+For the monopole, this method reproduces the true power spectrum monopole for the mock catalogs with residuals of $< 1\%$ at $k \sim 0.3 \; h/\mathrm{Mpc}$ and $< 10\%$ at $k \sim 0.8 \; h/\mathrm{Mpc}$ -- a significant improvement from existing correction methods, especially at small scales ($k > 0.1\; h/\mathrm{Mpc}$).
+In our second method, we model the effect of fiber collisions on the true galaxy power spectrum by Fourier transforming an analytical estimate of the effect of fiber collisions on the two-point correlation function.
+Using this method we are able to reproduce the power spectrum quadrupole with fiber collisions from the true power spectrum to within sample variance for $k < 0.6\;h/\mathrm{Mpc}$ ({\bf MADEUPNUMBER}).
+{\bf INCLUDE MORE NUMBERS}.
+With statistical uncertainty no longer dominating galaxy clustering measurements, the methods we present in accounting for fiber collisions will allow us to extend power spectrum measurements to smaller scales than previous possible.
+
+%We present our fiber collision correction method for the power spectrum monopole, which first statistically reconstructs the clustering of fiber-collided pairs by modeling the distribution of the line-of-sight displacements between them, and then properly accounts for fiber collisions in the shot-noise correction term of the power spectrum estimator.
+Using our method, we successfully reproduce the true power spectrum monopole for the mock catalogs with residuals of $< 1\%$ at $k \sim 0.3 \; h/\mathrm{Mpc}$ and $< 10\%$ at $k \sim 0.8 \; h/\mathrm{Mpc}$.
+Our comparisons to other correction methods demonstrate that our method most accurately reconstructs the true power spectrum from fiber-collided galaxy data especially at small scales ($k > 0.1\; h/\mathrm{Mpc}$), with the added advantage that our method can be validated and calibrated in observed data.
 \end{abstract}
@@
 \section{Introduction} 
-As of 2015, millions of redshifts to distant galaxies have been obtained through redshift surveys.
+As of 2015, millions of redshifts to distance galaxies have been obtained through redshift surveys.
 Cosmological measurements such as galaxy clustering statistics are no longer dominated by uncertainties from statistical precision, but from systematic effects of the measurements.
-These surveys, such as the 2dF Galaxy Redshift Survey (2dFGRS; \citealt{Colless:1999aa}) and the Sloan Digital Sky Survey III Baryon Oscillation Spectroscopic Survey (SDSS-III BOSS; \citealt{Anderson:2012aa, Dawson:2013aa}) and future surveys such as the Extended Baryon Oscillation Spectroscopic Survey (eBOSS; {\bf WHO DO CITE?}) use fiber-fed spectrographs.
+These surveys, such as the 2dF Galaxy Redshift Survey (2dFGRS; \citealt{Colless:1999aa}) and the Sloan Digital Sky Survey III Baryon Oscillation Spectroscopic Survey (SDSS-III BOSS; \citealt{Anderson:2012aa, Dawson:2013aa}) and future surveys such as the Extended Baryon Oscillation Spectroscopic Survey (eBOSS; \citealt{Dawson:2015aa}), use fiber-fed spectrographs.
 
 For each galaxy, a fiber is used to obtain a spectroscopic redshift.
-However, due to the physical size of the fiber housing, if two galaxies are located within the fiber collision angular scale from one another on the sky, separate fibers cannot be placed adjacently to observe them simultaneously (\citealt{Yoon:2008aa} {\bf CITE MORE}).
-In these situations, only a single redshift is measured.
+However, due to the physical size of the fiber housing, if two galaxies are located within the fiber collision angular scale from one another on the sky, separate fibers cannot be placed adjacently to observe them simultaneously (\citealt{Yoon:2008aa} {\bf CITE MORE?}).
+In these situations, the redshifts of only a single redshift is measured.
 With redshifts of galaxies in close angular proximities missing from the sample, any clustering statistic probing these scales will be systematically affected.
 
-As our cosmological surveys extend further to higher redshifts, the systematic effect becomes more severe because the fiber collision angular scale corresponds to a larger comoving scale, thereby affecting our measurements on larger scales.
-SDSS-III BOSS, in particular, has an angular fiber collision scale of $62''$.
-This corresponds to $\sim 0.4 \;\mathrm{Mpc}/h$ at the center of the survey's redshift redshift range; fiber collided galaxies account for $\sim 5\%$ of the galaxy sample (\citealt{Anderson:2012aa}).
-Although this accounts for a relatively small fraction of redshifts, its effect on clustering measurements such as the power spectrum is significant.
-They must to be accounted for to probe smaller scales and higher order statistics such as the three-point correlation function or the bispectrum.
-Even with the use of robotic fiber positioner technology in future surveys such as the Dark Energy Survey Instrument (DESI; \citealt{Schlegel:2011aa, Morales:2012aa, Makarem:2014aa})
-% What is the fiber positioner areas called??
-will render fiber collisions obsolete. Therefore, accounting for the systematic effects remains an unavoidable challenge for clustering statistics.
+As our cosmological surveys extend further to higher redshifts, the systematic effect becomes more severe, because the fiber collision angular scale corresponds to a larger comoving scale, thereby affecting our measurements on larger scales.
+SDSS-III BOSS, in particular, has an angular fiber collision scale of $62\arcsec$.
+This corresponds to $\sim 0.43 \;\mathrm{Mpc}/h$ at the center of the survey's redshift redshift range; fiber-collided galaxies account for $\sim 5\%$ of the galaxy sample (\citealt{Anderson:2012aa}).
+While this may seem like a relatively small fraction of redshifts, its effect on clustering measurements such as the power spectrum is significant and need be accounted for in order to probe smaller scales and higher order statistics such as the three-point correlation function or the bispectrum.
+Future spectroscopic surveys such as the Dark Energy Survey Instrument (DESI; \citealt{Schlegel:2011aa, Morales:2012aa, Makarem:2014aa}), will use robotic fiber positioner technology.
+Unfortunately this will only increase the effect of fiber collisions.
+Therefore, accounting for fiber collisions will be an unavoidable challenge for clustering statistics in the near future.
 
 To correct for fiber collisions, one common approach used in clustering statistics is the nearest neighbor method (\citealt{Zehavi:2002aa, Berlind:2006aa, Anderson:2012aa}).
-For fiber collided galaxies without resolved redshifts, the method assigns the statistical weight of the fiber collided galaxy to its nearest angular neighbor.
+For fiber-collided galaxies without resolved redshifts, the method assigns the statistical weight of the fiber-collided galaxy to its nearest angular neighbor.
 This provides a reasonable correction for the fiber collision effects at scales much larger than the fiber collision scales; however the correction falls short near the fiber collision scale.
@@
 While this shot-noise term adjustment has been calibrated within the mock catalogs used to interpret the BOSS clustering results there is no way to validate and calibrate these methods independently for observations.
-Methods of this kind rely entirely on the accuracy of the mock catalogs to constrain fiber collisions, which is especially concerning since fiber collisions systematically affect small scales and mock catalogs may not be realiable at such small scales (\citealt{Heitmann:2008aa, Schneider:2015aa}).
+Methods of this kind rely entirely on the accuracy of the mock catalogs to constrain fiber collisions, which is especially concerning since fiber collisions systematically affect small scales and mock catalogs may not be reliable at such small scales (\citealt{Heitmann:2008aa, Schneider:2015aa}).
 
 Recently \cite{Guo:2012aa}, focusing on SDSS-III BOSS like samples, proposed a fiber collision correction method for the 2PCF that is able to reasonably correct for fiber collisions above and below the collision scale.
-\cite{Guo:2012aa} estimates the total contribution of fiber collided galaxies to the two point correlation function by examining the pair statistics in overlapping tiling regions of the survey, where a smaller fraction of galaxies suffer from fiber collisions.
-Unfortunately, due to the complex geometry of the overlapping regions, this method is difficult to apply to Fourier clustering measurements.
-As a result, we propose a fiber collision correction method that, first, improves upon the nearest neighbor method by using the distribution of the line-of-sight displacement between resolved fiber collided galaxies to statistically reconstruct the clustering of fiber collided galaxies; and properly accounts for fiber collisions in the shot-noise correction term of the power spectrum estimator.
+\cite{Guo:2012aa} estimates the total contribution of fiber-collided galaxies to the two point correlation function by examining the pair statistics in overlapping tiling regions of the survey, where a smaller fraction of galaxies suffer from fiber collisions.
+Unfortunately, applying this method to Fourier clustering measurements is intractable due to the complex geometry of the overlapping regions.
+As a result, we propose two methods to account for fiber collisions in power spectrum measurements.
+The first improves upon the nearest neighbor method by using the distribution of the line-of-sight displacement between resolved fiber collided galaxies to statistically reconstruct the clustering of fiber-collided galaxies; and properly accounts for fiber collisions in the shot-noise correction term of the power spectrum estimator.
+This method seeks to recover the true power spectrum from fiber collided galaxy catalogs.
+The second, on the other hand, uses the Fourier transform of an analytic estimate of the effect of fiber collisions in the 2PCF in order to model the effect of fiber collisions and reproduce the fiber collided power spectrum from the true power spectrum.
 
-In Section \ref{sec:catalog}, we present a brief description of the simulated mock catalogs with realistically applied fiber collisions and the power spectrum estimator used throughout the paper.
-Then during our discussion of the two components of our correction method in Section \ref{sec:fc_corr}, we quantify the effects of fiber collisions of power spectrum measurements and test and compare correction methods in the literature.
-Afterwards, we present our correction method, test it on the mock catalogs, and compare it to other correction methods in Section \ref{sec:results}.
+In Section \ref{sec:catalog}, we briefly describe the simulated mock catalogs with realistically applied fiber collisions and the power spectrum estimator used throughout the paper.
+We demonstrate the effects of fiber collisions on power spectrum measurements and compare correction methods in the literature in Section \ref{sec:fc_corr}.
+Afterwards we present our two methods of accounting for fiber collisions and then in Section \ref{sec:results} apply the methods to the mock catalogs.
 Finally in Section \ref{sec:summary} we summarize and discuss our results.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% fiber collided Mock catalogs
+% Fiber-collided Mock catalogs
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{fiber collided Mock catalogs} \label{sec:catalog}
+\section{Fiber-collided Mock catalogs} \label{sec:catalog}
 For various purposes such as calculating covariance matrices or estimating cosmic variance, simulated mock catalogs play a crucial role in interpreting clustering measurements of observed galaxies (\citealt{Scoccimarro:2002aa, Anderson:2012aa, Manera:2013aa}).
@@
 A direct way of understanding the effects of fiber collisions on clustering statistics in observations is to first apply fiber collisions to mock catalogs and then compare the clustering statistics obtained from mock catalogs with and without the fiber collisions.
-Correction methods for fiber collisions can then be applied to the fiber collided mocks and the merit of the correction method can be quantified by how successfully they reproduce the clustering statistics of the original mock catalogs without fiber collisions.
+Correction methods for fiber collisions can then be applied to the fiber-collided mocks and the merit of the correction method can be quantified by how successfully they reproduce the clustering statistics of the original mock catalogs without fiber collisions.
 The optimal correction method can then be applied to the observed data with some assurance that it accounts for fiber collisions and improves the clustering measurements.
@@
 When applying the fiber collisions to the mock catalogs, it is essential to apply them in the same manner they affect the observational data.
-For BOSS, galaxies within $62"$ are fiber collided (\citealt{Anderson:2012aa}).
+For BOSS, galaxies within $62\arcsec$ are fiber-collided (\citealt{Anderson:2012aa}).
 In reality, this simple criteria is further complicated by the tiling scheme of observing plates that create overlapping regions, which have a higher success rate in resolving galaxy spectra within the fiber collision angular scale (\citealt{Guo:2012aa}).
@@
 Effects of fiber collisions must be understood and interpreted in conjunction with these other systematic effects.
-Therefore, in this paper, we use LasDamas (\citealt{McBride:2009aa, McBride:2011aa}), Quick Particle Mesh (\citealt{White:2014aa}), and Tiling mock catalogs ({\bf CITATIONS?}), which have already been extensively used in interpreting clustering results for SDSS and BOSS and are generated through different prescriptions.
-Therefore they provide unique data sets to measure the effects of fiber collisions and to test our correction method tailored for BOSS.
+Therefore, in this paper, we use LasDamas (\citealt{McBride:2009aa, McBride:2011aa}), Quick Particle Mesh (\citealt{White:2014aa}), and Nseries ({\bf CITATION?}) catalogs, which have already been extensively used in interpreting clustering results for SDSS and BOSS and are generated through different prescriptions.
+Therefore they provide a robust sets of data to measure the effects of fiber collisions and to test our correction method tailored for BOSS.
 %Each of these mock catalogs use some sort of N-body dark matter simulation along with a HOD prescription to populate the dark matter halos with ``galaxies".
@@
 
-The LasDamas Galaxy mock catalogs are constructed from the Oriana N-body Large Suite of Dark Matter Simulations (LasDamas) with $1280^3$ particles with a box with side length, $L_\mathrm{Box} = 2400\;\mathrm{Mpc}/h$.
-The N-body LasDamas simulations use a spatially flat $\Lambda$CDM cosmology with $\Omega_\mathrm{m} = 0.25$, $\Omega_\Lambda = 0.75$, $\Omega_\mathrm{b} = 0.04$, $\sigma_8 = 0.8$, $n_\mathrm{s} = 1$ and $h=0.7$.
+The LasDamas Galaxy mock catalogs is constructed from the Oriana N-body Large Suite of Dark Matter Simulations (LasDamas) with $1280^3$ particles with a box with side length, $L_\mathrm{Box} = 2400\;\mathrm{Mpc}/h$.
+The N-body LasDamas simulations uses a spatially flat $\Lambda$CDM cosmology with $\Omega_\mathrm{m} = 0.25$, $\Omega_\Lambda = 0.75$, $\Omega_\mathrm{b} = 0.04$, $\sigma_8 = 0.8$, $n_\mathrm{s} = 1$ and $h=0.7$.
 The dark matter halos are then identified using a friends-of-friends (FOF) algorithm (\citealt{Davis:1985aa}) with a linking length $b = 0.2 $ times the mean interparticle separation.
@@
 The HOD prescription is specified so that the galaxy mock catalogs reproduce the galaxy number density and projected correlation function of the observed SDSS Luminous Red Galaxy sample with $M_g < -21.8$.
-The LasDamas galaxy mock catalogs have 40 realizations, each of which spans the redshift range, $0.16 < z < 0.44$ and are restricted to the survey geometry of SDSS Data Release 7.
+The LasDamas galaxy mock catalogs have 40 realizations each of which spans the redshift range, $0.16 < z < 0.44$ and are restricted to the survey geometry of SDSS Data Release 7.
 They also include redshift space distortions from velocities, but do not model fiber collisions.
 
-To model the fiber collisions of the observed galaxies in BOSS, we impose fiber collisions at the angular scale of $62''$.
-Once we identify galaxies within $62''$ of each other, we arbitrary select one of the galaxies and assign the statistical weights of the other galaxies within $62''$ of it.
+To model the fiber collisions of the observed galaxies in BOSS, we impose fiber collisions at the angular scale of $62\arcsec$.
+Once we identify galaxies within $62\arcsec$ of each other, we arbitrary select one of the galaxies and assign the statistical weights of the other galaxies within $62\arcsec$ of it.
 Roughly $\sim 2.5 \%$ of the galaxies in the LasDamas mock catalogs are affected by fiber collisions.
@@
 The mock galaxy sample is then trimmed to the BOSS CMASS survey footprint, downsampled based on angular sky completeness (sector completeness) and radial selection.
-Furthermore, QPM mocks model the fiber collisions of the BOSS CMASS sample ($62''$ angular fiber collision scale).
+Furthermore, QPM mocks model the fiber collisions of the BOSS CMASS sample ($62\arcsec$ angular fiber collision scale).
 The QPM galaxy mock catalog uses the following $\Lambda$CDM cosmology: $\Omega_\mathrm{m} = 0.29$, $\Omega_\Lambda = 0.71$, $\sigma_8 = 0.8$, $n_\mathrm{s} = 0.97$ and $h=0.7$.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Powerspectrum Estimator
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Power Spectrum Estimator} \label{sec:pk_est}
-In this paper, we focus on the effects of fiber collisions on the galaxy power spectrum out of the other clustering measurements.
-Throughout the paper, when we measure the power spectrum, we use the standard \cite{Feldman:1994aa} (hereafter FKP) estimator and the following formalisms from the FKP paper:
-\begin{equation} \label{eq:fkppk}
-P({\bf k}) = <|F({\bf k})|^2> - \frac{(1+\alpha) \int d^3r \;\bar{n}({\bf r})w_{\mathrm{FKP}}^2({\bf r})} {\int d^3r \; \bar{n}^2({\bf r})w_{\mathrm{FKP}}^2({\bf r})},
+In this paper, we focus on the effects of fiber collisions on the galaxy power spectrum out of the other clustering measurements, more specifically the monopole and quadrupole of the power spectrum.
+Throughout the paper, when we measure the power spectrum we use the estimator described in \cite{Scoccimarro:2015aa} and the formalism therein.
+To reiterate Section III.
+A.
+in \cite{Scoccimarro:2015aa}, we calculate the monopole component of the power spectrum using:
+\begin{equation}\label{eq:roman_p0k}
+\widehat{P_0}(k) = \frac{1}{I_{22}} \left[ \int \frac{d\Omega_k}{4 \pi} |F_0({\bf k})|^2 - N_0 \right]
 \end{equation}
@@
 \begin{equation}
-F({\bf r}) = \frac{w_\mathrm{FKP}({\bf r}) [n_g({\bf r}) - \alpha n_r({\bf r})]} {[\int d^3r \; \bar{n}^2({\bf r})w_\mathrm{FKP}^2({\bf r})]^{\frac{1}{2}}} 
+F_0({\bf k}) = \left( \sum_{j = 1}^{N_g} - \alpha \sum_{j=1}^{N_r} \right) w_j\;e^{i {\bf k}\cdot{\bf x}_j}
 \end{equation}
-and the second term represents the constant shot-noise contribution to the power due to the discrete density field of our galaxies.
-$n_g$ is the galaxy density, $n_r$ is the density of the synthetic random catalog, $\alpha$ is the ratio of the number of galaxies over the number of synthetic random galaxies, $\bar{n}$ is the mean density of the galaxies, and $w_{\mathrm{FKP}}$ is the minimum variance weight derived in \cite{Feldman:1994aa}:
+with standard normalization constant
+\begin{equation} \label{eq:i22}
+I_{22} = \alpha \sum^{N_g}_{j=1} \bar{n}({\bf x}_j)w_j^2
+\end{equation}
+and shot noise term
+\begin{equation} \label{eq:roman_shotnoise}
+N_0 = \left( \sum_{j = 1}^{N_g} - \alpha^2 \sum_{j=1}^{N_r} \right) w_j^2. 
+\end{equation}
+$N_0$ represents the constant shot noise contribution to the power due to the discrete density field of our galaxies.
+$\alpha$ is the ratio of the number of galaxies ($N_g$) over the number of synthetic random galaxies ($N_r$), $\bar{n}({\bf x})$ is the mean density of the galaxies at position ${\bf x}$, and $w_j$ is weight of each object, which includes the the minimum variance weight derived in \cite{Feldman:1994aa}:
 \begin{equation}
-w_{\mathrm{FKP}} ({\bf r}) = \frac{1}{1+\bar{n}({\bf r}) P_0}
+w_{\mathrm{FKP}} ({\bf x}_j) = \frac{1}{1+\bar{n}({\bf x}_j) P_0}
 \end{equation}
-where $P_0$ is the power spectrum amplitude at which the error is minimized. We use $P_0 = 20000\; \mathrm{Mpc}^3/h^3$ for our analysis, which corresponds to $k \sim 0.1\; h/\mathrm{Mpc}$.
+where $P_0$ is the power spectrum amplitude at which the error is minimized.
+We use $P_0 = 20000\; \mathrm{Mpc}^3/h^3$ for our analysis, which corresponds to $k \sim 0.1\; h/\mathrm{Mpc}$.
+We note that the shot noise term in Eq.
+\ref{eq:roman_shotnoise} differs from the standard shot noise term from \cite{Feldman:1994aa}, which uses $N_0^\mathrm{FKP} = \alpha (1+\alpha) \sum^{N_r}_{j=1} w_j^2.
+$The difference between shot noise formulations will be discussed further in Section \ref{sec:shotnoise}.
 
+For the quadrupole, 
+\begin{equation}\label{eq:roman_p2k}
+\widehat{P_2}(k) = \frac{5}{I_{22}} \int \frac{d\Omega_k}{4 \pi} F_2({\bf k}) F_0^*({\bf k})
+\end{equation}
+where 
+\begin{equation}
+F_2({\bf k}) = \frac{3}{2}\hat{k}_a\hat{k}_b Q^{ab}({\bf k}) - \frac{1}{2} F_0({\bf k})
+\end{equation}
+with 
+\begin{equation}
+Q^{ab}({\bf k}) = \left( \sum_{j = 1}^{N_g} - \alpha \sum_{j=1}^{N_r} \right) \hat{x}_j^a\hat{x}_j^b w_j \;e^{i {\bf k}\cdot{\bf x}_j}
+\end{equation}
+
+% P(k) plot for mocks and BOSS
 \begin{figure}
@@
 \includegraphics[scale=0.5]{fcpaper_pk_comp.png} 
-\caption{Average power spectrum $\overline{P(k)}$ for BOSS DR12 (black) and the mock catalogs LasDamas (blue), QPM (orange), and Tiling Mock (green), listed in Section \ref{sec:catalog} using the FKP $P(k)$ estimator.
-The width of the $P(k)$ for LasDamas and QPM represent the sample variance ($\Delta P(k)$) calculated from the multiple realizations of the mock catalogs.
-We emphasize that fiber collisions were not applied to the mock catalogs for the $P(k)$ measurements.
-Meanwhile, galaxy weights (Equation \ref{eq:weight}) are applied to the BOSS DR12 $P(k)$ measurement.
+\caption{Average power spectrum monopole $\overline{P_0(k)}$ and quadrupole $\overline{P_2(k)}$ for BOSS DR12 (black) and the mock catalogs LasDamas (blue), QPM (orange), and Tiling Mock (green), listed in Section \ref{sec:catalog} using the estimator from \cite{Scoccimarro:2015aa}.
+The width of the $P_{l}(k)$ for LasDamas and QPM represent the sample variance ($\Delta P_{l}(k)$) calculated from the realizations of the mock catalogs.
+We emphasize that fiber collisions were not applied to the mock catalogs for the measurements above.
+Meanwhile, galaxy weights (Equation \ref{eq:weight}) are applied to the BOSS DR12 $P_l(k)$ measurements.
 We remind readers that the LasDamas mock catalog has an overall greater $\overline{P(k)}$ due to the fact that the catalog spans the SDSS LRG sample redshift range instead of the BOSS redshift range of the other mock catalogs.} \label{fig:mockpk}
@@
 
-For LasDamas, QPM, and Tiling mock catalogs we use the FKP estimator described above to measure the power spectrum in Figure \ref{fig:mockpk}.
-The fiber collisions described previously are not applied to the mock catalogs in the $P(k)$ calculations for Figure \ref{fig:mockpk}.
-Without fiber collisions, we use the exact formulation of Equation \ref{eq:fkppk} in the FKP power spectrum estimator.
+In Figure \ref{fig:mockpk}, we plot the $P_0(k)$ and $P_2(k)$ calculated using Eq.
+\ref{eq:roman_p0k} and Eq.
+\ref{eq:roman_p2k}, respectively, for LasDamas, QPM, and Tiling mock catalogs.
+The fiber collisions described previously are not applied to the mock catalogs in the $P(k)$ calculations.
+Without fiber collisions, the weights of the objects is equivalent to the FKP weights, $w_j = w_{j,\mathrm{FKP}}$.
 
-We also plot the $P(k)$ from the BOSS Data Release 12 CMASS data (\cmasscolor) in Figure \ref{fig:mockpk}.
+We also plot the $P_0(k)$ and $P_2(k)$ from the BOSS Data Release 12 CMASS data (\cmasscolor) in Figure \ref{fig:mockpk}.
 For BOSS DR12 CMASS, systematic weights are assigned to the galaxies in order to account for sector completeness, redshift failures, and fiber collisions.
@@
 \end{equation} 
-(\citealt{Anderson:2012aa, Beutler:2014aa}).
-As a result, we modify Equation \ref{eq:fkppk} when we calculate the power spectrum.
-Instead of the galaxy density term $n_g({\bf r})$ we use a weighted galaxy density term $n'_g({\bf r}) = n_g({\bf r}) w({\bf r})$, which includes the systematic weights for each galaxy.
-Also, instead of $\alpha = N_{\mathrm{gal}}/N_\mathrm{ran}$ we use $\alpha ' = N'_\mathrm{gal}/N_\mathrm{ran}$ where $N'_\mathrm{gal} = \sum_\mathrm{gal} w_\mathrm{tot}$.
+(\citealt{Anderson:2012aa, Beutler:2014aa}), which are included in the object weights $w_j$ along with $w_{j, \mathrm{FKP}}$.
+The statistical weights are also included in the factor $\alpha$.
+So for the BOSS $P_0(k)$ and $P_2(k)$ calculations, $w_j = w_{j, \mathrm{tot}} \times w_{j, \mathrm{FKP}}$ and $\alpha' = \sum_{j=1}^{N_g} w_\mathrm{tot} / N_r$.
 
-For LasDamas and QPM, which have multiple realizations, we compute the sample variance of the power spectrum
+Furthermore, for the mock catalogs with multiple realizations (LasDamas, QPM and Nseries), we compute the sample variance of the power spectrum monopole and quadrupole
 \begin{equation} \label{eq:pk_var}
-\Delta P (k)= \sqrt{\frac{1}{N_\mathrm{realization}} \sum\limits_i^{N_\mathrm{realization}} (P_i(k)- \overline{P(k)})^2 }. 
+\Delta P_l (k)= \sqrt{\frac{1}{N_\mathrm{mocks}} \sum\limits_{i=1}^{N_\mathrm{mocks}} (P^i_l(k)- \overline{P_l(k)})^2 }\;\; (l= 0, 2). 
 \end{equation}
-$N_\mathrm{realization}$ is the total number of realizations (40 for LasDamas and 1000 for QPM) and $P_i(k)$ is the power spectrum for each realization.
+$N_\mathrm{mock}$ is the total number of realizations (40 for LasDamas and 1000 for QPM) and $P^i_l(k)$ is the power spectrum ($l=0$ monopole, $l=2$ quadrupole) for each realization.
 $\Delta P(k)$ is represented by the width of the $P(k)$ in Figure \ref{fig:mockpk}.
@@
 For galaxies without resolved spectroscopic redshifts due to fiber collisions, the entire statistical weight of the galaxy is assigned to its nearest angular neighbor.
-This method effectively assumes that all galaxies within the angular fiber collision scale ($< 62 "$ for BOSS) are correlated with one another.
+This method assumes that all galaxies within the angular fiber collision scale ($< 62 "$ for BOSS) are correlated with one another.
 In other words, the method assumes that galaxies within the fiber collision angular scale reside in the same halo so displacing one and placing it on top of the other does not significantly alter the clustering statistics.
-One consequence of this method however is that galaxies within the angular fiber collision scale purely by coincidence (hereafter referred to as ``chance alignments") are incorrectly assumed to be gravitationally correlated, so when their statistical weight is added to its nearest angular neighbor, they are in fact displaced significantly from their true position.
+One consequence of this method however is that galaxies within the angular fiber collision scale purely by coincidence (hereafter referred to as ``chance alignments") are incorrectly assumed to be gravitationally correlated, so when their statistical weight is added to its nearest angular neighbor, they are in fact displaced significantly from its true position.
 For BOSS, the nearest angular neighbor method can displace galaxies by up to $500 \;\mathrm{Mpc}$.
-Furthermore even for fiber collided galaxies that reside in the same group or cluster, up-weighting the nearest neighbor ignores halo-scale line-of-sight displacements, which as we present in Section \ref{sec:dlos}, are significant.
+Furthermore even for fiber-collided galaxies that reside in the same group or cluster, up-weighting the nearest neighbor ignores halo-scale line-of-sight displacements, which as we present in Section \ref{sec:dlos}, are significant.
 
 Although the nearest-neighbor method provides a reasonable estimate at large scales, in Section \ref{sec:dlos} we demonstrate that at small scales its effects on the power spectrum are significant and dominate sample variance.
-We present an improved method to account for correlated fiber collided galaxies using the line-of-sight displacement between fiber collided pairs.
+We present an improved method to account for correlated fiber-collided galaxies using the line-of-sight displacement between fiber-collided pairs.
 Then in Section \ref{sec:shotnoise}, we present modifications to the FKP power spectrum estimator in order to properly account for fiber collisions through the shot-noise correction term in the estimator.
-
-% MAKE SURE IT IS CLEAR THAT OUR CORRECTION METHOD COMBINES THE TWO.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Line-of-Sight Displacement of fiber collided Pairs} \label{sec:dlos}
-It is impossible to determine definitely from observed galaxy data whether individual fiber collided galaxies without resolved spectroscopic redshift are correlated or chance alignments.
-Fortunately, using the fiber collided pairs with resolved redshifts (mainly in the overlapping regions mentioned in Section \ref{sec:catalog}), it is possible to model the line-of-sight displacement of the fiber collided pairs and the fraction of galaxy pairs that are corrected and uncorrelated.
+\subsection{Line-of-Sight Displacement of Fiber-collided Pairs} \label{sec:dlos}
+It is impossible to determine from observed galaxy data whether fiber-collided galaxies without resolved spectroscopic redshift are correlated or chance alignments.
+Fortunately, using the fiber-collided pairs with resolved redshifts (mainly in the overlapping regions mentioned in Section \ref{sec:catalog}), it is possible to model the line-of-sight displacement of the fiber-collided pairs and the fraction of galaxy pairs that are corrected and uncorrelated.
 
-For simulated mock catalogs, described in Section \ref{sec:catalog}, modeling the fiber collided galaxy pairs is a much more direct task since fiber collisions are post-processed after the simulated galaxy positions are generated.
+For simulated mock catalogs, described in Section \ref{sec:catalog}, modeling the fiber-collided galaxy pairs is a much more direct task since fiber collisions are post-processed after the simulated galaxy positions are generated.
 All redshift values are provided for all galaxies regardless of angular proximity and the fiber collisions imposed on the mock catalogs are represented through the galaxies' ``fiber collision weights" ($w_\mathrm{fc}$).
-So for a fiber collided pair, one galaxy (``the nearest neighbor") will have the fiber collision weight of both galaxies, while the other has $w_\mathrm{fc} = 0$.
-Nonetheless, with redshifts of both fiber collided pair galaxies in mock catalogs, we can model the correlated and uncorrelated fiber collided pairs in order to better correct for fiber collisions.
+So for a fiber-collided pair, one galaxy (``the nearest neighbor") will have the fiber collision weight of both galaxies, while the other has $w_\mathrm{fc} = 0$.
+Nonetheless, with redshifts of both fiber-collided pair galaxies in mock catalogs, we can model the correlated and uncorrelated fiber-collided pairs in order to better correct for fiber collisions.
 
-To determine whether or not fiber collided pairs are correlated, we examine the comoving line-of-sight displacement ($d_{\mathrm{LOS}}$) of fiber collided galaxy pairs.
+To determine whether or not fiber-collided pairs are correlated, we examine the comoving line-of-sight displacement ($d_{\mathrm{LOS}}$) of fiber-collided galaxy pairs.
 We calculate the $d_{\mathrm{LOS}}$ by taking the difference of the line-of-sight comoving distance from the resolved redshifts:
@@
 \end{equation}
-$D_{\mathrm{C}}(z)$ is the line-of-sight comoving distance at redshift $z$ (\citealt{Hogg:1999aa}). $z_1$ and $z_2$ represent the resolved redshifts of the galaxies in the fiber collided pair.
+$D_{\mathrm{C}}(z)$ is the line-of-sight comoving distance at redshift $z$ (\citealt{Hogg:1999aa}). $z_1$ and $z_2$ represent the resolved redshifts of the galaxies in the fiber-collided pair.
 
-After calculating the $d_{\mathrm{LOS}}$ for every fiber collided pairs, in Figure \ref{fig:d_los} we present the distribution of $d_{\mathrm{LOS}}$ for LasDamas (\ldgcolor), QPM (\qpmcolor), Tiling Mock (\tmcolor), and BOSS DR12 (\cmasscolor).
+After calculating the $d_{\mathrm{LOS}}$ for every fiber-collided pairs, in Figure \ref{fig:d_los} we present the distribution of $d_{\mathrm{LOS}}$ for LasDamas (\ldgcolor), QPM (\qpmcolor), Tiling Mock (\tmcolor), and BOSS DR12 (\cmasscolor).
 All of the $d_{\mathrm{LOS}}$ distributions contain two components: a peak contained within the range $-20\;\mathrm{Mpc} < d_{\mathrm{LOS}} < 20\;\mathrm{Mpc}$ and a flat component (hereafter "tail" component) outside the peak that extends to $d_{\mathrm{LOS}} \sim \pm 500 \;\mathrm{Mpc}$ (entire range of the distribution not displayed in Figure \ref{fig:d_los}).
-For the BOSS data, since we cannot compute the $d_\mathrm{LOS}$ for fiber collided pairs without spectra, the $d_\mathrm{LOS}$ distribution only reflects the $d_\mathrm{LOS}$ from fiber collided pairs {\em with} resolved spectroscopic redshifts, mostly from tile overlapping regions of the BOSS survey.
+For the BOSS data, since we cannot compute the $d_\mathrm{LOS}$ for fiber-collided pairs without resolved spectra, the $d_\mathrm{LOS}$ distribution only reflects the $d_\mathrm{LOS}$ from fiber-colldied pairs {\em with} resolved spectroscopic redshifts, mostly from tile overlapping regions of the BOSS survey.
 
@@
 These galaxies in over-dense regions cause the peak in the $d_{\mathrm{LOS}}$ distribution.
-The ``tail" component is composed of chance alignment galaxy pairs that happen to be in close angular proximity.
+While the ``tail" component is composed of chance alignment galaxy pairs that are arbitrarily in close angular proximity even when they are not correlated.
 
@@
 
-Using the best-fit to the peak of the $d_{\mathrm{LOS}}$ distribution, we estimate the fraction of fiber collided pairs that are within the peak: 
+Using the best-fit to the peak of the $d_{\mathrm{LOS}}$ distribution, we estimate the fraction of fiber-collided pairs that are within the peak: 
 \begin{equation}
@@
 \end{equation}
-where $N_{\mathrm{pairs}}$ is the total number of fiber collided pairs.
-As mentioned above, this portion of fiber collided pairs are galaxy pairs that are correlated.
+where $N_{\mathrm{pairs}}$ is the total number of fiber-collided pairs.
+As mentioned above, this portion of fiber-collided pairs are galaxy pairs that are correlated.
 We list the $f_{\mathrm{peak}}$ values for each of the data catalogs in Table \ref{tab:mpfit}.
@@
 By simply incorporating the peak of the $d_{\mathrm{LOS}}$ distribution, we are able to significantly improve clustering statistics on small scales.
-Rather than placing the fiber collided galaxy on top of its nearest angular neighbor as NN correction does, placing the fiber collided galaxy at a displacement sampled from the $d_{\mathrm{LOS}}$ distribution away from its nearest neighbor better accounts for the small scale in clustering measurements.
+Rather than placing the fiber-collided galaxy on top of its nearest angular neighbor as NN correction does, placing the fiber-collided galaxy at a displacement sampled from the $d_{\mathrm{LOS}}$ distribution away from its nearest neighbor better accounts for the small scale in clustering measurements.
 On mock catalogs, we test this by first applying the NN to the mock catalogs.
-We then sample a displacement $d_i$ from $p(d_\mathrm{LOS})$ (Equation \ref{eq:peak}) for each fiber collided pair.
-Afterwards we ``place" the fiber collided galaxy a distance $d_i$ from the nearest neighbor galaxy assign $w_\mathrm{fc} = 1$ and reduce the $w_\mathrm{fc}$ of the the nearest-neighbor by 1.
+We then sample a displacement $d_i$ from $p(d_\mathrm{LOS})$ (Equation \ref{eq:peak}) for each fiber-collided pair.
+Afterwards we ``place" the fiber-collided galaxy a distance $d_i$ from the nearest neighbor galaxy assign $w_\mathrm{fc} = 1$ and reduce the $w_\mathrm{fc}$ of the the nearest-neighbor by 1.
 We refer to this method as ``$d_\mathrm{LOS}$-peak".
@@
 The $d_\mathrm{LOS}$-peak correction is the first part of our correction method we present in this paper.
-We test it by applying it to the mock catalogs and comparing the resulting power spectrums.
+Nonetheless, we test it by applying it to the mock catalogs and comparing the resulting power spectrums.
 For each of the mock catalogs (LasDamas, QPM, and Tiling Mock) we use the FKP power spectrum estimator from Section \ref{sec:pk_est} to compute the power spectrums of the mock catalogs without fiber collisions, with fiber collisions corrected using NN method, and with fiber collisions corrected using the $d_\mathrm{LOS}$-peak correction.
 We note that both the NN and the $d_\mathrm{LOS}$-peak correction methods alter the redshift distribution of our samples by a negligible amount $< 1\%$.
-Therefore, the synthetic random catalogs and the $\bar{n}(z)$ values do not need to be adjusted in the FKP $P(k)$ calculations in our case.
+Therefore, the synthetic random catalogs and the $\bar{n}(z)$ values do not need to be adjusted in the FKP $P(k)$ calculations.
 
 Since we are interested in how well fiber collision correction methods can reproduce the power spectrum without fiber collisions (i.e.
-``true" power spectrum, unsullied by systematic effects), in Figure \ref{fig:peakonly} we plot the ratio of the average power spectrum $\overline{P(k)}$ (averaged over the realizations) computed from fiber collided mock catalogs with corrections over the $\overline{P(k)}$ from the fiber collision-less original mock catalogs: $\overline{P_{\mathrm{corr}}(k)}/\overline{P_\mathrm{true}(k)}$.
+``true" power spectrum, unsullied by systematic effects), in Figure \ref{fig:peakonly} we plot the ratio of the average power spectrum $\overline{P(k)}$ (averaged over the realizations) computed from fiber-collided mock catalogs with corrections over the $\overline{P(k)}$ from the fiber collision-less original mock catalogs: $\overline{P_{\mathrm{corr}}(k)}/\overline{P_\mathrm{true}(k)}$.
 The ratio for the NN method is plotted in blue while the ratio for the $d_{\mathrm{LOS}}$-peak correction is plotted in orange.
@@
 The $P(k)$s obtained from these methods are dominated by the systematic effects of fiber collisions on small scales.
-Although the $d_\mathrm{LOS}$-peak method improves upon the NN method by statistical reconstructing the clustering of correlated fiber collided pairs within the peak of the $d_\mathrm{LOS}$ distribution, there is still room for improvement since the method does not yet properly account for chance alignments (uncorrelated fiber collision pairs).
+Although the $d_\mathrm{LOS}$-peak method improves upon the NN method by statistical reconstructing the clustering of correlated fiber-collided pairs within the peak of the $d_\mathrm{LOS}$ distribution, there is still room for improvement since the method does not yet properly account for chance alignments (uncorrelated fiber collision pairs).
 Unfortunately, an extension of the $d_\mathrm{LOS}$-peak method to the entire $d_\mathrm{LOS}$ distribution range is not feasible because such a correction results in an overall reduction of the $P(k)$.
-This is caused by the statistical sampling of the $d_\mathrm{LOS}$, which would inevitably displace some fiber collided pairs that are actually correlated pairs as chance alignments and the other way around.
-Therefore, in the following section we provide more robust correction method to account for the chance alignment fiber collided pairs.
+This is caused by the statistical sampling of the $d_\mathrm{LOS}$, which would inevitably displace some fiber-collided pairs that are actually correlated pairs as chance alignments and the other way around.
+Therefore, in the following section we provide more robust correction method to account for the chance alignment fiber-collided pairs.
 
@@
 In this section we introduce the other part of our fiber collision correction method that involve the shot-noise correction term of the FKP power spectrum estimator.
-By modifying the shot noise term of the FKP estimator to account for fiber collisions, we present a more robust correction method that accounts for the chance aligned fiber collided pairs.
+By modifying the shot noise term of the FKP estimator to account for fiber collisions, we present a more robust correction method that accounts for the chance aligned fiber-collided pairs.
 
@@
 In practice, the integrals in Equation \ref{eq:fkp_sn_int} can be written in terms of discrete sums over the random catalog.
-The spatial integral $\int d^3r \; \bar{n}({\bf r}) ...$ can be computed as the discrete sum $\alpha \sum_{\mathrm{ran}}...$.
+The spacial integral $\int d^3r \; \bar{n}({\bf r}) ...$ can be computed as the discrete sum $\alpha \sum_{\mathrm{ran}}...$.
 With this conversion,
@@
 \ref{eq:ourshot} is equivalent to the shot-noise contribution from ``false pairs" in \cite{Gil-Marin:2014aa}.
-%In \cite{Gil-Marin:2014aa}, they justify the use of the two separate shot-noise terms with the argument that, if the fiber collided pairs are true pairs it would not modify %insert reason 
+%In \cite{Gil-Marin:2014aa}, they justify the use of the two separate shot-noise terms with the argument that, if the fiber-collided pairs are true pairs it would not modify %insert reason 
 %While the $P(k)$ using the \cite{Gil-Marin:2014aa} shot-noise term does in fact correct for fiber collisions significantly (below), since the parameter is determined in mock catalogs, the value cannot be validated in the actual BOSS data .
 
-In order to compare the different $P_\mathrm{shot}$ derivations, we apply each of them ($P^\mathrm{FKP}_\mathrm{shot}$, $P^\mathrm{Hahn+}_\mathrm{shot}$, $P^\mathrm{B2014}_\mathrm{shot}$ and $P^\mathrm{GM2014}_\mathrm{shot}$) to the fiber collided mock catalogs with nearest-neighbor weights.
+In order to compare the different $P_\mathrm{shot}$ derivations, we apply each of them ($P^\mathrm{FKP}_\mathrm{shot}$, $P^\mathrm{Hahn+}_\mathrm{shot}$, $P^\mathrm{B2014}_\mathrm{shot}$ and $P^\mathrm{GM2014}_\mathrm{shot}$) to the fiber-collided mock catalogs with nearest-neighbor weights.
 To clarify, $P^\mathrm{FKP}_\mathrm{shot}$, $P^\mathrm{Hahn+}_\mathrm{shot}$, $P^\mathrm{B2014}_\mathrm{shot}$ and $P^\mathrm{GM2014}_\mathrm{shot}$ are calculated using Eq.
@@
 The shot-noise correction term we present in Eq.
-\ref{eq:ourshot} should only correct for the shot-noise contribution to the power spectrum from chance alignment fiber collided pairs - not from correlated pairs.
-Because we apply the shot-noise correction to all fiber collided pairs indiscriminately in Figure \ref{fig:shotnoise}, the shot-noise correction term over-subtracts the power spectrum as we find in Figure \ref{fig:shotnoise}.
+\ref{eq:ourshot} should only correct for the shot-noise contribution to the power spectrum from chance alignment fiber-collided pairs - not from correlated pairs.
+Because we apply the shot-noise correction to all fiber-collided pairs indiscriminately in Figure \ref{fig:shotnoise}, the shot-noise correction term over-subtracts the power spectrum as we find in Figure \ref{fig:shotnoise}.
 In the following section we present our fiber collision correction method, that combines the $d_\mathrm{LOS}$-peak correction of Section \ref{sec:dlos} and Eq.
@@
 \subsection{fiber collision Correction Method} \label{sec:apply}
-In Section \ref{sec:dlos} we derive a method to better statistically reconstruct the clustering of correlated fiber collided pairs using using the peak of the $d_\mathrm{LOS}$ distribution.
+In Section \ref{sec:dlos} we derive a method to better statistically reconstruct the clustering of correlated fiber-collided pairs using using the peak of the $d_\mathrm{LOS}$ distribution.
 Then in Section \ref{sec:shotnoise} we presented our formulation of the shot-noise correction term, which accounts for the added discreteness from chance aligned fiber collision pairs.
@@
 
-We begin once again with the fiber collided mock catalogs with the nearest-neighbor weights that accurately imitate the effects of fiber collision on the actual observed BOSS data.
-Then as described in Section \ref{sec:dlos}, we calculate the $d_\mathrm{LOS}$ distribution of all fiber collided pairs in each mock catalog.
-From the $d_\mathrm{LOS}$ distribution, we compute the fraction of fiber collided pairs within the peak of the distribution ($f_\mathrm{peak}$; Section \ref{sec:dlos}).
-We then select $f_\mathrm{peak}$ of the fiber collided pairs and designate them as correlated pairs that lie within the peak of the $d_\mathrm{LOS}$ distribution.
-We refer to these fiber collided pairs as ``peak-assigned" pairs.
+We begin once again with the fiber-collided mock catalogs with the nearest-neighbor weights that accurately imitate the effects of fiber collision on the actual observed BOSS data.
+Then as described in Section \ref{sec:dlos}, we calculate the $d_\mathrm{LOS}$ distribution of all fiber-collided pairs in each mock catalog.
+From the $d_\mathrm{LOS}$ distribution, we compute the fraction of fiber-collided pairs within the peak of the distribution ($f_\mathrm{peak}$; Section \ref{sec:dlos}).
+We then select $f_\mathrm{peak}$ of the fiber-collided pairs and designate them as correlated pairs that lie within the peak of the $d_\mathrm{LOS}$ distribution.
+We refer to these fiber-collided pairs as ``peak-assigned" pairs.
 
@@
 
-We keep the nearest-neighbor fiber collision weights imposed in the beginning for the remaining fiber collided pairs that are not ``peak-assigned" ($1-f_\mathrm{peak}$ of the fiber collided pairs).
-The resulting mock catalog has $f_\mathrm{peak}$ fewer galaxies with $w_\mathrm{cp} > 1$ compared to the fiber collided mock catalogs with nearest-neighbor weights that we started from; however, the total statistical weight ($\sum_\mathrm{gal} w_\mathrm{tot}$) of the mock catalog is conserved.
+We keep the nearest-neighbor fiber collision weights imposed in the beginning for the remaining fiber-collided pairs that are not ``peak-assigned" ($1-f_\mathrm{peak}$ of the fiber-collided pairs).
+The resulting mock catalog has $f_\mathrm{peak}$ fewer galaxies with $w_\mathrm{cp} > 1$ compared to the fiber-collided mock catalogs with nearest-neighbor weights that we started from; however, the total statistical weight ($\sum_\mathrm{gal} w_\mathrm{tot}$) of the mock catalog is conserved.
 
@@
 Using simulated mock catalogs for SDSS data with realistically imposed fiber collisions, we quantify the systematic effects of fiber collisions on galaxy clustering measurements - in particular the power spectrum.
-Although fiber collisions have little significant effect on the power spectrum at large scales, their effect quickly overtakes the sample variance at scales smaller than $k > 0.1 \;h/\mathrm{Mpc}$.
-At the smallest scales that we explore in this paper, $k \sim 0.3  \;h/\mathrm{Mpc}$, fiber collisions have over a $10 \%$ effect on the power spectrum.
+Although fiber collisions have little significant effect on the power spectrum at large scales, its effect quickly overtakes the sample variance at scales smaller than $k > 0.1 \;h/\mathrm{Mpc}$.
+At the smallest scales that we explore in this paper, $k \sim 0.3$, fiber collisions have over a $10 \%$ effect on the power spectrum.
 Consequently at these small scales, measurements of the power spectrum is dominated by the uncertainties from systematic effects of fiber collisions.
 
-Fortunately, using the fiber collided mock catalogs used in this paper, we are able to model the distribution of the line-of-sight displacement between fiber collided pairs.
-With this model, we are able to statistically reconstruct the clustering fiber collided galaxies that reside in the same halo.
-Combining this correction with a modification of the shot-noise term in the power spectrum estimator to properly account for the discreteness added by the nearest-neighbor weights of chance aligned fiber collided pairs, we devise a new fiber collision correction method that is able to reconstruct the true power spectrum from fiber collided data even to $k \sim 0.3 \;h/\mathrm{Mpc}$.
+Fortunately, through the fiber-collided mock catalogs used in this paper, we are able to model the distribution of the line-of-sight displacement between fiber-collided pairs.
+Using this model, we are able to statistically reconstruct the clustering fiber-collided galaxies that reside in the same halo.
+Combining this correction with a modification of the shot-noise term in the power spectrum estimator to properly account for the discreteness added by the nearest-neighbor weights of chance aligned fiber-collided pairs, we devise a new fiber collision correction method that is able to reconstruct the true power spectrum from fiber-collided data even to $k \sim 0.3 \;h/\mathrm{Mpc}$.
 Throughout the entire $k$ range explored in our analysis, our correction method reconstructs $P_\mathrm{true}(k)$ safely within the sample variance.
@@
 Furthermore, while the correction method of \cite{Gil-Marin:2014aa} is comparable our correction method, the parameter $x_\mathrm{PS}$ used in the method is calculated solely through a weighted galaxy mock catalog.
-As an added advantage, our correction method can also be callibrated by the observed data rather than only through the mock catalogs.
+As an added advantage, our correction method can also be validated by the observed data rather than only through the mock catalogs.
 Therefore our correction method does not depend on the accuracy of the mock catalogs, thereby making it's application to observations further reliable.

### 2015-12-16 fc_paper/fc_paper.tex
restructuring the new paper

@@
 We present two methods to account for fiber collisions in the power spectrum.
-The first method statistically reconstructs the clustering of fiber collided galaxy pairs by modeling the distribution of the line-of-sight displacement between them using cases where both redshifts are obtained.
+The first method statistically reconstructs the clustering of fiber collided galaxy pairs by modeling the distribution of the line-of-sight displacements between them using cases where both redshifts are obtained.
 The method properly accounts for fiber collisions in the shot-noise correction term of the power spectrum estimator.
-For the monopole, this method reproduces the true power spectrum monopole for the mock catalogs with residuals of $< 1\%$ at $k \sim 0.3 \; h/\mathrm{Mpc}$ and $< 10\%$ at $k \sim 0.8 \; h/\mathrm{Mpc}$ -- a significant improvement from existing correction methods, especially at small scales ($k > 0.1\; h/\mathrm{Mpc}$).
+For the monopole, this method reproduces the true power spectrum for the mock catalogs with residuals of $< 1\%$ at $k \sim 0.3 \; h/\mathrm{Mpc}$ and $< 10\%$ at $k \sim 0.8 \; h/\mathrm{Mpc}$ -- a significant improvement from existing correction methods, especially at small scales ($k > 0.1\; h/\mathrm{Mpc}$).
 In our second method, we model the effect of fiber collisions on the true galaxy power spectrum by Fourier transforming an analytical estimate of the effect of fiber collisions on the two-point correlation function.
@@
 Our comparisons to other correction methods demonstrate that our method most accurately reconstructs the true power spectrum from fiber-collided galaxy data especially at small scales ($k > 0.1\; h/\mathrm{Mpc}$), with the added advantage that our method can be validated and calibrated in observed data.
+
 \end{abstract}
@@
 In Section \ref{sec:catalog}, we briefly describe the simulated mock catalogs with realistically applied fiber collisions and the power spectrum estimator used throughout the paper.
-We demonstrate the effects of fiber collisions on power spectrum measurements and compare correction methods in the literature in Section \ref{sec:fc_corr}.
-Afterwards we present our two methods of accounting for fiber collisions and then in Section \ref{sec:results} apply the methods to the mock catalogs.
+We demonstrate the effects of fiber collisions on power spectrum measurements and how the nearest neighbor method does not adequately account for fiber collisions at small scales in Section \ref{sec:fc_pk}.
+We then present our two methods of accounting for fiber collisions in Section \ref{sec:dlospeak} and Section \ref{sec:fourier} respectively.
+We then apply our methods to the mock catalogs and compare correction methods in the literature in Section \ref{sec:results}.
 Finally in Section \ref{sec:summary} we summarize and discuss our results.
@@
 \def \tmcolor{green}
+
+% FIGURE %%%%%%
 \begin{figure}
 \begin{center}
-\includegraphics[scale=0.45]{fcpaper_z_dist.png} \label{fig:zdist}
+\includegraphics[scale=0.35]{mock_catalog_z_dist} \label{fig:zdist}
 \caption{Normalized galaxy redshift distribution for LasDamas (\ldgcolor), QPM (\qpmcolor), and Tiling Mock (\tmcolor) mock catalogs.
@@
 
+% P(k) plot for mocks and BOSS ---------------------------------------------------------------------------------------------------------------------------------------------------------------------
+\begin{figure*}
+\begin{center}
+\includegraphics[scale=0.5]{mock_catalog_Plk.png} 
+\caption{Average power spectrum monopole $\overline{P_0(k)}$ and quadrupole $|\overline{P_2(k)}|$ for BOSS DR12 (black) and the mock catalogs LasDamas (blue), QPM (orange), Nseries (red), and Tiling Mock (green), listed in Section \ref{sec:catalog} using the estimator from \cite{Scoccimarro:2015aa}.
+The width of the $P_{l}(k)$ for LasDamas and QPM represent the sample variance ($\Delta P_{l}(k)$) calculated from the realizations of the mock catalogs.
+For $l = 2$, we plot the absolute value of $P_2(k)$ because $P_2(k) < 0$ for $k \gtrsim 0.35\;h/\mathrm{Mpc}$.
+We emphasize that fiber collisions were not applied to the mock catalogs for the measurements above.
+Meanwhile, galaxy weights (Equation \ref{eq:weight}) are applied to the BOSS DR12 $P_l(k)$ measurements.
+We remind readers that the LasDamas mock catalog has an overall greater $\overline{P(k)}$ due to the fact that the catalog spans the SDSS LRG sample redshift range instead of the BOSS redshift range of the other mock catalogs.} \label{fig:mockpk}
+\end{center}
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{Power Spectrum Estimator} \label{sec:pk_est}
+
 In this paper, we focus on the effects of fiber collisions on the galaxy power spectrum out of the other clustering measurements, more specifically the monopole and quadrupole of the power spectrum.
@@
 
-% P(k) plot for mocks and BOSS
-\begin{figure}
-\begin{center}
-\includegraphics[scale=0.5]{fcpaper_pk_comp.png} 
-\caption{Average power spectrum monopole $\overline{P_0(k)}$ and quadrupole $\overline{P_2(k)}$ for BOSS DR12 (black) and the mock catalogs LasDamas (blue), QPM (orange), and Tiling Mock (green), listed in Section \ref{sec:catalog} using the estimator from \cite{Scoccimarro:2015aa}.
-The width of the $P_{l}(k)$ for LasDamas and QPM represent the sample variance ($\Delta P_{l}(k)$) calculated from the realizations of the mock catalogs.
-We emphasize that fiber collisions were not applied to the mock catalogs for the measurements above.
-Meanwhile, galaxy weights (Equation \ref{eq:weight}) are applied to the BOSS DR12 $P_l(k)$ measurements.
-We remind readers that the LasDamas mock catalog has an overall greater $\overline{P(k)}$ due to the fact that the catalog spans the SDSS LRG sample redshift range instead of the BOSS redshift range of the other mock catalogs.} \label{fig:mockpk}
-\end{center}
-\end{figure}
-
 In Figure \ref{fig:mockpk}, we plot the $P_0(k)$ and $P_2(k)$ calculated using Eq.
@@
 Each galaxy has a statistical weight determined by,
+
 \begin{equation} \label{eq:weight}
-w_\mathrm{tot} = w_\mathrm{sys} (w_\mathrm{rf} + w_\mathrm{fc} -1), 
+w_{j, \mathrm{tot}} = w_{j, \mathrm{sys}} (w_{j, \mathrm{rf}} + w_{j, \mathrm{fc}} -1), 
 \end{equation} 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% fiber collision Correction Method
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Accounting for Fiber Collisions} \label{sec:fc_corr}
+%Although the nearest-neighbor method provides a reasonable estimate at large scales, in Section \ref{sec:fc_pk} we demonstrate that at small scales its effects on the power spectrum are significant and dominate sample variance.
+In order to correct for this effect, in Section \ref{sec:dlospeak} we present an improved method to account for correlated fiber collided galaxies that uses the line-of-sight displacement between fiber collided pairs (Section \ref{sec:dlos}) and a shot-noise correction term in the power spectrum estimator that properly takes into account fiber collisions (Section \ref{sec:shotnoise}).
+In Section \ref{sec:fourier}, we present a complementary method that models the effect of fiber collisions on the power spectrum using an analytic estimate of the effect of fiber collisions on the 2PCF.
+\begin{figure*}
+\begin{center}
+\includegraphics[scale=0.55]{fcpaper_pk_peakonly_comp.png} 
+\caption{The ratio of $\overline{P_\mathrm{corr} (k)}$ using the nearest-neighbor (NN) correction (blue) and $d_\mathrm{LOS}$-peak correction (orange) over the true $\overline{P(k)}$ for LasDamas (left panel), QPM (middle panel), and Tiling Mock (right panel) catalogs.
+The NN correction and $d_\mathrm{LOS}$-peak correction methods are described in Section \ref{sec:dlos}.
+We also plot the ratio of the sample variance to the true $\overline{P_\mathrm{true}(k)}$, $\Delta P_\mathrm{true}(k) / \overline{P_\mathrm{true}(k)}$ (black; dashed) for comparison.
+Incorporating the $d_{\mathrm{LOS}}$ distribution significantly improves the correction of fiber collisions for $k > 0.1 \; h/\mathrm{Mpc}$; however, neither method is able to constrain the systematic effects of fiber collisions significantly below the sample variance at $k > 0.2 \; h/\mathrm{Mpc}$.}\label{fig:fc_pk}
+\end{center}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Effects of Fiber Collision on the Power Spectrum 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Nearest Angular Neighbor Method} \label{sec:fc_pk}
+A common approach in accounting for fiber collisions in clustering measurements has been to use the nearest angular neighbor method (\citealt{Zehavi:2002aa, Berlind:2006aa, Anderson:2012aa}), hereafter NN method.
+For galaxies without resolved spectroscopic redshifts due to fiber collisions, the entire statistical weight of the galaxy is assigned to its nearest angular neighbor.
+This method effectively assumes that all galaxies within the angular fiber collision scale ($< 62 \arcsec$ for BOSS) are correlated with one another.
+In other words, the method assumes that galaxies within the fiber collision angular scale reside in the same halo so displacing one of the galaxies and placing it on top of the other does not significantly alter the clustering statistics.
+One consequence of this method however is that galaxies within the angular fiber collision scale purely by coincidence (hereafter referred to as ``chance alignments") are incorrectly assumed to be gravitationally correlated, so when their statistical weight is added to its nearest angular neighbor, they are in fact displaced significantly from their true position.
+For BOSS, the nearest angular neighbor method can displace galaxies by up to $500 \;\mathrm{Mpc}$.
+Furthermore even for fiber-collided galaxies that reside in the same group or cluster, up-weighting the nearest neighbor ignores halo-scale line-of-sight displacements.
+
+% Not only quantify the effect of fiber collisions, but the break down of the NN method for P(k) at high k. 
+To precisely quantify the effect of fiber collisions on the power spectrum, in Figure \ref{fig:fc_pk}, we compare $P_0(k)$ and $P_2(k)$ measured using the NN method for mock catalogs with fiber collisions to the $P_0(k)$ and $P_2(k)$ measurements for mock catalogs without fiber collisions.
+The $P_0(k)$ measurements are made using Eq.
+\ref{eq:roman_p0k} with a standard FKP shot noise ($N_0^{FKP}$) rather than $N_0$ from Eq.
+\ref{eq:roman_shotnoise}, which is effectively just the standard power spectrum estimator from \cite{Feldman:1994aa}.
+$P_2(k)$ measurements are made using Eq.
+\ref{eq:roman_p2k}.
+\begin{itemize}
+	\item Description of Figure \ref{fig:fc_pk} focusing on the scales where the NN method breaks down and quantifying the residuals. 
+\end{itemize}
+
+In order to correct for this effect, in following section we present an improved method to account for correlated fiber collided galaxies that uses the line-of-sight displacement between fiber collided pairs (Section \ref{sec:dlos}) and a corrected shot-noise correction term in the power spectrum estimator that properly takes into account fiber collisions (Section \ref{sec:shotnoise}).
+
 \begin{figure*}
@@
 \end{figure*}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% fiber collision Correction Method
+% DLOSPEAK METHOD 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{fiber collision Correction Method} \label{sec:fc_corr}
-As mentioned above, a common approach in accounting for fiber collisions in clustering measurements has been to use the nearest angular neighbor method (\citealt{Zehavi:2002aa, Berlind:2006aa, Anderson:2012aa}).
-For galaxies without resolved spectroscopic redshifts due to fiber collisions, the entire statistical weight of the galaxy is assigned to its nearest angular neighbor.
-This method assumes that all galaxies within the angular fiber collision scale ($< 62 "$ for BOSS) are correlated with one another.
-In other words, the method assumes that galaxies within the fiber collision angular scale reside in the same halo so displacing one and placing it on top of the other does not significantly alter the clustering statistics.
-One consequence of this method however is that galaxies within the angular fiber collision scale purely by coincidence (hereafter referred to as ``chance alignments") are incorrectly assumed to be gravitationally correlated, so when their statistical weight is added to its nearest angular neighbor, they are in fact displaced significantly from its true position.
-For BOSS, the nearest angular neighbor method can displace galaxies by up to $500 \;\mathrm{Mpc}$.
-Furthermore even for fiber-collided galaxies that reside in the same group or cluster, up-weighting the nearest neighbor ignores halo-scale line-of-sight displacements, which as we present in Section \ref{sec:dlos}, are significant.
-
-Although the nearest-neighbor method provides a reasonable estimate at large scales, in Section \ref{sec:dlos} we demonstrate that at small scales its effects on the power spectrum are significant and dominate sample variance.
-We present an improved method to account for correlated fiber-collided galaxies using the line-of-sight displacement between fiber-collided pairs.
-Then in Section \ref{sec:shotnoise}, we present modifications to the FKP power spectrum estimator in order to properly account for fiber collisions through the shot-noise correction term in the estimator.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% LOS DISPLACEMENT
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Line-of-Sight Displacement of Fiber-collided Pairs} \label{sec:dlos}
-It is impossible to determine from observed galaxy data whether fiber-collided galaxies without resolved spectroscopic redshift are correlated or chance alignments.
-Fortunately, using the fiber-collided pairs with resolved redshifts (mainly in the overlapping regions mentioned in Section \ref{sec:catalog}), it is possible to model the line-of-sight displacement of the fiber-collided pairs and the fraction of galaxy pairs that are corrected and uncorrelated.
+\subsection{First Method} \label{sec:dlospeak}
+% LOS DISPLACEMENT %%%%
+\subsubsection{Line-of-Sight Displacement of Fiber Collided Pairs} \label{sec:dlos}
+It is impossible to determine definitely from observed galaxy data whether individual fiber collided galaxies without resolved spectroscopic redshift are correlated or chance alignments.
+Fortunately, using the fiber collided pairs with resolved redshifts (mainly in the overlapping regions mentioned in Section \ref{sec:catalog}), it is possible to model the line-of-sight displacement of the fiber collided pairs and measure the fraction of pairs that are corrected and uncorrelated.
 
 For simulated mock catalogs, described in Section \ref{sec:catalog}, modeling the fiber-collided galaxy pairs is a much more direct task since fiber collisions are post-processed after the simulated galaxy positions are generated.
-All redshift values are provided for all galaxies regardless of angular proximity and the fiber collisions imposed on the mock catalogs are represented through the galaxies' ``fiber collision weights" ($w_\mathrm{fc}$).
-So for a fiber-collided pair, one galaxy (``the nearest neighbor") will have the fiber collision weight of both galaxies, while the other has $w_\mathrm{fc} = 0$.
-Nonetheless, with redshifts of both fiber-collided pair galaxies in mock catalogs, we can model the correlated and uncorrelated fiber-collided pairs in order to better correct for fiber collisions.
+Redshift values are provided for all galaxies regardless of angular proximity and the fiber collisions imposed on the mock catalogs are represented through the galaxies' ``fiber collision weights" ($w_\mathrm{fc}$).
+So in a situation where only two galaxies are within the fiber collision angular scale, one galaxy (``the nearest neighbor") will have the fiber collision weight of both galaxies ($w_{\mathrm{fc}} = 2$), while the other has $w_\mathrm{fc} = 0$.
+Nonetheless, since we actually have redshifts of both fiber-collided pair galaxies in mock catalogs, we can model the correlated and uncorrelated fiber-collided pairs in order to better understand the effects of fiber collisions.
 
-To determine whether or not fiber-collided pairs are correlated, we examine the comoving line-of-sight displacement ($d_{\mathrm{LOS}}$) of fiber-collided galaxy pairs.
+To determine whether or not fiber collided pairs are correlated, we examine the comoving line-of-sight displacement ($d_{\mathrm{LOS}}$) of fiber collided galaxy pairs.
 We calculate the $d_{\mathrm{LOS}}$ by taking the difference of the line-of-sight comoving distance from the resolved redshifts:
@@
 \end{equation}
-$D_{\mathrm{C}}(z)$ is the line-of-sight comoving distance at redshift $z$ (\citealt{Hogg:1999aa}). $z_1$ and $z_2$ represent the resolved redshifts of the galaxies in the fiber-collided pair.
+$D_{\mathrm{C}}(z)$ is the line-of-sight comoving distance at redshift $z$ (\citealt{Hogg:1999aa}). $z_1$ and $z_2$ represent the resolved redshifts of the two galaxies in the fiber collided pair.
 
-After calculating the $d_{\mathrm{LOS}}$ for every fiber-collided pairs, in Figure \ref{fig:d_los} we present the distribution of $d_{\mathrm{LOS}}$ for LasDamas (\ldgcolor), QPM (\qpmcolor), Tiling Mock (\tmcolor), and BOSS DR12 (\cmasscolor).
-All of the $d_{\mathrm{LOS}}$ distributions contain two components: a peak contained within the range $-20\;\mathrm{Mpc} < d_{\mathrm{LOS}} < 20\;\mathrm{Mpc}$ and a flat component (hereafter "tail" component) outside the peak that extends to $d_{\mathrm{LOS}} \sim \pm 500 \;\mathrm{Mpc}$ (entire range of the distribution not displayed in Figure \ref{fig:d_los}).
-For the BOSS data, since we cannot compute the $d_\mathrm{LOS}$ for fiber-collided pairs without resolved spectra, the $d_\mathrm{LOS}$ distribution only reflects the $d_\mathrm{LOS}$ from fiber-colldied pairs {\em with} resolved spectroscopic redshifts, mostly from tile overlapping regions of the BOSS survey.
+After calculating the $d_{\mathrm{LOS}}$ for every fiber collided pairs, in Figure \ref{fig:d_los} we present the distribution of $d_{\mathrm{LOS}}$ for LasDamas (\ldgcolor), QPM (\qpmcolor), Tiling Mock (\tmcolor), and BOSS DR12 (\cmasscolor).
+All of the $d_{\mathrm{LOS}}$ distributions contain two components: a peak roughly contained within the range $-20\;\mathrm{Mpc} < d_{\mathrm{LOS}} < 20\;\mathrm{Mpc}$ and a flat component (hereafter "tail" component) outside the peak that extends to $d_{\mathrm{LOS}} \sim \pm 500 \;\mathrm{Mpc}$ (entire range of the distribution not displayed in Figure \ref{fig:d_los}).
+For the BOSS data, since we cannot compute the $d_\mathrm{LOS}$ for fiber collided pairs without spectra, the $d_\mathrm{LOS}$ distribution only reflects the $d_\mathrm{LOS}$ from fiber collided pairs {\em with} resolved spectroscopic redshifts, mostly from tile overlapping regions of the BOSS survey.
 
@@
 These galaxies in over-dense regions cause the peak in the $d_{\mathrm{LOS}}$ distribution.
-While the ``tail" component is composed of chance alignment galaxy pairs that are arbitrarily in close angular proximity even when they are not correlated.
+The ``tail" component is composed of chance aligned galaxy pairs that happen to be in close angular proximity.
 
@@
 We list the values of $\sigma$ obtained for the mock catalogs in Table \ref{tab:mpfit}.
-Both Table \ref{tab:mpfit} and Figure \ref{fig:d_los} illustrate that the $d_{\mathrm{LOS}}$ distributions for the mock catalogs closely trace the distribution of the BOSS DR12, which further goes to support the use of mock catalogs in our investigation of fiber collisions.
+Both Table \ref{tab:mpfit} and Figure \ref{fig:d_los} illustrate that the $d_{\mathrm{LOS}}$ distributions for the mock catalogs closely trace the distribution of the BOSS DR12, which further goes to support the use of mock catalogs in our investigation.
 
@@
 %    \bigskip 
-{\bf Notes}: Best-fit parameter $\sigma$ and peak fraction $f_{\mathrm{peak}}$ for the $d_{\mathrm{LOS}}$ distributions in Figure \ref{fig:d_los}. 
+{\bf Notes}: Best-fit parameter $\sigma$ (Eq. \ref{eq:peak}) and peak fraction $f_{\mathrm{peak}}$ (Eq. \ref{eq:fpeak}) for the $d_{\mathrm{LOS}}$ distributions in Figure \ref{fig:d_los}. 
 \end{table}
 
-Using the best-fit to the peak of the $d_{\mathrm{LOS}}$ distribution, we estimate the fraction of fiber-collided pairs that are within the peak: 
-\begin{equation}
+Using the best-fit to the peak of the $d_{\mathrm{LOS}}$ distribution, we estimate the fraction of fiber collided pairs that are within the peak as
+\begin{equation} \label{eq:fpeak}
 f_{\mathrm{peak}} = \frac{\sum\limits_{\mathrm{peak}} p(d_{\mathrm{LOS}})}{N_{\mathrm{pairs}}}, 
 \end{equation}
-where $N_{\mathrm{pairs}}$ is the total number of fiber-collided pairs.
-As mentioned above, this portion of fiber-collided pairs are galaxy pairs that are correlated.
+where $N_{\mathrm{pairs}}$ is the total number of fiber collided pairs.
+As mentioned above, this portion of fiber collided pairs are galaxy pairs that are correlated.
 We list the $f_{\mathrm{peak}}$ values for each of the data catalogs in Table \ref{tab:mpfit}.
@@
 
-For the most commonly used nearest angular neighbor method (hereafter NN method) to be entirely correct, the $d_{\mathrm{LOS}}$ distribution in Figure \ref{fig:d_los} would have to be a delta function, which is clearly not the case.
+For the NN method to be entirely correct, the $d_{\mathrm{LOS}}$ distribution in Figure \ref{fig:d_los} would have to be a delta function, which is clearly not the case.
 By simply incorporating the peak of the $d_{\mathrm{LOS}}$ distribution, we are able to significantly improve clustering statistics on small scales.
-Rather than placing the fiber-collided galaxy on top of its nearest angular neighbor as NN correction does, placing the fiber-collided galaxy at a displacement sampled from the $d_{\mathrm{LOS}}$ distribution away from its nearest neighbor better accounts for the small scale in clustering measurements.
+Rather than placing the fiber collided galaxy on top of its nearest angular neighbor as the NN correction does, placing the fiber collided galaxy at a displacement, sampled from the $d_{\mathrm{LOS}}$ distribution, apart from its nearest neighbor better accounts for the small scale in clustering measurements.
+
 On mock catalogs, we test this by first applying the NN to the mock catalogs.
-We then sample a displacement $d_i$ from $p(d_\mathrm{LOS})$ (Equation \ref{eq:peak}) for each fiber-collided pair.
-Afterwards we ``place" the fiber-collided galaxy a distance $d_i$ from the nearest neighbor galaxy assign $w_\mathrm{fc} = 1$ and reduce the $w_\mathrm{fc}$ of the the nearest-neighbor by 1.
+We then sample a displacement $d_i$ from $p(d_\mathrm{LOS})$ (Equation \ref{eq:peak}) for each fiber collided pair.
+Afterwards we ``place" the fiber collided galaxy a distance $d_i$ from the nearest neighbor galaxy assign $w_\mathrm{fc} = 1$ and reduce the $w_\mathrm{fc}$ of the the nearest-neighbor by 1.
 We refer to this method as ``$d_\mathrm{LOS}$-peak".
 
-\begin{figure*}
-\begin{center}
-\includegraphics[scale=0.55]{fcpaper_pk_peakonly_comp.png} 
-\caption{The ratio of $\overline{P_\mathrm{corr} (k)}$ using the nearest-neighbor (NN) correction (blue) and $d_\mathrm{LOS}$-peak correction (orange) over the true $\overline{P(k)}$ for LasDamas (left panel), QPM (middle panel), and Tiling Mock (right panel) catalogs.
+%\begin{figure*}
+%\begin{center}
+%\includegraphics[scale=0.55]{fcpaper_pk_peakonly_comp.png} 
+%\caption{The ratio of $\overline{P_\mathrm{corr} (k)}$ using the nearest-neighbor (NN) correction (blue) and $d_\mathrm{LOS}$-peak correction (orange) over the true $\overline{P(k)}$ for LasDamas (left panel), QPM (middle panel), and Tiling Mock (right panel) catalogs.
 The NN correction and $d_\mathrm{LOS}$-peak correction methods are described in Section \ref{sec:dlos}.
@@
 Incorporating the $d_{\mathrm{LOS}}$ distribution significantly improves the correction of fiber collisions for $k > 0.1 \; h/\mathrm{Mpc}$; however, neither method is able to constrain the systematic effects of fiber collisions significantly below the sample variance at $k > 0.2 \; h/\mathrm{Mpc}$.}\label{fig:peakonly}
-\end{center}
-\end{figure*}
+%\end{center}
+%\end{figure*}
 
-The $d_\mathrm{LOS}$-peak correction is the first part of our correction method we present in this paper.
-Nonetheless, we test it by applying it to the mock catalogs and comparing the resulting power spectrums.
+%The $d_\mathrm{LOS}$-peak correction is the first part of our correction method we present in this paper.
+We test it by applying it to the mock catalogs and comparing the resulting power spectrums.
 For each of the mock catalogs (LasDamas, QPM, and Tiling Mock) we use the FKP power spectrum estimator from Section \ref{sec:pk_est} to compute the power spectrums of the mock catalogs without fiber collisions, with fiber collisions corrected using NN method, and with fiber collisions corrected using the $d_\mathrm{LOS}$-peak correction.
 We note that both the NN and the $d_\mathrm{LOS}$-peak correction methods alter the redshift distribution of our samples by a negligible amount $< 1\%$.
-Therefore, the synthetic random catalogs and the $\bar{n}(z)$ values do not need to be adjusted in the FKP $P(k)$ calculations.
+Therefore, the synthetic random catalogs and the $\bar{n}(z)$ values do not need to be adjusted in the FKP $P(k)$ calculations in our case.
 
-Since we are interested in how well fiber collision correction methods can reproduce the power spectrum without fiber collisions (i.e.
-``true" power spectrum, unsullied by systematic effects), in Figure \ref{fig:peakonly} we plot the ratio of the average power spectrum $\overline{P(k)}$ (averaged over the realizations) computed from fiber-collided mock catalogs with corrections over the $\overline{P(k)}$ from the fiber collision-less original mock catalogs: $\overline{P_{\mathrm{corr}}(k)}/\overline{P_\mathrm{true}(k)}$.
+%Since we are interested in how well fiber collision correction methods can reproduce the power spectrum without fiber collisions (i.e.
+``true" power spectrum, unsullied by systematic effects), in Figure \ref{fig:peakonly} we plot the ratio of the average power spectrum $\overline{P(k)}$ (averaged over the realizations) computed from fiber collided mock catalogs with corrections over the $\overline{P(k)}$ from the fiber collision-less original mock catalogs: $\overline{P_{\mathrm{corr}}(k)}/\overline{P_\mathrm{true}(k)}$.
 The ratio for the NN method is plotted in blue while the ratio for the $d_{\mathrm{LOS}}$-peak correction is plotted in orange.
@@
 
-When we compare the NN method and the $d_\mathrm{LOS}$-peak correction to the sample variance ratio ($\Delta P_\mathrm{true}(k) / \overline{P_\mathrm{true}(k)}$), we find that neither of these methods sufficiently correct for fiber collisions at $k > 0.1\; h/\mathrm{Mpc}$.
+%When we compare the NN method and the $d_\mathrm{LOS}$-peak correction to the sample variance ratio ($\Delta P_\mathrm{true}(k) / \overline{P_\mathrm{true}(k)}$), we find that neither of these methods sufficiently correct for fiber collisions at $k > 0.1\; h/\mathrm{Mpc}$.
 The $P(k)$s obtained from these methods are dominated by the systematic effects of fiber collisions on small scales.
-Although the $d_\mathrm{LOS}$-peak method improves upon the NN method by statistical reconstructing the clustering of correlated fiber-collided pairs within the peak of the $d_\mathrm{LOS}$ distribution, there is still room for improvement since the method does not yet properly account for chance alignments (uncorrelated fiber collision pairs).
+Although the $d_\mathrm{LOS}$-peak method improves upon the NN method by statistical reconstructing the clustering of correlated fiber collided pairs within the peak of the $d_\mathrm{LOS}$ distribution, there is still room for improvement since the method does not yet properly account for chance alignments (uncorrelated fiber collision pairs).
 Unfortunately, an extension of the $d_\mathrm{LOS}$-peak method to the entire $d_\mathrm{LOS}$ distribution range is not feasible because such a correction results in an overall reduction of the $P(k)$.
-This is caused by the statistical sampling of the $d_\mathrm{LOS}$, which would inevitably displace some fiber-collided pairs that are actually correlated pairs as chance alignments and the other way around.
-Therefore, in the following section we provide more robust correction method to account for the chance alignment fiber-collided pairs.
+This is caused by the statistical sampling of the $d_\mathrm{LOS}$, which would inevitably displace some fiber collided pairs that are actually correlated pairs as chance alignments and the other way around.
+Therefore, in the following section we provide more robust correction method to account for the chance alignment fiber collided pairs.
 
@@
 In this section we introduce the other part of our fiber collision correction method that involve the shot-noise correction term of the FKP power spectrum estimator.
-By modifying the shot noise term of the FKP estimator to account for fiber collisions, we present a more robust correction method that accounts for the chance aligned fiber-collided pairs.
+By modifying the shot noise term of the FKP estimator to account for fiber collisions, we present a more robust correction method that accounts for the chance aligned fiber collided pairs.
 
@@
 In practice, the integrals in Equation \ref{eq:fkp_sn_int} can be written in terms of discrete sums over the random catalog.
-The spacial integral $\int d^3r \; \bar{n}({\bf r}) ...$ can be computed as the discrete sum $\alpha \sum_{\mathrm{ran}}...$.
+The spatial integral $\int d^3r \; \bar{n}({\bf r}) ...$ can be computed as the discrete sum $\alpha \sum_{\mathrm{ran}}...$.
 With this conversion,
@@
 \ref{eq:ourshot} is equivalent to the shot-noise contribution from ``false pairs" in \cite{Gil-Marin:2014aa}.
-%In \cite{Gil-Marin:2014aa}, they justify the use of the two separate shot-noise terms with the argument that, if the fiber-collided pairs are true pairs it would not modify %insert reason 
+
+%In \cite{Gil-Marin:2014aa}, they justify the use of the two separate shot-noise terms with the argument that, if the fiber collided pairs are true pairs it would not modify %insert reason 
 %While the $P(k)$ using the \cite{Gil-Marin:2014aa} shot-noise term does in fact correct for fiber collisions significantly (below), since the parameter is determined in mock catalogs, the value cannot be validated in the actual BOSS data .
 
-In order to compare the different $P_\mathrm{shot}$ derivations, we apply each of them ($P^\mathrm{FKP}_\mathrm{shot}$, $P^\mathrm{Hahn+}_\mathrm{shot}$, $P^\mathrm{B2014}_\mathrm{shot}$ and $P^\mathrm{GM2014}_\mathrm{shot}$) to the fiber-collided mock catalogs with nearest-neighbor weights.
+In order to compare the different $P_\mathrm{shot}$ derivations, we apply each of them ($P^\mathrm{FKP}_\mathrm{shot}$, $P^\mathrm{Hahn+}_\mathrm{shot}$, $P^\mathrm{B2014}_\mathrm{shot}$ and $P^\mathrm{GM2014}_\mathrm{shot}$) to the fiber collided mock catalogs with nearest-neighbor weights.
 To clarify, $P^\mathrm{FKP}_\mathrm{shot}$, $P^\mathrm{Hahn+}_\mathrm{shot}$, $P^\mathrm{B2014}_\mathrm{shot}$ and $P^\mathrm{GM2014}_\mathrm{shot}$ are calculated using Eq.
@@
 The shot-noise correction term we present in Eq.
-\ref{eq:ourshot} should only correct for the shot-noise contribution to the power spectrum from chance alignment fiber-collided pairs - not from correlated pairs.
-Because we apply the shot-noise correction to all fiber-collided pairs indiscriminately in Figure \ref{fig:shotnoise}, the shot-noise correction term over-subtracts the power spectrum as we find in Figure \ref{fig:shotnoise}.
+\ref{eq:ourshot} should only correct for the shot-noise contribution to the power spectrum from chance alignment fiber collided pairs - not from correlated pairs.
+Because we apply the shot-noise correction to all fiber collided pairs indiscriminately in Figure \ref{fig:shotnoise}, the shot-noise correction term over-subtracts the power spectrum as we find in Figure \ref{fig:shotnoise}.
 In the following section we present our fiber collision correction method, that combines the $d_\mathrm{LOS}$-peak correction of Section \ref{sec:dlos} and Eq.
@@
 \subsection{fiber collision Correction Method} \label{sec:apply}
-In Section \ref{sec:dlos} we derive a method to better statistically reconstruct the clustering of correlated fiber-collided pairs using using the peak of the $d_\mathrm{LOS}$ distribution.
+In Section \ref{sec:dlos} we derive a method to better statistically reconstruct the clustering of correlated fiber collided pairs using using the peak of the $d_\mathrm{LOS}$ distribution.
 Then in Section \ref{sec:shotnoise} we presented our formulation of the shot-noise correction term, which accounts for the added discreteness from chance aligned fiber collision pairs.
@@
 
-We begin once again with the fiber-collided mock catalogs with the nearest-neighbor weights that accurately imitate the effects of fiber collision on the actual observed BOSS data.
-Then as described in Section \ref{sec:dlos}, we calculate the $d_\mathrm{LOS}$ distribution of all fiber-collided pairs in each mock catalog.
-From the $d_\mathrm{LOS}$ distribution, we compute the fraction of fiber-collided pairs within the peak of the distribution ($f_\mathrm{peak}$; Section \ref{sec:dlos}).
-We then select $f_\mathrm{peak}$ of the fiber-collided pairs and designate them as correlated pairs that lie within the peak of the $d_\mathrm{LOS}$ distribution.
-We refer to these fiber-collided pairs as ``peak-assigned" pairs.
+We begin once again with the fiber collided mock catalogs with the nearest-neighbor weights that accurately imitate the effects of fiber collision on the actual observed BOSS data.
+Then as described in Section \ref{sec:dlos}, we calculate the $d_\mathrm{LOS}$ distribution of all fiber collided pairs in each mock catalog.
+From the $d_\mathrm{LOS}$ distribution, we compute the fraction of fiber collided pairs within the peak of the distribution ($f_\mathrm{peak}$; Section \ref{sec:dlos}).
+We then select $f_\mathrm{peak}$ of the fiber collided pairs and designate them as correlated pairs that lie within the peak of the $d_\mathrm{LOS}$ distribution.
+We refer to these fiber collided pairs as ``peak-assigned" pairs.
 
@@
 
-We keep the nearest-neighbor fiber collision weights imposed in the beginning for the remaining fiber-collided pairs that are not ``peak-assigned" ($1-f_\mathrm{peak}$ of the fiber-collided pairs).
-The resulting mock catalog has $f_\mathrm{peak}$ fewer galaxies with $w_\mathrm{cp} > 1$ compared to the fiber-collided mock catalogs with nearest-neighbor weights that we started from; however, the total statistical weight ($\sum_\mathrm{gal} w_\mathrm{tot}$) of the mock catalog is conserved.
+We keep the nearest-neighbor fiber collision weights imposed in the beginning for the remaining fiber collided pairs that are not ``peak-assigned" ($1-f_\mathrm{peak}$ of the fiber collided pairs).
+The resulting mock catalog has $f_\mathrm{peak}$ fewer galaxies with $w_\mathrm{cp} > 1$ compared to the fiber collided mock catalogs with nearest-neighbor weights that we started from; however, the total statistical weight ($\sum_\mathrm{gal} w_\mathrm{tot}$) of the mock catalog is conserved.
 
@@
 Using simulated mock catalogs for SDSS data with realistically imposed fiber collisions, we quantify the systematic effects of fiber collisions on galaxy clustering measurements - in particular the power spectrum.
-Although fiber collisions have little significant effect on the power spectrum at large scales, its effect quickly overtakes the sample variance at scales smaller than $k > 0.1 \;h/\mathrm{Mpc}$.
-At the smallest scales that we explore in this paper, $k \sim 0.3$, fiber collisions have over a $10 \%$ effect on the power spectrum.
+Although fiber collisions have little significant effect on the power spectrum at large scales, their effect quickly overtakes the sample variance at scales smaller than $k > 0.1 \;h/\mathrm{Mpc}$.
+At the smallest scales that we explore in this paper, $k \sim 0.3  \;h/\mathrm{Mpc}$, fiber collisions have over a $10 \%$ effect on the power spectrum.
 Consequently at these small scales, measurements of the power spectrum is dominated by the uncertainties from systematic effects of fiber collisions.
 
-Fortunately, through the fiber-collided mock catalogs used in this paper, we are able to model the distribution of the line-of-sight displacement between fiber-collided pairs.
-Using this model, we are able to statistically reconstruct the clustering fiber-collided galaxies that reside in the same halo.
-Combining this correction with a modification of the shot-noise term in the power spectrum estimator to properly account for the discreteness added by the nearest-neighbor weights of chance aligned fiber-collided pairs, we devise a new fiber collision correction method that is able to reconstruct the true power spectrum from fiber-collided data even to $k \sim 0.3 \;h/\mathrm{Mpc}$.
+Fortunately, using the fiber collided mock catalogs used in this paper, we are able to model the distribution of the line-of-sight displacement between fiber collided pairs.
+With this model, we are able to statistically reconstruct the clustering fiber collided galaxies that reside in the same halo.
+Combining this correction with a modification of the shot-noise term in the power spectrum estimator to properly account for the discreteness added by the nearest-neighbor weights of chance aligned fiber collided pairs, we devise a new fiber collision correction method that is able to reconstruct the true power spectrum from fiber collided data even to $k \sim 0.3 \;h/\mathrm{Mpc}$.
 Throughout the entire $k$ range explored in our analysis, our correction method reconstructs $P_\mathrm{true}(k)$ safely within the sample variance.
@@
 Furthermore, while the correction method of \cite{Gil-Marin:2014aa} is comparable our correction method, the parameter $x_\mathrm{PS}$ used in the method is calculated solely through a weighted galaxy mock catalog.
-As an added advantage, our correction method can also be validated by the observed data rather than only through the mock catalogs.
+As an added advantage, our correction method can also be callibrated by the observed data rather than only through the mock catalogs.
 Therefore our correction method does not depend on the accuracy of the mock catalogs, thereby making it's application to observations further reliable.

### 2015-12-17 fc_paper/fc_paper.tex
Some structural edits to the paper. Need to work on content.

@@
 %define general packages
+\usepackage{color}
 \usepackage{epsfig}
@@
 \usepackage{courier}
+
+\newcommand{\todo}[1]{{\bf \textcolor{red}{ #1}}}
+%\newcommand\todo[1]{{\color{red}#1}}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Accounting for Fiber Collisions} \label{sec:fc_corr}
+\section{Fiber Collision Methods} \label{sec:fc_corr}
 %Although the nearest-neighbor method provides a reasonable estimate at large scales, in Section \ref{sec:fc_pk} we demonstrate that at small scales its effects on the power spectrum are significant and dominate sample variance.
@@
 \ref{eq:roman_p2k}.
-\begin{itemize}
-	\item Description of Figure \ref{fig:fc_pk} focusing on the scales where the NN method breaks down and quantifying the residuals. 
-\end{itemize}
+\todo{Description of Figure \ref{fig:fc_pk} focusing on the scales where the NN method breaks down and quantifying the residuals.}
 
@@
 \includegraphics[scale=0.575]{fcpaper_dlos_dist.png}
-\caption{Normalized distribution of $d_{\mathrm{LOS}}$ for LasDamas (\ldgcolor), QPM (\qpmcolor), and Tiling Mock (\tmcolor) mock catalogs.
+\caption{\todo{bin CMASS with wider bins}Normalized distribution of $d_{\mathrm{LOS}}$ for LasDamas (\ldgcolor), QPM (\qpmcolor), and Tiling Mock (\tmcolor) mock catalogs.
 The normalized $d_{\mathrm{LOS}}$ distribution of BOSS DR12 is also plotted (\cmasscolor).
@@
 \subsection{First Method} \label{sec:dlospeak}
+\todo{Come up with better title for subsection}
 % LOS DISPLACEMENT %%%%
@@
 It is impossible to determine definitely from observed galaxy data whether individual fiber collided galaxies without resolved spectroscopic redshift are correlated or chance alignments.
-Fortunately, using the fiber collided pairs with resolved redshifts (mainly in the overlapping regions mentioned in Section \ref{sec:catalog}), it is possible to model the line-of-sight displacement of the fiber collided pairs and measure the fraction of pairs that are corrected and uncorrelated.
+Fortunately, using the fiber collided pairs with resolved redshifts (mainly in the overlapping regions mentioned in Section \ref{sec:catalog}), it is possible to model the line-of-sight displacement of the fiber collided pairs and measure the fraction of pairs that are correlated and uncorrelated.
 
@@
 Redshift values are provided for all galaxies regardless of angular proximity and the fiber collisions imposed on the mock catalogs are represented through the galaxies' ``fiber collision weights" ($w_\mathrm{fc}$).
-So in a situation where only two galaxies are within the fiber collision angular scale, one galaxy (``the nearest neighbor") will have the fiber collision weight of both galaxies ($w_{\mathrm{fc}} = 2$), while the other has $w_\mathrm{fc} = 0$.
+For example, in a situation where only two galaxies are within the fiber collision angular scale, the NN method assigns one galaxy (``the nearest neighbor") the fiber collision weight of both galaxies ($w_{\mathrm{fc}} = 2$), while the other has $w_\mathrm{fc} = 0$.
 Nonetheless, since we actually have redshifts of both fiber-collided pair galaxies in mock catalogs, we can model the correlated and uncorrelated fiber-collided pairs in order to better understand the effects of fiber collisions.
@@
 
-After calculating the $d_{\mathrm{LOS}}$ for every fiber collided pairs, in Figure \ref{fig:d_los} we present the distribution of $d_{\mathrm{LOS}}$ for LasDamas (\ldgcolor), QPM (\qpmcolor), Tiling Mock (\tmcolor), and BOSS DR12 (\cmasscolor).
-All of the $d_{\mathrm{LOS}}$ distributions contain two components: a peak roughly contained within the range $-20\;\mathrm{Mpc} < d_{\mathrm{LOS}} < 20\;\mathrm{Mpc}$ and a flat component (hereafter "tail" component) outside the peak that extends to $d_{\mathrm{LOS}} \sim \pm 500 \;\mathrm{Mpc}$ (entire range of the distribution not displayed in Figure \ref{fig:d_los}).
+After calculating the $d_{\mathrm{LOS}}$ for every fiber collided pairs, in Figure \ref{fig:d_los} we present the distribution of $d_{\mathrm{LOS}}$ for \todo{LasDamas (\ldgcolor), QPM (\qpmcolor), Tiling Mock (\tmcolor), and BOSS DR12 (\cmasscolor)}.
+All of the $d_{\mathrm{LOS}}$ distributions contain two components: a peak roughly contained within the range $-20\;\mathrm{Mpc} < d_{\mathrm{LOS}} < 20\;\mathrm{Mpc}$ and a flat component (hereafter "tail" component) outside the peak that extends to $d_{\mathrm{LOS}} \sim \pm 500 \;\mathrm{Mpc}$.
+The entire range of the distribution is not displayed in Figure \ref{fig:d_los}.
 For the BOSS data, since we cannot compute the $d_\mathrm{LOS}$ for fiber collided pairs without spectra, the $d_\mathrm{LOS}$ distribution only reflects the $d_\mathrm{LOS}$ from fiber collided pairs {\em with} resolved spectroscopic redshifts, mostly from tile overlapping regions of the BOSS survey.
@@
 %    \bigskip 
-{\bf Notes}: Best-fit parameter $\sigma$ (Eq. \ref{eq:peak}) and peak fraction $f_{\mathrm{peak}}$ (Eq. \ref{eq:fpeak}) for the $d_{\mathrm{LOS}}$ distributions in Figure \ref{fig:d_los}. 
+{\bf Notes}: \todo{update this table} Best-fit parameter $\sigma$ (Eq.
+\ref{eq:peak}) and peak fraction $f_{\mathrm{peak}}$ (Eq.
+\ref{eq:fpeak}) for the $d_{\mathrm{LOS}}$ distributions in Figure \ref{fig:d_los}.
+\smallskip
 \end{table}
@@
 Rather than placing the fiber collided galaxy on top of its nearest angular neighbor as the NN correction does, placing the fiber collided galaxy at a displacement, sampled from the $d_{\mathrm{LOS}}$ distribution, apart from its nearest neighbor better accounts for the small scale in clustering measurements.
+However,
 
@@
 We refer to this method as ``$d_\mathrm{LOS}$-peak".
+
+\todo{Instead of describing dLOS peak only, describe how "peak-assigned" galaxies are determined. Then transition to the shot noise correction term}.
+
+In Section \ref{sec:dlos} we derive a method to better statistically reconstruct the clustering of correlated fiber collided pairs using using the peak of the $d_\mathrm{LOS}$ distribution.
+Then in Section \ref{sec:shotnoise} we presented our formulation of the shot-noise correction term, which accounts for the added discreteness from chance aligned fiber collision pairs.
+We now combine these two methods and present our fiber collision correction method.
+
+We begin once again with the fiber collided mock catalogs with the nearest-neighbor weights that accurately imitate the effects of fiber collision on the actual observed BOSS data.
+Then as described in Section \ref{sec:dlos}, we calculate the $d_\mathrm{LOS}$ distribution of all fiber collided pairs in each mock catalog.
+From the $d_\mathrm{LOS}$ distribution, we compute the fraction of fiber collided pairs within the peak of the distribution ($f_\mathrm{peak}$; Section \ref{sec:dlos}).
+We then select $f_\mathrm{peak}$ of the fiber collided pairs and designate them as correlated pairs that lie within the peak of the $d_\mathrm{LOS}$ distribution.
+We refer to these fiber collided pairs as ``peak-assigned" pairs.
+
+Each of these ``peak-assigned" pairs, by the nearest-neighbor weights, consist of a galaxy with $w_\mathrm{fc} > 1$ (the ``nearest-neighbor" galaxy) and another with $w_\mathrm{fc} = 0$ (the ``collided" galaxy).
+We disregard the collided galaxy.
+For each of the nearest-neighbor galaxies, we sample a value $d_\mathrm{peak-assigned}$ from the Gaussian best-fit to the $d_\mathrm{LOS}$ distribution peak and place a galaxy with $w_\mathrm{fc} = 1$ at a comoving distance $d_\mathrm{peak-assigned}$ away from the nearest-neighbor galaxy.
+At the same time, we reduce $w_\mathrm{fc}$ of the nearest-neighbor galaxy (the one that was originally up-weighted) by $1$.
+This process is repeated until the nearest-neighbor galaxy has $w_\mathrm{fc} =1$ in the case of triplets or higher.
+
+We keep the nearest-neighbor fiber collision weights imposed in the beginning for the remaining fiber collided pairs that are not ``peak-assigned" ($1-f_\mathrm{peak}$ of the fiber collided pairs).
+The resulting mock catalog has $f_\mathrm{peak}$ fewer galaxies with $w_\mathrm{cp} > 1$ compared to the fiber collided mock catalogs with nearest-neighbor weights that we started from; however, the total statistical weight ($\sum_\mathrm{gal} w_\mathrm{tot}$) of the mock catalog is conserved.
+
+Next, we use the FKP estimator with the Eq.
+\ref{eq:ourshot} shot-noise correction term described in Section \ref{sec:shotnoise} to calculate the $P(k)$ for our $d_\mathrm{LOS}$-peak corrected mock catalogs.
+In Figure \ref{fig:peaksn}, we present the ratio of the $\overline{P(k)}$ computed using our fiber collision correction method over $\overline{P_\mathrm{true}(k)}$.
+To assess the merit of the fiber collision correction, we once again over-plot the sample variance of the mock catalogs.
+For LasDamas, at $k \sim 0.3 \; h/\mathrm{Mpc}$, $P(k)/P_\mathrm{true}(k) - 1 \sim 0.5 \%$ and throughout the $k$ range, $0.3 \% < P(k)/P_\mathrm{true}(k) - 1 < 1.3 \%$.
+For QPM, at $k \sim 0.3 \; h/\mathrm{Mpc}$, $P(k)/P_\mathrm{true}(k) - 1 \sim 0.04 \%$ and throughout the $k$ range, $0.3 \% < P(k)/P_\mathrm{true}(k) - 1 < 1.3 \%$.
+{\bf include numbers here when Ngrid=960 is done}.
+Moreover for the mock catalogs with sample variance measurements (LasDamas and QPM), the $P(k)$ ratio is significantly below the sample variance throughout the entire $k$ range probed and even at $k\sim 0.3\;h/\mathrm{Mpc}$.
 
@@
 \subsection{Shot Noise Correction} \label{sec:shotnoise} 
+\todo{Discuss the different shot-noise correction considerations in the literature}
 Both the NN method and the $d_\mathrm{LOS}$-peak correction do not sufficiently account for the systematic effects of fiber collisions in the power spectrum.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Fourier Tophat Method 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Second Method} \ref{sec:fourier}
+\begin{itemize}
+\item \todo{Figure of 2PCF that demonstrates a pretty clear tophat} 
+\item \todo{The ultimate equations for calculating the tophat convolution}
+\item \todo{Polynomials estimations of the integral?}
+\item \todo{Figures of the fourier tophat method in action}
+\end{itemize}
+
 \begin{figure*}
@@
 \section{Results} \label{sec:results}
-\subsection{fiber collision Correction Method} \label{sec:apply}
-In Section \ref{sec:dlos} we derive a method to better statistically reconstruct the clustering of correlated fiber collided pairs using using the peak of the $d_\mathrm{LOS}$ distribution.
-Then in Section \ref{sec:shotnoise} we presented our formulation of the shot-noise correction term, which accounts for the added discreteness from chance aligned fiber collision pairs.
-We now combine these two methods and present our fiber collision correction method.
-
-We begin once again with the fiber collided mock catalogs with the nearest-neighbor weights that accurately imitate the effects of fiber collision on the actual observed BOSS data.
-Then as described in Section \ref{sec:dlos}, we calculate the $d_\mathrm{LOS}$ distribution of all fiber collided pairs in each mock catalog.
-From the $d_\mathrm{LOS}$ distribution, we compute the fraction of fiber collided pairs within the peak of the distribution ($f_\mathrm{peak}$; Section \ref{sec:dlos}).
-We then select $f_\mathrm{peak}$ of the fiber collided pairs and designate them as correlated pairs that lie within the peak of the $d_\mathrm{LOS}$ distribution.
-We refer to these fiber collided pairs as ``peak-assigned" pairs.
-
-Each of these ``peak-assigned" pairs, by the nearest-neighbor weights, consist of a galaxy with $w_\mathrm{fc} > 1$ (the ``nearest-neighbor" galaxy) and another with $w_\mathrm{fc} = 0$ (the ``collided" galaxy).
-We disregard the collided galaxy.
-For each of the nearest-neighbor galaxies, we sample a value $d_\mathrm{peak-assigned}$ from the Gaussian best-fit to the $d_\mathrm{LOS}$ distribution peak and place a galaxy with $w_\mathrm{fc} = 1$ at a comoving distance $d_\mathrm{peak-assigned}$ away from the nearest-neighbor galaxy.
-At the same time, we reduce $w_\mathrm{fc}$ of the nearest-neighbor galaxy (the one that was originally up-weighted) by $1$.
-This process is repeated until the nearest-neighbor galaxy has $w_\mathrm{fc} =1$ in the case of triplets or higher.
-
-We keep the nearest-neighbor fiber collision weights imposed in the beginning for the remaining fiber collided pairs that are not ``peak-assigned" ($1-f_\mathrm{peak}$ of the fiber collided pairs).
-The resulting mock catalog has $f_\mathrm{peak}$ fewer galaxies with $w_\mathrm{cp} > 1$ compared to the fiber collided mock catalogs with nearest-neighbor weights that we started from; however, the total statistical weight ($\sum_\mathrm{gal} w_\mathrm{tot}$) of the mock catalog is conserved.
-
-Next, we use the FKP estimator with the Eq.
-\ref{eq:ourshot} shot-noise correction term described in Section \ref{sec:shotnoise} to calculate the $P(k)$ for our $d_\mathrm{LOS}$-peak corrected mock catalogs.
-In Figure \ref{fig:peaksn}, we present the ratio of the $\overline{P(k)}$ computed using our fiber collision correction method over $\overline{P_\mathrm{true}(k)}$.
-To assess the merit of the fiber collision correction, we once again over-plot the sample variance of the mock catalogs.
-For LasDamas, at $k \sim 0.3 \; h/\mathrm{Mpc}$, $P(k)/P_\mathrm{true}(k) - 1 \sim 0.5 \%$ and throughout the $k$ range, $0.3 \% < P(k)/P_\mathrm{true}(k) - 1 < 1.3 \%$.
-For QPM, at $k \sim 0.3 \; h/\mathrm{Mpc}$, $P(k)/P_\mathrm{true}(k) - 1 \sim 0.04 \%$ and throughout the $k$ range, $0.3 \% < P(k)/P_\mathrm{true}(k) - 1 < 1.3 \%$.
-{\bf include numbers here when Ngrid=960 is done}.
-Moreover for the mock catalogs with sample variance measurements (LasDamas and QPM), the $P(k)$ ratio is significantly below the sample variance throughout the entire $k$ range probed and even at $k\sim 0.3\;h/\mathrm{Mpc}$.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-12-31 fc_paper/fc_paper.tex
minor changes

--- 2015-12-15 fc_paper/fc_paper.tex
@@
 
-\title{Accounting for Fiber Collisions in the Galaxy Power Spectrum Measurements}
+\title{A Fiber Collision Correction Method for the BOSS Power Spectrum}
 
@@
 Roman~Scoccimarro\altaffilmark{1}, 
-Michael R.~Blanton\altaffilmark{1}, 
-moreauthors} 
+Michael R.~Blanton\altaffilmark{1}, others} 
 \altaffiltext{1}{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Place, New York, NY 10003; chh327@nyu.edu}
@@
 Fiber-fed multi-object spectroscopic surveys, with their ability to collect an unprecedented number of redshifts, dominate cosmological studies.
-However physical constraints, which limit these surveys from successfully collecting redshifts from galaxies too close to each other on the focal plane, ultimately lead to significant systematic effects on galaxy clustering measurements.
-Using simulated mock catalogs, extensively used in interpreting large-scale structure clustering results of the Sloan Digital Sky Survey, we investigate the effects of fiber collisions on the galaxy power spectrum monopole and quadrupole and compare methods currently used to correct for fiber collisions in the literature and assess their success in reconstructing the true power spectrum.
+However physical constraints limit these surveys from successfully collecting redshifts from galaxies that are too close to each other on the focal plane, which ultimately leads to significant systematic effects on galaxy clustering measurements.
+Using simulated mock catalogs, extensively used in interpreting large-scale structure clustering results of the Sloan Digital Sky Survey, we investigate the effects of fiber collisions on the galaxy power spectrum and compare the methods currently used to correct for fiber collisions in the literature and assess their success in reconstructing the true power spectrum.
 
-We present two methods to account for fiber collisions in the power spectrum.
-The first method statistically reconstructs the clustering of fiber collided galaxy pairs by modeling the distribution of the line-of-sight displacement between them using cases where both redshifts are obtained.
+We present our fiber collision correction method, which first statistically reconstructs the clustering of fiber collided pairs by modeling the distribution of the line-of-sight displacements between them using cases where both redshifts are obtained.
 The method properly accounts for fiber collisions in the shot-noise correction term of the power spectrum estimator.
-For the monopole, this method reproduces the true power spectrum monopole for the mock catalogs with residuals of $< 1\%$ at $k \sim 0.3 \; h/\mathrm{Mpc}$ and $< 10\%$ at $k \sim 0.8 \; h/\mathrm{Mpc}$ -- a significant improvement from existing correction methods, especially at small scales ($k > 0.1\; h/\mathrm{Mpc}$).
-In our second method, we model the effect of fiber collisions on the true galaxy power spectrum by Fourier transforming an analytical estimate of the effect of fiber collisions on the two-point correlation function.
-Using this method we are able to reproduce the power spectrum quadrupole with fiber collisions from the true power spectrum to within sample variance for $k < 0.6\;h/\mathrm{Mpc}$ ({\bf MADEUPNUMBER}).
-{\bf INCLUDE MORE NUMBERS}.
-With statistical uncertainty no longer dominating galaxy clustering measurements, the methods we present in accounting for fiber collisions will allow us to extend power spectrum measurements to smaller scales than previous possible.
-
-%We present our fiber collision correction method for the power spectrum monopole, which first statistically reconstructs the clustering of fiber-collided pairs by modeling the distribution of the line-of-sight displacements between them, and then properly accounts for fiber collisions in the shot-noise correction term of the power spectrum estimator.
-Using our method, we successfully reproduce the true power spectrum monopole for the mock catalogs with residuals of $< 1\%$ at $k \sim 0.3 \; h/\mathrm{Mpc}$ and $< 10\%$ at $k \sim 0.8 \; h/\mathrm{Mpc}$.
-Our comparisons to other correction methods demonstrate that our method most accurately reconstructs the true power spectrum from fiber-collided galaxy data especially at small scales ($k > 0.1\; h/\mathrm{Mpc}$), with the added advantage that our method can be validated and calibrated in observed data.
+Using our method, we successfully reproduce the true power spectrum for the mock catalogs with residuals of $< 1\%$ at $k \sim 0.3 \; h/\mathrm{Mpc}$ and $< 10\%$ at $k \sim 0.8 \; h/\mathrm{Mpc}$.
+Our comparisons to other existing correction methods demonstrate that our method most accurately reconstructs the true power spectrum from fiber collided galaxy data especially at small scales ($k > 0.1\; h/\mathrm{Mpc}$), with the added advantage that our method can be validated and calibrated in observed data.
+With statistical uncertainty no longer dominating galaxy clustering measurements, our correction method will allow us to extend power spectrum measurements to smaller scales than previously possible.
 \end{abstract}
@@
 \section{Introduction} 
-As of 2015, millions of redshifts to distance galaxies have been obtained through redshift surveys.
+As of 2015, millions of redshifts to distant galaxies have been obtained through redshift surveys.
 Cosmological measurements such as galaxy clustering statistics are no longer dominated by uncertainties from statistical precision, but from systematic effects of the measurements.
-These surveys, such as the 2dF Galaxy Redshift Survey (2dFGRS; \citealt{Colless:1999aa}) and the Sloan Digital Sky Survey III Baryon Oscillation Spectroscopic Survey (SDSS-III BOSS; \citealt{Anderson:2012aa, Dawson:2013aa}) and future surveys such as the Extended Baryon Oscillation Spectroscopic Survey (eBOSS; \citealt{Dawson:2015aa}), use fiber-fed spectrographs.
+These surveys, such as the 2dF Galaxy Redshift Survey (2dFGRS; \citealt{Colless:1999aa}) and the Sloan Digital Sky Survey III Baryon Oscillation Spectroscopic Survey (SDSS-III BOSS; \citealt{Anderson:2012aa, Dawson:2013aa}) and future surveys such as the Extended Baryon Oscillation Spectroscopic Survey (eBOSS; {\bf WHO DO CITE?}) use fiber-fed spectrographs.
 
 For each galaxy, a fiber is used to obtain a spectroscopic redshift.
-However, due to the physical size of the fiber housing, if two galaxies are located within the fiber collision angular scale from one another on the sky, separate fibers cannot be placed adjacently to observe them simultaneously (\citealt{Yoon:2008aa} {\bf CITE MORE?}).
-In these situations, the redshifts of only a single redshift is measured.
+However, due to the physical size of the fiber housing, if two galaxies are located within the fiber collision angular scale from one another on the sky, separate fibers cannot be placed adjacently to observe them simultaneously (\citealt{Yoon:2008aa} {\bf CITE MORE}).
+In these situations, only a single redshift is measured.
 With redshifts of galaxies in close angular proximities missing from the sample, any clustering statistic probing these scales will be systematically affected.
 
-As our cosmological surveys extend further to higher redshifts, the systematic effect becomes more severe, because the fiber collision angular scale corresponds to a larger comoving scale, thereby affecting our measurements on larger scales.
-SDSS-III BOSS, in particular, has an angular fiber collision scale of $62\arcsec$.
-This corresponds to $\sim 0.43 \;\mathrm{Mpc}/h$ at the center of the survey's redshift redshift range; fiber-collided galaxies account for $\sim 5\%$ of the galaxy sample (\citealt{Anderson:2012aa}).
-While this may seem like a relatively small fraction of redshifts, its effect on clustering measurements such as the power spectrum is significant and need be accounted for in order to probe smaller scales and higher order statistics such as the three-point correlation function or the bispectrum.
-Future spectroscopic surveys such as the Dark Energy Survey Instrument (DESI; \citealt{Schlegel:2011aa, Morales:2012aa, Makarem:2014aa}), will use robotic fiber positioner technology.
-Unfortunately this will only increase the effect of fiber collisions.
-Therefore, accounting for fiber collisions will be an unavoidable challenge for clustering statistics in the near future.
+As our cosmological surveys extend further to higher redshifts, the systematic effect becomes more severe because the fiber collision angular scale corresponds to a larger comoving scale, thereby affecting our measurements on larger scales.
+SDSS-III BOSS, in particular, has an angular fiber collision scale of $62''$.
+This corresponds to $\sim 0.4 \;\mathrm{Mpc}/h$ at the center of the survey's redshift redshift range; fiber collided galaxies account for $\sim 5\%$ of the galaxy sample (\citealt{Anderson:2012aa}).
+Although this accounts for a relatively small fraction of redshifts, its effect on clustering measurements such as the power spectrum is significant.
+They must to be accounted for to probe smaller scales and higher order statistics such as the three-point correlation function or the bispectrum.
+Even with the use of robotic fiber positioner technology in future surveys such as the Dark Energy Survey Instrument (DESI; \citealt{Schlegel:2011aa, Morales:2012aa, Makarem:2014aa}), the effects of collisions caused by the fiber positioners will need to be understood.
+Therefore, accounting for the systematic effects remains an unavoidable challenge for clustering statistics.
 
 To correct for fiber collisions, one common approach used in clustering statistics is the nearest neighbor method (\citealt{Zehavi:2002aa, Berlind:2006aa, Anderson:2012aa}).
-For fiber-collided galaxies without resolved redshifts, the method assigns the statistical weight of the fiber-collided galaxy to its nearest angular neighbor.
+For fiber collided galaxies without resolved redshifts, the method assigns the statistical weight of the fiber collided galaxy to its nearest angular neighbor.
 This provides a reasonable correction for the fiber collision effects at scales much larger than the fiber collision scales; however the correction falls short near the fiber collision scale.
@@
 While this shot-noise term adjustment has been calibrated within the mock catalogs used to interpret the BOSS clustering results there is no way to validate and calibrate these methods independently for observations.
-Methods of this kind rely entirely on the accuracy of the mock catalogs to constrain fiber collisions, which is especially concerning since fiber collisions systematically affect small scales and mock catalogs may not be reliable at such small scales (\citealt{Heitmann:2008aa, Schneider:2015aa}).
+Methods of this kind rely entirely on the accuracy of the mock catalogs to constrain fiber collisions, which is especially concerning since fiber collisions systematically affect small scales and mock catalogs may not be realiable at such small scales (\citealt{Heitmann:2008aa, Schneider:2015aa}).
 
 Recently \cite{Guo:2012aa}, focusing on SDSS-III BOSS like samples, proposed a fiber collision correction method for the 2PCF that is able to reasonably correct for fiber collisions above and below the collision scale.
-\cite{Guo:2012aa} estimates the total contribution of fiber-collided galaxies to the two point correlation function by examining the pair statistics in overlapping tiling regions of the survey, where a smaller fraction of galaxies suffer from fiber collisions.
-Unfortunately, applying this method to Fourier clustering measurements is intractable due to the complex geometry of the overlapping regions.
-As a result, we propose two methods to account for fiber collisions in power spectrum measurements.
-The first improves upon the nearest neighbor method by using the distribution of the line-of-sight displacement between resolved fiber collided galaxies to statistically reconstruct the clustering of fiber-collided galaxies; and properly accounts for fiber collisions in the shot-noise correction term of the power spectrum estimator.
-This method seeks to recover the true power spectrum from fiber collided galaxy catalogs.
-The second, on the other hand, uses the Fourier transform of an analytic estimate of the effect of fiber collisions in the 2PCF in order to model the effect of fiber collisions and reproduce the fiber collided power spectrum from the true power spectrum.
+\cite{Guo:2012aa} estimates the total contribution of fiber collided galaxies to the two point correlation function by examining the pair statistics in overlapping tiling regions of the survey, where a smaller fraction of galaxies suffer from fiber collisions.
+Unfortunately, due to the complex geometry of the overlapping regions, this method is difficult to apply to Fourier clustering measurements.
+As a result, we propose a fiber collision correction method that, first, improves upon the nearest neighbor method by using the distribution of the line-of-sight displacement between resolved fiber collided galaxies to statistically reconstruct the clustering of fiber collided galaxies; and properly accounts for fiber collisions in the shot-noise correction term of the power spectrum estimator.
 
-In Section \ref{sec:catalog}, we briefly describe the simulated mock catalogs with realistically applied fiber collisions and the power spectrum estimator used throughout the paper.
-We demonstrate the effects of fiber collisions on power spectrum measurements and compare correction methods in the literature in Section \ref{sec:fc_corr}.
-Afterwards we present our two methods of accounting for fiber collisions and then in Section \ref{sec:results} apply the methods to the mock catalogs.
+In Section \ref{sec:catalog}, we present a brief description of the simulated mock catalogs with realistically applied fiber collisions and the power spectrum estimator used throughout the paper.
+Then during our discussion of the two components of our correction method in Section \ref{sec:fc_corr}, we quantify the effects of fiber collisions of power spectrum measurements and test and compare correction methods in the literature.
+Afterwards, we present our correction method, test it on the mock catalogs, and compare it to other correction methods in Section \ref{sec:results}.
 Finally in Section \ref{sec:summary} we summarize and discuss our results.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Fiber-collided Mock catalogs
+% fiber collided Mock catalogs
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Fiber-collided Mock catalogs} \label{sec:catalog}
+\section{fiber collided Mock catalogs} \label{sec:catalog}
 For various purposes such as calculating covariance matrices or estimating cosmic variance, simulated mock catalogs play a crucial role in interpreting clustering measurements of observed galaxies (\citealt{Scoccimarro:2002aa, Anderson:2012aa, Manera:2013aa}).
@@
 A direct way of understanding the effects of fiber collisions on clustering statistics in observations is to first apply fiber collisions to mock catalogs and then compare the clustering statistics obtained from mock catalogs with and without the fiber collisions.
-Correction methods for fiber collisions can then be applied to the fiber-collided mocks and the merit of the correction method can be quantified by how successfully they reproduce the clustering statistics of the original mock catalogs without fiber collisions.
+Correction methods for fiber collisions can then be applied to the fiber collided mocks and the merit of the correction method can be quantified by how successfully they reproduce the clustering statistics of the original mock catalogs without fiber collisions.
 The optimal correction method can then be applied to the observed data with some assurance that it accounts for fiber collisions and improves the clustering measurements.
@@
 When applying the fiber collisions to the mock catalogs, it is essential to apply them in the same manner they affect the observational data.
-For BOSS, galaxies within $62\arcsec$ are fiber-collided (\citealt{Anderson:2012aa}).
+For BOSS, galaxies within $62"$ are fiber collided (\citealt{Anderson:2012aa}).
 In reality, this simple criteria is further complicated by the tiling scheme of observing plates that create overlapping regions, which have a higher success rate in resolving galaxy spectra within the fiber collision angular scale (\citealt{Guo:2012aa}).
@@
 Effects of fiber collisions must be understood and interpreted in conjunction with these other systematic effects.
-Therefore, in this paper, we use LasDamas (\citealt{McBride:2009aa, McBride:2011aa}), Quick Particle Mesh (\citealt{White:2014aa}), and Nseries ({\bf CITATION?}) catalogs, which have already been extensively used in interpreting clustering results for SDSS and BOSS and are generated through different prescriptions.
-Therefore they provide a robust sets of data to measure the effects of fiber collisions and to test our correction method tailored for BOSS.
+Therefore, in this paper, we use LasDamas (\citealt{McBride:2009aa, McBride:2011aa}), Quick Particle Mesh (\citealt{White:2014aa}), and Tiling mock catalogs ({\bf CITATIONS?}), which have already been extensively used in interpreting clustering results for SDSS and BOSS and are generated through different prescriptions.
+Therefore they provide unique data sets to measure the effects of fiber collisions and to test our correction method tailored for BOSS.
 %Each of these mock catalogs use some sort of N-body dark matter simulation along with a HOD prescription to populate the dark matter halos with ``galaxies".
@@
 
-The LasDamas Galaxy mock catalogs is constructed from the Oriana N-body Large Suite of Dark Matter Simulations (LasDamas) with $1280^3$ particles with a box with side length, $L_\mathrm{Box} = 2400\;\mathrm{Mpc}/h$.
-The N-body LasDamas simulations uses a spatially flat $\Lambda$CDM cosmology with $\Omega_\mathrm{m} = 0.25$, $\Omega_\Lambda = 0.75$, $\Omega_\mathrm{b} = 0.04$, $\sigma_8 = 0.8$, $n_\mathrm{s} = 1$ and $h=0.7$.
+The LasDamas Galaxy mock catalogs are constructed from the Oriana N-body Large Suite of Dark Matter Simulations (LasDamas) with $1280^3$ particles with a box with side length, $L_\mathrm{Box} = 2400\;\mathrm{Mpc}/h$.
+The N-body LasDamas simulations use a spatially flat $\Lambda$CDM cosmology with $\Omega_\mathrm{m} = 0.25$, $\Omega_\Lambda = 0.75$, $\Omega_\mathrm{b} = 0.04$, $\sigma_8 = 0.8$, $n_\mathrm{s} = 1$ and $h=0.7$.
 The dark matter halos are then identified using a friends-of-friends (FOF) algorithm (\citealt{Davis:1985aa}) with a linking length $b = 0.2 $ times the mean interparticle separation.
@@
 The HOD prescription is specified so that the galaxy mock catalogs reproduce the galaxy number density and projected correlation function of the observed SDSS Luminous Red Galaxy sample with $M_g < -21.8$.
-The LasDamas galaxy mock catalogs have 40 realizations each of which spans the redshift range, $0.16 < z < 0.44$ and are restricted to the survey geometry of SDSS Data Release 7.
+The LasDamas galaxy mock catalogs have 40 realizations, each of which spans the redshift range, $0.16 < z < 0.44$ and are restricted to the survey geometry of SDSS Data Release 7.
 They also include redshift space distortions from velocities, but do not model fiber collisions.
 
-To model the fiber collisions of the observed galaxies in BOSS, we impose fiber collisions at the angular scale of $62\arcsec$.
-Once we identify galaxies within $62\arcsec$ of each other, we arbitrary select one of the galaxies and assign the statistical weights of the other galaxies within $62\arcsec$ of it.
+To model the fiber collisions of the observed galaxies in BOSS, we impose fiber collisions at the angular scale of $62''$.
+Once we identify galaxies within $62''$ of each other, we arbitrary select one of the galaxies and assign the statistical weights of the other galaxies within $62''$ of it.
 Roughly $\sim 2.5 \%$ of the galaxies in the LasDamas mock catalogs are affected by fiber collisions.
@@
 The mock galaxy sample is then trimmed to the BOSS CMASS survey footprint, downsampled based on angular sky completeness (sector completeness) and radial selection.
-Furthermore, QPM mocks model the fiber collisions of the BOSS CMASS sample ($62\arcsec$ angular fiber collision scale).
+Furthermore, QPM mocks model the fiber collisions of the BOSS CMASS sample ($62''$ angular fiber collision scale).
 The QPM galaxy mock catalog uses the following $\Lambda$CDM cosmology: $\Omega_\mathrm{m} = 0.29$, $\Omega_\Lambda = 0.71$, $\sigma_8 = 0.8$, $n_\mathrm{s} = 0.97$ and $h=0.7$.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Powerspectrum Estimator
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Power Spectrum Estimator} \label{sec:pk_est}
-In this paper, we focus on the effects of fiber collisions on the galaxy power spectrum out of the other clustering measurements, more specifically the monopole and quadrupole of the power spectrum.
-Throughout the paper, when we measure the power spectrum we use the estimator described in \cite{Scoccimarro:2015aa} and the formalism therein.
-To reiterate Section III.
-A.
-in \cite{Scoccimarro:2015aa}, we calculate the monopole component of the power spectrum using:
-\begin{equation}\label{eq:roman_p0k}
-\widehat{P_0}(k) = \frac{1}{I_{22}} \left[ \int \frac{d\Omega_k}{4 \pi} |F_0({\bf k})|^2 - N_0 \right]
+In this paper, we focus on the effects of fiber collisions on the galaxy power spectrum out of the other clustering measurements.
+Throughout the paper, when we measure the power spectrum, we use the standard \cite{Feldman:1994aa} (hereafter FKP) estimator and the following formalisms from the FKP paper:
+\begin{equation} \label{eq:fkppk}
+P({\bf k}) = <|F({\bf k})|^2> - \frac{(1+\alpha) \int d^3r \;\bar{n}({\bf r})w_{\mathrm{FKP}}^2({\bf r})} {\int d^3r \; \bar{n}^2({\bf r})w_{\mathrm{FKP}}^2({\bf r})},
 \end{equation}  
@@
 \begin{equation}
-F_0({\bf k}) = \left( \sum_{j = 1}^{N_g} - \alpha \sum_{j=1}^{N_r} \right) w_j\;e^{i {\bf k}\cdot{\bf x}_j}
+F({\bf r}) = \frac{w_\mathrm{FKP}({\bf r}) [n_g({\bf r}) - \alpha n_r({\bf r})]} {[\int d^3r \; \bar{n}^2({\bf r})w_\mathrm{FKP}^2({\bf r})]^{\frac{1}{2}}} 
 \end{equation}
-with standard normalization constant
-\begin{equation} \label{eq:i22}
-I_{22} = \alpha \sum^{N_g}_{j=1} \bar{n}({\bf x}_j)w_j^2
+and the second term represents the constant shot-noise contribution to the power due to the discrete density field of our galaxies.
+$n_g$ is the galaxy density, $n_r$ is the density of the synthetic random catalog, $\alpha$ is the ratio of the number of galaxies over the number of synthetic random galaxies, $\bar{n}$ is the mean density of the galaxies, and $w_{\mathrm{FKP}}$ is the minimum variance weight derived in \cite{Feldman:1994aa}:
+\begin{equation}
+w_{\mathrm{FKP}} ({\bf r}) = \frac{1}{1+\bar{n}({\bf r}) P_0}
 \end{equation}
-and shot noise term
-\begin{equation} \label{eq:roman_shotnoise}
-N_0 = \left( \sum_{j = 1}^{N_g} - \alpha^2 \sum_{j=1}^{N_r} \right) w_j^2. 
-\end{equation}
-$N_0$ represents the constant shot noise contribution to the power due to the discrete density field of our galaxies.
-$\alpha$ is the ratio of the number of galaxies ($N_g$) over the number of synthetic random galaxies ($N_r$), $\bar{n}({\bf x})$ is the mean density of the galaxies at position ${\bf x}$, and $w_j$ is weight of each object, which includes the the minimum variance weight derived in \cite{Feldman:1994aa}:
-\begin{equation}
-w_{\mathrm{FKP}} ({\bf x}_j) = \frac{1}{1+\bar{n}({\bf x}_j) P_0}
-\end{equation}
-where $P_0$ is the power spectrum amplitude at which the error is minimized.
-We use $P_0 = 20000\; \mathrm{Mpc}^3/h^3$ for our analysis, which corresponds to $k \sim 0.1\; h/\mathrm{Mpc}$.
-We note that the shot noise term in Eq.
-\ref{eq:roman_shotnoise} differs from the standard shot noise term from \cite{Feldman:1994aa}, which uses $N_0^\mathrm{FKP} = \alpha (1+\alpha) \sum^{N_r}_{j=1} w_j^2.
-$The difference between shot noise formulations will be discussed further in Section \ref{sec:shotnoise}.
+where $P_0$ is the power spectrum amplitude at which the error is minimized. We use $P_0 = 20000\; \mathrm{Mpc}^3/h^3$ for our analysis, which corresponds to $k \sim 0.1\; h/\mathrm{Mpc}$.
 
-For the quadrupole, 
-\begin{equation}\label{eq:roman_p2k}
-\widehat{P_2}(k) = \frac{5}{I_{22}} \int \frac{d\Omega_k}{4 \pi} F_2({\bf k}) F_0^*({\bf k})
-\end{equation}
-where 
-\begin{equation}
-F_2({\bf k}) = \frac{3}{2}\hat{k}_a\hat{k}_b Q^{ab}({\bf k}) - \frac{1}{2} F_0({\bf k})
-\end{equation}
-with 
-\begin{equation}
-Q^{ab}({\bf k}) = \left( \sum_{j = 1}^{N_g} - \alpha \sum_{j=1}^{N_r} \right) \hat{x}_j^a\hat{x}_j^b w_j \;e^{i {\bf k}\cdot{\bf x}_j}
-\end{equation}
-
-% P(k) plot for mocks and BOSS
 \begin{figure}
@@
 \includegraphics[scale=0.5]{fcpaper_pk_comp.png} 
-\caption{Average power spectrum monopole $\overline{P_0(k)}$ and quadrupole $\overline{P_2(k)}$ for BOSS DR12 (black) and the mock catalogs LasDamas (blue), QPM (orange), and Tiling Mock (green), listed in Section \ref{sec:catalog} using the estimator from \cite{Scoccimarro:2015aa}.
-The width of the $P_{l}(k)$ for LasDamas and QPM represent the sample variance ($\Delta P_{l}(k)$) calculated from the realizations of the mock catalogs.
-We emphasize that fiber collisions were not applied to the mock catalogs for the measurements above.
-Meanwhile, galaxy weights (Equation \ref{eq:weight}) are applied to the BOSS DR12 $P_l(k)$ measurements.
+\caption{Average power spectrum $\overline{P(k)}$ for BOSS DR12 (black) and the mock catalogs LasDamas (blue), QPM (orange), and Tiling Mock (green), listed in Section \ref{sec:catalog} using the FKP $P(k)$ estimator.
+The width of the $P(k)$ for LasDamas and QPM represent the sample variance ($\Delta P(k)$) calculated from the multiple realizations of the mock catalogs.
+We emphasize that fiber collisions were not applied to the mock catalogs for the $P(k)$ measurements.
+Meanwhile, galaxy weights (Equation \ref{eq:weight}) are applied to the BOSS DR12 $P(k)$ measurement.
 We remind readers that the LasDamas mock catalog has an overall greater $\overline{P(k)}$ due to the fact that the catalog spans the SDSS LRG sample redshift range instead of the BOSS redshift range of the other mock catalogs.} \label{fig:mockpk}
@@
 
-In Figure \ref{fig:mockpk}, we plot the $P_0(k)$ and $P_2(k)$ calculated using Eq.
-\ref{eq:roman_p0k} and Eq.
-\ref{eq:roman_p2k}, respectively, for LasDamas, QPM, and Tiling mock catalogs.
-The fiber collisions described previously are not applied to the mock catalogs in the $P(k)$ calculations.
-Without fiber collisions, the weights of the objects is equivalent to the FKP weights, $w_j = w_{j,\mathrm{FKP}}$.
+For LasDamas, QPM, and Tiling mock catalogs we use the FKP estimator described above to measure the power spectrum in Figure \ref{fig:mockpk}.
+The fiber collisions described previously are not applied to the mock catalogs in the $P(k)$ calculations for Figure \ref{fig:mockpk}.
+Without fiber collisions, we use the exact formulation of Equation \ref{eq:fkppk} in the FKP power spectrum estimator.
 
-We also plot the $P_0(k)$ and $P_2(k)$ from the BOSS Data Release 12 CMASS data (\cmasscolor) in Figure \ref{fig:mockpk}.
+We also plot the $P(k)$ from the BOSS Data Release 12 CMASS data (\cmasscolor) in Figure \ref{fig:mockpk}.
 For BOSS DR12 CMASS, systematic weights are assigned to the galaxies in order to account for sector completeness, redshift failures, and fiber collisions.
@@
 \end{equation} 
-(\citealt{Anderson:2012aa, Beutler:2014aa}), which are included in the object weights $w_j$ along with $w_{j, \mathrm{FKP}}$.
-The statistical weights are also included in the factor $\alpha$.
-So for the BOSS $P_0(k)$ and $P_2(k)$ calculations, $w_j = w_{j, \mathrm{tot}} \times w_{j, \mathrm{FKP}}$ and $\alpha' = \sum_{j=1}^{N_g} w_\mathrm{tot} / N_r$.
+(\citealt{Anderson:2012aa, Beutler:2014aa}).
+As a result, we modify Equation \ref{eq:fkppk} when we calculate the power spectrum.
+Instead of the galaxy density term $n_g({\bf r})$ we use a weighted galaxy density term $n'_g({\bf r}) = n_g({\bf r}) w({\bf r})$, which includes the systematic weights for each galaxy.
+Also, instead of $\alpha = N_{\mathrm{gal}}/N_\mathrm{ran}$ we use $\alpha ' = N'_\mathrm{gal}/N_\mathrm{ran}$ where $N'_\mathrm{gal} = \sum_\mathrm{gal} w_\mathrm{tot}$.
 
-Furthermore, for the mock catalogs with multiple realizations (LasDamas, QPM and Nseries), we compute the sample variance of the power spectrum monopole and quadrupole
+For LasDamas and QPM, which have multiple realizations, we compute the sample variance of the power spectrum
 \begin{equation} \label{eq:pk_var}
-\Delta P_l (k)= \sqrt{\frac{1}{N_\mathrm{mocks}} \sum\limits_{i=1}^{N_\mathrm{mocks}} (P^i_l(k)- \overline{P_l(k)})^2 }\;\; (l= 0, 2). 
+\Delta P (k)= \sqrt{\frac{1}{N_\mathrm{realization}} \sum\limits_i^{N_\mathrm{realization}} (P_i(k)- \overline{P(k)})^2 }. 
 \end{equation}
-$N_\mathrm{mock}$ is the total number of realizations (40 for LasDamas and 1000 for QPM) and $P^i_l(k)$ is the power spectrum ($l=0$ monopole, $l=2$ quadrupole) for each realization.
+$N_\mathrm{realization}$ is the total number of realizations (40 for LasDamas and 1000 for QPM) and $P_i(k)$ is the power spectrum for each realization.
 $\Delta P(k)$ is represented by the width of the $P(k)$ in Figure \ref{fig:mockpk}.
@@
 For galaxies without resolved spectroscopic redshifts due to fiber collisions, the entire statistical weight of the galaxy is assigned to its nearest angular neighbor.
-This method assumes that all galaxies within the angular fiber collision scale ($< 62 "$ for BOSS) are correlated with one another.
+This method effectively assumes that all galaxies within the angular fiber collision scale ($< 62 "$ for BOSS) are correlated with one another.
 In other words, the method assumes that galaxies within the fiber collision angular scale reside in the same halo so displacing one and placing it on top of the other does not significantly alter the clustering statistics.
-One consequence of this method however is that galaxies within the angular fiber collision scale purely by coincidence (hereafter referred to as ``chance alignments") are incorrectly assumed to be gravitationally correlated, so when their statistical weight is added to its nearest angular neighbor, they are in fact displaced significantly from its true position.
+One consequence of this method however is that galaxies within the angular fiber collision scale purely by coincidence (hereafter referred to as ``chance alignments") are incorrectly assumed to be gravitationally correlated, so when their statistical weight is added to its nearest angular neighbor, they are in fact displaced significantly from their true position.
 For BOSS, the nearest angular neighbor method can displace galaxies by up to $500 \;\mathrm{Mpc}$.
-Furthermore even for fiber-collided galaxies that reside in the same group or cluster, up-weighting the nearest neighbor ignores halo-scale line-of-sight displacements, which as we present in Section \ref{sec:dlos}, are significant.
+Furthermore even for fiber collided galaxies that reside in the same group or cluster, up-weighting the nearest neighbor ignores halo-scale line-of-sight displacements, which as we present in Section \ref{sec:dlos}, are significant.
 
 Although the nearest-neighbor method provides a reasonable estimate at large scales, in Section \ref{sec:dlos} we demonstrate that at small scales its effects on the power spectrum are significant and dominate sample variance.
-We present an improved method to account for correlated fiber-collided galaxies using the line-of-sight displacement between fiber-collided pairs.
+We present an improved method to account for correlated fiber collided galaxies using the line-of-sight displacement between fiber collided pairs.
 Then in Section \ref{sec:shotnoise}, we present modifications to the FKP power spectrum estimator in order to properly account for fiber collisions through the shot-noise correction term in the estimator.
+
+% MAKE SURE IT IS CLEAR THAT OUR CORRECTION METHOD COMBINES THE TWO.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Line-of-Sight Displacement of Fiber-collided Pairs} \label{sec:dlos}
-It is impossible to determine from observed galaxy data whether fiber-collided galaxies without resolved spectroscopic redshift are correlated or chance alignments.
-Fortunately, using the fiber-collided pairs with resolved redshifts (mainly in the overlapping regions mentioned in Section \ref{sec:catalog}), it is possible to model the line-of-sight displacement of the fiber-collided pairs and the fraction of galaxy pairs that are corrected and uncorrelated.
+\subsection{Line-of-Sight Displacement of fiber collided Pairs} \label{sec:dlos}
+It is impossible to determine definitely from observed galaxy data whether individual fiber collided galaxies without resolved spectroscopic redshift are correlated or chance alignments.
+Fortunately, using the fiber collided pairs with resolved redshifts (mainly in the overlapping regions mentioned in Section \ref{sec:catalog}), it is possible to model the line-of-sight displacement of the fiber collided pairs and the fraction of galaxy pairs that are corrected and uncorrelated.
 
-For simulated mock catalogs, described in Section \ref{sec:catalog}, modeling the fiber-collided galaxy pairs is a much more direct task since fiber collisions are post-processed after the simulated galaxy positions are generated.
+For simulated mock catalogs, described in Section \ref{sec:catalog}, modeling the fiber collided galaxy pairs is a much more direct task since fiber collisions are post-processed after the simulated galaxy positions are generated.
 All redshift values are provided for all galaxies regardless of angular proximity and the fiber collisions imposed on the mock catalogs are represented through the galaxies' ``fiber collision weights" ($w_\mathrm{fc}$).
-So for a fiber-collided pair, one galaxy (``the nearest neighbor") will have the fiber collision weight of both galaxies, while the other has $w_\mathrm{fc} = 0$.
-Nonetheless, with redshifts of both fiber-collided pair galaxies in mock catalogs, we can model the correlated and uncorrelated fiber-collided pairs in order to better correct for fiber collisions.
+So for a fiber collided pair, one galaxy (``the nearest neighbor") will have the fiber collision weight of both galaxies, while the other has $w_\mathrm{fc} = 0$.
+Nonetheless, with redshifts of both fiber collided pair galaxies in mock catalogs, we can model the correlated and uncorrelated fiber collided pairs in order to better correct for fiber collisions.
 
-To determine whether or not fiber-collided pairs are correlated, we examine the comoving line-of-sight displacement ($d_{\mathrm{LOS}}$) of fiber-collided galaxy pairs.
+To determine whether or not fiber collided pairs are correlated, we examine the comoving line-of-sight displacement ($d_{\mathrm{LOS}}$) of fiber collided galaxy pairs.
 We calculate the $d_{\mathrm{LOS}}$ by taking the difference of the line-of-sight comoving distance from the resolved redshifts:
@@
 \end{equation}
-where $N_{\mathrm{pairs}}$ is the total number of fiber-collided pairs.
-As mentioned above, this portion of fiber-collided pairs are galaxy pairs that are correlated.
+where $N_{\mathrm{pairs}}$ is the total number of fiber collided pairs.
+As mentioned above, this portion of fiber collided pairs are galaxy pairs that are correlated.
 We list the $f_{\mathrm{peak}}$ values for each of the data catalogs in Table \ref{tab:mpfit}.
@@
 By simply incorporating the peak of the $d_{\mathrm{LOS}}$ distribution, we are able to significantly improve clustering statistics on small scales.
-Rather than placing the fiber-collided galaxy on top of its nearest angular neighbor as NN correction does, placing the fiber-collided galaxy at a displacement sampled from the $d_{\mathrm{LOS}}$ distribution away from its nearest neighbor better accounts for the small scale in clustering measurements.
+Rather than placing the fiber collided galaxy on top of its nearest angular neighbor as NN correction does, placing the fiber collided galaxy at a displacement sampled from the $d_{\mathrm{LOS}}$ distribution away from its nearest neighbor better accounts for the small scale in clustering measurements.
 On mock catalogs, we test this by first applying the NN to the mock catalogs.
-We then sample a displacement $d_i$ from $p(d_\mathrm{LOS})$ (Equation \ref{eq:peak}) for each fiber-collided pair.
-Afterwards we ``place" the fiber-collided galaxy a distance $d_i$ from the nearest neighbor galaxy assign $w_\mathrm{fc} = 1$ and reduce the $w_\mathrm{fc}$ of the the nearest-neighbor by 1.
+We then sample a displacement $d_i$ from $p(d_\mathrm{LOS})$ (Equation \ref{eq:peak}) for each fiber collided pair.
+Afterwards we ``place" the fiber collided galaxy a distance $d_i$ from the nearest neighbor galaxy assign $w_\mathrm{fc} = 1$ and reduce the $w_\mathrm{fc}$ of the the nearest-neighbor by 1.
 We refer to this method as ``$d_\mathrm{LOS}$-peak".
@@
 The $d_\mathrm{LOS}$-peak correction is the first part of our correction method we present in this paper.
-Nonetheless, we test it by applying it to the mock catalogs and comparing the resulting power spectrums.
+We test it by applying it to the mock catalogs and comparing the resulting power spectrums.
 For each of the mock catalogs (LasDamas, QPM, and Tiling Mock) we use the FKP power spectrum estimator from Section \ref{sec:pk_est} to compute the power spectrums of the mock catalogs without fiber collisions, with fiber collisions corrected using NN method, and with fiber collisions corrected using the $d_\mathrm{LOS}$-peak correction.
 We note that both the NN and the $d_\mathrm{LOS}$-peak correction methods alter the redshift distribution of our samples by a negligible amount $< 1\%$.
-Therefore, the synthetic random catalogs and the $\bar{n}(z)$ values do not need to be adjusted in the FKP $P(k)$ calculations.
+Therefore, the synthetic random catalogs and the $\bar{n}(z)$ values do not need to be adjusted in the FKP $P(k)$ calculations in our case.
 
 Since we are interested in how well fiber collision correction methods can reproduce the power spectrum without fiber collisions (i.e.
-``true" power spectrum, unsullied by systematic effects), in Figure \ref{fig:peakonly} we plot the ratio of the average power spectrum $\overline{P(k)}$ (averaged over the realizations) computed from fiber-collided mock catalogs with corrections over the $\overline{P(k)}$ from the fiber collision-less original mock catalogs: $\overline{P_{\mathrm{corr}}(k)}/\overline{P_\mathrm{true}(k)}$.
+``true" power spectrum, unsullied by systematic effects), in Figure \ref{fig:peakonly} we plot the ratio of the average power spectrum $\overline{P(k)}$ (averaged over the realizations) computed from fiber collided mock catalogs with corrections over the $\overline{P(k)}$ from the fiber collision-less original mock catalogs: $\overline{P_{\mathrm{corr}}(k)}/\overline{P_\mathrm{true}(k)}$.
 The ratio for the NN method is plotted in blue while the ratio for the $d_{\mathrm{LOS}}$-peak correction is plotted in orange.
@@
 The $P(k)$s obtained from these methods are dominated by the systematic effects of fiber collisions on small scales.
-Although the $d_\mathrm{LOS}$-peak method improves upon the NN method by statistical reconstructing the clustering of correlated fiber-collided pairs within the peak of the $d_\mathrm{LOS}$ distribution, there is still room for improvement since the method does not yet properly account for chance alignments (uncorrelated fiber collision pairs).
+Although the $d_\mathrm{LOS}$-peak method improves upon the NN method by statistical reconstructing the clustering of correlated fiber collided pairs within the peak of the $d_\mathrm{LOS}$ distribution, there is still room for improvement since the method does not yet properly account for chance alignments (uncorrelated fiber collision pairs).
 Unfortunately, an extension of the $d_\mathrm{LOS}$-peak method to the entire $d_\mathrm{LOS}$ distribution range is not feasible because such a correction results in an overall reduction of the $P(k)$.
-This is caused by the statistical sampling of the $d_\mathrm{LOS}$, which would inevitably displace some fiber-collided pairs that are actually correlated pairs as chance alignments and the other way around.
-Therefore, in the following section we provide more robust correction method to account for the chance alignment fiber-collided pairs.
+This is caused by the statistical sampling of the $d_\mathrm{LOS}$, which would inevitably displace some fiber collided pairs that are actually correlated pairs as chance alignments and the other way around.
+Therefore, in the following section we provide more robust correction method to account for the chance alignment fiber collided pairs.
 
@@
 \ref{eq:ourshot} is equivalent to the shot-noise contribution from ``false pairs" in \cite{Gil-Marin:2014aa}.
-%In \cite{Gil-Marin:2014aa}, they justify the use of the two separate shot-noise terms with the argument that, if the fiber-collided pairs are true pairs it would not modify %insert reason 
+%In \cite{Gil-Marin:2014aa}, they justify the use of the two separate shot-noise terms with the argument that, if the fiber collided pairs are true pairs it would not modify %insert reason 
 %While the $P(k)$ using the \cite{Gil-Marin:2014aa} shot-noise term does in fact correct for fiber collisions significantly (below), since the parameter is determined in mock catalogs, the value cannot be validated in the actual BOSS data .
 
-In order to compare the different $P_\mathrm{shot}$ derivations, we apply each of them ($P^\mathrm{FKP}_\mathrm{shot}$, $P^\mathrm{Hahn+}_\mathrm{shot}$, $P^\mathrm{B2014}_\mathrm{shot}$ and $P^\mathrm{GM2014}_\mathrm{shot}$) to the fiber-collided mock catalogs with nearest-neighbor weights.
+In order to compare the different $P_\mathrm{shot}$ derivations, we apply each of them ($P^\mathrm{FKP}_\mathrm{shot}$, $P^\mathrm{Hahn+}_\mathrm{shot}$, $P^\mathrm{B2014}_\mathrm{shot}$ and $P^\mathrm{GM2014}_\mathrm{shot}$) to the fiber collided mock catalogs with nearest-neighbor weights.
 To clarify, $P^\mathrm{FKP}_\mathrm{shot}$, $P^\mathrm{Hahn+}_\mathrm{shot}$, $P^\mathrm{B2014}_\mathrm{shot}$ and $P^\mathrm{GM2014}_\mathrm{shot}$ are calculated using Eq.

### 2015-12-31 fc_paper/fc_paper.tex

--- 2015-12-17 fc_paper/fc_paper.tex
@@
 Future spectroscopic surveys such as the Dark Energy Survey Instrument (DESI; \citealt{Schlegel:2011aa, Morales:2012aa, Makarem:2014aa}), will use robotic fiber positioner technology.
-Unfortunately this will only increase the effect of fiber collisions.
-Therefore, accounting for fiber collisions will be an unavoidable challenge for clustering statistics in the near future.
+Unfortunately this will not resolve the issues caused by fiber collisions and the effects of collisions caused by the fiber positions will need to be understood.
+Therefore, accounting for fiber collisions remains an unavoidable challenge for clustering statistics in the near future.
 
